### 2018-07-03 main.tex
Initial ShareLaTeX Import

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2017
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2017}

%\usepackage{nips_2017}

% to compile a camera-ready version, add the [final] option, e.g.:
 \usepackage[final]{nips_2017}

%\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
% For citations
\usepackage{natbib}
\usepackage{amsthm}
% For algorithms
%\usepackage[algcompatible]{algpseudocode}
%\usepackage{algorithm}
%\usepackage{algorithmicx}
%\usepackage[noend]{algcompatible}
\usepackage[vlined,linesnumbered,ruled]{algorithm2e}
\usepackage{bbm}
\usepackage{amsfonts}
\usepackage{amsmath}           
\usepackage{mathtools}    
\usepackage{amsopn}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumerate}
%%%%%%%%%%%%%%%%%% toc 
\usepackage{scrwfile}
\TOCclone[\contentsname~(\appendixname)]{toc}{atoc}
\newcommand\StartAppendixEntries{}
\AfterTOCHead[toc]{%
  \renewcommand\StartAppendixEntries{\value{tocdepth}=-10000\relax}%
}
\AfterTOCHead[atoc]{%
  \edef\maintocdepth{\the\value{tocdepth}}%
  \value{tocdepth}=-10000\relax%
  \renewcommand\StartAppendixEntries{\value{tocdepth}=\maintocdepth\relax}%
}
\newcommand*\appendixwithtoc{%
  \cleardoublepage
  \appendix
  \addtocontents{toc}{\protect\StartAppendixEntries}
  \listofatoc
}
\usepackage{blindtext}
\usepackage{color}
%%%%%%%%%%%%%%%%%% toc

%%%%%%%%%%%%%%%% HEADER 
\newcommand{\EG}{\textsc{Epoch-Greedy}\xspace}
\newcommand{\EPG}{\textsc{$\epsilon$-Greedy}\xspace}
\newcommand{\minimonster}{\textsc{ILOVETOCONBANDITS}\xspace}
\newcommand{\ILTCB}{\textsc{ILTCB}\xspace}
\newcommand{\AdaEG}{\textsc{Ada-Greedy}\xspace}
\newcommand{\AdaILTCB}{\textsc{Ada-ILTCB}\xspace}
\newcommand{\AdaPE}{\textsc{Ada-PE}\xspace}
\newcommand{\corral}{\textsc{Corral}\xspace}
\newcommand{\bistro}{\textsc{BISTRO+}\xspace}
\newcommand{\base}[1]{{{\cal{B}}_{#1}}}
\newcommand{\scale}{\rho}
\newcommand{\FS}{\text{FS}}

\newcommand{\calA}{{\mathcal{A}}}
\newcommand{\calX}{{\mathcal{X}}}
\newcommand{\calS}{{\mathcal{S}}}
\newcommand{\calI}{{\mathcal{I}}}
\newcommand{\calJ}{{\mathcal{J}}}
\newcommand{\calK}{{\mathcal{K}}}
\newcommand{\calD}{{\mathcal{D}}}
\newcommand{\calE}{{\mathcal{E}}}
\newcommand{\calR}{{\mathcal{R}}}
\newcommand{\calT}{{\mathcal{T}}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\avgR}{\wh{\cal{R}}}
\newcommand{\ips}{\wh{r}}
\newcommand{\whpi}{\wh{\pi}}
\newcommand{\whE}{\wh{\E}}
\newcommand{\whV}{\wh{V}}
\newcommand{\Reg}{\text{\rm Reg}}
\newcommand{\whReg}{\wh{\text{\rm Reg}}}
\newcommand{\flg}{\text{\rm flag}}
\newcommand{\one}{\boldsymbol{1}}
\newcommand{\var}{\Delta}
\newcommand{\p}{\prime}
\newcommand{\nb}{\nabla}
\newcommand{\e}{\mathbf{e}}

\DeclareMathOperator*{\arginf}{arginf}
\DeclareMathOperator*{\argsup}{argsup}
\DeclareMathOperator*{\range}{range}
\DeclareMathOperator*{\mydet}{det_{+}}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\DeclarePairedDelimiter\bigabs{\big\lvert}{\big\rvert}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\DeclarePairedDelimiter\bigceil{\big\lceil}{\big\rceil}
\DeclarePairedDelimiter\bigfloor{\big\lfloor}{\big\rfloor}

\newcommand{\field}[1]{\mathbb{#1}}
\newcommand{\fY}{\field{Y}}
\newcommand{\fX}{\field{X}}
\newcommand{\fH}{\field{H}}
\newcommand{\fR}{\field{R}}
\newcommand{\fN}{\field{N}}
\newcommand{\E}{\field{E}}
\newcommand{\err}{\text{err}}

\newcommand{\theset}[2]{ \left\{ {#1} \,:\, {#2} \right\} }
\newcommand{\inner}[1]{ \left\langle {#1} \right\rangle }
\newcommand{\Ind}[1]{ \field{I}_{\{{#1}\}} }
\newcommand{\eye}[1]{ \boldsymbol{I}_{#1} }
\newcommand{\norm}[1]{\left\|{#1}\right\|}
%\newcommand{\trace}[1]{\text{tr}\left({#1}\right)}
\newcommand{\trace}[1]{\textsc{tr}({#1})}
\newcommand{\diag}[1]{\mathrm{diag}\!\left\{{#1}\right\}}

\newcommand{\defeq}{\stackrel{\rm def}{=}}
\newcommand{\sgn}{\mbox{\sc sgn}}
\newcommand{\scI}{\mathcal{I}}
\newcommand{\scO}{\mathcal{O}}
\newcommand{\scN}{\mathcal{N}}

\newcommand{\dt}{\displaystyle}
\renewcommand{\ss}{\subseteq}
\newcommand{\wh}{\widehat}
\newcommand{\wt}{\widetilde}
\newcommand{\ve}{\varepsilon}
\newcommand{\hlambda}{\wh{\lambda}}
\newcommand{\yhat}{\wh{y}}

\newcommand{\hDelta}{\wh{\Delta}}
\newcommand{\hdelta}{\wh{\delta}}
\newcommand{\spin}{\{-1,+1\}}
%\newcommand{\calS}{\mathcal{S}}
\newcommand{\calC}{\mathcal{C}}

%%%%%%%%%%%%%%%%%%%%%%%%

\newtheorem{assumption}{Assumption}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\DeclareMathOperator{\val}{val}
\DeclareMathOperator{\spa}{sp}
\DeclareMathOperator{\solve}{solve}
\allowdisplaybreaks

% Packages hyperref and algorithmic misbehave sometimes.  We can fix
% this with the following command.
%\newcommand{\theHalgorithm}{\arabic{algorithm}}

\usepackage{amsmath}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}

\title{Bandit Multiclass Classification}

%\author{}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

%#############################################################################
%    Introduction
%#############################################################################

\section{A Regret Lower Bound for A Certain Type of Algorithms}
In this section, we try to construct an error lower bound for a certain type of algorithms. This type of algorithms does not make update when it makes a wrong prediction. For simplicity, we only consider binary classification.  More formally, the algorithms we consider satisfy the following assumption.

\begin{assumption}[Algorithm]
Let $p_t(x)$ be the algorithm's probability of predicting class $1$ (recall we consider binary classification) at round $t$ if it receives the feature vector $x\in \calX \subset \mathbb{R}^d$. We assume $p_t(\cdot)$ is totally determined by all previous \textbf{correct} examples. In other words, $p_t(\cdot)$ is determined by the tuple $((x_{\tau_1}, y_{\tau_1}), \ldots, (x_{\tau_N}, y_{\tau_N}))$ where $1\leq \tau_1 < \tau_2 \ldots < \tau_N < t$ are the rounds that the learner makes correct prediction. 
\end{assumption}

\begin{assumption}[linearly separable with a margin]
We assume the samples are linearly separable with margin $\gamma$ (i.e., any two points with different labels have distance no less than $\gamma$). 
\end{assumption}

\begin{definition}[Free space]
The free space at time $t$ is the set of points whose label is still underdetermined given $(x_1, y_1), \ldots, (x_{t-1},y_{t-1})$. For example, the $\gamma$-ball centered around any already presented point is excluded from the free space. Denote the free space at time $t$ by $\FS_t$.  
\end{definition}
The free space's definition simply means that at time $t$, the adversary can pick any point $x_t$ in $\FS_t$ and assign the label $y_t$ to either $1$ or $2$ without violating the linearly separable and the $\gamma$-margin assumption.

Below we present the Adversary's strategy of constructing $(x_t, y_t)$.

\begin{algorithm}[H]
\caption{Adversary's strategy}
Pick $x_1$ randomly from $\calX$, and let $y_1=1$. \\
\For{$t=2, \ldots, T$}{
    \If{$\tilde{y}_{t-1} \neq y_{t-1}$}{
        Let $(x_t, y_t)=(x_{t-1}, y_{t-1})$
    }
    \ElseIf{$\FS_{t}$ is not empty}{
        Pick $x_t\in \FS_{t}$. Because of this $x_t$, the free space's volume is reduced. We denote the reduction amount by $V_t=v(\FS_{t+1})-v(\FS_{t})\leq V$. (i.e., $V$ is a global upper bound of $V_t$) \\
        If $p_t(x_t)\geq 1-\max\left\{\sqrt{V},\frac{1}{\sqrt{T}}\right\}$, then label $y_t=2$; otherwise, label $y_t=1$. 
    }
    \Else{
        Randomly assign $(x_t,y_t)$ with some value that does not violate the assumption. 
    }
}
\end{algorithm}

%\textbf{Analysis}. We assume that in the ``else'' case in the above algorithm, we can always pick $x_t$ such that $V_t\leq V$ (we will show how to pick such $x_t$ later).

\begin{definition}[history]
Let $\calH_t$ be the history before time $t$: $\calH_t=\{ (x_s, y_s, \tilde{y}_s) \}_{s=1}^{t-1}$. We use $\E_t[\cdot]$ to denote $\E[\cdot | \calH_t]$. 
\end{definition}

\begin{lemma}
If $\exists t$ such $p_t(x_t)\geq 1-\max\left\{ \sqrt{V}, \frac{1}{\sqrt{T}} \right\}$, then $\E_t\left[ \sum_{s=t}^T  \one[\tilde{y}_s\neq y_s] \right] \geq \Omega\left(\min\left\{\frac{1}{\sqrt{V}},\sqrt{T}\right\}\right)$.
\end{lemma}
\begin{proof}
By of the condition and the adversary strategy, we have $y_t=2$. Therefore, the learner will predict the true label with probability $\leq \max \left\{ \sqrt{V}, \frac{1}{\sqrt{T}} \right\}$. And note that if the learner predicts incorrectly at time $t$, then at time $t+1$ the feature vector remains the same $(x_{t+1}=x_t)$ , and the learner's probability of prediction also remains the same $(p_{t+1}(\cdot)=p_t(\cdot))$. Therefore, the expected number of mistakes before the first correct guess is (roughly) larger than  $\frac{1}{\max\left\{\sqrt{V}, \frac{1}{\sqrt{T}}\right\}}=\min\left\{\frac{1}{\sqrt{V}}, \sqrt{T}\right\}$. 
\end{proof}

\begin{lemma}
If $\forall s$, $p_s(x_s)\leq 1-\max\left\{\sqrt{V}, \frac{1}{\sqrt{T}}\right\}$, then $\sum_{s=1}^T \E_s[\one[\tilde{y}_s\neq y_s]] = \Omega\left(\min\left\{\sqrt{T}, \frac{1}{\sqrt{V}}\right\}\right)$.
\end{lemma}

\begin{proof}
By the condition and the adversary strategy, we know that the probability of error is larger than $\max\left\{\sqrt{V},\frac{1}{\sqrt{T}}\right\}$ at all time $t$ \textit{before the free space is used up}. Since each time the free space only reduces by $V$, in the first $\frac{1}{V}$ rounds (assume the total volume is $1$), the free space is still all available. Therefore, 
\begin{align*}
    \sum_{s=1}^T \E_s[\one[\tilde{y}_s\neq y_s]] \geq \min\left\{ T,\frac{1}{V} \right\}\times \max\left\{ \sqrt{V}, \frac{1}{\sqrt{T}} \right\}=\min\left\{\sqrt{T}, \frac{1}{\sqrt{V}}\right\}. 
\end{align*}
\end{proof}

\textbf{Discussion}. We believe that $V$ can be in the order of $\mathcal{O}\left(\gamma^d\right)$ (some weaker thing like $\mathcal{O}\left(\gamma^{d/2}\right)$ is also acceptable). Basically, we need to figure out the following question: can we construct a sequence of points $\{x_1,x_2, \ldots\}$ , such that for every $t$, $x_t$'s distance with $\text{conichull}\{x_1,\ldots, x_{t-1}\}$ is larger than $\gamma$, but the volume difference $v(\text{conichull}\{x_1,\ldots, x_{t}\}) - v(\text{conichull}\{x_1,\ldots, x_{t-1}\})$ is upper bounded by $V$?

This lower bound does not rule out those algorithms that change its probability vector based on the $\textbf{count}$ of consecutive errors. This type of algorithm may still easy to be implemented (like QBC). Also it does not rule out the banditron algorithm.

\section{Biased Halving: Trading Error with Complexity}
\begin{algorithm}[H]
\caption{Banditron}
\textbf{Define}: $\Omega=\{W\in \mathbb{R}^{Kd}: \|\e_i^\top W\|_2\leq D\}$.\\
For a set $S$ of $W$'s, $S(i|x)$ is the subset of $S$ that outputs class $i$ given feature vector $x$, i.e., $S(i|x)=\{W\in S: (Wx)_i \geq (Wx)_j \ \forall j\}$\\
$|S|$ denotes the volumn of $S$. \\
\textbf{parameter}: $\alpha \in (0,1)$ \\
$\Omega_1=\Omega$.  \\
\For{$ t=1,\ldots, T $}{
\If{$\argmax_i \frac{|\Omega_t(i|x_t)|}{|\Omega_t|} \geq 1-\alpha$}{ \label{line:case1}
        Let $\tilde{y}_t=i$.\\ 
        \If{$\tilde{y}_t \neq y_t$}{
            $\Omega_{t+1}=\Omega_t \backslash \Omega_t(\tilde{y}_t|x_t)$. \label{line:cut}
        }
    }
\label{line:case2}\Else{
        Let $\tilde{y}_t\sim \text{unif}([K])$. \\
        \If{$\tilde{y}_t=y_t$}{
            $\Omega_{t+1}=\Omega_t(\tilde{y}_t|x_t)$. \label{line:cut2}
        }
    }
}
\end{algorithm}

\textbf{Assumption}: If the volume of $\Omega_t$ becomes smaller than $\frac{|\Omega|}{N}$, then the algorithm won't make any error anymore. $N$ should be in the order of $\Theta(\frac{1}{\gamma^{Kd}})$.  \\
\textbf{Rough analysis:} \\
Each time the algorithm makes an error in Line~\ref{line:case1}, the volume becomes $\alpha$ times the original volume. So the algorithm will not make more than $ \frac{\ln N}{\ln \frac{1}{\alpha}} $ mistakes in this case.

In the case of Line~\ref{line:case2}, $K\ln \frac{1}{\delta}$ errors will accompany with a $(1-\alpha)$-factor shrinkage in the volume. Therefore, the number of errors occurred in this case is upper bounded by $ \frac{K\ln\frac{1}{\delta}\ln N}{\ln \frac{1}{1-\alpha}}\leq \frac{K\ln\frac{1}{\delta}\ln N}{\alpha} $.

Now we discuss about the complexity. The main issue is how to maintain $\Omega_t$. Each time the algorithm enters Line~\ref{line:cut}, $\Omega_t$ becomes more and more fragmented. But if $\Omega_t$ can be maintained with $M$ convex cones, then $\Omega_{t+1}$ can be maintained with $(K-1)M\leq KM$ convex cones. And we assume each cone's volume can be computed in \text{poly}($T$) time. Each time the algorithm enters Line~\ref{line:cut2}, the number of convex cones does not increase.

By the above discussion, there will be no more than $K^{\frac{\ln N}{\ln \frac{1}{\alpha}}}$ convex cones to maintain. And the error bound is in the order of $\frac{K\ln\frac{1}{\delta}\ln N}{\alpha}$ for some $\alpha<\frac{1}{2}$. Let's try to balance the number of errors and computational complexity. Let
\begin{align*}
    &K^{\frac{\ln N}{\ln \frac{1}{\alpha}}}\approx\frac{K\ln\frac{1}{\delta}\ln N}{\alpha}\\
    \Rightarrow &~ \frac{\ln N}{\ln\frac{1}{\alpha}} \ln K \approx  \ln\left(K\ln\frac{1}{\delta}\ln N\right) + \ln\frac{1}{\alpha}\\
    \Rightarrow &~ \text{pick\ }\ln\frac{1}{\alpha}=\sqrt{\ln N}.
\end{align*}
Thus the computational complexity is in the order of $K^{\sqrt{\ln N}}\times \text{poly}(T)=K^{\sqrt{Kd\ln\frac{1}{\delta}}}$. The error bound is $\mathcal{O}\left( e^{\sqrt{Kd\ln \frac{1}{\delta}}} K^2 d \ln\frac{1}{\delta}\ln\frac{1}{\gamma} \right)$.

Another viewpoint: let $\frac{1}{\alpha}=K^\beta$, then the complexity is $\left(\frac{1}{\gamma}\right)^{\frac{Kd}{\beta}}\times \text{poly}(T)$ and the error bound is $K^{\beta+1}\ln\frac{1}{\delta}\ln N$.

\section{Cone Algorithm}
\begin{algorithm}[H]
\caption{Banditron}
\textbf{definition}: $K\triangleq$ number of classes, $\gamma\triangleq$  margin\\
\textbf{Initialize}: $\calS_1=\cdots=\calS_K=\phi$ (empty set) \\
\For{$t=1, \ldots, T$}{
    Receive $x_t\in \mathbb{R}^d$. \\
    Define the cone $\calC_i = \left\{x\in\mathbb{R}^d: x=\sum_{j=1}^{|\calS_i|} \alpha_jy_j, \text{\ where\ } y_j\in \calS_i, \alpha_j\geq 0 \right\}$ \\
    (that is, $\calC_i$ is the conic hull of $\calS_i$) \\
    Check whether $x_t$ belongs to, or has distance smaller than $\gamma$, to one of $\calC_1, \ldots, \calC_K$. \\
    If so, classify $x_t$ to the corresponding class (say class $i$), and let $\calS_i\leftarrow \calS_i \cup \{x_t\}$. {\color{red} This prediction will be correct for sure by our margin assumption.}\\
    If not, let $\tilde{y}_t\sim \text{unif}([K])$ and predict $\tilde{y}_t$. If $\tilde{y}_t=y_t$, then $\calS_{y_t}\leftarrow \calS_{y_t} \cup \{x_t\}$. 
}
\end{algorithm}

\section{One-against-all Perceptron}
Actually, same as Chicheng's writeup's Section 5: Fixed-Threshold Perceptron.

\section{Gradient Descent {\color{red} [TODO]}}
\iffalse
\section{Continuous EXP4 with Uniform Exploration}

\begin{algorithm}[H]
\caption{Banditron}
\textbf{Parameters}: feasible set $\Omega\subset \mathbb{R}^{K\times d}$ \\
\textbf{Definitions}: $\ell_t(W)\triangleq [1-(Wx_t)_{y_t}+\max_{r\in[K]}(Wx_t)_r]_+$ (hinge loss)\\
\For{$t=1, \ldots, T$}{
    Receive $x_t\in \mathbb{R}^d$. \\
    Define 
    \begin{gather*}
    q_t(W)=\frac{\exp(-\alpha \sum_{s=1}^{t-1} \hat{\ell}_s(W))}{\int_{U\in \Omega} \exp(-\alpha \sum_{s=1}^{t-1} \hat{\ell}_s(U))dU }, \ \ \ \ \forall W\in\Omega, 
    %\Omega_k^t\triangleq\{W\in\Omega: k=\argmax_{r\in[K]} (Wx_t)_r\} \ \ \ \text{i.e., the set of $W$'s that predict class $k$ at time $t$}\\
    %p_t(k)=\int_{W\in \Omega_k^t} q_t(W)dW, \ \ \ \ \forall k\in[K], \\
    %\tilde{p}_t(k) \propto p_t(k)\one[p_t(k)\geq \epsilon]
    \end{gather*} 
    where $\hat{\ell}_s(W)=\one[\tilde{y}_s=y_s]\left(\frac{\one[\hat{y}_s= y_s]\ell_s(W)}{1-\gamma+\frac{\gamma}{K}} + \frac{\one[\hat{y}_s\neq y_s]\ell_s(W)}{\frac{\gamma}{K}}\right)$.\\
    Sample $W_t\sim q_t$, and let $\hat{y}_t = \argmax_{r\in[K]}(W_tx_t)_r$.\\
    Let $\tilde{y}_t=\hat{y}_t$ with probability $1-\gamma$, and $\tilde{y}_t\sim \text{unif}([K])$ with probability $\gamma$. 
}
\end{algorithm}

%\begin{assumption}
%\label{assump:zero}
%   Assume we know there exists a $W^*\in \Omega$ having zero loss (i.e., $\ell_t(W^*)=0$ for all $t$). 
%\end{assumption}

%\begin{definition}
%Define $\tilde{q}_t(W) = q_t(W)\times \frac{\tilde{p}_t(k')}{p_t(k')}$ with $k' = \argmax_r(Wx_t)_r$ (i.e., letting $\tilde{q}_t$ scales with $\tilde{p}_t$). 
%\end{definition}
%\begin{definition}
%Define $\bar{\ell}_t(k)=\int_{W\in\Omega_k^t} \tilde{q}_t(W)\ell_t(W)dW \big/ \int_{W\in\Omega_k^t} \tilde{q}_t(W)dW $, that is, the average loss over $W$'s that predicts class $k$. Defining this is because our problem is slightly different from traditional contextual bandit formulation: with hinge loss, the loss received by different experts may be different even if they predict the same class/action. Note that while $\ell_t(\cdot), \hat{\ell}_t(\cdot)$ are losses for experts, $\bar{\ell}_t(\cdot)$ is loss for actions. 
%\end{definition}

%\begin{lemma}
%$\int_{W\in\Omega}q_t(W)\hat{\ell}_t(W)\geq (1-K\epsilon)\bar{\ell}_t(\hat{y}_t)$. 
%\end{lemma}
%\begin{proof}
%By the definition of $\tilde{p}_t$, we have $1\leq \frac{\tilde{p}_t(k)}{p_t(k)}\leq \frac{1}{1-K\epsilon}$ for all $k$. Thus $1\leq \frac{\tilde{q}_t(W)}{q_t(W)}\leq \frac{1}{1-K\epsilon}$ for all $W$.  Therefore, 
%\begin{align*}
%    \int_{W\in\Omega}q_t(W)\hat{\ell}_t(W)dW&\geq (1-K\epsilon)\int_{W\in\Omega}\tilde{q}_t(W)\hat{\ell}_t(W)dW \\
%    &=(1-K\epsilon)\left(\one[\hat{y}_t=y_t]\sum_{k=1}^K \tilde{p}_t(k)\bar{\ell}_t(k) + \one[\hat{y}_t\neq y_t]\sum_{k=1}^K \tilde{p}_t(k)\bar{a}_t(k)\right). 
%\end{align*}
%\end{proof}

%\begin{lemma}
%\label{lemma:simple}
%The following facts hold: \\
%(1) $ \hat{\ell}_t(W)\leq \ell_t(W)$ for all $W$. \\
%(2) $ \hat{\ell}_t(W_t) \geq \ell_t(W_t) $. 
%\end{lemma}
%\begin{proof}
%\ \\
%(1) $ \hat{\ell}_t(W)\leq \one[\hat{y}_t=y_t]\ell_t(W)+\one[\hat{y}_t\neq y_t]\ell_t(W) = \ell_t(W)$. \\
%(2) $ \hat{\ell}_t(W_t)\geq \one[\hat{y}_t\neq y_t]a_t(W_t)=\one[\hat{y}_t\neq y_t]=\ell_t(W_t)$. 
%\end{proof}

%By standard analysis of the exponential weight algorithm (or see page 9 of \cite{bubeck2017kernel}), we have 
%\begin{align*}
%\E\left[\sum_{t=1}^T\int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right] &\leq \E\left[\sum_{t=1}^T\hat{\ell}_t(W^*) + \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \alpha \sum_{t=1}^T\int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)^2dW\right] \\ 
%&\leq \E\left[\sum_{t=1}^T\hat{\ell}_t(W^*) + \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \alpha \sum_{t=1}^T\int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right],
%\end{align*}
%which implies $\E\left[\sum_{t=1}^T\hat{\ell}_t(W_t)\right]\leq  \E\left[\sum_{t=1}^T  \hat{\ell}_t(W^*) \right]+\frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha(1-\alpha)}+\frac{\alpha}{1-\alpha}\E\left[\sum_{t=1}^T\hat{\ell}_t(W^*)\right] $. Combining Lemma~\ref{lemma:simple}, we get a small-loss regret bound.

%\textbf{Note.} Considering $\delta(W^*)$ as a distribution in a region surrounding $W^*$ which has $1/(TD)^{dK}$ $\Omega$'s volume, then $\textbf{Ent}(q_1||\delta(W^*))$ should be in the order of $dK\log (TD)$.

%\textbf{Discussion.} \\
%(1) It seems even okay to define $\hat{\ell}_s(W)=\one[\hat{y}_s\neq y_s]a_s(W)$. \\
%(2) $q_t(\cdot)$ can be sampled when $\sum_{s=1}^{t-1}\hat{\ell}_s(W)$ is convex (not very sure, but I believe so from papers like \cite{lovasz2006fast,narayanan2013efficient,bubeck2015sampling}). The part $ \one[\hat{y}_s=y_s]\ell_s(W)$ can become convex if we define $\ell(W)$ to be the hinge loss; however, the part $\one[\hat{y}_s\neq y_s]a_s(W)$ does not seem to be easy. This corresponds to constructing a loss function when the learner is wrong, and is somewhat related to the issue we met previously: the region $\{W: \hat{y}_t\neq \argmax_r (Wx_t)_r \}$ is non-convex.

%\section{Continuous EXP4 for Banditron with Uniform Exploration}
\begin{lemma}
$\E_{\tilde{y}_t}[\hat{\ell}_t(W)] = \ell_t(W)$ for all $W$. 
\end{lemma}
\begin{proof}
\begin{align*}
\E_{\tilde{y}_t}[\hat{\ell}_t(W)] &= \E_{\tilde{y}_t}\left[ \one[\hat{y}_s=y_s] \frac{\one[\tilde{y}_s=y_s]\ell_t(W)}{1-\gamma+\frac{\gamma}{K}}   +
\one[\hat{y}_s\neq y_s] \frac{\one[\tilde{y}_s = y_s]\ell_t(W)}{\frac{\gamma}{K}}\right] \\
& = \one[\hat{y}_s=y_s] \ell_t(W)   +
\one[\hat{y}_s\neq y_s] \ell_t(W) = \ell_t(W). 
\end{align*}
\end{proof}

%\begin{lemma}
%$\E_{\tilde{y}_t}[(\hat{\ell}_t(W))^2] \leq \frac{2K}{\gamma}(\ell_t(W))^2\leq \frac{2K}{\gamma}\ell_t(W)$ for all $W$. 
%\end{lemma}

Plugging these lemmas in the previous hedge bound, we can get \begin{align*}
&\E\left[\sum_{t=1}^T  \ell_{t}(W_{t})  \right]\\
&=\E\left[\sum_{t=1}^T  \int_{W\in\Omega} q_t(W)\ell_t(W)dW  \right] \\
&=\E\left[\sum_{t=1}^T \E_{\tilde{y}_t} \left[ \int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right] \right]\\
&\leq \E\left[\sum_{t=1}^T \E_{\tilde{y}_t} \left[ \hat{\ell}_t(W^*) \right]+ \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \alpha \sum_{t=1}^T \E_{\tilde{y}_t}\left[ \int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)^2dW \right] \right] \\ 
&\leq \E\left[\sum_{t=1}^T \E_{\tilde{y}_t}\left[ \hat{\ell}_t(W^*) \right] + \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \frac{2K\alpha}{\gamma} \sum_{t=1}^T \E_{\tilde{y}_t}\left[ \int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right]\right]
\end{align*}

... to bound the regret, it would be something like bounding $\frac{1}{1-\frac{K\alpha}{\gamma}}\left(\frac{1}{\alpha}+\frac{K\alpha}{\gamma}L^* + \gamma T\right)$, which gives $(L^*T)^{1/3} + \sqrt{T}$ regret bound.

\textbf{Discussion.} We can change $\ell_t(\cdot)$ to any reasonable convex loss (e.g., logsitic loss or second-order loss). 
\fi

%\textbf{Observation}. Alekh's paper's results can be generalized to losses with $\Phi_t$ a strongly and smoothly convex function. 
\begin{assumption}
$\|x_t\|_2^2\leq 1$. There is a $W^*\in\mathcal{W}$ such that $\ell_t(W^*)\leq 0$ for all $t$ ($\ell_t$ and $\mathcal{W}$ are defined below).  
\end{assumption}

\begin{algorithm}[H]
\caption{Banditron}
\textbf{Input}: $D\geq 2$, $\epsilon$ (picked in a later lemma). \\
\textbf{Definition}: 
\begin{align*}
    \ell_t(W) &\triangleq [1-(Wx_t)_{y_t} + \max_{r\neq y_t}(Wx_t)_r]_+^2 \ \ \ \ \text{(squared hinge loss)} \\
    & = \Phi_t(Wx_t), 
    %\Phi_t(z) \triangleq \sum_{i\neq y_t} \psi(z_{y_t}-z_i).
\end{align*}
where $\Phi_t(z)\triangleq [1-\e_{y_t}^\top z + \max_{r\neq y_t} \e_r^\top z]_+^2$. \\
Also, define $\mathcal{W}=\{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2\leq D \text{\ for all }i\in[K]\}$. \\
\textbf{Initialization}: $W_1=0, M_1=I$.\\ 
\For{$t=1, \ldots, T$}{
   Observe $x_t$. \\
   \If{$ \| x_t \|_{M_t^{-1}} \geq \epsilon$ {\color{red} \text{and} $\|W_t-W^*\|_F\geq 1$}}{
       Draw $\tilde{y}_t \sim \text{unif}([K])$. 
   }
   \Else{
       Draw $\tilde{y}_t = \hat{y}_t \triangleq \argmax_{r\in[K]}(W_tx_t)_r$. 
   }
   \If{ $\tilde{y}_t=y_t$ }{
       $Z_t\leftarrow 1$, \\
       $M_{t+1}\leftarrow M_t + Z_t\ell_t(W_t)x_tx_t^\top$,\\
       $W_{t+1} \leftarrow \Pi_{\mathcal{W}} (W_t - \eta_{t+1}\nabla \ell_t(W_t))$, \ \ \ \ \ where $\eta_{t+1} = \frac{1}{8}$. \\
       ($\Pi_{\mathcal{W}}$ is the projection operator onto $\mathcal{W}$ w.r.t. Frobenius norm)
   }
   \Else{
       $Z_t\leftarrow 0$,  \\
       $M_{t+1}\leftarrow M_t$,\\
       $W_{t+1}\leftarrow W_t$.
   }

}
\end{algorithm}
\iffalse
We will pick 
\begin{align*}
     \psi(u)=\begin{cases}
        \frac{1}{2K(1-D)^2}(u-D)^2 - \frac{1}{2K}, & \text{if $u\geq 1$} \\
        \left(1+\frac{1}{K(1-D)}\right)u^2 + \left(-2-\frac{1}{K(1-D)}\right)u + 1 &\text{if $u\leq 1$},  
     \end{cases}
\end{align*}
It has the following properties: \\
(1) It is continuous and differentiable. \\
(2) It is $\frac{1}{2K(1-D)^2}$-strongly convex and $1$-smooth. \\
(3) It decreases in $[-D,D]$, passing through $(0,1),(1,0)$, and $(D,\frac{-1}{2K})$. \\
(4) Its minimum value $\frac{-1}{2K}$ is attained at $u=D$.

\begin{lemma} 
 For the above specific choice of $\psi$, $\Phi_t$ is $\frac{1}{2KD^2}$-strongly convex and $2K$-smooth (i.e., its Hessian has eigenvalues all within $[\frac{1}{2KD^2}, 2K]$).

\end{lemma}
\begin{proof}
It is clear that $\frac{\partial^2}{\partial z_j\partial z_i}\Phi_t(z)=0$ for $i\neq j$. Also, $\frac{\partial^2}{\partial^2 z_i} \Phi_t(z)\geq \frac{1}{2K(1-D)^2}\geq \frac{1}{2KD^2}$ and $\frac{\partial^2}{\partial^2 z_i} \Phi_t(z)\leq K\left(1+\frac{1}{K(1-D)}\right)\leq 2K$. 
\end{proof}

\begin{lemma}
\label{lemma:error_cond}
If $\argmax_r (Wx_t)_r = y_t$, then $\ell_t(W) \leq K$; 
If $\argmax_r (Wx_t)_r \neq y_t$, then $\ell_t(W) \geq 1$.  
\end{lemma}
\begin{proof}
If $\argmax_r (Wx_t)_r = y_t$, then $z_{y_t}-z_i\geq 0$ for all $i$, and thus $\Phi_t(z)< K\psi(0)=K$; 
If $\argmax_r (Wx_t)_r \triangleq j \neq y_t$, then $\Phi_t(z)\geq \psi(z_{y_t}-z_j) - K\times \frac{1}{2K}\geq \psi(0)-\frac{1}{2}=\frac{1}{2}$. 
This is clear by the definition of $\ell_t$. 
\end{proof}
\fi
%\begin{definition}
%$\|W\|_M^2 \triangleq \sum_{i=1}^K \|\e_i^\top W\|_M^2 $.\\
%$\gamma_\ell \triangleq \frac{1}{2KD^2}$; $\gamma_u\triangleq 2K$ (convexity and smoothity of $\Phi_t$). 
%\end{definition}

%\begin{lemma}
%For any $W^*\in \mathcal{W}$, with probability at least $1-\delta$, 
%\begin{align*} 
%    \|W_t-W^*\|_{M_t} \leq \tilde{\mathcal{O}}\left(\frac{\sqrt{Kd}}{\gamma_\ell} + D\sqrt{\gamma}\right).
%\end{align*}
%(the $\tilde{\mathcal{O}}$ notation hides $\ln T$, $\ln \frac{1}{\delta}$, $\ln \frac{1}{\gamma}$ factors)
%\end{lemma}
%\begin{proof}
%By the first order optimality condition, we have for all $W^*\in \mathcal{W}$, 
%\begin{align*}
%    \inner{\gamma W_t+\sum_{s=1}^{t-1}Z_s \nabla \ell_s(W_t), W^*-W_t}\geq 0. 
%\end{align*}
%Rearranging it and plugging in the property $\nb\ell_s(W)=\nb\Phi_s(Wx_s)x_s^\top$ gives 
%\begin{align}
%    \sum_{s=1}^{t-1} Z_s\inner{ -\nb\Phi_s(W^*x_s),W_tx_s-W^*x_s} \geq  \sum_{s=1}^{t-1} Z_s\inner{ \nb\Phi_s(W_t x_s)-\nb\Phi_s(W^*x_s),W_tx_s-W^*x_s}+\gamma\inner{W_t, W_t-W^*}. 
%    \label{eqn:key}
%\end{align}
%By $\Phi_s$'s convexity and that $\norm{W}_F^2\leq KD^2$ for all $W\in \mathcal{W}$, the RHS of \eqref{eqn:key} can be lower bounded by 
%\begin{align*}
%    \gamma_\ell\sum_{s=1}^{t-1} Z_s\norm{W_t x_s-W^*x_s}_2^2 - 2\gamma KD^2 \geq \gamma_\ell \norm{W_t-W^*}_{M_t}^2-2\gamma KD^2. 
%\end{align*}
%The LHS is upper bounded by 
%\begin{align*}
%    \sum_{i=1}^K \sum_{s=1}^{t-1} Z_s (-\nb_i\Phi_s(W^*x_s))\inner{\e_iW_t-\e_iW^*, x_s}
%\end{align*}
%\end{proof}

\begin{lemma}
\label{lemma:bound_gradient}
$\norm{\nb\ell_t(W)}_F^2 \leq 8\ell_t(W)$. 
\end{lemma}
\begin{proof}
$    \|\nb\ell_t(W)\|_F^2 = \|\nb\Phi_t(Wx_t)x_t^\top\|_{F}^2 \leq \left(2\sqrt{\Phi_t(Wx_t)}\right)^2\times 2\|x_t\|_{2}^2 \leq 8\ell_t(W).  
$
\end{proof}

\begin{lemma}
\label{lemma:decreasing error}
Let $L_{t+1}\triangleq \sum_{s=1}^t Z_s\ell_s(W_s)$. Then 
$\|W_{t+1}-W^*\|_F^2 \leq \exp\left(-\frac{L_{t+1}}{32KD^2}\right)$. 
\end{lemma}
\begin{proof}
Let $Z_{t}=1$. 
\begin{align*}
    \|W_{t+1}-W^*\|_F^2 &\leq \|W_t - \eta_{t+1}\nb\ell_t(W_t)-W^*\|_F^2 \\
    & = \| W_t - W^* \|_F^2 - 2\eta_{t+1}\inner{\nb\ell_t(W_t),W_t-W^*}_F + \eta_{t+1}^2\|\nb\ell_t(W_t)\|_F^2.  
\end{align*}
By the separable assumption we have $\ell_t(W^*)\leq 0$. Since $\ell_t$ is convex, $\inner{\nb\ell_t(W_t), W_t-W^*} \geq \ell_t(W_t)-\ell_t(W^*)\geq \ell_t(W_t)$. Continuing the above calculation and using Lemma~\ref{lemma:bound_gradient}, we get 
\begin{align*}
    \|W_{t+1}-W^*\|_F^2 &\leq \|W_t-W^*\|_2^2 - 2\eta_{t+1}\ell_t(W_t) + 8\eta_{t+1}^2 \ell_t(W_t) \\ 
    &\leq \|W_t-W^*\|_F^2 - \frac{1}{8}\ell_{t}(W_t) \\
    &\leq \|W_t-W^*\|_F^2 \left(1-\frac{\ell_t(W_t)}{32KD^2}\right)  \text{\ \ \ \ because $\|W_t-W^*\|_F^2\leq 4KD^2$} \\
    &\leq \|W_t-W^*\|_F^2 \exp\left(-\frac{\ell_t(W_t)}{32KD^2}\right)
\end{align*}
By induction, we can get
\begin{align*}
    \|W_{t+1}-W^*\|_F^2 &\leq KD^2 \exp\left( -\frac{L_{t+1}}{32KD^2} \right) 
    %&\leq KD^2 \left(\frac{8KD^2}{A_{t+1}}\right)   %\ \ \ \ \ \text{because $\exp(-x)<1/x$ for any $x>0$} \\
    %& = \frac{8K^2D^4}{A_{t+1}}. 
\end{align*}
\end{proof}

\begin{definition}
$\norm{W}_{M}^2\triangleq \sum_{i=1}^K \norm{\e_i^\top W}_{M}^2$.
\end{definition}
With this definition we have $\|Wx_t\|_2^2 = \sum_{i=1}^K (\e_i^\top Wx_t)^2 \leq \sum_{i=1}^K \|\e_i^\top W\|_M^2 \|x_t\|_{M^{-1}}^2\leq \|W\|_M^2 \|x_t\|_{M^{-1}}^2$

\begin{lemma}
\begin{align*}
\|W_{t}-W^*\|_{M_{t}}^2 \leq (1+L_t)K^2D^2 \exp\left(-\frac{L_t}{32KD^2}\right) \leq 32K^3D^4. 
\end{align*}
\end{lemma}
\begin{proof}
Because we assume $\|x_t\|_2^2\leq 1$, it holds that $ M_t \preceq (1+L_t) I$. Therefore $\|W_t-W^*\|_{M_t}^2 \leq (1+L_t)\|W_t-W^*\|_I^2 =  (1+L_t) \sum_{i=1}^K \| \e_i^\top (W_t-W^*) \|_2^2 \leq (1+L_t) K \|W_t-W^*\|_F^2 $. By Lemma~\ref{lemma:decreasing error} this is bounded by $(1+L_t)K^2D^2\exp\left( -\frac{L_t}{32KD^2} \right)$, which can further be bounded by a constant related to $K$ and $D$. For example, using the property $\exp(-x)\leq \frac{1}{(1+x)^2}$ for all $x>0$, it can be upper bounded by $(1+L_t)K^2D^2 \times \frac{(32KD^2)^2}{(L_t+32KD^2)^2} \leq \frac{32^2K^4D^6}{32KD^2+L_t}\leq 32K^3D^4$.   
\end{proof}

\begin{lemma}
\label{lemma: xbounded}
If $\|x_t\|_{M_t^{-1}}\leq \epsilon = \frac{1}{4D\sqrt{32K^3D^4}}$, then $\hat{y}_t=y_t$. 
\end{lemma}
\begin{proof}
By the convexity of $\ell_t$, 
\begin{align*}
    \ell_t(W_t)\leq \ell_t(W_t)-\ell_t(W^*)&\leq \inner{\nb \ell_t(W_t), W_t-W^*}\\
     & = \inner{\nb\Phi_t(W_tx_t)x_t^\top, W_t - W^*} \\
    & = \inner{\nb\Phi_t(W_tx_t), W_tx_t - W^*x_t} \\
    & \leq 4D\norm{W_tx_t-W^*x_t}_2 \\
    & \leq 4D\norm{W_t-W^*}_{M_t}\norm{x_t}_{M_t^{-1}} \leq 1.
\end{align*}
This implies $\hat{y}_t=y_t$. 
\end{proof}

Therefore, when we do not explore, we know $W_t$ will predict correctly! Thus we only need to bound the number of errors occurred in exploration rounds, which is calculated by the following lemma. 
\begin{lemma}
\label{lemma:N}
$\sum_{t=1}^T \one[\tilde{y}_t\neq y_t] \leq ???$ with probability at least $1-\delta$. 
\end{lemma}

\begin{proof}
By the above discussion, $\sum_{t=1}^T \one[\tilde{y}_t\neq y_t] \leq N\triangleq \sum_{t=1}^T Z_t$, the number of exploration rounds. 
\begin{align*}
    N &= \sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right]\\
    &\leq \left(K\ln \frac{1}{\delta}\right)\sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right]Z_t \tag{when $\|x_t\|_{M_t^{-1}}\geq \epsilon$, $\tilde{y}_t=y_t$ with probability $\frac{1}{K}$} \\
    & \leq \frac{K\ln \frac{1}{\delta}}{\epsilon^2}\sum_{t=1}^T \norm{x_t}_{M_t^{-1}}^2 Z_t \leq \max_{t\in[T]}\left(\frac{1}{\ell_{t}(W_t)}\right)\times \frac{K\ln T\ln \frac{1}{\delta}}{\epsilon^2}. 
\end{align*}
\end{proof}

\textbf{Discussion}. 
In the calculation of Lemma~\ref{lemma: xbounded},  we can actually get $\ell_t(W_t)^2 \leq \norm{\nb\Phi_t(W_tx_t)}_2^2\norm{W_t-W^*}_{M_t}^2\norm{x_t}_{M_t^{-1}}^2$. Similar to the calculation in Lemma~\ref{lemma:decreasing error}, $\norm{\nb\Phi_t(W_tx_t)}_2^2$ is bounded by constant times $\ell_t(W_t)$. So the exploration criterion could potentially become $\ell_t(W_t)\|x_t\|_{M_t^{-1}}^2\geq \frac{1}{\epsilon^2}$, which makes Lemma~\ref{lemma:N} go through. The problem is just we do not know $\ell_t(W_t)$ in general.

%\section{Reservoir Sampling}
%\textbf{Observation}. In Algorithm 2 of the SOBA paper, $\tilde{\ell}$ is constructed as a $ \tilde{\mathcal{O}}(\gamma \eta)$-exp-concave function which appears at the rate of $\gamma$. What if we divide a $\tilde{\mathcal{O}}(\gamma\eta)$-exp-concave function into roughly $1/\gamma$ $\tilde{\mathcal{O}}(\eta)$-exp-concave functions?

%\begin{algorithm}[H]
%\caption{Banditron}
%\textbf{Input}: $D\geq 2$, $\epsilon$, $\gamma$. \\
%\textbf{Definition}:

%\end{algorithm}

\newpage
%\bibliography{adaptivity} 
%\bibliographystyle{plain}

\end{document}

### 2018-07-18 main.tex

@@
 
-\textbf{Assumption}: If the volume of $\Omega_t$ becomes smaller than $\frac{|\Omega|}{N}$, then the algorithm won't make any error anymore.
+\textbf{Conjecture(should be true)}: If the volume of $\Omega_t$ becomes smaller than $\frac{|\Omega|}{N}$, then the algorithm won't make any error anymore.
 $N$ should be in the order of $\Theta(\frac{1}{\gamma^{Kd}})$.
@@
 
+\section{How hard it is to use the feedback only from wrong guesses?}
+The halving algorithm can actually run if we can do ``uniform sampling'' over the version space.
+But it is even unknown whether we can efficiently pick a model from the version space.
+The problem is that we get a lot of feedback in the form of ``feature $x_t$ does not belong to class $\tilde{y}_t$'', which we don't know how to use.
+
+The following is just an attempt (not successful but might be interesting...) to say that it might be not easy to figure out a model if the learner is only presented with this kind of ``error message''.
+
+The problem is formulated as follows. 
+Given $N$ points in a row, each one with a class $c_i\in [K]$, $\forall i\in [N]$. We call these $N$ points \textit{separable} if the following statement holds: 
+\begin{center}
+    If $c_i=c_j$ for some $i\leq j$, then $c_i=c_{i+1}=\cdots=c_j$.
+\end{center}
+For example, if $N=5, K=3$, then $(c_1,c_2, c_3, c_4,c_5)=(3,3,1,1,1)$ is separable, but $(c_1,c_2,c_3,c_4,c_5)=(2,1,2,2,2)$ is not. 
+\ \\
+\ \\
+Now you have $N$ conditions, in which the $i$-th condition only says something like ``$c_i\neq k$'' for some $k$. \\
+(1) Can you efficiently decide whether there exists an assignment of $(c_1,\ldots,c_N)$ such that these $N$ points are separable and satisfy all the conditions? \\
+(2) If it is guaranteed that there are separable solutions, can you efficiently find one of them?\\ (Efficient: the complexity is polynomial in $N$ and $K$)
+\ \\
+\ \\
+\textbf{Example 1}. \\
+$N=5, K=3$: \\
+$c_1\neq 1$ \\
+$c_2\neq 2$ \\
+$c_3\neq 3$ \\
+$c_4\neq 1$ \\
+$c_5\neq 2$ \\
+$\Rightarrow (c_1,c_2,c_3,c_4,c_5)=(2,1,1,3,3)$ or $(3,3,2,2,1)$ are separable solutions. \\
+\ \\
+\textbf{Example 2}. \\
+$N=7, K=3$: \\
+$c_1\neq 1$ \\
+$c_2\neq 2$ \\
+$c_3\neq 3$ \\
+$c_4\neq 1$ \\
+$c_5\neq 2$ \\
+$c_6\neq 3$ \\
+$c_7\neq 1$ \\
+$\Rightarrow$ There is no separable solution. \\
+
+It turns out this specific 1-dimensional problem is equivalent to check whether there is a \textbf{missing permutation} of $[K]$ / find a missing permutation in the given subsequence.
+In example 1, the existed permutations are $(1,2,3), (1,3,2), (2,3,1), (3,1,2)$, the missing ones are $(2,1,3)$ and $(3,2,1)$.
+So the solutions can be $(2,1,3)$ or $(3,2,1)$ (with some repetition).
+In Example 2, all permutations are as subsequences, so there is no solution.
+
+We can prove this equivalence considering two directions: \\
+(1) If there is a solution with the class labels following a permutation, then that permutation cannot be a subsequence of the given sequence. \\
+(2) If there is a missing permutation in the given sequence, then there is a class assignment that follows this permutation.
+
 \section{Cone Algorithm}
@@
 \section{One-against-all Perceptron}
-Actually, same as Chicheng's writeup's Section 5: Fixed-Threshold Perceptron.
+Same as Chicheng's writeup's Section 5: Fixed-Threshold Perceptron.
 
 \section{Gradient Descent {\color{red} [TODO]}}
-\iffalse
-\section{Continuous EXP4 with Uniform Exploration}
-
-\begin{algorithm}[H]
-\caption{Banditron}
-\textbf{Parameters}: feasible set $\Omega\subset \mathbb{R}^{K\times d}$ \\
-\textbf{Definitions}: $\ell_t(W)\triangleq [1-(Wx_t)_{y_t}+\max_{r\in[K]}(Wx_t)_r]_+$ (hinge loss)\\
-\For{$t=1, \ldots, T$}{
-    Receive $x_t\in \mathbb{R}^d$. \\
-    Define 
-    \begin{gather*}
-    q_t(W)=\frac{\exp(-\alpha \sum_{s=1}^{t-1} \hat{\ell}_s(W))}{\int_{U\in \Omega} \exp(-\alpha \sum_{s=1}^{t-1} \hat{\ell}_s(U))dU }, \ \ \ \ \forall W\in\Omega, 
-    %\Omega_k^t\triangleq\{W\in\Omega: k=\argmax_{r\in[K]} (Wx_t)_r\} \ \ \ \text{i.e., the set of $W$'s that predict class $k$ at time $t$}\\
-    %p_t(k)=\int_{W\in \Omega_k^t} q_t(W)dW, \ \ \ \ \forall k\in[K], \\
-    %\tilde{p}_t(k) \propto p_t(k)\one[p_t(k)\geq \epsilon]
-    \end{gather*} 
-    where $\hat{\ell}_s(W)=\one[\tilde{y}_s=y_s]\left(\frac{\one[\hat{y}_s= y_s]\ell_s(W)}{1-\gamma+\frac{\gamma}{K}} + \frac{\one[\hat{y}_s\neq y_s]\ell_s(W)}{\frac{\gamma}{K}}\right)$.\\
-    Sample $W_t\sim q_t$, and let $\hat{y}_t = \argmax_{r\in[K]}(W_tx_t)_r$.\\
-    Let $\tilde{y}_t=\hat{y}_t$ with probability $1-\gamma$, and $\tilde{y}_t\sim \text{unif}([K])$ with probability $\gamma$. 
-}
-\end{algorithm}
-
-%\begin{assumption}
-%\label{assump:zero}
-%   Assume we know there exists a $W^*\in \Omega$ having zero loss (i.e., $\ell_t(W^*)=0$ for all $t$). 
-%\end{assumption}
-
-%\begin{definition}
-%Define $\tilde{q}_t(W) = q_t(W)\times \frac{\tilde{p}_t(k')}{p_t(k')}$ with $k' = \argmax_r(Wx_t)_r$ (i.e., letting $\tilde{q}_t$ scales with $\tilde{p}_t$). 
-%\end{definition}
-%\begin{definition}
-%Define $\bar{\ell}_t(k)=\int_{W\in\Omega_k^t} \tilde{q}_t(W)\ell_t(W)dW \big/ \int_{W\in\Omega_k^t} \tilde{q}_t(W)dW $, that is, the average loss over $W$'s that predicts class $k$.
-Defining this is because our problem is slightly different from traditional contextual bandit formulation: with hinge loss, the loss received by different experts may be different even if they predict the same class/action.
-Note that while $\ell_t(\cdot), \hat{\ell}_t(\cdot)$ are losses for experts, $\bar{\ell}_t(\cdot)$ is loss for actions.
-%\end{definition}
-
-%\begin{lemma}
-%$\int_{W\in\Omega}q_t(W)\hat{\ell}_t(W)\geq (1-K\epsilon)\bar{\ell}_t(\hat{y}_t)$. 
-%\end{lemma}
-%\begin{proof}
-%By the definition of $\tilde{p}_t$, we have $1\leq \frac{\tilde{p}_t(k)}{p_t(k)}\leq \frac{1}{1-K\epsilon}$ for all $k$.
-Thus $1\leq \frac{\tilde{q}_t(W)}{q_t(W)}\leq \frac{1}{1-K\epsilon}$ for all $W$.
-Therefore,
-%\begin{align*}
-%    \int_{W\in\Omega}q_t(W)\hat{\ell}_t(W)dW&\geq (1-K\epsilon)\int_{W\in\Omega}\tilde{q}_t(W)\hat{\ell}_t(W)dW \\
-%    &=(1-K\epsilon)\left(\one[\hat{y}_t=y_t]\sum_{k=1}^K \tilde{p}_t(k)\bar{\ell}_t(k) + \one[\hat{y}_t\neq y_t]\sum_{k=1}^K \tilde{p}_t(k)\bar{a}_t(k)\right). 
-%\end{align*}
-%\end{proof}
-
-%\begin{lemma}
-%\label{lemma:simple}
-%The following facts hold: \\
-%(1) $ \hat{\ell}_t(W)\leq \ell_t(W)$ for all $W$. \\
-%(2) $ \hat{\ell}_t(W_t) \geq \ell_t(W_t) $. 
-%\end{lemma}
-%\begin{proof}
-%\ \\
-%(1) $ \hat{\ell}_t(W)\leq \one[\hat{y}_t=y_t]\ell_t(W)+\one[\hat{y}_t\neq y_t]\ell_t(W) = \ell_t(W)$. \\
-%(2) $ \hat{\ell}_t(W_t)\geq \one[\hat{y}_t\neq y_t]a_t(W_t)=\one[\hat{y}_t\neq y_t]=\ell_t(W_t)$. 
-%\end{proof}
-
-%By standard analysis of the exponential weight algorithm (or see page 9 of \cite{bubeck2017kernel}), we have 
-%\begin{align*}
-%\E\left[\sum_{t=1}^T\int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right] &\leq \E\left[\sum_{t=1}^T\hat{\ell}_t(W^*) + \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \alpha \sum_{t=1}^T\int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)^2dW\right] \\
-%&\leq \E\left[\sum_{t=1}^T\hat{\ell}_t(W^*) + \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \alpha \sum_{t=1}^T\int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right],
-%\end{align*}
-%which implies $\E\left[\sum_{t=1}^T\hat{\ell}_t(W_t)\right]\leq  \E\left[\sum_{t=1}^T  \hat{\ell}_t(W^*) \right]+\frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha(1-\alpha)}+\frac{\alpha}{1-\alpha}\E\left[\sum_{t=1}^T\hat{\ell}_t(W^*)\right] $.
-Combining Lemma~\ref{lemma:simple}, we get a small-loss regret bound.
-
-%\textbf{Note.} Considering $\delta(W^*)$ as a distribution in a region surrounding $W^*$ which has $1/(TD)^{dK}$ $\Omega$'s volume, then $\textbf{Ent}(q_1||\delta(W^*))$ should be in the order of $dK\log (TD)$.
-
-%\textbf{Discussion.} \\
-%(1) It seems even okay to define $\hat{\ell}_s(W)=\one[\hat{y}_s\neq y_s]a_s(W)$. \\
-%(2) $q_t(\cdot)$ can be sampled when $\sum_{s=1}^{t-1}\hat{\ell}_s(W)$ is convex (not very sure, but I believe so from papers like \cite{lovasz2006fast,narayanan2013efficient,bubeck2015sampling}).
-The part $ \one[\hat{y}_s=y_s]\ell_s(W)$ can become convex if we define $\ell(W)$ to be the hinge loss; however, the part $\one[\hat{y}_s\neq y_s]a_s(W)$ does not seem to be easy.
-This corresponds to constructing a loss function when the learner is wrong, and is somewhat related to the issue we met previously: the region $\{W: \hat{y}_t\neq \argmax_r (Wx_t)_r \}$ is non-convex.
-
-%\section{Continuous EXP4 for Banditron with Uniform Exploration}
-\begin{lemma}
-$\E_{\tilde{y}_t}[\hat{\ell}_t(W)] = \ell_t(W)$ for all $W$. 
-\end{lemma}
-\begin{proof}
-\begin{align*}
-\E_{\tilde{y}_t}[\hat{\ell}_t(W)] &= \E_{\tilde{y}_t}\left[ \one[\hat{y}_s=y_s] \frac{\one[\tilde{y}_s=y_s]\ell_t(W)}{1-\gamma+\frac{\gamma}{K}}   +
-\one[\hat{y}_s\neq y_s] \frac{\one[\tilde{y}_s = y_s]\ell_t(W)}{\frac{\gamma}{K}}\right] \\
-& = \one[\hat{y}_s=y_s] \ell_t(W)   +
-\one[\hat{y}_s\neq y_s] \ell_t(W) = \ell_t(W). 
-\end{align*}
-\end{proof}
-
-%\begin{lemma}
-%$\E_{\tilde{y}_t}[(\hat{\ell}_t(W))^2] \leq \frac{2K}{\gamma}(\ell_t(W))^2\leq \frac{2K}{\gamma}\ell_t(W)$ for all $W$. 
-%\end{lemma}
-
-Plugging these lemmas in the previous hedge bound, we can get \begin{align*}
-&\E\left[\sum_{t=1}^T  \ell_{t}(W_{t})  \right]\\
-&=\E\left[\sum_{t=1}^T  \int_{W\in\Omega} q_t(W)\ell_t(W)dW  \right] \\
-&=\E\left[\sum_{t=1}^T \E_{\tilde{y}_t} \left[ \int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right] \right]\\
-&\leq \E\left[\sum_{t=1}^T \E_{\tilde{y}_t} \left[ \hat{\ell}_t(W^*) \right]+ \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \alpha \sum_{t=1}^T \E_{\tilde{y}_t}\left[ \int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)^2dW \right] \right] \\
-&\leq \E\left[\sum_{t=1}^T \E_{\tilde{y}_t}\left[ \hat{\ell}_t(W^*) \right] + \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \frac{2K\alpha}{\gamma} \sum_{t=1}^T \E_{\tilde{y}_t}\left[ \int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right]\right]
-\end{align*}
-
-...
-to bound the regret, it would be something like bounding $\frac{1}{1-\frac{K\alpha}{\gamma}}\left(\frac{1}{\alpha}+\frac{K\alpha}{\gamma}L^* + \gamma T\right)$, which gives $(L^*T)^{1/3} + \sqrt{T}$ regret bound.
-
-\textbf{Discussion.} We can change $\ell_t(\cdot)$ to any reasonable convex loss (e.g., logsitic loss or second-order loss). 
-\fi
 
@@
 
+\section{Continuous EXP4 with Uniform Exploration}
+
+\begin{algorithm}[H]
+\caption{Banditron}
+\textbf{Parameters}: feasible set $\Omega\subset \mathbb{R}^{K\times d}$ \\
+\textbf{Definitions}: $\ell_t(W)\triangleq [1-(Wx_t)_{y_t}+\max_{r\in[K]}(Wx_t)_r]_+$ (hinge loss)\\
+\For{$t=1, \ldots, T$}{
+    Receive $x_t\in \mathbb{R}^d$. \\
+    Define 
+    \begin{gather*}
+    q_t(W)=\frac{\exp(-\alpha \sum_{s=1}^{t-1} \hat{\ell}_s(W))}{\int_{U\in \Omega} \exp(-\alpha \sum_{s=1}^{t-1} \hat{\ell}_s(U))dU }, \ \ \ \ \forall W\in\Omega, 
+    %\Omega_k^t\triangleq\{W\in\Omega: k=\argmax_{r\in[K]} (Wx_t)_r\} \ \ \ \text{i.e., the set of $W$'s that predict class $k$ at time $t$}\\
+    %p_t(k)=\int_{W\in \Omega_k^t} q_t(W)dW, \ \ \ \ \forall k\in[K], \\
+    %\tilde{p}_t(k) \propto p_t(k)\one[p_t(k)\geq \epsilon]
+    \end{gather*} 
+    where $\hat{\ell}_s(W)=\one[\tilde{y}_s=y_s]\left(\frac{\one[\hat{y}_s= y_s]\ell_s(W)}{1-\gamma+\frac{\gamma}{K}} + \frac{\one[\hat{y}_s\neq y_s]\ell_s(W)}{\frac{\gamma}{K}}\right)$.\\
+    Sample $W_t\sim q_t$, and let $\hat{y}_t = \argmax_{r\in[K]}(W_tx_t)_r$.\\
+    Let $\tilde{y}_t=\hat{y}_t$ with probability $1-\gamma$, and $\tilde{y}_t\sim \text{unif}([K])$ with probability $\gamma$. 
+}
+\end{algorithm}
+
+%\begin{assumption}
+%\label{assump:zero}
+%   Assume we know there exists a $W^*\in \Omega$ having zero loss (i.e., $\ell_t(W^*)=0$ for all $t$). 
+%\end{assumption}
+
+%\begin{definition}
+%Define $\tilde{q}_t(W) = q_t(W)\times \frac{\tilde{p}_t(k')}{p_t(k')}$ with $k' = \argmax_r(Wx_t)_r$ (i.e., letting $\tilde{q}_t$ scales with $\tilde{p}_t$). 
+%\end{definition}
+%\begin{definition}
+%Define $\bar{\ell}_t(k)=\int_{W\in\Omega_k^t} \tilde{q}_t(W)\ell_t(W)dW \big/ \int_{W\in\Omega_k^t} \tilde{q}_t(W)dW $, that is, the average loss over $W$'s that predicts class $k$.
+Defining this is because our problem is slightly different from traditional contextual bandit formulation: with hinge loss, the loss received by different experts may be different even if they predict the same class/action.
+Note that while $\ell_t(\cdot), \hat{\ell}_t(\cdot)$ are losses for experts, $\bar{\ell}_t(\cdot)$ is loss for actions.
+%\end{definition}
+
+%\begin{lemma}
+%$\int_{W\in\Omega}q_t(W)\hat{\ell}_t(W)\geq (1-K\epsilon)\bar{\ell}_t(\hat{y}_t)$. 
+%\end{lemma}
+%\begin{proof}
+%By the definition of $\tilde{p}_t$, we have $1\leq \frac{\tilde{p}_t(k)}{p_t(k)}\leq \frac{1}{1-K\epsilon}$ for all $k$.
+Thus $1\leq \frac{\tilde{q}_t(W)}{q_t(W)}\leq \frac{1}{1-K\epsilon}$ for all $W$.
+Therefore,
+%\begin{align*}
+%    \int_{W\in\Omega}q_t(W)\hat{\ell}_t(W)dW&\geq (1-K\epsilon)\int_{W\in\Omega}\tilde{q}_t(W)\hat{\ell}_t(W)dW \\
+%    &=(1-K\epsilon)\left(\one[\hat{y}_t=y_t]\sum_{k=1}^K \tilde{p}_t(k)\bar{\ell}_t(k) + \one[\hat{y}_t\neq y_t]\sum_{k=1}^K \tilde{p}_t(k)\bar{a}_t(k)\right). 
+%\end{align*}
+%\end{proof}
+
+%\begin{lemma}
+%\label{lemma:simple}
+%The following facts hold: \\
+%(1) $ \hat{\ell}_t(W)\leq \ell_t(W)$ for all $W$. \\
+%(2) $ \hat{\ell}_t(W_t) \geq \ell_t(W_t) $. 
+%\end{lemma}
+%\begin{proof}
+%\ \\
+%(1) $ \hat{\ell}_t(W)\leq \one[\hat{y}_t=y_t]\ell_t(W)+\one[\hat{y}_t\neq y_t]\ell_t(W) = \ell_t(W)$. \\
+%(2) $ \hat{\ell}_t(W_t)\geq \one[\hat{y}_t\neq y_t]a_t(W_t)=\one[\hat{y}_t\neq y_t]=\ell_t(W_t)$. 
+%\end{proof}
+
+%By standard analysis of the exponential weight algorithm (or see page 9 of \cite{bubeck2017kernel}), we have 
+%\begin{align*}
+%\E\left[\sum_{t=1}^T\int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right] &\leq \E\left[\sum_{t=1}^T\hat{\ell}_t(W^*) + \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \alpha \sum_{t=1}^T\int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)^2dW\right] \\
+%&\leq \E\left[\sum_{t=1}^T\hat{\ell}_t(W^*) + \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \alpha \sum_{t=1}^T\int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right],
+%\end{align*}
+%which implies $\E\left[\sum_{t=1}^T\hat{\ell}_t(W_t)\right]\leq  \E\left[\sum_{t=1}^T  \hat{\ell}_t(W^*) \right]+\frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha(1-\alpha)}+\frac{\alpha}{1-\alpha}\E\left[\sum_{t=1}^T\hat{\ell}_t(W^*)\right] $.
+Combining Lemma~\ref{lemma:simple}, we get a small-loss regret bound.
+
+%\textbf{Note.} Considering $\delta(W^*)$ as a distribution in a region surrounding $W^*$ which has $1/(TD)^{dK}$ $\Omega$'s volume, then $\textbf{Ent}(q_1||\delta(W^*))$ should be in the order of $dK\log (TD)$.
+
+%\textbf{Discussion.} \\
+%(1) It seems even okay to define $\hat{\ell}_s(W)=\one[\hat{y}_s\neq y_s]a_s(W)$. \\
+%(2) $q_t(\cdot)$ can be sampled when $\sum_{s=1}^{t-1}\hat{\ell}_s(W)$ is convex (not very sure, but I believe so from papers like \cite{lovasz2006fast,narayanan2013efficient,bubeck2015sampling}).
+The part $ \one[\hat{y}_s=y_s]\ell_s(W)$ can become convex if we define $\ell(W)$ to be the hinge loss; however, the part $\one[\hat{y}_s\neq y_s]a_s(W)$ does not seem to be easy.
+This corresponds to constructing a loss function when the learner is wrong, and is somewhat related to the issue we met previously: the region $\{W: \hat{y}_t\neq \argmax_r (Wx_t)_r \}$ is non-convex.
+
+%\section{Continuous EXP4 for Banditron with Uniform Exploration}
+\begin{lemma}
+$\E_{\tilde{y}_t}[\hat{\ell}_t(W)] = \ell_t(W)$ for all $W$. 
+\end{lemma}
+\begin{proof}
+\begin{align*}
+\E_{\tilde{y}_t}[\hat{\ell}_t(W)] &= \E_{\tilde{y}_t}\left[ \one[\hat{y}_s=y_s] \frac{\one[\tilde{y}_s=y_s]\ell_t(W)}{1-\gamma+\frac{\gamma}{K}}   +
+\one[\hat{y}_s\neq y_s] \frac{\one[\tilde{y}_s = y_s]\ell_t(W)}{\frac{\gamma}{K}}\right] \\
+& = \one[\hat{y}_s=y_s] \ell_t(W)   +
+\one[\hat{y}_s\neq y_s] \ell_t(W) = \ell_t(W). 
+\end{align*}
+\end{proof}
+
+%\begin{lemma}
+%$\E_{\tilde{y}_t}[(\hat{\ell}_t(W))^2] \leq \frac{2K}{\gamma}(\ell_t(W))^2\leq \frac{2K}{\gamma}\ell_t(W)$ for all $W$. 
+%\end{lemma}
+
+Plugging these lemmas in the previous hedge bound, we can get \begin{align*}
+&\E\left[\sum_{t=1}^T  \ell_{t}(W_{t})  \right]\\
+&=\E\left[\sum_{t=1}^T  \int_{W\in\Omega} q_t(W)\ell_t(W)dW  \right] \\
+&=\E\left[\sum_{t=1}^T \E_{\tilde{y}_t} \left[ \int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right] \right]\\
+&\leq \E\left[\sum_{t=1}^T \E_{\tilde{y}_t} \left[ \hat{\ell}_t(W^*) \right]+ \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \alpha \sum_{t=1}^T \E_{\tilde{y}_t}\left[ \int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)^2dW \right] \right] \\
+&\leq \E\left[\sum_{t=1}^T \E_{\tilde{y}_t}\left[ \hat{\ell}_t(W^*) \right] + \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \frac{2K\alpha}{\gamma} \sum_{t=1}^T \E_{\tilde{y}_t}\left[ \int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right]\right]
+\end{align*}
+
+...
+to bound the regret, it would be something like bounding $\frac{1}{1-\frac{K\alpha}{\gamma}}\left(\frac{1}{\alpha}+\frac{K\alpha}{\gamma}L^* + \gamma T\right)$, which gives $(L^*T)^{1/3} + \sqrt{T}$ regret bound.
+
+\textbf{Discussion.} We can change $\ell_t(\cdot)$ to any reasonable convex loss (e.g., logsitic loss or second-order loss).
+
 \newpage

### 2018-07-18 main.tex
Add something

@@
 (1) If there is a solution with the class labels following a permutation, then that permutation cannot be a subsequence of the given sequence. \\
-(2) If there is a missing permutation in the given sequence, then there is a class assignment that follows this permutation.
+(2) If there is a missing permutation in the given sequence, then there is a class assignment that follows this permutation.\\ 
+They should be straightforward by trying some examples.
 

### 2018-07-18 main.tex
Add Sec 1-3

@@
 
-It turns out this specific 1-dimensional problem is equivalent to check whether there is a \textbf{missing permutation} of $[K]$ / find a missing permutation in the given subsequence.
-In example 1, the existed permutations are $(1,2,3), (1,3,2), (2,3,1), (3,1,2)$, the missing ones are $(2,1,3)$ and $(3,2,1)$.
+It turns out this specific 1-dimensional problem is equivalent to identify a \textbf{missing permutation} of $[K]$ as a subsequence in the given sequence.
+In Example 1, the existing permutations are $(1,2,3), (1,3,2), (2,3,1), (3,1,2)$, the missing ones are $(2,1,3)$ and $(3,2,1)$.
 So the solutions can be $(2,1,3)$ or $(3,2,1)$ (with some repetition).

### 2018-08-08 main.tex
.

@@
 \usepackage{enumerate}
+\usepackage{soul}
 %%%%%%%%%%%%%%%%%% toc 
@@
 \newcommand{\avgR}{\wh{\cal{R}}}
+\newcommand{\calW}{{\mathcal{W}}}
 \newcommand{\ips}{\wh{r}}
@@
 
-%#############################################################################
-%    Introduction
-%#############################################################################
+\section{Problem Statement}
+A multiclass linear classifier is defined by a matrix $W\in \mathbb{R}^{K\times d}$, where $K$ is the number of classes ($K\geq 3$) and $d$ is the dimension of the feature vector.
+A set of samples $\{(x_t, y_t)\}_{t=1}^T$ where $x_t\in \mathbb{R}^d$ and $y_t\in[K]$ is called \textit{linearly separable} if there exists a $W^*$ such that $ y_t= \argmax_{y\in[K]} (W^*x_t)_y $ for all $t\in[T]$.
+(Note that $(W^*x_t)_y$ can also be written as $\e_y^\top W^* x_t$)
+
+A set of samples $\{(x_t, y_t)\}_{t=1}^T$ is called \textit{linearly separable with a margin $\gamma$} if there exists a $W^*$ with $\|\e_i^\top W^*\|_2\leq 1$ for all $i$ and $(W^*x_t)_{y_t} \geq \max_{y\neq y_t} (W^*x_t)_{y} + \gamma$ for all $t$.
+For simplicity, we define the set where $W^*$ lies in as $\calW = \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W^*\|_2\leq 1\}$.
+
+Consider the following \textit{online multiclass classification} problem: at time $t$, the environment first reveals $x_t\in \mathbb{R}^d$ (and we assume $\|x_t\|_2\leq 1$), then the learner predicts some label $\tilde{y}_t\in [K]$; finally the environment reveals the true label $y_t\in[K]$.
+It is known that if the samples are linearly separable, then the learner will only make constant mistakes.
+It is achievable with the following simple perceptron algorithm:
+
+\begin{algorithm}[H]
+\caption{Perceptron}
+$W_1=\mathbf{0}$\\
+\For{$t=1$ to $T$}{
+   Predict $\tilde{y}_t=\argmax_y (W_tx_t)_y$ \\
+   Update $W_{t+1}\leftarrow W_t + (\e_{y_t}-\e_{\tilde{y}_t})x_t^\top$. 
+}
+\end{algorithm}
+The analysis is simple. On one hand we have (note $\langle A,B \rangle:=\text{Tr}(A^\top B)$):
+\begin{align*}
+    \langle W_t, W^* \rangle &= \langle W_{t-1}, W^* \rangle + \langle (\e_{y_t}-\e_{\tilde{y}_t})x_t^\top, W^* \rangle \\
+    &= \langle W_{t-1}, W^* \rangle + (\e_{y_t}^\top W^* x_t-\e_{\tilde{y}_t}^\top W^* x_t) \\
+    &\geq \langle W_{t-1}, W^* \rangle + \gamma\one[\tilde{y}_t\neq y_t]. 
+\end{align*}
+By induction, we get $\langle W_{T+1}, W^* \rangle \geq \gamma\sum_{t=1}^T \one[\tilde{y}_t\neq y_t]$.
+
+On the other hand, 
+\begin{align*}
+    \langle W_{T+1}, W^* \rangle \leq \|W_{T+1}\|_F\|W^*\|_F \leq \sqrt{2K\sum_{t=1}^T \one[\tilde{y}_t \neq y_t] \|x_t\|_2^2}\times 1 \leq \sqrt{2K\sum_{t=1}^T \one[\tilde{y}_t \neq y_t] } 
+\end{align*}
+Combining the above two inequality, we get $ \sum_{t=1}^T \one[\tilde{y}_t \neq y_t] \leq \frac{4K}{\gamma^2}$.
+
+The \textit{bandit multiclass classification} problem proceeds in a very similar way.
+The only difference is that the learner only knows whether she predicts \textbf{correctly or not}, rather than gets the true label (i.e., in each round, the feedback is only $\one[\tilde{y}_t=y_t]$, rather than $y_t$).
+Surprisingly, with this extremely limited feedback, the learner can still make only constant mistakes.
+It can be achieved with the following variant of \textit{halving algorithm}:
+
+\begin{algorithm}[H]
+\caption{Halving}
+Discretize the space of $W$ (i.e., the $\calW$ as defined in the beginning) with balls of radius $\frac{1}{2\gamma}$.
+Let the set of discretization points be $\calS$.
+Then this is saying that for all $W\in \calW$, there is always a $W'\in \calS$ such that $\|W-W'\|_F\leq \frac{1}{2\gamma}$.\\
+Let $\calS_1=\calS$ \\
+\For{$t=1$ to $T$}{
+    Let $\calS_t(y) = \{W\in \calS_t: (Wx_t)_y \geq (Wx_t)_i \ \forall i\in[K]\}$ (i.e., the set of $W$'s in $\calS_t$ that predict $y$ as the label of $x_t$) \\
+    Let $\tilde{y}_t = \argmax_y |\calS_t(y)|$ (i.e., pick the majority vote)\\
+    \If{$\tilde{y}_t\neq y_t$}{
+        $\calS_{t+1}=\calS_t \backslash \calS_t(\tilde{y}_t)$ (i.e., eliminate the $W$'s that are inconsistent with the outcomes)
+    }
+    \Else{
+        $\calS_{t+1}=\calS_t$
+    }
+}
+\end{algorithm}
+\textbf{Analysis}.
+The majority in $\calS_t$ always has cardinality no less than $\frac{1}{K}|\calS_t|$.
+So every time the learner predicts incorrectly, the size of $|\calS_t|$ shrinks by an order of $(1-\frac{1}{K})$.
+By our margin assumption, there is a $W'\in \calS$ which incurs no error in all samples.
+Therefore, $|S_t|\geq 1$ always holds.
+This means the number of errors is bounded by the order of $\frac{\log(|\calS|)}{-\log(1-\frac{1}{K})}\leq \mathcal{O}\left( K^2d\log \frac{1}{\gamma} \right)$.
+
+The main issue of this halving algorithm is that it is \textbf{inefficient} in the sense that $|\calS|$ is in the order of $\frac{1}{\gamma^{Kd}}$.
+
+Hence, we want to answer the following question: \ul{for bandit multiclass classification, can we have an efficient algorithm (time complexity polynomial in $K,d,\frac{1}{\gamma}, T$) that guarantees constant mistake bound (polynomial in $K,d,\frac{1}{\gamma}$) in the $\gamma$-separable case?} (An unsolved open problem in \cite{kakade2008efficient})
+
+\section{Naive Approaches}
+\begin{itemize}
+    \item \textbf{Exhausting the feature space}: discretize the feature space into $ \left(\frac{1}{\gamma}\right)^{\mathcal{O}(d)} $ blocks.
+The margin assumption guarantees that two points in a block would have the same label (so we can give every block a label).
+Each time a new point $x_t$ comes, see whether the learner already knows the correct label for that block.
+If yes, predict that label; if not, randomly choose a label that has not been chosen for that block.
+\\
+    $\Rightarrow $ error bound: $K\left(\frac{1}{\gamma}\right)^{\mathcal{O}(d)} $. 
+    \item \textbf{Exhausting the hypothesis space}: Discretize the hypothesis space into $\left(\frac{1}{\gamma}\right)^{Kd}$ discretization points (like in the halving algorithm).
+For each of them, make predictions based on it until it makes an mistake.
+\\
+    $\Rightarrow $ error bound: $\left(\frac{1}{\gamma}\right)^{Kd}$. 
+\end{itemize}
+
+\section{Difficulties}
+\label{section: difficulty}
+Efficient classification algorithms often optimize a convex surrogate loss rather than a 0-1 loss. Examples include: 
+\begin{itemize}
+    \item Hinge loss: $\ell_t(W) = [1-(Wx_t)_{y_t}+\max_{y\neq y_t}(Wx_t)_{y}]_+$. 
+    \item Logistic loss: $\ell_t(W)=-\ln\frac{\exp((Wx_t)_{y_t})}{\sum_{y}\exp((Wx_t)_y)}$
+    \item A family of loss that interpolates hinge loss and squared hinge loss (see \cite{beygelzimer2017efficient}'s Eq.(3))
+\end{itemize}
+In full-information setting, one can directly use online convex optimization techniques to deal with the above loss functions (learning over the space of $W$).
+
+Many works for bandit classification reuse this kind of convex optimization schemes, together with explicit exploration and inverse propensity weighting \cite{kakade2008efficient, hazan2011newtron, beygelzimer2017efficient, foster2018logistic}.
+However, because it is hard to estimate these losses when the true label $y_t$ is not known, some of these algorithms \cite{beygelzimer2017efficient, foster2018logistic} simply do not update when the learner makes a mistake ($\tilde{y}_t \neq y_t$).
+We give this kind of algorithm an error lower bound $\Omega\left(\left(\frac{1}{\gamma}\right)^{(d-1)/2}\right)$ in Section~\ref{section: passive lower bound}.
+
+It indeed looks hard to design a convex loss for $W$'s when the learner makes a mistake: when $\tilde{y}_t
+\neq y_t$, the set of $W$'s that we want to penalize (i.e., to assign larger loss) is $\{W: (Wx_t)_{\tilde{y}_t} \geq (Wx_t)_{y}, \forall y \}$, which is a convex cone in the space of $W$.
+It is impossible for a convex function to be large only in a convex subset (the case $K=2$, on the other hand, does not have this issue).
+Can we argue that if the learner is restricted to use convex losses in the space of $W$, she will have to suffer exponential (in $K$) errors?
+
+\section{One-versus-all Kernel Perceptron}
+\subsection{One-versus-all Perceptron}
+Our assumption of linearly separable with a margin is 
+\begin{align}
+ (W^*x_t)_{y_t} \geq (W^*x_t)_{y} + \gamma, \ \forall y\neq y_t. \label{eqn:weaker}
+\end{align}
+As discussed in Section~\ref{section: difficulty}, it seems hard to make update when $\tilde{y}_t\neq y_t$ and achieve a constant and polynomial error bound.
+
+For a moment, in this subsection we make the following stronger margin assumption (which we call \textit{one-versus-all separable} with a margin): 
+\begin{align}
+\begin{cases}
+    (W^*x_t)_{y_t} \geq \gamma/2 \\
+    (W^*x_t)_y \leq -\gamma/2, \forall y\neq y_t.
+\end{cases}
+\label{eqn:stronger}
+\end{align}
+Clearly, one-versus-all separability implies linearly separability, but not the other way around.
+With one-versus-all separability assumption, we can view the problem as $K$ parallel binary classification problem.
+The following algorithm achieves constant error bound:
+\begin{algorithm}[H]
+\caption{One-versus-all Perceptron}
+\label{alg:ova}
+Initialize $w_t^{(1)}=\ldots=w_t^{(K)}=\mathbf{0}\in \mathbb{R}^d$\\
+\For{$t=1$ to $T$}{
+   \If{$\exists y$ such that $w_t^{(y)\top} x_t \geq 0$}{
+       Assign $\tilde{y}_t$ to any $y$ with $w_t^{(y)\top}  x_t \geq 0$ \\
+       Predict $\tilde{y}_t$ \\
+       \lIf{$\tilde{y}_t\neq y_t$}{ update $w_t^{(\tilde{y}_t)} \leftarrow w_t^{(\tilde{y}_t)} - x_t$ } \label{line:update1}
+   }
+   \Else{
+       Pick $\tilde{y}_t$ randomly from $
+       \text{unif}[K]$ \label{line:explore}\\
+       Predict $\tilde{y}_t$ \\
+       \lIf{$\tilde{y}_t = y_t$}{ update $w_t^{(\tilde{y}_t)} \leftarrow w_t^{(\tilde{y}_t)} + x_t$ } \label{line:update2}
+   }
+}
+\end{algorithm}
+\textbf{Analysis}.
+Note that when the algorithm enters Line~\ref{line:update1} or Line~\ref{line:update2}, the binary classifier $w_t^{(\tilde{y}_t)}$ is making an error.
+Let the number of times the algorithm enters Line~\ref{line:update1} and Line~\ref{line:update2} be $M$ and $N$ respectively.
+By the error bound of binary perceptron $\mathcal{O}\left(\frac{1}{\gamma^2}\right)$, we have that $M+N=\mathcal{O}\left(\frac{K}{\gamma^2}\right)$.
+Then note that the number of times the algorithm makes a mistake (i.e.
+$\tilde{y}_t\neq y_t$) is upper bounded by $M$ plus how many times the algorithm explores in Line~\ref{line:explore}; and when the algorithm explores, with probability $\frac{1}{K}$ it enters Line~\ref{line:update2}.
+Therefore, the number of mistakes is bounded (in expectation) by $\E[M+KN]=\mathcal{O}\left(\frac{K^2}{\gamma^2}\right)$.
+
+\subsection{One-versus-all Kernel Perceptron}
+With the polynomial kernel defined in \cite{klivans2004learning}, we can transform the weaker assumption \eqref{eqn:weaker} in the original feature space to the stronger one \eqref{eqn:stronger} in a transformed feature space.
+Indeed, in the original feature space, class $i$ corresponds to an intersection of $K-1$ halfspaces: $ \{x: (w_i^*-w_j^*)^\top x \geq 0, \forall j\neq i\} $, which is the subject of \cite{klivans2004learning} (here, $w_i^{*\top}$ equals to $\e_i^\top W^*$ defined above).
+Directly using their kernel construction, we can have margin $ \left(\frac{\gamma}{d}\right)^{\Omega(K\log K\log (1/\gamma))} $ in the transformed feature space.
+Running kernelized version of Algorithm~\ref{alg:ova}, we can get $ K^2\left(\frac{d}{\gamma}\right)^{\mathcal{O}(K\log K\log (1/\gamma))} $ error bound directly.
 
 \section{A Regret Lower Bound for A Certain Type of Algorithms}
+\label{section: passive lower bound}
 In this section, we try to construct an error lower bound for a certain type of algorithms.
@@
 
-\textbf{Discussion}.
-We believe that $V$ can be in the order of $\mathcal{O}\left(\gamma^d\right)$ (some weaker thing like $\mathcal{O}\left(\gamma^{d/2}\right)$ is also acceptable).
-Basically, we need to figure out the following question: can we construct a sequence of points $\{x_1,x_2, \ldots\}$ , such that for every $t$, $x_t$'s distance with $\text{conichull}\{x_1,\ldots, x_{t-1}\}$ is larger than $\gamma$, but the volume difference $v(\text{conichull}\{x_1,\ldots, x_{t}\}) - v(\text{conichull}\{x_1,\ldots, x_{t-1}\})$ is upper bounded by $V$?
+\textbf{Discussion}. There is a construction such that $1/V$ can be of order $\Omega\left( \left(\frac{1}{\gamma}\right)^{(d-1)/2} \right)$.
 
-This lower bound does not rule out those algorithms that change its probability vector based on the $\textbf{count}$ of consecutive errors.
+%This lower bound does not rule out those algorithms that change its probability vector based on the $\textbf{count}$ of consecutive errors.
 This type of algorithm may still easy to be implemented (like QBC).
 Also it does not rule out the banditron algorithm.
+
+\section{How hard it is to use the feedback only from wrong guesses?}
+The halving algorithm can actually run if we can do ``uniform sampling'' over the version space.
+But it is even unknown whether we can efficiently pick a model from the version space.
+The problem is that we get a lot of feedback in the form of ``feature $x_t$ does not belong to class $\tilde{y}_t$'', which we don't know how to use.
+
+The following is just an attempt (not successful but might be interesting...) to say that it might be not easy to figure out a model if the learner is only presented with this kind of ``error message''.
+
+The problem is formulated as follows. 
+Given $N$ points in a row, each one with a class $c_i\in [K]$, $\forall i\in [N]$. We call these $N$ points \textit{separable} if the following statement holds: 
+\begin{center}
+    If $c_i=c_j$ for some $i\leq j$, then $c_i=c_{i+1}=\cdots=c_j$.
+\end{center}
+For example, if $N=5, K=3$, then $(c_1,c_2, c_3, c_4,c_5)=(3,3,1,1,1)$ is separable, but $(c_1,c_2,c_3,c_4,c_5)=(2,1,2,2,2)$ is not. 
+\ \\
+\ \\
+Now you have $N$ conditions, in which the $i$-th condition only says something like ``$c_i\neq k$'' for some $k$. \\
+(1) Can you efficiently decide whether there exists an assignment of $(c_1,\ldots,c_N)$ such that these $N$ points are separable and satisfy all the conditions? \\
+(2) If it is guaranteed that there are separable solutions, can you efficiently find one of them?\\ (Efficient: the complexity is polynomial in $N$ and $K$)
+\ \\
+\ \\
+\textbf{Example 1}. \\
+$N=5, K=3$: \\
+$c_1\neq 1$ \\
+$c_2\neq 2$ \\
+$c_3\neq 3$ \\
+$c_4\neq 1$ \\
+$c_5\neq 2$ \\
+$\Rightarrow (c_1,c_2,c_3,c_4,c_5)=(2,1,1,3,3)$ or $(3,3,2,2,1)$ are separable solutions. \\
+\ \\
+\textbf{Example 2}. \\
+$N=7, K=3$: \\
+$c_1\neq 1$ \\
+$c_2\neq 2$ \\
+$c_3\neq 3$ \\
+$c_4\neq 1$ \\
+$c_5\neq 2$ \\
+$c_6\neq 3$ \\
+$c_7\neq 1$ \\
+$\Rightarrow$ There is no separable solution. \\
+
+It turns out this specific 1-dimensional problem is equivalent to identify a \textbf{missing permutation} of $[K]$ as a subsequence in the given sequence.
+In Example 1, the existing permutations are $(1,2,3), (1,3,2), (2,3,1), (3,1,2)$, the missing ones are $(2,1,3)$ and $(3,2,1)$.
+So the solutions can be $(2,1,3)$ or $(3,2,1)$ (with some repetition).
+In Example 2, all permutations are as subsequences, so there is no solution.
+
+We can prove this equivalence considering two directions: \\
+(1) If there is a solution with the class labels following a permutation, then that permutation cannot be a subsequence of the given sequence. \\
+(2) If there is a missing permutation in the given sequence, then there is a class assignment that follows this permutation.\\ 
+They should be straightforward by trying some examples.
+
+%\section{Cone Algorithm}
+%\begin{algorithm}[H]
+%\caption{Banditron}
+%\textbf{definition}: $K\triangleq$ number of classes, $\gamma\triangleq$  margin\\
+%\textbf{Initialize}: $\calS_1=\cdots=\calS_K=\phi$ (empty set) \\
+%\For{$t=1, \ldots, T$}{
+%    Receive $x_t\in \mathbb{R}^d$. \\
+%    Define the cone $\calC_i = \left\{x\in\mathbb{R}^d: x=\sum_{j=1}^{|\calS_i|} \alpha_jy_j, \text{\ where\ } y_j\in \calS_i, \alpha_j\geq 0 \right\}$ \\
+%    (that is, $\calC_i$ is the conic hull of $\calS_i$) \\
+%    Check whether $x_t$ belongs to, or has distance smaller than $\gamma$, to one of $\calC_1, \ldots, \calC_K$. \\
+%    If so, classify $x_t$ to the corresponding class (say class $i$), and let $\calS_i\leftarrow \calS_i \cup \{x_t\}$.
+{\color{red} This prediction will be correct for sure by our margin assumption.}\\
+%    If not, let $\tilde{y}_t\sim \text{unif}([K])$ and predict $\tilde{y}_t$. If $\tilde{y}_t=y_t$, then $\calS_{y_t}\leftarrow \calS_{y_t} \cup \{x_t\}$. 
+%}
+%\end{algorithm}
 
@@
 Another viewpoint: let $\frac{1}{\alpha}=K^\beta$, then the complexity is $\left(\frac{1}{\gamma}\right)^{\frac{Kd}{\beta}}\times \text{poly}(T)$ and the error bound is $K^{\beta+1}\ln\frac{1}{\delta}\ln N$.
-
-\section{How hard it is to use the feedback only from wrong guesses?}
-The halving algorithm can actually run if we can do ``uniform sampling'' over the version space.
-But it is even unknown whether we can efficiently pick a model from the version space.
-The problem is that we get a lot of feedback in the form of ``feature $x_t$ does not belong to class $\tilde{y}_t$'', which we don't know how to use.
-
-The following is just an attempt (not successful but might be interesting...) to say that it might be not easy to figure out a model if the learner is only presented with this kind of ``error message''.
-
-The problem is formulated as follows. 
-Given $N$ points in a row, each one with a class $c_i\in [K]$, $\forall i\in [N]$. We call these $N$ points \textit{separable} if the following statement holds: 
-\begin{center}
-    If $c_i=c_j$ for some $i\leq j$, then $c_i=c_{i+1}=\cdots=c_j$.
-\end{center}
-For example, if $N=5, K=3$, then $(c_1,c_2, c_3, c_4,c_5)=(3,3,1,1,1)$ is separable, but $(c_1,c_2,c_3,c_4,c_5)=(2,1,2,2,2)$ is not. 
-\ \\
-\ \\
-Now you have $N$ conditions, in which the $i$-th condition only says something like ``$c_i\neq k$'' for some $k$. \\
-(1) Can you efficiently decide whether there exists an assignment of $(c_1,\ldots,c_N)$ such that these $N$ points are separable and satisfy all the conditions? \\
-(2) If it is guaranteed that there are separable solutions, can you efficiently find one of them?\\ (Efficient: the complexity is polynomial in $N$ and $K$)
-\ \\
-\ \\
-\textbf{Example 1}. \\
-$N=5, K=3$: \\
-$c_1\neq 1$ \\
-$c_2\neq 2$ \\
-$c_3\neq 3$ \\
-$c_4\neq 1$ \\
-$c_5\neq 2$ \\
-$\Rightarrow (c_1,c_2,c_3,c_4,c_5)=(2,1,1,3,3)$ or $(3,3,2,2,1)$ are separable solutions. \\
-\ \\
-\textbf{Example 2}. \\
-$N=7, K=3$: \\
-$c_1\neq 1$ \\
-$c_2\neq 2$ \\
-$c_3\neq 3$ \\
-$c_4\neq 1$ \\
-$c_5\neq 2$ \\
-$c_6\neq 3$ \\
-$c_7\neq 1$ \\
-$\Rightarrow$ There is no separable solution. \\
-
-It turns out this specific 1-dimensional problem is equivalent to identify a \textbf{missing permutation} of $[K]$ as a subsequence in the given sequence.
-In Example 1, the existing permutations are $(1,2,3), (1,3,2), (2,3,1), (3,1,2)$, the missing ones are $(2,1,3)$ and $(3,2,1)$.
-So the solutions can be $(2,1,3)$ or $(3,2,1)$ (with some repetition).
-In Example 2, all permutations are as subsequences, so there is no solution.
-
-We can prove this equivalence considering two directions: \\
-(1) If there is a solution with the class labels following a permutation, then that permutation cannot be a subsequence of the given sequence. \\
-(2) If there is a missing permutation in the given sequence, then there is a class assignment that follows this permutation.\\ 
-They should be straightforward by trying some examples.
-
-\section{Cone Algorithm}
-\begin{algorithm}[H]
-\caption{Banditron}
-\textbf{definition}: $K\triangleq$ number of classes, $\gamma\triangleq$  margin\\
-\textbf{Initialize}: $\calS_1=\cdots=\calS_K=\phi$ (empty set) \\
-\For{$t=1, \ldots, T$}{
-    Receive $x_t\in \mathbb{R}^d$. \\
-    Define the cone $\calC_i = \left\{x\in\mathbb{R}^d: x=\sum_{j=1}^{|\calS_i|} \alpha_jy_j, \text{\ where\ } y_j\in \calS_i, \alpha_j\geq 0 \right\}$ \\
-    (that is, $\calC_i$ is the conic hull of $\calS_i$) \\
-    Check whether $x_t$ belongs to, or has distance smaller than $\gamma$, to one of $\calC_1, \ldots, \calC_K$. \\
-    If so, classify $x_t$ to the corresponding class (say class $i$), and let $\calS_i\leftarrow \calS_i \cup \{x_t\}$.
-{\color{red} This prediction will be correct for sure by our margin assumption.}\\
-    If not, let $\tilde{y}_t\sim \text{unif}([K])$ and predict $\tilde{y}_t$. If $\tilde{y}_t=y_t$, then $\calS_{y_t}\leftarrow \calS_{y_t} \cup \{x_t\}$. 
-}
-\end{algorithm}
-
-\section{One-against-all Perceptron}
-Same as Chicheng's writeup's Section 5: Fixed-Threshold Perceptron.
 
@@
 \newpage
-%\bibliography{adaptivity} 
-%\bibliographystyle{plain}
+\bibliography{adaptivity} 
+\bibliographystyle{plain}
 

### 2018-08-10 main.tex
.

@@
 \usepackage{amsthm}
+\usepackage{makecell}
 % For algorithms
@@
 
-\section{One-versus-all Kernel Perceptron}
-\subsection{One-versus-all Perceptron}
+\section{One-versus-all Perceptron}
 Our assumption of linearly separable with a margin is 
@@
 
-\subsection{One-versus-all Kernel Perceptron}
+\section{One-versus-all Kernel Perceptron}
 With the polynomial kernel defined in \cite{klivans2004learning}, we can transform the weaker assumption \eqref{eqn:weaker} in the original feature space to the stronger one \eqref{eqn:stronger} in a transformed feature space.
@@
 Running kernelized version of Algorithm~\ref{alg:ova}, we can get $ K^2\left(\frac{d}{\gamma}\right)^{\mathcal{O}(K\log K\log (1/\gamma))} $ error bound directly.
+
+\subsection{Refinement for \cite{klivans2004learning}'s Fact 1}
+\begin{lemma}
+   For $i=1,\ldots, \ell$ let $q^{(i)}(x)=\sum_S c^{(i)}_{S} x_S $ be a polynomial over $x_1, \ldots, x_d$ with $\|q^{(i)}\|^2\leq M_i$.
+Then (1) if $q^{(1)}\ldots q^{(\ell)}$ has degree at most $\deg$, we have $\|q^{(1)}\ldots q^{(\ell)}\|^2 \leq (\deg)^{O(\deg)} \prod_i M_i$, and (2) we have $\|q^{(1)}+\ldots+q^{(\ell)}\|^2\leq \ell(M_1+\ldots+M_\ell)$.
+\end{lemma}
+\begin{proof}
+For the first bound, we bound the ratio between the following two values:  $ \|q^{(1)}\ldots q^{(\ell)}\|^2 $ and $\|q^{(1)}\|^2\ldots \|q^{(\ell)}\|^2$. 
+\begin{align}
+    n_1&=\prod_{i=1}^\ell \|q^{(i)}\|^2 
+    = \prod_{i=1}^\ell \left(\sum_{S_i} \left(c^{(i)}_{S_i}\right)^2 \right)
+    = \sum_{(S_1,\ldots,S_\ell)}  \left(\prod_{i=1}^\ell \left(c^{(i)}_{S_i}\right)^2 \right)
+    = \sum_{(S_1,\ldots,S_\ell)}  \left(\prod_{i=1}^\ell c^{(i)}_{S_i}\right)^2 \nonumber\\
+    &= \sum_S \sum_{\substack{(S_1,\ldots,S_\ell): \\ S_1\times\ldots S_\ell=S}}  \left(\prod_{i=1}^\ell c^{(i)}_{S_i}\right)^2
+\end{align}
+\begin{align}
+    n_2=\|q^{(1)}\ldots q^{(\ell)}\|^2 = \sum_{S} c_S^2 
+    = \sum_S \left( \sum_{\substack{(S_1,\ldots, S_\ell): \\ S_1\times\ldots\times S_\ell=S }} \left(c_{S_1}^{(1)}\ldots c_{S_\ell}^{(\ell)} \right) \right)^2 
+    = \sum_S \left( \sum_{\substack{(S_1,\ldots, S_\ell): \\ S_1\times\ldots\times S_\ell=S }} \prod_{i=1}^\ell c_{S_i}^{(i)} \right)^2 
+\end{align}
+Let $M$ be an upper bound of the number of terms involved in the summation $ \sum_{\substack{(S_1,\ldots, S_\ell): \\ S_1\times\ldots\times S_\ell=S }} $, then by Cauchy-Schwarz's inequality we have $ n_2\leq Mn_1 $.
+
+$M$ counts the number of different $(S_1,\ldots, S_\ell)$'s with $S_1\times \ldots \times S_\ell=S$. Since $S$ has degree at most $\deg$, we can bound $M$ by $ \ell^{\deg}$.
+
+The second bound can be obtained by applying Cauchy-Schwarz once.
+
+\end{proof}
+
+\subsection{Refinement for \cite{klivans2004learning}'s Theorem 10}
+\begin{lemma}
+Under the same condition as in \cite{klivans2004learning}'s Theorem 10, the PTF has margin on $X$ is at least $(1/t)^{O(r\log r + r\log\log t)}$. 
+\end{lemma}
+\begin{proof}
+We simply follow the construction in the original paper.
+$\|1-w^i\cdot x\|^2\leq 4$ can imply $\|(1-w^i\cdot x)^j\|^2\leq j^{O(j)}4^j \leq j^{O(j)}$.
+Then $\|a_j(1-w^i\cdot x)^j\|^2\leq 2^{2r}r^{O(r)}=r^{O(r)}$ follows.
+Thus $\|T_r(1-w^i\cdot x)\|^2=\|\sum_{j=0}^r a_j (1-w^i\cdot x)^j\|^2 \leq (r+1)^2 r^{O(r)} = r^{O(r)}$.
+Then, $\left(P(w^i\cdot x)\right)^{\log 2t}\leq (\log t)^{O(r\log t)}\times r^{O(r\log t)}\leq (r\log t)^{O(r\log t)}$.
+Finally, $\|p\|^2\leq (t+1)^2 (r\log t)^{O(r\log t)} \leq (t+1)^2 \left(  t^{O(r\log r + r\log\log t)}\right) = t^{O(r\log r + r\log\log t)}$.
+\end{proof}
+
+\subsection{Refinement for \cite{klivans2004learning}'s Theorem 7}
+\begin{lemma}
+Under the same condition as in \cite{klivans2004learning}'s Theorem 7, the PTF has margin on $X$ is at least $\left( \frac{\rho}{t\log t \log \frac{1}{\rho}} \right)^{O(t\log t\log 1/\rho)}$. 
+\end{lemma}
+\begin{proof}
+Using the same construction, we bound $\|p\|$.
+First, we have $\|\frac{2w^i\cdot x}{\rho}\|^2\leq \frac{4}{\rho^2}$ and $\|\left(\frac{2w^i\cdot x}{\rho}\right)^j\|^2\leq j^j\left(\frac{4}{\rho^2}\right)^j=\left(\frac{4j}{\rho^2}\right)^j$.
+$a(x), b(x)$ are polynomials of degree $O(\log t\log \frac{1}{\rho})$ with coefficients of magnitude $\left(\frac{1}{\rho}\right)^{O(\log t\log 1/\rho)}$.
+Thus
+\begin{align*}
+    \|a(2w^i\cdot x/\rho)\|^2 &\leq 
+    \left( \frac{\log t \log \frac{1}{\rho}}{\rho} \right)^{O(\log t\log 1/\rho)}  \times  \left(\frac{1}{\rho}\right)^{O(\log t\log 1/\rho)}\\
+    &\leq \left( \frac{\log t \log \frac{1}{\rho}}{\rho} \right)^{O(\log t\log 1/\rho)}.
+\end{align*}
+Same holds for $\|b(2w^i\cdot x/\rho)\|^2$.
+Finally we have $\|B(x)\|^2 \leq (t)^{O(t\log t\log 1/\rho)} \times \left( \frac{\log t \log \frac{1}{\rho}}{\rho} \right)^{O(t\log t\log 1/\rho)} = \left( \frac{t\log t \log \frac{1}{\rho}}{\rho} \right)^{O(t\log t\log 1/\rho)}$
+\end{proof}
+
+\section{Regret Lower Bound for Explore-then-Exploit Algorithms {\color{red}[TODO]}}
 

### 2018-08-14 main.tex
Add discussions on one-sided banditron and selectron

@@
 \section{Problem Statement}
-A multiclass linear classifier is defined by a matrix $W\in \mathbb{R}^{K\times d}$, where $K$ is the number of classes ($K\geq 3$) and $d$ is the dimension of the feature vector.
-A set of samples $\{(x_t, y_t)\}_{t=1}^T$ where $x_t\in \mathbb{R}^d$ and $y_t\in[K]$ is called \textit{linearly separable} if there exists a $W^*$ such that $ y_t= \argmax_{y\in[K]} (W^*x_t)_y $ for all $t\in[T]$.
-(Note that $(W^*x_t)_y$ can also be written as $\e_y^\top W^* x_t$)
-
-A set of samples $\{(x_t, y_t)\}_{t=1}^T$ is called \textit{linearly separable with a margin $\gamma$} if there exists a $W^*$ with $\|\e_i^\top W^*\|_2\leq 1$ for all $i$ and $(W^*x_t)_{y_t} \geq \max_{y\neq y_t} (W^*x_t)_{y} + \gamma$ for all $t$.
-For simplicity, we define the set where $W^*$ lies in as $\calW = \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W^*\|_2\leq 1\}$.
+A multiclass linear classifier is defined by a set of $K$ vectors $w^{(1)}, \ldots, w^{(K)}\in \mathbb{R}^d$ (or a compact matrix form $W = [w^{(1)}\ w^{(2)}\  \cdots\  w^{(K)}]^\top \in \mathbb{R}^{K\times d}$), where $K$ is the number of classes ($K\geq 3$) and $d$ is the dimension of the feature vector.
+A set of samples $\{(x_t, y_t)\}_{t=1}^T$ where $x_t\in \mathbb{R}^d$ and $y_t\in[K]$ is called \textit{linearly separable} if there exists a $w_*^{(1)}, \ldots, w_*^{(K)}$ (or simply $W_*$) such that $ y_t= \argmax_{y\in[K]} (W_{*}x_t)_y $ for all $t\in[T]$.
+
+A set of samples $\{(x_t, y_t)\}_{t=1}^T$ is called \textit{linearly separable with a margin $\gamma$} if there exists $W_*$ with $\|w^{(i)}_*\|_2\leq 1$ for all $i$ and $(W_{*}x_t)_{y_t} \geq \max_{y\neq y_t} (W_*x_t)_y + \gamma$ for all $t$.
+We define the set $\calW = \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W^*\|_2\leq 1\}$.
+Therefore, $W_*\in \calW$.
 
@@
    Predict $\tilde{y}_t=\argmax_y (W_tx_t)_y$ \\
-   Update $W_{t+1}\leftarrow W_t + (\e_{y_t}-\e_{\tilde{y}_t})x_t^\top$. 
+   Update $W_{t+1}\leftarrow W_t + (\e_{y_t}-\e_{\tilde{y}_t})x_t^\top$ \\
+   (same as updating $w^{(y_t)}_{t+1} \leftarrow w^{(y_t)}_t + x_t$ and $w^{(\hat{y}_t)}_{t+1} \leftarrow w^{(\hat{y}_t)}_t - x_t$ when $\hat{y}_t\neq y_t$). 
 }
@@
 \begin{align*}
-    \langle W_t, W^* \rangle &= \langle W_{t-1}, W^* \rangle + \langle (\e_{y_t}-\e_{\tilde{y}_t})x_t^\top, W^* \rangle \\
-    &= \langle W_{t-1}, W^* \rangle + (\e_{y_t}^\top W^* x_t-\e_{\tilde{y}_t}^\top W^* x_t) \\
-    &\geq \langle W_{t-1}, W^* \rangle + \gamma\one[\tilde{y}_t\neq y_t]. 
-\end{align*}
-By induction, we get $\langle W_{T+1}, W^* \rangle \geq \gamma\sum_{t=1}^T \one[\tilde{y}_t\neq y_t]$.
+    \langle W_t, W_* \rangle &= \langle W_{t-1}, W_* \rangle + \langle (\e_{y_t}-\e_{\tilde{y}_t})x_t^\top, W_* \rangle \\
+    &= \langle W_{t-1}, W_* \rangle + (\e_{y_t}^\top W_* x_t-\e_{\tilde{y}_t}^\top W_* x_t) \\
+    &\geq \langle W_{t-1}, W_* \rangle + \gamma\one[\tilde{y}_t\neq y_t]. 
+\end{align*}
+By induction, we get $\langle W_{T+1}, W_* \rangle \geq \gamma\sum_{t=1}^T \one[\tilde{y}_t\neq y_t]$.
 
@@
 \begin{align*}
-    \langle W_{T+1}, W^* \rangle \leq \|W_{T+1}\|_F\|W^*\|_F \leq \sqrt{2K\sum_{t=1}^T \one[\tilde{y}_t \neq y_t] \|x_t\|_2^2}\times 1 \leq \sqrt{2K\sum_{t=1}^T \one[\tilde{y}_t \neq y_t] } 
+    \langle W_{T+1}, W_* \rangle \leq \|W_{T+1}\|_F\|W_*\|_F \leq \sqrt{2K\sum_{t=1}^T \one[\tilde{y}_t \neq y_t] \|x_t\|_2^2}\times 1 \leq \sqrt{2K\sum_{t=1}^T \one[\tilde{y}_t \neq y_t] } 
 \end{align*}
@@
 \section{One-versus-all Perceptron}
+\label{sec:ova}
 Our assumption of linearly separable with a margin is 
 \begin{align}
- (W^*x_t)_{y_t} \geq (W^*x_t)_{y} + \gamma, \ \forall y\neq y_t. \label{eqn:weaker}
+ (W_*x_t)_{y_t} \geq (W_*x_t)_{y} + \gamma, \ \forall y\neq y_t. \label{eqn:weaker}
 \end{align}
@@
 
-For a moment, in this subsection we make the following stronger margin assumption (which we call \textit{one-versus-all separable} with a margin): 
+For a moment, in this section we make the following stronger margin assumption (which we call \textit{one-versus-all separable} with a margin): 
 \begin{align}
 \begin{cases}
-    (W^*x_t)_{y_t} \geq \gamma/2 \\
-    (W^*x_t)_y \leq -\gamma/2, \forall y\neq y_t.
+    (W_*x_t)_{y_t} \geq \gamma/2 \\
+    (W_*x_t)_y \leq -\gamma/2, \forall y\neq y_t.
 \end{cases}
@@
 \section{One-versus-all Kernel Perceptron}
-With the polynomial kernel defined in \cite{klivans2004learning}, we can transform the weaker assumption \eqref{eqn:weaker} in the original feature space to the stronger one \eqref{eqn:stronger} in a transformed feature space.
+%With the polynomial kernel defined in \cite{klivans2004learning}, we can transform the weaker assumption \eqref{eqn:weaker} in the original feature space to the stronger one \eqref{eqn:stronger} in a transformed feature space.
 Indeed, in the original feature space, class $i$ corresponds to an intersection of $K-1$ halfspaces: $ \{x: (w_i^*-w_j^*)^\top x \geq 0, \forall j\neq i\} $, which is the subject of \cite{klivans2004learning} (here, $w_i^{*\top}$ equals to $\e_i^\top W^*$ defined above).
@@
 Running kernelized version of Algorithm~\ref{alg:ova}, we can get $ K^2\left(\frac{d}{\gamma}\right)^{\mathcal{O}(K\log K\log (1/\gamma))} $ error bound directly.
+The idea here is to do a feature transformation such that if the original assumption \eqref{eqn:weaker} is satisfied, then in the transformed feature space, \eqref{eqn:stronger} will be satisfied, then we can run the one-versus-all perceptron given in \ref{sec:ova}.
+Under the original assumption, each class corresponds to an intersection of $K-1$ halfspaces in the feature spaces (i.e., class $i$ corresponds to $\{x\in\mathbb{R}^d: w_*^{(i)\top}x \geq w_*^{(j)\top}x, \ \forall j\neq i\}$).
+We want this region to become a halfspace in the transformed space.
+Fortunately, this is possible when there is a margin, and is exactly what is done in \cite{klivans2004learning}.
 
@@
    For $i=1,\ldots, \ell$ let $q^{(i)}(x)=\sum_S c^{(i)}_{S} x_S $ be a polynomial over $x_1, \ldots, x_d$ with $\|q^{(i)}\|^2\leq M_i$.
-Then (1) if $q^{(1)}\ldots q^{(\ell)}$ has degree at most $\deg$, we have $\|q^{(1)}\ldots q^{(\ell)}\|^2 \leq (\deg)^{O(\deg)} \prod_i M_i$, and (2) we have $\|q^{(1)}+\ldots+q^{(\ell)}\|^2\leq \ell(M_1+\ldots+M_\ell)$.
+Then (1) if $q^{(1)}\ldots q^{(\ell)}$ has degree at most $\deg$, we have $\|q^{(1)}\ldots q^{(\ell)}\|^2 \leq \ell^{\deg} \prod_i M_i$, and (2) we have $\|q^{(1)}+\ldots+q^{(\ell)}\|^2\leq \ell(M_1+\ldots+M_\ell)$.
 \end{lemma}
@@
 Finally we have $\|B(x)\|^2 \leq (t)^{O(t\log t\log 1/\rho)} \times \left( \frac{\log t \log \frac{1}{\rho}}{\rho} \right)^{O(t\log t\log 1/\rho)} = \left( \frac{t\log t \log \frac{1}{\rho}}{\rho} \right)^{O(t\log t\log 1/\rho)}$
-\end{proof}
+
+%Another refinement is that we can show $|B(x)|\geq $
+
+\end{proof}
+
+%\subsection{Possibilities of using other kernels}
+
+\section{A Recipe of Designing Efficient Algorithms}
+We have seen that if the data is ``one-versus-all'' separable with a margin, then constant error is achievable.
+To have constant error, a key is that every time an error occurs, the learner should make significant progress.
+
+Besides one-versus-all separability, are there other kinds of conditions under which we can easily make progress when we make a mistake?
+If such condition exists, then we have the following recipe of designing algorithms that have constant error bound:
+\begin{itemize}
+    \item Design an algorithm that has constant mistake bound under some assumption. 
+    \item Design feature transformation such that our original linear separability satisfies the above assumption in the transformed space. 
+\end{itemize}
+Our kernel perceptron exactly follows the above procedure. Following is another example.
+
+\subsection{One-sided banditron}
+Consider the following algorithm. \\
+\begin{algorithm}[H]
+\caption{Ond-sided banditron}
+\label{alg:one-sided}
+\textbf{Define}: $\Omega\subseteq \mathbb{R}^{K\times d}$ is a convex set, and we assume $W^* \in \Omega_t$ for all $t$. Learning rate $\eta$. \\
+\textbf{Initialize}: $W_1=\mathbf{0}$. \\
+\For{$t=1, \ldots, T$}{
+   Receive $x_t\in \mathbb{R}^d$. \\
+   Predict $\hat{y}_t = \argmax_{y\in[K]} (W_tx_t)_y$. \\
+   \If{$\hat{y}_t \neq y_t$}{
+       $W_{t+1}'\leftarrow W_t - \eta\e_{\hat{y}_t} x_t^\top$.\\
+       $W_{t+1}=\Pi_{\Omega_{t+1}}(W_{t+1}') \triangleq \argmin_{W\in\Omega_{t+1}}\|W-W_{t+1}'\|_F$. 
+   }
+}
+\end{algorithm}
+\ \\
+The above algorithm is similar to banditron but only performs \textit{one-sided} update and never explicitly explores to get label.
+Below we check under what condition can this algorithm have constant error bound.
+
+Following standard analysis for online gradient descent, we have when the learner makes a mistake:
+\begin{align}
+    \|W_{t+1}-W^*\|_F^2 &\leq \|W_{t+1}'-W^*\|_F^2 = \|W_t - W^* - \eta \e_{\hat{y}_t}x_t^\top \|_F^2 \nonumber \\
+    &= \|W_t-W^*\|_F^2 - 2\eta ((W_tx_t)_{\hat{y}_t} - (W^*x_t)_{\hat{y}_t}) + \eta^2\|x_t\|_2^2 
+    \label{eqn:update_rule}
+    %&\leq \|W_t-W^*\|_F^2 - 2\eta ((W_tx_t)_{\hat{y}_t} - (W^*x_t)_{\hat{y}_t}) + \eta^2. 
+\end{align}
+
+We see that if the condition 
+\begin{align}
+    (W_tx_t)_{\hat{y}_t} - (W^*x_t)_{\hat{y}_t} \geq \Delta  \label{eqn:one-sided condition}
+\end{align}
+holds whenever $\hat{y}_t\neq y_t$ and we pick $\eta = \Delta/\sup_\tau\|x_\tau\|_2^2$, then we always have
+\begin{align*}
+    \|W_{t+1}-W^*\|_F^2 \leq \|W_{t}-W^*\|_F^2 -\frac{2\Delta^2}{\sup_\tau\|x_\tau\|_2^2} + \frac{\Delta^2}{\sup_\tau\|x_\tau\|_2^2} = \|W_{t}-W^*\|_F^2 - \frac{\Delta^2}{\sup_\tau\|x_\tau\|_2^2} 
+\end{align*}
+whenever $\hat{y}_t\neq y_t$. Then we have the error bound 
+\begin{align*}
+    \sum_{t=1}^T \one[\hat{y}_t\neq y_t] \leq \frac{\|W^*\|_F^2 \sup_{\tau}\|x_\tau\|_2^2}{\Delta^2}   
+\end{align*}
+because $\|W_t - W^*\|_F^2$ is always non-negative and $\|W_1-W^*\|_F^2=\|W^*\|_F^2$. \\
+
+The following analysis leads to the same bound but is more standard. Let $M_t=\one[\hat{y}_t\neq y_t]$. By \eqref{eqn:update_rule} and \eqref{eqn:one-sided condition} we have
+\begin{align*}
+    \Delta \sum_{t=1}^T M_t  \leq \sum_{t=1}^T M_t\left((W_tx_t)_{\hat{y}_t} - (W^*x_t)_{\hat{y}_t}\right) \leq \frac{\|W^*\|_F^2}{2\eta} + \frac{\eta}{2}\sup_\tau\|x_\tau\|_2^2\sum_{t=1}^T M_t
+\end{align*}
+Picking appropriate $\eta$ and solving for $\sum_{t=1}^T M_t$ we get the same error bound.
+
+A candidate set of assumptions that leads to \eqref{eqn:one-sided condition} is the \textit{sum-to-zero} assumption: 
+\begin{itemize}
+    \item $\sum_{i=1}^K \e_i^\top W^* = 0$ (so we pick $\Omega_t = \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2\leq 1, \sum_{i=1}^K \e_i^\top W=0\}$) \\
+    \item $ (W^*x_t)_y \leq -\Delta $ for all $y\neq y_t$. 
+\end{itemize}
+They are similar to the assumptions made in \cite{2018arXiv180610745F}.
+We see that the above two conditions indeed lead to~\eqref{eqn:one-sided condition}: $(W_tx_t)_{\hat{y}_t} = \max_y (W_tx_t)_y \geq \frac{1}{K}\sum_{i=1}^K (W_tx_t)_i =0 $ (recall that we always project $W_t$ back to $\Omega_t$), and when $\hat{y}_t\neq y_t$ we have $(W^*x_t)_{\hat{y}_t}\leq -\Delta$.
+Unfortunately, this set of assumptions is even stronger than the one-versus-all separable assumption.
+
+Although the one-versus-all assumption is similar, there we do not perform projection for $W_t$, so it is possible that $\max_y (W_tx_t)_y < 0$. It that case, what we do is uniformly sample a label.\\
+
+\textbf{Questions}:
+\begin{itemize}
+\item Can we avoid the projection step for one-sided banditron (just like perceptron)?
+\item Are there other natural assumptions that guarantee \eqref{eqn:one-sided condition}? 
+\end{itemize}
+
+\subsection{Algorithms that can update without true labels}
+Algorithm~\ref{alg:one-sided} can update without the information of $y_t$.
+One can think of Algorithm~\ref{alg:one-sided} as a gradient algorithm  on the loss function $\ell_t(W) = \one[\hat{y}_t\neq y_t](Wx_t)_{\hat{y}_t}$.
+As a comparison, one can think of the surrogate loss function in \cite{2018arXiv180610745F} as $\ell_t(W)=\sum_{y=1}^K \one[y\neq y_t][\Delta+(Wx_t)_y]_+ $ (some scaling and notations are changed for better comparison), whose inverse propensity weighting estimator becomes $\tilde{\ell}_t(W)= \frac{1}{p_{t,\hat{y}_t}}\one[\hat{y}_t\neq y_t][\Delta+(Wx_t)_{
+\hat{y}_t}]_+$. One can see that they are closely related, except that in~\cite{2018arXiv180610745F}
+when $(Wx_t)_{\hat{y}_t}\leq -\Delta$, the loss for $W$ is set to zero (which makes no difference under the sum-to-zero assumption).
+
+\section{Logarithmic Regret for Strongly Convex Losses}
+\subsection{Gradient descent}
+In some previous works (we will visit them in the next subsection), it is assumed that the labels are generated with the following process: 
+\begin{align}
+    p(y|x) = \nabla_y\Phi(W^*x), 
+\end{align}
+which some $\Phi: \mathbb{R}^K \rightarrow \mathbb{R}$.
+The margin assumption is defined as 
+\begin{align}
+    p(y_t|x_t) - \max_{y\neq y_t}p(y|x_t) \geq \Delta, \forall t.  \label{eqn:new margin}
+\end{align}
+This margin assumption is a special case of the Tsybakov condition investigated in ~\cite{agarwal2013selective}. 
+Defining $\hat{y}_t = \argmax_y \nabla\Phi(W_tx_t)$ and $y^*_t = \argmax_y \nabla\Phi(W^*x_t) $ The regret is defined as
+\begin{align}
+    \Reg_T &= \sum_{t=1}^T \E\left[ \one[\hat{y}_t\neq y_t] - \one[y_t^*\neq y_t]\right] \nonumber \\
+    &= \sum_{t=1}^T \sum_{i=1}^K \left(\one[\hat{y}_t\neq i] - \one[y^*_t\neq i]\right)\nabla_i\Phi(W^*x_t). \label{eqn:new regret}
+\end{align}
+
+Below we argue that if $\Phi$ is strongly convex and smooth, then the following algorithm (exactly the algorithm in \cite{agarwal2013selective}) achieves regret logarithmic in $T$.
+
+\begin{assumption}
+\begin{align*}
+     \Phi(v) + \inner{\nb\Phi(v),u-v} + \frac{\gamma_\ell}{2}\|u-v\|_2^2 \leq \Phi(u)-\Phi(v)\leq \Phi(v) + \inner{\nb\Phi(v),u-v} + \frac{\gamma_u}{2}\|u-v\|_2^2. 
+\end{align*}
+That is, $\Phi$ is $\gamma_\ell$-strongly convex and $\gamma_u$-smooth. 
+\end{assumption}
+
+\begin{algorithm}[H]
+\caption{Selectron \cite{agarwal2013selective}}
+\textbf{Define}: $\epsilon\triangleq \Delta/(2\gamma_u C')$, where $C'$ is defined in Lemma~\ref{lem:decreasing error} $\eta\triangleq \frac{\sup_{W\in\Omega}\|W\|_F^2}{\gamma_\ell}$, $\Omega\triangleq$ a convex set where $W^*$ lies in.
+\\
+\textbf{Definition}: $\ell_t(W)=\Phi(Wx_t) - (Wx_t)_{y_t}$.\\
+\textbf{Initialization}: $W_1=0, M_1=I$.\\ 
+\For{$t=1, \ldots, T$}{
+   Observe $x_t$. \\
+   \If{$ \| x_t \|_{M_t^{-1}} \geq \epsilon$}{
+       Draw $\tilde{y}_t \sim \text{unif}([K])$. 
+   }
+   \Else{
+       Draw $\tilde{y}_t = \hat{y}_t \triangleq \argmax_{y\in[K]}(W_tx_t)_y$. 
+   }
+   \If{ $\tilde{y}_t=y_t$ }{
+       $Z_t\leftarrow 1$, \\
+       $M_{t+1}\leftarrow M_t + Z_tx_tx_t^\top$,\\
+       $W_{t+1} = \argmin_{W\in\Omega}\left\{ \sum_{s=1}^t Z_s \ell_s(W) + \frac{1}{2\eta}\|W\|_F^2 \right\}$. 
+   }
+   \Else{
+       $Z_t\leftarrow 0$,  \\
+       $M_{t+1}\leftarrow M_t$,\\
+       $W_{t+1}\leftarrow W_t$.
+   }
+
+}
+\end{algorithm}
+
+\begin{theorem}
+\label{lemma:new main}
+The selective sampling algorithm achieves
+\begin{align*}
+    \Reg_T\leq \tilde{O}\left( \frac{\gamma_u^2}{\gamma_\ell^2}\frac{K^2d}{\Delta^2} \right). 
+\end{align*}
+\end{theorem}
+
+The proof of this theorem is decomposed to the following three lemmas.
+
+\begin{definition}
+$\norm{W}_{M}^2\triangleq \sum_{i=1}^K \norm{\e_i^\top W}_{M}^2$.
+\end{definition}
+With this definition we have $\|Wx_t\|_2^2 = \sum_{i=1}^K (\e_i^\top Wx_t)^2 \leq \sum_{i=1}^K \|\e_i^\top W\|_M^2 \|x_t\|_{M^{-1}}^2\leq \|W\|_M^2 \|x_t\|_{M^{-1}}^2$
+
+\begin{lemma}[Proposition 1 of \cite{agarwal2013selective}]
+\label{lem:decreasing error}
+With probability at least $1-\delta$,
+\begin{align*}
+\|W_t-W^*\|_{M_t} \leq C' \triangleq \frac{2C\sqrt{dK}}{\gamma_\ell} + \sqrt{\frac{2}{\eta \gamma_\ell}}\sup_{W\in \Omega}\|W\|_F, 
+\end{align*}
+where $C$ hides some $\log t$ and $\log(1/\delta)$ terms (defined in the proof). 
+\end{lemma}
+
+\begin{proof}
+By the first-order optimality condition on $W_{t}$ we have
+\begin{align*}
+    0\geq \inner{\frac{1}{\eta} W_{t} + \sum_{s=1}^{t-1} Z_s\nb\ell_s(W_t), W_{t}-W^*}. 
+\end{align*}
+By the definition of $\ell_t$, 
+\begin{align*}
+    0 &\geq \inner{\frac{1}{\eta} W_{t} + \sum_{s=1}^{t-1} Z_s\nb\ell_s(W_t),  W_{t}-W^*} \\
+    & = \inner{\sum_{s=1}^{t-1} Z_s\left(\nb\Phi(W_t x_s) - \e_{y_s} \right)x_s^\top,  W_{t}-W^*} + \frac{1}{\eta}\inner{W_t, W_t-W^*} \\
+    & = \inner{\sum_{s=1}^{t-1} Z_s\left(\nb\Phi(W_t x_s) - \nb\Phi(W^*x_s) + \xi_s \right)x_s^\top, W_{t}-W^*} + \frac{1}{\eta}\inner{W_t, W_t-W^*} , \tag{let $\xi_s\triangleq \nb\Phi(W^*x_s)-\e_{y_s}$} \\
+    & = \inner{\sum_{s=1}^{t-1} Z_s\left(\nb\Phi(W_t x_s) - \nb\Phi(W^*x_s) + \xi_s \right), W_t x_s- W^*x_s} + \frac{1}{\eta}\inner{W_t, W_t-W^*}, \\
+    & \geq \gamma_\ell \sum_{s=1}^{t-1} Z_s\|W_tx_s-W^*x_s\|_2^2 + \sum_{s=1}^{t-1} Z_s\inner{\xi_s, W_tx_s-W^*x_s} + \frac{1}{\eta} \inner{W_t, W_t-W^*}. 
+\end{align*}
+Rearranging gives 
+\begin{align}
+    \sum_{s=1}^{t-1} Z_s\inner{\xi_s, W^*x_s-W_tx_s} &\geq \gamma_\ell \sum_{s=1}^{t-1} Z_s\|W_tx_s-W^*x_s\|_2^2 + \frac{1}{\eta} \inner{W_t, W_t-W^*} \nonumber \\
+    &= \gamma_\ell \sum_{s=1}^{t-1} Z_s\sum_{i=1}^K \langle \e_iW_t-\e_iW^*, x_s\rangle^2 + \frac{1}{\eta} \inner{W_t, W_t-W^*} \nonumber \\
+    & \geq \gamma_\ell \|W_t-W^*\|_{M_t}^2 - \frac{2}{\eta} \sup_{W\in \Omega}\|W\|_F^2.  \label{eqn:lower}
+\end{align}
+On the other hand, 
+\begin{align}
+    \sum_{s=1}^{t-1} Z_s\inner{\xi_s, W^*x_s-W_tx_s} &= \sum_{i=1}^K  \sum_{s=1}^{t-1} Z_s\xi_{s,i} ((W^*x_s)_i-(W_tx_s)_i) \nonumber \\
+    & = \sum_{i=1}^K  \sum_{s=1}^{t-1} Z_s\xi_{s,i} \langle W^*_i-W_{t,i}, x_s\rangle \nonumber \\
+    &\leq \sum_{i=1}^K \Bigg\| \sum_{s=1}^{t-1} Z_s\xi_{s,i}x_s \Bigg\|_{M_t^{-1}} \|W^*_i-W_{t,i}\|_{M_t}.   \label{eqn:upper}
+\end{align}
+Note that $\{\xi_{s,i}\}_{s}$ is a martingale difference sequence.
+Using \cite{filippi2010parametric}'s Lemma 1 in Appendix A.1 with constant $c_m = \sup_\tau\|x_\tau\|_2=1, \lambda_0 = \frac{1}{\eta\gamma_\ell}, R=2$ yields with probability at least $1-\delta/K$
+\begin{align*}
+    \Bigg\| \sum_{s=1}^{t-1} Z_s\xi_{s,i}x_s \Bigg\|_{M_t^{-1}} \leq 2\sqrt{3+2\log(1+\eta\gamma_\ell)}\sqrt{d\log t}\sqrt{\log(dK/\delta)} \triangleq \sqrt{d}C.
+\end{align*}
+Thus, by~\eqref{eqn:upper} we get with proability $1-\delta$
+\begin{align*}
+    \sum_{s=1}^{t-1} Z_s\inner{\xi_s, W^*x_s-W_tx_s} &= C\sqrt{d}\sum_{i=1}^K \|W^*_i-W_{t,i}\|_{M_t} = C\sqrt{dK} \|W^*-W_{t}\|_{M_t}, 
+\end{align*}
+where in the last inequality we use $\sum_{i=1}^K a_i\leq \sqrt{K}\sqrt{\sum_{i=1}^K a_i^2}$. Combining with~\eqref{eqn:lower} we get 
+\begin{align*}
+    \|W_t-W^*\|_{M_t} \leq \frac{2C\sqrt{dK}}{\gamma_\ell} + \sqrt{\frac{2}{\eta \gamma_\ell}}\sup_{W\in \Omega}\|W\|_F. 
+\end{align*}
+
+\end{proof}
+
+\begin{lemma}
+\label{lem: xbounded}
+If $\|x_t\|_{M_t^{-1}}\leq \epsilon = \Delta/(2\gamma_u C')$, then $\hat{y}_t=y^*_t$. 
+\end{lemma}
+\begin{proof}
+\begin{align*}
+\nb \Phi_{y_t^*}(W^*x_t) - \nb\Phi_{\hat{y}_t}(W^*x_t) 
+ &\leq \nb \Phi_{y_t^*}(W^*x_t) -    \nb\Phi_{\hat{y}_t}(W^*x_t) 
+ - \nb \Phi_{y_t^*}(W_tx_t) + \nb \Phi_{\hat{y}_t}(W_tx_t) \\
+ & \leq 2\gamma_u \|W^*x_t-W_tx_t\|_2 \\
+ & \leq 2\gamma_u \|W^*-W_t\|_{M_t}\|x_2\|_{M_t^{-1}} \\
+ & \leq \Delta. \tag{by Lemma~\ref{lem:decreasing error}}
+\end{align*}
+By the margin assumption \eqref{eqn:new margin}, $\hat{y}_t = y_t^*$. 
+\end{proof}
+
+From Lemma~\ref{lem: xbounded} and the regret definition~\eqref{eqn:new regret}, we see that in the rounds $\|x_t\|_{M_t^{-1}}\leq \epsilon$, the regret is zero.
+The following lemma bounds the number of rounds with $\|x_t\|_{M_t^{-1}} > \epsilon $
+
+\begin{lemma}
+\label{lem:N}
+$ \sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right] \leq \frac{K\ln T\ln \frac{1}{\delta}}{\epsilon^2}$ with probability at least $1-\delta$. 
+\end{lemma}
+
+\begin{proof}
+\begin{align*}
+    &~ \sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right]\\
+    &\leq \left(K\ln \frac{1}{\delta}\right)\sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right]Z_t \tag{when $\|x_t\|_{M_t^{-1}}\geq \epsilon$, $\tilde{y}_t=y_t$ with probability $\frac{1}{K}$} \\
+    & \leq \frac{K\ln \frac{1}{\delta}}{\epsilon^2}\sum_{t=1}^T \norm{x_t}_{M_t^{-1}}^2 Z_t \leq \frac{K\ln T\ln \frac{1}{\delta}}{\epsilon^2}. 
+\end{align*}
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{lemma:new main}]
+    By Lemma~\ref{lem: xbounded} and~\ref{lem:N}, 
+    \begin{align*}
+        \Reg_T &= \sum_{t=1}^T \sum_{i=1}^K \left(\one[\hat{y}_t\neq i] - \one[y^*_t\neq i]\right)\nabla_i\Phi(W^*x_t) \\
+        & \leq \sum_{t=1}^T \left(\one\left[\|x_t\|_{M_t^{-1}}>\epsilon\right]\right) \sum_{i=1}^K \nabla_i\Phi(W^*x_t) \\
+        & \leq \sum_{t=1}^T \left(\one\left[\|x_t\|_{M_t^{-1}}>\epsilon\right]\right) \\
+        & \leq \tilde{O}\left( \frac{K\gamma_u^2C'^2}{\Delta^2} \right). 
+    \end{align*}
+    Using the definition of $C'$ we get the final bound. 
+\end{proof}
+
+\subsection{Revisiting the stochastic assumptions made in \cite{crammer2013multiclass} and \cite{agarwal2013selective}}
+In \cite{crammer2013multiclass} and \cite{agarwal2013selective}, the feature vectors $x_t$'s are adversarially picked, while $y_t$ is generated based on some conditional distribution based on $x_t$.
+For example, in \cite{crammer2013multiclass}, the label is generated through
+\begin{align}
+    p(y_t = i | x_t) = \frac{\alpha + (W^*x_t)_i}{\alpha+1}, \label{eqn:confidit assumption}
+\end{align}
+where $W^* \in \Omega \triangleq \{W\in \mathbb{R}^{K\times d}: \sum_{i=1}^K (Wx_t)_i = \alpha+1-K\alpha \text{\ and\ } -\alpha \leq (Wx_t)_i\}$; a valid $\Phi$ is 
+\begin{align}
+    \Phi(u) = \frac{1}{2(\alpha+1)}\|u\|_2^2 + \frac{\alpha}{\alpha+1}\sum_{i=1}^K u_i. 
+\end{align}
+in \cite{agarwal2013selective}, the labels are generated by 
+\begin{align}
+    p(y_t = i | x_t) = \frac{\exp((W^*x_t)_i)}{\sum_{j=1}^K \exp((W^*x_t)_j) },
+\end{align}
+where $W^* \in \Omega \triangleq \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2 \leq D \}$, and $\Phi$ can be defined as
+\begin{align}
+    \Phi(u) = \log\left(\sum_{i=1}^K \exp(u_i) \right). 
+\end{align}
+
+\textbf{Discussions}:  \\
+\begin{itemize}
+    \item Although \cite{hazan2011newtron, foster2018logistic} do not make stochastic assumptions, their loss functions are indeed strongly-convex and smooth (although $\gamma_u/\gamma_\ell$ can be quite large).
+It is worth notice that \cite{foster2018logistic} also obtained some logarithmic bound (their Theorem 3), but the bound is margin-independent.
+It seems that their Theorem 3 is tighter than our bound here.
+Not sure if it is because they use improper learning (we indeed should see whether improper learning helps in our problem).
+There is a $\alpha$ parameter in \cite{hazan2011newtron}, somehow it looks related to margin.
+    \item How is the assumptions in this section related to \cite{pillaud2017exponential}? 
+    \item We indeed have tried to use this kind of selective sampling idea to get finite error bound (see Section \ref{sec:kwik}).
+But there it seems that impossible to find a $\Phi(Wx_t)$ that is at the same time strongly convex, $\Phi(Wx_t)\geq 0$, $\Phi(W^*x_t)\leq 0$ (or other type of losses with which a logarithmic/constant regret bound implies logarithmic/constant error bound).
+\end{itemize}
+
+%For simplicity, now we focus on the model assumed in \cite{crammer2013multiclass}.
+Besides the model, we assume the following ``margin assumption'' that is suitable for this kind of stochastic model:
+%\begin{align}
+%p(y_t|x_t) > \max_{y\neq y_t} p(y|x_t) + \gamma. 
+%\end{align} \label{eqn:stochastic margin}
+%This is also similar to the gap condition in \cite{pillaud2017exponential}. When this margin assumption is applied to the model assumption~\eqref{eqn:confidit assumption}, we get 
+%\begin{align}
+%    (W^*x_t)_{y_t} \geq \max_{y\neq y_t} (W^*x_t)_{y} + (\alpha+1)\gamma. 
+%\end{align}
+%This is similar to the linear separability in the non-stochastic case. But this is not enough for~\eqref{eqn:one-sided condition}. To make \eqref{eqn:one-sided condition} holds, we can
+
+%Below is a set of assumptions that is sufficient for \eqref{eqn:one-sided condition}: 
+%\begin{itemize}
+%    \item $\|\e_i^\top W^*\|_2\leq 1$ for all $i$ and $ \|x\|_2\leq 1 $ 
+%    \item $W^*_{ij} \geq 0, x_j \geq 0, \forall i,j$ (which implies $(W^*x)_y\geq 0$ for all $x$ and $y$) \\ 
+%    \item $(W^*x_t)_{y_t} \geq K\max_{y\neq y_t}(W^*x_t)_{y}  + 2K\Delta$ 
+%    \item Pick $\Omega_t = \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2\leq 1, W_{ij}\geq 0, \sum_{i=1}^K (Wx_t)_i \geq 2K\Delta \}$ (one can verify that $\Omega_t$ is convex, and $W^*\in \Omega_t$ if $W^*$ satisfies the above three assumptions).
+%\end{itemize}
+%To see why these assumptions imply \eqref{eqn:one-sided condition}, suppose that $\hat{y}_t\neq y_t$.
+Note that $(W_tx_t)_{\hat{y}_t} \geq \frac{1}{K}\sum_{i=1}^K (W_tx_t)_i\geq 2\Delta$, where the first inequality is because $\hat{y}_t=\argmax_y(W_tx_t)_i$ and the second inequality is because $W_t\in\Omega_t$.
+On the other hand,
+
+\section{A KWIK Algorithm {\color{red} [TODO]}}
+\label{sec:kwik}
+%\textbf{Observation}. Alekh's paper's results can be generalized to losses with $\Phi_t$ a strongly and smoothly convex function. 
+\begin{assumption}
+$\|x_t\|_2^2\leq 1$. There is a $W^*\in\mathcal{W}$ such that $\ell_t(W^*)\leq 0$ for all $t$ ($\ell_t$ and $\mathcal{W}$ are defined below).  
+\end{assumption}
+
+\begin{algorithm}[H]
+\caption{KWIK Banditron}
+\textbf{Input}: $D\geq 2$, $\epsilon$ (picked in a later lemma). \\
+\textbf{Definition}: 
+\begin{align*}
+    \ell_t(W) &\triangleq [1-(Wx_t)_{y_t} + \max_{r\neq y_t}(Wx_t)_r]_+^2 \ \ \ \ \text{(squared hinge loss)} \\
+    & = \Phi_t(Wx_t), 
+    %\Phi_t(z) \triangleq \sum_{i\neq y_t} \psi(z_{y_t}-z_i).
+\end{align*}
+where $\Phi_t(z)\triangleq [1-\e_{y_t}^\top z + \max_{r\neq y_t} \e_r^\top z]_+^2$. \\
+Also, define $\mathcal{W}=\{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2\leq D \text{\ for all }i\in[K]\}$. \\
+\textbf{Initialization}: $W_1=0, M_1=I$.\\ 
+\For{$t=1, \ldots, T$}{
+   Observe $x_t$. \\
+   \If{$ \| x_t \|_{M_t^{-1}} \geq \epsilon$ {\color{red} \text{and} $\|W_t-W^*\|_F\geq 1$}}{
+       Draw $\tilde{y}_t \sim \text{unif}([K])$. 
+   }
+   \Else{
+       Draw $\tilde{y}_t = \hat{y}_t \triangleq \argmax_{r\in[K]}(W_tx_t)_r$. 
+   }
+   \If{ $\tilde{y}_t=y_t$ }{
+       $Z_t\leftarrow 1$, \\
+       $M_{t+1}\leftarrow M_t + Z_t\ell_t(W_t)x_tx_t^\top$,\\
+       $W_{t+1} \leftarrow \Pi_{\mathcal{W}} (W_t - \eta_{t+1}\nabla \ell_t(W_t))$, \ \ \ \ \ where $\eta_{t+1} = \frac{1}{8}$. \\
+       ($\Pi_{\mathcal{W}}$ is the projection operator onto $\mathcal{W}$ w.r.t. Frobenius norm)
+   }
+   \Else{
+       $Z_t\leftarrow 0$,  \\
+       $M_{t+1}\leftarrow M_t$,\\
+       $W_{t+1}\leftarrow W_t$.
+   }
+
+}
+\end{algorithm}
+\iffalse
+We will pick 
+\begin{align*}
+     \psi(u)=\begin{cases}
+        \frac{1}{2K(1-D)^2}(u-D)^2 - \frac{1}{2K}, & \text{if $u\geq 1$} \\
+        \left(1+\frac{1}{K(1-D)}\right)u^2 + \left(-2-\frac{1}{K(1-D)}\right)u + 1 &\text{if $u\leq 1$},  
+     \end{cases}
+\end{align*}
+It has the following properties: \\
+(1) It is continuous and differentiable. \\
+(2) It is $\frac{1}{2K(1-D)^2}$-strongly convex and $1$-smooth. \\
+(3) It decreases in $[-D,D]$, passing through $(0,1),(1,0)$, and $(D,\frac{-1}{2K})$. \\
+(4) Its minimum value $\frac{-1}{2K}$ is attained at $u=D$.
+
+\begin{lemma} 
+ For the above specific choice of $\psi$, $\Phi_t$ is $\frac{1}{2KD^2}$-strongly convex and $2K$-smooth (i.e., its Hessian has eigenvalues all within $[\frac{1}{2KD^2}, 2K]$).
+
+\end{lemma}
+\begin{proof}
+It is clear that $\frac{\partial^2}{\partial z_j\partial z_i}\Phi_t(z)=0$ for $i\neq j$.
+Also, $\frac{\partial^2}{\partial^2 z_i} \Phi_t(z)\geq \frac{1}{2K(1-D)^2}\geq \frac{1}{2KD^2}$ and $\frac{\partial^2}{\partial^2 z_i} \Phi_t(z)\leq K\left(1+\frac{1}{K(1-D)}\right)\leq 2K$.
+\end{proof}
+
+\begin{lemma}
+\label{lemma:error_cond}
+If $\argmax_r (Wx_t)_r = y_t$, then $\ell_t(W) \leq K$; 
+If $\argmax_r (Wx_t)_r \neq y_t$, then $\ell_t(W) \geq 1$.  
+\end{lemma}
+\begin{proof}
+If $\argmax_r (Wx_t)_r = y_t$, then $z_{y_t}-z_i\geq 0$ for all $i$, and thus $\Phi_t(z)< K\psi(0)=K$; 
+If $\argmax_r (Wx_t)_r \triangleq j \neq y_t$, then $\Phi_t(z)\geq \psi(z_{y_t}-z_j) - K\times \frac{1}{2K}\geq \psi(0)-\frac{1}{2}=\frac{1}{2}$. 
+This is clear by the definition of $\ell_t$. 
+\end{proof}
+\fi
+%\begin{definition}
+%$\|W\|_M^2 \triangleq \sum_{i=1}^K \|\e_i^\top W\|_M^2 $.\\
+%$\gamma_\ell \triangleq \frac{1}{2KD^2}$; $\gamma_u\triangleq 2K$ (convexity and smoothity of $\Phi_t$). 
+%\end{definition}
+
+%\begin{lemma}
+%For any $W^*\in \mathcal{W}$, with probability at least $1-\delta$, 
+%\begin{align*} 
+%    \|W_t-W^*\|_{M_t} \leq \tilde{\mathcal{O}}\left(\frac{\sqrt{Kd}}{\gamma_\ell} + D\sqrt{\gamma}\right).
+%\end{align*}
+%(the $\tilde{\mathcal{O}}$ notation hides $\ln T$, $\ln \frac{1}{\delta}$, $\ln \frac{1}{\gamma}$ factors)
+%\end{lemma}
+%\begin{proof}
+%By the first order optimality condition, we have for all $W^*\in \mathcal{W}$, 
+%\begin{align*}
+%    \inner{\gamma W_t+\sum_{s=1}^{t-1}Z_s \nabla \ell_s(W_t), W^*-W_t}\geq 0. 
+%\end{align*}
+%Rearranging it and plugging in the property $\nb\ell_s(W)=\nb\Phi_s(Wx_s)x_s^\top$ gives 
+%\begin{align}
+%    \sum_{s=1}^{t-1} Z_s\inner{ -\nb\Phi_s(W^*x_s),W_tx_s-W^*x_s} \geq  \sum_{s=1}^{t-1} Z_s\inner{ \nb\Phi_s(W_t x_s)-\nb\Phi_s(W^*x_s),W_tx_s-W^*x_s}+\gamma\inner{W_t, W_t-W^*}. 
+%    \label{eqn:key}
+%\end{align}
+%By $\Phi_s$'s convexity and that $\norm{W}_F^2\leq KD^2$ for all $W\in \mathcal{W}$, the RHS of \eqref{eqn:key} can be lower bounded by 
+%\begin{align*}
+%    \gamma_\ell\sum_{s=1}^{t-1} Z_s\norm{W_t x_s-W^*x_s}_2^2 - 2\gamma KD^2 \geq \gamma_\ell \norm{W_t-W^*}_{M_t}^2-2\gamma KD^2. 
+%\end{align*}
+%The LHS is upper bounded by 
+%\begin{align*}
+%    \sum_{i=1}^K \sum_{s=1}^{t-1} Z_s (-\nb_i\Phi_s(W^*x_s))\inner{\e_iW_t-\e_iW^*, x_s}
+%\end{align*}
+%\end{proof}
+
+\begin{lemma}
+\label{lemma:bound_gradient}
+$\norm{\nb\ell_t(W)}_F^2 \leq 8\ell_t(W)$. 
+\end{lemma}
+\begin{proof}
+$    \|\nb\ell_t(W)\|_F^2 = \|\nb\Phi_t(Wx_t)x_t^\top\|_{F}^2 \leq \left(2\sqrt{\Phi_t(Wx_t)}\right)^2\times 2\|x_t\|_{2}^2 \leq 8\ell_t(W).  
+$
+\end{proof}
+
+\begin{lemma}
+\label{lemma:decreasing error}
+Let $L_{t+1}\triangleq \sum_{s=1}^t Z_s\ell_s(W_s)$. Then 
+$\|W_{t+1}-W^*\|_F^2 \leq \exp\left(-\frac{L_{t+1}}{32KD^2}\right)$. 
+\end{lemma}
+\begin{proof}
+Let $Z_{t}=1$. 
+\begin{align*}
+    \|W_{t+1}-W^*\|_F^2 &\leq \|W_t - \eta_{t+1}\nb\ell_t(W_t)-W^*\|_F^2 \\
+    & = \| W_t - W^* \|_F^2 - 2\eta_{t+1}\inner{\nb\ell_t(W_t),W_t-W^*}_F + \eta_{t+1}^2\|\nb\ell_t(W_t)\|_F^2.  
+\end{align*}
+By the separable assumption we have $\ell_t(W^*)\leq 0$.
+Since $\ell_t$ is convex, $\inner{\nb\ell_t(W_t), W_t-W^*} \geq \ell_t(W_t)-\ell_t(W^*)\geq \ell_t(W_t)$.
+Continuing the above calculation and using Lemma~\ref{lemma:bound_gradient}, we get
+\begin{align*}
+    \|W_{t+1}-W^*\|_F^2 &\leq \|W_t-W^*\|_2^2 - 2\eta_{t+1}\ell_t(W_t) + 8\eta_{t+1}^2 \ell_t(W_t) \\ 
+    &\leq \|W_t-W^*\|_F^2 - \frac{1}{8}\ell_{t}(W_t) \\
+    &\leq \|W_t-W^*\|_F^2 \left(1-\frac{\ell_t(W_t)}{32KD^2}\right)  \text{\ \ \ \ because $\|W_t-W^*\|_F^2\leq 4KD^2$} \\
+    &\leq \|W_t-W^*\|_F^2 \exp\left(-\frac{\ell_t(W_t)}{32KD^2}\right)
+\end{align*}
+By induction, we can get
+\begin{align*}
+    \|W_{t+1}-W^*\|_F^2 &\leq KD^2 \exp\left( -\frac{L_{t+1}}{32KD^2} \right) 
+    %&\leq KD^2 \left(\frac{8KD^2}{A_{t+1}}\right)   %\ \ \ \ \ \text{because $\exp(-x)<1/x$ for any $x>0$} \\
+    %& = \frac{8K^2D^4}{A_{t+1}}. 
+\end{align*}
+\end{proof}
+
+\begin{definition}
+$\norm{W}_{M}^2\triangleq \sum_{i=1}^K \norm{\e_i^\top W}_{M}^2$.
+\end{definition}
+With this definition we have $\|Wx_t\|_2^2 = \sum_{i=1}^K (\e_i^\top Wx_t)^2 \leq \sum_{i=1}^K \|\e_i^\top W\|_M^2 \|x_t\|_{M^{-1}}^2\leq \|W\|_M^2 \|x_t\|_{M^{-1}}^2$
+
+\begin{lemma}
+\begin{align*}
+\|W_{t}-W^*\|_{M_{t}}^2 \leq (1+L_t)K^2D^2 \exp\left(-\frac{L_t}{32KD^2}\right) \leq 32K^3D^4. 
+\end{align*}
+\end{lemma}
+\begin{proof}
+Because we assume $\|x_t\|_2^2\leq 1$, it holds that $ M_t \preceq (1+L_t) I$.
+Therefore $\|W_t-W^*\|_{M_t}^2 \leq (1+L_t)\|W_t-W^*\|_I^2 =  (1+L_t) \sum_{i=1}^K \| \e_i^\top (W_t-W^*) \|_2^2 \leq (1+L_t) K \|W_t-W^*\|_F^2 $.
+By Lemma~\ref{lemma:decreasing error} this is bounded by $(1+L_t)K^2D^2\exp\left( -\frac{L_t}{32KD^2} \right)$, which can further be bounded by a constant related to $K$ and $D$.
+For example, using the property $\exp(-x)\leq \frac{1}{(1+x)^2}$ for all $x>0$, it can be upper bounded by $(1+L_t)K^2D^2 \times \frac{(32KD^2)^2}{(L_t+32KD^2)^2} \leq \frac{32^2K^4D^6}{32KD^2+L_t}\leq 32K^3D^4$.
+\end{proof}
+
+\begin{lemma}
+\label{lemma: xbounded}
+If $\|x_t\|_{M_t^{-1}}\leq \epsilon = \frac{1}{4D\sqrt{32K^3D^4}}$, then $\hat{y}_t=y_t$. 
+\end{lemma}
+\begin{proof}
+By the convexity of $\ell_t$, 
+\begin{align*}
+    \ell_t(W_t)\leq \ell_t(W_t)-\ell_t(W^*)&\leq \inner{\nb \ell_t(W_t), W_t-W^*}\\
+     & = \inner{\nb\Phi_t(W_tx_t)x_t^\top, W_t - W^*} \\
+    & = \inner{\nb\Phi_t(W_tx_t), W_tx_t - W^*x_t} \\
+    & \leq 4D\norm{W_tx_t-W^*x_t}_2 \\
+    & \leq 4D\norm{W_t-W^*}_{M_t}\norm{x_t}_{M_t^{-1}} \leq 1.
+\end{align*}
+This implies $\hat{y}_t=y_t$. 
+\end{proof}
+
+Therefore, when we do not explore, we know $W_t$ will predict correctly! Thus we only need to bound the number of errors occurred in exploration rounds, which is calculated by the following lemma.
+
+\begin{lemma}[{\color{blue} The conclusion is not meaningful}]
+\label{lemma:N}
+$\sum_{t=1}^T \one[\tilde{y}_t\neq y_t] \leq \max_{t\in[T]}\left(\frac{1}{\ell_{t}(W_t)}\right)\times \frac{K\ln T\ln \frac{1}{\delta}}{\epsilon^2}$ with probability at least $1-\delta$. 
+\end{lemma}
+
+\begin{proof}
+By the above discussion, $\sum_{t=1}^T \one[\tilde{y}_t\neq y_t] \leq N\triangleq \sum_{t=1}^T Z_t$, the number of exploration rounds. 
+\begin{align*}
+    N &= \sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right]\\
+    &\leq \left(K\ln \frac{1}{\delta}\right)\sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right]Z_t \tag{when $\|x_t\|_{M_t^{-1}}\geq \epsilon$, $\tilde{y}_t=y_t$ with probability $\frac{1}{K}$} \\
+    & \leq \frac{K\ln \frac{1}{\delta}}{\epsilon^2}\sum_{t=1}^T \norm{x_t}_{M_t^{-1}}^2 Z_t \leq \max_{t\in[T]}\left(\frac{1}{\ell_{t}(W_t)}\right)\times \frac{K\ln T\ln \frac{1}{\delta}}{\epsilon^2}.
+\end{align*}
+\end{proof}
+
+\textbf{Discussion}. 
+In the calculation of Lemma~\ref{lemma: xbounded},  we can actually get $\ell_t(W_t)^2 \leq \norm{\nb\Phi_t(W_tx_t)}_2^2\norm{W_t-W^*}_{M_t}^2\norm{x_t}_{M_t^{-1}}^2$.
+Similar to the calculation in Lemma~\ref{lemma:decreasing error}, $\norm{\nb\Phi_t(W_tx_t)}_2^2$ is bounded by constant times $\ell_t(W_t)$.
+So the exploration criterion could potentially become $\ell_t(W_t)\|x_t\|_{M_t^{-1}}^2\geq \frac{1}{\epsilon^2}$, which makes Lemma~\ref{lemma:N} go through.
+The problem is we do not know $\ell_t(W_t)$ in general.
 
@@
 
-\section{How hard it is to use the feedback only from wrong guesses?}
+\section{How Hard It Is Only Using The Weak Labels?}
 The halving algorithm can actually run if we can do ``uniform sampling'' over the version space.
@@
 
-\section{Gradient Descent {\color{red} [TODO]}}
-
-%\textbf{Observation}. Alekh's paper's results can be generalized to losses with $\Phi_t$ a strongly and smoothly convex function. 
-\begin{assumption}
-$\|x_t\|_2^2\leq 1$. There is a $W^*\in\mathcal{W}$ such that $\ell_t(W^*)\leq 0$ for all $t$ ($\ell_t$ and $\mathcal{W}$ are defined below).  
-\end{assumption}
-
-\begin{algorithm}[H]
-\caption{Banditron}
-\textbf{Input}: $D\geq 2$, $\epsilon$ (picked in a later lemma). \\
-\textbf{Definition}: 
-\begin{align*}
-    \ell_t(W) &\triangleq [1-(Wx_t)_{y_t} + \max_{r\neq y_t}(Wx_t)_r]_+^2 \ \ \ \ \text{(squared hinge loss)} \\
-    & = \Phi_t(Wx_t), 
-    %\Phi_t(z) \triangleq \sum_{i\neq y_t} \psi(z_{y_t}-z_i).
-\end{align*}
-where $\Phi_t(z)\triangleq [1-\e_{y_t}^\top z + \max_{r\neq y_t} \e_r^\top z]_+^2$. \\
-Also, define $\mathcal{W}=\{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2\leq D \text{\ for all }i\in[K]\}$. \\
-\textbf{Initialization}: $W_1=0, M_1=I$.\\ 
-\For{$t=1, \ldots, T$}{
-   Observe $x_t$. \\
-   \If{$ \| x_t \|_{M_t^{-1}} \geq \epsilon$ {\color{red} \text{and} $\|W_t-W^*\|_F\geq 1$}}{
-       Draw $\tilde{y}_t \sim \text{unif}([K])$. 
-   }
-   \Else{
-       Draw $\tilde{y}_t = \hat{y}_t \triangleq \argmax_{r\in[K]}(W_tx_t)_r$. 
-   }
-   \If{ $\tilde{y}_t=y_t$ }{
-       $Z_t\leftarrow 1$, \\
-       $M_{t+1}\leftarrow M_t + Z_t\ell_t(W_t)x_tx_t^\top$,\\
-       $W_{t+1} \leftarrow \Pi_{\mathcal{W}} (W_t - \eta_{t+1}\nabla \ell_t(W_t))$, \ \ \ \ \ where $\eta_{t+1} = \frac{1}{8}$. \\
-       ($\Pi_{\mathcal{W}}$ is the projection operator onto $\mathcal{W}$ w.r.t. Frobenius norm)
-   }
-   \Else{
-       $Z_t\leftarrow 0$,  \\
-       $M_{t+1}\leftarrow M_t$,\\
-       $W_{t+1}\leftarrow W_t$.
-   }
-
-}
-\end{algorithm}
-\iffalse
-We will pick 
-\begin{align*}
-     \psi(u)=\begin{cases}
-        \frac{1}{2K(1-D)^2}(u-D)^2 - \frac{1}{2K}, & \text{if $u\geq 1$} \\
-        \left(1+\frac{1}{K(1-D)}\right)u^2 + \left(-2-\frac{1}{K(1-D)}\right)u + 1 &\text{if $u\leq 1$},  
-     \end{cases}
-\end{align*}
-It has the following properties: \\
-(1) It is continuous and differentiable. \\
-(2) It is $\frac{1}{2K(1-D)^2}$-strongly convex and $1$-smooth. \\
-(3) It decreases in $[-D,D]$, passing through $(0,1),(1,0)$, and $(D,\frac{-1}{2K})$. \\
-(4) Its minimum value $\frac{-1}{2K}$ is attained at $u=D$.
-
-\begin{lemma} 
- For the above specific choice of $\psi$, $\Phi_t$ is $\frac{1}{2KD^2}$-strongly convex and $2K$-smooth (i.e., its Hessian has eigenvalues all within $[\frac{1}{2KD^2}, 2K]$).
-
-\end{lemma}
-\begin{proof}
-It is clear that $\frac{\partial^2}{\partial z_j\partial z_i}\Phi_t(z)=0$ for $i\neq j$.
-Also, $\frac{\partial^2}{\partial^2 z_i} \Phi_t(z)\geq \frac{1}{2K(1-D)^2}\geq \frac{1}{2KD^2}$ and $\frac{\partial^2}{\partial^2 z_i} \Phi_t(z)\leq K\left(1+\frac{1}{K(1-D)}\right)\leq 2K$.
-\end{proof}
-
-\begin{lemma}
-\label{lemma:error_cond}
-If $\argmax_r (Wx_t)_r = y_t$, then $\ell_t(W) \leq K$; 
-If $\argmax_r (Wx_t)_r \neq y_t$, then $\ell_t(W) \geq 1$.  
-\end{lemma}
-\begin{proof}
-If $\argmax_r (Wx_t)_r = y_t$, then $z_{y_t}-z_i\geq 0$ for all $i$, and thus $\Phi_t(z)< K\psi(0)=K$; 
-If $\argmax_r (Wx_t)_r \triangleq j \neq y_t$, then $\Phi_t(z)\geq \psi(z_{y_t}-z_j) - K\times \frac{1}{2K}\geq \psi(0)-\frac{1}{2}=\frac{1}{2}$. 
-This is clear by the definition of $\ell_t$. 
-\end{proof}
-\fi
-%\begin{definition}
-%$\|W\|_M^2 \triangleq \sum_{i=1}^K \|\e_i^\top W\|_M^2 $.\\
-%$\gamma_\ell \triangleq \frac{1}{2KD^2}$; $\gamma_u\triangleq 2K$ (convexity and smoothity of $\Phi_t$). 
-%\end{definition}
-
-%\begin{lemma}
-%For any $W^*\in \mathcal{W}$, with probability at least $1-\delta$, 
-%\begin{align*} 
-%    \|W_t-W^*\|_{M_t} \leq \tilde{\mathcal{O}}\left(\frac{\sqrt{Kd}}{\gamma_\ell} + D\sqrt{\gamma}\right).
-%\end{align*}
-%(the $\tilde{\mathcal{O}}$ notation hides $\ln T$, $\ln \frac{1}{\delta}$, $\ln \frac{1}{\gamma}$ factors)
-%\end{lemma}
-%\begin{proof}
-%By the first order optimality condition, we have for all $W^*\in \mathcal{W}$, 
-%\begin{align*}
-%    \inner{\gamma W_t+\sum_{s=1}^{t-1}Z_s \nabla \ell_s(W_t), W^*-W_t}\geq 0. 
-%\end{align*}
-%Rearranging it and plugging in the property $\nb\ell_s(W)=\nb\Phi_s(Wx_s)x_s^\top$ gives 
-%\begin{align}
-%    \sum_{s=1}^{t-1} Z_s\inner{ -\nb\Phi_s(W^*x_s),W_tx_s-W^*x_s} \geq  \sum_{s=1}^{t-1} Z_s\inner{ \nb\Phi_s(W_t x_s)-\nb\Phi_s(W^*x_s),W_tx_s-W^*x_s}+\gamma\inner{W_t, W_t-W^*}. 
-%    \label{eqn:key}
-%\end{align}
-%By $\Phi_s$'s convexity and that $\norm{W}_F^2\leq KD^2$ for all $W\in \mathcal{W}$, the RHS of \eqref{eqn:key} can be lower bounded by 
-%\begin{align*}
-%    \gamma_\ell\sum_{s=1}^{t-1} Z_s\norm{W_t x_s-W^*x_s}_2^2 - 2\gamma KD^2 \geq \gamma_\ell \norm{W_t-W^*}_{M_t}^2-2\gamma KD^2. 
-%\end{align*}
-%The LHS is upper bounded by 
-%\begin{align*}
-%    \sum_{i=1}^K \sum_{s=1}^{t-1} Z_s (-\nb_i\Phi_s(W^*x_s))\inner{\e_iW_t-\e_iW^*, x_s}
-%\end{align*}
-%\end{proof}
-
-\begin{lemma}
-\label{lemma:bound_gradient}
-$\norm{\nb\ell_t(W)}_F^2 \leq 8\ell_t(W)$. 
-\end{lemma}
-\begin{proof}
-$    \|\nb\ell_t(W)\|_F^2 = \|\nb\Phi_t(Wx_t)x_t^\top\|_{F}^2 \leq \left(2\sqrt{\Phi_t(Wx_t)}\right)^2\times 2\|x_t\|_{2}^2 \leq 8\ell_t(W).  
-$
-\end{proof}
-
-\begin{lemma}
-\label{lemma:decreasing error}
-Let $L_{t+1}\triangleq \sum_{s=1}^t Z_s\ell_s(W_s)$. Then 
-$\|W_{t+1}-W^*\|_F^2 \leq \exp\left(-\frac{L_{t+1}}{32KD^2}\right)$. 
-\end{lemma}
-\begin{proof}
-Let $Z_{t}=1$. 
-\begin{align*}
-    \|W_{t+1}-W^*\|_F^2 &\leq \|W_t - \eta_{t+1}\nb\ell_t(W_t)-W^*\|_F^2 \\
-    & = \| W_t - W^* \|_F^2 - 2\eta_{t+1}\inner{\nb\ell_t(W_t),W_t-W^*}_F + \eta_{t+1}^2\|\nb\ell_t(W_t)\|_F^2.  
-\end{align*}
-By the separable assumption we have $\ell_t(W^*)\leq 0$.
-Since $\ell_t$ is convex, $\inner{\nb\ell_t(W_t), W_t-W^*} \geq \ell_t(W_t)-\ell_t(W^*)\geq \ell_t(W_t)$.
-Continuing the above calculation and using Lemma~\ref{lemma:bound_gradient}, we get
-\begin{align*}
-    \|W_{t+1}-W^*\|_F^2 &\leq \|W_t-W^*\|_2^2 - 2\eta_{t+1}\ell_t(W_t) + 8\eta_{t+1}^2 \ell_t(W_t) \\ 
-    &\leq \|W_t-W^*\|_F^2 - \frac{1}{8}\ell_{t}(W_t) \\
-    &\leq \|W_t-W^*\|_F^2 \left(1-\frac{\ell_t(W_t)}{32KD^2}\right)  \text{\ \ \ \ because $\|W_t-W^*\|_F^2\leq 4KD^2$} \\
-    &\leq \|W_t-W^*\|_F^2 \exp\left(-\frac{\ell_t(W_t)}{32KD^2}\right)
-\end{align*}
-By induction, we can get
-\begin{align*}
-    \|W_{t+1}-W^*\|_F^2 &\leq KD^2 \exp\left( -\frac{L_{t+1}}{32KD^2} \right) 
-    %&\leq KD^2 \left(\frac{8KD^2}{A_{t+1}}\right)   %\ \ \ \ \ \text{because $\exp(-x)<1/x$ for any $x>0$} \\
-    %& = \frac{8K^2D^4}{A_{t+1}}. 
-\end{align*}
-\end{proof}
-
-\begin{definition}
-$\norm{W}_{M}^2\triangleq \sum_{i=1}^K \norm{\e_i^\top W}_{M}^2$.
-\end{definition}
-With this definition we have $\|Wx_t\|_2^2 = \sum_{i=1}^K (\e_i^\top Wx_t)^2 \leq \sum_{i=1}^K \|\e_i^\top W\|_M^2 \|x_t\|_{M^{-1}}^2\leq \|W\|_M^2 \|x_t\|_{M^{-1}}^2$
-
-\begin{lemma}
-\begin{align*}
-\|W_{t}-W^*\|_{M_{t}}^2 \leq (1+L_t)K^2D^2 \exp\left(-\frac{L_t}{32KD^2}\right) \leq 32K^3D^4. 
-\end{align*}
-\end{lemma}
-\begin{proof}
-Because we assume $\|x_t\|_2^2\leq 1$, it holds that $ M_t \preceq (1+L_t) I$.
-Therefore $\|W_t-W^*\|_{M_t}^2 \leq (1+L_t)\|W_t-W^*\|_I^2 =  (1+L_t) \sum_{i=1}^K \| \e_i^\top (W_t-W^*) \|_2^2 \leq (1+L_t) K \|W_t-W^*\|_F^2 $.
-By Lemma~\ref{lemma:decreasing error} this is bounded by $(1+L_t)K^2D^2\exp\left( -\frac{L_t}{32KD^2} \right)$, which can further be bounded by a constant related to $K$ and $D$.
-For example, using the property $\exp(-x)\leq \frac{1}{(1+x)^2}$ for all $x>0$, it can be upper bounded by $(1+L_t)K^2D^2 \times \frac{(32KD^2)^2}{(L_t+32KD^2)^2} \leq \frac{32^2K^4D^6}{32KD^2+L_t}\leq 32K^3D^4$.
-\end{proof}
-
-\begin{lemma}
-\label{lemma: xbounded}
-If $\|x_t\|_{M_t^{-1}}\leq \epsilon = \frac{1}{4D\sqrt{32K^3D^4}}$, then $\hat{y}_t=y_t$. 
-\end{lemma}
-\begin{proof}
-By the convexity of $\ell_t$, 
-\begin{align*}
-    \ell_t(W_t)\leq \ell_t(W_t)-\ell_t(W^*)&\leq \inner{\nb \ell_t(W_t), W_t-W^*}\\
-     & = \inner{\nb\Phi_t(W_tx_t)x_t^\top, W_t - W^*} \\
-    & = \inner{\nb\Phi_t(W_tx_t), W_tx_t - W^*x_t} \\
-    & \leq 4D\norm{W_tx_t-W^*x_t}_2 \\
-    & \leq 4D\norm{W_t-W^*}_{M_t}\norm{x_t}_{M_t^{-1}} \leq 1.
-\end{align*}
-This implies $\hat{y}_t=y_t$. 
-\end{proof}
-
-Therefore, when we do not explore, we know $W_t$ will predict correctly! Thus we only need to bound the number of errors occurred in exploration rounds, which is calculated by the following lemma. 
-\begin{lemma}
-\label{lemma:N}
-$\sum_{t=1}^T \one[\tilde{y}_t\neq y_t] \leq ???$ with probability at least $1-\delta$. 
-\end{lemma}
-
-\begin{proof}
-By the above discussion, $\sum_{t=1}^T \one[\tilde{y}_t\neq y_t] \leq N\triangleq \sum_{t=1}^T Z_t$, the number of exploration rounds. 
-\begin{align*}
-    N &= \sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right]\\
-    &\leq \left(K\ln \frac{1}{\delta}\right)\sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right]Z_t \tag{when $\|x_t\|_{M_t^{-1}}\geq \epsilon$, $\tilde{y}_t=y_t$ with probability $\frac{1}{K}$} \\
-    & \leq \frac{K\ln \frac{1}{\delta}}{\epsilon^2}\sum_{t=1}^T \norm{x_t}_{M_t^{-1}}^2 Z_t \leq \max_{t\in[T]}\left(\frac{1}{\ell_{t}(W_t)}\right)\times \frac{K\ln T\ln \frac{1}{\delta}}{\epsilon^2}.
-\end{align*}
-\end{proof}
-
-\textbf{Discussion}. 
-In the calculation of Lemma~\ref{lemma: xbounded},  we can actually get $\ell_t(W_t)^2 \leq \norm{\nb\Phi_t(W_tx_t)}_2^2\norm{W_t-W^*}_{M_t}^2\norm{x_t}_{M_t^{-1}}^2$.
-Similar to the calculation in Lemma~\ref{lemma:decreasing error}, $\norm{\nb\Phi_t(W_tx_t)}_2^2$ is bounded by constant times $\ell_t(W_t)$.
-So the exploration criterion could potentially become $\ell_t(W_t)\|x_t\|_{M_t^{-1}}^2\geq \frac{1}{\epsilon^2}$, which makes Lemma~\ref{lemma:N} go through.
-The problem is just we do not know $\ell_t(W_t)$ in general.
-
 %\section{Reservoir Sampling}

### 2018-08-14 main.tex
Modify One-sided banditron and Selectron

@@
 Same holds for $\|b(2w^i\cdot x/\rho)\|^2$.
-Finally we have $\|B(x)\|^2 \leq (t)^{O(t\log t\log 1/\rho)} \times \left( \frac{\log t \log \frac{1}{\rho}}{\rho} \right)^{O(t\log t\log 1/\rho)} = \left( \frac{t\log t \log \frac{1}{\rho}}{\rho} \right)^{O(t\log t\log 1/\rho)}$
-
+Finally we have $\|B(x)\|^2 \leq (t)^{O(t\log t\log 1/\rho)} \times \left( \frac{\log t \log \frac{1}{\rho}}{\rho} \right)^{O(t\log t\log 1/\rho)} = \left( \frac{t\log t \log \frac{1}{\rho}}{\rho} \right)^{O(t\log t\log 1/\rho)}$\\
+\ \\ 
+{\color{red}[TODO] Refined lower bound for $|B(x)|$}
 %Another refinement is that we can show $|B(x)|\geq $
@@
 
-\section{A Recipe of Designing Efficient Algorithms}
+\section{A Recipe for Designing Efficient Algorithms}
 We have seen that if the data is ``one-versus-all'' separable with a margin, then constant error is achievable.
-To have constant error, a key is that every time an error occurs, the learner should make significant progress.
+To have constant error, a key is that every time there is a mistake, the learner should make significant progress.
 
 Besides one-versus-all separability, are there other kinds of conditions under which we can easily make progress when we make a mistake?
-If such condition exists, then we have the following recipe of designing algorithms that have constant error bound:
+If such condition exists, then we have the following recipe of designing algorithms that have constant mistake bound:
 \begin{itemize}
@@
 The above algorithm is similar to banditron but only performs \textit{one-sided} update and never explicitly explores to get label.
-Below we check under what condition can this algorithm have constant error bound.
+Below we check under what condition can this algorithm have constant mistake bound.
 
@@
 
-A candidate set of assumptions that leads to \eqref{eqn:one-sided condition} is the \textit{sum-to-zero} assumption: 
+A candidate set of assumptions that leads to \eqref{eqn:one-sided condition} is the \textit{sum-to-zero + margin} assumption: 
 \begin{itemize}
@@
 \hat{y}_t}]_+$. One can see that they are closely related, except that in~\cite{2018arXiv180610745F}
-when $(Wx_t)_{\hat{y}_t}\leq -\Delta$, the loss for $W$ is set to zero (which makes no difference under the sum-to-zero assumption).
-
-\section{Logarithmic Regret for Strongly Convex Losses}
+when $(Wx_t)_{\hat{y}_t}\leq -\Delta$, the loss for $W$ is set to zero (which makes no difference under the sum-to-zero + margin assumption).
+
+\section{Logarithmic Regret for Strongly Convex and Smooth Losses}
 \subsection{Gradient descent}
@@
 \begin{align}
-    \Reg_T &= \sum_{t=1}^T \E\left[ \one[\hat{y}_t\neq y_t] - \one[y_t^*\neq y_t]\right] \nonumber \\
+    \Reg_T &= \sum_{t=1}^T \E\left[ \one[\hat{y}_t\neq y_t] - \one[y_t^*\neq y_t]\right] \tag{the $\E[\cdot]$ is conditioned on all history before time $t$ and the randomness is from $y_t$} \\
     &= \sum_{t=1}^T \sum_{i=1}^K \left(\one[\hat{y}_t\neq i] - \one[y^*_t\neq i]\right)\nabla_i\Phi(W^*x_t). \label{eqn:new regret}
@@
 
-Below we argue that if $\Phi$ is strongly convex and smooth, then the following algorithm (exactly the algorithm in \cite{agarwal2013selective}) achieves regret logarithmic in $T$.
+Below we argue that if $\Phi$ is strongly convex and smooth, then the following algorithm (almost exactly the algorithm in \cite{agarwal2013selective} except that we replace label query by uniform exploration) achieves regret logarithmic in $T$.
 
 \begin{assumption}
-\begin{align*}
-     \Phi(v) + \inner{\nb\Phi(v),u-v} + \frac{\gamma_\ell}{2}\|u-v\|_2^2 \leq \Phi(u)-\Phi(v)\leq \Phi(v) + \inner{\nb\Phi(v),u-v} + \frac{\gamma_u}{2}\|u-v\|_2^2. 
+For any $u,v$, 
+\begin{align*}
+     \Phi(v) + \inner{\nb\Phi(v),u-v} + \frac{\gamma_\ell}{2}\|u-v\|_2^2 \leq \Phi(u)\leq \Phi(v) + \inner{\nb\Phi(v),u-v} + \frac{\gamma_u}{2}\|u-v\|_2^2. 
 \end{align*}
@@
 \caption{Selectron \cite{agarwal2013selective}}
-\textbf{Define}: $\epsilon\triangleq \Delta/(2\gamma_u C')$, where $C'$ is defined in Lemma~\ref{lem:decreasing error} $\eta\triangleq \frac{\sup_{W\in\Omega}\|W\|_F^2}{\gamma_\ell}$, $\Omega\triangleq$ a convex set where $W^*$ lies in.
-\\
-\textbf{Definition}: $\ell_t(W)=\Phi(Wx_t) - (Wx_t)_{y_t}$.\\
+\textbf{Definition}: $\epsilon\triangleq \Delta/(2\gamma_u C')$, where $C'$ is defined in Lemma~\ref{lem:decreasing error}, \\
+$\eta\triangleq \frac{\sup_{W\in\Omega}\|W\|_F^2}{\gamma_\ell}$, \\
+$\Omega\triangleq$ a convex set where $W^*$ lies in.  \\
+$\ell_t(W)=\Phi(Wx_t) - (Wx_t)_{y_t}$.\\
 \textbf{Initialization}: $W_1=0, M_1=I$.\\ 
@@
     & = \inner{\sum_{s=1}^{t-1} Z_s\left(\nb\Phi(W_t x_s) - \e_{y_s} \right)x_s^\top,  W_{t}-W^*} + \frac{1}{\eta}\inner{W_t, W_t-W^*} \\
-    & = \inner{\sum_{s=1}^{t-1} Z_s\left(\nb\Phi(W_t x_s) - \nb\Phi(W^*x_s) + \xi_s \right)x_s^\top, W_{t}-W^*} + \frac{1}{\eta}\inner{W_t, W_t-W^*} , \tag{let $\xi_s\triangleq \nb\Phi(W^*x_s)-\e_{y_s}$} \\
+    & = \inner{\sum_{s=1}^{t-1} Z_s\left(\nb\Phi(W_t x_s) - \nb\Phi(W^*x_s) + \xi_s \right)x_s^\top, W_{t}-W^*} + \frac{1}{\eta}\inner{W_t, W_t-W^*} , \tag{let $\xi_s\triangleq \nb\Phi(W^*x_s)-\e_{y_s}$; note that $\E[\xi_s]=\mathbf{0}$} \\
     & = \inner{\sum_{s=1}^{t-1} Z_s\left(\nb\Phi(W_t x_s) - \nb\Phi(W^*x_s) + \xi_s \right), W_t x_s- W^*x_s} + \frac{1}{\eta}\inner{W_t, W_t-W^*}, \\
     & \geq \gamma_\ell \sum_{s=1}^{t-1} Z_s\|W_tx_s-W^*x_s\|_2^2 + \sum_{s=1}^{t-1} Z_s\inner{\xi_s, W_tx_s-W^*x_s} + \frac{1}{\eta} \inner{W_t, W_t-W^*}.
+\tag{for $\gamma_\ell$-strongly convex functions, $\inner{\nb\Phi(u)-\nb\Phi(v), u-v}\geq \gamma_\ell\|u-v\|_2^2$}
 \end{align*}
@@
 \begin{align}
-    \sum_{s=1}^{t-1} Z_s\inner{\xi_s, W^*x_s-W_tx_s} &\geq \gamma_\ell \sum_{s=1}^{t-1} Z_s\|W_tx_s-W^*x_s\|_2^2 + \frac{1}{\eta} \inner{W_t, W_t-W^*} \nonumber \\
-    &= \gamma_\ell \sum_{s=1}^{t-1} Z_s\sum_{i=1}^K \langle \e_iW_t-\e_iW^*, x_s\rangle^2 + \frac{1}{\eta} \inner{W_t, W_t-W^*} \nonumber \\
-    & \geq \gamma_\ell \|W_t-W^*\|_{M_t}^2 - \frac{2}{\eta} \sup_{W\in \Omega}\|W\|_F^2.  \label{eqn:lower}
+    \sum_{s=1}^{t-1} Z_s\inner{\xi_s, W^*x_s-W_tx_s} &\geq \gamma_\ell \sum_{s=1}^{t-1} Z_s\|W_tx_s-W^*x_s\|_2^2 - \frac{2}{\eta} \sup_{W\in \Omega}\|W\|_F^2 \nonumber \\
+    &= \gamma_\ell \sum_{s=1}^{t-1} Z_s\sum_{i=1}^K \langle \e_iW_t-\e_iW^*, x_s\rangle^2 - \frac{2}{\eta} \sup_{W\in \Omega}\|W\|_F^2 \nonumber \\
+    & = \gamma_\ell \|W_t-W^*\|_{M_t}^2 - \frac{2}{\eta} \sup_{W\in \Omega}\|W\|_F^2.  \label{eqn:lower}
 \end{align}
@@
 \end{align*}
-where in the last inequality we use $\sum_{i=1}^K a_i\leq \sqrt{K}\sqrt{\sum_{i=1}^K a_i^2}$. Combining with~\eqref{eqn:lower} we get 
+where in the last inequality we use $\sum_{i=1}^K a_i\leq \sqrt{K}\sqrt{\sum_{i=1}^K a_i^2}$. Combining with~\eqref{eqn:lower} and solving for $\|W_t-W^*\|_{M_t}$ we get 
 \begin{align*}
@@
 In \cite{crammer2013multiclass} and \cite{agarwal2013selective}, the feature vectors $x_t$'s are adversarially picked, while $y_t$ is generated based on some conditional distribution based on $x_t$.
-For example, in \cite{crammer2013multiclass}, the label is generated through
+For example, in \cite{crammer2013multiclass}, the label is generated by
 \begin{align}
@@
 \end{align}
-where $W^* \in \Omega \triangleq \{W\in \mathbb{R}^{K\times d}: \sum_{i=1}^K (Wx_t)_i = \alpha+1-K\alpha \text{\ and\ } -\alpha \leq (Wx_t)_i\}$; a valid $\Phi$ is 
+where $W^* \in \Omega_t \triangleq \{W\in \mathbb{R}^{K\times d}: \sum_{i=1}^K (Wx_t)_i = \alpha+1-K\alpha \text{\ and\ } -\alpha \leq (Wx_t)_i\}$; a valid $\Phi$ that satisfies \eqref{eqn:new margin} is
 \begin{align}
@@
 \end{align}
-where $W^* \in \Omega \triangleq \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2 \leq D \}$, and $\Phi$ can be defined as
+where $W^* \in \Omega \triangleq \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2 \leq D \}$, and $\Phi$ can be chosen as
 \begin{align}
@@
 There is a $\alpha$ parameter in \cite{hazan2011newtron}, somehow it looks related to margin.
-    \item How is the assumptions in this section related to \cite{pillaud2017exponential}? 
+    \item How is the assumptions/algorithms/bounds introduced in this section related to \cite{pillaud2017exponential}?
+They are similar in that they both assume $p(y|x)$ to be defined by some function in a known function class.
+The margin assumption \eqref{eqn:new margin} is a generalization of \cite{pillaud2017exponential}'s to the multiclass case.
+One can also view the FTRL step used in Selectron as the counterpart of the ridge regression step defined in \cite{pillaud2017exponential}.
     \item We indeed have tried to use this kind of selective sampling idea to get finite error bound (see Section \ref{sec:kwik}).
-But there it seems that impossible to find a $\Phi(Wx_t)$ that is at the same time strongly convex, $\Phi(Wx_t)\geq 0$, $\Phi(W^*x_t)\leq 0$ (or other type of losses with which a logarithmic/constant regret bound implies logarithmic/constant error bound).
+But it seems it is impossible/difficult to find a $\Phi(\cdot)$ that at the same time 1) is strongly convex, and 2) whose logarithmic/constant regret bound implies logarithmic/constant mistake bound.
 \end{itemize}
@@
 
-\textbf{Discussion}. There is a construction such that $1/V$ can be of order $\Omega\left( \left(\frac{1}{\gamma}\right)^{(d-1)/2} \right)$.
+\textbf{Discussion}. There is a construction such that $1/V$ can be of order $\Omega\left( \left(\frac{1}{\gamma}\right)^{(d-1)/2} \right)$. {\color{red} [TODO] How to construct such points?}
 
@@
 
-It turns out this specific 1-dimensional problem is equivalent to identify a \textbf{missing permutation} of $[K]$ as a subsequence in the given sequence.
+It turns out this specific 1-dimensional problem is equivalent to identify a \textbf{missing permutation} of $[K]$ as a subsequence in the weak-label sequence.
 In Example 1, the existing permutations are $(1,2,3), (1,3,2), (2,3,1), (3,1,2)$, the missing ones are $(2,1,3)$ and $(3,2,1)$.
 So the solutions can be $(2,1,3)$ or $(3,2,1)$ (with some repetition).
-In Example 2, all permutations are as subsequences, so there is no solution.
+In Example 2, all permutations appear in the weak-label sequence, so there is no solution.
 
 We can prove this equivalence considering two directions: \\
-(1) If there is a solution with the class labels following a permutation, then that permutation cannot be a subsequence of the given sequence. \\
-(2) If there is a missing permutation in the given sequence, then there is a class assignment that follows this permutation.\\ 
-They should be straightforward by trying some examples.
+(1) If there is a solution whose class labels follow a permutation, then that permutation cannot be a subsequence of the weak-label sequence. \\
+(2) If there is a missing permutation in the weak-label sequence, then there is a class label assignment that follows this permutation.\\ 
+{\color{red} [TODO] Proof}
 

### 2018-08-15 main.tex
add a last paragraph to Selectron section
Type-2 margin

@@
 \end{align}
-which some $\Phi: \mathbb{R}^K \rightarrow \mathbb{R}$.
+with some $\Phi: \mathbb{R}^K \rightarrow \mathbb{R}$. This is a \textit{generalized linear model}.  
 The margin assumption is defined as 
@@
 \end{align}
+
+{\color{blue} Type 2 margin assumption: }\\
+{\color{blue} 
+\begin{align}
+    (W^*x_t)_{y_t} - \max_{y\neq y_t}(W^*x_t)_{y} \geq \Delta. 
+\end{align}
+
+}
+
 This margin assumption is a special case of the Tsybakov condition investigated in ~\cite{agarwal2013selective}. 
@@
 \end{align*}
+{\color{blue} For Type 2 margin assumption, the bound is
+\begin{align*}
+    \Reg_T \leq \tilde{O}\left(\frac{1}{\gamma_\ell^2}\frac{K^2d}{\Delta^2}\right).
+\end{align*}
+
+}
 \end{theorem}
@@
 \label{lem: xbounded}
-If $\|x_t\|_{M_t^{-1}}\leq \epsilon = \Delta/(2\gamma_u C')$, then $\hat{y}_t=y^*_t$. 
+If $\|x_t\|_{M_t^{-1}}\leq \epsilon = \Delta/(2\gamma_u C')$, then $\hat{y}_t=y^*_t$. {\color{blue}(For Type 2 margin assumption, we set $\epsilon=\Delta/2C'$)}
 \end{lemma}
@@
 
+{\color{blue} For Type 2 margin assumption, the proof is following:  
+\begin{proof}
+\begin{align*}
+    (W^*x_t)_{y_t^*} - (W^*x_t)_{\hat{y}_t} &\leq (W^*x_t)_{y_t^*} - (W^*x_t)_{\hat{y}_t} - (W_tx_t)_{y_t^*} + (W_tx_t)_{\hat{y}_t} \\
+    &\leq 2\|W^*x_t-W_tx_t\|_2\\
+    & \leq 2 \|W^*-W_t\|_{M_t}\|x_2\|_{M_t^{-1}} \\
+    & \leq \Delta.
+\end{align*}
+\end{proof}
+}
+
 From Lemma~\ref{lem: xbounded} and the regret definition~\eqref{eqn:new regret}, we see that in the rounds $\|x_t\|_{M_t^{-1}}\leq \epsilon$, the regret is zero.
@@
 \begin{align}
-    p(y_t = i | x_t) = \frac{\exp((W^*x_t)_i)}{\sum_{j=1}^K \exp((W^*x_t)_j) },
-\end{align}
-where $W^* \in \Omega \triangleq \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2 \leq D \}$, and $\Phi$ can be chosen as
-\begin{align}
-    \Phi(u) = \log\left(\sum_{i=1}^K \exp(u_i) \right). 
+    p(y_t = i | x_t) = \frac{\exp(\beta(W^*x_t)_i)}{\sum_{j=1}^K \exp(\beta(W^*x_t)_j) },
+\end{align}
+where $W^* \in \Omega \triangleq \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2 \leq 1 \}$, and $\Phi$ can be chosen as
+\begin{align}
+    \Phi(u) = \frac{1}{\beta}\log\left(\sum_{i=1}^K \exp(\beta u_i) \right). 
+\end{align}
+
+If we want, we can also cast our original linear separability to this framework: 
+\begin{align}
+    p(y_t=i|x_t) = \one\left[(W^*x_t)_i \geq (W^*x_t)_j, \forall j\neq i\right]. 
+\end{align}
+A natural definition of $\Phi$ is
+\begin{align}
+    \Phi(u) = \max_i u_i. 
 \end{align}

### 2018-10-11 main.tex
(add nothing)

@@
 
-\section{Logarithmic Regret for Strongly Convex and Smooth Losses}
+\section{Logarithmic Regret for Strongly Convex Smooth Losses}
 \subsection{Gradient descent}
@@
    \Else{
-       Draw $\tilde{y}_t = \hat{y}_t \triangleq \argmax_{y\in[K]}(W_tx_t)_y$. 
+       Draw $\tilde{y}_t = \hat{y}_t \triangleq \argmax_{i\in[K]}(W_tx_t)_i$. 
    }
@@
        $Z_t\leftarrow 1$, \\
-       $M_{t+1}\leftarrow M_t + Z_tx_tx_t^\top$,\\
+       $M_{t+1}\leftarrow M_t + x_tx_t^\top$,\\
        $W_{t+1} = \argmin_{W\in\Omega}\left\{ \sum_{s=1}^t Z_s \ell_s(W) + \frac{1}{2\eta}\|W\|_F^2 \right\}$. 
@@
        $M_{t+1}\leftarrow M_t$,\\
+       $W_{t+1}\leftarrow W_t$.
+   }
+
+}
+\end{algorithm}
+
+\begin{algorithm}[H]
+\caption{Confidit \cite{crammer2013multiclass}}
+\textbf{Definition}: $\epsilon\triangleq \Delta/(2\gamma_u C')$, where $C'$ is defined in Lemma~\ref{lem:decreasing error}, \\
+$\eta\triangleq \frac{\sup_{W\in\Omega}\|W\|_F^2}{\gamma_\ell}$, \\
+$\Omega\triangleq$ a convex set where $W^*$ lies in.  \\
+$\ell_t(W)=\Phi(Wx_t) - (Wx_t)_{y_t}$.\\
+\textbf{Initialization}: $W_1=\mathbf{0}^{K\times d}, M_{1,i}=I^{d\times d}, \forall i\in[K]$.\\ 
+\For{$t=1, \ldots, T$}{
+   Observe $x_t$. \\
+   Draw $\tilde{y}_t = \argmax_{i\in[K]} \left\{ (W_tx_t)_i + \|x_t\|_{M_{t,i}^{-1}} \right\}$. \\
+   $M_{t+1,\tilde{y}_t}\leftarrow M_{t,\tilde{y}_t} + x_tx_t^\top$, $M_{t+1,i}\leftarrow M_{t,i}, \forall i\neq \tilde{y}_t,$\\
+   \If{ $\tilde{y}_t=y_t$ }{
+       $Z_t\leftarrow 1$, \\
+       $M_{t+1,y_t}\leftarrow M_{t,y_t} + x_tx_t^\top$, $M_{t+1,i}\leftarrow M_{t,i}, \forall i\neq y_t,$\\
+       $W_{t+1} = \argmin_{W\in\Omega}\left\{ \sum_{s=1}^t Z_s \ell_s(W) + \frac{1}{2\eta}\|W\|_F^2 \right\}$. 
+   }
+   \Else{
+       $Z_t\leftarrow 0$,  \\
+       $M_{t+1,i}\leftarrow M_{t,i}, \forall i$,\\
        $W_{t+1}\leftarrow W_t$.
@@
 \begin{align*}
-\nb \Phi_{y_t^*}(W^*x_t) - \nb\Phi_{\hat{y}_t}(W^*x_t) 
- &\leq \nb \Phi_{y_t^*}(W^*x_t) -    \nb\Phi_{\hat{y}_t}(W^*x_t) 
- - \nb \Phi_{y_t^*}(W_tx_t) + \nb \Phi_{\hat{y}_t}(W_tx_t) \\
+\nb_{y_t^*} \Phi(W^*x_t) - \nb_{\hat{y}_t} \Phi(W^*x_t) 
+ &\leq \nb_{y_t^*} \Phi(W^*x_t) -    \nb_{\hat{y}_t} \Phi(W^*x_t) 
+ - \nb_{y_t^*} \Phi(W_tx_t) + \nb_{\hat{y}_t} \Phi(W_tx_t) \\
  & \leq 2\gamma_u \|W^*x_t-W_tx_t\|_2 \\
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+%%%% Below are failed attempt to prove the hardness
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\iffalse
+\section{Reduction from the 3SAT problem}
+In this section, we try to argue the hardness of the following margin-constrained weak-label learning problem: 
+\textit{
+\ \\
+Given weak-labeled samples $\{(x_t, \bar{y}_t)\}_{t=1}^T \subset \mathbb{R}^d \times [K]$, a margin parameter $\gamma$, and an absolute value bound $B$, find $W\in \mathbb{K\times d}$ such that $ \forall i,j, |W_{ij}|\leq B$ and $\forall t$,
+\begin{align*}
+(Wx_t)_{\bar{y}_t} \leq \max_{i\in [K]} (Wx_t)_i - \gamma. 
+\end{align*}
+}
+
+Below we reduce 3SAT to this problem.
+For an $N$-variable 3SAT problem, we construct a weak-label problem with $K=2N+1$ classes.
+For convenience, we give names to these $2N+1$ classes: $(1, a_1, b_1, \ldots, a_N, b_N)=(1,2,3,\ldots, 2N+1)$.
+
+Now we construct training samples that encode this 3SAT problem. For a clause $x_{i_1}\vee \cdots \vee x_{i_p} \vee \bar{x}_{j_1}\vee \cdots \vee \bar{x}_{j_n}$, we construct the following sample: 
+\begin{align}
+    (x,\bar{y}) = \left(\e_1 + \sum_{k=1}^p \e_{a_k} + \sum_{k=1}^n \e_{b_k}, 1 \right) \label{sample1}
+\end{align}
+
+For each $i\in [K]$, we construct two samples: 
+\begin{align}
+    (x,\bar{y}) &= \left( \e_1 + \e_{a_i} + \e_{b_i}, 1 \right), \\
+    (x, \bar{y}) &= \left( -\e_1 - \e_{a_i} - \e_{b_i}, 1 \right). 
+\end{align}
+
+The ranking problem has two kinds of constraints: $(S,i)$ and $(T,j)$, where $S, T\subseteq [K]$, $i\in S$, $j\in T$.
+The goal is to determine whether there exists a ranking over $[K]$ such that for all constraints $(S,i)$, $i$ is not the first-ranked element in $S$; for all $(T,j)$, $j$ is not the last-ranked element in $T$.
+This problem is proved to be hard.
+
+Below we prove that the weak-label learning problem is harder than the ranking problem. Thus we would try to use a weak-label learning algorithm to solve the ranking problem. Below is the algorithm:
+
+\begin{algorithm}[H]
+\caption{Reduction from ranking problem to weak-label learning problem}
+\textbf{Parameter: $0 < \epsilon < \frac{1}{2K^2}$}, $\#$features$=\#$classes$=K$, $\delta\triangleq 1+K\epsilon$. \\
+For each $(S,i)$ in the ranking problem, construct the following feature and weak-label pair: 
+\begin{align}
+    (x,\bar{y}) = \left( \sum_{q\in S} \e_q + (K\epsilon) \e_i , i\right). \label{feat1}
+\end{align}\\
+For example, if $S=\{1,3,4\}$ and $i=3$, then we construct the following weak training sample: 
+\begin{align*}
+    ((1+ K\epsilon, 0, 1,1), 3)
+\end{align*}\\
+
+For each $(T,j)$ in the ranking problem, we construct the following $K-1$ pairs: 
+\begin{align}
+    (x,\bar{y}) = \left( \sum_{q\in T} -\e_q - \delta \e_\ell , j\right), \forall \ell\neq j. \label{feat2}
+\end{align}\\
+For example, if $T=\{1,3,4\}$ and $j=3$, then we construct the following weak training samples: 
+\begin{align*}
+    &((-1, -\delta, -1,-1), 3)\\
+    &((-1, 0, -1-\delta, -1), 3)\\
+    &((-1,0,-1,-1-\delta), 3)
+\end{align*}\\
+
+Besides, for every $p\in [K]$, we construct the strong-label sample: 
+\begin{align}
+    (x,y) = (\e_p, p); \label{feat3}
+\end{align}\\
+
+and for any $(p,q)$, $q\neq p$, we construct the strong-label sample: \begin{align}
+    (x,y) = (-\e_q + \epsilon \e_p, p). \label{feat4}
+\end{align}\\
+Input all above samples to the weak-label algorithm, and get the linear classifier $W=[w_{pq}]$.
+Output the ranking of $p$ based on the value of $\sum_{q=1}^{K} w_{pq}$, from larger to smaller (i.e., the ranking is based on the scores for the feature $x=\e_1+\ldots+\e_K$).
+\end{algorithm}
+In the following two subsections, we show the correctness of the above reduction.
+
+\subsection{Solution for weak-label implies solution for ranking}
+In this subsection, we assume we have a solution $[w_{pq}]$ for the weak-label problem. 
+\begin{lemma}
+\label{lemma:eps_bound}
+(We have shown this in our discussion) For any $p, q, r\in [K]$, $p\neq q$, 
+\begin{align}
+    w_{pq} - w_{rq} \leq \epsilon(w_{pp}-w_{rp}). \label{eqn: eps_bound}
+\end{align}
+\end{lemma}
+\begin{proof}
+    Using \eqref{feat4}, and comparing the scores between class $p$ and $r$, we get 
+    \begin{align*}
+        -w_{pq} + \epsilon w_{pp} \geq -w_{rq} + \epsilon w_{rp}.
+    \end{align*}
+    Rearranging completes the proof. 
+\end{proof}
+\begin{lemma}
+\label{lemma:dominant_diag}
+For any $p, r\in [K]$, $w_{pp}\geq w_{rp}$. 
+\end{lemma}
+\begin{proof}
+    Using \eqref{feat3} and comparing the scores between class $p$ and $r$ complete the proof. 
+\end{proof}
+\begin{lemma}
+\label{lemma:S constraint}
+    For any $(S,i)$ constraint from the ranking problem, there exists a $i'\neq i$ such that 
+    \begin{align*}
+        \sum_{q=1}^K w_{iq} < \sum_{q=1}^K w_{i'q}. 
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    By the weak-label condition in \eqref{feat1}, there is a $i'\neq i$ such that 
+    \begin{align*}
+        \sum_{q\in S} w_{iq} + (K\epsilon) w_{ii} < \sum_{q\in S} w_{i'q} + (K\epsilon) w_{i'i}. 
+    \end{align*}
+    Note that $i\in S$, summing \eqref{eqn: eps_bound} over elements not in $S$ we get 
+    \begin{align*}
+        \sum_{q\notin S} (w_{iq} - w_{i'q}) \leq \sum_{q\notin S} \epsilon (w_{ii}-w_{i'i}) \leq K\epsilon(w_{ii}-w_{i'i}), 
+    \end{align*}
+    where in the last inequality we use the fact $w_{ii}-w_{i'i}\geq 0$ implied by Lemma~\ref{lemma:dominant_diag}. 
+    Combining the above two inequalities, we get $\sum_{q=1}^K (w_{iq}-w_{i'q})<(K\epsilon-K\epsilon)(w_{ii}-w_{i'i})=0$, which finishes the proof. 
+\end{proof}
+\begin{lemma}
+\label{lemma:T constraint}
+For any $(T,j)$ constraint from the ranking problem, there exists a $j'\neq j$ such that 
+\begin{align*}
+    \sum_{q=1}^K w_{jq} > \sum_{q=1}^K w_{j'q}. 
+\end{align*}
+\end{lemma}
+\begin{proof}
+By the weak label condition in \eqref{feat2}, there exists a $j'\neq j$ such that 
+\begin{align*}
+     \sum_{q\in T} w_{j'q} + \delta w_{j'j'} < \sum_{q\in T} w_{jq} + \delta w_{jj'} \tag{letting $\ell=j'$ in \eqref{feat2}}
+\end{align*}
+Consider two cases: \\
+(1) $j'\in T$, then summing \eqref{eqn: eps_bound} over elements not in $T$, we have
+\begin{align*}
+    \sum_{q\notin T} (w_{j'q}-w_{jq}) < \sum_{q\notin T} \epsilon(w_{j'j'}-w_{jj'}) \leq K\epsilon(w_{j'j'}-w_{jj'}),  
+\end{align*}
+where in the last inequality we use the fact $w_{j'j'}-w_{jj'}\geq 0$ implied by Lemma~\ref{lemma:dominant_diag}. \\
+(2) $j'\notin T$, then 
+\begin{align*}
+    \sum_{q\notin T} (w_{j'q}-w_{jq}) &= (w_{j'j'}-w_{jj'})+\sum_{q\notin T, q\neq j'}(w_{j'q}-w_{jq})\\
+    &\leq (w_{j'j'}-w_{jj'})+\sum_{q\notin T, q\neq j'}(w_{j'j'}-w_{jj'}) \tag{Lemma~\ref{lemma:eps_bound}}\\
+    &\leq (1+K\epsilon) (w_{j'j'}-w_{jj'})
+\end{align*}
+In either case, we have $\sum_{q=1}^K (w_{j'q}-w_{jq})<(1+K\epsilon-\delta)(w_{j'j'}-w_{jj'})\leq 0$, which completes the proof. 
+\end{proof}
+By Lemma~\ref{lemma:S constraint} and~\ref{lemma:T constraint}, if we rank element $p$ based on the value of $\sum_{q=1}^K w_{pq}$, then this satisfies all constraints from the ranking problem, and thus gives it the valid solution.
+
+\subsection{Solution for ranking implies solution for weak-label}
+This direction is more straightforward.
+Suppose we have a solution for the ranking problem, then we create a diagonal matrix $W$ where the diagonal elements are a permutation of $\{1, (1+2K\epsilon), (1+2K\epsilon)^2, \ldots, (1+2K\epsilon)^{K-1}\}$: the first-ranked element takes the value $K$, the second takes $K-1$, and so on.
+It's easy to verify that \eqref{feat1}-\eqref{feat4} are all satisfied.
+\fi
+
 \newpage

### 2018-10-11 ptf_margin.tex
added elaboration on norm bound

--- 2018-08-14 main.tex
@@
 \usepackage{soul}
+\usepackage{commath}
 %%%%%%%%%%%%%%%%%% toc
@@
 \DeclareMathOperator*{\mydet}{det_{+}}
-\DeclarePairedDelimiter\abs{\lvert}{\rvert}
+%\DeclarePairedDelimiter\abs{\lvert}{\rvert}
 \DeclarePairedDelimiter\bigabs{\big\lvert}{\big\rvert}
@@
 \newcommand{\eye}[1]{ \boldsymbol{I}_{#1} }
-\newcommand{\norm}[1]{\left\|{#1}\right\|}
+%\newcommand{\norm}[1]{\left\|{#1}\right\|}
 %\newcommand{\trace}[1]{\text{tr}\left({#1}\right)}
@@
 \newtheorem{remark}[theorem]{Remark}
+\newtheorem{fact}[theorem]{Fact}
 \DeclareMathOperator{\val}{val}
@@
 
-\section{Problem Statement}
-A multiclass linear classifier is defined by a set of $K$ vectors $w^{(1)}, \ldots, w^{(K)}\in \mathbb{R}^d$ (or a compact matrix form $W = [w^{(1)}\ w^{(2)}\  \cdots\  w^{(K)}]^\top \in \mathbb{R}^{K\times d}$), where $K$ is the number of classes ($K\geq 3$) and $d$ is the dimension of the feature vector.
-A set of samples $\{(x_t, y_t)\}_{t=1}^T$ where $x_t\in \mathbb{R}^d$ and $y_t\in[K]$ is called \textit{linearly separable} if there exists a $w_*^{(1)}, \ldots, w_*^{(K)}$ (or simply $W_*$) such that $ y_t= \argmax_{y\in[K]} (W_{*}x_t)_y $ for all $t\in[T]$.
+\section{Learning intersection of halfspaces with a margin}
+Suppose we are given examples $S = \cbr{(x, y)}$, where $x$ is in $\cbr{x \in \fR^d: \| x \| \leq 1}$, and $y$ is in $\cbr{-1,+1}$.
+\begin{definition}
+$S$ is said to be separable by an intersection of halfspaces with margin parameter $\gamma > 0$, if there exists $t$ linear classifiers $v_1, \ldots, v_t$ (all of which are in $\cbr{v \in \fR^d: \| v \| \leq 1}$),
+such that for every $(x,y)$ in $S$:
+\begin{enumerate}
+  \item If $y = +1$, then $v_i \cdot x \geq \gamma$ holds simultaneously for all $i$ in $[t]$.
+  \item If $y = -1$, then there exists an $i$ in $[t]$, $v_i \cdot x \leq -\gamma$.
+\end{enumerate}
+\label{def:int-margin}
+\end{definition}
 
-A set of samples $\{(x_t, y_t)\}_{t=1}^T$ is called \textit{linearly separable with a margin $\gamma$} if there exists $W_*$ with $\|w^{(i)}_*\|_2\leq 1$ for all $i$ and $(W_{*}x_t)_{y_t} \geq \max_{y\neq y_t} (W_*x_t)_y + \gamma$ for all $t$.
-We define the set $\calW = \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W^*\|_2\leq 1\}$.
-Therefore, $W_*\in \calW$.
+Given a set $S$ separable by an intersection of halfspaces with a margin $\gamma$, our goal is to find a feature map $\phi: \fR^d \to \fR^{d'}$, such that the dataset $S' = \cbr{(\phi(x), y): (x,y) \in S}$ is linearly separable by a margin $\gamma' > 0$.
+That is, for every $(\phi(x), y)$ in $S'$, and
+there exists a vector $u$ in $\fR^{d'}$, such that for every $(\phi(x), y)$ in $S'$, $\frac{y u \cdot \phi(x)}{\|u\|\| \phi(x)\|} \geq \gamma'$.
+In addition, we would like our feature map $\phi$ to correspond to a kernel function $k(x,x') = \inner{\phi(x), \phi(x')}$ that can be efficiently evaluated.
 
-Consider the following \textit{online multiclass classification} problem: at time $t$, the environment first reveals $x_t\in \mathbb{R}^d$ (and we assume $\|x_t\|_2\leq 1$), then the learner predicts some label $\tilde{y}_t\in [K]$; finally the environment reveals the true label $y_t\in[K]$.
-It is known that if the samples are linearly separable, then the learner will only make constant mistakes.
-It is achievable with the following simple perceptron algorithm:
+\section{Construction of polynomials}
+Our $\phi$'s in considerations are as follows: TODO: fix the constant in phi so that it has norm at most 1.
+\begin{enumerate}
+\item $\phi(x) = (x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0} = (x_S)_{S \in N^d, \|S\|_1 \leq \deg}$.
+This corresponds to the complete symmetric kernel $K_{\deg}$.
+\item $\phi(x) = ( \sqrt{ {\deg \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$.
+This corresponds to the polynomial kernel
+$K_{\deg}'(x,x') = (1 + \inner{x, x'})^{\deg}$.
+\item $\phi(x) = ( \sqrt{ (\frac 1 2)^{i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$.
+This coresponds to the kernel $K(x,x') = \frac{1}{1 - \frac 1 2 \inner{x,x'}}$.
+\end{enumerate}
 
-\begin{algorithm}[H]
-\caption{Perceptron}
-$W_1=\mathbf{0}$\\
-\For{$t=1$ to $T$}{
-   Predict $\tilde{y}_t=\argmax_y (W_tx_t)_y$ \\
-   Update $W_{t+1}\leftarrow W_t + (\e_{y_t}-\e_{\tilde{y}_t})x_t^\top$ \\
-   (same as updating $w^{(y_t)}_{t+1} \leftarrow w^{(y_t)}_t + x_t$ and $w^{(\hat{y}_t)}_{t+1} \leftarrow w^{(\hat{y}_t)}_t - x_t$ when $\hat{y}_t\neq y_t$). 
-}
-\end{algorithm}
-The analysis is simple. On one hand we have (note $\langle A,B \rangle:=\text{Tr}(A^\top B)$):
-\begin{align*}
-    \langle W_t, W_* \rangle &= \langle W_{t-1}, W_* \rangle + \langle (\e_{y_t}-\e_{\tilde{y}_t})x_t^\top, W_* \rangle \\
-    &= \langle W_{t-1}, W_* \rangle + (\e_{y_t}^\top W_* x_t-\e_{\tilde{y}_t}^\top W_* x_t) \\
-    &\geq \langle W_{t-1}, W_* \rangle + \gamma\one[\tilde{y}_t\neq y_t]. 
-\end{align*}
-By induction, we get $\langle W_{T+1}, W_* \rangle \geq \gamma\sum_{t=1}^T \one[\tilde{y}_t\neq y_t]$.
+For a polynomial $p = \sum_{S \in \fN^d} c_S x_S$, define $\|p\|$, the norm of $p$, as the $\ell_2$ norm of the vector that contains its coefficients on every monomial, that is $\|p\| = \| (c_S)_{S \in \fN^d} \| = \sqrt{\sum_{S \in \fN^d} c_S^2}$.
+This is also the RKHS norm of $p$ wrt the complete symmetric kernel $K_{\deg}$, for $\deg \geq \deg(p)$.
 
-On the other hand, 
-\begin{align*}
-    \langle W_{T+1}, W_* \rangle \leq \|W_{T+1}\|_F\|W_*\|_F \leq \sqrt{2K\sum_{t=1}^T \one[\tilde{y}_t \neq y_t] \|x_t\|_2^2}\times 1 \leq \sqrt{2K\sum_{t=1}^T \one[\tilde{y}_t \neq y_t] } 
-\end{align*}
-Combining the above two inequality, we get $ \sum_{t=1}^T \one[\tilde{y}_t \neq y_t] \leq \frac{4K}{\gamma^2}$.
+\subsection{Construction using rational functions}
 
-The \textit{bandit multiclass classification} problem proceeds in a very similar way.
-The only difference is that the learner only knows whether she predicts \textbf{correctly or not}, rather than gets the true label (i.e., in each round, the feedback is only $\one[\tilde{y}_t=y_t]$, rather than $y_t$).
-Surprisingly, with this extremely limited feedback, the learner can still make only constant mistakes.
-It can be achieved with the following variant of \textit{halving algorithm}:
+\subsection{Construction using Chebyshev polynomials}
+\paragraph{The construction.} Define
+\[ p(x) = t + \frac 1 2 - \sum_{i=1}^t (T_{\ceil{\sqrt{\frac 2 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}, \]
+where
+$T_r(\cdot)$ is the $r$-th order Chebyshev polynomial. Denote by $C_i(x) = (T_{\ceil{\sqrt{\frac 2 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}$. $p$ can therefore be simplified to
+\[ p(x) = t + \frac 1 2 - \sum_{i=1}^t C_i(x). \]
 
-\begin{algorithm}[H]
-\caption{Halving}
-Discretize the space of $W$ (i.e., the $\calW$ as defined in the beginning) with balls of radius $\frac{1}{2\gamma}$.
-Let the set of discretization points be $\calS$.
-Then this is saying that for all $W\in \calW$, there is always a $W'\in \calS$ such that $\|W-W'\|_F\leq \frac{1}{2\gamma}$.\\
-Let $\calS_1=\calS$ \\
-\For{$t=1$ to $T$}{
-    Let $\calS_t(y) = \{W\in \calS_t: (Wx_t)_y \geq (Wx_t)_i \ \forall i\in[K]\}$ (i.e., the set of $W$'s in $\calS_t$ that predict $y$ as the label of $x_t$) \\
-    Let $\tilde{y}_t = \argmax_y |\calS_t(y)|$ (i.e., pick the majority vote)\\
-    \If{$\tilde{y}_t\neq y_t$}{
-        $\calS_{t+1}=\calS_t \backslash \calS_t(\tilde{y}_t)$ (i.e., eliminate the $W$'s that are inconsistent with the outcomes)
-    }
-    \Else{
-        $\calS_{t+1}=\calS_t$
-    }
-}
-\end{algorithm}
-\textbf{Analysis}.
-The majority in $\calS_t$ always has cardinality no less than $\frac{1}{K}|\calS_t|$.
-So every time the learner predicts incorrectly, the size of $|\calS_t|$ shrinks by an order of $(1-\frac{1}{K})$.
-By our margin assumption, there is a $W'\in \calS$ which incurs no error in all samples.
-Therefore, $|S_t|\geq 1$ always holds.
-This means the number of errors is bounded by the order of $\frac{\log(|\calS|)}{-\log(1-\frac{1}{K})}\leq \mathcal{O}\left( K^2d\log \frac{1}{\gamma} \right)$.
-
-The main issue of this halving algorithm is that it is \textbf{inefficient} in the sense that $|\calS|$ is in the order of $\frac{1}{\gamma^{Kd}}$.
-
-Hence, we want to answer the following question: \ul{for bandit multiclass classification, can we have an efficient algorithm (time complexity polynomial in $K,d,\frac{1}{\gamma}, T$) that guarantees constant mistake bound (polynomial in $K,d,\frac{1}{\gamma}$) in the $\gamma$-separable case?} (An unsolved open problem in \cite{kakade2008efficient})
-
-\section{Naive Approaches}
-\begin{itemize}
-    \item \textbf{Exhausting the feature space}: discretize the feature space into $ \left(\frac{1}{\gamma}\right)^{\mathcal{O}(d)} $ blocks.
-The margin assumption guarantees that two points in a block would have the same label (so we can give every block a label).
-Each time a new point $x_t$ comes, see whether the learner already knows the correct label for that block.
-If yes, predict that label; if not, randomly choose a label that has not been chosen for that block.
-\\
-    $\Rightarrow $ error bound: $K\left(\frac{1}{\gamma}\right)^{\mathcal{O}(d)} $. 
-    \item \textbf{Exhausting the hypothesis space}: Discretize the hypothesis space into $\left(\frac{1}{\gamma}\right)^{Kd}$ discretization points (like in the halving algorithm).
-For each of them, make predictions based on it until it makes an mistake.
-\\
-    $\Rightarrow $ error bound: $\left(\frac{1}{\gamma}\right)^{Kd}$. 
-\end{itemize}
-
-\section{Difficulties}
-\label{section: difficulty}
-Efficient classification algorithms often optimize a convex surrogate loss rather than a 0-1 loss. Examples include: 
-\begin{itemize}
-    \item Hinge loss: $\ell_t(W) = [1-(Wx_t)_{y_t}+\max_{y\neq y_t}(Wx_t)_{y}]_+$. 
-    \item Logistic loss: $\ell_t(W)=-\ln\frac{\exp((Wx_t)_{y_t})}{\sum_{y}\exp((Wx_t)_y)}$
-    \item A family of loss that interpolates hinge loss and squared hinge loss (see \cite{beygelzimer2017efficient}'s Eq.(3))
-\end{itemize}
-In full-information setting, one can directly use online convex optimization techniques to deal with the above loss functions (learning over the space of $W$).
-
-Many works for bandit classification reuse this kind of convex optimization schemes, together with explicit exploration and inverse propensity weighting \cite{kakade2008efficient, hazan2011newtron, beygelzimer2017efficient, foster2018logistic}.
-However, because it is hard to estimate these losses when the true label $y_t$ is not known, some of these algorithms \cite{beygelzimer2017efficient, foster2018logistic} simply do not update when the learner makes a mistake ($\tilde{y}_t \neq y_t$).
-We give this kind of algorithm an error lower bound $\Omega\left(\left(\frac{1}{\gamma}\right)^{(d-1)/2}\right)$ in Section~\ref{section: passive lower bound}.
-
-It indeed looks hard to design a convex loss for $W$'s when the learner makes a mistake: when $\tilde{y}_t
-\neq y_t$, the set of $W$'s that we want to penalize (i.e., to assign larger loss) is $\{W: (Wx_t)_{\tilde{y}_t} \geq (Wx_t)_{y}, \forall y \}$, which is a convex cone in the space of $W$.
-It is impossible for a convex function to be large only in a convex subset (the case $K=2$, on the other hand, does not have this issue).
-Can we argue that if the learner is restricted to use convex losses in the space of $W$, she will have to suffer exponential (in $K$) errors?
-
-\section{One-versus-all Perceptron}
-\label{sec:ova}
-Our assumption of linearly separable with a margin is 
-\begin{align}
- (W_*x_t)_{y_t} \geq (W_*x_t)_{y} + \gamma, \ \forall y\neq y_t. \label{eqn:weaker}
-\end{align}
-As discussed in Section~\ref{section: difficulty}, it seems hard to make update when $\tilde{y}_t\neq y_t$ and achieve a constant and polynomial error bound.
-
-For a moment, in this section we make the following stronger margin assumption (which we call \textit{one-versus-all separable} with a margin): 
-\begin{align}
-\begin{cases}
-    (W_*x_t)_{y_t} \geq \gamma/2 \\
-    (W_*x_t)_y \leq -\gamma/2, \forall y\neq y_t.
-\end{cases}
-\label{eqn:stronger}
-\end{align}
-Clearly, one-versus-all separability implies linearly separability, but not the other way around.
-With one-versus-all separability assumption, we can view the problem as $K$ parallel binary classification problem.
-The following algorithm achieves constant error bound:
-\begin{algorithm}[H]
-\caption{One-versus-all Perceptron}
-\label{alg:ova}
-Initialize $w_t^{(1)}=\ldots=w_t^{(K)}=\mathbf{0}\in \mathbb{R}^d$\\
-\For{$t=1$ to $T$}{
-   \If{$\exists y$ such that $w_t^{(y)\top} x_t \geq 0$}{
-       Assign $\tilde{y}_t$ to any $y$ with $w_t^{(y)\top}  x_t \geq 0$ \\
-       Predict $\tilde{y}_t$ \\
-       \lIf{$\tilde{y}_t\neq y_t$}{ update $w_t^{(\tilde{y}_t)} \leftarrow w_t^{(\tilde{y}_t)} - x_t$ } \label{line:update1}
-   }
-   \Else{
-       Pick $\tilde{y}_t$ randomly from $
-       \text{unif}[K]$ \label{line:explore}\\
-       Predict $\tilde{y}_t$ \\
-       \lIf{$\tilde{y}_t = y_t$}{ update $w_t^{(\tilde{y}_t)} \leftarrow w_t^{(\tilde{y}_t)} + x_t$ } \label{line:update2}
-   }
-}
-\end{algorithm}
-\textbf{Analysis}.
-Note that when the algorithm enters Line~\ref{line:update1} or Line~\ref{line:update2}, the binary classifier $w_t^{(\tilde{y}_t)}$ is making an error.
-Let the number of times the algorithm enters Line~\ref{line:update1} and Line~\ref{line:update2} be $M$ and $N$ respectively.
-By the error bound of binary perceptron $\mathcal{O}\left(\frac{1}{\gamma^2}\right)$, we have that $M+N=\mathcal{O}\left(\frac{K}{\gamma^2}\right)$.
-Then note that the number of times the algorithm makes a mistake (i.e.
-$\tilde{y}_t\neq y_t$) is upper bounded by $M$ plus how many times the algorithm explores in Line~\ref{line:explore}; and when the algorithm explores, with probability $\frac{1}{K}$ it enters Line~\ref{line:update2}.
-Therefore, the number of mistakes is bounded (in expectation) by $\E[M+KN]=\mathcal{O}\left(\frac{K^2}{\gamma^2}\right)$.
-
-\section{One-versus-all Kernel Perceptron}
-%With the polynomial kernel defined in \cite{klivans2004learning}, we can transform the weaker assumption \eqref{eqn:weaker} in the original feature space to the stronger one \eqref{eqn:stronger} in a transformed feature space.
-Indeed, in the original feature space, class $i$ corresponds to an intersection of $K-1$ halfspaces: $ \{x: (w_i^*-w_j^*)^\top x \geq 0, \forall j\neq i\} $, which is the subject of \cite{klivans2004learning} (here, $w_i^{*\top}$ equals to $\e_i^\top W^*$ defined above).
-Directly using their kernel construction, we can have margin $ \left(\frac{\gamma}{d}\right)^{\Omega(K\log K\log (1/\gamma))} $ in the transformed feature space.
-Running kernelized version of Algorithm~\ref{alg:ova}, we can get $ K^2\left(\frac{d}{\gamma}\right)^{\mathcal{O}(K\log K\log (1/\gamma))} $ error bound directly.
-The idea here is to do a feature transformation such that if the original assumption \eqref{eqn:weaker} is satisfied, then in the transformed feature space, \eqref{eqn:stronger} will be satisfied, then we can run the one-versus-all perceptron given in \ref{sec:ova}.
-Under the original assumption, each class corresponds to an intersection of $K-1$ halfspaces in the feature spaces (i.e., class $i$ corresponds to $\{x\in\mathbb{R}^d: w_*^{(i)\top}x \geq w_*^{(j)\top}x, \ \forall j\neq i\}$).
-We want this region to become a halfspace in the transformed space.
-Fortunately, this is possible when there is a margin, and is exactly what is done in \cite{klivans2004learning}.
-
-\subsection{Refinement for \cite{klivans2004learning}'s Fact 1}
-\begin{lemma}
-   For $i=1,\ldots, \ell$ let $q^{(i)}(x)=\sum_S c^{(i)}_{S} x_S $ be a polynomial over $x_1, \ldots, x_d$ with $\|q^{(i)}\|^2\leq M_i$.
-Then (1) if $q^{(1)}\ldots q^{(\ell)}$ has degree at most $\deg$, we have $\|q^{(1)}\ldots q^{(\ell)}\|^2 \leq \ell^{\deg} \prod_i M_i$, and (2) we have $\|q^{(1)}+\ldots+q^{(\ell)}\|^2\leq \ell(M_1+\ldots+M_\ell)$.
+\begin{lemma}[~\cite{klivans2004learning}]
+For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y p(x) \geq \frac 1 2$.
 \end{lemma}
 \begin{proof}
-For the first bound, we bound the ratio between the following two values:  $ \|q^{(1)}\ldots q^{(\ell)}\|^2 $ and $\|q^{(1)}\|^2\ldots \|q^{(\ell)}\|^2$. 
-\begin{align}
-    n_1&=\prod_{i=1}^\ell \|q^{(i)}\|^2 
-    = \prod_{i=1}^\ell \left(\sum_{S_i} \left(c^{(i)}_{S_i}\right)^2 \right)
-    = \sum_{(S_1,\ldots,S_\ell)}  \left(\prod_{i=1}^\ell \left(c^{(i)}_{S_i}\right)^2 \right)
-    = \sum_{(S_1,\ldots,S_\ell)}  \left(\prod_{i=1}^\ell c^{(i)}_{S_i}\right)^2 \nonumber\\
-    &= \sum_S \sum_{\substack{(S_1,\ldots,S_\ell): \\ S_1\times\ldots S_\ell=S}}  \left(\prod_{i=1}^\ell c^{(i)}_{S_i}\right)^2
-\end{align}
-\begin{align}
-    n_2=\|q^{(1)}\ldots q^{(\ell)}\|^2 = \sum_{S} c_S^2 
-    = \sum_S \left( \sum_{\substack{(S_1,\ldots, S_\ell): \\ S_1\times\ldots\times S_\ell=S }} \left(c_{S_1}^{(1)}\ldots c_{S_\ell}^{(\ell)} \right) \right)^2 
-    = \sum_S \left( \sum_{\substack{(S_1,\ldots, S_\ell): \\ S_1\times\ldots\times S_\ell=S }} \prod_{i=1}^\ell c_{S_i}^{(i)} \right)^2 
-\end{align}
-Let $M$ be an upper bound of the number of terms involved in the summation $ \sum_{\substack{(S_1,\ldots, S_\ell): \\ S_1\times\ldots\times S_\ell=S }} $, then by Cauchy-Schwarz's inequality we have $ n_2\leq Mn_1 $.
+We consider the two cases regarding the label of the example.
+\begin{enumerate}
+\item Suppose $y = 1$, then for all $i$ in $[t]$, $v_i \cdot x \geq \gamma$. This implies that for all
+$i$ in $[t]$, $1 - v_i \cdot x \in [0, 1-\gamma]$. By item~\ref{item:bound-in} of Fact~\ref{fact:cheb}, we have that for all $i$, $|C_i(x)| \leq 1$.
+Therefore, $p(x) \geq t + \frac 1 2 - t \geq \frac 1 2$.
 
-$M$ counts the number of different $(S_1,\ldots, S_\ell)$'s with $S_1\times \ldots \times S_\ell=S$. Since $S$ has degree at most $\deg$, we can bound $M$ by $ \ell^{\deg}$.
-
-The second bound can be obtained by applying Cauchy-Schwarz once.
-
+\item Suppose $y = -1$.
+First observe that for all $i$, $T_{\ceil{\sqrt{\frac 2 \gamma}}}(1 - v_i \cdot x)) \geq -1$.
+This is because of items~\ref{item:bound-in} and~\ref{item:bound-out} of Fact~\ref{fact:cheb}.
+This implies that $C_i(x) \geq -1$.
+On the other hand, by Definition~\ref{def:int-margin}, there exists an $i_0$ in $[t]$, such that $v_{i_0} \cdot x \leq -\gamma$. By item~\ref{item:bound-out} of Fact~\ref{fact:cheb}, we have that
+$C_{i_0}(x) \geq (1 + \gamma \cdot \frac 1 \gamma)^{\ceil{\log 2t}} \geq 2t$. Therefore,
+\[ p(x) = t + \frac 1 2 - C_{i_0}(x) - \sum_{i \neq i_0} C_i(x) \leq t + \frac 1 2 - 2t + (t-1) \leq -\frac 1 2. \]
+\end{enumerate}
 \end{proof}
 
-\subsection{Refinement for \cite{klivans2004learning}'s Theorem 10}
+\begin{fact}
+$T_r(\cdot)$ has the following properties:
+\begin{enumerate}
+  \item If $|z| \leq 1$, then $|T_r(z)| \leq 1$. \label{item:bound-in}
+  \item If $z > 1$, then $T_r(z) \geq 1 + r^2 (z-1)$. \label{item:bound-out}
+  \item $T_r(z)$ can be written as $\sum_{l=0}^r c_l z^l$, where coefficients $c_l$ are bounded by $2^r$ in absolute value.
+\end{enumerate}
+\label{fact:cheb}
+\end{fact}
+
+\paragraph{Norm bound.} We now bound $\| p \|$. First, for all $i$, as $v_i$ has norm at most 1,
+\[ \| (1 - v_i \cdot x) \|^2 \leq 2. \]
+Therefore, by Lemma~\ref{lem:norm-oper},
+\[ \| c_l (1 - v_i \cdot x)^l \|^2 = c_l^2 \| (1 - v_i \cdot x)^l \|_2^2 \leq 2^{2r} l^l 2^l. \]
+Hence,
+\[ \| T_r(1 - v_i \cdot x) \|^2 = \| \sum_{l=0}^r c_l (1 - v_i \cdot x)^l \|^2 \leq (r+1) \cdot \sum_{l=0}^r 2^{2r} l^l 2^l \leq (r+1)^2 (8r)^r. \]
+And by Lemma~\ref{lem:norm-oper},
+\[ \| C_r(x) \|^2 \leq (\ceil{\log 2t})^{\ceil{\log 2t} r} \cdot ((r+1)^2 (8r)^r)^{\ceil{\log 2t}}. \]
+Therefore,
+\[ \| p(x) \|^2 \leq (t+1) \cdot ((t+\frac 1 2)^2 + t (\ceil{\log 2t})^{\ceil{\log 2t} r} \cdot ((r+1)^2 (8r)^r)^{\ceil{\log 2t}}) \leq 2 \cdot (32 r \ceil{\log 2t})^{2r \ceil{\log 2t}}  \]
+where the last inequality uses the fact that $2^{2r \ceil{\log 2t}} \geq \max(2t^2, r^2)$.
+\section{Auxiliary lemmas}
 \begin{lemma}
-Under the same condition as in \cite{klivans2004learning}'s Theorem 10, the PTF has margin on $X$ is at least $(1/t)^{O(r\log r + r\log\log t)}$. 
+   For $i=1,\ldots, \ell$ let $q^{(i)}(x)=\sum_S c^{(i)}_{S} x_S $ be a polynomial over $x_1, \ldots, x_d$. Then
+   \begin{enumerate}
+     \item if $q^{(1)}\ldots q^{(\ell)}$ has degree at most $\deg$, we have $\|\prod_{i=1}^{\ell} q^{(i)}\|^2 \leq \ell^{\deg} \prod_{i=1}^{\ell} \|q^{(i)}\|^2$.
+Specifically, for a polynomial $p$ of degree $s$, $\|p^\ell \|^2 \leq  \ell^{\ell s} (\|p\|^2)^\ell$.
+     \item $\|\sum_{i=1}^{\ell} q^{(i)}\|^2 \leq \ell(\sum_{i=1}^{\ell} \|q^{(i)}\|^2)$.
+   \end{enumerate}
+   \label{lem:norm-oper}
 \end{lemma}
-\begin{proof}
-We simply follow the construction in the original paper.
-$\|1-w^i\cdot x\|^2\leq 4$ can imply $\|(1-w^i\cdot x)^j\|^2\leq j^{O(j)}4^j \leq j^{O(j)}$.
-Then $\|a_j(1-w^i\cdot x)^j\|^2\leq 2^{2r}r^{O(r)}=r^{O(r)}$ follows.
-Thus $\|T_r(1-w^i\cdot x)\|^2=\|\sum_{j=0}^r a_j (1-w^i\cdot x)^j\|^2 \leq (r+1)^2 r^{O(r)} = r^{O(r)}$.
-Then, $\left(P(w^i\cdot x)\right)^{\log 2t}\leq (\log t)^{O(r\log t)}\times r^{O(r\log t)}\leq (r\log t)^{O(r\log t)}$.
-Finally, $\|p\|^2\leq (t+1)^2 (r\log t)^{O(r\log t)} \leq (t+1)^2 \left(  t^{O(r\log r + r\log\log t)}\right) = t^{O(r\log r + r\log\log t)}$.
-\end{proof}
-
-\subsection{Refinement for \cite{klivans2004learning}'s Theorem 7}
-\begin{lemma}
-Under the same condition as in \cite{klivans2004learning}'s Theorem 7, the PTF has margin on $X$ is at least $\left( \frac{\rho}{t\log t \log \frac{1}{\rho}} \right)^{O(t\log t\log 1/\rho)}$. 
-\end{lemma}
-\begin{proof}
-Using the same construction, we bound $\|p\|$.
-First, we have $\|\frac{2w^i\cdot x}{\rho}\|^2\leq \frac{4}{\rho^2}$ and $\|\left(\frac{2w^i\cdot x}{\rho}\right)^j\|^2\leq j^j\left(\frac{4}{\rho^2}\right)^j=\left(\frac{4j}{\rho^2}\right)^j$.
-$a(x), b(x)$ are polynomials of degree $O(\log t\log \frac{1}{\rho})$ with coefficients of magnitude $\left(\frac{1}{\rho}\right)^{O(\log t\log 1/\rho)}$.
-Thus
-\begin{align*}
-    \|a(2w^i\cdot x/\rho)\|^2 &\leq 
-    \left( \frac{\log t \log \frac{1}{\rho}}{\rho} \right)^{O(\log t\log 1/\rho)}  \times  \left(\frac{1}{\rho}\right)^{O(\log t\log 1/\rho)}\\
-    &\leq \left( \frac{\log t \log \frac{1}{\rho}}{\rho} \right)^{O(\log t\log 1/\rho)}.
-\end{align*}
-Same holds for $\|b(2w^i\cdot x/\rho)\|^2$.
-Finally we have $\|B(x)\|^2 \leq (t)^{O(t\log t\log 1/\rho)} \times \left( \frac{\log t \log \frac{1}{\rho}}{\rho} \right)^{O(t\log t\log 1/\rho)} = \left( \frac{t\log t \log \frac{1}{\rho}}{\rho} \right)^{O(t\log t\log 1/\rho)}$\\
-\ \\ 
-{\color{red}[TODO] Refined lower bound for $|B(x)|$}
-%Another refinement is that we can show $|B(x)|\geq $
-
-\end{proof}
-
-%\subsection{Possibilities of using other kernels}
-
-\section{A Recipe for Designing Efficient Algorithms}
-We have seen that if the data is ``one-versus-all'' separable with a margin, then constant error is achievable.
-To have constant error, a key is that every time there is a mistake, the learner should make significant progress.
-
-Besides one-versus-all separability, are there other kinds of conditions under which we can easily make progress when we make a mistake?
-If such condition exists, then we have the following recipe of designing algorithms that have constant mistake bound:
-\begin{itemize}
-    \item Design an algorithm that has constant mistake bound under some assumption. 
-    \item Design feature transformation such that our original linear separability satisfies the above assumption in the transformed space. 
-\end{itemize}
-Our kernel perceptron exactly follows the above procedure. Following is another example.
-
-\subsection{One-sided banditron}
-Consider the following algorithm. \\
-\begin{algorithm}[H]
-\caption{Ond-sided banditron}
-\label{alg:one-sided}
-\textbf{Define}: $\Omega\subseteq \mathbb{R}^{K\times d}$ is a convex set, and we assume $W^* \in \Omega_t$ for all $t$. Learning rate $\eta$. \\
-\textbf{Initialize}: $W_1=\mathbf{0}$. \\
-\For{$t=1, \ldots, T$}{
-   Receive $x_t\in \mathbb{R}^d$. \\
-   Predict $\hat{y}_t = \argmax_{y\in[K]} (W_tx_t)_y$. \\
-   \If{$\hat{y}_t \neq y_t$}{
-       $W_{t+1}'\leftarrow W_t - \eta\e_{\hat{y}_t} x_t^\top$.\\
-       $W_{t+1}=\Pi_{\Omega_{t+1}}(W_{t+1}') \triangleq \argmin_{W\in\Omega_{t+1}}\|W-W_{t+1}'\|_F$. 
-   }
-}
-\end{algorithm}
-\ \\
-The above algorithm is similar to banditron but only performs \textit{one-sided} update and never explicitly explores to get label.
-Below we check under what condition can this algorithm have constant mistake bound.
-
-Following standard analysis for online gradient descent, we have when the learner makes a mistake:
-\begin{align}
-    \|W_{t+1}-W^*\|_F^2 &\leq \|W_{t+1}'-W^*\|_F^2 = \|W_t - W^* - \eta \e_{\hat{y}_t}x_t^\top \|_F^2 \nonumber \\
-    &= \|W_t-W^*\|_F^2 - 2\eta ((W_tx_t)_{\hat{y}_t} - (W^*x_t)_{\hat{y}_t}) + \eta^2\|x_t\|_2^2 
-    \label{eqn:update_rule}
-    %&\leq \|W_t-W^*\|_F^2 - 2\eta ((W_tx_t)_{\hat{y}_t} - (W^*x_t)_{\hat{y}_t}) + \eta^2. 
-\end{align}
-
-We see that if the condition 
-\begin{align}
-    (W_tx_t)_{\hat{y}_t} - (W^*x_t)_{\hat{y}_t} \geq \Delta  \label{eqn:one-sided condition}
-\end{align}
-holds whenever $\hat{y}_t\neq y_t$ and we pick $\eta = \Delta/\sup_\tau\|x_\tau\|_2^2$, then we always have
-\begin{align*}
-    \|W_{t+1}-W^*\|_F^2 \leq \|W_{t}-W^*\|_F^2 -\frac{2\Delta^2}{\sup_\tau\|x_\tau\|_2^2} + \frac{\Delta^2}{\sup_\tau\|x_\tau\|_2^2} = \|W_{t}-W^*\|_F^2 - \frac{\Delta^2}{\sup_\tau\|x_\tau\|_2^2} 
-\end{align*}
-whenever $\hat{y}_t\neq y_t$. Then we have the error bound 
-\begin{align*}
-    \sum_{t=1}^T \one[\hat{y}_t\neq y_t] \leq \frac{\|W^*\|_F^2 \sup_{\tau}\|x_\tau\|_2^2}{\Delta^2}   
-\end{align*}
-because $\|W_t - W^*\|_F^2$ is always non-negative and $\|W_1-W^*\|_F^2=\|W^*\|_F^2$. \\
-
-The following analysis leads to the same bound but is more standard. Let $M_t=\one[\hat{y}_t\neq y_t]$. By \eqref{eqn:update_rule} and \eqref{eqn:one-sided condition} we have
-\begin{align*}
-    \Delta \sum_{t=1}^T M_t  \leq \sum_{t=1}^T M_t\left((W_tx_t)_{\hat{y}_t} - (W^*x_t)_{\hat{y}_t}\right) \leq \frac{\|W^*\|_F^2}{2\eta} + \frac{\eta}{2}\sup_\tau\|x_\tau\|_2^2\sum_{t=1}^T M_t
-\end{align*}
-Picking appropriate $\eta$ and solving for $\sum_{t=1}^T M_t$ we get the same error bound.
-
-A candidate set of assumptions that leads to \eqref{eqn:one-sided condition} is the \textit{sum-to-zero + margin} assumption: 
-\begin{itemize}
-    \item $\sum_{i=1}^K \e_i^\top W^* = 0$ (so we pick $\Omega_t = \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2\leq 1, \sum_{i=1}^K \e_i^\top W=0\}$) \\
-    \item $ (W^*x_t)_y \leq -\Delta $ for all $y\neq y_t$. 
-\end{itemize}
-They are similar to the assumptions made in \cite{2018arXiv180610745F}.
-We see that the above two conditions indeed lead to~\eqref{eqn:one-sided condition}: $(W_tx_t)_{\hat{y}_t} = \max_y (W_tx_t)_y \geq \frac{1}{K}\sum_{i=1}^K (W_tx_t)_i =0 $ (recall that we always project $W_t$ back to $\Omega_t$), and when $\hat{y}_t\neq y_t$ we have $(W^*x_t)_{\hat{y}_t}\leq -\Delta$.
-Unfortunately, this set of assumptions is even stronger than the one-versus-all separable assumption.
-
-Although the one-versus-all assumption is similar, there we do not perform projection for $W_t$, so it is possible that $\max_y (W_tx_t)_y < 0$. It that case, what we do is uniformly sample a label.\\
-
-\textbf{Questions}:
-\begin{itemize}
-\item Can we avoid the projection step for one-sided banditron (just like perceptron)?
-\item Are there other natural assumptions that guarantee \eqref{eqn:one-sided condition}? 
-\end{itemize}
-
-\subsection{Algorithms that can update without true labels}
-Algorithm~\ref{alg:one-sided} can update without the information of $y_t$.
-One can think of Algorithm~\ref{alg:one-sided} as a gradient algorithm  on the loss function $\ell_t(W) = \one[\hat{y}_t\neq y_t](Wx_t)_{\hat{y}_t}$.
-As a comparison, one can think of the surrogate loss function in \cite{2018arXiv180610745F} as $\ell_t(W)=\sum_{y=1}^K \one[y\neq y_t][\Delta+(Wx_t)_y]_+ $ (some scaling and notations are changed for better comparison), whose inverse propensity weighting estimator becomes $\tilde{\ell}_t(W)= \frac{1}{p_{t,\hat{y}_t}}\one[\hat{y}_t\neq y_t][\Delta+(Wx_t)_{
-\hat{y}_t}]_+$. One can see that they are closely related, except that in~\cite{2018arXiv180610745F}
-when $(Wx_t)_{\hat{y}_t}\leq -\Delta$, the loss for $W$ is set to zero (which makes no difference under the sum-to-zero + margin assumption).
-
-\section{Logarithmic Regret for Strongly Convex and Smooth Losses}
-\subsection{Gradient descent}
-In some previous works (we will visit them in the next subsection), it is assumed that the labels are generated with the following process: 
-\begin{align}
-    p(y|x) = \nabla_y\Phi(W^*x), 
-\end{align}
-which some $\Phi: \mathbb{R}^K \rightarrow \mathbb{R}$.
-The margin assumption is defined as 
-\begin{align}
-    p(y_t|x_t) - \max_{y\neq y_t}p(y|x_t) \geq \Delta, \forall t.  \label{eqn:new margin}
-\end{align}
-This margin assumption is a special case of the Tsybakov condition investigated in ~\cite{agarwal2013selective}. 
-Defining $\hat{y}_t = \argmax_y \nabla\Phi(W_tx_t)$ and $y^*_t = \argmax_y \nabla\Phi(W^*x_t) $ The regret is defined as
-\begin{align}
-    \Reg_T &= \sum_{t=1}^T \E\left[ \one[\hat{y}_t\neq y_t] - \one[y_t^*\neq y_t]\right] \tag{the $\E[\cdot]$ is conditioned on all history before time $t$ and the randomness is from $y_t$} \\
-    &= \sum_{t=1}^T \sum_{i=1}^K \left(\one[\hat{y}_t\neq i] - \one[y^*_t\neq i]\right)\nabla_i\Phi(W^*x_t). \label{eqn:new regret}
-\end{align}
-
-Below we argue that if $\Phi$ is strongly convex and smooth, then the following algorithm (almost exactly the algorithm in \cite{agarwal2013selective} except that we replace label query by uniform exploration) achieves regret logarithmic in $T$.
-
-\begin{assumption}
-For any $u,v$, 
-\begin{align*}
-     \Phi(v) + \inner{\nb\Phi(v),u-v} + \frac{\gamma_\ell}{2}\|u-v\|_2^2 \leq \Phi(u)\leq \Phi(v) + \inner{\nb\Phi(v),u-v} + \frac{\gamma_u}{2}\|u-v\|_2^2. 
-\end{align*}
-That is, $\Phi$ is $\gamma_\ell$-strongly convex and $\gamma_u$-smooth. 
-\end{assumption}
-
-\begin{algorithm}[H]
-\caption{Selectron \cite{agarwal2013selective}}
-\textbf{Definition}: $\epsilon\triangleq \Delta/(2\gamma_u C')$, where $C'$ is defined in Lemma~\ref{lem:decreasing error}, \\
-$\eta\triangleq \frac{\sup_{W\in\Omega}\|W\|_F^2}{\gamma_\ell}$, \\
-$\Omega\triangleq$ a convex set where $W^*$ lies in.  \\
-$\ell_t(W)=\Phi(Wx_t) - (Wx_t)_{y_t}$.\\
-\textbf{Initialization}: $W_1=0, M_1=I$.\\ 
-\For{$t=1, \ldots, T$}{
-   Observe $x_t$. \\
-   \If{$ \| x_t \|_{M_t^{-1}} \geq \epsilon$}{
-       Draw $\tilde{y}_t \sim \text{unif}([K])$. 
-   }
-   \Else{
-       Draw $\tilde{y}_t = \hat{y}_t \triangleq \argmax_{y\in[K]}(W_tx_t)_y$. 
-   }
-   \If{ $\tilde{y}_t=y_t$ }{
-       $Z_t\leftarrow 1$, \\
-       $M_{t+1}\leftarrow M_t + Z_tx_tx_t^\top$,\\
-       $W_{t+1} = \argmin_{W\in\Omega}\left\{ \sum_{s=1}^t Z_s \ell_s(W) + \frac{1}{2\eta}\|W\|_F^2 \right\}$. 
-   }
-   \Else{
-       $Z_t\leftarrow 0$,  \\
-       $M_{t+1}\leftarrow M_t$,\\
-       $W_{t+1}\leftarrow W_t$.
-   }
-
-}
-\end{algorithm}
-
-\begin{theorem}
-\label{lemma:new main}
-The selective sampling algorithm achieves
-\begin{align*}
-    \Reg_T\leq \tilde{O}\left( \frac{\gamma_u^2}{\gamma_\ell^2}\frac{K^2d}{\Delta^2} \right). 
-\end{align*}
-\end{theorem}
-
-The proof of this theorem is decomposed to the following three lemmas.
-
-\begin{definition}
-$\norm{W}_{M}^2\triangleq \sum_{i=1}^K \norm{\e_i^\top W}_{M}^2$.
-\end{definition}
-With this definition we have $\|Wx_t\|_2^2 = \sum_{i=1}^K (\e_i^\top Wx_t)^2 \leq \sum_{i=1}^K \|\e_i^\top W\|_M^2 \|x_t\|_{M^{-1}}^2\leq \|W\|_M^2 \|x_t\|_{M^{-1}}^2$
-
-\begin{lemma}[Proposition 1 of \cite{agarwal2013selective}]
-\label{lem:decreasing error}
-With probability at least $1-\delta$,
-\begin{align*}
-\|W_t-W^*\|_{M_t} \leq C' \triangleq \frac{2C\sqrt{dK}}{\gamma_\ell} + \sqrt{\frac{2}{\eta \gamma_\ell}}\sup_{W\in \Omega}\|W\|_F, 
-\end{align*}
-where $C$ hides some $\log t$ and $\log(1/\delta)$ terms (defined in the proof). 
-\end{lemma}
-
-\begin{proof}
-By the first-order optimality condition on $W_{t}$ we have
-\begin{align*}
-    0\geq \inner{\frac{1}{\eta} W_{t} + \sum_{s=1}^{t-1} Z_s\nb\ell_s(W_t), W_{t}-W^*}. 
-\end{align*}
-By the definition of $\ell_t$, 
-\begin{align*}
-    0 &\geq \inner{\frac{1}{\eta} W_{t} + \sum_{s=1}^{t-1} Z_s\nb\ell_s(W_t),  W_{t}-W^*} \\
-    & = \inner{\sum_{s=1}^{t-1} Z_s\left(\nb\Phi(W_t x_s) - \e_{y_s} \right)x_s^\top,  W_{t}-W^*} + \frac{1}{\eta}\inner{W_t, W_t-W^*} \\
-    & = \inner{\sum_{s=1}^{t-1} Z_s\left(\nb\Phi(W_t x_s) - \nb\Phi(W^*x_s) + \xi_s \right)x_s^\top, W_{t}-W^*} + \frac{1}{\eta}\inner{W_t, W_t-W^*} , \tag{let $\xi_s\triangleq \nb\Phi(W^*x_s)-\e_{y_s}$; note that $\E[\xi_s]=\mathbf{0}$} \\
-    & = \inner{\sum_{s=1}^{t-1} Z_s\left(\nb\Phi(W_t x_s) - \nb\Phi(W^*x_s) + \xi_s \right), W_t x_s- W^*x_s} + \frac{1}{\eta}\inner{W_t, W_t-W^*}, \\
-    & \geq \gamma_\ell \sum_{s=1}^{t-1} Z_s\|W_tx_s-W^*x_s\|_2^2 + \sum_{s=1}^{t-1} Z_s\inner{\xi_s, W_tx_s-W^*x_s} + \frac{1}{\eta} \inner{W_t, W_t-W^*}.
-\tag{for $\gamma_\ell$-strongly convex functions, $\inner{\nb\Phi(u)-\nb\Phi(v), u-v}\geq \gamma_\ell\|u-v\|_2^2$}
-\end{align*}
-Rearranging gives 
-\begin{align}
-    \sum_{s=1}^{t-1} Z_s\inner{\xi_s, W^*x_s-W_tx_s} &\geq \gamma_\ell \sum_{s=1}^{t-1} Z_s\|W_tx_s-W^*x_s\|_2^2 - \frac{2}{\eta} \sup_{W\in \Omega}\|W\|_F^2 \nonumber \\
-    &= \gamma_\ell \sum_{s=1}^{t-1} Z_s\sum_{i=1}^K \langle \e_iW_t-\e_iW^*, x_s\rangle^2 - \frac{2}{\eta} \sup_{W\in \Omega}\|W\|_F^2 \nonumber \\
-    & = \gamma_\ell \|W_t-W^*\|_{M_t}^2 - \frac{2}{\eta} \sup_{W\in \Omega}\|W\|_F^2.  \label{eqn:lower}
-\end{align}
-On the other hand, 
-\begin{align}
-    \sum_{s=1}^{t-1} Z_s\inner{\xi_s, W^*x_s-W_tx_s} &= \sum_{i=1}^K  \sum_{s=1}^{t-1} Z_s\xi_{s,i} ((W^*x_s)_i-(W_tx_s)_i) \nonumber \\
-    & = \sum_{i=1}^K  \sum_{s=1}^{t-1} Z_s\xi_{s,i} \langle W^*_i-W_{t,i}, x_s\rangle \nonumber \\
-    &\leq \sum_{i=1}^K \Bigg\| \sum_{s=1}^{t-1} Z_s\xi_{s,i}x_s \Bigg\|_{M_t^{-1}} \|W^*_i-W_{t,i}\|_{M_t}.   \label{eqn:upper}
-\end{align}
-Note that $\{\xi_{s,i}\}_{s}$ is a martingale difference sequence.
-Using \cite{filippi2010parametric}'s Lemma 1 in Appendix A.1 with constant $c_m = \sup_\tau\|x_\tau\|_2=1, \lambda_0 = \frac{1}{\eta\gamma_\ell}, R=2$ yields with probability at least $1-\delta/K$
-\begin{align*}
-    \Bigg\| \sum_{s=1}^{t-1} Z_s\xi_{s,i}x_s \Bigg\|_{M_t^{-1}} \leq 2\sqrt{3+2\log(1+\eta\gamma_\ell)}\sqrt{d\log t}\sqrt{\log(dK/\delta)} \triangleq \sqrt{d}C.
-\end{align*}
-Thus, by~\eqref{eqn:upper} we get with proability $1-\delta$
-\begin{align*}
-    \sum_{s=1}^{t-1} Z_s\inner{\xi_s, W^*x_s-W_tx_s} &= C\sqrt{d}\sum_{i=1}^K \|W^*_i-W_{t,i}\|_{M_t} = C\sqrt{dK} \|W^*-W_{t}\|_{M_t}, 
-\end{align*}
-where in the last inequality we use $\sum_{i=1}^K a_i\leq \sqrt{K}\sqrt{\sum_{i=1}^K a_i^2}$. Combining with~\eqref{eqn:lower} and solving for $\|W_t-W^*\|_{M_t}$ we get 
-\begin{align*}
-    \|W_t-W^*\|_{M_t} \leq \frac{2C\sqrt{dK}}{\gamma_\ell} + \sqrt{\frac{2}{\eta \gamma_\ell}}\sup_{W\in \Omega}\|W\|_F. 
-\end{align*}
-
-\end{proof}
-
-\begin{lemma}
-\label{lem: xbounded}
-If $\|x_t\|_{M_t^{-1}}\leq \epsilon = \Delta/(2\gamma_u C')$, then $\hat{y}_t=y^*_t$. 
-\end{lemma}
-\begin{proof}
-\begin{align*}
-\nb \Phi_{y_t^*}(W^*x_t) - \nb\Phi_{\hat{y}_t}(W^*x_t) 
- &\leq \nb \Phi_{y_t^*}(W^*x_t) -    \nb\Phi_{\hat{y}_t}(W^*x_t) 
- - \nb \Phi_{y_t^*}(W_tx_t) + \nb \Phi_{\hat{y}_t}(W_tx_t) \\
- & \leq 2\gamma_u \|W^*x_t-W_tx_t\|_2 \\
- & \leq 2\gamma_u \|W^*-W_t\|_{M_t}\|x_2\|_{M_t^{-1}} \\
- & \leq \Delta. \tag{by Lemma~\ref{lem:decreasing error}}
-\end{align*}
-By the margin assumption \eqref{eqn:new margin}, $\hat{y}_t = y_t^*$. 
-\end{proof}
-
-From Lemma~\ref{lem: xbounded} and the regret definition~\eqref{eqn:new regret}, we see that in the rounds $\|x_t\|_{M_t^{-1}}\leq \epsilon$, the regret is zero.
-The following lemma bounds the number of rounds with $\|x_t\|_{M_t^{-1}} > \epsilon $
-
-\begin{lemma}
-\label{lem:N}
-$ \sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right] \leq \frac{K\ln T\ln \frac{1}{\delta}}{\epsilon^2}$ with probability at least $1-\delta$. 
-\end{lemma}
-
-\begin{proof}
-\begin{align*}
-    &~ \sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right]\\
-    &\leq \left(K\ln \frac{1}{\delta}\right)\sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right]Z_t \tag{when $\|x_t\|_{M_t^{-1}}\geq \epsilon$, $\tilde{y}_t=y_t$ with probability $\frac{1}{K}$} \\
-    & \leq \frac{K\ln \frac{1}{\delta}}{\epsilon^2}\sum_{t=1}^T \norm{x_t}_{M_t^{-1}}^2 Z_t \leq \frac{K\ln T\ln \frac{1}{\delta}}{\epsilon^2}. 
-\end{align*}
-\end{proof}
-
-\begin{proof}[Proof of Theorem~\ref{lemma:new main}]
-    By Lemma~\ref{lem: xbounded} and~\ref{lem:N}, 
-    \begin{align*}
-        \Reg_T &= \sum_{t=1}^T \sum_{i=1}^K \left(\one[\hat{y}_t\neq i] - \one[y^*_t\neq i]\right)\nabla_i\Phi(W^*x_t) \\
-        & \leq \sum_{t=1}^T \left(\one\left[\|x_t\|_{M_t^{-1}}>\epsilon\right]\right) \sum_{i=1}^K \nabla_i\Phi(W^*x_t) \\
-        & \leq \sum_{t=1}^T \left(\one\left[\|x_t\|_{M_t^{-1}}>\epsilon\right]\right) \\
-        & \leq \tilde{O}\left( \frac{K\gamma_u^2C'^2}{\Delta^2} \right). 
-    \end{align*}
-    Using the definition of $C'$ we get the final bound. 
-\end{proof}
-
-\subsection{Revisiting the stochastic assumptions made in \cite{crammer2013multiclass} and \cite{agarwal2013selective}}
-In \cite{crammer2013multiclass} and \cite{agarwal2013selective}, the feature vectors $x_t$'s are adversarially picked, while $y_t$ is generated based on some conditional distribution based on $x_t$.
-For example, in \cite{crammer2013multiclass}, the label is generated by
-\begin{align}
-    p(y_t = i | x_t) = \frac{\alpha + (W^*x_t)_i}{\alpha+1}, \label{eqn:confidit assumption}
-\end{align}
-where $W^* \in \Omega_t \triangleq \{W\in \mathbb{R}^{K\times d}: \sum_{i=1}^K (Wx_t)_i = \alpha+1-K\alpha \text{\ and\ } -\alpha \leq (Wx_t)_i\}$; a valid $\Phi$ that satisfies \eqref{eqn:new margin} is
-\begin{align}
-    \Phi(u) = \frac{1}{2(\alpha+1)}\|u\|_2^2 + \frac{\alpha}{\alpha+1}\sum_{i=1}^K u_i. 
-\end{align}
-in \cite{agarwal2013selective}, the labels are generated by 
-\begin{align}
-    p(y_t = i | x_t) = \frac{\exp((W^*x_t)_i)}{\sum_{j=1}^K \exp((W^*x_t)_j) },
-\end{align}
-where $W^* \in \Omega \triangleq \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2 \leq D \}$, and $\Phi$ can be chosen as
-\begin{align}
-    \Phi(u) = \log\left(\sum_{i=1}^K \exp(u_i) \right). 
-\end{align}
-
-\textbf{Discussions}:  \\
-\begin{itemize}
-    \item Although \cite{hazan2011newtron, foster2018logistic} do not make stochastic assumptions, their loss functions are indeed strongly-convex and smooth (although $\gamma_u/\gamma_\ell$ can be quite large).
-It is worth notice that \cite{foster2018logistic} also obtained some logarithmic bound (their Theorem 3), but the bound is margin-independent.
-It seems that their Theorem 3 is tighter than our bound here.
-Not sure if it is because they use improper learning (we indeed should see whether improper learning helps in our problem).
-There is a $\alpha$ parameter in \cite{hazan2011newtron}, somehow it looks related to margin.
-    \item How is the assumptions/algorithms/bounds introduced in this section related to \cite{pillaud2017exponential}?
-They are similar in that they both assume $p(y|x)$ to be defined by some function in a known function class.
-The margin assumption \eqref{eqn:new margin} is a generalization of \cite{pillaud2017exponential}'s to the multiclass case.
-One can also view the FTRL step used in Selectron as the counterpart of the ridge regression step defined in \cite{pillaud2017exponential}.
-    \item We indeed have tried to use this kind of selective sampling idea to get finite error bound (see Section \ref{sec:kwik}).
-But it seems it is impossible/difficult to find a $\Phi(\cdot)$ that at the same time 1) is strongly convex, and 2) whose logarithmic/constant regret bound implies logarithmic/constant mistake bound.
-\end{itemize}
-
-%For simplicity, now we focus on the model assumed in \cite{crammer2013multiclass}.
-Besides the model, we assume the following ``margin assumption'' that is suitable for this kind of stochastic model:
-%\begin{align}
-%p(y_t|x_t) > \max_{y\neq y_t} p(y|x_t) + \gamma. 
-%\end{align} \label{eqn:stochastic margin}
-%This is also similar to the gap condition in \cite{pillaud2017exponential}. When this margin assumption is applied to the model assumption~\eqref{eqn:confidit assumption}, we get 
-%\begin{align}
-%    (W^*x_t)_{y_t} \geq \max_{y\neq y_t} (W^*x_t)_{y} + (\alpha+1)\gamma. 
-%\end{align}
-%This is similar to the linear separability in the non-stochastic case. But this is not enough for~\eqref{eqn:one-sided condition}. To make \eqref{eqn:one-sided condition} holds, we can
-
-%Below is a set of assumptions that is sufficient for \eqref{eqn:one-sided condition}: 
-%\begin{itemize}
-%    \item $\|\e_i^\top W^*\|_2\leq 1$ for all $i$ and $ \|x\|_2\leq 1 $ 
-%    \item $W^*_{ij} \geq 0, x_j \geq 0, \forall i,j$ (which implies $(W^*x)_y\geq 0$ for all $x$ and $y$) \\ 
-%    \item $(W^*x_t)_{y_t} \geq K\max_{y\neq y_t}(W^*x_t)_{y}  + 2K\Delta$ 
-%    \item Pick $\Omega_t = \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2\leq 1, W_{ij}\geq 0, \sum_{i=1}^K (Wx_t)_i \geq 2K\Delta \}$ (one can verify that $\Omega_t$ is convex, and $W^*\in \Omega_t$ if $W^*$ satisfies the above three assumptions).
-%\end{itemize}
-%To see why these assumptions imply \eqref{eqn:one-sided condition}, suppose that $\hat{y}_t\neq y_t$.
-Note that $(W_tx_t)_{\hat{y}_t} \geq \frac{1}{K}\sum_{i=1}^K (W_tx_t)_i\geq 2\Delta$, where the first inequality is because $\hat{y}_t=\argmax_y(W_tx_t)_i$ and the second inequality is because $W_t\in\Omega_t$.
-On the other hand,
-
-\section{A KWIK Algorithm {\color{red} [TODO]}}
-\label{sec:kwik}
-%\textbf{Observation}. Alekh's paper's results can be generalized to losses with $\Phi_t$ a strongly and smoothly convex function. 
-\begin{assumption}
-$\|x_t\|_2^2\leq 1$. There is a $W^*\in\mathcal{W}$ such that $\ell_t(W^*)\leq 0$ for all $t$ ($\ell_t$ and $\mathcal{W}$ are defined below).  
-\end{assumption}
-
-\begin{algorithm}[H]
-\caption{KWIK Banditron}
-\textbf{Input}: $D\geq 2$, $\epsilon$ (picked in a later lemma). \\
-\textbf{Definition}: 
-\begin{align*}
-    \ell_t(W) &\triangleq [1-(Wx_t)_{y_t} + \max_{r\neq y_t}(Wx_t)_r]_+^2 \ \ \ \ \text{(squared hinge loss)} \\
-    & = \Phi_t(Wx_t), 
-    %\Phi_t(z) \triangleq \sum_{i\neq y_t} \psi(z_{y_t}-z_i).
-\end{align*}
-where $\Phi_t(z)\triangleq [1-\e_{y_t}^\top z + \max_{r\neq y_t} \e_r^\top z]_+^2$. \\
-Also, define $\mathcal{W}=\{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2\leq D \text{\ for all }i\in[K]\}$. \\
-\textbf{Initialization}: $W_1=0, M_1=I$.\\ 
-\For{$t=1, \ldots, T$}{
-   Observe $x_t$. \\
-   \If{$ \| x_t \|_{M_t^{-1}} \geq \epsilon$ {\color{red} \text{and} $\|W_t-W^*\|_F\geq 1$}}{
-       Draw $\tilde{y}_t \sim \text{unif}([K])$. 
-   }
-   \Else{
-       Draw $\tilde{y}_t = \hat{y}_t \triangleq \argmax_{r\in[K]}(W_tx_t)_r$. 
-   }
-   \If{ $\tilde{y}_t=y_t$ }{
-       $Z_t\leftarrow 1$, \\
-       $M_{t+1}\leftarrow M_t + Z_t\ell_t(W_t)x_tx_t^\top$,\\
-       $W_{t+1} \leftarrow \Pi_{\mathcal{W}} (W_t - \eta_{t+1}\nabla \ell_t(W_t))$, \ \ \ \ \ where $\eta_{t+1} = \frac{1}{8}$. \\
-       ($\Pi_{\mathcal{W}}$ is the projection operator onto $\mathcal{W}$ w.r.t. Frobenius norm)
-   }
-   \Else{
-       $Z_t\leftarrow 0$,  \\
-       $M_{t+1}\leftarrow M_t$,\\
-       $W_{t+1}\leftarrow W_t$.
-   }
-
-}
-\end{algorithm}
-\iffalse
-We will pick 
-\begin{align*}
-     \psi(u)=\begin{cases}
-        \frac{1}{2K(1-D)^2}(u-D)^2 - \frac{1}{2K}, & \text{if $u\geq 1$} \\
-        \left(1+\frac{1}{K(1-D)}\right)u^2 + \left(-2-\frac{1}{K(1-D)}\right)u + 1 &\text{if $u\leq 1$},  
-     \end{cases}
-\end{align*}
-It has the following properties: \\
-(1) It is continuous and differentiable. \\
-(2) It is $\frac{1}{2K(1-D)^2}$-strongly convex and $1$-smooth. \\
-(3) It decreases in $[-D,D]$, passing through $(0,1),(1,0)$, and $(D,\frac{-1}{2K})$. \\
-(4) Its minimum value $\frac{-1}{2K}$ is attained at $u=D$.
-
-\begin{lemma} 
- For the above specific choice of $\psi$, $\Phi_t$ is $\frac{1}{2KD^2}$-strongly convex and $2K$-smooth (i.e., its Hessian has eigenvalues all within $[\frac{1}{2KD^2}, 2K]$).
-
-\end{lemma}
-\begin{proof}
-It is clear that $\frac{\partial^2}{\partial z_j\partial z_i}\Phi_t(z)=0$ for $i\neq j$.
-Also, $\frac{\partial^2}{\partial^2 z_i} \Phi_t(z)\geq \frac{1}{2K(1-D)^2}\geq \frac{1}{2KD^2}$ and $\frac{\partial^2}{\partial^2 z_i} \Phi_t(z)\leq K\left(1+\frac{1}{K(1-D)}\right)\leq 2K$.
-\end{proof}
-
-\begin{lemma}
-\label{lemma:error_cond}
-If $\argmax_r (Wx_t)_r = y_t$, then $\ell_t(W) \leq K$; 
-If $\argmax_r (Wx_t)_r \neq y_t$, then $\ell_t(W) \geq 1$.  
-\end{lemma}
-\begin{proof}
-If $\argmax_r (Wx_t)_r = y_t$, then $z_{y_t}-z_i\geq 0$ for all $i$, and thus $\Phi_t(z)< K\psi(0)=K$; 
-If $\argmax_r (Wx_t)_r \triangleq j \neq y_t$, then $\Phi_t(z)\geq \psi(z_{y_t}-z_j) - K\times \frac{1}{2K}\geq \psi(0)-\frac{1}{2}=\frac{1}{2}$. 
-This is clear by the definition of $\ell_t$. 
-\end{proof}
-\fi
-%\begin{definition}
-%$\|W\|_M^2 \triangleq \sum_{i=1}^K \|\e_i^\top W\|_M^2 $.\\
-%$\gamma_\ell \triangleq \frac{1}{2KD^2}$; $\gamma_u\triangleq 2K$ (convexity and smoothity of $\Phi_t$). 
-%\end{definition}
-
-%\begin{lemma}
-%For any $W^*\in \mathcal{W}$, with probability at least $1-\delta$, 
-%\begin{align*} 
-%    \|W_t-W^*\|_{M_t} \leq \tilde{\mathcal{O}}\left(\frac{\sqrt{Kd}}{\gamma_\ell} + D\sqrt{\gamma}\right).
-%\end{align*}
-%(the $\tilde{\mathcal{O}}$ notation hides $\ln T$, $\ln \frac{1}{\delta}$, $\ln \frac{1}{\gamma}$ factors)
-%\end{lemma}
-%\begin{proof}
-%By the first order optimality condition, we have for all $W^*\in \mathcal{W}$, 
-%\begin{align*}
-%    \inner{\gamma W_t+\sum_{s=1}^{t-1}Z_s \nabla \ell_s(W_t), W^*-W_t}\geq 0. 
-%\end{align*}
-%Rearranging it and plugging in the property $\nb\ell_s(W)=\nb\Phi_s(Wx_s)x_s^\top$ gives 
-%\begin{align}
-%    \sum_{s=1}^{t-1} Z_s\inner{ -\nb\Phi_s(W^*x_s),W_tx_s-W^*x_s} \geq  \sum_{s=1}^{t-1} Z_s\inner{ \nb\Phi_s(W_t x_s)-\nb\Phi_s(W^*x_s),W_tx_s-W^*x_s}+\gamma\inner{W_t, W_t-W^*}. 
-%    \label{eqn:key}
-%\end{align}
-%By $\Phi_s$'s convexity and that $\norm{W}_F^2\leq KD^2$ for all $W\in \mathcal{W}$, the RHS of \eqref{eqn:key} can be lower bounded by 
-%\begin{align*}
-%    \gamma_\ell\sum_{s=1}^{t-1} Z_s\norm{W_t x_s-W^*x_s}_2^2 - 2\gamma KD^2 \geq \gamma_\ell \norm{W_t-W^*}_{M_t}^2-2\gamma KD^2. 
-%\end{align*}
-%The LHS is upper bounded by 
-%\begin{align*}
-%    \sum_{i=1}^K \sum_{s=1}^{t-1} Z_s (-\nb_i\Phi_s(W^*x_s))\inner{\e_iW_t-\e_iW^*, x_s}
-%\end{align*}
-%\end{proof}
-
-\begin{lemma}
-\label{lemma:bound_gradient}
-$\norm{\nb\ell_t(W)}_F^2 \leq 8\ell_t(W)$. 
-\end{lemma}
-\begin{proof}
-$    \|\nb\ell_t(W)\|_F^2 = \|\nb\Phi_t(Wx_t)x_t^\top\|_{F}^2 \leq \left(2\sqrt{\Phi_t(Wx_t)}\right)^2\times 2\|x_t\|_{2}^2 \leq 8\ell_t(W).  
-$
-\end{proof}
-
-\begin{lemma}
-\label{lemma:decreasing error}
-Let $L_{t+1}\triangleq \sum_{s=1}^t Z_s\ell_s(W_s)$. Then 
-$\|W_{t+1}-W^*\|_F^2 \leq \exp\left(-\frac{L_{t+1}}{32KD^2}\right)$. 
-\end{lemma}
-\begin{proof}
-Let $Z_{t}=1$. 
-\begin{align*}
-    \|W_{t+1}-W^*\|_F^2 &\leq \|W_t - \eta_{t+1}\nb\ell_t(W_t)-W^*\|_F^2 \\
-    & = \| W_t - W^* \|_F^2 - 2\eta_{t+1}\inner{\nb\ell_t(W_t),W_t-W^*}_F + \eta_{t+1}^2\|\nb\ell_t(W_t)\|_F^2.  
-\end{align*}
-By the separable assumption we have $\ell_t(W^*)\leq 0$.
-Since $\ell_t$ is convex, $\inner{\nb\ell_t(W_t), W_t-W^*} \geq \ell_t(W_t)-\ell_t(W^*)\geq \ell_t(W_t)$.
-Continuing the above calculation and using Lemma~\ref{lemma:bound_gradient}, we get
-\begin{align*}
-    \|W_{t+1}-W^*\|_F^2 &\leq \|W_t-W^*\|_2^2 - 2\eta_{t+1}\ell_t(W_t) + 8\eta_{t+1}^2 \ell_t(W_t) \\ 
-    &\leq \|W_t-W^*\|_F^2 - \frac{1}{8}\ell_{t}(W_t) \\
-    &\leq \|W_t-W^*\|_F^2 \left(1-\frac{\ell_t(W_t)}{32KD^2}\right)  \text{\ \ \ \ because $\|W_t-W^*\|_F^2\leq 4KD^2$} \\
-    &\leq \|W_t-W^*\|_F^2 \exp\left(-\frac{\ell_t(W_t)}{32KD^2}\right)
-\end{align*}
-By induction, we can get
-\begin{align*}
-    \|W_{t+1}-W^*\|_F^2 &\leq KD^2 \exp\left( -\frac{L_{t+1}}{32KD^2} \right) 
-    %&\leq KD^2 \left(\frac{8KD^2}{A_{t+1}}\right)   %\ \ \ \ \ \text{because $\exp(-x)<1/x$ for any $x>0$} \\
-    %& = \frac{8K^2D^4}{A_{t+1}}. 
-\end{align*}
-\end{proof}
-
-\begin{definition}
-$\norm{W}_{M}^2\triangleq \sum_{i=1}^K \norm{\e_i^\top W}_{M}^2$.
-\end{definition}
-With this definition we have $\|Wx_t\|_2^2 = \sum_{i=1}^K (\e_i^\top Wx_t)^2 \leq \sum_{i=1}^K \|\e_i^\top W\|_M^2 \|x_t\|_{M^{-1}}^2\leq \|W\|_M^2 \|x_t\|_{M^{-1}}^2$
-
-\begin{lemma}
-\begin{align*}
-\|W_{t}-W^*\|_{M_{t}}^2 \leq (1+L_t)K^2D^2 \exp\left(-\frac{L_t}{32KD^2}\right) \leq 32K^3D^4. 
-\end{align*}
-\end{lemma}
-\begin{proof}
-Because we assume $\|x_t\|_2^2\leq 1$, it holds that $ M_t \preceq (1+L_t) I$.
-Therefore $\|W_t-W^*\|_{M_t}^2 \leq (1+L_t)\|W_t-W^*\|_I^2 =  (1+L_t) \sum_{i=1}^K \| \e_i^\top (W_t-W^*) \|_2^2 \leq (1+L_t) K \|W_t-W^*\|_F^2 $.
-By Lemma~\ref{lemma:decreasing error} this is bounded by $(1+L_t)K^2D^2\exp\left( -\frac{L_t}{32KD^2} \right)$, which can further be bounded by a constant related to $K$ and $D$.
-For example, using the property $\exp(-x)\leq \frac{1}{(1+x)^2}$ for all $x>0$, it can be upper bounded by $(1+L_t)K^2D^2 \times \frac{(32KD^2)^2}{(L_t+32KD^2)^2} \leq \frac{32^2K^4D^6}{32KD^2+L_t}\leq 32K^3D^4$.
-\end{proof}
-
-\begin{lemma}
-\label{lemma: xbounded}
-If $\|x_t\|_{M_t^{-1}}\leq \epsilon = \frac{1}{4D\sqrt{32K^3D^4}}$, then $\hat{y}_t=y_t$. 
-\end{lemma}
-\begin{proof}
-By the convexity of $\ell_t$, 
-\begin{align*}
-    \ell_t(W_t)\leq \ell_t(W_t)-\ell_t(W^*)&\leq \inner{\nb \ell_t(W_t), W_t-W^*}\\
-     & = \inner{\nb\Phi_t(W_tx_t)x_t^\top, W_t - W^*} \\
-    & = \inner{\nb\Phi_t(W_tx_t), W_tx_t - W^*x_t} \\
-    & \leq 4D\norm{W_tx_t-W^*x_t}_2 \\
-    & \leq 4D\norm{W_t-W^*}_{M_t}\norm{x_t}_{M_t^{-1}} \leq 1.
-\end{align*}
-This implies $\hat{y}_t=y_t$. 
-\end{proof}
-
-Therefore, when we do not explore, we know $W_t$ will predict correctly! Thus we only need to bound the number of errors occurred in exploration rounds, which is calculated by the following lemma.
-
-\begin{lemma}[{\color{blue} The conclusion is not meaningful}]
-\label{lemma:N}
-$\sum_{t=1}^T \one[\tilde{y}_t\neq y_t] \leq \max_{t\in[T]}\left(\frac{1}{\ell_{t}(W_t)}\right)\times \frac{K\ln T\ln \frac{1}{\delta}}{\epsilon^2}$ with probability at least $1-\delta$. 
-\end{lemma}
-
-\begin{proof}
-By the above discussion, $\sum_{t=1}^T \one[\tilde{y}_t\neq y_t] \leq N\triangleq \sum_{t=1}^T Z_t$, the number of exploration rounds. 
-\begin{align*}
-    N &= \sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right]\\
-    &\leq \left(K\ln \frac{1}{\delta}\right)\sum_{t=1}^T \one\left[\norm{x_t}_{M_t^{-1}}> \epsilon\right]Z_t \tag{when $\|x_t\|_{M_t^{-1}}\geq \epsilon$, $\tilde{y}_t=y_t$ with probability $\frac{1}{K}$} \\
-    & \leq \frac{K\ln \frac{1}{\delta}}{\epsilon^2}\sum_{t=1}^T \norm{x_t}_{M_t^{-1}}^2 Z_t \leq \max_{t\in[T]}\left(\frac{1}{\ell_{t}(W_t)}\right)\times \frac{K\ln T\ln \frac{1}{\delta}}{\epsilon^2}.
-\end{align*}
-\end{proof}
-
-\textbf{Discussion}. 
-In the calculation of Lemma~\ref{lemma: xbounded},  we can actually get $\ell_t(W_t)^2 \leq \norm{\nb\Phi_t(W_tx_t)}_2^2\norm{W_t-W^*}_{M_t}^2\norm{x_t}_{M_t^{-1}}^2$.
-Similar to the calculation in Lemma~\ref{lemma:decreasing error}, $\norm{\nb\Phi_t(W_tx_t)}_2^2$ is bounded by constant times $\ell_t(W_t)$.
-So the exploration criterion could potentially become $\ell_t(W_t)\|x_t\|_{M_t^{-1}}^2\geq \frac{1}{\epsilon^2}$, which makes Lemma~\ref{lemma:N} go through.
-The problem is we do not know $\ell_t(W_t)$ in general.
-
-\section{Regret Lower Bound for Explore-then-Exploit Algorithms {\color{red}[TODO]}}
-
-\section{A Regret Lower Bound for A Certain Type of Algorithms}
-\label{section: passive lower bound}
-In this section, we try to construct an error lower bound for a certain type of algorithms.
-This type of algorithms does not make update when it makes a wrong prediction.
-For simplicity, we only consider binary classification.
-More formally, the algorithms we consider satisfy the following assumption.
-
-\begin{assumption}[Algorithm]
-Let $p_t(x)$ be the algorithm's probability of predicting class $1$ (recall we consider binary classification) at round $t$ if it receives the feature vector $x\in \calX \subset \mathbb{R}^d$.
-We assume $p_t(\cdot)$ is totally determined by all previous \textbf{correct} examples.
-In other words, $p_t(\cdot)$ is determined by the tuple $((x_{\tau_1}, y_{\tau_1}), \ldots, (x_{\tau_N}, y_{\tau_N}))$ where $1\leq \tau_1 < \tau_2 \ldots < \tau_N < t$ are the rounds that the learner makes correct prediction.
-\end{assumption}
-
-\begin{assumption}[linearly separable with a margin]
-We assume the samples are linearly separable with margin $\gamma$ (i.e., any two points with different labels have distance no less than $\gamma$). 
-\end{assumption}
-
-\begin{definition}[Free space]
-The free space at time $t$ is the set of points whose label is still underdetermined given $(x_1, y_1), \ldots, (x_{t-1},y_{t-1})$.
-For example, the $\gamma$-ball centered around any already presented point is excluded from the free space.
-Denote the free space at time $t$ by $\FS_t$.
-\end{definition}
-The free space's definition simply means that at time $t$, the adversary can pick any point $x_t$ in $\FS_t$ and assign the label $y_t$ to either $1$ or $2$ without violating the linearly separable and the $\gamma$-margin assumption.
-
-Below we present the Adversary's strategy of constructing $(x_t, y_t)$.
-
-\begin{algorithm}[H]
-\caption{Adversary's strategy}
-Pick $x_1$ randomly from $\calX$, and let $y_1=1$. \\
-\For{$t=2, \ldots, T$}{
-    \If{$\tilde{y}_{t-1} \neq y_{t-1}$}{
-        Let $(x_t, y_t)=(x_{t-1}, y_{t-1})$
-    }
-    \ElseIf{$\FS_{t}$ is not empty}{
-        Pick $x_t\in \FS_{t}$.
-Because of this $x_t$, the free space's volume is reduced.
-We denote the reduction amount by $V_t=v(\FS_{t+1})-v(\FS_{t})\leq V$.
-(i.e., $V$ is a global upper bound of $V_t$) \\
-        If $p_t(x_t)\geq 1-\max\left\{\sqrt{V},\frac{1}{\sqrt{T}}\right\}$, then label $y_t=2$; otherwise, label $y_t=1$. 
-    }
-    \Else{
-        Randomly assign $(x_t,y_t)$ with some value that does not violate the assumption. 
-    }
-}
-\end{algorithm}
-
-%\textbf{Analysis}. We assume that in the ``else'' case in the above algorithm, we can always pick $x_t$ such that $V_t\leq V$ (we will show how to pick such $x_t$ later).
-
-\begin{definition}[history]
-Let $\calH_t$ be the history before time $t$: $\calH_t=\{ (x_s, y_s, \tilde{y}_s) \}_{s=1}^{t-1}$. We use $\E_t[\cdot]$ to denote $\E[\cdot | \calH_t]$. 
-\end{definition}
-
-\begin{lemma}
-If $\exists t$ such $p_t(x_t)\geq 1-\max\left\{ \sqrt{V}, \frac{1}{\sqrt{T}} \right\}$, then $\E_t\left[ \sum_{s=t}^T  \one[\tilde{y}_s\neq y_s] \right] \geq \Omega\left(\min\left\{\frac{1}{\sqrt{V}},\sqrt{T}\right\}\right)$.
-\end{lemma}
-\begin{proof}
-By of the condition and the adversary strategy, we have $y_t=2$.
-Therefore, the learner will predict the true label with probability $\leq \max \left\{ \sqrt{V}, \frac{1}{\sqrt{T}} \right\}$.
-And note that if the learner predicts incorrectly at time $t$, then at time $t+1$ the feature vector remains the same $(x_{t+1}=x_t)$ , and the learner's probability of prediction also remains the same $(p_{t+1}(\cdot)=p_t(\cdot))$.
-Therefore, the expected number of mistakes before the first correct guess is (roughly) larger than  $\frac{1}{\max\left\{\sqrt{V}, \frac{1}{\sqrt{T}}\right\}}=\min\left\{\frac{1}{\sqrt{V}}, \sqrt{T}\right\}$.
-\end{proof}
-
-\begin{lemma}
-If $\forall s$, $p_s(x_s)\leq 1-\max\left\{\sqrt{V}, \frac{1}{\sqrt{T}}\right\}$, then $\sum_{s=1}^T \E_s[\one[\tilde{y}_s\neq y_s]] = \Omega\left(\min\left\{\sqrt{T}, \frac{1}{\sqrt{V}}\right\}\right)$.
-\end{lemma}
-
-\begin{proof}
-By the condition and the adversary strategy, we know that the probability of error is larger than $\max\left\{\sqrt{V},\frac{1}{\sqrt{T}}\right\}$ at all time $t$ \textit{before the free space is used up}.
-Since each time the free space only reduces by $V$, in the first $\frac{1}{V}$ rounds (assume the total volume is $1$), the free space is still all available.
-Therefore,
-\begin{align*}
-    \sum_{s=1}^T \E_s[\one[\tilde{y}_s\neq y_s]] \geq \min\left\{ T,\frac{1}{V} \right\}\times \max\left\{ \sqrt{V}, \frac{1}{\sqrt{T}} \right\}=\min\left\{\sqrt{T}, \frac{1}{\sqrt{V}}\right\}. 
-\end{align*}
-\end{proof}
-
-\textbf{Discussion}. There is a construction such that $1/V$ can be of order $\Omega\left( \left(\frac{1}{\gamma}\right)^{(d-1)/2} \right)$. {\color{red} [TODO] How to construct such points?}
-
-%This lower bound does not rule out those algorithms that change its probability vector based on the $\textbf{count}$ of consecutive errors.
-This type of algorithm may still easy to be implemented (like QBC).
-Also it does not rule out the banditron algorithm.
-
-\section{How Hard It Is Only Using The Weak Labels?}
-The halving algorithm can actually run if we can do ``uniform sampling'' over the version space.
-But it is even unknown whether we can efficiently pick a model from the version space.
-The problem is that we get a lot of feedback in the form of ``feature $x_t$ does not belong to class $\tilde{y}_t$'', which we don't know how to use.
-
-The following is just an attempt (not successful but might be interesting...) to say that it might be not easy to figure out a model if the learner is only presented with this kind of ``error message''.
-
-The problem is formulated as follows. 
-Given $N$ points in a row, each one with a class $c_i\in [K]$, $\forall i\in [N]$. We call these $N$ points \textit{separable} if the following statement holds: 
-\begin{center}
-    If $c_i=c_j$ for some $i\leq j$, then $c_i=c_{i+1}=\cdots=c_j$.
-\end{center}
-For example, if $N=5, K=3$, then $(c_1,c_2, c_3, c_4,c_5)=(3,3,1,1,1)$ is separable, but $(c_1,c_2,c_3,c_4,c_5)=(2,1,2,2,2)$ is not. 
-\ \\
-\ \\
-Now you have $N$ conditions, in which the $i$-th condition only says something like ``$c_i\neq k$'' for some $k$. \\
-(1) Can you efficiently decide whether there exists an assignment of $(c_1,\ldots,c_N)$ such that these $N$ points are separable and satisfy all the conditions? \\
-(2) If it is guaranteed that there are separable solutions, can you efficiently find one of them?\\ (Efficient: the complexity is polynomial in $N$ and $K$)
-\ \\
-\ \\
-\textbf{Example 1}. \\
-$N=5, K=3$: \\
-$c_1\neq 1$ \\
-$c_2\neq 2$ \\
-$c_3\neq 3$ \\
-$c_4\neq 1$ \\
-$c_5\neq 2$ \\
-$\Rightarrow (c_1,c_2,c_3,c_4,c_5)=(2,1,1,3,3)$ or $(3,3,2,2,1)$ are separable solutions. \\
-\ \\
-\textbf{Example 2}. \\
-$N=7, K=3$: \\
-$c_1\neq 1$ \\
-$c_2\neq 2$ \\
-$c_3\neq 3$ \\
-$c_4\neq 1$ \\
-$c_5\neq 2$ \\
-$c_6\neq 3$ \\
-$c_7\neq 1$ \\
-$\Rightarrow$ There is no separable solution. \\
-
-It turns out this specific 1-dimensional problem is equivalent to identify a \textbf{missing permutation} of $[K]$ as a subsequence in the weak-label sequence.
-In Example 1, the existing permutations are $(1,2,3), (1,3,2), (2,3,1), (3,1,2)$, the missing ones are $(2,1,3)$ and $(3,2,1)$.
-So the solutions can be $(2,1,3)$ or $(3,2,1)$ (with some repetition).
-In Example 2, all permutations appear in the weak-label sequence, so there is no solution.
-
-We can prove this equivalence considering two directions: \\
-(1) If there is a solution whose class labels follow a permutation, then that permutation cannot be a subsequence of the weak-label sequence. \\
-(2) If there is a missing permutation in the weak-label sequence, then there is a class label assignment that follows this permutation.\\ 
-{\color{red} [TODO] Proof}
-
-%\section{Cone Algorithm}
-%\begin{algorithm}[H]
-%\caption{Banditron}
-%\textbf{definition}: $K\triangleq$ number of classes, $\gamma\triangleq$  margin\\
-%\textbf{Initialize}: $\calS_1=\cdots=\calS_K=\phi$ (empty set) \\
-%\For{$t=1, \ldots, T$}{
-%    Receive $x_t\in \mathbb{R}^d$. \\
-%    Define the cone $\calC_i = \left\{x\in\mathbb{R}^d: x=\sum_{j=1}^{|\calS_i|} \alpha_jy_j, \text{\ where\ } y_j\in \calS_i, \alpha_j\geq 0 \right\}$ \\
-%    (that is, $\calC_i$ is the conic hull of $\calS_i$) \\
-%    Check whether $x_t$ belongs to, or has distance smaller than $\gamma$, to one of $\calC_1, \ldots, \calC_K$. \\
-%    If so, classify $x_t$ to the corresponding class (say class $i$), and let $\calS_i\leftarrow \calS_i \cup \{x_t\}$.
-{\color{red} This prediction will be correct for sure by our margin assumption.}\\
-%    If not, let $\tilde{y}_t\sim \text{unif}([K])$ and predict $\tilde{y}_t$. If $\tilde{y}_t=y_t$, then $\calS_{y_t}\leftarrow \calS_{y_t} \cup \{x_t\}$. 
-%}
-%\end{algorithm}
-
-\section{Biased Halving: Trading Error with Complexity}
-\begin{algorithm}[H]
-\caption{Banditron}
-\textbf{Define}: $\Omega=\{W\in \mathbb{R}^{Kd}: \|\e_i^\top W\|_2\leq D\}$.\\
-For a set $S$ of $W$'s, $S(i|x)$ is the subset of $S$ that outputs class $i$ given feature vector $x$, i.e., $S(i|x)=\{W\in S: (Wx)_i \geq (Wx)_j \ \forall j\}$\\
-$|S|$ denotes the volumn of $S$. \\
-\textbf{parameter}: $\alpha \in (0,1)$ \\
-$\Omega_1=\Omega$.  \\
-\For{$ t=1,\ldots, T $}{
-\If{$\argmax_i \frac{|\Omega_t(i|x_t)|}{|\Omega_t|} \geq 1-\alpha$}{ \label{line:case1}
-        Let $\tilde{y}_t=i$.\\ 
-        \If{$\tilde{y}_t \neq y_t$}{
-            $\Omega_{t+1}=\Omega_t \backslash \Omega_t(\tilde{y}_t|x_t)$. \label{line:cut}
-        }
-    }
-\label{line:case2}\Else{
-        Let $\tilde{y}_t\sim \text{unif}([K])$. \\
-        \If{$\tilde{y}_t=y_t$}{
-            $\Omega_{t+1}=\Omega_t(\tilde{y}_t|x_t)$. \label{line:cut2}
-        }
-    }
-}
-\end{algorithm}
-
-\textbf{Conjecture(should be true)}: If the volume of $\Omega_t$ becomes smaller than $\frac{|\Omega|}{N}$, then the algorithm won't make any error anymore.
-$N$ should be in the order of $\Theta(\frac{1}{\gamma^{Kd}})$.
-\\
-\textbf{Rough analysis:} \\
-Each time the algorithm makes an error in Line~\ref{line:case1}, the volume becomes $\alpha$ times the original volume.
-So the algorithm will not make more than $ \frac{\ln N}{\ln \frac{1}{\alpha}} $ mistakes in this case.
-
-In the case of Line~\ref{line:case2}, $K\ln \frac{1}{\delta}$ errors will accompany with a $(1-\alpha)$-factor shrinkage in the volume.
-Therefore, the number of errors occurred in this case is upper bounded by $ \frac{K\ln\frac{1}{\delta}\ln N}{\ln \frac{1}{1-\alpha}}\leq \frac{K\ln\frac{1}{\delta}\ln N}{\alpha} $.
-
-Now we discuss about the complexity.
-The main issue is how to maintain $\Omega_t$.
-Each time the algorithm enters Line~\ref{line:cut}, $\Omega_t$ becomes more and more fragmented.
-But if $\Omega_t$ can be maintained with $M$ convex cones, then $\Omega_{t+1}$ can be maintained with $(K-1)M\leq KM$ convex cones.
-And we assume each cone's volume can be computed in \text{poly}($T$) time.
-Each time the algorithm enters Line~\ref{line:cut2}, the number of convex cones does not increase.
-
-By the above discussion, there will be no more than $K^{\frac{\ln N}{\ln \frac{1}{\alpha}}}$ convex cones to maintain.
-And the error bound is in the order of $\frac{K\ln\frac{1}{\delta}\ln N}{\alpha}$ for some $\alpha<\frac{1}{2}$.
-Let's try to balance the number of errors and computational complexity.
-Let
-\begin{align*}
-    &K^{\frac{\ln N}{\ln \frac{1}{\alpha}}}\approx\frac{K\ln\frac{1}{\delta}\ln N}{\alpha}\\
-    \Rightarrow &~ \frac{\ln N}{\ln\frac{1}{\alpha}} \ln K \approx  \ln\left(K\ln\frac{1}{\delta}\ln N\right) + \ln\frac{1}{\alpha}\\
-    \Rightarrow &~ \text{pick\ }\ln\frac{1}{\alpha}=\sqrt{\ln N}.
-\end{align*}
-Thus the computational complexity is in the order of $K^{\sqrt{\ln N}}\times \text{poly}(T)=K^{\sqrt{Kd\ln\frac{1}{\delta}}}$.
-The error bound is $\mathcal{O}\left( e^{\sqrt{Kd\ln \frac{1}{\delta}}} K^2 d \ln\frac{1}{\delta}\ln\frac{1}{\gamma} \right)$.
-
-Another viewpoint: let $\frac{1}{\alpha}=K^\beta$, then the complexity is $\left(\frac{1}{\gamma}\right)^{\frac{Kd}{\beta}}\times \text{poly}(T)$ and the error bound is $K^{\beta+1}\ln\frac{1}{\delta}\ln N$.
-
-%\section{Reservoir Sampling}
-%\textbf{Observation}.
-In Algorithm 2 of the SOBA paper, $\tilde{\ell}$ is constructed as a $ \tilde{\mathcal{O}}(\gamma \eta)$-exp-concave function which appears at the rate of $\gamma$.
-What if we divide a $\tilde{\mathcal{O}}(\gamma\eta)$-exp-concave function into roughly $1/\gamma$ $\tilde{\mathcal{O}}(\eta)$-exp-concave functions?
-
-%\begin{algorithm}[H]
-%\caption{Banditron}
-%\textbf{Input}: $D\geq 2$, $\epsilon$, $\gamma$. \\
-%\textbf{Definition}:
-
-%\end{algorithm}
-
-\section{Continuous EXP4 with Uniform Exploration}
-
-\begin{algorithm}[H]
-\caption{Banditron}
-\textbf{Parameters}: feasible set $\Omega\subset \mathbb{R}^{K\times d}$ \\
-\textbf{Definitions}: $\ell_t(W)\triangleq [1-(Wx_t)_{y_t}+\max_{r\in[K]}(Wx_t)_r]_+$ (hinge loss)\\
-\For{$t=1, \ldots, T$}{
-    Receive $x_t\in \mathbb{R}^d$. \\
-    Define 
-    \begin{gather*}
-    q_t(W)=\frac{\exp(-\alpha \sum_{s=1}^{t-1} \hat{\ell}_s(W))}{\int_{U\in \Omega} \exp(-\alpha \sum_{s=1}^{t-1} \hat{\ell}_s(U))dU }, \ \ \ \ \forall W\in\Omega, 
-    %\Omega_k^t\triangleq\{W\in\Omega: k=\argmax_{r\in[K]} (Wx_t)_r\} \ \ \ \text{i.e., the set of $W$'s that predict class $k$ at time $t$}\\
-    %p_t(k)=\int_{W\in \Omega_k^t} q_t(W)dW, \ \ \ \ \forall k\in[K], \\
-    %\tilde{p}_t(k) \propto p_t(k)\one[p_t(k)\geq \epsilon]
-    \end{gather*} 
-    where $\hat{\ell}_s(W)=\one[\tilde{y}_s=y_s]\left(\frac{\one[\hat{y}_s= y_s]\ell_s(W)}{1-\gamma+\frac{\gamma}{K}} + \frac{\one[\hat{y}_s\neq y_s]\ell_s(W)}{\frac{\gamma}{K}}\right)$.\\
-    Sample $W_t\sim q_t$, and let $\hat{y}_t = \argmax_{r\in[K]}(W_tx_t)_r$.\\
-    Let $\tilde{y}_t=\hat{y}_t$ with probability $1-\gamma$, and $\tilde{y}_t\sim \text{unif}([K])$ with probability $\gamma$. 
-}
-\end{algorithm}
-
-%\begin{assumption}
-%\label{assump:zero}
-%   Assume we know there exists a $W^*\in \Omega$ having zero loss (i.e., $\ell_t(W^*)=0$ for all $t$). 
-%\end{assumption}
-
-%\begin{definition}
-%Define $\tilde{q}_t(W) = q_t(W)\times \frac{\tilde{p}_t(k')}{p_t(k')}$ with $k' = \argmax_r(Wx_t)_r$ (i.e., letting $\tilde{q}_t$ scales with $\tilde{p}_t$). 
-%\end{definition}
-%\begin{definition}
-%Define $\bar{\ell}_t(k)=\int_{W\in\Omega_k^t} \tilde{q}_t(W)\ell_t(W)dW \big/ \int_{W\in\Omega_k^t} \tilde{q}_t(W)dW $, that is, the average loss over $W$'s that predicts class $k$.
-Defining this is because our problem is slightly different from traditional contextual bandit formulation: with hinge loss, the loss received by different experts may be different even if they predict the same class/action.
-Note that while $\ell_t(\cdot), \hat{\ell}_t(\cdot)$ are losses for experts, $\bar{\ell}_t(\cdot)$ is loss for actions.
-%\end{definition}
-
-%\begin{lemma}
-%$\int_{W\in\Omega}q_t(W)\hat{\ell}_t(W)\geq (1-K\epsilon)\bar{\ell}_t(\hat{y}_t)$. 
-%\end{lemma}
-%\begin{proof}
-%By the definition of $\tilde{p}_t$, we have $1\leq \frac{\tilde{p}_t(k)}{p_t(k)}\leq \frac{1}{1-K\epsilon}$ for all $k$.
-Thus $1\leq \frac{\tilde{q}_t(W)}{q_t(W)}\leq \frac{1}{1-K\epsilon}$ for all $W$.
-Therefore,
-%\begin{align*}
-%    \int_{W\in\Omega}q_t(W)\hat{\ell}_t(W)dW&\geq (1-K\epsilon)\int_{W\in\Omega}\tilde{q}_t(W)\hat{\ell}_t(W)dW \\
-%    &=(1-K\epsilon)\left(\one[\hat{y}_t=y_t]\sum_{k=1}^K \tilde{p}_t(k)\bar{\ell}_t(k) + \one[\hat{y}_t\neq y_t]\sum_{k=1}^K \tilde{p}_t(k)\bar{a}_t(k)\right). 
-%\end{align*}
-%\end{proof}
-
-%\begin{lemma}
-%\label{lemma:simple}
-%The following facts hold: \\
-%(1) $ \hat{\ell}_t(W)\leq \ell_t(W)$ for all $W$. \\
-%(2) $ \hat{\ell}_t(W_t) \geq \ell_t(W_t) $. 
-%\end{lemma}
-%\begin{proof}
-%\ \\
-%(1) $ \hat{\ell}_t(W)\leq \one[\hat{y}_t=y_t]\ell_t(W)+\one[\hat{y}_t\neq y_t]\ell_t(W) = \ell_t(W)$. \\
-%(2) $ \hat{\ell}_t(W_t)\geq \one[\hat{y}_t\neq y_t]a_t(W_t)=\one[\hat{y}_t\neq y_t]=\ell_t(W_t)$. 
-%\end{proof}
-
-%By standard analysis of the exponential weight algorithm (or see page 9 of \cite{bubeck2017kernel}), we have 
-%\begin{align*}
-%\E\left[\sum_{t=1}^T\int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right] &\leq \E\left[\sum_{t=1}^T\hat{\ell}_t(W^*) + \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \alpha \sum_{t=1}^T\int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)^2dW\right] \\
-%&\leq \E\left[\sum_{t=1}^T\hat{\ell}_t(W^*) + \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \alpha \sum_{t=1}^T\int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right],
-%\end{align*}
-%which implies $\E\left[\sum_{t=1}^T\hat{\ell}_t(W_t)\right]\leq  \E\left[\sum_{t=1}^T  \hat{\ell}_t(W^*) \right]+\frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha(1-\alpha)}+\frac{\alpha}{1-\alpha}\E\left[\sum_{t=1}^T\hat{\ell}_t(W^*)\right] $.
-Combining Lemma~\ref{lemma:simple}, we get a small-loss regret bound.
-
-%\textbf{Note.} Considering $\delta(W^*)$ as a distribution in a region surrounding $W^*$ which has $1/(TD)^{dK}$ $\Omega$'s volume, then $\textbf{Ent}(q_1||\delta(W^*))$ should be in the order of $dK\log (TD)$.
-
-%\textbf{Discussion.} \\
-%(1) It seems even okay to define $\hat{\ell}_s(W)=\one[\hat{y}_s\neq y_s]a_s(W)$. \\
-%(2) $q_t(\cdot)$ can be sampled when $\sum_{s=1}^{t-1}\hat{\ell}_s(W)$ is convex (not very sure, but I believe so from papers like \cite{lovasz2006fast,narayanan2013efficient,bubeck2015sampling}).
-The part $ \one[\hat{y}_s=y_s]\ell_s(W)$ can become convex if we define $\ell(W)$ to be the hinge loss; however, the part $\one[\hat{y}_s\neq y_s]a_s(W)$ does not seem to be easy.
-This corresponds to constructing a loss function when the learner is wrong, and is somewhat related to the issue we met previously: the region $\{W: \hat{y}_t\neq \argmax_r (Wx_t)_r \}$ is non-convex.
-
-%\section{Continuous EXP4 for Banditron with Uniform Exploration}
-\begin{lemma}
-$\E_{\tilde{y}_t}[\hat{\ell}_t(W)] = \ell_t(W)$ for all $W$. 
-\end{lemma}
-\begin{proof}
-\begin{align*}
-\E_{\tilde{y}_t}[\hat{\ell}_t(W)] &= \E_{\tilde{y}_t}\left[ \one[\hat{y}_s=y_s] \frac{\one[\tilde{y}_s=y_s]\ell_t(W)}{1-\gamma+\frac{\gamma}{K}}   +
-\one[\hat{y}_s\neq y_s] \frac{\one[\tilde{y}_s = y_s]\ell_t(W)}{\frac{\gamma}{K}}\right] \\
-& = \one[\hat{y}_s=y_s] \ell_t(W)   +
-\one[\hat{y}_s\neq y_s] \ell_t(W) = \ell_t(W). 
-\end{align*}
-\end{proof}
-
-%\begin{lemma}
-%$\E_{\tilde{y}_t}[(\hat{\ell}_t(W))^2] \leq \frac{2K}{\gamma}(\ell_t(W))^2\leq \frac{2K}{\gamma}\ell_t(W)$ for all $W$. 
-%\end{lemma}
-
-Plugging these lemmas in the previous hedge bound, we can get \begin{align*}
-&\E\left[\sum_{t=1}^T  \ell_{t}(W_{t})  \right]\\
-&=\E\left[\sum_{t=1}^T  \int_{W\in\Omega} q_t(W)\ell_t(W)dW  \right] \\
-&=\E\left[\sum_{t=1}^T \E_{\tilde{y}_t} \left[ \int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right] \right]\\
-&\leq \E\left[\sum_{t=1}^T \E_{\tilde{y}_t} \left[ \hat{\ell}_t(W^*) \right]+ \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \alpha \sum_{t=1}^T \E_{\tilde{y}_t}\left[ \int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)^2dW \right] \right] \\
-&\leq \E\left[\sum_{t=1}^T \E_{\tilde{y}_t}\left[ \hat{\ell}_t(W^*) \right] + \frac{\textbf{Ent}(q_1||\delta(W^*))}{\alpha} + \frac{2K\alpha}{\gamma} \sum_{t=1}^T \E_{\tilde{y}_t}\left[ \int_{W\in\Omega} q_t(W)\hat{\ell}_t(W)dW \right]\right]
-\end{align*}
-
-...
-to bound the regret, it would be something like bounding $\frac{1}{1-\frac{K\alpha}{\gamma}}\left(\frac{1}{\alpha}+\frac{K\alpha}{\gamma}L^* + \gamma T\right)$, which gives $(L^*T)^{1/3} + \sqrt{T}$ regret bound.
-
-\textbf{Discussion.} We can change $\ell_t(\cdot)$ to any reasonable convex loss (e.g., logsitic loss or second-order loss).
 

### 2018-10-11 ptf_margin.tex
started rational approximation

@@
 \subsection{Construction using rational functions}
+\paragraph{The construction.} Define
+\[
+  Q(x) = \sum_{i=1}^t S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) - (t - \frac 1 2).
+\]
+where function
+\[
+S_n^k(x) = \frac{P_n(-x)^{h(k)} - P_n(x)^{h(k)}}{P_n(-x)^{h(k)} + P_n(x)^{h(k)}} = \frac{A_n^k(x)}{B_n^k(x)},
+\]
+$h(k)$ is the smallest odd integer greater than $\log(2k+1)$, and $P_n(x) = (x - 1) \cdot \prod_{i=1}^n (x - 2^i)^2$.
+
+\begin{lemma}[~\cite{klivans2004learning}]
+For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y Q(x) \geq \frac 1 2$.
+\end{lemma}
+\begin{proof}
+We consider two cases regarding the label of the example.
+\end{proof}
+
+\begin{fact}
+$S_n^k(\cdot)$ has the following properties:
+\begin{enumerate}
+\item If $x$ is in $[1, 2^n]$, then $S_n(x)$ is in $[1, 1 + \frac 1 k]$.
+\item If $x$ is in $[2^{-n}, -1]$, then $S_n(x)$ is in $[-1 - \frac 1 k, -1]$.
+\item If $x$ is in $[-1, 1]$, then $|S_n(x)|$ is in $[-1, 1]$.
+\item For all $x$ in $\fR$, $|B_n^k(x)| \geq \frac{2k}{2k+1} 2^{\frac{n(n-1)h(k)}2}$.
+\end{enumerate}
+\end{fact}
 

### 2018-10-12 ptf_margin.tex
in the middle of rational approximation

@@
 \item $\phi(x) = ( \sqrt{ (\frac 1 2)^{i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$.
-This coresponds to the kernel $K(x,x') = \frac{1}{1 - \frac 1 2 \inner{x,x'}}$.
+This corresponds to the kernel $K(x,x') = \frac{1}{1 - \frac 1 2 \inner{x,x'}}$.
 \end{enumerate}
@@
 $h(k)$ is the smallest odd integer greater than $\log(2k+1)$, and $P_n(x) = (x - 1) \cdot \prod_{i=1}^n (x - 2^i)^2$.
+Denote by $D_i(x) = S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma})$. $Q$ can therefore be simplified to 
+\[ Q(x) = \sum_{i=1}^t D_i(x) - (t - \frac 1 2). \]
 
@@
 We consider two cases regarding the label of the example.
+\begin{enumerate}
+\item Suppose $y = 1$, then for all $i$ in $[t]$, $v_i \cdot x \in [\gamma, 1]$. This implies that $\frac{v_i \cdot x}{\gamma} \in [1, \frac 1 \gamma]$. 
+By item~\ref{item:sign-rt} of Fact~\ref{fact:newman}, we have that $D_i(x) \in [1, 1+ \frac 1 {2t}]$. 
+Hence, $Q(x) \geq t - (t - \frac 1 2) \geq \frac 1 2$.
+
+\item Suppose $y = -1$. First observe that for all $i$ in $[t]$, $\frac{v_i \cdot x}{\gamma} \in [-\frac 1\gamma, \frac 1 \gamma]$. By items~\ref{item:sign-rt},
+~\ref{item:sign-lt} and~\ref{item:sign-mid} of Fact~\ref{fact:newman}, we have that $S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) \leq 1+ \frac 1 {2t}$.
+In addition, by Definition~\ref{def:int-margin}, there exists an $i_0$ in $[t]$, such that $v_{i_0} \cdot x \leq -\gamma$. 
+By item~\ref{item:bound-out} of Fact~\ref{fact:cheb}, we have that
+$D_{i_0}(x) \in [-1 - \frac 1 {2t}, -1]$.
+Hence, 
+\[ Q(x) = D_{i_0}(x) + \sum_{i \neq i_0} D_i(x) - (t - \frac 1 2)
+\leq -1 + (t-1)(1 + \frac 1 {2t}) - (t - \frac 1 2) \leq - \frac 1 2. \]
+%\leq -1 + t-1 + \frac{t-1}{2t} - (t - \frac 1 2)
+
+\end{enumerate}
 \end{proof}
@@
 \begin{enumerate}
-\item If $x$ is in $[1, 2^n]$, then $S_n(x)$ is in $[1, 1 + \frac 1 k]$.
-\item If $x$ is in $[2^{-n}, -1]$, then $S_n(x)$ is in $[-1 - \frac 1 k, -1]$.
-\item If $x$ is in $[-1, 1]$, then $|S_n(x)|$ is in $[-1, 1]$.
-\item For all $x$ in $\fR$, $|B_n^k(x)| \geq \frac{2k}{2k+1} 2^{\frac{n(n-1)h(k)}2}$.
+\item If $x$ is in $[1, 2^n]$, then $S_n^k(x)$ is in $[1, 1 + \frac 1 k]$. \label{item:sign-rt}
+\item If $x$ is in $[-2^{-n}, -1]$, then $S_n^k(x)$ is in $[-1 - \frac 1 k, -1]$. \label{item:sign-lt}
+\item If $x$ is in $[-1, 1]$, then $|S_n^k(x)|$ is in $[-1, 1]$. \label{item:sign-mid}
+\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $\abs{B_n^k(x)} \geq 2^{\frac{n(n-1)h(k)}2 - 1}$. \label{item:sign-denom}
 \end{enumerate}
+\label{fact:newman}
 \end{fact}
+\begin{proof}
+We prove all the items accordingly.
+\begin{enumerate}
+\item Observe that $S_n^k(x)$ can be written as:
+\[ S_n^k(x) = \frac{1 + (-\frac{P_n(x)}{P_n(-x)})^{h(k)}}{ 1 - (-\frac{P_n(x)}{P_n(-x)})^{h(k)} }.  \]
+Denote by $r = (-\frac{P_n(x)}{P_n(-x)})^{h(k)}$. By item~\ref{item:x-large} of Fact~\ref{fact:pn}, $r \in [0, \frac{1}{2k+1}]$. This implies that 
+$S_n^k(x) = \frac{1+r}{1-r} \in [1, 1 + \frac 1 k]$.
+
+\item The item follows from item~\ref{item:sign-rt} and the fact that $S_n^k(\cdot)$ is an odd function.
+
+\item Note that if $x$ is in $[0, 1]$, then by item~\ref{item:x-small} of Fact~\ref{fact:pn}, $r = (-\frac{P_n(x)}{P_n(-x)})^{h(k)} \in [-1, 0]$.
+This implies that $S_n^k(x) = \frac{1+r}{1-r} \in [0,1]$.
+As $S_n^k$ is an odd function, we also have that $S_n^k(x) \in [-1, 0]$ for all $x$ in $[-1, 0]$.
+This proves the item.
+
+\item If $x$ is in $[1,2^n]$, then $\abs{B_n^k(x)} = \abs{P_n(-x)^{h(k)}} (1 - r) \geq \abs{P_n(-x)^{h(k)}} \cdot \frac{2k}{2k+1} \geq 2^{\frac{n(n-1)h(k)}{2}} \cdot \frac{2k}{2k+1}$.
+If $x$ is in $[0,1]$, as both $P_n(-x)$ and $-P_n(x)$ are $\leq 0$, we have $\abs{B_n^k(x)} \geq \abs{P_n(-x)^{h(k)}} \geq 2^{\frac{n(n-1)h(k)}{2}}$. Therefore, for all $x \in [0,2^n]$, 
+$\abs{B_n^k(x)} \geq \frac 1 2 2^{\frac{n(n-1)h(k)}2}$. The item is concluded by noticing that $B_n^k(x)$ is an even function.
+
+\end{enumerate}
+
+\end{proof}
+
+\begin{fact}
+The following is true:
+\begin{enumerate}
+\item If $x \in [0,1]$, then $0 \leq -P_n(x) \leq -P_n(-x)$. \label{item:x-small}
+\item If $x \in [1, 2^n]$, then $0 \leq 4P_n(x) \leq -P_n(-x)$. \label{item:x-large}
+\end{enumerate}
+\label{fact:pn}
+\end{fact}
+\begin{proof}
+First, observe that for any $x \geq 0$, for all $i$, $(x+2^i)^2 \geq (x - 2^i)^2$ holds.
+
+For the first item, given that $x \in [0,1]$, $-(-x-1) \geq 1-x \geq 0$. Therefore,
+\[ \frac{-P_n(-x)}{-P_n(x)} = \frac{-(-x-1)}{1-x} \prod_{i =1}^n \frac{(x+2^i)^2}{(x - 2^i)^2}  \geq 1. \]
+
+For the second item, given that $x \geq 1$, $-(-x-1) \geq x-1 \geq 0$. In addition, as $x$ is in $[1,2^n]$, there exists an $i_0 \in [n]$ such that $2^{i_0-1} \leq x \leq 2^i_0$. Therefore, 
+$(x+2^i)^2 \geq 4(x - 2^i)^2$. Hence,
+\[ \frac{-P_n(-x)}{P_n(x)} = \frac{-(-x-1)}{ x-1} \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \geq 4. \]
+
+\end{proof}
 

### 2018-10-12 ptf_margin.tex
.

@@
 
+\newcommand{\cz}[1]{\textcolor{blue}{Chicheng: #1}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{enumerate}
-\item $\phi(x) = (x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0} = (x_S)_{S \in N^d, \|S\|_1 \leq \deg}$.
+\item $\phi_1(x) = (x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0} = (x_S)_{S \in N^d, \|S\|_1 \leq \deg}$.
 This corresponds to the complete symmetric kernel $K_{\deg}$.
-\item $\phi(x) = ( \sqrt{ {\deg \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$.
+\item $\phi_2(x) = ( \sqrt{ {\deg \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$.
 This corresponds to the polynomial kernel
 $K_{\deg}'(x,x') = (1 + \inner{x, x'})^{\deg}$.
-\item $\phi(x) = ( \sqrt{ (\frac 1 2)^{i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$.
+\item $\phi_3(x) = ( \sqrt{ (\frac 1 2)^{i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$.
 This corresponds to the kernel $K(x,x') = \frac{1}{1 - \frac 1 2 \inner{x,x'}}$.
@@
 \subsection{Construction using rational functions}
-\paragraph{The construction.} Define
+\paragraph{The construction.} Define rational function
 \[
@@
 \[
-S_n^k(x) = \frac{P_n(-x)^{h(k)} - P_n(x)^{h(k)}}{P_n(-x)^{h(k)} + P_n(x)^{h(k)}} = \frac{A_n^k(x)}{B_n^k(x)},
+S_n^k(x) = \frac{P_n(-x)^{h(k)} - P_n(x)^{h(k)}}{P_n(-x)^{h(k)} + P_n(x)^{h(k)}},
 \]
 $h(k)$ is the smallest odd integer greater than $\log(2k+1)$, and $P_n(x) = (x - 1) \cdot \prod_{i=1}^n (x - 2^i)^2$.
-Denote by $D_i(x) = S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma})$. $Q$ can therefore be simplified to 
-\[ Q(x) = \sum_{i=1}^t D_i(x) - (t - \frac 1 2). \]
+
+Now denote by $A_n^k(x) = P_n(x)^{h(k)} - P_n(-x)^{h(k)}$, $B_n^k(x) = -P_n(-x)^{h(k)} - P_n(x)^{h(k)}$.
+\cz{Note the difference between this line and KS04 - we multiply by $B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}\gamma)$ as opposed to its square.
+The latter would also work, but it will make the equations more cumbersome.}
+Define polynomial $p$ as
+\begin{eqnarray*}
+  p(x) &:=& \sum_{i=1}^t A_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) \cdot \prod_{j \neq i} B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) - (t-\frac12) \prod_{j=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma})
+\end{eqnarray*}
+
+It can be seen that
+$p(x) = \prod_{i=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}\gamma) \cdot Q(x)$.
 
@@
 For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y Q(x) \geq \frac 1 2$.
+As a consequence, $y p(x) \geq 2^{\frac{n(n-1)h(2t)t}2 - 2}$.
 \end{lemma}
@@
 %\leq -1 + t-1 + \frac{t-1}{2t} - (t - \frac 1 2)
-
 \end{enumerate}
+To summarize, we have shown that for all $(x,y)$ in $S$, $y Q(x) \geq \frac 1 2$.
+Therefore,
+\[ y p(x) = y Q(x) \cdot \prod_{i=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}\gamma) \geq \frac 1 2 ((1-\frac{1}{4t+1}) \cdot 2^{\frac{n(n-1)h(2t)}2})^t \geq 2^{\frac{n(n-1)h(2t)t}2 - 2}.
+\]
 \end{proof}
@@
 \item If $x$ is in $[-1, 1]$, then $|S_n^k(x)|$ is in $[-1, 1]$. \label{item:sign-mid}
-\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $\abs{B_n^k(x)} \geq 2^{\frac{n(n-1)h(k)}2 - 1}$. \label{item:sign-denom}
+\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $B_n^k(x) \geq (1-\frac{1}{2k+1}) \cdot 2^{\frac{n(n-1)h(k)}2}$. \label{item:sign-denom}
 \end{enumerate}
@@
 
-\item If $x$ is in $[1,2^n]$, then $\abs{B_n^k(x)} = \abs{P_n(-x)^{h(k)}} (1 - r) \geq \abs{P_n(-x)^{h(k)}} \cdot \frac{2k}{2k+1} \geq 2^{\frac{n(n-1)h(k)}{2}} \cdot \frac{2k}{2k+1}$.
-If $x$ is in $[0,1]$, as both $P_n(-x)$ and $-P_n(x)$ are $\leq 0$, we have $\abs{B_n^k(x)} \geq \abs{P_n(-x)^{h(k)}} \geq 2^{\frac{n(n-1)h(k)}{2}}$. Therefore, for all $x \in [0,2^n]$, 
-$\abs{B_n^k(x)} \geq \frac 1 2 2^{\frac{n(n-1)h(k)}2}$. The item is concluded by noticing that $B_n^k(x)$ is an even function.
+\item Noticing that $B_n^k(x)$ is an even function, without loss of generality, suppose $x \geq 0$.
+First, note that if $x \geq 0$, then $\abs{P_n(-x)} \geq \prod_{i=1}^n 2^{2i} = 2^{n(n-1)}$.
+If $x$ is in $[1,2^n]$, then $B_n^k(x) = \abs{P_n(-x)^{h(k)}} (1 - r) \geq \abs{P_n(-x)^{h(k)}} \cdot \frac{2k}{2k+1} \geq 2^{n(n-1)h(k)} \cdot \frac{2k}{2k+1}$.
+If $x$ is in $[0,1]$, as both $P_n(-x)$ and $-P_n(x)$ are $\leq 0$, we have $B_n^k(x) \geq \abs{P_n(-x)^{h(k)}} \geq 2^{n(n-1)h(k)}$. Therefore, for all $x \in [0,2^n]$,
+$\abs{B_n^k(x)} \geq (1-\frac{1}{2k+1}) 2^{n(n-1)h(k)$.
+\end{enumerate}
+\end{proof}
 
-\end{enumerate}
+\paragraph{Norm bound.} We bound the norm of $p$ using the theorem below.
+\begin{theorem}
+$p(x)$ can be written as $\inner{c, \phi_1(x)}$ for some $c$ such that $\|c\| \leq$.
+\end{theorem}
+\begin{proof}
+Let $n = \ceil{\log \frac 1 \gamma}$.
+
+First, for all $i$ in $[t]$ and $l$ in $\cbr{0,1,\ldots,n}$,
+\[ \| (\frac{v_i \cdot x}{\gamma} - 2^l) \|^2 \leq \frac{1}{\gamma^2} + 2^{2l} \leq 2 \cdot 2^{2n}. \]
+This implies that
+\[ \| P_n(\frac{v_i \cdot x}{\gamma}) \|^2 \leq ((4n+2) \cdot 2^{2n})^{2n+1}. \]
+Therefore,
+\[ \| P_n(\frac{v_i \cdot x}{\gamma})^{h(k)} \|^2 \leq h(k)^{(2n+1)h(k)} \cdot ((4n+2) \cdot 2^{2n})^{(2n+1)h(k)}. \]
+%$A_n^k(x) = P_n(x)^{h(k)} - P_n(-x)^{h(k)}$, $B_n^k(x) = -P_n(-x)^{h(k)} - P_n(x)^{h(k)}$
+By the definition of $A_n^k$ and $B_n^k$, we have
+\[ \| A_n^k(\frac{v_i \cdot x}{\gamma}) \|^2,  \| B_n^k(\frac{v_i \cdot x}{\gamma}) \|^2 \leq ((8n+4) h(k) \cdot 2^{2n})^{(2n+1)h(k)}. \]
+
+%\sum_{i=1}^t A_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) \cdot \prod_{j \neq i} B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) - (t-\frac12) \prod_{j=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma})
+Hence, for every $i$ in $[t]$,
+\[
+\| A_n^{2t}(\frac{v_i \cdot x}{\gamma}) \cdot \prod_{j \neq i} B_n^{2t}(\frac{v_j \cdot x}{\gamma}) \|^2
+\leq
+t^{(2n+1) h(k) t} \cdot ((8n+4) h(k) \cdot 2^{2n})^{(2n+1)h(k)t}.
+\]
+Similarly,
+\[
+\| \prod_{i=1}^t B_n^{2t}(\frac{v_i \cdot x}{\gamma}) \|^2 \leq t^{(2n+1) h(k) t} \cdot ((8n+4) h(k) \cdot 2^{2n})^{(2n+1)h(k)t}.
+\]
+Therefore,
+\[
+\| p(x) \|^2 \leq ((t - \frac 1 2)^2 + t) \cdot ((8n+4) h(k) t \cdot 2^{2n})^{(2n+1)h(k)t} \leq ((16n+8) h(k) t \cdot 2^{2n})^{(2n+1)h(k)t}.
+\]
+where the last inequality uses that $2^{(2n+1)h(k)t} \geq t^2 + \frac 1 4$.
 

### 2018-10-12 ptf_margin.tex
margin lower bounds (proof not written yet)

@@
 \begin{definition}
-$S$ is said to be separable by an intersection of halfspaces with margin parameter $\gamma > 0$, if there exists $t$ linear classifiers $v_1, \ldots, v_t$ (all of which are in $\cbr{v \in \fR^d: \| v \| \leq 1}$),
+Dataset $S$ is said to be separable by an intersection of halfspaces with margin parameter $\gamma > 0$, if there exists $t$ linear classifiers $v_1, \ldots, v_t$ (all of which are in $\cbr{v \in \fR^d: \| v \| \leq 1}$),
 such that for every $(x,y)$ in $S$:
@@
 Given a set $S$ separable by an intersection of halfspaces with a margin $\gamma$, our goal is to find a feature map $\phi: \fR^d \to \fR^{d'}$, such that the dataset $S' = \cbr{(\phi(x), y): (x,y) \in S}$ is linearly separable by a margin $\gamma' > 0$.
-That is, for every $(\phi(x), y)$ in $S'$, and
-there exists a vector $u$ in $\fR^{d'}$, such that for every $(\phi(x), y)$ in $S'$, $\frac{y u \cdot \phi(x)}{\|u\|\| \phi(x)\|} \geq \gamma'$.
+\begin{definition}
+Dataset $T$ is said to be separable by halfspace with margin parameter $\rho > 0$, if there exists a linear classifier $u$, such that,
+\[ \min_{(x,y) \in T} y u \cdot x \geq \rho \|u\| \max_{(x,y) \in T} \| x \|. \]
+\end{definition}
+
+That is,
+there exists a vector $u$ in $\fR^{d'}$, such that $\min_{(x,y) \in S} y u \cdot \phi(x) \geq \gamma' \|u\| \max_{(x,y) \in S} \| \phi(x) \|$.
 In addition, we would like our feature map $\phi$ to correspond to a kernel function $k(x,x') = \inner{\phi(x), \phi(x')}$ that can be efficiently evaluated.
@@
 \section{Construction of polynomials}
-Our $\phi$'s in considerations are as follows: TODO: fix the constant in phi so that it has norm at most 1.
+Our $\phi$'s in considerations are as follows:
 \begin{enumerate}
-\item $\phi_1(x) = (x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0} = (x_S)_{S \in N^d, \|S\|_1 \leq \deg}$.
-This corresponds to the complete symmetric kernel $K_{\deg}$.
-\item $\phi_2(x) = ( \sqrt{ {\deg \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$.
+%\sqrt{\frac{1}{\deg+1}}
+\item $\phi_{s}(x) = ( x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq s, i_1, \ldots, i_d \geq 0} = (x_S)_{S \in N^d, \|S\|_1 \leq s}$.
+This corresponds to the complete symmetric kernel $K_s$.
+Note that for all $x$ such that $\| x \|_2 \leq 1$,
+$\inner{\phi_{s}(x), \phi_{s}(x)} \leq \sum_{i=0}^s \|x\|^{2i} \leq 1 + s$.
+
+%\frac{1}{2^{\deg}}
+\item $\phi_{s}'(x) = ( \sqrt{ {s \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq s, i_1, \ldots, i_d \geq 0}$.
 This corresponds to the polynomial kernel
-$K_{\deg}'(x,x') = (1 + \inner{x, x'})^{\deg}$.
-\item $\phi_3(x) = ( \sqrt{ (\frac 1 2)^{i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$.
+$K_s'(x,x') = (1 + \inner{x, x'})^s$. Note that for all $x$ such that $\| x \|_2 \leq 1$,
+$\inner{\phi_s'(x), \phi_s'(x)} = K_s'(x,x) = (1 + \|x\|^2)^s \leq 2^s$.
+
+\item $\phi_0(x) = ( \sqrt{ (\frac 1 2)^{i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1, \ldots, i_d \geq 0}$.
 This corresponds to the kernel $K(x,x') = \frac{1}{1 - \frac 1 2 \inner{x,x'}}$.
+Note that for all $x$ such that $\| x \|_2 \leq 1$,
+$\inner{\phi_0(x), \phi_0(x)} = K(x,x) \leq 2$.
 \end{enumerate}
@@
 For a polynomial $p = \sum_{S \in \fN^d} c_S x_S$, define $\|p\|$, the norm of $p$, as the $\ell_2$ norm of the vector that contains its coefficients on every monomial, that is $\|p\| = \| (c_S)_{S \in \fN^d} \| = \sqrt{\sum_{S \in \fN^d} c_S^2}$.
-This is also the RKHS norm of $p$ wrt the complete symmetric kernel $K_{\deg}$, for $\deg \geq \deg(p)$.
+We have the following simple result.
+\begin{lemma}
+Suppose polynomial $p$ has degree $\deg$, and has norm $\|p\|$. Then
+\begin{enumerate}
+\item For any degree $s \geq \deg$, $p$ can be written as $\inner{c, \phi_s(x)}$, where $\|c\| = \|p\|$.
+\item For any degree $s \geq \deg$, $p$ can be written as $\inner{c', \phi_s'(x)}$, where $\|c_0\| \leq \|p\|$.
+\item $p$ can be written as $\inner{c_0, \phi_0(x)}$, where $\|c_0\| \leq 2^{\frac{\deg}{2}} \|p\|$.
+\end{enumerate}
+\end{lemma}
+\begin{proof}
+Note that $p(x)$ can be written as $\sum_{i_1,\ldots,i_d \in \fN} c_{i_1,\ldots,i_d} x_1^{i_1} \ldots x_d^{i_d}$. As $p$ has degree $\deg$, $c_{i_1,\ldots,i_d} = 0$ for $i_1 + \ldots + i_d > \deg$.
+
+The first item follows as $\phi_s(x)$ contains all monomials in $p$.
+
+For the second item, we define $(c')_{i_1,\ldots,i_d} = \frac{c_{i_1,\ldots,i_d}}{\sqrt{ {s \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}}$ for all $(i_1,\ldots,i_d) \in \fN, i_1+\ldots+i_d \leq s$.
+It can be seen that $\inner{c', \phi_s'(x)} = \inner{c, \phi_s(x)}$, and
+$\| c' \| \leq \| c \| = \| p \|$.
+
+For the third item, we define $(c_0)_{i_1,\ldots,i_d} = \frac{c_{i_1,\ldots,i_d}}{\sqrt{ (\frac 1 2)^{i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}}$ for all $(i_1,\ldots,i_d) \in \fN$.
+As $c_{i_1,\ldots,i_d} = 0$ for $i_1 + \ldots + i_d > \deg$, $|(c_0)_{i_1,\ldots,i_d}| \leq 2^{\frac{\deg}{2}} |c_{i_1,\ldots,i_d}|$.
+This implies that
+$\| c_0 \| \leq 2^{\frac{\deg}{2}} \| c \| = 2^{\frac{\deg}{2}} \| p \| $.
+\end{proof}
+
+%This is also the RKHS norm of $p$ wrt the complete symmetric kernel $K_{\deg}$, for $\deg \geq \deg(p)$.
 
@@
 For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y Q(x) \geq \frac 1 2$.
-As a consequence, $y p(x) \geq 2^{\frac{n(n-1)h(2t)t}2 - 2}$.
+As a consequence, $y p(x) \geq 2^{n(n-1)h(2t)t - 2}$.
 \end{lemma}
@@
 Therefore,
-\[ y p(x) = y Q(x) \cdot \prod_{i=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}\gamma) \geq \frac 1 2 ((1-\frac{1}{4t+1}) \cdot 2^{\frac{n(n-1)h(2t)}2})^t \geq 2^{\frac{n(n-1)h(2t)t}2 - 2}.
-\]
+\[ y p(x) = y Q(x) \cdot \prod_{i=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}\gamma) \geq \frac 1 2 ((1-\frac{1}{4t+1}) \cdot 2^{n(n-1)h(2t)})^t \geq 2^{n(n-1)h(2t)t - 2}. \]
 \end{proof}
@@
 \item If $x$ is in $[-1, 1]$, then $|S_n^k(x)|$ is in $[-1, 1]$. \label{item:sign-mid}
-\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $B_n^k(x) \geq (1-\frac{1}{2k+1}) \cdot 2^{\frac{n(n-1)h(k)}2}$. \label{item:sign-denom}
+\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $B_n^k(x) \geq (1-\frac{1}{2k+1}) \cdot 2^{n(n-1)h(k)}$. \label{item:sign-denom}
 \end{enumerate}
@@
 If $x$ is in $[0,1]$, as both $P_n(-x)$ and $-P_n(x)$ are $\leq 0$, we have $B_n^k(x) \geq \abs{P_n(-x)^{h(k)}} \geq 2^{n(n-1)h(k)}$. Therefore, for all $x \in [0,2^n]$,
-$\abs{B_n^k(x)} \geq (1-\frac{1}{2k+1}) 2^{n(n-1)h(k)$.
+$\abs{B_n^k(x)} \geq (1-\frac{1}{2k+1}) 2^{n(n-1)h(k)}$.
 \end{enumerate}
@@
 
-\paragraph{Norm bound.} We bound the norm of $p$ using the theorem below.
+\paragraph{Norm bound.} We bound the norm of $p$ in the theorem below.
 \begin{theorem}
-$p(x)$ can be written as $\inner{c, \phi_1(x)}$ for some $c$ such that $\|c\| \leq$.
+$p(x)$ has degree $\deg = (2\ceil{\log \frac 1 \gamma}+1)h(2t)t$, and has norm $\|p\| \leq ((16\ceil{\log \frac 1 \gamma}+8) h(2t) t \cdot \frac 1 \gamma)^{(2\ceil{\log \frac 1 \gamma}+1)h(2t)t}$.
 \end{theorem}
 \begin{proof}
+The degree of $p$ follows from the
 Let $n = \ceil{\log \frac 1 \gamma}$.
@@
 Therefore,
-\[ \| P_n(\frac{v_i \cdot x}{\gamma})^{h(k)} \|^2 \leq h(k)^{(2n+1)h(k)} \cdot ((4n+2) \cdot 2^{2n})^{(2n+1)h(k)}. \]
+\[ \| P_n(\frac{v_i \cdot x}{\gamma})^{h(2t)} \|^2 \leq h(2t)^{(2n+1)h(2t)} \cdot ((4n+2) \cdot 2^{2n})^{(2n+1)h(2t)}. \]
 %$A_n^k(x) = P_n(x)^{h(k)} - P_n(-x)^{h(k)}$, $B_n^k(x) = -P_n(-x)^{h(k)} - P_n(x)^{h(k)}$
 By the definition of $A_n^k$ and $B_n^k$, we have
-\[ \| A_n^k(\frac{v_i \cdot x}{\gamma}) \|^2,  \| B_n^k(\frac{v_i \cdot x}{\gamma}) \|^2 \leq ((8n+4) h(k) \cdot 2^{2n})^{(2n+1)h(k)}. \]
+\[ \| A_n^{2t}(\frac{v_i \cdot x}{\gamma}) \|^2,  \| B_n^{2t}(\frac{v_i \cdot x}{\gamma}) \|^2 \leq ((8n+4) h(2t) \cdot 2^{2n})^{(2n+1)h(2t)}. \]
 
@@
 \leq
-t^{(2n+1) h(k) t} \cdot ((8n+4) h(k) \cdot 2^{2n})^{(2n+1)h(k)t}.
+t^{(2n+1) h(2t) t} \cdot ((8n+4) h(2t) \cdot 2^{2n})^{(2n+1)h(2t)t}.
 \]
@@
 \[
-\| \prod_{i=1}^t B_n^{2t}(\frac{v_i \cdot x}{\gamma}) \|^2 \leq t^{(2n+1) h(k) t} \cdot ((8n+4) h(k) \cdot 2^{2n})^{(2n+1)h(k)t}.
+\| \prod_{i=1}^t B_n^{2t}(\frac{v_i \cdot x}{\gamma}) \|^2 \leq t^{(2n+1) h(2t) t} \cdot ((8n+4) h(2t) \cdot 2^{2n})^{(2n+1)h(2t)t}.
 \]
@@
 \[
-\| p(x) \|^2 \leq ((t - \frac 1 2)^2 + t) \cdot ((8n+4) h(k) t \cdot 2^{2n})^{(2n+1)h(k)t} \leq ((16n+8) h(k) t \cdot 2^{2n})^{(2n+1)h(k)t}.
+\| p(x) \|^2 \leq ((t - \frac 1 2)^2 + t) \cdot ((8n+4) h(2t) t \cdot 2^{2n})^{(2n+1)h(2t)t} \leq ((16n+8) h(2t) t \cdot 2^{2n})^{(2n+1)h(2t)t}.
 \]
-where the last inequality uses that $2^{(2n+1)h(k)t} \geq t^2 + \frac 1 4$.
-
+where the second inequality uses that $2^{(2n+1)h(2t)t} \geq t^2 + \frac 1 4$.
+This implies that $p(x)$ can be written as $\inner{c, \phi_1(x)}$, where $\| c \|_2^2 \leq ((16n+8) h(2t) t \cdot 2^{2n})^{(2n+1)h(2t)t}$.
+Taking square roots on both sides, the theorem follows from algebra.
+%Hence, $\| c \|_2 \leq ((16n+8) h(2t) t \cdot 2^n)^{(2n+1)h(2t)t}$.
 \end{proof}
@@
 
-For the first item, given that $x \in [0,1]$, $-(-x-1) \geq 1-x \geq 0$. Therefore,
-\[ \frac{-P_n(-x)}{-P_n(x)} = \frac{-(-x-1)}{1-x} \prod_{i =1}^n \frac{(x+2^i)^2}{(x - 2^i)^2}  \geq 1. \]
+For the first item, given that $x \in [0,1]$, $1+x \geq 1-x \geq 0$. Therefore,
+\[ \frac{-P_n(-x)}{-P_n(x)} = \frac{1+x}{1-x} \prod_{i =1}^n \frac{(x+2^i)^2}{(x - 2^i)^2}  \geq 1. \]
 
-For the second item, given that $x \geq 1$, $-(-x-1) \geq x-1 \geq 0$. In addition, as $x$ is in $[1,2^n]$, there exists an $i_0 \in [n]$ such that $2^{i_0-1} \leq x \leq 2^i_0$. Therefore,
+For the second item, given that $x \geq 1$, $1+x \geq x-1 \geq 0$. In addition, as $x$ is in $[1,2^n]$, there exists an $i_0 \in [n]$ such that $2^{i_0-1} \leq x \leq 2^i_0$. Therefore,
 $(x+2^i)^2 \geq 4(x - 2^i)^2$. Hence,
-\[ \frac{-P_n(-x)}{P_n(x)} = \frac{-(-x-1)}{ x-1} \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \geq 4. \]
+\[ \frac{-P_n(-x)}{P_n(x)} = \frac{1+x}{ x-1} \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \geq 4. \]
 
@@
 \paragraph{The construction.} Define
-\[ p(x) = t + \frac 1 2 - \sum_{i=1}^t (T_{\ceil{\sqrt{\frac 2 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}, \]
+\[ p(x) = t + \frac 1 2 - \sum_{i=1}^t (T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}, \]
 where
-$T_r(\cdot)$ is the $r$-th order Chebyshev polynomial. Denote by $C_i(x) = (T_{\ceil{\sqrt{\frac 2 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}$. $p$ can therefore be simplified to
+$T_r(\cdot)$ is the $r$-th order Chebyshev polynomial. Denote by $C_i(x) = (T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}$. $p$ can therefore be simplified to
 \[ p(x) = t + \frac 1 2 - \sum_{i=1}^t C_i(x). \]
@@
 \item Suppose $y = -1$.
-First observe that for all $i$, $T_{\ceil{\sqrt{\frac 2 \gamma}}}(1 - v_i \cdot x)) \geq -1$.
+First observe that for all $i$, $T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x)) \geq -1$.
 This is because of items~\ref{item:bound-in} and~\ref{item:bound-out} of Fact~\ref{fact:cheb}.
@@
 
-\paragraph{Norm bound.} We now bound $\| p \|$. First, for all $i$, as $v_i$ has norm at most 1,
+\paragraph{Norm bound.} We bound the norm of $p$ in the theorem below.
+\begin{theorem}
+$p(x)$ has degree $\deg = \ceil{\sqrt{\frac1\gamma}} \cdot \ceil{\log(2t)}$, and has norm $\|p\| \leq 2 \cdot (256 \ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t})^{\ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t}}$.
+\end{theorem}
+\begin{proof}
+Denote by $r = \ceil{\sqrt{\frac1\gamma}}$.
+First, for all $i$, as $v_i$ has norm at most 1,
 \[ \| (1 - v_i \cdot x) \|^2 \leq 2. \]
@@
 Hence,
-\[ \| T_r(1 - v_i \cdot x) \|^2 = \| \sum_{l=0}^r c_l (1 - v_i \cdot x)^l \|^2 \leq (r+1) \cdot \sum_{l=0}^r 2^{2r} l^l 2^l \leq (r+1)^2 (8r)^r. \]
+\[ \| T_r(1 - v_i \cdot x) \|^2 = \| \sum_{l=0}^r c_l (1 - v_i \cdot x)^l \|^2 \leq (r+1) \cdot \sum_{l=0}^r 2^{2r} l^l 2^l \leq (r+1)^2 (8r)^r \leq (32r)^r. \]
+where the last inequality uses the fact that $(r+1)^2 \leq 2^r$.
 And by Lemma~\ref{lem:norm-oper},
-\[ \| C_r(x) \|^2 \leq (\ceil{\log 2t})^{\ceil{\log 2t} r} \cdot ((r+1)^2 (8r)^r)^{\ceil{\log 2t}}. \]
+\[ \| C_r(x) \|^2 \leq (\ceil{\log 2t})^{\ceil{\log 2t} r} \cdot ((32r)^r)^{\ceil{\log 2t}}. \]
 Therefore,
-\[ \| p(x) \|^2 \leq (t+1) \cdot ((t+\frac 1 2)^2 + t (\ceil{\log 2t})^{\ceil{\log 2t} r} \cdot ((r+1)^2 (8r)^r)^{\ceil{\log 2t}}) \leq 2 \cdot (32 r \ceil{\log 2t})^{2r \ceil{\log 2t}}  \]
-where the last inequality uses the fact that $2^{2r \ceil{\log 2t}} \geq \max(2t^2, r^2)$.
+\[ \| p(x) \|^2 \leq (t+1) \cdot ((t+\frac 1 2)^2 + t (32 r\ceil{\log 2t})^{\ceil{\log 2t} r}) \leq 2 \cdot (256 r \ceil{\log 2t})^{r \ceil{\log 2t}}  \]
+where the last inequality uses the fact that $(t+1)((t+\frac12)^2+t) \leq 2 \cdot 8^{\ceil{\log 2t}}$ and algebra.
+%$2^{2r \ceil{\log 2t}} \geq \max(2t^2, r^2)$.
+\end{proof}
+
+\section{Margin lower bounds on respective feature maps}
+\paragraph{Margin bounds using non-adaptive feature maps.}
+\begin{theorem}
+Suppose we are given an integer $s$, and a set of examples $S$ separable by an intersection of halfspaces by margin $\gamma$. Define the mapped dataset $S'=\cbr{(\phi_s(x),y): (x,y) \in S}$. Then,
+\begin{enumerate}
+\item If $s \geq (2\ceil{\log \frac 1 \gamma}+1) h(2t) t$, then $S'$ is separable by a halfspace with margin
+\[
+\gamma' = \frac{1}{ ( (16 \ceil{\log \frac 1 \gamma} + 8 ) h(2t) t 2^{\ceil{\log \frac 1 \gamma}})^{(2\ceil{\log \frac 1 \gamma} + 1 ) h(2t) t} }.
+\]
+\item If $s \geq \ceil{\sqrt{\frac1\gamma}} \cdot \ceil{\log(2t)}$, then $S'$ is separable by a halfspace with margin
+\[
+\gamma' = \frac{1}{4 \cdot (256 \ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t})^{\ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t}}}.
+\]
+\end{enumerate}
+\end{theorem}
+
+\paragraph{Margin bounds using adaptive-degree feature map.}
+\begin{theorem}
+Suppose we are given a set of examples $S$ separable by an intersection of halfspaces by margin $\gamma$.
+Define the mapped dataset $S'=\cbr{(\phi_0(x),y): (x,y) \in S}$.
+Then, $S'$ is separable by some halfspace with margin
+\[
+\gamma' =
+\max(
+\frac{1}{ \sqrt{2} ( (32 \ceil{\log \frac 1 \gamma} + 16 ) h(2t) t 2^{\ceil{\log \frac 1 \gamma}})^{(2\ceil{\log \frac 1 \gamma} + 1 ) h(2t) t} },
+\frac{1}{4 \sqrt{2} \cdot (512 \ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t})^{\ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t}}}
+)
+\]
+\end{theorem}
+
+%\ceil{\log \frac 1 \gamma} + 1 ) h(2t) t
+%2^\ceil{\log \frac 1 \gamma} )^{ (2  }
+
+%and has norm $\|p\| \leq ((16\ceil{\log \frac 1 \gamma}+8) h(2t) t \cdot \frac 1 \gamma)^{(2\ceil{\log \frac 1 \gamma}+1)h(2t)t}$.
+
 \section{Auxiliary lemmas}

### 2018-10-12 ptf_margin.tex
some remarks

@@
 \end{definition}
+\cz{Looking at~\cite{klivans2004learning} and its proof, it assumes that for all $(x,y)$ in $S$, $|v_i \cdot x| \geq \gamma$.
+In our subsequent proofs, we show that it can be in fact weakened to the condition above, which is also more suitable for online bandit multiclass linear classification.}
 
@@
 \item If $x$ is in $[-1, 1]$, then $|S_n^k(x)|$ is in $[-1, 1]$. \label{item:sign-mid}
-\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $B_n^k(x) \geq (1-\frac{1}{2k+1}) \cdot 2^{n(n-1)h(k)}$. \label{item:sign-denom}
+\cz{This fact is based on discussions with Chen-Yu, which we found important but was omitted by~\cite{klivans2004learning}.}
+\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $B_n^k(x) \geq (1-\frac{1}{2k+1}) \cdot 2^{n(n-1)h(k)}$.
+\cz{This is a refined lower bound of Lemma 6 of~\cite{klivans2004learning}; we got rid of the weird
+requirement that ``the fractional part of $x$ is at least $2^{-n}$''.}
+\label{item:sign-denom}
 \end{enumerate}
@@
 $(x+2^i)^2 \geq 4(x - 2^i)^2$. Hence,
-\[ \frac{-P_n(-x)}{P_n(x)} = \frac{1+x}{ x-1} \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \geq 4. \]
-
+\[ \frac{-P_n(-x)}{P_n(x)} = \frac{1+x}{ x-1} \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \geq 4. \]
 \end{proof}

### 2018-10-16 ptf_margin.tex
a pass over ptf_margin

@@
 
-\section{Construction of polynomials}
+\section{Construction of large margin feature mappings using polynomials}
 Our $\phi$'s in considerations are as follows:
@@
 %\sqrt{\frac{1}{\deg+1}}
-\item $\phi_{s}(x) = ( x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq s, i_1, \ldots, i_d \geq 0} = (x_S)_{S \in N^d, \|S\|_1 \leq s}$.
+\item $\phi_{s}(x) = ( x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq s, i_1, \ldots, i_d \geq 0} = (x_S)_{S \in \fN^d, \|S\|_1 \leq s}$.
 This corresponds to the complete symmetric kernel $K_s$.
@@
 \item For any degree $s \geq \deg$, $p$ can be written as $\inner{c, \phi_s(x)}$, where $\|c\| = \|p\|$.
-\item For any degree $s \geq \deg$, $p$ can be written as $\inner{c', \phi_s'(x)}$, where $\|c_0\| \leq \|p\|$.
+\item For any degree $s \geq \deg$, $p$ can be written as $\inner{c', \phi_s'(x)}$, where $\|c'\| \leq \|p\|$.
 \item $p$ can be written as $\inner{c_0, \phi_0(x)}$, where $\|c_0\| \leq 2^{\frac{\deg}{2}} \|p\|$.
@@
 \end{lemma}
+\label{lem:fm-convert}
 \begin{proof}
@@
 
-The first item follows as $\phi_s(x)$ contains all monomials in $p$.
+The first item follows as $\phi_s(x)$ contains all monomials of degree at most $s$, which in turn contains all monomials in $p$.
 
-For the second item, we define $(c')_{i_1,\ldots,i_d} = \frac{c_{i_1,\ldots,i_d}}{\sqrt{ {s \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}}$ for all $(i_1,\ldots,i_d) \in \fN, i_1+\ldots+i_d \leq s$.
+For the second item, we define $(c')_{i_1,\ldots,i_d} = \frac{c_{i_1,\ldots,i_d}}{\sqrt{ {s \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}}$ for all $(i_1,\ldots,i_d) \in \fN$.
 It can be seen that $\inner{c', \phi_s'(x)} = \inner{c, \phi_s(x)}$, and
@@
 
-\subsection{Construction using rational functions}
+\subsection{Large margin polynomial via rational functions}
 \paragraph{The construction.} Define rational function
@@
 \]
-where function
+where for $k,n$ in $\fN$, function
 \[
@@
 Now denote by $A_n^k(x) = P_n(x)^{h(k)} - P_n(-x)^{h(k)}$, $B_n^k(x) = -P_n(-x)^{h(k)} - P_n(x)^{h(k)}$.
+Also, define $D_i(x) = S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma})$.
+
 \cz{Note the difference between this line and KS04 - we multiply by $B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}\gamma)$ as opposed to its square.
@@
 
-\begin{lemma}[~\cite{klivans2004learning}]
+\begin{lemma}[\cite{klivans2004learning}]
 For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y Q(x) \geq \frac 1 2$.
-As a consequence, $y p(x) \geq 2^{n(n-1)h(2t)t - 2}$.
+As a consequence, $y p(x) \geq 2^{\ceil{\log \frac 1 \gamma}(\ceil{\log \frac 1 \gamma}-1)h(2t)t - 2}$.
+\label{lem:rational-margin}
 \end{lemma}
@@
 In addition, by Definition~\ref{def:int-margin}, there exists an $i_0$ in $[t]$, such that $v_{i_0} \cdot x \leq -\gamma$.
-By item~\ref{item:bound-out} of Fact~\ref{fact:cheb}, we have that
+By item~\ref{item:sign-lt} of Fact~\ref{fact:newman}, we have that
 $D_{i_0}(x) \in [-1 - \frac 1 {2t}, -1]$.
@@
 To summarize, we have shown that for all $(x,y)$ in $S$, $y Q(x) \geq \frac 1 2$.
-Therefore,
+Therefore, by item~\ref{item:sign-denom} of Fact~\ref{fact:newman}, 
 \[ y p(x) = y Q(x) \cdot \prod_{i=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}\gamma) \geq \frac 1 2 ((1-\frac{1}{4t+1}) \cdot 2^{n(n-1)h(2t)})^t \geq 2^{n(n-1)h(2t)t - 2}. \]
@@
 \begin{fact}
-$S_n^k(\cdot)$ has the following properties:
+For $k, n$ in $\fN$, $S_n^k(\cdot)$ has the following properties:
 \begin{enumerate}
@@
 \cz{This fact is based on discussions with Chen-Yu, which we found important but was omitted by~\cite{klivans2004learning}.}
-\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $B_n^k(x) \geq (1-\frac{1}{2k+1}) \cdot 2^{n(n-1)h(k)}$.
+\item For all $x$ in $[-2^{n}, 2^{n}]$, $B_n^k(x) \geq (1-\frac{1}{2k+1}) \cdot 2^{n(n-1)h(k)}$.
 \cz{This is a refined lower bound of Lemma 6 of~\cite{klivans2004learning}; we got rid of the weird
@@
 First, note that if $x \geq 0$, then $\abs{P_n(-x)} \geq \prod_{i=1}^n 2^{2i} = 2^{n(n-1)}$.
-If $x$ is in $[1,2^n]$, then $B_n^k(x) = \abs{P_n(-x)^{h(k)}} (1 - r) \geq \abs{P_n(-x)^{h(k)}} \cdot \frac{2k}{2k+1} \geq 2^{n(n-1)h(k)} \cdot \frac{2k}{2k+1}$.
-If $x$ is in $[0,1]$, as both $P_n(-x)$ and $-P_n(x)$ are $\leq 0$, we have $B_n^k(x) \geq \abs{P_n(-x)^{h(k)}} \geq 2^{n(n-1)h(k)}$. Therefore, for all $x \in [0,2^n]$,
-$\abs{B_n^k(x)} \geq (1-\frac{1}{2k+1}) 2^{n(n-1)h(k)}$.
+If $x$ is in $[1,2^n]$, then $B_n^k(x) = (-P_n(-x))^{h(k)} (1 - r) \geq (-P_n(-x))^{h(k)} \cdot \frac{2k}{2k+1} \geq 2^{n(n-1)h(k)} \cdot \frac{2k}{2k+1}$.
+If $x$ is in $[0,1]$, as both $P_n(-x)$ and $-P_n(x)$ are $\leq 0$, we have $B_n^k(x) \geq (-P_n(-x))^{h(k)} \geq 2^{n(n-1)h(k)}$. Therefore, for all $x \in [0,2^n]$,
+$B_n^k(x) \geq (1-\frac{1}{2k+1}) 2^{n(n-1)h(k)}$.
 \end{enumerate}
+\end{proof}
+
+\begin{fact}
+The following are true:
+\begin{enumerate}
+\item If $x \in [0,1]$, then $0 \leq -P_n(x) \leq -P_n(-x)$. \label{item:x-small}
+\item If $x \in [1, 2^n]$, then $0 \leq 4P_n(x) \leq -P_n(-x)$. \label{item:x-large}
+\end{enumerate}
+\label{fact:pn}
+\end{fact}
+\begin{proof}
+First, observe that for any $x \geq 0$, for all $i$, $(x+2^i)^2 \geq (x - 2^i)^2$ holds.
+
+For the first item, given that $x \in [0,1]$, $1+x \geq 1-x \geq 0$. Therefore,
+\[ \frac{-P_n(-x)}{-P_n(x)} = \frac{1+x}{1-x} \cdot \prod_{i =1}^n \frac{(x+2^i)^2}{(x - 2^i)^2}  \geq 1. \]
+
+For the second item, given that $x \geq 1$, $1+x \geq x-1 \geq 0$. In addition, as $x$ is in $[1,2^n]$, there exists an $i_0 \in [n]$ such that $2^{i_0-1} \leq x \leq 2^i_0$. Therefore,
+$(x+2^i)^2 \geq 4(x - 2^i)^2$. Hence,
+\[ \frac{-P_n(-x)}{P_n(x)} = \frac{1+x}{ x-1} \cdot \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \cdot \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \geq 4. \]
 \end{proof}
@@
 $p(x)$ has degree $\deg = (2\ceil{\log \frac 1 \gamma}+1)h(2t)t$, and has norm $\|p\| \leq ((16\ceil{\log \frac 1 \gamma}+8) h(2t) t \cdot \frac 1 \gamma)^{(2\ceil{\log \frac 1 \gamma}+1)h(2t)t}$.
+\label{thm:rational-norm}
 \end{theorem}
@@
 
-\begin{fact}
-The following is true:
-\begin{enumerate}
-\item If $x \in [0,1]$, then $0 \leq -P_n(x) \leq -P_n(-x)$. \label{item:x-small}
-\item If $x \in [1, 2^n]$, then $0 \leq 4P_n(x) \leq -P_n(-x)$. \label{item:x-large}
-\end{enumerate}
-\label{fact:pn}
-\end{fact}
-\begin{proof}
-First, observe that for any $x \geq 0$, for all $i$, $(x+2^i)^2 \geq (x - 2^i)^2$ holds.
-
-For the first item, given that $x \in [0,1]$, $1+x \geq 1-x \geq 0$. Therefore,
-\[ \frac{-P_n(-x)}{-P_n(x)} = \frac{1+x}{1-x} \prod_{i =1}^n \frac{(x+2^i)^2}{(x - 2^i)^2}  \geq 1. \]
-
-For the second item, given that $x \geq 1$, $1+x \geq x-1 \geq 0$. In addition, as $x$ is in $[1,2^n]$, there exists an $i_0 \in [n]$ such that $2^{i_0-1} \leq x \leq 2^i_0$. Therefore,
-$(x+2^i)^2 \geq 4(x - 2^i)^2$. Hence,
-\[ \frac{-P_n(-x)}{P_n(x)} = \frac{1+x}{ x-1} \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \geq 4. \]
-\end{proof}
-
-\subsection{Construction using Chebyshev polynomials}
+\subsection{Large margin polynomials via Chebyshev polynomials}
 \paragraph{The construction.} Define
@@
 
-\begin{lemma}[~\cite{klivans2004learning}]
+\begin{lemma}[\cite{klivans2004learning}]
 For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y p(x) \geq \frac 1 2$.
+\label{lem:cheb-margin}
 \end{lemma}
@@
 \item Suppose $y = -1$.
-First observe that for all $i$, $T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x)) \geq -1$.
-This is because of items~\ref{item:bound-in} and~\ref{item:bound-out} of Fact~\ref{fact:cheb}.
+First observe that for all $i$, $T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x) \geq -1$.
+This is because of items~\ref{item:bound-in} and~\ref{item:bound-out} of Fact~\ref{fact:cheb}, and that $1 - v_i \cdot x \geq 0$.
 This implies that $C_i(x) \geq -1$.
@@
 $p(x)$ has degree $\deg = \ceil{\sqrt{\frac1\gamma}} \cdot \ceil{\log(2t)}$, and has norm $\|p\| \leq 2 \cdot (256 \ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t})^{\ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t}}$.
+\label{thm:cheb-norm}
 \end{theorem}
@@
 Therefore, by Lemma~\ref{lem:norm-oper},
-\[ \| c_l (1 - v_i \cdot x)^l \|^2 = c_l^2 \| (1 - v_i \cdot x)^l \|_2^2 \leq 2^{2r} l^l 2^l. \]
+\[ \| c_l (1 - v_i \cdot x)^l \|^2 = c_l^2 \| (1 - v_i \cdot x)^l \|^2 \leq 2^{2r} l^l 2^l. \]
 Hence,
@@
 
+\begin{proof}
+\begin{enumerate}
+\item From Lemma~\ref{lem:rational-margin} and Theorem~\ref{thm:rational-norm}, 
+along with the fact that $s \geq (2\ceil{\log \frac 1 \gamma}+1) h(2t) t$,
+we know that there exists some polynomial $p = \inner{c, \phi_s(x)}$, such that
+$y \inner{c, \phi_s(x)} \geq  2^{\ceil{\log \frac 1 \gamma}(\ceil{\log \frac 1 \gamma}-1)h(2t)t - 2}$ and 
+$\|c\| \leq ((16\ceil{\log \frac 1 \gamma}+8) h(2t) t \cdot \frac 1 \gamma)^{(2\ceil{\log \frac 1 \gamma}+1)h(2t)t}$. This implies that $S'$ is separable by a halfspace with the desired margin.
+
+\item From Lemma~\ref{lem:cheb-margin} and Theorem~\ref{thm:cheb-norm},
+along with the fact that $s \geq \ceil{\sqrt{\frac1\gamma}} \cdot \ceil{\log(2t)}$, we know that there exists some polynomial $p = \inner{c, \phi_s(x)}$, such that
+$y \inner{c, \phi_s(x)} \geq \frac 1 2$ and
+$\| c \| \leq 2 \cdot (256 \ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t})^{\ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t}}$. This implies that $S'$ is separable by a halfspace with the desired margin.
+\end{enumerate}
+\end{proof}
+
 \paragraph{Margin bounds using adaptive-degree feature map.}
@@
 \end{theorem}
+
+\begin{proof}
+%The proof the essentially the same as the proof of 
+\begin{enumerate}
+\item From Lemma~\ref{lem:rational-margin} and Theorem~\ref{thm:rational-norm}, 
+we know that there exists some polynomial $p(x)$ of degree at most $(2\ceil{\log \frac 1 \gamma}+1) h(2t) t$, such that
+$y p(x) \geq  2^{\ceil{\log \frac 1 \gamma}(\ceil{\log \frac 1 \gamma}-1)h(2t)t - 2}$ and 
+$\|p\| \leq ((16\ceil{\log \frac 1 \gamma}+8) h(2t) t \cdot \frac 1 \gamma)^{(2\ceil{\log \frac 1 \gamma}+1)h(2t)t}$. 
+By Lemma~\ref{lem:fm-convert}, there is some vector $c$, such that $y \inner{c, \phi_0(x)} = y p(x)$ for all $(x,y)$ in $S$	, and $\| c \| \leq 2^{\frac 1 2 \cdot (2\ceil{\log \frac 1 \gamma}+1) h(2t) t} \| p \|$.
+This implies that $S'$ is separable by a halfspace with the desired margin.
+
+\item From Lemma~\ref{lem:cheb-margin} and Theorem~\ref{thm:cheb-norm}, we know that there exists some polynomial $p(x)$ of degree $\ceil{\sqrt{\frac1\gamma}} \cdot \ceil{\log(2t)}$ such that
+$y p(x) \geq \frac 1 2$ and
+$\| p \| \leq 2 \cdot (256 \ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t})^{\ceil{\sqrt{\frac1\gamma}} \ceil{\log 2t}}$. 
+By Lemma~\ref{lem:fm-convert}, there is some vector $c$, such that $y \inner{c, \phi_0(x)} = y p(x)$ for all $(x,y)$ in $S,$ and $\| c \| \leq 2^{\frac 1 2 \cdot \ceil{\sqrt{\frac1\gamma}} \cdot \ceil{\log(2t)}} \| p \|$.
+This implies that $S'$ is separable by a halfspace with the desired margin.
+\end{enumerate}
+
+\end{proof}
 

### 2018-10-18 main.tex
ova algorithm

@@
 
-$M$ counts the number of different $(S_1,\ldots, S_\ell)$'s with $S_1\times \ldots \times S_\ell=S$. Since $S$ has degree at most $\deg$, we can bound $M$ by $ \ell^{\deg}$.
+$M$ counts the number of different $(S_1,\ldots, S_\ell)$'s with $S_1\times \ldots \times S_\ell=S$.
+Since $S$ has degree at most $\deg$, we can bound $M$ by $ \ell^{\deg}$.
+\footnote{This can be seen in two ways.
+First, we can think of ``assigning'' elements in $S$ to one of $(S_1,\ldots, S_\ell)$; every partition $S_1,\ldots,S_\ell$ can be achieved by some assignment - this can have at most $\ell^{\deg}$ ways.
+Second, consider $S = (s_1, \ldots, s_d)$.
+Consider decomposing each coordinate of $S$ - coordinate $i$ has ${s_i + \ell - 1 \choose \ell - 1}$ ways to partition to $\ell$ parts.
+Therefore the total number of possible partitions is $\prod_{i=1}^d {s_i + \ell - 1 \choose \ell - 1} \leq \prod_{i=1}^d \ell^{s_i} \leq \ell^{\deg}$.}
 
@@
 
-%For simplicity, now we focus on the model assumed in \cite{crammer2013multiclass}.
-Besides the model, we assume the following ``margin assumption'' that is suitable for this kind of stochastic model:
+%For simplicity, now we focus on the model assumed in \cite{crammer2013multiclass}. Besides the model, we assume the following ``margin assumption'' that is suitable for this kind of stochastic model:
 %\begin{align}

### 2018-10-18 ptf_margin.tex
ova algorithm

@@
 
+\DeclareMathOperator*{\sep}{sep}
 \DeclareMathOperator*{\arginf}{arginf}
@@
 
-\section{Learning intersection of halfspaces with a margin}
-Suppose we are given examples $S = \cbr{(x, y)}$, where $x$ is in $\cbr{x \in \fR^d: \| x \| \leq 1}$, and $y$ is in $\cbr{-1,+1}$.
+\section{Preliminaries}
 \begin{definition}
-Dataset $S$ is said to be separable by an intersection of halfspaces with margin parameter $\gamma > 0$, if there exists $t$ linear classifiers $v_1, \ldots, v_t$ (all of which are in $\cbr{v \in \fR^d: \| v \| \leq 1}$),
+$S \subset (\calX \times [K])^*$ is said to be {\em linearly separable} with margin parameter $\gamma > 0$, if there exists an multiclass linear classifier $W \in \fR^{K \times d}$ ($\| W \|_F \leq 1$),
+such that for every $(x,y)$ in $S$,
+$W_y \cdot x \geq W_{y'} \cdot x + \gamma \max_{(x,y) \in S} \| x \|_2$ holds simultaneously for all $y' \neq y$.
+\label{def:mc-margin}
+\end{definition}
+
+\begin{definition}
+$S \subset (\calX \times [K])^*$ is said to be {\em one-versus-all (OvA) linearly separable} with margin parameter $\gamma > 0$, if there exists an multiclass linear classifier $W \in \fR^{k \times d}$ ($\| W \|_F \leq 1$),
+such that for every $(x,y)$ in $S$,
+$W_y \cdot x \geq \gamma \max_{(x,y) \in S} \| x \|_2 $, 
+and 
+$W_{y'} \cdot x \leq -\gamma \max_{(x,y) \in S} \| x \|_2$
+holds simultaneously for all $y' \neq y$.
+\label{def:mc-ova-margin}
+\end{definition}
+
+For every example $(x, y)$, denote by 
+\[ b_y^i = \begin{cases} +1  & y_t = i \\ -1 & y_t \neq i \end{cases} \]
+its one-versus-all label. The above definition is equivalent to: there exists a $W$ in $\fR^{K \times d}$ ($\|W\|_F \leq 1$),
+for every $i$ in $[K]$,
+for every $(x, y)$ in $S$,
+\[ 
+b_y^i W_i \cdot x \geq \gamma \max_{(x,y) \in S} \| x \|_2.
+\]
+
+\cz{The reason we are using this specific notion of linear separability is:
+1. We need a direct comparison of $\gamma$'s before and after feature transformation, therefore a ``normalized'' notion of margin is used.  
+2.
+Alternative notions such as $\frac{W_y \cdot x}{\| x \|_2} \geq \gamma$ requires normalizing each example, in order to get a $\frac{1}{\gamma^2}$ mistake bound.
+If kernel Perceptron is used, this extra normalization step is equivalent to using a new kernel $k'(x,x') = \frac{k(x,x')}{\sqrt{k(x,x) k(x',x')}}$ as opposed to using the original kernel $k$ - we would like to avoid this techinicality for ease of presentation.}
+
+\section{Main algorithm}
+Our key observation is that, we can reduce the problem of online bandit linear multiclass learning under linear separability to the same problem under OvA linear separability.
+Specifically, inspired by~\cite{klivans2004learning}, we define
+a feature map $\phi: \fR^d \to \fR^{d'}$, such that if the original dataset $S$ is linearly separable with margin $\gamma > 0$, then the dataset tranformed by $\phi$, $S' := \cbr{(\phi(x), y): (x,y) \in S}$ is OvA linearly separable with margin $\gamma' > 0$.
+Built on this feature map, we propose an efficient algorithm that has a finite mistake bound in the linearly separable setting.
+Its key idea is to
+run an algorithm that has a finite mistake bound under OvA linear separability, upon the transformed examples $(\phi(x), y)$. 
+%a Perceptron-based algorithm that achieves a finite mistake bound under strong linear separablilty, and show how it can be combined with the feature map $\phi$ to get a
+%online learning intersection of halfspaces.
+
+\begin{algorithm}[H]
+\caption{Main Algorithm}
+\label{alg:ova}
+\SetKwInOut{Input}{Input} 
+\Input{Feature mapping $\phi$}
+Initialize $w_t^{(1)}=\ldots=w_t^{(K)}=\mathbf{0}\in \mathbb{R}^{d'}$\\
+\For{$t=1$ to $T$}{
+   \If{$\exists y$ such that $w_t^{(y)\top} \phi(x_t) \geq 0$}{
+       Assign $\tilde{y}_t$ to any $y$ with $w_t^{(y)\top}  \phi(x_t) \geq 0$ \\
+       Predict $\tilde{y}_t$ \\
+       \lIf{$\tilde{y}_t\neq y_t$}{ update $w_t^{(\tilde{y}_t)} \leftarrow w_t^{(\tilde{y}_t)} - \phi(x_t)$ } \label{line:update1}
+   }
+   \Else{
+       Pick $\tilde{y}_t$ randomly from $
+       \text{unif}([K])$ \label{line:explore}\\
+       Predict $\tilde{y}_t$ \\
+       \lIf{$\tilde{y}_t = y_t$}{ update $w_t^{(\tilde{y}_t)} \leftarrow w_t^{(\tilde{y}_t)} + \phi(x_t)$ } \label{line:update2}
+   }
+}
+\end{algorithm}
+
+We have the following guarantees of the above algorithm.
+\begin{theorem}
+Suppose feature map $\phi$ is such that for \cbr{(\phi(x_t), y_t): t \in [T]} is OvA linearly separable by margin $\gamma'$ except for $N$ points. Then, 
+the expected cumulative number of mistakes made by Algorithm~\ref{alg:ova} is at most $K \cdot ( (1 + \frac 1 {\gamma'}) N + \sqrt{ (1 + \frac 1 {\gamma'}) N \cdot \frac{1}{\gamma'^2} } + \frac{1}{\gamma'^2})$.
+\end{theorem}
+
+\begin{corollary}
+Suppose feature map $\phi$ is such that \cbr{(\phi(x_t), y_t): t \in [T]} is OvA linearly separable by margin $\gamma'$, then the cumulative number of mistakes made by Algorithm~\ref{alg:ova} is $\frac{K}{\gamma'^2}$.
+\end{corollary}
+
+\begin{proof}
+Denote by $U_{t,1}$ (resp. $U_{t,2}$) the indicator in the ``if'' branch (resp. ``else'' branch) at time $t$. In addition, denote by $U_t^y$ the indicator of $w_t^{(y)}$ gets updated at 
+round $t$.
+It can be easily seen that $U_{t,1} + U_{t,2} = \sum_{y=1}^k U_t^y = U_t^{\tilde{y}_t}$, which is equal to the indicator of Algorithm~\ref{alg:ova} making an update at iteration $t$.
+Let $N_{t,2}$ be the indicator of Algorithm~\ref{alg:ova} encounters the ``else'' branch at time $t$.
+Throughout, we also use the shorthand that $b_{t,i} = b_{y_t}^i$.
+
+% for every $y$ in $[K]$, we have the following bound on $\sum_{t=1}^T U_t^y$: for all $w_y \in \fR^d$ and all $\rho > 0$,
+%\begin{eqnarray*}
+%\sum_{t=1}^T U_t^y 
+%\leq
+%\sum_{t=1}^T U_t^y (1 - \frac{b_{t,y} w_y \phi(x_t)}{\rho})_+ 
+%+ \sqrt{(\sum_{t=1}^T U_t^y (1 - \frac{b_{t,y} w_y \phi(x_t)}{\rho})_+) \cdot \frac{\|w_y\|^2 R^2}{\rho^2} } 
+%+ \frac{\|w_y\|^2 R^2}{\rho^2}
+%\end{eqnarray*}
+%
+%Summing over all $y$ in $[K]$ and doing some algebra,
+
+By standard analysis of the Perceptron algorithm, we have that for all $W \in \fR^{K \times d}$, and all $\rho > 0$,
+\begin{equation}
+\sum_{t=1}^T U_t^{\tilde{y}_t} 
+\leq 
+\sum_{t=1}^T  U_t^{\tilde{y}_t} (1 - \frac{b_{t,y} w_{\tilde{y}_t} \phi(x_t)}{\rho})_+ 
++ \sqrt{(\sum_{t=1}^T  U_t^{\tilde{y}_t} (1 - \frac{b_{t,y} w_{\tilde{y}_t} \phi(x_t)}{\rho})_+) \cdot \frac{\|W\|_F^2 R^2}{\rho^2} } 
++ \frac{\|W\|_F^2 R^2}{\rho^2},
+\label{eqn:perceptron-mb}
+\end{equation}
+where $R = \max_{t=1}^T \| \phi(x_t)\|$.
+
+Denote by $S_{\sep}$ the indices of examples in $\cbr{(x_t, y_t)}_{t=1}^T$ that is separable by a margin $\gamma$.
+Take $W = W^*$, and $\rho = \gamma' \max_{t=1}^T \| \phi(x_t) \|_2$, we have that for all $t$ in $S_{\sep}$, for all $y$ in $[K]$, $(1 - \frac{b_{t,y} W^*_y \phi(x_t)}{\rho})_+ = 0$.
+For $t$ not in $S_{\sep}$,
+$\sum_{y=1}^K U_t^y (1 - \frac{b_{t,y} W^*_y \phi(x_t)}{\rho})_+ \leq (1 + \frac{1}{\gamma'})$. 
+This implies that $\sum_{t=1}^T  \sum_{y=1}^K U_t^y (1 - \frac{b_{t,y} w_y \phi(x_t)}{\rho})_+ \leq N(1 + \frac 1 {\gamma'})$.
+
+Combining with Equation~\eqref{eqn:perceptron-mb}, we get 
+\[
+\sum_{t=1}^T U_t^{\tilde{y}_t}  \leq (1 + \frac 1 {\gamma'}) N + \sqrt{ (1 + \frac 1 {\gamma'}) N \cdot \frac{1}{\gamma'^2} } + \frac{1}{\gamma'^2}.
+\]
+
+Now, observe that $M_t$, the mistake indicator at time $t$ is at most $U_{t,1} + N_{t,2}$.
+Also, note that $\E[U_{t,2} | N_{t,2}] \geq \frac 1 K \cdot N_{t,2}$, as conditioned on $N_{t,2} = 1$, with probability $\frac 1 K$, $U_{t,2} = 1$ .
+This implies that
+\[
+\E[\sum_{t=1}^T M_t ] \leq \E[\sum_{t=1}^T U_{t,1} + N_{t,2} ] \leq K \E[\sum_{t=1}^T U_{t,1} + U_{t,2} ]  \leq K ((1 + \frac 1 {\gamma'}) N + \sqrt{ (1 + \frac 1 {\gamma'}) N \cdot \frac{1}{\gamma'^2} } + \frac{1}{\gamma'^2}).
+\]
+\end{proof}
+
+%\section{Learning intersection of halfspaces with a margin}
+
+\section{Feature mappings that induce OvA linear separability from linear separability}
+
+How do we come up with a feature map that maps a linearly separable dataset to a OvA linearly separable dataset?
+Recall Definition~\ref{def:mc-ova-margin}, it suffices to give a feature map $\phi$ that for every $i$ in $K$, dataset $S_i = \cbr{(x, b_y^i): (x,y) \in S}$ is separable after the transformation.
+What property does dataset $S^i$ possess?
+Observe that for all examples $(x,y)$ in $S$ such that $b_y^i = +1$ (i.e.
+$y = i$), $x$ is such that $(w_i - w_{y'}) \cdot x \geq \gamma$ for all $y' \neq i$.
+For all examples $(x,y)$ in $S$ such that $b_y^i = -1$ (i.e.
+$y \neq i$), $x$ is such that
+$(w_y - w_i) \cdot x \geq \gamma$, specifically, $(w_i - w_{y'}) \cdot x \leq -\gamma$ for some $y' \neq i$. This motivates the following definition.
+
+%Suppose we are given examples 
+\begin{definition}
+Suppose we are given dataset $S = \cbr{(x, y)}$, where $x$ is in $\cbr{x \in \fR^d: \| x \| \leq 1}$, and $y$ is in $\cbr{-1,+1}$.
+$S$ is said to be separable by an intersection of halfspaces with margin parameter $\gamma > 0$, if there exists $t$ linear classifiers $v_1, \ldots, v_t$ (all of which are in $\cbr{v \in \fR^d: \| v \| \leq 1}$),
 such that for every $(x,y)$ in $S$:
@@
 
-\section{Construction of large margin feature mappings using polynomials}
 Our $\phi$'s in considerations are as follows:

### 2018-10-18 ptf_margin.tex
edits

@@
 
-For every example $(x, y)$, denote by 
-\[ b_y^i = \begin{cases} +1  & y_t = i \\ -1 & y_t \neq i \end{cases} \]
-its one-versus-all label. The above definition is equivalent to: there exists a $W$ in $\fR^{K \times d}$ ($\|W\|_F \leq 1$),
+For every example $(x, y)$, and a label $i$ in $[K]$, denote by 
+\[ b_y^i = \begin{cases} +1  & y = i \\ -1 & y \neq i \end{cases} \]
+its one-versus-all label for problem $i$. The above definition is equivalent to: there exists a $W$ in $\fR^{K \times d}$ ($\|W\|_F \leq 1$),
 for every $i$ in $[K]$,
@@
 \begin{proof}
-Denote by $U_{t,1}$ (resp. $U_{t,2}$) the indicator in the ``if'' branch (resp. ``else'' branch) at time $t$. In addition, denote by $U_t^y$ the indicator of $w_t^{(y)}$ gets updated at 
-round $t$.
-It can be easily seen that $U_{t,1} + U_{t,2} = \sum_{y=1}^k U_t^y = U_t^{\tilde{y}_t}$, which is equal to the indicator of Algorithm~\ref{alg:ova} making an update at iteration $t$.
-Let $N_{t,2}$ be the indicator of Algorithm~\ref{alg:ova} encounters the ``else'' branch at time $t$.
-Throughout, we also use the shorthand that $b_{t,i} = b_{y_t}^i$.
+Denote by $U_{t,1}$ (resp.
+$U_{t,2}$) the indicator in the ``if'' branch (resp.
+``else'' branch) at time $t$.
+Let $U_t = U_{t,1} + U_{t,2}$ be the indicator of Algorithm~\ref{alg:ova} making an update at iteration $t$.
+% In addition, denote by $U_t^y$ the indicator of $w_t^{(y)}$ gets updated at 
+%round $t$. It can be easily seen that $U_{t,1} + U_{t,2} = \sum_{y=1}^k U_t^y = U_t^{\tilde{y}_t} = U_t$, which is equal to the . 
+Let $N_{t,2}$ be the indicator of Algorithm~\ref{alg:ova} encounters the ``else'' branch at time $t$. Throughout, we also use the shorthand that $b_{t,i} = b_{y_t}^i$.
 
@@
 
-By standard analysis of the Perceptron algorithm, we have that for all $W \in \fR^{K \times d}$, and all $\rho > 0$,
+Conceptually, Algorithm~\ref{alg:ova} is equivalent to Perceptron over examples $(\phi(x_t) \otimes e_{\tilde{y}_t}, b_{t, \tilde{y}_t})$.
+Therefore, by standard analysis of the Perceptron algorithm, we have that for all $W \in \fR^{K \times d}$, and all $\rho > 0$,
 \begin{equation}
-\sum_{t=1}^T U_t^{\tilde{y}_t} 
+\sum_{t=1}^T U_t 
 \leq 
-\sum_{t=1}^T  U_t^{\tilde{y}_t} (1 - \frac{b_{t,y} w_{\tilde{y}_t} \phi(x_t)}{\rho})_+ 
-+ \sqrt{(\sum_{t=1}^T  U_t^{\tilde{y}_t} (1 - \frac{b_{t,y} w_{\tilde{y}_t} \phi(x_t)}{\rho})_+) \cdot \frac{\|W\|_F^2 R^2}{\rho^2} } 
+\sum_{t=1}^T  U_t (1 - \frac{b_{t,\tilde{y}_t} w_{\tilde{y}_t} \phi(x_t)}{\rho})_+ 
++ \sqrt{(\sum_{t=1}^T  U_t (1 - \frac{b_{t,y} w_{\tilde{y}_t} \phi(x_t)}{\rho})_+) \cdot \frac{\|W\|_F^2 R^2}{\rho^2} } 
 + \frac{\|W\|_F^2 R^2}{\rho^2},
@@
 For $t$ not in $S_{\sep}$,
-$\sum_{y=1}^K U_t^y (1 - \frac{b_{t,y} W^*_y \phi(x_t)}{\rho})_+ \leq (1 + \frac{1}{\gamma'})$. 
-This implies that $\sum_{t=1}^T  \sum_{y=1}^K U_t^y (1 - \frac{b_{t,y} w_y \phi(x_t)}{\rho})_+ \leq N(1 + \frac 1 {\gamma'})$.
+$U_t (1 - \frac{b_{t,\tilde{y}_t} W^*_{\tilde{y}_t} \phi(x_t)}{\rho})_+ \leq (1 + \frac{1}{\gamma'})$. 
+This implies that $\sum_{t=1}^T  U_t (1 - \frac{b_{t,\tilde{y}_t} W^*_{\tilde{y}_t} \phi(x_t)}{\rho})_+ \leq N(1 + \frac 1 {\gamma'})$.
 
@@
 \[
-\sum_{t=1}^T U_t^{\tilde{y}_t}  \leq (1 + \frac 1 {\gamma'}) N + \sqrt{ (1 + \frac 1 {\gamma'}) N \cdot \frac{1}{\gamma'^2} } + \frac{1}{\gamma'^2}.
+\sum_{t=1}^T U_t  \leq (1 + \frac 1 {\gamma'}) N + \sqrt{ (1 + \frac 1 {\gamma'}) N \cdot \frac{1}{\gamma'^2} } + \frac{1}{\gamma'^2}.
 \]
@@
 %\section{Learning intersection of halfspaces with a margin}
-
 \section{Feature mappings that induce OvA linear separability from linear separability}
@@
 What property does dataset $S^i$ possess?
-Observe that for all examples $(x,y)$ in $S$ such that $b_y^i = +1$ (i.e.
-$y = i$), $x$ is such that $(w_i - w_{y'}) \cdot x \geq \gamma$ for all $y' \neq i$.
-For all examples $(x,y)$ in $S$ such that $b_y^i = -1$ (i.e.
-$y \neq i$), $x$ is such that
-$(w_y - w_i) \cdot x \geq \gamma$, specifically, $(w_i - w_{y'}) \cdot x \leq -\gamma$ for some $y' \neq i$. This motivates the following definition.
+Observe that for all examples $(x,b_y^i)$ in $S_i$ such that $b_y^i = +1$, $x$ lies in the region $\cbr{x: (w_i - w_{y'}) \cdot x \geq \gamma, \text{ for all } y' \neq i}$.
+For all examples $(x,b_y^i)$ in $S_i$ such that $b_y^i = -1$, $x$ lies in the region $\cbr{x: (w_i - w_{y'}) \cdot x \leq -\gamma, \text{ for some } y' \neq i}$.
+%$(w_y - w_i) \cdot x \geq \gamma$, specifically, $(w_i - w_{y'}) \cdot x \leq -\gamma$ for some $y' \neq i$. 
+This motivates the following definition.
 

### 2018-11-12 arxiv-version/main.tex
Initial commit

\documentclass[12pt]{article}

\title{Online Multiclass Linear Classification with Bandit Feedback}

\author{
Alina Beygelzimer \and
D\'avid P\'al \and
Bal\'azs Sz\"or\'enyi \and
Devanathan Thiruvenkatachari \and
Chen-Yu Wei \and
Chicheng Zhang
}

\begin{document}

\maketitle

\end{document}

### 2018-11-12 arxiv-version/main.tex
Work on the introduction

@@
 \documentclass[12pt]{article}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsthm}
+\usepackage{fullpage}
+\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
+\usepackage{natbib}
 
@@
 
+\begin{abstract}
+TODO
+\end{abstract}
+
+\section{Introduction}
+
+We study the online multiclass classification problem with bandit feedback. The
+problem was initially proposed by \cite{Kakade-Shalev-Shwartz-Tewari-2008}. The
+corresponding problem with full information feedback is solved by the classical
+\textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
+\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}). The problem is quite
+natural and potential applications include online advertising and online content
+optimization.
+
+In this paper, we focus on the special case when the data is \emph{linearly
+separable with a margin}. In the full-information feedback setting, it is well
+know that if the data set lies in the ball of radius $R$ centered at the origin
+and is linearly separable with a margin $\gamma$ then the \textsc{Multiclass
+Perceptron} algorithm makes at most $(R/\gamma)^2$ mistakes. This result very
+satisfactory since the upper bound on the number of mistakes is
+information-theoretically optimal and at the same time the \textsc{Multiclass
+Perceptron} algorithm has low time and memory complexity.
+
+The bandit feedback setting, however, is much more challenging. We propose three
+algorithms with various time-complexity-versus-mistake-bound trade-offs. Two of
+these algorithms map the data into a high-dimensional space induced by a kernel.
+In this space the data become so called \emph{strongly separable} making the
+learning essentially trivial. The two algorithms differ by the choice of the
+kernel. The crux of the problem is th analysis of approximation properties of
+these kernels and has been studied previously by \cite{???} in the context of
+learning intersection of halfspaces. The third algorithm is based on the obvious
+idea that two points that are close enough must have the same label. Here, close
+enough means that they cannot be separated from each other by a linear separator
+with a margin.
+
+All three algorithms run in time that is polynomial in the dimension of the
+feature vectors, the number of classes and the number of rounds. At the same
+time, all three algorithms make number of mistakes that does \emph{not} depend
+on the number of rounds only on the margin, number of classes, dimension of the
+feature vectors, and the radius of the ball in which the data lie.
+
+Finally, we study two questions related to the computational and
+information-theoretic hardness of the problem. Any algorithm for the bandit
+setting collects information in the form of so called \emph{strongly labeled}
+and \emph{weakly labeled} examples. Strongly-labeled examples are those for
+which we know the class label. Weakly labeled example is an example for which we
+know that class label can be anything except for a particular one class. First,
+we show the offline problem of finding any linear separator consistent with
+given set of strongly- and weakly-labeled examples is NP-hard. Second, we show
+that any algorithm that ignores weakly labeled examples must make at least
+$\Omega(???)$ mistakes.
+
+\bibliographystyle{plainnat}
+\bibliography{biblio}
+
 \end{document}

### 2018-11-13 arxiv-version/main.tex
More work on arxiv paper

@@
 \section{Introduction}
+\label{section:introduction}
 
@@
 
-In this paper, we focus on the special case when the data is \emph{linearly
+In this paper, we focus on the special case when the examples are \emph{linearly
 separable with a margin}. In the full-information feedback setting, it is well
-know that if the data set lies in the ball of radius $R$ centered at the origin
+know that if the examples lie in the ball of radius $R$ centered at the origin
 and is linearly separable with a margin $\gamma$ then the \textsc{Multiclass
-Perceptron} algorithm makes at most $(R/\gamma)^2$ mistakes. This result very
+Perceptron} algorithm makes at most $(R/\gamma)^2$ mistakes. This result is very
 satisfactory since the upper bound on the number of mistakes is
@@
 
-The bandit feedback setting, however, is much more challenging. We propose three
-algorithms with various time-complexity-versus-mistake-bound trade-offs. Two of
-these algorithms map the data into a high-dimensional space induced by a kernel.
-In this space the data become so called \emph{strongly separable} making the
-learning essentially trivial. The two algorithms differ by the choice of the
-kernel. The crux of the problem is th analysis of approximation properties of
-these kernels and has been studied previously by \cite{???} in the context of
-learning intersection of halfspaces. The third algorithm is based on the obvious
-idea that two points that are close enough must have the same label. Here, close
-enough means that they cannot be separated from each other by a linear separator
-with a margin.
+The bandit feedback setting, however, is much more challenging. We start by
+dissecting the notion of linear separability. We define two notions of linear
+separability for multiclass classification. the ``standard'' linear separability
+and \emph{strong linear separability}. For binary classification, these two
+definitions are identical. However, they differ for multiclass classification.
+For multiclass classification with $K$ clases the standard notion of linear
+separability means that the examples from each class lie in an intersection of
+$K-1$ halfspaces and the examples outside the class lie in the complement of the
+intersection of the halfspaces. Strong linear separability means that examples
+from each class can be separated from the remaining examples by a \emph{single}
+hyperplane. We will give a more precise definition
+in Section~\ref{section:notions-of-linear-separability}.
+
+We provide a simple and efficient algorithm for the bandit feedback setting if
+the examples are strongly linearly separable. The algorithm runs $K$ copies a
+\textsc{Binary Perceptron} algorithm.
+
+For the standard notion of linear separability, we propose three algorithms with
+various time-complexity-versus-mistake-bound trade-offs. Two of these algorithms
+map the examples into a high-dimensional vector space induced by a kernel. In
+this space the examples become \emph{strongly linearly separable}. This allows
+us to run a kernelized version of the algorithm for the strongly linearly
+separable case.
+
+The two kernel-based algorithms differ by the choice of the kernel. The crux of
+the problem is the analysis of the approximation properties of these kernels and
+the way margin in original space under standard linear separability notion gets
+transformed into a margin in the high-dimensional space under the strong
+separability notion. This problem is related to the problem of learning
+intersection of halfspaces and has been studied previously by
+\cite{Klivans-Servedio-2008}.
+
+The third algorithm is based on the obvious idea that two points that are close
+enough must have the same label. Here, close enough means that they cannot be
+separated from each other by a linear separator with a margin.
 
@@
 time, all three algorithms make number of mistakes that does \emph{not} depend
-on the number of rounds only on the margin, number of classes, dimension of the
-feature vectors, and the radius of the ball in which the data lie.
+on the number of rounds. Instead, their number of mistakes depends only on the
+margin, number of classes, dimension of the feature vectors, and the radius of
+the ball in which the data lie.
 
@@
 know that class label can be anything except for a particular one class. First,
-we show the offline problem of finding any linear separator consistent with
-given set of strongly- and weakly-labeled examples is NP-hard. Second, we show
-that any algorithm that ignores weakly labeled examples must make at least
-$\Omega(???)$ mistakes.
+we show the offline problem of determining if a linear multiclass separator
+exists for a set of strongly- and weakly-labeled examples is NP-complete.
+Second, we show that any algorithm that uses only strongly-labeled examples and
+ignores weakly labeled examples makes at least $\Omega(???)$ mistakes.
+
+\section{Related work}
+\label{section:related-work}
+
+TODO
+
+\section{Notions of linear separability}
+\label{section:notions-of-linear-separability}
+
+TODO
+
+\section{Algorithm for strongly linearly separable data}
+
+TODO
+
+\section{Converting linear separability to strong linear separability}
+
+TODO
+
+\section{Nearest neighbor algorithm}
+
+TODO
+
+\section{NP-hardness of the weak labeling problem}
+
+TODO
+
+\section{Mistake lower bound for ignorant algorithms}
+
+TODO
 

### 2018-11-13 arxiv-version/main.tex
Add game protocol and a reference

@@
 
+% LaTeX packages
+\usepackage{algorithm}
+\usepackage{algorithmic}
 \usepackage{amsmath}
@@
 \usepackage{natbib}
+
+% Math commands
+\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]}
 
@@
 We study the online multiclass classification problem with bandit feedback. The
-problem was initially proposed by \cite{Kakade-Shalev-Shwartz-Tewari-2008}. The
-corresponding problem with full information feedback is solved by the classical
-\textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
+protocol of the problem is stated below. The problem was initially proposed by
+\cite{Kakade-Shalev-Shwartz-Tewari-2008}. The corresponding problem with full
+information feedback is solved by the classical \textsc{Multiclass Perceptron}
+algorithm and its variants (see e.g.
 \cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}). The problem is quite
 natural and potential applications include online advertising and online content
-optimization.
+optimization where the feedback corresponds to a user's click.
+
+\begin{algorithm}[h]
+\caption{Online multiclass classification with bandit feedback
+\label{algorithm:game-protocol}}
+\begin{algorithmic}[1]
+{
+\REQUIRE{Number of classes $K$}
+\FOR{$t=1,2,\dots$}
+\STATE{Receive feature vector $x_t$}
+\STATE{Environment \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
+\STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
+\STATE{Receive feedback $z_t \in \{0,1\}$ where $z_t = \begin{cases}
+1 & \text{if $\widehat y_t = y_t$,} \\
+0 & \text{if $\widehat y_t \neq y_t$.}
+\end{cases}$
+}
+\ENDFOR
+}
+\end{algorithmic}
+\end{algorithm}
 
@@
 separable with a margin}. In the full-information feedback setting, it is well
-know that if the examples lie in the ball of radius $R$ centered at the origin
-and is linearly separable with a margin $\gamma$ then the \textsc{Multiclass
-Perceptron} algorithm makes at most $(R/\gamma)^2$ mistakes. This result is very
-satisfactory since the upper bound on the number of mistakes is
-information-theoretically optimal and at the same time the \textsc{Multiclass
-Perceptron} algorithm has low time and memory complexity.
+know that if the examples have norm at most $R$ and are linearly separable with
+a margin $\gamma$ then the \textsc{Multiclass Perceptron} algorithm makes at
+most $(R/\gamma)^2$ mistakes. This result is very satisfactory since the upper
+bound on the number of mistakes is information-theoretically optimal and at the
+same time the \textsc{Multiclass Perceptron} algorithm has low time and memory
+complexity.
 
@@
 dissecting the notion of linear separability. We define two notions of linear
-separability for multiclass classification. the ``standard'' linear separability
+separability for multiclass classification: the standard linear separability
 and \emph{strong linear separability}. For binary classification, these two
 definitions are identical. However, they differ for multiclass classification.
-For multiclass classification with $K$ clases the standard notion of linear
+For multiclass classification with $K$ classes the standard notion of linear
 separability means that the examples from each class lie in an intersection of
@@
 from each class can be separated from the remaining examples by a \emph{single}
-hyperplane. We will give a more precise definition
+hyperplane. We state the definitions precisely
 in Section~\ref{section:notions-of-linear-separability}.
 
-We provide a simple and efficient algorithm for the bandit feedback setting if
-the examples are strongly linearly separable. The algorithm runs $K$ copies a
-\textsc{Binary Perceptron} algorithm.
+If the examples are strongly linearly separable, there is a simple and efficient
+algorithm for the bandit feedback setting that makes at most $?/\gamma^2$
+mistakes. The algorithm runs $K$ copies of the \textsc{Binary Perceptron}
+algorithm.
 
@@
 we show the offline problem of determining if a linear multiclass separator
-exists for a set of strongly- and weakly-labeled examples is NP-complete.
-Second, we show that any algorithm that uses only strongly-labeled examples and
-ignores weakly labeled examples makes at least $\Omega(???)$ mistakes.
+exists for a set of strongly- and weakly-labeled examples is NP-complete. This
+result is a simple consequence of the fact learning intersection of halfspaces
+is NP-complete~\citep{Blum-Rivest-1993}. Second, we show that any algorithm that
+uses only strongly-labeled examples and ignores weakly labeled examples makes at
+least $\Omega(???)$ mistakes.
 

### 2018-11-13 arxiv-version/main.tex
Add definition of linear separability

@@
 
-% Math commands
-\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]}
+% Math environments
+\newtheorem{definition}{Definition}
+\newtheorem{proposition}[definition]{Proposition}
+\newtheorem{lemma}[definition]{Lemma}
+\newtheorem{theorem}[definition]{Theorem}
+\newtheorem{corollary}[definition]{Corollary}
+
+% Math symbols and commands
+\newcommand{\R}{\mathbb{R}}  % set of real numbers
+\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]} % indicator
+\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
+\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
 
@@
 
+We define two notions of linear separability for multiclass classification. The
+first notion is the standard notion of linear separability used in the proof of
+mistake bound for the \textsc{Multiclass Perceptron} algorithm. The second
+notion is stronger, i.e. more restrictive. However, it is more suitable for the
+bandit setting, since it allows for a simple and efficient algorithm; see
+Section~\ref{section:algorithm-for-strongly-linearly-separable-data}.
+
+\begin{definition}
+Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
+integer, and let $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
+y_2), \dots, (x_T, y_T)$ labeled examples in $V \times \{1,2,\dots,K\}$.
+
+The examples are said to be \emph{linearly separable with a
+margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
+that
+\begin{align}
+\label{equation:linear-separability-1}
+& \sum_{i=1}^K \norm{w_i}^2 = 1 \; , \\
+\label{equation:linear-separability-2}
+& \forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; .
+\end{align}
+
+The examples are said to be \emph{strongly linearly separable with a
+margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
+that
+\begin{align}
+\label{equation:strong-linear-separability-1}
+\forall i \in \{1,2,\dots,K\} \qquad \qquad \norm{w_i}^2 & = 1 \; , \\
+\label{equation:strong-linear-separability-2}
+\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
+\label{equation:strong-linear-separability-3}
+\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
+\end{align}
+\end{definition}
+
+It is easy to see that if labeled examples are strongly linearly
+separable with margin $\gamma$ then they are linearly separable with margin
+$2\gamma/\sqrt{K}$. Indeed, if $w_1, w_2, \dots, w_K \in V$
+satisfy \eqref{equation:strong-linear-separability-1},
+\eqref{equation:strong-linear-separability-2},
+\eqref{equation:strong-linear-separability-3} then $w_1' = w_1/\sqrt{K}, w_2' =
+w_2/\sqrt{K}, \dots, w_K' = w_K/\sqrt{K}$ satisfy
+\eqref{equation:linear-separability-1} and
+\eqref{equation:linear-separability-2} with margin $\gamma' = 2\gamma/\sqrt{K}$.
+
+Similarly, if $K=2$ and labeled examples are linearly separable
+with a margin $\gamma$ then they are strongly linear separable with margin $??$.
+Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1}
+and \eqref{equation:linear-separability-2} then \dots
+
 TODO
@@
 \section{Algorithm for strongly linearly separable data}
+\label{section:algorithm-for-strongly-linearly-separable-data}
 

### 2018-11-13 arxiv-version/main.tex
Add figure

@@
 \usepackage{natbib}
+\usepackage{tikz}
+
+% TikZ packages
+\usetikzlibrary{arrows}
+\usetikzlibrary{backgrounds}
+\usetikzlibrary{calc}
+\usetikzlibrary{cd}  % commutative diagrams
+\usetikzlibrary{intersections}
+\usetikzlibrary{patterns}
+\usetikzlibrary{shapes}
+\usetikzlibrary{through}
 
@@
 \label{equation:linear-separability-1}
-& \sum_{i=1}^K \norm{w_i}^2 = 1 \; , \\
+& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
 \label{equation:linear-separability-2}
@@
 \label{equation:strong-linear-separability-1}
-\forall i \in \{1,2,\dots,K\} \qquad \qquad \norm{w_i}^2 & = 1 \; , \\
+\forall i \in \{1,2,\dots,K\} \qquad \qquad \norm{w_i}^2 & \le 1 \; , \\
 \label{equation:strong-linear-separability-2}
@@
 
-Similarly, if $K=2$ and labeled examples are linearly separable
-with a margin $\gamma$ then they are strongly linear separable with margin $??$.
-Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1}
-and \eqref{equation:linear-separability-2} then \dots
+Similarly, if $K=2$ and labeled examples are linearly separable with a margin
+$\gamma$ then they are strongly linearly separable with the same margin
+$\gamma$. Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1}
+and \eqref{equation:linear-separability-2} then $w_1' = w_1 - w_2$ and $w_2' =
+w_2 - w_1$ satisfy \eqref{equation:strong-linear-separability-1},
+\eqref{equation:strong-linear-separability-2},
+\eqref{equation:strong-linear-separability-3}.
 
-TODO
+However, if $K=3$ there exists a set of labeled examples in an inner product
+space that is linearly separable with a positive margin $\gamma$ but it is not
+strongly linearly separable for any positive $\gamma$. This is best illustrated
+on Figure~\ref{figure:linearly-separable-examples-with-margin}.
+
+\begin{figure}
+\begin{center}
+\input{figures/linearly-separable-examples-with-margin}
+\end{center}
+\caption{The figure shows labeled examples in $\R^2$ that are linearly separable with a
+positive margin $\gamma$. There are $K=3$ classes. The examples of each class
+are colored white, gray and black respectively. All examples lie in the ball of
+radius $R$ centered at the origin. However, the examples are \emph{not} strongly
+linearly separable for any positive margin $\gamma$.
+}
+\label{figure:linearly-separable-examples-with-margin}
+\end{figure}
 

### 2018-11-13 arxiv-version/main.tex
Add algorithm for strongly separable case

@@
 \end{center}
-\caption{The figure shows labeled examples in $\R^2$ that are linearly separable with a
-positive margin $\gamma$. There are $K=3$ classes. The examples of each class
-are colored white, gray and black respectively. All examples lie in the ball of
-radius $R$ centered at the origin. However, the examples are \emph{not} strongly
-linearly separable for any positive margin $\gamma$.
+\caption{The figure shows labeled examples in $\R^2$. There are $K=3$ classes. The
+examples of each class are colored white, gray and black respectively. All
+examples lie in the ball of radius $R$ centered at the origin. While the
+examples are linearly separable with a positive margin $\gamma$, they are
+\emph{not} strongly linearly separable for any positive margin $\gamma$,
+however.
 }
@@
 
+\begin{algorithm}[h]
+\caption{Algorithm for strongly linearly separable examples
+\label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
+\begin{algorithmic}[1]
+{
+\REQUIRE{Number of classes $K$}
+\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
+\FOR{$t=1,2,\dots$}
+\STATE{Receive feature vector $x_t$}
+\STATE{Compute $S_t = \{ i ~:~ \ip{w_i^{(t)}}{x_t} > 0 \}$}
+\IF{$|S_t| = 1$}
+\STATE{Predict $\widehat y_t$ where $\widehat y_t \in S_t$}
+\ELSE
+\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
+\ENDIF
+\STATE{Receive feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t = y_t}$}
+\STATE{Update $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
+\IF{$z_t = 0$}
+\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
+\ELSE
+\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)}$}
+\ENDIF
+\ENDFOR
+}
+\end{algorithmic}
+\end{algorithm}
+
+\begin{theorem}
+Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
+integer, $\gamma$ a positive real number, $R$ be a non-negative real number
+If $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples
+in $V \times \{1,2,\dots,K\}$ such that the examples are strongly separable with
+margin $\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ then
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
+makes at most $K (R/\gamma)^2$ mistakes.
+\end{theorem}
+
+\begin{proof}
 TODO
+\end{proof}
 

### 2018-11-14 arxiv-version/main.tex
Small fixes

@@
 \label{equation:strong-linear-separability-1}
-\forall i \in \{1,2,\dots,K\} \qquad \qquad \norm{w_i}^2 & \le 1 \; , \\
+\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
 \label{equation:strong-linear-separability-2}
@@
 
-However, if $K=3$ there exists a set of labeled examples in an inner product
+However, if $K \ge 3$ there exists a set of labeled examples in an inner product
 space that is linearly separable with a positive margin $\gamma$ but it is not
-strongly linearly separable for any positive $\gamma$. This is best illustrated
-on Figure~\ref{figure:linearly-separable-examples-with-margin}.
+strongly linearly separable for any positive $\gamma$. Such set of examples is
+shown in Figure~\ref{figure:linearly-separable-examples-with-margin}.
 

### 2018-11-15 arxiv-version/main.tex
Add multiclass perceptron

@@
 \newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
+\DeclareMathOperator*{\argmax}{argmax}
+\DeclareMathOperator*{\argmin}{argmin}
+\DeclareMathOperator*{\Exp}{\mathbf{E}}  % expected value
 
@@
 
-We study the online multiclass classification problem with bandit feedback. The
-protocol of the problem is stated below. The problem was initially proposed by
+We study the \textsc{Online Multiclass Classification with Bandit Feedback}
+problem. The protocol of the problem is stated below. The goal is to design an
+algorithm that makes small number of mistakes $\sum_{t=1}^T z_t = \sum_{t=1}^T
+\indicator{\widehat y_t \neq y_t}$. The problem was initially proposed by
 \cite{Kakade-Shalev-Shwartz-Tewari-2008}. The corresponding problem with full
@@
 \begin{algorithm}[h]
-\caption{Online multiclass classification with bandit feedback
+\caption{\textsc{Online Multiclass Classification with Bandit Feedback}
 \label{algorithm:game-protocol}}
@@
 {
-\REQUIRE{Number of classes $K$}
-\FOR{$t=1,2,\dots$}
-\STATE{Receive feature vector $x_t$}
+\REQUIRE{Number of classes $K$. Number of rounds $T$.}
+\FOR{$t=1,2,\dots,T$}
+\STATE{Observe feature vector $x_t$}
 \STATE{Environment \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
 \STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Receive feedback $z_t \in \{0,1\}$ where $z_t = \begin{cases}
-1 & \text{if $\widehat y_t = y_t$,} \\
-0 & \text{if $\widehat y_t \neq y_t$.}
+\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \begin{cases}
+0 & \text{if $\widehat y_t = y_t$,} \\
+1 & \text{if $\widehat y_t \neq y_t$.}
 \end{cases}$
@@
 a margin $\gamma$ then the \textsc{Multiclass Perceptron} algorithm makes at
-most $(R/\gamma)^2$ mistakes. This result is very satisfactory since the upper
-bound on the number of mistakes is information-theoretically optimal and at the
-same time the \textsc{Multiclass Perceptron} algorithm has low time and memory
-complexity.
+most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes. This result is very satisfactory
+since the upper bound on the number of mistakes is information-theoretically
+optimal and at the same time the \textsc{Multiclass Perceptron} algorithm has
+low time and memory complexity.
 
@@
 If the examples are strongly linearly separable, there is a simple and efficient
-algorithm for the bandit feedback setting that makes at most $?/\gamma^2$
-mistakes. The algorithm runs $K$ copies of the \textsc{Binary Perceptron}
-algorithm.
+algorithm for the bandit feedback setting with expected number of mistakes
+at most $K (R/\gamma)^2$. The algorithm can be viewed as running $K$ copies of
+the \textsc{Binary Perceptron} algorithm, one copy for each class.
 
@@
 map the examples into a high-dimensional vector space induced by a kernel. In
-this space the examples become \emph{strongly linearly separable}. This allows
+this space the examples become \emph{strongly} linearly separable. This allows
 us to run a kernelized version of the algorithm for the strongly linearly
@@
 \label{equation:linear-separability-1}
-& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
+\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
 \label{equation:linear-separability-2}
-& \forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; .
+\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} & \ge \ip{x_t}{w_i} + \gamma \; .
 \end{align}
@@
 separable with margin $\gamma$ then they are linearly separable with margin
-$2\gamma/\sqrt{K}$. Indeed, if $w_1, w_2, \dots, w_K \in V$
+$2\gamma$. Indeed, if $w_1, w_2, \dots, w_K \in V$
 satisfy \eqref{equation:strong-linear-separability-1},
 \eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3} then $w_1' = w_1/\sqrt{K}, w_2' =
-w_2/\sqrt{K}, \dots, w_K' = w_K/\sqrt{K}$ satisfy
+\eqref{equation:strong-linear-separability-3} then they satisfy
 \eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} with margin $\gamma' = 2\gamma/\sqrt{K}$.
+\eqref{equation:linear-separability-2} with margin $\gamma' = 2\gamma$.
 
 Similarly, if $K=2$ and labeled examples are linearly separable with a margin
-$\gamma$ then they are strongly linearly separable with the same margin
-$\gamma$. Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1}
-and \eqref{equation:linear-separability-2} then $w_1' = w_1 - w_2$ and $w_2' =
-w_2 - w_1$ satisfy \eqref{equation:strong-linear-separability-1},
+$\gamma$ then they are strongly linearly separable with margin $\gamma/2$.
+Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1} and
+\eqref{equation:linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$,
+$w_2' = \frac{w_2 - w_1}{2}$ and $\gamma'=\gamma/2$ satisfy
+\eqref{equation:strong-linear-separability-1},
 \eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3}.
+\eqref{equation:strong-linear-separability-3} since $\norm{w_i'}^2 \le
+(\frac{1}{2} \norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le \frac{1}{2}\norm{w_1}^2 +
+\frac{1}{2}\norm{w_2}^2$ for $i=1,2$.
 
-However, if $K \ge 3$ there exists a set of labeled examples in an inner product
+However, for $K \ge 3$ there exists a set of labeled examples in an inner product
 space that is linearly separable with a positive margin $\gamma$ but it is not
-strongly linearly separable for any positive $\gamma$. Such set of examples is
-shown in Figure~\ref{figure:linearly-separable-examples-with-margin}.
+strongly linearly separable with any positive margin $\gamma$. Such set of labeled
+examples is shown in
+Figure~\ref{figure:linearly-separable-examples-with-margin}.
 
@@
 \end{center}
-\caption{The figure shows labeled examples in $\R^2$. There are $K=3$ classes. The
-examples of each class are colored white, gray and black respectively. All
-examples lie in the ball of radius $R$ centered at the origin. While the
-examples are linearly separable with a positive margin $\gamma$, they are
-\emph{not} strongly linearly separable for any positive margin $\gamma$,
-however.
+\caption{The figure shows labeled examples in $\R^2$. The examples belong to
+$K=3$ classes colored white, gray and black respectively. Each class lies in a
+$120^\circ$ wedge. While the examples are linearly separable with a positive
+margin $\gamma$, they are \emph{not} strongly linearly separable for any
+positive margin $\gamma$.
 }
@@
 \end{figure}
+
+The notion of linear separability with a margin is standard. It used in the
+full-information setting to upper bound the number of mistakes of the
+\textsc{Multiclass Perceptron} algorithm. For completeness, we state the
+algorithm below. It is a folklore result that if a set of labeled examples is
+separable with a margin $\gamma$ and the norm of the examples is bounded by $R$
+then \textsc{Multiclass Perceptron} algorithm makes at most $\left\lfloor
+(R/\gamma)^2 \right \rfloor$ mistakes. Another folklore result is that
+\textsc{Multiclass Perceptron} is an optimal algorithm in the sense that any
+deterministic algorithm makes $\left\lfloor (R/\gamma)^2 \right \rfloor$
+mistakes in the worst case. For completeness, we give proofs  in
+Section~\ref{section:multiclass-perceptron-proofs} for both of these results.
+
+\begin{algorithm}[h]
+\caption{\textsc{Multiclass Perceptron}
+\label{algorithm:mutliclass-perceptron}}
+\begin{algorithmic}[1]
+{
+\REQUIRE{Number of classes $K$. Number of rounds $T$.}
+\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
+\FOR{$t=1,2,\dots,T$}
+\STATE{Observe feature vector $x_t$}
+\STATE{Predict $\widehat y_t = \argmax_{i \in \{1,2,\dots,K\}} \ip{w_t^{(i)}}{x_t}$}
+\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
+\IF{$\widehat y_t \neq y_t$}
+\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}$}
+\STATE{Update $w_{y_t}^{(t+1)} = w_{y_t}^{(t)} + x_t$}
+\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
+\ELSE
+\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
+\ENDIF
+\ENDFOR
+}
+\end{algorithmic}
+\end{algorithm}
 
@@
 {
-\REQUIRE{Number of classes $K$}
+\REQUIRE{Number of classes $K$. Number of rounds $T$.}
 \STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
-\FOR{$t=1,2,\dots$}
+\FOR{$t=1,2,\dots,T$}
 \STATE{Receive feature vector $x_t$}
-\STATE{Compute $S_t = \{ i ~:~ \ip{w_i^{(t)}}{x_t} > 0 \}$}
-\IF{$|S_t| = 1$}
-\STATE{Predict $\widehat y_t$ where $\widehat y_t \in S_t$}
+\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$}
+\IF{$S_t = \emptyset$}
+\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
 \ELSE
-\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
+\STATE{Predict $\widehat y_t \sim \text{Uniform}(S_t)$}
 \ENDIF
-\STATE{Receive feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t = y_t}$}
-\STATE{Update $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
-\IF{$z_t = 0$}
+\STATE{Receive feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
+\IF{$S_t = \emptyset$}
+\IF{$z_t = 1$}
+\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
+\ELSE
+\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
+\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$}
+\ENDIF
+\ELSE
+\IF{$z_t = 1$}
+\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
 \STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
 \ELSE
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)}$}
+\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
+\ENDIF
 \ENDIF
@@
 
+\appendix
+
+\section{Multiclass Perceptron}
+\label{section:multiclass-perceptron-proofs}
+
+\begin{theorem}[Upper bound]
+Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
+integer, let $\gamma$ be a positive real number and let $R$ be a non-negative real
+number. If $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled
+examples in $V \times \{1,2,\dots,K\}$ that are linearly separable with margin
+$\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
+then \textsc{Multiclass Perceptron} algorithm makes at most $\lfloor
+2(R/\gamma)^2 \rfloor$ mistakes.
+\end{theorem}
+
+\begin{proof}
+Let $M = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$ be the number of
+mistakes the algorithm makes. Since the $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots,
+w_K^{(t)})$ changes only if a mistake is made, we can upper bound $\sum_{i=1}^K
+\norm{w_i^{(t)}}^2$ in terms of number of mistakes.
+If a mistake happens in round $t$,
+\begin{align*}
+\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
+& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) + \norm{w_{y_t}^{(t)} + x_t}^2 + \norm{w_{\widehat y_t}^{(t)} - x_t}^2 \\
+& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) + \norm{w_{y_t}^{(t)}}^2 + \norm{w_{\widehat y_t}^{(t)}}^2 + 2 \norm{x_t}^2 + 2 \ip{w_{y_t}^{(t)} - w_{\widehat y_t}^{(t)}}{x_t} \\
+& = \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 \norm{x_t}^2 + 2 \ip{w_{y_t}^{(t)} - w_{\widehat y_t}^{(t)}}{x_t} \\
+& \le \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 \norm{x_t}^2 \\
+& \le \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 R^2 \; .
+\end{align*}
+So each time a mistake happens, $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ increases by at most $2R^2$. Thus,
+$$
+\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le 2R^2 M \; .
+$$
+Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors satisfying the
+\eqref{equation:linear-separability-1} and
+\eqref{equation:linear-separability-2}. We lower bound $\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$. This quantity changes
+only when a mistakes happens. If mistake happens in round $t$, we have
+\begin{align*}
+\sum_{i=1}^K \ip{w_i^*}{w_i^{(t+1)}}
+& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus {y_t, \widehat y_t}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^*}{w_{y_t}^{(t)} + x_t} + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} - x_t} \\
+& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^* - w_{\widehat y_t}^*}{x_t} \\
+& \ge  \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \gamma \; .
+\end{align*}
+Thus, after $M$ mistakes,
+$$
+\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma M \; .
+$$
+We upper bound the left hand side by using Cauchy-Schwartz inequality twice and
+the condition \eqref{equation:linear-separability-1} on $w_1^*, w_2^*, \dots,
+w_K^*$. We have
+$$
+\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
+\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
+\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
+\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
+$$
+Combining all inequalities, we get
+$$
+(\gamma M)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le 2R^2 M \; .
+$$
+We conclude that $M \le 2(R/\gamma)^2$. Since $M$ is an integer, $M \le \lfloor 2(R/\gamma)^2 \rfloor$.
+\end{proof}
+
+\begin{theorem}[Lower bound]
+Let $K$ be a positive integer, let $\gamma$ be a positive real number and let
+$R$ be a non-negative real number. For any deterministic algorithm for the
+full-information multiclass classification there exists an inner product space
+$(V, \ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
+examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ examples in $V \times
+\{1,2,\dots,K\}$ that are linearly separable with margin $\gamma$, the norms
+satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the algorithm
+makes at least $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
+\end{theorem}
+
+\begin{proof}
+TODO
+\end{proof}
+
 \end{document}

### 2018-11-15 arxiv-version/main.tex
Lower bound for multiclass perceptron

@@
 
-In this paper, we focus on the special case when the examples are \emph{linearly
-separable with a margin}. In the full-information feedback setting, it is well
-know that if the examples have norm at most $R$ and are linearly separable with
-a margin $\gamma$ then the \textsc{Multiclass Perceptron} algorithm makes at
-most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes. This result is very satisfactory
-since the upper bound on the number of mistakes is information-theoretically
-optimal and at the same time the \textsc{Multiclass Perceptron} algorithm has
-low time and memory complexity.
+In this paper, we focus on the special case when the examples lie in $\R^d$ and
+are \emph{linearly separable with a margin}. In the full-information feedback
+setting, it is well know that if the examples have norm at most $R$ and are
+linearly separable with a margin $\gamma$ then the \textsc{Multiclass
+Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
+This result is very satisfactory since the upper bound on the number of mistakes
+is information-theoretically optimal and at the same time the \textsc{Multiclass
+Perceptron} algorithm has low time and memory complexity.
 
 The bandit feedback setting, however, is much more challenging. We start by
-dissecting the notion of linear separability. We define two notions of linear
-separability for multiclass classification: the standard linear separability
-and \emph{strong linear separability}. For binary classification, these two
-definitions are identical. However, they differ for multiclass classification.
-For multiclass classification with $K$ classes the standard notion of linear
-separability means that the examples from each class lie in an intersection of
-$K-1$ halfspaces and the examples outside the class lie in the complement of the
-intersection of the halfspaces. Strong linear separability means that examples
-from each class can be separated from the remaining examples by a \emph{single}
-hyperplane. We state the definitions precisely
-in Section~\ref{section:notions-of-linear-separability}.
+dissecting the notion of linear separability in the multiclass setting. Beside
+the standard notion of linear separability, we define also and \emph{strong
+linear separability}. For binary classification, these two definitions are
+identical. However, they differ for multiclass classification. For multiclass
+classification with $K$ classes the standard notion of linear separability means
+that the examples from each class lie in an intersection of $K-1$ halfspaces and
+the examples outside of the class lie in the complement of the intersection of
+the halfspaces. Strong linear separability means that examples from each class
+can be separated from the remaining examples by a \emph{single} hyperplane. We
+state the definitions precisely in
+Section~\ref{section:notions-of-linear-separability}.
 
-If the examples are strongly linearly separable, there is a simple and efficient
-algorithm for the bandit feedback setting with expected number of mistakes
-at most $K (R/\gamma)^2$. The algorithm can be viewed as running $K$ copies of
-the \textsc{Binary Perceptron} algorithm, one copy for each class.
+For the case when the examples are strongly linearly separable, we design a
+simple and efficient algorithm with expected number of mistakes at most $K
+(R/\gamma)^2$. The algorithm can be viewed as running $K$ copies of the
+\textsc{Binary Perceptron} algorithm, one copy for each class. Intuitively
+speaking, the factor $K$ is the price we pay for the bandit feedback,
+or more precisely, the lack of full-information feedback.
 
@@
 various time-complexity-versus-mistake-bound trade-offs. Two of these algorithms
-map the examples into a high-dimensional vector space induced by a kernel. In
-this space the examples become \emph{strongly} linearly separable. This allows
-us to run a kernelized version of the algorithm for the strongly linearly
-separable case.
+map the examples into a high-dimensional inner product space induced by a
+kernel. In this space the examples become \emph{strongly} linearly separable.
+This allows us to run a kernelized version of the algorithm for the strongly
+linearly separable case.
 
@@
 then \textsc{Multiclass Perceptron} algorithm makes at most $\left\lfloor
-(R/\gamma)^2 \right \rfloor$ mistakes. Another folklore result is that
+2(R/\gamma)^2 \right \rfloor$ mistakes. Another folklore result is that
 \textsc{Multiclass Perceptron} is an optimal algorithm in the sense that any
-deterministic algorithm makes $\left\lfloor (R/\gamma)^2 \right \rfloor$
+deterministic algorithm makes $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
 mistakes in the worst case. For completeness, we give proofs  in
@@
 {
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
+\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
 \STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
 \FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$}
+\STATE{Observe feature vector $x_t \in V$}
 \STATE{Predict $\widehat y_t = \argmax_{i \in \{1,2,\dots,K\}} \ip{w_t^{(i)}}{x_t}$}
@@
 \begin{algorithm}[h]
-\caption{Algorithm for strongly linearly separable examples
+\caption{\textsc{Bandit Algorithm for Strongly Linearly Separable Examples}
 \label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
@@
 {
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
+\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
 \STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
 \FOR{$t=1,2,\dots,T$}
-\STATE{Receive feature vector $x_t$}
+\STATE{Observe feature vector $x_t \in V$}
 \STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$}
@@
 \ENDIF
-\STATE{Receive feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
+\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
 \IF{$S_t = \emptyset$}
@@
 
-\begin{theorem}[Upper bound]
+\begin{theorem}[Mistake upper bound]
 Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
@@
 
-\begin{theorem}[Lower bound]
+\begin{algorithm}[h]
+\caption{\textsc{Full-Information Multiclass Classification}
+\label{algorithm:mutliclass-classification}}
+\begin{algorithmic}[1]
+{
+\REQUIRE{Number of classes $K$. Number of rounds $T$.}
+\FOR{$t=1,2,\dots,T$}
+\STATE{Observe feature vector $x_t$}
+\STATE{Predict $\widehat y_t \in \{1,2,\dots,K\}$}
+\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
+\ENDFOR
+}
+\end{algorithmic}
+\end{algorithm}
+
+\begin{theorem}[Mistake lower bound]
 Let $K$ be a positive integer, let $\gamma$ be a positive real number and let
 $R$ be a non-negative real number. For any deterministic algorithm for the
-full-information multiclass classification there exists an inner product space
-$(V, \ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ examples in $V \times
-\{1,2,\dots,K\}$ that are linearly separable with margin $\gamma$, the norms
-satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the algorithm
-makes at least $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
+\textsc{Full-Information Multiclass Classification} problem there exists an
+inner product space $(V, \ip{\cdot}{\cdot})$, a non-negative integer $T$ and a
+sequence of labeled examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$
+examples in $V \times \{1,2,\dots,K\}$ that are linearly separable with margin
+$\gamma$, the norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
+and the algorithm makes at least $\lfloor (R/\gamma)^2 \rfloor$ mistakes.
 \end{theorem}
@@
 \begin{proof}
-TODO
+Let $T = \lfloor (R/\gamma)^2 \rfloor$ and let $x_1, x_2, \dots, x_T$ be the
+orthogonal vectors such that $\norm{x_t} = R$ for all $t=1,2,\dots,T$. For
+example, we can take $V = \R^T$ and $x_t = R e_t$ where $e_t$ is $t$-th element
+of the standard orthonormal basis of $\R^T$.
+
+Since the algorithm is deterministic, we can construct the sequence of labels
+$y_1, y_2, \dots, y_T$ adaptively based on the predictions $\widehat y_1,
+\widehat y_2, \dots, \widehat y_T$ of the algorithm. We define $y_t$ to be any
+element of $\{1,2,\dots,K\}$ not equal to $\widehat y_t$. This way the algorithm
+makes a mistake in every round $t=1,2,\dots,T$.
+
+It remains to show that the examples we have constructed are linearly separable
+with margin $\gamma$. To prove that we demostrate vectors $w_1, w_2, \dots, w_K$
+satisfying conditions \eqref{equation:linear-separability-1} and
+\eqref{equation:linear-separability-2}. We define
+$$
+w_i = \frac{1}{R\sqrt{T}} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} x_t \qquad \qquad \text{for $i=1,2,\dots,K$.}
+$$
+Let $a_i = |\{ t ~:~ 1 \le t \le T, \ y_t = i \}|$ be the number of occurences of label $i$.
+It is easy to see that
+$$
+\norm{w_i}^2 = \frac{1}{R^2 T} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} \norm{x_t}^2 = \frac{a_i}{T} \qquad \qquad \text{for $i=1,2,\dots,K$.}
+$$
+Since $\sum_{i=1}^K a_i = T$, the condition
+\eqref{equation:linear-separability-1} holds. To verify condition
+\eqref{equation:linear-separability-2} consider any labeled example $(x_t,
+y_t)$. Then, by definition of $w_{y_t}$ we have
+$$
+\ip{w_{y_t}}{x_t}
+= \frac{1}{R\sqrt{T}} \sum_{\substack{s : 1 \le s \le T \\ y_s = y_t}} \ip{x_s}{x_t}
+= \frac{1}{R\sqrt{T}} \norm{x_t}^2
+= \frac{R}{\sqrt{T}}
+\ge \frac{R}{R/\gamma}
+= \gamma \; .
+$$
+and for any $i \in \{1,2,\dots,K\} \setminus \{y_t\}$ we have
+$\ip{w_i}{x_t} = 0$. Therefore, condition \eqref{equation:linear-separability-2} holds.
 \end{proof}

### 2018-11-19 arxiv-version/main.tex
Add proof for the strongly linearly separable case

@@
 \usepackage{natbib}
+\usepackage{thmtools}
 \usepackage{tikz}
@@
 
+The notion of linear separability with a margin is standard. It used in the
+full-information setting to upper bound the number of mistakes of the
+\textsc{Multiclass Perceptron} algorithm. For completeness, we state the
+algorithm in Appendix~\ref{section:multiclass-perceptron-proofs}. It is a
+folklore result that if a set of labeled examples is separable with a margin
+$\gamma$ and the norm of the examples is bounded by $R$ then \textsc{Multiclass
+Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
+mistakes. Another folklore result is that \textsc{Multiclass Perceptron} is
+essentially optimal in the sense that any deterministic algorithm must make
+$\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
+completeness, we give proofs of both of these results in
+Section~\ref{section:multiclass-perceptron-proofs}.
+
+The notion of strong linear separability is new.
+
 It is easy to see that if labeled examples are strongly linearly
@@
 \end{figure}
-
-The notion of linear separability with a margin is standard. It used in the
-full-information setting to upper bound the number of mistakes of the
-\textsc{Multiclass Perceptron} algorithm. For completeness, we state the
-algorithm below. It is a folklore result that if a set of labeled examples is
-separable with a margin $\gamma$ and the norm of the examples is bounded by $R$
-then \textsc{Multiclass Perceptron} algorithm makes at most $\left\lfloor
-2(R/\gamma)^2 \right \rfloor$ mistakes. Another folklore result is that
-\textsc{Multiclass Perceptron} is an optimal algorithm in the sense that any
-deterministic algorithm makes $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
-mistakes in the worst case. For completeness, we give proofs  in
-Section~\ref{section:multiclass-perceptron-proofs} for both of these results.
-
-\begin{algorithm}[h]
-\caption{\textsc{Multiclass Perceptron}
-\label{algorithm:mutliclass-perceptron}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
-\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t \in V$}
-\STATE{Predict $\widehat y_t = \argmax_{i \in \{1,2,\dots,K\}} \ip{w_t^{(i)}}{x_t}$}
-\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
-\IF{$\widehat y_t \neq y_t$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}$}
-\STATE{Update $w_{y_t}^{(t+1)} = w_{y_t}^{(t)} + x_t$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ENDIF
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
 
@@
 Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
-integer, $\gamma$ a positive real number, $R$ be a non-negative real number
-If $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples
-in $V \times \{1,2,\dots,K\}$ such that the examples are strongly separable with
-margin $\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ then
+integer, $\gamma$ a positive real number, $R$ be a non-negative real number If
+$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
+$V \times \{1,2,\dots,K\}$ such that the examples are strongly separable with
+margin $\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ then the
+expected number of mistakes
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-makes at most $K (R/\gamma)^2$ mistakes.
+makes is at most $K(K-1) \lfloor (R/\gamma)^2 \rfloor$ mistakes.
 \end{theorem}
@@
 \begin{proof}
-TODO
+Let $M = \sum_{t=1}^T z_t$ be the number of mistakes the algorithm makes. Let $A
+= \sum_{t ~:~ S_t \neq \emptyset} z_t$ be the number of mistakes in the rounds
+when $S_t \neq \emptyset$ and let $B = \sum_{t ~:~ S_t = \emptyset} z_t$ be the
+number of mistakes in the rounds when $S_t = \emptyset$. Obviously, $M = A + B$.
+We upper bound $A$ and $B$ separately.
+
+Let $C$ be the number of times line 16 gets executed. Let $U$ be the number of
+times line 16 or line 21 get executed. In other words, $U$ the number of times
+the weight vectors are updated. Clearly, $U = A + C$. We know that $U \le
+\frac{K} \lfloor (R/\gamma)^2 \rfloor$.
+
+The key observation is that $\Exp[B] = (K-1) \Exp[C]$ since there the $1/K$
+probability that the algorithm guesses the correct label correctly if $S_t =
+\emptyset$. Putting all the information together, we get that
+\begin{align*}
+\Exp[M]
+& = \Exp[A] + \Exp[B] \\
+& = \Exp[A] + (K-1) \Exp[C]  \\
+& \le (K-1) \Exp[A + C] \\
+& = (K-1) \Exp[U]  \\
+& \le K(K-1) \lfloor (R/\gamma)^2 \rfloor \; .
+\end{align*}
 \end{proof}
@@
 
+\textsc{Multiclass Perceptron} is an algorithm for \textsc{Online Multiclass
+Classification}. Both the protocol for the problem and the algorithm are stated
+below. The algorithm assumes that the feature vectors come from an inner product
+space $(V, \ip{\cdot}{\cdot})$.
+
+Two results are folklore. The first result is
+\autoref{theorem:mutliclass-perceptron-mistake-upper-bound} which states that if
+examples are linearly separable with margin $\gamma$ and examples have norm
+at most $R$ then the algorithm makes at most $\lfloor 2 (R/\gamma)^2 \rfloor$
+mistakes. The second result is
+\autoref{theorem:online-multiclass-classification-mistake-lower-bound} which
+states that under the same assumptions as in
+\autoref{theorem:online-multiclass-classification-mistake-lower-bound}
+\emph{any} deterministic algorithm for \textsc{Online Multiclass Classification}
+must make at least $\lfloor (R/\gamma)^2 \rfloor$ mistakes in the worst case.
+
+\begin{algorithm}[h]
+\caption{\textsc{Online Multiclass Classification}
+\label{algorithm:mutliclass-classification}}
+\begin{algorithmic}[1]
+{
+\REQUIRE{Number of classes $K$. Number of rounds $T$.}
+\FOR{$t=1,2,\dots,T$}
+\STATE{Observe feature vector $x_t$}
+\STATE{Predict $\widehat y_t \in \{1,2,\dots,K\}$}
+\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
+\ENDFOR
+}
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[h]
+\caption{\textsc{Multiclass Perceptron}
+\label{algorithm:mutliclass-perceptron}}
+\begin{algorithmic}[1]
+{
+\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
+\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
+\FOR{$t=1,2,\dots,T$}
+\STATE{Observe feature vector $x_t \in V$}
+\STATE{Predict $\widehat y_t = \argmax_{i \in \{1,2,\dots,K\}} \ip{w_t^{(i)}}{x_t}$}
+\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
+\IF{$\widehat y_t \neq y_t$}
+\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}$}
+\STATE{Update $w_{y_t}^{(t+1)} = w_{y_t}^{(t)} + x_t$}
+\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
+\ELSE
+\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
+\ENDIF
+\ENDFOR
+}
+\end{algorithmic}
+\end{algorithm}
+
 \begin{theorem}[Mistake upper bound]
+\label{theorem:mutliclass-perceptron-mistake-upper-bound}
 Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
@@
 
-\begin{algorithm}[h]
-\caption{\textsc{Full-Information Multiclass Classification}
-\label{algorithm:mutliclass-classification}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$}
-\STATE{Predict $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
 \begin{theorem}[Mistake lower bound]
+\label{theorem:online-multiclass-classification-mistake-lower-bound}
 Let $K$ be a positive integer, let $\gamma$ be a positive real number and let

### 2018-11-19 arxiv-version/main.tex
Add more explanations

@@
 \usepackage{amsthm}
+\usepackage{caption}
 \usepackage{fullpage}
@@
 
-We study the \textsc{Online Multiclass Classification with Bandit Feedback}
-problem. The protocol of the problem is stated below. The goal is to design an
-algorithm that makes small number of mistakes $\sum_{t=1}^T z_t = \sum_{t=1}^T
-\indicator{\widehat y_t \neq y_t}$. The problem was initially proposed by
-\cite{Kakade-Shalev-Shwartz-Tewari-2008}. The corresponding problem with full
-information feedback is solved by the classical \textsc{Multiclass Perceptron}
-algorithm and its variants (see e.g.
-\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}). The problem is quite
-natural and potential applications include online advertising and online content
-optimization where the feedback corresponds to a user's click.
+We design new algorithms for the problem of \textsc{Online Multiclass
+Classification with Bandit Feedback}. In this problem, in each round $t$, the
+algorithm receives a feature vector $x_t$ and algorithm has to predict one of
+$K$ possible classes. Imediately after the algorithm makes its prediction, it
+receives feedback whether the prediction was correct or not. However, in
+contrast with the standard, so called full information setting, the algorithm
+does \emph{not} receive the correct label. In other words, the feedback is
+purely binary (correct prediction or incorrect prediction). To allow for
+meaningful randomized strategies, we assume that the correct label for round $t$
+is chosen prior to algorithm's prediction in that round.\footnote{The reader can
+assume throughout the paper a simpler model of the so called \emph{oblivious
+adversary} where the whole sequence of labeled examples $(x_1, y_1), (x_2, y_2),
+\dots, (x_T, y_T)$ is chosen before the first round of the game.} The protocol
+of the problem is stated below.
 
@@
 
+The goal is to design an algorithm that makes small number of mistakes
+$\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$. The problem
+was initially proposed by \cite{Kakade-Shalev-Shwartz-Tewari-2008}. The
+corresponding problem with full information feedback is solved by the classical
+\textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
+\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}). The problem is quite
+natural and potential applications include online advertising and online content
+optimization where the feedback corresponds to a user's click.
+
 In this paper, we focus on the special case when the examples lie in $\R^d$ and
@@
 
-The bandit feedback setting, however, is much more challenging. We start by
-dissecting the notion of linear separability in the multiclass setting. Beside
-the standard notion of linear separability, we define also and \emph{strong
-linear separability}. For binary classification, these two definitions are
-identical. However, they differ for multiclass classification. For multiclass
-classification with $K$ classes the standard notion of linear separability means
-that the examples from each class lie in an intersection of $K-1$ halfspaces and
-the examples outside of the class lie in the complement of the intersection of
-the halfspaces. Strong linear separability means that examples from each class
-can be separated from the remaining examples by a \emph{single} hyperplane. We
-state the definitions precisely in
+The bandit feedback setting, however, is much more challenging. To understand
+the differences, we dissect the notion of linear separability in the multiclass
+setting. Beside the standard notion of linear separability, we define also
+\emph{strong linear separability}. For binary classification, these two
+definitions are identical. However, they differ for multiclass classification.
+For multiclass classification with $K$ classes the standard notion of linear
+separability means that the examples from each class lie in an intersection of
+$K-1$ halfspaces and the examples outside of the class lie in the complement of
+the intersection of the halfspaces. Strong linear separability means that
+examples from each class can be separated from the remaining examples by a
+\emph{single} hyperplane. We state the definitions precisely in
 Section~\ref{section:notions-of-linear-separability}.
@@
 For the case when the examples are strongly linearly separable, we design a
-simple and efficient algorithm with expected number of mistakes at most $K
-(R/\gamma)^2$. The algorithm can be viewed as running $K$ copies of the
-\textsc{Binary Perceptron} algorithm, one copy for each class. Intuitively
-speaking, the factor $K$ is the price we pay for the bandit feedback,
-or more precisely, the lack of full-information feedback.
+simple and efficient algorithm with expected number of mistakes at most $K(K-1)
+\lfloor (R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies
+of the \textsc{Binary Perceptron} algorithm, one copy for each class.
+Intuitively speaking, the factor $K(K-1)$ is the price we pay for the bandit
+feedback, or more precisely, the lack of full-information feedback.
 
@@
 exists for a set of strongly- and weakly-labeled examples is NP-complete. This
-result is a simple consequence of the fact learning intersection of halfspaces
-is NP-complete~\citep{Blum-Rivest-1993}. Second, we show that any algorithm that
-uses only strongly-labeled examples and ignores weakly labeled examples makes at
-least $\Omega(???)$ mistakes.
+result is a simple consequence of the fact that learning intersection of
+halfspaces is NP-complete~\citep{Blum-Rivest-1993}. Second, we show that any
+algorithm that uses only strongly-labeled examples and ignores weakly labeled
+examples makes at least $\Omega(???)$ mistakes.
 
@@
 integer, and let $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
-y_2), \dots, (x_T, y_T)$ labeled examples in $V \times \{1,2,\dots,K\}$.
+y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.
 
@@
 \end{center}
-\caption{The figure shows labeled examples in $\R^2$. The examples belong to
+\caption[]{The figure shows labeled examples in $\R^2$. The examples belong to
 $K=3$ classes colored white, gray and black respectively. Each class lies in a
-$120^\circ$ wedge. While the examples are linearly separable with a positive
-margin $\gamma$, they are \emph{not} strongly linearly separable for any
-positive margin $\gamma$.
+$120^\circ$ wedge. In other words, each class lies in an intersection of two
+halfspaces.
+
+While the examples are linearly separable with a positive margin $\gamma$, they
+are \emph{not} strongly linearly separable for any positive margin $\gamma$.
 }
@@
 \label{section:algorithm-for-strongly-linearly-separable-data}
+
+In this section, we present an algorithm for \textsc{Online Multiclass
+Classification with Bandit Feedback} and prove an upper bound on the number of
+mistakes under the assumption that the examples are strongly linearly separable
+with a margin. The algorithm is stated
+Algorithm~\eqref{algorithm:algorithm-for-strongly-linearly-separable-examples}
+below and the mistake upper bound is stated as
+\autoref{theorem:stronglys-separable-example-mistake-upper-bound}.
+
+The idea behind the algorithm is to use $K$ copies of the \textsc{Binary
+Perceptron} algorithm. Each copy corresponds to a class. In each round, each
+copy makes a binary decision whether the feature vector belongs their respective
+class or not. If at least one copy makes a positive prediction, the algorithm
+predicts accordingly. If multiple copies make positive predictions, the
+algorithm chooses one of them at random. If all copies make negative
+predictions, the algorithms makes a blind guess.
 
@@
 \begin{theorem}
+\label{theorem:stronglys-separable-example-mistake-upper-bound}
 Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
@@
 Let $C$ be the number of times line 16 gets executed. Let $U$ be the number of
-times line 16 or line 21 get executed. In other words, $U$ the number of times
-the weight vectors are updated. Clearly, $U = A + C$. We know that $U \le
-\frac{K} \lfloor (R/\gamma)^2 \rfloor$.
+times line 16 or line 21 get executed. In other words, $U$ is the number of
+times the weight vectors are updated. Clearly, $U = A + C$. We know that $U \le
+K \lfloor (R/\gamma)^2 \rfloor$.
 
-The key observation is that $\Exp[B] = (K-1) \Exp[C]$ since there the $1/K$
-probability that the algorithm guesses the correct label correctly if $S_t =
-\emptyset$. Putting all the information together, we get that
+The key observation is that $\Exp[B] = (K-1) \Exp[C]$ since if $S_t =
+\emptyset$, there is $1/K$ probability that the algorithm guesses the correct
+label correctly and $(K-1)/K$ probability that it guesses is incorrectly.
+Putting all the information together, we get that
 \begin{align*}

### 2018-11-20 arxiv-version/main.tex
Improve mistake bound by a factor K.

@@
 We design new algorithms for the problem of \textsc{Online Multiclass
-Classification with Bandit Feedback}. In this problem, in each round $t$, the
-algorithm receives a feature vector $x_t$ and algorithm has to predict one of
-$K$ possible classes. Imediately after the algorithm makes its prediction, it
+Classification with Bandit Feedback}. In this problem, in each round, the
+algorithm receives a feature vector and algorithm has to predict one of $K$
+possible classes. Imediately after the algorithm makes its prediction, it
 receives feedback whether the prediction was correct or not. However, in
 contrast with the standard, so called full information setting, the algorithm
-does \emph{not} receive the correct label. In other words, the feedback is
-purely binary (correct prediction or incorrect prediction). To allow for
-meaningful randomized strategies, we assume that the correct label for round $t$
-is chosen prior to algorithm's prediction in that round.\footnote{The reader can
-assume throughout the paper a simpler model of the so called \emph{oblivious
-adversary} where the whole sequence of labeled examples $(x_1, y_1), (x_2, y_2),
-\dots, (x_T, y_T)$ is chosen before the first round of the game.} The protocol
-of the problem is stated below.
+does \emph{not} receive the correct label. The feedback is only binary, correct
+prediction or incorrect prediction. To allow for meaningful randomized
+strategies, we assume that the correct label in a particular round is chosen
+prior to algorithm's prediction in that round.\footnote{The reader can assume
+throughout the paper a simpler model of the so called \emph{oblivious adversary}
+where the whole sequence of labeled examples $(x_1, y_1), (x_2, y_2), \dots,
+(x_T, y_T)$ is chosen before the first round of the game.} The protocol of the
+problem is stated below.
 
@@
 For the case when the examples are strongly linearly separable, we design a
-simple and efficient algorithm with expected number of mistakes at most $K(K-1)
+simple and efficient algorithm with expected number of mistakes at most $(K-1)
 \lfloor (R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies
 of the \textsc{Binary Perceptron} algorithm, one copy for each class.
-Intuitively speaking, the factor $K(K-1)$ is the price we pay for the bandit
-feedback, or more precisely, the lack of full-information feedback.
+Intuitively speaking, the factor $K-1$ is the price we pay for the bandit
+feedback, or more precisely, the lack of full-information feedback. We also
+prove that any algorithm makes $K \lfloor (R/\gamma)^2 \rfloor / ??$ in the
+worst case in this setting.
 
@@
 mistakes under the assumption that the examples are strongly linearly separable
-with a margin. The algorithm is stated
-Algorithm~\eqref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-below and the mistake upper bound is stated as
+with a margin. The algorithm is stated as
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
+the mistake upper bound is stated as
 \autoref{theorem:stronglys-separable-example-mistake-upper-bound}.
@@
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-makes is at most $K(K-1) \lfloor (R/\gamma)^2 \rfloor$ mistakes.
+makes is at most $(K-1) \lfloor (R/\gamma)^2 \rfloor$ mistakes.
 \end{theorem}
@@
 times line 16 or line 21 get executed. In other words, $U$ is the number of
-times the weight vectors are updated. Clearly, $U = A + C$. We know that $U \le
-K \lfloor (R/\gamma)^2 \rfloor$.
+times the weight vectors are updated. Clearly, $U = A + C$.
 
@@
 & \le (K-1) \Exp[A + C] \\
-& = (K-1) \Exp[U]  \\
-& \le K(K-1) \lfloor (R/\gamma)^2 \rfloor \; .
+& = (K-1) \Exp[U]  \; .
 \end{align*}
+
+To finish the proof, we need to upper bound the number of updates, $U$. We claim
+that $U \le \lfloor (R/\gamma)^2 \rfloor$. The proof of this upper bound is
+similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
+algorithm. Let $w_1^*, w_2^*, \dots, w_K^* \in V$ satisfy
+\eqref{equation:strong-linear-separability-1},
+\eqref{equation:strong-linear-separability-2} and
+\eqref{equation:strong-linear-separability-3}.
+The $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$
+changes only if there is an update in round $t$.
+We investigate how $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ and
+$\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$ change. If there is an update in round $t$,
+we have
+\begin{align*}
+\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
+& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t+1)}}^2 \\
+& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t}^2 \\
+& = \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 + \underbrace{(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t}}_{\le 0} \\
+& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 \\
+& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + R^2 \; .
+\end{align*}
+Therefore, after $U$ updates,
+$$
+\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
+$$
+Similarly, if there is an update in round $t$, we have
+\begin{align*}
+\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}
+& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
+& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
+& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
+& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \gamma
+\end{align*}
+where the last inequality follows from \eqref{equation:strong-linear-separability-2}
+and \eqref{equation:strong-linear-separability-3} and case analysis whether $z_t = 0$ or $z_t = 1$.
+Thus, after $U$ updates,
+$$
+\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma U \; .
+$$
+Applying Cauchy-Schwartz's inequality twice, we get that
+$$
+\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
+\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
+\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
+\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
+$$
+Combining the upper and lower bounds on $\sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}$ inequalities, we get
+$$
+(\gamma U)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
+$$
+We conclude that $U \le (R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor (R/\gamma)^2 \rfloor$.
 \end{proof}
@@
 \sum_{i=1}^K \ip{w_i^*}{w_i^{(t+1)}}
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus {y_t, \widehat y_t}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^*}{w_{y_t}^{(t)} + x_t} + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} - x_t} \\
+& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^*}{w_{y_t}^{(t)} + x_t} + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} - x_t} \\
 & = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^* - w_{\widehat y_t}^*}{x_t} \\

### 2018-11-20 arxiv-version/main.tex
Small fixes

@@
 contrast with the standard, so called full information setting, the algorithm
-does \emph{not} receive the correct label. The feedback is only binary, correct
-prediction or incorrect prediction. To allow for meaningful randomized
-strategies, we assume that the correct label in a particular round is chosen
-prior to algorithm's prediction in that round.\footnote{The reader can assume
-throughout the paper a simpler model of the so called \emph{oblivious adversary}
-where the whole sequence of labeled examples $(x_1, y_1), (x_2, y_2), \dots,
-(x_T, y_T)$ is chosen before the first round of the game.} The protocol of the
-problem is stated below.
+does \emph{not} receive the correct label. The feedback is only binary. To allow
+for meaningful randomized strategies, we assume that the correct label in a
+particular round is chosen prior to algorithm's prediction in that
+round.\footnote{The reader can assume throughout the paper a simpler model of
+the so called \emph{oblivious adversary} where the whole sequence of labeled
+examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is chosen before the first
+round of the game.} The protocol of the problem is stated below.
 
@@
 the intersection of the halfspaces. Strong linear separability means that
-examples from each class can be separated from the remaining examples by a
+examples from each class is separated from the remaining examples by a
 \emph{single} hyperplane. We state the definitions precisely in
@@
 
-\begin{definition}
+\begin{definition}[Linear separability]
 Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
@@
 Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$,
-$w_2' = \frac{w_2 - w_1}{2}$ and $\gamma'=\gamma/2$ satisfy
+\eqref{equation:linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$, $w_2' =
+\frac{w_2 - w_1}{2}$ and $\gamma'=\gamma/2$ satisfy
 \eqref{equation:strong-linear-separability-1},
 \eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3} since $\norm{w_i'}^2 \le
-(\frac{1}{2} \norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le \frac{1}{2}\norm{w_1}^2 +
-\frac{1}{2}\norm{w_2}^2$ for $i=1,2$.
+\eqref{equation:strong-linear-separability-3}. The last two conditions are easy
+to see. The first condition follows from $\norm{w_i'}^2 \le (\frac{1}{2}
+\norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le \frac{1}{2}\norm{w_1}^2 +
+\frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
 
@@
 While the examples are linearly separable with a positive margin $\gamma$, they
-are \emph{not} strongly linearly separable for any positive margin $\gamma$.
+are \emph{not} strongly linearly separable with any positive margin $\gamma$.
 }
@@
 the mistake upper bound is stated as
-\autoref{theorem:stronglys-separable-example-mistake-upper-bound}.
+\autoref{theorem:strongly-separable-example-mistake-upper-bound}.
 
@@
 
-\begin{theorem}
-\label{theorem:stronglys-separable-example-mistake-upper-bound}
+\begin{theorem}[Mistake upper bound]
+\label{theorem:strongly-separable-example-mistake-upper-bound}
 Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
@@
 Let $C$ be the number of times line 16 gets executed. Let $U$ be the number of
-times line 16 or line 21 get executed. In other words, $U$ is the number of
-times the weight vectors are updated. Clearly, $U = A + C$.
+times line 16 and line 21 get executed. In other words, $U$ is the number of
+times the $K$-tuple of vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets
+updated. Clearly, $U = A + C$.
 
@@
 \emptyset$, there is $1/K$ probability that the algorithm guesses the correct
-label correctly and $(K-1)/K$ probability that it guesses is incorrectly.
+label and with probability $(K-1)/K$ algorithm's guess is incorrect.
 Putting all the information together, we get that
@@
 similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
-algorithm. Let $w_1^*, w_2^*, \dots, w_K^* \in V$ satisfy
+algorithm. Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors that satisfy
 \eqref{equation:strong-linear-separability-1},
@@
 $$
-Applying Cauchy-Schwartz's inequality twice, we get that
+Applying Cauchy-Schwartz's inequality twice and assumption
+\eqref{equation:strong-linear-separability-1}, we get that
 $$
@@
 $$
-Combining the upper and lower bounds on $\sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}$ inequalities, we get
+Combining the upper and lower bounds on $\sum_{i=1}^K \norm{w_i^{(T+1)}}^2$ inequalities, we get
 $$
@@
 We conclude that $U \le (R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor (R/\gamma)^2 \rfloor$.
+\end{proof}
+
+\begin{theorem}[Mistake lower bound]
+\label{theorem:strongly-separable-example-mistake-lower-bound} Let $K$ be a
+positive integer, let $\gamma$ be a positive real number and let $R$ be a
+non-negative real number. For any algorithm for the \textsc{Online Multiclass
+Classification with Bandit Feedback} there exists an inner product space $(V,
+\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
+examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ examples in $V \times
+\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
+norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
+number mistakes the algorithm is at least $K \lfloor (R/\gamma)^2 \rfloor/ ??$.
+\end{theorem}
+
+\begin{proof}
+TODO
 \end{proof}
@@
 $R$ be a non-negative real number. For any deterministic algorithm for the
-\textsc{Full-Information Multiclass Classification} problem there exists an
+\textsc{Online Multiclass Classification} problem there exists an
 inner product space $(V, \ip{\cdot}{\cdot})$, a non-negative integer $T$ and a

### 2018-11-20 arxiv-version/main.tex
Start proof of lower bound

@@
 Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
-integer, $\gamma$ a positive real number, $R$ be a non-negative real number If
+integer, $\gamma$ a positive real number, $R$ be a non-negative real number. If
 $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
@@
 \begin{theorem}[Mistake lower bound]
-\label{theorem:strongly-separable-example-mistake-lower-bound} Let $K$ be a
-positive integer, let $\gamma$ be a positive real number and let $R$ be a
-non-negative real number. For any algorithm for the \textsc{Online Multiclass
-Classification with Bandit Feedback} there exists an inner product space $(V,
-\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ examples in $V \times
-\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
-norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
-number mistakes the algorithm is at least $K \lfloor (R/\gamma)^2 \rfloor/ ??$.
+\label{theorem:strongly-separable-example-mistake-lower-bound}
+Let $\gamma$ be a positive real number and let $R$ be a non-negative real
+number. For any algorithm for the \textsc{Online Multiclass Classification with
+Bandit Feedback} with $K \le \frac{1}{2}(R/\gamma)^2$ classes there exists an inner
+product space $(V, \ip{\cdot}{\cdot})$, a non-negative integer $T$ and a
+sequence of labeled examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$
+in $V \times \{1,2,\dots,K\}$ that are strongly linearly separable with
+margin $\gamma$, the norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T}
+\le R$ and the expected number of mistakes the algorithm makes is at least $K
+\lfloor \frac{1}{8} (R/\gamma)^2 \rfloor/ ??$.
 \end{theorem}
@@
 \begin{proof}
+Let $M = \lfloor \frac{1}{8} (R/\gamma)^2 \rfloor$. Let $V = \R^{M+1}$ equipped with the
+standard inner product.  Let $e_1, e_2, \dots, e_{M+1}$ be the standard
+orthonormal basis of $\R^{M+1}$. We define vectors $v_1, v_2, \dots, v_M \in V$
+where $v_i = \frac{R}{\sqrt{2}}(e_i + e_{M+1})$ for $i=1,2,\dots,M$. Let $\ell_1, \ell_2,
+\dots, \ell_M$ be chosen i.i.d. uniformly at random from $\{1,2,\dots,K\}$ and
+independently of any randomness used the by the algorithm.
+
+Let $T = M K$. We define examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ as
+follows:
+$$
+\begin{array}{lclclclcl}
+(x_1, y_1) & = & (x_2, y_2) & = & \cdots & = & (x_K, y_K) & = & (v_1, \ell_1) \; , \\
+(x_{K+1},y_{K+1}) & = & (x_{K+2}, y_{K+2}) & = & \cdots & = & (x_{2K}, y_{2K}) & = & (v_2, \ell_2) \; , \\
+& \vdots & \\
+(x_{(M-1)K+1}, y_{(M-1)K+1})  & = & (x_{(M-1)K+2}, y_{(M-1)K+2}) & = & \cdots & = & (x_{MK}, y_{MK}) & = & (v_M, \ell_M) \; .
+\end{array}
+$$
+
+Clearly, norm of each example is $R$. We show that the examples are strongly
+separable with margin $\gamma$. In order to see that consider $w_1^*, w_2^*,
+\dots, w_K^* \in V$ defined by
+$$
+w_i^* = 2 \frac{\gamma}{R} \left( \sum_{j ~:~ \ell_j = i} e_j \right) - \frac{\gamma}{R} e_{M+1} \qquad \quad \text{for $i=1,2,\dots,K$.}
+$$
+Since for any $i \in \{1,2,\dots,K\}$ and any $j \in \{1,2,\dots,M\}$,
+$$
+\ip{w_i^*}{v_j} =
+\begin{cases}
+\gamma & \text{if $\ell_j = i$,} \\
+- \gamma & \text{if $\ell_j \neq i$,}
+\end{cases}
+$$
+it means that $w_1^*, w_2^*, \dots, w_K^*$ satisfy
+\eqref{equation:strong-linear-separability-2} and
+\eqref{equation:strong-linear-separability-3}. Condition \eqref{equation:strong-linear-separability-1}
+is satisfied since
+$$
+\sum_{i=1}^K \norm{w_i^*}^2
+= 4 \frac{\gamma^2}{R^2} \sum_{j=1}^M \norm{e_j}^2 + \frac{\gamma^2}{R^2} K \norm{e_{M+1}}^2
+= 4\frac{\gamma^2}{R^2} M + \frac{\gamma^2}{R^2} K
+\le \frac{1}{2} + \frac{1}{2}
+= 1 \; .
+$$
+
+It remains to show that the expected number of mistakes the algorithm makes is
+at least $K M / ??$.
+
 TODO

### 2018-11-21 arxiv-version/main.tex
Finish lower bound proof

@@
 Classification with Bandit Feedback}. In this problem, in each round, the
-algorithm receives a feature vector and algorithm has to predict one of $K$
+algorithm receives a feature vector and the algorithm has to predict one of $K$
 possible classes. Imediately after the algorithm makes its prediction, it
@@
 feedback, or more precisely, the lack of full-information feedback. We also
-prove that any algorithm makes $K \lfloor (R/\gamma)^2 \rfloor / ??$ in the
-worst case in this setting.
+prove that any (possibly randomized) algorithm makes $\Omega(K (R/\gamma)^2))$
+mistakes in the worst case.
 
@@
 first notion is the standard notion of linear separability used in the proof of
-mistake bound for the \textsc{Multiclass Perceptron} algorithm. The second
+the mistake bound for the \textsc{Multiclass Perceptron} algorithm. The second
 notion is stronger, i.e. more restrictive. However, it is more suitable for the
@@
 \ELSE
-\STATE{Predict $\widehat y_t \sim \text{Uniform}(S_t)$}
+\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
 \ENDIF
@@
 number. For any algorithm for the \textsc{Online Multiclass Classification with
-Bandit Feedback} with $K \le \frac{1}{2}(R/\gamma)^2$ classes there exists an inner
+Bandit Feedback} with $K \le \frac{1}{4}(R/\gamma)^2$ classes there exists an inner
 product space $(V, \ip{\cdot}{\cdot})$, a non-negative integer $T$ and a
@@
 margin $\gamma$, the norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T}
-\le R$ and the expected number of mistakes the algorithm makes is at least $K
-\lfloor \frac{1}{8} (R/\gamma)^2 \rfloor/ ??$.
+\le R$ and the expected number of mistakes the algorithm makes is at least $\frac{K-1}{2}
+\lfloor \frac{1}{16} (R/\gamma)^2 \rfloor$.
 \end{theorem}
@@
 \begin{proof}
-Let $M = \lfloor \frac{1}{8} (R/\gamma)^2 \rfloor$. Let $V = \R^{M+1}$ equipped with the
-standard inner product.  Let $e_1, e_2, \dots, e_{M+1}$ be the standard
-orthonormal basis of $\R^{M+1}$. We define vectors $v_1, v_2, \dots, v_M \in V$
-where $v_i = \frac{R}{\sqrt{2}}(e_i + e_{M+1})$ for $i=1,2,\dots,M$. Let $\ell_1, \ell_2,
-\dots, \ell_M$ be chosen i.i.d. uniformly at random from $\{1,2,\dots,K\}$ and
-independently of any randomness used the by the algorithm.
-
-Let $T = M K$. We define examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ as
-follows:
+We use probabilistic method. Let $M = \lfloor \frac{1}{16} (R/\gamma)^2 \rfloor$.
+Let $V = \R^{M+1}$ equipped with the standard inner product.  Let $e_1, e_2,
+\dots, e_{M+1}$ be the standard orthonormal basis of $V$. We define
+vectors $v_1, v_2, \dots, v_M \in V$ where $v_i = \frac{R}{\sqrt{2}}(e_i +
+e_{M+1})$ for $i=1,2,\dots,M$. Let $\ell_1, \ell_2, \dots, \ell_M$ be chosen
+i.i.d. uniformly at random from $\{1,2,\dots,K\}$ and independently of any
+randomness used the by the algorithm. Let $T = M K$. We define examples $(x_1,
+y_1), (x_2, y_2), \dots, (x_T, y_T)$ as follows:
 $$
@@
 
-Clearly, norm of each example is $R$. We show that the examples are strongly
-separable with margin $\gamma$. In order to see that consider $w_1^*, w_2^*,
-\dots, w_K^* \in V$ defined by
+With probability one, norm of each example is $R$. We show that with probability
+one, the examples are strongly separable with margin $\gamma$. In order to see
+that consider $w_1^*, w_2^*, \dots, w_K^* \in V$ defined by
 $$
-w_i^* = 2 \frac{\gamma}{R} \left( \sum_{j ~:~ \ell_j = i} e_j \right) - \frac{\gamma}{R} e_{M+1} \qquad \quad \text{for $i=1,2,\dots,K$.}
+w_i^* = 2 \sqrt{2} \frac{\gamma}{R} \left( \sum_{j ~:~ \ell_j = i} e_j \right) - \sqrt{2} \frac{\gamma}{R} e_{M+1} \qquad \quad \text{for $i=1,2,\dots,K$.}
 $$
@@
 \sum_{i=1}^K \norm{w_i^*}^2
-= 4 \frac{\gamma^2}{R^2} \sum_{j=1}^M \norm{e_j}^2 + \frac{\gamma^2}{R^2} K \norm{e_{M+1}}^2
-= 4\frac{\gamma^2}{R^2} M + \frac{\gamma^2}{R^2} K
+= 8 \frac{\gamma^2}{R^2} \sum_{j=1}^M \norm{e_j}^2 + 2 \frac{\gamma^2}{R^2} K \norm{e_{M+1}}^2
+= 8 \frac{\gamma^2}{R^2} M + 2 \frac{\gamma^2}{R^2} K
 \le \frac{1}{2} + \frac{1}{2}
@@
 
-It remains to show that the expected number of mistakes the algorithm makes is
-at least $K M / ??$.
+It remains to lower bound the expected number of mistakes of the algorithm. For
+any $j \in \{1,2,\dots,M\}$, consider the expected number of mistakes the
+algorithm makes in rounds $K(j-1) + 1, K(j-1) + 2, \dots, Kj$. In these rounds,
+the algorithm is guessing the label $\ell_j$. Since $\ell_j$ is chosen uniformly
+at random from the set $\{1,2,\dots,K\}$ and feedback is only binary, the
+expected number of mistakes the algorithm makes in these rounds is at least
+$\frac{K-1}{2}$. Altogether, the algorithm makes at least $\frac{K-1}{2} M$
+mistakes in expectation.
 
-TODO
+Finally, since strong separability and norm condition hold with probability one,
+there exists a particular (i.e. deterministic) sequence of examples for which
+the algorithm makes at least $\frac{K-1}{2} M$ mistakes.
 \end{proof}

### 2018-11-21 arxiv-version/main.tex
Start the NP-hardness section

@@
 
+Any algorithm for the bandit setting collects information in the form of so
+called \emph{strongly labeled} and \emph{weakly labeled} examples.
+Strongly-labeled examples are those for which we know the class label. Weakly
+labeled example is an example for which we know that class label can be anything
+except for a particular one class.
+
+A natural strategy for each round is to find vectors $w_1, w_2, \dots, w_K$ that
+linearly separate the examples see in previous rounds and use the vectors to
+predict label in the next round. More precisely, we want to find both the
+vectors $w_1, w_2, \dots, w_K$ and label for each exaple consistent with its
+weak and/or strong labels such that $w_1, w_2, \dots, w_K$ linearly separate the
+labeled examples. We show this problem is NP-hard even for $K=3$.
+
+Clearly, the problem is at least as hard as the decision version of the problem
+where the goal is to determine if such vectors and labeling exist. We show that
+this problem is NP-complete.
+
+Formally, the input to the decision problem are positive integers $d, T, K$ and
+a sequence $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \{0,1\}^d \times
+\{1,2,\dots,K, \overline{1}, \overline{2}, \dots, \overline{K}\}$ of strongly
+and weakly labeled examples. The numbers $1,2,\dots,K$ correspond to strong
+labels and the symbols $\overline{1}, \overline{2}, \dots, \overline{K}$
+correspond to weak labels. We adopt the convention that $\overline{\overline{i}}
+= i$ for any positive integer $i$. The goal is to determine whether or not there
+exist vectors $w_1, w_2, \dots, w_K \in \R^d$ that satisfy the following
+conditions for all $t=1,2,\dots,T$,
+\begin{align*}
+y_t \in \{1,2,\dots,K\} \qquad & \Longrightarrow \qquad & \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \qquad \ip{w_{y_t}}{x_t} & > \ip{w_i}{x_t} \; , \\
+y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \qquad & \Longrightarrow & \qquad \exists i \in \{1,2,\dots,K\} \qquad \ip{w_i}{x_t} & > \ip{w_{\overline{y_t}}}{x_t} \; .
+\end{align*}
+
 TODO

### 2018-11-25 arxiv-version/main.tex
Add references and start another section

@@
 algorithm receives a feature vector and the algorithm has to predict one of $K$
-possible classes. Imediately after the algorithm makes its prediction, it
+possible classes. Immediately after the algorithm makes its prediction, it
 receives feedback whether the prediction was correct or not. However, in
@@
 \label{section:related-work}
+
+\cite{Abernethy-Rakhlin-2009}
+
+\cite{Hazan-Kale-2011}
+
+\cite{Foster-Krishnamurthy-2018}
 
@@
 \section{Converting linear separability to strong linear separability}
+\label{section:converting-linear-separability-to-strong-linear-separability}
 
+In this section, we show how construct a mapping $\phi$ of points in the unit
+ball $B_d$ of $\R^d$ into a high dimensional inner product space that has the
+property if any set of labeled examples in $B_d$ is linearly separable with a
+margin $\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
+linearly separable with a margin $\gamma'$ and their norms are bounded by $R'$.
+The parameters $\gamma'$ and $R'$ are functions of the old margin $\gamma$ and
+the number of classes $K$, and the are specified in the theorems below.
+
+Equipped with the mapping $\phi$, we can utilize
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
+\autoref{theorem:strongly-separable-example-mistake-upper-bound} from the
+previous section and we obtain an algorithm for linearly separable examples and
+an upper bound on its number of mistakes. As a computational speed up, instead
+of working with the mapped examples $\phi(x_1), \phi(x_2), \dots$ explicitly, we
+can use the kernelized version of
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
+that uses a kernel function $k(x,x') = \ip{\phi(x)}{\phi(x')}$.
+
+We construct several different mappings $\phi$. The parameters $R'$ and
+$\gamma'$ for the different mappings are essentially the same. However, one
+mapping has the advantage of having a kernel $k(x,x')$ that is faster to
+evaluate. Another mapping has the advantage that one does \emph{not} need to
+know the initial margin $\gamma$. In other words, the same mapping works for all
+possible values of $\gamma > 0$. The idea behind all the mappings is that
+polynomials are universal function approximators, which is a well known fact
+expressed by the classical Stone-Weierstrass theorem~\citep[page 159]{Rudin-1976}.
+
+\subsection{Polynomials}
+TODO
+
+\subsection{Rational Kernel}
 TODO
@@
 A natural strategy for each round is to find vectors $w_1, w_2, \dots, w_K$ that
-linearly separate the examples see in previous rounds and use the vectors to
-predict label in the next round. More precisely, we want to find both the
-vectors $w_1, w_2, \dots, w_K$ and label for each exaple consistent with its
+linearly separate the examples seen in the previous rounds and use the vectors
+to predict the label in the next round. More precisely, we want to find both the
+vectors $w_1, w_2, \dots, w_K$ and label for each example consistent with its
 weak and/or strong labels such that $w_1, w_2, \dots, w_K$ linearly separate the
@@
 It remains to show that the examples we have constructed are linearly separable
-with margin $\gamma$. To prove that we demostrate vectors $w_1, w_2, \dots, w_K$
+with margin $\gamma$. To prove that we demonstrate vectors $w_1, w_2, \dots, w_K$
 satisfying conditions \eqref{equation:linear-separability-1} and
@@
 $$
-Let $a_i = |\{ t ~:~ 1 \le t \le T, \ y_t = i \}|$ be the number of occurences of label $i$.
+Let $a_i = |\{ t ~:~ 1 \le t \le T, \ y_t = i \}|$ be the number of occurrences of label $i$.
 It is easy to see that

### 2018-11-26 arxiv-version/main.tex
State the polynomial approximation theorem

@@
 \newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
+%\DeclareMathOperator*{\deg}{deg}
 \DeclareMathOperator*{\argmax}{argmax}
@@
 We construct several different mappings $\phi$. The parameters $R'$ and
-$\gamma'$ for the different mappings are essentially the same. However, one
-mapping has the advantage of having a kernel $k(x,x')$ that is faster to
-evaluate. Another mapping has the advantage that one does \emph{not} need to
-know the initial margin $\gamma$. In other words, the same mapping works for all
-possible values of $\gamma > 0$. The idea behind all the mappings is that
-polynomials are universal function approximators, which is a well known fact
-expressed by the classical Stone-Weierstrass theorem~\citep[page 159]{Rudin-1976}.
+$\gamma'$ for the different mappings are not the same, but the ratios
+$R'/\gamma'$ are qualitively the same. However, one mapping has the advantage of
+having a kernel $k(x,x')$ that is faster to evaluate. Another mapping has the
+advantage that one does \emph{not} need to know the initial margin $\gamma$. In
+other words, the same mapping works for all possible values of $\gamma > 0$.
+
+The idea behind all the mappings is that, on a compact set, multivariate
+polynomials uniformly approximate any continuous function. This is result is a
+special case of the well known Stone-Weierstrass theorem~\citep[Section
+10.10]{Davidson-Donsig-2010}. In our case, we use a multivariate polynomial to
+approximate the indicator function corresponding to the intersection of $K-1$
+halfspaces. This polynomial separates examples in one class from examples in the
+other classes. To be able to quantify $\gamma'$ and $R'$ as well as time
+complexity of evaluating $k(x,x')$ we need to quantify certain parameters
+of the approximating polynomial (degree, norm, range of values).
+The parameters are quantified in \autoref{theorem:polynomial-approximation}
+stated below.
+
+Before we state the theorem, recall that a polynomial of $d$ variables is a
+function $p:\R^d \to \R$ of the form
+$$
+p(x) = p(x_1, x_2, \dots, x_d) = \sum_{i_1, i_2, \dots, i_d} c_{i_1, i_2, \dots, i_d} x_1^{i_1} x_2^{i_2} \dots x_d^{i_d}
+$$
+where the sum ranges over a finite set of tuples $(i_1, i_2, \dots, i_d)$ of
+non-negative integers and $c_{i_1, i_2, \dots, i_d}$ is a real coefficient. The
+\emph{degree} of a polynomial $p$, denoted by $\deg(p)$, is the largest value of
+$i_1 + i_2 + \dots + i_d$ for which the coefficient is non-zero. The \emph{norm
+of a polynomial} $p$ is defined as
+$$
+\norm{p} = \sqrt{\sum_{i_1, i_2, \dots, i_d} \left(c_{i_1, i_2, \dots, i_d} \right)^2 } \; .
+$$
+
+\begin{theorem}
+\label{theorem:polynomial-approximation}
+Let $w_1, w_2, \dots, w_K \in \R^d$ be such that $\sum_{i=1}^K \norm{w_1}^2 \le 1$.
+Let $\gamma > 0$. There exists a polynomial $p:\R^d \to \R$ such that
+\begin{itemize}
+\item $p(x) \ge 1$ for all $x \in \bigcap_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \ge \ip{w_i}{x} + \gamma \}$
+\item $p(x) \le -1$ for all $x \in \bigcup_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \le \ip{w_i}{x} - \gamma \}$
+\item $\deg(p) \le ???$
+\item $\norm{p} \le ???$
+\item $|p(x)| \le ???$ for all $x \in \R^d$ such that $\norm{x} \le 1$
+\end{itemize}
+\end{theorem}
 

### 2018-11-27 arxiv-version/main.tex
Improve intro, add a reference

@@
 does \emph{not} receive the correct label. The feedback is only binary. To allow
-for meaningful randomized strategies, we assume that the correct label in a
+for meaningful use of randomization, we assume that the correct label in a
 particular round is chosen prior to algorithm's prediction in that
@@
 the intersection of the halfspaces. Strong linear separability means that
-examples from each class is separated from the remaining examples by a
+examples from each class are separated from the remaining examples by a
 \emph{single} hyperplane. We state the definitions precisely in
@@
 
-For the standard notion of linear separability, we propose three algorithms with
-various time-complexity-versus-mistake-bound trade-offs. Two of these algorithms
-map the examples into a high-dimensional inner product space induced by a
-kernel. In this space the examples become \emph{strongly} linearly separable.
-This allows us to run a kernelized version of the algorithm for the strongly
-linearly separable case.
+For the standard notion of linear separability, we propose several algorithms
+with various time-complexity-versus-mistake-bound trade-offs. First class of
+algorithms map the examples into a high-dimensional inner product space. In this
+space the examples become \emph{strongly} linearly separable. This allows us to
+run the algorithm for the strongly linearly separable case. All of these
+algorithms can be kernelized. (Some of them have to be kernalized since the
+underlying inner product space is infinite dimensional.) Kernelization does not
+change the input-output behavior of the algorithm, it only affects its time
+complexity.
 
-The two kernel-based algorithms differ by the choice of the kernel. The crux of
-the problem is the analysis of the approximation properties of these kernels and
-the way margin in original space under standard linear separability notion gets
-transformed into a margin in the high-dimensional space under the strong
-separability notion. This problem is related to the problem of learning
-intersection of halfspaces and has been studied previously by
-\cite{Klivans-Servedio-2008}.
+These algorithms differ by choice of the mapping or, equivalently, choice of the
+kernel. The crux of the problem is the analysis of the approximation properties
+of these mappings/kernels and the way margin in original space under standard
+linear separability notion gets transformed into a margin in the
+high-dimensional space under the strong separability notion. This problem is
+related to the problem of learning intersection of halfspaces and has been
+studied previously by \cite{Klivans-Servedio-2008}.
 
-The third algorithm is based on the obvious idea that two points that are close
-enough must have the same label. Here, close enough means that they cannot be
-separated from each other by a linear separator with a margin.
+Finally, we propose a very different algorithm that is based on the obvious idea
+that two points that are close enough must have the same label. Here, close
+enough means that they cannot be separated from each other by a linear separator
+with a margin.
 
-All three algorithms run in time that is polynomial in the dimension of the
+All the algorithms run in time that is polynomial in the dimension of the
 feature vectors, the number of classes and the number of rounds. At the same
-time, all three algorithms make number of mistakes that does \emph{not} depend
+time, all the algorithms make number of mistakes that does \emph{not} depend
 on the number of rounds. Instead, their number of mistakes depends only on the
@@
 know that class label can be anything except for a particular one class. First,
-we show the offline problem of determining if a linear multiclass separator
-exists for a set of strongly- and weakly-labeled examples is NP-complete. This
-result is a simple consequence of the fact that learning intersection of
-halfspaces is NP-complete~\citep{Blum-Rivest-1993}. Second, we show that any
-algorithm that uses only strongly-labeled examples and ignores weakly labeled
-examples makes at least $\Omega(???)$ mistakes.
+we show the offline problem of finding a linear multiclass separator consistent
+with the strongly- and weakly-labeled examples is NP-hard. This result is a
+simple consequence of the fact that finding an intersection of two halfspaces
+consistent with binary-labeled examples is NP-hard~\citep{Blum-Rivest-1993}.
+Second, we show that any algorithm that uses only strongly-labeled examples and
+ignores weakly labeled examples makes at least $\Omega(???)$ mistakes.
 
@@
 
-\cite{Abernethy-Rakhlin-2009}
+\begin{itemize}
+\item \cite{Abernethy-Rakhlin-2009}
 
-\cite{Hazan-Kale-2011}
+\item \cite{Hazan-Kale-2011}
 
-\cite{Foster-Krishnamurthy-2018}
+\item \cite{Beygelzimer-Orabona-Zhang-2017}
+
+\item \cite{Foster-Krishnamurthy-2018}
+\end{itemize}
 

### 2018-11-27 arxiv-version/main.tex
Add proposition about Chebyshev polynomials

@@
 special case of the well known Stone-Weierstrass theorem~\citep[Section
-10.10]{Davidson-Donsig-2010}. In our case, we use a multivariate polynomial to
+10.10]{Davidson-Donsig-2010}. In our case, we use a multivariate polynomials to
 approximate the indicator function corresponding to the intersection of $K-1$
@@
 of the approximating polynomial (degree, norm, range of values).
-The parameters are quantified in \autoref{theorem:polynomial-approximation}
+The parameters are quantified in \autoref{theorem:polynomial-approximation-1}
+and \autoref{theorem:polynomial-approximation-2}
 stated below.
@@
 
-\begin{theorem}
-\label{theorem:polynomial-approximation}
+\begin{theorem}[Polynomial approximation of intersection of halfspaces (1)]
+\label{theorem:polynomial-approximation-1}
 Let $w_1, w_2, \dots, w_K \in \R^d$ be such that $\sum_{i=1}^K \norm{w_1}^2 \le 1$.
@@
 
-\subsection{Polynomials}
+\begin{theorem}[Polynomial approximation of intersection of halfspaces (2)]
+\label{theorem:polynomial-approximation-2}
+Let $w_1, w_2, \dots, w_K \in \R^d$ be such that $\sum_{i=1}^K \norm{w_1}^2 \le 1$.
+Let $\gamma > 0$. There exists a polynomial $p:\R^d \to \R$ such that
+\begin{itemize}
+\item $p(x) \ge 1$ for all $x \in \bigcap_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \ge \ip{w_i}{x} + \gamma \}$
+\item $p(x) \le -1$ for all $x \in \bigcup_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \le \ip{w_i}{x} - \gamma \}$
+\item $\deg(p) \le ???$
+\item $\norm{p} \le ???$
+\item $|p(x)| \le ???$ for all $x \in \R^d$ such that $\norm{x} \le 1$
+\end{itemize}
+\end{theorem}
+
+The proofs of the theorems can be found in
+Sections~\ref{section:proof-of-polynomial-approximation-1}~and~\ref{section:proof-of-polynomial-approximation-2}
+respectively.
+
+\subsection{Proof of \autoref{theorem:polynomial-approximation-1}}
+\label{section:proof-of-polynomial-approximation-1}
 TODO
+
+\subsection{Proof of \autoref{theorem:polynomial-approximation-2}}
+\label{section:proof-of-polynomial-approximation-2}
+
+To construct the polynomial $p$ we use Chebyshev polynomials of the first kind.
+Chebyshev polynomials of the fist kind form an infinite sequence of polynomials
+$T_0(z), T_1(z), T_2(z), \dots$ of single real variable $z$. They are defined
+by recurrence
+\begin{align*}
+T_0(z) & = 1 \; , \\
+T_1(z) & = z \; , \\
+T_{n+1}(z) & = 2zT_n(z) - T_{n-1}(z) & \text{for $n \ge 1$.}
+\end{align*}
+
+\begin{proposition}
+Chebyshev polynomials satisfy for any $n \ge 0$
+\begin{enumerate}
+\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$.
+\item If $z > 1$ then $T_n(z) \ge 1 + n^2(z - 1)$.
+\item Absolute value of all coefficients of $T_n(z)$ is at most $2^n$.
+\end{enumerate}
+\end{proposition}
 

### 2018-11-27 arxiv-version/main.tex
Almost finish properties of Chebyshev polynomials

@@
 \DeclareMathOperator*{\Exp}{\mathbf{E}}  % expected value
+\DeclareMathOperator{\diff}{d \!} % differential
 
@@
 In this section, we show how construct a mapping $\phi$ of points in the unit
-ball $B_d$ of $\R^d$ into a high dimensional inner product space that has the
-property if any set of labeled examples in $B_d$ is linearly separable with a
+ball of $\R^d$ into a high dimensional inner product space that has the
+property if any set of labeled examples in the unit ball is linearly separable with a
 margin $\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
@@
 The idea behind all the mappings is that, on a compact set, multivariate
-polynomials uniformly approximate any continuous function. This is result is a
-special case of the well known Stone-Weierstrass theorem~\citep[Section
-10.10]{Davidson-Donsig-2010}. In our case, we use a multivariate polynomials to
-approximate the indicator function corresponding to the intersection of $K-1$
-halfspaces. This polynomial separates examples in one class from examples in the
-other classes. To be able to quantify $\gamma'$ and $R'$ as well as time
-complexity of evaluating $k(x,x')$ we need to quantify certain parameters
-of the approximating polynomial (degree, norm, range of values).
-The parameters are quantified in \autoref{theorem:polynomial-approximation-1}
-and \autoref{theorem:polynomial-approximation-2}
-stated below.
+polynomials uniformly approximate any continuous function. This result is a
+special case of the well known Stone-Weierstrass theorem; see
+e.g.~\citep[Section~10.10]{Davidson-Donsig-2010}. In our case, we use
+multivariate polynomials to approximate the indicator function corresponding to
+the intersection of $K-1$ halfspaces. This polynomial separates examples in one
+class from examples in the other classes. To be able to quantify $\gamma'$ and
+$R'$ as well as time complexity of evaluating $k(x,x')$ we need to quantify
+certain parameters of the approximating polynomial (degree, norm, range of
+values). The parameters are quantified in
+\autoref{theorem:polynomial-approximation-1} and
+\autoref{theorem:polynomial-approximation-2} stated below.
 
@@
 
-\begin{theorem}[Polynomial approximation of intersection of halfspaces (1)]
+\begin{theorem}[Polynomial approximation of intersection of halfspaces I]
 \label{theorem:polynomial-approximation-1}
-Let $w_1, w_2, \dots, w_K \in \R^d$ be such that $\sum_{i=1}^K \norm{w_1}^2 \le 1$.
+Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1}, \norm{v_2}, \dots, \norm{v_m} \le 1$.
 Let $\gamma > 0$. There exists a polynomial $p:\R^d \to \R$ such that
-\begin{itemize}
-\item $p(x) \ge 1$ for all $x \in \bigcap_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \ge \ip{w_i}{x} + \gamma \}$
-\item $p(x) \le -1$ for all $x \in \bigcup_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \le \ip{w_i}{x} - \gamma \}$
+\begin{enumerate}
+\item $p(x) \ge 1$ for all $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
+\item $p(x) \le -1$ for all $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
 \item $\deg(p) \le ???$
@@
 \item $|p(x)| \le ???$ for all $x \in \R^d$ such that $\norm{x} \le 1$
-\end{itemize}
+\end{enumerate}
 \end{theorem}
 
-\begin{theorem}[Polynomial approximation of intersection of halfspaces (2)]
+\begin{theorem}[Polynomial approximation of intersection of halfspaces II]
 \label{theorem:polynomial-approximation-2}
-Let $w_1, w_2, \dots, w_K \in \R^d$ be such that $\sum_{i=1}^K \norm{w_1}^2 \le 1$.
+Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1}, \norm{v_2}, \dots, \norm{v_m} \le 1$.
 Let $\gamma > 0$. There exists a polynomial $p:\R^d \to \R$ such that
-\begin{itemize}
-\item $p(x) \ge 1$ for all $x \in \bigcap_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \ge \ip{w_i}{x} + \gamma \}$
-\item $p(x) \le -1$ for all $x \in \bigcup_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \le \ip{w_i}{x} - \gamma \}$
+\begin{enumerate}
+\item $p(x) \ge 1/2$ for all $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
+\item $p(x) \le -1/2$ for all $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
 \item $\deg(p) \le ???$
@@
 \item $|p(x)| \le ???$ for all $x \in \R^d$ such that $\norm{x} \le 1$
-\end{itemize}
+\end{enumerate}
 \end{theorem}
@@
 $T_0(z), T_1(z), T_2(z), \dots$ of single real variable $z$. They are defined
-by recurrence
+by the recurrence
 \begin{align*}
@@
 \end{align*}
+Chebyshev polynomials have a lot of interesting properties.
+We will need properties listed in
+\autoref{proposition:properties-of-chebyshev-polynomials} below.
+Interested reader can learn more about Chebyshev polynomials
+from the book by \cite{Mason-Handscomb-2002}.
 
-\begin{proposition}
-Chebyshev polynomials satisfy for any $n \ge 0$
+\begin{proposition}[Properties of Chebyshev polynomials]
+\label{proposition:properties-of-chebyshev-polynomials}
+Chebyshev polynomials satisfy
 \begin{enumerate}
-\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$.
-\item If $z > 1$ then $T_n(z) \ge 1 + n^2(z - 1)$.
-\item Absolute value of all coefficients of $T_n(z)$ is at most $2^n$.
+\item $\deg(T_n) = n$ for all $n \ge 0$.
+\item If $n \ge 1$, the leading coefficient of $T_n(z)$ is $2^{n-1}$.
+\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$ and all $n \ge 0$.
+\item $T_n(z) \ge 1 + n^2(z - 1)$ for all $z \ge 1$ and all $n \ge 0$.
+\item All coefficients of $T_n(z)$ lie in the interval $\left[-(1+\sqrt{2})^n, (1+\sqrt{2})^n \right]$.
 \end{enumerate}
 \end{proposition}
+
+\begin{proof}[Proof of \autoref{proposition:properties-of-chebyshev-polynomials}]
+The first two proprties easily follow from the recurrence.
+
+The third property is a direct consequence of
+\begin{equation}
+\label{equation:trigonometric-chebyshev}
+T_n(\cos(\theta)) = \cos(n \theta) \qquad \quad \text{for all $\theta \in \R$.}
+\end{equation}
+since for any $x \in [-1,1]$ there exists $\theta \in \R$ such that $\cos(\theta) = x$.
+Equation \eqref{equation:trigonometric-chebyshev} is proved by induction on $n$. Indeed, by definition
+$$
+T_0(\cos(\theta)) = 1 = \cos(0 \theta) \qquad \text{and} \qquad T_1(\cos(\theta)) = \cos(\theta) \; .
+$$
+For $n \ge 1$, we have
+\begin{align*}
+T_{n+1}(\cos(\theta))
+& = 2 \cos(\theta) T_n(\cos(\theta)) - T_{n-1}(\cos(\theta)) \\
+& = 2 \cos(\theta) \cos(n \theta) - \cos((n-1)\theta)) \; ,
+\end{align*}
+where the last step follow by induction hypothesis.
+It remains to show that the last expression equals $\cos((n+1)\theta)$.
+This can be derived from the trigonometric formula
+$$
+\cos(\alpha \pm \beta) = \cos(\alpha) \cos(\beta) \mp \sin(\alpha) \sin(\beta) \; .
+$$
+By substituting $\alpha = n \theta$ and $\beta = \theta$, we get two equations
+\begin{align*}
+\cos((n+1) \theta) & = \cos(n \theta) \cos(\theta) - \sin(n \theta) \sin(\theta) \; , \\
+\cos((n-1) \theta) & = \cos(n \theta) \cos(\theta) + \sin(n \theta) \sin(\theta) \; .
+\end{align*}
+Summing them yields
+$$
+\cos((n+1)\theta) + \cos((n-1) \theta) = 2 \cos(n \theta) \cos(\theta)
+$$
+which finishes the proof of equation \eqref{equation:trigonometric-chebyshev}.
+
+To verify the fourth property we first show that
+\begin{equation}
+\label{equation:hyperbolic-chebyshev}
+T_n(\cosh(\theta)) = \cosh(n \theta) \qquad \quad \text{for all $\theta \in \R$.}
+\end{equation}
+The proof of equation~\eqref{equation:hyperbolic-chebyshev} is the same
+as the proof of equation \eqref{equation:trigonometric-chebyshev} except
+that we replace $\cos$ and $\sin$ with $\cosh$ and $\sinh$ respectively.
+
+Note that $\cosh(\theta) = \frac{e^{\theta} + e^{-\theta}}{2}$ is an even
+continuous function that maps $\R$ onto $[1,+\infty)$, is strictly decreasing
+on $(-\infty,0]$, and is strictly increasing on $[0,\infty)$. Thus the fourth
+property is equivalent to
+$$
+T_n(\cosh(\theta)) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for any $\theta \ge 0$.}
+$$
+For $\theta = 0$, according to \eqref{equation:hyperbolic-chebyshev} both sides
+are equal to $1$. The proof will be finished, if we prove that the derivative of
+the left hand side is greater or equal to the derivative of the right hand side.
+That is, we need to prove that
+\begin{equation}
+\label{equation:hyperbolic-chebyshev-derivative-inequality}
+\frac{\diff T_n(\cosh(\theta))}{\diff \theta} \ge \frac{\diff (1 + n^2 (\cosh(\theta) - 1))}{\diff \theta} \qquad \text{for any $\theta \ge 0$.}
+\end{equation}
+Using \eqref{equation:hyperbolic-chebyshev} and recalling that $\diff \cosh(\theta) / \diff \theta = \sinh(\theta)$ we
+can express the derivatives as
+\begin{align*}
+\frac{\diff T_n(\cosh(\theta))}{\diff \theta} & = \frac{\diff \cosh(n \theta))}{\diff \theta} = n \sinh(n \theta) \; , \\
+\frac{\diff (1 + n^2 (\cosh(\theta) - 1))}{\diff \theta} & = n^2 \sinh(\theta) \; .
+\end{align*}
+TODO
+
+To verify the fifth property let $a_n$ be the magnitude of the largest
+coefficient of $T_n(z)$. The recurrence for Chebyshev polynomials
+implies that the sequence $a_0, a_1, a_2, \dots$ satisfies
+\begin{align*}
+a_0 & = a_1 = 1 \; , \\
+a_{n+1} & \le 2 a_n + a_{n-1} & \text{for $n \ge 1$.}
+\end{align*}
+It remains to show that $a_n \le (1 + \sqrt{2})^n$ for all $n \ge 0$. We do this
+by induction on $n$. For $n=0$ and $n=1$ the inequality trivially holds. For $n
+\ge 1$, we have
+\begin{align*}
+a_{n+1} \le 2 a_n + a_{n-1}
+& \le 2 (1 + \sqrt{2})^n + (1 + \sqrt{2})^{n-1} \\
+& = (1 + \sqrt{2})^{n-1} (2 (1 + \sqrt{2}) + 1) \\
+& = (1 + \sqrt{2})^{n-1} (3 + 2\sqrt{2}) \\
+& = (1 + \sqrt{2})^{n-1} (1 + \sqrt{2})^2 \\
+& = (1 + \sqrt{2})^{n+1} \; .
+\end{align*}
+
+\end{proof}
+
+Let $r = \left\lceil \log_2(2m) \right\rceil$ and $s = \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$.
+We define the polynomial $p:\R^d \to \R$ as
+$$
+p(x) = m + \frac{1}{2} - \sum_{i=1}^m \left( T_s(1 - \ip{v_i}{x}) \right)^r \; .
+$$
+It remains to show that $p$ has properties 1--5.
 

### 2018-11-28 arxiv-version/main.tex
Finish proof of properties of Chebyshev polynomials

@@
 
-However, for $K \ge 3$ there exists a set of labeled examples in an inner product
-space that is linearly separable with a positive margin $\gamma$ but it is not
-strongly linearly separable with any positive margin $\gamma$. Such set of labeled
-examples is shown in
+However, for any $K \ge 3$ and any inner product space of dimension at least
+$2$, there exists a set of labeled examples that is linearly separable with a
+positive margin $\gamma$ but it is not strongly linearly separable with any
+positive margin $\gamma$. An example of such set of labeled examples is shown in
 Figure~\ref{figure:linearly-separable-examples-with-margin}.
@@
 Perceptron} algorithm. Each copy corresponds to a class. In each round, each
-copy makes a binary decision whether the feature vector belongs their respective
+copy makes a binary decision whether the feature vector belongs its respective
 class or not. If at least one copy makes a positive prediction, the algorithm
 predicts accordingly. If multiple copies make positive predictions, the
-algorithm chooses one of them at random. If all copies make negative
+algorithm chooses one of them arbitrarily. If all copies make negative
 predictions, the algorithms makes a blind guess.
@@
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-makes is at most $(K-1) \lfloor (R/\gamma)^2 \rfloor$ mistakes.
+makes is at most $(K-1) \lfloor (R/\gamma)^2 \rfloor$.
 \end{theorem}
@@
 Let $\gamma$ be a positive real number and let $R$ be a non-negative real
-number. For any algorithm for the \textsc{Online Multiclass Classification with
-Bandit Feedback} with $K \le \frac{1}{4}(R/\gamma)^2$ classes there exists an inner
-product space $(V, \ip{\cdot}{\cdot})$, a non-negative integer $T$ and a
-sequence of labeled examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$
-in $V \times \{1,2,\dots,K\}$ that are strongly linearly separable with
-margin $\gamma$, the norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T}
-\le R$ and the expected number of mistakes the algorithm makes is at least $\frac{K-1}{2}
-\lfloor \frac{1}{16} (R/\gamma)^2 \rfloor$.
+number. For any (possibly randomized) algorithm for the \textsc{Online
+Multiclass Classification with Bandit Feedback} with $K \le
+\frac{1}{4}(R/\gamma)^2$ classes there exists an inner product space $(V,
+\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
+examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ in $V \times
+\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
+norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
+number of mistakes the algorithm makes is at least $\frac{K-1}{2} \lfloor
+\frac{1}{16} (R/\gamma)^2 \rfloor$.
 \end{theorem}
@@
 there exists a particular (i.e. deterministic) sequence of examples for which
-the algorithm makes at least $\frac{K-1}{2} M$ mistakes.
+the algorithm makes at least $\frac{K-1}{2} M$ mistakes in expectation
+over its internal randomization.
 \end{proof}
@@
 e.g.~\citep[Section~10.10]{Davidson-Donsig-2010}. In our case, we use
-multivariate polynomials to approximate the indicator function corresponding to
+multivariate polynomial to approximate the indicator function corresponding to
 the intersection of $K-1$ halfspaces. This polynomial separates examples in one
@@
 certain parameters of the approximating polynomial (degree, norm, range of
-values). The parameters are quantified in
-\autoref{theorem:polynomial-approximation-1} and
-\autoref{theorem:polynomial-approximation-2} stated below.
+values). We construct two different polynomials with different paremeters. The
+parameters are quantified in
+Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
+stated below.
 
-Before we state the theorem, recall that a polynomial of $d$ variables is a
+Before we state the theorems, recall that a polynomial of $d$ variables is a
 function $p:\R^d \to \R$ of the form
@@
 $$
-T_n(\cosh(\theta)) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for any $\theta \ge 0$.}
+T_n(\cosh(\theta)) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$.}
 $$
 For $\theta = 0$, according to \eqref{equation:hyperbolic-chebyshev} both sides
-are equal to $1$. The proof will be finished, if we prove that the derivative of
-the left hand side is greater or equal to the derivative of the right hand side.
+are equal to $1$. Thus, it is sufficient to prove that the derivative of the
+left hand side is greater or equal to the derivative of the right hand side.
 That is, we need to prove that
@@
 \label{equation:hyperbolic-chebyshev-derivative-inequality}
-\frac{\diff T_n(\cosh(\theta))}{\diff \theta} \ge \frac{\diff (1 + n^2 (\cosh(\theta) - 1))}{\diff \theta} \qquad \text{for any $\theta \ge 0$.}
+\frac{\diff T_n(\cosh(\theta))}{\diff \theta} \ge \frac{\diff (1 + n^2 (\cosh(\theta) - 1))}{\diff \theta} \qquad \text{for all $\theta \ge 0$.}
 \end{equation}
-Using \eqref{equation:hyperbolic-chebyshev} and recalling that $\diff \cosh(\theta) / \diff \theta = \sinh(\theta)$ we
+Using \eqref{equation:hyperbolic-chebyshev} and recalling that $\frac{\diff \cosh(\theta)}{\diff \theta} = \sinh(\theta)$ we
 can express the derivatives as
@@
 \end{align*}
-TODO
+The inequality \eqref{equation:hyperbolic-chebyshev-derivative-inequality} is thus equivalent to
+$$
+\sinh(n \theta) \ge n \sinh(\theta) \qquad \text{for all $\theta \ge 0$.}
+$$
+Tho prove this inequality we use the summation formula
+$$
+\sinh(\alpha + \beta) = \sinh(\alpha) \cosh(\beta) + \sinh(\beta) \cosh(\beta)
+$$
+and the observation that for $\theta \ge 0$, $\cosh(\theta) \ge 1$ and $\sinh(\theta) \ge 0$. Thus,
+$$
+\sinh(\alpha + \beta) \ge \sinh(\alpha) + \sinh(\beta) \qquad \text{for $\alpha, \beta \ge 0$.}
+$$
+Thus by induction on $n$, we see that $\sinh(n \theta) \ge n \sinh(\theta)$ for all $\theta \ge 0$.
 

### 2018-11-28 arxiv-version/main.tex
Small fixes in the introduction

@@
 Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
-This result is very satisfactory since the upper bound on the number of mistakes
+This result is very satisfying since the upper bound on the number of mistakes
 is information-theoretically optimal and at the same time the \textsc{Multiclass
@@
 setting collects information in the form of so called \emph{strongly labeled}
-and \emph{weakly labeled} examples. Strongly-labeled examples are those for
+and \emph{weakly labeled} examples. Strongly labeled examples are those for
 which we know the class label. Weakly labeled example is an example for which we
@@
 we show the offline problem of finding a linear multiclass separator consistent
-with the strongly- and weakly-labeled examples is NP-hard. This result is a
-simple consequence of the fact that finding an intersection of two halfspaces
-consistent with binary-labeled examples is NP-hard~\citep{Blum-Rivest-1993}.
-Second, we show that any algorithm that uses only strongly-labeled examples and
-ignores weakly labeled examples makes at least $\Omega(???)$ mistakes.
+with a set of strongly and weakly labeled examples is NP-hard. This result is a
+consequence of the fact that finding an intersection of two halfspaces
+consistent with a set of binary-labeled examples is
+NP-hard~\citep{Blum-Rivest-1993}. Second, we show that any algorithm that uses
+only strongly-labeled examples and ignores weakly labeled examples makes at
+least $\Omega(???)$ mistakes.
 

### 2018-11-28 arxiv-version/main.tex
Add auxilliary lemma

@@
 $$
+It is not hard to see that this indeed a norm, since we can interpret it as
+a Euclidean norm of the vector of the coefficients of the polynomial.
 
@@
 TODO
+
+\begin{proposition}[Properties of the norm of polynomials]
+\hspace{1cm} % Dummy space
+\begin{enumerate}
+\item Let $p_1, p_2, \dots, p_n$ be multivariate polynomials and
+let $p(x) = \prod_{i=1}^n p_i(x)$ be their product. Then, $\norm{p}^2 \le n^{\sum_{i=1}^n \deg(p_i)} \prod_{i=1}^n \norm{p_i}^2$.
+\item Let $q$ be a multivariate polynomial of degree at most $s$ and let $p(x) = (q(x))^n$. Then, $\norm{p}^2 \le n^{ns} \norm{q}^{2n}$.
+\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then, $\norm{\sum_{i=1}^n p_i}^2 \le n \sum_{i=1}^n \norm{p_i}^2$.
+\end{enumerate}
+\end{proposition}
+
+\begin{proof}
+TODO
+
+The second part follows from the first part by setting $p_1 = p_2 = \dots p_n = q$.
+
+To prove the third part we use generalized triangle inequality and
+an inequality $(\sum_{i=1}^n a_i)^2 \le n \sum_{i=1}^n a_i^2$ valid
+for any real numbers $a_1, a_2, \dots, a_n$. (The latter inequality follows from the inequality
+between arithmetic mean and qudratic mean, $\frac{1}{n} \sum_{i=1}^n a_i \le \sqrt{\frac{1}{n} \sum_{i=1}^n a_i^2}$.)
+We have
+\begin{align*}
+\norm{\sum_{i=1}^n p_i}^2 = \left( \norm{\sum_{i=1}^n p_i} \right)^2 \le \left(\sum_{i=1}^n \norm{p_i} \right)^2 \le n \sum_{i=1}^n \norm{p_i}^2 \; .
+\end{align*}
+\end{proof}
 

### 2018-11-28 arxiv-version/main.tex
Work on proof of auxiliary lemma

--- 2018-11-28 arxiv-version/main.tex
@@
 $$
-where the sum ranges over a finite set of tuples $(i_1, i_2, \dots, i_d)$ of
+where the sum ranges over a finite set of $d$-tuples $(i_1, i_2, \dots, i_d)$ of
 non-negative integers and $c_{i_1, i_2, \dots, i_d}$ is a real coefficient. The
@@
 \label{section:proof-of-polynomial-approximation-1}
-TODO
+
+\begin{lemma}[Inequality]
+\label{lemma:inequality}
+For any real numbers $b_1, b_2, \dots, b_n$,
+$$
+\left( \sum_{i=1}^n b_i \right)^2 \le n \sum_{i=1}^n b_i^2 \; .
+$$
+\end{lemma}
+
+\autoref{lemma:inequality} follows from Cauchy-Schwartz inequality applied to
+vectors $(b_1, b_2, \dots, b_n)$ and $(1,1,\dots,1)$.
+
+\begin{proposition}[Properties of the norm of polynomials]
+\hspace{1cm} % Dummy space
+\begin{enumerate}
+\item Let $p_1, p_2, \dots, p_n$ be multivariate polynomials and
+let $p(x) = \prod_{j=1}^n p_j(x)$ be their product. Then, $\norm{p}^2 \le n^{\sum_{j=1}^n \deg(p_j)} \prod_{j=1}^n \norm{p_j}^2$.
+\item Let $q$ be a multivariate polynomial of degree at most $s$ and let $p(x) = (q(x))^n$. Then, $\norm{p}^2 \le n^{ns} \norm{q}^{2n}$.
+\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then, $\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
+\end{enumerate}
+\end{proposition}
+
+\begin{proof}
+Using multi-index notation we can write any multivariate polynomial $p$ as
+$$
+p(x) = \sum_A c_A x^A
+$$
+where $A = (i_1, i_2, \dots, i_d)$ is a multi-index (i.e. a $d$-tuple of
+non-negative integers), $x^A = x_1^{i_1} x_2^{i_2} \dots x_d^{i_d}$ is a
+monomial and $c_A = c_{i_1, i_2, \dots, i_d}$ is the corresponding real
+coefficient. The sum is over a finite subset of $d$-tuples of non-negative
+integers. Using this notation, the norm of a polynomial $p$ can be written as
+$$
+\norm{p} = \sqrt{\sum_A (c_A)^2} \; .
+$$
+For a multi-index $A = (i_1, i_2, \dots, i_d)$ we define its $1$-norm as
+$\norm{A}_1 = i_1 + i_2 + \dots + i_d$.
+
+To prove the first part, we express $p_j$ as
+$$
+p_j(x) = \sum_{A_j} c^{(j)}_{A_j} x^{A_j} \; .
+$$
+If $p$ has expansion $p(x) = \sum_A c_A x^A$ then its coefficient $c_A$ for any multi-index $A$ is
+$$
+c_A = \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \; .
+$$
+Therefore,
+\begin{multline*}
+\norm{p}^2
+= \sum_{A} (c_A)^2
+= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \right)^2
+= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
+\end{multline*}
+and
+\begin{multline*}
+\prod_{i=1}^n \norm{p_i}^2
+= \prod_{i=1}^n \left( \sum_{A_i} (c^{(i)}_{A_i})^2 \right)
+= \sum_{(A_1, A_2, \dots, A_n)} \prod_{j=1}^n (c^{(j)}_{A_j})^2
+= \sum_{(A_1, A_2, \dots, A_n)} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
+= \sum_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
+\end{multline*}
+where in both cases the outer sum is over multi-indices $A$ such that $\norm{A}_1 \le \deg(p)$.
+To finish the proof, it is sufficient to prove that for any $A$ such that $\norm{A}_1 \le \deg(p)$,
+$$
+\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
+\le n^{\deg(p)} \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
+$$
+This inequality follows from \autoref{lemma:inequality} as long we can show that
+the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 + A_2 + \dots +
+A_n = A$ is upper bounded by $n^{\deg(p)}$.
+
+The second part follows from the first part by setting $p_1 = p_2 = \dots p_n = q$.
+
+To prove the third part we use generalized triangle inequality and an
+\autoref{lemma:inequality}. We have
+\begin{align*}
+\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
+\end{align*}
+\end{proof}
 

### 2018-11-29 arxiv-version/main.tex
Add a reference
More work on polynomials

@@
 \STATE{Observe feature vector $x_t$}
-\STATE{Environment \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
+\STATE{Adversary \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
 \STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
@@
 related to the problem of learning intersection of halfspaces and has been
-studied previously by \cite{Klivans-Servedio-2008}.
+studied previously by \cite{Klivans-Servedio-2008}. As an important technical
+achievement, we improve on the results of \cite{Klivans-Servedio-2008} by
+removing completely the dependency on the original dimension $d$.
 
@@
 
+\item \cite{Chen-Chen-Zhang-Chen-Zhang-2009}
+
 \item \cite{Hazan-Kale-2011}
@@
 \item \cite{Beygelzimer-Orabona-Zhang-2017}
+
+\item \cite{Foster-Kale-Luo-Mohri-Sridharan-2018}
 
@@
 
-\section{Converting linear separability to strong linear separability}
-\label{section:converting-linear-separability-to-strong-linear-separability}
+\section{From linear separability to strong linear separability}
+\label{section:from-linear-separability-to-strong-linear-separability}
 
@@
 
-We construct several different mappings $\phi$. The parameters $R'$ and
-$\gamma'$ for the different mappings are not the same, but the ratios
-$R'/\gamma'$ are qualitively the same. However, one mapping has the advantage of
-having a kernel $k(x,x')$ that is faster to evaluate. Another mapping has the
-advantage that one does \emph{not} need to know the initial margin $\gamma$. In
-other words, the same mapping works for all possible values of $\gamma > 0$.
-
-The idea behind all the mappings is that, on a compact set, multivariate
-polynomials uniformly approximate any continuous function. This result is a
-special case of the well known Stone-Weierstrass theorem; see
-e.g.~\citep[Section~10.10]{Davidson-Donsig-2010}. In our case, we use
-multivariate polynomial to approximate the indicator function corresponding to
-the intersection of $K-1$ halfspaces. This polynomial separates examples in one
-class from examples in the other classes. To be able to quantify $\gamma'$ and
-$R'$ as well as time complexity of evaluating $k(x,x')$ we need to quantify
-certain parameters of the approximating polynomial (degree, norm, range of
-values). We construct two different polynomials with different paremeters. The
+We construct several different mappings $\phi$. The mappings differ in the
+parameters $R'$, $\gamma'$, time complexity of evaluating $\phi(x)$, and time
+complexity of evaluating $k(x,x')$. Some of the mappings depend the original
+margin $\gamma$. In practice, the margin parameter $\gamma$ is not known, which
+makes these mappings impractical. However, one of the mappings we construct
+does \emph{not} depend $\gamma$.
+
+The idea behind all the mappings is polynomial approximation. According to the
+well known Stone-Weierstrass theorem (see
+e.g.~\citep[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
+multivariate polynomials uniformly approximate any continuous function. In our
+case, we use multivariate polynomial to approximate the indicator function
+corresponding to the intersection of $K-1$ halfspaces. This polynomial separates
+examples in one class from examples in the other classes. To be able to quantify
+$R'$, $\gamma'$ and time complexities of evaluating $\phi(x)$ and $k(x,x')$, we
+need to quantify certain parameters of the approximating polynomial (degree,
+norm). We construct two different polynomials with different paremeters. The
 parameters are quantified in
@@
 
-\subsection{Proof of \autoref{theorem:polynomial-approximation-1}}
-\label{section:proof-of-polynomial-approximation-1}
-
-\begin{lemma}[Inequality]
-\label{lemma:inequality}
+\section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
+
+For the proofs of the theorems we need several auxilliary results.
+
+\begin{lemma}[Simple inequality]
+\label{lemma:simple-inequality}
 For any real numbers $b_1, b_2, \dots, b_n$,
@@
 
-\autoref{lemma:inequality} follows from Cauchy-Schwartz inequality applied to
+\begin{proof}
+The lemma follows from Cauchy-Schwartz inequality applied to
 vectors $(b_1, b_2, \dots, b_n)$ and $(1,1,\dots,1)$.
+\end{proof}
+
+\begin{lemma}[Bound on binomial coefficients]
+\label{lemma:binomial-bound}
+For any integers $n,k$ such that $n \ge k \ge 0$,
+$$
+\binom{n}{k} \le (n - k + 1)^k \; .
+$$
+\end{lemma}
+
+\begin{proof}
+If $k = 0$, the inequality trivially holds. For the rest of the proof we can
+assume $k \ge 1$. We write the binomial coefficient as
+$$
+\binom{n}{k} = \frac{n(n-1)\cdots(n-k+1)}{k(k-1) \cdots 1} = \frac{n}{k} \cdot \frac{n-1}{k - 1} \cdots \frac{n-k+1}{1} \; .
+$$
+We claim that
+$$
+\frac{n}{k} \le \frac{n-1}{k - 1} \le \cdots \le \frac{n-k+1}{1}
+$$
+from which the lemma follows by upper bounding all the fractions by $n-k+1$.
+It remains to prove that for any $j=0,1,\dots,k-1$,
+$$
+\frac{n - j + 1}{k - j + 1} \le \frac{n - j}{k - j} \; .
+$$
+Mutliplying by the (positive) denonimators, we get an equivalent inequality
+$$
+(n - j + 1)(k - j) \le (n - j)(k - j + 1) \; .
+$$
+Cancelling common terms leads to an equivalent inequality
+$$
+k - j \le n - j \; ,
+$$
+which holds by the assumption on $n \ge k$.
+\end{proof}
 
@@
 where in both cases the outer sum is over multi-indices $A$ such that $\norm{A}_1 \le \deg(p)$.
-To finish the proof, it is sufficient to prove that for any $A$ such that $\norm{A}_1 \le \deg(p)$,
+\autoref{lemma:simple-inequality} implies that for any multi-index $A$,
 $$
 \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\le n^{\deg(p)} \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
-$$
-This inequality follows from \autoref{lemma:inequality} as long we can show that
-the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 + A_2 + \dots +
-A_n = A$ is upper bounded by $n^{\deg(p)}$.
+\le M_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
+$$
+where $M_A$ is the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 +
+A_2 + \dots + A_n = A$.
+
+To finish the proof, it is sufficient to prove that
+$M_A \le n^{\deg(p)}$. To prove this inequality, consider a multi-index
+$A = (i_1, i_2, \dots, i_d)$ and consider its $\ell$-th coordinate $i_\ell$.
+In order for $A_1 + A_2 + \dots + A_n = A$, the $\ell$-th coordinates of
+$A_1, A_2, \dots, A_n$ need to sum to $i_\ell$. There are exactly $\binom{i_\ell + n - 1}{i_\ell}$
+possibilities for the choice of $\ell$-th coordinates of $A_1, A_2, \dots, A_n$.
+The total number of choices is thus
+$$
+M_A = \prod_{\ell=1}^d \binom{i_\ell + n - 1}{i_\ell} \; .
+$$
+Using \autoref{lemma:binomial-bound}, we upper bound it as
+$$
+M_A \le \prod_{\ell=1}^d n^{i_\ell} = n^{\norm{A}_1} \le n^{\deg(p)} \; .
+$$
 
@@
 
-To prove the third part we use generalized triangle inequality and an
-\autoref{lemma:inequality}. We have
+To prove the third part we use generalized triangle inequality and
+\autoref{lemma:simple-inequality}. We have
 \begin{align*}
@@
 \end{proof}
+
+\subsection{Proof of \autoref{theorem:polynomial-approximation-1}}
+\label{section:proof-of-polynomial-approximation-1}
+
+TODO
 
@@
 \item If $n \ge 1$, the leading coefficient of $T_n(z)$ is $2^{n-1}$.
+\item $T_n(\cos(\theta)) = \cos(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
+\item $T_n(\cosh(\theta)) = \cosh(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
 \item $|T_n(z)| \le 1$ for all $z \in [-1,1]$ and all $n \ge 0$.
@@
 \begin{proof}[Proof of \autoref{proposition:properties-of-chebyshev-polynomials}]
-The first two proprties easily follow from the recurrence.
-
-The third property is a direct consequence of
-\begin{equation}
-\label{equation:trigonometric-chebyshev}
-T_n(\cos(\theta)) = \cos(n \theta) \qquad \quad \text{for all $\theta \in \R$.}
-\end{equation}
-since for any $x \in [-1,1]$ there exists $\theta \in \R$ such that $\cos(\theta) = x$.
-Equation \eqref{equation:trigonometric-chebyshev} is proved by induction on $n$. Indeed, by definition
+The first two properties can be easily proven by induction on $n$ using the recurrence.
+
+We prove third property by induction on $n$. Indeed, by definition
 $$
@@
 $$
-which finishes the proof of equation \eqref{equation:trigonometric-chebyshev}.
-
-To verify the fourth property we first show that
-\begin{equation}
-\label{equation:hyperbolic-chebyshev}
-T_n(\cosh(\theta)) = \cosh(n \theta) \qquad \quad \text{for all $\theta \in \R$.}
-\end{equation}
-The proof of equation~\eqref{equation:hyperbolic-chebyshev} is the same
-as the proof of equation \eqref{equation:trigonometric-chebyshev} except
-that we replace $\cos$ and $\sin$ with $\cosh$ and $\sinh$ respectively.
-
-Note that $\cosh(\theta) = \frac{e^{\theta} + e^{-\theta}}{2}$ is an even
-continuous function that maps $\R$ onto $[1,+\infty)$, is strictly decreasing
-on $(-\infty,0]$, and is strictly increasing on $[0,\infty)$. Thus the fourth
-property is equivalent to
-$$
-T_n(\cosh(\theta)) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$.}
-$$
-For $\theta = 0$, according to \eqref{equation:hyperbolic-chebyshev} both sides
-are equal to $1$. Thus, it is sufficient to prove that the derivative of the
-left hand side is greater or equal to the derivative of the right hand side.
-That is, we need to prove that
-\begin{equation}
-\label{equation:hyperbolic-chebyshev-derivative-inequality}
-\frac{\diff T_n(\cosh(\theta))}{\diff \theta} \ge \frac{\diff (1 + n^2 (\cosh(\theta) - 1))}{\diff \theta} \qquad \text{for all $\theta \ge 0$.}
-\end{equation}
-Using \eqref{equation:hyperbolic-chebyshev} and recalling that $\frac{\diff \cosh(\theta)}{\diff \theta} = \sinh(\theta)$ we
-can express the derivatives as
-\begin{align*}
-\frac{\diff T_n(\cosh(\theta))}{\diff \theta} & = \frac{\diff \cosh(n \theta))}{\diff \theta} = n \sinh(n \theta) \; , \\
-\frac{\diff (1 + n^2 (\cosh(\theta) - 1))}{\diff \theta} & = n^2 \sinh(\theta) \; .
-\end{align*}
-The inequality \eqref{equation:hyperbolic-chebyshev-derivative-inequality} is thus equivalent to
+which finishes the proof.
+
+Fourth property has the similar proof as third property. It suffices
+to replace $\cos$ and $\sin$ with $\cosh$ and $\sinh$ respectively.
+
+Fifth property follows from the third property. Indeed, for any $z \in [-1,1]$
+there exists $\theta \in \R$ such that $\cos \theta = z$. Thus, $|T_n(z)| =
+|T_n(\cos(\theta))| = |\cos(n\theta)| \le 1$.
+
+The sixth property is equivalent to
+$$
+T_n(\cosh(\theta)) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$,}
+$$
+since $\cosh(\theta) = \frac{e^{\theta} + e^{-\theta}}{2}$ is an even continuous
+function that maps $\R$ onto $[1,+\infty)$, is strictly decreasing on
+$(-\infty,0]$, and is strictly increasing on $[0,\infty)$. Using the fourth
+property the last inequality is equivalent to
+$$
+\cosh(n \theta) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$.}
+$$
+For $\theta = 0$, both sides are equal to $1$. Thus, it is sufficient to prove
+that the derivative of the left hand side is greater or equal to the derivative
+of the right hand side. Recalling that $[\cosh(\theta)]' = \sinh(\theta)$, this
+means that we need to show that
 $$
@@
 $$
-\sinh(\alpha + \beta) = \sinh(\alpha) \cosh(\beta) + \sinh(\beta) \cosh(\beta)
-$$
-and the observation that for $\theta \ge 0$, $\cosh(\theta) \ge 1$ and $\sinh(\theta) \ge 0$. Thus,
-$$
-\sinh(\alpha + \beta) \ge \sinh(\alpha) + \sinh(\beta) \qquad \text{for $\alpha, \beta \ge 0$.}
-$$
-Thus by induction on $n$, we see that $\sinh(n \theta) \ge n \sinh(\theta)$ for all $\theta \ge 0$.
-
-To verify the fifth property let $a_n$ be the magnitude of the largest
-coefficient of $T_n(z)$. The recurrence for Chebyshev polynomials
-implies that the sequence $a_0, a_1, a_2, \dots$ satisfies
+\sinh(\alpha + \beta) = \sinh(\alpha) \cosh(\beta) + \sinh(\beta) \cosh(\beta) \; .
+$$
+If $\alpha, \beta$ are non-negative then $\sinh(\alpha), \sinh(\beta)$ are
+non-negative and $\cosh(\alpha), \cosh(\beta) \ge 1$. Hence,
+$$
+\sinh(\alpha + \beta) \ge \sinh(\alpha) + \sinh(\beta) \qquad \text{for any $\alpha, \beta \ge 0$.}
+$$
+This implies that (using induction on $n$) that $\sinh(n \theta) \ge n
+\sinh(\theta)$ for all $\theta \ge 0$.
+
+To verify the seventh property let $a_n$ be the magnitude of the largest
+coefficient of $T_n(z)$. The recurrence for Chebyshev polynomials implies that
+the sequence $a_0, a_1, a_2, \dots$ satisfies
 \begin{align*}

### 2018-11-29 arxiv-version/main.tex
Proof of one of the polynomial approximation theorems

@@
 makes these mappings impractical. However, one of the mappings we construct
-does \emph{not} depend $\gamma$.
+does \emph{not} depend on $\gamma$.
 
@@
 $$
-p(x) = p(x_1, x_2, \dots, x_d) = \sum_{i_1, i_2, \dots, i_d} c_{i_1, i_2, \dots, i_d} x_1^{i_1} x_2^{i_2} \dots x_d^{i_d}
-$$
-where the sum ranges over a finite set of $d$-tuples $(i_1, i_2, \dots, i_d)$ of
-non-negative integers and $c_{i_1, i_2, \dots, i_d}$ is a real coefficient. The
-\emph{degree} of a polynomial $p$, denoted by $\deg(p)$, is the largest value of
-$i_1 + i_2 + \dots + i_d$ for which the coefficient is non-zero. The \emph{norm
-of a polynomial} $p$ is defined as
-$$
-\norm{p} = \sqrt{\sum_{i_1, i_2, \dots, i_d} \left(c_{i_1, i_2, \dots, i_d} \right)^2 } \; .
-$$
-It is not hard to see that this indeed a norm, since we can interpret it as
-a Euclidean norm of the vector of the coefficients of the polynomial.
+p(x) = p(x_1, x_2, \dots, x_d) = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
+$$
+where the sum ranges over a finite set of $d$-tuples $(\alpha_1, \alpha_2,
+\dots, \alpha_d)$ of non-negative integers and $c_{\alpha_1, \alpha_2, \dots,
+\alpha_d}$ is a real coefficient. The \emph{degree} of a polynomial $p$, denoted
+by $\deg(p)$, is the largest value of $\alpha_1 + \alpha_2 + \dots + \alpha_d$
+for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is non-zero.
+The \emph{norm of a polynomial} $p$ is defined as
+$$
+\norm{p} = \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} \left(c_{\alpha_1, \alpha_2, \dots, \alpha_d} \right)^2 } \; .
+$$
+It is easy see that this is indeed a norm, since we can interpret it as a
+Euclidean norm of the vector of the coefficients of the polynomial.
 
@@
 \label{theorem:polynomial-approximation-1}
-Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1}, \norm{v_2}, \dots, \norm{v_m} \le 1$.
-Let $\gamma > 0$. There exists a polynomial $p:\R^d \to \R$ such that
+Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
+\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma > 0$. There exists a
+multivariate polynomial $p:\R^d \to \R$ such that
 \begin{enumerate}
-\item $p(x) \ge 1$ for all $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-\item $p(x) \le -1$ for all $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
+\item $p(x) \ge 1$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
+\item $p(x) \le -1$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
 \item $\deg(p) \le ???$
 \item $\norm{p} \le ???$
-\item $|p(x)| \le ???$ for all $x \in \R^d$ such that $\norm{x} \le 1$
 \end{enumerate}
@@
 \label{theorem:polynomial-approximation-2}
-Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1}, \norm{v_2}, \dots, \norm{v_m} \le 1$.
-Let $\gamma > 0$. There exists a polynomial $p:\R^d \to \R$ such that
+Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
+\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma > 0$. There exists a
+multivariate polynomial $p:\R^d \to \R$ such that
 \begin{enumerate}
-\item $p(x) \ge 1/2$ for all $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-\item $p(x) \le -1/2$ for all $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-\item $\deg(p) \le ???$
-\item $\norm{p} \le ???$
-\item $|p(x)| \le ???$ for all $x \in \R^d$ such that $\norm{x} \le 1$
+\item $p(x) \ge 1/2$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
+\item $p(x) \le -1/2$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
+\item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$
+\item $\displaystyle \norm{p} \le \left( 188 \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil \right)^{\frac{1}{2} \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil}$
 \end{enumerate}
@@
 The proofs of the theorems can be found in
-Sections~\ref{section:proof-of-polynomial-approximation-1}~and~\ref{section:proof-of-polynomial-approximation-2}
-respectively.
+Section~\ref{section:proof-of-polynomial-approximation}.
+
+TODO: Mappings and kernels!
 
 \section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
+\label{section:proof-of-polynomial-approximation}.
 
@@
 $$
-\binom{n}{k} = \frac{n(n-1)\cdots(n-k+1)}{k(k-1) \cdots 1} = \frac{n}{k} \cdot \frac{n-1}{k - 1} \cdots \frac{n-k+1}{1} \; .
+\binom{n}{k}
+= \frac{n(n-1)\cdots(n-k+1)}{k(k-1) \cdots 1}
+= \frac{n}{k} \cdot \frac{n-1}{k - 1} \cdots \frac{n-k+1}{1} \; .
 $$
@@
 
-\begin{proposition}[Properties of the norm of polynomials]
+\begin{lemma}[Properties of the norm of polynomials]
+\label{lemma:properties-of-norm-of-polynomials}
 \hspace{1cm} % Dummy space
 \begin{enumerate}
-\item Let $p_1, p_2, \dots, p_n$ be multivariate polynomials and
-let $p(x) = \prod_{j=1}^n p_j(x)$ be their product. Then, $\norm{p}^2 \le n^{\sum_{j=1}^n \deg(p_j)} \prod_{j=1}^n \norm{p_j}^2$.
-\item Let $q$ be a multivariate polynomial of degree at most $s$ and let $p(x) = (q(x))^n$. Then, $\norm{p}^2 \le n^{ns} \norm{q}^{2n}$.
-\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then, $\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
+\item Let $p_1, p_2, \dots, p_n$ be multivariate polynomials and let $p(x) =
+\prod_{j=1}^n p_j(x)$ be their product.  Then, $\norm{p}^2 \le n^{\sum_{j=1}^n
+\deg(p_j)} \prod_{j=1}^n \norm{p_j}^2$.
+
+\item Let $q$ be a multivariate polynomial of degree at most $s$ and let $p(x) =
+(q(x))^n$. Then, $\norm{p}^2 \le n^{ns} \norm{q}^{2n}$.
+
+\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then,
+$\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
 \end{enumerate}
-\end{proposition}
+\end{lemma}
 
@@
 $$
-where $A = (i_1, i_2, \dots, i_d)$ is a multi-index (i.e. a $d$-tuple of
-non-negative integers), $x^A = x_1^{i_1} x_2^{i_2} \dots x_d^{i_d}$ is a
-monomial and $c_A = c_{i_1, i_2, \dots, i_d}$ is the corresponding real
+where $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ is a multi-index (i.e. a $d$-tuple of
+non-negative integers), $x^A = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}$ is a
+monomial and $c_A = c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is the corresponding real
 coefficient. The sum is over a finite subset of $d$-tuples of non-negative
@@
 $$
-For a multi-index $A = (i_1, i_2, \dots, i_d)$ we define its $1$-norm as
-$\norm{A}_1 = i_1 + i_2 + \dots + i_d$.
+For a multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ we define its
+$1$-norm as $\norm{A}_1 = \alpha_1 + \alpha_2 + \dots + \alpha_d$.
 
@@
 $$
-If $p$ has expansion $p(x) = \sum_A c_A x^A$ then its coefficient $c_A$ for any multi-index $A$ is
+Since $p(x) = \prod_{i=1}^n p_j(x)$, the coefficients of its expansion $p(x) =
+\sum_A c_A x^A$ are
 $$
@@
 
-To finish the proof, it is sufficient to prove that
-$M_A \le n^{\deg(p)}$. To prove this inequality, consider a multi-index
-$A = (i_1, i_2, \dots, i_d)$ and consider its $\ell$-th coordinate $i_\ell$.
-In order for $A_1 + A_2 + \dots + A_n = A$, the $\ell$-th coordinates of
-$A_1, A_2, \dots, A_n$ need to sum to $i_\ell$. There are exactly $\binom{i_\ell + n - 1}{i_\ell}$
-possibilities for the choice of $\ell$-th coordinates of $A_1, A_2, \dots, A_n$.
-The total number of choices is thus
-$$
-M_A = \prod_{\ell=1}^d \binom{i_\ell + n - 1}{i_\ell} \; .
+To finish the proof, it is sufficient to prove that $M_A \le n^{\deg(p)}$ for
+any $A$ such that $\norm{A}_1 \le \deg(p)$. To prove this inequality, consider a
+multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ and consider its $i$-th coordinate
+$\alpha_i$. In order for $A_1 + A_2 + \dots + A_n = A$ to hold, the $i$-th
+coordinates of $A_1, A_2, \dots, A_n$ need to sum to $\alpha_i$. There are exactly
+$\binom{\alpha_i + n - 1}{\alpha_i}$ possibilities for the choice of $i$-th
+coordinates of $A_1, A_2, \dots, A_n$. The total number of choices is thus
+$$
+M_A = \prod_{i=1}^d \binom{\alpha_i + n - 1}{\alpha_i} \; .
 $$
@@
 $$
-M_A \le \prod_{\ell=1}^d n^{i_\ell} = n^{\norm{A}_1} \le n^{\deg(p)} \; .
+M_A \le \prod_{i=1}^d n^{\alpha_i} = n^{\norm{A}_1} \le n^{\deg(p)} \; .
 $$
@@
 \item $T_n(z) \ge 1 + n^2(z - 1)$ for all $z \ge 1$ and all $n \ge 0$.
-\item All coefficients of $T_n(z)$ lie in the interval $\left[-(1+\sqrt{2})^n, (1+\sqrt{2})^n \right]$.
+\item $\norm{T_n} \le (1+\sqrt{2})^n$ for all $n \ge 0$
 \end{enumerate}
@@
 
-To verify the seventh property let $a_n$ be the magnitude of the largest
-coefficient of $T_n(z)$. The recurrence for Chebyshev polynomials implies that
-the sequence $a_0, a_1, a_2, \dots$ satisfies
-\begin{align*}
-a_0 & = a_1 = 1 \; , \\
-a_{n+1} & \le 2 a_n + a_{n-1} & \text{for $n \ge 1$.}
-\end{align*}
-It remains to show that $a_n \le (1 + \sqrt{2})^n$ for all $n \ge 0$. We do this
-by induction on $n$. For $n=0$ and $n=1$ the inequality trivially holds. For $n
-\ge 1$, we have
-\begin{align*}
-a_{n+1} \le 2 a_n + a_{n-1}
+We verify the seventh property by induction on $n$.
+For $n=0$ and $n=1$ the inequality trivially holds, since $\norm{T_0} = \norm{T_1} = 1$.
+For $n \ge 1$, since $T_{n+1}(z) = 2zT_n(z) - T_{n-1}(z)$,
+\begin{align*}
+\norm{T_{n+1}}
+& \le 2 \norm{T_n} + \norm{T_{n-1}} \\
 & \le 2 (1 + \sqrt{2})^n + (1 + \sqrt{2})^{n-1} \\
@@
 
-\subsection{Rational Kernel}
-TODO
+To verify the first property notice that if $x \in \R^d$ satisfies $\norm{x} \le
+1$ and $\ip{v_i}{x} \ge \gamma$ then since $\norm{v_i} \le 1$ we have
+$\ip{v_i}{x} \in [0,1]$. Thus, $T_s(1 - \ip{v_i}{x})$ and $\left( T_s(1 -
+\ip{v_i}{x}) \right)^r$ lie in the interval $[-1,1]$. Therefore,
+$$
+p(x) \ge m + \frac{1}{2} - m \ge \frac{1}{2} \; .
+$$
+
+To verify the second property consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d
+~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Clearly, $\norm{x} \le 1$
+and there exists at least one $i \in \{1,2,\dots,m\}$ such that $\ip{v_i}{x} \le
+- \gamma$. Therefore, $1 - \ip{v_i}{x} \ge 1 + \gamma$ and~\autoref{proposition:properties-of-chebyshev-polynomials} (part 6)
+imply that
+$$
+T_s(1 - \ip{v_i}{x}) \ge 1 + s^2 \gamma \ge 2
+$$
+and thus
+$$
+\left( T_s(1 - \ip{v_i}{x}) \right)^r \ge 2^r \ge 2m \; .
+$$
+On the oter hand for any $j \in \{1,2,\dots,m\}$, we have $\ip{v_j}{x} \in
+[-1,1]$ and thus $1 - \ip{v_j}{x}$ lies in the interval $[0,2]$. According to
+\autoref{proposition:properties-of-chebyshev-polynomials} (parts 5 and 6), $T_s(1 - \ip{v_j}{x})
+\ge -1$. Therefore,
+$$
+p(x) = m + \frac{1}{2} - \left( T_s(1 - \ip{v_i}{x}) \right)^r - \sum_{\substack{j ~:~  1 \le j \le m \\ j \neq i}} \le m + \frac{1}{2} - 2m + (m - 1) \le - \frac{1}{2} \; .
+$$
+
+The third property follows from observation that degree of $p$
+is the same as the degree of any one of the terms
+$\left( T_s(1 - \ip{v_i}{x}) \right)^r$ which is $r \cdot s$.
+
+To prove the fourth property, we need to upper bound the norm of $p$.
+Let $f_i(x) = 1 - \ip{v_i}{x}$, let $g_i(x) = T_s(1 - \ip{v_i}{x})$
+and let $h_i(x) = (T_s(1 - \ip{v_i}{x}))^r$. We have
+$$
+\norm{f_i}^2 = 1 + \norm{v_i}^2 \le 1 + 1 = 2 \; .
+$$
+Let $T_s(z) = \sum_{j=0}^s c_j z^j$ be the expansion of $s$-th Chebyshev polynomial.
+Then,
+\begin{align*}
+\norm{g_i}^2
+& = \norm{ \sum_{j=0}^s c_j (f_i)^j }^2 \\
+& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 & \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
+& = (s + 1) \sum_{j=0}^s (c_j)^2 \norm{(f_i)^j}^2 \\
+& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} & \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
+& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j 2^{2j} \\
+& \le (s + 1) s^s 2^{2s} \sum_{j=0}^s (c_j)^2 \\
+& = (s + 1) s^s 2^{2s} \norm{T_s}^2 \\
+& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} & \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
+& = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
+& \le \left(8(1+\sqrt{2})^2 s \right)^s & \text{(since $s+1 \le 2^s$ for any integers $s \ge 0$)} \\
+& \le \left(47 s \right)^s \; .
+\end{align*}
+Finally,
+\begin{align*}
+\norm{p}
+& \le m + \frac{1}{2} + \sum_{i=1}^m \norm{(g_i)^r} \\
+& = m + \frac{1}{2} + \sum_{i=1}^m \sqrt{\norm{(g_i)^r}^2} \\
+& \le m + \frac{1}{2} + \sum_{i=1}^m \sqrt{r^{rs} \norm{g_i}^{2r}} \\
+& \le m + \frac{1}{2} + m r^{rs/2} \left(47 s \right)^{rs/2} \\
+& = m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \; .
+\end{align*}
+We can further upper bound the last expression by using that $m \le \frac{1}{2} 2^r$.
+Since $r,s \ge 1$,
+\begin{align*}
+\norm{p}
+& \le m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \\
+& \le \frac{1}{2} 2^r + \frac{1}{2} + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
+& \le 2^r + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
+& = 2^r \left(1 + \frac{1}{2} \left(47 rs \right)^{rs/2} \right) \\
+& = 2^r \left(47 rs \right)^{rs/2} \\
+& \le 4^{rs/2} \left(47 rs \right)^{rs/2} \\
+& \le \left(188 rs \right)^{rs/2} \; .
+\end{align*}
+Substituting for $r$ and $s$ finishes the proof.
 

### 2018-11-30 arxiv-version/figures/pizza-slice.tex
Add figure of pizza slice

\begin{tikzpicture}

  \useasboundingbox (-5.5,-5.5) rectangle (5.5,5.5);
  % \draw[help lines] (-5.5,-5.5) rectangle (5.5,5.5);

  % Grid and coordinate axes
  %% \draw[help lines] (-5.2,-5.2) grid (5.2,5.2);
  %% \draw[thick, ->, >=latex] (-5.2,0) -- (5.2,0);
  %% \draw[thick, ->,  >=latex] (0,-5.2) -- (0,5.2);

  % Notable points
  \coordinate (Origin) at (0,0);

  \coordinate [label={[xshift=-10mm, yshift=5mm]$\ip{v_1}{x} = 0$}] (A) at (120:5);
  \coordinate [label={[xshift=-10mm, yshift=-10mm]$\ip{v_2}{x} = 0$}] (B) at (240:5);

  % Circle which contains all the examples.
  % \draw (Origin) circle (5cm);

  \draw[dashed] (Origin) -- (A);
  \draw[dashed] (Origin) -- (B);

  \coordinate (A1) at ($(120:0.5*sqrt{97} - 0.5) - (1,0)$);
  \coordinate (B1) at ($(240:0.5*sqrt{97} - 0.5) - (1,0)$);

  \coordinate (A2) at ($(120:0.5*sqrt{97} + 0.5) + (1,0)$);
  \coordinate (B2) at ($(240:0.5*sqrt{97} + 0.5) + (1,0)$);

  \draw[ultra thick] ($(Origin) - (1,0)$) -- (A1);
  \draw[ultra thick] ($(Origin) - (1,0)$) -- (B1);

  \draw[ultra thick] ($(Origin) + (1,0)$) -- (A2);
  \draw[ultra thick] ($(Origin) + (1,0)$) -- (B2);

  \pic [ultra thick, draw, angle radius=5cm] {angle=A1--Origin--B1};
  \pic [ultra thick, draw, angle radius=5cm] {angle=B2--Origin--A2};

  \coordinate (C) at (120:3);
  \coordinate [label={[xshift=-6mm, yshift=-4mm]$\gamma$}] (C1) at ($(120:3) + (0.75, 0.43301270189221932338)$);
  \coordinate [label={[xshift=+3mm, yshift=+2mm]$\gamma$}] (C2) at ($(120:3) - (0.75, 0.43301270189221932338)$);
  \draw[<->, >=latex, ultra thick] (C1) -- (C) -- (C2);

  \coordinate (D) at (240:3);
  \coordinate [label={[xshift=+4mm, yshift=-8mm]$\gamma$}] (D1) at ($(240:3) + (-0.75, 0.43301270189221932338)$);
  \coordinate [label={[xshift=-5mm, yshift=-3mm]$\gamma$}] (D2) at ($(240:3) - (-0.75, 0.43301270189221932338)$);
  \draw[<->, >=latex, ultra thick] (D1) -- (D) -- (D2);

  \coordinate [label={$R^+$}](R1) at ($(Origin) - (3,0)$);
  \coordinate [label={$R^-$}](R2) at ($(Origin) + (3,0)$);

\end{tikzpicture}

### 2018-11-30 arxiv-version/main.tex
Add figure of pizza slice

@@
 \usepackage{amsthm}
-\usepackage{caption}
+\usepackage[singlelinecheck=false]{caption}
 \usepackage{fullpage}
@@
 \usetikzlibrary{arrows}
+\usetikzlibrary{angles}
 \usetikzlibrary{backgrounds}
@@
 The proofs of the theorems can be found in
-Section~\ref{section:proof-of-polynomial-approximation}.
+Section~\ref{section:proof-of-polynomial-approximation}. The geometric
+interpretation of the two regions described in parts 1 and 2 of the theorems is
+explained in Figure~\ref{figure:pizza-slice}.
+
+\begin{figure}
+\begin{center}
+\input{figures/pizza-slice}
+\end{center}
+\caption[]{The figure shows the two regions used in parts 1 and 2 of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
+for the case $m=d=2$ and a particular choice of vectors $v_1$ and $v_2$. These regions are
+\begin{align*}
+R^+ & = \displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\} \; , \\
+R^- & = \displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\} \; .
+\end{align*}
+}
+\label{figure:pizza-slice}
+\end{figure}
 

### 2018-11-30 arxiv-version/main.tex
Start proof of Theorem 4.

@@
 \end{center}
-\caption[]{The figure shows the two regions used in parts 1 and 2 of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
-for the case $m=d=2$ and a particular choice of vectors $v_1$ and $v_2$. These regions are
+\caption[]{The figure shows the two regions used in parts 1 and 2 of
+Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
+for the case $m=d=2$ and a particular choice of vectors $v_1, v_2$ and margin
+parameter $\gamma$. These regions are
 \begin{align*}
@@
 \end{align*}
+The separating hyperplanes $\ip{v_1}{x} = 0$ and $\ip{v_2}{x} = 0$ are shown as dashed lines.
 }
@@
 
+We define several univariate polynomials
+\begin{align*}
+P_n(z) & = (z - 1) \prod_{i=1}^n (z - 2^i)^2 && \text{for $n \ge 0$,} \\
+A_{n,k}(z) & = (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$,} \\
+B_{n,k}(z) & = - (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$.}
+\end{align*}
+Let $r = 2 \left\lceil \frac{1}{2} \log(4m + 1) \right\rceil + 1$ and $s = \left \lceil \log(1/\gamma) \right \rceil$.
+We define the polynomial $p:\R^d \to \R$ as
+$$
+p(x) = \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_i}{x}}{\gamma} \right)
+- \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_i}{x}}{\gamma} \right) \; .
+$$
+For convenienence we define univariate rational function
+\begin{align*}
+S_{n,k}(z) & = \frac{A_{n,k}(z)}{B_{n,k}(z)} && \text{for $n,k \ge 0$,}
+\end{align*}
+and a multivariate rational function
+$$
+Q(x) = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \; .
+$$
+It easy to verify that
+$$
+p(x) = Q(x) \prod_{i=1}^m B_{s,r} \left( \frac{\ip{v_i}{x}}{\gamma} \right) \; .
+$$
+
+\begin{proposition}[Properties of $P_n$]
+\hspace{1cm} % Dummy space
+\begin{enumerate}
+\item If $z \in [0,1]$ then $P_n(-z) \le P_n(z) \le 0$.
+\item If $z \in [1,2^n]$ then $0 \le 4P_n(z) \le -P_n(-z)$.
+\end{enumerate}
+\end{proposition}
+
+\begin{proof}
+To prove the first part, note that $P_n(z)$ and $P_n(-z)$ are non-positive for
+$z \in [0,1]$. If $z=1$ then $P_n(z)=P_n(-z) = 0$. For $z \in [0,1)$, we have
+$$
+\frac{P_n(-z)}{P_n(z)} = \frac{1+x}{1-x} \prod_{i=1}^n \frac{(x+2^i)^2}{(x-2^i)^2} \ge 1 \; .
+$$
 TODO
+\end{proof}
+
+\begin{proposition}[Properties of $S_{n,k}$]
+\hspace{1cm} % Dummy space
+\begin{enumerate}
+\item
+\end{enumerate}
+\end{proposition}
+
+\begin{proof}
+TODO
+\end{proof}
 

### 2018-12-01 arxiv-version/main.tex
Small fixes

@@
 
-The key observation is that $\Exp[B] = (K-1) \Exp[C]$ since if $S_t =
-\emptyset$, there is $1/K$ probability that the algorithm guesses the correct
-label and with probability $(K-1)/K$ algorithm's guess is incorrect.
-Putting all the information together, we get that
+The key observation is that $\Exp[B] = (K-1) \Exp[C]$. The equality holds
+because if $S_t = \emptyset$, there is $1/K$ probability that the algorithm
+guesses the correct label and with probability $(K-1)/K$ algorithm's guess is
+incorrect. Putting all the information together, we get that
 \begin{align*}
@@
 where the last inequality follows from \eqref{equation:strong-linear-separability-2}
-and \eqref{equation:strong-linear-separability-3} and case analysis whether $z_t = 0$ or $z_t = 1$.
+and \eqref{equation:strong-linear-separability-3} and analysis of the cases $z_t = 0$ and $z_t = 1$.
 Thus, after $U$ updates,
@@
 norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
-number of mistakes the algorithm makes is at least $\frac{K-1}{2} \lfloor
-\frac{1}{16} (R/\gamma)^2 \rfloor$.
+number of mistakes the algorithm makes is at least $\frac{K-1}{2} \left\lfloor
+\frac{1}{16} (R/\gamma)^2 \right\rfloor$.
 \end{theorem}
@@
 \begin{proof}
-We use probabilistic method. Let $M = \lfloor \frac{1}{16} (R/\gamma)^2 \rfloor$.
+We use probabilistic method. Let $M = \left\lfloor \frac{1}{16} (R/\gamma)^2 \right\rfloor$.
 Let $V = \R^{M+1}$ equipped with the standard inner product.  Let $e_1, e_2,
@@
 e.g.~\citep[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
-multivariate polynomials uniformly approximate any continuous function. In our
-case, we use multivariate polynomial to approximate the indicator function
-corresponding to the intersection of $K-1$ halfspaces. This polynomial separates
-examples in one class from examples in the other classes. To be able to quantify
-$R'$, $\gamma'$ and time complexities of evaluating $\phi(x)$ and $k(x,x')$, we
-need to quantify certain parameters of the approximating polynomial (degree,
-norm). We construct two different polynomials with different paremeters. The
-parameters are quantified in
+multivariate polynomials uniformly approximate any continuous function.
+Intuitively speaking, we use a multivariate polynomial to approximate, on the
+unit ball of $\R^d$, the indicator function corresponding to the intersection of
+$m=K-1$ halfspaces. Within margin $\gamma$ along the decision boundary, we allow
+the polynomial to attain arbitrary value. The polynomial separates examples in
+one class from examples in the other classes. To be able to quantify $R'$,
+$\gamma'$ and time complexities of evaluating $\phi(x)$ and $k(x,x')$, we need
+to quantify certain parameters of the approximating polynomial. We construct two
+different polynomials with different paremeters. The parameters are quantified
+in
 Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
@@
 \section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
-\label{section:proof-of-polynomial-approximation}.
+\label{section:proof-of-polynomial-approximation}
 
@@
 $$
-\frac{P_n(-z)}{P_n(z)} = \frac{1+x}{1-x} \prod_{i=1}^n \frac{(x+2^i)^2}{(x-2^i)^2} \ge 1 \; .
+\frac{P_n(-z)}{P_n(z)} = \frac{1+z}{1-z} \prod_{i=1}^n \frac{(z+2^i)^2}{(z-2^i)^2} \ge 1 \; .
 $$
@@
 \norm{w_i^{(t)}}^2$ in terms of number of mistakes.
-If a mistake happens in round $t$,
+If a mistake happens in round $t$ then
 \begin{align*}

### 2018-12-01 arxiv-version/main.tex
More work on polynomials

@@
 $$
-p(x) = \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_i}{x}}{\gamma} \right)
-- \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_i}{x}}{\gamma} \right) \; .
+p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
+- \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
 $$
@@
 $$
-p(x) = Q(x) \prod_{i=1}^m B_{s,r} \left( \frac{\ip{v_i}{x}}{\gamma} \right) \; .
+p(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
 $$
@@
 \begin{proposition}[Properties of $P_n$]
+\label{proposition:properties-of-p-n}
 \hspace{1cm} % Dummy space
@@
 To prove the first part, note that $P_n(z)$ and $P_n(-z)$ are non-positive for
-$z \in [0,1]$. If $z=1$ then $P_n(z)=P_n(-z) = 0$. For $z \in [0,1)$, we have
-$$
-\frac{P_n(-z)}{P_n(z)} = \frac{1+z}{1-z} \prod_{i=1}^n \frac{(z+2^i)^2}{(z-2^i)^2} \ge 1 \; .
-$$
-TODO
+$z \in [0,1]$. For $z=1$, $P_n(z) = 0$. For $z \in [0,1)$, we have
+$$
+\frac{P_n(-z)}{P_n(z)} = \frac{1+z}{1-z} \prod_{i=1}^n \frac{(z+2^i)^2}{(z-2^i)^2} \ge 1
+$$
+since each of the fractions is at least $1$.
+
+To prove the second part, notice that $P_n(z)$ is non-negative and $P_n(-z)$ is
+negative for any $z \in [1,2^n]$. Now, fix $z \in [1,2^n]$ and let $j \in
+\{1,2,\dots,n\}$ be such that $2^{j-1} \le z \le 2^j$. This implies that
+$(z+2^{j})^2 \ge 4 (z - 2^j)^2$. Therefore,
+$$
+\frac{-P_n(-z)}{P_n(z)}
+= \frac{1+z}{z-1} \cdot \frac{(z+2^j)^2}{(z-2^j)} \prod_{\substack{i ~:~ 1 \le i \le n \\ i \neq j}} \frac{(z+2^j)^2}{(z-2^j)}
+\ge 4 \;
+$$
+since one fraction is at least $4$ and all other fractions are at least $1$.
 \end{proof}
@@
 \begin{proposition}[Properties of $S_{n,k}$]
-\hspace{1cm} % Dummy space
+For any integer $n \ge 0$,
 \begin{enumerate}
-\item
+\item If $z \in [1,2^n]$ then $S_{n,r}(z) \in [1,1+\frac{1}{2m}]$.
+\item If $z \in [-2^n, -1]$ then $S_{n,r} \in [-1-\frac{1}{2m}, -1]$.
+\item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
+\item If $z \in [-2,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n-1)r}$
 \end{enumerate}
@@
 \begin{proof}
+Note that $B_{n,r}(z)$ is an even function and $A_{n,r}(z)$ is an odd function.
+Therefore, $S_{n,r}(z)$ is odd. Also notice that $r$ is an odd integer.
+
+\begin{enumerate}
+\item Observe that $S_{n,r}(z)$ can be written as
+$$
+S_{n,r}(z) = \frac{1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} \; .
+$$
+Let $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
+part 2 of~\autoref{proposition:properties-of-p-n}, $c \in [0,\frac{1}{4^r}] =
+[0,\frac{1}{4m+1}]$. Thus, $S_{n,r}(z) = \frac{1+c}{1-c} \in [1,1 +
+\frac{1}{2m}]$.
+
+\item The statement follows part 1 and the fact that $S_{n,r}(z)$ is odd.
+
+\item Observe that $S_{n,r}(z)$ can be written as
+$$
+S_{n,r}(z) = \frac{1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}
+$$
+and let $c = \left( - \frac{P_n(z)}{P_(-z)}\right)^r$. If $z \in [0,1]$, by part
+1 of~\autoref{proposition:properties-of-p-n} and the fact that $r$ is odd, $c
+\in [-1,0]$, and thus, $S_{n,r}(z) = \frac{1+c}{1-c} \in [0,1]$. Since
+$S_{n,r}(z)$ is odd, for $z \in [-1,0]$, $S_{n,r}(z) \in [-1,0]$.
+
+\item TODO
+
+\end{enumerate}
+\end{proof}
+
+Clearly, $\deg(A_{s,r}) = \deg(B_{s,r}) = (s+1)r$ and thus $\deg(p) = (s+1)rm$.
 TODO
-\end{proof}
 

### 2018-12-18 arxiv-version/main.tex
Fixes

@@
 particular round is chosen prior to algorithm's prediction in that
-round.\footnote{The reader can assume throughout the paper a simpler model of
+round.\footnote{All our results apply to also to a simpler model of
 the so called \emph{oblivious adversary} where the whole sequence of labeled
@@
 \textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
-\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}). The problem is quite
-natural and potential applications include online advertising and online content
-optimization where the feedback corresponds to a user's click.
+\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}). The bandit feedback
+version is a mathematically natural model and potential applications include
+online advertising and online content optimization where the binary feedback
+corresponds to a click.
 
@@
 change the input-output behavior of the algorithm, it only affects its time
-complexity.
+and memory complexity.
 
@@
 kernel. The crux of the problem is the analysis of the approximation properties
-of these mappings/kernels and the way margin in original space under standard
-linear separability notion gets transformed into a margin in the
+of these mappings/kernels and the way margin in the original space $\R^d$ under
+standard linear separability notion gets transformed into a margin in the
 high-dimensional space under the strong separability notion. This problem is
@@
 completeness, we give proofs of both of these results in
-Section~\ref{section:multiclass-perceptron-proofs}.
+Appendix~\ref{section:multiclass-perceptron-proofs}.
 
@@
 algorithm chooses one of them arbitrarily. If all copies make negative
-predictions, the algorithms makes a blind guess.
+predictions, the algorithms makes a uniformly random guess.
 
@@
 \STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
-\ELSE
-\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
-\ENDIF
 \STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
-\IF{$S_t = \emptyset$}
 \IF{$z_t = 1$}
@@
 \ELSE
+\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
+\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
 \IF{$z_t = 1$}
@@
 Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
-integer, $\gamma$ a positive real number, $R$ be a non-negative real number. If
+integer, let $\gamma$ a positive real number, let $R$ be a non-negative real number. If
 $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
@@
 
-Let $C$ be the number of times line 16 gets executed. Let $U$ be the number of
-times line 16 and line 21 get executed. In other words, $U$ is the number of
+Let $C$ be the number of times line 12 gets executed. Let $U$ be the number of
+times line 12 and line 19 get executed. In other words, $U$ is the number of
 times the $K$-tuple of vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets
@@
 we have
+\begingroup
+\allowdisplaybreaks
 \begin{align*}
@@
 \end{align*}
+\endgroup
 Therefore, after $U$ updates,
@@
 \end{proof}
+
+The upper bound $(K-1) \lfloor (R/\gamma)^2 \rfloor$ on the expected number of
+mistakes of
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
+optimal to within constant factor as long as the number of classes $K$ is
+at most $O((R/\gamma)^2)$. This is proved in
+\autoref{theorem:strongly-separable-example-mistake-lower-bound} below.
+
+Irrespective of any conditions on $K$, $R$, and $\gamma$, a trivial lower bound
+on the expected number of mistakes of any randomized algorithm is
+$\frac{K-1}{2}$. (Adversary chooses the same example over and over.) However, it
+is unclear if the trivial lower bound is the best possible if $K$ is large,
+i.e., $\omega((R/\gamma)^2)$. We leave this as an open problem.
 
@@
 
-In this section, we show how construct a mapping $\phi$ of points in the unit
+In this section, we show how to construct a mapping $\phi$ from the unit
 ball of $\R^d$ into a high dimensional inner product space that has the
-property if any set of labeled examples in the unit ball is linearly separable with a
+property if a set of labeled examples in the unit ball is linearly separable with a
 margin $\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
@@
 interpretation of the two regions described in parts 1 and 2 of the theorems is
-explained in Figure~\ref{figure:pizza-slice}.
+explained in Figure~\ref{figure:pizza-slice}. Similar but weaker results were
+proved by~\cite{Klivans-Servedio-2008}. In particular, we prove that the degrees
+of the polynomials, their norms, and their ``margins'' (parts 1 and 2 of theorems)
+are independent of the dimension $d$.
 

### 2018-12-18 arxiv-version/main.tex
Finish proof of properties of S_{n,r} and B_{n,r}

@@
 \item $p(x) \le -1$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-\item $\deg(p) \le ???$
+\item $\deg(p) \le m (2 \left\lceil \frac{1}{2} \log(4m + 1) \right\rceil + 1) (2 \left \lceil \log(1/\gamma) \right \rceil + 1)$
 \item $\norm{p} \le ???$
@@
 proved by~\cite{Klivans-Servedio-2008}. In particular, we prove that the degrees
-of the polynomials, their norms, and their ``margins'' (parts 1 and 2 of theorems)
-are independent of the dimension $d$.
+of the polynomials, their norms, and their ``margins'' (parts 1 and 2 of
+theorems) are independent of the dimension $d$.
 
@@
 $$
+Clearly, $\deg(P_n) = 2n+1$. Thus, $\deg(A_{n,k})$ and $\deg(B_{n,k})$ are at
+most  $(2n+1)k$, and therefore $\deg(p) \le m (2s+1) r$.
+
 For convenienence we define univariate rational function
@@
 \item If $z \in [1,2^n]$ then $0 \le 4P_n(z) \le -P_n(-z)$.
+\item If $z \ge 0$ then $-P_n(-z) \ge 2^{n(n-1)}$.
 \end{enumerate}
@@
 To prove the first part, note that $P_n(z)$ and $P_n(-z)$ are non-positive for
-$z \in [0,1]$. For $z=1$, $P_n(z) = 0$. For $z \in [0,1)$, we have
-$$
-\frac{P_n(-z)}{P_n(z)} = \frac{1+z}{1-z} \prod_{i=1}^n \frac{(z+2^i)^2}{(z-2^i)^2} \ge 1
-$$
-since each of the fractions is at least $1$.
+$z \in [0,1]$. We can write $\frac{P_n(z)}{P_n(-z)}$ as a product of $n+1$
+non-negative fractions
+$$
+\frac{P_n(z)}{P_n(-z)} = \frac{1-z}{1+z} \prod_{i=1}^n \frac{(z+2^i)^2}{(z-2^i)^2} \; .
+$$
+The first part follows from the observation that each fraction is upper bounded
+by $1$.
 
 To prove the second part, notice that $P_n(z)$ is non-negative and $P_n(-z)$ is
-negative for any $z \in [1,2^n]$. Now, fix $z \in [1,2^n]$ and let $j \in
+non-positive for any $z \in [1,2^n]$. Now, fix $z \in [1,2^n]$ and let $j \in
 \{1,2,\dots,n\}$ be such that $2^{j-1} \le z \le 2^j$. This implies that
-$(z+2^{j})^2 \ge 4 (z - 2^j)^2$. Therefore,
-$$
-\frac{-P_n(-z)}{P_n(z)}
-= \frac{1+z}{z-1} \cdot \frac{(z+2^j)^2}{(z-2^j)} \prod_{\substack{i ~:~ 1 \le i \le n \\ i \neq j}} \frac{(z+2^j)^2}{(z-2^j)}
-\ge 4 \;
-$$
-since one fraction is at least $4$ and all other fractions are at least $1$.
+$(z+2^{j})^2 \ge 4 (z - 2^j)^2$. We can write $\frac{P_n(z)}{-P_n(-z)}$ as a
+product of $n+1$ non-negative fractions
+$$
+\frac{P_n(z)}{-P_n(-z)}
+= \frac{z-1}{z+1} \cdot \frac{(z-2^j)^2}{(z+2^j)^2} \prod_{\substack{i ~:~ 1 \le i \le n \\ i \neq j}} \frac{(z-2^i)^2}{(z+2^i)^2} \; .
+$$
+The second part follows from the observation that the second fraction is upper
+bounded by $1/4$ and all other fractions are upper bounded by $1$.
+
+The third part follows from
+$$
+-P_n(-z) = (1+z) \prod_{i=1}^n (z+2^i)^2 \ge \prod_{i=1}^n 2^{2i} = 2^{n(n-1)} \; .
+$$
 \end{proof}
 
-\begin{proposition}[Properties of $S_{n,k}$]
-For any integer $n \ge 0$,
+\begin{proposition}[Properties of $S_{n,r}$ and $B_{n,r}$]
+For any integer $n \ge 0$ and $r = 2 \left\lceil \frac{1}{2} \log(4m + 1) \right\rceil + 1$,
 \begin{enumerate}
@@
 \item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
-\item If $z \in [-2,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n-1)r}$
+\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n-1)r}$.
 \end{enumerate}
@@
 $$
-S_{n,r}(z) = \frac{1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} \; .
-$$
-Let $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{proposition:properties-of-p-n}, $c \in [0,\frac{1}{4^r}] =
-[0,\frac{1}{4m+1}]$. Thus, $S_{n,r}(z) = \frac{1+c}{1-c} \in [1,1 +
-\frac{1}{2m}]$.
-
-\item The statement follows part 1 and the fact that $S_{n,r}(z)$ is odd.
+S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
+$$
+where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
+part 2 of~\autoref{proposition:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. By
+the definition of $r$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
+$S_{n,r}(z) = \frac{1+c}{1-c} \in [1,1 + \frac{1}{2m}]$.
+
+\item Since $S_{n,r}(z)$ is odd, the statement follows from part 1.
 
@@
 $$
-S_{n,r}(z) = \frac{1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}
-$$
-and let $c = \left( - \frac{P_n(z)}{P_(-z)}\right)^r$. If $z \in [0,1]$, by part
+S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
+$$
+where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. If $z \in [0,1]$, by part
 1 of~\autoref{proposition:properties-of-p-n} and the fact that $r$ is odd, $c
@@
 
-\item TODO
-
+\item Since $B_{n,r}(z)$ is even, we can without loss generality assume that $z \ge
+0$. We consider two cases.
+
+Case $z \in [0,1]$. Since $r$ is odd and $P_n(z)$ is non-positive,
+$$
+B_{n,r}(z) = - (P_n(z))^r + \left(- P_{n}(-z)\right)^r \ge \left(- P_{n}(-z)\right)^r \ge 2^{n(n-1)r} \ge 2^{n(n-1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
+$$
+where the second last inequality follows from part 3 of \autoref{proposition:properties-of-p-n}.
+
+Case $z \in [1,2^n]$. Since $r$ is odd,
+$$
+B_{n,r}(z) = \left(- P_{n}(-z)\right)^r \left(1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r \right) = \left(- P_{n}(-z)\right)^r (1 - c)
+$$
+where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
+part 2 of~\autoref{proposition:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. By
+the definition of $r$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
+$$
+B_{n,r}(z) \ge \left(- P_{n}(-z)\right)^r \left( 1 - \frac{1}{4m+1} \right) \ge 2^{n(n-1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
+$$
+where the last inequality follows from part 3 of \autoref{proposition:properties-of-p-n}.
 \end{enumerate}
@@
 
-Clearly, $\deg(A_{s,r}) = \deg(B_{s,r}) = (s+1)r$ and thus $\deg(p) = (s+1)rm$.
 TODO

### 2018-12-18 arxiv-version/main.tex
Reduce to rational approximation

@@
 Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
-\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma > 0$. There exists a
+\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$. There exists a
 multivariate polynomial $p:\R^d \to \R$ such that
 \begin{enumerate}
-\item $p(x) \ge 1$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-\item $p(x) \le -1$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-\item $\deg(p) \le m (2 \left\lceil \frac{1}{2} \log(4m + 1) \right\rceil + 1) (2 \left \lceil \log(1/\gamma) \right \rceil + 1)$
+\item $\displaystyle p(x) \ge m^{\frac{1}{2} m \log^2(1/\gamma)}$
+for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
+
+\item $\displaystyle p(x) \le - m^{\frac{1}{2} m \log^2(1/\gamma)}$
+for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
+
+\item $\deg(p) \le m (2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1) (2 \left \lceil \log(1/\gamma) \right \rceil + 1)$
 \item $\norm{p} \le ???$
@@
 Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
-\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma > 0$. There exists a
+\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$. There exists a
 multivariate polynomial $p:\R^d \to \R$ such that
@@
 \end{align*}
-Let $r = 2 \left\lceil \frac{1}{2} \log(4m + 1) \right\rceil + 1$ and $s = \left \lceil \log(1/\gamma) \right \rceil$.
+Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$ and $s = \left \lceil \log(1/\gamma) \right \rceil$.
 We define the polynomial $p:\R^d \to \R$ as
@@
 \item If $z \in [1,2^n]$ then $0 \le 4P_n(z) \le -P_n(-z)$.
-\item If $z \ge 0$ then $-P_n(-z) \ge 2^{n(n-1)}$.
+\item If $z \ge 0$ then $-P_n(-z) \ge 2^{n(n+1)}$.
 \end{enumerate}
@@
 $$
--P_n(-z) = (1+z) \prod_{i=1}^n (z+2^i)^2 \ge \prod_{i=1}^n 2^{2i} = 2^{n(n-1)} \; .
+-P_n(-z) = (1+z) \prod_{i=1}^n (z+2^i)^2 \ge \prod_{i=1}^n 2^{2i} = 2^{n(n+1)} \; .
 $$
@@
 \begin{proposition}[Properties of $S_{n,r}$ and $B_{n,r}$]
-For any integer $n \ge 0$ and $r = 2 \left\lceil \frac{1}{2} \log(4m + 1) \right\rceil + 1$,
+\label{proposition:properties-of-s-n-r}
+For any integer $n \ge 0$ and $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$,
 \begin{enumerate}
@@
 \item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
-\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n-1)r}$.
+\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
 \end{enumerate}
@@
 where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{proposition:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. By
-the definition of $r$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
+part 2 of~\autoref{proposition:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. Since
+$r \ge \frac{1}{2} \log_2(4m+1)$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
 $S_{n,r}(z) = \frac{1+c}{1-c} \in [1,1 + \frac{1}{2m}]$.
@@
 $$
-B_{n,r}(z) = - (P_n(z))^r + \left(- P_{n}(-z)\right)^r \ge \left(- P_{n}(-z)\right)^r \ge 2^{n(n-1)r} \ge 2^{n(n-1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
+B_{n,r}(z) = - (P_n(z))^r + \left(- P_{n}(-z)\right)^r \ge \left(- P_{n}(-z)\right)^r \ge 2^{n(n+1)r} \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
 $$
@@
 $$
-B_{n,r}(z) \ge \left(- P_{n}(-z)\right)^r \left( 1 - \frac{1}{4m+1} \right) \ge 2^{n(n-1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
+B_{n,r}(z) \ge \left(- P_{n}(-z)\right)^r \left( 1 - \frac{1}{4m+1} \right) \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
 $$
@@
 \end{proof}
+
+To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-1}
+note that \autoref{proposition:properties-of-s-n-r} implies that
+\begin{align*}
+|p(x)|
+& = |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
+& \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
+& \ge |Q(x)| \cdot 2^{s(s+1)rm} e^{-4} && \text{(since $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4}$)} \\
+& \ge 4 |Q(x)| \cdot 2^{s^2rm} && \text{(since $e^{-4} \ge 1/2$ and $2^{rms} \ge 8$)} \\
+& \ge 4 |Q(x)| \cdot (4m+1)^{s^2m/2} && \text{(since $r \ge 1 + \frac{1}{2} \log_2(4m+1)$)} \\
+& \ge 2 |Q(x)| \cdot m^{s^2m/2} \; .
+\end{align*}
+It thus remains to prove that
+\begin{align}
+Q(x) & \ge \frac{1}{2} && \text{for all} \ x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\} \; , \\
+Q(x) & \le -\frac{1}{2} && \text{for all} \ x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\} \; .
+\end{align}
 

### 2018-12-18 arxiv-version/main.tex
Fixes

@@
 \label{proposition:properties-of-s-n-r}
-For any integer $n \ge 0$ and $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$,
+Let $n,m$ be non-negative integers.
+Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$. Then,
 \begin{enumerate}
@@
 \end{align*}
-It thus remains to prove that
+Since $p(x)$ and $Q(x)$ have the same sign, it remains to prove that
 \begin{align}
+\label{equation:rational-margin-1}
 Q(x) & \ge \frac{1}{2} && \text{for all} \ x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\} \; , \\
+\label{equation:rational-margin-2}
 Q(x) & \le -\frac{1}{2} && \text{for all} \ x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\} \; .
 \end{align}
-
+Consider any $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$. Then,
+$\frac{\ip{v_i}{x}}{\gamma} \in [1, \frac{1}{\gamma}]$.
+By part 1 of \autoref{proposition:properties-of-s-n-r}, $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \in [1, 1 + \frac{1}{2m}]$
+and in particular $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \ge 1$.
+Thus, $Q(x) = \left( \sum_{i=1}^m S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \right) - (m - 1/2) \ge m - (m - 1/2) = 1/2$.
+
+Consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
+Observe that $\frac{\ip{v_i}{x}}{\gamma} \in [-\frac{1}{\gamma}, \frac{1}{\gamma}]$.
 TODO

### 2018-12-19 arxiv-version/main.tex
Finish margin separation for rational function

--- 2018-12-18 arxiv-version/main.tex
@@
 
-\begin{proposition}[Properties of $P_n$]
-\label{proposition:properties-of-p-n}
+\begin{lemma}[Properties of $P_n$]
+\label{lemma:properties-of-p-n}
 \hspace{1cm} % Dummy space
@@
 \end{enumerate}
-\end{proposition}
+\end{lemma}
 
@@
 
-\begin{proposition}[Properties of $S_{n,r}$ and $B_{n,r}$]
-\label{proposition:properties-of-s-n-r}
-For any integer $n \ge 0$ and $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$,
+\begin{lemma}[Properties of $S_{n,r}$ and $B_{n,r}$]
+\label{lemma:properties-of-s-n-r}
+Let $n,m$ be non-negative integers.
+Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$. Then,
 \begin{enumerate}
@@
 where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{proposition:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. Since
+part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. Since
 $r \ge \frac{1}{2} \log_2(4m+1)$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
@@
 where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. If $z \in [0,1]$, by part
-1 of~\autoref{proposition:properties-of-p-n} and the fact that $r$ is odd, $c
+1 of~\autoref{lemma:properties-of-p-n} and the fact that $r$ is odd, $c
 \in [-1,0]$, and thus, $S_{n,r}(z) = \frac{1+c}{1-c} \in [0,1]$. Since
@@
 $$
-where the second last inequality follows from part 3 of \autoref{proposition:properties-of-p-n}.
+where the second last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
 
@@
 where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{proposition:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. By
+part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. By
 the definition of $r$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
@@
 $$
-where the last inequality follows from part 3 of \autoref{proposition:properties-of-p-n}.
+where the last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
 \end{enumerate}
@@
 
+\begin{lemma}[Properties of $Q(x)$]
+\label{lemma:properties-of-q}
+The rational function $Q(x)$ satisfies
+\begin{enumerate}
+\item $Q(x) \ge \frac{1}{2}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
+\item $Q(x) \le -\frac{1}{2}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+To prove part 1, consider any $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \
+\ip{v_i}{x} \ge \gamma \right\}$. Then, $\frac{\ip{v_i}{x}}{\gamma} \in [1,
+\frac{1}{\gamma}]$. By part 1 of \autoref{lemma:properties-of-s-n-r},
+$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \in [1, 1 + \frac{1}{2m}]$ and
+in particular $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \ge 1$. Thus,
+$$
+Q(x) = \left( \sum_{i=1}^m S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \right) - (m - 1/2) \ge m - (m - 1/2) = 1/2 \; .
+$$
+
+To prove part 2, consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~
+\norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Observe that
+$\frac{\ip{v_i}{x}}{\gamma} \in [-\frac{1}{\gamma}, \frac{1}{\gamma}]$. Consider
+$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right)$ for any $i \in
+\{1,2,\dots,m\}$. Parts 1,2, and 3 of \autoref{lemma:properties-of-s-n-r}
+and the fact $1/\gamma \le 2^s$ imply that
+$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \le 1 +
+\frac{1}{2m}$ for all $i \in \{1,2,\dots,m\}$. By the choice of $x$, there
+exists $j \in \{1,2,\dots,m\}$ such that $\ip{v_j}{x} \le - \gamma$. Part 2 of
+\autoref{lemma:properties-of-s-n-r} implies that
+$S_{s,r}\left(\frac{\ip{v_j}{x}}{\gamma}\right) \in [-1-\frac{1}{2m},-1]$. Thus,
+\begin{align*}
+Q(x)
+& = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
+& = S_{s,r}\left( \frac{\ip{v_j}{x}}{\gamma} \right) + \left( \sum_{\substack{i ~:~ 1 \le i \le m \\ i \neq j}} S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
+& \le -1 + (m-1) \left( 1 + \frac{1}{2m} \right) - \left(m - \frac{1}{2} \right) \\
+& \le 1/2 \; .
+\end{align*}
+\end{proof}
+
 To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-1}
-note that \autoref{proposition:properties-of-s-n-r} implies that
+first note that part 4 of \autoref{lemma:properties-of-s-n-r} implies that
+for any $x$ such that $\norm{x} \le 1$,
+$B_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right)$ is positive.
+Thus $p(x)$ and $Q(x)$ have the same sign on the unit ball.
+\autoref{lemma:properties-of-q} states that $Q(x) \ge 1/2$
+and $Q(x) \le -1/2$ in the two respective regions of the unit ball.
+It remains to show that $|p(x)| \ge m^{s^2m/2}$ in those regions.
+Consider any $x$ in either
+$\displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
+or in $\displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
+Then,
 \begin{align*}
@@
 & \ge 4 |Q(x)| \cdot (4m+1)^{s^2m/2} && \text{(since $r \ge 1 + \frac{1}{2} \log_2(4m+1)$)} \\
-& \ge 2 |Q(x)| \cdot m^{s^2m/2} \; .
-\end{align*}
-It thus remains to prove that
-\begin{align}
-Q(x) & \ge \frac{1}{2} && \text{for all} \ x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\} \; , \\
-Q(x) & \le -\frac{1}{2} && \text{for all} \ x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\} \; .
-\end{align}
-
+& \ge 2 |Q(x)| \cdot m^{s^2m/2} \\
+& \ge m^{s^2m/2} && \text{(\autoref{lemma:properties-of-q})} \; .
+\end{align*}
 TODO

### 2018-12-19 arxiv-version/main.tex
Start upper bounding the norm

@@
 \begin{enumerate}
-\item $\displaystyle p(x) \ge m^{\frac{1}{2} m \log^2(1/\gamma)}$
+\item $\displaystyle p(x) \ge m^{\frac{1}{2} m (\log_2(1/\gamma))^2}$
 for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
 
-\item $\displaystyle p(x) \le - m^{\frac{1}{2} m \log^2(1/\gamma)}$
+\item $\displaystyle p(x) \le - m^{\frac{1}{2} m (\log_2(1/\gamma))^2}$
 for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
 
-\item $\deg(p) \le m (2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1) (2 \left \lceil \log(1/\gamma) \right \rceil + 1)$
+\item $\deg(p) \le m (2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1) (2 \left \lceil \log_2(1/\gamma) \right \rceil + 1)$
 \item $\norm{p} \le ???$
@@
 
-To prove the first part, we express $p_j$ as
+To prove the part 1, we express $p_j$ as
 $$
@@
 
-The second part follows from the first part by setting $p_1 = p_2 = \dots p_n = q$.
-
-To prove the third part we use generalized triangle inequality and
+Part 2 follows from the part 1 by setting $p_1 = p_2 = \dots p_n = q$.
+
+To prove the part 3, we use generalized triangle inequality and
 \autoref{lemma:simple-inequality}. We have
@@
 \end{align*}
-Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$ and $s = \left \lceil \log(1/\gamma) \right \rceil$.
+Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$ and $s = \left \lceil \log_2(1/\gamma) \right \rceil$.
 We define the polynomial $p:\R^d \to \R$ as
@@
 $$
-Clearly, $\deg(P_n) = 2n+1$. Thus, $\deg(A_{n,k})$ and $\deg(B_{n,k})$ are at
-most  $(2n+1)k$, and therefore $\deg(p) \le m (2s+1) r$.
 
@@
 \end{align*}
-TODO
+
+To prove part 3 of \autoref{theorem:polynomial-approximation-1} note that
+$\deg(P_n) = 2n+1$. Thus, $\deg(A_{n,k})$ and $\deg(B_{n,k})$ are at most
+$(2n+1)k$. Therefore $\deg(p) \le m (2s+1) r$.
+
+It remains to prove part 4 of \autoref{theorem:polynomial-approximation-1}.
+For any $i \in \{0,1,2,\dots,s\}$ and any $v \in \R^d$ such that $\norm{v} \le 1$
+define multivariate polynomials
+\begin{align*}
+f_{i,v}(x) & = \frac{\ip{v}{x}}{\gamma} - 2^i \; , \\
+q_v(x) & = P_s \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
+a_v(x) & = A_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
+b_v(x) & = B_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; .
+\end{align*}
+Note that
+$$
+p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
+$$
+We bound the norms of these polynomials. We have
+$$
+\norm{f_{i,v}}^2 = \norm{v}^2/\gamma^2 + 2^{2i} \le 2 \cdot 2^s \; .
+$$
+where we used that $1/\gamma \le 2^s$ and $\norm{v} \le 1$.
+Since $q_v(x) = f_{i,v}(\frac{\ip{v}{x}}{\gamma}) \prod_{i=1}^s \left(f_{i,v}(\frac{\ip{v}{x}})\right)^2$,
+using part 1 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $q_v$
+as
+$$
+\norm{q_v}^2 \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \le  (2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \; .
+$$
+Using parts 3 and 2 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $a_v$ as
+\begin{align*}
+\norm{a_v}^2
+& \le 2\norm{(q_v)^r}^2 + 2\norm{(q_{-v})^r}^2 \\
+& \le 2 r^{r(2s+1)} \norm{q_v}^{2r} + 2 r^{r(2s+1)} \norm{q_{-v}}^{2r} \\
+& \le 4 r^{r(2s+1)} \left((2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \right)^{2r} \; .
+\end{align*}
+The same upper bound holds for $\norm{b_v}^2$. Finally,
+\begin{align*}
+\norm{p}
+& \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
+& \le \left[ \sum_{i=1}^m m^{???/2} \norm{a_{v_i}} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} \norm{b_{v_j}} \right] + \left(m - \frac{1}{2} \right) m^{???/2} \prod_{j=1}^m \norm{b_{v_j}} \\
+& \le (2m-1/2) m^{???/2} \norm{a_v}^m 
+\end{align*}
 

### 2018-12-20 arxiv-version/main.tex
Finished proof of polynomial approximation

@@
 \begin{enumerate}
-\item $\displaystyle p(x) \ge m^{\frac{1}{2} m (\log_2(1/\gamma))^2}$
-for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-
-\item $\displaystyle p(x) \le - m^{\frac{1}{2} m (\log_2(1/\gamma))^2}$
-for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-
-\item $\deg(p) \le m (2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1) (2 \left \lceil \log_2(1/\gamma) \right \rceil + 1)$
-\item $\norm{p} \le ???$
-\end{enumerate}
-\end{theorem}
-
-\begin{theorem}[Polynomial approximation of intersection of halfspaces II]
-\label{theorem:polynomial-approximation-2}
-Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
-\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$. There exists a
-multivariate polynomial $p:\R^d \to \R$ such that
-\begin{enumerate}
 \item $p(x) \ge 1/2$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
@@
 
+\begin{theorem}[Polynomial approximation of intersection of halfspaces II]
+\label{theorem:polynomial-approximation-2}
+Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
+\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$.
+Define
+$$
+r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1 \qquad \text{and} \qquad s = \left \lceil \log_2(1/\gamma) \right \rceil \; .
+$$
+Then, there exists a multivariate polynomial $p:\R^d \to \R$ such that
+\begin{enumerate}
+\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$
+for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
+
+\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$
+for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
+
+\item $\deg(p) \le (2s+1) rm$
+\item $\norm{p} \le (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm}$
+\end{enumerate}
+\end{theorem}
+
 The proofs of the theorems can be found in
@@
 explained in Figure~\ref{figure:pizza-slice}. Similar but weaker results were
-proved by~\cite{Klivans-Servedio-2008}. In particular, we prove that the degrees
-of the polynomials, their norms, and their ``margins'' (parts 1 and 2 of
-theorems) are independent of the dimension $d$.
+proved by~\cite{Klivans-Servedio-2008}. In particular, the bounds in parts
+1, 2, 3, 4 of the theorems are independent of the dimension $d$.
 
@@
 
-We define several univariate polynomials
-\begin{align*}
-P_n(z) & = (z - 1) \prod_{i=1}^n (z - 2^i)^2 && \text{for $n \ge 0$,} \\
-A_{n,k}(z) & = (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$,} \\
-B_{n,k}(z) & = - (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$.}
-\end{align*}
-Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$ and $s = \left \lceil \log_2(1/\gamma) \right \rceil$.
-We define the polynomial $p:\R^d \to \R$ as
-$$
-p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
-- \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-$$
-
-For convenienence we define univariate rational function
-\begin{align*}
-S_{n,k}(z) & = \frac{A_{n,k}(z)}{B_{n,k}(z)} && \text{for $n,k \ge 0$,}
-\end{align*}
-and a multivariate rational function
-$$
-Q(x) = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \; .
-$$
-It easy to verify that
-$$
-p(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-$$
-
-\begin{lemma}[Properties of $P_n$]
-\label{lemma:properties-of-p-n}
-\hspace{1cm} % Dummy space
-\begin{enumerate}
-\item If $z \in [0,1]$ then $P_n(-z) \le P_n(z) \le 0$.
-\item If $z \in [1,2^n]$ then $0 \le 4P_n(z) \le -P_n(-z)$.
-\item If $z \ge 0$ then $-P_n(-z) \ge 2^{n(n+1)}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-To prove the first part, note that $P_n(z)$ and $P_n(-z)$ are non-positive for
-$z \in [0,1]$. We can write $\frac{P_n(z)}{P_n(-z)}$ as a product of $n+1$
-non-negative fractions
-$$
-\frac{P_n(z)}{P_n(-z)} = \frac{1-z}{1+z} \prod_{i=1}^n \frac{(z+2^i)^2}{(z-2^i)^2} \; .
-$$
-The first part follows from the observation that each fraction is upper bounded
-by $1$.
-
-To prove the second part, notice that $P_n(z)$ is non-negative and $P_n(-z)$ is
-non-positive for any $z \in [1,2^n]$. Now, fix $z \in [1,2^n]$ and let $j \in
-\{1,2,\dots,n\}$ be such that $2^{j-1} \le z \le 2^j$. This implies that
-$(z+2^{j})^2 \ge 4 (z - 2^j)^2$. We can write $\frac{P_n(z)}{-P_n(-z)}$ as a
-product of $n+1$ non-negative fractions
-$$
-\frac{P_n(z)}{-P_n(-z)}
-= \frac{z-1}{z+1} \cdot \frac{(z-2^j)^2}{(z+2^j)^2} \prod_{\substack{i ~:~ 1 \le i \le n \\ i \neq j}} \frac{(z-2^i)^2}{(z+2^i)^2} \; .
-$$
-The second part follows from the observation that the second fraction is upper
-bounded by $1/4$ and all other fractions are upper bounded by $1$.
-
-The third part follows from
-$$
--P_n(-z) = (1+z) \prod_{i=1}^n (z+2^i)^2 \ge \prod_{i=1}^n 2^{2i} = 2^{n(n+1)} \; .
-$$
-\end{proof}
-
-\begin{lemma}[Properties of $S_{n,r}$ and $B_{n,r}$]
-\label{lemma:properties-of-s-n-r}
-Let $n,m$ be non-negative integers.
-Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$. Then,
-\begin{enumerate}
-\item If $z \in [1,2^n]$ then $S_{n,r}(z) \in [1,1+\frac{1}{2m}]$.
-\item If $z \in [-2^n, -1]$ then $S_{n,r} \in [-1-\frac{1}{2m}, -1]$.
-\item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
-\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-Note that $B_{n,r}(z)$ is an even function and $A_{n,r}(z)$ is an odd function.
-Therefore, $S_{n,r}(z)$ is odd. Also notice that $r$ is an odd integer.
-
-\begin{enumerate}
-\item Observe that $S_{n,r}(z)$ can be written as
-$$
-S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. Since
-$r \ge \frac{1}{2} \log_2(4m+1)$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
-$S_{n,r}(z) = \frac{1+c}{1-c} \in [1,1 + \frac{1}{2m}]$.
-
-\item Since $S_{n,r}(z)$ is odd, the statement follows from part 1.
-
-\item Observe that $S_{n,r}(z)$ can be written as
-$$
-S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. If $z \in [0,1]$, by part
-1 of~\autoref{lemma:properties-of-p-n} and the fact that $r$ is odd, $c
-\in [-1,0]$, and thus, $S_{n,r}(z) = \frac{1+c}{1-c} \in [0,1]$. Since
-$S_{n,r}(z)$ is odd, for $z \in [-1,0]$, $S_{n,r}(z) \in [-1,0]$.
-
-\item Since $B_{n,r}(z)$ is even, we can without loss generality assume that $z \ge
-0$. We consider two cases.
-
-Case $z \in [0,1]$. Since $r$ is odd and $P_n(z)$ is non-positive,
-$$
-B_{n,r}(z) = - (P_n(z))^r + \left(- P_{n}(-z)\right)^r \ge \left(- P_{n}(-z)\right)^r \ge 2^{n(n+1)r} \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
-where the second last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
-
-Case $z \in [1,2^n]$. Since $r$ is odd,
-$$
-B_{n,r}(z) = \left(- P_{n}(-z)\right)^r \left(1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r \right) = \left(- P_{n}(-z)\right)^r (1 - c)
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. By
-the definition of $r$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
-$$
-B_{n,r}(z) \ge \left(- P_{n}(-z)\right)^r \left( 1 - \frac{1}{4m+1} \right) \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
-where the last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
-\end{enumerate}
-\end{proof}
-
-\begin{lemma}[Properties of $Q(x)$]
-\label{lemma:properties-of-q}
-The rational function $Q(x)$ satisfies
-\begin{enumerate}
-\item $Q(x) \ge \frac{1}{2}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
-\item $Q(x) \le -\frac{1}{2}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-To prove part 1, consider any $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \
-\ip{v_i}{x} \ge \gamma \right\}$. Then, $\frac{\ip{v_i}{x}}{\gamma} \in [1,
-\frac{1}{\gamma}]$. By part 1 of \autoref{lemma:properties-of-s-n-r},
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \in [1, 1 + \frac{1}{2m}]$ and
-in particular $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \ge 1$. Thus,
-$$
-Q(x) = \left( \sum_{i=1}^m S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \right) - (m - 1/2) \ge m - (m - 1/2) = 1/2 \; .
-$$
-
-To prove part 2, consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~
-\norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Observe that
-$\frac{\ip{v_i}{x}}{\gamma} \in [-\frac{1}{\gamma}, \frac{1}{\gamma}]$. Consider
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right)$ for any $i \in
-\{1,2,\dots,m\}$. Parts 1,2, and 3 of \autoref{lemma:properties-of-s-n-r}
-and the fact $1/\gamma \le 2^s$ imply that
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \le 1 +
-\frac{1}{2m}$ for all $i \in \{1,2,\dots,m\}$. By the choice of $x$, there
-exists $j \in \{1,2,\dots,m\}$ such that $\ip{v_j}{x} \le - \gamma$. Part 2 of
-\autoref{lemma:properties-of-s-n-r} implies that
-$S_{s,r}\left(\frac{\ip{v_j}{x}}{\gamma}\right) \in [-1-\frac{1}{2m},-1]$. Thus,
-\begin{align*}
-Q(x)
-& = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& = S_{s,r}\left( \frac{\ip{v_j}{x}}{\gamma} \right) + \left( \sum_{\substack{i ~:~ 1 \le i \le m \\ i \neq j}} S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& \le -1 + (m-1) \left( 1 + \frac{1}{2m} \right) - \left(m - \frac{1}{2} \right) \\
-& \le 1/2 \; .
-\end{align*}
-\end{proof}
-
-To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-1}
-first note that part 4 of \autoref{lemma:properties-of-s-n-r} implies that
-for any $x$ such that $\norm{x} \le 1$,
-$B_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right)$ is positive.
-Thus $p(x)$ and $Q(x)$ have the same sign on the unit ball.
-\autoref{lemma:properties-of-q} states that $Q(x) \ge 1/2$
-and $Q(x) \le -1/2$ in the two respective regions of the unit ball.
-It remains to show that $|p(x)| \ge m^{s^2m/2}$ in those regions.
-Consider any $x$ in either
-$\displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-or in $\displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
-Then,
-\begin{align*}
-|p(x)|
-& = |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
-& \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
-& \ge |Q(x)| \cdot 2^{s(s+1)rm} e^{-4} && \text{(since $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4}$)} \\
-& \ge 4 |Q(x)| \cdot 2^{s^2rm} && \text{(since $e^{-4} \ge 1/2$ and $2^{rms} \ge 8$)} \\
-& \ge 4 |Q(x)| \cdot (4m+1)^{s^2m/2} && \text{(since $r \ge 1 + \frac{1}{2} \log_2(4m+1)$)} \\
-& \ge 2 |Q(x)| \cdot m^{s^2m/2} \\
-& \ge m^{s^2m/2} && \text{(\autoref{lemma:properties-of-q})} \; .
-\end{align*}
-
-To prove part 3 of \autoref{theorem:polynomial-approximation-1} note that
-$\deg(P_n) = 2n+1$. Thus, $\deg(A_{n,k})$ and $\deg(B_{n,k})$ are at most
-$(2n+1)k$. Therefore $\deg(p) \le m (2s+1) r$.
-
-It remains to prove part 4 of \autoref{theorem:polynomial-approximation-1}.
-For any $i \in \{0,1,2,\dots,s\}$ and any $v \in \R^d$ such that $\norm{v} \le 1$
-define multivariate polynomials
-\begin{align*}
-f_{i,v}(x) & = \frac{\ip{v}{x}}{\gamma} - 2^i \; , \\
-q_v(x) & = P_s \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
-a_v(x) & = A_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
-b_v(x) & = B_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; .
-\end{align*}
-Note that
-$$
-p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
-$$
-We bound the norms of these polynomials. We have
-$$
-\norm{f_{i,v}}^2 = \norm{v}^2/\gamma^2 + 2^{2i} \le 2 \cdot 2^s \; .
-$$
-where we used that $1/\gamma \le 2^s$ and $\norm{v} \le 1$.
-Since $q_v(x) = f_{i,v}(\frac{\ip{v}{x}}{\gamma}) \prod_{i=1}^s \left(f_{i,v}(\frac{\ip{v}{x}})\right)^2$,
-using part 1 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $q_v$
-as
-$$
-\norm{q_v}^2 \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \le  (2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \; .
-$$
-Using parts 3 and 2 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $a_v$ as
-\begin{align*}
-\norm{a_v}^2
-& \le 2\norm{(q_v)^r}^2 + 2\norm{(q_{-v})^r}^2 \\
-& \le 2 r^{r(2s+1)} \norm{q_v}^{2r} + 2 r^{r(2s+1)} \norm{q_{-v}}^{2r} \\
-& \le 4 r^{r(2s+1)} \left((2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \right)^{2r} \; .
-\end{align*}
-The same upper bound holds for $\norm{b_v}^2$. Finally,
-\begin{align*}
-\norm{p}
-& \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
-& \le \left[ \sum_{i=1}^m m^{???/2} \norm{a_{v_i}} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} \norm{b_{v_j}} \right] + \left(m - \frac{1}{2} \right) m^{???/2} \prod_{j=1}^m \norm{b_{v_j}} \\
-& \le (2m-1/2) m^{???/2} \norm{a_v}^m 
-\end{align*}
-
-\subsection{Proof of \autoref{theorem:polynomial-approximation-2}}
-\label{section:proof-of-polynomial-approximation-2}
-
 To construct the polynomial $p$ we use Chebyshev polynomials of the first kind.
@@
 Then,
+\begingroup
+\allowdisplaybreaks
 \begin{align*}
@@
 & = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
-& \le \left(8(1+\sqrt{2})^2 s \right)^s & \text{(since $s+1 \le 2^s$ for any integers $s \ge 0$)} \\
+& \le \left(8(1+\sqrt{2})^2 s \right)^s & \text{(since $s+1 \le 2^s$ for any integer $s \ge 0$)} \\
 & \le \left(47 s \right)^s \; .
 \end{align*}
+\endgroup
 Finally,
@@
 Substituting for $r$ and $s$ finishes the proof.
+
+\subsection{Proof of \autoref{theorem:polynomial-approximation-2}}
+\label{section:proof-of-polynomial-approximation-2}
+
+We define several univariate polynomials
+\begin{align*}
+P_n(z) & = (z - 1) \prod_{i=1}^n (z - 2^i)^2 && \text{for $n \ge 0$,} \\
+A_{n,k}(z) & = (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$,} \\
+B_{n,k}(z) & = - (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$.}
+\end{align*}
+We define the polynomial $p:\R^d \to \R$ as
+$$
+p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
+- \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
+$$
+
+For convenienence we define univariate rational function
+\begin{align*}
+S_{n,k}(z) & = \frac{A_{n,k}(z)}{B_{n,k}(z)} && \text{for $n,k \ge 0$,}
+\end{align*}
+and a multivariate rational function
+$$
+Q(x) = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \; .
+$$
+It easy to verify that
+$$
+p(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
+$$
+
+\begin{lemma}[Properties of $P_n$]
+\label{lemma:properties-of-p-n}
+\hspace{1cm} % Dummy space
+\begin{enumerate}
+\item If $z \in [0,1]$ then $P_n(-z) \le P_n(z) \le 0$.
+\item If $z \in [1,2^n]$ then $0 \le 4P_n(z) \le -P_n(-z)$.
+\item If $z \ge 0$ then $-P_n(-z) \ge 2^{n(n+1)}$.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+To prove the first part, note that $P_n(z)$ and $P_n(-z)$ are non-positive for
+$z \in [0,1]$. We can write $\frac{P_n(z)}{P_n(-z)}$ as a product of $n+1$
+non-negative fractions
+$$
+\frac{P_n(z)}{P_n(-z)} = \frac{1-z}{1+z} \prod_{i=1}^n \frac{(z+2^i)^2}{(z-2^i)^2} \; .
+$$
+The first part follows from the observation that each fraction is upper bounded
+by $1$.
+
+To prove the second part, notice that $P_n(z)$ is non-negative and $P_n(-z)$ is
+non-positive for any $z \in [1,2^n]$. Now, fix $z \in [1,2^n]$ and let $j \in
+\{1,2,\dots,n\}$ be such that $2^{j-1} \le z \le 2^j$. This implies that
+$(z+2^{j})^2 \ge 4 (z - 2^j)^2$. We can write $\frac{P_n(z)}{-P_n(-z)}$ as a
+product of $n+1$ non-negative fractions
+$$
+\frac{P_n(z)}{-P_n(-z)}
+= \frac{z-1}{z+1} \cdot \frac{(z-2^j)^2}{(z+2^j)^2} \prod_{\substack{i ~:~ 1 \le i \le n \\ i \neq j}} \frac{(z-2^i)^2}{(z+2^i)^2} \; .
+$$
+The second part follows from the observation that the second fraction is upper
+bounded by $1/4$ and all other fractions are upper bounded by $1$.
+
+The third part follows from
+$$
+-P_n(-z) = (1+z) \prod_{i=1}^n (z+2^i)^2 \ge \prod_{i=1}^n 2^{2i} = 2^{n(n+1)} \; .
+$$
+\end{proof}
+
+\begin{lemma}[Properties of $S_{n,r}$ and $B_{n,r}$]
+\label{lemma:properties-of-s-n-r}
+Let $n,m$ be non-negative integers.
+Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$. Then,
+\begin{enumerate}
+\item If $z \in [1,2^n]$ then $S_{n,r}(z) \in [1,1+\frac{1}{2m}]$.
+\item If $z \in [-2^n, -1]$ then $S_{n,r} \in [-1-\frac{1}{2m}, -1]$.
+\item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
+\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+Note that $B_{n,r}(z)$ is an even function and $A_{n,r}(z)$ is an odd function.
+Therefore, $S_{n,r}(z)$ is odd. Also notice that $r$ is an odd integer.
+
+\begin{enumerate}
+\item Observe that $S_{n,r}(z)$ can be written as
+$$
+S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
+$$
+where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
+part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. Since
+$r \ge \frac{1}{2} \log_2(4m+1)$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
+$S_{n,r}(z) = \frac{1+c}{1-c} \in [1,1 + \frac{1}{2m}]$.
+
+\item Since $S_{n,r}(z)$ is odd, the statement follows from part 1.
+
+\item Observe that $S_{n,r}(z)$ can be written as
+$$
+S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
+$$
+where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. If $z \in [0,1]$, by part
+1 of~\autoref{lemma:properties-of-p-n} and the fact that $r$ is odd, $c
+\in [-1,0]$, and thus, $S_{n,r}(z) = \frac{1+c}{1-c} \in [0,1]$. Since
+$S_{n,r}(z)$ is odd, for $z \in [-1,0]$, $S_{n,r}(z) \in [-1,0]$.
+
+\item Since $B_{n,r}(z)$ is even, we can without loss generality assume that $z \ge
+0$. We consider two cases.
+
+Case $z \in [0,1]$. Since $r$ is odd and $P_n(z)$ is non-positive,
+$$
+B_{n,r}(z) = - (P_n(z))^r + \left(- P_{n}(-z)\right)^r \ge \left(- P_{n}(-z)\right)^r \ge 2^{n(n+1)r} \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
+$$
+where the second last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
+
+Case $z \in [1,2^n]$. Since $r$ is odd,
+$$
+B_{n,r}(z) = \left(- P_{n}(-z)\right)^r \left(1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r \right) = \left(- P_{n}(-z)\right)^r (1 - c)
+$$
+where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
+part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. By
+the definition of $r$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
+$$
+B_{n,r}(z) \ge \left(- P_{n}(-z)\right)^r \left( 1 - \frac{1}{4m+1} \right) \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
+$$
+where the last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
+\end{enumerate}
+\end{proof}
+
+\begin{lemma}[Properties of $Q(x)$]
+\label{lemma:properties-of-q}
+The rational function $Q(x)$ satisfies
+\begin{enumerate}
+\item $Q(x) \ge \frac{1}{2}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
+\item $Q(x) \le -\frac{1}{2}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+To prove part 1, consider any $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \
+\ip{v_i}{x} \ge \gamma \right\}$. Then, $\frac{\ip{v_i}{x}}{\gamma} \in [1,
+\frac{1}{\gamma}]$. By part 1 of \autoref{lemma:properties-of-s-n-r},
+$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \in [1, 1 + \frac{1}{2m}]$ and
+in particular $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \ge 1$. Thus,
+$$
+Q(x) = \left( \sum_{i=1}^m S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \right) - (m - 1/2) \ge m - (m - 1/2) = 1/2 \; .
+$$
+
+To prove part 2, consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~
+\norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Observe that
+$\frac{\ip{v_i}{x}}{\gamma} \in [-\frac{1}{\gamma}, \frac{1}{\gamma}]$. Consider
+$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right)$ for any $i \in
+\{1,2,\dots,m\}$. Parts 1,2, and 3 of \autoref{lemma:properties-of-s-n-r}
+and the fact $1/\gamma \le 2^s$ imply that
+$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \le 1 +
+\frac{1}{2m}$ for all $i \in \{1,2,\dots,m\}$. By the choice of $x$, there
+exists $j \in \{1,2,\dots,m\}$ such that $\ip{v_j}{x} \le - \gamma$. Part 2 of
+\autoref{lemma:properties-of-s-n-r} implies that
+$S_{s,r}\left(\frac{\ip{v_j}{x}}{\gamma}\right) \in [-1-\frac{1}{2m},-1]$. Thus,
+\begin{align*}
+Q(x)
+& = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
+& = S_{s,r}\left( \frac{\ip{v_j}{x}}{\gamma} \right) + \left( \sum_{\substack{i ~:~ 1 \le i \le m \\ i \neq j}} S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
+& \le -1 + (m-1) \left( 1 + \frac{1}{2m} \right) - \left(m - \frac{1}{2} \right) \\
+& \le 1/2 \; .
+\end{align*}
+\end{proof}
+
+To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-2} first
+note that part 4 of \autoref{lemma:properties-of-s-n-r} implies that for any $x$
+such that $\norm{x} \le 1$, $B_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right)$
+is positive. Thus $p(x)$ and $Q(x)$ have the same sign on the unit ball.
+Consider any $x$ in either
+$\displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
+or in
+$\displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
+\autoref{lemma:properties-of-q} states that $|Q(x)| \ge 1/2$ and the sign
+depends on which of the two sets $x$ lies in. Since signs of $Q(x)$ and $p(x)$
+are the same, it remains to show that $|p(x)| \ge m^{s^2m/2}$. Indeed,
+\begin{align*}
+|p(x)|
+& = |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
+& \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
+& \ge \frac{1}{2} |Q(x)| \cdot 2^{s(s+1)rm} && \text{(since $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4} \ge 1/2$)} \\
+& \ge \frac{1}{4} \cdot 2^{s(s+1)rm} && \text{(\autoref{lemma:properties-of-q})} \; .
+\end{align*}
+
+To prove part 3 of \autoref{theorem:polynomial-approximation-2} note that
+$\deg(P_s) = 2s+1$. Thus, $\deg(A_{s,r})$ and $\deg(B_{s,r})$ are at most
+$(2s+1)r$. Therefore, $\deg(p) \le (2s+1) rm$.
+
+It remains to prove part 4 of \autoref{theorem:polynomial-approximation-2}.
+For any $i \in \{0,1,2,\dots,s\}$ and any $v \in \R^d$ such that $\norm{v} \le 1$
+define multivariate polynomials
+\begin{align*}
+f_{i,v}(x) & = \frac{\ip{v}{x}}{\gamma} - 2^i \; , \\
+q_v(x) & = P_s \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
+a_v(x) & = A_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
+b_v(x) & = B_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; .
+\end{align*}
+Note that
+$$
+p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
+$$
+We bound the norms of these polynomials. We have
+$$
+\norm{f_{i,v}}^2 = \norm{v}^2/\gamma^2 + 2^{2i} \le 2 \cdot 2^s \; .
+$$
+where we used that $1/\gamma \le 2^s$ and $\norm{v} \le 1$.
+Since $q_v(x) = f_{i,v}(\frac{\ip{v}{x}}{\gamma}) \prod_{i=1}^s \left(f_{i,v}(\frac{\ip{v}{x}})\right)^2$,
+using part 1 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $q_v$
+as
+$$
+\norm{q_v}^2 \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \le  (2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \; .
+$$
+Using parts 3 and 2 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $a_v$ as
+\begin{align*}
+\norm{a_v}^2
+& \le 2\norm{(q_v)^r}^2 + 2\norm{(q_{-v})^r}^2 \\
+& \le 2 r^{r(2s+1)} \norm{q_v}^{2r} + 2 r^{r(2s+1)} \norm{q_{-v}}^{2r} \\
+& \le 4 r^{r(2s+1)} \left((2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \right)^{2r} \\
+& = 4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \; .
+\end{align*}
+The same upper bound holds for $\norm{b_v}^2$. Finally,
+\begin{align*}
+\norm{p}
+& \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
+& \le \left[ \sum_{i=1}^m m^{(s+1/2)rm} \norm{a_{v_i}} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} \norm{b_{v_j}} \right] + \left(m - \frac{1}{2} \right) m^{(s+1/2)rm} \prod_{j=1}^m \norm{b_{v_j}} \\
+& \le (2m-1/2) m^{(s+1/2)rm} \left(4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \right)^{m/2} \\
+& = (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm} \; .
+\end{align*}
 

### 2018-12-20 arxiv-version/main.tex
Add mappings and kernels

@@
 
-TODO: Mappings and kernels!
+We construct the three different mappings $\phi_n, \psi_n, \rho$. The first two
+are parametrized by a non-negative integer $n$. The domain of $\phi_n$ and
+$\psi_n$ is $\R^d$. The domain of $\rho$ is the unit ball of $\R^d$. The
+co-domain for $\phi_n$ and $\psi_n$ is $\R^p$ where $p = \sum_{i=0}^n
+\binom{i+d-1}{d-1}$ equipped with the standard inner product $\ip{x}{x'} =
+\sum_{i=1}^p x_i x'_i$. The co-domain is the classical separable Hilbert space
+$\ell_2 = \{ x \in \R^\infty ~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped
+with the standard inner product $\ip{x}{x'} = \sum_{i=1}^\infty x_i x'_i$. We
+index the coordinates of the co-domain $\R^p$ by $d$-tuples $(\alpha_1,
+\alpha_2, \dots, \alpha_d)$ of non-negative integers such that $\alpha_1 +
+\alpha_2 + \dots + \alpha_d \le n$. Similarly, we index the coordinates of
+$\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
+integers. The mappings are defined by
+\begin{align*}
+\left(\phi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
+& = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
+\\
+\left(\psi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
+& = \sqrt{\binom{n}{\alpha_1 + \alpha_2 + \dots + \alpha_d} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
+\\
+\left(\rho(x)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
+& = \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
+\end{align*}
+where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
+is the multinomial coefficient and $\binom{n}{k} = \frac{n!}{(n-k)!k!}$ is the binomial coefficient.
+
+Mappings $\psi_n$ and $\rho$ have simple-to-compute kernels
+\begin{align*}
+K_{\psi_n}(x,x') & = \ip{\psi_n(x)}{\psi_n(x')}_{\R^p} = \left( 1 + \ip{x}{x'} \right)^n \; , \\
+K_{\rho}(x,x') & = \ip{\rho(x)}{\rho(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}} \; .
+\end{align*}
+In passing we note that the formula for $K_\rho$ implies the mapping $\rho$ is
+well defined. Indeed, since $K_{\rho}(x,x) < +\infty$ for any $x$ in the unit
+ball of $\R^d$, it means that $\rho(x)$ indeed lies in $\ell_2$.
+
+TODO
 

### 2018-12-20 arxiv-version/main.tex
Spellcheck

@@
 run the algorithm for the strongly linearly separable case. All of these
-algorithms can be kernelized. (Some of them have to be kernalized since the
+algorithms can be kernelized. (Some of them have to be kernelized since the
 underlying inner product space is infinite dimensional.) Kernelization does not
@@
 to quantify certain parameters of the approximating polynomial. We construct two
-different polynomials with different paremeters. The parameters are quantified
+different polynomials with different parameters. The parameters are quantified
 in
@@
 We construct the three different mappings $\phi_n, \psi_n, \rho$. The first two
-are parametrized by a non-negative integer $n$. The domain of $\phi_n$ and
+are parameterized by a non-negative integer $n$. The domain of $\phi_n$ and
 $\psi_n$ is $\R^d$. The domain of $\rho$ is the unit ball of $\R^d$. The
@@
 
-For the proofs of the theorems we need several auxilliary results.
+For the proofs of the theorems we need several auxiliary results.
 
@@
 $$
-Mutliplying by the (positive) denonimators, we get an equivalent inequality
+Multiplying by the (positive) denominators, we get an equivalent inequality
 $$
@@
 $$
-On the oter hand for any $j \in \{1,2,\dots,m\}$, we have $\ip{v_j}{x} \in
+On the other hand for any $j \in \{1,2,\dots,m\}$, we have $\ip{v_j}{x} \in
 [-1,1]$ and thus $1 - \ip{v_j}{x}$ lies in the interval $[0,2]$. According to
@@
 
-For convenienence we define univariate rational function
+For convenience we define univariate rational function
 \begin{align*}

### 2018-12-20 arxiv-version/main.tex
Small fix

@@
 
-In this section, we show how to construct a mapping $\phi$ from the unit
-ball of $\R^d$ into a high dimensional inner product space that has the
-property if a set of labeled examples in the unit ball is linearly separable with a
-margin $\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
+In this section, we show how to construct a mapping $\phi$ from the unit ball of
+$\R^d$ into a high dimensional inner product space that has the property that if
+a set of labeled examples in the unit ball is linearly separable with a margin
+$\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
 linearly separable with a margin $\gamma'$ and their norms are bounded by $R'$.

### 2018-12-27 arxiv-version/main.tex
minor intro

@@
 \usepackage{tikz}
+\usepackage{color}
+\usepackage{comment}
 
@@
 \DeclareMathOperator{\diff}{d \!} % differential
+\DeclareMathOperator*{\polylog}{polylog}
+
+\definecolor{darkgreen}{rgb}{0,0.5,0}
+\definecolor{darkred}{rgb}{0.7,0,0}
+\definecolor{teal}{rgb}{0.3,0.8,0.8}
+\definecolor{orange}{rgb}{1.0,0.5,0.0}
+\definecolor{purple}{rgb}{0.8,0.0,0.8}
+\definecolor{blue}{rgb}{0.0,0.0,1.0}
+\newcommand{\kibitz}[2]{{\textcolor{#1}{\textsf{\footnotesize #2}}}}
+\newcommand{\alina}[1]{\kibitz{darkred}{[AB: #1]}}
+\newcommand{\david}[1]{\kibitz{darkgreen}{[DP: #1]}}
+\newcommand{\balazs}[1]{\kibitz{purple}{[BS: #1]}}
+\newcommand{\deva}[1]{\kibitz{teal}{[DT: #1]}}
+\newcommand{\chenyu}[1]{\kibitz{orange}{[CW: #1]}}
+\newcommand{\chicheng}[1]{\kibitz{blue}{[CZ: #1]}}
 
@@
 \begin{abstract}
-TODO
+We study the problem of efficient online multiclass linear classification with bandit feedback, where all examples belong to one of $K$ classes and lie in the $d$-dimensional Euclidean space.
+Previous works have left open the challenge of designing efficient algorithms with finite mistake bounds
+when the data is linearly separable by a margin $\gamma$.
+In this work, we take a first step towards this problem.
+We identify two notions of linear separability:
+one-versus-all (OvA) linear separability and weakly linear separability.
+\begin{enumerate}
+\item Under the OvA
+linear separability condition, we design an efficient algorithm that achieves a near-optimal mistake bound of $O(\frac{K}{\gamma^2})$.
+\item Under the more challenging weakly linear separability condition, we design an efficient algorithm with a mistake bound of $2^{\tilde{O}(\min(K \log^2 \frac 1 \gamma, \log K \sqrt{\frac 1 \gamma})) }$ \footnote{We use the notation $\tilde{O}(f(\cdot)) = O( f(\cdot) \polylog(f(\cdot)) )$.}.
+Our algorithm is based on a reduction from weakly linear separability to OvA linear separability via an infinite dimensional monomial feature map, which in turn is inspired by ~\cite{Klivans-Servedio-2008}'s work on learning intersection of halfspaces.
+\end{enumerate}
+
+%We focus on the setting where there are $K$ classes, and there is a $d$-dimensional multiclass linear classifier that separates all the examples shown with a positive margin $\gamma$.
+%$2^{O(\min(K \log^2 K \log^2 \frac 1 \gamma, \log K \log \log K \sqrt \frac 1 \gamma \log \frac 1\gamma))}$
+%$\min( (\log K \sqrt{\frac 1 \gamma})^{O(\log K \sqrt{\frac 1 \gamma})}, K^{O(K \log K \log^2 \frac1\gamma)} )$.
+
 \end{abstract}
@@
 
-We design new algorithms for the problem of \textsc{Online Multiclass
-Classification with Bandit Feedback}. In this problem, in each round, the
-algorithm receives a feature vector and the algorithm has to predict one of $K$
-possible classes. Immediately after the algorithm makes its prediction, it
-receives feedback whether the prediction was correct or not. However, in
-contrast with the standard, so called full information setting, the algorithm
-does \emph{not} receive the correct label. The feedback is only binary. To allow
-for meaningful use of randomization, we assume that the correct label in a
-particular round is chosen prior to algorithm's prediction in that
-round.\footnote{All our results apply to also to a simpler model of
+We study the problem of \textsc{Online Multiclass Linear
+Classification with Bandit Feedback}~\cite{Kakade-Shalev-Shwartz-Tewari-2008}.
+The problem can be viewed as a game between the learner and the environment:
+at each timestep $t$, the environment chooses an example $(x_t, y_t)$, where its feature
+part $x_t \in \R^d$ is revealed to the learner.
+\footnote{All our results apply to also to a simpler model of
 the so called \emph{oblivious adversary} where the whole sequence of labeled
 examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is chosen before the first
-round of the game.} The protocol of the problem is stated below.
+round of the game.}
+Upon receiving this example, the
+learner is asked to make a prediction $\hat{y}_t$.
+the learner receives feedback immediately after making its prediction.
+In contrast with the standard full information setting (where the feedback given is the correct label $y_t$), the feedback given is only a binary indicator
+whether the prediction was correct or not. The protocol of the problem is formally stated below.
+
+%In this problem, in each round, the
+%learner receives a feature vector and is asked to predict one of $K$
+%possible classes. To allow
+%for meaningful use of randomization, we assume that the correct label in a
+%particular round is chosen prior to algorithm's prediction in that
+%round.
+%Immediately after the learner makes its prediction, it
+%receives feedback whether the prediction was correct or not. However, in
+%contrast with the standard, so called full information setting, the algorithm
+%does \emph{not} receive the correct label. The feedback is only binary.
 
@@
 \STATE{Adversary \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
+\chicheng{Or we simply say: Adversary chooses example $(x_t, y_t)$, where $x_t$ is reveal to the learner.}
 \STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
@@
 
-The goal is to design an algorithm that makes small number of mistakes
-$\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$. The problem
-was initially proposed by \cite{Kakade-Shalev-Shwartz-Tewari-2008}. The
-corresponding problem with full information feedback is solved by the classical
-\textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
-\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}). The bandit feedback
-version is a mathematically natural model and potential applications include
-online advertising and online content optimization where the binary feedback
-corresponds to a click.
+The performance is of the learner is measured by its cumulative number of mistakes
+$\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$. The bandit feedback
+ is a natural feedback model motivated by applications including
+online advertising and online content optimization, where the learner only gets to
+see the loss of its action taken.
+%where the binary feedback corresponds to a click
+%The
+%corresponding problem with full information feedback is solved by the classical
+%\textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
+%\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}).
 
 In this paper, we focus on the special case when the examples lie in $\R^d$ and
-are \emph{linearly separable with a margin}. In the full-information feedback
-setting, it is well know that if the examples have norm at most $R$ and are
+are \emph{linearly separable with a margin}.
+\chicheng{I wonder if we should introduce the two notions of linear separability here,
+because strong linear separability is also worth mentioning in the full-information setting.
+}
+
+In the full-information feedback
+setting, it is well known that if the examples have norm at most $R$ and are
 linearly separable with a margin $\gamma$ then the \textsc{Multiclass

### 2018-12-27 ptf_margin.tex
minor intro

@@
 $\inner{\phi_0(x), \phi_0(x)} = K(x,x) \leq 2$.
+
+\item $\phi(x) = \sqrt{{i_1+\ldots+i_d \choose i_1 \ldots i_d}} x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq s, i_1, \ldots, i_d \geq 0}$.
+This corresponds to the multinomial kernel $K(x,x') = \sum_{i=0}^s \inner{x,x'}^i$.
+Note that for all $x$ such that $\| x \|_2 \leq 1$,
+$\inner{\phi(x), \phi(x)} = K(x,x) = \sum_{i=0}^s \|x\|^{2i} \leq s+1$.
+
+\item $\phi(x) = (\sqrt{\frac{1}{i_1!
+\ldots i_d!}} x_1^{i_1} \ldots x_d^{i_d})_{i_1, \ldots, i_d \geq 0}$.
+This corresponds to the kernel $K(x,x') = \exp(\inner{x,y})$.
+Note that for all $x$ such that $\|x\|_2 \leq 1$, $\inner{\phi(x), \phi(x)} \leq e$.
+
+\cz{Actually I wasn't able to get the RBF kernel working in our problem, as every term in the feature map will be a monomial term *with a $\exp(-\frac{\|x\|_2^2}{2})$ scaling*; it is unclear how to represent a polynomial as $\inner{c, \phi(x)}$.}
+
 \end{enumerate}

### 2019-01-03 arxiv-version/main.tex
related work on bandit multiclass; broader related work on cb not covered yet

@@
 % Math symbols and commands
+\newcommand{\calF}{\mathcal{F}}  % set of real numbers
 \newcommand{\R}{\mathbb{R}}  % set of real numbers
@@
 \label{section:related-work}
+The problem of bandit multiclass linear classification is initially formulated
+ by the pioneering work of~\cite{Kakade-Shalev-Shwartz-Tewari-2008}. In that work,
+ two computationally
+ inefficient algorithms that work in the $\gamma$-weak linearly separable setting are proposed: one with a mistake bound of
+ $O(k^2 d \ln(\frac{d}{\gamma^2}))$, the other with a mistake bound of $\tilde{O}(\frac{k^2}{\gamma^2} \ln T)$.
+ In addition, the authors propose the Banditron algorithm, a computationally efficient
+ algorithm that has a $O(T^{2/3})$ regret in the general setting, and has a
+ $O(\sqrt{T})$ mistake bound in the $\gamma$-weak linearly separable setting.
+The polynomial dependence of Banditron's mistake bound on the time horizon is undesirable
+for problems with a long time horizon.
+ One key open question left by~\cite{Kakade-Shalev-Shwartz-Tewari-2008} is whether
+ one can deesign computationally efficient algorithms that achieve mistake bounds that match or improve over those of inefficient algorithms.
+ In this paper, we take a step towards answering this question, showing that
+ efficient algorithms with mistake bounds quasipolynomial in the margin parameter can be obtained.
+
+ %Whether one can design an efficient algorithm with a
+ %finite mistake bound that has no dimensionality dependence is mentioned as an open problem in
+ %~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, where in this paper we provide a positive answer.
+ %$O(k^2 d \ln(\frac{d}{\gamma^2}))$
+
+Many works consider bandit multiclass classification in the general non-separable setting.
+\cite{Abernethy-Rakhlin-2009} poses the open problem of whether one can design
+and efficient algorithm to get a $O(\sqrt{T})$ regret against some reasonable loss functions.
+\cite{CrammerG13} shows that such an algorithm can be obtained, under the assumption that the distribution of the label $y$ conditioned on feature $x$ satisfies certain parametric noise assumption.
+\cite{Hazan-Kale-2011} developed the Newtron algorithm, which has a regret
+between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass logistic loss, where the exact order of the regret depends on the diameter of the benchmark class.
+In particular, if the diameter is $O(\ln T)$, its regret bound would become
+$O(T^{2/3})$.
+The SOBA algorithm by \cite{Beygelzimer-Orabona-Zhang-2017} achieves a regret of $\tilde{O}(\sqrt{T})$ against the $\eta$-loss~\cite{Orabona-Cesa-Bianchi-Gentile-2012}; in addition, their regret bound does not depend sensitively on the diameter of the benchmark class.
+\cite{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a regret of $\tilde{O}(\sqrt{T})$ against the multiclass logistic loss, where it doubly-exponentially improves over \cite{Hazan-Kale-2011}'s regret on its dependence on the diameter of the benchmark class.
+Recently, \cite{Foster-Krishnamurthy-2018} developed a rich theory on contextual bandits with surrogate losses, focusing on benchmarks of the form $\min_{f \in \calF} \frac 1 K \sum_{i=1}^K \phi( f_i(x) )$, where $\calF$ contains function $f$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$,
+and $\phi(s) = \max(1 - \frac s \gamma, 0)$ and $\min(1, \max(1 - \frac s \gamma, 0))$.
+On one hand, it gives information-theoretic mistake upper bounds under various settings of $\calF$, for instance parametric and nonparametric classes; On the other hand, it gives an efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of $\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$.
+
+\cite{Chen-Lin-Lu-2014, Zhang-Jung-Tewari-2018} study online bandit multiclass boosting under bandit feedback, where one can view online boosting as online linear classification by treating each base hypothesis as a separate feature.
+\cite{Chen-Lin-Lu-2014}'s online weak learning condition implies that there is a convex combination of base hypotheses that one-versus-all separates all examples with a margin.
+Under this condition, it gives an algorithm with a $O(T^{3/4})$ mistake bound.
+\cite{Zhang-Jung-Tewari-2018} considers an online weak learning condition that implies that there is a convex combination of base hypotheses that weakly separates all examples with a margin (See~\cite{Mukherjee-Schapire-2013}, Theorem 3).
+Under this condition, it gives an algorithm with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge parameter; in addition, it gives an adaptive algorithm with a $O(T^{3/4})$ mistake bound.
+
+%\cite{Chen-Chen-Zhang-Chen-Zhang-2009} studies the approach of reducing bandit multiclass learning to online binary classification using one-versus-all reduction. They show that
+
+%Their results do not imply a finite mistake bound in the weakly separable setting, in that the benchmark loss can still be $\Omega(T)$.
 

### 2019-01-07 arxiv-version/main.tex
minor
ignorant lower bound lemma

@@
 \usepackage{comment}
+\usepackage{commath}
+\usepackage{dsfont}
 
@@
 % Math symbols and commands
-\newcommand{\calF}{\mathcal{F}}  % set of real numbers
+\newcommand{\calF}{\mathcal{F}}
+\newcommand{\one}{\mathds{1}}
 \newcommand{\R}{\mathbb{R}}  % set of real numbers
@@
 \newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
-\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
+%\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
 %\DeclareMathOperator*{\deg}{deg}
+
 \DeclareMathOperator*{\argmax}{argmax}
@@
 
-\begin{itemize}
-\item \cite{Abernethy-Rakhlin-2009}
-
-\item \cite{Chen-Chen-Zhang-Chen-Zhang-2009}
-
-\item \cite{Hazan-Kale-2011}
-
-\item \cite{Beygelzimer-Orabona-Zhang-2017}
-
-\item \cite{Foster-Kale-Luo-Mohri-Sridharan-2018}
-
-\item \cite{Foster-Krishnamurthy-2018}
-\end{itemize}
-
-TODO
+%\begin{itemize}
+%\item \cite{Abernethy-Rakhlin-2009}
+
+%\item \cite{Chen-Chen-Zhang-Chen-Zhang-2009}
+
+%\item \cite{Hazan-Kale-2011}
+
+%\item \cite{Beygelzimer-Orabona-Zhang-2017}
+
+%\item \cite{Foster-Kale-Luo-Mohri-Sridharan-2018}
+
+%\item \cite{Foster-Krishnamurthy-2018}
+%\end{itemize}
+
+%TODO
 
@@
 
-TODO
+\begin{lemma}
+For any $\gamma \in (0,\frac 1 {160})$,
+there exists a set of $N$ examples $x_1, \ldots, x_N$ and vectors $w_1, \ldots, w_N$ ($N = (\Omega(\frac{1}{\gamma}))^{(d-2)/2}$), such that:
+$\| x_i \|_2 \leq 1$, $\| w_i \|_2 \leq 1$ for all $i$ in $[N]$, and for all $i, j$ in $[N]$,
+\[ w_i \cdot x_j \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases} \]
+\label{lem:embed_d_gamma}
+\end{lemma}
+\begin{proof}
+By Lemma 6 of~\cite{Long1995}, there exists a set of $N = (\frac{1}{2\sqrt{40\gamma}})^{d-2}$ $(d-1)$-dimensional vectors $z_1, \ldots, z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that
+$\theta(z_i, z_j) \geq \sqrt{40 \gamma}$. As $\cos\theta \geq 1-\theta^2/5$ for every $\theta \in [0,\pi]$,
+this implies that
+\[ z_i \cdot z_j \begin{cases} = 1 ,& i = j, \\ \leq 1- 8\gamma ,& i \neq j. \end{cases} \]
+
+Define $x_i = (\frac12 z_i, \frac12)$, and $w_i = (\frac 12 z_i, -\frac 12(1-4\gamma))$ for all $i$ in $[N]$.
+It can be easily checked that for all $i$, $\|x_i\| \leq 1$ and $\|w_i\| \leq 1$.
+In addition,
+\[ w_i \cdot x_j = \frac 1 4 z_i \cdot z_j - \frac {1-4\gamma} 4 \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases}\]
+\end{proof}
 

### 2019-01-07 arxiv-version/algorithm-for-strongly-linearly-separable-data.tex
Split sections in separate files

--- 2018-12-27 arxiv-version/main.tex
@@
-\documentclass[12pt]{article}
-
-% LaTeX packages
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage[singlelinecheck=false]{caption}
-\usepackage{fullpage}
-\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
-\usepackage{natbib}
-\usepackage{thmtools}
-\usepackage{tikz}
-\usepackage{color}
-\usepackage{comment}
-
-% TikZ packages
-\usetikzlibrary{arrows}
-\usetikzlibrary{angles}
-\usetikzlibrary{backgrounds}
-\usetikzlibrary{calc}
-\usetikzlibrary{cd}  % commutative diagrams
-\usetikzlibrary{intersections}
-\usetikzlibrary{patterns}
-\usetikzlibrary{shapes}
-\usetikzlibrary{through}
-
-% Math environments
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}[definition]{Proposition}
-\newtheorem{lemma}[definition]{Lemma}
-\newtheorem{theorem}[definition]{Theorem}
-\newtheorem{corollary}[definition]{Corollary}
-
-% Math symbols and commands
-\newcommand{\R}{\mathbb{R}}  % set of real numbers
-\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]} % indicator
-\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
-\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
-%\DeclareMathOperator*{\deg}{deg}
-\DeclareMathOperator*{\argmax}{argmax}
-\DeclareMathOperator*{\argmin}{argmin}
-\DeclareMathOperator*{\Exp}{\mathbf{E}}  % expected value
-\DeclareMathOperator{\diff}{d \!} % differential
-\DeclareMathOperator*{\polylog}{polylog}
-
-\definecolor{darkgreen}{rgb}{0,0.5,0}
-\definecolor{darkred}{rgb}{0.7,0,0}
-\definecolor{teal}{rgb}{0.3,0.8,0.8}
-\definecolor{orange}{rgb}{1.0,0.5,0.0}
-\definecolor{purple}{rgb}{0.8,0.0,0.8}
-\definecolor{blue}{rgb}{0.0,0.0,1.0}
-\newcommand{\kibitz}[2]{{\textcolor{#1}{\textsf{\footnotesize #2}}}}
-\newcommand{\alina}[1]{\kibitz{darkred}{[AB: #1]}}
-\newcommand{\david}[1]{\kibitz{darkgreen}{[DP: #1]}}
-\newcommand{\balazs}[1]{\kibitz{purple}{[BS: #1]}}
-\newcommand{\deva}[1]{\kibitz{teal}{[DT: #1]}}
-\newcommand{\chenyu}[1]{\kibitz{orange}{[CW: #1]}}
-\newcommand{\chicheng}[1]{\kibitz{blue}{[CZ: #1]}}
-
-\title{Online Multiclass Linear Classification with Bandit Feedback}
-
-\author{
-Alina Beygelzimer \and
-D\'avid P\'al \and
-Bal\'azs Sz\"or\'enyi \and
-Devanathan Thiruvenkatachari \and
-Chen-Yu Wei \and
-Chicheng Zhang
-}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-We study the problem of efficient online multiclass linear classification with bandit feedback, where all examples belong to one of $K$ classes and lie in the $d$-dimensional Euclidean space.
-Previous works have left open the challenge of designing efficient algorithms with finite mistake bounds
-when the data is linearly separable by a margin $\gamma$.
-In this work, we take a first step towards this problem.
-We identify two notions of linear separability:
-one-versus-all (OvA) linear separability and weakly linear separability.
-\begin{enumerate}
-\item Under the OvA
-linear separability condition, we design an efficient algorithm that achieves a near-optimal mistake bound of $O(\frac{K}{\gamma^2})$.
-\item Under the more challenging weakly linear separability condition, we design an efficient algorithm with a mistake bound of $2^{\tilde{O}(\min(K \log^2 \frac 1 \gamma, \log K \sqrt{\frac 1 \gamma})) }$ \footnote{We use the notation $\tilde{O}(f(\cdot)) = O( f(\cdot) \polylog(f(\cdot)) )$.}.
-Our algorithm is based on a reduction from weakly linear separability to OvA linear separability via an infinite dimensional monomial feature map, which in turn is inspired by ~\cite{Klivans-Servedio-2008}'s work on learning intersection of halfspaces.
-\end{enumerate}
-
-%We focus on the setting where there are $K$ classes, and there is a $d$-dimensional multiclass linear classifier that separates all the examples shown with a positive margin $\gamma$.
-%$2^{O(\min(K \log^2 K \log^2 \frac 1 \gamma, \log K \log \log K \sqrt \frac 1 \gamma \log \frac 1\gamma))}$
-%$\min( (\log K \sqrt{\frac 1 \gamma})^{O(\log K \sqrt{\frac 1 \gamma})}, K^{O(K \log K \log^2 \frac1\gamma)} )$.
-
-\end{abstract}
-
-\section{Introduction}
-\label{section:introduction}
-
-We study the problem of \textsc{Online Multiclass Linear
-Classification with Bandit Feedback}~\cite{Kakade-Shalev-Shwartz-Tewari-2008}.
-The problem can be viewed as a game between the learner and the environment:
-at each timestep $t$, the environment chooses an example $(x_t, y_t)$, where its feature
-part $x_t \in \R^d$ is revealed to the learner.
-\footnote{All our results apply to also to a simpler model of
-the so called \emph{oblivious adversary} where the whole sequence of labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is chosen before the first
-round of the game.}
-Upon receiving this example, the
-learner is asked to make a prediction $\hat{y}_t$.
-the learner receives feedback immediately after making its prediction.
-In contrast with the standard full information setting (where the feedback given is the correct label $y_t$), the feedback given is only a binary indicator
-whether the prediction was correct or not. The protocol of the problem is formally stated below.
-
-%In this problem, in each round, the
-%learner receives a feature vector and is asked to predict one of $K$
-%possible classes. To allow
-%for meaningful use of randomization, we assume that the correct label in a
-%particular round is chosen prior to algorithm's prediction in that
-%round.
-%Immediately after the learner makes its prediction, it
-%receives feedback whether the prediction was correct or not. However, in
-%contrast with the standard, so called full information setting, the algorithm
-%does \emph{not} receive the correct label. The feedback is only binary.
-
-\begin{algorithm}[h]
-\caption{\textsc{Online Multiclass Classification with Bandit Feedback}
-\label{algorithm:game-protocol}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$}
-\STATE{Adversary \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
-\chicheng{Or we simply say: Adversary chooses example $(x_t, y_t)$, where $x_t$ is reveal to the learner.}
-\STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \begin{cases}
-0 & \text{if $\widehat y_t = y_t$,} \\
-1 & \text{if $\widehat y_t \neq y_t$.}
-\end{cases}$
-}
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-The performance is of the learner is measured by its cumulative number of mistakes
-$\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$. The bandit feedback
- is a natural feedback model motivated by applications including
-online advertising and online content optimization, where the learner only gets to
-see the loss of its action taken.
-%where the binary feedback corresponds to a click
-%The
-%corresponding problem with full information feedback is solved by the classical
-%\textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
-%\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}).
-
-In this paper, we focus on the special case when the examples lie in $\R^d$ and
-are \emph{linearly separable with a margin}.
-\chicheng{I wonder if we should introduce the two notions of linear separability here,
-because strong linear separability is also worth mentioning in the full-information setting.
-}
-
-In the full-information feedback
-setting, it is well known that if the examples have norm at most $R$ and are
-linearly separable with a margin $\gamma$ then the \textsc{Multiclass
-Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
-This result is very satisfying since the upper bound on the number of mistakes
-is information-theoretically optimal and at the same time the \textsc{Multiclass
-Perceptron} algorithm has low time and memory complexity.
-
-The bandit feedback setting, however, is much more challenging. To understand
-the differences, we dissect the notion of linear separability in the multiclass
-setting. Beside the standard notion of linear separability, we define also
-\emph{strong linear separability}. For binary classification, these two
-definitions are identical. However, they differ for multiclass classification.
-For multiclass classification with $K$ classes the standard notion of linear
-separability means that the examples from each class lie in an intersection of
-$K-1$ halfspaces and the examples outside of the class lie in the complement of
-the intersection of the halfspaces. Strong linear separability means that
-examples from each class are separated from the remaining examples by a
-\emph{single} hyperplane. We state the definitions precisely in
-Section~\ref{section:notions-of-linear-separability}.
-
-For the case when the examples are strongly linearly separable, we design a
-simple and efficient algorithm with expected number of mistakes at most $(K-1)
-\lfloor (R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies
-of the \textsc{Binary Perceptron} algorithm, one copy for each class.
-Intuitively speaking, the factor $K-1$ is the price we pay for the bandit
-feedback, or more precisely, the lack of full-information feedback. We also
-prove that any (possibly randomized) algorithm makes $\Omega(K (R/\gamma)^2))$
-mistakes in the worst case.
-
-For the standard notion of linear separability, we propose several algorithms
-with various time-complexity-versus-mistake-bound trade-offs. First class of
-algorithms map the examples into a high-dimensional inner product space. In this
-space the examples become \emph{strongly} linearly separable. This allows us to
-run the algorithm for the strongly linearly separable case. All of these
-algorithms can be kernelized. (Some of them have to be kernelized since the
-underlying inner product space is infinite dimensional.) Kernelization does not
-change the input-output behavior of the algorithm, it only affects its time
-and memory complexity.
-
-These algorithms differ by choice of the mapping or, equivalently, choice of the
-kernel. The crux of the problem is the analysis of the approximation properties
-of these mappings/kernels and the way margin in the original space $\R^d$ under
-standard linear separability notion gets transformed into a margin in the
-high-dimensional space under the strong separability notion. This problem is
-related to the problem of learning intersection of halfspaces and has been
-studied previously by \cite{Klivans-Servedio-2008}. As an important technical
-achievement, we improve on the results of \cite{Klivans-Servedio-2008} by
-removing completely the dependency on the original dimension $d$.
-
-Finally, we propose a very different algorithm that is based on the obvious idea
-that two points that are close enough must have the same label. Here, close
-enough means that they cannot be separated from each other by a linear separator
-with a margin.
-
-All the algorithms run in time that is polynomial in the dimension of the
-feature vectors, the number of classes and the number of rounds. At the same
-time, all the algorithms make number of mistakes that does \emph{not} depend
-on the number of rounds. Instead, their number of mistakes depends only on the
-margin, number of classes, dimension of the feature vectors, and the radius of
-the ball in which the data lie.
-
-Finally, we study two questions related to the computational and
-information-theoretic hardness of the problem. Any algorithm for the bandit
-setting collects information in the form of so called \emph{strongly labeled}
-and \emph{weakly labeled} examples. Strongly labeled examples are those for
-which we know the class label. Weakly labeled example is an example for which we
-know that class label can be anything except for a particular one class. First,
-we show the offline problem of finding a linear multiclass separator consistent
-with a set of strongly and weakly labeled examples is NP-hard. This result is a
-consequence of the fact that finding an intersection of two halfspaces
-consistent with a set of binary-labeled examples is
-NP-hard~\citep{Blum-Rivest-1993}. Second, we show that any algorithm that uses
-only strongly-labeled examples and ignores weakly labeled examples makes at
-least $\Omega(???)$ mistakes.
-
-\section{Related work}
-\label{section:related-work}
-
-\begin{itemize}
-\item \cite{Abernethy-Rakhlin-2009}
-
-\item \cite{Chen-Chen-Zhang-Chen-Zhang-2009}
-
-\item \cite{Hazan-Kale-2011}
-
-\item \cite{Beygelzimer-Orabona-Zhang-2017}
-
-\item \cite{Foster-Kale-Luo-Mohri-Sridharan-2018}
-
-\item \cite{Foster-Krishnamurthy-2018}
-\end{itemize}
-
-TODO
-
-\section{Notions of linear separability}
-\label{section:notions-of-linear-separability}
-
-We define two notions of linear separability for multiclass classification. The
-first notion is the standard notion of linear separability used in the proof of
-the mistake bound for the \textsc{Multiclass Perceptron} algorithm. The second
-notion is stronger, i.e. more restrictive. However, it is more suitable for the
-bandit setting, since it allows for a simple and efficient algorithm; see
-Section~\ref{section:algorithm-for-strongly-linearly-separable-data}.
-
-\begin{definition}[Linear separability]
-Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
-integer, and let $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
-y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.
-
-The examples are said to be \emph{linearly separable with a
-margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
-that
-\begin{align}
-\label{equation:linear-separability-1}
-\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
-\label{equation:linear-separability-2}
-\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} & \ge \ip{x_t}{w_i} + \gamma \; .
-\end{align}
-
-The examples are said to be \emph{strongly linearly separable with a
-margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
-that
-\begin{align}
-\label{equation:strong-linear-separability-1}
-\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
-\label{equation:strong-linear-separability-2}
-\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
-\label{equation:strong-linear-separability-3}
-\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
-\end{align}
-\end{definition}
-
-The notion of linear separability with a margin is standard. It used in the
-full-information setting to upper bound the number of mistakes of the
-\textsc{Multiclass Perceptron} algorithm. For completeness, we state the
-algorithm in Appendix~\ref{section:multiclass-perceptron-proofs}. It is a
-folklore result that if a set of labeled examples is separable with a margin
-$\gamma$ and the norm of the examples is bounded by $R$ then \textsc{Multiclass
-Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
-mistakes. Another folklore result is that \textsc{Multiclass Perceptron} is
-essentially optimal in the sense that any deterministic algorithm must make
-$\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
-completeness, we give proofs of both of these results in
-Appendix~\ref{section:multiclass-perceptron-proofs}.
-
-The notion of strong linear separability is new.
-
-It is easy to see that if labeled examples are strongly linearly
-separable with margin $\gamma$ then they are linearly separable with margin
-$2\gamma$. Indeed, if $w_1, w_2, \dots, w_K \in V$
-satisfy \eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3} then they satisfy
-\eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} with margin $\gamma' = 2\gamma$.
-
-Similarly, if $K=2$ and labeled examples are linearly separable with a margin
-$\gamma$ then they are strongly linearly separable with margin $\gamma/2$.
-Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$, $w_2' =
-\frac{w_2 - w_1}{2}$ and $\gamma'=\gamma/2$ satisfy
-\eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3}. The last two conditions are easy
-to see. The first condition follows from $\norm{w_i'}^2 \le (\frac{1}{2}
-\norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le \frac{1}{2}\norm{w_1}^2 +
-\frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
-
-However, for any $K \ge 3$ and any inner product space of dimension at least
-$2$, there exists a set of labeled examples that is linearly separable with a
-positive margin $\gamma$ but it is not strongly linearly separable with any
-positive margin $\gamma$. An example of such set of labeled examples is shown in
-Figure~\ref{figure:linearly-separable-examples-with-margin}.
-
-\begin{figure}
-\begin{center}
-\input{figures/linearly-separable-examples-with-margin}
-\end{center}
-\caption[]{The figure shows labeled examples in $\R^2$. The examples belong to
-$K=3$ classes colored white, gray and black respectively. Each class lies in a
-$120^\circ$ wedge. In other words, each class lies in an intersection of two
-halfspaces.
-
-While the examples are linearly separable with a positive margin $\gamma$, they
-are \emph{not} strongly linearly separable with any positive margin $\gamma$.
-}
-\label{figure:linearly-separable-examples-with-margin}
-\end{figure}
-
 \section{Algorithm for strongly linearly separable data}
@@
 \end{proof}
-
-\section{From linear separability to strong linear separability}
-\label{section:from-linear-separability-to-strong-linear-separability}
-
-In this section, we show how to construct a mapping $\phi$ from the unit ball of
-$\R^d$ into a high dimensional inner product space that has the property that if
-a set of labeled examples in the unit ball is linearly separable with a margin
-$\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
-linearly separable with a margin $\gamma'$ and their norms are bounded by $R'$.
-The parameters $\gamma'$ and $R'$ are functions of the old margin $\gamma$ and
-the number of classes $K$, and the are specified in the theorems below.
-
-Equipped with the mapping $\phi$, we can utilize
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
-\autoref{theorem:strongly-separable-example-mistake-upper-bound} from the
-previous section and we obtain an algorithm for linearly separable examples and
-an upper bound on its number of mistakes. As a computational speed up, instead
-of working with the mapped examples $\phi(x_1), \phi(x_2), \dots$ explicitly, we
-can use the kernelized version of
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-that uses a kernel function $k(x,x') = \ip{\phi(x)}{\phi(x')}$.
-
-We construct several different mappings $\phi$. The mappings differ in the
-parameters $R'$, $\gamma'$, time complexity of evaluating $\phi(x)$, and time
-complexity of evaluating $k(x,x')$. Some of the mappings depend the original
-margin $\gamma$. In practice, the margin parameter $\gamma$ is not known, which
-makes these mappings impractical. However, one of the mappings we construct
-does \emph{not} depend on $\gamma$.
-
-The idea behind all the mappings is polynomial approximation. According to the
-well known Stone-Weierstrass theorem (see
-e.g.~\citep[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
-multivariate polynomials uniformly approximate any continuous function.
-Intuitively speaking, we use a multivariate polynomial to approximate, on the
-unit ball of $\R^d$, the indicator function corresponding to the intersection of
-$m=K-1$ halfspaces. Within margin $\gamma$ along the decision boundary, we allow
-the polynomial to attain arbitrary value. The polynomial separates examples in
-one class from examples in the other classes. To be able to quantify $R'$,
-$\gamma'$ and time complexities of evaluating $\phi(x)$ and $k(x,x')$, we need
-to quantify certain parameters of the approximating polynomial. We construct two
-different polynomials with different parameters. The parameters are quantified
-in
-Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
-stated below.
-
-Before we state the theorems, recall that a polynomial of $d$ variables is a
-function $p:\R^d \to \R$ of the form
-$$
-p(x) = p(x_1, x_2, \dots, x_d) = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-$$
-where the sum ranges over a finite set of $d$-tuples $(\alpha_1, \alpha_2,
-\dots, \alpha_d)$ of non-negative integers and $c_{\alpha_1, \alpha_2, \dots,
-\alpha_d}$ is a real coefficient. The \emph{degree} of a polynomial $p$, denoted
-by $\deg(p)$, is the largest value of $\alpha_1 + \alpha_2 + \dots + \alpha_d$
-for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is non-zero.
-The \emph{norm of a polynomial} $p$ is defined as
-$$
-\norm{p} = \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} \left(c_{\alpha_1, \alpha_2, \dots, \alpha_d} \right)^2 } \; .
-$$
-It is easy see that this is indeed a norm, since we can interpret it as a
-Euclidean norm of the vector of the coefficients of the polynomial.
-
-\begin{theorem}[Polynomial approximation of intersection of halfspaces I]
-\label{theorem:polynomial-approximation-1}
-Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
-\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$. There exists a
-multivariate polynomial $p:\R^d \to \R$ such that
-\begin{enumerate}
-\item $p(x) \ge 1/2$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-\item $p(x) \le -1/2$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-\item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$
-\item $\displaystyle \norm{p} \le \left( 188 \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil \right)^{\frac{1}{2} \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil}$
-\end{enumerate}
-\end{theorem}
-
-\begin{theorem}[Polynomial approximation of intersection of halfspaces II]
-\label{theorem:polynomial-approximation-2}
-Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
-\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$.
-Define
-$$
-r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1 \qquad \text{and} \qquad s = \left \lceil \log_2(1/\gamma) \right \rceil \; .
-$$
-Then, there exists a multivariate polynomial $p:\R^d \to \R$ such that
-\begin{enumerate}
-\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$
-for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-
-\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$
-for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-
-\item $\deg(p) \le (2s+1) rm$
-\item $\norm{p} \le (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm}$
-\end{enumerate}
-\end{theorem}
-
-The proofs of the theorems can be found in
-Section~\ref{section:proof-of-polynomial-approximation}. The geometric
-interpretation of the two regions described in parts 1 and 2 of the theorems is
-explained in Figure~\ref{figure:pizza-slice}. Similar but weaker results were
-proved by~\cite{Klivans-Servedio-2008}. In particular, the bounds in parts
-1, 2, 3, 4 of the theorems are independent of the dimension $d$.
-
-\begin{figure}
-\begin{center}
-\input{figures/pizza-slice}
-\end{center}
-\caption[]{The figure shows the two regions used in parts 1 and 2 of
-Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
-for the case $m=d=2$ and a particular choice of vectors $v_1, v_2$ and margin
-parameter $\gamma$. These regions are
-\begin{align*}
-R^+ & = \displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\} \; , \\
-R^- & = \displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\} \; .
-\end{align*}
-The separating hyperplanes $\ip{v_1}{x} = 0$ and $\ip{v_2}{x} = 0$ are shown as dashed lines.
-}
-\label{figure:pizza-slice}
-\end{figure}
-
-We construct the three different mappings $\phi_n, \psi_n, \rho$. The first two
-are parameterized by a non-negative integer $n$. The domain of $\phi_n$ and
-$\psi_n$ is $\R^d$. The domain of $\rho$ is the unit ball of $\R^d$. The
-co-domain for $\phi_n$ and $\psi_n$ is $\R^p$ where $p = \sum_{i=0}^n
-\binom{i+d-1}{d-1}$ equipped with the standard inner product $\ip{x}{x'} =
-\sum_{i=1}^p x_i x'_i$. The co-domain is the classical separable Hilbert space
-$\ell_2 = \{ x \in \R^\infty ~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped
-with the standard inner product $\ip{x}{x'} = \sum_{i=1}^\infty x_i x'_i$. We
-index the coordinates of the co-domain $\R^p$ by $d$-tuples $(\alpha_1,
-\alpha_2, \dots, \alpha_d)$ of non-negative integers such that $\alpha_1 +
-\alpha_2 + \dots + \alpha_d \le n$. Similarly, we index the coordinates of
-$\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
-integers. The mappings are defined by
-\begin{align*}
-\left(\phi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-\\
-\left(\psi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = \sqrt{\binom{n}{\alpha_1 + \alpha_2 + \dots + \alpha_d} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-\\
-\left(\rho(x)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-\end{align*}
-where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
-is the multinomial coefficient and $\binom{n}{k} = \frac{n!}{(n-k)!k!}$ is the binomial coefficient.
-
-Mappings $\psi_n$ and $\rho$ have simple-to-compute kernels
-\begin{align*}
-K_{\psi_n}(x,x') & = \ip{\psi_n(x)}{\psi_n(x')}_{\R^p} = \left( 1 + \ip{x}{x'} \right)^n \; , \\
-K_{\rho}(x,x') & = \ip{\rho(x)}{\rho(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}} \; .
-\end{align*}
-In passing we note that the formula for $K_\rho$ implies the mapping $\rho$ is
-well defined. Indeed, since $K_{\rho}(x,x) < +\infty$ for any $x$ in the unit
-ball of $\R^d$, it means that $\rho(x)$ indeed lies in $\ell_2$.
-
-TODO
-
-\section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
-\label{section:proof-of-polynomial-approximation}
-
-For the proofs of the theorems we need several auxiliary results.
-
-\begin{lemma}[Simple inequality]
-\label{lemma:simple-inequality}
-For any real numbers $b_1, b_2, \dots, b_n$,
-$$
-\left( \sum_{i=1}^n b_i \right)^2 \le n \sum_{i=1}^n b_i^2 \; .
-$$
-\end{lemma}
-
-\begin{proof}
-The lemma follows from Cauchy-Schwartz inequality applied to
-vectors $(b_1, b_2, \dots, b_n)$ and $(1,1,\dots,1)$.
-\end{proof}
-
-\begin{lemma}[Bound on binomial coefficients]
-\label{lemma:binomial-bound}
-For any integers $n,k$ such that $n \ge k \ge 0$,
-$$
-\binom{n}{k} \le (n - k + 1)^k \; .
-$$
-\end{lemma}
-
-\begin{proof}
-If $k = 0$, the inequality trivially holds. For the rest of the proof we can
-assume $k \ge 1$. We write the binomial coefficient as
-$$
-\binom{n}{k}
-= \frac{n(n-1)\cdots(n-k+1)}{k(k-1) \cdots 1}
-= \frac{n}{k} \cdot \frac{n-1}{k - 1} \cdots \frac{n-k+1}{1} \; .
-$$
-We claim that
-$$
-\frac{n}{k} \le \frac{n-1}{k - 1} \le \cdots \le \frac{n-k+1}{1}
-$$
-from which the lemma follows by upper bounding all the fractions by $n-k+1$.
-It remains to prove that for any $j=0,1,\dots,k-1$,
-$$
-\frac{n - j + 1}{k - j + 1} \le \frac{n - j}{k - j} \; .
-$$
-Multiplying by the (positive) denominators, we get an equivalent inequality
-$$
-(n - j + 1)(k - j) \le (n - j)(k - j + 1) \; .
-$$
-Cancelling common terms leads to an equivalent inequality
-$$
-k - j \le n - j \; ,
-$$
-which holds by the assumption on $n \ge k$.
-\end{proof}
-
-\begin{lemma}[Properties of the norm of polynomials]
-\label{lemma:properties-of-norm-of-polynomials}
-\hspace{1cm} % Dummy space
-\begin{enumerate}
-\item Let $p_1, p_2, \dots, p_n$ be multivariate polynomials and let $p(x) =
-\prod_{j=1}^n p_j(x)$ be their product.  Then, $\norm{p}^2 \le n^{\sum_{j=1}^n
-\deg(p_j)} \prod_{j=1}^n \norm{p_j}^2$.
-
-\item Let $q$ be a multivariate polynomial of degree at most $s$ and let $p(x) =
-(q(x))^n$. Then, $\norm{p}^2 \le n^{ns} \norm{q}^{2n}$.
-
-\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then,
-$\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-Using multi-index notation we can write any multivariate polynomial $p$ as
-$$
-p(x) = \sum_A c_A x^A
-$$
-where $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ is a multi-index (i.e. a $d$-tuple of
-non-negative integers), $x^A = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}$ is a
-monomial and $c_A = c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is the corresponding real
-coefficient. The sum is over a finite subset of $d$-tuples of non-negative
-integers. Using this notation, the norm of a polynomial $p$ can be written as
-$$
-\norm{p} = \sqrt{\sum_A (c_A)^2} \; .
-$$
-For a multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ we define its
-$1$-norm as $\norm{A}_1 = \alpha_1 + \alpha_2 + \dots + \alpha_d$.
-
-To prove the part 1, we express $p_j$ as
-$$
-p_j(x) = \sum_{A_j} c^{(j)}_{A_j} x^{A_j} \; .
-$$
-Since $p(x) = \prod_{i=1}^n p_j(x)$, the coefficients of its expansion $p(x) =
-\sum_A c_A x^A$ are
-$$
-c_A = \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \; .
-$$
-Therefore,
-\begin{multline*}
-\norm{p}^2
-= \sum_{A} (c_A)^2
-= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \right)^2
-= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\end{multline*}
-and
-\begin{multline*}
-\prod_{i=1}^n \norm{p_i}^2
-= \prod_{i=1}^n \left( \sum_{A_i} (c^{(i)}_{A_i})^2 \right)
-= \sum_{(A_1, A_2, \dots, A_n)} \prod_{j=1}^n (c^{(j)}_{A_j})^2
-= \sum_{(A_1, A_2, \dots, A_n)} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
-= \sum_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\end{multline*}
-where in both cases the outer sum is over multi-indices $A$ such that $\norm{A}_1 \le \deg(p)$.
-\autoref{lemma:simple-inequality} implies that for any multi-index $A$,
-$$
-\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\le M_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
-$$
-where $M_A$ is the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 +
-A_2 + \dots + A_n = A$.
-
-To finish the proof, it is sufficient to prove that $M_A \le n^{\deg(p)}$ for
-any $A$ such that $\norm{A}_1 \le \deg(p)$. To prove this inequality, consider a
-multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ and consider its $i$-th coordinate
-$\alpha_i$. In order for $A_1 + A_2 + \dots + A_n = A$ to hold, the $i$-th
-coordinates of $A_1, A_2, \dots, A_n$ need to sum to $\alpha_i$. There are exactly
-$\binom{\alpha_i + n - 1}{\alpha_i}$ possibilities for the choice of $i$-th
-coordinates of $A_1, A_2, \dots, A_n$. The total number of choices is thus
-$$
-M_A = \prod_{i=1}^d \binom{\alpha_i + n - 1}{\alpha_i} \; .
-$$
-Using \autoref{lemma:binomial-bound}, we upper bound it as
-$$
-M_A \le \prod_{i=1}^d n^{\alpha_i} = n^{\norm{A}_1} \le n^{\deg(p)} \; .
-$$
-
-Part 2 follows from the part 1 by setting $p_1 = p_2 = \dots p_n = q$.
-
-To prove the part 3, we use generalized triangle inequality and
-\autoref{lemma:simple-inequality}. We have
-\begin{align*}
-\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
-\end{align*}
-\end{proof}
-
-\subsection{Proof of \autoref{theorem:polynomial-approximation-1}}
-\label{section:proof-of-polynomial-approximation-1}
-
-To construct the polynomial $p$ we use Chebyshev polynomials of the first kind.
-Chebyshev polynomials of the fist kind form an infinite sequence of polynomials
-$T_0(z), T_1(z), T_2(z), \dots$ of single real variable $z$. They are defined
-by the recurrence
-\begin{align*}
-T_0(z) & = 1 \; , \\
-T_1(z) & = z \; , \\
-T_{n+1}(z) & = 2zT_n(z) - T_{n-1}(z) & \text{for $n \ge 1$.}
-\end{align*}
-Chebyshev polynomials have a lot of interesting properties.
-We will need properties listed in
-\autoref{proposition:properties-of-chebyshev-polynomials} below.
-Interested reader can learn more about Chebyshev polynomials
-from the book by \cite{Mason-Handscomb-2002}.
-
-\begin{proposition}[Properties of Chebyshev polynomials]
-\label{proposition:properties-of-chebyshev-polynomials}
-Chebyshev polynomials satisfy
-\begin{enumerate}
-\item $\deg(T_n) = n$ for all $n \ge 0$.
-\item If $n \ge 1$, the leading coefficient of $T_n(z)$ is $2^{n-1}$.
-\item $T_n(\cos(\theta)) = \cos(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
-\item $T_n(\cosh(\theta)) = \cosh(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
-\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$ and all $n \ge 0$.
-\item $T_n(z) \ge 1 + n^2(z - 1)$ for all $z \ge 1$ and all $n \ge 0$.
-\item $\norm{T_n} \le (1+\sqrt{2})^n$ for all $n \ge 0$
-\end{enumerate}
-\end{proposition}
-
-\begin{proof}[Proof of \autoref{proposition:properties-of-chebyshev-polynomials}]
-The first two properties can be easily proven by induction on $n$ using the recurrence.
-
-We prove third property by induction on $n$. Indeed, by definition
-$$
-T_0(\cos(\theta)) = 1 = \cos(0 \theta) \qquad \text{and} \qquad T_1(\cos(\theta)) = \cos(\theta) \; .
-$$
-For $n \ge 1$, we have
-\begin{align*}
-T_{n+1}(\cos(\theta))
-& = 2 \cos(\theta) T_n(\cos(\theta)) - T_{n-1}(\cos(\theta)) \\
-& = 2 \cos(\theta) \cos(n \theta) - \cos((n-1)\theta)) \; ,
-\end{align*}
-where the last step follow by induction hypothesis.
-It remains to show that the last expression equals $\cos((n+1)\theta)$.
-This can be derived from the trigonometric formula
-$$
-\cos(\alpha \pm \beta) = \cos(\alpha) \cos(\beta) \mp \sin(\alpha) \sin(\beta) \; .
-$$
-By substituting $\alpha = n \theta$ and $\beta = \theta$, we get two equations
-\begin{align*}
-\cos((n+1) \theta) & = \cos(n \theta) \cos(\theta) - \sin(n \theta) \sin(\theta) \; , \\
-\cos((n-1) \theta) & = \cos(n \theta) \cos(\theta) + \sin(n \theta) \sin(\theta) \; .
-\end{align*}
-Summing them yields
-$$
-\cos((n+1)\theta) + \cos((n-1) \theta) = 2 \cos(n \theta) \cos(\theta)
-$$
-which finishes the proof.
-
-Fourth property has the similar proof as third property. It suffices
-to replace $\cos$ and $\sin$ with $\cosh$ and $\sinh$ respectively.
-
-Fifth property follows from the third property. Indeed, for any $z \in [-1,1]$
-there exists $\theta \in \R$ such that $\cos \theta = z$. Thus, $|T_n(z)| =
-|T_n(\cos(\theta))| = |\cos(n\theta)| \le 1$.
-
-The sixth property is equivalent to
-$$
-T_n(\cosh(\theta)) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$,}
-$$
-since $\cosh(\theta) = \frac{e^{\theta} + e^{-\theta}}{2}$ is an even continuous
-function that maps $\R$ onto $[1,+\infty)$, is strictly decreasing on
-$(-\infty,0]$, and is strictly increasing on $[0,\infty)$. Using the fourth
-property the last inequality is equivalent to
-$$
-\cosh(n \theta) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$.}
-$$
-For $\theta = 0$, both sides are equal to $1$. Thus, it is sufficient to prove
-that the derivative of the left hand side is greater or equal to the derivative
-of the right hand side. Recalling that $[\cosh(\theta)]' = \sinh(\theta)$, this
-means that we need to show that
-$$
-\sinh(n \theta) \ge n \sinh(\theta) \qquad \text{for all $\theta \ge 0$.}
-$$
-Tho prove this inequality we use the summation formula
-$$
-\sinh(\alpha + \beta) = \sinh(\alpha) \cosh(\beta) + \sinh(\beta) \cosh(\beta) \; .
-$$
-If $\alpha, \beta$ are non-negative then $\sinh(\alpha), \sinh(\beta)$ are
-non-negative and $\cosh(\alpha), \cosh(\beta) \ge 1$. Hence,
-$$
-\sinh(\alpha + \beta) \ge \sinh(\alpha) + \sinh(\beta) \qquad \text{for any $\alpha, \beta \ge 0$.}
-$$
-This implies that (using induction on $n$) that $\sinh(n \theta) \ge n
-\sinh(\theta)$ for all $\theta \ge 0$.
-
-We verify the seventh property by induction on $n$.
-For $n=0$ and $n=1$ the inequality trivially holds, since $\norm{T_0} = \norm{T_1} = 1$.
-For $n \ge 1$, since $T_{n+1}(z) = 2zT_n(z) - T_{n-1}(z)$,
-\begin{align*}
-\norm{T_{n+1}}
-& \le 2 \norm{T_n} + \norm{T_{n-1}} \\
-& \le 2 (1 + \sqrt{2})^n + (1 + \sqrt{2})^{n-1} \\
-& = (1 + \sqrt{2})^{n-1} (2 (1 + \sqrt{2}) + 1) \\
-& = (1 + \sqrt{2})^{n-1} (3 + 2\sqrt{2}) \\
-& = (1 + \sqrt{2})^{n-1} (1 + \sqrt{2})^2 \\
-& = (1 + \sqrt{2})^{n+1} \; .
-\end{align*}
-
-\end{proof}
-
-Let $r = \left\lceil \log_2(2m) \right\rceil$ and $s = \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$.
-We define the polynomial $p:\R^d \to \R$ as
-$$
-p(x) = m + \frac{1}{2} - \sum_{i=1}^m \left( T_s(1 - \ip{v_i}{x}) \right)^r \; .
-$$
-It remains to show that $p$ has properties 1--5.
-
-To verify the first property notice that if $x \in \R^d$ satisfies $\norm{x} \le
-1$ and $\ip{v_i}{x} \ge \gamma$ then since $\norm{v_i} \le 1$ we have
-$\ip{v_i}{x} \in [0,1]$. Thus, $T_s(1 - \ip{v_i}{x})$ and $\left( T_s(1 -
-\ip{v_i}{x}) \right)^r$ lie in the interval $[-1,1]$. Therefore,
-$$
-p(x) \ge m + \frac{1}{2} - m \ge \frac{1}{2} \; .
-$$
-
-To verify the second property consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d
-~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Clearly, $\norm{x} \le 1$
-and there exists at least one $i \in \{1,2,\dots,m\}$ such that $\ip{v_i}{x} \le
-- \gamma$. Therefore, $1 - \ip{v_i}{x} \ge 1 + \gamma$ and~\autoref{proposition:properties-of-chebyshev-polynomials} (part 6)
-imply that
-$$
-T_s(1 - \ip{v_i}{x}) \ge 1 + s^2 \gamma \ge 2
-$$
-and thus
-$$
-\left( T_s(1 - \ip{v_i}{x}) \right)^r \ge 2^r \ge 2m \; .
-$$
-On the other hand for any $j \in \{1,2,\dots,m\}$, we have $\ip{v_j}{x} \in
-[-1,1]$ and thus $1 - \ip{v_j}{x}$ lies in the interval $[0,2]$. According to
-\autoref{proposition:properties-of-chebyshev-polynomials} (parts 5 and 6), $T_s(1 - \ip{v_j}{x})
-\ge -1$. Therefore,
-$$
-p(x) = m + \frac{1}{2} - \left( T_s(1 - \ip{v_i}{x}) \right)^r - \sum_{\substack{j ~:~  1 \le j \le m \\ j \neq i}} \le m + \frac{1}{2} - 2m + (m - 1) \le - \frac{1}{2} \; .
-$$
-
-The third property follows from observation that degree of $p$
-is the same as the degree of any one of the terms
-$\left( T_s(1 - \ip{v_i}{x}) \right)^r$ which is $r \cdot s$.
-
-To prove the fourth property, we need to upper bound the norm of $p$.
-Let $f_i(x) = 1 - \ip{v_i}{x}$, let $g_i(x) = T_s(1 - \ip{v_i}{x})$
-and let $h_i(x) = (T_s(1 - \ip{v_i}{x}))^r$. We have
-$$
-\norm{f_i}^2 = 1 + \norm{v_i}^2 \le 1 + 1 = 2 \; .
-$$
-Let $T_s(z) = \sum_{j=0}^s c_j z^j$ be the expansion of $s$-th Chebyshev polynomial.
-Then,
-\begingroup
-\allowdisplaybreaks
-\begin{align*}
-\norm{g_i}^2
-& = \norm{ \sum_{j=0}^s c_j (f_i)^j }^2 \\
-& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 & \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
-& = (s + 1) \sum_{j=0}^s (c_j)^2 \norm{(f_i)^j}^2 \\
-& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} & \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
-& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j 2^{2j} \\
-& \le (s + 1) s^s 2^{2s} \sum_{j=0}^s (c_j)^2 \\
-& = (s + 1) s^s 2^{2s} \norm{T_s}^2 \\
-& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} & \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
-& = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
-& \le \left(8(1+\sqrt{2})^2 s \right)^s & \text{(since $s+1 \le 2^s$ for any integer $s \ge 0$)} \\
-& \le \left(47 s \right)^s \; .
-\end{align*}
-\endgroup
-Finally,
-\begin{align*}
-\norm{p}
-& \le m + \frac{1}{2} + \sum_{i=1}^m \norm{(g_i)^r} \\
-& = m + \frac{1}{2} + \sum_{i=1}^m \sqrt{\norm{(g_i)^r}^2} \\
-& \le m + \frac{1}{2} + \sum_{i=1}^m \sqrt{r^{rs} \norm{g_i}^{2r}} \\
-& \le m + \frac{1}{2} + m r^{rs/2} \left(47 s \right)^{rs/2} \\
-& = m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \; .
-\end{align*}
-We can further upper bound the last expression by using that $m \le \frac{1}{2} 2^r$.
-Since $r,s \ge 1$,
-\begin{align*}
-\norm{p}
-& \le m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \\
-& \le \frac{1}{2} 2^r + \frac{1}{2} + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
-& \le 2^r + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
-& = 2^r \left(1 + \frac{1}{2} \left(47 rs \right)^{rs/2} \right) \\
-& = 2^r \left(47 rs \right)^{rs/2} \\
-& \le 4^{rs/2} \left(47 rs \right)^{rs/2} \\
-& \le \left(188 rs \right)^{rs/2} \; .
-\end{align*}
-Substituting for $r$ and $s$ finishes the proof.
-
-\subsection{Proof of \autoref{theorem:polynomial-approximation-2}}
-\label{section:proof-of-polynomial-approximation-2}
-
-We define several univariate polynomials
-\begin{align*}
-P_n(z) & = (z - 1) \prod_{i=1}^n (z - 2^i)^2 && \text{for $n \ge 0$,} \\
-A_{n,k}(z) & = (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$,} \\
-B_{n,k}(z) & = - (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$.}
-\end{align*}
-We define the polynomial $p:\R^d \to \R$ as
-$$
-p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
-- \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-$$
-
-For convenience we define univariate rational function
-\begin{align*}
-S_{n,k}(z) & = \frac{A_{n,k}(z)}{B_{n,k}(z)} && \text{for $n,k \ge 0$,}
-\end{align*}
-and a multivariate rational function
-$$
-Q(x) = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \; .
-$$
-It easy to verify that
-$$
-p(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-$$
-
-\begin{lemma}[Properties of $P_n$]
-\label{lemma:properties-of-p-n}
-\hspace{1cm} % Dummy space
-\begin{enumerate}
-\item If $z \in [0,1]$ then $P_n(-z) \le P_n(z) \le 0$.
-\item If $z \in [1,2^n]$ then $0 \le 4P_n(z) \le -P_n(-z)$.
-\item If $z \ge 0$ then $-P_n(-z) \ge 2^{n(n+1)}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-To prove the first part, note that $P_n(z)$ and $P_n(-z)$ are non-positive for
-$z \in [0,1]$. We can write $\frac{P_n(z)}{P_n(-z)}$ as a product of $n+1$
-non-negative fractions
-$$
-\frac{P_n(z)}{P_n(-z)} = \frac{1-z}{1+z} \prod_{i=1}^n \frac{(z+2^i)^2}{(z-2^i)^2} \; .
-$$
-The first part follows from the observation that each fraction is upper bounded
-by $1$.
-
-To prove the second part, notice that $P_n(z)$ is non-negative and $P_n(-z)$ is
-non-positive for any $z \in [1,2^n]$. Now, fix $z \in [1,2^n]$ and let $j \in
-\{1,2,\dots,n\}$ be such that $2^{j-1} \le z \le 2^j$. This implies that
-$(z+2^{j})^2 \ge 4 (z - 2^j)^2$. We can write $\frac{P_n(z)}{-P_n(-z)}$ as a
-product of $n+1$ non-negative fractions
-$$
-\frac{P_n(z)}{-P_n(-z)}
-= \frac{z-1}{z+1} \cdot \frac{(z-2^j)^2}{(z+2^j)^2} \prod_{\substack{i ~:~ 1 \le i \le n \\ i \neq j}} \frac{(z-2^i)^2}{(z+2^i)^2} \; .
-$$
-The second part follows from the observation that the second fraction is upper
-bounded by $1/4$ and all other fractions are upper bounded by $1$.
-
-The third part follows from
-$$
--P_n(-z) = (1+z) \prod_{i=1}^n (z+2^i)^2 \ge \prod_{i=1}^n 2^{2i} = 2^{n(n+1)} \; .
-$$
-\end{proof}
-
-\begin{lemma}[Properties of $S_{n,r}$ and $B_{n,r}$]
-\label{lemma:properties-of-s-n-r}
-Let $n,m$ be non-negative integers.
-Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$. Then,
-\begin{enumerate}
-\item If $z \in [1,2^n]$ then $S_{n,r}(z) \in [1,1+\frac{1}{2m}]$.
-\item If $z \in [-2^n, -1]$ then $S_{n,r} \in [-1-\frac{1}{2m}, -1]$.
-\item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
-\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-Note that $B_{n,r}(z)$ is an even function and $A_{n,r}(z)$ is an odd function.
-Therefore, $S_{n,r}(z)$ is odd. Also notice that $r$ is an odd integer.
-
-\begin{enumerate}
-\item Observe that $S_{n,r}(z)$ can be written as
-$$
-S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. Since
-$r \ge \frac{1}{2} \log_2(4m+1)$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
-$S_{n,r}(z) = \frac{1+c}{1-c} \in [1,1 + \frac{1}{2m}]$.
-
-\item Since $S_{n,r}(z)$ is odd, the statement follows from part 1.
-
-\item Observe that $S_{n,r}(z)$ can be written as
-$$
-S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. If $z \in [0,1]$, by part
-1 of~\autoref{lemma:properties-of-p-n} and the fact that $r$ is odd, $c
-\in [-1,0]$, and thus, $S_{n,r}(z) = \frac{1+c}{1-c} \in [0,1]$. Since
-$S_{n,r}(z)$ is odd, for $z \in [-1,0]$, $S_{n,r}(z) \in [-1,0]$.
-
-\item Since $B_{n,r}(z)$ is even, we can without loss generality assume that $z \ge
-0$. We consider two cases.
-
-Case $z \in [0,1]$. Since $r$ is odd and $P_n(z)$ is non-positive,
-$$
-B_{n,r}(z) = - (P_n(z))^r + \left(- P_{n}(-z)\right)^r \ge \left(- P_{n}(-z)\right)^r \ge 2^{n(n+1)r} \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
-where the second last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
-
-Case $z \in [1,2^n]$. Since $r$ is odd,
-$$
-B_{n,r}(z) = \left(- P_{n}(-z)\right)^r \left(1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r \right) = \left(- P_{n}(-z)\right)^r (1 - c)
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. By
-the definition of $r$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
-$$
-B_{n,r}(z) \ge \left(- P_{n}(-z)\right)^r \left( 1 - \frac{1}{4m+1} \right) \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
-where the last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
-\end{enumerate}
-\end{proof}
-
-\begin{lemma}[Properties of $Q(x)$]
-\label{lemma:properties-of-q}
-The rational function $Q(x)$ satisfies
-\begin{enumerate}
-\item $Q(x) \ge \frac{1}{2}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
-\item $Q(x) \le -\frac{1}{2}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-To prove part 1, consider any $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \
-\ip{v_i}{x} \ge \gamma \right\}$. Then, $\frac{\ip{v_i}{x}}{\gamma} \in [1,
-\frac{1}{\gamma}]$. By part 1 of \autoref{lemma:properties-of-s-n-r},
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \in [1, 1 + \frac{1}{2m}]$ and
-in particular $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \ge 1$. Thus,
-$$
-Q(x) = \left( \sum_{i=1}^m S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \right) - (m - 1/2) \ge m - (m - 1/2) = 1/2 \; .
-$$
-
-To prove part 2, consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~
-\norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Observe that
-$\frac{\ip{v_i}{x}}{\gamma} \in [-\frac{1}{\gamma}, \frac{1}{\gamma}]$. Consider
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right)$ for any $i \in
-\{1,2,\dots,m\}$. Parts 1,2, and 3 of \autoref{lemma:properties-of-s-n-r}
-and the fact $1/\gamma \le 2^s$ imply that
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \le 1 +
-\frac{1}{2m}$ for all $i \in \{1,2,\dots,m\}$. By the choice of $x$, there
-exists $j \in \{1,2,\dots,m\}$ such that $\ip{v_j}{x} \le - \gamma$. Part 2 of
-\autoref{lemma:properties-of-s-n-r} implies that
-$S_{s,r}\left(\frac{\ip{v_j}{x}}{\gamma}\right) \in [-1-\frac{1}{2m},-1]$. Thus,
-\begin{align*}
-Q(x)
-& = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& = S_{s,r}\left( \frac{\ip{v_j}{x}}{\gamma} \right) + \left( \sum_{\substack{i ~:~ 1 \le i \le m \\ i \neq j}} S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& \le -1 + (m-1) \left( 1 + \frac{1}{2m} \right) - \left(m - \frac{1}{2} \right) \\
-& \le 1/2 \; .
-\end{align*}
-\end{proof}
-
-To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-2} first
-note that part 4 of \autoref{lemma:properties-of-s-n-r} implies that for any $x$
-such that $\norm{x} \le 1$, $B_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right)$
-is positive. Thus $p(x)$ and $Q(x)$ have the same sign on the unit ball.
-Consider any $x$ in either
-$\displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-or in
-$\displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
-\autoref{lemma:properties-of-q} states that $|Q(x)| \ge 1/2$ and the sign
-depends on which of the two sets $x$ lies in. Since signs of $Q(x)$ and $p(x)$
-are the same, it remains to show that $|p(x)| \ge m^{s^2m/2}$. Indeed,
-\begin{align*}
-|p(x)|
-& = |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
-& \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
-& \ge \frac{1}{2} |Q(x)| \cdot 2^{s(s+1)rm} && \text{(since $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4} \ge 1/2$)} \\
-& \ge \frac{1}{4} \cdot 2^{s(s+1)rm} && \text{(\autoref{lemma:properties-of-q})} \; .
-\end{align*}
-
-To prove part 3 of \autoref{theorem:polynomial-approximation-2} note that
-$\deg(P_s) = 2s+1$. Thus, $\deg(A_{s,r})$ and $\deg(B_{s,r})$ are at most
-$(2s+1)r$. Therefore, $\deg(p) \le (2s+1) rm$.
-
-It remains to prove part 4 of \autoref{theorem:polynomial-approximation-2}.
-For any $i \in \{0,1,2,\dots,s\}$ and any $v \in \R^d$ such that $\norm{v} \le 1$
-define multivariate polynomials
-\begin{align*}
-f_{i,v}(x) & = \frac{\ip{v}{x}}{\gamma} - 2^i \; , \\
-q_v(x) & = P_s \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
-a_v(x) & = A_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
-b_v(x) & = B_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; .
-\end{align*}
-Note that
-$$
-p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
-$$
-We bound the norms of these polynomials. We have
-$$
-\norm{f_{i,v}}^2 = \norm{v}^2/\gamma^2 + 2^{2i} \le 2 \cdot 2^s \; .
-$$
-where we used that $1/\gamma \le 2^s$ and $\norm{v} \le 1$.
-Since $q_v(x) = f_{i,v}(\frac{\ip{v}{x}}{\gamma}) \prod_{i=1}^s \left(f_{i,v}(\frac{\ip{v}{x}})\right)^2$,
-using part 1 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $q_v$
-as
-$$
-\norm{q_v}^2 \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \le  (2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \; .
-$$
-Using parts 3 and 2 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $a_v$ as
-\begin{align*}
-\norm{a_v}^2
-& \le 2\norm{(q_v)^r}^2 + 2\norm{(q_{-v})^r}^2 \\
-& \le 2 r^{r(2s+1)} \norm{q_v}^{2r} + 2 r^{r(2s+1)} \norm{q_{-v}}^{2r} \\
-& \le 4 r^{r(2s+1)} \left((2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \right)^{2r} \\
-& = 4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \; .
-\end{align*}
-The same upper bound holds for $\norm{b_v}^2$. Finally,
-\begin{align*}
-\norm{p}
-& \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
-& \le \left[ \sum_{i=1}^m m^{(s+1/2)rm} \norm{a_{v_i}} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} \norm{b_{v_j}} \right] + \left(m - \frac{1}{2} \right) m^{(s+1/2)rm} \prod_{j=1}^m \norm{b_{v_j}} \\
-& \le (2m-1/2) m^{(s+1/2)rm} \left(4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \right)^{m/2} \\
-& = (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm} \; .
-\end{align*}
-
-\section{Nearest neighbor algorithm}
-
-TODO
-
-\section{NP-hardness of the weak labeling problem}
-
-Any algorithm for the bandit setting collects information in the form of so
-called \emph{strongly labeled} and \emph{weakly labeled} examples.
-Strongly-labeled examples are those for which we know the class label. Weakly
-labeled example is an example for which we know that class label can be anything
-except for a particular one class.
-
-A natural strategy for each round is to find vectors $w_1, w_2, \dots, w_K$ that
-linearly separate the examples seen in the previous rounds and use the vectors
-to predict the label in the next round. More precisely, we want to find both the
-vectors $w_1, w_2, \dots, w_K$ and label for each example consistent with its
-weak and/or strong labels such that $w_1, w_2, \dots, w_K$ linearly separate the
-labeled examples. We show this problem is NP-hard even for $K=3$.
-
-Clearly, the problem is at least as hard as the decision version of the problem
-where the goal is to determine if such vectors and labeling exist. We show that
-this problem is NP-complete.
-
-Formally, the input to the decision problem are positive integers $d, T, K$ and
-a sequence $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \{0,1\}^d \times
-\{1,2,\dots,K, \overline{1}, \overline{2}, \dots, \overline{K}\}$ of strongly
-and weakly labeled examples. The numbers $1,2,\dots,K$ correspond to strong
-labels and the symbols $\overline{1}, \overline{2}, \dots, \overline{K}$
-correspond to weak labels. We adopt the convention that $\overline{\overline{i}}
-= i$ for any positive integer $i$. The goal is to determine whether or not there
-exist vectors $w_1, w_2, \dots, w_K \in \R^d$ that satisfy the following
-conditions for all $t=1,2,\dots,T$,
-\begin{align*}
-y_t \in \{1,2,\dots,K\} \qquad & \Longrightarrow \qquad & \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \qquad \ip{w_{y_t}}{x_t} & > \ip{w_i}{x_t} \; , \\
-y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \qquad & \Longrightarrow & \qquad \exists i \in \{1,2,\dots,K\} \qquad \ip{w_i}{x_t} & > \ip{w_{\overline{y_t}}}{x_t} \; .
-\end{align*}
-
-TODO
-
-\section{Mistake lower bound for ignorant algorithms}
-
-TODO
-
-\bibliographystyle{plainnat}
-\bibliography{biblio}
-
-\appendix
-
-\section{Multiclass Perceptron}
-\label{section:multiclass-perceptron-proofs}
-
-\textsc{Multiclass Perceptron} is an algorithm for \textsc{Online Multiclass
-Classification}. Both the protocol for the problem and the algorithm are stated
-below. The algorithm assumes that the feature vectors come from an inner product
-space $(V, \ip{\cdot}{\cdot})$.
-
-Two results are folklore. The first result is
-\autoref{theorem:mutliclass-perceptron-mistake-upper-bound} which states that if
-examples are linearly separable with margin $\gamma$ and examples have norm
-at most $R$ then the algorithm makes at most $\lfloor 2 (R/\gamma)^2 \rfloor$
-mistakes. The second result is
-\autoref{theorem:online-multiclass-classification-mistake-lower-bound} which
-states that under the same assumptions as in
-\autoref{theorem:online-multiclass-classification-mistake-lower-bound}
-\emph{any} deterministic algorithm for \textsc{Online Multiclass Classification}
-must make at least $\lfloor (R/\gamma)^2 \rfloor$ mistakes in the worst case.
-
-\begin{algorithm}[h]
-\caption{\textsc{Online Multiclass Classification}
-\label{algorithm:mutliclass-classification}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$}
-\STATE{Predict $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[h]
-\caption{\textsc{Multiclass Perceptron}
-\label{algorithm:mutliclass-perceptron}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
-\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t \in V$}
-\STATE{Predict $\widehat y_t = \argmax_{i \in \{1,2,\dots,K\}} \ip{w_t^{(i)}}{x_t}$}
-\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
-\IF{$\widehat y_t \neq y_t$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}$}
-\STATE{Update $w_{y_t}^{(t+1)} = w_{y_t}^{(t)} + x_t$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ENDIF
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{theorem}[Mistake upper bound]
-\label{theorem:mutliclass-perceptron-mistake-upper-bound}
-Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
-integer, let $\gamma$ be a positive real number and let $R$ be a non-negative real
-number. If $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled
-examples in $V \times \{1,2,\dots,K\}$ that are linearly separable with margin
-$\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
-then \textsc{Multiclass Perceptron} algorithm makes at most $\lfloor
-2(R/\gamma)^2 \rfloor$ mistakes.
-\end{theorem}
-
-\begin{proof}
-Let $M = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$ be the number of
-mistakes the algorithm makes. Since the $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots,
-w_K^{(t)})$ changes only if a mistake is made, we can upper bound $\sum_{i=1}^K
-\norm{w_i^{(t)}}^2$ in terms of number of mistakes.
-If a mistake happens in round $t$ then
-\begin{align*}
-\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
-& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) + \norm{w_{y_t}^{(t)} + x_t}^2 + \norm{w_{\widehat y_t}^{(t)} - x_t}^2 \\
-& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) + \norm{w_{y_t}^{(t)}}^2 + \norm{w_{\widehat y_t}^{(t)}}^2 + 2 \norm{x_t}^2 + 2 \ip{w_{y_t}^{(t)} - w_{\widehat y_t}^{(t)}}{x_t} \\
-& = \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 \norm{x_t}^2 + 2 \ip{w_{y_t}^{(t)} - w_{\widehat y_t}^{(t)}}{x_t} \\
-& \le \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 \norm{x_t}^2 \\
-& \le \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 R^2 \; .
-\end{align*}
-So each time a mistake happens, $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ increases by at most $2R^2$. Thus,
-$$
-\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le 2R^2 M \; .
-$$
-Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors satisfying the
-\eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2}. We lower bound $\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$. This quantity changes
-only when a mistakes happens. If mistake happens in round $t$, we have
-\begin{align*}
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(t+1)}}
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^*}{w_{y_t}^{(t)} + x_t} + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} - x_t} \\
-& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^* - w_{\widehat y_t}^*}{x_t} \\
-& \ge  \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \gamma \; .
-\end{align*}
-Thus, after $M$ mistakes,
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma M \; .
-$$
-We upper bound the left hand side by using Cauchy-Schwartz inequality twice and
-the condition \eqref{equation:linear-separability-1} on $w_1^*, w_2^*, \dots,
-w_K^*$. We have
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
-\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
-$$
-Combining all inequalities, we get
-$$
-(\gamma M)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le 2R^2 M \; .
-$$
-We conclude that $M \le 2(R/\gamma)^2$. Since $M$ is an integer, $M \le \lfloor 2(R/\gamma)^2 \rfloor$.
-\end{proof}
-
-\begin{theorem}[Mistake lower bound]
-\label{theorem:online-multiclass-classification-mistake-lower-bound}
-Let $K$ be a positive integer, let $\gamma$ be a positive real number and let
-$R$ be a non-negative real number. For any deterministic algorithm for the
-\textsc{Online Multiclass Classification} problem there exists an
-inner product space $(V, \ip{\cdot}{\cdot})$, a non-negative integer $T$ and a
-sequence of labeled examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$
-examples in $V \times \{1,2,\dots,K\}$ that are linearly separable with margin
-$\gamma$, the norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
-and the algorithm makes at least $\lfloor (R/\gamma)^2 \rfloor$ mistakes.
-\end{theorem}
-
-\begin{proof}
-Let $T = \lfloor (R/\gamma)^2 \rfloor$ and let $x_1, x_2, \dots, x_T$ be the
-orthogonal vectors such that $\norm{x_t} = R$ for all $t=1,2,\dots,T$. For
-example, we can take $V = \R^T$ and $x_t = R e_t$ where $e_t$ is $t$-th element
-of the standard orthonormal basis of $\R^T$.
-
-Since the algorithm is deterministic, we can construct the sequence of labels
-$y_1, y_2, \dots, y_T$ adaptively based on the predictions $\widehat y_1,
-\widehat y_2, \dots, \widehat y_T$ of the algorithm. We define $y_t$ to be any
-element of $\{1,2,\dots,K\}$ not equal to $\widehat y_t$. This way the algorithm
-makes a mistake in every round $t=1,2,\dots,T$.
-
-It remains to show that the examples we have constructed are linearly separable
-with margin $\gamma$. To prove that we demonstrate vectors $w_1, w_2, \dots, w_K$
-satisfying conditions \eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2}. We define
-$$
-w_i = \frac{1}{R\sqrt{T}} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} x_t \qquad \qquad \text{for $i=1,2,\dots,K$.}
-$$
-Let $a_i = |\{ t ~:~ 1 \le t \le T, \ y_t = i \}|$ be the number of occurrences of label $i$.
-It is easy to see that
-$$
-\norm{w_i}^2 = \frac{1}{R^2 T} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} \norm{x_t}^2 = \frac{a_i}{T} \qquad \qquad \text{for $i=1,2,\dots,K$.}
-$$
-Since $\sum_{i=1}^K a_i = T$, the condition
-\eqref{equation:linear-separability-1} holds. To verify condition
-\eqref{equation:linear-separability-2} consider any labeled example $(x_t,
-y_t)$. Then, by definition of $w_{y_t}$ we have
-$$
-\ip{w_{y_t}}{x_t}
-= \frac{1}{R\sqrt{T}} \sum_{\substack{s : 1 \le s \le T \\ y_s = y_t}} \ip{x_s}{x_t}
-= \frac{1}{R\sqrt{T}} \norm{x_t}^2
-= \frac{R}{\sqrt{T}}
-\ge \frac{R}{R/\gamma}
-= \gamma \; .
-$$
-and for any $i \in \{1,2,\dots,K\} \setminus \{y_t\}$ we have
-$\ip{w_i}{x_t} = 0$. Therefore, condition \eqref{equation:linear-separability-2} holds.
-\end{proof}
-
-\end{document}

### 2019-01-07 arxiv-version/appendix-multiclass-perceptron.tex
Split sections in separate files

--- 2018-12-27 arxiv-version/main.tex
@@
-\documentclass[12pt]{article}
-
-% LaTeX packages
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage[singlelinecheck=false]{caption}
-\usepackage{fullpage}
-\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
-\usepackage{natbib}
-\usepackage{thmtools}
-\usepackage{tikz}
-\usepackage{color}
-\usepackage{comment}
-
-% TikZ packages
-\usetikzlibrary{arrows}
-\usetikzlibrary{angles}
-\usetikzlibrary{backgrounds}
-\usetikzlibrary{calc}
-\usetikzlibrary{cd}  % commutative diagrams
-\usetikzlibrary{intersections}
-\usetikzlibrary{patterns}
-\usetikzlibrary{shapes}
-\usetikzlibrary{through}
-
-% Math environments
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}[definition]{Proposition}
-\newtheorem{lemma}[definition]{Lemma}
-\newtheorem{theorem}[definition]{Theorem}
-\newtheorem{corollary}[definition]{Corollary}
-
-% Math symbols and commands
-\newcommand{\R}{\mathbb{R}}  % set of real numbers
-\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]} % indicator
-\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
-\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
-%\DeclareMathOperator*{\deg}{deg}
-\DeclareMathOperator*{\argmax}{argmax}
-\DeclareMathOperator*{\argmin}{argmin}
-\DeclareMathOperator*{\Exp}{\mathbf{E}}  % expected value
-\DeclareMathOperator{\diff}{d \!} % differential
-\DeclareMathOperator*{\polylog}{polylog}
-
-\definecolor{darkgreen}{rgb}{0,0.5,0}
-\definecolor{darkred}{rgb}{0.7,0,0}
-\definecolor{teal}{rgb}{0.3,0.8,0.8}
-\definecolor{orange}{rgb}{1.0,0.5,0.0}
-\definecolor{purple}{rgb}{0.8,0.0,0.8}
-\definecolor{blue}{rgb}{0.0,0.0,1.0}
-\newcommand{\kibitz}[2]{{\textcolor{#1}{\textsf{\footnotesize #2}}}}
-\newcommand{\alina}[1]{\kibitz{darkred}{[AB: #1]}}
-\newcommand{\david}[1]{\kibitz{darkgreen}{[DP: #1]}}
-\newcommand{\balazs}[1]{\kibitz{purple}{[BS: #1]}}
-\newcommand{\deva}[1]{\kibitz{teal}{[DT: #1]}}
-\newcommand{\chenyu}[1]{\kibitz{orange}{[CW: #1]}}
-\newcommand{\chicheng}[1]{\kibitz{blue}{[CZ: #1]}}
-
-\title{Online Multiclass Linear Classification with Bandit Feedback}
-
-\author{
-Alina Beygelzimer \and
-D\'avid P\'al \and
-Bal\'azs Sz\"or\'enyi \and
-Devanathan Thiruvenkatachari \and
-Chen-Yu Wei \and
-Chicheng Zhang
-}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-We study the problem of efficient online multiclass linear classification with bandit feedback, where all examples belong to one of $K$ classes and lie in the $d$-dimensional Euclidean space.
-Previous works have left open the challenge of designing efficient algorithms with finite mistake bounds
-when the data is linearly separable by a margin $\gamma$.
-In this work, we take a first step towards this problem.
-We identify two notions of linear separability:
-one-versus-all (OvA) linear separability and weakly linear separability.
-\begin{enumerate}
-\item Under the OvA
-linear separability condition, we design an efficient algorithm that achieves a near-optimal mistake bound of $O(\frac{K}{\gamma^2})$.
-\item Under the more challenging weakly linear separability condition, we design an efficient algorithm with a mistake bound of $2^{\tilde{O}(\min(K \log^2 \frac 1 \gamma, \log K \sqrt{\frac 1 \gamma})) }$ \footnote{We use the notation $\tilde{O}(f(\cdot)) = O( f(\cdot) \polylog(f(\cdot)) )$.}.
-Our algorithm is based on a reduction from weakly linear separability to OvA linear separability via an infinite dimensional monomial feature map, which in turn is inspired by ~\cite{Klivans-Servedio-2008}'s work on learning intersection of halfspaces.
-\end{enumerate}
-
-%We focus on the setting where there are $K$ classes, and there is a $d$-dimensional multiclass linear classifier that separates all the examples shown with a positive margin $\gamma$.
-%$2^{O(\min(K \log^2 K \log^2 \frac 1 \gamma, \log K \log \log K \sqrt \frac 1 \gamma \log \frac 1\gamma))}$
-%$\min( (\log K \sqrt{\frac 1 \gamma})^{O(\log K \sqrt{\frac 1 \gamma})}, K^{O(K \log K \log^2 \frac1\gamma)} )$.
-
-\end{abstract}
-
-\section{Introduction}
-\label{section:introduction}
-
-We study the problem of \textsc{Online Multiclass Linear
-Classification with Bandit Feedback}~\cite{Kakade-Shalev-Shwartz-Tewari-2008}.
-The problem can be viewed as a game between the learner and the environment:
-at each timestep $t$, the environment chooses an example $(x_t, y_t)$, where its feature
-part $x_t \in \R^d$ is revealed to the learner.
-\footnote{All our results apply to also to a simpler model of
-the so called \emph{oblivious adversary} where the whole sequence of labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is chosen before the first
-round of the game.}
-Upon receiving this example, the
-learner is asked to make a prediction $\hat{y}_t$.
-the learner receives feedback immediately after making its prediction.
-In contrast with the standard full information setting (where the feedback given is the correct label $y_t$), the feedback given is only a binary indicator
-whether the prediction was correct or not. The protocol of the problem is formally stated below.
-
-%In this problem, in each round, the
-%learner receives a feature vector and is asked to predict one of $K$
-%possible classes. To allow
-%for meaningful use of randomization, we assume that the correct label in a
-%particular round is chosen prior to algorithm's prediction in that
-%round.
-%Immediately after the learner makes its prediction, it
-%receives feedback whether the prediction was correct or not. However, in
-%contrast with the standard, so called full information setting, the algorithm
-%does \emph{not} receive the correct label. The feedback is only binary.
-
-\begin{algorithm}[h]
-\caption{\textsc{Online Multiclass Classification with Bandit Feedback}
-\label{algorithm:game-protocol}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$}
-\STATE{Adversary \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
-\chicheng{Or we simply say: Adversary chooses example $(x_t, y_t)$, where $x_t$ is reveal to the learner.}
-\STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \begin{cases}
-0 & \text{if $\widehat y_t = y_t$,} \\
-1 & \text{if $\widehat y_t \neq y_t$.}
-\end{cases}$
-}
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-The performance is of the learner is measured by its cumulative number of mistakes
-$\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$. The bandit feedback
- is a natural feedback model motivated by applications including
-online advertising and online content optimization, where the learner only gets to
-see the loss of its action taken.
-%where the binary feedback corresponds to a click
-%The
-%corresponding problem with full information feedback is solved by the classical
-%\textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
-%\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}).
-
-In this paper, we focus on the special case when the examples lie in $\R^d$ and
-are \emph{linearly separable with a margin}.
-\chicheng{I wonder if we should introduce the two notions of linear separability here,
-because strong linear separability is also worth mentioning in the full-information setting.
-}
-
-In the full-information feedback
-setting, it is well known that if the examples have norm at most $R$ and are
-linearly separable with a margin $\gamma$ then the \textsc{Multiclass
-Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
-This result is very satisfying since the upper bound on the number of mistakes
-is information-theoretically optimal and at the same time the \textsc{Multiclass
-Perceptron} algorithm has low time and memory complexity.
-
-The bandit feedback setting, however, is much more challenging. To understand
-the differences, we dissect the notion of linear separability in the multiclass
-setting. Beside the standard notion of linear separability, we define also
-\emph{strong linear separability}. For binary classification, these two
-definitions are identical. However, they differ for multiclass classification.
-For multiclass classification with $K$ classes the standard notion of linear
-separability means that the examples from each class lie in an intersection of
-$K-1$ halfspaces and the examples outside of the class lie in the complement of
-the intersection of the halfspaces. Strong linear separability means that
-examples from each class are separated from the remaining examples by a
-\emph{single} hyperplane. We state the definitions precisely in
-Section~\ref{section:notions-of-linear-separability}.
-
-For the case when the examples are strongly linearly separable, we design a
-simple and efficient algorithm with expected number of mistakes at most $(K-1)
-\lfloor (R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies
-of the \textsc{Binary Perceptron} algorithm, one copy for each class.
-Intuitively speaking, the factor $K-1$ is the price we pay for the bandit
-feedback, or more precisely, the lack of full-information feedback. We also
-prove that any (possibly randomized) algorithm makes $\Omega(K (R/\gamma)^2))$
-mistakes in the worst case.
-
-For the standard notion of linear separability, we propose several algorithms
-with various time-complexity-versus-mistake-bound trade-offs. First class of
-algorithms map the examples into a high-dimensional inner product space. In this
-space the examples become \emph{strongly} linearly separable. This allows us to
-run the algorithm for the strongly linearly separable case. All of these
-algorithms can be kernelized. (Some of them have to be kernelized since the
-underlying inner product space is infinite dimensional.) Kernelization does not
-change the input-output behavior of the algorithm, it only affects its time
-and memory complexity.
-
-These algorithms differ by choice of the mapping or, equivalently, choice of the
-kernel. The crux of the problem is the analysis of the approximation properties
-of these mappings/kernels and the way margin in the original space $\R^d$ under
-standard linear separability notion gets transformed into a margin in the
-high-dimensional space under the strong separability notion. This problem is
-related to the problem of learning intersection of halfspaces and has been
-studied previously by \cite{Klivans-Servedio-2008}. As an important technical
-achievement, we improve on the results of \cite{Klivans-Servedio-2008} by
-removing completely the dependency on the original dimension $d$.
-
-Finally, we propose a very different algorithm that is based on the obvious idea
-that two points that are close enough must have the same label. Here, close
-enough means that they cannot be separated from each other by a linear separator
-with a margin.
-
-All the algorithms run in time that is polynomial in the dimension of the
-feature vectors, the number of classes and the number of rounds. At the same
-time, all the algorithms make number of mistakes that does \emph{not} depend
-on the number of rounds. Instead, their number of mistakes depends only on the
-margin, number of classes, dimension of the feature vectors, and the radius of
-the ball in which the data lie.
-
-Finally, we study two questions related to the computational and
-information-theoretic hardness of the problem. Any algorithm for the bandit
-setting collects information in the form of so called \emph{strongly labeled}
-and \emph{weakly labeled} examples. Strongly labeled examples are those for
-which we know the class label. Weakly labeled example is an example for which we
-know that class label can be anything except for a particular one class. First,
-we show the offline problem of finding a linear multiclass separator consistent
-with a set of strongly and weakly labeled examples is NP-hard. This result is a
-consequence of the fact that finding an intersection of two halfspaces
-consistent with a set of binary-labeled examples is
-NP-hard~\citep{Blum-Rivest-1993}. Second, we show that any algorithm that uses
-only strongly-labeled examples and ignores weakly labeled examples makes at
-least $\Omega(???)$ mistakes.
-
-\section{Related work}
-\label{section:related-work}
-
-\begin{itemize}
-\item \cite{Abernethy-Rakhlin-2009}
-
-\item \cite{Chen-Chen-Zhang-Chen-Zhang-2009}
-
-\item \cite{Hazan-Kale-2011}
-
-\item \cite{Beygelzimer-Orabona-Zhang-2017}
-
-\item \cite{Foster-Kale-Luo-Mohri-Sridharan-2018}
-
-\item \cite{Foster-Krishnamurthy-2018}
-\end{itemize}
-
-TODO
-
-\section{Notions of linear separability}
-\label{section:notions-of-linear-separability}
-
-We define two notions of linear separability for multiclass classification. The
-first notion is the standard notion of linear separability used in the proof of
-the mistake bound for the \textsc{Multiclass Perceptron} algorithm. The second
-notion is stronger, i.e. more restrictive. However, it is more suitable for the
-bandit setting, since it allows for a simple and efficient algorithm; see
-Section~\ref{section:algorithm-for-strongly-linearly-separable-data}.
-
-\begin{definition}[Linear separability]
-Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
-integer, and let $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
-y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.
-
-The examples are said to be \emph{linearly separable with a
-margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
-that
-\begin{align}
-\label{equation:linear-separability-1}
-\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
-\label{equation:linear-separability-2}
-\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} & \ge \ip{x_t}{w_i} + \gamma \; .
-\end{align}
-
-The examples are said to be \emph{strongly linearly separable with a
-margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
-that
-\begin{align}
-\label{equation:strong-linear-separability-1}
-\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
-\label{equation:strong-linear-separability-2}
-\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
-\label{equation:strong-linear-separability-3}
-\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
-\end{align}
-\end{definition}
-
-The notion of linear separability with a margin is standard. It used in the
-full-information setting to upper bound the number of mistakes of the
-\textsc{Multiclass Perceptron} algorithm. For completeness, we state the
-algorithm in Appendix~\ref{section:multiclass-perceptron-proofs}. It is a
-folklore result that if a set of labeled examples is separable with a margin
-$\gamma$ and the norm of the examples is bounded by $R$ then \textsc{Multiclass
-Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
-mistakes. Another folklore result is that \textsc{Multiclass Perceptron} is
-essentially optimal in the sense that any deterministic algorithm must make
-$\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
-completeness, we give proofs of both of these results in
-Appendix~\ref{section:multiclass-perceptron-proofs}.
-
-The notion of strong linear separability is new.
-
-It is easy to see that if labeled examples are strongly linearly
-separable with margin $\gamma$ then they are linearly separable with margin
-$2\gamma$. Indeed, if $w_1, w_2, \dots, w_K \in V$
-satisfy \eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3} then they satisfy
-\eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} with margin $\gamma' = 2\gamma$.
-
-Similarly, if $K=2$ and labeled examples are linearly separable with a margin
-$\gamma$ then they are strongly linearly separable with margin $\gamma/2$.
-Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$, $w_2' =
-\frac{w_2 - w_1}{2}$ and $\gamma'=\gamma/2$ satisfy
-\eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3}. The last two conditions are easy
-to see. The first condition follows from $\norm{w_i'}^2 \le (\frac{1}{2}
-\norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le \frac{1}{2}\norm{w_1}^2 +
-\frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
-
-However, for any $K \ge 3$ and any inner product space of dimension at least
-$2$, there exists a set of labeled examples that is linearly separable with a
-positive margin $\gamma$ but it is not strongly linearly separable with any
-positive margin $\gamma$. An example of such set of labeled examples is shown in
-Figure~\ref{figure:linearly-separable-examples-with-margin}.
-
-\begin{figure}
-\begin{center}
-\input{figures/linearly-separable-examples-with-margin}
-\end{center}
-\caption[]{The figure shows labeled examples in $\R^2$. The examples belong to
-$K=3$ classes colored white, gray and black respectively. Each class lies in a
-$120^\circ$ wedge. In other words, each class lies in an intersection of two
-halfspaces.
-
-While the examples are linearly separable with a positive margin $\gamma$, they
-are \emph{not} strongly linearly separable with any positive margin $\gamma$.
-}
-\label{figure:linearly-separable-examples-with-margin}
-\end{figure}
-
-\section{Algorithm for strongly linearly separable data}
-\label{section:algorithm-for-strongly-linearly-separable-data}
-
-In this section, we present an algorithm for \textsc{Online Multiclass
-Classification with Bandit Feedback} and prove an upper bound on the number of
-mistakes under the assumption that the examples are strongly linearly separable
-with a margin. The algorithm is stated as
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
-the mistake upper bound is stated as
-\autoref{theorem:strongly-separable-example-mistake-upper-bound}.
-
-The idea behind the algorithm is to use $K$ copies of the \textsc{Binary
-Perceptron} algorithm. Each copy corresponds to a class. In each round, each
-copy makes a binary decision whether the feature vector belongs its respective
-class or not. If at least one copy makes a positive prediction, the algorithm
-predicts accordingly. If multiple copies make positive predictions, the
-algorithm chooses one of them arbitrarily. If all copies make negative
-predictions, the algorithms makes a uniformly random guess.
-
-\begin{algorithm}[h]
-\caption{\textsc{Bandit Algorithm for Strongly Linearly Separable Examples}
-\label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
-\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t \in V$}
-\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$}
-\IF{$S_t = \emptyset$}
-\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
-\IF{$z_t = 1$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$}
-\ENDIF
-\ELSE
-\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
-\IF{$z_t = 1$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ENDIF
-\ENDIF
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{theorem}[Mistake upper bound]
-\label{theorem:strongly-separable-example-mistake-upper-bound}
-Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
-integer, let $\gamma$ a positive real number, let $R$ be a non-negative real number. If
-$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
-$V \times \{1,2,\dots,K\}$ such that the examples are strongly separable with
-margin $\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ then the
-expected number of mistakes
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-makes is at most $(K-1) \lfloor (R/\gamma)^2 \rfloor$.
-\end{theorem}
-
-\begin{proof}
-Let $M = \sum_{t=1}^T z_t$ be the number of mistakes the algorithm makes. Let $A
-= \sum_{t ~:~ S_t \neq \emptyset} z_t$ be the number of mistakes in the rounds
-when $S_t \neq \emptyset$ and let $B = \sum_{t ~:~ S_t = \emptyset} z_t$ be the
-number of mistakes in the rounds when $S_t = \emptyset$. Obviously, $M = A + B$.
-We upper bound $A$ and $B$ separately.
-
-Let $C$ be the number of times line 12 gets executed. Let $U$ be the number of
-times line 12 and line 19 get executed. In other words, $U$ is the number of
-times the $K$-tuple of vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets
-updated. Clearly, $U = A + C$.
-
-The key observation is that $\Exp[B] = (K-1) \Exp[C]$. The equality holds
-because if $S_t = \emptyset$, there is $1/K$ probability that the algorithm
-guesses the correct label and with probability $(K-1)/K$ algorithm's guess is
-incorrect. Putting all the information together, we get that
-\begin{align*}
-\Exp[M]
-& = \Exp[A] + \Exp[B] \\
-& = \Exp[A] + (K-1) \Exp[C]  \\
-& \le (K-1) \Exp[A + C] \\
-& = (K-1) \Exp[U]  \; .
-\end{align*}
-
-To finish the proof, we need to upper bound the number of updates, $U$. We claim
-that $U \le \lfloor (R/\gamma)^2 \rfloor$. The proof of this upper bound is
-similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
-algorithm. Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors that satisfy
-\eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2} and
-\eqref{equation:strong-linear-separability-3}.
-The $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$
-changes only if there is an update in round $t$.
-We investigate how $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ and
-$\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$ change. If there is an update in round $t$,
-we have
-\begingroup
-\allowdisplaybreaks
-\begin{align*}
-\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t+1)}}^2 \\
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t}^2 \\
-& = \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 + \underbrace{(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t}}_{\le 0} \\
-& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 \\
-& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + R^2 \; .
-\end{align*}
-\endgroup
-Therefore, after $U$ updates,
-$$
-\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
-$$
-Similarly, if there is an update in round $t$, we have
-\begin{align*}
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
-& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
-& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \gamma
-\end{align*}
-where the last inequality follows from \eqref{equation:strong-linear-separability-2}
-and \eqref{equation:strong-linear-separability-3} and analysis of the cases $z_t = 0$ and $z_t = 1$.
-Thus, after $U$ updates,
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma U \; .
-$$
-Applying Cauchy-Schwartz's inequality twice and assumption
-\eqref{equation:strong-linear-separability-1}, we get that
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
-\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
-$$
-Combining the upper and lower bounds on $\sum_{i=1}^K \norm{w_i^{(T+1)}}^2$ inequalities, we get
-$$
-(\gamma U)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
-$$
-We conclude that $U \le (R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor (R/\gamma)^2 \rfloor$.
-\end{proof}
-
-The upper bound $(K-1) \lfloor (R/\gamma)^2 \rfloor$ on the expected number of
-mistakes of
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
-optimal to within constant factor as long as the number of classes $K$ is
-at most $O((R/\gamma)^2)$. This is proved in
-\autoref{theorem:strongly-separable-example-mistake-lower-bound} below.
-
-Irrespective of any conditions on $K$, $R$, and $\gamma$, a trivial lower bound
-on the expected number of mistakes of any randomized algorithm is
-$\frac{K-1}{2}$. (Adversary chooses the same example over and over.) However, it
-is unclear if the trivial lower bound is the best possible if $K$ is large,
-i.e., $\omega((R/\gamma)^2)$. We leave this as an open problem.
-
-\begin{theorem}[Mistake lower bound]
-\label{theorem:strongly-separable-example-mistake-lower-bound}
-Let $\gamma$ be a positive real number and let $R$ be a non-negative real
-number. For any (possibly randomized) algorithm for the \textsc{Online
-Multiclass Classification with Bandit Feedback} with $K \le
-\frac{1}{4}(R/\gamma)^2$ classes there exists an inner product space $(V,
-\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ in $V \times
-\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
-norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
-number of mistakes the algorithm makes is at least $\frac{K-1}{2} \left\lfloor
-\frac{1}{16} (R/\gamma)^2 \right\rfloor$.
-\end{theorem}
-
-\begin{proof}
-We use probabilistic method. Let $M = \left\lfloor \frac{1}{16} (R/\gamma)^2 \right\rfloor$.
-Let $V = \R^{M+1}$ equipped with the standard inner product.  Let $e_1, e_2,
-\dots, e_{M+1}$ be the standard orthonormal basis of $V$. We define
-vectors $v_1, v_2, \dots, v_M \in V$ where $v_i = \frac{R}{\sqrt{2}}(e_i +
-e_{M+1})$ for $i=1,2,\dots,M$. Let $\ell_1, \ell_2, \dots, \ell_M$ be chosen
-i.i.d. uniformly at random from $\{1,2,\dots,K\}$ and independently of any
-randomness used the by the algorithm. Let $T = M K$. We define examples $(x_1,
-y_1), (x_2, y_2), \dots, (x_T, y_T)$ as follows:
-$$
-\begin{array}{lclclclcl}
-(x_1, y_1) & = & (x_2, y_2) & = & \cdots & = & (x_K, y_K) & = & (v_1, \ell_1) \; , \\
-(x_{K+1},y_{K+1}) & = & (x_{K+2}, y_{K+2}) & = & \cdots & = & (x_{2K}, y_{2K}) & = & (v_2, \ell_2) \; , \\
-& \vdots & \\
-(x_{(M-1)K+1}, y_{(M-1)K+1})  & = & (x_{(M-1)K+2}, y_{(M-1)K+2}) & = & \cdots & = & (x_{MK}, y_{MK}) & = & (v_M, \ell_M) \; .
-\end{array}
-$$
-
-With probability one, norm of each example is $R$. We show that with probability
-one, the examples are strongly separable with margin $\gamma$. In order to see
-that consider $w_1^*, w_2^*, \dots, w_K^* \in V$ defined by
-$$
-w_i^* = 2 \sqrt{2} \frac{\gamma}{R} \left( \sum_{j ~:~ \ell_j = i} e_j \right) - \sqrt{2} \frac{\gamma}{R} e_{M+1} \qquad \quad \text{for $i=1,2,\dots,K$.}
-$$
-Since for any $i \in \{1,2,\dots,K\}$ and any $j \in \{1,2,\dots,M\}$,
-$$
-\ip{w_i^*}{v_j} =
-\begin{cases}
-\gamma & \text{if $\ell_j = i$,} \\
-- \gamma & \text{if $\ell_j \neq i$,}
-\end{cases}
-$$
-it means that $w_1^*, w_2^*, \dots, w_K^*$ satisfy
-\eqref{equation:strong-linear-separability-2} and
-\eqref{equation:strong-linear-separability-3}. Condition \eqref{equation:strong-linear-separability-1}
-is satisfied since
-$$
-\sum_{i=1}^K \norm{w_i^*}^2
-= 8 \frac{\gamma^2}{R^2} \sum_{j=1}^M \norm{e_j}^2 + 2 \frac{\gamma^2}{R^2} K \norm{e_{M+1}}^2
-= 8 \frac{\gamma^2}{R^2} M + 2 \frac{\gamma^2}{R^2} K
-\le \frac{1}{2} + \frac{1}{2}
-= 1 \; .
-$$
-
-It remains to lower bound the expected number of mistakes of the algorithm. For
-any $j \in \{1,2,\dots,M\}$, consider the expected number of mistakes the
-algorithm makes in rounds $K(j-1) + 1, K(j-1) + 2, \dots, Kj$. In these rounds,
-the algorithm is guessing the label $\ell_j$. Since $\ell_j$ is chosen uniformly
-at random from the set $\{1,2,\dots,K\}$ and feedback is only binary, the
-expected number of mistakes the algorithm makes in these rounds is at least
-$\frac{K-1}{2}$. Altogether, the algorithm makes at least $\frac{K-1}{2} M$
-mistakes in expectation.
-
-Finally, since strong separability and norm condition hold with probability one,
-there exists a particular (i.e. deterministic) sequence of examples for which
-the algorithm makes at least $\frac{K-1}{2} M$ mistakes in expectation
-over its internal randomization.
-\end{proof}
-
-\section{From linear separability to strong linear separability}
-\label{section:from-linear-separability-to-strong-linear-separability}
-
-In this section, we show how to construct a mapping $\phi$ from the unit ball of
-$\R^d$ into a high dimensional inner product space that has the property that if
-a set of labeled examples in the unit ball is linearly separable with a margin
-$\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
-linearly separable with a margin $\gamma'$ and their norms are bounded by $R'$.
-The parameters $\gamma'$ and $R'$ are functions of the old margin $\gamma$ and
-the number of classes $K$, and the are specified in the theorems below.
-
-Equipped with the mapping $\phi$, we can utilize
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
-\autoref{theorem:strongly-separable-example-mistake-upper-bound} from the
-previous section and we obtain an algorithm for linearly separable examples and
-an upper bound on its number of mistakes. As a computational speed up, instead
-of working with the mapped examples $\phi(x_1), \phi(x_2), \dots$ explicitly, we
-can use the kernelized version of
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-that uses a kernel function $k(x,x') = \ip{\phi(x)}{\phi(x')}$.
-
-We construct several different mappings $\phi$. The mappings differ in the
-parameters $R'$, $\gamma'$, time complexity of evaluating $\phi(x)$, and time
-complexity of evaluating $k(x,x')$. Some of the mappings depend the original
-margin $\gamma$. In practice, the margin parameter $\gamma$ is not known, which
-makes these mappings impractical. However, one of the mappings we construct
-does \emph{not} depend on $\gamma$.
-
-The idea behind all the mappings is polynomial approximation. According to the
-well known Stone-Weierstrass theorem (see
-e.g.~\citep[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
-multivariate polynomials uniformly approximate any continuous function.
-Intuitively speaking, we use a multivariate polynomial to approximate, on the
-unit ball of $\R^d$, the indicator function corresponding to the intersection of
-$m=K-1$ halfspaces. Within margin $\gamma$ along the decision boundary, we allow
-the polynomial to attain arbitrary value. The polynomial separates examples in
-one class from examples in the other classes. To be able to quantify $R'$,
-$\gamma'$ and time complexities of evaluating $\phi(x)$ and $k(x,x')$, we need
-to quantify certain parameters of the approximating polynomial. We construct two
-different polynomials with different parameters. The parameters are quantified
-in
-Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
-stated below.
-
-Before we state the theorems, recall that a polynomial of $d$ variables is a
-function $p:\R^d \to \R$ of the form
-$$
-p(x) = p(x_1, x_2, \dots, x_d) = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-$$
-where the sum ranges over a finite set of $d$-tuples $(\alpha_1, \alpha_2,
-\dots, \alpha_d)$ of non-negative integers and $c_{\alpha_1, \alpha_2, \dots,
-\alpha_d}$ is a real coefficient. The \emph{degree} of a polynomial $p$, denoted
-by $\deg(p)$, is the largest value of $\alpha_1 + \alpha_2 + \dots + \alpha_d$
-for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is non-zero.
-The \emph{norm of a polynomial} $p$ is defined as
-$$
-\norm{p} = \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} \left(c_{\alpha_1, \alpha_2, \dots, \alpha_d} \right)^2 } \; .
-$$
-It is easy see that this is indeed a norm, since we can interpret it as a
-Euclidean norm of the vector of the coefficients of the polynomial.
-
-\begin{theorem}[Polynomial approximation of intersection of halfspaces I]
-\label{theorem:polynomial-approximation-1}
-Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
-\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$. There exists a
-multivariate polynomial $p:\R^d \to \R$ such that
-\begin{enumerate}
-\item $p(x) \ge 1/2$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-\item $p(x) \le -1/2$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-\item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$
-\item $\displaystyle \norm{p} \le \left( 188 \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil \right)^{\frac{1}{2} \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil}$
-\end{enumerate}
-\end{theorem}
-
-\begin{theorem}[Polynomial approximation of intersection of halfspaces II]
-\label{theorem:polynomial-approximation-2}
-Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
-\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$.
-Define
-$$
-r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1 \qquad \text{and} \qquad s = \left \lceil \log_2(1/\gamma) \right \rceil \; .
-$$
-Then, there exists a multivariate polynomial $p:\R^d \to \R$ such that
-\begin{enumerate}
-\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$
-for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-
-\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$
-for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-
-\item $\deg(p) \le (2s+1) rm$
-\item $\norm{p} \le (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm}$
-\end{enumerate}
-\end{theorem}
-
-The proofs of the theorems can be found in
-Section~\ref{section:proof-of-polynomial-approximation}. The geometric
-interpretation of the two regions described in parts 1 and 2 of the theorems is
-explained in Figure~\ref{figure:pizza-slice}. Similar but weaker results were
-proved by~\cite{Klivans-Servedio-2008}. In particular, the bounds in parts
-1, 2, 3, 4 of the theorems are independent of the dimension $d$.
-
-\begin{figure}
-\begin{center}
-\input{figures/pizza-slice}
-\end{center}
-\caption[]{The figure shows the two regions used in parts 1 and 2 of
-Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
-for the case $m=d=2$ and a particular choice of vectors $v_1, v_2$ and margin
-parameter $\gamma$. These regions are
-\begin{align*}
-R^+ & = \displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\} \; , \\
-R^- & = \displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\} \; .
-\end{align*}
-The separating hyperplanes $\ip{v_1}{x} = 0$ and $\ip{v_2}{x} = 0$ are shown as dashed lines.
-}
-\label{figure:pizza-slice}
-\end{figure}
-
-We construct the three different mappings $\phi_n, \psi_n, \rho$. The first two
-are parameterized by a non-negative integer $n$. The domain of $\phi_n$ and
-$\psi_n$ is $\R^d$. The domain of $\rho$ is the unit ball of $\R^d$. The
-co-domain for $\phi_n$ and $\psi_n$ is $\R^p$ where $p = \sum_{i=0}^n
-\binom{i+d-1}{d-1}$ equipped with the standard inner product $\ip{x}{x'} =
-\sum_{i=1}^p x_i x'_i$. The co-domain is the classical separable Hilbert space
-$\ell_2 = \{ x \in \R^\infty ~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped
-with the standard inner product $\ip{x}{x'} = \sum_{i=1}^\infty x_i x'_i$. We
-index the coordinates of the co-domain $\R^p$ by $d$-tuples $(\alpha_1,
-\alpha_2, \dots, \alpha_d)$ of non-negative integers such that $\alpha_1 +
-\alpha_2 + \dots + \alpha_d \le n$. Similarly, we index the coordinates of
-$\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
-integers. The mappings are defined by
-\begin{align*}
-\left(\phi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-\\
-\left(\psi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = \sqrt{\binom{n}{\alpha_1 + \alpha_2 + \dots + \alpha_d} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-\\
-\left(\rho(x)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-\end{align*}
-where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
-is the multinomial coefficient and $\binom{n}{k} = \frac{n!}{(n-k)!k!}$ is the binomial coefficient.
-
-Mappings $\psi_n$ and $\rho$ have simple-to-compute kernels
-\begin{align*}
-K_{\psi_n}(x,x') & = \ip{\psi_n(x)}{\psi_n(x')}_{\R^p} = \left( 1 + \ip{x}{x'} \right)^n \; , \\
-K_{\rho}(x,x') & = \ip{\rho(x)}{\rho(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}} \; .
-\end{align*}
-In passing we note that the formula for $K_\rho$ implies the mapping $\rho$ is
-well defined. Indeed, since $K_{\rho}(x,x) < +\infty$ for any $x$ in the unit
-ball of $\R^d$, it means that $\rho(x)$ indeed lies in $\ell_2$.
-
-TODO
-
-\section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
-\label{section:proof-of-polynomial-approximation}
-
-For the proofs of the theorems we need several auxiliary results.
-
-\begin{lemma}[Simple inequality]
-\label{lemma:simple-inequality}
-For any real numbers $b_1, b_2, \dots, b_n$,
-$$
-\left( \sum_{i=1}^n b_i \right)^2 \le n \sum_{i=1}^n b_i^2 \; .
-$$
-\end{lemma}
-
-\begin{proof}
-The lemma follows from Cauchy-Schwartz inequality applied to
-vectors $(b_1, b_2, \dots, b_n)$ and $(1,1,\dots,1)$.
-\end{proof}
-
-\begin{lemma}[Bound on binomial coefficients]
-\label{lemma:binomial-bound}
-For any integers $n,k$ such that $n \ge k \ge 0$,
-$$
-\binom{n}{k} \le (n - k + 1)^k \; .
-$$
-\end{lemma}
-
-\begin{proof}
-If $k = 0$, the inequality trivially holds. For the rest of the proof we can
-assume $k \ge 1$. We write the binomial coefficient as
-$$
-\binom{n}{k}
-= \frac{n(n-1)\cdots(n-k+1)}{k(k-1) \cdots 1}
-= \frac{n}{k} \cdot \frac{n-1}{k - 1} \cdots \frac{n-k+1}{1} \; .
-$$
-We claim that
-$$
-\frac{n}{k} \le \frac{n-1}{k - 1} \le \cdots \le \frac{n-k+1}{1}
-$$
-from which the lemma follows by upper bounding all the fractions by $n-k+1$.
-It remains to prove that for any $j=0,1,\dots,k-1$,
-$$
-\frac{n - j + 1}{k - j + 1} \le \frac{n - j}{k - j} \; .
-$$
-Multiplying by the (positive) denominators, we get an equivalent inequality
-$$
-(n - j + 1)(k - j) \le (n - j)(k - j + 1) \; .
-$$
-Cancelling common terms leads to an equivalent inequality
-$$
-k - j \le n - j \; ,
-$$
-which holds by the assumption on $n \ge k$.
-\end{proof}
-
-\begin{lemma}[Properties of the norm of polynomials]
-\label{lemma:properties-of-norm-of-polynomials}
-\hspace{1cm} % Dummy space
-\begin{enumerate}
-\item Let $p_1, p_2, \dots, p_n$ be multivariate polynomials and let $p(x) =
-\prod_{j=1}^n p_j(x)$ be their product.  Then, $\norm{p}^2 \le n^{\sum_{j=1}^n
-\deg(p_j)} \prod_{j=1}^n \norm{p_j}^2$.
-
-\item Let $q$ be a multivariate polynomial of degree at most $s$ and let $p(x) =
-(q(x))^n$. Then, $\norm{p}^2 \le n^{ns} \norm{q}^{2n}$.
-
-\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then,
-$\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-Using multi-index notation we can write any multivariate polynomial $p$ as
-$$
-p(x) = \sum_A c_A x^A
-$$
-where $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ is a multi-index (i.e. a $d$-tuple of
-non-negative integers), $x^A = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}$ is a
-monomial and $c_A = c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is the corresponding real
-coefficient. The sum is over a finite subset of $d$-tuples of non-negative
-integers. Using this notation, the norm of a polynomial $p$ can be written as
-$$
-\norm{p} = \sqrt{\sum_A (c_A)^2} \; .
-$$
-For a multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ we define its
-$1$-norm as $\norm{A}_1 = \alpha_1 + \alpha_2 + \dots + \alpha_d$.
-
-To prove the part 1, we express $p_j$ as
-$$
-p_j(x) = \sum_{A_j} c^{(j)}_{A_j} x^{A_j} \; .
-$$
-Since $p(x) = \prod_{i=1}^n p_j(x)$, the coefficients of its expansion $p(x) =
-\sum_A c_A x^A$ are
-$$
-c_A = \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \; .
-$$
-Therefore,
-\begin{multline*}
-\norm{p}^2
-= \sum_{A} (c_A)^2
-= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \right)^2
-= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\end{multline*}
-and
-\begin{multline*}
-\prod_{i=1}^n \norm{p_i}^2
-= \prod_{i=1}^n \left( \sum_{A_i} (c^{(i)}_{A_i})^2 \right)
-= \sum_{(A_1, A_2, \dots, A_n)} \prod_{j=1}^n (c^{(j)}_{A_j})^2
-= \sum_{(A_1, A_2, \dots, A_n)} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
-= \sum_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\end{multline*}
-where in both cases the outer sum is over multi-indices $A$ such that $\norm{A}_1 \le \deg(p)$.
-\autoref{lemma:simple-inequality} implies that for any multi-index $A$,
-$$
-\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\le M_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
-$$
-where $M_A$ is the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 +
-A_2 + \dots + A_n = A$.
-
-To finish the proof, it is sufficient to prove that $M_A \le n^{\deg(p)}$ for
-any $A$ such that $\norm{A}_1 \le \deg(p)$. To prove this inequality, consider a
-multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ and consider its $i$-th coordinate
-$\alpha_i$. In order for $A_1 + A_2 + \dots + A_n = A$ to hold, the $i$-th
-coordinates of $A_1, A_2, \dots, A_n$ need to sum to $\alpha_i$. There are exactly
-$\binom{\alpha_i + n - 1}{\alpha_i}$ possibilities for the choice of $i$-th
-coordinates of $A_1, A_2, \dots, A_n$. The total number of choices is thus
-$$
-M_A = \prod_{i=1}^d \binom{\alpha_i + n - 1}{\alpha_i} \; .
-$$
-Using \autoref{lemma:binomial-bound}, we upper bound it as
-$$
-M_A \le \prod_{i=1}^d n^{\alpha_i} = n^{\norm{A}_1} \le n^{\deg(p)} \; .
-$$
-
-Part 2 follows from the part 1 by setting $p_1 = p_2 = \dots p_n = q$.
-
-To prove the part 3, we use generalized triangle inequality and
-\autoref{lemma:simple-inequality}. We have
-\begin{align*}
-\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
-\end{align*}
-\end{proof}
-
-\subsection{Proof of \autoref{theorem:polynomial-approximation-1}}
-\label{section:proof-of-polynomial-approximation-1}
-
-To construct the polynomial $p$ we use Chebyshev polynomials of the first kind.
-Chebyshev polynomials of the fist kind form an infinite sequence of polynomials
-$T_0(z), T_1(z), T_2(z), \dots$ of single real variable $z$. They are defined
-by the recurrence
-\begin{align*}
-T_0(z) & = 1 \; , \\
-T_1(z) & = z \; , \\
-T_{n+1}(z) & = 2zT_n(z) - T_{n-1}(z) & \text{for $n \ge 1$.}
-\end{align*}
-Chebyshev polynomials have a lot of interesting properties.
-We will need properties listed in
-\autoref{proposition:properties-of-chebyshev-polynomials} below.
-Interested reader can learn more about Chebyshev polynomials
-from the book by \cite{Mason-Handscomb-2002}.
-
-\begin{proposition}[Properties of Chebyshev polynomials]
-\label{proposition:properties-of-chebyshev-polynomials}
-Chebyshev polynomials satisfy
-\begin{enumerate}
-\item $\deg(T_n) = n$ for all $n \ge 0$.
-\item If $n \ge 1$, the leading coefficient of $T_n(z)$ is $2^{n-1}$.
-\item $T_n(\cos(\theta)) = \cos(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
-\item $T_n(\cosh(\theta)) = \cosh(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
-\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$ and all $n \ge 0$.
-\item $T_n(z) \ge 1 + n^2(z - 1)$ for all $z \ge 1$ and all $n \ge 0$.
-\item $\norm{T_n} \le (1+\sqrt{2})^n$ for all $n \ge 0$
-\end{enumerate}
-\end{proposition}
-
-\begin{proof}[Proof of \autoref{proposition:properties-of-chebyshev-polynomials}]
-The first two properties can be easily proven by induction on $n$ using the recurrence.
-
-We prove third property by induction on $n$. Indeed, by definition
-$$
-T_0(\cos(\theta)) = 1 = \cos(0 \theta) \qquad \text{and} \qquad T_1(\cos(\theta)) = \cos(\theta) \; .
-$$
-For $n \ge 1$, we have
-\begin{align*}
-T_{n+1}(\cos(\theta))
-& = 2 \cos(\theta) T_n(\cos(\theta)) - T_{n-1}(\cos(\theta)) \\
-& = 2 \cos(\theta) \cos(n \theta) - \cos((n-1)\theta)) \; ,
-\end{align*}
-where the last step follow by induction hypothesis.
-It remains to show that the last expression equals $\cos((n+1)\theta)$.
-This can be derived from the trigonometric formula
-$$
-\cos(\alpha \pm \beta) = \cos(\alpha) \cos(\beta) \mp \sin(\alpha) \sin(\beta) \; .
-$$
-By substituting $\alpha = n \theta$ and $\beta = \theta$, we get two equations
-\begin{align*}
-\cos((n+1) \theta) & = \cos(n \theta) \cos(\theta) - \sin(n \theta) \sin(\theta) \; , \\
-\cos((n-1) \theta) & = \cos(n \theta) \cos(\theta) + \sin(n \theta) \sin(\theta) \; .
-\end{align*}
-Summing them yields
-$$
-\cos((n+1)\theta) + \cos((n-1) \theta) = 2 \cos(n \theta) \cos(\theta)
-$$
-which finishes the proof.
-
-Fourth property has the similar proof as third property. It suffices
-to replace $\cos$ and $\sin$ with $\cosh$ and $\sinh$ respectively.
-
-Fifth property follows from the third property. Indeed, for any $z \in [-1,1]$
-there exists $\theta \in \R$ such that $\cos \theta = z$. Thus, $|T_n(z)| =
-|T_n(\cos(\theta))| = |\cos(n\theta)| \le 1$.
-
-The sixth property is equivalent to
-$$
-T_n(\cosh(\theta)) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$,}
-$$
-since $\cosh(\theta) = \frac{e^{\theta} + e^{-\theta}}{2}$ is an even continuous
-function that maps $\R$ onto $[1,+\infty)$, is strictly decreasing on
-$(-\infty,0]$, and is strictly increasing on $[0,\infty)$. Using the fourth
-property the last inequality is equivalent to
-$$
-\cosh(n \theta) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$.}
-$$
-For $\theta = 0$, both sides are equal to $1$. Thus, it is sufficient to prove
-that the derivative of the left hand side is greater or equal to the derivative
-of the right hand side. Recalling that $[\cosh(\theta)]' = \sinh(\theta)$, this
-means that we need to show that
-$$
-\sinh(n \theta) \ge n \sinh(\theta) \qquad \text{for all $\theta \ge 0$.}
-$$
-Tho prove this inequality we use the summation formula
-$$
-\sinh(\alpha + \beta) = \sinh(\alpha) \cosh(\beta) + \sinh(\beta) \cosh(\beta) \; .
-$$
-If $\alpha, \beta$ are non-negative then $\sinh(\alpha), \sinh(\beta)$ are
-non-negative and $\cosh(\alpha), \cosh(\beta) \ge 1$. Hence,
-$$
-\sinh(\alpha + \beta) \ge \sinh(\alpha) + \sinh(\beta) \qquad \text{for any $\alpha, \beta \ge 0$.}
-$$
-This implies that (using induction on $n$) that $\sinh(n \theta) \ge n
-\sinh(\theta)$ for all $\theta \ge 0$.
-
-We verify the seventh property by induction on $n$.
-For $n=0$ and $n=1$ the inequality trivially holds, since $\norm{T_0} = \norm{T_1} = 1$.
-For $n \ge 1$, since $T_{n+1}(z) = 2zT_n(z) - T_{n-1}(z)$,
-\begin{align*}
-\norm{T_{n+1}}
-& \le 2 \norm{T_n} + \norm{T_{n-1}} \\
-& \le 2 (1 + \sqrt{2})^n + (1 + \sqrt{2})^{n-1} \\
-& = (1 + \sqrt{2})^{n-1} (2 (1 + \sqrt{2}) + 1) \\
-& = (1 + \sqrt{2})^{n-1} (3 + 2\sqrt{2}) \\
-& = (1 + \sqrt{2})^{n-1} (1 + \sqrt{2})^2 \\
-& = (1 + \sqrt{2})^{n+1} \; .
-\end{align*}
-
-\end{proof}
-
-Let $r = \left\lceil \log_2(2m) \right\rceil$ and $s = \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$.
-We define the polynomial $p:\R^d \to \R$ as
-$$
-p(x) = m + \frac{1}{2} - \sum_{i=1}^m \left( T_s(1 - \ip{v_i}{x}) \right)^r \; .
-$$
-It remains to show that $p$ has properties 1--5.
-
-To verify the first property notice that if $x \in \R^d$ satisfies $\norm{x} \le
-1$ and $\ip{v_i}{x} \ge \gamma$ then since $\norm{v_i} \le 1$ we have
-$\ip{v_i}{x} \in [0,1]$. Thus, $T_s(1 - \ip{v_i}{x})$ and $\left( T_s(1 -
-\ip{v_i}{x}) \right)^r$ lie in the interval $[-1,1]$. Therefore,
-$$
-p(x) \ge m + \frac{1}{2} - m \ge \frac{1}{2} \; .
-$$
-
-To verify the second property consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d
-~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Clearly, $\norm{x} \le 1$
-and there exists at least one $i \in \{1,2,\dots,m\}$ such that $\ip{v_i}{x} \le
-- \gamma$. Therefore, $1 - \ip{v_i}{x} \ge 1 + \gamma$ and~\autoref{proposition:properties-of-chebyshev-polynomials} (part 6)
-imply that
-$$
-T_s(1 - \ip{v_i}{x}) \ge 1 + s^2 \gamma \ge 2
-$$
-and thus
-$$
-\left( T_s(1 - \ip{v_i}{x}) \right)^r \ge 2^r \ge 2m \; .
-$$
-On the other hand for any $j \in \{1,2,\dots,m\}$, we have $\ip{v_j}{x} \in
-[-1,1]$ and thus $1 - \ip{v_j}{x}$ lies in the interval $[0,2]$. According to
-\autoref{proposition:properties-of-chebyshev-polynomials} (parts 5 and 6), $T_s(1 - \ip{v_j}{x})
-\ge -1$. Therefore,
-$$
-p(x) = m + \frac{1}{2} - \left( T_s(1 - \ip{v_i}{x}) \right)^r - \sum_{\substack{j ~:~  1 \le j \le m \\ j \neq i}} \le m + \frac{1}{2} - 2m + (m - 1) \le - \frac{1}{2} \; .
-$$
-
-The third property follows from observation that degree of $p$
-is the same as the degree of any one of the terms
-$\left( T_s(1 - \ip{v_i}{x}) \right)^r$ which is $r \cdot s$.
-
-To prove the fourth property, we need to upper bound the norm of $p$.
-Let $f_i(x) = 1 - \ip{v_i}{x}$, let $g_i(x) = T_s(1 - \ip{v_i}{x})$
-and let $h_i(x) = (T_s(1 - \ip{v_i}{x}))^r$. We have
-$$
-\norm{f_i}^2 = 1 + \norm{v_i}^2 \le 1 + 1 = 2 \; .
-$$
-Let $T_s(z) = \sum_{j=0}^s c_j z^j$ be the expansion of $s$-th Chebyshev polynomial.
-Then,
-\begingroup
-\allowdisplaybreaks
-\begin{align*}
-\norm{g_i}^2
-& = \norm{ \sum_{j=0}^s c_j (f_i)^j }^2 \\
-& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 & \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
-& = (s + 1) \sum_{j=0}^s (c_j)^2 \norm{(f_i)^j}^2 \\
-& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} & \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
-& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j 2^{2j} \\
-& \le (s + 1) s^s 2^{2s} \sum_{j=0}^s (c_j)^2 \\
-& = (s + 1) s^s 2^{2s} \norm{T_s}^2 \\
-& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} & \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
-& = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
-& \le \left(8(1+\sqrt{2})^2 s \right)^s & \text{(since $s+1 \le 2^s$ for any integer $s \ge 0$)} \\
-& \le \left(47 s \right)^s \; .
-\end{align*}
-\endgroup
-Finally,
-\begin{align*}
-\norm{p}
-& \le m + \frac{1}{2} + \sum_{i=1}^m \norm{(g_i)^r} \\
-& = m + \frac{1}{2} + \sum_{i=1}^m \sqrt{\norm{(g_i)^r}^2} \\
-& \le m + \frac{1}{2} + \sum_{i=1}^m \sqrt{r^{rs} \norm{g_i}^{2r}} \\
-& \le m + \frac{1}{2} + m r^{rs/2} \left(47 s \right)^{rs/2} \\
-& = m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \; .
-\end{align*}
-We can further upper bound the last expression by using that $m \le \frac{1}{2} 2^r$.
-Since $r,s \ge 1$,
-\begin{align*}
-\norm{p}
-& \le m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \\
-& \le \frac{1}{2} 2^r + \frac{1}{2} + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
-& \le 2^r + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
-& = 2^r \left(1 + \frac{1}{2} \left(47 rs \right)^{rs/2} \right) \\
-& = 2^r \left(47 rs \right)^{rs/2} \\
-& \le 4^{rs/2} \left(47 rs \right)^{rs/2} \\
-& \le \left(188 rs \right)^{rs/2} \; .
-\end{align*}
-Substituting for $r$ and $s$ finishes the proof.
-
-\subsection{Proof of \autoref{theorem:polynomial-approximation-2}}
-\label{section:proof-of-polynomial-approximation-2}
-
-We define several univariate polynomials
-\begin{align*}
-P_n(z) & = (z - 1) \prod_{i=1}^n (z - 2^i)^2 && \text{for $n \ge 0$,} \\
-A_{n,k}(z) & = (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$,} \\
-B_{n,k}(z) & = - (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$.}
-\end{align*}
-We define the polynomial $p:\R^d \to \R$ as
-$$
-p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
-- \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-$$
-
-For convenience we define univariate rational function
-\begin{align*}
-S_{n,k}(z) & = \frac{A_{n,k}(z)}{B_{n,k}(z)} && \text{for $n,k \ge 0$,}
-\end{align*}
-and a multivariate rational function
-$$
-Q(x) = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \; .
-$$
-It easy to verify that
-$$
-p(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-$$
-
-\begin{lemma}[Properties of $P_n$]
-\label{lemma:properties-of-p-n}
-\hspace{1cm} % Dummy space
-\begin{enumerate}
-\item If $z \in [0,1]$ then $P_n(-z) \le P_n(z) \le 0$.
-\item If $z \in [1,2^n]$ then $0 \le 4P_n(z) \le -P_n(-z)$.
-\item If $z \ge 0$ then $-P_n(-z) \ge 2^{n(n+1)}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-To prove the first part, note that $P_n(z)$ and $P_n(-z)$ are non-positive for
-$z \in [0,1]$. We can write $\frac{P_n(z)}{P_n(-z)}$ as a product of $n+1$
-non-negative fractions
-$$
-\frac{P_n(z)}{P_n(-z)} = \frac{1-z}{1+z} \prod_{i=1}^n \frac{(z+2^i)^2}{(z-2^i)^2} \; .
-$$
-The first part follows from the observation that each fraction is upper bounded
-by $1$.
-
-To prove the second part, notice that $P_n(z)$ is non-negative and $P_n(-z)$ is
-non-positive for any $z \in [1,2^n]$. Now, fix $z \in [1,2^n]$ and let $j \in
-\{1,2,\dots,n\}$ be such that $2^{j-1} \le z \le 2^j$. This implies that
-$(z+2^{j})^2 \ge 4 (z - 2^j)^2$. We can write $\frac{P_n(z)}{-P_n(-z)}$ as a
-product of $n+1$ non-negative fractions
-$$
-\frac{P_n(z)}{-P_n(-z)}
-= \frac{z-1}{z+1} \cdot \frac{(z-2^j)^2}{(z+2^j)^2} \prod_{\substack{i ~:~ 1 \le i \le n \\ i \neq j}} \frac{(z-2^i)^2}{(z+2^i)^2} \; .
-$$
-The second part follows from the observation that the second fraction is upper
-bounded by $1/4$ and all other fractions are upper bounded by $1$.
-
-The third part follows from
-$$
--P_n(-z) = (1+z) \prod_{i=1}^n (z+2^i)^2 \ge \prod_{i=1}^n 2^{2i} = 2^{n(n+1)} \; .
-$$
-\end{proof}
-
-\begin{lemma}[Properties of $S_{n,r}$ and $B_{n,r}$]
-\label{lemma:properties-of-s-n-r}
-Let $n,m$ be non-negative integers.
-Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$. Then,
-\begin{enumerate}
-\item If $z \in [1,2^n]$ then $S_{n,r}(z) \in [1,1+\frac{1}{2m}]$.
-\item If $z \in [-2^n, -1]$ then $S_{n,r} \in [-1-\frac{1}{2m}, -1]$.
-\item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
-\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-Note that $B_{n,r}(z)$ is an even function and $A_{n,r}(z)$ is an odd function.
-Therefore, $S_{n,r}(z)$ is odd. Also notice that $r$ is an odd integer.
-
-\begin{enumerate}
-\item Observe that $S_{n,r}(z)$ can be written as
-$$
-S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. Since
-$r \ge \frac{1}{2} \log_2(4m+1)$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
-$S_{n,r}(z) = \frac{1+c}{1-c} \in [1,1 + \frac{1}{2m}]$.
-
-\item Since $S_{n,r}(z)$ is odd, the statement follows from part 1.
-
-\item Observe that $S_{n,r}(z)$ can be written as
-$$
-S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. If $z \in [0,1]$, by part
-1 of~\autoref{lemma:properties-of-p-n} and the fact that $r$ is odd, $c
-\in [-1,0]$, and thus, $S_{n,r}(z) = \frac{1+c}{1-c} \in [0,1]$. Since
-$S_{n,r}(z)$ is odd, for $z \in [-1,0]$, $S_{n,r}(z) \in [-1,0]$.
-
-\item Since $B_{n,r}(z)$ is even, we can without loss generality assume that $z \ge
-0$. We consider two cases.
-
-Case $z \in [0,1]$. Since $r$ is odd and $P_n(z)$ is non-positive,
-$$
-B_{n,r}(z) = - (P_n(z))^r + \left(- P_{n}(-z)\right)^r \ge \left(- P_{n}(-z)\right)^r \ge 2^{n(n+1)r} \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
-where the second last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
-
-Case $z \in [1,2^n]$. Since $r$ is odd,
-$$
-B_{n,r}(z) = \left(- P_{n}(-z)\right)^r \left(1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r \right) = \left(- P_{n}(-z)\right)^r (1 - c)
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. By
-the definition of $r$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
-$$
-B_{n,r}(z) \ge \left(- P_{n}(-z)\right)^r \left( 1 - \frac{1}{4m+1} \right) \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
-where the last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
-\end{enumerate}
-\end{proof}
-
-\begin{lemma}[Properties of $Q(x)$]
-\label{lemma:properties-of-q}
-The rational function $Q(x)$ satisfies
-\begin{enumerate}
-\item $Q(x) \ge \frac{1}{2}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
-\item $Q(x) \le -\frac{1}{2}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-To prove part 1, consider any $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \
-\ip{v_i}{x} \ge \gamma \right\}$. Then, $\frac{\ip{v_i}{x}}{\gamma} \in [1,
-\frac{1}{\gamma}]$. By part 1 of \autoref{lemma:properties-of-s-n-r},
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \in [1, 1 + \frac{1}{2m}]$ and
-in particular $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \ge 1$. Thus,
-$$
-Q(x) = \left( \sum_{i=1}^m S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \right) - (m - 1/2) \ge m - (m - 1/2) = 1/2 \; .
-$$
-
-To prove part 2, consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~
-\norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Observe that
-$\frac{\ip{v_i}{x}}{\gamma} \in [-\frac{1}{\gamma}, \frac{1}{\gamma}]$. Consider
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right)$ for any $i \in
-\{1,2,\dots,m\}$. Parts 1,2, and 3 of \autoref{lemma:properties-of-s-n-r}
-and the fact $1/\gamma \le 2^s$ imply that
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \le 1 +
-\frac{1}{2m}$ for all $i \in \{1,2,\dots,m\}$. By the choice of $x$, there
-exists $j \in \{1,2,\dots,m\}$ such that $\ip{v_j}{x} \le - \gamma$. Part 2 of
-\autoref{lemma:properties-of-s-n-r} implies that
-$S_{s,r}\left(\frac{\ip{v_j}{x}}{\gamma}\right) \in [-1-\frac{1}{2m},-1]$. Thus,
-\begin{align*}
-Q(x)
-& = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& = S_{s,r}\left( \frac{\ip{v_j}{x}}{\gamma} \right) + \left( \sum_{\substack{i ~:~ 1 \le i \le m \\ i \neq j}} S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& \le -1 + (m-1) \left( 1 + \frac{1}{2m} \right) - \left(m - \frac{1}{2} \right) \\
-& \le 1/2 \; .
-\end{align*}
-\end{proof}
-
-To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-2} first
-note that part 4 of \autoref{lemma:properties-of-s-n-r} implies that for any $x$
-such that $\norm{x} \le 1$, $B_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right)$
-is positive. Thus $p(x)$ and $Q(x)$ have the same sign on the unit ball.
-Consider any $x$ in either
-$\displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-or in
-$\displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
-\autoref{lemma:properties-of-q} states that $|Q(x)| \ge 1/2$ and the sign
-depends on which of the two sets $x$ lies in. Since signs of $Q(x)$ and $p(x)$
-are the same, it remains to show that $|p(x)| \ge m^{s^2m/2}$. Indeed,
-\begin{align*}
-|p(x)|
-& = |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
-& \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
-& \ge \frac{1}{2} |Q(x)| \cdot 2^{s(s+1)rm} && \text{(since $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4} \ge 1/2$)} \\
-& \ge \frac{1}{4} \cdot 2^{s(s+1)rm} && \text{(\autoref{lemma:properties-of-q})} \; .
-\end{align*}
-
-To prove part 3 of \autoref{theorem:polynomial-approximation-2} note that
-$\deg(P_s) = 2s+1$. Thus, $\deg(A_{s,r})$ and $\deg(B_{s,r})$ are at most
-$(2s+1)r$. Therefore, $\deg(p) \le (2s+1) rm$.
-
-It remains to prove part 4 of \autoref{theorem:polynomial-approximation-2}.
-For any $i \in \{0,1,2,\dots,s\}$ and any $v \in \R^d$ such that $\norm{v} \le 1$
-define multivariate polynomials
-\begin{align*}
-f_{i,v}(x) & = \frac{\ip{v}{x}}{\gamma} - 2^i \; , \\
-q_v(x) & = P_s \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
-a_v(x) & = A_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
-b_v(x) & = B_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; .
-\end{align*}
-Note that
-$$
-p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
-$$
-We bound the norms of these polynomials. We have
-$$
-\norm{f_{i,v}}^2 = \norm{v}^2/\gamma^2 + 2^{2i} \le 2 \cdot 2^s \; .
-$$
-where we used that $1/\gamma \le 2^s$ and $\norm{v} \le 1$.
-Since $q_v(x) = f_{i,v}(\frac{\ip{v}{x}}{\gamma}) \prod_{i=1}^s \left(f_{i,v}(\frac{\ip{v}{x}})\right)^2$,
-using part 1 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $q_v$
-as
-$$
-\norm{q_v}^2 \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \le  (2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \; .
-$$
-Using parts 3 and 2 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $a_v$ as
-\begin{align*}
-\norm{a_v}^2
-& \le 2\norm{(q_v)^r}^2 + 2\norm{(q_{-v})^r}^2 \\
-& \le 2 r^{r(2s+1)} \norm{q_v}^{2r} + 2 r^{r(2s+1)} \norm{q_{-v}}^{2r} \\
-& \le 4 r^{r(2s+1)} \left((2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \right)^{2r} \\
-& = 4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \; .
-\end{align*}
-The same upper bound holds for $\norm{b_v}^2$. Finally,
-\begin{align*}
-\norm{p}
-& \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
-& \le \left[ \sum_{i=1}^m m^{(s+1/2)rm} \norm{a_{v_i}} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} \norm{b_{v_j}} \right] + \left(m - \frac{1}{2} \right) m^{(s+1/2)rm} \prod_{j=1}^m \norm{b_{v_j}} \\
-& \le (2m-1/2) m^{(s+1/2)rm} \left(4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \right)^{m/2} \\
-& = (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm} \; .
-\end{align*}
-
-\section{Nearest neighbor algorithm}
-
-TODO
-
-\section{NP-hardness of the weak labeling problem}
-
-Any algorithm for the bandit setting collects information in the form of so
-called \emph{strongly labeled} and \emph{weakly labeled} examples.
-Strongly-labeled examples are those for which we know the class label. Weakly
-labeled example is an example for which we know that class label can be anything
-except for a particular one class.
-
-A natural strategy for each round is to find vectors $w_1, w_2, \dots, w_K$ that
-linearly separate the examples seen in the previous rounds and use the vectors
-to predict the label in the next round. More precisely, we want to find both the
-vectors $w_1, w_2, \dots, w_K$ and label for each example consistent with its
-weak and/or strong labels such that $w_1, w_2, \dots, w_K$ linearly separate the
-labeled examples. We show this problem is NP-hard even for $K=3$.
-
-Clearly, the problem is at least as hard as the decision version of the problem
-where the goal is to determine if such vectors and labeling exist. We show that
-this problem is NP-complete.
-
-Formally, the input to the decision problem are positive integers $d, T, K$ and
-a sequence $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \{0,1\}^d \times
-\{1,2,\dots,K, \overline{1}, \overline{2}, \dots, \overline{K}\}$ of strongly
-and weakly labeled examples. The numbers $1,2,\dots,K$ correspond to strong
-labels and the symbols $\overline{1}, \overline{2}, \dots, \overline{K}$
-correspond to weak labels. We adopt the convention that $\overline{\overline{i}}
-= i$ for any positive integer $i$. The goal is to determine whether or not there
-exist vectors $w_1, w_2, \dots, w_K \in \R^d$ that satisfy the following
-conditions for all $t=1,2,\dots,T$,
-\begin{align*}
-y_t \in \{1,2,\dots,K\} \qquad & \Longrightarrow \qquad & \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \qquad \ip{w_{y_t}}{x_t} & > \ip{w_i}{x_t} \; , \\
-y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \qquad & \Longrightarrow & \qquad \exists i \in \{1,2,\dots,K\} \qquad \ip{w_i}{x_t} & > \ip{w_{\overline{y_t}}}{x_t} \; .
-\end{align*}
-
-TODO
-
-\section{Mistake lower bound for ignorant algorithms}
-
-TODO
-
-\bibliographystyle{plainnat}
-\bibliography{biblio}
-
-\appendix
-
 \section{Multiclass Perceptron}
@@
 \end{proof}
-
-\end{document}

### 2019-01-07 arxiv-version/from-linear-separability-to-strong-linear-separability.tex
Split sections in separate files

--- 2018-12-27 arxiv-version/main.tex
@@
-\documentclass[12pt]{article}
-
-% LaTeX packages
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage[singlelinecheck=false]{caption}
-\usepackage{fullpage}
-\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
-\usepackage{natbib}
-\usepackage{thmtools}
-\usepackage{tikz}
-\usepackage{color}
-\usepackage{comment}
-
-% TikZ packages
-\usetikzlibrary{arrows}
-\usetikzlibrary{angles}
-\usetikzlibrary{backgrounds}
-\usetikzlibrary{calc}
-\usetikzlibrary{cd}  % commutative diagrams
-\usetikzlibrary{intersections}
-\usetikzlibrary{patterns}
-\usetikzlibrary{shapes}
-\usetikzlibrary{through}
-
-% Math environments
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}[definition]{Proposition}
-\newtheorem{lemma}[definition]{Lemma}
-\newtheorem{theorem}[definition]{Theorem}
-\newtheorem{corollary}[definition]{Corollary}
-
-% Math symbols and commands
-\newcommand{\R}{\mathbb{R}}  % set of real numbers
-\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]} % indicator
-\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
-\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
-%\DeclareMathOperator*{\deg}{deg}
-\DeclareMathOperator*{\argmax}{argmax}
-\DeclareMathOperator*{\argmin}{argmin}
-\DeclareMathOperator*{\Exp}{\mathbf{E}}  % expected value
-\DeclareMathOperator{\diff}{d \!} % differential
-\DeclareMathOperator*{\polylog}{polylog}
-
-\definecolor{darkgreen}{rgb}{0,0.5,0}
-\definecolor{darkred}{rgb}{0.7,0,0}
-\definecolor{teal}{rgb}{0.3,0.8,0.8}
-\definecolor{orange}{rgb}{1.0,0.5,0.0}
-\definecolor{purple}{rgb}{0.8,0.0,0.8}
-\definecolor{blue}{rgb}{0.0,0.0,1.0}
-\newcommand{\kibitz}[2]{{\textcolor{#1}{\textsf{\footnotesize #2}}}}
-\newcommand{\alina}[1]{\kibitz{darkred}{[AB: #1]}}
-\newcommand{\david}[1]{\kibitz{darkgreen}{[DP: #1]}}
-\newcommand{\balazs}[1]{\kibitz{purple}{[BS: #1]}}
-\newcommand{\deva}[1]{\kibitz{teal}{[DT: #1]}}
-\newcommand{\chenyu}[1]{\kibitz{orange}{[CW: #1]}}
-\newcommand{\chicheng}[1]{\kibitz{blue}{[CZ: #1]}}
-
-\title{Online Multiclass Linear Classification with Bandit Feedback}
-
-\author{
-Alina Beygelzimer \and
-D\'avid P\'al \and
-Bal\'azs Sz\"or\'enyi \and
-Devanathan Thiruvenkatachari \and
-Chen-Yu Wei \and
-Chicheng Zhang
-}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-We study the problem of efficient online multiclass linear classification with bandit feedback, where all examples belong to one of $K$ classes and lie in the $d$-dimensional Euclidean space.
-Previous works have left open the challenge of designing efficient algorithms with finite mistake bounds
-when the data is linearly separable by a margin $\gamma$.
-In this work, we take a first step towards this problem.
-We identify two notions of linear separability:
-one-versus-all (OvA) linear separability and weakly linear separability.
-\begin{enumerate}
-\item Under the OvA
-linear separability condition, we design an efficient algorithm that achieves a near-optimal mistake bound of $O(\frac{K}{\gamma^2})$.
-\item Under the more challenging weakly linear separability condition, we design an efficient algorithm with a mistake bound of $2^{\tilde{O}(\min(K \log^2 \frac 1 \gamma, \log K \sqrt{\frac 1 \gamma})) }$ \footnote{We use the notation $\tilde{O}(f(\cdot)) = O( f(\cdot) \polylog(f(\cdot)) )$.}.
-Our algorithm is based on a reduction from weakly linear separability to OvA linear separability via an infinite dimensional monomial feature map, which in turn is inspired by ~\cite{Klivans-Servedio-2008}'s work on learning intersection of halfspaces.
-\end{enumerate}
-
-%We focus on the setting where there are $K$ classes, and there is a $d$-dimensional multiclass linear classifier that separates all the examples shown with a positive margin $\gamma$.
-%$2^{O(\min(K \log^2 K \log^2 \frac 1 \gamma, \log K \log \log K \sqrt \frac 1 \gamma \log \frac 1\gamma))}$
-%$\min( (\log K \sqrt{\frac 1 \gamma})^{O(\log K \sqrt{\frac 1 \gamma})}, K^{O(K \log K \log^2 \frac1\gamma)} )$.
-
-\end{abstract}
-
-\section{Introduction}
-\label{section:introduction}
-
-We study the problem of \textsc{Online Multiclass Linear
-Classification with Bandit Feedback}~\cite{Kakade-Shalev-Shwartz-Tewari-2008}.
-The problem can be viewed as a game between the learner and the environment:
-at each timestep $t$, the environment chooses an example $(x_t, y_t)$, where its feature
-part $x_t \in \R^d$ is revealed to the learner.
-\footnote{All our results apply to also to a simpler model of
-the so called \emph{oblivious adversary} where the whole sequence of labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is chosen before the first
-round of the game.}
-Upon receiving this example, the
-learner is asked to make a prediction $\hat{y}_t$.
-the learner receives feedback immediately after making its prediction.
-In contrast with the standard full information setting (where the feedback given is the correct label $y_t$), the feedback given is only a binary indicator
-whether the prediction was correct or not. The protocol of the problem is formally stated below.
-
-%In this problem, in each round, the
-%learner receives a feature vector and is asked to predict one of $K$
-%possible classes. To allow
-%for meaningful use of randomization, we assume that the correct label in a
-%particular round is chosen prior to algorithm's prediction in that
-%round.
-%Immediately after the learner makes its prediction, it
-%receives feedback whether the prediction was correct or not. However, in
-%contrast with the standard, so called full information setting, the algorithm
-%does \emph{not} receive the correct label. The feedback is only binary.
-
-\begin{algorithm}[h]
-\caption{\textsc{Online Multiclass Classification with Bandit Feedback}
-\label{algorithm:game-protocol}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$}
-\STATE{Adversary \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
-\chicheng{Or we simply say: Adversary chooses example $(x_t, y_t)$, where $x_t$ is reveal to the learner.}
-\STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \begin{cases}
-0 & \text{if $\widehat y_t = y_t$,} \\
-1 & \text{if $\widehat y_t \neq y_t$.}
-\end{cases}$
-}
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-The performance is of the learner is measured by its cumulative number of mistakes
-$\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$. The bandit feedback
- is a natural feedback model motivated by applications including
-online advertising and online content optimization, where the learner only gets to
-see the loss of its action taken.
-%where the binary feedback corresponds to a click
-%The
-%corresponding problem with full information feedback is solved by the classical
-%\textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
-%\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}).
-
-In this paper, we focus on the special case when the examples lie in $\R^d$ and
-are \emph{linearly separable with a margin}.
-\chicheng{I wonder if we should introduce the two notions of linear separability here,
-because strong linear separability is also worth mentioning in the full-information setting.
-}
-
-In the full-information feedback
-setting, it is well known that if the examples have norm at most $R$ and are
-linearly separable with a margin $\gamma$ then the \textsc{Multiclass
-Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
-This result is very satisfying since the upper bound on the number of mistakes
-is information-theoretically optimal and at the same time the \textsc{Multiclass
-Perceptron} algorithm has low time and memory complexity.
-
-The bandit feedback setting, however, is much more challenging. To understand
-the differences, we dissect the notion of linear separability in the multiclass
-setting. Beside the standard notion of linear separability, we define also
-\emph{strong linear separability}. For binary classification, these two
-definitions are identical. However, they differ for multiclass classification.
-For multiclass classification with $K$ classes the standard notion of linear
-separability means that the examples from each class lie in an intersection of
-$K-1$ halfspaces and the examples outside of the class lie in the complement of
-the intersection of the halfspaces. Strong linear separability means that
-examples from each class are separated from the remaining examples by a
-\emph{single} hyperplane. We state the definitions precisely in
-Section~\ref{section:notions-of-linear-separability}.
-
-For the case when the examples are strongly linearly separable, we design a
-simple and efficient algorithm with expected number of mistakes at most $(K-1)
-\lfloor (R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies
-of the \textsc{Binary Perceptron} algorithm, one copy for each class.
-Intuitively speaking, the factor $K-1$ is the price we pay for the bandit
-feedback, or more precisely, the lack of full-information feedback. We also
-prove that any (possibly randomized) algorithm makes $\Omega(K (R/\gamma)^2))$
-mistakes in the worst case.
-
-For the standard notion of linear separability, we propose several algorithms
-with various time-complexity-versus-mistake-bound trade-offs. First class of
-algorithms map the examples into a high-dimensional inner product space. In this
-space the examples become \emph{strongly} linearly separable. This allows us to
-run the algorithm for the strongly linearly separable case. All of these
-algorithms can be kernelized. (Some of them have to be kernelized since the
-underlying inner product space is infinite dimensional.) Kernelization does not
-change the input-output behavior of the algorithm, it only affects its time
-and memory complexity.
-
-These algorithms differ by choice of the mapping or, equivalently, choice of the
-kernel. The crux of the problem is the analysis of the approximation properties
-of these mappings/kernels and the way margin in the original space $\R^d$ under
-standard linear separability notion gets transformed into a margin in the
-high-dimensional space under the strong separability notion. This problem is
-related to the problem of learning intersection of halfspaces and has been
-studied previously by \cite{Klivans-Servedio-2008}. As an important technical
-achievement, we improve on the results of \cite{Klivans-Servedio-2008} by
-removing completely the dependency on the original dimension $d$.
-
-Finally, we propose a very different algorithm that is based on the obvious idea
-that two points that are close enough must have the same label. Here, close
-enough means that they cannot be separated from each other by a linear separator
-with a margin.
-
-All the algorithms run in time that is polynomial in the dimension of the
-feature vectors, the number of classes and the number of rounds. At the same
-time, all the algorithms make number of mistakes that does \emph{not} depend
-on the number of rounds. Instead, their number of mistakes depends only on the
-margin, number of classes, dimension of the feature vectors, and the radius of
-the ball in which the data lie.
-
-Finally, we study two questions related to the computational and
-information-theoretic hardness of the problem. Any algorithm for the bandit
-setting collects information in the form of so called \emph{strongly labeled}
-and \emph{weakly labeled} examples. Strongly labeled examples are those for
-which we know the class label. Weakly labeled example is an example for which we
-know that class label can be anything except for a particular one class. First,
-we show the offline problem of finding a linear multiclass separator consistent
-with a set of strongly and weakly labeled examples is NP-hard. This result is a
-consequence of the fact that finding an intersection of two halfspaces
-consistent with a set of binary-labeled examples is
-NP-hard~\citep{Blum-Rivest-1993}. Second, we show that any algorithm that uses
-only strongly-labeled examples and ignores weakly labeled examples makes at
-least $\Omega(???)$ mistakes.
-
-\section{Related work}
-\label{section:related-work}
-
-\begin{itemize}
-\item \cite{Abernethy-Rakhlin-2009}
-
-\item \cite{Chen-Chen-Zhang-Chen-Zhang-2009}
-
-\item \cite{Hazan-Kale-2011}
-
-\item \cite{Beygelzimer-Orabona-Zhang-2017}
-
-\item \cite{Foster-Kale-Luo-Mohri-Sridharan-2018}
-
-\item \cite{Foster-Krishnamurthy-2018}
-\end{itemize}
-
-TODO
-
-\section{Notions of linear separability}
-\label{section:notions-of-linear-separability}
-
-We define two notions of linear separability for multiclass classification. The
-first notion is the standard notion of linear separability used in the proof of
-the mistake bound for the \textsc{Multiclass Perceptron} algorithm. The second
-notion is stronger, i.e. more restrictive. However, it is more suitable for the
-bandit setting, since it allows for a simple and efficient algorithm; see
-Section~\ref{section:algorithm-for-strongly-linearly-separable-data}.
-
-\begin{definition}[Linear separability]
-Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
-integer, and let $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
-y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.
-
-The examples are said to be \emph{linearly separable with a
-margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
-that
-\begin{align}
-\label{equation:linear-separability-1}
-\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
-\label{equation:linear-separability-2}
-\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} & \ge \ip{x_t}{w_i} + \gamma \; .
-\end{align}
-
-The examples are said to be \emph{strongly linearly separable with a
-margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
-that
-\begin{align}
-\label{equation:strong-linear-separability-1}
-\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
-\label{equation:strong-linear-separability-2}
-\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
-\label{equation:strong-linear-separability-3}
-\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
-\end{align}
-\end{definition}
-
-The notion of linear separability with a margin is standard. It used in the
-full-information setting to upper bound the number of mistakes of the
-\textsc{Multiclass Perceptron} algorithm. For completeness, we state the
-algorithm in Appendix~\ref{section:multiclass-perceptron-proofs}. It is a
-folklore result that if a set of labeled examples is separable with a margin
-$\gamma$ and the norm of the examples is bounded by $R$ then \textsc{Multiclass
-Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
-mistakes. Another folklore result is that \textsc{Multiclass Perceptron} is
-essentially optimal in the sense that any deterministic algorithm must make
-$\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
-completeness, we give proofs of both of these results in
-Appendix~\ref{section:multiclass-perceptron-proofs}.
-
-The notion of strong linear separability is new.
-
-It is easy to see that if labeled examples are strongly linearly
-separable with margin $\gamma$ then they are linearly separable with margin
-$2\gamma$. Indeed, if $w_1, w_2, \dots, w_K \in V$
-satisfy \eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3} then they satisfy
-\eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} with margin $\gamma' = 2\gamma$.
-
-Similarly, if $K=2$ and labeled examples are linearly separable with a margin
-$\gamma$ then they are strongly linearly separable with margin $\gamma/2$.
-Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$, $w_2' =
-\frac{w_2 - w_1}{2}$ and $\gamma'=\gamma/2$ satisfy
-\eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3}. The last two conditions are easy
-to see. The first condition follows from $\norm{w_i'}^2 \le (\frac{1}{2}
-\norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le \frac{1}{2}\norm{w_1}^2 +
-\frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
-
-However, for any $K \ge 3$ and any inner product space of dimension at least
-$2$, there exists a set of labeled examples that is linearly separable with a
-positive margin $\gamma$ but it is not strongly linearly separable with any
-positive margin $\gamma$. An example of such set of labeled examples is shown in
-Figure~\ref{figure:linearly-separable-examples-with-margin}.
-
-\begin{figure}
-\begin{center}
-\input{figures/linearly-separable-examples-with-margin}
-\end{center}
-\caption[]{The figure shows labeled examples in $\R^2$. The examples belong to
-$K=3$ classes colored white, gray and black respectively. Each class lies in a
-$120^\circ$ wedge. In other words, each class lies in an intersection of two
-halfspaces.
-
-While the examples are linearly separable with a positive margin $\gamma$, they
-are \emph{not} strongly linearly separable with any positive margin $\gamma$.
-}
-\label{figure:linearly-separable-examples-with-margin}
-\end{figure}
-
-\section{Algorithm for strongly linearly separable data}
-\label{section:algorithm-for-strongly-linearly-separable-data}
-
-In this section, we present an algorithm for \textsc{Online Multiclass
-Classification with Bandit Feedback} and prove an upper bound on the number of
-mistakes under the assumption that the examples are strongly linearly separable
-with a margin. The algorithm is stated as
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
-the mistake upper bound is stated as
-\autoref{theorem:strongly-separable-example-mistake-upper-bound}.
-
-The idea behind the algorithm is to use $K$ copies of the \textsc{Binary
-Perceptron} algorithm. Each copy corresponds to a class. In each round, each
-copy makes a binary decision whether the feature vector belongs its respective
-class or not. If at least one copy makes a positive prediction, the algorithm
-predicts accordingly. If multiple copies make positive predictions, the
-algorithm chooses one of them arbitrarily. If all copies make negative
-predictions, the algorithms makes a uniformly random guess.
-
-\begin{algorithm}[h]
-\caption{\textsc{Bandit Algorithm for Strongly Linearly Separable Examples}
-\label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
-\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t \in V$}
-\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$}
-\IF{$S_t = \emptyset$}
-\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
-\IF{$z_t = 1$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$}
-\ENDIF
-\ELSE
-\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
-\IF{$z_t = 1$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ENDIF
-\ENDIF
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{theorem}[Mistake upper bound]
-\label{theorem:strongly-separable-example-mistake-upper-bound}
-Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
-integer, let $\gamma$ a positive real number, let $R$ be a non-negative real number. If
-$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
-$V \times \{1,2,\dots,K\}$ such that the examples are strongly separable with
-margin $\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ then the
-expected number of mistakes
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-makes is at most $(K-1) \lfloor (R/\gamma)^2 \rfloor$.
-\end{theorem}
-
-\begin{proof}
-Let $M = \sum_{t=1}^T z_t$ be the number of mistakes the algorithm makes. Let $A
-= \sum_{t ~:~ S_t \neq \emptyset} z_t$ be the number of mistakes in the rounds
-when $S_t \neq \emptyset$ and let $B = \sum_{t ~:~ S_t = \emptyset} z_t$ be the
-number of mistakes in the rounds when $S_t = \emptyset$. Obviously, $M = A + B$.
-We upper bound $A$ and $B$ separately.
-
-Let $C$ be the number of times line 12 gets executed. Let $U$ be the number of
-times line 12 and line 19 get executed. In other words, $U$ is the number of
-times the $K$-tuple of vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets
-updated. Clearly, $U = A + C$.
-
-The key observation is that $\Exp[B] = (K-1) \Exp[C]$. The equality holds
-because if $S_t = \emptyset$, there is $1/K$ probability that the algorithm
-guesses the correct label and with probability $(K-1)/K$ algorithm's guess is
-incorrect. Putting all the information together, we get that
-\begin{align*}
-\Exp[M]
-& = \Exp[A] + \Exp[B] \\
-& = \Exp[A] + (K-1) \Exp[C]  \\
-& \le (K-1) \Exp[A + C] \\
-& = (K-1) \Exp[U]  \; .
-\end{align*}
-
-To finish the proof, we need to upper bound the number of updates, $U$. We claim
-that $U \le \lfloor (R/\gamma)^2 \rfloor$. The proof of this upper bound is
-similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
-algorithm. Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors that satisfy
-\eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2} and
-\eqref{equation:strong-linear-separability-3}.
-The $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$
-changes only if there is an update in round $t$.
-We investigate how $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ and
-$\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$ change. If there is an update in round $t$,
-we have
-\begingroup
-\allowdisplaybreaks
-\begin{align*}
-\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t+1)}}^2 \\
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t}^2 \\
-& = \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 + \underbrace{(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t}}_{\le 0} \\
-& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 \\
-& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + R^2 \; .
-\end{align*}
-\endgroup
-Therefore, after $U$ updates,
-$$
-\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
-$$
-Similarly, if there is an update in round $t$, we have
-\begin{align*}
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
-& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
-& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \gamma
-\end{align*}
-where the last inequality follows from \eqref{equation:strong-linear-separability-2}
-and \eqref{equation:strong-linear-separability-3} and analysis of the cases $z_t = 0$ and $z_t = 1$.
-Thus, after $U$ updates,
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma U \; .
-$$
-Applying Cauchy-Schwartz's inequality twice and assumption
-\eqref{equation:strong-linear-separability-1}, we get that
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
-\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
-$$
-Combining the upper and lower bounds on $\sum_{i=1}^K \norm{w_i^{(T+1)}}^2$ inequalities, we get
-$$
-(\gamma U)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
-$$
-We conclude that $U \le (R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor (R/\gamma)^2 \rfloor$.
-\end{proof}
-
-The upper bound $(K-1) \lfloor (R/\gamma)^2 \rfloor$ on the expected number of
-mistakes of
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
-optimal to within constant factor as long as the number of classes $K$ is
-at most $O((R/\gamma)^2)$. This is proved in
-\autoref{theorem:strongly-separable-example-mistake-lower-bound} below.
-
-Irrespective of any conditions on $K$, $R$, and $\gamma$, a trivial lower bound
-on the expected number of mistakes of any randomized algorithm is
-$\frac{K-1}{2}$. (Adversary chooses the same example over and over.) However, it
-is unclear if the trivial lower bound is the best possible if $K$ is large,
-i.e., $\omega((R/\gamma)^2)$. We leave this as an open problem.
-
-\begin{theorem}[Mistake lower bound]
-\label{theorem:strongly-separable-example-mistake-lower-bound}
-Let $\gamma$ be a positive real number and let $R$ be a non-negative real
-number. For any (possibly randomized) algorithm for the \textsc{Online
-Multiclass Classification with Bandit Feedback} with $K \le
-\frac{1}{4}(R/\gamma)^2$ classes there exists an inner product space $(V,
-\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ in $V \times
-\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
-norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
-number of mistakes the algorithm makes is at least $\frac{K-1}{2} \left\lfloor
-\frac{1}{16} (R/\gamma)^2 \right\rfloor$.
-\end{theorem}
-
-\begin{proof}
-We use probabilistic method. Let $M = \left\lfloor \frac{1}{16} (R/\gamma)^2 \right\rfloor$.
-Let $V = \R^{M+1}$ equipped with the standard inner product.  Let $e_1, e_2,
-\dots, e_{M+1}$ be the standard orthonormal basis of $V$. We define
-vectors $v_1, v_2, \dots, v_M \in V$ where $v_i = \frac{R}{\sqrt{2}}(e_i +
-e_{M+1})$ for $i=1,2,\dots,M$. Let $\ell_1, \ell_2, \dots, \ell_M$ be chosen
-i.i.d. uniformly at random from $\{1,2,\dots,K\}$ and independently of any
-randomness used the by the algorithm. Let $T = M K$. We define examples $(x_1,
-y_1), (x_2, y_2), \dots, (x_T, y_T)$ as follows:
-$$
-\begin{array}{lclclclcl}
-(x_1, y_1) & = & (x_2, y_2) & = & \cdots & = & (x_K, y_K) & = & (v_1, \ell_1) \; , \\
-(x_{K+1},y_{K+1}) & = & (x_{K+2}, y_{K+2}) & = & \cdots & = & (x_{2K}, y_{2K}) & = & (v_2, \ell_2) \; , \\
-& \vdots & \\
-(x_{(M-1)K+1}, y_{(M-1)K+1})  & = & (x_{(M-1)K+2}, y_{(M-1)K+2}) & = & \cdots & = & (x_{MK}, y_{MK}) & = & (v_M, \ell_M) \; .
-\end{array}
-$$
-
-With probability one, norm of each example is $R$. We show that with probability
-one, the examples are strongly separable with margin $\gamma$. In order to see
-that consider $w_1^*, w_2^*, \dots, w_K^* \in V$ defined by
-$$
-w_i^* = 2 \sqrt{2} \frac{\gamma}{R} \left( \sum_{j ~:~ \ell_j = i} e_j \right) - \sqrt{2} \frac{\gamma}{R} e_{M+1} \qquad \quad \text{for $i=1,2,\dots,K$.}
-$$
-Since for any $i \in \{1,2,\dots,K\}$ and any $j \in \{1,2,\dots,M\}$,
-$$
-\ip{w_i^*}{v_j} =
-\begin{cases}
-\gamma & \text{if $\ell_j = i$,} \\
-- \gamma & \text{if $\ell_j \neq i$,}
-\end{cases}
-$$
-it means that $w_1^*, w_2^*, \dots, w_K^*$ satisfy
-\eqref{equation:strong-linear-separability-2} and
-\eqref{equation:strong-linear-separability-3}. Condition \eqref{equation:strong-linear-separability-1}
-is satisfied since
-$$
-\sum_{i=1}^K \norm{w_i^*}^2
-= 8 \frac{\gamma^2}{R^2} \sum_{j=1}^M \norm{e_j}^2 + 2 \frac{\gamma^2}{R^2} K \norm{e_{M+1}}^2
-= 8 \frac{\gamma^2}{R^2} M + 2 \frac{\gamma^2}{R^2} K
-\le \frac{1}{2} + \frac{1}{2}
-= 1 \; .
-$$
-
-It remains to lower bound the expected number of mistakes of the algorithm. For
-any $j \in \{1,2,\dots,M\}$, consider the expected number of mistakes the
-algorithm makes in rounds $K(j-1) + 1, K(j-1) + 2, \dots, Kj$. In these rounds,
-the algorithm is guessing the label $\ell_j$. Since $\ell_j$ is chosen uniformly
-at random from the set $\{1,2,\dots,K\}$ and feedback is only binary, the
-expected number of mistakes the algorithm makes in these rounds is at least
-$\frac{K-1}{2}$. Altogether, the algorithm makes at least $\frac{K-1}{2} M$
-mistakes in expectation.
-
-Finally, since strong separability and norm condition hold with probability one,
-there exists a particular (i.e. deterministic) sequence of examples for which
-the algorithm makes at least $\frac{K-1}{2} M$ mistakes in expectation
-over its internal randomization.
-\end{proof}
-
 \section{From linear separability to strong linear separability}
@@
 TODO
-
-\section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
-\label{section:proof-of-polynomial-approximation}
-
-For the proofs of the theorems we need several auxiliary results.
-
-\begin{lemma}[Simple inequality]
-\label{lemma:simple-inequality}
-For any real numbers $b_1, b_2, \dots, b_n$,
-$$
-\left( \sum_{i=1}^n b_i \right)^2 \le n \sum_{i=1}^n b_i^2 \; .
-$$
-\end{lemma}
-
-\begin{proof}
-The lemma follows from Cauchy-Schwartz inequality applied to
-vectors $(b_1, b_2, \dots, b_n)$ and $(1,1,\dots,1)$.
-\end{proof}
-
-\begin{lemma}[Bound on binomial coefficients]
-\label{lemma:binomial-bound}
-For any integers $n,k$ such that $n \ge k \ge 0$,
-$$
-\binom{n}{k} \le (n - k + 1)^k \; .
-$$
-\end{lemma}
-
-\begin{proof}
-If $k = 0$, the inequality trivially holds. For the rest of the proof we can
-assume $k \ge 1$. We write the binomial coefficient as
-$$
-\binom{n}{k}
-= \frac{n(n-1)\cdots(n-k+1)}{k(k-1) \cdots 1}
-= \frac{n}{k} \cdot \frac{n-1}{k - 1} \cdots \frac{n-k+1}{1} \; .
-$$
-We claim that
-$$
-\frac{n}{k} \le \frac{n-1}{k - 1} \le \cdots \le \frac{n-k+1}{1}
-$$
-from which the lemma follows by upper bounding all the fractions by $n-k+1$.
-It remains to prove that for any $j=0,1,\dots,k-1$,
-$$
-\frac{n - j + 1}{k - j + 1} \le \frac{n - j}{k - j} \; .
-$$
-Multiplying by the (positive) denominators, we get an equivalent inequality
-$$
-(n - j + 1)(k - j) \le (n - j)(k - j + 1) \; .
-$$
-Cancelling common terms leads to an equivalent inequality
-$$
-k - j \le n - j \; ,
-$$
-which holds by the assumption on $n \ge k$.
-\end{proof}
-
-\begin{lemma}[Properties of the norm of polynomials]
-\label{lemma:properties-of-norm-of-polynomials}
-\hspace{1cm} % Dummy space
-\begin{enumerate}
-\item Let $p_1, p_2, \dots, p_n$ be multivariate polynomials and let $p(x) =
-\prod_{j=1}^n p_j(x)$ be their product.  Then, $\norm{p}^2 \le n^{\sum_{j=1}^n
-\deg(p_j)} \prod_{j=1}^n \norm{p_j}^2$.
-
-\item Let $q$ be a multivariate polynomial of degree at most $s$ and let $p(x) =
-(q(x))^n$. Then, $\norm{p}^2 \le n^{ns} \norm{q}^{2n}$.
-
-\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then,
-$\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-Using multi-index notation we can write any multivariate polynomial $p$ as
-$$
-p(x) = \sum_A c_A x^A
-$$
-where $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ is a multi-index (i.e. a $d$-tuple of
-non-negative integers), $x^A = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}$ is a
-monomial and $c_A = c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is the corresponding real
-coefficient. The sum is over a finite subset of $d$-tuples of non-negative
-integers. Using this notation, the norm of a polynomial $p$ can be written as
-$$
-\norm{p} = \sqrt{\sum_A (c_A)^2} \; .
-$$
-For a multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ we define its
-$1$-norm as $\norm{A}_1 = \alpha_1 + \alpha_2 + \dots + \alpha_d$.
-
-To prove the part 1, we express $p_j$ as
-$$
-p_j(x) = \sum_{A_j} c^{(j)}_{A_j} x^{A_j} \; .
-$$
-Since $p(x) = \prod_{i=1}^n p_j(x)$, the coefficients of its expansion $p(x) =
-\sum_A c_A x^A$ are
-$$
-c_A = \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \; .
-$$
-Therefore,
-\begin{multline*}
-\norm{p}^2
-= \sum_{A} (c_A)^2
-= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \right)^2
-= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\end{multline*}
-and
-\begin{multline*}
-\prod_{i=1}^n \norm{p_i}^2
-= \prod_{i=1}^n \left( \sum_{A_i} (c^{(i)}_{A_i})^2 \right)
-= \sum_{(A_1, A_2, \dots, A_n)} \prod_{j=1}^n (c^{(j)}_{A_j})^2
-= \sum_{(A_1, A_2, \dots, A_n)} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
-= \sum_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\end{multline*}
-where in both cases the outer sum is over multi-indices $A$ such that $\norm{A}_1 \le \deg(p)$.
-\autoref{lemma:simple-inequality} implies that for any multi-index $A$,
-$$
-\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\le M_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
-$$
-where $M_A$ is the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 +
-A_2 + \dots + A_n = A$.
-
-To finish the proof, it is sufficient to prove that $M_A \le n^{\deg(p)}$ for
-any $A$ such that $\norm{A}_1 \le \deg(p)$. To prove this inequality, consider a
-multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ and consider its $i$-th coordinate
-$\alpha_i$. In order for $A_1 + A_2 + \dots + A_n = A$ to hold, the $i$-th
-coordinates of $A_1, A_2, \dots, A_n$ need to sum to $\alpha_i$. There are exactly
-$\binom{\alpha_i + n - 1}{\alpha_i}$ possibilities for the choice of $i$-th
-coordinates of $A_1, A_2, \dots, A_n$. The total number of choices is thus
-$$
-M_A = \prod_{i=1}^d \binom{\alpha_i + n - 1}{\alpha_i} \; .
-$$
-Using \autoref{lemma:binomial-bound}, we upper bound it as
-$$
-M_A \le \prod_{i=1}^d n^{\alpha_i} = n^{\norm{A}_1} \le n^{\deg(p)} \; .
-$$
-
-Part 2 follows from the part 1 by setting $p_1 = p_2 = \dots p_n = q$.
-
-To prove the part 3, we use generalized triangle inequality and
-\autoref{lemma:simple-inequality}. We have
-\begin{align*}
-\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
-\end{align*}
-\end{proof}
-
-\subsection{Proof of \autoref{theorem:polynomial-approximation-1}}
-\label{section:proof-of-polynomial-approximation-1}
-
-To construct the polynomial $p$ we use Chebyshev polynomials of the first kind.
-Chebyshev polynomials of the fist kind form an infinite sequence of polynomials
-$T_0(z), T_1(z), T_2(z), \dots$ of single real variable $z$. They are defined
-by the recurrence
-\begin{align*}
-T_0(z) & = 1 \; , \\
-T_1(z) & = z \; , \\
-T_{n+1}(z) & = 2zT_n(z) - T_{n-1}(z) & \text{for $n \ge 1$.}
-\end{align*}
-Chebyshev polynomials have a lot of interesting properties.
-We will need properties listed in
-\autoref{proposition:properties-of-chebyshev-polynomials} below.
-Interested reader can learn more about Chebyshev polynomials
-from the book by \cite{Mason-Handscomb-2002}.
-
-\begin{proposition}[Properties of Chebyshev polynomials]
-\label{proposition:properties-of-chebyshev-polynomials}
-Chebyshev polynomials satisfy
-\begin{enumerate}
-\item $\deg(T_n) = n$ for all $n \ge 0$.
-\item If $n \ge 1$, the leading coefficient of $T_n(z)$ is $2^{n-1}$.
-\item $T_n(\cos(\theta)) = \cos(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
-\item $T_n(\cosh(\theta)) = \cosh(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
-\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$ and all $n \ge 0$.
-\item $T_n(z) \ge 1 + n^2(z - 1)$ for all $z \ge 1$ and all $n \ge 0$.
-\item $\norm{T_n} \le (1+\sqrt{2})^n$ for all $n \ge 0$
-\end{enumerate}
-\end{proposition}
-
-\begin{proof}[Proof of \autoref{proposition:properties-of-chebyshev-polynomials}]
-The first two properties can be easily proven by induction on $n$ using the recurrence.
-
-We prove third property by induction on $n$. Indeed, by definition
-$$
-T_0(\cos(\theta)) = 1 = \cos(0 \theta) \qquad \text{and} \qquad T_1(\cos(\theta)) = \cos(\theta) \; .
-$$
-For $n \ge 1$, we have
-\begin{align*}
-T_{n+1}(\cos(\theta))
-& = 2 \cos(\theta) T_n(\cos(\theta)) - T_{n-1}(\cos(\theta)) \\
-& = 2 \cos(\theta) \cos(n \theta) - \cos((n-1)\theta)) \; ,
-\end{align*}
-where the last step follow by induction hypothesis.
-It remains to show that the last expression equals $\cos((n+1)\theta)$.
-This can be derived from the trigonometric formula
-$$
-\cos(\alpha \pm \beta) = \cos(\alpha) \cos(\beta) \mp \sin(\alpha) \sin(\beta) \; .
-$$
-By substituting $\alpha = n \theta$ and $\beta = \theta$, we get two equations
-\begin{align*}
-\cos((n+1) \theta) & = \cos(n \theta) \cos(\theta) - \sin(n \theta) \sin(\theta) \; , \\
-\cos((n-1) \theta) & = \cos(n \theta) \cos(\theta) + \sin(n \theta) \sin(\theta) \; .
-\end{align*}
-Summing them yields
-$$
-\cos((n+1)\theta) + \cos((n-1) \theta) = 2 \cos(n \theta) \cos(\theta)
-$$
-which finishes the proof.
-
-Fourth property has the similar proof as third property. It suffices
-to replace $\cos$ and $\sin$ with $\cosh$ and $\sinh$ respectively.
-
-Fifth property follows from the third property. Indeed, for any $z \in [-1,1]$
-there exists $\theta \in \R$ such that $\cos \theta = z$. Thus, $|T_n(z)| =
-|T_n(\cos(\theta))| = |\cos(n\theta)| \le 1$.
-
-The sixth property is equivalent to
-$$
-T_n(\cosh(\theta)) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$,}
-$$
-since $\cosh(\theta) = \frac{e^{\theta} + e^{-\theta}}{2}$ is an even continuous
-function that maps $\R$ onto $[1,+\infty)$, is strictly decreasing on
-$(-\infty,0]$, and is strictly increasing on $[0,\infty)$. Using the fourth
-property the last inequality is equivalent to
-$$
-\cosh(n \theta) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$.}
-$$
-For $\theta = 0$, both sides are equal to $1$. Thus, it is sufficient to prove
-that the derivative of the left hand side is greater or equal to the derivative
-of the right hand side. Recalling that $[\cosh(\theta)]' = \sinh(\theta)$, this
-means that we need to show that
-$$
-\sinh(n \theta) \ge n \sinh(\theta) \qquad \text{for all $\theta \ge 0$.}
-$$
-Tho prove this inequality we use the summation formula
-$$
-\sinh(\alpha + \beta) = \sinh(\alpha) \cosh(\beta) + \sinh(\beta) \cosh(\beta) \; .
-$$
-If $\alpha, \beta$ are non-negative then $\sinh(\alpha), \sinh(\beta)$ are
-non-negative and $\cosh(\alpha), \cosh(\beta) \ge 1$. Hence,
-$$
-\sinh(\alpha + \beta) \ge \sinh(\alpha) + \sinh(\beta) \qquad \text{for any $\alpha, \beta \ge 0$.}
-$$
-This implies that (using induction on $n$) that $\sinh(n \theta) \ge n
-\sinh(\theta)$ for all $\theta \ge 0$.
-
-We verify the seventh property by induction on $n$.
-For $n=0$ and $n=1$ the inequality trivially holds, since $\norm{T_0} = \norm{T_1} = 1$.
-For $n \ge 1$, since $T_{n+1}(z) = 2zT_n(z) - T_{n-1}(z)$,
-\begin{align*}
-\norm{T_{n+1}}
-& \le 2 \norm{T_n} + \norm{T_{n-1}} \\
-& \le 2 (1 + \sqrt{2})^n + (1 + \sqrt{2})^{n-1} \\
-& = (1 + \sqrt{2})^{n-1} (2 (1 + \sqrt{2}) + 1) \\
-& = (1 + \sqrt{2})^{n-1} (3 + 2\sqrt{2}) \\
-& = (1 + \sqrt{2})^{n-1} (1 + \sqrt{2})^2 \\
-& = (1 + \sqrt{2})^{n+1} \; .
-\end{align*}
-
-\end{proof}
-
-Let $r = \left\lceil \log_2(2m) \right\rceil$ and $s = \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$.
-We define the polynomial $p:\R^d \to \R$ as
-$$
-p(x) = m + \frac{1}{2} - \sum_{i=1}^m \left( T_s(1 - \ip{v_i}{x}) \right)^r \; .
-$$
-It remains to show that $p$ has properties 1--5.
-
-To verify the first property notice that if $x \in \R^d$ satisfies $\norm{x} \le
-1$ and $\ip{v_i}{x} \ge \gamma$ then since $\norm{v_i} \le 1$ we have
-$\ip{v_i}{x} \in [0,1]$. Thus, $T_s(1 - \ip{v_i}{x})$ and $\left( T_s(1 -
-\ip{v_i}{x}) \right)^r$ lie in the interval $[-1,1]$. Therefore,
-$$
-p(x) \ge m + \frac{1}{2} - m \ge \frac{1}{2} \; .
-$$
-
-To verify the second property consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d
-~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Clearly, $\norm{x} \le 1$
-and there exists at least one $i \in \{1,2,\dots,m\}$ such that $\ip{v_i}{x} \le
-- \gamma$. Therefore, $1 - \ip{v_i}{x} \ge 1 + \gamma$ and~\autoref{proposition:properties-of-chebyshev-polynomials} (part 6)
-imply that
-$$
-T_s(1 - \ip{v_i}{x}) \ge 1 + s^2 \gamma \ge 2
-$$
-and thus
-$$
-\left( T_s(1 - \ip{v_i}{x}) \right)^r \ge 2^r \ge 2m \; .
-$$
-On the other hand for any $j \in \{1,2,\dots,m\}$, we have $\ip{v_j}{x} \in
-[-1,1]$ and thus $1 - \ip{v_j}{x}$ lies in the interval $[0,2]$. According to
-\autoref{proposition:properties-of-chebyshev-polynomials} (parts 5 and 6), $T_s(1 - \ip{v_j}{x})
-\ge -1$. Therefore,
-$$
-p(x) = m + \frac{1}{2} - \left( T_s(1 - \ip{v_i}{x}) \right)^r - \sum_{\substack{j ~:~  1 \le j \le m \\ j \neq i}} \le m + \frac{1}{2} - 2m + (m - 1) \le - \frac{1}{2} \; .
-$$
-
-The third property follows from observation that degree of $p$
-is the same as the degree of any one of the terms
-$\left( T_s(1 - \ip{v_i}{x}) \right)^r$ which is $r \cdot s$.
-
-To prove the fourth property, we need to upper bound the norm of $p$.
-Let $f_i(x) = 1 - \ip{v_i}{x}$, let $g_i(x) = T_s(1 - \ip{v_i}{x})$
-and let $h_i(x) = (T_s(1 - \ip{v_i}{x}))^r$. We have
-$$
-\norm{f_i}^2 = 1 + \norm{v_i}^2 \le 1 + 1 = 2 \; .
-$$
-Let $T_s(z) = \sum_{j=0}^s c_j z^j$ be the expansion of $s$-th Chebyshev polynomial.
-Then,
-\begingroup
-\allowdisplaybreaks
-\begin{align*}
-\norm{g_i}^2
-& = \norm{ \sum_{j=0}^s c_j (f_i)^j }^2 \\
-& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 & \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
-& = (s + 1) \sum_{j=0}^s (c_j)^2 \norm{(f_i)^j}^2 \\
-& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} & \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
-& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j 2^{2j} \\
-& \le (s + 1) s^s 2^{2s} \sum_{j=0}^s (c_j)^2 \\
-& = (s + 1) s^s 2^{2s} \norm{T_s}^2 \\
-& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} & \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
-& = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
-& \le \left(8(1+\sqrt{2})^2 s \right)^s & \text{(since $s+1 \le 2^s$ for any integer $s \ge 0$)} \\
-& \le \left(47 s \right)^s \; .
-\end{align*}
-\endgroup
-Finally,
-\begin{align*}
-\norm{p}
-& \le m + \frac{1}{2} + \sum_{i=1}^m \norm{(g_i)^r} \\
-& = m + \frac{1}{2} + \sum_{i=1}^m \sqrt{\norm{(g_i)^r}^2} \\
-& \le m + \frac{1}{2} + \sum_{i=1}^m \sqrt{r^{rs} \norm{g_i}^{2r}} \\
-& \le m + \frac{1}{2} + m r^{rs/2} \left(47 s \right)^{rs/2} \\
-& = m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \; .
-\end{align*}
-We can further upper bound the last expression by using that $m \le \frac{1}{2} 2^r$.
-Since $r,s \ge 1$,
-\begin{align*}
-\norm{p}
-& \le m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \\
-& \le \frac{1}{2} 2^r + \frac{1}{2} + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
-& \le 2^r + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
-& = 2^r \left(1 + \frac{1}{2} \left(47 rs \right)^{rs/2} \right) \\
-& = 2^r \left(47 rs \right)^{rs/2} \\
-& \le 4^{rs/2} \left(47 rs \right)^{rs/2} \\
-& \le \left(188 rs \right)^{rs/2} \; .
-\end{align*}
-Substituting for $r$ and $s$ finishes the proof.
-
-\subsection{Proof of \autoref{theorem:polynomial-approximation-2}}
-\label{section:proof-of-polynomial-approximation-2}
-
-We define several univariate polynomials
-\begin{align*}
-P_n(z) & = (z - 1) \prod_{i=1}^n (z - 2^i)^2 && \text{for $n \ge 0$,} \\
-A_{n,k}(z) & = (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$,} \\
-B_{n,k}(z) & = - (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$.}
-\end{align*}
-We define the polynomial $p:\R^d \to \R$ as
-$$
-p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
-- \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-$$
-
-For convenience we define univariate rational function
-\begin{align*}
-S_{n,k}(z) & = \frac{A_{n,k}(z)}{B_{n,k}(z)} && \text{for $n,k \ge 0$,}
-\end{align*}
-and a multivariate rational function
-$$
-Q(x) = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \; .
-$$
-It easy to verify that
-$$
-p(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-$$
-
-\begin{lemma}[Properties of $P_n$]
-\label{lemma:properties-of-p-n}
-\hspace{1cm} % Dummy space
-\begin{enumerate}
-\item If $z \in [0,1]$ then $P_n(-z) \le P_n(z) \le 0$.
-\item If $z \in [1,2^n]$ then $0 \le 4P_n(z) \le -P_n(-z)$.
-\item If $z \ge 0$ then $-P_n(-z) \ge 2^{n(n+1)}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-To prove the first part, note that $P_n(z)$ and $P_n(-z)$ are non-positive for
-$z \in [0,1]$. We can write $\frac{P_n(z)}{P_n(-z)}$ as a product of $n+1$
-non-negative fractions
-$$
-\frac{P_n(z)}{P_n(-z)} = \frac{1-z}{1+z} \prod_{i=1}^n \frac{(z+2^i)^2}{(z-2^i)^2} \; .
-$$
-The first part follows from the observation that each fraction is upper bounded
-by $1$.
-
-To prove the second part, notice that $P_n(z)$ is non-negative and $P_n(-z)$ is
-non-positive for any $z \in [1,2^n]$. Now, fix $z \in [1,2^n]$ and let $j \in
-\{1,2,\dots,n\}$ be such that $2^{j-1} \le z \le 2^j$. This implies that
-$(z+2^{j})^2 \ge 4 (z - 2^j)^2$. We can write $\frac{P_n(z)}{-P_n(-z)}$ as a
-product of $n+1$ non-negative fractions
-$$
-\frac{P_n(z)}{-P_n(-z)}
-= \frac{z-1}{z+1} \cdot \frac{(z-2^j)^2}{(z+2^j)^2} \prod_{\substack{i ~:~ 1 \le i \le n \\ i \neq j}} \frac{(z-2^i)^2}{(z+2^i)^2} \; .
-$$
-The second part follows from the observation that the second fraction is upper
-bounded by $1/4$ and all other fractions are upper bounded by $1$.
-
-The third part follows from
-$$
--P_n(-z) = (1+z) \prod_{i=1}^n (z+2^i)^2 \ge \prod_{i=1}^n 2^{2i} = 2^{n(n+1)} \; .
-$$
-\end{proof}
-
-\begin{lemma}[Properties of $S_{n,r}$ and $B_{n,r}$]
-\label{lemma:properties-of-s-n-r}
-Let $n,m$ be non-negative integers.
-Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$. Then,
-\begin{enumerate}
-\item If $z \in [1,2^n]$ then $S_{n,r}(z) \in [1,1+\frac{1}{2m}]$.
-\item If $z \in [-2^n, -1]$ then $S_{n,r} \in [-1-\frac{1}{2m}, -1]$.
-\item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
-\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-Note that $B_{n,r}(z)$ is an even function and $A_{n,r}(z)$ is an odd function.
-Therefore, $S_{n,r}(z)$ is odd. Also notice that $r$ is an odd integer.
-
-\begin{enumerate}
-\item Observe that $S_{n,r}(z)$ can be written as
-$$
-S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. Since
-$r \ge \frac{1}{2} \log_2(4m+1)$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
-$S_{n,r}(z) = \frac{1+c}{1-c} \in [1,1 + \frac{1}{2m}]$.
-
-\item Since $S_{n,r}(z)$ is odd, the statement follows from part 1.
-
-\item Observe that $S_{n,r}(z)$ can be written as
-$$
-S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. If $z \in [0,1]$, by part
-1 of~\autoref{lemma:properties-of-p-n} and the fact that $r$ is odd, $c
-\in [-1,0]$, and thus, $S_{n,r}(z) = \frac{1+c}{1-c} \in [0,1]$. Since
-$S_{n,r}(z)$ is odd, for $z \in [-1,0]$, $S_{n,r}(z) \in [-1,0]$.
-
-\item Since $B_{n,r}(z)$ is even, we can without loss generality assume that $z \ge
-0$. We consider two cases.
-
-Case $z \in [0,1]$. Since $r$ is odd and $P_n(z)$ is non-positive,
-$$
-B_{n,r}(z) = - (P_n(z))^r + \left(- P_{n}(-z)\right)^r \ge \left(- P_{n}(-z)\right)^r \ge 2^{n(n+1)r} \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
-where the second last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
-
-Case $z \in [1,2^n]$. Since $r$ is odd,
-$$
-B_{n,r}(z) = \left(- P_{n}(-z)\right)^r \left(1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r \right) = \left(- P_{n}(-z)\right)^r (1 - c)
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. By
-the definition of $r$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
-$$
-B_{n,r}(z) \ge \left(- P_{n}(-z)\right)^r \left( 1 - \frac{1}{4m+1} \right) \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
-where the last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
-\end{enumerate}
-\end{proof}
-
-\begin{lemma}[Properties of $Q(x)$]
-\label{lemma:properties-of-q}
-The rational function $Q(x)$ satisfies
-\begin{enumerate}
-\item $Q(x) \ge \frac{1}{2}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
-\item $Q(x) \le -\frac{1}{2}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-To prove part 1, consider any $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \
-\ip{v_i}{x} \ge \gamma \right\}$. Then, $\frac{\ip{v_i}{x}}{\gamma} \in [1,
-\frac{1}{\gamma}]$. By part 1 of \autoref{lemma:properties-of-s-n-r},
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \in [1, 1 + \frac{1}{2m}]$ and
-in particular $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \ge 1$. Thus,
-$$
-Q(x) = \left( \sum_{i=1}^m S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \right) - (m - 1/2) \ge m - (m - 1/2) = 1/2 \; .
-$$
-
-To prove part 2, consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~
-\norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Observe that
-$\frac{\ip{v_i}{x}}{\gamma} \in [-\frac{1}{\gamma}, \frac{1}{\gamma}]$. Consider
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right)$ for any $i \in
-\{1,2,\dots,m\}$. Parts 1,2, and 3 of \autoref{lemma:properties-of-s-n-r}
-and the fact $1/\gamma \le 2^s$ imply that
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \le 1 +
-\frac{1}{2m}$ for all $i \in \{1,2,\dots,m\}$. By the choice of $x$, there
-exists $j \in \{1,2,\dots,m\}$ such that $\ip{v_j}{x} \le - \gamma$. Part 2 of
-\autoref{lemma:properties-of-s-n-r} implies that
-$S_{s,r}\left(\frac{\ip{v_j}{x}}{\gamma}\right) \in [-1-\frac{1}{2m},-1]$. Thus,
-\begin{align*}
-Q(x)
-& = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& = S_{s,r}\left( \frac{\ip{v_j}{x}}{\gamma} \right) + \left( \sum_{\substack{i ~:~ 1 \le i \le m \\ i \neq j}} S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& \le -1 + (m-1) \left( 1 + \frac{1}{2m} \right) - \left(m - \frac{1}{2} \right) \\
-& \le 1/2 \; .
-\end{align*}
-\end{proof}
-
-To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-2} first
-note that part 4 of \autoref{lemma:properties-of-s-n-r} implies that for any $x$
-such that $\norm{x} \le 1$, $B_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right)$
-is positive. Thus $p(x)$ and $Q(x)$ have the same sign on the unit ball.
-Consider any $x$ in either
-$\displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-or in
-$\displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
-\autoref{lemma:properties-of-q} states that $|Q(x)| \ge 1/2$ and the sign
-depends on which of the two sets $x$ lies in. Since signs of $Q(x)$ and $p(x)$
-are the same, it remains to show that $|p(x)| \ge m^{s^2m/2}$. Indeed,
-\begin{align*}
-|p(x)|
-& = |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
-& \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
-& \ge \frac{1}{2} |Q(x)| \cdot 2^{s(s+1)rm} && \text{(since $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4} \ge 1/2$)} \\
-& \ge \frac{1}{4} \cdot 2^{s(s+1)rm} && \text{(\autoref{lemma:properties-of-q})} \; .
-\end{align*}
-
-To prove part 3 of \autoref{theorem:polynomial-approximation-2} note that
-$\deg(P_s) = 2s+1$. Thus, $\deg(A_{s,r})$ and $\deg(B_{s,r})$ are at most
-$(2s+1)r$. Therefore, $\deg(p) \le (2s+1) rm$.
-
-It remains to prove part 4 of \autoref{theorem:polynomial-approximation-2}.
-For any $i \in \{0,1,2,\dots,s\}$ and any $v \in \R^d$ such that $\norm{v} \le 1$
-define multivariate polynomials
-\begin{align*}
-f_{i,v}(x) & = \frac{\ip{v}{x}}{\gamma} - 2^i \; , \\
-q_v(x) & = P_s \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
-a_v(x) & = A_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
-b_v(x) & = B_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; .
-\end{align*}
-Note that
-$$
-p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
-$$
-We bound the norms of these polynomials. We have
-$$
-\norm{f_{i,v}}^2 = \norm{v}^2/\gamma^2 + 2^{2i} \le 2 \cdot 2^s \; .
-$$
-where we used that $1/\gamma \le 2^s$ and $\norm{v} \le 1$.
-Since $q_v(x) = f_{i,v}(\frac{\ip{v}{x}}{\gamma}) \prod_{i=1}^s \left(f_{i,v}(\frac{\ip{v}{x}})\right)^2$,
-using part 1 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $q_v$
-as
-$$
-\norm{q_v}^2 \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \le  (2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \; .
-$$
-Using parts 3 and 2 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $a_v$ as
-\begin{align*}
-\norm{a_v}^2
-& \le 2\norm{(q_v)^r}^2 + 2\norm{(q_{-v})^r}^2 \\
-& \le 2 r^{r(2s+1)} \norm{q_v}^{2r} + 2 r^{r(2s+1)} \norm{q_{-v}}^{2r} \\
-& \le 4 r^{r(2s+1)} \left((2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \right)^{2r} \\
-& = 4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \; .
-\end{align*}
-The same upper bound holds for $\norm{b_v}^2$. Finally,
-\begin{align*}
-\norm{p}
-& \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
-& \le \left[ \sum_{i=1}^m m^{(s+1/2)rm} \norm{a_{v_i}} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} \norm{b_{v_j}} \right] + \left(m - \frac{1}{2} \right) m^{(s+1/2)rm} \prod_{j=1}^m \norm{b_{v_j}} \\
-& \le (2m-1/2) m^{(s+1/2)rm} \left(4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \right)^{m/2} \\
-& = (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm} \; .
-\end{align*}
-
-\section{Nearest neighbor algorithm}
-
-TODO
-
-\section{NP-hardness of the weak labeling problem}
-
-Any algorithm for the bandit setting collects information in the form of so
-called \emph{strongly labeled} and \emph{weakly labeled} examples.
-Strongly-labeled examples are those for which we know the class label. Weakly
-labeled example is an example for which we know that class label can be anything
-except for a particular one class.
-
-A natural strategy for each round is to find vectors $w_1, w_2, \dots, w_K$ that
-linearly separate the examples seen in the previous rounds and use the vectors
-to predict the label in the next round. More precisely, we want to find both the
-vectors $w_1, w_2, \dots, w_K$ and label for each example consistent with its
-weak and/or strong labels such that $w_1, w_2, \dots, w_K$ linearly separate the
-labeled examples. We show this problem is NP-hard even for $K=3$.
-
-Clearly, the problem is at least as hard as the decision version of the problem
-where the goal is to determine if such vectors and labeling exist. We show that
-this problem is NP-complete.
-
-Formally, the input to the decision problem are positive integers $d, T, K$ and
-a sequence $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \{0,1\}^d \times
-\{1,2,\dots,K, \overline{1}, \overline{2}, \dots, \overline{K}\}$ of strongly
-and weakly labeled examples. The numbers $1,2,\dots,K$ correspond to strong
-labels and the symbols $\overline{1}, \overline{2}, \dots, \overline{K}$
-correspond to weak labels. We adopt the convention that $\overline{\overline{i}}
-= i$ for any positive integer $i$. The goal is to determine whether or not there
-exist vectors $w_1, w_2, \dots, w_K \in \R^d$ that satisfy the following
-conditions for all $t=1,2,\dots,T$,
-\begin{align*}
-y_t \in \{1,2,\dots,K\} \qquad & \Longrightarrow \qquad & \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \qquad \ip{w_{y_t}}{x_t} & > \ip{w_i}{x_t} \; , \\
-y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \qquad & \Longrightarrow & \qquad \exists i \in \{1,2,\dots,K\} \qquad \ip{w_i}{x_t} & > \ip{w_{\overline{y_t}}}{x_t} \; .
-\end{align*}
-
-TODO
-
-\section{Mistake lower bound for ignorant algorithms}
-
-TODO
-
-\bibliographystyle{plainnat}
-\bibliography{biblio}
-
-\appendix
-
-\section{Multiclass Perceptron}
-\label{section:multiclass-perceptron-proofs}
-
-\textsc{Multiclass Perceptron} is an algorithm for \textsc{Online Multiclass
-Classification}. Both the protocol for the problem and the algorithm are stated
-below. The algorithm assumes that the feature vectors come from an inner product
-space $(V, \ip{\cdot}{\cdot})$.
-
-Two results are folklore. The first result is
-\autoref{theorem:mutliclass-perceptron-mistake-upper-bound} which states that if
-examples are linearly separable with margin $\gamma$ and examples have norm
-at most $R$ then the algorithm makes at most $\lfloor 2 (R/\gamma)^2 \rfloor$
-mistakes. The second result is
-\autoref{theorem:online-multiclass-classification-mistake-lower-bound} which
-states that under the same assumptions as in
-\autoref{theorem:online-multiclass-classification-mistake-lower-bound}
-\emph{any} deterministic algorithm for \textsc{Online Multiclass Classification}
-must make at least $\lfloor (R/\gamma)^2 \rfloor$ mistakes in the worst case.
-
-\begin{algorithm}[h]
-\caption{\textsc{Online Multiclass Classification}
-\label{algorithm:mutliclass-classification}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$}
-\STATE{Predict $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[h]
-\caption{\textsc{Multiclass Perceptron}
-\label{algorithm:mutliclass-perceptron}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
-\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t \in V$}
-\STATE{Predict $\widehat y_t = \argmax_{i \in \{1,2,\dots,K\}} \ip{w_t^{(i)}}{x_t}$}
-\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
-\IF{$\widehat y_t \neq y_t$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}$}
-\STATE{Update $w_{y_t}^{(t+1)} = w_{y_t}^{(t)} + x_t$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ENDIF
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{theorem}[Mistake upper bound]
-\label{theorem:mutliclass-perceptron-mistake-upper-bound}
-Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
-integer, let $\gamma$ be a positive real number and let $R$ be a non-negative real
-number. If $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled
-examples in $V \times \{1,2,\dots,K\}$ that are linearly separable with margin
-$\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
-then \textsc{Multiclass Perceptron} algorithm makes at most $\lfloor
-2(R/\gamma)^2 \rfloor$ mistakes.
-\end{theorem}
-
-\begin{proof}
-Let $M = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$ be the number of
-mistakes the algorithm makes. Since the $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots,
-w_K^{(t)})$ changes only if a mistake is made, we can upper bound $\sum_{i=1}^K
-\norm{w_i^{(t)}}^2$ in terms of number of mistakes.
-If a mistake happens in round $t$ then
-\begin{align*}
-\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
-& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) + \norm{w_{y_t}^{(t)} + x_t}^2 + \norm{w_{\widehat y_t}^{(t)} - x_t}^2 \\
-& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) + \norm{w_{y_t}^{(t)}}^2 + \norm{w_{\widehat y_t}^{(t)}}^2 + 2 \norm{x_t}^2 + 2 \ip{w_{y_t}^{(t)} - w_{\widehat y_t}^{(t)}}{x_t} \\
-& = \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 \norm{x_t}^2 + 2 \ip{w_{y_t}^{(t)} - w_{\widehat y_t}^{(t)}}{x_t} \\
-& \le \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 \norm{x_t}^2 \\
-& \le \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 R^2 \; .
-\end{align*}
-So each time a mistake happens, $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ increases by at most $2R^2$. Thus,
-$$
-\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le 2R^2 M \; .
-$$
-Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors satisfying the
-\eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2}. We lower bound $\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$. This quantity changes
-only when a mistakes happens. If mistake happens in round $t$, we have
-\begin{align*}
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(t+1)}}
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^*}{w_{y_t}^{(t)} + x_t} + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} - x_t} \\
-& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^* - w_{\widehat y_t}^*}{x_t} \\
-& \ge  \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \gamma \; .
-\end{align*}
-Thus, after $M$ mistakes,
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma M \; .
-$$
-We upper bound the left hand side by using Cauchy-Schwartz inequality twice and
-the condition \eqref{equation:linear-separability-1} on $w_1^*, w_2^*, \dots,
-w_K^*$. We have
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
-\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
-$$
-Combining all inequalities, we get
-$$
-(\gamma M)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le 2R^2 M \; .
-$$
-We conclude that $M \le 2(R/\gamma)^2$. Since $M$ is an integer, $M \le \lfloor 2(R/\gamma)^2 \rfloor$.
-\end{proof}
-
-\begin{theorem}[Mistake lower bound]
-\label{theorem:online-multiclass-classification-mistake-lower-bound}
-Let $K$ be a positive integer, let $\gamma$ be a positive real number and let
-$R$ be a non-negative real number. For any deterministic algorithm for the
-\textsc{Online Multiclass Classification} problem there exists an
-inner product space $(V, \ip{\cdot}{\cdot})$, a non-negative integer $T$ and a
-sequence of labeled examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$
-examples in $V \times \{1,2,\dots,K\}$ that are linearly separable with margin
-$\gamma$, the norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
-and the algorithm makes at least $\lfloor (R/\gamma)^2 \rfloor$ mistakes.
-\end{theorem}
-
-\begin{proof}
-Let $T = \lfloor (R/\gamma)^2 \rfloor$ and let $x_1, x_2, \dots, x_T$ be the
-orthogonal vectors such that $\norm{x_t} = R$ for all $t=1,2,\dots,T$. For
-example, we can take $V = \R^T$ and $x_t = R e_t$ where $e_t$ is $t$-th element
-of the standard orthonormal basis of $\R^T$.
-
-Since the algorithm is deterministic, we can construct the sequence of labels
-$y_1, y_2, \dots, y_T$ adaptively based on the predictions $\widehat y_1,
-\widehat y_2, \dots, \widehat y_T$ of the algorithm. We define $y_t$ to be any
-element of $\{1,2,\dots,K\}$ not equal to $\widehat y_t$. This way the algorithm
-makes a mistake in every round $t=1,2,\dots,T$.
-
-It remains to show that the examples we have constructed are linearly separable
-with margin $\gamma$. To prove that we demonstrate vectors $w_1, w_2, \dots, w_K$
-satisfying conditions \eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2}. We define
-$$
-w_i = \frac{1}{R\sqrt{T}} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} x_t \qquad \qquad \text{for $i=1,2,\dots,K$.}
-$$
-Let $a_i = |\{ t ~:~ 1 \le t \le T, \ y_t = i \}|$ be the number of occurrences of label $i$.
-It is easy to see that
-$$
-\norm{w_i}^2 = \frac{1}{R^2 T} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} \norm{x_t}^2 = \frac{a_i}{T} \qquad \qquad \text{for $i=1,2,\dots,K$.}
-$$
-Since $\sum_{i=1}^K a_i = T$, the condition
-\eqref{equation:linear-separability-1} holds. To verify condition
-\eqref{equation:linear-separability-2} consider any labeled example $(x_t,
-y_t)$. Then, by definition of $w_{y_t}$ we have
-$$
-\ip{w_{y_t}}{x_t}
-= \frac{1}{R\sqrt{T}} \sum_{\substack{s : 1 \le s \le T \\ y_s = y_t}} \ip{x_s}{x_t}
-= \frac{1}{R\sqrt{T}} \norm{x_t}^2
-= \frac{R}{\sqrt{T}}
-\ge \frac{R}{R/\gamma}
-= \gamma \; .
-$$
-and for any $i \in \{1,2,\dots,K\} \setminus \{y_t\}$ we have
-$\ip{w_i}{x_t} = 0$. Therefore, condition \eqref{equation:linear-separability-2} holds.
-\end{proof}
-
-\end{document}

### 2019-01-07 arxiv-version/introduction.tex
Split sections in separate files

--- 2018-12-27 arxiv-version/main.tex
@@
-\documentclass[12pt]{article}
-
-% LaTeX packages
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage[singlelinecheck=false]{caption}
-\usepackage{fullpage}
-\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
-\usepackage{natbib}
-\usepackage{thmtools}
-\usepackage{tikz}
-\usepackage{color}
-\usepackage{comment}
-
-% TikZ packages
-\usetikzlibrary{arrows}
-\usetikzlibrary{angles}
-\usetikzlibrary{backgrounds}
-\usetikzlibrary{calc}
-\usetikzlibrary{cd}  % commutative diagrams
-\usetikzlibrary{intersections}
-\usetikzlibrary{patterns}
-\usetikzlibrary{shapes}
-\usetikzlibrary{through}
-
-% Math environments
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}[definition]{Proposition}
-\newtheorem{lemma}[definition]{Lemma}
-\newtheorem{theorem}[definition]{Theorem}
-\newtheorem{corollary}[definition]{Corollary}
-
-% Math symbols and commands
-\newcommand{\R}{\mathbb{R}}  % set of real numbers
-\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]} % indicator
-\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
-\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
-%\DeclareMathOperator*{\deg}{deg}
-\DeclareMathOperator*{\argmax}{argmax}
-\DeclareMathOperator*{\argmin}{argmin}
-\DeclareMathOperator*{\Exp}{\mathbf{E}}  % expected value
-\DeclareMathOperator{\diff}{d \!} % differential
-\DeclareMathOperator*{\polylog}{polylog}
-
-\definecolor{darkgreen}{rgb}{0,0.5,0}
-\definecolor{darkred}{rgb}{0.7,0,0}
-\definecolor{teal}{rgb}{0.3,0.8,0.8}
-\definecolor{orange}{rgb}{1.0,0.5,0.0}
-\definecolor{purple}{rgb}{0.8,0.0,0.8}
-\definecolor{blue}{rgb}{0.0,0.0,1.0}
-\newcommand{\kibitz}[2]{{\textcolor{#1}{\textsf{\footnotesize #2}}}}
-\newcommand{\alina}[1]{\kibitz{darkred}{[AB: #1]}}
-\newcommand{\david}[1]{\kibitz{darkgreen}{[DP: #1]}}
-\newcommand{\balazs}[1]{\kibitz{purple}{[BS: #1]}}
-\newcommand{\deva}[1]{\kibitz{teal}{[DT: #1]}}
-\newcommand{\chenyu}[1]{\kibitz{orange}{[CW: #1]}}
-\newcommand{\chicheng}[1]{\kibitz{blue}{[CZ: #1]}}
-
-\title{Online Multiclass Linear Classification with Bandit Feedback}
-
-\author{
-Alina Beygelzimer \and
-D\'avid P\'al \and
-Bal\'azs Sz\"or\'enyi \and
-Devanathan Thiruvenkatachari \and
-Chen-Yu Wei \and
-Chicheng Zhang
-}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-We study the problem of efficient online multiclass linear classification with bandit feedback, where all examples belong to one of $K$ classes and lie in the $d$-dimensional Euclidean space.
-Previous works have left open the challenge of designing efficient algorithms with finite mistake bounds
-when the data is linearly separable by a margin $\gamma$.
-In this work, we take a first step towards this problem.
-We identify two notions of linear separability:
-one-versus-all (OvA) linear separability and weakly linear separability.
-\begin{enumerate}
-\item Under the OvA
-linear separability condition, we design an efficient algorithm that achieves a near-optimal mistake bound of $O(\frac{K}{\gamma^2})$.
-\item Under the more challenging weakly linear separability condition, we design an efficient algorithm with a mistake bound of $2^{\tilde{O}(\min(K \log^2 \frac 1 \gamma, \log K \sqrt{\frac 1 \gamma})) }$ \footnote{We use the notation $\tilde{O}(f(\cdot)) = O( f(\cdot) \polylog(f(\cdot)) )$.}.
-Our algorithm is based on a reduction from weakly linear separability to OvA linear separability via an infinite dimensional monomial feature map, which in turn is inspired by ~\cite{Klivans-Servedio-2008}'s work on learning intersection of halfspaces.
-\end{enumerate}
-
-%We focus on the setting where there are $K$ classes, and there is a $d$-dimensional multiclass linear classifier that separates all the examples shown with a positive margin $\gamma$.
-%$2^{O(\min(K \log^2 K \log^2 \frac 1 \gamma, \log K \log \log K \sqrt \frac 1 \gamma \log \frac 1\gamma))}$
-%$\min( (\log K \sqrt{\frac 1 \gamma})^{O(\log K \sqrt{\frac 1 \gamma})}, K^{O(K \log K \log^2 \frac1\gamma)} )$.
-
-\end{abstract}
-
 \section{Introduction}
@@
 least $\Omega(???)$ mistakes.
-
-\section{Related work}
-\label{section:related-work}
-
-\begin{itemize}
-\item \cite{Abernethy-Rakhlin-2009}
-
-\item \cite{Chen-Chen-Zhang-Chen-Zhang-2009}
-
-\item \cite{Hazan-Kale-2011}
-
-\item \cite{Beygelzimer-Orabona-Zhang-2017}
-
-\item \cite{Foster-Kale-Luo-Mohri-Sridharan-2018}
-
-\item \cite{Foster-Krishnamurthy-2018}
-\end{itemize}
-
-TODO
-
-\section{Notions of linear separability}
-\label{section:notions-of-linear-separability}
-
-We define two notions of linear separability for multiclass classification. The
-first notion is the standard notion of linear separability used in the proof of
-the mistake bound for the \textsc{Multiclass Perceptron} algorithm. The second
-notion is stronger, i.e. more restrictive. However, it is more suitable for the
-bandit setting, since it allows for a simple and efficient algorithm; see
-Section~\ref{section:algorithm-for-strongly-linearly-separable-data}.
-
-\begin{definition}[Linear separability]
-Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
-integer, and let $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
-y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.
-
-The examples are said to be \emph{linearly separable with a
-margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
-that
-\begin{align}
-\label{equation:linear-separability-1}
-\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
-\label{equation:linear-separability-2}
-\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} & \ge \ip{x_t}{w_i} + \gamma \; .
-\end{align}
-
-The examples are said to be \emph{strongly linearly separable with a
-margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
-that
-\begin{align}
-\label{equation:strong-linear-separability-1}
-\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
-\label{equation:strong-linear-separability-2}
-\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
-\label{equation:strong-linear-separability-3}
-\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
-\end{align}
-\end{definition}
-
-The notion of linear separability with a margin is standard. It used in the
-full-information setting to upper bound the number of mistakes of the
-\textsc{Multiclass Perceptron} algorithm. For completeness, we state the
-algorithm in Appendix~\ref{section:multiclass-perceptron-proofs}. It is a
-folklore result that if a set of labeled examples is separable with a margin
-$\gamma$ and the norm of the examples is bounded by $R$ then \textsc{Multiclass
-Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
-mistakes. Another folklore result is that \textsc{Multiclass Perceptron} is
-essentially optimal in the sense that any deterministic algorithm must make
-$\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
-completeness, we give proofs of both of these results in
-Appendix~\ref{section:multiclass-perceptron-proofs}.
-
-The notion of strong linear separability is new.
-
-It is easy to see that if labeled examples are strongly linearly
-separable with margin $\gamma$ then they are linearly separable with margin
-$2\gamma$. Indeed, if $w_1, w_2, \dots, w_K \in V$
-satisfy \eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3} then they satisfy
-\eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} with margin $\gamma' = 2\gamma$.
-
-Similarly, if $K=2$ and labeled examples are linearly separable with a margin
-$\gamma$ then they are strongly linearly separable with margin $\gamma/2$.
-Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$, $w_2' =
-\frac{w_2 - w_1}{2}$ and $\gamma'=\gamma/2$ satisfy
-\eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3}. The last two conditions are easy
-to see. The first condition follows from $\norm{w_i'}^2 \le (\frac{1}{2}
-\norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le \frac{1}{2}\norm{w_1}^2 +
-\frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
-
-However, for any $K \ge 3$ and any inner product space of dimension at least
-$2$, there exists a set of labeled examples that is linearly separable with a
-positive margin $\gamma$ but it is not strongly linearly separable with any
-positive margin $\gamma$. An example of such set of labeled examples is shown in
-Figure~\ref{figure:linearly-separable-examples-with-margin}.
-
-\begin{figure}
-\begin{center}
-\input{figures/linearly-separable-examples-with-margin}
-\end{center}
-\caption[]{The figure shows labeled examples in $\R^2$. The examples belong to
-$K=3$ classes colored white, gray and black respectively. Each class lies in a
-$120^\circ$ wedge. In other words, each class lies in an intersection of two
-halfspaces.
-
-While the examples are linearly separable with a positive margin $\gamma$, they
-are \emph{not} strongly linearly separable with any positive margin $\gamma$.
-}
-\label{figure:linearly-separable-examples-with-margin}
-\end{figure}
-
-\section{Algorithm for strongly linearly separable data}
-\label{section:algorithm-for-strongly-linearly-separable-data}
-
-In this section, we present an algorithm for \textsc{Online Multiclass
-Classification with Bandit Feedback} and prove an upper bound on the number of
-mistakes under the assumption that the examples are strongly linearly separable
-with a margin. The algorithm is stated as
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
-the mistake upper bound is stated as
-\autoref{theorem:strongly-separable-example-mistake-upper-bound}.
-
-The idea behind the algorithm is to use $K$ copies of the \textsc{Binary
-Perceptron} algorithm. Each copy corresponds to a class. In each round, each
-copy makes a binary decision whether the feature vector belongs its respective
-class or not. If at least one copy makes a positive prediction, the algorithm
-predicts accordingly. If multiple copies make positive predictions, the
-algorithm chooses one of them arbitrarily. If all copies make negative
-predictions, the algorithms makes a uniformly random guess.
-
-\begin{algorithm}[h]
-\caption{\textsc{Bandit Algorithm for Strongly Linearly Separable Examples}
-\label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
-\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t \in V$}
-\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$}
-\IF{$S_t = \emptyset$}
-\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
-\IF{$z_t = 1$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$}
-\ENDIF
-\ELSE
-\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
-\IF{$z_t = 1$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ENDIF
-\ENDIF
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{theorem}[Mistake upper bound]
-\label{theorem:strongly-separable-example-mistake-upper-bound}
-Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
-integer, let $\gamma$ a positive real number, let $R$ be a non-negative real number. If
-$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
-$V \times \{1,2,\dots,K\}$ such that the examples are strongly separable with
-margin $\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ then the
-expected number of mistakes
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-makes is at most $(K-1) \lfloor (R/\gamma)^2 \rfloor$.
-\end{theorem}
-
-\begin{proof}
-Let $M = \sum_{t=1}^T z_t$ be the number of mistakes the algorithm makes. Let $A
-= \sum_{t ~:~ S_t \neq \emptyset} z_t$ be the number of mistakes in the rounds
-when $S_t \neq \emptyset$ and let $B = \sum_{t ~:~ S_t = \emptyset} z_t$ be the
-number of mistakes in the rounds when $S_t = \emptyset$. Obviously, $M = A + B$.
-We upper bound $A$ and $B$ separately.
-
-Let $C$ be the number of times line 12 gets executed. Let $U$ be the number of
-times line 12 and line 19 get executed. In other words, $U$ is the number of
-times the $K$-tuple of vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets
-updated. Clearly, $U = A + C$.
-
-The key observation is that $\Exp[B] = (K-1) \Exp[C]$. The equality holds
-because if $S_t = \emptyset$, there is $1/K$ probability that the algorithm
-guesses the correct label and with probability $(K-1)/K$ algorithm's guess is
-incorrect. Putting all the information together, we get that
-\begin{align*}
-\Exp[M]
-& = \Exp[A] + \Exp[B] \\
-& = \Exp[A] + (K-1) \Exp[C]  \\
-& \le (K-1) \Exp[A + C] \\
-& = (K-1) \Exp[U]  \; .
-\end{align*}
-
-To finish the proof, we need to upper bound the number of updates, $U$. We claim
-that $U \le \lfloor (R/\gamma)^2 \rfloor$. The proof of this upper bound is
-similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
-algorithm. Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors that satisfy
-\eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2} and
-\eqref{equation:strong-linear-separability-3}.
-The $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$
-changes only if there is an update in round $t$.
-We investigate how $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ and
-$\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$ change. If there is an update in round $t$,
-we have
-\begingroup
-\allowdisplaybreaks
-\begin{align*}
-\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t+1)}}^2 \\
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t}^2 \\
-& = \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 + \underbrace{(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t}}_{\le 0} \\
-& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 \\
-& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + R^2 \; .
-\end{align*}
-\endgroup
-Therefore, after $U$ updates,
-$$
-\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
-$$
-Similarly, if there is an update in round $t$, we have
-\begin{align*}
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
-& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
-& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \gamma
-\end{align*}
-where the last inequality follows from \eqref{equation:strong-linear-separability-2}
-and \eqref{equation:strong-linear-separability-3} and analysis of the cases $z_t = 0$ and $z_t = 1$.
-Thus, after $U$ updates,
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma U \; .
-$$
-Applying Cauchy-Schwartz's inequality twice and assumption
-\eqref{equation:strong-linear-separability-1}, we get that
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
-\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
-$$
-Combining the upper and lower bounds on $\sum_{i=1}^K \norm{w_i^{(T+1)}}^2$ inequalities, we get
-$$
-(\gamma U)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
-$$
-We conclude that $U \le (R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor (R/\gamma)^2 \rfloor$.
-\end{proof}
-
-The upper bound $(K-1) \lfloor (R/\gamma)^2 \rfloor$ on the expected number of
-mistakes of
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
-optimal to within constant factor as long as the number of classes $K$ is
-at most $O((R/\gamma)^2)$. This is proved in
-\autoref{theorem:strongly-separable-example-mistake-lower-bound} below.
-
-Irrespective of any conditions on $K$, $R$, and $\gamma$, a trivial lower bound
-on the expected number of mistakes of any randomized algorithm is
-$\frac{K-1}{2}$. (Adversary chooses the same example over and over.) However, it
-is unclear if the trivial lower bound is the best possible if $K$ is large,
-i.e., $\omega((R/\gamma)^2)$. We leave this as an open problem.
-
-\begin{theorem}[Mistake lower bound]
-\label{theorem:strongly-separable-example-mistake-lower-bound}
-Let $\gamma$ be a positive real number and let $R$ be a non-negative real
-number. For any (possibly randomized) algorithm for the \textsc{Online
-Multiclass Classification with Bandit Feedback} with $K \le
-\frac{1}{4}(R/\gamma)^2$ classes there exists an inner product space $(V,
-\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ in $V \times
-\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
-norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
-number of mistakes the algorithm makes is at least $\frac{K-1}{2} \left\lfloor
-\frac{1}{16} (R/\gamma)^2 \right\rfloor$.
-\end{theorem}
-
-\begin{proof}
-We use probabilistic method. Let $M = \left\lfloor \frac{1}{16} (R/\gamma)^2 \right\rfloor$.
-Let $V = \R^{M+1}$ equipped with the standard inner product.  Let $e_1, e_2,
-\dots, e_{M+1}$ be the standard orthonormal basis of $V$. We define
-vectors $v_1, v_2, \dots, v_M \in V$ where $v_i = \frac{R}{\sqrt{2}}(e_i +
-e_{M+1})$ for $i=1,2,\dots,M$. Let $\ell_1, \ell_2, \dots, \ell_M$ be chosen
-i.i.d. uniformly at random from $\{1,2,\dots,K\}$ and independently of any
-randomness used the by the algorithm. Let $T = M K$. We define examples $(x_1,
-y_1), (x_2, y_2), \dots, (x_T, y_T)$ as follows:
-$$
-\begin{array}{lclclclcl}
-(x_1, y_1) & = & (x_2, y_2) & = & \cdots & = & (x_K, y_K) & = & (v_1, \ell_1) \; , \\
-(x_{K+1},y_{K+1}) & = & (x_{K+2}, y_{K+2}) & = & \cdots & = & (x_{2K}, y_{2K}) & = & (v_2, \ell_2) \; , \\
-& \vdots & \\
-(x_{(M-1)K+1}, y_{(M-1)K+1})  & = & (x_{(M-1)K+2}, y_{(M-1)K+2}) & = & \cdots & = & (x_{MK}, y_{MK}) & = & (v_M, \ell_M) \; .
-\end{array}
-$$
-
-With probability one, norm of each example is $R$. We show that with probability
-one, the examples are strongly separable with margin $\gamma$. In order to see
-that consider $w_1^*, w_2^*, \dots, w_K^* \in V$ defined by
-$$
-w_i^* = 2 \sqrt{2} \frac{\gamma}{R} \left( \sum_{j ~:~ \ell_j = i} e_j \right) - \sqrt{2} \frac{\gamma}{R} e_{M+1} \qquad \quad \text{for $i=1,2,\dots,K$.}
-$$
-Since for any $i \in \{1,2,\dots,K\}$ and any $j \in \{1,2,\dots,M\}$,
-$$
-\ip{w_i^*}{v_j} =
-\begin{cases}
-\gamma & \text{if $\ell_j = i$,} \\
-- \gamma & \text{if $\ell_j \neq i$,}
-\end{cases}
-$$
-it means that $w_1^*, w_2^*, \dots, w_K^*$ satisfy
-\eqref{equation:strong-linear-separability-2} and
-\eqref{equation:strong-linear-separability-3}. Condition \eqref{equation:strong-linear-separability-1}
-is satisfied since
-$$
-\sum_{i=1}^K \norm{w_i^*}^2
-= 8 \frac{\gamma^2}{R^2} \sum_{j=1}^M \norm{e_j}^2 + 2 \frac{\gamma^2}{R^2} K \norm{e_{M+1}}^2
-= 8 \frac{\gamma^2}{R^2} M + 2 \frac{\gamma^2}{R^2} K
-\le \frac{1}{2} + \frac{1}{2}
-= 1 \; .
-$$
-
-It remains to lower bound the expected number of mistakes of the algorithm. For
-any $j \in \{1,2,\dots,M\}$, consider the expected number of mistakes the
-algorithm makes in rounds $K(j-1) + 1, K(j-1) + 2, \dots, Kj$. In these rounds,
-the algorithm is guessing the label $\ell_j$. Since $\ell_j$ is chosen uniformly
-at random from the set $\{1,2,\dots,K\}$ and feedback is only binary, the
-expected number of mistakes the algorithm makes in these rounds is at least
-$\frac{K-1}{2}$. Altogether, the algorithm makes at least $\frac{K-1}{2} M$
-mistakes in expectation.
-
-Finally, since strong separability and norm condition hold with probability one,
-there exists a particular (i.e. deterministic) sequence of examples for which
-the algorithm makes at least $\frac{K-1}{2} M$ mistakes in expectation
-over its internal randomization.
-\end{proof}
-
-\section{From linear separability to strong linear separability}
-\label{section:from-linear-separability-to-strong-linear-separability}
-
-In this section, we show how to construct a mapping $\phi$ from the unit ball of
-$\R^d$ into a high dimensional inner product space that has the property that if
-a set of labeled examples in the unit ball is linearly separable with a margin
-$\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
-linearly separable with a margin $\gamma'$ and their norms are bounded by $R'$.
-The parameters $\gamma'$ and $R'$ are functions of the old margin $\gamma$ and
-the number of classes $K$, and the are specified in the theorems below.
-
-Equipped with the mapping $\phi$, we can utilize
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
-\autoref{theorem:strongly-separable-example-mistake-upper-bound} from the
-previous section and we obtain an algorithm for linearly separable examples and
-an upper bound on its number of mistakes. As a computational speed up, instead
-of working with the mapped examples $\phi(x_1), \phi(x_2), \dots$ explicitly, we
-can use the kernelized version of
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-that uses a kernel function $k(x,x') = \ip{\phi(x)}{\phi(x')}$.
-
-We construct several different mappings $\phi$. The mappings differ in the
-parameters $R'$, $\gamma'$, time complexity of evaluating $\phi(x)$, and time
-complexity of evaluating $k(x,x')$. Some of the mappings depend the original
-margin $\gamma$. In practice, the margin parameter $\gamma$ is not known, which
-makes these mappings impractical. However, one of the mappings we construct
-does \emph{not} depend on $\gamma$.
-
-The idea behind all the mappings is polynomial approximation. According to the
-well known Stone-Weierstrass theorem (see
-e.g.~\citep[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
-multivariate polynomials uniformly approximate any continuous function.
-Intuitively speaking, we use a multivariate polynomial to approximate, on the
-unit ball of $\R^d$, the indicator function corresponding to the intersection of
-$m=K-1$ halfspaces. Within margin $\gamma$ along the decision boundary, we allow
-the polynomial to attain arbitrary value. The polynomial separates examples in
-one class from examples in the other classes. To be able to quantify $R'$,
-$\gamma'$ and time complexities of evaluating $\phi(x)$ and $k(x,x')$, we need
-to quantify certain parameters of the approximating polynomial. We construct two
-different polynomials with different parameters. The parameters are quantified
-in
-Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
-stated below.
-
-Before we state the theorems, recall that a polynomial of $d$ variables is a
-function $p:\R^d \to \R$ of the form
-$$
-p(x) = p(x_1, x_2, \dots, x_d) = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-$$
-where the sum ranges over a finite set of $d$-tuples $(\alpha_1, \alpha_2,
-\dots, \alpha_d)$ of non-negative integers and $c_{\alpha_1, \alpha_2, \dots,
-\alpha_d}$ is a real coefficient. The \emph{degree} of a polynomial $p$, denoted
-by $\deg(p)$, is the largest value of $\alpha_1 + \alpha_2 + \dots + \alpha_d$
-for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is non-zero.
-The \emph{norm of a polynomial} $p$ is defined as
-$$
-\norm{p} = \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} \left(c_{\alpha_1, \alpha_2, \dots, \alpha_d} \right)^2 } \; .
-$$
-It is easy see that this is indeed a norm, since we can interpret it as a
-Euclidean norm of the vector of the coefficients of the polynomial.
-
-\begin{theorem}[Polynomial approximation of intersection of halfspaces I]
-\label{theorem:polynomial-approximation-1}
-Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
-\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$. There exists a
-multivariate polynomial $p:\R^d \to \R$ such that
-\begin{enumerate}
-\item $p(x) \ge 1/2$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-\item $p(x) \le -1/2$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-\item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$
-\item $\displaystyle \norm{p} \le \left( 188 \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil \right)^{\frac{1}{2} \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil}$
-\end{enumerate}
-\end{theorem}
-
-\begin{theorem}[Polynomial approximation of intersection of halfspaces II]
-\label{theorem:polynomial-approximation-2}
-Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
-\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$.
-Define
-$$
-r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1 \qquad \text{and} \qquad s = \left \lceil \log_2(1/\gamma) \right \rceil \; .
-$$
-Then, there exists a multivariate polynomial $p:\R^d \to \R$ such that
-\begin{enumerate}
-\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$
-for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-
-\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$
-for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-
-\item $\deg(p) \le (2s+1) rm$
-\item $\norm{p} \le (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm}$
-\end{enumerate}
-\end{theorem}
-
-The proofs of the theorems can be found in
-Section~\ref{section:proof-of-polynomial-approximation}. The geometric
-interpretation of the two regions described in parts 1 and 2 of the theorems is
-explained in Figure~\ref{figure:pizza-slice}. Similar but weaker results were
-proved by~\cite{Klivans-Servedio-2008}. In particular, the bounds in parts
-1, 2, 3, 4 of the theorems are independent of the dimension $d$.
-
-\begin{figure}
-\begin{center}
-\input{figures/pizza-slice}
-\end{center}
-\caption[]{The figure shows the two regions used in parts 1 and 2 of
-Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
-for the case $m=d=2$ and a particular choice of vectors $v_1, v_2$ and margin
-parameter $\gamma$. These regions are
-\begin{align*}
-R^+ & = \displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\} \; , \\
-R^- & = \displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\} \; .
-\end{align*}
-The separating hyperplanes $\ip{v_1}{x} = 0$ and $\ip{v_2}{x} = 0$ are shown as dashed lines.
-}
-\label{figure:pizza-slice}
-\end{figure}
-
-We construct the three different mappings $\phi_n, \psi_n, \rho$. The first two
-are parameterized by a non-negative integer $n$. The domain of $\phi_n$ and
-$\psi_n$ is $\R^d$. The domain of $\rho$ is the unit ball of $\R^d$. The
-co-domain for $\phi_n$ and $\psi_n$ is $\R^p$ where $p = \sum_{i=0}^n
-\binom{i+d-1}{d-1}$ equipped with the standard inner product $\ip{x}{x'} =
-\sum_{i=1}^p x_i x'_i$. The co-domain is the classical separable Hilbert space
-$\ell_2 = \{ x \in \R^\infty ~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped
-with the standard inner product $\ip{x}{x'} = \sum_{i=1}^\infty x_i x'_i$. We
-index the coordinates of the co-domain $\R^p$ by $d$-tuples $(\alpha_1,
-\alpha_2, \dots, \alpha_d)$ of non-negative integers such that $\alpha_1 +
-\alpha_2 + \dots + \alpha_d \le n$. Similarly, we index the coordinates of
-$\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
-integers. The mappings are defined by
-\begin{align*}
-\left(\phi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-\\
-\left(\psi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = \sqrt{\binom{n}{\alpha_1 + \alpha_2 + \dots + \alpha_d} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-\\
-\left(\rho(x)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-\end{align*}
-where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
-is the multinomial coefficient and $\binom{n}{k} = \frac{n!}{(n-k)!k!}$ is the binomial coefficient.
-
-Mappings $\psi_n$ and $\rho$ have simple-to-compute kernels
-\begin{align*}
-K_{\psi_n}(x,x') & = \ip{\psi_n(x)}{\psi_n(x')}_{\R^p} = \left( 1 + \ip{x}{x'} \right)^n \; , \\
-K_{\rho}(x,x') & = \ip{\rho(x)}{\rho(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}} \; .
-\end{align*}
-In passing we note that the formula for $K_\rho$ implies the mapping $\rho$ is
-well defined. Indeed, since $K_{\rho}(x,x) < +\infty$ for any $x$ in the unit
-ball of $\R^d$, it means that $\rho(x)$ indeed lies in $\ell_2$.
-
-TODO
-
-\section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
-\label{section:proof-of-polynomial-approximation}
-
-For the proofs of the theorems we need several auxiliary results.
-
-\begin{lemma}[Simple inequality]
-\label{lemma:simple-inequality}
-For any real numbers $b_1, b_2, \dots, b_n$,
-$$
-\left( \sum_{i=1}^n b_i \right)^2 \le n \sum_{i=1}^n b_i^2 \; .
-$$
-\end{lemma}
-
-\begin{proof}
-The lemma follows from Cauchy-Schwartz inequality applied to
-vectors $(b_1, b_2, \dots, b_n)$ and $(1,1,\dots,1)$.
-\end{proof}
-
-\begin{lemma}[Bound on binomial coefficients]
-\label{lemma:binomial-bound}
-For any integers $n,k$ such that $n \ge k \ge 0$,
-$$
-\binom{n}{k} \le (n - k + 1)^k \; .
-$$
-\end{lemma}
-
-\begin{proof}
-If $k = 0$, the inequality trivially holds. For the rest of the proof we can
-assume $k \ge 1$. We write the binomial coefficient as
-$$
-\binom{n}{k}
-= \frac{n(n-1)\cdots(n-k+1)}{k(k-1) \cdots 1}
-= \frac{n}{k} \cdot \frac{n-1}{k - 1} \cdots \frac{n-k+1}{1} \; .
-$$
-We claim that
-$$
-\frac{n}{k} \le \frac{n-1}{k - 1} \le \cdots \le \frac{n-k+1}{1}
-$$
-from which the lemma follows by upper bounding all the fractions by $n-k+1$.
-It remains to prove that for any $j=0,1,\dots,k-1$,
-$$
-\frac{n - j + 1}{k - j + 1} \le \frac{n - j}{k - j} \; .
-$$
-Multiplying by the (positive) denominators, we get an equivalent inequality
-$$
-(n - j + 1)(k - j) \le (n - j)(k - j + 1) \; .
-$$
-Cancelling common terms leads to an equivalent inequality
-$$
-k - j \le n - j \; ,
-$$
-which holds by the assumption on $n \ge k$.
-\end{proof}
-
-\begin{lemma}[Properties of the norm of polynomials]
-\label{lemma:properties-of-norm-of-polynomials}
-\hspace{1cm} % Dummy space
-\begin{enumerate}
-\item Let $p_1, p_2, \dots, p_n$ be multivariate polynomials and let $p(x) =
-\prod_{j=1}^n p_j(x)$ be their product.  Then, $\norm{p}^2 \le n^{\sum_{j=1}^n
-\deg(p_j)} \prod_{j=1}^n \norm{p_j}^2$.
-
-\item Let $q$ be a multivariate polynomial of degree at most $s$ and let $p(x) =
-(q(x))^n$. Then, $\norm{p}^2 \le n^{ns} \norm{q}^{2n}$.
-
-\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then,
-$\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-Using multi-index notation we can write any multivariate polynomial $p$ as
-$$
-p(x) = \sum_A c_A x^A
-$$
-where $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ is a multi-index (i.e. a $d$-tuple of
-non-negative integers), $x^A = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}$ is a
-monomial and $c_A = c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is the corresponding real
-coefficient. The sum is over a finite subset of $d$-tuples of non-negative
-integers. Using this notation, the norm of a polynomial $p$ can be written as
-$$
-\norm{p} = \sqrt{\sum_A (c_A)^2} \; .
-$$
-For a multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ we define its
-$1$-norm as $\norm{A}_1 = \alpha_1 + \alpha_2 + \dots + \alpha_d$.
-
-To prove the part 1, we express $p_j$ as
-$$
-p_j(x) = \sum_{A_j} c^{(j)}_{A_j} x^{A_j} \; .
-$$
-Since $p(x) = \prod_{i=1}^n p_j(x)$, the coefficients of its expansion $p(x) =
-\sum_A c_A x^A$ are
-$$
-c_A = \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \; .
-$$
-Therefore,
-\begin{multline*}
-\norm{p}^2
-= \sum_{A} (c_A)^2
-= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \right)^2
-= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\end{multline*}
-and
-\begin{multline*}
-\prod_{i=1}^n \norm{p_i}^2
-= \prod_{i=1}^n \left( \sum_{A_i} (c^{(i)}_{A_i})^2 \right)
-= \sum_{(A_1, A_2, \dots, A_n)} \prod_{j=1}^n (c^{(j)}_{A_j})^2
-= \sum_{(A_1, A_2, \dots, A_n)} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
-= \sum_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\end{multline*}
-where in both cases the outer sum is over multi-indices $A$ such that $\norm{A}_1 \le \deg(p)$.
-\autoref{lemma:simple-inequality} implies that for any multi-index $A$,
-$$
-\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\le M_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
-$$
-where $M_A$ is the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 +
-A_2 + \dots + A_n = A$.
-
-To finish the proof, it is sufficient to prove that $M_A \le n^{\deg(p)}$ for
-any $A$ such that $\norm{A}_1 \le \deg(p)$. To prove this inequality, consider a
-multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ and consider its $i$-th coordinate
-$\alpha_i$. In order for $A_1 + A_2 + \dots + A_n = A$ to hold, the $i$-th
-coordinates of $A_1, A_2, \dots, A_n$ need to sum to $\alpha_i$. There are exactly
-$\binom{\alpha_i + n - 1}{\alpha_i}$ possibilities for the choice of $i$-th
-coordinates of $A_1, A_2, \dots, A_n$. The total number of choices is thus
-$$
-M_A = \prod_{i=1}^d \binom{\alpha_i + n - 1}{\alpha_i} \; .
-$$
-Using \autoref{lemma:binomial-bound}, we upper bound it as
-$$
-M_A \le \prod_{i=1}^d n^{\alpha_i} = n^{\norm{A}_1} \le n^{\deg(p)} \; .
-$$
-
-Part 2 follows from the part 1 by setting $p_1 = p_2 = \dots p_n = q$.
-
-To prove the part 3, we use generalized triangle inequality and
-\autoref{lemma:simple-inequality}. We have
-\begin{align*}
-\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
-\end{align*}
-\end{proof}
-
-\subsection{Proof of \autoref{theorem:polynomial-approximation-1}}
-\label{section:proof-of-polynomial-approximation-1}
-
-To construct the polynomial $p$ we use Chebyshev polynomials of the first kind.
-Chebyshev polynomials of the fist kind form an infinite sequence of polynomials
-$T_0(z), T_1(z), T_2(z), \dots$ of single real variable $z$. They are defined
-by the recurrence
-\begin{align*}
-T_0(z) & = 1 \; , \\
-T_1(z) & = z \; , \\
-T_{n+1}(z) & = 2zT_n(z) - T_{n-1}(z) & \text{for $n \ge 1$.}
-\end{align*}
-Chebyshev polynomials have a lot of interesting properties.
-We will need properties listed in
-\autoref{proposition:properties-of-chebyshev-polynomials} below.
-Interested reader can learn more about Chebyshev polynomials
-from the book by \cite{Mason-Handscomb-2002}.
-
-\begin{proposition}[Properties of Chebyshev polynomials]
-\label{proposition:properties-of-chebyshev-polynomials}
-Chebyshev polynomials satisfy
-\begin{enumerate}
-\item $\deg(T_n) = n$ for all $n \ge 0$.
-\item If $n \ge 1$, the leading coefficient of $T_n(z)$ is $2^{n-1}$.
-\item $T_n(\cos(\theta)) = \cos(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
-\item $T_n(\cosh(\theta)) = \cosh(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
-\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$ and all $n \ge 0$.
-\item $T_n(z) \ge 1 + n^2(z - 1)$ for all $z \ge 1$ and all $n \ge 0$.
-\item $\norm{T_n} \le (1+\sqrt{2})^n$ for all $n \ge 0$
-\end{enumerate}
-\end{proposition}
-
-\begin{proof}[Proof of \autoref{proposition:properties-of-chebyshev-polynomials}]
-The first two properties can be easily proven by induction on $n$ using the recurrence.
-
-We prove third property by induction on $n$. Indeed, by definition
-$$
-T_0(\cos(\theta)) = 1 = \cos(0 \theta) \qquad \text{and} \qquad T_1(\cos(\theta)) = \cos(\theta) \; .
-$$
-For $n \ge 1$, we have
-\begin{align*}
-T_{n+1}(\cos(\theta))
-& = 2 \cos(\theta) T_n(\cos(\theta)) - T_{n-1}(\cos(\theta)) \\
-& = 2 \cos(\theta) \cos(n \theta) - \cos((n-1)\theta)) \; ,
-\end{align*}
-where the last step follow by induction hypothesis.
-It remains to show that the last expression equals $\cos((n+1)\theta)$.
-This can be derived from the trigonometric formula
-$$
-\cos(\alpha \pm \beta) = \cos(\alpha) \cos(\beta) \mp \sin(\alpha) \sin(\beta) \; .
-$$
-By substituting $\alpha = n \theta$ and $\beta = \theta$, we get two equations
-\begin{align*}
-\cos((n+1) \theta) & = \cos(n \theta) \cos(\theta) - \sin(n \theta) \sin(\theta) \; , \\
-\cos((n-1) \theta) & = \cos(n \theta) \cos(\theta) + \sin(n \theta) \sin(\theta) \; .
-\end{align*}
-Summing them yields
-$$
-\cos((n+1)\theta) + \cos((n-1) \theta) = 2 \cos(n \theta) \cos(\theta)
-$$
-which finishes the proof.
-
-Fourth property has the similar proof as third property. It suffices
-to replace $\cos$ and $\sin$ with $\cosh$ and $\sinh$ respectively.
-
-Fifth property follows from the third property. Indeed, for any $z \in [-1,1]$
-there exists $\theta \in \R$ such that $\cos \theta = z$. Thus, $|T_n(z)| =
-|T_n(\cos(\theta))| = |\cos(n\theta)| \le 1$.
-
-The sixth property is equivalent to
-$$
-T_n(\cosh(\theta)) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$,}
-$$
-since $\cosh(\theta) = \frac{e^{\theta} + e^{-\theta}}{2}$ is an even continuous
-function that maps $\R$ onto $[1,+\infty)$, is strictly decreasing on
-$(-\infty,0]$, and is strictly increasing on $[0,\infty)$. Using the fourth
-property the last inequality is equivalent to
-$$
-\cosh(n \theta) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$.}
-$$
-For $\theta = 0$, both sides are equal to $1$. Thus, it is sufficient to prove
-that the derivative of the left hand side is greater or equal to the derivative
-of the right hand side. Recalling that $[\cosh(\theta)]' = \sinh(\theta)$, this
-means that we need to show that
-$$
-\sinh(n \theta) \ge n \sinh(\theta) \qquad \text{for all $\theta \ge 0$.}
-$$
-Tho prove this inequality we use the summation formula
-$$
-\sinh(\alpha + \beta) = \sinh(\alpha) \cosh(\beta) + \sinh(\beta) \cosh(\beta) \; .
-$$
-If $\alpha, \beta$ are non-negative then $\sinh(\alpha), \sinh(\beta)$ are
-non-negative and $\cosh(\alpha), \cosh(\beta) \ge 1$. Hence,
-$$
-\sinh(\alpha + \beta) \ge \sinh(\alpha) + \sinh(\beta) \qquad \text{for any $\alpha, \beta \ge 0$.}
-$$
-This implies that (using induction on $n$) that $\sinh(n \theta) \ge n
-\sinh(\theta)$ for all $\theta \ge 0$.
-
-We verify the seventh property by induction on $n$.
-For $n=0$ and $n=1$ the inequality trivially holds, since $\norm{T_0} = \norm{T_1} = 1$.
-For $n \ge 1$, since $T_{n+1}(z) = 2zT_n(z) - T_{n-1}(z)$,
-\begin{align*}
-\norm{T_{n+1}}
-& \le 2 \norm{T_n} + \norm{T_{n-1}} \\
-& \le 2 (1 + \sqrt{2})^n + (1 + \sqrt{2})^{n-1} \\
-& = (1 + \sqrt{2})^{n-1} (2 (1 + \sqrt{2}) + 1) \\
-& = (1 + \sqrt{2})^{n-1} (3 + 2\sqrt{2}) \\
-& = (1 + \sqrt{2})^{n-1} (1 + \sqrt{2})^2 \\
-& = (1 + \sqrt{2})^{n+1} \; .
-\end{align*}
-
-\end{proof}
-
-Let $r = \left\lceil \log_2(2m) \right\rceil$ and $s = \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$.
-We define the polynomial $p:\R^d \to \R$ as
-$$
-p(x) = m + \frac{1}{2} - \sum_{i=1}^m \left( T_s(1 - \ip{v_i}{x}) \right)^r \; .
-$$
-It remains to show that $p$ has properties 1--5.
-
-To verify the first property notice that if $x \in \R^d$ satisfies $\norm{x} \le
-1$ and $\ip{v_i}{x} \ge \gamma$ then since $\norm{v_i} \le 1$ we have
-$\ip{v_i}{x} \in [0,1]$. Thus, $T_s(1 - \ip{v_i}{x})$ and $\left( T_s(1 -
-\ip{v_i}{x}) \right)^r$ lie in the interval $[-1,1]$. Therefore,
-$$
-p(x) \ge m + \frac{1}{2} - m \ge \frac{1}{2} \; .
-$$
-
-To verify the second property consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d
-~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Clearly, $\norm{x} \le 1$
-and there exists at least one $i \in \{1,2,\dots,m\}$ such that $\ip{v_i}{x} \le
-- \gamma$. Therefore, $1 - \ip{v_i}{x} \ge 1 + \gamma$ and~\autoref{proposition:properties-of-chebyshev-polynomials} (part 6)
-imply that
-$$
-T_s(1 - \ip{v_i}{x}) \ge 1 + s^2 \gamma \ge 2
-$$
-and thus
-$$
-\left( T_s(1 - \ip{v_i}{x}) \right)^r \ge 2^r \ge 2m \; .
-$$
-On the other hand for any $j \in \{1,2,\dots,m\}$, we have $\ip{v_j}{x} \in
-[-1,1]$ and thus $1 - \ip{v_j}{x}$ lies in the interval $[0,2]$. According to
-\autoref{proposition:properties-of-chebyshev-polynomials} (parts 5 and 6), $T_s(1 - \ip{v_j}{x})
-\ge -1$. Therefore,
-$$
-p(x) = m + \frac{1}{2} - \left( T_s(1 - \ip{v_i}{x}) \right)^r - \sum_{\substack{j ~:~  1 \le j \le m \\ j \neq i}} \le m + \frac{1}{2} - 2m + (m - 1) \le - \frac{1}{2} \; .
-$$
-
-The third property follows from observation that degree of $p$
-is the same as the degree of any one of the terms
-$\left( T_s(1 - \ip{v_i}{x}) \right)^r$ which is $r \cdot s$.
-
-To prove the fourth property, we need to upper bound the norm of $p$.
-Let $f_i(x) = 1 - \ip{v_i}{x}$, let $g_i(x) = T_s(1 - \ip{v_i}{x})$
-and let $h_i(x) = (T_s(1 - \ip{v_i}{x}))^r$. We have
-$$
-\norm{f_i}^2 = 1 + \norm{v_i}^2 \le 1 + 1 = 2 \; .
-$$
-Let $T_s(z) = \sum_{j=0}^s c_j z^j$ be the expansion of $s$-th Chebyshev polynomial.
-Then,
-\begingroup
-\allowdisplaybreaks
-\begin{align*}
-\norm{g_i}^2
-& = \norm{ \sum_{j=0}^s c_j (f_i)^j }^2 \\
-& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 & \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
-& = (s + 1) \sum_{j=0}^s (c_j)^2 \norm{(f_i)^j}^2 \\
-& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} & \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
-& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j 2^{2j} \\
-& \le (s + 1) s^s 2^{2s} \sum_{j=0}^s (c_j)^2 \\
-& = (s + 1) s^s 2^{2s} \norm{T_s}^2 \\
-& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} & \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
-& = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
-& \le \left(8(1+\sqrt{2})^2 s \right)^s & \text{(since $s+1 \le 2^s$ for any integer $s \ge 0$)} \\
-& \le \left(47 s \right)^s \; .
-\end{align*}
-\endgroup
-Finally,
-\begin{align*}
-\norm{p}
-& \le m + \frac{1}{2} + \sum_{i=1}^m \norm{(g_i)^r} \\
-& = m + \frac{1}{2} + \sum_{i=1}^m \sqrt{\norm{(g_i)^r}^2} \\
-& \le m + \frac{1}{2} + \sum_{i=1}^m \sqrt{r^{rs} \norm{g_i}^{2r}} \\
-& \le m + \frac{1}{2} + m r^{rs/2} \left(47 s \right)^{rs/2} \\
-& = m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \; .
-\end{align*}
-We can further upper bound the last expression by using that $m \le \frac{1}{2} 2^r$.
-Since $r,s \ge 1$,
-\begin{align*}
-\norm{p}
-& \le m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \\
-& \le \frac{1}{2} 2^r + \frac{1}{2} + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
-& \le 2^r + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
-& = 2^r \left(1 + \frac{1}{2} \left(47 rs \right)^{rs/2} \right) \\
-& = 2^r \left(47 rs \right)^{rs/2} \\
-& \le 4^{rs/2} \left(47 rs \right)^{rs/2} \\
-& \le \left(188 rs \right)^{rs/2} \; .
-\end{align*}
-Substituting for $r$ and $s$ finishes the proof.
-
-\subsection{Proof of \autoref{theorem:polynomial-approximation-2}}
-\label{section:proof-of-polynomial-approximation-2}
-
-We define several univariate polynomials
-\begin{align*}
-P_n(z) & = (z - 1) \prod_{i=1}^n (z - 2^i)^2 && \text{for $n \ge 0$,} \\
-A_{n,k}(z) & = (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$,} \\
-B_{n,k}(z) & = - (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$.}
-\end{align*}
-We define the polynomial $p:\R^d \to \R$ as
-$$
-p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
-- \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-$$
-
-For convenience we define univariate rational function
-\begin{align*}
-S_{n,k}(z) & = \frac{A_{n,k}(z)}{B_{n,k}(z)} && \text{for $n,k \ge 0$,}
-\end{align*}
-and a multivariate rational function
-$$
-Q(x) = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \; .
-$$
-It easy to verify that
-$$
-p(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-$$
-
-\begin{lemma}[Properties of $P_n$]
-\label{lemma:properties-of-p-n}
-\hspace{1cm} % Dummy space
-\begin{enumerate}
-\item If $z \in [0,1]$ then $P_n(-z) \le P_n(z) \le 0$.
-\item If $z \in [1,2^n]$ then $0 \le 4P_n(z) \le -P_n(-z)$.
-\item If $z \ge 0$ then $-P_n(-z) \ge 2^{n(n+1)}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-To prove the first part, note that $P_n(z)$ and $P_n(-z)$ are non-positive for
-$z \in [0,1]$. We can write $\frac{P_n(z)}{P_n(-z)}$ as a product of $n+1$
-non-negative fractions
-$$
-\frac{P_n(z)}{P_n(-z)} = \frac{1-z}{1+z} \prod_{i=1}^n \frac{(z+2^i)^2}{(z-2^i)^2} \; .
-$$
-The first part follows from the observation that each fraction is upper bounded
-by $1$.
-
-To prove the second part, notice that $P_n(z)$ is non-negative and $P_n(-z)$ is
-non-positive for any $z \in [1,2^n]$. Now, fix $z \in [1,2^n]$ and let $j \in
-\{1,2,\dots,n\}$ be such that $2^{j-1} \le z \le 2^j$. This implies that
-$(z+2^{j})^2 \ge 4 (z - 2^j)^2$. We can write $\frac{P_n(z)}{-P_n(-z)}$ as a
-product of $n+1$ non-negative fractions
-$$
-\frac{P_n(z)}{-P_n(-z)}
-= \frac{z-1}{z+1} \cdot \frac{(z-2^j)^2}{(z+2^j)^2} \prod_{\substack{i ~:~ 1 \le i \le n \\ i \neq j}} \frac{(z-2^i)^2}{(z+2^i)^2} \; .
-$$
-The second part follows from the observation that the second fraction is upper
-bounded by $1/4$ and all other fractions are upper bounded by $1$.
-
-The third part follows from
-$$
--P_n(-z) = (1+z) \prod_{i=1}^n (z+2^i)^2 \ge \prod_{i=1}^n 2^{2i} = 2^{n(n+1)} \; .
-$$
-\end{proof}
-
-\begin{lemma}[Properties of $S_{n,r}$ and $B_{n,r}$]
-\label{lemma:properties-of-s-n-r}
-Let $n,m$ be non-negative integers.
-Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$. Then,
-\begin{enumerate}
-\item If $z \in [1,2^n]$ then $S_{n,r}(z) \in [1,1+\frac{1}{2m}]$.
-\item If $z \in [-2^n, -1]$ then $S_{n,r} \in [-1-\frac{1}{2m}, -1]$.
-\item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
-\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-Note that $B_{n,r}(z)$ is an even function and $A_{n,r}(z)$ is an odd function.
-Therefore, $S_{n,r}(z)$ is odd. Also notice that $r$ is an odd integer.
-
-\begin{enumerate}
-\item Observe that $S_{n,r}(z)$ can be written as
-$$
-S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. Since
-$r \ge \frac{1}{2} \log_2(4m+1)$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
-$S_{n,r}(z) = \frac{1+c}{1-c} \in [1,1 + \frac{1}{2m}]$.
-
-\item Since $S_{n,r}(z)$ is odd, the statement follows from part 1.
-
-\item Observe that $S_{n,r}(z)$ can be written as
-$$
-S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. If $z \in [0,1]$, by part
-1 of~\autoref{lemma:properties-of-p-n} and the fact that $r$ is odd, $c
-\in [-1,0]$, and thus, $S_{n,r}(z) = \frac{1+c}{1-c} \in [0,1]$. Since
-$S_{n,r}(z)$ is odd, for $z \in [-1,0]$, $S_{n,r}(z) \in [-1,0]$.
-
-\item Since $B_{n,r}(z)$ is even, we can without loss generality assume that $z \ge
-0$. We consider two cases.
-
-Case $z \in [0,1]$. Since $r$ is odd and $P_n(z)$ is non-positive,
-$$
-B_{n,r}(z) = - (P_n(z))^r + \left(- P_{n}(-z)\right)^r \ge \left(- P_{n}(-z)\right)^r \ge 2^{n(n+1)r} \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
-where the second last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
-
-Case $z \in [1,2^n]$. Since $r$ is odd,
-$$
-B_{n,r}(z) = \left(- P_{n}(-z)\right)^r \left(1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r \right) = \left(- P_{n}(-z)\right)^r (1 - c)
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. By
-the definition of $r$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
-$$
-B_{n,r}(z) \ge \left(- P_{n}(-z)\right)^r \left( 1 - \frac{1}{4m+1} \right) \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
-where the last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
-\end{enumerate}
-\end{proof}
-
-\begin{lemma}[Properties of $Q(x)$]
-\label{lemma:properties-of-q}
-The rational function $Q(x)$ satisfies
-\begin{enumerate}
-\item $Q(x) \ge \frac{1}{2}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
-\item $Q(x) \le -\frac{1}{2}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-To prove part 1, consider any $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \
-\ip{v_i}{x} \ge \gamma \right\}$. Then, $\frac{\ip{v_i}{x}}{\gamma} \in [1,
-\frac{1}{\gamma}]$. By part 1 of \autoref{lemma:properties-of-s-n-r},
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \in [1, 1 + \frac{1}{2m}]$ and
-in particular $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \ge 1$. Thus,
-$$
-Q(x) = \left( \sum_{i=1}^m S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \right) - (m - 1/2) \ge m - (m - 1/2) = 1/2 \; .
-$$
-
-To prove part 2, consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~
-\norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Observe that
-$\frac{\ip{v_i}{x}}{\gamma} \in [-\frac{1}{\gamma}, \frac{1}{\gamma}]$. Consider
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right)$ for any $i \in
-\{1,2,\dots,m\}$. Parts 1,2, and 3 of \autoref{lemma:properties-of-s-n-r}
-and the fact $1/\gamma \le 2^s$ imply that
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \le 1 +
-\frac{1}{2m}$ for all $i \in \{1,2,\dots,m\}$. By the choice of $x$, there
-exists $j \in \{1,2,\dots,m\}$ such that $\ip{v_j}{x} \le - \gamma$. Part 2 of
-\autoref{lemma:properties-of-s-n-r} implies that
-$S_{s,r}\left(\frac{\ip{v_j}{x}}{\gamma}\right) \in [-1-\frac{1}{2m},-1]$. Thus,
-\begin{align*}
-Q(x)
-& = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& = S_{s,r}\left( \frac{\ip{v_j}{x}}{\gamma} \right) + \left( \sum_{\substack{i ~:~ 1 \le i \le m \\ i \neq j}} S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& \le -1 + (m-1) \left( 1 + \frac{1}{2m} \right) - \left(m - \frac{1}{2} \right) \\
-& \le 1/2 \; .
-\end{align*}
-\end{proof}
-
-To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-2} first
-note that part 4 of \autoref{lemma:properties-of-s-n-r} implies that for any $x$
-such that $\norm{x} \le 1$, $B_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right)$
-is positive. Thus $p(x)$ and $Q(x)$ have the same sign on the unit ball.
-Consider any $x$ in either
-$\displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-or in
-$\displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
-\autoref{lemma:properties-of-q} states that $|Q(x)| \ge 1/2$ and the sign
-depends on which of the two sets $x$ lies in. Since signs of $Q(x)$ and $p(x)$
-are the same, it remains to show that $|p(x)| \ge m^{s^2m/2}$. Indeed,
-\begin{align*}
-|p(x)|
-& = |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
-& \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
-& \ge \frac{1}{2} |Q(x)| \cdot 2^{s(s+1)rm} && \text{(since $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4} \ge 1/2$)} \\
-& \ge \frac{1}{4} \cdot 2^{s(s+1)rm} && \text{(\autoref{lemma:properties-of-q})} \; .
-\end{align*}
-
-To prove part 3 of \autoref{theorem:polynomial-approximation-2} note that
-$\deg(P_s) = 2s+1$. Thus, $\deg(A_{s,r})$ and $\deg(B_{s,r})$ are at most
-$(2s+1)r$. Therefore, $\deg(p) \le (2s+1) rm$.
-
-It remains to prove part 4 of \autoref{theorem:polynomial-approximation-2}.
-For any $i \in \{0,1,2,\dots,s\}$ and any $v \in \R^d$ such that $\norm{v} \le 1$
-define multivariate polynomials
-\begin{align*}
-f_{i,v}(x) & = \frac{\ip{v}{x}}{\gamma} - 2^i \; , \\
-q_v(x) & = P_s \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
-a_v(x) & = A_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
-b_v(x) & = B_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; .
-\end{align*}
-Note that
-$$
-p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
-$$
-We bound the norms of these polynomials. We have
-$$
-\norm{f_{i,v}}^2 = \norm{v}^2/\gamma^2 + 2^{2i} \le 2 \cdot 2^s \; .
-$$
-where we used that $1/\gamma \le 2^s$ and $\norm{v} \le 1$.
-Since $q_v(x) = f_{i,v}(\frac{\ip{v}{x}}{\gamma}) \prod_{i=1}^s \left(f_{i,v}(\frac{\ip{v}{x}})\right)^2$,
-using part 1 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $q_v$
-as
-$$
-\norm{q_v}^2 \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \le  (2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \; .
-$$
-Using parts 3 and 2 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $a_v$ as
-\begin{align*}
-\norm{a_v}^2
-& \le 2\norm{(q_v)^r}^2 + 2\norm{(q_{-v})^r}^2 \\
-& \le 2 r^{r(2s+1)} \norm{q_v}^{2r} + 2 r^{r(2s+1)} \norm{q_{-v}}^{2r} \\
-& \le 4 r^{r(2s+1)} \left((2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \right)^{2r} \\
-& = 4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \; .
-\end{align*}
-The same upper bound holds for $\norm{b_v}^2$. Finally,
-\begin{align*}
-\norm{p}
-& \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
-& \le \left[ \sum_{i=1}^m m^{(s+1/2)rm} \norm{a_{v_i}} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} \norm{b_{v_j}} \right] + \left(m - \frac{1}{2} \right) m^{(s+1/2)rm} \prod_{j=1}^m \norm{b_{v_j}} \\
-& \le (2m-1/2) m^{(s+1/2)rm} \left(4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \right)^{m/2} \\
-& = (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm} \; .
-\end{align*}
-
-\section{Nearest neighbor algorithm}
-
-TODO
-
-\section{NP-hardness of the weak labeling problem}
-
-Any algorithm for the bandit setting collects information in the form of so
-called \emph{strongly labeled} and \emph{weakly labeled} examples.
-Strongly-labeled examples are those for which we know the class label. Weakly
-labeled example is an example for which we know that class label can be anything
-except for a particular one class.
-
-A natural strategy for each round is to find vectors $w_1, w_2, \dots, w_K$ that
-linearly separate the examples seen in the previous rounds and use the vectors
-to predict the label in the next round. More precisely, we want to find both the
-vectors $w_1, w_2, \dots, w_K$ and label for each example consistent with its
-weak and/or strong labels such that $w_1, w_2, \dots, w_K$ linearly separate the
-labeled examples. We show this problem is NP-hard even for $K=3$.
-
-Clearly, the problem is at least as hard as the decision version of the problem
-where the goal is to determine if such vectors and labeling exist. We show that
-this problem is NP-complete.
-
-Formally, the input to the decision problem are positive integers $d, T, K$ and
-a sequence $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \{0,1\}^d \times
-\{1,2,\dots,K, \overline{1}, \overline{2}, \dots, \overline{K}\}$ of strongly
-and weakly labeled examples. The numbers $1,2,\dots,K$ correspond to strong
-labels and the symbols $\overline{1}, \overline{2}, \dots, \overline{K}$
-correspond to weak labels. We adopt the convention that $\overline{\overline{i}}
-= i$ for any positive integer $i$. The goal is to determine whether or not there
-exist vectors $w_1, w_2, \dots, w_K \in \R^d$ that satisfy the following
-conditions for all $t=1,2,\dots,T$,
-\begin{align*}
-y_t \in \{1,2,\dots,K\} \qquad & \Longrightarrow \qquad & \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \qquad \ip{w_{y_t}}{x_t} & > \ip{w_i}{x_t} \; , \\
-y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \qquad & \Longrightarrow & \qquad \exists i \in \{1,2,\dots,K\} \qquad \ip{w_i}{x_t} & > \ip{w_{\overline{y_t}}}{x_t} \; .
-\end{align*}
-
-TODO
-
-\section{Mistake lower bound for ignorant algorithms}
-
-TODO
-
-\bibliographystyle{plainnat}
-\bibliography{biblio}
-
-\appendix
-
-\section{Multiclass Perceptron}
-\label{section:multiclass-perceptron-proofs}
-
-\textsc{Multiclass Perceptron} is an algorithm for \textsc{Online Multiclass
-Classification}. Both the protocol for the problem and the algorithm are stated
-below. The algorithm assumes that the feature vectors come from an inner product
-space $(V, \ip{\cdot}{\cdot})$.
-
-Two results are folklore. The first result is
-\autoref{theorem:mutliclass-perceptron-mistake-upper-bound} which states that if
-examples are linearly separable with margin $\gamma$ and examples have norm
-at most $R$ then the algorithm makes at most $\lfloor 2 (R/\gamma)^2 \rfloor$
-mistakes. The second result is
-\autoref{theorem:online-multiclass-classification-mistake-lower-bound} which
-states that under the same assumptions as in
-\autoref{theorem:online-multiclass-classification-mistake-lower-bound}
-\emph{any} deterministic algorithm for \textsc{Online Multiclass Classification}
-must make at least $\lfloor (R/\gamma)^2 \rfloor$ mistakes in the worst case.
-
-\begin{algorithm}[h]
-\caption{\textsc{Online Multiclass Classification}
-\label{algorithm:mutliclass-classification}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$}
-\STATE{Predict $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[h]
-\caption{\textsc{Multiclass Perceptron}
-\label{algorithm:mutliclass-perceptron}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
-\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t \in V$}
-\STATE{Predict $\widehat y_t = \argmax_{i \in \{1,2,\dots,K\}} \ip{w_t^{(i)}}{x_t}$}
-\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
-\IF{$\widehat y_t \neq y_t$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}$}
-\STATE{Update $w_{y_t}^{(t+1)} = w_{y_t}^{(t)} + x_t$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ENDIF
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{theorem}[Mistake upper bound]
-\label{theorem:mutliclass-perceptron-mistake-upper-bound}
-Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
-integer, let $\gamma$ be a positive real number and let $R$ be a non-negative real
-number. If $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled
-examples in $V \times \{1,2,\dots,K\}$ that are linearly separable with margin
-$\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
-then \textsc{Multiclass Perceptron} algorithm makes at most $\lfloor
-2(R/\gamma)^2 \rfloor$ mistakes.
-\end{theorem}
-
-\begin{proof}
-Let $M = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$ be the number of
-mistakes the algorithm makes. Since the $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots,
-w_K^{(t)})$ changes only if a mistake is made, we can upper bound $\sum_{i=1}^K
-\norm{w_i^{(t)}}^2$ in terms of number of mistakes.
-If a mistake happens in round $t$ then
-\begin{align*}
-\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
-& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) + \norm{w_{y_t}^{(t)} + x_t}^2 + \norm{w_{\widehat y_t}^{(t)} - x_t}^2 \\
-& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) + \norm{w_{y_t}^{(t)}}^2 + \norm{w_{\widehat y_t}^{(t)}}^2 + 2 \norm{x_t}^2 + 2 \ip{w_{y_t}^{(t)} - w_{\widehat y_t}^{(t)}}{x_t} \\
-& = \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 \norm{x_t}^2 + 2 \ip{w_{y_t}^{(t)} - w_{\widehat y_t}^{(t)}}{x_t} \\
-& \le \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 \norm{x_t}^2 \\
-& \le \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 R^2 \; .
-\end{align*}
-So each time a mistake happens, $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ increases by at most $2R^2$. Thus,
-$$
-\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le 2R^2 M \; .
-$$
-Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors satisfying the
-\eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2}. We lower bound $\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$. This quantity changes
-only when a mistakes happens. If mistake happens in round $t$, we have
-\begin{align*}
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(t+1)}}
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^*}{w_{y_t}^{(t)} + x_t} + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} - x_t} \\
-& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^* - w_{\widehat y_t}^*}{x_t} \\
-& \ge  \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \gamma \; .
-\end{align*}
-Thus, after $M$ mistakes,
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma M \; .
-$$
-We upper bound the left hand side by using Cauchy-Schwartz inequality twice and
-the condition \eqref{equation:linear-separability-1} on $w_1^*, w_2^*, \dots,
-w_K^*$. We have
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
-\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
-$$
-Combining all inequalities, we get
-$$
-(\gamma M)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le 2R^2 M \; .
-$$
-We conclude that $M \le 2(R/\gamma)^2$. Since $M$ is an integer, $M \le \lfloor 2(R/\gamma)^2 \rfloor$.
-\end{proof}
-
-\begin{theorem}[Mistake lower bound]
-\label{theorem:online-multiclass-classification-mistake-lower-bound}
-Let $K$ be a positive integer, let $\gamma$ be a positive real number and let
-$R$ be a non-negative real number. For any deterministic algorithm for the
-\textsc{Online Multiclass Classification} problem there exists an
-inner product space $(V, \ip{\cdot}{\cdot})$, a non-negative integer $T$ and a
-sequence of labeled examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$
-examples in $V \times \{1,2,\dots,K\}$ that are linearly separable with margin
-$\gamma$, the norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
-and the algorithm makes at least $\lfloor (R/\gamma)^2 \rfloor$ mistakes.
-\end{theorem}
-
-\begin{proof}
-Let $T = \lfloor (R/\gamma)^2 \rfloor$ and let $x_1, x_2, \dots, x_T$ be the
-orthogonal vectors such that $\norm{x_t} = R$ for all $t=1,2,\dots,T$. For
-example, we can take $V = \R^T$ and $x_t = R e_t$ where $e_t$ is $t$-th element
-of the standard orthonormal basis of $\R^T$.
-
-Since the algorithm is deterministic, we can construct the sequence of labels
-$y_1, y_2, \dots, y_T$ adaptively based on the predictions $\widehat y_1,
-\widehat y_2, \dots, \widehat y_T$ of the algorithm. We define $y_t$ to be any
-element of $\{1,2,\dots,K\}$ not equal to $\widehat y_t$. This way the algorithm
-makes a mistake in every round $t=1,2,\dots,T$.
-
-It remains to show that the examples we have constructed are linearly separable
-with margin $\gamma$. To prove that we demonstrate vectors $w_1, w_2, \dots, w_K$
-satisfying conditions \eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2}. We define
-$$
-w_i = \frac{1}{R\sqrt{T}} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} x_t \qquad \qquad \text{for $i=1,2,\dots,K$.}
-$$
-Let $a_i = |\{ t ~:~ 1 \le t \le T, \ y_t = i \}|$ be the number of occurrences of label $i$.
-It is easy to see that
-$$
-\norm{w_i}^2 = \frac{1}{R^2 T} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} \norm{x_t}^2 = \frac{a_i}{T} \qquad \qquad \text{for $i=1,2,\dots,K$.}
-$$
-Since $\sum_{i=1}^K a_i = T$, the condition
-\eqref{equation:linear-separability-1} holds. To verify condition
-\eqref{equation:linear-separability-2} consider any labeled example $(x_t,
-y_t)$. Then, by definition of $w_{y_t}$ we have
-$$
-\ip{w_{y_t}}{x_t}
-= \frac{1}{R\sqrt{T}} \sum_{\substack{s : 1 \le s \le T \\ y_s = y_t}} \ip{x_s}{x_t}
-= \frac{1}{R\sqrt{T}} \norm{x_t}^2
-= \frac{R}{\sqrt{T}}
-\ge \frac{R}{R/\gamma}
-= \gamma \; .
-$$
-and for any $i \in \{1,2,\dots,K\} \setminus \{y_t\}$ we have
-$\ip{w_i}{x_t} = 0$. Therefore, condition \eqref{equation:linear-separability-2} holds.
-\end{proof}
-
-\end{document}

### 2019-01-07 arxiv-version/main.tex
minor
Split sections in separate files

--- 2018-12-27 arxiv-version/main.tex
@@
 % Math symbols and commands
+\newcommand{\calF}{\mathcal{F}}
+\newcommand{\one}{\mathds{1}}
 \newcommand{\R}{\mathbb{R}}  % set of real numbers
@@
 
-\section{Introduction}
-\label{section:introduction}
+\input{introduction}
 
-We study the problem of \textsc{Online Multiclass Linear
-Classification with Bandit Feedback}~\cite{Kakade-Shalev-Shwartz-Tewari-2008}.
-The problem can be viewed as a game between the learner and the environment:
-at each timestep $t$, the environment chooses an example $(x_t, y_t)$, where its feature
-part $x_t \in \R^d$ is revealed to the learner.
-\footnote{All our results apply to also to a simpler model of
-the so called \emph{oblivious adversary} where the whole sequence of labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is chosen before the first
-round of the game.}
-Upon receiving this example, the
-learner is asked to make a prediction $\hat{y}_t$.
-the learner receives feedback immediately after making its prediction.
-In contrast with the standard full information setting (where the feedback given is the correct label $y_t$), the feedback given is only a binary indicator
-whether the prediction was correct or not. The protocol of the problem is formally stated below.
+\input{related-work}
 
-%In this problem, in each round, the
-%learner receives a feature vector and is asked to predict one of $K$
-%possible classes. To allow
-%for meaningful use of randomization, we assume that the correct label in a
-%particular round is chosen prior to algorithm's prediction in that
-%round.
-%Immediately after the learner makes its prediction, it
-%receives feedback whether the prediction was correct or not. However, in
-%contrast with the standard, so called full information setting, the algorithm
-%does \emph{not} receive the correct label. The feedback is only binary.
+\input{notions-of-linear-separability}
 
-\begin{algorithm}[h]
-\caption{\textsc{Online Multiclass Classification with Bandit Feedback}
-\label{algorithm:game-protocol}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$}
-\STATE{Adversary \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
-\chicheng{Or we simply say: Adversary chooses example $(x_t, y_t)$, where $x_t$ is reveal to the learner.}
-\STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \begin{cases}
-0 & \text{if $\widehat y_t = y_t$,} \\
-1 & \text{if $\widehat y_t \neq y_t$.}
-\end{cases}$
-}
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
+\input{algorithm-for-strongly-linearly-separable-data}
 
-The performance is of the learner is measured by its cumulative number of mistakes
-$\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$. The bandit feedback
- is a natural feedback model motivated by applications including
-online advertising and online content optimization, where the learner only gets to
-see the loss of its action taken.
-%where the binary feedback corresponds to a click
-%The
-%corresponding problem with full information feedback is solved by the classical
-%\textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
-%\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}).
+\input{from-linear-separability-to-strong-linear-separability}
 
-In this paper, we focus on the special case when the examples lie in $\R^d$ and
-are \emph{linearly separable with a margin}.
-\chicheng{I wonder if we should introduce the two notions of linear separability here,
-because strong linear separability is also worth mentioning in the full-information setting.
-}
+\input{proofs-of-polynomial-approximation-theorems}
 
-In the full-information feedback
-setting, it is well known that if the examples have norm at most $R$ and are
-linearly separable with a margin $\gamma$ then the \textsc{Multiclass
-Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
-This result is very satisfying since the upper bound on the number of mistakes
-is information-theoretically optimal and at the same time the \textsc{Multiclass
-Perceptron} algorithm has low time and memory complexity.
+\input{nearest-neighbor-algorithm}
 
-The bandit feedback setting, however, is much more challenging. To understand
-the differences, we dissect the notion of linear separability in the multiclass
-setting. Beside the standard notion of linear separability, we define also
-\emph{strong linear separability}. For binary classification, these two
-definitions are identical. However, they differ for multiclass classification.
-For multiclass classification with $K$ classes the standard notion of linear
-separability means that the examples from each class lie in an intersection of
-$K-1$ halfspaces and the examples outside of the class lie in the complement of
-the intersection of the halfspaces. Strong linear separability means that
-examples from each class are separated from the remaining examples by a
-\emph{single} hyperplane. We state the definitions precisely in
-Section~\ref{section:notions-of-linear-separability}.
+\input{np-hardness-of-the-weak-labeling-problem}
 
-For the case when the examples are strongly linearly separable, we design a
-simple and efficient algorithm with expected number of mistakes at most $(K-1)
-\lfloor (R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies
-of the \textsc{Binary Perceptron} algorithm, one copy for each class.
-Intuitively speaking, the factor $K-1$ is the price we pay for the bandit
-feedback, or more precisely, the lack of full-information feedback. We also
-prove that any (possibly randomized) algorithm makes $\Omega(K (R/\gamma)^2))$
-mistakes in the worst case.
-
-For the standard notion of linear separability, we propose several algorithms
-with various time-complexity-versus-mistake-bound trade-offs. First class of
-algorithms map the examples into a high-dimensional inner product space. In this
-space the examples become \emph{strongly} linearly separable. This allows us to
-run the algorithm for the strongly linearly separable case. All of these
-algorithms can be kernelized. (Some of them have to be kernelized since the
-underlying inner product space is infinite dimensional.) Kernelization does not
-change the input-output behavior of the algorithm, it only affects its time
-and memory complexity.
-
-These algorithms differ by choice of the mapping or, equivalently, choice of the
-kernel. The crux of the problem is the analysis of the approximation properties
-of these mappings/kernels and the way margin in the original space $\R^d$ under
-standard linear separability notion gets transformed into a margin in the
-high-dimensional space under the strong separability notion. This problem is
-related to the problem of learning intersection of halfspaces and has been
-studied previously by \cite{Klivans-Servedio-2008}. As an important technical
-achievement, we improve on the results of \cite{Klivans-Servedio-2008} by
-removing completely the dependency on the original dimension $d$.
-
-Finally, we propose a very different algorithm that is based on the obvious idea
-that two points that are close enough must have the same label. Here, close
-enough means that they cannot be separated from each other by a linear separator
-with a margin.
-
-All the algorithms run in time that is polynomial in the dimension of the
-feature vectors, the number of classes and the number of rounds. At the same
-time, all the algorithms make number of mistakes that does \emph{not} depend
-on the number of rounds. Instead, their number of mistakes depends only on the
-margin, number of classes, dimension of the feature vectors, and the radius of
-the ball in which the data lie.
-
-Finally, we study two questions related to the computational and
-information-theoretic hardness of the problem. Any algorithm for the bandit
-setting collects information in the form of so called \emph{strongly labeled}
-and \emph{weakly labeled} examples. Strongly labeled examples are those for
-which we know the class label. Weakly labeled example is an example for which we
-know that class label can be anything except for a particular one class. First,
-we show the offline problem of finding a linear multiclass separator consistent
-with a set of strongly and weakly labeled examples is NP-hard. This result is a
-consequence of the fact that finding an intersection of two halfspaces
-consistent with a set of binary-labeled examples is
-NP-hard~\citep{Blum-Rivest-1993}. Second, we show that any algorithm that uses
-only strongly-labeled examples and ignores weakly labeled examples makes at
-least $\Omega(???)$ mistakes.
-
-\section{Related work}
-\label{section:related-work}
-
-\begin{itemize}
-\item \cite{Abernethy-Rakhlin-2009}
-
-\item \cite{Chen-Chen-Zhang-Chen-Zhang-2009}
-
-\item \cite{Hazan-Kale-2011}
-
-\item \cite{Beygelzimer-Orabona-Zhang-2017}
-
-\item \cite{Foster-Kale-Luo-Mohri-Sridharan-2018}
-
-\item \cite{Foster-Krishnamurthy-2018}
-\end{itemize}
-
-TODO
-
-\section{Notions of linear separability}
-\label{section:notions-of-linear-separability}
-
-We define two notions of linear separability for multiclass classification. The
-first notion is the standard notion of linear separability used in the proof of
-the mistake bound for the \textsc{Multiclass Perceptron} algorithm. The second
-notion is stronger, i.e. more restrictive. However, it is more suitable for the
-bandit setting, since it allows for a simple and efficient algorithm; see
-Section~\ref{section:algorithm-for-strongly-linearly-separable-data}.
-
-\begin{definition}[Linear separability]
-Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
-integer, and let $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
-y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.
-
-The examples are said to be \emph{linearly separable with a
-margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
-that
-\begin{align}
-\label{equation:linear-separability-1}
-\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
-\label{equation:linear-separability-2}
-\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} & \ge \ip{x_t}{w_i} + \gamma \; .
-\end{align}
-
-The examples are said to be \emph{strongly linearly separable with a
-margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
-that
-\begin{align}
-\label{equation:strong-linear-separability-1}
-\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
-\label{equation:strong-linear-separability-2}
-\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
-\label{equation:strong-linear-separability-3}
-\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
-\end{align}
-\end{definition}
-
-The notion of linear separability with a margin is standard. It used in the
-full-information setting to upper bound the number of mistakes of the
-\textsc{Multiclass Perceptron} algorithm. For completeness, we state the
-algorithm in Appendix~\ref{section:multiclass-perceptron-proofs}. It is a
-folklore result that if a set of labeled examples is separable with a margin
-$\gamma$ and the norm of the examples is bounded by $R$ then \textsc{Multiclass
-Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
-mistakes. Another folklore result is that \textsc{Multiclass Perceptron} is
-essentially optimal in the sense that any deterministic algorithm must make
-$\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
-completeness, we give proofs of both of these results in
-Appendix~\ref{section:multiclass-perceptron-proofs}.
-
-The notion of strong linear separability is new.
-
-It is easy to see that if labeled examples are strongly linearly
-separable with margin $\gamma$ then they are linearly separable with margin
-$2\gamma$. Indeed, if $w_1, w_2, \dots, w_K \in V$
-satisfy \eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3} then they satisfy
-\eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} with margin $\gamma' = 2\gamma$.
-
-Similarly, if $K=2$ and labeled examples are linearly separable with a margin
-$\gamma$ then they are strongly linearly separable with margin $\gamma/2$.
-Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$, $w_2' =
-\frac{w_2 - w_1}{2}$ and $\gamma'=\gamma/2$ satisfy
-\eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3}. The last two conditions are easy
-to see. The first condition follows from $\norm{w_i'}^2 \le (\frac{1}{2}
-\norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le \frac{1}{2}\norm{w_1}^2 +
-\frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
-
-However, for any $K \ge 3$ and any inner product space of dimension at least
-$2$, there exists a set of labeled examples that is linearly separable with a
-positive margin $\gamma$ but it is not strongly linearly separable with any
-positive margin $\gamma$. An example of such set of labeled examples is shown in
-Figure~\ref{figure:linearly-separable-examples-with-margin}.
-
-\begin{figure}
-\begin{center}
-\input{figures/linearly-separable-examples-with-margin}
-\end{center}
-\caption[]{The figure shows labeled examples in $\R^2$. The examples belong to
-$K=3$ classes colored white, gray and black respectively. Each class lies in a
-$120^\circ$ wedge. In other words, each class lies in an intersection of two
-halfspaces.
-
-While the examples are linearly separable with a positive margin $\gamma$, they
-are \emph{not} strongly linearly separable with any positive margin $\gamma$.
-}
-\label{figure:linearly-separable-examples-with-margin}
-\end{figure}
-
-\section{Algorithm for strongly linearly separable data}
-\label{section:algorithm-for-strongly-linearly-separable-data}
-
-In this section, we present an algorithm for \textsc{Online Multiclass
-Classification with Bandit Feedback} and prove an upper bound on the number of
-mistakes under the assumption that the examples are strongly linearly separable
-with a margin. The algorithm is stated as
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
-the mistake upper bound is stated as
-\autoref{theorem:strongly-separable-example-mistake-upper-bound}.
-
-The idea behind the algorithm is to use $K$ copies of the \textsc{Binary
-Perceptron} algorithm. Each copy corresponds to a class. In each round, each
-copy makes a binary decision whether the feature vector belongs its respective
-class or not. If at least one copy makes a positive prediction, the algorithm
-predicts accordingly. If multiple copies make positive predictions, the
-algorithm chooses one of them arbitrarily. If all copies make negative
-predictions, the algorithms makes a uniformly random guess.
-
-\begin{algorithm}[h]
-\caption{\textsc{Bandit Algorithm for Strongly Linearly Separable Examples}
-\label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
-\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t \in V$}
-\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$}
-\IF{$S_t = \emptyset$}
-\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
-\IF{$z_t = 1$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$}
-\ENDIF
-\ELSE
-\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
-\IF{$z_t = 1$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ENDIF
-\ENDIF
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{theorem}[Mistake upper bound]
-\label{theorem:strongly-separable-example-mistake-upper-bound}
-Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
-integer, let $\gamma$ a positive real number, let $R$ be a non-negative real number. If
-$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
-$V \times \{1,2,\dots,K\}$ such that the examples are strongly separable with
-margin $\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ then the
-expected number of mistakes
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-makes is at most $(K-1) \lfloor (R/\gamma)^2 \rfloor$.
-\end{theorem}
-
-\begin{proof}
-Let $M = \sum_{t=1}^T z_t$ be the number of mistakes the algorithm makes. Let $A
-= \sum_{t ~:~ S_t \neq \emptyset} z_t$ be the number of mistakes in the rounds
-when $S_t \neq \emptyset$ and let $B = \sum_{t ~:~ S_t = \emptyset} z_t$ be the
-number of mistakes in the rounds when $S_t = \emptyset$. Obviously, $M = A + B$.
-We upper bound $A$ and $B$ separately.
-
-Let $C$ be the number of times line 12 gets executed. Let $U$ be the number of
-times line 12 and line 19 get executed. In other words, $U$ is the number of
-times the $K$-tuple of vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets
-updated. Clearly, $U = A + C$.
-
-The key observation is that $\Exp[B] = (K-1) \Exp[C]$. The equality holds
-because if $S_t = \emptyset$, there is $1/K$ probability that the algorithm
-guesses the correct label and with probability $(K-1)/K$ algorithm's guess is
-incorrect. Putting all the information together, we get that
-\begin{align*}
-\Exp[M]
-& = \Exp[A] + \Exp[B] \\
-& = \Exp[A] + (K-1) \Exp[C]  \\
-& \le (K-1) \Exp[A + C] \\
-& = (K-1) \Exp[U]  \; .
-\end{align*}
-
-To finish the proof, we need to upper bound the number of updates, $U$. We claim
-that $U \le \lfloor (R/\gamma)^2 \rfloor$. The proof of this upper bound is
-similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
-algorithm. Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors that satisfy
-\eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2} and
-\eqref{equation:strong-linear-separability-3}.
-The $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$
-changes only if there is an update in round $t$.
-We investigate how $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ and
-$\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$ change. If there is an update in round $t$,
-we have
-\begingroup
-\allowdisplaybreaks
-\begin{align*}
-\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t+1)}}^2 \\
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t}^2 \\
-& = \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 + \underbrace{(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t}}_{\le 0} \\
-& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 \\
-& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + R^2 \; .
-\end{align*}
-\endgroup
-Therefore, after $U$ updates,
-$$
-\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
-$$
-Similarly, if there is an update in round $t$, we have
-\begin{align*}
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
-& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
-& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \gamma
-\end{align*}
-where the last inequality follows from \eqref{equation:strong-linear-separability-2}
-and \eqref{equation:strong-linear-separability-3} and analysis of the cases $z_t = 0$ and $z_t = 1$.
-Thus, after $U$ updates,
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma U \; .
-$$
-Applying Cauchy-Schwartz's inequality twice and assumption
-\eqref{equation:strong-linear-separability-1}, we get that
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
-\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
-$$
-Combining the upper and lower bounds on $\sum_{i=1}^K \norm{w_i^{(T+1)}}^2$ inequalities, we get
-$$
-(\gamma U)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
-$$
-We conclude that $U \le (R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor (R/\gamma)^2 \rfloor$.
-\end{proof}
-
-The upper bound $(K-1) \lfloor (R/\gamma)^2 \rfloor$ on the expected number of
-mistakes of
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
-optimal to within constant factor as long as the number of classes $K$ is
-at most $O((R/\gamma)^2)$. This is proved in
-\autoref{theorem:strongly-separable-example-mistake-lower-bound} below.
-
-Irrespective of any conditions on $K$, $R$, and $\gamma$, a trivial lower bound
-on the expected number of mistakes of any randomized algorithm is
-$\frac{K-1}{2}$. (Adversary chooses the same example over and over.) However, it
-is unclear if the trivial lower bound is the best possible if $K$ is large,
-i.e., $\omega((R/\gamma)^2)$. We leave this as an open problem.
-
-\begin{theorem}[Mistake lower bound]
-\label{theorem:strongly-separable-example-mistake-lower-bound}
-Let $\gamma$ be a positive real number and let $R$ be a non-negative real
-number. For any (possibly randomized) algorithm for the \textsc{Online
-Multiclass Classification with Bandit Feedback} with $K \le
-\frac{1}{4}(R/\gamma)^2$ classes there exists an inner product space $(V,
-\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ in $V \times
-\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
-norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
-number of mistakes the algorithm makes is at least $\frac{K-1}{2} \left\lfloor
-\frac{1}{16} (R/\gamma)^2 \right\rfloor$.
-\end{theorem}
-
-\begin{proof}
-We use probabilistic method. Let $M = \left\lfloor \frac{1}{16} (R/\gamma)^2 \right\rfloor$.
-Let $V = \R^{M+1}$ equipped with the standard inner product.  Let $e_1, e_2,
-\dots, e_{M+1}$ be the standard orthonormal basis of $V$. We define
-vectors $v_1, v_2, \dots, v_M \in V$ where $v_i = \frac{R}{\sqrt{2}}(e_i +
-e_{M+1})$ for $i=1,2,\dots,M$. Let $\ell_1, \ell_2, \dots, \ell_M$ be chosen
-i.i.d. uniformly at random from $\{1,2,\dots,K\}$ and independently of any
-randomness used the by the algorithm. Let $T = M K$. We define examples $(x_1,
-y_1), (x_2, y_2), \dots, (x_T, y_T)$ as follows:
-$$
-\begin{array}{lclclclcl}
-(x_1, y_1) & = & (x_2, y_2) & = & \cdots & = & (x_K, y_K) & = & (v_1, \ell_1) \; , \\
-(x_{K+1},y_{K+1}) & = & (x_{K+2}, y_{K+2}) & = & \cdots & = & (x_{2K}, y_{2K}) & = & (v_2, \ell_2) \; , \\
-& \vdots & \\
-(x_{(M-1)K+1}, y_{(M-1)K+1})  & = & (x_{(M-1)K+2}, y_{(M-1)K+2}) & = & \cdots & = & (x_{MK}, y_{MK}) & = & (v_M, \ell_M) \; .
-\end{array}
-$$
-
-With probability one, norm of each example is $R$. We show that with probability
-one, the examples are strongly separable with margin $\gamma$. In order to see
-that consider $w_1^*, w_2^*, \dots, w_K^* \in V$ defined by
-$$
-w_i^* = 2 \sqrt{2} \frac{\gamma}{R} \left( \sum_{j ~:~ \ell_j = i} e_j \right) - \sqrt{2} \frac{\gamma}{R} e_{M+1} \qquad \quad \text{for $i=1,2,\dots,K$.}
-$$
-Since for any $i \in \{1,2,\dots,K\}$ and any $j \in \{1,2,\dots,M\}$,
-$$
-\ip{w_i^*}{v_j} =
-\begin{cases}
-\gamma & \text{if $\ell_j = i$,} \\
-- \gamma & \text{if $\ell_j \neq i$,}
-\end{cases}
-$$
-it means that $w_1^*, w_2^*, \dots, w_K^*$ satisfy
-\eqref{equation:strong-linear-separability-2} and
-\eqref{equation:strong-linear-separability-3}. Condition \eqref{equation:strong-linear-separability-1}
-is satisfied since
-$$
-\sum_{i=1}^K \norm{w_i^*}^2
-= 8 \frac{\gamma^2}{R^2} \sum_{j=1}^M \norm{e_j}^2 + 2 \frac{\gamma^2}{R^2} K \norm{e_{M+1}}^2
-= 8 \frac{\gamma^2}{R^2} M + 2 \frac{\gamma^2}{R^2} K
-\le \frac{1}{2} + \frac{1}{2}
-= 1 \; .
-$$
-
-It remains to lower bound the expected number of mistakes of the algorithm. For
-any $j \in \{1,2,\dots,M\}$, consider the expected number of mistakes the
-algorithm makes in rounds $K(j-1) + 1, K(j-1) + 2, \dots, Kj$. In these rounds,
-the algorithm is guessing the label $\ell_j$. Since $\ell_j$ is chosen uniformly
-at random from the set $\{1,2,\dots,K\}$ and feedback is only binary, the
-expected number of mistakes the algorithm makes in these rounds is at least
-$\frac{K-1}{2}$. Altogether, the algorithm makes at least $\frac{K-1}{2} M$
-mistakes in expectation.
-
-Finally, since strong separability and norm condition hold with probability one,
-there exists a particular (i.e. deterministic) sequence of examples for which
-the algorithm makes at least $\frac{K-1}{2} M$ mistakes in expectation
-over its internal randomization.
-\end{proof}
-
-\section{From linear separability to strong linear separability}
-\label{section:from-linear-separability-to-strong-linear-separability}
-
-In this section, we show how to construct a mapping $\phi$ from the unit ball of
-$\R^d$ into a high dimensional inner product space that has the property that if
-a set of labeled examples in the unit ball is linearly separable with a margin
-$\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
-linearly separable with a margin $\gamma'$ and their norms are bounded by $R'$.
-The parameters $\gamma'$ and $R'$ are functions of the old margin $\gamma$ and
-the number of classes $K$, and the are specified in the theorems below.
-
-Equipped with the mapping $\phi$, we can utilize
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
-\autoref{theorem:strongly-separable-example-mistake-upper-bound} from the
-previous section and we obtain an algorithm for linearly separable examples and
-an upper bound on its number of mistakes. As a computational speed up, instead
-of working with the mapped examples $\phi(x_1), \phi(x_2), \dots$ explicitly, we
-can use the kernelized version of
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-that uses a kernel function $k(x,x') = \ip{\phi(x)}{\phi(x')}$.
-
-We construct several different mappings $\phi$. The mappings differ in the
-parameters $R'$, $\gamma'$, time complexity of evaluating $\phi(x)$, and time
-complexity of evaluating $k(x,x')$. Some of the mappings depend the original
-margin $\gamma$. In practice, the margin parameter $\gamma$ is not known, which
-makes these mappings impractical. However, one of the mappings we construct
-does \emph{not} depend on $\gamma$.
-
-The idea behind all the mappings is polynomial approximation. According to the
-well known Stone-Weierstrass theorem (see
-e.g.~\citep[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
-multivariate polynomials uniformly approximate any continuous function.
-Intuitively speaking, we use a multivariate polynomial to approximate, on the
-unit ball of $\R^d$, the indicator function corresponding to the intersection of
-$m=K-1$ halfspaces. Within margin $\gamma$ along the decision boundary, we allow
-the polynomial to attain arbitrary value. The polynomial separates examples in
-one class from examples in the other classes. To be able to quantify $R'$,
-$\gamma'$ and time complexities of evaluating $\phi(x)$ and $k(x,x')$, we need
-to quantify certain parameters of the approximating polynomial. We construct two
-different polynomials with different parameters. The parameters are quantified
-in
-Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
-stated below.
-
-Before we state the theorems, recall that a polynomial of $d$ variables is a
-function $p:\R^d \to \R$ of the form
-$$
-p(x) = p(x_1, x_2, \dots, x_d) = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-$$
-where the sum ranges over a finite set of $d$-tuples $(\alpha_1, \alpha_2,
-\dots, \alpha_d)$ of non-negative integers and $c_{\alpha_1, \alpha_2, \dots,
-\alpha_d}$ is a real coefficient. The \emph{degree} of a polynomial $p$, denoted
-by $\deg(p)$, is the largest value of $\alpha_1 + \alpha_2 + \dots + \alpha_d$
-for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is non-zero.
-The \emph{norm of a polynomial} $p$ is defined as
-$$
-\norm{p} = \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} \left(c_{\alpha_1, \alpha_2, \dots, \alpha_d} \right)^2 } \; .
-$$
-It is easy see that this is indeed a norm, since we can interpret it as a
-Euclidean norm of the vector of the coefficients of the polynomial.
-
-\begin{theorem}[Polynomial approximation of intersection of halfspaces I]
-\label{theorem:polynomial-approximation-1}
-Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
-\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$. There exists a
-multivariate polynomial $p:\R^d \to \R$ such that
-\begin{enumerate}
-\item $p(x) \ge 1/2$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-\item $p(x) \le -1/2$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-\item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$
-\item $\displaystyle \norm{p} \le \left( 188 \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil \right)^{\frac{1}{2} \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil}$
-\end{enumerate}
-\end{theorem}
-
-\begin{theorem}[Polynomial approximation of intersection of halfspaces II]
-\label{theorem:polynomial-approximation-2}
-Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
-\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$.
-Define
-$$
-r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1 \qquad \text{and} \qquad s = \left \lceil \log_2(1/\gamma) \right \rceil \; .
-$$
-Then, there exists a multivariate polynomial $p:\R^d \to \R$ such that
-\begin{enumerate}
-\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$
-for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-
-\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$
-for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-
-\item $\deg(p) \le (2s+1) rm$
-\item $\norm{p} \le (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm}$
-\end{enumerate}
-\end{theorem}
-
-The proofs of the theorems can be found in
-Section~\ref{section:proof-of-polynomial-approximation}. The geometric
-interpretation of the two regions described in parts 1 and 2 of the theorems is
-explained in Figure~\ref{figure:pizza-slice}. Similar but weaker results were
-proved by~\cite{Klivans-Servedio-2008}. In particular, the bounds in parts
-1, 2, 3, 4 of the theorems are independent of the dimension $d$.
-
-\begin{figure}
-\begin{center}
-\input{figures/pizza-slice}
-\end{center}
-\caption[]{The figure shows the two regions used in parts 1 and 2 of
-Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
-for the case $m=d=2$ and a particular choice of vectors $v_1, v_2$ and margin
-parameter $\gamma$. These regions are
-\begin{align*}
-R^+ & = \displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\} \; , \\
-R^- & = \displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\} \; .
-\end{align*}
-The separating hyperplanes $\ip{v_1}{x} = 0$ and $\ip{v_2}{x} = 0$ are shown as dashed lines.
-}
-\label{figure:pizza-slice}
-\end{figure}
-
-We construct the three different mappings $\phi_n, \psi_n, \rho$. The first two
-are parameterized by a non-negative integer $n$. The domain of $\phi_n$ and
-$\psi_n$ is $\R^d$. The domain of $\rho$ is the unit ball of $\R^d$. The
-co-domain for $\phi_n$ and $\psi_n$ is $\R^p$ where $p = \sum_{i=0}^n
-\binom{i+d-1}{d-1}$ equipped with the standard inner product $\ip{x}{x'} =
-\sum_{i=1}^p x_i x'_i$. The co-domain is the classical separable Hilbert space
-$\ell_2 = \{ x \in \R^\infty ~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped
-with the standard inner product $\ip{x}{x'} = \sum_{i=1}^\infty x_i x'_i$. We
-index the coordinates of the co-domain $\R^p$ by $d$-tuples $(\alpha_1,
-\alpha_2, \dots, \alpha_d)$ of non-negative integers such that $\alpha_1 +
-\alpha_2 + \dots + \alpha_d \le n$. Similarly, we index the coordinates of
-$\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
-integers. The mappings are defined by
-\begin{align*}
-\left(\phi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-\\
-\left(\psi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = \sqrt{\binom{n}{\alpha_1 + \alpha_2 + \dots + \alpha_d} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-\\
-\left(\rho(x)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-\end{align*}
-where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
-is the multinomial coefficient and $\binom{n}{k} = \frac{n!}{(n-k)!k!}$ is the binomial coefficient.
-
-Mappings $\psi_n$ and $\rho$ have simple-to-compute kernels
-\begin{align*}
-K_{\psi_n}(x,x') & = \ip{\psi_n(x)}{\psi_n(x')}_{\R^p} = \left( 1 + \ip{x}{x'} \right)^n \; , \\
-K_{\rho}(x,x') & = \ip{\rho(x)}{\rho(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}} \; .
-\end{align*}
-In passing we note that the formula for $K_\rho$ implies the mapping $\rho$ is
-well defined. Indeed, since $K_{\rho}(x,x) < +\infty$ for any $x$ in the unit
-ball of $\R^d$, it means that $\rho(x)$ indeed lies in $\ell_2$.
-
-TODO
-
-\section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
-\label{section:proof-of-polynomial-approximation}
-
-For the proofs of the theorems we need several auxiliary results.
-
-\begin{lemma}[Simple inequality]
-\label{lemma:simple-inequality}
-For any real numbers $b_1, b_2, \dots, b_n$,
-$$
-\left( \sum_{i=1}^n b_i \right)^2 \le n \sum_{i=1}^n b_i^2 \; .
-$$
-\end{lemma}
-
-\begin{proof}
-The lemma follows from Cauchy-Schwartz inequality applied to
-vectors $(b_1, b_2, \dots, b_n)$ and $(1,1,\dots,1)$.
-\end{proof}
-
-\begin{lemma}[Bound on binomial coefficients]
-\label{lemma:binomial-bound}
-For any integers $n,k$ such that $n \ge k \ge 0$,
-$$
-\binom{n}{k} \le (n - k + 1)^k \; .
-$$
-\end{lemma}
-
-\begin{proof}
-If $k = 0$, the inequality trivially holds. For the rest of the proof we can
-assume $k \ge 1$. We write the binomial coefficient as
-$$
-\binom{n}{k}
-= \frac{n(n-1)\cdots(n-k+1)}{k(k-1) \cdots 1}
-= \frac{n}{k} \cdot \frac{n-1}{k - 1} \cdots \frac{n-k+1}{1} \; .
-$$
-We claim that
-$$
-\frac{n}{k} \le \frac{n-1}{k - 1} \le \cdots \le \frac{n-k+1}{1}
-$$
-from which the lemma follows by upper bounding all the fractions by $n-k+1$.
-It remains to prove that for any $j=0,1,\dots,k-1$,
-$$
-\frac{n - j + 1}{k - j + 1} \le \frac{n - j}{k - j} \; .
-$$
-Multiplying by the (positive) denominators, we get an equivalent inequality
-$$
-(n - j + 1)(k - j) \le (n - j)(k - j + 1) \; .
-$$
-Cancelling common terms leads to an equivalent inequality
-$$
-k - j \le n - j \; ,
-$$
-which holds by the assumption on $n \ge k$.
-\end{proof}
-
-\begin{lemma}[Properties of the norm of polynomials]
-\label{lemma:properties-of-norm-of-polynomials}
-\hspace{1cm} % Dummy space
-\begin{enumerate}
-\item Let $p_1, p_2, \dots, p_n$ be multivariate polynomials and let $p(x) =
-\prod_{j=1}^n p_j(x)$ be their product.  Then, $\norm{p}^2 \le n^{\sum_{j=1}^n
-\deg(p_j)} \prod_{j=1}^n \norm{p_j}^2$.
-
-\item Let $q$ be a multivariate polynomial of degree at most $s$ and let $p(x) =
-(q(x))^n$. Then, $\norm{p}^2 \le n^{ns} \norm{q}^{2n}$.
-
-\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then,
-$\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-Using multi-index notation we can write any multivariate polynomial $p$ as
-$$
-p(x) = \sum_A c_A x^A
-$$
-where $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ is a multi-index (i.e. a $d$-tuple of
-non-negative integers), $x^A = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}$ is a
-monomial and $c_A = c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is the corresponding real
-coefficient. The sum is over a finite subset of $d$-tuples of non-negative
-integers. Using this notation, the norm of a polynomial $p$ can be written as
-$$
-\norm{p} = \sqrt{\sum_A (c_A)^2} \; .
-$$
-For a multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ we define its
-$1$-norm as $\norm{A}_1 = \alpha_1 + \alpha_2 + \dots + \alpha_d$.
-
-To prove the part 1, we express $p_j$ as
-$$
-p_j(x) = \sum_{A_j} c^{(j)}_{A_j} x^{A_j} \; .
-$$
-Since $p(x) = \prod_{i=1}^n p_j(x)$, the coefficients of its expansion $p(x) =
-\sum_A c_A x^A$ are
-$$
-c_A = \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \; .
-$$
-Therefore,
-\begin{multline*}
-\norm{p}^2
-= \sum_{A} (c_A)^2
-= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \right)^2
-= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\end{multline*}
-and
-\begin{multline*}
-\prod_{i=1}^n \norm{p_i}^2
-= \prod_{i=1}^n \left( \sum_{A_i} (c^{(i)}_{A_i})^2 \right)
-= \sum_{(A_1, A_2, \dots, A_n)} \prod_{j=1}^n (c^{(j)}_{A_j})^2
-= \sum_{(A_1, A_2, \dots, A_n)} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
-= \sum_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\end{multline*}
-where in both cases the outer sum is over multi-indices $A$ such that $\norm{A}_1 \le \deg(p)$.
-\autoref{lemma:simple-inequality} implies that for any multi-index $A$,
-$$
-\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\le M_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
-$$
-where $M_A$ is the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 +
-A_2 + \dots + A_n = A$.
-
-To finish the proof, it is sufficient to prove that $M_A \le n^{\deg(p)}$ for
-any $A$ such that $\norm{A}_1 \le \deg(p)$. To prove this inequality, consider a
-multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ and consider its $i$-th coordinate
-$\alpha_i$. In order for $A_1 + A_2 + \dots + A_n = A$ to hold, the $i$-th
-coordinates of $A_1, A_2, \dots, A_n$ need to sum to $\alpha_i$. There are exactly
-$\binom{\alpha_i + n - 1}{\alpha_i}$ possibilities for the choice of $i$-th
-coordinates of $A_1, A_2, \dots, A_n$. The total number of choices is thus
-$$
-M_A = \prod_{i=1}^d \binom{\alpha_i + n - 1}{\alpha_i} \; .
-$$
-Using \autoref{lemma:binomial-bound}, we upper bound it as
-$$
-M_A \le \prod_{i=1}^d n^{\alpha_i} = n^{\norm{A}_1} \le n^{\deg(p)} \; .
-$$
-
-Part 2 follows from the part 1 by setting $p_1 = p_2 = \dots p_n = q$.
-
-To prove the part 3, we use generalized triangle inequality and
-\autoref{lemma:simple-inequality}. We have
-\begin{align*}
-\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
-\end{align*}
-\end{proof}
-
-\subsection{Proof of \autoref{theorem:polynomial-approximation-1}}
-\label{section:proof-of-polynomial-approximation-1}
-
-To construct the polynomial $p$ we use Chebyshev polynomials of the first kind.
-Chebyshev polynomials of the fist kind form an infinite sequence of polynomials
-$T_0(z), T_1(z), T_2(z), \dots$ of single real variable $z$. They are defined
-by the recurrence
-\begin{align*}
-T_0(z) & = 1 \; , \\
-T_1(z) & = z \; , \\
-T_{n+1}(z) & = 2zT_n(z) - T_{n-1}(z) & \text{for $n \ge 1$.}
-\end{align*}
-Chebyshev polynomials have a lot of interesting properties.
-We will need properties listed in
-\autoref{proposition:properties-of-chebyshev-polynomials} below.
-Interested reader can learn more about Chebyshev polynomials
-from the book by \cite{Mason-Handscomb-2002}.
-
-\begin{proposition}[Properties of Chebyshev polynomials]
-\label{proposition:properties-of-chebyshev-polynomials}
-Chebyshev polynomials satisfy
-\begin{enumerate}
-\item $\deg(T_n) = n$ for all $n \ge 0$.
-\item If $n \ge 1$, the leading coefficient of $T_n(z)$ is $2^{n-1}$.
-\item $T_n(\cos(\theta)) = \cos(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
-\item $T_n(\cosh(\theta)) = \cosh(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
-\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$ and all $n \ge 0$.
-\item $T_n(z) \ge 1 + n^2(z - 1)$ for all $z \ge 1$ and all $n \ge 0$.
-\item $\norm{T_n} \le (1+\sqrt{2})^n$ for all $n \ge 0$
-\end{enumerate}
-\end{proposition}
-
-\begin{proof}[Proof of \autoref{proposition:properties-of-chebyshev-polynomials}]
-The first two properties can be easily proven by induction on $n$ using the recurrence.
-
-We prove third property by induction on $n$. Indeed, by definition
-$$
-T_0(\cos(\theta)) = 1 = \cos(0 \theta) \qquad \text{and} \qquad T_1(\cos(\theta)) = \cos(\theta) \; .
-$$
-For $n \ge 1$, we have
-\begin{align*}
-T_{n+1}(\cos(\theta))
-& = 2 \cos(\theta) T_n(\cos(\theta)) - T_{n-1}(\cos(\theta)) \\
-& = 2 \cos(\theta) \cos(n \theta) - \cos((n-1)\theta)) \; ,
-\end{align*}
-where the last step follow by induction hypothesis.
-It remains to show that the last expression equals $\cos((n+1)\theta)$.
-This can be derived from the trigonometric formula
-$$
-\cos(\alpha \pm \beta) = \cos(\alpha) \cos(\beta) \mp \sin(\alpha) \sin(\beta) \; .
-$$
-By substituting $\alpha = n \theta$ and $\beta = \theta$, we get two equations
-\begin{align*}
-\cos((n+1) \theta) & = \cos(n \theta) \cos(\theta) - \sin(n \theta) \sin(\theta) \; , \\
-\cos((n-1) \theta) & = \cos(n \theta) \cos(\theta) + \sin(n \theta) \sin(\theta) \; .
-\end{align*}
-Summing them yields
-$$
-\cos((n+1)\theta) + \cos((n-1) \theta) = 2 \cos(n \theta) \cos(\theta)
-$$
-which finishes the proof.
-
-Fourth property has the similar proof as third property. It suffices
-to replace $\cos$ and $\sin$ with $\cosh$ and $\sinh$ respectively.
-
-Fifth property follows from the third property. Indeed, for any $z \in [-1,1]$
-there exists $\theta \in \R$ such that $\cos \theta = z$. Thus, $|T_n(z)| =
-|T_n(\cos(\theta))| = |\cos(n\theta)| \le 1$.
-
-The sixth property is equivalent to
-$$
-T_n(\cosh(\theta)) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$,}
-$$
-since $\cosh(\theta) = \frac{e^{\theta} + e^{-\theta}}{2}$ is an even continuous
-function that maps $\R$ onto $[1,+\infty)$, is strictly decreasing on
-$(-\infty,0]$, and is strictly increasing on $[0,\infty)$. Using the fourth
-property the last inequality is equivalent to
-$$
-\cosh(n \theta) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$.}
-$$
-For $\theta = 0$, both sides are equal to $1$. Thus, it is sufficient to prove
-that the derivative of the left hand side is greater or equal to the derivative
-of the right hand side. Recalling that $[\cosh(\theta)]' = \sinh(\theta)$, this
-means that we need to show that
-$$
-\sinh(n \theta) \ge n \sinh(\theta) \qquad \text{for all $\theta \ge 0$.}
-$$
-Tho prove this inequality we use the summation formula
-$$
-\sinh(\alpha + \beta) = \sinh(\alpha) \cosh(\beta) + \sinh(\beta) \cosh(\beta) \; .
-$$
-If $\alpha, \beta$ are non-negative then $\sinh(\alpha), \sinh(\beta)$ are
-non-negative and $\cosh(\alpha), \cosh(\beta) \ge 1$. Hence,
-$$
-\sinh(\alpha + \beta) \ge \sinh(\alpha) + \sinh(\beta) \qquad \text{for any $\alpha, \beta \ge 0$.}
-$$
-This implies that (using induction on $n$) that $\sinh(n \theta) \ge n
-\sinh(\theta)$ for all $\theta \ge 0$.
-
-We verify the seventh property by induction on $n$.
-For $n=0$ and $n=1$ the inequality trivially holds, since $\norm{T_0} = \norm{T_1} = 1$.
-For $n \ge 1$, since $T_{n+1}(z) = 2zT_n(z) - T_{n-1}(z)$,
-\begin{align*}
-\norm{T_{n+1}}
-& \le 2 \norm{T_n} + \norm{T_{n-1}} \\
-& \le 2 (1 + \sqrt{2})^n + (1 + \sqrt{2})^{n-1} \\
-& = (1 + \sqrt{2})^{n-1} (2 (1 + \sqrt{2}) + 1) \\
-& = (1 + \sqrt{2})^{n-1} (3 + 2\sqrt{2}) \\
-& = (1 + \sqrt{2})^{n-1} (1 + \sqrt{2})^2 \\
-& = (1 + \sqrt{2})^{n+1} \; .
-\end{align*}
-
-\end{proof}
-
-Let $r = \left\lceil \log_2(2m) \right\rceil$ and $s = \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$.
-We define the polynomial $p:\R^d \to \R$ as
-$$
-p(x) = m + \frac{1}{2} - \sum_{i=1}^m \left( T_s(1 - \ip{v_i}{x}) \right)^r \; .
-$$
-It remains to show that $p$ has properties 1--5.
-
-To verify the first property notice that if $x \in \R^d$ satisfies $\norm{x} \le
-1$ and $\ip{v_i}{x} \ge \gamma$ then since $\norm{v_i} \le 1$ we have
-$\ip{v_i}{x} \in [0,1]$. Thus, $T_s(1 - \ip{v_i}{x})$ and $\left( T_s(1 -
-\ip{v_i}{x}) \right)^r$ lie in the interval $[-1,1]$. Therefore,
-$$
-p(x) \ge m + \frac{1}{2} - m \ge \frac{1}{2} \; .
-$$
-
-To verify the second property consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d
-~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Clearly, $\norm{x} \le 1$
-and there exists at least one $i \in \{1,2,\dots,m\}$ such that $\ip{v_i}{x} \le
-- \gamma$. Therefore, $1 - \ip{v_i}{x} \ge 1 + \gamma$ and~\autoref{proposition:properties-of-chebyshev-polynomials} (part 6)
-imply that
-$$
-T_s(1 - \ip{v_i}{x}) \ge 1 + s^2 \gamma \ge 2
-$$
-and thus
-$$
-\left( T_s(1 - \ip{v_i}{x}) \right)^r \ge 2^r \ge 2m \; .
-$$
-On the other hand for any $j \in \{1,2,\dots,m\}$, we have $\ip{v_j}{x} \in
-[-1,1]$ and thus $1 - \ip{v_j}{x}$ lies in the interval $[0,2]$. According to
-\autoref{proposition:properties-of-chebyshev-polynomials} (parts 5 and 6), $T_s(1 - \ip{v_j}{x})
-\ge -1$. Therefore,
-$$
-p(x) = m + \frac{1}{2} - \left( T_s(1 - \ip{v_i}{x}) \right)^r - \sum_{\substack{j ~:~  1 \le j \le m \\ j \neq i}} \le m + \frac{1}{2} - 2m + (m - 1) \le - \frac{1}{2} \; .
-$$
-
-The third property follows from observation that degree of $p$
-is the same as the degree of any one of the terms
-$\left( T_s(1 - \ip{v_i}{x}) \right)^r$ which is $r \cdot s$.
-
-To prove the fourth property, we need to upper bound the norm of $p$.
-Let $f_i(x) = 1 - \ip{v_i}{x}$, let $g_i(x) = T_s(1 - \ip{v_i}{x})$
-and let $h_i(x) = (T_s(1 - \ip{v_i}{x}))^r$. We have
-$$
-\norm{f_i}^2 = 1 + \norm{v_i}^2 \le 1 + 1 = 2 \; .
-$$
-Let $T_s(z) = \sum_{j=0}^s c_j z^j$ be the expansion of $s$-th Chebyshev polynomial.
-Then,
-\begingroup
-\allowdisplaybreaks
-\begin{align*}
-\norm{g_i}^2
-& = \norm{ \sum_{j=0}^s c_j (f_i)^j }^2 \\
-& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 & \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
-& = (s + 1) \sum_{j=0}^s (c_j)^2 \norm{(f_i)^j}^2 \\
-& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} & \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
-& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j 2^{2j} \\
-& \le (s + 1) s^s 2^{2s} \sum_{j=0}^s (c_j)^2 \\
-& = (s + 1) s^s 2^{2s} \norm{T_s}^2 \\
-& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} & \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
-& = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
-& \le \left(8(1+\sqrt{2})^2 s \right)^s & \text{(since $s+1 \le 2^s$ for any integer $s \ge 0$)} \\
-& \le \left(47 s \right)^s \; .
-\end{align*}
-\endgroup
-Finally,
-\begin{align*}
-\norm{p}
-& \le m + \frac{1}{2} + \sum_{i=1}^m \norm{(g_i)^r} \\
-& = m + \frac{1}{2} + \sum_{i=1}^m \sqrt{\norm{(g_i)^r}^2} \\
-& \le m + \frac{1}{2} + \sum_{i=1}^m \sqrt{r^{rs} \norm{g_i}^{2r}} \\
-& \le m + \frac{1}{2} + m r^{rs/2} \left(47 s \right)^{rs/2} \\
-& = m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \; .
-\end{align*}
-We can further upper bound the last expression by using that $m \le \frac{1}{2} 2^r$.
-Since $r,s \ge 1$,
-\begin{align*}
-\norm{p}
-& \le m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \\
-& \le \frac{1}{2} 2^r + \frac{1}{2} + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
-& \le 2^r + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
-& = 2^r \left(1 + \frac{1}{2} \left(47 rs \right)^{rs/2} \right) \\
-& = 2^r \left(47 rs \right)^{rs/2} \\
-& \le 4^{rs/2} \left(47 rs \right)^{rs/2} \\
-& \le \left(188 rs \right)^{rs/2} \; .
-\end{align*}
-Substituting for $r$ and $s$ finishes the proof.
-
-\subsection{Proof of \autoref{theorem:polynomial-approximation-2}}
-\label{section:proof-of-polynomial-approximation-2}
-
-We define several univariate polynomials
-\begin{align*}
-P_n(z) & = (z - 1) \prod_{i=1}^n (z - 2^i)^2 && \text{for $n \ge 0$,} \\
-A_{n,k}(z) & = (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$,} \\
-B_{n,k}(z) & = - (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$.}
-\end{align*}
-We define the polynomial $p:\R^d \to \R$ as
-$$
-p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
-- \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-$$
-
-For convenience we define univariate rational function
-\begin{align*}
-S_{n,k}(z) & = \frac{A_{n,k}(z)}{B_{n,k}(z)} && \text{for $n,k \ge 0$,}
-\end{align*}
-and a multivariate rational function
-$$
-Q(x) = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \; .
-$$
-It easy to verify that
-$$
-p(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-$$
-
-\begin{lemma}[Properties of $P_n$]
-\label{lemma:properties-of-p-n}
-\hspace{1cm} % Dummy space
-\begin{enumerate}
-\item If $z \in [0,1]$ then $P_n(-z) \le P_n(z) \le 0$.
-\item If $z \in [1,2^n]$ then $0 \le 4P_n(z) \le -P_n(-z)$.
-\item If $z \ge 0$ then $-P_n(-z) \ge 2^{n(n+1)}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-To prove the first part, note that $P_n(z)$ and $P_n(-z)$ are non-positive for
-$z \in [0,1]$. We can write $\frac{P_n(z)}{P_n(-z)}$ as a product of $n+1$
-non-negative fractions
-$$
-\frac{P_n(z)}{P_n(-z)} = \frac{1-z}{1+z} \prod_{i=1}^n \frac{(z+2^i)^2}{(z-2^i)^2} \; .
-$$
-The first part follows from the observation that each fraction is upper bounded
-by $1$.
-
-To prove the second part, notice that $P_n(z)$ is non-negative and $P_n(-z)$ is
-non-positive for any $z \in [1,2^n]$. Now, fix $z \in [1,2^n]$ and let $j \in
-\{1,2,\dots,n\}$ be such that $2^{j-1} \le z \le 2^j$. This implies that
-$(z+2^{j})^2 \ge 4 (z - 2^j)^2$. We can write $\frac{P_n(z)}{-P_n(-z)}$ as a
-product of $n+1$ non-negative fractions
-$$
-\frac{P_n(z)}{-P_n(-z)}
-= \frac{z-1}{z+1} \cdot \frac{(z-2^j)^2}{(z+2^j)^2} \prod_{\substack{i ~:~ 1 \le i \le n \\ i \neq j}} \frac{(z-2^i)^2}{(z+2^i)^2} \; .
-$$
-The second part follows from the observation that the second fraction is upper
-bounded by $1/4$ and all other fractions are upper bounded by $1$.
-
-The third part follows from
-$$
--P_n(-z) = (1+z) \prod_{i=1}^n (z+2^i)^2 \ge \prod_{i=1}^n 2^{2i} = 2^{n(n+1)} \; .
-$$
-\end{proof}
-
-\begin{lemma}[Properties of $S_{n,r}$ and $B_{n,r}$]
-\label{lemma:properties-of-s-n-r}
-Let $n,m$ be non-negative integers.
-Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$. Then,
-\begin{enumerate}
-\item If $z \in [1,2^n]$ then $S_{n,r}(z) \in [1,1+\frac{1}{2m}]$.
-\item If $z \in [-2^n, -1]$ then $S_{n,r} \in [-1-\frac{1}{2m}, -1]$.
-\item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
-\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-Note that $B_{n,r}(z)$ is an even function and $A_{n,r}(z)$ is an odd function.
-Therefore, $S_{n,r}(z)$ is odd. Also notice that $r$ is an odd integer.
-
-\begin{enumerate}
-\item Observe that $S_{n,r}(z)$ can be written as
-$$
-S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. Since
-$r \ge \frac{1}{2} \log_2(4m+1)$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
-$S_{n,r}(z) = \frac{1+c}{1-c} \in [1,1 + \frac{1}{2m}]$.
-
-\item Since $S_{n,r}(z)$ is odd, the statement follows from part 1.
-
-\item Observe that $S_{n,r}(z)$ can be written as
-$$
-S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. If $z \in [0,1]$, by part
-1 of~\autoref{lemma:properties-of-p-n} and the fact that $r$ is odd, $c
-\in [-1,0]$, and thus, $S_{n,r}(z) = \frac{1+c}{1-c} \in [0,1]$. Since
-$S_{n,r}(z)$ is odd, for $z \in [-1,0]$, $S_{n,r}(z) \in [-1,0]$.
-
-\item Since $B_{n,r}(z)$ is even, we can without loss generality assume that $z \ge
-0$. We consider two cases.
-
-Case $z \in [0,1]$. Since $r$ is odd and $P_n(z)$ is non-positive,
-$$
-B_{n,r}(z) = - (P_n(z))^r + \left(- P_{n}(-z)\right)^r \ge \left(- P_{n}(-z)\right)^r \ge 2^{n(n+1)r} \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
-where the second last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
-
-Case $z \in [1,2^n]$. Since $r$ is odd,
-$$
-B_{n,r}(z) = \left(- P_{n}(-z)\right)^r \left(1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r \right) = \left(- P_{n}(-z)\right)^r (1 - c)
-$$
-where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
-part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. By
-the definition of $r$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
-$$
-B_{n,r}(z) \ge \left(- P_{n}(-z)\right)^r \left( 1 - \frac{1}{4m+1} \right) \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
-where the last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
-\end{enumerate}
-\end{proof}
-
-\begin{lemma}[Properties of $Q(x)$]
-\label{lemma:properties-of-q}
-The rational function $Q(x)$ satisfies
-\begin{enumerate}
-\item $Q(x) \ge \frac{1}{2}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
-\item $Q(x) \le -\frac{1}{2}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-To prove part 1, consider any $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \
-\ip{v_i}{x} \ge \gamma \right\}$. Then, $\frac{\ip{v_i}{x}}{\gamma} \in [1,
-\frac{1}{\gamma}]$. By part 1 of \autoref{lemma:properties-of-s-n-r},
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \in [1, 1 + \frac{1}{2m}]$ and
-in particular $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \ge 1$. Thus,
-$$
-Q(x) = \left( \sum_{i=1}^m S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \right) - (m - 1/2) \ge m - (m - 1/2) = 1/2 \; .
-$$
-
-To prove part 2, consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~
-\norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Observe that
-$\frac{\ip{v_i}{x}}{\gamma} \in [-\frac{1}{\gamma}, \frac{1}{\gamma}]$. Consider
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right)$ for any $i \in
-\{1,2,\dots,m\}$. Parts 1,2, and 3 of \autoref{lemma:properties-of-s-n-r}
-and the fact $1/\gamma \le 2^s$ imply that
-$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \le 1 +
-\frac{1}{2m}$ for all $i \in \{1,2,\dots,m\}$. By the choice of $x$, there
-exists $j \in \{1,2,\dots,m\}$ such that $\ip{v_j}{x} \le - \gamma$. Part 2 of
-\autoref{lemma:properties-of-s-n-r} implies that
-$S_{s,r}\left(\frac{\ip{v_j}{x}}{\gamma}\right) \in [-1-\frac{1}{2m},-1]$. Thus,
-\begin{align*}
-Q(x)
-& = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& = S_{s,r}\left( \frac{\ip{v_j}{x}}{\gamma} \right) + \left( \sum_{\substack{i ~:~ 1 \le i \le m \\ i \neq j}} S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& \le -1 + (m-1) \left( 1 + \frac{1}{2m} \right) - \left(m - \frac{1}{2} \right) \\
-& \le 1/2 \; .
-\end{align*}
-\end{proof}
-
-To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-2} first
-note that part 4 of \autoref{lemma:properties-of-s-n-r} implies that for any $x$
-such that $\norm{x} \le 1$, $B_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right)$
-is positive. Thus $p(x)$ and $Q(x)$ have the same sign on the unit ball.
-Consider any $x$ in either
-$\displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-or in
-$\displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
-\autoref{lemma:properties-of-q} states that $|Q(x)| \ge 1/2$ and the sign
-depends on which of the two sets $x$ lies in. Since signs of $Q(x)$ and $p(x)$
-are the same, it remains to show that $|p(x)| \ge m^{s^2m/2}$. Indeed,
-\begin{align*}
-|p(x)|
-& = |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
-& \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
-& \ge \frac{1}{2} |Q(x)| \cdot 2^{s(s+1)rm} && \text{(since $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4} \ge 1/2$)} \\
-& \ge \frac{1}{4} \cdot 2^{s(s+1)rm} && \text{(\autoref{lemma:properties-of-q})} \; .
-\end{align*}
-
-To prove part 3 of \autoref{theorem:polynomial-approximation-2} note that
-$\deg(P_s) = 2s+1$. Thus, $\deg(A_{s,r})$ and $\deg(B_{s,r})$ are at most
-$(2s+1)r$. Therefore, $\deg(p) \le (2s+1) rm$.
-
-It remains to prove part 4 of \autoref{theorem:polynomial-approximation-2}.
-For any $i \in \{0,1,2,\dots,s\}$ and any $v \in \R^d$ such that $\norm{v} \le 1$
-define multivariate polynomials
-\begin{align*}
-f_{i,v}(x) & = \frac{\ip{v}{x}}{\gamma} - 2^i \; , \\
-q_v(x) & = P_s \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
-a_v(x) & = A_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
-b_v(x) & = B_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; .
-\end{align*}
-Note that
-$$
-p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
-$$
-We bound the norms of these polynomials. We have
-$$
-\norm{f_{i,v}}^2 = \norm{v}^2/\gamma^2 + 2^{2i} \le 2 \cdot 2^s \; .
-$$
-where we used that $1/\gamma \le 2^s$ and $\norm{v} \le 1$.
-Since $q_v(x) = f_{i,v}(\frac{\ip{v}{x}}{\gamma}) \prod_{i=1}^s \left(f_{i,v}(\frac{\ip{v}{x}})\right)^2$,
-using part 1 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $q_v$
-as
-$$
-\norm{q_v}^2 \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \le  (2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \; .
-$$
-Using parts 3 and 2 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $a_v$ as
-\begin{align*}
-\norm{a_v}^2
-& \le 2\norm{(q_v)^r}^2 + 2\norm{(q_{-v})^r}^2 \\
-& \le 2 r^{r(2s+1)} \norm{q_v}^{2r} + 2 r^{r(2s+1)} \norm{q_{-v}}^{2r} \\
-& \le 4 r^{r(2s+1)} \left((2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \right)^{2r} \\
-& = 4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \; .
-\end{align*}
-The same upper bound holds for $\norm{b_v}^2$. Finally,
-\begin{align*}
-\norm{p}
-& \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
-& \le \left[ \sum_{i=1}^m m^{(s+1/2)rm} \norm{a_{v_i}} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} \norm{b_{v_j}} \right] + \left(m - \frac{1}{2} \right) m^{(s+1/2)rm} \prod_{j=1}^m \norm{b_{v_j}} \\
-& \le (2m-1/2) m^{(s+1/2)rm} \left(4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \right)^{m/2} \\
-& = (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm} \; .
-\end{align*}
-
-\section{Nearest neighbor algorithm}
-
-TODO
-
-\section{NP-hardness of the weak labeling problem}
-
-Any algorithm for the bandit setting collects information in the form of so
-called \emph{strongly labeled} and \emph{weakly labeled} examples.
-Strongly-labeled examples are those for which we know the class label. Weakly
-labeled example is an example for which we know that class label can be anything
-except for a particular one class.
-
-A natural strategy for each round is to find vectors $w_1, w_2, \dots, w_K$ that
-linearly separate the examples seen in the previous rounds and use the vectors
-to predict the label in the next round. More precisely, we want to find both the
-vectors $w_1, w_2, \dots, w_K$ and label for each example consistent with its
-weak and/or strong labels such that $w_1, w_2, \dots, w_K$ linearly separate the
-labeled examples. We show this problem is NP-hard even for $K=3$.
-
-Clearly, the problem is at least as hard as the decision version of the problem
-where the goal is to determine if such vectors and labeling exist. We show that
-this problem is NP-complete.
-
-Formally, the input to the decision problem are positive integers $d, T, K$ and
-a sequence $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \{0,1\}^d \times
-\{1,2,\dots,K, \overline{1}, \overline{2}, \dots, \overline{K}\}$ of strongly
-and weakly labeled examples. The numbers $1,2,\dots,K$ correspond to strong
-labels and the symbols $\overline{1}, \overline{2}, \dots, \overline{K}$
-correspond to weak labels. We adopt the convention that $\overline{\overline{i}}
-= i$ for any positive integer $i$. The goal is to determine whether or not there
-exist vectors $w_1, w_2, \dots, w_K \in \R^d$ that satisfy the following
-conditions for all $t=1,2,\dots,T$,
-\begin{align*}
-y_t \in \{1,2,\dots,K\} \qquad & \Longrightarrow \qquad & \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \qquad \ip{w_{y_t}}{x_t} & > \ip{w_i}{x_t} \; , \\
-y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \qquad & \Longrightarrow & \qquad \exists i \in \{1,2,\dots,K\} \qquad \ip{w_i}{x_t} & > \ip{w_{\overline{y_t}}}{x_t} \; .
-\end{align*}
-
-TODO
-
-\section{Mistake lower bound for ignorant algorithms}
-
-TODO
+\input{mistake-lower-bound-for-ignorant-algorithms}
 
@@
 
-\section{Multiclass Perceptron}
-\label{section:multiclass-perceptron-proofs}
-
-\textsc{Multiclass Perceptron} is an algorithm for \textsc{Online Multiclass
-Classification}. Both the protocol for the problem and the algorithm are stated
-below. The algorithm assumes that the feature vectors come from an inner product
-space $(V, \ip{\cdot}{\cdot})$.
-
-Two results are folklore. The first result is
-\autoref{theorem:mutliclass-perceptron-mistake-upper-bound} which states that if
-examples are linearly separable with margin $\gamma$ and examples have norm
-at most $R$ then the algorithm makes at most $\lfloor 2 (R/\gamma)^2 \rfloor$
-mistakes. The second result is
-\autoref{theorem:online-multiclass-classification-mistake-lower-bound} which
-states that under the same assumptions as in
-\autoref{theorem:online-multiclass-classification-mistake-lower-bound}
-\emph{any} deterministic algorithm for \textsc{Online Multiclass Classification}
-must make at least $\lfloor (R/\gamma)^2 \rfloor$ mistakes in the worst case.
-
-\begin{algorithm}[h]
-\caption{\textsc{Online Multiclass Classification}
-\label{algorithm:mutliclass-classification}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$}
-\STATE{Predict $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[h]
-\caption{\textsc{Multiclass Perceptron}
-\label{algorithm:mutliclass-perceptron}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
-\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t \in V$}
-\STATE{Predict $\widehat y_t = \argmax_{i \in \{1,2,\dots,K\}} \ip{w_t^{(i)}}{x_t}$}
-\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
-\IF{$\widehat y_t \neq y_t$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}$}
-\STATE{Update $w_{y_t}^{(t+1)} = w_{y_t}^{(t)} + x_t$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ENDIF
-\ENDFOR
-}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{theorem}[Mistake upper bound]
-\label{theorem:mutliclass-perceptron-mistake-upper-bound}
-Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
-integer, let $\gamma$ be a positive real number and let $R$ be a non-negative real
-number. If $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled
-examples in $V \times \{1,2,\dots,K\}$ that are linearly separable with margin
-$\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
-then \textsc{Multiclass Perceptron} algorithm makes at most $\lfloor
-2(R/\gamma)^2 \rfloor$ mistakes.
-\end{theorem}
-
-\begin{proof}
-Let $M = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$ be the number of
-mistakes the algorithm makes. Since the $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots,
-w_K^{(t)})$ changes only if a mistake is made, we can upper bound $\sum_{i=1}^K
-\norm{w_i^{(t)}}^2$ in terms of number of mistakes.
-If a mistake happens in round $t$ then
-\begin{align*}
-\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
-& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) + \norm{w_{y_t}^{(t)} + x_t}^2 + \norm{w_{\widehat y_t}^{(t)} - x_t}^2 \\
-& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) + \norm{w_{y_t}^{(t)}}^2 + \norm{w_{\widehat y_t}^{(t)}}^2 + 2 \norm{x_t}^2 + 2 \ip{w_{y_t}^{(t)} - w_{\widehat y_t}^{(t)}}{x_t} \\
-& = \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 \norm{x_t}^2 + 2 \ip{w_{y_t}^{(t)} - w_{\widehat y_t}^{(t)}}{x_t} \\
-& \le \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 \norm{x_t}^2 \\
-& \le \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 R^2 \; .
-\end{align*}
-So each time a mistake happens, $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ increases by at most $2R^2$. Thus,
-$$
-\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le 2R^2 M \; .
-$$
-Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors satisfying the
-\eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2}. We lower bound $\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$. This quantity changes
-only when a mistakes happens. If mistake happens in round $t$, we have
-\begin{align*}
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(t+1)}}
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^*}{w_{y_t}^{(t)} + x_t} + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} - x_t} \\
-& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^* - w_{\widehat y_t}^*}{x_t} \\
-& \ge  \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \gamma \; .
-\end{align*}
-Thus, after $M$ mistakes,
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma M \; .
-$$
-We upper bound the left hand side by using Cauchy-Schwartz inequality twice and
-the condition \eqref{equation:linear-separability-1} on $w_1^*, w_2^*, \dots,
-w_K^*$. We have
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
-\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
-$$
-Combining all inequalities, we get
-$$
-(\gamma M)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le 2R^2 M \; .
-$$
-We conclude that $M \le 2(R/\gamma)^2$. Since $M$ is an integer, $M \le \lfloor 2(R/\gamma)^2 \rfloor$.
-\end{proof}
-
-\begin{theorem}[Mistake lower bound]
-\label{theorem:online-multiclass-classification-mistake-lower-bound}
-Let $K$ be a positive integer, let $\gamma$ be a positive real number and let
-$R$ be a non-negative real number. For any deterministic algorithm for the
-\textsc{Online Multiclass Classification} problem there exists an
-inner product space $(V, \ip{\cdot}{\cdot})$, a non-negative integer $T$ and a
-sequence of labeled examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$
-examples in $V \times \{1,2,\dots,K\}$ that are linearly separable with margin
-$\gamma$, the norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
-and the algorithm makes at least $\lfloor (R/\gamma)^2 \rfloor$ mistakes.
-\end{theorem}
-
-\begin{proof}
-Let $T = \lfloor (R/\gamma)^2 \rfloor$ and let $x_1, x_2, \dots, x_T$ be the
-orthogonal vectors such that $\norm{x_t} = R$ for all $t=1,2,\dots,T$. For
-example, we can take $V = \R^T$ and $x_t = R e_t$ where $e_t$ is $t$-th element
-of the standard orthonormal basis of $\R^T$.
-
-Since the algorithm is deterministic, we can construct the sequence of labels
-$y_1, y_2, \dots, y_T$ adaptively based on the predictions $\widehat y_1,
-\widehat y_2, \dots, \widehat y_T$ of the algorithm. We define $y_t$ to be any
-element of $\{1,2,\dots,K\}$ not equal to $\widehat y_t$. This way the algorithm
-makes a mistake in every round $t=1,2,\dots,T$.
-
-It remains to show that the examples we have constructed are linearly separable
-with margin $\gamma$. To prove that we demonstrate vectors $w_1, w_2, \dots, w_K$
-satisfying conditions \eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2}. We define
-$$
-w_i = \frac{1}{R\sqrt{T}} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} x_t \qquad \qquad \text{for $i=1,2,\dots,K$.}
-$$
-Let $a_i = |\{ t ~:~ 1 \le t \le T, \ y_t = i \}|$ be the number of occurrences of label $i$.
-It is easy to see that
-$$
-\norm{w_i}^2 = \frac{1}{R^2 T} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} \norm{x_t}^2 = \frac{a_i}{T} \qquad \qquad \text{for $i=1,2,\dots,K$.}
-$$
-Since $\sum_{i=1}^K a_i = T$, the condition
-\eqref{equation:linear-separability-1} holds. To verify condition
-\eqref{equation:linear-separability-2} consider any labeled example $(x_t,
-y_t)$. Then, by definition of $w_{y_t}$ we have
-$$
-\ip{w_{y_t}}{x_t}
-= \frac{1}{R\sqrt{T}} \sum_{\substack{s : 1 \le s \le T \\ y_s = y_t}} \ip{x_s}{x_t}
-= \frac{1}{R\sqrt{T}} \norm{x_t}^2
-= \frac{R}{\sqrt{T}}
-\ge \frac{R}{R/\gamma}
-= \gamma \; .
-$$
-and for any $i \in \{1,2,\dots,K\} \setminus \{y_t\}$ we have
-$\ip{w_i}{x_t} = 0$. Therefore, condition \eqref{equation:linear-separability-2} holds.
-\end{proof}
+\input{appendix-multiclass-perceptron}
 

### 2019-01-07 arxiv-version/mistake-lower-bound-for-ignorant-algorithms.tex
Split sections in separate files

\section{Mistake lower bound for ignorant algorithms}

\begin{lemma}
For any $\gamma \in (0,\frac 1 {160})$,
there exists a set of $N$ examples $x_1, \ldots, x_N$ and vectors $w_1, \ldots, w_N$ ($N = (\Omega(\frac{1}{\gamma}))^{(d-2)/2}$), such that:
$\| x_i \|_2 \leq 1$, $\| w_i \|_2 \leq 1$ for all $i$ in $[N]$, and for all $i, j$ in $[N]$,
\[ w_i \cdot x_j \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases} \]
\label{lem:embed_d_gamma}
\end{lemma}
\begin{proof}
By Lemma 6 of~\cite{Long1995}, there exists a set of $N = (\frac{1}{2\sqrt{40\gamma}})^{d-2}$ $(d-1)$-dimensional vectors $z_1, \ldots, z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that
$\theta(z_i, z_j) \geq \sqrt{40 \gamma}$. As $\cos\theta \leq 1-\theta^2/5$ for every $\theta \in [0,\pi]$,
this implies that
\[ z_i \cdot z_j \begin{cases} = 1 ,& i = j, \\ \leq 1- 8\gamma ,& i \neq j. \end{cases} \]

Define $x_i = (\frac12 z_i, \frac12)$, and $w_i = (\frac 12 z_i, -\frac 12(1-4\gamma))$ for all $i$ in $[N]$. It can be easily checked that for all $i$, $\|x_i\| \leq 1$ and $\|w_i\| \leq 1$. In addition,
\[ w_i \cdot x_j = \frac 1 4 z_i \cdot z_j - \frac {1-4\gamma} 4 \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases}\]
\end{proof}

### 2019-01-07 arxiv-version/notions-of-linear-separability.tex
Split sections in separate files

\section{Notions of linear separability}
\label{section:notions-of-linear-separability}

We define two notions of linear separability for multiclass classification. The
first notion is the standard notion of linear separability used in the proof of
the mistake bound for the \textsc{Multiclass Perceptron} algorithm. The second
notion is stronger, i.e. more restrictive. However, it is more suitable for the
bandit setting, since it allows for a simple and efficient algorithm; see
Section~\ref{section:algorithm-for-strongly-linearly-separable-data}.

\begin{definition}[Linear separability]
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
integer, and let $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.

The examples are said to be \emph{linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:linear-separability-1}
\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
\label{equation:linear-separability-2}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} & \ge \ip{x_t}{w_i} + \gamma \; .
\end{align}

The examples are said to be \emph{strongly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:strong-linear-separability-1}
\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
\label{equation:strong-linear-separability-2}
\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
\label{equation:strong-linear-separability-3}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
\end{align}
\end{definition}

The notion of linear separability with a margin is standard. It used in the
full-information setting to upper bound the number of mistakes of the
\textsc{Multiclass Perceptron} algorithm. For completeness, we state the
algorithm in Appendix~\ref{section:multiclass-perceptron-proofs}. It is a
folklore result that if a set of labeled examples is separable with a margin
$\gamma$ and the norm of the examples is bounded by $R$ then \textsc{Multiclass
Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
mistakes. Another folklore result is that \textsc{Multiclass Perceptron} is
essentially optimal in the sense that any deterministic algorithm must make
$\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
completeness, we give proofs of both of these results in
Appendix~\ref{section:multiclass-perceptron-proofs}.

The notion of strong linear separability is new.

It is easy to see that if labeled examples are strongly linearly
separable with margin $\gamma$ then they are linearly separable with margin
$2\gamma$. Indeed, if $w_1, w_2, \dots, w_K \in V$
satisfy \eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3} then they satisfy
\eqref{equation:linear-separability-1} and
\eqref{equation:linear-separability-2} with margin $\gamma' = 2\gamma$.

Similarly, if $K=2$ and labeled examples are linearly separable with a margin
$\gamma$ then they are strongly linearly separable with margin $\gamma/2$.
Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1} and
\eqref{equation:linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$, $w_2' =
\frac{w_2 - w_1}{2}$ and $\gamma'=\gamma/2$ satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3}. The last two conditions are easy
to see. The first condition follows from $\norm{w_i'}^2 \le (\frac{1}{2}
\norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le \frac{1}{2}\norm{w_1}^2 +
\frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.

However, for any $K \ge 3$ and any inner product space of dimension at least
$2$, there exists a set of labeled examples that is linearly separable with a
positive margin $\gamma$ but it is not strongly linearly separable with any
positive margin $\gamma$. An example of such set of labeled examples is shown in
Figure~\ref{figure:linearly-separable-examples-with-margin}.

\begin{figure}
\begin{center}
\input{figures/linearly-separable-examples-with-margin}
\end{center}
\caption[]{The figure shows labeled examples in $\R^2$. The examples belong to
$K=3$ classes colored white, gray and black respectively. Each class lies in a
$120^\circ$ wedge. In other words, each class lies in an intersection of two
halfspaces.

While the examples are linearly separable with a positive margin $\gamma$, they
are \emph{not} strongly linearly separable with any positive margin $\gamma$.
}
\label{figure:linearly-separable-examples-with-margin}
\end{figure}

### 2019-01-07 arxiv-version/np-hardness-of-the-weak-labeling-problem.tex
Split sections in separate files

\section{NP-hardness of the weak labeling problem}

Any algorithm for the bandit setting collects information in the form of so
called \emph{strongly labeled} and \emph{weakly labeled} examples.
Strongly-labeled examples are those for which we know the class label. Weakly
labeled example is an example for which we know that class label can be anything
except for a particular one class.

A natural strategy for each round is to find vectors $w_1, w_2, \dots, w_K$ that
linearly separate the examples seen in the previous rounds and use the vectors
to predict the label in the next round. More precisely, we want to find both the
vectors $w_1, w_2, \dots, w_K$ and label for each example consistent with its
weak and/or strong labels such that $w_1, w_2, \dots, w_K$ linearly separate the
labeled examples. We show this problem is NP-hard even for $K=3$.

Clearly, the problem is at least as hard as the decision version of the problem
where the goal is to determine if such vectors and labeling exist. We show that
this problem is NP-complete.

Formally, the input to the decision problem are positive integers $d, T, K$ and
a sequence $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \{0,1\}^d \times
\{1,2,\dots,K, \overline{1}, \overline{2}, \dots, \overline{K}\}$ of strongly
and weakly labeled examples. The numbers $1,2,\dots,K$ correspond to strong
labels and the symbols $\overline{1}, \overline{2}, \dots, \overline{K}$
correspond to weak labels. We adopt the convention that $\overline{\overline{i}}
= i$ for any positive integer $i$. The goal is to determine whether or not there
exist vectors $w_1, w_2, \dots, w_K \in \R^d$ that satisfy the following
conditions for all $t=1,2,\dots,T$,
\begin{align*}
y_t \in \{1,2,\dots,K\} \qquad & \Longrightarrow \qquad & \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \qquad \ip{w_{y_t}}{x_t} & > \ip{w_i}{x_t} \; , \\
y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \qquad & \Longrightarrow & \qquad \exists i \in \{1,2,\dots,K\} \qquad \ip{w_i}{x_t} & > \ip{w_{\overline{y_t}}}{x_t} \; .
\end{align*}

TODO

### 2019-01-07 arxiv-version/proofs-of-polynomial-approximation-theorems.tex
Split sections in separate files

\section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
\label{section:proof-of-polynomial-approximation}

For the proofs of the theorems we need several auxiliary results.

\begin{lemma}[Simple inequality]
\label{lemma:simple-inequality}
For any real numbers $b_1, b_2, \dots, b_n$,
$$
\left( \sum_{i=1}^n b_i \right)^2 \le n \sum_{i=1}^n b_i^2 \; .
$$
\end{lemma}

\begin{proof}
The lemma follows from Cauchy-Schwartz inequality applied to
vectors $(b_1, b_2, \dots, b_n)$ and $(1,1,\dots,1)$.
\end{proof}

\begin{lemma}[Bound on binomial coefficients]
\label{lemma:binomial-bound}
For any integers $n,k$ such that $n \ge k \ge 0$,
$$
\binom{n}{k} \le (n - k + 1)^k \; .
$$
\end{lemma}

\begin{proof}
If $k = 0$, the inequality trivially holds. For the rest of the proof we can
assume $k \ge 1$. We write the binomial coefficient as
$$
\binom{n}{k}
= \frac{n(n-1)\cdots(n-k+1)}{k(k-1) \cdots 1}
= \frac{n}{k} \cdot \frac{n-1}{k - 1} \cdots \frac{n-k+1}{1} \; .
$$
We claim that
$$
\frac{n}{k} \le \frac{n-1}{k - 1} \le \cdots \le \frac{n-k+1}{1}
$$
from which the lemma follows by upper bounding all the fractions by $n-k+1$.
It remains to prove that for any $j=0,1,\dots,k-1$,
$$
\frac{n - j + 1}{k - j + 1} \le \frac{n - j}{k - j} \; .
$$
Multiplying by the (positive) denominators, we get an equivalent inequality
$$
(n - j + 1)(k - j) \le (n - j)(k - j + 1) \; .
$$
Cancelling common terms leads to an equivalent inequality
$$
k - j \le n - j \; ,
$$
which holds by the assumption on $n \ge k$.
\end{proof}

\begin{lemma}[Properties of the norm of polynomials]
\label{lemma:properties-of-norm-of-polynomials}
\hspace{1cm} % Dummy space
\begin{enumerate}
\item Let $p_1, p_2, \dots, p_n$ be multivariate polynomials and let $p(x) =
\prod_{j=1}^n p_j(x)$ be their product.  Then, $\norm{p}^2 \le n^{\sum_{j=1}^n
\deg(p_j)} \prod_{j=1}^n \norm{p_j}^2$.

\item Let $q$ be a multivariate polynomial of degree at most $s$ and let $p(x) =
(q(x))^n$. Then, $\norm{p}^2 \le n^{ns} \norm{q}^{2n}$.

\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then,
$\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
\end{enumerate}
\end{lemma}

\begin{proof}
Using multi-index notation we can write any multivariate polynomial $p$ as
$$
p(x) = \sum_A c_A x^A
$$
where $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ is a multi-index (i.e. a $d$-tuple of
non-negative integers), $x^A = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}$ is a
monomial and $c_A = c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is the corresponding real
coefficient. The sum is over a finite subset of $d$-tuples of non-negative
integers. Using this notation, the norm of a polynomial $p$ can be written as
$$
\norm{p} = \sqrt{\sum_A (c_A)^2} \; .
$$
For a multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ we define its
$1$-norm as $\norm{A}_1 = \alpha_1 + \alpha_2 + \dots + \alpha_d$.

To prove the part 1, we express $p_j$ as
$$
p_j(x) = \sum_{A_j} c^{(j)}_{A_j} x^{A_j} \; .
$$
Since $p(x) = \prod_{i=1}^n p_j(x)$, the coefficients of its expansion $p(x) =
\sum_A c_A x^A$ are
$$
c_A = \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \; .
$$
Therefore,
\begin{multline*}
\norm{p}^2
= \sum_{A} (c_A)^2
= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \right)^2
= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\end{multline*}
and
\begin{multline*}
\prod_{i=1}^n \norm{p_i}^2
= \prod_{i=1}^n \left( \sum_{A_i} (c^{(i)}_{A_i})^2 \right)
= \sum_{(A_1, A_2, \dots, A_n)} \prod_{j=1}^n (c^{(j)}_{A_j})^2
= \sum_{(A_1, A_2, \dots, A_n)} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
= \sum_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\end{multline*}
where in both cases the outer sum is over multi-indices $A$ such that $\norm{A}_1 \le \deg(p)$.
\autoref{lemma:simple-inequality} implies that for any multi-index $A$,
$$
\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\le M_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
$$
where $M_A$ is the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 +
A_2 + \dots + A_n = A$.

To finish the proof, it is sufficient to prove that $M_A \le n^{\deg(p)}$ for
any $A$ such that $\norm{A}_1 \le \deg(p)$. To prove this inequality, consider a
multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ and consider its $i$-th coordinate
$\alpha_i$. In order for $A_1 + A_2 + \dots + A_n = A$ to hold, the $i$-th
coordinates of $A_1, A_2, \dots, A_n$ need to sum to $\alpha_i$. There are exactly
$\binom{\alpha_i + n - 1}{\alpha_i}$ possibilities for the choice of $i$-th
coordinates of $A_1, A_2, \dots, A_n$. The total number of choices is thus
$$
M_A = \prod_{i=1}^d \binom{\alpha_i + n - 1}{\alpha_i} \; .
$$
Using \autoref{lemma:binomial-bound}, we upper bound it as
$$
M_A \le \prod_{i=1}^d n^{\alpha_i} = n^{\norm{A}_1} \le n^{\deg(p)} \; .
$$

Part 2 follows from the part 1 by setting $p_1 = p_2 = \dots p_n = q$.

To prove the part 3, we use generalized triangle inequality and
\autoref{lemma:simple-inequality}. We have
\begin{align*}
\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
\end{align*}
\end{proof}

\subsection{Proof of \autoref{theorem:polynomial-approximation-1}}
\label{section:proof-of-polynomial-approximation-1}

To construct the polynomial $p$ we use Chebyshev polynomials of the first kind.
Chebyshev polynomials of the fist kind form an infinite sequence of polynomials
$T_0(z), T_1(z), T_2(z), \dots$ of single real variable $z$. They are defined
by the recurrence
\begin{align*}
T_0(z) & = 1 \; , \\
T_1(z) & = z \; , \\
T_{n+1}(z) & = 2zT_n(z) - T_{n-1}(z) & \text{for $n \ge 1$.}
\end{align*}
Chebyshev polynomials have a lot of interesting properties.
We will need properties listed in
\autoref{proposition:properties-of-chebyshev-polynomials} below.
Interested reader can learn more about Chebyshev polynomials
from the book by \cite{Mason-Handscomb-2002}.

\begin{proposition}[Properties of Chebyshev polynomials]
\label{proposition:properties-of-chebyshev-polynomials}
Chebyshev polynomials satisfy
\begin{enumerate}
\item $\deg(T_n) = n$ for all $n \ge 0$.
\item If $n \ge 1$, the leading coefficient of $T_n(z)$ is $2^{n-1}$.
\item $T_n(\cos(\theta)) = \cos(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
\item $T_n(\cosh(\theta)) = \cosh(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$ and all $n \ge 0$.
\item $T_n(z) \ge 1 + n^2(z - 1)$ for all $z \ge 1$ and all $n \ge 0$.
\item $\norm{T_n} \le (1+\sqrt{2})^n$ for all $n \ge 0$
\end{enumerate}
\end{proposition}

\begin{proof}[Proof of \autoref{proposition:properties-of-chebyshev-polynomials}]
The first two properties can be easily proven by induction on $n$ using the recurrence.

We prove third property by induction on $n$. Indeed, by definition
$$
T_0(\cos(\theta)) = 1 = \cos(0 \theta) \qquad \text{and} \qquad T_1(\cos(\theta)) = \cos(\theta) \; .
$$
For $n \ge 1$, we have
\begin{align*}
T_{n+1}(\cos(\theta))
& = 2 \cos(\theta) T_n(\cos(\theta)) - T_{n-1}(\cos(\theta)) \\
& = 2 \cos(\theta) \cos(n \theta) - \cos((n-1)\theta)) \; ,
\end{align*}
where the last step follow by induction hypothesis.
It remains to show that the last expression equals $\cos((n+1)\theta)$.
This can be derived from the trigonometric formula
$$
\cos(\alpha \pm \beta) = \cos(\alpha) \cos(\beta) \mp \sin(\alpha) \sin(\beta) \; .
$$
By substituting $\alpha = n \theta$ and $\beta = \theta$, we get two equations
\begin{align*}
\cos((n+1) \theta) & = \cos(n \theta) \cos(\theta) - \sin(n \theta) \sin(\theta) \; , \\
\cos((n-1) \theta) & = \cos(n \theta) \cos(\theta) + \sin(n \theta) \sin(\theta) \; .
\end{align*}
Summing them yields
$$
\cos((n+1)\theta) + \cos((n-1) \theta) = 2 \cos(n \theta) \cos(\theta)
$$
which finishes the proof.

Fourth property has the similar proof as third property. It suffices
to replace $\cos$ and $\sin$ with $\cosh$ and $\sinh$ respectively.

Fifth property follows from the third property. Indeed, for any $z \in [-1,1]$
there exists $\theta \in \R$ such that $\cos \theta = z$. Thus, $|T_n(z)| =
|T_n(\cos(\theta))| = |\cos(n\theta)| \le 1$.

The sixth property is equivalent to
$$
T_n(\cosh(\theta)) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$,}
$$
since $\cosh(\theta) = \frac{e^{\theta} + e^{-\theta}}{2}$ is an even continuous
function that maps $\R$ onto $[1,+\infty)$, is strictly decreasing on
$(-\infty,0]$, and is strictly increasing on $[0,\infty)$. Using the fourth
property the last inequality is equivalent to
$$
\cosh(n \theta) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$.}
$$
For $\theta = 0$, both sides are equal to $1$. Thus, it is sufficient to prove
that the derivative of the left hand side is greater or equal to the derivative
of the right hand side. Recalling that $[\cosh(\theta)]' = \sinh(\theta)$, this
means that we need to show that
$$
\sinh(n \theta) \ge n \sinh(\theta) \qquad \text{for all $\theta \ge 0$.}
$$
Tho prove this inequality we use the summation formula
$$
\sinh(\alpha + \beta) = \sinh(\alpha) \cosh(\beta) + \sinh(\beta) \cosh(\beta) \; .
$$
If $\alpha, \beta$ are non-negative then $\sinh(\alpha), \sinh(\beta)$ are
non-negative and $\cosh(\alpha), \cosh(\beta) \ge 1$. Hence,
$$
\sinh(\alpha + \beta) \ge \sinh(\alpha) + \sinh(\beta) \qquad \text{for any $\alpha, \beta \ge 0$.}
$$
This implies that (using induction on $n$) that $\sinh(n \theta) \ge n
\sinh(\theta)$ for all $\theta \ge 0$.

We verify the seventh property by induction on $n$.
For $n=0$ and $n=1$ the inequality trivially holds, since $\norm{T_0} = \norm{T_1} = 1$.
For $n \ge 1$, since $T_{n+1}(z) = 2zT_n(z) - T_{n-1}(z)$,
\begin{align*}
\norm{T_{n+1}}
& \le 2 \norm{T_n} + \norm{T_{n-1}} \\
& \le 2 (1 + \sqrt{2})^n + (1 + \sqrt{2})^{n-1} \\
& = (1 + \sqrt{2})^{n-1} (2 (1 + \sqrt{2}) + 1) \\
& = (1 + \sqrt{2})^{n-1} (3 + 2\sqrt{2}) \\
& = (1 + \sqrt{2})^{n-1} (1 + \sqrt{2})^2 \\
& = (1 + \sqrt{2})^{n+1} \; .
\end{align*}

\end{proof}

Let $r = \left\lceil \log_2(2m) \right\rceil$ and $s = \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$.
We define the polynomial $p:\R^d \to \R$ as
$$
p(x) = m + \frac{1}{2} - \sum_{i=1}^m \left( T_s(1 - \ip{v_i}{x}) \right)^r \; .
$$
It remains to show that $p$ has properties 1--5.

To verify the first property notice that if $x \in \R^d$ satisfies $\norm{x} \le
1$ and $\ip{v_i}{x} \ge \gamma$ then since $\norm{v_i} \le 1$ we have
$\ip{v_i}{x} \in [0,1]$. Thus, $T_s(1 - \ip{v_i}{x})$ and $\left( T_s(1 -
\ip{v_i}{x}) \right)^r$ lie in the interval $[-1,1]$. Therefore,
$$
p(x) \ge m + \frac{1}{2} - m \ge \frac{1}{2} \; .
$$

To verify the second property consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d
~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Clearly, $\norm{x} \le 1$
and there exists at least one $i \in \{1,2,\dots,m\}$ such that $\ip{v_i}{x} \le
- \gamma$. Therefore, $1 - \ip{v_i}{x} \ge 1 + \gamma$ and~\autoref{proposition:properties-of-chebyshev-polynomials} (part 6)
imply that
$$
T_s(1 - \ip{v_i}{x}) \ge 1 + s^2 \gamma \ge 2
$$
and thus
$$
\left( T_s(1 - \ip{v_i}{x}) \right)^r \ge 2^r \ge 2m \; .
$$
On the other hand for any $j \in \{1,2,\dots,m\}$, we have $\ip{v_j}{x} \in
[-1,1]$ and thus $1 - \ip{v_j}{x}$ lies in the interval $[0,2]$. According to
\autoref{proposition:properties-of-chebyshev-polynomials} (parts 5 and 6), $T_s(1 - \ip{v_j}{x})
\ge -1$. Therefore,
$$
p(x) = m + \frac{1}{2} - \left( T_s(1 - \ip{v_i}{x}) \right)^r - \sum_{\substack{j ~:~  1 \le j \le m \\ j \neq i}} \le m + \frac{1}{2} - 2m + (m - 1) \le - \frac{1}{2} \; .
$$

The third property follows from observation that degree of $p$
is the same as the degree of any one of the terms
$\left( T_s(1 - \ip{v_i}{x}) \right)^r$ which is $r \cdot s$.

To prove the fourth property, we need to upper bound the norm of $p$.
Let $f_i(x) = 1 - \ip{v_i}{x}$, let $g_i(x) = T_s(1 - \ip{v_i}{x})$
and let $h_i(x) = (T_s(1 - \ip{v_i}{x}))^r$. We have
$$
\norm{f_i}^2 = 1 + \norm{v_i}^2 \le 1 + 1 = 2 \; .
$$
Let $T_s(z) = \sum_{j=0}^s c_j z^j$ be the expansion of $s$-th Chebyshev polynomial.
Then,
\begingroup
\allowdisplaybreaks
\begin{align*}
\norm{g_i}^2
& = \norm{ \sum_{j=0}^s c_j (f_i)^j }^2 \\
& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 & \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
& = (s + 1) \sum_{j=0}^s (c_j)^2 \norm{(f_i)^j}^2 \\
& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} & \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j 2^{2j} \\
& \le (s + 1) s^s 2^{2s} \sum_{j=0}^s (c_j)^2 \\
& = (s + 1) s^s 2^{2s} \norm{T_s}^2 \\
& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} & \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
& = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
& \le \left(8(1+\sqrt{2})^2 s \right)^s & \text{(since $s+1 \le 2^s$ for any integer $s \ge 0$)} \\
& \le \left(47 s \right)^s \; .
\end{align*}
\endgroup
Finally,
\begin{align*}
\norm{p}
& \le m + \frac{1}{2} + \sum_{i=1}^m \norm{(g_i)^r} \\
& = m + \frac{1}{2} + \sum_{i=1}^m \sqrt{\norm{(g_i)^r}^2} \\
& \le m + \frac{1}{2} + \sum_{i=1}^m \sqrt{r^{rs} \norm{g_i}^{2r}} \\
& \le m + \frac{1}{2} + m r^{rs/2} \left(47 s \right)^{rs/2} \\
& = m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \; .
\end{align*}
We can further upper bound the last expression by using that $m \le \frac{1}{2} 2^r$.
Since $r,s \ge 1$,
\begin{align*}
\norm{p}
& \le m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \\
& \le \frac{1}{2} 2^r + \frac{1}{2} + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
& \le 2^r + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
& = 2^r \left(1 + \frac{1}{2} \left(47 rs \right)^{rs/2} \right) \\
& = 2^r \left(47 rs \right)^{rs/2} \\
& \le 4^{rs/2} \left(47 rs \right)^{rs/2} \\
& \le \left(188 rs \right)^{rs/2} \; .
\end{align*}
Substituting for $r$ and $s$ finishes the proof.

\subsection{Proof of \autoref{theorem:polynomial-approximation-2}}
\label{section:proof-of-polynomial-approximation-2}

We define several univariate polynomials
\begin{align*}
P_n(z) & = (z - 1) \prod_{i=1}^n (z - 2^i)^2 && \text{for $n \ge 0$,} \\
A_{n,k}(z) & = (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$,} \\
B_{n,k}(z) & = - (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$.}
\end{align*}
We define the polynomial $p:\R^d \to \R$ as
$$
p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
- \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
$$

For convenience we define univariate rational function
\begin{align*}
S_{n,k}(z) & = \frac{A_{n,k}(z)}{B_{n,k}(z)} && \text{for $n,k \ge 0$,}
\end{align*}
and a multivariate rational function
$$
Q(x) = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \; .
$$
It easy to verify that
$$
p(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
$$

\begin{lemma}[Properties of $P_n$]
\label{lemma:properties-of-p-n}
\hspace{1cm} % Dummy space
\begin{enumerate}
\item If $z \in [0,1]$ then $P_n(-z) \le P_n(z) \le 0$.
\item If $z \in [1,2^n]$ then $0 \le 4P_n(z) \le -P_n(-z)$.
\item If $z \ge 0$ then $-P_n(-z) \ge 2^{n(n+1)}$.
\end{enumerate}
\end{lemma}

\begin{proof}
To prove the first part, note that $P_n(z)$ and $P_n(-z)$ are non-positive for
$z \in [0,1]$. We can write $\frac{P_n(z)}{P_n(-z)}$ as a product of $n+1$
non-negative fractions
$$
\frac{P_n(z)}{P_n(-z)} = \frac{1-z}{1+z} \prod_{i=1}^n \frac{(z+2^i)^2}{(z-2^i)^2} \; .
$$
The first part follows from the observation that each fraction is upper bounded
by $1$.

To prove the second part, notice that $P_n(z)$ is non-negative and $P_n(-z)$ is
non-positive for any $z \in [1,2^n]$. Now, fix $z \in [1,2^n]$ and let $j \in
\{1,2,\dots,n\}$ be such that $2^{j-1} \le z \le 2^j$. This implies that
$(z+2^{j})^2 \ge 4 (z - 2^j)^2$. We can write $\frac{P_n(z)}{-P_n(-z)}$ as a
product of $n+1$ non-negative fractions
$$
\frac{P_n(z)}{-P_n(-z)}
= \frac{z-1}{z+1} \cdot \frac{(z-2^j)^2}{(z+2^j)^2} \prod_{\substack{i ~:~ 1 \le i \le n \\ i \neq j}} \frac{(z-2^i)^2}{(z+2^i)^2} \; .
$$
The second part follows from the observation that the second fraction is upper
bounded by $1/4$ and all other fractions are upper bounded by $1$.

The third part follows from
$$
-P_n(-z) = (1+z) \prod_{i=1}^n (z+2^i)^2 \ge \prod_{i=1}^n 2^{2i} = 2^{n(n+1)} \; .
$$
\end{proof}

\begin{lemma}[Properties of $S_{n,r}$ and $B_{n,r}$]
\label{lemma:properties-of-s-n-r}
Let $n,m$ be non-negative integers.
Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$. Then,
\begin{enumerate}
\item If $z \in [1,2^n]$ then $S_{n,r}(z) \in [1,1+\frac{1}{2m}]$.
\item If $z \in [-2^n, -1]$ then $S_{n,r} \in [-1-\frac{1}{2m}, -1]$.
\item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
\end{enumerate}
\end{lemma}

\begin{proof}
Note that $B_{n,r}(z)$ is an even function and $A_{n,r}(z)$ is an odd function.
Therefore, $S_{n,r}(z)$ is odd. Also notice that $r$ is an odd integer.

\begin{enumerate}
\item Observe that $S_{n,r}(z)$ can be written as
$$
S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
$$
where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. Since
$r \ge \frac{1}{2} \log_2(4m+1)$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
$S_{n,r}(z) = \frac{1+c}{1-c} \in [1,1 + \frac{1}{2m}]$.

\item Since $S_{n,r}(z)$ is odd, the statement follows from part 1.

\item Observe that $S_{n,r}(z)$ can be written as
$$
S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
$$
where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. If $z \in [0,1]$, by part
1 of~\autoref{lemma:properties-of-p-n} and the fact that $r$ is odd, $c
\in [-1,0]$, and thus, $S_{n,r}(z) = \frac{1+c}{1-c} \in [0,1]$. Since
$S_{n,r}(z)$ is odd, for $z \in [-1,0]$, $S_{n,r}(z) \in [-1,0]$.

\item Since $B_{n,r}(z)$ is even, we can without loss generality assume that $z \ge
0$. We consider two cases.

Case $z \in [0,1]$. Since $r$ is odd and $P_n(z)$ is non-positive,
$$
B_{n,r}(z) = - (P_n(z))^r + \left(- P_{n}(-z)\right)^r \ge \left(- P_{n}(-z)\right)^r \ge 2^{n(n+1)r} \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
$$
where the second last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.

Case $z \in [1,2^n]$. Since $r$ is odd,
$$
B_{n,r}(z) = \left(- P_{n}(-z)\right)^r \left(1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r \right) = \left(- P_{n}(-z)\right)^r (1 - c)
$$
where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. By
the definition of $r$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
$$
B_{n,r}(z) \ge \left(- P_{n}(-z)\right)^r \left( 1 - \frac{1}{4m+1} \right) \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
$$
where the last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
\end{enumerate}
\end{proof}

\begin{lemma}[Properties of $Q(x)$]
\label{lemma:properties-of-q}
The rational function $Q(x)$ satisfies
\begin{enumerate}
\item $Q(x) \ge \frac{1}{2}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
\item $Q(x) \le -\frac{1}{2}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
\end{enumerate}
\end{lemma}

\begin{proof}
To prove part 1, consider any $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \
\ip{v_i}{x} \ge \gamma \right\}$. Then, $\frac{\ip{v_i}{x}}{\gamma} \in [1,
\frac{1}{\gamma}]$. By part 1 of \autoref{lemma:properties-of-s-n-r},
$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \in [1, 1 + \frac{1}{2m}]$ and
in particular $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \ge 1$. Thus,
$$
Q(x) = \left( \sum_{i=1}^m S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \right) - (m - 1/2) \ge m - (m - 1/2) = 1/2 \; .
$$

To prove part 2, consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~
\norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Observe that
$\frac{\ip{v_i}{x}}{\gamma} \in [-\frac{1}{\gamma}, \frac{1}{\gamma}]$. Consider
$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right)$ for any $i \in
\{1,2,\dots,m\}$. Parts 1,2, and 3 of \autoref{lemma:properties-of-s-n-r}
and the fact $1/\gamma \le 2^s$ imply that
$S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \le 1 +
\frac{1}{2m}$ for all $i \in \{1,2,\dots,m\}$. By the choice of $x$, there
exists $j \in \{1,2,\dots,m\}$ such that $\ip{v_j}{x} \le - \gamma$. Part 2 of
\autoref{lemma:properties-of-s-n-r} implies that
$S_{s,r}\left(\frac{\ip{v_j}{x}}{\gamma}\right) \in [-1-\frac{1}{2m},-1]$. Thus,
\begin{align*}
Q(x)
& = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
& = S_{s,r}\left( \frac{\ip{v_j}{x}}{\gamma} \right) + \left( \sum_{\substack{i ~:~ 1 \le i \le m \\ i \neq j}} S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
& \le -1 + (m-1) \left( 1 + \frac{1}{2m} \right) - \left(m - \frac{1}{2} \right) \\
& \le 1/2 \; .
\end{align*}
\end{proof}

To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-2} first
note that part 4 of \autoref{lemma:properties-of-s-n-r} implies that for any $x$
such that $\norm{x} \le 1$, $B_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right)$
is positive. Thus $p(x)$ and $Q(x)$ have the same sign on the unit ball.
Consider any $x$ in either
$\displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
or in
$\displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
\autoref{lemma:properties-of-q} states that $|Q(x)| \ge 1/2$ and the sign
depends on which of the two sets $x$ lies in. Since signs of $Q(x)$ and $p(x)$
are the same, it remains to show that $|p(x)| \ge m^{s^2m/2}$. Indeed,
\begin{align*}
|p(x)|
& = |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
& \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
& \ge \frac{1}{2} |Q(x)| \cdot 2^{s(s+1)rm} && \text{(since $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4} \ge 1/2$)} \\
& \ge \frac{1}{4} \cdot 2^{s(s+1)rm} && \text{(\autoref{lemma:properties-of-q})} \; .
\end{align*}

To prove part 3 of \autoref{theorem:polynomial-approximation-2} note that
$\deg(P_s) = 2s+1$. Thus, $\deg(A_{s,r})$ and $\deg(B_{s,r})$ are at most
$(2s+1)r$. Therefore, $\deg(p) \le (2s+1) rm$.

It remains to prove part 4 of \autoref{theorem:polynomial-approximation-2}.
For any $i \in \{0,1,2,\dots,s\}$ and any $v \in \R^d$ such that $\norm{v} \le 1$
define multivariate polynomials
\begin{align*}
f_{i,v}(x) & = \frac{\ip{v}{x}}{\gamma} - 2^i \; , \\
q_v(x) & = P_s \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
a_v(x) & = A_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; , \\
b_v(x) & = B_{s,r} \left( \frac{\ip{v}{x}}{\gamma} \right) \; .
\end{align*}
Note that
$$
p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
$$
We bound the norms of these polynomials. We have
$$
\norm{f_{i,v}}^2 = \norm{v}^2/\gamma^2 + 2^{2i} \le 2 \cdot 2^s \; .
$$
where we used that $1/\gamma \le 2^s$ and $\norm{v} \le 1$.
Since $q_v(x) = f_{i,v}(\frac{\ip{v}{x}}{\gamma}) \prod_{i=1}^s \left(f_{i,v}(\frac{\ip{v}{x}})\right)^2$,
using part 1 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $q_v$
as
$$
\norm{q_v}^2 \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \le  (2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \; .
$$
Using parts 3 and 2 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $a_v$ as
\begin{align*}
\norm{a_v}^2
& \le 2\norm{(q_v)^r}^2 + 2\norm{(q_{-v})^r}^2 \\
& \le 2 r^{r(2s+1)} \norm{q_v}^{2r} + 2 r^{r(2s+1)} \norm{q_{-v}}^{2r} \\
& \le 4 r^{r(2s+1)} \left((2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \right)^{2r} \\
& = 4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \; .
\end{align*}
The same upper bound holds for $\norm{b_v}^2$. Finally,
\begin{align*}
\norm{p}
& \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
& \le \left[ \sum_{i=1}^m m^{(s+1/2)rm} \norm{a_{v_i}} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} \norm{b_{v_j}} \right] + \left(m - \frac{1}{2} \right) m^{(s+1/2)rm} \prod_{j=1}^m \norm{b_{v_j}} \\
& \le (2m-1/2) m^{(s+1/2)rm} \left(4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \right)^{m/2} \\
& = (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm} \; .
\end{align*}

### 2019-01-07 arxiv-version/related-work.tex
Split sections in separate files

\section{Related work}
\label{section:related-work}
The problem of bandit multiclass linear classification is initially formulated
 by the pioneering work of~\cite{Kakade-Shalev-Shwartz-Tewari-2008}. In that work,
 two computationally
 inefficient algorithms that work in the $\gamma$-weak linearly separable setting are proposed: one with a mistake bound of
 $O(k^2 d \ln(\frac{d}{\gamma^2}))$, the other with a mistake bound of $\tilde{O}(\frac{k^2}{\gamma^2} \ln T)$.
 In addition, the authors propose the Banditron algorithm, a computationally efficient
 algorithm that has a $O(T^{2/3})$ regret in the general setting, and has a
 $O(\sqrt{T})$ mistake bound in the $\gamma$-weak linearly separable setting.
The polynomial dependence of Banditron's mistake bound on the time horizon is undesirable
for problems with a long time horizon.
 One key open question left by~\cite{Kakade-Shalev-Shwartz-Tewari-2008} is whether
 one can deesign computationally efficient algorithms that achieve mistake bounds that match or improve over those of inefficient algorithms.
 In this paper, we take a step towards answering this question, showing that
 efficient algorithms with mistake bounds quasipolynomial in the margin parameter can be obtained.

 %Whether one can design an efficient algorithm with a
 %finite mistake bound that has no dimensionality dependence is mentioned as an open problem in
 %~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, where in this paper we provide a positive answer.
 %$O(k^2 d \ln(\frac{d}{\gamma^2}))$

Many works consider bandit multiclass classification in the general non-separable setting.
\cite{Abernethy-Rakhlin-2009} poses the open problem of whether one can design
and efficient algorithm to get a $O(\sqrt{T})$ regret against some reasonable loss functions.
\cite{CrammerG13} shows that such an algorithm can be obtained, under the assumption that the distribution of the label $y$ conditioned on feature $x$ satisfies certain parametric noise assumption.
\cite{Hazan-Kale-2011} developed the Newtron algorithm, which has a regret
between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass logistic loss, where the exact order of the regret depends on the diameter of the benchmark class. In particular, if the diameter is $O(\ln T)$, its regret bound would become
$O(T^{2/3})$.
The SOBA algorithm by \cite{Beygelzimer-Orabona-Zhang-2017} achieves a regret of $\tilde{O}(\sqrt{T})$ against the $\eta$-loss~\cite{Orabona-Cesa-Bianchi-Gentile-2012}; in addition, their regret bound does not depend sensitively on the diameter of the benchmark class.
\cite{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a regret of $\tilde{O}(\sqrt{T})$ against the multiclass logistic loss, where it doubly-exponentially improves over \cite{Hazan-Kale-2011}'s regret on its dependence on the diameter of the benchmark class.
Recently, \cite{Foster-Krishnamurthy-2018} developed a rich theory on contextual bandits with surrogate losses, focusing on benchmarks of the form $\min_{f \in \calF} \frac 1 K \sum_{i=1}^K \phi( f_i(x) )$, where $\calF$ contains function $f$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$,
and $\phi(s) = \max(1 - \frac s \gamma, 0)$ and $\min(1, \max(1 - \frac s \gamma, 0))$.
On one hand, it gives information-theoretic mistake upper bounds under various settings of $\calF$, for instance parametric and nonparametric classes; On the other hand, it gives an efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of $\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$.

\cite{Chen-Lin-Lu-2014, Zhang-Jung-Tewari-2018} study online bandit multiclass boosting under bandit feedback, where one can view online boosting as online linear classification by treating each base hypothesis as a separate feature.
\cite{Chen-Lin-Lu-2014}'s online weak learning condition implies that there is a convex combination of base hypotheses that one-versus-all separates all examples with a margin. Under this condition, it gives an algorithm with a $O(T^{3/4})$ mistake bound.
\cite{Zhang-Jung-Tewari-2018} considers an online weak learning condition that implies that there is a convex combination of base hypotheses that weakly separates all examples with a margin (See~\cite{Mukherjee-Schapire-2013}, Theorem 3). Under this condition, it gives an algorithm with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge parameter; in addition, it gives an adaptive algorithm with a $O(T^{3/4})$ mistake bound.

%\cite{Chen-Chen-Zhang-Chen-Zhang-2009} studies the approach of reducing bandit multiclass learning to online binary classification using one-versus-all reduction. They show that

%Their results do not imply a finite mistake bound in the weakly separable setting, in that the benchmark loss can still be $\Omega(T)$.

%\begin{itemize}
%\item \cite{Abernethy-Rakhlin-2009}

%\item \cite{Chen-Chen-Zhang-Chen-Zhang-2009}

%\item \cite{Hazan-Kale-2011}

%\item \cite{Beygelzimer-Orabona-Zhang-2017}

%\item \cite{Foster-Kale-Luo-Mohri-Sridharan-2018}

%\item \cite{Foster-Krishnamurthy-2018}
%\end{itemize}

%TODO

### 2019-01-07 arxiv-version/mistake-lower-bound-for-ignorant-algorithms.tex
Clean-up bibliography

@@
 \begin{proof}
-By Lemma 6 of~\cite{Long1995}, there exists a set of $N = (\frac{1}{2\sqrt{40\gamma}})^{d-2}$ $(d-1)$-dimensional vectors $z_1, \ldots, z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that
+By Lemma 6 of~\cite{Long-1995}, there exists a set of $N = (\frac{1}{2\sqrt{40\gamma}})^{d-2}$ $(d-1)$-dimensional vectors $z_1, \ldots, z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that
 $\theta(z_i, z_j) \geq \sqrt{40 \gamma}$. As $\cos\theta \leq 1-\theta^2/5$ for every $\theta \in [0,\pi]$,

### 2019-01-07 arxiv-version/related-work.tex
Clean-up bibliography

@@
 and efficient algorithm to get a $O(\sqrt{T})$ regret against some reasonable loss functions.
-\cite{CrammerG13} shows that such an algorithm can be obtained, under the assumption that the distribution of the label $y$ conditioned on feature $x$ satisfies certain parametric noise assumption.
+\cite{Crammer-Gentile-2013} shows that such an algorithm can be obtained, under the assumption that the distribution of the label $y$ conditioned on feature $x$ satisfies certain parametric noise assumption.
 \cite{Hazan-Kale-2011} developed the Newtron algorithm, which has a regret

### 2019-01-07 arxiv-version/introduction.tex
Some clean ups

@@
 
-We study the problem of \textsc{Online Multiclass Linear
-Classification with Bandit Feedback}~\cite{Kakade-Shalev-Shwartz-Tewari-2008}.
-The problem can be viewed as a game between the learner and the environment:
-at each timestep $t$, the environment chooses an example $(x_t, y_t)$, where its feature
-part $x_t \in \R^d$ is revealed to the learner.
-\footnote{All our results apply to also to a simpler model of
-the so called \emph{oblivious adversary} where the whole sequence of labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is chosen before the first
-round of the game.}
-Upon receiving this example, the
-learner is asked to make a prediction $\hat{y}_t$.
-the learner receives feedback immediately after making its prediction.
-In contrast with the standard full information setting (where the feedback given is the correct label $y_t$), the feedback given is only a binary indicator
-whether the prediction was correct or not. The protocol of the problem is formally stated below.
-
-%In this problem, in each round, the
-%learner receives a feature vector and is asked to predict one of $K$
-%possible classes. To allow
-%for meaningful use of randomization, we assume that the correct label in a
-%particular round is chosen prior to algorithm's prediction in that
-%round.
-%Immediately after the learner makes its prediction, it
-%receives feedback whether the prediction was correct or not. However, in
-%contrast with the standard, so called full information setting, the algorithm
-%does \emph{not} receive the correct label. The feedback is only binary.
+We study the problem of \textsc{Online Multiclass Linear Classification with
+Bandit Feedback}~\cite{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
+viewed as a game between the learner and the adversary: at each timestep $t$,
+the adversary chooses an example $(x_t, y_t)$ where the feature vector $x_t \in
+\R^d$ is revealed to the learner and the correct label $y_t$ is kept secret by
+the adversary. Upon receiving the feature vector $x_t$, the learner is asked to
+make a prediction $\widehat{y}_t$. Immediately after making its prediction, the
+learner receives a feedback. In contrast with the standard full information
+setting (where the feedback given is the correct label $y_t$), here the feedback
+is only a binary indicator of whether the prediction was correct or not. The
+protocol of the problem is formally stated below.
 
@@
 
-The performance is of the learner is measured by its cumulative number of mistakes
-$\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$. The bandit feedback
- is a natural feedback model motivated by applications including
-online advertising and online content optimization, where the learner only gets to
-see the loss of its action taken.
-%where the binary feedback corresponds to a click
-%The
-%corresponding problem with full information feedback is solved by the classical
-%\textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
-%\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}).
+The performance is of the learner is measured by its cumulative number of
+mistakes $\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$.
+The bandit feedback is a natural feedback model motivated by applications
+including online advertising and online content optimization.
 
@@
 }
+\david{The formal definitions are in a section of their own.}
 

### 2019-01-07 arxiv-version/main.tex
Some clean ups

@@
 \begin{abstract}
-We study the problem of efficient online multiclass linear classification with bandit feedback, where all examples belong to one of $K$ classes and lie in the $d$-dimensional Euclidean space.
-Previous works have left open the challenge of designing efficient algorithms with finite mistake bounds
-when the data is linearly separable by a margin $\gamma$.
-In this work, we take a first step towards this problem.
-We identify two notions of linear separability:
-one-versus-all (OvA) linear separability and weakly linear separability.
+We study the problem of efficient online multiclass linear classification with
+bandit feedback, where all examples belong to one of $K$ classes and lie in the
+$d$-dimensional Euclidean space. Previous works have left open the challenge of
+designing efficient algorithms with finite mistake bounds when the data is
+linearly separable by a margin $\gamma$. In this work, we take a first step
+towards this problem. We identify two notions of linear separability:
+strong linear separability and weak linear separability.
 \begin{enumerate}
-\item Under the OvA
-linear separability condition, we design an efficient algorithm that achieves a near-optimal mistake bound of $O(\frac{K}{\gamma^2})$.
-\item Under the more challenging weakly linear separability condition, we design an efficient algorithm with a mistake bound of $2^{\tilde{O}(\min(K \log^2 \frac 1 \gamma, \log K \sqrt{\frac 1 \gamma})) }$ \footnote{We use the notation $\tilde{O}(f(\cdot)) = O( f(\cdot) \polylog(f(\cdot)) )$.}.
-Our algorithm is based on a reduction from weakly linear separability to OvA linear separability via an infinite dimensional monomial feature map, which in turn is inspired by ~\cite{Klivans-Servedio-2008}'s work on learning intersection of halfspaces.
+\item Under the strong linear separability condition, we design an efficient
+algorithm that achieves a near-optimal mistake bound of $O\left(\frac{K}{\gamma^2} \right)$.
+
+\item Under the more challenging weak linear separability condition, we design
+an efficient algorithm with a mistake bound of $2^{\widetilde{O}(\min(K \log^2
+\frac{1}{\gamma}, \log K \sqrt{\frac 1 \gamma}))}$ \footnote{We use the notation
+$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}. Our algorithm is
+based on a reduction from weak linear separability to strong linear separability
+via an infinite dimensional monomial feature map, which in turn is inspired by
+\cite{Klivans-Servedio-2008}'s work on learning intersection of halfspaces.
 \end{enumerate}
-
-%We focus on the setting where there are $K$ classes, and there is a $d$-dimensional multiclass linear classifier that separates all the examples shown with a positive margin $\gamma$.
-%$2^{O(\min(K \log^2 K \log^2 \frac 1 \gamma, \log K \log \log K \sqrt \frac 1 \gamma \log \frac 1\gamma))}$
-%$\min( (\log K \sqrt{\frac 1 \gamma})^{O(\log K \sqrt{\frac 1 \gamma})}, K^{O(K \log K \log^2 \frac1\gamma)} )$.
-
 \end{abstract}
@@
 \input{introduction}
-
 \input{related-work}
-
 \input{notions-of-linear-separability}
-
 \input{algorithm-for-strongly-linearly-separable-data}
-
 \input{from-linear-separability-to-strong-linear-separability}
-
 \input{proofs-of-polynomial-approximation-theorems}
-
 \input{nearest-neighbor-algorithm}
-
 \input{np-hardness-of-the-weak-labeling-problem}
-
 \input{mistake-lower-bound-for-ignorant-algorithms}

### 2019-01-07 arxiv-version/related-work.tex
Some clean ups

--- 2019-01-07 arxiv-version/related-work.tex
@@
 \label{section:related-work}
-The problem of bandit multiclass linear classification is initially formulated
- by the pioneering work of~\cite{Kakade-Shalev-Shwartz-Tewari-2008}. In that work,
- two computationally
- inefficient algorithms that work in the $\gamma$-weak linearly separable setting are proposed: one with a mistake bound of
- $O(k^2 d \ln(\frac{d}{\gamma^2}))$, the other with a mistake bound of $\tilde{O}(\frac{k^2}{\gamma^2} \ln T)$.
- In addition, the authors propose the Banditron algorithm, a computationally efficient
- algorithm that has a $O(T^{2/3})$ regret in the general setting, and has a
- $O(\sqrt{T})$ mistake bound in the $\gamma$-weak linearly separable setting.
-The polynomial dependence of Banditron's mistake bound on the time horizon is undesirable
-for problems with a long time horizon.
- One key open question left by~\cite{Kakade-Shalev-Shwartz-Tewari-2008} is whether
- one can deesign computationally efficient algorithms that achieve mistake bounds that match or improve over those of inefficient algorithms.
- In this paper, we take a step towards answering this question, showing that
- efficient algorithms with mistake bounds quasipolynomial in the margin parameter can be obtained.
 
- %Whether one can design an efficient algorithm with a
- %finite mistake bound that has no dimensionality dependence is mentioned as an open problem in
- %~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, where in this paper we provide a positive answer.
- %$O(k^2 d \ln(\frac{d}{\gamma^2}))$
+The problem of bandit multiclass linear classification was initially formulated
+by the pioneering work of~\cite{Kakade-Shalev-Shwartz-Tewari-2008}. In that
+work, two computationally inefficient algorithms that work in the $\gamma$-weak
+linearly separable setting are proposed: one with a mistake bound of $O(k^2 d
+\ln(\frac{d}{\gamma^2}))$, the other with a mistake bound of
+$\widetilde{O}(\frac{k^2}{\gamma^2} \ln T)$. In addition, the authors propose
+the \textsc{Banditron} algorithm, a computationally efficient algorithm that has
+a $O(T^{2/3})$ regret in the general setting, and has a $O(\sqrt{T})$ mistake
+bound in the $\gamma$-weak linearly separable setting. The polynomial dependence
+of \textsc{Banditron}'s mistake bound on the time horizon is undesirable for
+problems with a long time horizon. One key open question left
+by~\cite{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can deesign
+computationally efficient algorithms that achieve mistake bounds that match or
+improve over those of inefficient algorithms. In this paper, we take a step
+towards answering this question, showing that efficient algorithms with mistake
+bounds quasipolynomial in the margin parameter can be obtained.
 
-Many works consider bandit multiclass classification in the general non-separable setting.
-\cite{Abernethy-Rakhlin-2009} poses the open problem of whether one can design
-and efficient algorithm to get a $O(\sqrt{T})$ regret against some reasonable loss functions.
-\cite{CrammerG13} shows that such an algorithm can be obtained, under the assumption that the distribution of the label $y$ conditioned on feature $x$ satisfies certain parametric noise assumption.
-\cite{Hazan-Kale-2011} developed the Newtron algorithm, which has a regret
-between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass logistic loss, where the exact order of the regret depends on the diameter of the benchmark class.
-In particular, if the diameter is $O(\ln T)$, its regret bound would become
-$O(T^{2/3})$.
-The SOBA algorithm by \cite{Beygelzimer-Orabona-Zhang-2017} achieves a regret of $\tilde{O}(\sqrt{T})$ against the $\eta$-loss~\cite{Orabona-Cesa-Bianchi-Gentile-2012}; in addition, their regret bound does not depend sensitively on the diameter of the benchmark class.
-\cite{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a regret of $\tilde{O}(\sqrt{T})$ against the multiclass logistic loss, where it doubly-exponentially improves over \cite{Hazan-Kale-2011}'s regret on its dependence on the diameter of the benchmark class.
-Recently, \cite{Foster-Krishnamurthy-2018} developed a rich theory on contextual bandits with surrogate losses, focusing on benchmarks of the form $\min_{f \in \calF} \frac 1 K \sum_{i=1}^K \phi( f_i(x) )$, where $\calF$ contains function $f$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$,
-and $\phi(s) = \max(1 - \frac s \gamma, 0)$ and $\min(1, \max(1 - \frac s \gamma, 0))$.
-On one hand, it gives information-theoretic mistake upper bounds under various settings of $\calF$, for instance parametric and nonparametric classes; On the other hand, it gives an efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of $\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$.
+%Whether one can design an efficient algorithm with a finite mistake bound that
+%has no dimensionality dependence is mentioned as an open problem in
+%~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, where in this paper we provide a
+%positive answer. $O(k^2 d \ln(\frac{d}{\gamma^2}))$
 
-\cite{Chen-Lin-Lu-2014, Zhang-Jung-Tewari-2018} study online bandit multiclass boosting under bandit feedback, where one can view online boosting as online linear classification by treating each base hypothesis as a separate feature.
-\cite{Chen-Lin-Lu-2014}'s online weak learning condition implies that there is a convex combination of base hypotheses that one-versus-all separates all examples with a margin.
-Under this condition, it gives an algorithm with a $O(T^{3/4})$ mistake bound.
-\cite{Zhang-Jung-Tewari-2018} considers an online weak learning condition that implies that there is a convex combination of base hypotheses that weakly separates all examples with a margin (See~\cite{Mukherjee-Schapire-2013}, Theorem 3).
-Under this condition, it gives an algorithm with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge parameter; in addition, it gives an adaptive algorithm with a $O(T^{3/4})$ mistake bound.
+Many works consider bandit multiclass classification in the general
+non-separable setting. \cite{Abernethy-Rakhlin-2009} poses the open problem of
+whether one can design and efficient algorithm to get a $O(\sqrt{T})$ regret
+against some reasonable loss functions. \cite{Crammer-Gentile-2013} show that
+such an algorithm can be obtained, under the assumption that the distribution of
+the label $y_t$ conditioned on feature vector $x_t$ satisfies certain parametric
+noise assumption. \cite{Hazan-Kale-2011} developed the \textsc{Newtron}
+algorithm, which has a regret between $O(\ln T)$ and $O(T^{2/3})$ against the
+multiclass logistic loss, where the exact order of the regret depends on the
+diameter of the benchmark class. In particular, if the diameter is $O(\ln T)$,
+its regret bound would become $O(T^{2/3})$. The SOBA algorithm by
+\cite{Beygelzimer-Orabona-Zhang-2017} achieves a regret of
+$\widetilde{O}(\sqrt{T})$ against the
+$\eta$-loss~\cite{Orabona-Cesa-Bianchi-Gentile-2012}. In addition, their regret
+bound does not depend sensitively on the diameter of the benchmark class.
+\cite{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a
+regret of $\widetilde{O}(\sqrt{T})$ against the multiclass logistic loss, where
+it doubly-exponentially improves over \cite{Hazan-Kale-2011}'s regret on its
+dependence on the diameter of the benchmark class. Recently,
+\cite{Foster-Krishnamurthy-2018} developed a rich theory on contextual bandits
+with surrogate losses, focusing on benchmarks of the form $\min_{f \in \calF}
+\frac{1}{K} \sum_{i=1}^K \phi( f_i(x) )$, where $\calF$ contains function $f$
+such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac s
+\gamma, 0)$ and $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
+information-theoretic mistake upper bounds under various settings of $\calF$,
+for instance parametric and nonparametric classes. On the other hand, it gives
+an efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of
+$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$.
 
-%\cite{Chen-Chen-Zhang-Chen-Zhang-2009} studies the approach of reducing bandit multiclass learning to online binary classification using one-versus-all reduction. They show that
+\cite{Chen-Lin-Lu-2014, Zhang-Jung-Tewari-2018} study online bandit multiclass
+boosting under bandit feedback, where one can view online boosting as online
+linear classification by treating each base hypothesis as a separate feature.
+\cite{Chen-Lin-Lu-2014}'s online weak learning condition implies that there is a
+convex combination of base hypotheses that one-versus-all separates all examples
+with a margin. Under this condition, it gives an algorithm with a $O(T^{3/4})$
+mistake bound. \cite{Zhang-Jung-Tewari-2018} considers an online weak learning
+condition that implies that there is a convex combination of base hypotheses
+that weakly separates all examples with a margin
+(See~\cite{Mukherjee-Schapire-2013}, Theorem 3). Under this condition, it gives
+an algorithm with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge
+parameter. In addition, it gives an adaptive algorithm with a $O(T^{3/4})$
+mistake bound.
 
-%Their results do not imply a finite mistake bound in the weakly separable setting, in that the benchmark loss can still be $\Omega(T)$.
+%\cite{Chen-Chen-Zhang-Chen-Zhang-2009} studies the approach of reducing bandit
+%multiclass learning to online binary classification using one-versus-all
+%reduction. They show that
 
-%\begin{itemize}
-%\item \cite{Abernethy-Rakhlin-2009}
-
-%\item \cite{Chen-Chen-Zhang-Chen-Zhang-2009}
-
-%\item \cite{Hazan-Kale-2011}
-
-%\item \cite{Beygelzimer-Orabona-Zhang-2017}
-
-%\item \cite{Foster-Kale-Luo-Mohri-Sridharan-2018}
-
-%\item \cite{Foster-Krishnamurthy-2018}
-%\end{itemize}
-
-%TODO
+%Their results do not imply a finite mistake bound in the weakly separable
+%setting, in that the benchmark loss can still be $\Omega(T)$.

### 2019-01-09 arxiv-version/main.tex
literature

@@
 linearly separable by a margin $\gamma$. In this work, we take a first step
-towards this problem. We identify two notions of linear separability:
+towards this problem. We consider two notions of linear separability:
 strong linear separability and weak linear separability.
+
 \begin{enumerate}
@@
 $\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}. Our algorithm is
-based on a reduction from weak linear separability to strong linear separability
-via an infinite dimensional monomial feature map, which in turn is inspired by
+based on a infinite-dimensional feature mapping that transforms weak
+linear separable examples to strong linear separable examples, which in turn is inspired by
 \cite{Klivans-Servedio-2008}'s work on learning intersection of halfspaces.

### 2019-01-09 arxiv-version/notions-of-linear-separability.tex
literature

@@
 \begin{definition}[Linear separability]
-Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
-integer, and let $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
+Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
+integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
 y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.
@@
 \end{align}
+\label{def:linear-sep}
+\end{definition}
+
+\begin{definition}[Strong Linear separability]
+Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
+integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
+y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.
 
@@
 \end{align}
+\label{def:strong-linear-sep}
 \end{definition}
 
-The notion of linear separability with a margin is standard. It used in the
+The notion of linear separability with a margin is standard. It is used in the
 full-information setting to upper bound the number of mistakes of the
@@
 The notion of strong linear separability is new.
+\chicheng{I think the notion has appeared in~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}, however,
+they proposed an algorithm that doesn't achieve a finite mistake bound in the bandit
+setting under this assumption (although they claimed that they have done so, the proof was
+wrong..)}
 
@@
 
+\chicheng{Shall we change the $\gamma$ in Equations \eqref{equation:strong-linear-separability-2}, \eqref{equation:strong-linear-separability-3} to $\gamma/2$, to simplify the presentation?}
+
 However, for any $K \ge 3$ and any inner product space of dimension at least

### 2019-01-09 arxiv-version/related-work.tex
literature

@@
 by the pioneering work of~\cite{Kakade-Shalev-Shwartz-Tewari-2008}. In that
-work, two computationally inefficient algorithms that work in the $\gamma$-weak
-linearly separable setting are proposed: one with a mistake bound of $O(k^2 d
+work, two computationally inefficient algorithms that work in the standard
+linearly separable setting are proposed: one with a mistake bound of $O(K^2 d
 \ln(\frac{d}{\gamma^2}))$, the other with a mistake bound of
-$\widetilde{O}(\frac{k^2}{\gamma^2} \ln T)$. In addition, the authors propose
+$\widetilde{O}(\frac{K^2}{\gamma^2} \ln T)$. In addition, the authors propose
 the \textsc{Banditron} algorithm, a computationally efficient algorithm that has
-a $O(T^{2/3})$ regret in the general setting, and has a $O(\sqrt{T})$ mistake
+a $O(T^{2/3})$ regret against the multiclass hinge loss
+in the general setting, and has a $O(\sqrt{T})$ mistake
 bound in the $\gamma$-weak linearly separable setting. The polynomial dependence
@@
 problems with a long time horizon. One key open question left
-by~\cite{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can deesign
+by~\cite{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can design
 computationally efficient algorithms that achieve mistake bounds that match or
@@
 non-separable setting. \cite{Abernethy-Rakhlin-2009} poses the open problem of
-whether one can design and efficient algorithm to get a $O(\sqrt{T})$ regret
+whether one can design an efficient algorithm to get a $O(\sqrt{T})$ regret
 against some reasonable loss functions. \cite{Crammer-Gentile-2013} show that
-such an algorithm can be obtained, under the assumption that the distribution of
+such an algorithm can be obtained, provided that the distribution of
 the label $y_t$ conditioned on feature vector $x_t$ satisfies certain parametric
@@
 diameter of the benchmark class. In particular, if the diameter is $O(\ln T)$,
-its regret bound would become $O(T^{2/3})$. The SOBA algorithm by
+its regret bound would become $O(T^{2/3})$. The \textsc{SOBA} algorithm by
 \cite{Beygelzimer-Orabona-Zhang-2017} achieves a regret of
 $\widetilde{O}(\sqrt{T})$ against the
-$\eta$-loss~\cite{Orabona-Cesa-Bianchi-Gentile-2012}. In addition, their regret
+$\eta$-loss~\cite{Orabona-Cesa-Bianchi-Gentile-2012}. In addition, its regret
 bound does not depend sensitively on the diameter of the benchmark class.
@@
 it doubly-exponentially improves over \cite{Hazan-Kale-2011}'s regret on its
-dependence on the diameter of the benchmark class. Recently,
-\cite{Foster-Krishnamurthy-2018} developed a rich theory on contextual bandits
-with surrogate losses, focusing on benchmarks of the form $\min_{f \in \calF}
-\frac{1}{K} \sum_{i=1}^K \phi( f_i(x) )$, where $\calF$ contains function $f$
-such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac s
-\gamma, 0)$ and $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
-information-theoretic mistake upper bounds under various settings of $\calF$,
-for instance parametric and nonparametric classes. On the other hand, it gives
-an efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of
-$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$.
+dependence on the diameter of the benchmark class.
 
@@
 
+The online bandit multiclass learning is a special case of the contextual bandits
+problem~\cite{Auer-2003, Langford-Zhang-2007}, where the cost is the classification error.
+A series of works in the contextual bandits learning literature focuses on
+oracle-efficiency, that is, they assume access to an
+oracle that given a set of cost-sensitve learning examples,
+
+Recently, \cite{Foster-Krishnamurthy-2018} developed a rich theory on contextual bandits
+with surrogate losses, focusing on benchmarks of the form $\min_{f \in \calF}
+\frac{1}{K} \sum_{i=1}^K l_t(i) \phi( f_i(x) )$, where $\calF$ contains function $f$
+such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac s
+\gamma, 0)$ and $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
+information-theoretic mistake upper bounds under various settings of $\calF$,
+for instance parametric and nonparametric classes. On the other hand, it gives
+an efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of
+$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$.
+
 %\cite{Chen-Chen-Zhang-Chen-Zhang-2009} studies the approach of reducing bandit

### 2019-01-09 ICML-submission/figures/pizza-slice.tex
Start ICML submission

--- 2018-11-30 arxiv-version/figures/pizza-slice.tex
@@
   \coordinate (C) at (120:3);
-  \coordinate [label={[xshift=-6mm, yshift=-4mm]$\gamma$}] (C1) at ($(120:3) + (0.75, 0.43301270189221932338)$);
-  \coordinate [label={[xshift=+3mm, yshift=+2mm]$\gamma$}] (C2) at ($(120:3) - (0.75, 0.43301270189221932338)$);
-  \draw[<->, >=latex, ultra thick] (C1) -- (C) -- (C2);
+  \coordinate (C1) at ($(120:3) + (0.75, 0.43301270189221932338)$);
+  \coordinate (C2) at ($(120:3) - (0.75, 0.43301270189221932338)$);
+  \draw[<->, >=latex, ultra thick] (C1) -- (C);
+  \draw[<->, >=latex, ultra thick] (C2) -- (C);
+  \draw ($0.5*(C1) + 0.5*(C)$) node[above, xshift=-1mm] {$\gamma$};
+  \draw ($0.5*(C2) + 0.5*(C)$) node[above, xshift=-1mm] {$\gamma$};
 
   \coordinate (D) at (240:3);
-  \coordinate [label={[xshift=+4mm, yshift=-8mm]$\gamma$}] (D1) at ($(240:3) + (-0.75, 0.43301270189221932338)$);
-  \coordinate [label={[xshift=-5mm, yshift=-3mm]$\gamma$}] (D2) at ($(240:3) - (-0.75, 0.43301270189221932338)$);
-  \draw[<->, >=latex, ultra thick] (D1) -- (D) -- (D2);
+  \coordinate (D1) at ($(240:3) + (-0.75, 0.43301270189221932338)$);
+  \coordinate (D2) at ($(240:3) - (-0.75, 0.43301270189221932338)$);
+  \draw[<->, >=latex, ultra thick] (D1) -- (D);
+  \draw[<->, >=latex, ultra thick] (D2) -- (D);
+  \draw ($0.5*(D1) + 0.5*(D)$) node[below, xshift=-1mm] {$\gamma$};
+  \draw ($0.5*(D2) + 0.5*(D)$) node[below, xshift=-1mm] {$\gamma$};
 

### 2019-01-09 ICML-submission/introduction.tex
Start ICML submission

--- 2019-01-07 arxiv-version/introduction.tex
@@
 We study the problem of \textsc{Online Multiclass Linear Classification with
-Bandit Feedback}~\cite{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
+Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
 viewed as a game between the learner and the adversary: at each timestep $t$,
@@
 
-In this paper, we focus on the special case when the examples lie in $\R^d$ and
-are \emph{linearly separable with a margin}.
-\chicheng{I wonder if we should introduce the two notions of linear separability here,
-because strong linear separability is also worth mentioning in the full-information setting.
-}
-\david{The formal definitions are in a section of their own.}
+In this paper, we focus on the special case when the examples chosen by the
+adversary lie in $\R^d$ and
+are \emph{linearly separable with a margin}
+(see Definition~\ref{def:linear-sep} for a formal description).
+%\chicheng{I wonder if we should introduce the two notions of linear separability here,
+%because strong linear separability is also worth mentioning in the full-information setting.
+%}
+%\david{The formal definitions are in a section of their own.}
 
@@
 the differences, we dissect the notion of linear separability in the multiclass
-setting. Beside the standard notion of linear separability, we define also
-\emph{strong linear separability}. For binary classification, these two
-definitions are identical. However, they differ for multiclass classification.
-For multiclass classification with $K$ classes the standard notion of linear
+setting. Besides the standard notion of linear separability, we also consider
+\emph{strong linear separability} (see Definition~\ref{def:strong-linear-sep} for a formal description). For binary classification, these two
+definitions are identical.
+However, they differ for multiclass classification with $K \geq 3$.
+For multiclass classification with $K$ classes, the standard notion of linear
 separability means that the examples from each class lie in an intersection of
@@
 For the case when the examples are strongly linearly separable, we design a
-simple and efficient algorithm with expected number of mistakes at most $(K-1)
+simple and efficient algorithm with an expected number of mistakes at most $(K-1)
 \lfloor (R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies
@@
 For the standard notion of linear separability, we propose several algorithms
-with various time-complexity-versus-mistake-bound trade-offs. First class of
+with various time-complexity-versus-mistake-bound trade-offs.
+\chicheng{I wonder if we should just present the results using the rational kernel,
+ as results using other kernels are nonadaptive,
+ and achieve qualitatively similar mistake bounds.}
+First class of
 algorithms map the examples into a high-dimensional inner product space. In this

### 2019-01-09 ICML-submission/main-supplementary.tex
Start ICML submission

--- 2019-01-07 arxiv-version/main.tex
@@
-\documentclass[12pt]{article}
+\documentclass{article}
 
-% LaTeX packages
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage[singlelinecheck=false]{caption}
-\usepackage{fullpage}
-\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
-\usepackage{natbib}
-\usepackage{thmtools}
-\usepackage{tikz}
-\usepackage{color}
-\usepackage{comment}
-\usepackage{commath}
-\usepackage{dsfont}
-
-% TikZ packages
-\usetikzlibrary{arrows}
-\usetikzlibrary{angles}
-\usetikzlibrary{backgrounds}
-\usetikzlibrary{calc}
-\usetikzlibrary{cd}  % commutative diagrams
-\usetikzlibrary{intersections}
-\usetikzlibrary{patterns}
-\usetikzlibrary{shapes}
-\usetikzlibrary{through}
-
-% Math environments
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}[definition]{Proposition}
-\newtheorem{lemma}[definition]{Lemma}
-\newtheorem{theorem}[definition]{Theorem}
-\newtheorem{corollary}[definition]{Corollary}
-
-% Math symbols and commands
-\newcommand{\calF}{\mathcal{F}}
-\newcommand{\one}{\mathds{1}}
-\newcommand{\R}{\mathbb{R}}  % set of real numbers
-\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]} % indicator
-\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
-%\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
-%\DeclareMathOperator*{\deg}{deg}
-
-\DeclareMathOperator*{\argmax}{argmax}
-\DeclareMathOperator*{\argmin}{argmin}
-\DeclareMathOperator*{\Exp}{\mathbf{E}}  % expected value
-\DeclareMathOperator{\diff}{d \!} % differential
-\DeclareMathOperator*{\polylog}{polylog}
-
-\definecolor{darkgreen}{rgb}{0,0.5,0}
-\definecolor{darkred}{rgb}{0.7,0,0}
-\definecolor{teal}{rgb}{0.3,0.8,0.8}
-\definecolor{orange}{rgb}{1.0,0.5,0.0}
-\definecolor{purple}{rgb}{0.8,0.0,0.8}
-\definecolor{blue}{rgb}{0.0,0.0,1.0}
-\newcommand{\kibitz}[2]{{\textcolor{#1}{\textsf{\footnotesize #2}}}}
-\newcommand{\alina}[1]{\kibitz{darkred}{[AB: #1]}}
-\newcommand{\david}[1]{\kibitz{darkgreen}{[DP: #1]}}
-\newcommand{\balazs}[1]{\kibitz{purple}{[BS: #1]}}
-\newcommand{\deva}[1]{\kibitz{teal}{[DT: #1]}}
-\newcommand{\chenyu}[1]{\kibitz{orange}{[CW: #1]}}
-\newcommand{\chicheng}[1]{\kibitz{blue}{[CZ: #1]}}
-
-\title{Online Multiclass Linear Classification with Bandit Feedback}
-
-\author{
-Alina Beygelzimer \and
-D\'avid P\'al \and
-Bal\'azs Sz\"or\'enyi \and
-Devanathan Thiruvenkatachari \and
-Chen-Yu Wei \and
-Chicheng Zhang
-}
+\input{commands}
 
@@
 
-\maketitle
-
-\begin{abstract}
-We study the problem of efficient online multiclass linear classification with
-bandit feedback, where all examples belong to one of $K$ classes and lie in the
-$d$-dimensional Euclidean space. Previous works have left open the challenge of
-designing efficient algorithms with finite mistake bounds when the data is
-linearly separable by a margin $\gamma$. In this work, we take a first step
-towards this problem. We identify two notions of linear separability:
-strong linear separability and weak linear separability.
-\begin{enumerate}
-\item Under the strong linear separability condition, we design an efficient
-algorithm that achieves a near-optimal mistake bound of $O\left(\frac{K}{\gamma^2} \right)$.
-
-\item Under the more challenging weak linear separability condition, we design
-an efficient algorithm with a mistake bound of $2^{\widetilde{O}(\min(K \log^2
-\frac{1}{\gamma}, \log K \sqrt{\frac 1 \gamma}))}$ \footnote{We use the notation
-$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}. Our algorithm is
-based on a reduction from weak linear separability to strong linear separability
-via an infinite dimensional monomial feature map, which in turn is inspired by
-\cite{Klivans-Servedio-2008}'s work on learning intersection of halfspaces.
-\end{enumerate}
-\end{abstract}
-
+\input{title-and-abstract}
 \input{introduction}
@@
 \input{notions-of-linear-separability}
-\input{algorithm-for-strongly-linearly-separable-data}
-\input{from-linear-separability-to-strong-linear-separability}
-\input{proofs-of-polynomial-approximation-theorems}
-\input{nearest-neighbor-algorithm}
-\input{np-hardness-of-the-weak-labeling-problem}
-\input{mistake-lower-bound-for-ignorant-algorithms}
 
-\bibliographystyle{plainnat}
 \bibliography{biblio}
+\bibliographystyle{icml2019}
 
+% For actual submission remove everything below.
+% Use appendices only in supplementray material.
 \appendix
-
-\input{appendix-multiclass-perceptron}
+\clearpage
 

### 2019-01-09 ICML-submission/figures/linearly-separable-examples-with-margin.py

@@ -1,0 +1,78 @@
+#!/usr/bin/env python3
+
+import math
+import random
+
+NUMBER_CLASSES = 3
+NUMBER_EXAMPLES_PER_CLASS = 300
+RADIUS = 4.8
+MINIMUM_MARGIN = 0.5
+MINIMUM_DISTANCE = 0.7
+
+
+def print_points(points):
+    points.sort()
+    for angle, radius in points:
+        print("({:.2f}:{:.2f}) circle (2pt)".format(angle, radius))
+
+
+def distance(p, q):
+    p_angle, p_radius = p
+    px = p_radius * math.cos(math.radians(p_angle))
+    py = p_radius * math.sin(math.radians(p_angle))
+
+    q_angle, q_radius = q
+    qx = q_radius * math.cos(math.radians(q_angle))
+    qy = q_radius * math.sin(math.radians(q_angle))
+
+    dx = px - qx
+    dy = py - qy
+    return math.sqrt(dx * dx + dy * dy)
+
+
+def remove_close_points(points):
+    filtered = set()
+    for p in points:
+        is_close = False
+        for q in filtered:
+            if distance(p, q) < MINIMUM_DISTANCE:
+                is_close = True
+                break
+        if not is_close:
+            filtered.add(p)
+
+    return list(filtered)
+
+
+def margin(point, normal_angle):
+    normal_x = math.cos(math.radians(normal_angle))
+    normal_y = math.sin(math.radians(normal_angle))
+
+    angle, radius = point
+    x = radius * math.cos(math.radians(angle))
+    y = radius * math.sin(math.radians(angle))
+
+    margin = (x * normal_x) + (y * normal_y)
+    return margin
+
+
+def main():
+    for j in range(NUMBER_CLASSES):
+        begin_angle = 360.0 * j / NUMBER_CLASSES
+        end_angle = 360.0 * (j + 1) / NUMBER_CLASSES
+        print("% Class {} points. Angles between {} and {}".format(j, begin_angle, end_angle))
+        points = []
+        for i in range(NUMBER_EXAMPLES_PER_CLASS):
+            angle = random.uniform(begin_angle, end_angle)
+            radius = random.uniform(0, RADIUS)
+            point = (angle, radius)
+            if (margin(point, begin_angle + 90.0) > MINIMUM_MARGIN) and (margin(point, end_angle + 90.0) < - MINIMUM_MARGIN):
+                points.append(point)
+        points = remove_close_points(points)
[…]

### 2019-01-09 arxiv-version/algorithm-for-strongly-linearly-separable-data.tex
relwork, and some comments

@@
 
+\chicheng{I think this part need to be formalized. Can we assume without loss of generality
+that a deterministic prediction algorithm will have a smaller expected cost?
+If so, define $F(k)$ be the number of mistake that will be made by the algorithm,
+if the adversary commits to a label uniformly at random from $\cbr{1,2,\ldots,k}$,
+and the guessing of the label lasts for $k$ rounds.
+we can construct a recurrence of $F$: $F(k) = F(k-1) + \frac{k-1}{k}$, and $F(1) = 0$.
+Therefore, $F(K) = \Omega(K)$.}
+
 Finally, since strong separability and norm condition hold with probability one,

### 2019-01-09 arxiv-version/notions-of-linear-separability.tex
relwork, and some comments

@@
 
-\begin{definition}[Strong Linear separability]
+\begin{definition}[Strong linear separability]
 Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
@@
 folklore result that if a set of labeled examples is separable with a margin
-$\gamma$ and the norm of the examples is bounded by $R$ then \textsc{Multiclass
+$\gamma$ and the norm of the examples is bounded by $R$, then \textsc{Multiclass
 Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
@@
 
-The notion of strong linear separability is new.
+The notion of strong linear separability is new. Intuitively, strong linear separability
+means that, for each $i$, the set of examples with class $i$ and the set of example of other classes are separated by a linear classifier $w_i$.
+Formally, $w_i$ separates the set of examples $\cbr{(x_t, y_t): t \in \cbr{1,\ldots,T}, y_t = i}$ and
+$\cbr{(x_t, y_t): t \in \cbr{1,\ldots,T}, y_t \neq i}$.
+
 \chicheng{I think the notion has appeared in~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}, however,
@@
 
-It is easy to see that if labeled examples are strongly linearly
-separable with margin $\gamma$ then they are linearly separable with margin
+It is easy to see that if a set of labeled examples are strongly linearly
+separable with margin $\gamma$, then they are linearly separable with margin
 $2\gamma$. Indeed, if $w_1, w_2, \dots, w_K \in V$

### 2019-01-09 arxiv-version/related-work.tex
relwork, and some comments

@@
 linear classification by treating each base hypothesis as a separate feature.
-\cite{Chen-Lin-Lu-2014}'s online weak learning condition implies that there is a
-convex combination of base hypotheses that one-versus-all separates all examples
+\cite{Chen-Lin-Lu-2014}'s online weak learning condition implies that
+the set of examples is strongly separable by a convex combination of base hypotheses
 with a margin. Under this condition, it gives an algorithm with a $O(T^{3/4})$
 mistake bound. \cite{Zhang-Jung-Tewari-2018} considers an online weak learning
-condition that implies that there is a convex combination of base hypotheses
-that weakly separates all examples with a margin
-(See~\cite{Mukherjee-Schapire-2013}, Theorem 3). Under this condition, it gives
-an algorithm with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge
+condition, which implies that all examples is separable by a convex combination of base hypotheses with a margin (See~\cite{Mukherjee-Schapire-2013}, Theorem 3).
+Under this condition, it gives
+a boosting algorithm with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge
 parameter. In addition, it gives an adaptive algorithm with a $O(T^{3/4})$
@@
 
-The online bandit multiclass learning is a special case of the contextual bandits
-problem~\cite{Auer-2003, Langford-Zhang-2007}, where the cost is the classification error.
-A series of works in the contextual bandits learning literature focuses on
-oracle-efficiency, that is, they assume access to an
-oracle that given a set of cost-sensitve learning examples,
+There has been much literature on the contextual bandit learning problem~\citep{Auer-2003, Langford-Zhang-2007}.
+In this problem, the learner is given a policy class $\Pi$, and
+at each timestep $t$, an example $x_t$ is shown, with an associated cost vector $c_t$ hidden.
+The learner then takes an action $\hat{y}_t$, and observed the incurred cost $c_t$.
+The goal of the learner is to minimize its regret $\sum_{t=1}^T c_t(\hat{y}_t) - \min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
+The online bandit multiclass learning problem is a special case of the contextual bandits problem,
+where the cost $c_t(i)$ is the classification error $I(i \neq y_t)$,
+and the policy class $\Pi$ is the set of linear classifiers
+$\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$.
+A series of works in the contextual bandits learning literature focus on
+oracle-efficiency~\citep{DudikHKKLRZ11, Monster:2014, RakhlinS16, Syrgkanis2016a, Syrgkanis2016b}.
+Specifically, they assume access to a policy optimization
+oracle that receives a set of cost-sensitive learning examples and policy class $\Pi$,
+return the policy in $\Pi$ that minimizes its empirical cost on the examples, and the algorithm
+only call the oracle a polynomial number of times.
+However, these algorithms are not truly computationally efficient in our setting,
+as it is NP-hard in general to find a linear classifier that minimizes the empirical cost over a set of examples~\citep{arora1997hardness}.
 
-Recently, \cite{Foster-Krishnamurthy-2018} developed a rich theory on contextual bandits
+%as algorithms generate cost-sensitive examples that may not be linearly separable
+%Algorithms that satisfy oracle efficiency has been proposed in the literature, for
+%example.
+
+Recently, \cite{Foster-Krishnamurthy-2018} developed a rich theory of contextual bandits
 with surrogate losses, focusing on benchmarks of the form $\min_{f \in \calF}
-\frac{1}{K} \sum_{i=1}^K l_t(i) \phi( f_i(x) )$, where $\calF$ contains function $f$
+\sum_{t=1}^T \frac{1}{K} \sum_{i=1}^K c_t(i) \phi( f_i(x_t) )$,
+where $\calF$ contains score functions $f$
 such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac s
-\gamma, 0)$ and $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
+\gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
 information-theoretic mistake upper bounds under various settings of $\calF$,
-for instance parametric and nonparametric classes. On the other hand, it gives
+including parametric and nonparametric classes. On the other hand, it gives
 an efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of
-$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$.
+$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$. A direct
+application of this result to the online bandit multiclass learning problem
+yields an algorithm with a $O(\sqrt{T})$ mistake bound in the strong
+linearly separable setting.
 

### 2019-01-09 ICML-submission/related-work.tex

--- 2019-01-09 arxiv-version/related-work.tex
@@
 The online bandit multiclass learning is a special case of the contextual bandits
-problem~\cite{Auer-2003, Langford-Zhang-2007}, where the cost is the classification error.
+problem~\cite{Auer-2003, Langford-Zhang-2008}, where the cost is the classification error.
 A series of works in the contextual bandits learning literature focuses on

### 2019-01-09 ICML-submission/title-and-abstract.tex

--- 2019-01-09 arxiv-version/main.tex
@@
-\documentclass[12pt]{article}
+% The \icmltitle you define below is probably too long as a header.
+% Therefore, a short form for the running title is supplied here:
+\icmltitlerunning{Online Multiclass Linear Classification with Bandit Feedback}
 
-% LaTeX packages
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage[singlelinecheck=false]{caption}
-\usepackage{fullpage}
-\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
-\usepackage{natbib}
-\usepackage{thmtools}
-\usepackage{tikz}
-\usepackage{color}
-\usepackage{comment}
-\usepackage{commath}
-\usepackage{dsfont}
+\twocolumn[
+\icmltitle{Online Multiclass Linear Classification with Bandit Feedback}
 
-% TikZ packages
-\usetikzlibrary{arrows}
-\usetikzlibrary{angles}
-\usetikzlibrary{backgrounds}
-\usetikzlibrary{calc}
-\usetikzlibrary{cd}  % commutative diagrams
-\usetikzlibrary{intersections}
-\usetikzlibrary{patterns}
-\usetikzlibrary{shapes}
-\usetikzlibrary{through}
+\begin{icmlauthorlist}
+\icmlauthor{Alina Beygelzimer}{yahoo}
+\icmlauthor{D\'avid P\'al}{yahoo}
+\icmlauthor{Bal\'azs Sz\"or\'enyi}{yahoo}
+\icmlauthor{Devanathan Thiruvenkatachari}{nyu}
+\icmlauthor{Chen-Yu Wei}{usc}
+\icmlauthor{Chicheng Zhang}{microsoft}
 
-% Math environments
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}[definition]{Proposition}
-\newtheorem{lemma}[definition]{Lemma}
-\newtheorem{theorem}[definition]{Theorem}
-\newtheorem{corollary}[definition]{Corollary}
+\end{icmlauthorlist}
 
-% Math symbols and commands
-\newcommand{\calF}{\mathcal{F}}
-\newcommand{\one}{\mathds{1}}
-\newcommand{\R}{\mathbb{R}}  % set of real numbers
-\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]} % indicator
-\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
-%\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
-%\DeclareMathOperator*{\deg}{deg}
+\icmlaffiliation{yahoo}{Yahoo Research, New York, NY, USA}
+\icmlaffiliation{nyu}{New York University, New York, MA, USA}
+\icmlaffiliation{usc}{University of Southern California, Los Angeles, CA, USA}
+\icmlaffiliation{microsoft}{Microsoft Research, New York, NY, USA}
 
-\DeclareMathOperator*{\argmax}{argmax}
-\DeclareMathOperator*{\argmin}{argmin}
-\DeclareMathOperator*{\Exp}{\mathbf{E}}  % expected value
-\DeclareMathOperator{\diff}{d \!} % differential
-\DeclareMathOperator*{\polylog}{polylog}
+\icmlcorrespondingauthor{D\'avid P\'al}{davidko.pal@gmail.com}
 
-\definecolor{darkgreen}{rgb}{0,0.5,0}
-\definecolor{darkred}{rgb}{0.7,0,0}
-\definecolor{teal}{rgb}{0.3,0.8,0.8}
-\definecolor{orange}{rgb}{1.0,0.5,0.0}
-\definecolor{purple}{rgb}{0.8,0.0,0.8}
-\definecolor{blue}{rgb}{0.0,0.0,1.0}
-\newcommand{\kibitz}[2]{{\textcolor{#1}{\textsf{\footnotesize #2}}}}
-\newcommand{\alina}[1]{\kibitz{darkred}{[AB: #1]}}
-\newcommand{\david}[1]{\kibitz{darkgreen}{[DP: #1]}}
-\newcommand{\balazs}[1]{\kibitz{purple}{[BS: #1]}}
-\newcommand{\deva}[1]{\kibitz{teal}{[DT: #1]}}
-\newcommand{\chenyu}[1]{\kibitz{orange}{[CW: #1]}}
-\newcommand{\chicheng}[1]{\kibitz{blue}{[CZ: #1]}}
+\icmlkeywords{multi-armed bandits, contextual bandits, online classification, linear separability}
 
-\title{Online Multiclass Linear Classification with Bandit Feedback}
+\vskip 0.3in
+]
 
-\author{
-Alina Beygelzimer \and
-D\'avid P\'al \and
-Bal\'azs Sz\"or\'enyi \and
-Devanathan Thiruvenkatachari \and
-Chen-Yu Wei \and
-Chicheng Zhang
-}
-
-\begin{document}
-
-\maketitle
+\printAffiliationsAndNotice{}
 
@@
 linearly separable by a margin $\gamma$. In this work, we take a first step
-towards this problem. We consider two notions of linear separability:
-strong linear separability and weak linear separability.
+towards this problem. We consider two notions of linear separability: strong
+linear separability and weak linear separability.
 
@@
 \item Under the strong linear separability condition, we design an efficient
-algorithm that achieves a near-optimal mistake bound of $O\left(\frac{K}{\gamma^2} \right)$.
+algorithm that achieves a near-optimal mistake bound of
+$O\left(\frac{K}{\gamma^2} \right)$.
 
@@
 $\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}. Our algorithm is
-based on a infinite-dimensional feature mapping that transforms weak
-linear separable examples to strong linear separable examples, which in turn is inspired by
-\cite{Klivans-Servedio-2008}'s work on learning intersection of halfspaces.
+based on a infinite-dimensional feature mapping that transforms weak linear
+separable examples to strong linear separable examples, which in turn is
+inspired by \cite{Klivans-Servedio-2008}'s work on learning intersection of
+halfspaces.
 \end{enumerate}
 \end{abstract}
-
-\input{introduction}
-\input{related-work}
-\input{notions-of-linear-separability}
-\input{algorithm-for-strongly-linearly-separable-data}
-\input{from-linear-separability-to-strong-linear-separability}
-\input{proofs-of-polynomial-approximation-theorems}
-\input{nearest-neighbor-algorithm}
-\input{np-hardness-of-the-weak-labeling-problem}
-\input{mistake-lower-bound-for-ignorant-algorithms}
-
-\bibliographystyle{plainnat}
-\bibliography{biblio}
-
-\appendix
-
-\input{appendix-multiclass-perceptron}
-
-\end{document}

### 2019-01-09 arxiv-version/related-work.tex

@@
 
+The online bandit multiclass learning is a special case of the contextual bandits
+problem~\cite{Auer-2003, Langford-Zhang-2008}, where the cost is the classification error.
+A series of works in the contextual bandits learning literature focuses on
+oracle-efficiency, that is, they assume access to an
+oracle that given a set of cost-sensitve learning examples,
+
 There has been much literature on the contextual bandit learning problem~\citep{Auer-2003, Langford-Zhang-2007}.

### 2019-01-09 ICML-submission/related-work.tex
Fix bibfiles

--- 2019-01-09 arxiv-version/related-work.tex
@@
 
-There has been much literature on the contextual bandit learning problem~\citep{Auer-2003, Langford-Zhang-2007}.
+The online bandit multiclass learning is a special case of the contextual bandits
+problem~\cite{Auer-2003, Langford-Zhang-2008}, where the cost is the classification error.
+A series of works in the contextual bandits learning literature focuses on
+oracle-efficiency, that is, they assume access to an
+oracle that given a set of cost-sensitve learning examples,
+
+There has been much literature on the contextual bandit learning problem~\citep{Auer-2003, Langford-Zhang-2008}.
 In this problem, the learner is given a policy class $\Pi$, and
@@
 A series of works in the contextual bandits learning literature focus on
-oracle-efficiency~\citep{DudikHKKLRZ11, Monster:2014, RakhlinS16, Syrgkanis2016a, Syrgkanis2016b}.
+oracle-efficiency~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
+Agarwal-Hsu-Kale-Langford-Li-Schapire-2014,
+Rakhlin-Sridharan-2016,
+Syrgkanis-Krishnamurthy-Schapire-2016,
+Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
 Specifically, they assume access to a policy optimization
@@
 However, these algorithms are not truly computationally efficient in our setting,
-as it is NP-hard in general to find a linear classifier that minimizes the empirical cost over a set of examples~\citep{arora1997hardness}.
+as it is NP-hard in general to find a linear classifier that minimizes the empirical cost over a set of examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.
 

### 2019-01-09 arxiv-version/main.tex
Fix bibfiles

@@
 $\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}. Our algorithm is
-based on a infinite-dimensional feature mapping that transforms weak
-linear separable examples to strong linear separable examples, which in turn is inspired by
-\cite{Klivans-Servedio-2008}'s work on learning intersection of halfspaces.
+based on a infinite-dimensional feature mapping that transforms weak linear
+separable examples to strong linear separable examples, which in turn is
+inspired by \cite{Klivans-Servedio-2008}'s work on learning intersection of
+halfspaces.
 \end{enumerate}

### 2019-01-09 ICML-submission/introduction.tex
Fix formatting of definitions

@@
 In this paper, we focus on the special case when the examples chosen by the
-adversary lie in $\R^d$ and
-are \emph{linearly separable with a margin}
-(see Definition~\ref{def:linear-sep} for a formal description).
+adversary lie in $\R^d$ and are \emph{linearly separable with a margin} (see
+\autoref{definition:linear-separability} for a formal description).
 %\chicheng{I wonder if we should introduce the two notions of linear separability here,
@@
 
-In the full-information feedback
-setting, it is well known that if the examples have norm at most $R$ and are
-linearly separable with a margin $\gamma$ then the \textsc{Multiclass
-Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
-This result is very satisfying since the upper bound on the number of mistakes
-is information-theoretically optimal and at the same time the \textsc{Multiclass
-Perceptron} algorithm has low time and memory complexity.
+In the full-information feedback setting, it is well known that if the examples
+have norm at most $R$ and are linearly separable with a margin $\gamma$ then the
+\textsc{Multiclass Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2
+\rfloor$ mistakes. This result is very satisfying since the upper bound on the
+number of mistakes is information-theoretically optimal and at the same time the
+\textsc{Multiclass Perceptron} algorithm has low time and memory complexity.
 
@@
 setting. Besides the standard notion of linear separability, we also consider
-\emph{strong linear separability} (see Definition~\ref{def:strong-linear-sep} for a formal description). For binary classification, these two
-definitions are identical.
-However, they differ for multiclass classification with $K \geq 3$.
-For multiclass classification with $K$ classes, the standard notion of linear
-separability means that the examples from each class lie in an intersection of
-$K-1$ halfspaces and the examples outside of the class lie in the complement of
-the intersection of the halfspaces. Strong linear separability means that
-examples from each class are separated from the remaining examples by a
-\emph{single} hyperplane. We state the definitions precisely in
+\emph{strong linear separability} (see
+\autoref{definition:strong-linear-separability} for a formal description). For
+binary classification, these two definitions are identical. However, they differ
+for multiclass classification with $K \geq 3$. For multiclass classification
+with $K$ classes, the standard notion of linear separability means that the
+examples from each class lie in an intersection of $K-1$ halfspaces and the
+examples outside of the class lie in the complement of the intersection of the
+halfspaces. Strong linear separability means that examples from each class are
+separated from the remaining examples by a \emph{single} hyperplane. We state
+the definitions precisely in
 Section~\ref{section:notions-of-linear-separability}.

### 2019-01-09 ICML-submission/notions-of-linear-separability.tex
Fix formatting of definitions

--- 2019-01-09 arxiv-version/notions-of-linear-separability.tex
@@
 \begin{definition}[Linear separability]
+\label{definition:linear-separability}
 Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
@@
 \label{equation:linear-separability-1}
-\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
+& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
 \label{equation:linear-separability-2}
-\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} & \ge \ip{x_t}{w_i} + \gamma \; .
+& \begin{gathered}
+\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
+\ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; .
+\end{gathered}
 \end{align}
-\label{def:linear-sep}
 \end{definition}
@@
 \begin{definition}[Strong linear separability]
+\label{definition:strong-linear-separability}
 Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
@@
 \label{equation:strong-linear-separability-1}
-\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
+& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
 \label{equation:strong-linear-separability-2}
-\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
+& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \gamma \; , \\
 \label{equation:strong-linear-separability-3}
-\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
+& \begin{gathered}
+\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
+\ip{x_t}{w_i} \le - \gamma \; .
+\end{gathered}
 \end{align}
-\label{def:strong-linear-sep}
 \end{definition}

### 2019-01-09 ICML-submission/appendix-multiclass-perceptron.tex
Fix formatting in multi-class perceptron appendix

--- 2019-01-07 arxiv-version/appendix-multiclass-perceptron.tex
@@
 \begin{align*}
-\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
-& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) + \norm{w_{y_t}^{(t)} + x_t}^2 + \norm{w_{\widehat y_t}^{(t)} - x_t}^2 \\
-& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) + \norm{w_{y_t}^{(t)}}^2 + \norm{w_{\widehat y_t}^{(t)}}^2 + 2 \norm{x_t}^2 + 2 \ip{w_{y_t}^{(t)} - w_{\widehat y_t}^{(t)}}{x_t} \\
+& \sum_{i=1}^K \norm{w_i^{(t+1)}}^2 \\
+& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) \\
+& \qquad + \norm{w_{y_t}^{(t)} + x_t}^2 + \norm{w_{\widehat y_t}^{(t)} - x_t}^2 \\
+& = \left(\sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\} } \norm{w_i^{(t)}}^2 \right) + \norm{w_{y_t}^{(t)}}^2 + \norm{w_{\widehat y_t}^{(t)}}^2 \\
+& \qquad + 2 \norm{x_t}^2 + 2 \ip{w_{y_t}^{(t)} - w_{\widehat y_t}^{(t)}}{x_t} \\
 & = \left(\sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + 2 \norm{x_t}^2 + 2 \ip{w_{y_t}^{(t)} - w_{\widehat y_t}^{(t)}}{x_t} \\
@@
 \begin{align*}
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(t+1)}}
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^*}{w_{y_t}^{(t)} + x_t} + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} - x_t} \\
+& \sum_{i=1}^K \ip{w_i^*}{w_i^{(t+1)}} \\
+& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) \\
+& \qquad + \ip{w_{y_t}^*}{w_{y_t}^{(t)} + x_t} + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} - x_t} \\
 & = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{y_t}^* - w_{\widehat y_t}^*}{x_t} \\
@@
 w_K^*$. We have
-$$
+\begin{align*}
 \sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
-\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
-$$
+& \le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}} \\
+& \le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \\
+& \le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
+\end{align*}
 Combining all inequalities, we get
@@
 $$
-w_i = \frac{1}{R\sqrt{T}} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} x_t \qquad \qquad \text{for $i=1,2,\dots,K$.}
+w_i = \frac{1}{R\sqrt{T}} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} x_t \qquad \text{for $i=1,2,\dots,K$.}
 $$
@@
 $$
-\norm{w_i}^2 = \frac{1}{R^2 T} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} \norm{x_t}^2 = \frac{a_i}{T} \qquad \qquad \text{for $i=1,2,\dots,K$.}
+\norm{w_i}^2 = \frac{1}{R^2 T} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} \norm{x_t}^2 = \frac{a_i}{T} \qquad \text{for $i=1,2,\dots,K$.}
 $$
@@
 y_t)$. Then, by definition of $w_{y_t}$ we have
-$$
+\begin{align*}
 \ip{w_{y_t}}{x_t}
-= \frac{1}{R\sqrt{T}} \sum_{\substack{s : 1 \le s \le T \\ y_s = y_t}} \ip{x_s}{x_t}
-= \frac{1}{R\sqrt{T}} \norm{x_t}^2
-= \frac{R}{\sqrt{T}}
-\ge \frac{R}{R/\gamma}
-= \gamma \; .
-$$
+& = \frac{1}{R\sqrt{T}} \sum_{\substack{s : 1 \le s \le T \\ y_s = y_t}} \ip{x_s}{x_t} \\
+& = \frac{1}{R\sqrt{T}} \norm{x_t}^2 \\
+& = \frac{R}{\sqrt{T}} \\
+& \ge \frac{R}{R/\gamma} \\
+& = \gamma \; .
+\end{align*}
 and for any $i \in \{1,2,\dots,K\} \setminus \{y_t\}$ we have

### 2019-01-09 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Add algorithm for strongly separable data

--- 2019-01-09 arxiv-version/algorithm-for-strongly-linearly-separable-data.tex
@@
 {
-\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
+\REQUIRE{Number of classes $K$.}
+\REQUIRE{Number of rounds $T$.}
+\REQUIRE{Inner product space $(V,\ip{\cdot}{\cdot})$.}
 \STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
@@
 \STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
+\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
 \IF{$z_t = 1$}
@@
 \ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
+\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ \\ \qquad  for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
 \STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$}
@@
 \STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
+\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
 \IF{$z_t = 1$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
+\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
 \STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
@@
 \begin{align*}
-\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
+& \sum_{i=1}^K \norm{w_i^{(t+1)}}^2 \\
 & = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t+1)}}^2 \\
@@
 \begin{align*}
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}
+& \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \\
 & = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
+& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) \\
+& \qquad + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
 & = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
@@
 \eqref{equation:strong-linear-separability-1}, we get that
-$$
+\begin{align*}
 \sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
-\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
-\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
-$$
+& \le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}} \\
+& \le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \\
+& \le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
+\end{align*}
 Combining the upper and lower bounds on $\sum_{i=1}^K \norm{w_i^{(T+1)}}^2$ inequalities, we get
@@
 \begin{proof}
-We use probabilistic method. Let $M = \left\lfloor \frac{1}{16} (R/\gamma)^2 \right\rfloor$.
-Let $V = \R^{M+1}$ equipped with the standard inner product.  Let $e_1, e_2,
-\dots, e_{M+1}$ be the standard orthonormal basis of $V$. We define
-vectors $v_1, v_2, \dots, v_M \in V$ where $v_i = \frac{R}{\sqrt{2}}(e_i +
-e_{M+1})$ for $i=1,2,\dots,M$. Let $\ell_1, \ell_2, \dots, \ell_M$ be chosen
+We use probabilistic method. Let $M = \left\lfloor \frac{1}{16} (R/\gamma)^2
+\right\rfloor$. Let $V = \R^{M+1}$ equipped with the standard inner product.
+Let $e_1, e_2, \dots, e_{M+1}$ be the standard orthonormal basis of $V$. We
+define vectors $v_1, v_2, \dots, v_M \in V$ where $v_i = \frac{R}{\sqrt{2}}(e_i
++ e_{M+1})$ for $i=1,2,\dots,M$. Let $\ell_1, \ell_2, \dots, \ell_M$ be chosen
 i.i.d. uniformly at random from $\{1,2,\dots,K\}$ and independently of any
 randomness used the by the algorithm. Let $T = M K$. We define examples $(x_1,
-y_1), (x_2, y_2), \dots, (x_T, y_T)$ as follows:
+y_1), (x_2, y_2), \dots, (x_T, y_T)$ as follows. For any $j=1,2,\dots,M$ and any
+$i=1,2,\dots,K$,
 $$
-\begin{array}{lclclclcl}
-(x_1, y_1) & = & (x_2, y_2) & = & \cdots & = & (x_K, y_K) & = & (v_1, \ell_1) \; , \\
-(x_{K+1},y_{K+1}) & = & (x_{K+2}, y_{K+2}) & = & \cdots & = & (x_{2K}, y_{2K}) & = & (v_2, \ell_2) \; , \\
-& \vdots & \\
-(x_{(M-1)K+1}, y_{(M-1)K+1})  & = & (x_{(M-1)K+2}, y_{(M-1)K+2}) & = & \cdots & = & (x_{MK}, y_{MK}) & = & (v_M, \ell_M) \; .
-\end{array}
+(x_{(j-1)K + i}, y_{(j-1)K + i}) = (v_j, \ell_j)
 $$
@@
 $$
-w_i^* = 2 \sqrt{2} \frac{\gamma}{R} \left( \sum_{j ~:~ \ell_j = i} e_j \right) - \sqrt{2} \frac{\gamma}{R} e_{M+1} \qquad \quad \text{for $i=1,2,\dots,K$.}
+w_i^* = 2 \sqrt{2} \frac{\gamma}{R} \left( \sum_{j ~:~ \ell_j = i} e_j \right) - \sqrt{2} \frac{\gamma}{R} e_{M+1}
 $$
-Since for any $i \in \{1,2,\dots,K\}$ and any $j \in \{1,2,\dots,M\}$,
+for $i=1,2,\dots,K$. Since for any $i \in \{1,2,\dots,K\}$ and any $j \in
+\{1,2,\dots,M\}$,
 $$
@@
 is satisfied since
-$$
+\begin{multline*}
 \sum_{i=1}^K \norm{w_i^*}^2
-= 8 \frac{\gamma^2}{R^2} \sum_{j=1}^M \norm{e_j}^2 + 2 \frac{\gamma^2}{R^2} K \norm{e_{M+1}}^2
+= 8 \frac{\gamma^2}{R^2} \sum_{j=1}^M \norm{e_j}^2 + 2 \frac{\gamma^2}{R^2} K \norm{e_{M+1}}^2 \\
 = 8 \frac{\gamma^2}{R^2} M + 2 \frac{\gamma^2}{R^2} K
@@
 = 1 \; .
-$$
+\end{multline*}
 

### 2019-01-09 ICML-submission/appendix-multiclass-perceptron.tex
Add algorithm for strongly separable data
Rename linear separability to weak linear separability

@@
 \IF{$\widehat y_t \neq y_t$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}$}
+\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}$}
 \STATE{Update $w_{y_t}^{(t+1)} = w_{y_t}^{(t)} + x_t$}
@@
 number. If $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled
-examples in $V \times \{1,2,\dots,K\}$ that are linearly separable with margin
+examples in $V \times \{1,2,\dots,K\}$ that are weakly linearly separable with margin
 $\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
@@
 Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors satisfying the
-\eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2}. We lower bound $\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$. This quantity changes
+\eqref{equation:weak-linear-separability-1} and
+\eqref{equation:weak-linear-separability-2}. We lower bound $\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$. This quantity changes
 only when a mistakes happens. If mistake happens in round $t$, we have
@@
 We upper bound the left hand side by using Cauchy-Schwartz inequality twice and
-the condition \eqref{equation:linear-separability-1} on $w_1^*, w_2^*, \dots,
+the condition \eqref{equation:weak-linear-separability-1} on $w_1^*, w_2^*, \dots,
 w_K^*$. We have
@@
 sequence of labeled examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$
-examples in $V \times \{1,2,\dots,K\}$ that are linearly separable with margin
+examples in $V \times \{1,2,\dots,K\}$ that are weakly linearly separable with margin
 $\gamma$, the norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
@@
 with margin $\gamma$. To prove that we demonstrate vectors $w_1, w_2, \dots, w_K$
-satisfying conditions \eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2}. We define
+satisfying conditions \eqref{equation:weak-linear-separability-1} and
+\eqref{equation:weak-linear-separability-2}. We define
 $$
@@
 Since $\sum_{i=1}^K a_i = T$, the condition
-\eqref{equation:linear-separability-1} holds. To verify condition
-\eqref{equation:linear-separability-2} consider any labeled example $(x_t,
+\eqref{equation:weak-linear-separability-1} holds. To verify condition
+\eqref{equation:weak-linear-separability-2} consider any labeled example $(x_t,
 y_t)$. Then, by definition of $w_{y_t}$ we have
@@
 and for any $i \in \{1,2,\dots,K\} \setminus \{y_t\}$ we have
-$\ip{w_i}{x_t} = 0$. Therefore, condition \eqref{equation:linear-separability-2} holds.
+$\ip{w_i}{x_t} = 0$. Therefore, condition \eqref{equation:weak-linear-separability-2} holds.
 \end{proof}

### 2019-01-09 ICML-submission/introduction.tex
Add algorithm for strongly separable data
Rename linear separability to weak linear separability

--- 2019-01-09 ICML-submission/introduction.tex
@@
 Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
-viewed as a game between the learner and the adversary: at each timestep $t$,
-the adversary chooses an example $(x_t, y_t)$ where the feature vector $x_t \in
+viewed as a repeated game between the learner and the adversary. At each timestep $t$,
+the adversary chooses a labeled example $(x_t, y_t)$ where the feature vector, $x_t \in
 \R^d$ is revealed to the learner and the correct label $y_t$ is kept secret by
@@
 {
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
+\REQUIRE{Number of classes $K$.}
+\REQUIRE{Number of rounds $T$.}
 \FOR{$t=1,2,\dots,T$}
@@
 \STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \begin{cases}
+\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \begin{cases}
 0 & \text{if $\widehat y_t = y_t$,} \\
@@
 In this paper, we focus on the special case when the examples chosen by the
-adversary lie in $\R^d$ and
-are \emph{linearly separable with a margin}
-(see Definition~\ref{def:linear-sep} for a formal description).
-%\chicheng{I wonder if we should introduce the two notions of linear separability here,
-%because strong linear separability is also worth mentioning in the full-information setting.
-%}
-%\david{The formal definitions are in a section of their own.}
-
-In the full-information feedback
-setting, it is well known that if the examples have norm at most $R$ and are
-linearly separable with a margin $\gamma$ then the \textsc{Multiclass
-Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
-This result is very satisfying since the upper bound on the number of mistakes
-is information-theoretically optimal and at the same time the \textsc{Multiclass
-Perceptron} algorithm has low time and memory complexity.
-
-The bandit feedback setting, however, is much more challenging. To understand
-the differences, we dissect the notion of linear separability in the multiclass
-setting. Besides the standard notion of linear separability, we also consider
-\emph{strong linear separability} (see Definition~\ref{def:strong-linear-sep} for a formal description). For binary classification, these two
-definitions are identical.
-However, they differ for multiclass classification with $K \geq 3$.
+adversary lie in $\R^d$ and are linearly separable with a margin. We introduce
+two notions of linear separability, \emph{weak} and \emph{strong}. These are
+formally stated in
+Definitions~\ref{definition:weak-linear-separability}~and~\ref{definition:strong-linear-separability}.
+The standard notion of multiclass linear separability corresponds to the weak
+linear separability. For binary classification, these two notions are
+identical. However, they differ for multiclass classification with $K \geq 3$.
 For multiclass classification with $K$ classes, the standard notion of linear
@@
 examples from each class are separated from the remaining examples by a
-\emph{single} hyperplane. We state the definitions precisely in
-Section~\ref{section:notions-of-linear-separability}.
+\emph{single} hyperplane.
 
-For the case when the examples are strongly linearly separable, we design a
-simple and efficient algorithm with an expected number of mistakes at most $(K-1)
-\lfloor (R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies
-of the \textsc{Binary Perceptron} algorithm, one copy for each class.
-Intuitively speaking, the factor $K-1$ is the price we pay for the bandit
-feedback, or more precisely, the lack of full-information feedback. We also
-prove that any (possibly randomized) algorithm makes $\Omega(K (R/\gamma)^2))$
-mistakes in the worst case.
+In the full-information feedback setting, it is well known that if the examples
+have norm at most $R$ and are weakly linearly separable with a margin $\gamma$
+then the \textsc{Multiclass Perceptron} algorithm makes at most $\lfloor
+2(R/\gamma)^2 \rfloor$ mistakes. This result is very satisfying since the upper
+bound on the number of mistakes is information-theoretically optimal and at the
+same time the \textsc{Multiclass Perceptron} algorithm has low time and memory
+complexity.
+
+The bandit feedback setting, however, is much more challenging. For the case
+when the examples are strongly linearly separable, we design a simple and
+efficient algorithm with an expected number of mistakes at most $(K-1) \lfloor
+(R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies of the
+\textsc{Binary Perceptron} algorithm, one copy for each class. Intuitively
+speaking, the factor $K-1$ is the price we pay for the bandit feedback, or more
+precisely, the lack of full-information feedback. We also prove that any
+(possibly randomized) algorithm makes $\Omega(K (R/\gamma)^2))$ mistakes in the
+worst case.
 

### 2019-01-09 ICML-submission/notions-of-linear-separability.tex
Rename linear separability to weak linear separability

@@
 
-\begin{definition}[Linear separability]
-\label{definition:linear-separability}
+\begin{definition}[Weak linear separability]
+\label{definition:weak-linear-separability}
 Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
@@
 
-The examples are said to be \emph{linearly separable with a
+The examples are said to be \emph{weakly linearly separable with a
 margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
@@
 \begin{align}
-\label{equation:linear-separability-1}
+\label{equation:weak-linear-separability-1}
 & \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
-\label{equation:linear-separability-2}
+\label{equation:weak-linear-separability-2}
 & \begin{gathered}
@@
 
-The notion of linear separability with a margin is standard. It is used in the
+The notion of weak linear separability with a margin is standard. It is used in the
 full-information setting to upper bound the number of mistakes of the
-\textsc{Multiclass Perceptron} algorithm. For completeness, we state the
-algorithm in Appendix~\ref{section:multiclass-perceptron-proofs}. It is a
+\textsc{Multiclass Perceptron} algorithm. It is a
 folklore result that if a set of labeled examples is separable with a margin
@@
 $\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
-completeness, we give proofs of both of these results in
+completeness, we state the \textsc{Multiclass Perceptron} algorithm
+and give proofs of both of these results in
 Appendix~\ref{section:multiclass-perceptron-proofs}.
 
-The notion of strong linear separability is new. Intuitively, strong linear separability
-means that, for each $i$, the set of examples with class $i$ and the set of example of other classes are separated by a linear classifier $w_i$.
-Formally, $w_i$ separates the set of examples $\cbr{(x_t, y_t): t \in \cbr{1,\ldots,T}, y_t = i}$ and
-$\cbr{(x_t, y_t): t \in \cbr{1,\ldots,T}, y_t \neq i}$.
+The notion of strong linear separability is new. Intuitively, strong linear
+separability means that, for each $i$, the set of examples with class $i$ and
+the set of example of other classes are separated by a linear classifier $w_i$.
+Formally, $w_i$ separates the set of examples $\cbr{(x_t, y_t): t \in
+\cbr{1,\ldots,T}, y_t = i}$ and $\cbr{(x_t, y_t): t \in \cbr{1,\ldots,T}, y_t
+\neq i}$.
 
@@
 It is easy to see that if a set of labeled examples are strongly linearly
-separable with margin $\gamma$, then they are linearly separable with margin
+separable with margin $\gamma$, then they are weakly linearly separable with margin
 $2\gamma$. Indeed, if $w_1, w_2, \dots, w_K \in V$
@@
 \eqref{equation:strong-linear-separability-3} then they satisfy
-\eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} with margin $\gamma' = 2\gamma$.
+\eqref{equation:weak-linear-separability-1} and
+\eqref{equation:weak-linear-separability-2} with margin $\gamma' = 2\gamma$.
 
-Similarly, if $K=2$ and labeled examples are linearly separable with a margin
+Similarly, if $K=2$ and labeled examples are weakly linearly separable with a margin
 $\gamma$ then they are strongly linearly separable with margin $\gamma/2$.
-Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1} and
-\eqref{equation:linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$, $w_2' =
+Indeed, if $w_1, w_2$ satisfy \eqref{equation:weak-linear-separability-1} and
+\eqref{equation:weak-linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$, $w_2' =
 \frac{w_2 - w_1}{2}$ and $\gamma'=\gamma/2$ satisfy
@@
 
-\chicheng{Shall we change the $\gamma$ in Equations \eqref{equation:strong-linear-separability-2}, \eqref{equation:strong-linear-separability-3} to $\gamma/2$, to simplify the presentation?}
+\chicheng{Shall we change the $\gamma$ in Equations
+\eqref{equation:strong-linear-separability-2},
+\eqref{equation:strong-linear-separability-3} to $\gamma/2$, to simplify the
+presentation?}
 
 However, for any $K \ge 3$ and any inner product space of dimension at least
-$2$, there exists a set of labeled examples that is linearly separable with a
+$2$, there exists a set of labeled examples that is weakly linearly separable with a
 positive margin $\gamma$ but it is not strongly linearly separable with any
 positive margin $\gamma$. An example of such set of labeled examples is shown in
-Figure~\ref{figure:linearly-separable-examples-with-margin}.
+Figure~\ref{figure:weakly-linearly-separable-examples-with-margin}.
 
@@
 \begin{center}
-\input{figures/linearly-separable-examples-with-margin}
+\input{figures/weakly-linearly-separable-examples-with-margin}
 \end{center}
@@
 
-While the examples are linearly separable with a positive margin $\gamma$, they
+While the examples are weakly linearly separable with a positive margin $\gamma$, they
 are \emph{not} strongly linearly separable with any positive margin $\gamma$.
 }
-\label{figure:linearly-separable-examples-with-margin}
+\label{figure:weakly-linearly-separable-examples-with-margin}
 \end{figure}

### 2019-01-09 ICML-submission/related-work.tex
Rename linear separability to weak linear separability

@@
 The problem of bandit multiclass linear classification was initially formulated
-by the pioneering work of~\cite{Kakade-Shalev-Shwartz-Tewari-2008}. In that
+by the pioneering work of~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. In that
 work, two computationally inefficient algorithms that work in the standard
@@
 the \textsc{Banditron} algorithm, a computationally efficient algorithm that has
-a $O(T^{2/3})$ regret against the multiclass hinge loss
-in the general setting, and has a $O(\sqrt{T})$ mistake
-bound in the $\gamma$-weak linearly separable setting. The polynomial dependence
-of \textsc{Banditron}'s mistake bound on the time horizon is undesirable for
-problems with a long time horizon. One key open question left
-by~\cite{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can design
-computationally efficient algorithms that achieve mistake bounds that match or
-improve over those of inefficient algorithms. In this paper, we take a step
-towards answering this question, showing that efficient algorithms with mistake
-bounds quasipolynomial in the margin parameter can be obtained.
+a $O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
+and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weak linearly separable
+setting. The polynomial dependence of \textsc{Banditron}'s mistake bound on the
+time horizon is undesirable for problems with a long time horizon. One key open
+question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
+design computationally efficient algorithms that achieve mistake bounds that
+match or improve over those of inefficient algorithms. In this paper, we take a
+step towards answering this question, showing that efficient algorithms with
+mistake bounds quasipolynomial in the margin parameter can be obtained.
 
@@
 Many works consider bandit multiclass classification in the general
-non-separable setting. \cite{Abernethy-Rakhlin-2009} poses the open problem of
+non-separable setting. \citet{Abernethy-Rakhlin-2009} poses the open problem of
 whether one can design an efficient algorithm to get a $O(\sqrt{T})$ regret
-against some reasonable loss functions. \cite{Crammer-Gentile-2013} show that
-such an algorithm can be obtained, provided that the distribution of
-the label $y_t$ conditioned on feature vector $x_t$ satisfies certain parametric
-noise assumption. \cite{Hazan-Kale-2011} developed the \textsc{Newtron}
-algorithm, which has a regret between $O(\ln T)$ and $O(T^{2/3})$ against the
-multiclass logistic loss, where the exact order of the regret depends on the
-diameter of the benchmark class. In particular, if the diameter is $O(\ln T)$,
-its regret bound would become $O(T^{2/3})$. The \textsc{SOBA} algorithm by
-\cite{Beygelzimer-Orabona-Zhang-2017} achieves a regret of
+against some reasonable loss functions. \citet{Crammer-Gentile-2013} show that
+such an algorithm can be obtained, provided that the distribution of the label
+$y_t$ conditioned on feature vector $x_t$ satisfies certain parametric noise
+assumption. \citet{Hazan-Kale-2011} developed the \textsc{Newtron} algorithm,
+which has a regret between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass
+logistic loss, where the exact order of the regret depends on the diameter of
+the benchmark class. In particular, if the diameter is $O(\ln T)$, its regret
+bound would become $O(T^{2/3})$. The \textsc{SOBA} algorithm by
+\citet{Beygelzimer-Orabona-Zhang-2017} achieves a regret of
 $\widetilde{O}(\sqrt{T})$ against the
-$\eta$-loss~\cite{Orabona-Cesa-Bianchi-Gentile-2012}. In addition, its regret
+$\eta$-loss~\citet{Orabona-Cesa-Bianchi-Gentile-2012}. In addition, its regret
 bound does not depend sensitively on the diameter of the benchmark class.
-\cite{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a
+\citet{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a
 regret of $\widetilde{O}(\sqrt{T})$ against the multiclass logistic loss, where
-it doubly-exponentially improves over \cite{Hazan-Kale-2011}'s regret on its
+it doubly-exponentially improves over \citet{Hazan-Kale-2011}'s regret on its
 dependence on the diameter of the benchmark class.
 
-\cite{Chen-Lin-Lu-2014, Zhang-Jung-Tewari-2018} study online bandit multiclass
+\citet{Chen-Lin-Lu-2014, Zhang-Jung-Tewari-2018} study online bandit multiclass
 boosting under bandit feedback, where one can view online boosting as online
 linear classification by treating each base hypothesis as a separate feature.
-\cite{Chen-Lin-Lu-2014}'s online weak learning condition implies that
-the set of examples is strongly separable by a convex combination of base hypotheses
+\citet{Chen-Lin-Lu-2014}'s online weak learning condition implies that the set
+of examples is strongly separable by a convex combination of base hypotheses
 with a margin. Under this condition, it gives an algorithm with a $O(T^{3/4})$
-mistake bound. \cite{Zhang-Jung-Tewari-2018} considers an online weak learning
-condition, which implies that all examples is separable by a convex combination of base hypotheses with a margin (See~\cite{Mukherjee-Schapire-2013}, Theorem 3).
-Under this condition, it gives
-a boosting algorithm with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge
-parameter. In addition, it gives an adaptive algorithm with a $O(T^{3/4})$
-mistake bound.
+mistake bound. \citet{Zhang-Jung-Tewari-2018} considers an online weak learning
+condition, which implies that all examples is separable by a convex combination
+of base hypotheses with a margin (See~\cite{Mukherjee-Schapire-2013}, Theorem
+3). Under this condition, it gives a boosting algorithm with a $O(\sqrt{T})$
+mistake bound with the knowledge of the edge parameter. In addition, it gives an
+adaptive algorithm with a $O(T^{3/4})$ mistake bound.
 
-The online bandit multiclass learning is a special case of the contextual bandits
-problem~\cite{Auer-2003, Langford-Zhang-2008}, where the cost is the classification error.
-A series of works in the contextual bandits learning literature focuses on
-oracle-efficiency, that is, they assume access to an
-oracle that given a set of cost-sensitve learning examples,
+The online bandit multiclass learning is a special case of the contextual
+bandits problem~\citep{Auer-2003, Langford-Zhang-2008}, where the cost is the
+classification error. A series of works in the contextual bandits learning
+literature focuses on oracle-efficiency, that is, they assume access to an
+oracle that given a set of cost-sensitve learning examples.
 
-There has been much literature on the contextual bandit learning problem~\citep{Auer-2003, Langford-Zhang-2008}.
-In this problem, the learner is given a policy class $\Pi$, and
-at each timestep $t$, an example $x_t$ is shown, with an associated cost vector $c_t$ hidden.
-The learner then takes an action $\hat{y}_t$, and observed the incurred cost $c_t$.
-The goal of the learner is to minimize its regret $\sum_{t=1}^T c_t(\hat{y}_t) - \min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
-The online bandit multiclass learning problem is a special case of the contextual bandits problem,
-where the cost $c_t(i)$ is the classification error $I(i \neq y_t)$,
-and the policy class $\Pi$ is the set of linear classifiers
-$\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$.
-A series of works in the contextual bandits learning literature focus on
+There has been much literature on the contextual bandit learning
+problem~\citep{Auer-2003, Langford-Zhang-2008}. In this problem, the learner is
+given a policy class $\Pi$, and at each timestep $t$, an example $x_t$ is shown,
+with an associated cost vector $c_t$ hidden. The learner then takes an action
+$\hat{y}_t$, and observed the incurred cost $c_t$. The goal of the learner is to
+minimize its regret $\sum_{t=1}^T c_t(\hat{y}_t) - \min_{\pi \in \Pi}
+\sum_{t=1}^T c_t(\pi(x_t))$. The online bandit multiclass learning problem is a
+special case of the contextual bandits problem, where the cost $c_t(i)$ is the
+classification error $I(i \neq y_t)$, and the policy class $\Pi$ is the set of
+linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$. A
+series of works in the contextual bandits learning literature focus on
 oracle-efficiency~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
-Agarwal-Hsu-Kale-Langford-Li-Schapire-2014,
-Rakhlin-Sridharan-2016,
+Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
 Syrgkanis-Krishnamurthy-Schapire-2016,
-Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
-Specifically, they assume access to a policy optimization
-oracle that receives a set of cost-sensitive learning examples and policy class $\Pi$,
-return the policy in $\Pi$ that minimizes its empirical cost on the examples, and the algorithm
-only call the oracle a polynomial number of times.
-However, these algorithms are not truly computationally efficient in our setting,
-as it is NP-hard in general to find a linear classifier that minimizes the empirical cost over a set of examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.
+Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. Specifically, they assume access to
+a policy optimization oracle that receives a set of cost-sensitive learning
+examples and policy class $\Pi$, return the policy in $\Pi$ that minimizes its
+empirical cost on the examples, and the algorithm only call the oracle a
+polynomial number of times. However, these algorithms are not truly
+computationally efficient in our setting, as it is NP-hard in general to find a
+linear classifier that minimizes the empirical cost over a set of
+examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.
 
-%as algorithms generate cost-sensitive examples that may not be linearly separable
-%Algorithms that satisfy oracle efficiency has been proposed in the literature, for
-%example.
+%as algorithms generate cost-sensitive examples that may not be linearly
+%separable Algorithms that satisfy oracle efficiency has been proposed in the
+%literature, for example.
 
-Recently, \cite{Foster-Krishnamurthy-2018} developed a rich theory of contextual bandits
-with surrogate losses, focusing on benchmarks of the form $\min_{f \in \calF}
-\sum_{t=1}^T \frac{1}{K} \sum_{i=1}^K c_t(i) \phi( f_i(x_t) )$,
-where $\calF$ contains score functions $f$
-such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac s
-\gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
-information-theoretic mistake upper bounds under various settings of $\calF$,
-including parametric and nonparametric classes. On the other hand, it gives
-an efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of
-$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$. A direct
-application of this result to the online bandit multiclass learning problem
-yields an algorithm with a $O(\sqrt{T})$ mistake bound in the strong
-linearly separable setting.
+Recently, \citet{Foster-Krishnamurthy-2018} developed a rich theory of
+contextual bandits with surrogate losses, focusing on benchmarks of the form
+$\min_{f \in \calF} \sum_{t=1}^T \frac{1}{K} \sum_{i=1}^K c_t(i) \phi( f_i(x_t)
+)$, where $\calF$ contains score functions $f$ such that $\sum_{i=1}^K
+f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac s \gamma, 0)$ or $\min(1,
+\max(1 - \frac s \gamma, 0))$. On one hand, it gives information-theoretic
+mistake upper bounds under various settings of $\calF$, including parametric and
+nonparametric classes. On the other hand, it gives an efficient algorithm that
+has a $O(\sqrt{T})$ regret against the benchmark of $\calF = \cbr{x \mapsto W x:
+W \in \R^{k \times d}, \one^T W = 0}$. A direct application of this result to
+the online bandit multiclass learning problem yields an algorithm with a
+$O(\sqrt{T})$ mistake bound in the strong linearly separable setting.
 

### 2019-01-09 arxiv-version/introduction.tex
Rename linear separability to weak linear separability

@@
 
-In this paper, we focus on the special case when the examples lie in $\R^d$ and
-are \emph{linearly separable with a margin}.
-\chicheng{I wonder if we should introduce the two notions of linear separability here,
-because strong linear separability is also worth mentioning in the full-information setting.
-}
-\david{The formal definitions are in a section of their own.}
+In this paper, we focus on the special case when the examples chosen by the
+adversary lie in $\R^d$ and are \emph{linearly separable with a margin} (see
+\autoref{definition:linear-separability} for a formal description).
+%\chicheng{I wonder if we should introduce the two notions of linear separability here,
+%because strong linear separability is also worth mentioning in the full-information setting.
+%}
+%\david{The formal definitions are in a section of their own.}
 
-In the full-information feedback
-setting, it is well known that if the examples have norm at most $R$ and are
-linearly separable with a margin $\gamma$ then the \textsc{Multiclass
-Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
-This result is very satisfying since the upper bound on the number of mistakes
-is information-theoretically optimal and at the same time the \textsc{Multiclass
-Perceptron} algorithm has low time and memory complexity.
+In the full-information feedback setting, it is well known that if the examples
+have norm at most $R$ and are linearly separable with a margin $\gamma$ then the
+\textsc{Multiclass Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2
+\rfloor$ mistakes. This result is very satisfying since the upper bound on the
+number of mistakes is information-theoretically optimal and at the same time the
+\textsc{Multiclass Perceptron} algorithm has low time and memory complexity.
 
@@
 the differences, we dissect the notion of linear separability in the multiclass
-setting. Beside the standard notion of linear separability, we define also
-\emph{strong linear separability}. For binary classification, these two
-definitions are identical. However, they differ for multiclass classification.
-For multiclass classification with $K$ classes the standard notion of linear
-separability means that the examples from each class lie in an intersection of
-$K-1$ halfspaces and the examples outside of the class lie in the complement of
-the intersection of the halfspaces. Strong linear separability means that
-examples from each class are separated from the remaining examples by a
-\emph{single} hyperplane. We state the definitions precisely in
+setting. Besides the standard notion of linear separability, we also consider
+\emph{strong linear separability} (see
+\autoref{definition:strong-linear-separability} for a formal description). For
+binary classification, these two definitions are identical. However, they differ
+for multiclass classification with $K \geq 3$. For multiclass classification
+with $K$ classes, the standard notion of linear separability means that the
+examples from each class lie in an intersection of $K-1$ halfspaces and the
+examples outside of the class lie in the complement of the intersection of the
+halfspaces. Strong linear separability means that examples from each class are
+separated from the remaining examples by a \emph{single} hyperplane. We state
+the definitions precisely in
 Section~\ref{section:notions-of-linear-separability}.
@@
 related to the problem of learning intersection of halfspaces and has been
-studied previously by \cite{Klivans-Servedio-2008}. As an important technical
-achievement, we improve on the results of \cite{Klivans-Servedio-2008} by
+studied previously by \citet{Klivans-Servedio-2008}. As an important technical
+achievement, we improve on the results of \citet{Klivans-Servedio-2008} by
 removing completely the dependency on the original dimension $d$.

### 2019-01-09 ICML-submission/figures/pizza-slice.tex
Add one more section

@@
-\begin{tikzpicture}
+\begin{tikzpicture}[scale=0.5]
 
@@
 
-  \coordinate [label={[xshift=-10mm, yshift=5mm]$\ip{v_1}{x} = 0$}] (A) at (120:5);
-  \coordinate [label={[xshift=-10mm, yshift=-10mm]$\ip{v_2}{x} = 0$}] (B) at (240:5);
+  \coordinate [label={[xshift=-10mm, yshift=0mm]$\ip{v_1}{x} = 0$}] (A) at (120:5);
+  \coordinate [label={[xshift=-10mm, yshift=-5mm]$\ip{v_2}{x} = 0$}] (B) at (240:5);
 
@@
 
-  \pic [ultra thick, draw, angle radius=5cm] {angle=A1--Origin--B1};
-  \pic [ultra thick, draw, angle radius=5cm] {angle=B2--Origin--A2};
+  \pic [ultra thick, draw, angle radius=2.5cm] {angle=A1--Origin--B1};
+  \pic [ultra thick, draw, angle radius=2.5cm] {angle=B2--Origin--A2};
 
@@
   \coordinate (C2) at ($(120:3) - (0.75, 0.43301270189221932338)$);
-  \draw[<->, >=latex, ultra thick] (C1) -- (C);
-  \draw[<->, >=latex, ultra thick] (C2) -- (C);
+  \draw[<->, >=latex', ultra thick] (C1) -- (C);
+  \draw[<->, >=latex', ultra thick] (C2) -- (C);
   \draw ($0.5*(C1) + 0.5*(C)$) node[above, xshift=-1mm] {$\gamma$};
@@
   \coordinate (D2) at ($(240:3) - (-0.75, 0.43301270189221932338)$);
-  \draw[<->, >=latex, ultra thick] (D1) -- (D);
-  \draw[<->, >=latex, ultra thick] (D2) -- (D);
+  \draw[<->, >=latex', ultra thick] (D1) -- (D);
+  \draw[<->, >=latex', ultra thick] (D2) -- (D);
   \draw ($0.5*(D1) + 0.5*(D)$) node[below, xshift=-1mm] {$\gamma$};

### 2019-01-09 ICML-submission/from-linear-separability-to-strong-linear-separability.tex
Add one more section

--- 2019-01-07 arxiv-version/from-linear-separability-to-strong-linear-separability.tex
@@
 \begin{enumerate}
-\item $p(x) \ge 1/2$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-\item $p(x) \le -1/2$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
+\item $p(x) \ge 1/2$ \\ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
+\item $p(x) \le -1/2$ \\ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
 \item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$
@@
 \begin{enumerate}
-\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$
+\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$ \\
 for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
 
-\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$
+\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$ \\
 for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
@@
 parameter $\gamma$. These regions are
-\begin{align*}
-R^+ & = \displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\} \; , \\
-R^- & = \displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\} \; .
-\end{align*}
-The separating hyperplanes $\ip{v_1}{x} = 0$ and $\ip{v_2}{x} = 0$ are shown as dashed lines.
-}
+$R^+ = \displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
+$R^- = \displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
+The separating hyperplanes $\ip{v_1}{x} = 0$ and $\ip{v_2}{x} = 0$ are shown as dashed lines.}
 \label{figure:pizza-slice}
@@
 \begin{align*}
-\left(\phi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
+& \left(\phi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
+= x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
 \\
-\left(\psi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = \sqrt{\binom{n}{\alpha_1 + \alpha_2 + \dots + \alpha_d} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
+& \left(\psi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \\
+& \qquad \cdot \sqrt{\binom{n}{\alpha_1 + \alpha_2 + \dots + \alpha_d} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
 \\
-\left(\rho(x)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-& = \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
+& \left(\rho(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \\
+& \qquad \cdot \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
 \end{align*}

### 2019-01-09 ICML-submission/related-work.tex
Add one more section

@@
 
-\citet{Chen-Lin-Lu-2014, Zhang-Jung-Tewari-2018} study online bandit multiclass
-boosting under bandit feedback, where one can view online boosting as online
-linear classification by treating each base hypothesis as a separate feature.
-\citet{Chen-Lin-Lu-2014}'s online weak learning condition implies that the set
-of examples is strongly separable by a convex combination of base hypotheses
-with a margin. Under this condition, it gives an algorithm with a $O(T^{3/4})$
-mistake bound. \citet{Zhang-Jung-Tewari-2018} considers an online weak learning
-condition, which implies that all examples is separable by a convex combination
-of base hypotheses with a margin (See~\cite{Mukherjee-Schapire-2013}, Theorem
-3). Under this condition, it gives a boosting algorithm with a $O(\sqrt{T})$
-mistake bound with the knowledge of the edge parameter. In addition, it gives an
-adaptive algorithm with a $O(T^{3/4})$ mistake bound.
+\citet{Chen-Lin-Lu-2014} and \citet{Zhang-Jung-Tewari-2018} study online bandit
+multiclass boosting under bandit feedback, where one can view online boosting as
+online linear classification by treating each base hypothesis as a separate
+feature. \citet{Chen-Lin-Lu-2014}'s online weak learning condition implies that
+the set of examples is strongly separable by a convex combination of base
+hypotheses with a margin. Under this condition, it gives an algorithm with a
+$O(T^{3/4})$ mistake bound. \citet{Zhang-Jung-Tewari-2018} considers an online
+weak learning condition, which implies that all examples is separable by a
+convex combination of base hypotheses with a margin
+(See~\cite{Mukherjee-Schapire-2013}, Theorem 3). Under this condition, it gives
+a boosting algorithm with a $O(\sqrt{T})$ mistake bound with the knowledge of
+the edge parameter. In addition, it gives an adaptive algorithm with a
+$O(T^{3/4})$ mistake bound.
 

### 2019-01-10 arxiv-version/mistake-lower-bound-for-ignorant-algorithms.tex
add ignorant algorithm analysis

@@
 \section{Mistake lower bound for ignorant algorithms}
+In this section, we prove a mistake lower bound for a family of algorithms called \textit{ignorant algorithms}. 
+For simplicity, we assume $(x_t, y_t)\in\mathbb{R}^{d}\times [K]$ in this section. 
+As the name suggests, ignorant algorithms ignore the examples on which they make mistakes. 
+This assumption seems strong, but as we will explain below, it is actually natural, 
+and several recently proposed bandit classification algorithms that achieve the $\sqrt{T}$-regret bound belong to this family, e.g., SOBA~\citep{Beygelzimer-Orabona-Zhang-2017}, OBAMA~\citep{Foster-Kale-Luo-Mohri-Sridharan-2018}.
+We will see that under the $\gamma$-weak linearly separability assumption, 
+if a bandit classification algorithm wants to achieve a mistake bound better than $\Theta\left(\min\{\sqrt{T}, (1/\gamma)^{\Theta(d)}\}\right)$, where $d$ is the feature dimension, it must perform some meaningful update when it makes a mistake.
 
+The ignorant algorithm is formally defined as follows.  
+\begin{definition} \label{definition:ignorant-algorithm}
+    A bandit classification algorithm $\mathcal{A}$ is ignorant if for all $t\in[T]$, 
+    $\widehat y_t\in \{1,2\}$ is drawn from some distribution that is jointly determined by 
+    \begin{enumerate}
+        \item $x_t$
+        \item $H_t\triangleq \left( (x_{\tau_1}, y_{\tau_1}), (x_{\tau_2}, y_{\tau_2}), \ldots, (x_{\tau_{n_t}}, y_{\tau_{n_t}}) \right)$, 
+        where $1 \leq \tau_1<\ldots <\tau_{n_t} < t$, and $\{\tau_1, \ldots, \tau_{n_t}\}$ 
+        are the rounds in which the algorithm predicts correctly (that is, 
+        $\{\tau_1, \ldots, \tau_{n_t}\} = \{1\leq \tau<t: \widehat y_\tau=y_\tau\}$). 
+    \end{enumerate}
+    We use $p_t(\cdot|x_t)\in \{p\in \mathbb{R}_+^2: p^\top\mathbf{1}=1\}$ to denote the distribution $\widehat y_t$ is drawn from.
+Note that we let the current feature vector $x_t$ be an argument to $p_t$ to incorporate its dependency on $x_t$.
+Therefore, for an ignorant algorithm, the function $p_t(\cdot|\cdot)$ is only determined by $H_t$.
+\end{definition}
+
+An ignorant algorithm does not learn from mistakes in the following sense. Suppose that an ignorant algorithm predicts incorrectly at time $t$ ($\widehat y_t \neq y_t$). 
+Then at time $t+1$, if it is given the same feature vector $x_{t+1}=x_t$, it will predict the label with the same distribution $p_{t+1}(\cdot|x_{t+1})=p_{t+1}(\cdot|x_t)=p_t(\cdot|x_t)$. 
+Below we describe the difficulty of learning from mistakes using a class of natural approaches under the weak separability assumption. 
+Consider an approach similar to OBAMA: in each round $t$, 
+we create a \textit{convex} loss function $\widehat \ell_t: \mathbb{R}^{K\times d}\rightarrow \mathbb{R}$ that gives a loss value $\widehat \ell_t(W)$ to 
+all linear models $W\in\mathbb{R}^{K\times d}$ ($W=[w_1 \ldots w_K]^\top$ for $w_1, \ldots, w_K$ defined in Definition~\ref{definition:linear-separability}). 
+The requirement for $\widehat{\ell}_t$ to be convex is due to computational efficiency. 
+To let $\widehat{\ell}_t$ reflect the loss, if $\widehat y_t \neq y_t$, we want to assign larger loss values $\widehat{\ell_t}(W)$ to the inconsistent models $\mathcal{W}=\{W: \ip{w_{\widehat y_t}}{x_t} \geq \ip{w_i}{x_t}, \forall i\in[K]\}$,
+while for other $W$'s, we want $\widehat{\ell_t}(W)$ to be smaller. 
+The following fact can be verified when $K\geq 3$, which suggests there is no way to define the loss $\widehat \ell_t$ that satisfies the above properties constraints: 
+there exists $W_1, W_2, W_3$, where $W_2$ is in the line segment between $W_1$ and $W_3$, such that $W_2\in \mathcal{W}$, while $W_1, W_3 \notin \mathcal{W}$. 
+On one hand, by convexity, we should have $\widehat{\ell}_t(W_2)\leq \max\{\widehat{\ell}_t(W_1), \widehat{\ell}_t(W_3)\}$; 
+on the other hand, to penalize $\mathcal{W}$, we should have $\widehat{\ell}_t(W_2) > \widehat{\ell}_t(W_1)$ and $\widehat{\ell}_t(W_2) > \widehat{\ell}_t(W_3)$. 
+Clearly, these two requirements contradict each other.
+
+The following theorem states the mistake lower bound for ignorant algorithms. 
+\begin{theorem}[Mistake Lower Bound for Ignorant Algorithms]
+\label{theorem:ignorant_lower_bound}
+    Suppose $\mathcal{A}$ is an ignorant bandit classification algorithm. 
+    There exists an adversary that can sequentially choose $(x_1, y_1), (x_2, y_2), \ldots, (x_T, y_T) \in \mathbb{R}^d\times \{1,2\}$, 
+    such that $\forall t\in[T], \|x_t\|\leq 1$, $\{(x_t, y_t)\}_{t=1}^T$ is $\gamma$-strongly linearly separable, 
+    and the expected number of mistakes made by $\mathcal{A}$ is lower bounded as 
+    \begin{align*}
+        \Exp\left[ \sum_{t=1}^T \indicator{\widehat y_t \neq y_t} \right] \geq \frac{1}{10}\min\left\{\sqrt{T}, 
+        \left(\frac{1}{160\gamma}\right)^{\frac{d-2}{4}} \right\}. 
+    \end{align*}
+\end{theorem}
+Before proving the theorem, we need the following lemma. 
 \begin{lemma}
-For any $\gamma \in (0,\frac 1 {160})$,
-there exists a set of $N$ examples $x_1, \ldots, x_N$ and vectors $w_1, \ldots, w_N$ ($N = (\Omega(\frac{1}{\gamma}))^{(d-2)/2}$), such that:
-$\| x_i \|_2 \leq 1$, $\| w_i \|_2 \leq 1$ for all $i$ in $[N]$, and for all $i, j$ in $[N]$,
-\[ w_i \cdot x_j \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases} \]
 \label{lem:embed_d_gamma}
+Let $\gamma \in (0,\frac 1 {160})$. 
+There exists vectors $v_1, \ldots, v_N, u_1, \ldots, u_N\in \mathbb{R}^d$, where $N = (\Omega(\frac{1}{\gamma}))^{(d-2)/2}$, such that:
+$\| v_i \|_2 \leq 1$, $\| u_i \|_2 \leq 1$ for all $i$ in $[N]$, and for all $i, j$ in $[N]$,
+\[ u_i \cdot v_j \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases} \]
 \end{lemma}
@@
 
-Define $x_i = (\frac12 z_i, \frac12)$, and $w_i = (\frac 12 z_i, -\frac 12(1-4\gamma))$ for all $i$ in $[N]$.
-It can be easily checked that for all $i$, $\|x_i\| \leq 1$ and $\|w_i\| \leq 1$.
+Define $v_i = (\frac12 z_i, \frac12)$, and $u_i = (\frac 12 z_i, -\frac 12(1-4\gamma))$ for all $i$ in $[N]$.
+It can be easily checked that for all $i$, $\|v_i\| \leq 1$ and $\|u_i\| \leq 1$.
 In addition,
-\[ w_i \cdot x_j = \frac 1 4 z_i \cdot z_j - \frac {1-4\gamma} 4 \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases}\]
+\[ u_i \cdot v_j = \frac 1 4 z_i \cdot z_j - \frac {1-4\gamma} 4 \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases}\]
 \end{proof}
+
+\begin{proof}[Proof for Theorem~\ref{theorem:ignorant_lower_bound} (PartI: Mistake lower bound)]
+We consider the strategy for the adversary described in Algorithm~\ref{algorithm:adversary-strategy}. 
+\begin{algorithm}[h]
+\caption{\textsc{Adversary's strategy}}
+\label{algorithm:adversary-strategy}
+\begin{algorithmic}[1]
+{
+\STATE{\textbf{Define} $q_0=\max\left\{\frac{1}{\sqrt{T}}, \frac{1}{\sqrt{N}}\right\}$, where $N$ is defined in Lemma~\ref{lem:embed_d_gamma}.
+Also, let $v_1, \ldots, v_N$ be those defined in Lemma~\ref{lem:embed_d_gamma}.}
+\STATE{\textbf{Initialize} $\textsc{phase}= 1$. }
+\FOR{$t=1,\dots,\min\{T,N\}$}
+    \IF{$\textsc{phase}=1$}
+       \IF{$p_t(1|v_t)\geq 1-q_0$}
+          \STATE{$(x_t, y_t)\leftarrow (v_t, 1)$}
+       \ELSE
+          \STATE{$(x_t, y_t)\leftarrow (v_t, 2)$}
+          \STATE $\textsc{phase}\leftarrow 2$
+       \ENDIF
+    \ELSIF{$\textsc{phase}=2$}
+       \STATE $(x_t, y_t)\leftarrow (x_{t-1}, y_{t-1})$. 
+    \ENDIF
+\ENDFOR
+\FOR{$t=\min\{T,N\}+1, \ldots, T$}
+    \STATE $(x_t, y_t)\leftarrow (x_{t-1}, y_{t-1})$. 
+\ENDFOR
+
+}
+\end{algorithmic}
+\end{algorithm}
+For this strategy, we prove the mistake lower bound of any ignorant algorithm. 
+Define the indicators 
+\begin{align*}
+A_t &= \indicator{\forall \tau\leq t, p_\tau(1|x_\tau)<1-q_0} \\
+B_t &= \indicator{\exists \tau\leq t, p_\tau(1|x_\tau)\geq 1-q_0
+ \text{\ and\ } \forall s\in[\tau,t), \widehat y_s \neq y_s}. 
+\end{align*}
+Then we have 
+\begin{align}
+    \mathbf{E}\left[\sum_{t=1}^{T} \indicator{\widehat y_t\neq y_t}\right] 
+    &\geq \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
+    & \geq \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}A_t\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}B_t\right] \nonumber \\
+    & = \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \mathbf{E}_t\left[\indicator{\widehat y_t\neq y_t}A_t\right]\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right] \nonumber \\
+    & \geq \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} q_0 A_t\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right], 
+    \label{eqn:mistake_lower_bound_temp}
+\end{align}
+where in the first inequality we use $A_t+B_t\leq 1$; 
+in the equality, we use  $B_{t+1}=B_t\indicator{\widehat y_t\neq y_t}$ by $B_t$'s definition; 
+in the last inequality we use the fact that when $t\leq N$ and $A_t=1$, it must be $y_t=1$. 
+Now, denote $T_1 = \argmin_{\tau} \{ p_\tau(1|x_\tau) \geq 1-q_0 \}$ (if such $\tau$ does not exist or is larger than $\min\{T,N\}$, we simply let $T_1=\min\{T,N\}+1$). 
+Then $A_t=1$ for all $t\leq T_1-1$.
+
+Note that $B_{T_1}=1$, and for $t\geq T_1$ we have $\Exp[B_{t+1}=0|B_t=1]=\Pr[\widehat y_t=y_t|B_t=1]=\Pr[\widehat y_t=2|B_t=1]\leq q_0$ because the algorithm is ignorant.
+Thus the second term in \eqref{eqn:mistake_lower_bound_temp} can be calculated as
+
+\begin{align*}
+    \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}}B_{t+1}\right]\geq \mathbf{E}\left[\sum_{t=T_1}^{\min\{ T,N \}} (1-q_0)^{t-T_1+1} \right]
+    = \frac{1-q_0}{q_0}\mathbf{E}\left[1-(1-q_0)^{\min\{T,N\}-T_1+1}\right]. 
+\end{align*}
+Combining \eqref{eqn:mistake_lower_bound_temp} and the above inequalities, we get
+\begin{align}
+    \mathbf{E}\left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right]\geq \mathbf{E}\left[q_0(T_1-1)+\frac{1-q_0}{q_0}\left(1-(1-q_0)^{\min\{T,N\}-T_1+1}\right)\right].
+\label{eqn:mistake_lower_bound_temp2}
+\end{align}
+In the case $T_1\geq \frac{1}{2}\min\{T,N\}+1$, the right-hand side of \eqref{eqn:mistake_lower_bound_temp2} is lower bounded by $\frac{1}{2}q_0\min\{T,N\}=\frac{1}{2}\min\{\sqrt{T}, \sqrt{N}\}$; in the case $T_1< \frac{1}{2}\min\{T,N\}+1$, it is lower bounded by
+\begin{align*}
+    \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2}\min\{T,N\}}\right)= \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2q_0^2}}\right)\geq \frac{1-\frac{1}{\sqrt{2}}}{q_0}\left(1-\frac{1}{\sqrt{e}}\right)\geq \frac{1}{10}\min\{\sqrt{T}, \sqrt{N}\}.
+\end{align*}
+Combining both cases concludes the proof. 
+\end{proof}
+
+\begin{proof}[Proof for Theorem~\ref{theorem:ignorant_lower_bound} (Part II: linear separability)]
+Observe that in Algorithm~\ref{algorithm:adversary-strategy}, in the beginning the adversary always set the label to $1$; 
+once it sets $y_t=2$ at some $t$, it lets $(x_s, y_s)=(x_t, y_t)=(v_t, 2)$ for all $s\geq t$. 
+Consider $w_2=u_t$ and $w_1=-u_t$, for $u_t$ as defined in Lemma~\ref{lem:embed_d_gamma}. 
+Then by Lemma~\ref{lem:embed_d_gamma}, we have $\ip{w_2}{x_s} = \ip{u_t}{v_t} \geq \gamma, \forall s \geq t$ 
+and $\ip{w_2}{x_s} = \ip{u_t}{v_s} \leq - \gamma, \forall s< t$; 
+also $\ip{w_1}{x_s} \leq -\gamma, \forall s \geq t$ 
+and $\ip{w_1}{x_s} \geq  \gamma, \forall s<t$. 
+Thus, the example set is always $\gamma$-strongly separable. 
+\end{proof}

### 2019-01-10 ICML-submission/appendix-proofs-of-polynomial-approximation-theorems.tex
Fix formatting of the polynomial approximation theorems

--- 2019-01-07 arxiv-version/proofs-of-polynomial-approximation-theorems.tex
@@
 assume $k \ge 1$. We write the binomial coefficient as
-$$
+\begin{align*}
 \binom{n}{k}
-= \frac{n(n-1)\cdots(n-k+1)}{k(k-1) \cdots 1}
-= \frac{n}{k} \cdot \frac{n-1}{k - 1} \cdots \frac{n-k+1}{1} \; .
-$$
+& = \frac{n(n-1)\cdots(n-k+1)}{k(k-1) \cdots 1} \\
+& = \frac{n}{k} \cdot \frac{n-1}{k - 1} \cdots \frac{n-k+1}{1} \; .
+\end{align*}
 We claim that
@@
 $$
-which holds by the assumption on $n \ge k$.
+which since $n \ge k$ by assumption.
 \end{proof}
@@
 Therefore,
-\begin{multline*}
+\begin{align*}
 \norm{p}^2
-= \sum_{A} (c_A)^2
-= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \right)^2
-= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\end{multline*}
+& = \sum_{A} (c_A)^2 \\
+& = \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \right)^2 \\
+& = \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
+\end{align*}
 and
-\begin{multline*}
+\begin{align*}
 \prod_{i=1}^n \norm{p_i}^2
-= \prod_{i=1}^n \left( \sum_{A_i} (c^{(i)}_{A_i})^2 \right)
-= \sum_{(A_1, A_2, \dots, A_n)} \prod_{j=1}^n (c^{(j)}_{A_j})^2
-= \sum_{(A_1, A_2, \dots, A_n)} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
-= \sum_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
-\end{multline*}
+& = \prod_{i=1}^n \left( \sum_{A_i} (c^{(i)}_{A_i})^2 \right) \\
+& = \sum_{(A_1, A_2, \dots, A_n)} \prod_{j=1}^n (c^{(j)}_{A_j})^2 \\
+& = \sum_{(A_1, A_2, \dots, A_n)} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
+& = \sum_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
+\end{align*}
 where in both cases the outer sum is over multi-indices $A$ such that $\norm{A}_1 \le \deg(p)$.
 \autoref{lemma:simple-inequality} implies that for any multi-index $A$,
-$$
-\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
+\begin{multline*}
+\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
 \le M_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
-$$
+\end{multline*}
 where $M_A$ is the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 +
@@
 \autoref{lemma:simple-inequality}. We have
-\begin{align*}
-\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
-\end{align*}
+\begin{multline*}
+\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \\ \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
+\end{multline*}
 \end{proof}
@@
 $$
-T_0(\cos(\theta)) = 1 = \cos(0 \theta) \qquad \text{and} \qquad T_1(\cos(\theta)) = \cos(\theta) \; .
+T_0(\cos(\theta)) = 1 = \cos(0 \theta) \quad \text{and} \quad T_1(\cos(\theta)) = \cos(\theta) \; .
 $$
@@
 \ge -1$. Therefore,
-$$
-p(x) = m + \frac{1}{2} - \left( T_s(1 - \ip{v_i}{x}) \right)^r - \sum_{\substack{j ~:~  1 \le j \le m \\ j \neq i}} \le m + \frac{1}{2} - 2m + (m - 1) \le - \frac{1}{2} \; .
-$$
+\begin{align*}
+p(x) & = m + \frac{1}{2} - \left( T_s(1 - \ip{v_i}{x}) \right)^r \\
+& \qquad - \sum_{\substack{j ~:~  1 \le j \le m \\ j \neq i}} \left( T_s(1 - \ip{v_j}{x}) \right)^r \\
+& \le m + \frac{1}{2} - 2m + (m - 1) \\
+& \le - \frac{1}{2} \; .
+\end{align*}
 
@@
 & = \norm{ \sum_{j=0}^s c_j (f_i)^j }^2 \\
-& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 & \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
+& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 \qquad \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
 & = (s + 1) \sum_{j=0}^s (c_j)^2 \norm{(f_i)^j}^2 \\
-& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} & \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
+& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} \qquad \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
 & \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j 2^{2j} \\
@@
 & = (s + 1) s^s 2^{2s} \norm{T_s}^2 \\
-& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} & \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
+& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} \qquad \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
 & = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
-& \le \left(8(1+\sqrt{2})^2 s \right)^s & \text{(since $s+1 \le 2^s$ for any integer $s \ge 0$)} \\
+& \le \left(8(1+\sqrt{2})^2 s \right)^s \quad \text{(since $s+1 \le 2^s$ for any integer $s \ge 0$)} \\
 & \le \left(47 s \right)^s \; .
@@
 We define the polynomial $p:\R^d \to \R$ as
-$$
-p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
+\begin{multline*}
+p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right] \\
 - \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-$$
+\end{multline*}
 
@@
 \item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
-\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
+\item If $z \in [-2^n,2^n]$ then \\ $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
 \end{enumerate}
@@
 Case $z \in [0,1]$. Since $r$ is odd and $P_n(z)$ is non-positive,
-$$
-B_{n,r}(z) = - (P_n(z))^r + \left(- P_{n}(-z)\right)^r \ge \left(- P_{n}(-z)\right)^r \ge 2^{n(n+1)r} \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
+\begin{align*}
+B_{n,r}(z)
+& = - (P_n(z))^r + \left(- P_{n}(-z)\right)^r \\
+& \ge \left(- P_{n}(-z)\right)^r \ge 2^{n(n+1)r}  \\
+& \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
+\end{align*}
 where the second last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
@@
 Case $z \in [1,2^n]$. Since $r$ is odd,
-$$
-B_{n,r}(z) = \left(- P_{n}(-z)\right)^r \left(1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r \right) = \left(- P_{n}(-z)\right)^r (1 - c)
-$$
+\begin{align*}
+B_{n,r}(z)
+& = \left(- P_{n}(-z)\right)^r \left(1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r \right) \\
+& = \left(- P_{n}(-z)\right)^r (1 - c)
+\end{align*}
 where $c = \left( - \frac{P_n(z)}{P_n(-z)}\right)^r$. Since $z \in [1,2^n]$, by
@@
 the definition of $r$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
-$$
-B_{n,r}(z) \ge \left(- P_{n}(-z)\right)^r \left( 1 - \frac{1}{4m+1} \right) \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
-$$
+\begin{align*}
+B_{n,r}(z)
+& \ge \left(- P_{n}(-z)\right)^r \left( 1 - \frac{1}{4m+1} \right) \\
+& \ge 2^{n(n+1)r} \left( 1 - \frac{1}{4m+1} \right) \; .
+\end{align*}
 where the last inequality follows from part 3 of \autoref{lemma:properties-of-p-n}.
@@
 \begin{enumerate}
-\item $Q(x) \ge \frac{1}{2}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
-\item $Q(x) \le -\frac{1}{2}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
+\item $Q(x) \ge \frac{1}{2}$ \\ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
+\item $Q(x) \le -\frac{1}{2}$ \\ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
 \end{enumerate}
@@
 in particular $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \ge 1$. Thus,
-$$
-Q(x) = \left( \sum_{i=1}^m S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \right) - (m - 1/2) \ge m - (m - 1/2) = 1/2 \; .
-$$
+\begin{align*}
+Q(x)
+& = \left( \sum_{i=1}^m S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \right) - (m - 1/2) \\
+& \ge m - (m - 1/2) \\
+& = 1/2 \; .
+\end{align*}
 
@@
 & = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& = S_{s,r}\left( \frac{\ip{v_j}{x}}{\gamma} \right) + \left( \sum_{\substack{i ~:~ 1 \le i \le m \\ i \neq j}} S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
+& = S_{s,r}\left( \frac{\ip{v_j}{x}}{\gamma} \right) + \left( \sum_{\substack{i ~:~ 1 \le i \le m \\ i \neq j}} S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right)  \\
+& \qquad - \left(m - \frac{1}{2} \right) \\
 & \le -1 + (m-1) \left( 1 + \frac{1}{2m} \right) - \left(m - \frac{1}{2} \right) \\
@@
 & \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
-& \ge \frac{1}{2} |Q(x)| \cdot 2^{s(s+1)rm} && \text{(since $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4} \ge 1/2$)} \\
-& \ge \frac{1}{4} \cdot 2^{s(s+1)rm} && \text{(\autoref{lemma:properties-of-q})} \; .
+& \ge \frac{1}{2} |Q(x)| \cdot 2^{s(s+1)rm} \\
+& \ge \frac{1}{4} \cdot 2^{s(s+1)rm} \quad \text{(\autoref{lemma:properties-of-q})} \; .
 \end{align*}
+where we used that $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4} \ge 1/2$.
 
@@
 Note that
-$$
-p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
-$$
+\begin{multline*}
+p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right]  \\
+- \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
+\end{multline*}
 We bound the norms of these polynomials. We have
@@
 as
-$$
-\norm{q_v}^2 \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \le  (2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \; .
-$$
+\begin{align*}
+\norm{q_v}^2
+& \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \\
+& \le  (2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \; .
+\end{align*}
 Using parts 3 and 2 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $a_v$ as
@@
 \begin{align*}
-\norm{p}
+& \norm{p} \\
 & \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
-& \le \left[ \sum_{i=1}^m m^{(s+1/2)rm} \norm{a_{v_i}} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} \norm{b_{v_j}} \right] + \left(m - \frac{1}{2} \right) m^{(s+1/2)rm} \prod_{j=1}^m \norm{b_{v_j}} \\
+& \le \left[ \sum_{i=1}^m m^{(s+1/2)rm} \norm{a_{v_i}} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} \norm{b_{v_j}} \right] \\
+& \qquad + \left(m - \frac{1}{2} \right) m^{(s+1/2)rm} \prod_{j=1}^m \norm{b_{v_j}} \\
 & \le (2m-1/2) m^{(s+1/2)rm} \left(4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \right)^{m/2} \\

### 2019-01-10 ICML-submission/from-linear-separability-to-strong-linear-separability.tex
Add lemma bounding the norm of linear functions

@@
 The parameters $\gamma'$ and $R'$ are functions of the old margin $\gamma$ and
-the number of classes $K$, and the are specified in the theorems below.
+the number of classes $K$, and are specified in the theorems below.
 
@@
 function $p:\R^d \to \R$ of the form
-$$
-p(x) = p(x_1, x_2, \dots, x_d) = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-$$
+\begin{align*}
+p(x)
+& = p(x_1, x_2, \dots, x_d) \\
+& = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
+\end{align*}
 where the sum ranges over a finite set of $d$-tuples $(\alpha_1, \alpha_2,
@@
 $$
-r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1 \qquad \text{and} \qquad s = \left \lceil \log_2(1/\gamma) \right \rceil \; .
+r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(1/\gamma) \right \rceil \; .
 $$
@@
 $\psi_n$ is $\R^d$. The domain of $\rho$ is the unit ball of $\R^d$. The
-co-domain for $\phi_n$ and $\psi_n$ is $\R^p$ where $p = \sum_{i=0}^n
-\binom{i+d-1}{d-1}$ equipped with the standard inner product $\ip{x}{x'} =
-\sum_{i=1}^p x_i x'_i$. The co-domain is the classical separable Hilbert space
+co-domain of $\phi_n$ and $\psi_n$ is $\R^q$ where $q = \sum_{i=0}^n
+\binom{i+d-1}{d-1}$ equipped with the standard inner product $\ip{x}{x'}_{\R_q} =
+\sum_{i=1}^p x_i x'_i$. The co-domain of $\rho$ is the classical real separable Hilbert space
 $\ell_2 = \{ x \in \R^\infty ~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped
-with the standard inner product $\ip{x}{x'} = \sum_{i=1}^\infty x_i x'_i$. We
-index the coordinates of the co-domain $\R^p$ by $d$-tuples $(\alpha_1,
+with the standard inner product $\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. We
+index the coordinates of the co-domain $\R^q$ by $d$-tuples $(\alpha_1,
 \alpha_2, \dots, \alpha_d)$ of non-negative integers such that $\alpha_1 +
@@
 \begin{align*}
-K_{\psi_n}(x,x') & = \ip{\psi_n(x)}{\psi_n(x')}_{\R^p} = \left( 1 + \ip{x}{x'} \right)^n \; , \\
+K_{\psi_n}(x,x') & = \ip{\psi_n(x)}{\psi_n(x')}_{\R^q} = \left( 1 + \ip{x}{x'} \right)^n \; , \\
 K_{\rho}(x,x') & = \ip{\rho(x)}{\rho(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}} \; .
@@
 
-TODO
+Any mutlivariate polynomial in the orginal space $\R^d$ can be expressed as a
+linear function in the new feature spaces given by mappings $\phi_n, \psi_n,
+\rho$. The following lemma bounds the norm of the linear function in the terms
+of the norm of the polynomial. Recall that a linear function in a Hilbert space
+$(H, \ip{\cdot}{\cdot}_H)$ has the form $\ip{c}{x}_H$ for some vector $c \in H$
+and its norm is $\norm{c}_H = \sqrt{\ip{c}{c}}$.
+
+\begin{lemma}
+Let $d \ge 1$ and $n \ge 0$ be integers and let $q = \sum_{i=0}^n \binom{i+d-1}{d-1}$.
+Let $p:\R^d \to \R$ be a multivariate polynomial.
+\begin{enumerate}
+\item If $n \ge \deg(p)$ then there exists $c \in \R^q$ such that $p(x) = \ip{c}{\phi_n(x)}_{\R^q}$
+and $\norm{c}_{\R^q} = \norm{p}$.
+\item If $n \ge \deg(p)$ then there exists $c' \in \R^q$ such that $p(x) = \ip{c'}{\psi_n(x)}_{\R^q}$
+and $\norm{c'}_{\R^q} \le \norm{p}$.
+\item There exists $c'' \in \ell_2$ such that $p(x) = \ip{c''}{\psi_n(x)}_{\ell_2}$
+and $\norm{c''}_{\R^q} \le 2^{\deg(p)/2} \norm{p}$.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+Note that the polynomial $p$ can be written as
+$p(x) = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}$.
+There are $\sum_{i=0}^{\deg(p)} \binom{i+d-1}{d-1}$ coefficients $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$.
+If $n \ge \deg(p)$ these can be expressed as a vector in $c \in \R^q$. Thus, $p(x) = \ip{c}{\phi_n(x)}_{\R^q}$
+and
+$$
+\norm{c}_{\R^p} = \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} (c_{\alpha_1, \alpha_2, \dots, \alpha_d})^2} =  \norm{p} \; .
+$$
+
+We define $c' \in \R^q$ using the multi-index notation as
+$$
+c'_{\alpha_1, \alpha_2, \dots, \alpha_d}
+= \frac{c_{\alpha_1, \alpha_2, \dots, \alpha_d}}{\sqrt{\binom{n}{\alpha_1 + \alpha_2 + \dots + \alpha_d} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}} \; .
+$$
+We have $\ip{c'}{\psi_n(x)}_{\R^q} = \ip{c}{\phi_n(x)}_{\R^q} = p(x)$. Since
+$$
+|c'_{\alpha_1, \alpha_2, \dots, \alpha_d}| \le |c_{\alpha_1, \alpha_2, \dots, \alpha_d}| \; ,
+$$
+we have $\norm{c'}_{\R^q} \le \norm{c}_{\R^q} = \norm{p}$.
+
+Similarly, we define $c'' \in \ell_2$ using the multi-index notation as
+$$
+c''_{\alpha_1, \alpha_2, \dots, \alpha_d}
+= \frac{c_{\alpha_1, \alpha_2, \dots, \alpha_d} 2^{(\alpha_1 + \alpha_2 + \dots + \alpha_d)/2}}{\sqrt{\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}}
+$$
+for all tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ such that $\alpha_1 + \alpha_2 + \dots + \alpha_d \le \deg(p)$.
+Otherwise, we define $c''_{\alpha_1, \alpha_2, \dots, \alpha_d} = 0$. We have
+$\ip{c''}{\rho(x)}_{\ell_2} = \ip{c}{\phi_n(x)}_{\R^q} = p(x)$. Since
+\begin{align*}
+|c''_{\alpha_1, \alpha_2, \dots, \alpha_d}|
+& \le 2^{(\alpha_1 + \alpha_2 + \dots + \alpha_d)/2} |c''_{\alpha_1, \alpha_2, \dots, \alpha_d}| \\
+& \le 2^{\deg(p)/2} |c''_{\alpha_1, \alpha_2, \dots, \alpha_d}| \; ,
+\end{align*}
+we have $\norm{c''}_{\ell_2} \le 2^{\deg(p)/2} \norm{c}_{\R^q} = 2^{\deg(p)/2} \norm{p}$.
+\end{proof}

### 2019-01-10 ICML-submission/from-linear-separability-to-strong-linear-separability.tex
Add margin theorem

@@
 co-domain of $\phi_n$ and $\psi_n$ is $\R^q$ where $q = \sum_{i=0}^n
-\binom{i+d-1}{d-1}$ equipped with the standard inner product $\ip{x}{x'}_{\R_q} =
+\binom{i+d-1}{d-1}$ equipped with the standard inner product $\ip{x}{x'}_{\R^q} =
 \sum_{i=1}^p x_i x'_i$. The co-domain of $\rho$ is the classical real separable Hilbert space
@@
 
-\begin{lemma}
+\begin{lemma}[Norm bound]
+\label{lemma:norm-bound}
 Let $d \ge 1$ and $n \ge 0$ be integers and let $q = \sum_{i=0}^n \binom{i+d-1}{d-1}$.
@@
 \end{proof}
+
+Using the lemma and the polynomial approximation theorems, we can prove
+the mappings $\phi_n, \psi_n, \rho$ map any a weakly separable data
+to a strongly separable data set.
+
+\begin{theorem}
+Let $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \R^d \times \{1,2,\dots,K\}$
+labeled examples that are weakly linearly separable with margin $\gamma > 0$
+such that $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$. Then, the labeled
+examples $(\rho(x_1), y_1), (\rho(x_2), y_2), \dots, (\rho(x_T), y_T)$ are
+strongly linearly separable with margin
+$$
+\gamma' = \frac{1}{2\sqrt{K} \left(376 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}}
+$$
+and $\norm{\rho(x_1)}_{\ell_2}, \norm{\rho(x_2)}_{\ell_2}, \dots, \norm{\rho(x_T)}_{\ell_2} \le 2$.
+TODO
+\end{theorem}
+
+\begin{proof}
+First osberve that for any $t=1,2,\dots,T$,
+$$
+\norm{\rho(x_t)}_{\ell_2} = K_{\rho}(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
+$$
+
+Since the examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ are weakly linearly separable
+with margin $\gamma$ there are vectors $w_1, w_2, \dots, w_K$ satisfying
+\eqref{equation:weak-linear-separability-1} anf \eqref{equation:weak-linear-separability-2}.
+
+Fix any $i \in \{1,2,\dots,K\}$. Consider the $K-1$ vectors
+$(w_i - w_j)/2$ for $j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors
+have norm at most $1$.
+\autoref{theorem:polynomial-approximation-1} implies that
+there exists a polynomial $p_i:\R^d \to \R$ such
+that
+$$
+\deg(p) = \lceil \log_2(2m) \rceil \cdot \lceil \sqrt{\frac{2}{\gamma}} \rceil \; ,
+$$
+for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$ and if $y_t \neq i$ then $p_i(x_t) \le -1/2$,
+and
+$$
+\norm{p} \le \left(188 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2m) \rceil
+\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; .
+$$
+By \autoref{lemma:norm-bound} there exists $c_i \in \ell_2$ such that
+$\ip{c_i}{\rho(x)} = p(x)$ and
+$$
+\norm{c_i}_{\ell_2}
+\le \left(376 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2m) \rceil
+\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; .
+$$
+Define vector $u_i \in \ell_2$ as
+$$
+u_i = \frac{c_i}{\sqrt{K} \left(376 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2m) \rceil
+\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}} \; .
+$$
+
+Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$ and
+for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma'$
+and for all $j \in \{1,2,\dots,K\} \setminus \{y_t\}$,
+$\ip{u_j}{x_t} \le - \gamma'$. In other words,
+$(\rho(x_1), y_1), (\rho(x_2), y_2), \dots, (\rho(x_T), y_T)$ are
+strongly linearly separable with margin $\gamma'$.
+\end{proof}

### 2019-01-10 ICML-submission/related-work.tex
Add margin theorem

@@
 The problem of bandit multiclass linear classification was initially formulated
-by the pioneering work of~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. In that
-work, two computationally inefficient algorithms that work in the standard
-linearly separable setting are proposed: one with a mistake bound of $O(K^2 d
+in the pioneering work of~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed
+two computationally inefficient algorithms that work in the standard
+linearly separable setting, one with a mistake bound of $O(K^2 d
 \ln(\frac{d}{\gamma^2}))$, the other with a mistake bound of
@@
 weak learning condition, which implies that all examples is separable by a
-convex combination of base hypotheses with a margin
-(See~\cite{Mukherjee-Schapire-2013}, Theorem 3). Under this condition, it gives
-a boosting algorithm with a $O(\sqrt{T})$ mistake bound with the knowledge of
-the edge parameter. In addition, it gives an adaptive algorithm with a
-$O(T^{3/4})$ mistake bound.
+convex combination of base hypotheses with a margin; see~\citet[Theorem
+3]{Mukherjee-Schapire-2013}. Under this condition, it gives a boosting algorithm
+with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge parameter. In
+addition, it gives an adaptive algorithm with a $O(T^{3/4})$ mistake bound.
 
@@
 with an associated cost vector $c_t$ hidden. The learner then takes an action
-$\hat{y}_t$, and observed the incurred cost $c_t$. The goal of the learner is to
-minimize its regret $\sum_{t=1}^T c_t(\hat{y}_t) - \min_{\pi \in \Pi}
+$\widehat{y}_t$, and observed the incurred cost $c_t$. The goal of the learner is to
+minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{\pi \in \Pi}
 \sum_{t=1}^T c_t(\pi(x_t))$. The online bandit multiclass learning problem is a
 special case of the contextual bandits problem, where the cost $c_t(i)$ is the
-classification error $I(i \neq y_t)$, and the policy class $\Pi$ is the set of
+classification error $\indicator{i \neq y_t}$, and the policy class $\Pi$ is the set of
 linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$. A

### 2019-01-10 ICML-submission/title-and-abstract.tex
Rename linear separability to weak linear separability
Add margin theorem

@@
 linearly separable by a margin $\gamma$. In this work, we take a first step
-towards this problem. We consider two notions of linear separability: strong
-linear separability and weak linear separability.
+towards this problem. We consider two notions of linear separability,
+\emph{strong} and \emph{weak}.
 
@@
 separable examples to strong linear separable examples, which in turn is
-inspired by \cite{Klivans-Servedio-2008}'s work on learning intersection of
+inspired by the work of \citet{Klivans-Servedio-2008} on learning intersection of
 halfspaces.

### 2019-01-13 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
minor

@@
 
-\chicheng{I think this part need to be formalized. Can we assume without loss of generality
-that a deterministic prediction algorithm will have a smaller expected cost?
-If so, define $F(k)$ be the number of mistake that will be made by the algorithm,
-if the adversary commits to a label uniformly at random from $\cbr{1,2,\ldots,k}$,
-and the guessing of the label lasts for $k$ rounds.
-we can construct a recurrence of $F$: $F(k) = F(k-1) + \frac{k-1}{k}$, and $F(1) = 0$.
-Therefore, $F(K) = \Omega(K)$.}
+\chicheng{I think this part need to be formalized, by directly using
+~\cite{Daniely-Helbertal-2013}, Claim 2.}
+%Can we assume without loss of generality
+%that a deterministic prediction algorithm will have a smaller expected cost?
+%If so, define $F(k)$ be the number of mistake that will be made by the algorithm,
+%if the adversary commits to a label uniformly at random from $\cbr{1,2,\ldots,k}$,
+%and the guessing of the label lasts for $k$ rounds.
+%we can construct a recurrence of $F$: $F(k) = F(k-1) + \frac{k-1}{k}$, and $F(1) = 0$.
+%Therefore, $F(K) = \Omega(K)$.
 

### 2019-01-14 ICML-submission/related-work.tex
initial related work

@@
 
-The problem of bandit multiclass linear classification was initially formulated
-in the pioneering work of~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed
+The problem of online bandit multiclass learning was initially formulated
+in the pioneering work of~\cite{Auer-Long-1999}, under the name of
+``weak reinforcement model''. They show that if the set of examples shown is
+separable by a classifier in a prespecified hypothesis class $\calH$, then the optimal
+ mistake bound in the bandit setting can be upper bounded by the optimal mistake
+ bound in the full-information setting, times a factor of $(2.01 + o(1))K \ln K$.
+ (See~\cite{Long-2017} for improvements of the factor to $(1 + o(1)) K \ln K$.)
+ ~\cite{Daniely-Helbertal-2013} extend the results to the setting where the
+ performance of the algorithm is measured by its regret, i.e. the difference
+ between the number of mistake made by the algorithm and the number of mistake
+ made by the best classifier in $\calH$ in hindsight. However, all algorithms developed in
+ this context are computationally inefficient.
+
+The linear classification version of this problem
+is initially studied by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed
 two computationally inefficient algorithms that work in the standard

### 2019-01-14 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
kernelized algorithm (without guarantees yet)

@@
 \end{proof}
+
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
+can be extended to nonlinear classification using kernels~\cite{Scholkopf-Smola-Bach-2002}.
+For each class, as opposed
+to explicitly maintaining the weights for each class, we maintain
+the set of examples whose scaled feature transformations are added to the weights.
+We give a formal description in Algorithm~\ref{algorithm:kernelized}.
+
+\begin{algorithm}[h]
+\caption{\textsc{Kernelized Bandit Algorithm}
+\label{algorithm:kernelized}}
+\begin{algorithmic}[1]
+{
+\REQUIRE{Number of classes $K$.}
+\REQUIRE{Number of rounds $T$.}
+\REQUIRE{Kernel function  $k(\cdot, \cdot)$.}
+\STATE{Initialize $J_1^{(1)} = J_2^{(1)} = \dots = J_K^{(1)} = \emptyset$}
+\FOR{$t=1,2,\dots,T$}
+\STATE{Observe feature vector $x_t$.}
+\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \sum_{(x,y) \in J_i^{(t)}} y k(x, x_t) \ge 0 \right\}$}
+\IF{$S_t = \emptyset$}
+\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
+\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
+\IF{$z_t = 1$}
+\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
+\ELSE
+\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad  for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
+\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, +1)}$}
+\ENDIF
+\ELSE
+\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
+\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
+\IF{$z_t = 1$}
+\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
+\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, -1)}$}
+\ELSE
+\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
+\ENDIF
+\ENDIF
+\ENDFOR
+}
+\end{algorithmic}
+\end{algorithm}

### 2019-01-14 ICML-submission/introduction.tex
Add margin theorem
kernelized algorithm (without guarantees yet)

@@
 viewed as a repeated game between the learner and the adversary. At each timestep $t$,
-the adversary chooses a labeled example $(x_t, y_t)$ where the feature vector, $x_t \in
+the adversary chooses a labeled example $(x_t, y_t)$ where the feature vector $x_t \in
 \R^d$ is revealed to the learner and the correct label $y_t$ is kept secret by
@@
 
-\begin{algorithm}[h]
+\begin{protocol}[h]
 \caption{\textsc{Online Multiclass Classification with Bandit Feedback}
@@
 {
-\REQUIRE{Number of classes $K$.}
-\REQUIRE{Number of rounds $T$.}
+\REQUIRE{Number of classes $K$, number of rounds $T$.}
+%\REQUIRE{.}
 \FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$}
-\STATE{Adversary \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
-\chicheng{Or we simply say: Adversary chooses example $(x_t, y_t)$, where $x_t$ is reveal to the learner.}
+\STATE Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.
+%\STATE{Observe feature vector $x_t$}
+%\STATE{Adversary \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
+%\chicheng{Or we simply say: Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.}
 \STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
@@
 \end{algorithmic}
-\end{algorithm}
+\end{protocol}
 

### 2019-01-14 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
in the middle of proof of Thm 3

@@
 The idea behind the algorithm is to use $K$ copies of the \textsc{Binary
-Perceptron} algorithm. Each copy corresponds to a class. In each round, each
-copy makes a binary decision whether the feature vector belongs its respective
-class or not. If at least one copy makes a positive prediction, the algorithm
-predicts accordingly. If multiple copies make positive predictions, the
-algorithm chooses one of them arbitrarily. If all copies make negative
-predictions, the algorithms makes a uniformly random guess.
+Perceptron} algorithm, where each copy corresponds to a class.
+In each round, copy $i$
+makes a binary prediction, indicating whether the example belongs to class $i$ or not.
+If at least one copy makes a positive prediction, the algorithm
+chooses its prediction as one of the classes corresponding to a positive prediction.
+If all copies make negative
+predictions, the algorithms makes a prediction uniformly at random.
+
+%accordingly. If multiple copies make positive predictions, the
+%algorithm chooses one of them arbitrarily
 
@@
 \STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$}
+\label{line:pos-update}
 \ENDIF
@@
 \STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
+\label{line:neg-update}
 \ELSE
@@
 \label{theorem:strongly-separable-example-mistake-upper-bound}
-Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
-integer, let $\gamma$ a positive real number, let $R$ be a non-negative real number. If
+Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
+integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
 $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
-$V \times \{1,2,\dots,K\}$ such that the examples are strongly separable with
-margin $\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ then the
+$V \times \{1,2,\dots,K\}$ such that
+\begin{enumerate}
+  \item the examples are strongly separable with margin $\gamma$,
+  \item $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$,
+\end{enumerate}
+then the
 expected number of mistakes
@@
 \begin{proof}
-Let $M = \sum_{t=1}^T z_t$ be the number of mistakes the algorithm makes. Let $A
+Let $M = \sum_{t=1}^T z_t$ be the number of
+mistakes Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} makes.
+Let $A
 = \sum_{t ~:~ S_t \neq \emptyset} z_t$ be the number of mistakes in the rounds
 when $S_t \neq \emptyset$ and let $B = \sum_{t ~:~ S_t = \emptyset} z_t$ be the
-number of mistakes in the rounds when $S_t = \emptyset$. Obviously, $M = A + B$.
-We upper bound $A$ and $B$ separately.
+number of mistakes in the rounds when $S_t = \emptyset$.
+It can be easily seen that $M = A + B$. %We now upper bound $A$ and $B$ separately.
 
-Let $C$ be the number of times line 12 gets executed. Let $U$ be the number of
-times line 12 and line 19 get executed. In other words, $U$ is the number of
+Let $C$ be the number of times line~\ref{line:pos-update} gets executed. Let $U$ be the number of
+times line~\ref{line:pos-update} and line~\ref{line:neg-update} get executed. In other words, $U$ is the number of
 times the $K$-tuple of vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets
-updated. Clearly, $U = A + C$.
+updated. It can be easily seen that $U = A + C$.
 
@@
 
-To finish the proof, we need to upper bound the number of updates, $U$. We claim
+To finish the proof, we need to upper bound the number of updates $U$. We claim
 that $U \le \lfloor (R/\gamma)^2 \rfloor$. The proof of this upper bound is
@@
 $\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$ change. If there is an update in round $t$,
-we have
+by lines~\ref{line:pos-update} and~\ref{line:neg-update}, we always have
+$ w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t $,
+and for all $i \neq \widehat y_t$, $w_{i}^{(t+1)} = w_{i}^{(t)}$.
+Therefore,
 \begingroup
@@
 \endgroup
-Therefore, after $U$ updates,
+Hence, after $U$ updates,
 $$
@@
 $$
-Applying Cauchy-Schwartz's inequality twice and assumption
+Applying Cauchy-Schwartz's inequality twice, and using assumption
 \eqref{equation:strong-linear-separability-1}, we get that

### 2019-01-14 ICML-submission/notions-of-linear-separability.tex
in the middle of proof of Thm 3

@@
 \label{equation:strong-linear-separability-2}
-& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \gamma \; , \\
+& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \frac \gamma 2 \; , \\
 \label{equation:strong-linear-separability-3}
@@
 \forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
-\ip{x_t}{w_i} \le - \gamma \; .
+\ip{x_t}{w_i} \le - \frac \gamma 2 \; .
 \end{gathered}
@@
 
-The notion of strong linear separability is new. Intuitively, strong linear
-separability means that, for each $i$, the set of examples with class $i$ and
-the set of example of other classes are separated by a linear classifier $w_i$.
-Formally, $w_i$ separates the set of examples $\cbr{(x_t, y_t): t \in
-\cbr{1,\ldots,T}, y_t = i}$ and $\cbr{(x_t, y_t): t \in \cbr{1,\ldots,T}, y_t
-\neq i}$.
+The notion of strong linear separability has appeared in the literature
+(see e.g.~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}).
+\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009} claimed that their
+Conservative OVA algorithm with PA-I update has a finite mistake bound under the strong
+linear separability assumption, their proof of Theorem 2 is problematic: their
+Lemma 4 cannot be directly applied to the bandit setting,
+as the algorithm only makes updates on a subset of the rows of the weight matrix.}
+Intuitively, strong linear
+separability means that, for each class $i$, the set of examples belonging to class $i$ and
+the set of example belonging to the remaining $K-1$ classes are separated by
+a linear classifier $w_i$ by a margin $\frac \gamma 2$.
+%Formally, $w_i$ separates the set of examples $\cbr{(x_t, y_t): t \in
+%\cbr{1,\ldots,T}, y_t = i}$ and $\cbr{(x_t, y_t): t \in \cbr{1,\ldots,T}, y_t
+%\neq i}$.
 
-\chicheng{I think the notion has appeared in~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}, however,
-they proposed an algorithm that doesn't achieve a finite mistake bound in the bandit
-setting under this assumption (although they claimed that they have done so, the proof was
-wrong..)}
+%\chicheng{I think the notion has appeared in, however,
+%they proposed an algorithm that doesn't achieve a finite mistake bound in the bandit
+%setting under this assumption (although they claimed that they have done so, the proof was
+%wrong..)}
 
 It is easy to see that if a set of labeled examples are strongly linearly
-separable with margin $\gamma$, then they are weakly linearly separable with margin
-$2\gamma$. Indeed, if $w_1, w_2, \dots, w_K \in V$
+separable with margin $\gamma$, then they are weakly linearly separable with
+the same margin. Indeed, if $w_1, w_2, \dots, w_K \in V$
 satisfy \eqref{equation:strong-linear-separability-1},
@@
 \eqref{equation:weak-linear-separability-1} and
-\eqref{equation:weak-linear-separability-2} with margin $\gamma' = 2\gamma$.
+\eqref{equation:weak-linear-separability-2}.
 
-Similarly, if $K=2$ and labeled examples are weakly linearly separable with a margin
-$\gamma$ then they are strongly linearly separable with margin $\gamma/2$.
+%with margin $\gamma' = 2\gamma$.
+
+In the special case of $K=2$, if a set of labeled examples are weakly linearly separable with a margin
+$\gamma$, then they are strongly linearly separable with the same margin.
 Indeed, if $w_1, w_2$ satisfy \eqref{equation:weak-linear-separability-1} and
 \eqref{equation:weak-linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$, $w_2' =
-\frac{w_2 - w_1}{2}$ and $\gamma'=\gamma/2$ satisfy
+\frac{w_2 - w_1}{2}$ satisfy
 \eqref{equation:strong-linear-separability-1},
 \eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3}. The last two conditions are easy
-to see. The first condition follows from $\norm{w_i'}^2 \le (\frac{1}{2}
+\eqref{equation:strong-linear-separability-3}.
+The first condition follows from $\norm{w_i'}^2 \le (\frac{1}{2}
 \norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le \frac{1}{2}\norm{w_1}^2 +
-\frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
-
-\chicheng{Shall we change the $\gamma$ in Equations
-\eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3} to $\gamma/2$, to simplify the
-presentation?}
-
+\frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$. The last two condition
+follows from the fact that $w_1' - w_2' = w_1 - w_2$.
 However, for any $K \ge 3$ and any inner product space of dimension at least
@@
 
+%\chicheng{Shall we change the $\gamma$ in Equations
+%\eqref{equation:strong-linear-separability-2},
+%\eqref{equation:strong-linear-separability-3} to $\gamma/2$, to simplify the
+%presentation?}
+
 \begin{figure}
@@
 \end{center}
-\caption[]{The figure shows labeled examples in $\R^2$. The examples belong to
+\caption[]{A set of labeled examples in $\R^2$. The examples belong to
 $K=3$ classes colored white, gray and black respectively. Each class lies in a
@@
 halfspaces.
+\chicheng{Do we have an explicit formula for $W$ in this example? It might help
+to provide it.}
 
 While the examples are weakly linearly separable with a positive margin $\gamma$, they
-are \emph{not} strongly linearly separable with any positive margin $\gamma$.
+are \emph{not} strongly linearly separable with any positive margin $\gamma$. For instance,
+there do not exist linear separators that separates the
+examples belonging to the gray class from the examples belonging to the remaining two classes.
 }

### 2019-01-14 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
finished a pass over the first 4 sections

@@
 \begin{enumerate}
-  \item the examples are strongly separable with margin $\gamma$,
+  \item the examples are strongly linearly separable with margin $\gamma$ (Definition~\ref{definition:strong-linear-separability}),
   \item $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$,
@@
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-makes is at most $(K-1) \lfloor (R/\gamma)^2 \rfloor$.
+makes is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
 \end{theorem}
@@
 incorrect. Putting all the information together, we get that
-\begin{align*}
+\begin{align}
 \Exp[M]
-& = \Exp[A] + \Exp[B] \\
-& = \Exp[A] + (K-1) \Exp[C]  \\
-& \le (K-1) \Exp[A + C] \\
+& = \Exp[A] + \Exp[B] \nonumber \\
+& = \Exp[A] + (K-1) \Exp[C] \nonumber \\
+& \le (K-1) \Exp[A + C] \nonumber\\
 & = (K-1) \Exp[U]  \; .
-\end{align*}
+\label{eqn:mistake-update}
+\end{align}
 
@@
 Hence, after $U$ updates,
-$$
+\begin{equation}
 \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
-$$
+\label{eqn:norm-ub}
+\end{equation}
 Similarly, if there is an update in round $t$, we have
@@
 & = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
-& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \gamma
+& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \frac \gamma 2,
 \end{align*}
-where the last inequality follows from \eqref{equation:strong-linear-separability-2}
-and \eqref{equation:strong-linear-separability-3} and analysis of the cases $z_t = 0$ and $z_t = 1$.
+where the last inequality follows from a case analysis on $z_t$ and
+Definition~\ref{definition:strong-linear-separability}: if $z_t = 0$, then
+$\widehat y_t = y_t$, by Equation~\eqref{equation:strong-linear-separability-2}, we have
+that $\ip{w_{\widehat y_t}^*}{x_t} \geq \frac \gamma 2$;
+if $z_t = 1$, then $\widehat y_t \neq y_t$, by Equation~\eqref{equation:strong-linear-separability-3},
+we have that $\ip{w_{\widehat y_t}^*}{x_t} \leq -\frac \gamma 2$.
+
+%\eqref{equation:strong-linear-separability-2}
+%and \eqref{equation:strong-linear-separability-3} and analysis of the cases $z_t = 0$ and $z_t = 1$.
+
 Thus, after $U$ updates,
-$$
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma U \; .
-$$
+\begin{equation}
+\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \frac {\gamma U} 2 \; .
+\label{eqn:norm-lb}
+\end{equation}
 Applying Cauchy-Schwartz's inequality twice, and using assumption
@@
 \end{align*}
-Combining the upper and lower bounds on $\sum_{i=1}^K \norm{w_i^{(T+1)}}^2$ inequalities, we get
+Combining the above inequality with Equations~\eqref{eqn:norm-ub} and~\eqref{eqn:norm-lb}, we get
 $$
-(\gamma U)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
+(\frac{\gamma U}{2})^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
 $$
-We conclude that $U \le (R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor (R/\gamma)^2 \rfloor$.
+We conclude that $U \le 4(R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor 4(R/\gamma)^2 \rfloor$.
+
+Applying Equation~\eqref{eqn:mistake-update}, we get
+\[ \Exp[M] \leq (K-1) \Exp[U] \leq (K-1) \lfloor 4(R/\gamma)^2 \rfloor. \qedhere \]
 \end{proof}
 
-The upper bound $(K-1) \lfloor (R/\gamma)^2 \rfloor$ on the expected number of
+The upper bound $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$ on the expected number of
 mistakes of
@@
 
-Irrespective of any conditions on $K$, $R$, and $\gamma$, a trivial lower bound
+\begin{theorem}[Mistake lower bound]
+\label{theorem:strongly-separable-example-mistake-lower-bound}
+Let $\gamma$ be a positive real number, and $R$ be a non-negative real
+number. For any (possibly randomized) algorithm $\calA$ for the \textsc{Online
+Multiclass Classification with Bandit Feedback} with $K \le
+(R/\gamma)^2$ classes there exists an inner product space $(V,
+\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
+examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ in $V \times
+\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
+norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
+number of mistakes $\calA$ makes is at least $\frac{K-1}{2} \left\lfloor
+\frac{1}{4} (R/\gamma)^2 \right\rfloor$.
+\end{theorem}
+
+\paragraph{Remark.} Irrespective of any conditions on $K$, $R$, and $\gamma$, a trivial lower bound
 on the expected number of mistakes of any randomized algorithm is
@@
 
-\begin{theorem}[Mistake lower bound]
-\label{theorem:strongly-separable-example-mistake-lower-bound}
-Let $\gamma$ be a positive real number and let $R$ be a non-negative real
-number. For any (possibly randomized) algorithm for the \textsc{Online
-Multiclass Classification with Bandit Feedback} with $K \le
-\frac{1}{4}(R/\gamma)^2$ classes there exists an inner product space $(V,
-\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ in $V \times
-\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
-norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
-number of mistakes the algorithm makes is at least $\frac{K-1}{2} \left\lfloor
-\frac{1}{16} (R/\gamma)^2 \right\rfloor$.
-\end{theorem}
-
 \begin{proof}
-We use probabilistic method. Let $M = \left\lfloor \frac{1}{16} (R/\gamma)^2
+We use probabilistic method. Let $M = \left\lfloor \frac{1}{4} (R/\gamma)^2
 \right\rfloor$. Let $V = \R^{M+1}$ equipped with the standard inner product.
 Let $e_1, e_2, \dots, e_{M+1}$ be the standard orthonormal basis of $V$. We
-define vectors $v_1, v_2, \dots, v_M \in V$ where $v_i = \frac{R}{\sqrt{2}}(e_i
-+ e_{M+1})$ for $i=1,2,\dots,M$. Let $\ell_1, \ell_2, \dots, \ell_M$ be chosen
+define vectors $v_1, v_2, \dots, v_M \in V$ where $v_j = \frac{R}{\sqrt{2}}(e_j
++ e_{M+1})$ for $j=1,2,\dots,M$. Let $\ell_1, \ell_2, \dots, \ell_M$ be chosen
 i.i.d. uniformly at random from $\{1,2,\dots,K\}$ and independently of any
-randomness used the by the algorithm. Let $T = M K$. We define examples $(x_1,
+randomness used the by algorithm $\calA$. Let $T = M (K - 1)$. We define examples $(x_1,
 y_1), (x_2, y_2), \dots, (x_T, y_T)$ as follows. For any $j=1,2,\dots,M$ and any
-$i=1,2,\dots,K$,
+$h=1,2,\dots,K-1$,
 $$
-(x_{(j-1)K + i}, y_{(j-1)K + i}) = (v_j, \ell_j)
+(x_{(j-1)(K-1) + h}, y_{(j-1)(K-1) + h}) = (v_j, \ell_j)
 $$
 
-With probability one, norm of each example is $R$. We show that with probability
-one, the examples are strongly separable with margin $\gamma$. In order to see
-that consider $w_1^*, w_2^*, \dots, w_K^* \in V$ defined by
+With probability one, the norm of each example is exactly $R$.
+We show that with probability
+one, the examples are strongly separable with margin $\gamma$. To see
+that, consider $w_1^*, w_2^*, \dots, w_K^* \in V$ defined by
 $$
-w_i^* = 2 \sqrt{2} \frac{\gamma}{R} \left( \sum_{j ~:~ \ell_j = i} e_j \right) - \sqrt{2} \frac{\gamma}{R} e_{M+1}
+w_i^* = \sqrt{2} \frac{\gamma}{R} \left( \sum_{j ~:~ \ell_j = i} e_j \right) - \frac{\sqrt{2}}2 \frac{\gamma}{R} e_{M+1}
 $$
-for $i=1,2,\dots,K$. Since for any $i \in \{1,2,\dots,K\}$ and any $j \in
-\{1,2,\dots,M\}$,
-$$
-\ip{w_i^*}{v_j} =
-\begin{cases}
-\gamma & \text{if $\ell_j = i$,} \\
-- \gamma & \text{if $\ell_j \neq i$,}
-\end{cases}
-$$
-it means that $w_1^*, w_2^*, \dots, w_K^*$ satisfy
+for $i=1,2,\dots,K$.
+
+for $i \in \{1,2,\dots,K\}$ and any $j \in
+\{1,2,\dots,M\}$, we consider the inner product of $w_i^*$ and $v_j$.
+If $i = \ell_j$, $\ip{w_i^*}{v_j} = \gamma - \frac \gamma 2 = \frac \gamma 2$;
+otherwise $i \neq \ell_j$, in this case,
+$\ip{w_i^*}{v_j} = 0 - \frac \gamma 2 = - \frac \gamma 2$.
+This means that $w_1^*, w_2^*, \dots, w_K^*$ satisfy
+conditions
 \eqref{equation:strong-linear-separability-2} and
@@
 \sum_{i=1}^K \norm{w_i^*}^2
-= 8 \frac{\gamma^2}{R^2} \sum_{j=1}^M \norm{e_j}^2 + 2 \frac{\gamma^2}{R^2} K \norm{e_{M+1}}^2 \\
-= 8 \frac{\gamma^2}{R^2} M + 2 \frac{\gamma^2}{R^2} K
+= 2 \frac{\gamma^2}{R^2} \sum_{j=1}^M \norm{e_j}^2 +  \frac{\gamma^2}{2 R^2} K \norm{e_{M+1}}^2 \\
+= 2 \frac{\gamma^2}{R^2} M + \frac{\gamma^2}{2 R^2} K
 \le \frac{1}{2} + \frac{1}{2}
@@
 
-It remains to lower bound the expected number of mistakes of the algorithm. For
+It remains to lower bound the expected number of mistakes of $\calA$. For
 any $j \in \{1,2,\dots,M\}$, consider the expected number of mistakes the
-algorithm makes in rounds $K(j-1) + 1, K(j-1) + 2, \dots, Kj$. In these rounds,
-the algorithm is guessing the label $\ell_j$. Since $\ell_j$ is chosen uniformly
-at random from the set $\{1,2,\dots,K\}$ and feedback is only binary, the
-expected number of mistakes the algorithm makes in these rounds is at least
-$\frac{K-1}{2}$. Altogether, the algorithm makes at least $\frac{K-1}{2} M$
-mistakes in expectation.
+algorithm makes in rounds $(K-1)(j-1) + 1, (K-1)(j-1) + 2, \dots, (K-1)j$.
 
-\chicheng{I think this part need to be formalized, by directly using
-~\cite{Daniely-Helbertal-2013}, Claim 2.}
+Define a filtration $\cbr{\calB_j}_{j=0}^M$,
+where $\calB_j = \sigma((x_1, y_1), \ldots, (x_{(K-1)j}, y_{(K-1)j}))$
+for every $j$ in $\{1,2,\dots,M\}$.
+By Claim 2 of~\cite{Daniely-Helbertal-2013}, as $\ell_j$
+is chosen uniformly from $\cbr{1,\ldots,K}$ and independent of $\calB_{j-1}$,
+\[ \Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t \Bigg| \calB_{j-1} } \geq \frac{K-1}2. \]
+This implies that
+\[ \Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t } \geq \frac{K-1}2. \]
+Summing over all $j$ in $\{1,2,\dots,M\}$,
+\[ \Exp \sbr{ \sum_{t=1}^{(K-1)M} z_t} \geq \frac{K-1}2 \cdot M = \frac{K-1}2 \left\lfloor \frac 1 4 (R/\gamma)^2 \right\rfloor. \]
+
+%In these rounds,
+%the algorithm is guessing the label $\ell_j$. Since $\ell_j$ is chosen uniformly
+%at random from the set $\{1,2,\dots,K\}$ and feedback is only binary, the
+%expected number of mistakes the algorithm makes in these rounds is at least
+%$\frac{K-1}{2}$. Altogether, the algorithm makes at least $\frac{K-1}{2} M$
+%mistakes in expectation.
+
+%\chicheng{I think this part need to be formalized, by directly using
+%~\cite{Daniely-Helbertal-2013}, Claim 2.}
 %Can we assume without loss of generality
@@
 there exists a particular (i.e. deterministic) sequence of examples for which
-the algorithm makes at least $\frac{K-1}{2} M$ mistakes in expectation
+the algorithm makes at least $\frac{K-1}2 \left\lfloor \frac 1 4 (R/\gamma)^2 \right\rfloor$ mistakes in expectation
 over its internal randomization.
@@
 For each class, as opposed
-to explicitly maintaining the weights for each class, we maintain
-the set of examples whose scaled feature transformations are added to the weights.
-We give a formal description in Algorithm~\ref{algorithm:kernelized}.
+to explicitly maintaining the predictor's weights for each class, we maintain
+the set of examples whose scaled feature transformations are added to the weights in Perceptron updates.
+We give a formal description of the kernelized algorithm in Algorithm~\ref{algorithm:kernelized}.
 

### 2019-01-14 ICML-submission/notions-of-linear-separability.tex
finished a pass over the first 4 sections

@@
 Lemma 4 cannot be directly applied to the bandit setting,
-as the algorithm only makes updates on a subset of the rows of the weight matrix.}
+as the algorithm only makes updates on a subset of the $w_i$'s.}
 Intuitively, strong linear

### 2019-01-14 src/octave/compute_kernel.m
add codes

@@ -1,0 +1,183 @@
+function K = compute_kernel(in1,in2,in3,in4)
+% COMPUTE_KERNEL Calculates the kernel values
+%
+%   K = COMPUTE_KERNEL(X,IND1,IND2,KERNEL_PARAMS) calculates the kernel
+%   matrix for the data X, using the indexes in IND1 and IND2. The type of
+%   kernel and the parameters are passed through the structure
+%   KERNEL_PARAMS.
+%   K is a matrix with a number of rows equal to the number of indexes of
+%   IND1 and number of rows equal to the number of indexes in IND2.
+%
+%   K = COMPUTE_KERNEL(X1,X2,KERNEL_PARAMS) calculates the kernel matrix
+%   between the data X1 and the data X2. The type of kernel
+%   and the parameters are passed through the structure KERNEL_PARAMS.
+%   K is a matrix with a number of rows equal to the number of columns of
+%   X1 and number of rows equal to the number of columns of X2.
+%
+%   KERNEL_PARAMS is a struct with the field type with one of the following
+%   strings:
+%
+%       'linear'              Linear kernel or dot product
+%       'poly'                Polynomial kernel
+%       'rbf'                 Gaussian Radial Basis Function kernel
+%       'sigmoid'             Sigmoidal kernel
+%       'triangular'          Triangular kernel
+%       'intersection'        Intersection kernel
+%       'intersection_sparse' Intersection kernel for sparse matrices
+%       'expchi2'             Exponential Chi^2 kernel
+%       'expchi2_sparse'      Exponential Chi^2 kernel for sparse matrices
+%       'vovk_inf_poly'       Vovk infinite polynomial
+%
+%   The other fields of KERNEL_PARAMS depend on the specific kernel.
+%
+%   Note that K is always returned as a dense matrix.
+%
+%   Warning: For expchi2_sparse each feature vector must have sum of the
+%   elements equal to 1.
+%
+%   Example:
+%       % Load the data
+%       load synth_2d
+%       % Define a Gaussian kernel, with scale = 2
+%       hp.type='rbf'
+%       hp.gamma=2
+%       % Builds the kernel matrix
[…]

### 2019-01-14 src/octave/distort.m

@@ -1,0 +1,7 @@
+p=full(p);
+for i=1:size(p,1)
+  if rand<0.2
+    p(i,:)=p(i,:)*10^(sign(randn));
+  end
+end
+p=sparse(p);

### 2019-01-14 src/octave/generate_strong_separable.m

@@ -1,0 +1,36 @@
+function [W, X, Y] = generate_strong_separable(n_sample, dim, n_cla, margin)
+assert(dim >= n_cla); 
+randdim = randsample(dim, n_cla); 
+X = zeros(dim,n_sample);
+Y = zeros(n_sample,1);
+W = zeros(dim, n_cla); 
+for i=1:n_cla
+   W(randdim(i),i) = 1;
+end
+for i=1:n_sample
+    x_i = 2*rand(dim,1)-1;
+    x_i = x_i/norm(x_i); 
+    cla_i = randsample(n_cla, 1); 
+    for j=1:n_cla
+        if cla_i==j
+            x_i(randdim(j)) = max(abs(x_i(randdim(j))), margin); 
+        else
+            x_i(randdim(j)) = -max(abs(x_i(randdim(j))), margin);
+        end
+    end    
+    X(:,i) = x_i/norm(x_i);
+    
+    %%%%%%%%%%%%%%%% do two times %%%%%%%%%%%%%%%%
+    for j=1:n_cla
+        if cla_i==j
+            x_i(randdim(j)) = max(abs(x_i(randdim(j))), margin); 
+        else
+            x_i(randdim(j)) = -max(abs(x_i(randdim(j))), margin);
+        end
+    end    
+    X(:,i) = x_i/norm(x_i); 
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    
+    Y(i) = cla_i;
+end
+end

### 2019-01-14 src/octave/model_init.m

@@ -1,0 +1,49 @@
+function model = model_init(kernel,kerparam)
+% MODEL_INIT create an empty model for training
+%
+%   MODEL = MODEL_INIT(KERNEL_FUNCTION,KERNEL_PARAMS) returns an empty model,
+%   that will use KERNEL_FUNCTION with KERNEL_PARAMS.
+%
+%   MODEL = MODEL_INIT returns an empty model, setting the kernel to null. It
+%   is used for algorithms without kernels.
+%
+%   Example:
+%       % Define a Gaussian kernel, with scale = 2
+%       hp.type='rbf';
+%       hp.gamma=2;
+%       model_bak = model_init(@compute_kernel,hp);
+%
+%    This file is part of the DOGMA library for MATLAB.
+%    Copyright (C) 2009-2013, Francesco Orabona
+%    If you use this software in a paper you have to cite
+%     - Francesco Orabona. (2009)
+%       DOGMA: a MATLAB toolbox for Online Learning
+%       Software available at http://dogma.sourceforge.net
+%
+%    This program is free software: you can redistribute it and/or modify
+%    it under the terms of the GNU General Public License as published by
+%    the Free Software Foundation, either version 3 of the License, or
+%    (at your option) any later version.
+%
+%    This program is distributed in the hope that it will be useful,
+%    but WITHOUT ANY WARRANTY; without even the implied warranty of
+%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%    GNU General Public License for more details.
+%
+%    You should have received a copy of the GNU General Public License
+%    along with this program.  If not, see <http://www.gnu.org/licenses/>.
+%
+%    Contact the author: francesco [at] orabona.com
+
+if nargin==0 || isempty(kerparam)
+    kernel=[];
+    kerparam=[];
+end
+
+model.S=[];
+model.SV=[];
+model.ker=kernel;
+model.kerparam=kerparam;
+model.b=0;
+model.b2=0;
+model.step=1000;

### 2019-01-14 src/octave/ova_k_perceptron_train.m

@@ -1,0 +1,93 @@
+function model = ova_k_perceptron_train(X,Y,model)
+n = length(Y);   % number of training samples
+if isfield(model,'n_cla')==0
+    model.n_cla=max(Y);
+end
+
+%%%%%% the following implementation are similar to k_perceptron_train.m %%%%%%
+if isfield(model,'iter')==0
+    model.iter=0;
+    model.errTot=0;
+    model.aer=zeros(numel(Y),1);
+    model.pred=zeros(model.n_cla,numel(Y));
+    model.beta_list= cell(model.n_cla, 1);
+    %model.numSV_list=cell(model.n_cla, 1);
+    model.SV_list=cell(model.n_cla, 1); 
+    model.dim = size(X,1);
+end
+
+for j=1:model.n_cla
+    model.beta_list{j} = [];
+    model.SV_list{j} = zeros(model.dim,0);
+end
+%model.S_list
+for i=1:n
+    model.iter = model.iter+1;
+    val_f = zeros(1, model.n_cla); 
+    for j=1:model.n_cla
+        if numel(model.SV_list{j})>0
+           subK_f = feval(model.ker, model.SV_list{j}, X(:,i), model.kerparam); 
+           val_f(j) = model.beta_list{j} * subK_f; 
+        else
+           val_f(j) = 0;
+        end
+    end
+    
+    % if any of val_f is positive, pick the largest one (what if randomly pick one?)
+    % else uniformly randomly pick one
+    [maxval_f, maxidx] = max(val_f);
+    if maxval_f >= 0
+        Yhat = maxidx; 
+    else 
+        Yhat = unidrnd(model.n_cla);
+    end
+    
+    model.errTot = model.errTot + (Yhat~=Y(i));
+    model.aer(model.iter)=model.errTot/model.iter;
+    model.pred(:,model.iter)=val_f;
+    
+    if Yhat==Y(i)   % guess correctly
+        for j=1:model.n_cla
+            if(j~= Yhat && val_f(j)>=0)    % can possibly use val_f(j)>-margin
+                if size(model.SV_list{j},2) >= model.maxSV
+                    mn_idx = ceil(model.maxSV*rand); 
+                elseif numel(model.SV_list{j})==0
+                    mn_idx = 1; 
+                else
+                    mn_idx = size(model.SV_list{j},2)+1;
+                end
+                model.beta_list{j}(mn_idx) = -1; 
[…]

### 2019-01-14 src/octave/ova_perceptron_train.m

@@ -1,0 +1,69 @@
+function model = ova_perceptron_train(X,Y,model)
+n = length(Y);   % number of training samples
+if isfield(model,'n_cla')==0
+    model.n_cla=max(Y);
+end
+
+%%%%%% the following implementation are similar to k_perceptron_train.m %%%%%%
+if isfield(model,'iter')==0
+    model.iter=0;
+    model.errTot=0;
+    model.aer=zeros(numel(Y),1);
+    model.pred=zeros(model.n_cla,numel(Y));
+    model.w=zeros(model.n_cla,size(X,1));
+end
+
+if isfield(model, 'thres')==0
+    model.thres= 0;
+end
+
+for i=1:n
+    model.iter = model.iter+1;
+    val_f = zeros(1, model.n_cla); 
+    %size(val_f)
+    %size(model.w)
+    %size(X)
+    %i
+    for j=1:model.n_cla
+        val_f(j) = model.w(j,:)*X(:,i);
+    end
+    
+    %fprintf('val_f\n')
+    %val_f
+    % if any of val_f is positive, pick the largest one (what if randomly pick one?)
+    % else uniformly randomly pick one
+    [maxval_f, maxidx] = max(val_f);
+    %fprintf('maxidx\n')
+    %maxidx
+    if maxval_f >= model.thres
+        Yhat = maxidx; 
+    else 
+        Yhat = unidrnd(model.n_cla);
+    end
+    
+    model.errTot = model.errTot + (Yhat~=Y(i));
+    model.aer(model.iter)=model.errTot/model.iter;
+    model.pred(:,model.iter)=val_f;
+    
+    if Yhat==Y(i)   % guess correctly
+        for j=1:model.n_cla
+            if(j~= Yhat && val_f(j)>=0)    % can possibly use val_f(j)>-margin
+                model.w(j,:) = model.w(j,:) - X(:,i)';
+            end    
+        end
+        if val_f(Yhat) <= 0 % can possibly use f(Yhat) < gamma
+            model.w(Yhat,:) = model.w(Yhat,:) + X(:,i)';
+        end
+    else   % guess incorrectly
+        if val_f(Yhat) >= model.thres
+            model.w(Yhat,:) = model.w(Yhat,:) - X(:,i)';
+        end
+    end
+    
+    if mod(i,model.step)==0
+      fprintf('#%.0f \tAER:%5.2f\n', ...
+            ceil(i/1000), model.aer(model.iter)*100);
+    end    
+end
+%model.w
+end

### 2019-01-14 src/octave/perceptron_multi_train.m

@@ -1,0 +1,78 @@
+function model = perceptron_multi_train(X,Y,model)
+% PERCEPTRON_MULTI_TRAIN Perceptron multiclass algorithm
+%
+%    MODEL = PERCEPTRON_MULTI_TRAIN(X,Y,MODEL) trains a multiclass classifier
+%    according to the Perceptron algorithm.
+%
+%    Additional parameters:
+%    none
+%
+%   References:
+%
+%    This file is part of the DOGMA library for MATLAB.
+%    Copyright (C) 2009-2012, Francesco Orabona
+%    If you use this software in a paper you have to cite
+%     - Francesco Orabona. (2009)
+%       DOGMA: a MATLAB toolbox for Online Learning
+%       Software available at http://dogma.sourceforge.net
+%
+%    This program is free software: you can redistribute it and/or modify
+%    it under the terms of the GNU General Public License as published by
+%    the Free Software Foundation, either version 3 of the License, or
+%    (at your option) any later version.
+%
+%    This program is distributed in the hope that it will be useful,
+%    but WITHOUT ANY WARRANTY; without even the implied warranty of
+%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%    GNU General Public License for more details.
+%
+%    You should have received a copy of the GNU General Public License
+%    along with this program.  If not, see <http://www.gnu.org/licenses/>.
+%
+%    Contact the author: francesco [at] orabona.com
+
+n = length(Y);   % number of training samples
+
+if isfield(model,'n_cla')==0
+    model.n_cla=max(Y);
+end
+    
+if isfield(model,'iter')==0
+    model.iter=0;
+    model.w=zeros(model.n_cla,size(X,1));
+    model.w2=zeros(model.n_cla,size(X,1));
+    model.errTot=0;
+    model.numSV=zeros(numel(Y),1);
+    model.aer=zeros(numel(Y),1);
+    model.pred=zeros(model.n_cla,numel(Y));
+end
+
+for i=1:n
+    model.iter=model.iter+1;
+    
+    val_f=model.w*X(:,i);
+
+    Yi=Y(i);
+    
+    tmp=val_f; tmp(Yi)=-inf;
+    [mx_val,idx_mx_val]=max(tmp);
+
+    model.errTot=model.errTot+(val_f(Yi)<=mx_val);
[…]

### 2019-01-14 src/octave/run_experiments.m

@@ -1,0 +1,55 @@
+clear all;
+close all;
+
+%load syn_data_matlab
+load results_banditron_clean
+
+%[t, p] = libsvmread('/home/bremen/Projects/datasets/covtype.scale');
+%t=t';
+%p=p';
+
+model_bak=model_init();
+model_bak.n_cla=numel(unique(t));
+
+%[p,t_noise]=shuffledata(p,t_noise);
+%p(end+1,:)=1;
+
+%model_perc=perceptron_multi_train(p,t,model_bak);
+
+%noise=2.^(-16:-1);
+err=zeros(numel(noise),10);
+err_newtron=zeros(numel(noise),10);
+for j=1:10
+    for i=1:numel(noise)
+      %model_bak.gamma=noise(i);
+      %model_banditron=banditron_multi_train(p,t,model_bak);
+      %err(i,j)=model_banditron.aer(end);
+      
+      model_bak.gamma=noise(i);
+      model_newtron=newtron_diag_train(p,t,model_bak);
+      err_newtron(i,j)=model_newtron.aer(end);      
+    end
+end
+
+err_soba_diag=zeros(numel(noise),10);
+for j=1:10
+    for i=1:numel(noise)
+      model_bak.gamma=noise(i);
+      model_soba_diag=soba_diag_multi_train(p,t,model_bak);
+      err_soba_diag(i,j)=model_soba_diag.aer(end);      
+    end
+end
+
+
+%for i=1:numel(noise)
+%  model_bak.gamma=noise(i);
+%model_soba=soba_multi_train(p,t,model_bak);
+%  err_soba(i)=model_soba.aer(end);
+%end
+
+%save results_baselines_noise
+
+%plot(noise, err);
+%hold on;
+%plot(noise, model_perc.aer(end),'k');
+%plot(noise, model_soba.aer(end),'r');

### 2019-01-14 src/octave/shuffledata.m

@@ -1,0 +1,31 @@
+function [x,y] = shuffledata(x,y)
+% SHUFFLEDATA Shuffle instances and labels
+%
+%   [X,Y] = SHUFFLEDATA(X,Y) shuffles the instances X and the labels Y.
+%
+%    This file is part of the DOGMA library for MATLAB.
+%    Copyright (C) 2009-2012, Francesco Orabona
+%    If you use this software in a paper you have to cite
+%     - Francesco Orabona. (2009)
+%       DOGMA: a MATLAB toolbox for Online Learning
+%       Software available at http://dogma.sourceforge.net
+%
+%    This program is free software: you can redistribute it and/or modify
+%    it under the terms of the GNU General Public License as published by
+%    the Free Software Foundation, either version 3 of the License, or
+%    (at your option) any later version.
+%
+%    This program is distributed in the hope that it will be useful,
+%    but WITHOUT ANY WARRANTY; without even the implied warranty of
+%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%    GNU General Public License for more details.
+%
+%    You should have received a copy of the GNU General Public License
+%    along with this program.  If not, see <http://www.gnu.org/licenses/>.
+%
+%    Contact the author: francesco [at] orabona.com
+
+nSample = size(x,2);
+rp = randperm(nSample);
+x = x(:,rp);
+y = y(:,rp);

### 2019-01-14 src/octave/stdshade.m

@@ -1,0 +1,50 @@
+function stdshade(amatrix,alpha,acolor,F,smth)
+% usage: stdshading(amatrix,alpha,acolor,F,smth)
+% plot mean and sem/std coming from a matrix of data, at which each row is an
+% observation. sem/std is shown as shading.
+% - acolor defines the used color (default is red) 
+% - F assignes the used x axis (default is steps of 1).
+% - alpha defines transparency of the shading (default is no shading and black mean line)
+% - smth defines the smoothing factor (default is no smooth)
+% smusall 2010/4/23
+
+if exist('acolor','var')==0 || isempty(acolor)
+    acolor='r'; 
+end
+
+if exist('F','var')==0 || isempty(F)
+    F=1:size(amatrix,2);
+end
+
+if exist('smth','var')
+    if isempty(smth)
+        smth=1;
+    end
+else
+    smth=1;
+end  
+
+if ne(size(F,1),1)
+    F=F';
+end
+
+amean=smooth(nanmean(amatrix),smth)';
+astd=nanstd(amatrix); % to get std shading
+% astd=nanstd(amatrix)/sqrt(size(amatrix,1)); % to get sem shading
+
+semilogx(F,amean,acolor,'linewidth',1.5); %% change color or linewidth to adjust mean line
+hold on;
+
+if exist('alpha','var')==0 || isempty(alpha) 
+    fill([F fliplr(F)],[amean+astd fliplr(amean-astd)],acolor,'linestyle','none');
+    acolor='k';
+else
+    fill([F fliplr(F)],[amean+astd fliplr(amean-astd)],acolor, 'FaceAlpha', alpha,'linestyle','none');
+end
+semilogx(F,amean,acolor,'linewidth',1.5); %% change color or linewidth to adjust mean line
+
+
+end
+
+
+

### 2019-01-14 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Fix introduction

@@
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-can be extended to nonlinear classification using kernels~\cite{Scholkopf-Smola-Bach-2002}.
+can be extended to nonlinear classification using kernels~\cite{Scholkopf-Smola-2002, Shawe-Taylor-Cristianini-2004}.
 For each class, as opposed

### 2019-01-14 ICML-submission/introduction.tex
Fix introduction

@@
 Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
-viewed as a repeated game between the learner and the adversary. At each timestep $t$,
-the adversary chooses a labeled example $(x_t, y_t)$ where the feature vector $x_t \in
-\R^d$ is revealed to the learner and the correct label $y_t$ is kept secret by
-the adversary. Upon receiving the feature vector $x_t$, the learner is asked to
-make a prediction $\widehat{y}_t$. Immediately after making its prediction, the
-learner receives a feedback. In contrast with the standard full information
-setting (where the feedback given is the correct label $y_t$), here the feedback
-is only a binary indicator of whether the prediction was correct or not. The
-protocol of the problem is formally stated below.
+viewed as a repeated game between the learner and the adversary. At each
+timestep $t$, the adversary chooses a labeled example $(x_t, y_t)$ where the
+feature vector $x_t \in \R^d$ is revealed to the learner and the correct label
+$y_t$ is kept secret by the adversary. Upon receiving the feature vector $x_t$,
+the learner is asked to make a prediction $\widehat{y}_t$. Immediately after
+making its prediction, the learner receives a feedback. In contrast with the
+standard full information setting (where the feedback given is the correct label
+$y_t$), here the feedback is only a binary indicator of whether the prediction
+was correct or not. The protocol of the problem is formally stated below.
 
@@
 \REQUIRE{Number of classes $K$, number of rounds $T$.}
-%\REQUIRE{.}
 \FOR{$t=1,2,\dots,T$}
 \STATE Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.
-%\STATE{Observe feature vector $x_t$}
-%\STATE{Adversary \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
-%\chicheng{Or we simply say: Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.}
 \STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
@@
 
-The performance is of the learner is measured by its cumulative number of
+The performance of the learner is measured by its cumulative number of
 mistakes $\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$.
@@
 The standard notion of multiclass linear separability corresponds to the weak
-linear separability. For binary classification, these two notions are
-identical. However, they differ for multiclass classification with $K \geq 3$.
-For multiclass classification with $K$ classes, the standard notion of linear
-separability means that the examples from each class lie in an intersection of
-$K-1$ halfspaces and the examples outside of the class lie in the complement of
-the intersection of the halfspaces. Strong linear separability means that
-examples from each class are separated from the remaining examples by a
-\emph{single} hyperplane.
+linear separability. For binary classification, the weak and strong separability
+are identical. However, they differ for multiclass classification with $K \ge 3$
+classes. For multiclass classification with $K$ classes, the standard notion of
+linear separability means that the examples from each class lie in an
+intersection of $K-1$ halfspaces and the examples outside of the class lie in
+the complement of the intersection of the halfspaces. Strong linear separability
+means that examples from each class are separated from the remaining examples by
+a \emph{single} hyperplane.
 
@@
 efficient algorithm with an expected number of mistakes at most $(K-1) \lfloor
-(R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies of the
+4(R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies of the
 \textsc{Binary Perceptron} algorithm, one copy for each class. Intuitively
@@
 
-For the standard notion of linear separability, we propose several algorithms
-with various time-complexity-versus-mistake-bound trade-offs.
-\chicheng{I wonder if we should just present the results using the rational kernel,
- as results using other kernels are nonadaptive,
- and achieve qualitatively similar mistake bounds.}
-First class of
-algorithms map the examples into a high-dimensional inner product space. In this
-space the examples become \emph{strongly} linearly separable. This allows us to
-run the algorithm for the strongly linearly separable case. All of these
-algorithms can be kernelized. (Some of them have to be kernelized since the
-underlying inner product space is infinite dimensional.) Kernelization does not
-change the input-output behavior of the algorithm, it only affects its time
-and memory complexity.
+For the case when examples are weakly linearly separable, we construct a feature
+mapping $\phi$ such that makes them \emph{strongly} linearly separable. We then
+use the kernelized version of the algorithm for the strongly separable case; for
+more details on kernel methods see e.g.~\citet{Scholkopf-Smola-2002} and
+\citet{Shawe-Taylor-Cristianini-2004}. The kernel $k(x,y)$ corresponding to the
+feature mapping $\phi$ has a simple explicit formula and can be computed in
+$O(d)$ time.
 
-These algorithms differ by choice of the mapping or, equivalently, choice of the
-kernel. The crux of the problem is the analysis of the approximation properties
-of these mappings/kernels and the way margin in the original space $\R^d$ under
-standard linear separability notion gets transformed into a margin in the
-high-dimensional space under the strong separability notion. This problem is
+The number of mistakes of the kernelized algorithm depends on the margin in the
+corresponding feature space. We analyze how the margin parameter of weak
+separability in the original space $\R^d$ gets transformed into a margin
+parameter of strong separability in the new feature space. This problem is
 related to the problem of learning intersection of halfspaces and has been
-studied previously by \cite{Klivans-Servedio-2008}. As an important technical
-achievement, we improve on the results of \cite{Klivans-Servedio-2008} by
-removing completely the dependency on the original dimension $d$.
+studied previously by \citet{Klivans-Servedio-2008}. In fact, our analysis can
+be viewed as a follow up on their work. We improve on the results of
+\citet{Klivans-Servedio-2008} by removing the dependency on the original
+dimension $d$.
 
-Finally, we propose a very different algorithm that is based on the obvious idea
-that two points that are close enough must have the same label. Here, close
-enough means that they cannot be separated from each other by a linear separator
-with a margin.
-
-All the algorithms run in time that is polynomial in the dimension of the
-feature vectors, the number of classes and the number of rounds. At the same
-time, all the algorithms make number of mistakes that does \emph{not} depend
-on the number of rounds. Instead, their number of mistakes depends only on the
-margin, number of classes, dimension of the feature vectors, and the radius of
-the ball in which the data lie.
-
-Finally, we study two questions related to the computational and
-information-theoretic hardness of the problem. Any algorithm for the bandit
-setting collects information in the form of so called \emph{strongly labeled}
-and \emph{weakly labeled} examples. Strongly labeled examples are those for
-which we know the class label. Weakly labeled example is an example for which we
-know that class label can be anything except for a particular one class. First,
-we show the offline problem of finding a linear multiclass separator consistent
-with a set of strongly and weakly labeled examples is NP-hard. This result is a
-consequence of the fact that finding an intersection of two halfspaces
-consistent with a set of binary-labeled examples is
-NP-hard~\citep{Blum-Rivest-1993}. Second, we show that any algorithm that uses
-only strongly-labeled examples and ignores weakly labeled examples makes at
-least $\Omega(???)$ mistakes.
+The resulting kernelized algorithm runs in time that is polynomial in the
+original dimension of the feature vectors $d$, the number of classes $K$, and
+the number of rounds $T$. We prove that if the examples lie in unit ball of
+$\R^d$ and are weakly separable with margin $\gamma$, the algorithm makes at
+most $O(???)$ mistakes.

### 2019-01-14 ICML-submission/notions-of-linear-separability.tex
Fix introduction

@@
 
-The notion of strong linear separability has appeared in the literature
-(see e.g.~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}).
+The notion of strong linear separability has appeared in the literature;
+see e.g.~\citet{Chen-Chen-Zhang-Chen-Zhang-2009}.
 \footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009} claimed that their
 Conservative OVA algorithm with PA-I update has a finite mistake bound under the strong
-linear separability assumption, their proof of Theorem 2 is problematic: their
+linear separability assumption, their proof of Theorem 2 is incorrect. Their
 Lemma 4 cannot be directly applied to the bandit setting,

### 2019-01-14 ICML-submission/title-and-abstract.tex
Fix introduction

@@
 $\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}. Our algorithm is
-based on a infinite-dimensional feature mapping that transforms weak linear
-separable examples to strong linear separable examples, which in turn is
+based on a infinite-dimensional feature mapping that transforms weakly linear
+separable examples to strongly linear separable examples, which in turn is
 inspired by the work of \citet{Klivans-Servedio-2008} on learning intersection of

### 2019-01-14 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Fixes

@@
 The idea behind the algorithm is to use $K$ copies of the \textsc{Binary
-Perceptron} algorithm, where each copy corresponds to a class.
-In each round, copy $i$
-makes a binary prediction, indicating whether the example belongs to class $i$ or not.
-If at least one copy makes a positive prediction, the algorithm
-chooses its prediction as one of the classes corresponding to a positive prediction.
-If all copies make negative
-predictions, the algorithms makes a prediction uniformly at random.
-
-%accordingly. If multiple copies make positive predictions, the
-%algorithm chooses one of them arbitrarily
+Perceptron} algorithm, where each copy corresponds to a class. In each round,
+copy $i$ makes a binary prediction, indicating whether the example belongs to
+class $i$ or not. If at least one copy makes a positive prediction, the
+algorithm chooses its prediction as one of the classes corresponding to a
+positive prediction. If all copies make negative predictions, the algorithms
+makes a prediction uniformly at random.
 
@@
 number of mistakes in the rounds when $S_t = \emptyset$.
-It can be easily seen that $M = A + B$. %We now upper bound $A$ and $B$ separately.
+It can be easily seen that $M = A + B$.
 
-Let $C$ be the number of times line~\ref{line:pos-update} gets executed. Let $U$ be the number of
-times line~\ref{line:pos-update} and line~\ref{line:neg-update} get executed. In other words, $U$ is the number of
-times the $K$-tuple of vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets
-updated. It can be easily seen that $U = A + C$.
+Let $C$ be the number of times line~\ref{line:pos-update} gets executed. Let $U$
+be the number of times line~\ref{line:pos-update} or line~\ref{line:neg-update}
+get executed. In other words, $U$ is the number of times the $K$-tuple of
+vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets updated. It can be
+easily seen that $U = A + C$.
 
@@
 To finish the proof, we need to upper bound the number of updates $U$. We claim
-that $U \le \lfloor (R/\gamma)^2 \rfloor$. The proof of this upper bound is
+that $U \le \lfloor 4(R/\gamma)^2 \rfloor$. The proof of this upper bound is
 similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
@@
 Similarly, if there is an update in round $t$, we have
+\begingroup
+\allowdisplaybreaks
 \begin{align*}
@@
 \end{align*}
+\endgroup
 where the last inequality follows from a case analysis on $z_t$ and
 Definition~\ref{definition:strong-linear-separability}: if $z_t = 0$, then
-$\widehat y_t = y_t$, by Equation~\eqref{equation:strong-linear-separability-2}, we have
-that $\ip{w_{\widehat y_t}^*}{x_t} \geq \frac \gamma 2$;
-if $z_t = 1$, then $\widehat y_t \neq y_t$, by Equation~\eqref{equation:strong-linear-separability-3},
-we have that $\ip{w_{\widehat y_t}^*}{x_t} \leq -\frac \gamma 2$.
-
-%\eqref{equation:strong-linear-separability-2}
-%and \eqref{equation:strong-linear-separability-3} and analysis of the cases $z_t = 0$ and $z_t = 1$.
+$\widehat y_t = y_t$, by Equation~\eqref{equation:strong-linear-separability-2},
+we have that $\ip{w_{\widehat y_t}^*}{x_t} \geq \frac \gamma 2$; if $z_t = 1$,
+then $\widehat y_t \neq y_t$, by
+Equation~\eqref{equation:strong-linear-separability-3}, we have that
+$\ip{w_{\widehat y_t}^*}{x_t} \le -\frac \gamma 2$.
 
@@
 $$
-(\frac{\gamma U}{2})^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
+\left(\frac{\gamma U}{2} \right)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
 $$
@@
 Applying Equation~\eqref{eqn:mistake-update}, we get
-\[ \Exp[M] \leq (K-1) \Exp[U] \leq (K-1) \lfloor 4(R/\gamma)^2 \rfloor. \qedhere \]
+$$
+\Exp[M] \leq (K-1) \Exp[U] \leq (K-1) \lfloor 4(R/\gamma)^2 \rfloor \; . \qedhere
+$$
 \end{proof}
@@
 for every $j$ in $\{1,2,\dots,M\}$.
-By Claim 2 of~\cite{Daniely-Helbertal-2013}, as $\ell_j$
-is chosen uniformly from $\cbr{1,\ldots,K}$ and independent of $\calB_{j-1}$,
-\[ \Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t \Bigg| \calB_{j-1} } \geq \frac{K-1}2. \]
+By Claim 2 of~\citet{Daniely-Helbertal-2013}, as $\ell_j$
+is chosen uniformly from $\cbr{1,\dots,K}$ and independent of $\calB_{j-1}$,
+$$
+\Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t ~\Bigg|~ \calB_{j-1} } \geq \frac{K-1}2 \; .
+$$
 This implies that
-\[ \Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t } \geq \frac{K-1}2. \]
+$$
+\Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t } \ge \frac{K-1}2 \; .
+$$
 Summing over all $j$ in $\{1,2,\dots,M\}$,
-\[ \Exp \sbr{ \sum_{t=1}^{(K-1)M} z_t} \geq \frac{K-1}2 \cdot M = \frac{K-1}2 \left\lfloor \frac 1 4 (R/\gamma)^2 \right\rfloor. \]
+$$
+\Exp \sbr{ \sum_{t=1}^{(K-1)M} z_t} \geq \frac{K-1}2 \cdot M = \frac{K-1}2 \left\lfloor \frac 1 4 (R/\gamma)^2 \right\rfloor \; .
+$$
 
@@
 
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-can be extended to nonlinear classification using kernels~\cite{Scholkopf-Smola-2002, Shawe-Taylor-Cristianini-2004}.
-For each class, as opposed
-to explicitly maintaining the predictor's weights for each class, we maintain
-the set of examples whose scaled feature transformations are added to the weights in Perceptron updates.
-We give a formal description of the kernelized algorithm in Algorithm~\ref{algorithm:kernelized}.
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} can
+be extended to nonlinear classification using
+kernels~\cite{Scholkopf-Smola-2002, Shawe-Taylor-Cristianini-2004}. For each
+class, as opposed to explicitly maintaining the predictor's weights for each
+class, we maintain the set of examples whose scaled feature transformations are
+added to the weights in Perceptron updates. We give a formal description of the
+kernelized algorithm in Algorithm~\ref{algorithm:kernelized}.
 
@@
 \STATE{Observe feature vector $x_t$.}
-\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \sum_{(x,y) \in J_i^{(t)}} y k(x, x_t) \ge 0 \right\}$}
+\STATE{Compute \\ $S_t = \left\{ i ~:~ 1 \le i \le K, \ \sum_{(x,y) \in J_i^{(t)}} y k(x, x_t) \ge 0 \right\}$}
 \IF{$S_t = \emptyset$}

### 2019-01-14 ICML-submission/notions-of-linear-separability.tex
Fixes

@@
 
-The notion of weak linear separability with a margin is standard. It is used in the
-full-information setting to upper bound the number of mistakes of the
-\textsc{Multiclass Perceptron} algorithm. It is a
-folklore result that if a set of labeled examples is separable with a margin
-$\gamma$ and the norm of the examples is bounded by $R$, then \textsc{Multiclass
-Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
-mistakes. Another folklore result is that \textsc{Multiclass Perceptron} is
-essentially optimal in the sense that any deterministic algorithm must make
-$\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
-completeness, we state the \textsc{Multiclass Perceptron} algorithm
-and give proofs of both of these results in
-Appendix~\ref{section:multiclass-perceptron-proofs}.
+The notion of weak linear separability with a margin is standard. It is used in
+the full-information setting to upper bound the number of mistakes of the
+\textsc{Multiclass Perceptron} algorithm. It is a folklore result that if a set
+of labeled examples is separable with a margin $\gamma$ and the norm of the
+examples is bounded by $R$, then \textsc{Multiclass Perceptron} algorithm makes
+at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$ mistakes. Another folklore
+result is that \textsc{Multiclass Perceptron} is essentially optimal in the
+sense that any deterministic algorithm must make $\left\lfloor (R/\gamma)^2
+\right \rfloor$ mistakes in the worst case. For completeness, we state the
+\textsc{Multiclass Perceptron} algorithm and give proofs of both of these
+results in Appendix~\ref{section:multiclass-perceptron-proofs}.
 
-The notion of strong linear separability has appeared in the literature;
-see e.g.~\citet{Chen-Chen-Zhang-Chen-Zhang-2009}.
+The notion of strong linear separability has appeared in the literature; see
+e.g.~\citet{Chen-Chen-Zhang-Chen-Zhang-2009}.
 \footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009} claimed that their
-Conservative OVA algorithm with PA-I update has a finite mistake bound under the strong
-linear separability assumption, their proof of Theorem 2 is incorrect. Their
-Lemma 4 cannot be directly applied to the bandit setting,
-as the algorithm only makes updates on a subset of the $w_i$'s.}
-Intuitively, strong linear
-separability means that, for each class $i$, the set of examples belonging to class $i$ and
-the set of example belonging to the remaining $K-1$ classes are separated by
-a linear classifier $w_i$ by a margin $\frac \gamma 2$.
-%Formally, $w_i$ separates the set of examples $\cbr{(x_t, y_t): t \in
-%\cbr{1,\ldots,T}, y_t = i}$ and $\cbr{(x_t, y_t): t \in \cbr{1,\ldots,T}, y_t
-%\neq i}$.
-
-%\chicheng{I think the notion has appeared in, however,
-%they proposed an algorithm that doesn't achieve a finite mistake bound in the bandit
-%setting under this assumption (although they claimed that they have done so, the proof was
-%wrong..)}
+Conservative OVA algorithm with PA-I update has a finite mistake bound under the
+strong linear separability assumption, their proof of Theorem 2 is incorrect.
+Their Lemma 4 cannot be directly applied to the bandit setting, as the algorithm
+only makes updates on a subset of the $w_i$'s.} Intuitively, strong linear
+separability means that, for each class $i$, the set of examples belonging to
+class $i$ and the set of example belonging to the remaining $K-1$ classes are
+separated by a linear classifier $w_i$ by a margin $\frac \gamma 2$.
 
@@
 
-%with margin $\gamma' = 2\gamma$.
-
-In the special case of $K=2$, if a set of labeled examples are weakly linearly separable with a margin
-$\gamma$, then they are strongly linearly separable with the same margin.
-Indeed, if $w_1, w_2$ satisfy \eqref{equation:weak-linear-separability-1} and
-\eqref{equation:weak-linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$, $w_2' =
-\frac{w_2 - w_1}{2}$ satisfy
+In the special case of $K=2$, if a set of labeled examples are weakly linearly
+separable with a margin $\gamma$, then they are strongly linearly separable with
+the same margin. Indeed, if $w_1, w_2$ satisfy
+\eqref{equation:weak-linear-separability-1} and
+\eqref{equation:weak-linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$,
+$w_2' = \frac{w_2 - w_1}{2}$ satisfy
 \eqref{equation:strong-linear-separability-1},
 \eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3}.
-The first condition follows from $\norm{w_i'}^2 \le (\frac{1}{2}
-\norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le \frac{1}{2}\norm{w_1}^2 +
-\frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$. The last two condition
-follows from the fact that $w_1' - w_2' = w_1 - w_2$.
+\eqref{equation:strong-linear-separability-3}. The first condition follows from
+$\norm{w_i'}^2 \le (\frac{1}{2} \norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le
+\frac{1}{2}\norm{w_1}^2 + \frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
+The last two condition follows from the fact that $w_1' - w_2' = w_1 - w_2$.
+
 However, for any $K \ge 3$ and any inner product space of dimension at least
-$2$, there exists a set of labeled examples that is weakly linearly separable with a
-positive margin $\gamma$ but it is not strongly linearly separable with any
-positive margin $\gamma$. An example of such set of labeled examples is shown in
-Figure~\ref{figure:weakly-linearly-separable-examples-with-margin}.
-
-%\chicheng{Shall we change the $\gamma$ in Equations
-%\eqref{equation:strong-linear-separability-2},
-%\eqref{equation:strong-linear-separability-3} to $\gamma/2$, to simplify the
-%presentation?}
+$2$, there exists a set of labeled examples that is weakly linearly separable
+with a positive margin $\gamma$ but it is not strongly linearly separable with
+any positive margin $\gamma$. An example of such set of labeled examples is
+shown in~\autoref{figure:weakly-linearly-separable-examples-with-margin}.
 
@@
 
-While the examples are weakly linearly separable with a positive margin $\gamma$, they
-are \emph{not} strongly linearly separable with any positive margin $\gamma$. For instance,
-there do not exist linear separators that separates the
-examples belonging to the gray class from the examples belonging to the remaining two classes.
+While the examples are weakly linearly separable with a positive margin
+$\gamma$, they are \emph{not} strongly linearly separable with any positive
+margin $\gamma$. For instance, there do not exist linear separators that
+separates the examples belonging to the gray class from the examples belonging
+to the remaining two classes.
 }

### 2019-01-14 ICML-submission/related-work.tex
Fixes

@@
 
-The problem of online bandit multiclass learning was initially formulated
-in the pioneering work of~\cite{Auer-Long-1999}, under the name of
-``weak reinforcement model''. They show that if the set of examples shown is
-separable by a classifier in a prespecified hypothesis class $\calH$, then the optimal
- mistake bound in the bandit setting can be upper bounded by the optimal mistake
- bound in the full-information setting, times a factor of $(2.01 + o(1))K \ln K$.
- (See~\cite{Long-2017} for improvements of the factor to $(1 + o(1)) K \ln K$.)
- ~\cite{Daniely-Helbertal-2013} extend the results to the setting where the
+The problem of online bandit multiclass learning was initially formulated in the
+pioneering work of~\citet{Auer-Long-1999} under the name of ``weak reinforcement
+model''. They show that if the set of examples shown is separable by a
+classifier in a prespecified hypothesis class $\calH$, then the optimal mistake
+bound in the bandit setting can be upper bounded by the optimal mistake bound in
+the full-information setting, times a factor of $(2.01 + o(1))K \ln K$.
+\citet{Long-2017} later improved the factor to $(1 + o(1)) K \ln K$.
+\citet{Daniely-Helbertal-2013} extend the results to the setting where the
 performance of the algorithm is measured by its regret, i.e. the difference
 between the number of mistake made by the algorithm and the number of mistake
- made by the best classifier in $\calH$ in hindsight. However, all algorithms developed in
- this context are computationally inefficient.
+made by the best classifier in $\calH$ in hindsight. However, all algorithms
+developed in this context are computationally inefficient.
 
-The linear classification version of this problem
-is initially studied by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed
-two computationally inefficient algorithms that work in the standard
-linearly separable setting, one with a mistake bound of $O(K^2 d
-\ln(\frac{d}{\gamma^2}))$, the other with a mistake bound of
-$\widetilde{O}(\frac{K^2}{\gamma^2} \ln T)$. In addition, the authors propose
-the \textsc{Banditron} algorithm, a computationally efficient algorithm that has
-a $O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
-and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weak linearly separable
-setting. The polynomial dependence of \textsc{Banditron}'s mistake bound on the
-time horizon is undesirable for problems with a long time horizon. One key open
-question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
-design computationally efficient algorithms that achieve mistake bounds that
-match or improve over those of inefficient algorithms. In this paper, we take a
-step towards answering this question, showing that efficient algorithms with
-mistake bounds quasipolynomial in the margin parameter can be obtained.
+The linear classification version of this problem is initially studied
+by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed two computationally
+inefficient algorithms that work in the standard linearly separable setting, one
+with a mistake bound of $O(K^2 d \ln(\frac{d}{\gamma^2}))$, the other with a
+mistake bound of $\widetilde{O}(\frac{K^2}{\gamma^2} \ln T)$. In addition, the
+authors propose the \textsc{Banditron} algorithm, a computationally efficient
+algorithm that has a $O(T^{2/3})$ regret against the multiclass hinge loss in
+the general setting, and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weak
+linearly separable setting. The polynomial dependence of \textsc{Banditron}'s
+mistake bound on the time horizon is undesirable for problems with a long time
+horizon. One key open question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}
+is whether one can design computationally efficient algorithms that achieve
+mistake bounds that match or improve over those of inefficient algorithms. In
+this paper, we take a step towards answering this question, showing that
+efficient algorithms with mistake bounds quasipolynomial in the margin parameter
+can be obtained.
 

### 2019-01-14 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
First pass over section 5

@@
 there exists a particular (i.e. deterministic) sequence of examples for which
-the algorithm makes at least $\frac{K-1}2 \left\lfloor \frac 1 4 (R/\gamma)^2 \right\rfloor$ mistakes in expectation
-over its internal randomization.
+the algorithm makes at least $\frac{K-1}2 \left\lfloor \frac 1 4 (R/\gamma)^2
+\right\rfloor$ mistakes in expectation over its internal randomization.
 \end{proof}

### 2019-01-14 ICML-submission/from-linear-separability-to-strong-linear-separability.tex
First pass over section 5

@@
 
-In this section, we show how to construct a mapping $\phi$ from the unit ball of
-$\R^d$ into a high dimensional inner product space that has the property that if
-a set of labeled examples in the unit ball is linearly separable with a margin
-$\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
-linearly separable with a margin $\gamma'$ and their norms are bounded by $R'$.
-The parameters $\gamma'$ and $R'$ are functions of the old margin $\gamma$ and
-the number of classes $K$, and are specified in the theorems below.
+In this section, we construct and analyze a mapping $\phi$ from the unit ball of
+$\R^d$ into a infinite-dimensional inner product space that has the property
+that if a set of labeled examples in the unit ball is \emph{weakly} linearly
+separable with a margin $\gamma$, applying the mapping $\phi$ makes the examples
+\emph{strongly} linearly separable with a margin $\gamma'$ and their norms are
+bounded by $2$. The parameter $\gamma'$ is a function of the old margin $\gamma$
+and the number of classes $K$, and is specified in the
+\autoref{theorem:margin-transformation} below.
+
+The domain of $\phi$ is the unit ball of $\R^d$. The co-domain of $\phi$ is the classical real separable Hilbert space
+$\ell_2 = \{ x \in \R^\infty ~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped
+with the standard inner product $\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. We index the coordinates of
+$\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
+integers. The mapping is defined by
+\begin{align*}
+& \left(\phi(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \\
+& \qquad \cdot \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
+\end{align*}
+where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
+is the multinomial coefficient. The corresponding kernel is
+$$
+k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}} \; .
+$$
+In passing we note that the formula for $k$ implies the mapping $\phi$ is
+well defined. Indeed, since $k(x,x) < +\infty$ for any $x$ in the unit
+ball of $\R^d$, it means that $\phi(x)$ indeed lies in $\ell_2$.
 
 Equipped with the mapping $\phi$, we can utilize
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
+Algorithm~\ref{algorithm:kernelized} with kernel function $k(x,x') =
+\ip{\phi(x)}{\phi(x')}$ and
 \autoref{theorem:strongly-separable-example-mistake-upper-bound} from the
-previous section and we obtain an algorithm for linearly separable examples and
-an upper bound on its number of mistakes. As a computational speed up, instead
-of working with the mapped examples $\phi(x_1), \phi(x_2), \dots$ explicitly, we
-can use the kernelized version of
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-that uses a kernel function $k(x,x') = \ip{\phi(x)}{\phi(x')}$.
+previous section and we obtain an algorithm for weakly linearly separable
+examples and an upper bound on its number of mistakes.
 
-We construct several different mappings $\phi$. The mappings differ in the
-parameters $R'$, $\gamma'$, time complexity of evaluating $\phi(x)$, and time
-complexity of evaluating $k(x,x')$. Some of the mappings depend the original
-margin $\gamma$. In practice, the margin parameter $\gamma$ is not known, which
-makes these mappings impractical. However, one of the mappings we construct
-does \emph{not} depend on $\gamma$.
-
-The idea behind all the mappings is polynomial approximation. According to the
-well known Stone-Weierstrass theorem (see
-e.g.~\citep[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
+The idea behind construction and analysis of the mapping $\phi$ is polynomial
+approximation. According to the well known Stone-Weierstrass theorem (see
+e.g.~\citet[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
 multivariate polynomials uniformly approximate any continuous function.
@@
 
-We construct the three different mappings $\phi_n, \psi_n, \rho$. The first two
-are parameterized by a non-negative integer $n$. The domain of $\phi_n$ and
-$\psi_n$ is $\R^d$. The domain of $\rho$ is the unit ball of $\R^d$. The
-co-domain of $\phi_n$ and $\psi_n$ is $\R^q$ where $q = \sum_{i=0}^n
-\binom{i+d-1}{d-1}$ equipped with the standard inner product $\ip{x}{x'}_{\R^q} =
-\sum_{i=1}^p x_i x'_i$. The co-domain of $\rho$ is the classical real separable Hilbert space
-$\ell_2 = \{ x \in \R^\infty ~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped
-with the standard inner product $\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. We
-index the coordinates of the co-domain $\R^q$ by $d$-tuples $(\alpha_1,
-\alpha_2, \dots, \alpha_d)$ of non-negative integers such that $\alpha_1 +
-\alpha_2 + \dots + \alpha_d \le n$. Similarly, we index the coordinates of
-$\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
-integers. The mappings are defined by
-\begin{align*}
-& \left(\phi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
-= x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
-\\
-& \left(\psi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \\
-& \qquad \cdot \sqrt{\binom{n}{\alpha_1 + \alpha_2 + \dots + \alpha_d} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
-\\
-& \left(\rho(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \\
-& \qquad \cdot \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
-\end{align*}
-where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
-is the multinomial coefficient and $\binom{n}{k} = \frac{n!}{(n-k)!k!}$ is the binomial coefficient.
-
-Mappings $\psi_n$ and $\rho$ have simple-to-compute kernels
-\begin{align*}
-K_{\psi_n}(x,x') & = \ip{\psi_n(x)}{\psi_n(x')}_{\R^q} = \left( 1 + \ip{x}{x'} \right)^n \; , \\
-K_{\rho}(x,x') & = \ip{\rho(x)}{\rho(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}} \; .
-\end{align*}
-In passing we note that the formula for $K_\rho$ implies the mapping $\rho$ is
-well defined. Indeed, since $K_{\rho}(x,x) < +\infty$ for any $x$ in the unit
-ball of $\R^d$, it means that $\rho(x)$ indeed lies in $\ell_2$.
-
-Any mutlivariate polynomial in the orginal space $\R^d$ can be expressed as a
-linear function in the new feature spaces given by mappings $\phi_n, \psi_n,
-\rho$. The following lemma bounds the norm of the linear function in the terms
-of the norm of the polynomial. Recall that a linear function in a Hilbert space
-$(H, \ip{\cdot}{\cdot}_H)$ has the form $\ip{c}{x}_H$ for some vector $c \in H$
-and its norm is $\norm{c}_H = \sqrt{\ip{c}{c}}$.
+The following lemma expresses any multivariate polynomial in $\R^d$
+as a linear function in $\ell_2$ and gives an upper bound its the norm.
 
@@
 \label{lemma:norm-bound}
-Let $d \ge 1$ and $n \ge 0$ be integers and let $q = \sum_{i=0}^n \binom{i+d-1}{d-1}$.
 Let $p:\R^d \to \R$ be a multivariate polynomial.
-\begin{enumerate}
-\item If $n \ge \deg(p)$ then there exists $c \in \R^q$ such that $p(x) = \ip{c}{\phi_n(x)}_{\R^q}$
-and $\norm{c}_{\R^q} = \norm{p}$.
-\item If $n \ge \deg(p)$ then there exists $c' \in \R^q$ such that $p(x) = \ip{c'}{\psi_n(x)}_{\R^q}$
-and $\norm{c'}_{\R^q} \le \norm{p}$.
-\item There exists $c'' \in \ell_2$ such that $p(x) = \ip{c''}{\psi_n(x)}_{\ell_2}$
-and $\norm{c''}_{\R^q} \le 2^{\deg(p)/2} \norm{p}$.
-\end{enumerate}
+There exists $c \in \ell_2$ such that $p(x) = \ip{c}{\psi_n(x)}_{\ell_2}$
+and $\norm{c}_{\ell_2} \le 2^{\deg(p)/2} \norm{p}$.
 \end{lemma}
@@
 Note that the polynomial $p$ can be written as
-$p(x) = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}$.
-There are $\sum_{i=0}^{\deg(p)} \binom{i+d-1}{d-1}$ coefficients $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$.
-If $n \ge \deg(p)$ these can be expressed as a vector in $c \in \R^q$. Thus, $p(x) = \ip{c}{\phi_n(x)}_{\R^q}$
-and
+$p(x) = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c'_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}$.
+We define $c \in \ell_2$ using the multi-index notation as
 $$
-\norm{c}_{\R^p} = \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} (c_{\alpha_1, \alpha_2, \dots, \alpha_d})^2} =  \norm{p} \; .
-$$
-
-We define $c' \in \R^q$ using the multi-index notation as
-$$
-c'_{\alpha_1, \alpha_2, \dots, \alpha_d}
-= \frac{c_{\alpha_1, \alpha_2, \dots, \alpha_d}}{\sqrt{\binom{n}{\alpha_1 + \alpha_2 + \dots + \alpha_d} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}} \; .
-$$
-We have $\ip{c'}{\psi_n(x)}_{\R^q} = \ip{c}{\phi_n(x)}_{\R^q} = p(x)$. Since
-$$
-|c'_{\alpha_1, \alpha_2, \dots, \alpha_d}| \le |c_{\alpha_1, \alpha_2, \dots, \alpha_d}| \; ,
-$$
-we have $\norm{c'}_{\R^q} \le \norm{c}_{\R^q} = \norm{p}$.
-
-Similarly, we define $c'' \in \ell_2$ using the multi-index notation as
-$$
-c''_{\alpha_1, \alpha_2, \dots, \alpha_d}
-= \frac{c_{\alpha_1, \alpha_2, \dots, \alpha_d} 2^{(\alpha_1 + \alpha_2 + \dots + \alpha_d)/2}}{\sqrt{\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}}
+c_{\alpha_1, \alpha_2, \dots, \alpha_d}
+= \frac{c'_{\alpha_1, \alpha_2, \dots, \alpha_d} 2^{(\alpha_1 + \alpha_2 + \dots + \alpha_d)/2}}{\sqrt{\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}}
 $$
 for all tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ such that $\alpha_1 + \alpha_2 + \dots + \alpha_d \le \deg(p)$.
-Otherwise, we define $c''_{\alpha_1, \alpha_2, \dots, \alpha_d} = 0$. We have
-$\ip{c''}{\rho(x)}_{\ell_2} = \ip{c}{\phi_n(x)}_{\R^q} = p(x)$. Since
+Otherwise, we define $c_{\alpha_1, \alpha_2, \dots, \alpha_d} = 0$. Clearly,
+$\ip{c}{\phi(x)}_{\ell_2} = p(x)$.
+
+Since
 \begin{align*}
-|c''_{\alpha_1, \alpha_2, \dots, \alpha_d}|
-& \le 2^{(\alpha_1 + \alpha_2 + \dots + \alpha_d)/2} |c''_{\alpha_1, \alpha_2, \dots, \alpha_d}| \\
-& \le 2^{\deg(p)/2} |c''_{\alpha_1, \alpha_2, \dots, \alpha_d}| \; ,
+|c_{\alpha_1, \alpha_2, \dots, \alpha_d}|
+& \le 2^{(\alpha_1 + \alpha_2 + \dots + \alpha_d)/2} |c'_{\alpha_1, \alpha_2, \dots, \alpha_d}| \\
+& \le 2^{\deg(p)/2} |c'_{\alpha_1, \alpha_2, \dots, \alpha_d}| \; ,
 \end{align*}
-we have $\norm{c''}_{\ell_2} \le 2^{\deg(p)/2} \norm{c}_{\R^q} = 2^{\deg(p)/2} \norm{p}$.
+we have
+\begin{align*}
+\norm{c}_{\ell_2}
+& \le 2^{\deg(p)/2} \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} (c'_{\alpha_1, \alpha_2, \dots, \alpha_d})^2} \\
+& = 2^{\deg(p)/2} \norm{p} \; .
+\end{align*}
 \end{proof}
@@
 
-\begin{theorem}
+\begin{theorem}[Margin transformation]
+\label{theorem:margin-transformation}
 Let $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \R^d \times \{1,2,\dots,K\}$

### 2019-01-14 ICML-submission/from-linear-separability-to-strong-linear-separability.tex
Second pass over section 5

@@
 
-The domain of $\phi$ is the unit ball of $\R^d$. The co-domain of $\phi$ is the classical real separable Hilbert space
-$\ell_2 = \{ x \in \R^\infty ~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped
-with the standard inner product $\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. We index the coordinates of
+The domain of $\phi$ is the unit ball of $\R^d$. The co-domain of $\phi$ is the
+classical real separable Hilbert space $\ell_2 = \{ x \in \R^\infty ~:~
+\sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped with the standard inner product
+$\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. We index the coordinates of
 $\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
@@
 
-Using the lemma and the polynomial approximation theorems, we can prove
-the mappings $\phi_n, \psi_n, \rho$ map any a weakly separable data
-to a strongly separable data set.
+Using the lemma and the polynomial approximation theorems, we can prove the
+mapping $\phi$ maps any a weakly separable data to a strongly separable data
+set.
 
@@
 labeled examples that are weakly linearly separable with margin $\gamma > 0$
-such that $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$. Then, the labeled
-examples $(\rho(x_1), y_1), (\rho(x_2), y_2), \dots, (\rho(x_T), y_T)$ are
-strongly linearly separable with margin
-$$
-\gamma' = \frac{1}{2\sqrt{K} \left(376 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}}
-$$
-and $\norm{\rho(x_1)}_{\ell_2}, \norm{\rho(x_2)}_{\ell_2}, \dots, \norm{\rho(x_T)}_{\ell_2} \le 2$.
-TODO
+such that $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$.
+Let
+\begin{align*}
+r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(1/\gamma) \right \rceil \\
+\gamma_1 & = \frac{1}{2\sqrt{K} \left(376 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}} \\
+\gamma_2 & = ??
+\end{align*}
+Then, the labeled examples $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots,
+(\phi(x_T), y_T)$ are strongly linearly separable with margin $\gamma' =
+\max\{\gamma_1, \gamma_2\}$ and $\norm{\phi(x_1)}_{\ell_2},
+\norm{\phi(x_2)}_{\ell_2}, \dots, \norm{\phi(x_T)}_{\ell_2} \le 2$.
 \end{theorem}
@@
 $$
-\norm{\rho(x_t)}_{\ell_2} = K_{\rho}(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
+\norm{\phi(x_t)}_{\ell_2} = K_{\phi}(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
 $$
 
-Since the examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ are weakly linearly separable
-with margin $\gamma$ there are vectors $w_1, w_2, \dots, w_K$ satisfying
-\eqref{equation:weak-linear-separability-1} anf \eqref{equation:weak-linear-separability-2}.
+Since the examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ are weakly
+linearly separable with margin $\gamma$ there are vectors $w_1, w_2, \dots, w_K$
+satisfying \eqref{equation:weak-linear-separability-1} anf
+\eqref{equation:weak-linear-separability-2}.
 
-Fix any $i \in \{1,2,\dots,K\}$. Consider the $K-1$ vectors
-$(w_i - w_j)/2$ for $j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors
-have norm at most $1$.
-\autoref{theorem:polynomial-approximation-1} implies that
-there exists a polynomial $p_i:\R^d \to \R$ such
-that
-$$
-\deg(p) = \lceil \log_2(2m) \rceil \cdot \lceil \sqrt{\frac{2}{\gamma}} \rceil \; ,
-$$
-for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$ and if $y_t \neq i$ then $p_i(x_t) \le -1/2$,
+Fix any $i \in \{1,2,\dots,K\}$. Consider the $K-1$ vectors $(w_i - w_j)/2$ for
+$j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors have norm at most
+$1$.
+Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
+imply that there exists multivariate polynomials $p_i:\R^d \to \R$ and $q_i:\R^d
+\to \R$ such that
+\begin{align*}
+\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{\frac{2}{\gamma}} \right\rceil \; , \\
+\deg(q_i) & = (2K-5/2) 2^m \\
+& \qquad \cdot \left(2^{2s} r(K-1) (4s+2)^2 \right)^{(s+1/2)r(K-1)} \; .
+\end{align*}
+Futhermore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$, $q_i(x_t) \ge ???$ and if $y_t \neq i$ then $p_i(x_t) \le -1/2$,
+$q_i(x) \le - ???$
 and
-$$
-\norm{p} \le \left(188 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2m) \rceil
-\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; .
-$$
-By \autoref{lemma:norm-bound} there exists $c_i \in \ell_2$ such that
-$\ip{c_i}{\rho(x)} = p(x)$ and
-$$
+\begin{align*}
+\norm{p_i} & \le \left(188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
+\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; , \\
+\norm{p_i} & \le ??? .
+\end{align*}
+By \autoref{lemma:norm-bound} there exists $c_i, c_i' \in \ell_2$ such that
+$\ip{c_i}{\phi(x)} = p_i(x)$ and $\ip{c_i'}{\phi(x)} = q_i(x)$ and
+\begin{align*}
 \norm{c_i}_{\ell_2}
-\le \left(376 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2m) \rceil
-\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; .
-$$
-Define vector $u_i \in \ell_2$ as
-$$
-u_i = \frac{c_i}{\sqrt{K} \left(376 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2m) \rceil
-\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}} \; .
-$$
+& \le \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
+\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \\
+\norm{c'_i}_{\ell_2} & \le ??? \\
+\end{align*}
+Define vectors $u_i, u_i' \in \ell_2$ as
+\begin{align*}
+u_i & = \frac{c_i}{\sqrt{K} \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
+\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}} \; . \\
+u_i' & = ???
+\end{align*}
 
 Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$ and
-for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma'$
+$\norm{u_1'}^2 + \norm{u_2'}^2 + \dots + \norm{u_K'}^2 \le 1$.
+Futhermore, for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma_1$ and
+$\ip{u'_{y_t}}{x_t} \ge \gamma_2$
 and for all $j \in \{1,2,\dots,K\} \setminus \{y_t\}$,
-$\ip{u_j}{x_t} \le - \gamma'$. In other words,
-$(\rho(x_1), y_1), (\rho(x_2), y_2), \dots, (\rho(x_T), y_T)$ are
-strongly linearly separable with margin $\gamma'$.
+$\ip{u_j}{x_t} \le - \gamma_1$ and $\ip{u'_j}{x_t} \le - \gamma_2$. In other words,
+$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
+strongly linearly separable with margin $\gamma_1$ and also strongly separable with
+margin $\gamma_2$. Therefore, the examples are strongly separable with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
 \end{proof}

### 2019-01-14 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Finish section 5

@@
 the mistake upper bound is stated as
-\autoref{theorem:strongly-separable-example-mistake-upper-bound}.
+\autoref{theorem:strongly-separable-examples-mistake-upper-bound}.
 
@@
 \begin{theorem}[Mistake upper bound]
-\label{theorem:strongly-separable-example-mistake-upper-bound}
+\label{theorem:strongly-separable-examples-mistake-upper-bound}
 Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
@@
 at most $O((R/\gamma)^2)$. This is proved in
-\autoref{theorem:strongly-separable-example-mistake-lower-bound} below.
+\autoref{theorem:strongly-separable-examples-mistake-lower-bound} below.
 
 \begin{theorem}[Mistake lower bound]
-\label{theorem:strongly-separable-example-mistake-lower-bound}
+\label{theorem:strongly-separable-examples-mistake-lower-bound}
 Let $\gamma$ be a positive real number, and $R$ be a non-negative real

### 2019-01-14 ICML-submission/from-weak-separability-to-strong-separability.tex
Finish section 5

--- 2019-01-14 ICML-submission/from-linear-separability-to-strong-linear-separability.tex
@@
-\section{From linear separability to strong linear separability}
-\label{section:from-linear-separability-to-strong-linear-separability}
+\section{From weak separability to strong separability}
+\label{section:from-weak-separability-to-strong-separability}
 
@@
 that if a set of labeled examples in the unit ball is \emph{weakly} linearly
-separable with a margin $\gamma$, applying the mapping $\phi$ makes the examples
-\emph{strongly} linearly separable with a margin $\gamma'$ and their norms are
-bounded by $2$. The parameter $\gamma'$ is a function of the old margin $\gamma$
-and the number of classes $K$, and is specified in the
+separable with a margin $\gamma$ after applying the mapping $\phi$ the examples
+become \emph{strongly} linearly separable with a margin $\gamma'$ and their
+norms are bounded by $2$. The parameter $\gamma'$ is a function of the old
+margin $\gamma$ and the number of classes $K$, and is specified in the
 \autoref{theorem:margin-transformation} below.
@@
 $$
-k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}} \; .
+k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}_{\R^d}} \; .
 $$
-In passing we note that the formula for $k$ implies the mapping $\phi$ is
-well defined. Indeed, since $k(x,x) < +\infty$ for any $x$ in the unit
-ball of $\R^d$, it means that $\phi(x)$ indeed lies in $\ell_2$.
+We note that the formula for $k$ implies that $k(x,x) < +\infty$ for any $x$ in
+the unit ball of $\R^d$ and therefore $\phi(x)$ lies in $\ell_2$. We also note
+that kernel function $k(x,x')$ can be evaluated in $O(d)$ time.
 
-Equipped with the mapping $\phi$, we can utilize
-Algorithm~\ref{algorithm:kernelized} with kernel function $k(x,x') =
-\ip{\phi(x)}{\phi(x')}$ and
-\autoref{theorem:strongly-separable-example-mistake-upper-bound} from the
-previous section and we obtain an algorithm for weakly linearly separable
-examples and an upper bound on its number of mistakes.
+We derive a mistake bound for Algorithm~\ref{algorithm:kernelized} with kernel
+function $k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2}$ by simply invoking
+\autoref{theorem:strongly-separable-examples-mistake-upper-bound} with the
+modified margin $\gamma'$ from \autoref{theorem:margin-transformation} below.
+The mistake bound is stated as \autoref{corollary:weakly-separable-examples-mistake-upper-bound}.
 
@@
 the polynomial to attain arbitrary value. The polynomial separates examples in
-one class from examples in the other classes. To be able to quantify $R'$,
-$\gamma'$ and time complexities of evaluating $\phi(x)$ and $k(x,x')$, we need
-to quantify certain parameters of the approximating polynomial. We construct two
-different polynomials with different parameters. The parameters are quantified
-in
+one class from examples in the other classes. To be able to quantify $\gamma'$
+we need to quantify certain parameters of the approximating polynomial. We
+construct two different polynomials with different parameters. The parameters
+are quantified in
 Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
@@
 explained in Figure~\ref{figure:pizza-slice}. Similar but weaker results were
-proved by~\cite{Klivans-Servedio-2008}. In particular, the bounds in parts
-1, 2, 3, 4 of the theorems are independent of the dimension $d$.
+proved by~\citet{Klivans-Servedio-2008}. In particular, our bounds in parts 1,
+2, 3, 4 of
+Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
+are independent of the dimension $d$.
 
@@
 Let $p:\R^d \to \R$ be a multivariate polynomial.
-There exists $c \in \ell_2$ such that $p(x) = \ip{c}{\psi_n(x)}_{\ell_2}$
+There exists $c \in \ell_2$ such that $p(x) = \ip{c}{\phi(x)}_{\ell_2}$
 and $\norm{c}_{\ell_2} \le 2^{\deg(p)/2} \norm{p}$.
@@
 & \le 2^{\deg(p)/2} \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} (c'_{\alpha_1, \alpha_2, \dots, \alpha_d})^2} \\
-& = 2^{\deg(p)/2} \norm{p} \; .
+& = 2^{\deg(p)/2} \norm{p} \; . \qquad \qedhere
 \end{align*}
@@
 \begin{align*}
-r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(1/\gamma) \right \rceil \\
-\gamma_1 & = \frac{1}{2\sqrt{K} \left(376 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}} \\
-\gamma_2 & = ??
+r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(2/\gamma) \right \rceil \\
+\gamma_1 & = \frac{1}{2\sqrt{K}}  \\
+& \ \cdot \left(376 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; , \\
+\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4(2K-5/2) 2^{K-1}} \\
+& \ \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} \; .
 \end{align*}
@@
 $$
-\norm{\phi(x_t)}_{\ell_2} = K_{\phi}(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
+\norm{\phi(x_t)}_{\ell_2} = k(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
 $$
@@
 \deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{\frac{2}{\gamma}} \right\rceil \; , \\
-\deg(q_i) & = (2K-5/2) 2^m \\
-& \qquad \cdot \left(2^{2s} r(K-1) (4s+2)^2 \right)^{(s+1/2)r(K-1)} \; .
+\deg(q_i) & = (2s+1) r(K-1) \; .
 \end{align*}
-Futhermore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$, $q_i(x_t) \ge ???$ and if $y_t \neq i$ then $p_i(x_t) \le -1/2$,
-$q_i(x) \le - ???$
-and
+Futhermore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
+$q_i(x_t) \ge \frac{1}{4} \cdot 2^{s(s+1)r(K-1)}$ and if $y_t \neq i$ then
+$p_i(x_t) \le -1/2$, $q_i(x) \le - \frac{1}{4} \cdot 2^{s(s+1)r(K-1)}$ and
 \begin{align*}
@@
 \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; , \\
-\norm{p_i} & \le ??? .
+\norm{q_i} & \le (2K-5/2) 2^{K-1} \\
+& \qquad \cdot \left(2^{2s} r(K-1) (4s+2)^2 \right)^{(s+1/2)r(K-1)} \; .
 \end{align*}
@@
 \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \\
-\norm{c'_i}_{\ell_2} & \le ??? \\
+\norm{c'_i}_{\ell_2} & \le (2K-5/2) 2^{K-1} \\
+& \qquad \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{(s+1/2)r(K-1)} \; .
 \end{align*}
@@
 \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}} \; . \\
-u_i' & = ???
+u_i' & = \frac{c_i'  \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)}}{(2K-5/2) 2^{K-1}} \; .
 \end{align*}
@@
 $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
-strongly linearly separable with margin $\gamma_1$ and also strongly separable with
-margin $\gamma_2$. Therefore, the examples are strongly separable with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
+strongly linearly separable with margin $\gamma_1$ and also strongly linearly
+separable with margin $\gamma_2$. Therefore, the examples are strongly separable
+with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
 \end{proof}
+
+As a corollary of \autoref{theorem:margin-transformation} and
+\autoref{theorem:strongly-separable-examples-mistake-upper-bound}
+we get the mistake bound for Algorithm~\ref{algorithm:kernelized}
+under the weak separability condition.
+
+\begin{corollary}[Mistake upper bound]
+\label{corollary:weakly-separable-examples-mistake-upper-bound}
+Let $K$ be a positive
+integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
+$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
+$V \times \{1,2,\dots,K\}$ such that
+\begin{enumerate}
+  \item the examples are weakly linearly separable with margin $\gamma$ (Definition~\ref{definition:weak-linear-separability}),
+  \item $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$,
+\end{enumerate}
+then the expected number of mistakes
+Algorithm~\ref{algorithm:kernelized}
+makes is at most $2^{\widetilde{O}(\min(K \log^2
+\frac{1}{\gamma}, \sqrt{\frac{1}{\gamma}} \log K))}$.
+\end{corollary}

### 2019-01-14 ICML-submission/figures/pizza-slice.tex
Small fixes

@@
   \coordinate (C2) at ($(120:3) - (0.75, 0.43301270189221932338)$);
-  \draw[<->, >=latex', ultra thick] (C1) -- (C);
-  \draw[<->, >=latex', ultra thick] (C2) -- (C);
+
+  \draw [<->, >=latex, decoration={markings,mark=at position 1 with {\arrow[scale=0.5]{>}}},postaction={decorate}] (C1) -- (C);
+  \draw [<->, >=latex, decoration={markings,mark=at position 1 with {\arrow[scale=0.5]{>}}},postaction={decorate}] (C2) -- (C);
   \draw ($0.5*(C1) + 0.5*(C)$) node[above, xshift=-1mm] {$\gamma$};
@@
   \coordinate (D2) at ($(240:3) - (-0.75, 0.43301270189221932338)$);
-  \draw[<->, >=latex', ultra thick] (D1) -- (D);
-  \draw[<->, >=latex', ultra thick] (D2) -- (D);
+  \draw [<->, >=latex, decoration={markings,mark=at position 1 with {\arrow[scale=0.5]{>}}},postaction={decorate}] (D1) -- (D);
+  \draw [<->, >=latex, decoration={markings,mark=at position 1 with {\arrow[scale=0.5]{>}}},postaction={decorate}] (D2) -- (D);
   \draw ($0.5*(D1) + 0.5*(D)$) node[below, xshift=-1mm] {$\gamma$};

### 2019-01-15 ICML-submission/introduction.tex
pass over intro

@@
 the learner is asked to make a prediction $\widehat{y}_t$. Immediately after
-making its prediction, the learner receives a feedback. In contrast with the
+making its prediction, the learner receives feedback. In contrast with the
 standard full information setting (where the feedback given is the correct label
@@
 \STATE Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.
-\STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \begin{cases}
+\STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.}
+\STATE{Observe feedback $z_t \in \{0,1\}$, \\ \qquad where $z_t = \begin{cases}
 0 & \text{if $\widehat y_t = y_t$,} \\
@@
 including online advertising and online content optimization.
+\chicheng{Perhaps cite~\cite{Kakade-Shalev-Shwartz-Tewari-2008}?}
 
@@
 adversary lie in $\R^d$ and are linearly separable with a margin. We introduce
-two notions of linear separability, \emph{weak} and \emph{strong}. These are
+two notions of linear separability, \emph{weak} and \emph{strong},
 formally stated in
@@
 
-In the full-information feedback setting, it is well known that if the examples
-have norm at most $R$ and are weakly linearly separable with a margin $\gamma$
+In the full-information feedback setting, it is well known that if all examples
+have norm at most $R$ and are weakly linearly separable with a margin $\gamma$,
 then the \textsc{Multiclass Perceptron} algorithm makes at most $\lfloor
-2(R/\gamma)^2 \rfloor$ mistakes. This result is very satisfying since the upper
-bound on the number of mistakes is information-theoretically optimal and at the
-same time the \textsc{Multiclass Perceptron} algorithm has low time and memory
-complexity.
+2(R/\gamma)^2 \rfloor$ mistakes.
+The guarantees provided by \textsc{Multiclass Perceptron} is very satisfying,
+since it achieves an information-theoretically optimal mistake upper bound,
+while having low time and memory complexities.
+\footnote{These results are standard in the literature. For completeness, we present Theorems~\ref{theorem:mutliclass-perceptron-mistake-upper-bound}
+and~\ref{theorem:online-multiclass-classification-mistake-lower-bound},
+along with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs}.}
+%the \textsc{Multiclass Perceptron} algorithm
 
 The bandit feedback setting, however, is much more challenging. For the case
-when the examples are strongly linearly separable, we design a simple and
-efficient algorithm with an expected number of mistakes at most $(K-1) \lfloor
+when the examples are strongly linearly separable, to the best
+of our knowledge, it is not known how to design
+an efficient algorithm with a finite mistake bound before our work.
+\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009} claimed that their
+Conservative OVA algorithm with PA-I update has a finite mistake bound under the
+strong linear separability condition, their proof of Theorem 2 is incorrect.
+Their Lemma 4 cannot be directly applied to the bandit setting, as the algorithm
+only makes updates on a subset of the $w_i$'s.}
+We design a simple and
+efficient algorithm, namely
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
+that has an expected number of mistakes at most $(K-1) \lfloor
 4(R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies of the
@@
 
-For the case when examples are weakly linearly separable, we construct a feature
-mapping $\phi$ such that makes them \emph{strongly} linearly separable. We then
-use the kernelized version of the algorithm for the strongly separable case; for
+For the case when examples are weakly linearly separable,
+we construct a feature
+mapping $\phi$ that makes them \emph{strongly} linearly separable. We then
+use the kernelized version of the algorithm, namely Algorithm~\ref{algorithm:kernelized},
+ for the strongly separable case; for
  more details on kernel methods see e.g.~\citet{Scholkopf-Smola-2002} and
@@
 related to the problem of learning intersection of halfspaces and has been
-studied previously by \citet{Klivans-Servedio-2008}. In fact, our analysis can
-be viewed as a follow up on their work. We improve on the results of
-\citet{Klivans-Servedio-2008} by removing the dependency on the original
-dimension $d$.
+studied previously by \citet{Klivans-Servedio-2008}.
+As a side result, we improve on the results of
+\citet{Klivans-Servedio-2008} by removing the dependency of the margin parameter
+ on the original dimension $d$.
+%inspired by~\cite{Klivans-Servedio-2008},
+%In fact, our analysis can
+%be viewed as a follow up on their work.
 
@@
 $\R^d$ and are weakly separable with margin $\gamma$, the algorithm makes at
-most $O(???)$ mistakes.
+most $2^{\widetilde{O}(\min(K \log^2
+\frac{1}{\gamma}, \sqrt{\frac{1}{\gamma}} \log K))}$ mistakes.

### 2019-01-15 ICML-submission/notions-of-linear-separability.tex
pass over intro

@@
 e.g.~\citet{Chen-Chen-Zhang-Chen-Zhang-2009}.
-\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009} claimed that their
-Conservative OVA algorithm with PA-I update has a finite mistake bound under the
-strong linear separability assumption, their proof of Theorem 2 is incorrect.
-Their Lemma 4 cannot be directly applied to the bandit setting, as the algorithm
-only makes updates on a subset of the $w_i$'s.} Intuitively, strong linear
+Intuitively, strong linear
 separability means that, for each class $i$, the set of examples belonging to

### 2019-01-15 ICML-submission/title-and-abstract.tex
Finish section 5
pass over intro

--- 2019-01-10 ICML-submission/title-and-abstract.tex
@@
 an efficient algorithm with a mistake bound of $2^{\widetilde{O}(\min(K \log^2
-\frac{1}{\gamma}, \log K \sqrt{\frac 1 \gamma}))}$ \footnote{We use the notation
-$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}. Our algorithm is
-based on a infinite-dimensional feature mapping that transforms weak linear
-separable examples to strong linear separable examples, which in turn is
-inspired by the work of \citet{Klivans-Servedio-2008} on learning intersection of
-halfspaces.
+\frac{1}{\gamma}, \sqrt{\frac{1}{\gamma}} \log K))}$ \footnote{We use the notation
+$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}. Our algorithm
+is based on kernel Perceptron, which is inspired by the work
+of \citet{Klivans-Servedio-2008} on improperly learning intersection of halfspaces.
+%is based on a infinite-dimensional feature mapping that transforms weakly linear
+%separable examples to strongly linear separable examples, which in turn is
+%of \citet{Shalev-Shwartz-Shamir-Sridharan-2011},
 \end{enumerate}

### 2019-01-15 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
sect. 4

@@
 In this section, we present an algorithm for \textsc{Online Multiclass
-Classification with Bandit Feedback} and prove an upper bound on the number of
-mistakes under the assumption that the examples are strongly linearly separable
-with a margin. The algorithm is stated as
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
-the mistake upper bound is stated as
-\autoref{theorem:strongly-separable-examples-mistake-upper-bound}.
+Classification with Bandit Feedback}, namely Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}.
+Under the assumption that the examples are strongly linearly separable
+with a margin (Definition~\ref{definition:strong-linear-separability}),
+we prove \autoref{theorem:strongly-separable-examples-mistake-upper-bound},
+which gives an upper bound on its number of mistakes.
 
-The idea behind the algorithm is to use $K$ copies of the \textsc{Binary
-Perceptron} algorithm, where each copy corresponds to a class. In each round,
-copy $i$ makes a binary prediction, indicating whether the example belongs to
+%The algorithm is stated as
+% and
+%the mistake upper bound is stated as.
+
+The idea behind Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
+ is to use $K$ copies of the \textsc{Binary
+Perceptron} algorithm,
+\chicheng{Shall we define the binary Perceptron algorithm?}
+where each copy corresponds to a class. At each timestep $t$, upon seeing
+example $x_t$,
+copy $i$ makes a binary prediction on whether $x_t$ belongs to
 class $i$ or not. If at least one copy makes a positive prediction, the
@@
 integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
-$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
-$V \times \{1,2,\dots,K\}$ such that
+$L = ((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples in
+$V \times \{1,2,\dots,K\}$ such that:
 \begin{enumerate}
-  \item the examples are strongly linearly separable with margin $\gamma$ (Definition~\ref{definition:strong-linear-separability}),
+  \item $L$ is strongly linearly separable with margin $\gamma$,
   \item $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$,
@@
 
+%$A
+%= \sum_{t ~:~ S_t \neq \emptyset} z_t$
+%B = \sum_{t ~:~ S_t = \emptyset} z_t
+%\sum_{t ~:~ S_t = \emptyset}
 \begin{proof}
@@
 mistakes Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} makes.
-Let $A
-= \sum_{t ~:~ S_t \neq \emptyset} z_t$ be the number of mistakes in the rounds
-when $S_t \neq \emptyset$ and let $B = \sum_{t ~:~ S_t = \emptyset} z_t$ be the
+Let $A = \sum_{t=1}^T \one[S_t \neq \emptyset] z_t$ be the number of mistakes in the rounds
+when $S_t \neq \emptyset$, i.e. the number of rounds line~\ref{line:neg-update} is
+executed.
+In addition, let $B = \sum_{t=1}^T \one[S_t = \emptyset] z_t$ be the
 number of mistakes in the rounds when $S_t = \emptyset$.
@@
 
-Let $C$ be the number of times line~\ref{line:pos-update} gets executed. Let $U$
-be the number of times line~\ref{line:pos-update} or line~\ref{line:neg-update}
-get executed. In other words, $U$ is the number of times the $K$-tuple of
+Let $C = \sum_{t=1}^T \one[S_t = \emptyset](1 - z_t)$ be the number of rounds
+line~\ref{line:pos-update} gets executed. Let
+$U = \sum_{t=1}^T (\one[S_t \neq \emptyset] z_t + \one[S_t = \emptyset](1 - z_t))$
+be the number of rounds line~\ref{line:pos-update} or~\ref{line:neg-update}
+gets executed. In other words, $U$ is the number of times the $K$-tuple of
 vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets updated. It can be
@@
 
-The key observation is that $\Exp[B] = (K-1) \Exp[C]$. The equality holds
-because if $S_t = \emptyset$, there is $1/K$ probability that the algorithm
-guesses the correct label and with probability $(K-1)/K$ algorithm's guess is
-incorrect. Putting all the information together, we get that
+The key observation is that $\Exp[B] = (K-1) \Exp[C]$.
+To see this, note that if $S_t = \emptyset$, there is $1/K$ probability that the algorithm
+guesses the correct label ($z_t = 0$) and with probability $(K-1)/K$ algorithm's guess is
+incorrect ($z_t = 1$). Therefore,
+\[ \Exp[ z_t |S_t = \emptyset] = \frac{K-1}{K}, \]
+\[ \Exp[B] = \frac{K-1}{K} \Exp \sbr{ \sum_{t=1}^T \one[S_t = \emptyset] }, \]
+\[ \Exp[C] = \frac{1}{K} \Exp \sbr{ \sum_{t=1}^T \one[S_t = \emptyset] }. \]
+
+Putting all the information together, we get that
 \begin{align}

### 2019-01-15 ICML-submission/notions-of-linear-separability.tex
sect. 4

@@
 Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
-integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
-y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.
+integer, and $\gamma$ be a positive real number. Let $L = ((x_1, y_1), (x_2,
+y_2), \dots, (x_T, y_T))$ be a set of labeled examples in $V \times \{1,2,\dots,K\}$.
+\chicheng{This $L$ notion may be a bit confusing - feel free to edit}
 
-The examples are said to be \emph{weakly linearly separable with a
+$L$ is said to be \emph{weakly linearly separable with a
 margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
@@
 Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
-integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
-y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.
+integer, and $\gamma$ be a positive real number. Let $L = ((x_1, y_1), (x_2,
+y_2), \dots, (x_T, y_T))$ be labeled examples in $V \times \{1,2,\dots,K\}$.
 
-The examples are said to be \emph{strongly linearly separable with a
+$L$ is said to be \emph{strongly linearly separable with a
 margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
@@
 sense that any deterministic algorithm must make $\left\lfloor (R/\gamma)^2
-\right \rfloor$ mistakes in the worst case. For completeness, we state the
+\right \rfloor$ mistakes in the worst case.
+\chicheng{And any randomized algorithm must make $\left\lfloor (R/\gamma)^2
+\right \rfloor / 2$ mistakes?}
+For completeness, we state the
 \textsc{Multiclass Perceptron} algorithm and give proofs of both of these
 results in Appendix~\ref{section:multiclass-perceptron-proofs}.
+
+\chicheng{Shall we mention the multiclass margin notion that appeared in e.g.}
 
@@
 separability means that, for each class $i$, the set of examples belonging to
-class $i$ and the set of example belonging to the remaining $K-1$ classes are
+class $i$ and the set of examples belonging to the remaining $K-1$ classes are
 separated by a linear classifier $w_i$ by a margin $\frac \gamma 2$.
@@
 It is easy to see that if a set of labeled examples are strongly linearly
-separable with margin $\gamma$, then they are weakly linearly separable with
+separable with margin $\gamma$, then it is also weakly linearly separable with
 the same margin. Indeed, if $w_1, w_2, \dots, w_K \in V$
@@
 In the special case of $K=2$, if a set of labeled examples are weakly linearly
-separable with a margin $\gamma$, then they are strongly linearly separable with
+separable with a margin $\gamma$, then it is also strongly linearly separable with
 the same margin. Indeed, if $w_1, w_2$ satisfy
@@
 \eqref{equation:strong-linear-separability-2},
-\eqref{equation:strong-linear-separability-3}. The first condition follows from
+\eqref{equation:strong-linear-separability-3}.
+Equation~\eqref{equation:strong-linear-separability-1} follows from
 $\norm{w_i'}^2 \le (\frac{1}{2} \norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le
 \frac{1}{2}\norm{w_1}^2 + \frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
-The last two condition follows from the fact that $w_1' - w_2' = w_1 - w_2$.
+Equations~\eqref{equation:strong-linear-separability-2} and~\eqref{equation:strong-linear-separability-3} follow from the fact that $w_1' - w_2' = w_1 - w_2$.
 
@@
 $2$, there exists a set of labeled examples that is weakly linearly separable
-with a positive margin $\gamma$ but it is not strongly linearly separable with
+with a positive margin $\gamma$ but is not strongly linearly separable with
 any positive margin $\gamma$. An example of such set of labeled examples is

### 2019-01-15 ICML-submission/related-work.tex
sect. 4

--- 2019-01-10 ICML-submission/related-work.tex
@@
 
-The problem of bandit multiclass linear classification was initially formulated
-in the pioneering work of~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed
-two computationally inefficient algorithms that work in the standard
-linearly separable setting, one with a mistake bound of $O(K^2 d
-\ln(\frac{d}{\gamma^2}))$, the other with a mistake bound of
-$\widetilde{O}(\frac{K^2}{\gamma^2} \ln T)$. In addition, the authors propose
-the \textsc{Banditron} algorithm, a computationally efficient algorithm that has
-a $O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
-and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weak linearly separable
-setting. The polynomial dependence of \textsc{Banditron}'s mistake bound on the
-time horizon is undesirable for problems with a long time horizon. One key open
-question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
-design computationally efficient algorithms that achieve mistake bounds that
-match or improve over those of inefficient algorithms. In this paper, we take a
-step towards answering this question, showing that efficient algorithms with
-mistake bounds quasipolynomial in the margin parameter can be obtained.
+The problem of online bandit multiclass learning was initially formulated in the
+pioneering work of~\citet{Auer-Long-1999}, under the name of ``weak reinforcement
+model''. They showed that if all examples shown agrees with some
+classifier in a prespecified hypothesis class $\calH$, then the optimal mistake
+bound in the bandit setting can be upper bounded by the optimal mistake bound in
+the full information setting, times a factor of $(2.01 + o(1))K \ln K$.
+\citet{Long-2017} later improved the factor to $(1 + o(1)) K \ln K$ and showed its
+ near-optimality.
+\citet{Daniely-Helbertal-2013} extended the results to the setting where the
+performance of the algorithm is measured by its regret, i.e. the difference
+between the number of mistakes made by the algorithm and the number of mistakes
+made by the best classifier in $\calH$ in hindsight. However, all algorithms
+developed in this context are computationally inefficient.
+
+The linear classification version of this problem is initially studied
+by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed two computationally
+inefficient algorithms that work in the weakly linearly separable setting, one
+with a mistake bound of $O(K^2 d \ln(\frac{d}{\gamma}))$, the other with a
+mistake bound of $\widetilde{O}(\frac{K^2}{\gamma^2} \ln T)$.
+The latter result was later improved by \citet{Daniely-Helbertal-2013},
+which gives a computationally inefficient algorithm with a mistake
+upper bound of $\widetilde{O}(\frac{K}{\gamma^2})$.
+In addition, the
+authors propose the \textsc{Banditron} algorithm, a computationally efficient
+algorithm that has a $O(T^{2/3})$ regret against the multiclass hinge loss in
+the general setting, and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weak
+linearly separable setting. The polynomial dependence of \textsc{Banditron}'s
+mistake bound on the time horizon is undesirable for problems with a long time
+horizon. One key open question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}
+is whether one can design computationally efficient algorithms that achieve
+mistake bounds that match or improve over those of inefficient algorithms. In
+this paper, we take a step towards answering this question, showing that
+efficient algorithms with mistake bounds quasipolynomial in $\frac 1 \gamma$
+or quasipolynomial in $K$ can be obtained.
+
+%In addition, it also
+% shows that under different relationships between $k$, $d$ and $\gamma$,
+% the adversary can force the learner to incur $\Omega(K^2 d)$
+% or $\Omega(\frac{K}{\gamma^2})$ mistakes.
 
@@
 %positive answer. $O(k^2 d \ln(\frac{d}{\gamma^2}))$
+\chicheng{I significantly shortened the discussions of all those $\sqrt{T}$
+regret algorithms here, as I think they are not very relevant.}
 
-Many works consider bandit multiclass classification in the general
-non-separable setting. \citet{Abernethy-Rakhlin-2009} poses the open problem of
-whether one can design an efficient algorithm to get a $O(\sqrt{T})$ regret
-against some reasonable loss functions. \citet{Crammer-Gentile-2013} show that
-such an algorithm can be obtained, provided that the distribution of the label
-$y_t$ conditioned on feature vector $x_t$ satisfies certain parametric noise
-assumption. \citet{Hazan-Kale-2011} developed the \textsc{Newtron} algorithm,
-which has a regret between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass
-logistic loss, where the exact order of the regret depends on the diameter of
-the benchmark class. In particular, if the diameter is $O(\ln T)$, its regret
-bound would become $O(T^{2/3})$. The \textsc{SOBA} algorithm by
-\citet{Beygelzimer-Orabona-Zhang-2017} achieves a regret of
-$\widetilde{O}(\sqrt{T})$ against the
-$\eta$-loss~\citet{Orabona-Cesa-Bianchi-Gentile-2012}. In addition, its regret
-bound does not depend sensitively on the diameter of the benchmark class.
-\citet{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a
-regret of $\widetilde{O}(\sqrt{T})$ against the multiclass logistic loss, where
-it doubly-exponentially improves over \citet{Hazan-Kale-2011}'s regret on its
-dependence on the diameter of the benchmark class.
+Many works consider bandit multiclass classification in the general setting,
+where the data is not necessarily separable by some linear
+classifier~\cite{Abernethy-Rakhlin-2009,
+Wang-Jin-Valizadegan-2010,
+Crammer-Gentile-2013,
+Hazan-Kale-2011, Beygelzimer-Orabona-Zhang-2017,
+Foster-Kale-Luo-Mohri-Sridharan-2018}.
+In addition, \citet{Chen-Lin-Lu-2014, Zhang-Jung-Tewari-2018} study online bandit
+multiclass boosting under bandit feedback, where one can view boosting as
+linear classification by treating each base hypothesis as a separate
+feature.
+However, most of these works achieve a regret bound of order $\widetilde{O}(\sqrt{T})$
+to $O(T^{3/4})$. In the weakly separable setting, these algorithms
+only guarantees a mistake upper bound of $\widetilde{O}(\sqrt{T})$, which is
+undesirable for problems with a long time horizon.
+One exception is the \textsc{Newtron} algorithm, where with appropriate
+settings of parameter $\alpha$, it is able to achieve a $O(\ln T)$ regret.
+However, as argued
+in ~\citep[][Appendix D]{Beygelzimer-Orabona-Zhang-2017}, if the setting of $\alpha$
+makes the regret bound $O(\sqrt{T})$, the logistic loss of the best linear
+predictor would be $\Omega(T^{3/4})$. Therefore, \textsc{Newtron} is still only
+able to guarantee a mistake upper bound of $O(\sqrt{T})$ in the weakly separable setting.
 
-\citet{Chen-Lin-Lu-2014} and \citet{Zhang-Jung-Tewari-2018} study online bandit
-multiclass boosting under bandit feedback, where one can view online boosting as
-online linear classification by treating each base hypothesis as a separate
-feature. \citet{Chen-Lin-Lu-2014}'s online weak learning condition implies that
-the set of examples is strongly separable by a convex combination of base
-hypotheses with a margin. Under this condition, it gives an algorithm with a
-$O(T^{3/4})$ mistake bound. \citet{Zhang-Jung-Tewari-2018} considers an online
-weak learning condition, which implies that all examples is separable by a
-convex combination of base hypotheses with a margin; see~\citet[Theorem
-3]{Mukherjee-Schapire-2013}. Under this condition, it gives a boosting algorithm
-with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge parameter. In
-addition, it gives an adaptive algorithm with a $O(T^{3/4})$ mistake bound.
+%\citet{Abernethy-Rakhlin-2009} poses the open problem of
+%whether one can design an efficient algorithm to get a $O(\sqrt{T})$ regret
+%against some reasonable loss functions. \citet{Crammer-Gentile-2013} show that
+%such an algorithm can be obtained, provided that the distribution of the label
+%$y_t$ conditioned on feature vector $x_t$ satisfies certain parametric noise
+%assumption. \citet{Hazan-Kale-2011} developed the \textsc{Newtron} algorithm,
+%which has a regret between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass
+%logistic loss, where the exact order of the regret depends on the diameter of
+%the benchmark class. In particular, if the diameter is $O(\ln T)$, its regret
+%bound would become $O(T^{2/3})$. The \textsc{SOBA} algorithm by
+%\citet{Beygelzimer-Orabona-Zhang-2017} achieves a regret of
+%$\widetilde{O}(\sqrt{T})$ against the
+%$\eta$-loss~\citet{Orabona-Cesa-Bianchi-Gentile-2012}. In addition, its regret
+%bound does not depend sensitively on the diameter of the benchmark class.
+%\citet{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a
+%regret of $\widetilde{O}(\sqrt{T})$ against the multiclass logistic loss, where
+%it doubly-exponentially improves over \citet{Hazan-Kale-2011}'s regret on its
+%dependence on the diameter of the benchmark class.
 
-The online bandit multiclass learning is a special case of the contextual
-bandits problem~\citep{Auer-2003, Langford-Zhang-2008}, where the cost is the
-classification error. A series of works in the contextual bandits learning
-literature focuses on oracle-efficiency, that is, they assume access to an
-oracle that given a set of cost-sensitve learning examples.
+%\citet{Chen-Lin-Lu-2014}'s online weak learning condition implies that
+%the set of examples is strongly separable by a convex combination of base
+%hypotheses with a margin. Under this condition, it gives an algorithm with a
+%$O(T^{3/4})$ mistake bound. \citet{Zhang-Jung-Tewari-2018} considers an online
+%weak learning condition, which implies that all examples is separable by a
+%convex combination of base hypotheses with a margin; see~\citet[Theorem
+%3]{Mukherjee-Schapire-2013}. Under this condition, it gives a boosting algorithm
+%with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge parameter. In
+%addition, it gives an adaptive algorithm with a $O(T^{3/4})$ mistake bound.
 
-There has been much literature on the contextual bandit learning
+%Online bandit multiclass learning is a special case of the contextual
+%bandits problem~\citep{Auer-2003, Langford-Zhang-2008}, where the cost is the
+%classification error. A series of works in the contextual bandits
+%literature focuses on oracle-efficiency, that is, they assume access to an
+%oracle that given a set of cost-sensitve learning examples, generates .
+
+There is a large body of literature on the contextual bandit learning
 problem~\citep{Auer-2003, Langford-Zhang-2008}. In this problem, the learner is
@@
 with an associated cost vector $c_t$ hidden. The learner then takes an action
-$\widehat{y}_t$, and observed the incurred cost $c_t$. The goal of the learner is to
-minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{\pi \in \Pi}
+$\widehat{y}_t$, and observes the incurred cost $c_t(\widehat{y}_t)$.
+The goal of the learner is to minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{\pi \in \Pi}
 \sum_{t=1}^T c_t(\pi(x_t))$. The online bandit multiclass learning problem is a
@@
 Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. Specifically, they assume access to
-a policy optimization oracle that receives a set of cost-sensitive learning
-examples and policy class $\Pi$, return the policy in $\Pi$ that minimizes its
-empirical cost on the examples, and the algorithm only call the oracle a
+a policy optimization oracle that can return the policy in $\Pi$ that minimizes its
+empirical cost on any set of cost-sensitive examples, and the algorithm only calls the oracle a
 polynomial number of times. However, these algorithms are not truly
@@
 
+%that receives a set of cost-sensitive learning
+%examples and policy class $\Pi$,
 %as algorithms generate cost-sensitive examples that may not be linearly
@@
 Recently, \citet{Foster-Krishnamurthy-2018} developed a rich theory of
-contextual bandits with surrogate losses, focusing on benchmarks of the form
-$\min_{f \in \calF} \sum_{t=1}^T \frac{1}{K} \sum_{i=1}^K c_t(i) \phi( f_i(x_t)
+contextual bandits with surrogate losses, focusing on regrets of the form
+$\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{f \in \calF} \sum_{t=1}^T \frac{1}{K} \sum_{i=1}^K c_t(i) \phi( f_i(x_t)
 )$, where $\calF$ contains score functions $f$ such that $\sum_{i=1}^K
@@
 W \in \R^{k \times d}, \one^T W = 0}$. A direct application of this result to
-the online bandit multiclass learning problem yields an algorithm with a
-$O(\sqrt{T})$ mistake bound in the strong linearly separable setting.
+online bandit multiclass linear classification yields an algorithm with a
+$O(\sqrt{T})$ mistake bound in the strongly linearly separable setting.
 

### 2019-01-15 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
finished section 4

@@
 To finish the proof, we need to upper bound the number of updates $U$. We claim
-that $U \le \lfloor 4(R/\gamma)^2 \rfloor$. The proof of this upper bound is
+that $U \le \lfloor 4(R/\gamma)^2 \rfloor$ with probability 1.
+The proof of this upper bound is
 similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
@@
 \endgroup
+The inequality that $(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t} \leq 0$ is from a case analysis: if line~\ref{line:pos-update} is executed, then $z_t = 0$ and $\ip{w_i^{(t)}}{x_t} \ge 0$; otherwise line~\ref{line:neg-update} is executed, in which case $z_t = 1$ and $\ip{w_i^{(t)}}{x_t} \le 0$.
+
 Hence, after $U$ updates,
@@
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
-optimal to within constant factor as long as the number of classes $K$ is
+optimal upto constant factor, as long as the number of classes $K$ is
 at most $O((R/\gamma)^2)$. This is proved in
@@
 on the expected number of mistakes of any randomized algorithm is
-$\frac{K-1}{2}$. (Adversary chooses the same example over and over.) However, it
-is unclear if the trivial lower bound is the best possible if $K$ is large,
+$\frac{K-1}{2}$. To see this, note that the adversary can choose an example $(R e_1, y)$,
+where $y$ is a label chosen uniformly from $\cbr{1,2\ldots,K}$, and show this example $K-1$ times.
+The sequence of examples trivially satisfies the strong linear separability condition, and
+the $\frac{K-1}{2}$ expected mistake lower bound follows from Claim 2 of~\citet{Daniely-Helbertal-2013}.
+However, it is unclear if the trivial lower bound is the best possible if $K$ is large,
 i.e., $\omega((R/\gamma)^2)$. We leave this as an open problem.
@@
 
-for $i \in \{1,2,\dots,K\}$ and any $j \in
+for $i \in \{1,2,\dots,K\}$ and $j \in
 \{1,2,\dots,M\}$, we consider the inner product of $w_i^*$ and $v_j$.
 If $i = \ell_j$, $\ip{w_i^*}{v_j} = \gamma - \frac \gamma 2 = \frac \gamma 2$;
-otherwise $i \neq \ell_j$, in this case,
+otherwise $i \neq \ell_j$, in which case 
 $\ip{w_i^*}{v_j} = 0 - \frac \gamma 2 = - \frac \gamma 2$.

### 2019-01-15 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
before editing sect. 5

@@
   \item $L$ is strongly linearly separable with margin $\gamma$,
-  \item $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$,
+  \item for all $t$ in $\cbr{1,\ldots,T}$, $\norm{x_t} \le R$,
 \end{enumerate}
@@
 
+%$\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
 %$A
@@
 
+The following theorem is a direct consequence of Theorem~\ref{theorem:strongly-separable-examples-mistake-upper-bound}.
+
+\begin{theorem}[Mistake upper bound for kernelized algorithm]
+\label{theorem:kernelized-upper-bound}
+Let $k(\cdot, \cdot)$ be a kernel function with feature map $\phi$, $K$ be a positive
+integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
+$L = ((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples in
+$V \times \{1,2,\dots,K\}$ such that:
+\begin{enumerate}
+  \item $((\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T))$ is strongly linearly separable with margin $\gamma$,
+  \item for all $t$ in $\cbr{1,\ldots,T}$, $k(x_t,x_t) \le R^2$,
+\end{enumerate}
+then the
+expected number of mistakes
+Algorithm~\ref{algorithm:kernelized}
+makes is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
+\end{theorem}
+
 \begin{algorithm}[h]

### 2019-01-15 ICML-submission/from-weak-separability-to-strong-separability.tex
Small fixes
before editing sect. 5

@@
 \dots, \alpha_d)$ of non-negative integers and $c_{\alpha_1, \alpha_2, \dots,
-\alpha_d}$ is a real coefficient. The \emph{degree} of a polynomial $p$, denoted
+\alpha_d}$'s are real coefficients. The \emph{degree} of a polynomial $p$, denoted
 by $\deg(p)$, is the largest value of $\alpha_1 + \alpha_2 + \dots + \alpha_d$
 for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is non-zero.
-The \emph{norm of a polynomial} $p$ is defined as
+Following the terminology of~\cite{Klivans-Servedio-2008},
+the \emph{norm of a polynomial} $p$ is defined as
 $$
@@
 $$
-It is easy see that this is indeed a norm, since we can interpret it as a
+It is easy see that this is indeed a norm, since we can interpret it as the
 Euclidean norm of the vector of the coefficients of the polynomial.
@@
 \gamma_1 & = \frac{1}{2\sqrt{K}}  \\
-& \ \cdot \left(376 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; , \\
-\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4(2K-5/2) 2^{K-1}} \\
+& \ \cdot \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \\
+\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4\sqrt{K}(2K-5/2) 2^{K-1}} \\
 & \ \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} \; .
@@
 \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}} \; . \\
-u_i' & = \frac{c_i'  \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)}}{(2K-5/2) 2^{K-1}} \; .
+u_i' & = \frac{c_i'  \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)}}{\sqrt{K} (2K-5/2) 2^{K-1}} \; .
 \end{align*}
@@
 strongly linearly separable with margin $\gamma_1$ and also strongly linearly
-separable with margin $\gamma_2$. Therefore, the examples are strongly separable
-with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
+separable with margin $\gamma_2$. Therefore, the examples are strongly
+linearly separable with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
 \end{proof}

### 2019-01-15 ICML-submission/from-weak-separability-to-strong-separability.tex
almost finished pass over section 5

@@
 
-In this section, we construct and analyze a mapping $\phi$ from the unit ball of
-$\R^d$ into a infinite-dimensional inner product space that has the property
-that if a set of labeled examples in the unit ball is \emph{weakly} linearly
-separable with a margin $\gamma$ after applying the mapping $\phi$ the examples
-become \emph{strongly} linearly separable with a margin $\gamma'$ and their
+In this section, we focus on the setting of online bandit multiclass
+linear prediction, where the set of examples shown by the adversary is weakly
+linearly separable (Definition~\ref{definition:weak-linear-separability}).
+Throughout this section, we assume without loss of generality that
+all examples lie in $\B(0,1)$, the unit $\ell_2$ ball of
+$\R^d$.\footnote{Consider the following preprocessing step: upon seeing every
+example $x_t$, we define $\hat{x}_t = \frac{x_t}{\|x_t\|}$ as its $\ell_2$ normalization.
+It can be easily checked that if $(x_1,y_1), \ldots, (x_T,y_T)$ is weakly linearly
+separable by margin $\gamma$ and all $\| x_t \|$'s' have norm at most $R$, then the set of
+normalized examples $(\hat{x}_1,y_1), \ldots, (\hat{x}_T,y_T)$ is weakly linearly
+separable by margin $\gamma/R$.}
+Note that Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
+alone does not guarantee a finite mistake bound in this setting, as weak linear separability
+does not imply strong linear separability.
+
+%from the unit ball of
+%$\R^d$ into a infinite-dimensional inner product space that
+
+In this section, we consider a kernel function $k(\cdot, \cdot)$
+whose corresponding feature map $\phi(\cdot)$ can transform a set of
+\emph{weakly} linear separable examples to \emph{strongly} separable.
+Specifically, $\phi$
+has the property
+that if a set of labeled examples in the unit ball is weakly linearly
+separable with a margin $\gamma$, then after applying $\phi$ the examples
+become strongly linearly separable with a margin $\gamma'$ and their
 norms are bounded by $2$. The parameter $\gamma'$ is a function of the old
-margin $\gamma$ and the number of classes $K$, and is specified in the
+margin $\gamma$ and the number of classes $K$, and is specified in
 \autoref{theorem:margin-transformation} below.
 
-The domain of $\phi$ is the unit ball of $\R^d$. The co-domain of $\phi$ is the
+Specifically, the kernel function $k: \B(0,1) \times \B(0,1) \to \R$ is defined as:
+$$
+k(x,x') = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}_{\R^d}} \; ,
+$$
+We note that the formula for $k$ implies that $k(x,x) < +\infty$ for any $x$ in
+$\B(0,1)$. We also note
+that kernel function $k(x,x')$ can be evaluated in $O(d)$ time.
+
+Consider the
 classical real separable Hilbert space $\ell_2 = \{ x \in \R^\infty ~:~
 \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped with the standard inner product
-$\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. We index the coordinates of
+$\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$.
+Through indexing the coordinates of
 $\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
-integers. The mapping is defined by
+integers, the feature map that corresponds to $k$, $\phi: \B(0,1) \to \ell_2$, is defined as follows:
 \begin{align*}
@@
 where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
-is the multinomial coefficient. The corresponding kernel is
-$$
-k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}_{\R^d}} \; .
-$$
-We note that the formula for $k$ implies that $k(x,x) < +\infty$ for any $x$ in
-the unit ball of $\R^d$ and therefore $\phi(x)$ lies in $\ell_2$. We also note
-that kernel function $k(x,x')$ can be evaluated in $O(d)$ time.
+is the multinomial coefficient.
+It can be easily checked that
+\[ k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2}. \]
+
+%The mapping is defined by
+%and therefore $\phi(x)$ lies in $\ell_2$.
+%The domain of $\phi$ is the unit ball of $\R^d$. The co-domain of $\phi$ is
+
+\begin{theorem}[Margin transformation]
+\label{theorem:margin-transformation}
+Let $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \R^d \times \{1,2,\dots,K\}$
+labeled examples that are weakly linearly separable with margin $\gamma > 0$
+such that $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$.
+Let
+\begin{align*}
+r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(2/\gamma) \right \rceil \\
+\gamma_1 & = \frac{1}{2\sqrt{K}}  \\
+& \ \cdot \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \\
+\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4\sqrt{K}(2K-5/2) 2^{K-1}} \\
+& \ \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} \; .
+\end{align*}
+Then, the labeled examples $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots,
+(\phi(x_T), y_T)$ are strongly linearly separable with margin $\gamma' =
+\max\{\gamma_1, \gamma_2\}$ and $\norm{\phi(x_1)}_{\ell_2},
+\norm{\phi(x_2)}_{\ell_2}, \dots, \norm{\phi(x_T)}_{\ell_2} \le 2$.
+\end{theorem}
 
@@
 
+As a corollary of \autoref{theorem:margin-transformation} and
+\autoref{theorem:strongly-separable-examples-mistake-upper-bound}
+we get the mistake bound for Algorithm~\ref{algorithm:kernelized}
+under the weak separability condition.
+
+\begin{corollary}[Mistake upper bound]
+\label{corollary:weakly-separable-examples-mistake-upper-bound}
+Let $K$ be a positive
+integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
+$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
+$V \times \{1,2,\dots,K\}$ such that
+\begin{enumerate}
+  \item the examples are weakly linearly separable with margin $\gamma$ (Definition~\ref{definition:weak-linear-separability}),
+  \item $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$,
+\end{enumerate}
+then the expected number of mistakes
+Algorithm~\ref{algorithm:kernelized}
+makes is at most $2^{\widetilde{O}(\min(K \log^2
+\frac{1}{\gamma}, \sqrt{\frac{1}{\gamma}} \log K))}$.
+\end{corollary}
+
+\subsection{Proof of Theorem~\ref{theorem:margin-transformation}}
 The idea behind construction and analysis of the mapping $\phi$ is polynomial
@@
 
-\begin{theorem}[Margin transformation]
-\label{theorem:margin-transformation}
-Let $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \R^d \times \{1,2,\dots,K\}$
-labeled examples that are weakly linearly separable with margin $\gamma > 0$
-such that $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$.
-Let
-\begin{align*}
-r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(2/\gamma) \right \rceil \\
-\gamma_1 & = \frac{1}{2\sqrt{K}}  \\
-& \ \cdot \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \\
-\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4\sqrt{K}(2K-5/2) 2^{K-1}} \\
-& \ \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} \; .
-\end{align*}
-Then, the labeled examples $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots,
-(\phi(x_T), y_T)$ are strongly linearly separable with margin $\gamma' =
-\max\{\gamma_1, \gamma_2\}$ and $\norm{\phi(x_1)}_{\ell_2},
-\norm{\phi(x_2)}_{\ell_2}, \dots, \norm{\phi(x_T)}_{\ell_2} \le 2$.
-\end{theorem}
-
-\begin{proof}
+\begin{proof}[Proof of Theorem~\ref{theorem:margin-transformation}]
 First osberve that for any $t=1,2,\dots,T$,
@@
 \end{proof}
-
-As a corollary of \autoref{theorem:margin-transformation} and
-\autoref{theorem:strongly-separable-examples-mistake-upper-bound}
-we get the mistake bound for Algorithm~\ref{algorithm:kernelized}
-under the weak separability condition.
-
-\begin{corollary}[Mistake upper bound]
-\label{corollary:weakly-separable-examples-mistake-upper-bound}
-Let $K$ be a positive
-integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
-$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
-$V \times \{1,2,\dots,K\}$ such that
-\begin{enumerate}
-  \item the examples are weakly linearly separable with margin $\gamma$ (Definition~\ref{definition:weak-linear-separability}),
-  \item $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$,
-\end{enumerate}
-then the expected number of mistakes
-Algorithm~\ref{algorithm:kernelized}
-makes is at most $2^{\widetilde{O}(\min(K \log^2
-\frac{1}{\gamma}, \sqrt{\frac{1}{\gamma}} \log K))}$.
-\end{corollary}

### 2019-01-15 ICML-submission/from-weak-separability-to-strong-separability.tex
.

@@
 integers, the feature map that corresponds to $k$, $\phi: \B(0,1) \to \ell_2$, is defined as follows:
-\begin{align*}
-& \left(\phi(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \\
+\begin{align}
+& \left(\phi(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \nonumber \\
 & \qquad \cdot \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
-\end{align*}
+\label{eqn:phi}
+\end{align}
 where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
@@
 
+The following theorem is our main technical result in this section; we defer its
+proof to Section~\ref{sec:margin-trans}.
+
 \begin{theorem}[Margin transformation]
 \label{theorem:margin-transformation}
-Let $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \R^d \times \{1,2,\dots,K\}$
-labeled examples that are weakly linearly separable with margin $\gamma > 0$
-such that $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$.
-Let
+Let $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ in $\R^d \times \{1,2,\dots,K\}$
+be a set of labeled examples that is weakly linearly separable with margin $\gamma > 0$.
+In addition, for all $t$ in $\cbr{1,\ldots,T}$, $\norm{x_t} \le 1$.
+Let $\phi$ be as defined in Equation~\eqref{eqn:phi}, and
 \begin{align*}
-r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(2/\gamma) \right \rceil \\
+r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1, \quad \quad s = \left \lceil \log_2(2/\gamma) \right \rceil, \\
 \gamma_1 & = \frac{1}{2\sqrt{K}}  \\
-& \ \cdot \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \\
+& \ \cdot \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}, \\
 \gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4\sqrt{K}(2K-5/2) 2^{K-1}} \\
@@
 \end{align*}
-Then, the labeled examples $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots,
-(\phi(x_T), y_T)$ are strongly linearly separable with margin $\gamma' =
-\max\{\gamma_1, \gamma_2\}$ and $\norm{\phi(x_1)}_{\ell_2},
+Then, the set of labeled examples transformed by $\phi$,
+namely $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots,
+(\phi(x_T), y_T)$, is strongly linearly separable with margin $\gamma' =
+\max\{\gamma_1, \gamma_2\}$. In addition, $\norm{\phi(x_1)}_{\ell_2},
 \norm{\phi(x_2)}_{\ell_2}, \dots, \norm{\phi(x_T)}_{\ell_2} \le 2$.
@@
 
-We derive a mistake bound for Algorithm~\ref{algorithm:kernelized} with kernel
-function $k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2}$ by simply invoking
-\autoref{theorem:strongly-separable-examples-mistake-upper-bound} with the
-modified margin $\gamma'$ from \autoref{theorem:margin-transformation} below.
+We are now ready to derive a mistake bound for Algorithm~\ref{algorithm:kernelized} with kernel
+function $k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2}$. This is done by simply invoking
+\autoref{theorem:kernelized-upper-bound} with the
+modified margin $\gamma'$ from \autoref{theorem:margin-transformation}.
 The mistake bound is stated as \autoref{corollary:weakly-separable-examples-mistake-upper-bound}.
 
-As a corollary of \autoref{theorem:margin-transformation} and
-\autoref{theorem:strongly-separable-examples-mistake-upper-bound}
-we get the mistake bound for Algorithm~\ref{algorithm:kernelized}
-under the weak separability condition.
+%As a corollary of \autoref{theorem:margin-transformation} and
+%\autoref{theorem:strongly-separable-examples-mistake-upper-bound}
+%we get the mistake bound for Algorithm~\ref{algorithm:kernelized}
+%under the weak separability condition.
 
@@
 integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
-$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
+$L = ((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples in
 $V \times \{1,2,\dots,K\}$ such that
 \begin{enumerate}
-  \item the examples are weakly linearly separable with margin $\gamma$ (Definition~\ref{definition:weak-linear-separability}),
-  \item $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$,
+  \item $L$ is weakly linearly separable with margin $\gamma$,
+  \item for all $t$ in $\cbr{1,2,\ldots,T}$, $\norm{x_t} \le 1$,
 \end{enumerate}
@@
 \end{corollary}
+%, \norm{x_2}, \dots, \norm{x_T}
+% (Definition~\ref{definition:weak-linear-separability})
 
 \subsection{Proof of Theorem~\ref{theorem:margin-transformation}}
+\label{sec:margin-trans}
 The idea behind construction and analysis of the mapping $\phi$ is polynomial

### 2019-01-15 ICML-submission/from-weak-separability-to-strong-separability.tex
some intuition in Sect 5.1

@@
 \label{sec:margin-trans}
-The idea behind construction and analysis of the mapping $\phi$ is polynomial
-approximation. According to the well known Stone-Weierstrass theorem (see
+\paragraph{Overview.} The idea behind construction and analysis of the mapping $\phi$ is polynomial
+approximation. Specifically, we give $k$ polynomials $p_1$, $\ldots$, $p_k$,
+such that:
+\begin{equation}
+  \forall t \in \cbr{1,2,\ldots,T}, p_{y_t}(x_t) \geq \frac{\gamma'}2,
+  \label{eqn:poly-pos}
+\end{equation}
+\begin{equation}
+  \forall t \in \cbr{1,2,\ldots,T}, \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t}, p_i(x_t) \leq -\frac{\gamma'}2.
+  \label{eqn:poly-neg}
+\end{equation}
+As each polynomial $p_i$ can be written as
+$\ip{c_i}{\phi(x)}$ for some $c_i \in \ell_2$, it immediately shows that
+the set of examples $(\phi(x_1),y_1), \ldots, (\phi(x_T),y_T)$ is strongly linear separable.
+
+To construct $p_1, \ldots, p_k$ that satisfy Equations~\eqref{eqn:poly-pos}
+and~\eqref{eqn:poly-neg}, we consider constructing each $p_i$ separately.
+Specifically, $p_i$ needs to satisfy that:
+\begin{equation}
+  \forall t \in \cbr{1,2,\ldots,T}, y_t = i \Rightarrow p_i(y_t) \geq \frac{\gamma'}2,
+  \label{eqn:poly-pos-i}
+\end{equation}
+\begin{equation}
+  \forall t \in \cbr{1,2,\ldots,T}, y_t \neq i \Rightarrow p_i(y_t) \leq -\frac{\gamma'}2.
+  \label{eqn:poly-neg-i}
+\end{equation}
+
+Under the weak linear separability assumption, we note that all examples from class $i$
+lie in
+$R_i^+ := \cap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \geq \gamma}$, and all examples from other classes lie in
+$R_i^- := \cup_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \leq  -\gamma}$.
+Therefore, to satisfy Equations~\eqref{eqn:poly-pos-i} and~\eqref{eqn:poly-neg-i},
+it suffices to construct $p_i$ such that:
+\begin{align*}
+  x \in R_i^+ & \Rightarrow p_i(x) \geq \frac {\gamma'} 2\\
+  x \in R_i^- & \Rightarrow p_i(x) \leq - \frac {\gamma'} 2
+\end{align*}
+
+According to the well known Stone-Weierstrass theorem (see
 e.g.~\citet[Section~10.10]{Davidson-Donsig-2010}), on a compact set,

### 2019-01-15 ICML-submission/from-weak-separability-to-strong-separability.tex
.

@@
 lie in
-$R_i^+ := \cap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \geq \gamma}$, and all examples from other classes lie in
-$R_i^- := \cup_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \leq  -\gamma}$.
+\[ R_i^+ := \cap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \geq \gamma}, \] and all examples from the remaining classes lie in
+\[ R_i^- := \cup_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \leq  -\gamma}. \]
 Therefore, to satisfy Equations~\eqref{eqn:poly-pos-i} and~\eqref{eqn:poly-neg-i},

### 2019-01-15 ICML-submission/from-weak-separability-to-strong-separability.tex
Fixes

--- 2019-01-15 ICML-submission/from-weak-separability-to-strong-separability.tex
@@
 
-In this section, we focus on the setting of online bandit multiclass
-linear prediction, where the set of examples shown by the adversary is weakly
-linearly separable (Definition~\ref{definition:weak-linear-separability}).
-Throughout this section, we assume without loss of generality that
-all examples lie in $\B(0,1)$, the unit $\ell_2$ ball of
-$\R^d$.\footnote{Consider the following preprocessing step: upon seeing every
-example $x_t$, we define $\hat{x}_t = \frac{x_t}{\|x_t\|}$ as its $\ell_2$ normalization.
-It can be easily checked that if $(x_1,y_1), \ldots, (x_T,y_T)$ is weakly linearly
-separable by margin $\gamma$ and all $\| x_t \|$'s' have norm at most $R$, then the set of
-normalized examples $(\hat{x}_1,y_1), \ldots, (\hat{x}_T,y_T)$ is weakly linearly
-separable by margin $\gamma/R$.}
-Note that Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-alone does not guarantee a finite mistake bound in this setting, as weak linear separability
-does not imply strong linear separability.
+In this section, we case when the sequence of examples shown by the adversary is
+weakly linearly separable
+(Definition~\ref{definition:weak-linear-separability}). Throughout this section,
+we assume without loss of generality that all examples lie in the unit ball
+$\B(0,1) \subseteq \R^d$.\footnote{Consider the following preprocessing step:
+upon seeing every example $x_t$, we define $\hat{x}_t = \frac{x_t}{\norm{x_t}}$
+as its normalization. It can be easily checked that if $(x_1,y_1), \dots,
+(x_T,y_T)$ is weakly linearly separable by margin $\gamma$ and $\norm{x_t} \le
+\R$ for all $t$, then the set of normalized examples $(\hat{x}_1,y_1), \dots,
+(\hat{x}_T,y_T)$ is weakly linearly separable by margin $\gamma/R$.} Note that
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
+alone does not guarantee a finite mistake bound in this setting, as weak linear
+separability does not imply strong linear separability.
 
-%from the unit ball of
-%$\R^d$ into a infinite-dimensional inner product space that
+We consider a kernel function $k(\cdot, \cdot)$ whose corresponding feature map
+$\phi(\cdot)$ transforms any sequence of \emph{weakly} linearly separable
+examples to \emph{strongly} linearly separable sequence of examples.
+Specifically, $\phi$ has the property that if a set of labeled examples in
+$B(0,1)$ is weakly linearly separable with a margin $\gamma$, then after
+applying $\phi$ the examples become strongly linearly separable with a margin
+$\gamma'$ and their norms are bounded by $2$. The parameter $\gamma'$ is a
+function of the old margin $\gamma$ and the number of classes $K$, and is
+specified in \autoref{theorem:margin-transformation} below.
 
-In this section, we consider a kernel function $k(\cdot, \cdot)$
-whose corresponding feature map $\phi(\cdot)$ can transform a set of
-\emph{weakly} linear separable examples to \emph{strongly} separable.
-Specifically, $\phi$
-has the property
-that if a set of labeled examples in the unit ball is weakly linearly
-separable with a margin $\gamma$, then after applying $\phi$ the examples
-become strongly linearly separable with a margin $\gamma'$ and their
-norms are bounded by $2$. The parameter $\gamma'$ is a function of the old
-margin $\gamma$ and the number of classes $K$, and is specified in
-\autoref{theorem:margin-transformation} below.
+The kernel function $k:\B(0,1) \times \B(0,1) \to \R$ is defined as
+$$
+k(x,x') = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}_{\R^d}} \; .
+$$
+Note that kernel function $k(x,x')$ can be evaluated in $O(d)$ time.
 
-Specifically, the kernel function $k: \B(0,1) \times \B(0,1) \to \R$ is defined as:
-$$
-k(x,x') = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}_{\R^d}} \; ,
-$$
-We note that the formula for $k$ implies that $k(x,x) < +\infty$ for any $x$ in
-$\B(0,1)$. We also note
-that kernel function $k(x,x')$ can be evaluated in $O(d)$ time.
-
-Consider the
-classical real separable Hilbert space $\ell_2 = \{ x \in \R^\infty ~:~
-\sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped with the standard inner product
-$\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$.
-Through indexing the coordinates of
-$\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
-integers, the feature map that corresponds to $k$, $\phi: \B(0,1) \to \ell_2$, is defined as follows:
+Consider the classical real separable Hilbert space $\ell_2 = \{ x \in \R^\infty
+~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped with the standard inner
+product $\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. If we index the
+coordinates of $\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of
+non-negative integers, the feature map that corresponds to $k$ is $\phi: \B(0,1)
+\to \ell_2$,
 \begin{align}
@@
 & \qquad \cdot \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
-\label{eqn:phi}
+\label{equation:phi}
 \end{align}
-where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
-is the multinomial coefficient.
-It can be easily checked that
-\[ k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2}. \]
+where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots,
+\alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2!
+\dots \alpha_d!}$ is the multinomial coefficient. It can be easily checked that
+$$
+k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2}.
+$$
+The last equality together with the formula for $k$ implies that $k(x,x) <
++\infty$ for any $x$ in $\B(0,1)$.
 
-%The mapping is defined by
-%and therefore $\phi(x)$ lies in $\ell_2$.
-%The domain of $\phi$ is the unit ball of $\R^d$. The co-domain of $\phi$ is
-
-The following theorem is our main technical result in this section; we defer its
-proof to Section~\ref{sec:margin-trans}.
+The following theorem is our main technical result in this section. We defer its
+proof to Section~\ref{section:margin-transformation}.
 
@@
 \label{theorem:margin-transformation}
-Let $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ in $\R^d \times \{1,2,\dots,K\}$
-be a set of labeled examples that is weakly linearly separable with margin $\gamma > 0$.
-In addition, for all $t$ in $\cbr{1,\ldots,T}$, $\norm{x_t} \le 1$.
-Let $\phi$ be as defined in Equation~\eqref{eqn:phi}, and
+Let $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ in $\B(0,1) \times
+\{1,2,\dots,K\}$ be a sequence of labeled examples that is weakly linearly
+separable with margin $\gamma > 0$. Let $\phi$ be as defined in
+Equation~\eqref{equation:phi}, and
+\begingroup
+\allowdisplaybreaks
 \begin{align*}
@@
 \end{align*}
+\endgroup
 Then, the set of labeled examples transformed by $\phi$,
@@
 
-We are now ready to derive a mistake bound for Algorithm~\ref{algorithm:kernelized} with kernel
-function $k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2}$. This is done by simply invoking
-\autoref{theorem:kernelized-upper-bound} with the
-modified margin $\gamma'$ from \autoref{theorem:margin-transformation}.
-The mistake bound is stated as \autoref{corollary:weakly-separable-examples-mistake-upper-bound}.
-
-%As a corollary of \autoref{theorem:margin-transformation} and
-%\autoref{theorem:strongly-separable-examples-mistake-upper-bound}
-%we get the mistake bound for Algorithm~\ref{algorithm:kernelized}
-%under the weak separability condition.
+Using this theorem we derive a mistake bound for
+Algorithm~\ref{algorithm:kernelized} with kernel function $k(x,x') =
+\ip{\phi(x)}{\phi(x')}_{\ell_2}$. This is done by simply invoking
+\autoref{theorem:kernelized-upper-bound} with the modified margin $\gamma'$ from
+\autoref{theorem:margin-transformation}. The mistake bound is stated as
+\autoref{corollary:weakly-separable-examples-mistake-upper-bound} below.
 
@@
 \label{corollary:weakly-separable-examples-mistake-upper-bound}
-Let $K$ be a positive
-integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
-$L = ((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples in
-$V \times \{1,2,\dots,K\}$ such that
+Let $K$ be a positive integer and let $\gamma$ be a positive real number. If $L
+= ((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples
+in $V \times \{1,2,\dots,K\}$ such that
 \begin{enumerate}
 \item $L$ is weakly linearly separable with margin $\gamma$,
-  \item for all $t$ in $\cbr{1,2,\ldots,T}$, $\norm{x_t} \le 1$,
+\item for all $t$ in $\cbr{1,2,\dots,T}$, $\norm{x_t} \le 1$,
 \end{enumerate}
-then the expected number of mistakes
-Algorithm~\ref{algorithm:kernelized}
-makes is at most $2^{\widetilde{O}(\min(K \log^2
-\frac{1}{\gamma}, \sqrt{\frac{1}{\gamma}} \log K))}$.
+then the expected number of mistakes Algorithm~\ref{algorithm:kernelized} makes
+is at most $2^{\widetilde{O}(\min(K \log^2 \frac{1}{\gamma},
+\sqrt{\frac{1}{\gamma}} \log K))}$.
 \end{corollary}
-%, \norm{x_2}, \dots, \norm{x_T}
-% (Definition~\ref{definition:weak-linear-separability})
 
 \subsection{Proof of Theorem~\ref{theorem:margin-transformation}}
-\label{sec:margin-trans}
-The idea behind construction and analysis of the mapping $\phi$ is polynomial
-approximation. According to the well known Stone-Weierstrass theorem (see
+\label{section:margin-transformation}
+
+\paragraph{Overview.} The idea behind construction and analysis of the mapping
+$\phi$ is polynomial approximation. Specifically, we give $k$ polynomials $p_1$,
+$\ldots$, $p_k$, such that:
+\begin{align}
+\label{equation:poly-pos}
+& \forall t \in \cbr{1,2,\dots,T}, p_{y_t}(x_t) \ge \frac{\gamma'}2 \; ,
+\\
+\label{equation:poly-neg}
+& \begin{gathered}
+\forall t \in \cbr{1,2,\dots,T} \ \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t} \\
+p_i(x_t) \leq -\frac{\gamma'}2 \; .
+\end{gathered}
+\end{align}
+As each polynomial $p_i$ can be written as $\ip{c_i}{\phi(x)}$ for some $c_i \in
+\ell_2$, it immediately shows that the set of examples $(\phi(x_1),y_1), \ldots,
+(\phi(x_T),y_T)$ is strongly linear separable.
+
+To construct $p_1, p_2, \dots, p_k$ that satisfy
+Equations~\eqref{equation:poly-pos} and~\eqref{equation:poly-neg}, we consider
+constructing each $p_i$ separately. Specifically, $p_i$ needs to satisfy that:
+\begin{align}
+\label{equation:poly-pos-i}
+\forall t \in \cbr{1,2,\dots,T}, y_t = i \Rightarrow p_i(y_t) \ge \frac{\gamma'}2 \; , \\
+\label{equation:poly-neg-i}
+\forall t \in \cbr{1,2,\dots,T}, y_t \neq i \Rightarrow p_i(y_t) \le -\frac{\gamma'}2 \; .
+\end{align}
+
+Under the weak linear separability assumption, we note that all examples from
+class $i$ lie in
+\[ R_i^+ = \bigcap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \geq \gamma}, \] and all examples from the remaining classes lie in
+\[ R_i^- = \bigcup_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \leq  -\gamma}. \]
+Therefore, to satisfy Equations~\eqref{equation:poly-pos-i}
+and~\eqref{equation:poly-neg-i}, it suffices to construct $p_i$ such that:
+\begin{align*}
+x \in R_i^+ & \Rightarrow p_i(x) \ge \frac {\gamma'} 2 \\
+x \in R_i^- & \Rightarrow p_i(x) \le - \frac {\gamma'} 2
+\end{align*}
+
+According to the well known Stone-Weierstrass theorem (see
 e.g.~\citet[Section~10.10]{Davidson-Donsig-2010}), on a compact set,

### 2019-01-15 ICML-submission/introduction.tex
Fixes

@@
 mistakes $\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$.
-The bandit feedback is a natural feedback model motivated by applications
-including online advertising and online content optimization.
-\chicheng{Perhaps cite~\cite{Kakade-Shalev-Shwartz-Tewari-2008}?}
 
@@
 adversary lie in $\R^d$ and are linearly separable with a margin. We introduce
-two notions of linear separability, \emph{weak} and \emph{strong},
-formally stated in
+two notions of linear separability, \emph{weak} and \emph{strong}, formally
+stated in
 Definitions~\ref{definition:weak-linear-separability}~and~\ref{definition:strong-linear-separability}.
@@
 then the \textsc{Multiclass Perceptron} algorithm makes at most $\lfloor
-2(R/\gamma)^2 \rfloor$ mistakes.
-The guarantees provided by \textsc{Multiclass Perceptron} is very satisfying,
-since it achieves an information-theoretically optimal mistake upper bound,
-while having low time and memory complexities.
-\footnote{These results are standard in the literature. For completeness, we present Theorems~\ref{theorem:mutliclass-perceptron-mistake-upper-bound}
-and~\ref{theorem:online-multiclass-classification-mistake-lower-bound},
-along with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs}.}
-%the \textsc{Multiclass Perceptron} algorithm
+2(R/\gamma)^2 \rfloor$ mistakes. The guarantees provided by \textsc{Multiclass
+Perceptron} is very satisfying, since it achieves an information-theoretically
+optimal mistake upper bound, while having low time and memory complexities.
+\footnote{These results are standard in the literature. For completeness, we
+present Theorems~\ref{theorem:mutliclass-perceptron-mistake-upper-bound}
+and~\ref{theorem:online-multiclass-classification-mistake-lower-bound}, along
+with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs}.}
 
 The bandit feedback setting, however, is much more challenging. For the case
-when the examples are strongly linearly separable, to the best
-of our knowledge, it is not known how to design
-an efficient algorithm with a finite mistake bound before our work.
-\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009} claimed that their
-Conservative OVA algorithm with PA-I update has a finite mistake bound under the
-strong linear separability condition, their proof of Theorem 2 is incorrect.
-Their Lemma 4 cannot be directly applied to the bandit setting, as the algorithm
-only makes updates on a subset of the $w_i$'s.}
-We design a simple and
-efficient algorithm, namely
+when the examples are strongly linearly separable, to the best of our knowledge,
+it is not known how to design an efficient algorithm with a finite mistake bound
+before our work. \footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
+claimed that their Conservative OVA algorithm with PA-I update has a finite
+mistake bound under the strong linear separability condition, their proof of
+Theorem 2 is incorrect. Their Lemma 4 cannot be directly applied to the bandit
+setting, as the algorithm only makes updates on a subset of the $w_i$'s.} We
+design a simple and efficient algorithm, namely
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
-that has an expected number of mistakes at most $(K-1) \lfloor
-4(R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies of the
+that has an expected number of mistakes at most $(K-1) \lfloor 4(R/\gamma)^2
+\rfloor$. The algorithm can be viewed as running $K$ copies of the
 \textsc{Binary Perceptron} algorithm, one copy for each class. Intuitively
-speaking, the factor $K-1$ is the price we pay for the bandit feedback, or more
-precisely, the lack of full-information feedback. We also prove that any
-(possibly randomized) algorithm makes $\Omega(K (R/\gamma)^2))$ mistakes in the
-worst case.
+speaking, the $O(K)$ multiplicative factor is the price we pay for the bandit
+feedback, or more precisely, the lack of full-information feedback. We also
+prove that any (possibly randomized) algorithm makes $\Omega(K (R/\gamma)^2))$
+mistakes in the worst case.
 
-For the case when examples are weakly linearly separable,
-we construct a feature
-mapping $\phi$ that makes them \emph{strongly} linearly separable. We then
-use the kernelized version of the algorithm, namely Algorithm~\ref{algorithm:kernelized},
- for the strongly separable case; for
- more details on kernel methods see e.g.~\citet{Scholkopf-Smola-2002} and
-\citet{Shawe-Taylor-Cristianini-2004}. The kernel $k(x,y)$ corresponding to the
+For the case when examples are weakly linearly separable, we construct a feature
+mapping $\phi$ that makes them \emph{strongly} linearly separable. We then use
+the kernelized version of the algorithm, namely
+Algorithm~\ref{algorithm:kernelized}, for the strongly separable case; for more
+details on kernel methods see e.g.~\citet{Scholkopf-Smola-2002} and
+\citet{Shawe-Taylor-Cristianini-2004}. The kernel $k(x,x')$ corresponding to the
 feature mapping $\phi$ has a simple explicit formula and can be computed in
@@
 related to the problem of learning intersection of halfspaces and has been
-studied previously by \citet{Klivans-Servedio-2008}.
-As a side result, we improve on the results of
-\citet{Klivans-Servedio-2008} by removing the dependency of the margin parameter
- on the original dimension $d$.
-%inspired by~\cite{Klivans-Servedio-2008},
-%In fact, our analysis can
-%be viewed as a follow up on their work.
+studied previously by \citet{Klivans-Servedio-2008}. As a side result, we
+improve on the results of \citet{Klivans-Servedio-2008} by removing the
+dependency on the original dimension $d$.
 
@@
 $\R^d$ and are weakly separable with margin $\gamma$, the algorithm makes at
-most $2^{\widetilde{O}(\min(K \log^2
-\frac{1}{\gamma}, \sqrt{\frac{1}{\gamma}} \log K))}$ mistakes.
+most $2^{\widetilde{O}(\min(K \log^2 \frac{1}{\gamma}, \sqrt{\frac{1}{\gamma}}
+\log K))}$ mistakes.

### 2019-01-16 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
thm 12 for randomized

@@
 Define a filtration $\cbr{\calB_j}_{j=0}^M$,
-where $\calB_j = \sigma((x_1, y_1), \ldots, (x_{(K-1)j}, y_{(K-1)j}))$
+where $\calB_j = \sigma((x_1, y_1, \hat{y}_1), \ldots, (x_{(K-1)j}, y_{(K-1)j}, \hat{y}_{(K-1)j}))$
 for every $j$ in $\{1,2,\dots,M\}$.
 By Claim 2 of~\citet{Daniely-Helbertal-2013}, as $\ell_j$
-is chosen uniformly from $\cbr{1,\dots,K}$ and independent of $\calB_{j-1}$,
+is chosen uniformly from $\cbr{1,\dots,K}$ and independent of $\calB_{j-1}$ and $\calA$'s
+randomness,
 $$

### 2019-01-16 ICML-submission/appendix-multiclass-perceptron.tex
pass over intro
thm 12 for randomized

@@
 
-\begin{algorithm}[h]
+\begin{protocol}[h]
 \caption{\textsc{Online Multiclass Classification}
@@
 Let $K$ be a positive integer, let $\gamma$ be a positive real number and let
-$R$ be a non-negative real number. For any deterministic algorithm for the
+$R$ be a non-negative real number. For any (possibly randomized) algorithm
+$\calA$ for the
 \textsc{Online Multiclass Classification} problem there exists an
@@
 $\gamma$, the norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
-and the algorithm makes at least $\lfloor (R/\gamma)^2 \rfloor$ mistakes.
+and the algorithm makes at least $\frac 1 2 \lfloor (R/\gamma)^2 \rfloor$ mistakes.
 \end{theorem}
@@
 \begin{proof}
-Let $T = \lfloor (R/\gamma)^2 \rfloor$ and let $x_1, x_2, \dots, x_T$ be the
-orthogonal vectors such that $\norm{x_t} = R$ for all $t=1,2,\dots,T$. For
-example, we can take $V = \R^T$ and $x_t = R e_t$ where $e_t$ is $t$-th element
+Let $T = \lfloor (R/\gamma)^2 \rfloor$, $V = \R^T$, and for all $t$ in
+$\cbr{1,\ldots,T}$, define instance $x_t = R e_t$ where $e_t$ is $t$-th element
 of the standard orthonormal basis of $\R^T$.
+Let labels $y_1, \ldots, y_T$ be chosen i.i.d uniformly at random from
+$\cbr{1,2,\ldots,K}$ and independently of any randomness used by the algirithm
+$\calA$.
 
-Since the algorithm is deterministic, we can construct the sequence of labels
-$y_1, y_2, \dots, y_T$ adaptively based on the predictions $\widehat y_1,
-\widehat y_2, \dots, \widehat y_T$ of the algorithm. We define $y_t$ to be any
-element of $\{1,2,\dots,K\}$ not equal to $\widehat y_t$. This way the algorithm
-makes a mistake in every round $t=1,2,\dots,T$.
+%let $x_1, x_2, \dots, x_T$ be the
+%orthogonal vectors such that $\norm{x_t} = R$ for all $t=1,2,\dots,T$. For
+%example, we can take
 
-It remains to show that the examples we have constructed are linearly separable
-with margin $\gamma$. To prove that we demonstrate vectors $w_1, w_2, \dots, w_K$
+%Since the algorithm is deterministic, we can construct the sequence of labels
+%$y_1, y_2, \dots, y_T$ adaptively based on the predictions $\widehat y_1,
+%\widehat y_2, \dots, \widehat y_T$ of the algorithm. We define $y_t$ to be any
+%element of $\{1,2,\dots,K\}$ not equal to $\widehat y_t$. This way the algorithm
+%makes a mistake in every round $t=1,2,\dots,T$.
+
+We first show that the set of examples $(x_1,y_1)$, $\ldots$,
+$(x_T, y_T)$ we have constructed is weakly linearly separable
+with margin $\gamma$. To prove that, we demonstrate vectors $w_1, w_2, \dots, w_K$
 satisfying conditions \eqref{equation:weak-linear-separability-1} and
@@
 $$
-w_i = \frac{1}{R\sqrt{T}} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} x_t \qquad \text{for $i=1,2,\dots,K$.}
+w_i = \frac{\gamma}{R} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} e_t \qquad \text{for $i=1,2,\dots,K$.}
 $$
@@
 $$
-\norm{w_i}^2 = \frac{1}{R^2 T} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} \norm{x_t}^2 = \frac{a_i}{T} \qquad \text{for $i=1,2,\dots,K$.}
+\norm{w_i}^2 = \frac{\gamma^2}{R^2} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} \norm{e_t}^2 = \frac{a_i \gamma^2}{R^2} \qquad \text{for $i=1,2,\dots,K$.}
 $$
-Since $\sum_{i=1}^K a_i = T$, the condition
+Since $\sum_{i=1}^K a_i = T$,
+$\sum_{i=1}^K \norm{w_i}^2 = T \cdot \frac{\gamma^2}{R^2} \leq 1$, i.e.
+the condition
 \eqref{equation:weak-linear-separability-1} holds. To verify condition
 \eqref{equation:weak-linear-separability-2} consider any labeled example $(x_t,
-y_t)$. Then, by definition of $w_{y_t}$ we have
+y_t)$. Then, for any $i$ in $\cbr{1,\ldots,K}$, by the definition of $w_i$, we have
 \begin{align*}
-\ip{w_{y_t}}{x_t}
-& = \frac{1}{R\sqrt{T}} \sum_{\substack{s : 1 \le s \le T \\ y_s = y_t}} \ip{x_s}{x_t} \\
-& = \frac{1}{R\sqrt{T}} \norm{x_t}^2 \\
-& = \frac{R}{\sqrt{T}} \\
-& \ge \frac{R}{R/\gamma} \\
-& = \gamma \; .
+\ip{w_i}{x_t}
+& = \frac{\gamma}{R} \sum_{\substack{s : 1 \le s \le T \\ y_s = i}} \ip{e_s}{R e_t} \\
+& = \gamma \cdot \sum_{\substack{s : 1 \le s \le T \\ y_s = i}} \one[s = t] \\
+& = \gamma \cdot \one[y_t = i]
+\; .
 \end{align*}
-and for any $i \in \{1,2,\dots,K\} \setminus \{y_t\}$ we have
-$\ip{w_i}{x_t} = 0$. Therefore, condition \eqref{equation:weak-linear-separability-2} holds.
+Therefore, if $i = y_t$, $\ip{w_i}{x_t} = \gamma$;
+otherwise $i \neq y_t$, in which case $\ip{w_i}{x_t} = 0$.
+Hence, condition \eqref{equation:weak-linear-separability-2} holds.
+
+We now give a lower bound on the number of mistakes $\calA$ makes.
+Define a filtration $\cbr{\calB_t}_{t=0}^T$,
+where $\calB_t = \sigma((x_1, y_1, \hat{y}_1), \ldots, (x_t, y_t, \hat{y}_t))$.
+As $y_t$ is chosen uniformly from $\cbr{1,\ldots,K}$ and independent of
+$\calB_{t-1}$ and $\hat{y}_t$,
+\[ \Exp[ \indicator{\widehat y_t \neq y_t} | \calB_{t-1} ] \geq 1 - \frac 1 K \geq \frac 1 2. \]
+This implies that
+\[ \Exp[ \indicator{\widehat y_t \neq y_t} ] \geq \frac 1 2. \]
+Summing over all $t$ in $\cbr{1,\ldots,T}$, we conclude that
+\[ \Exp \sbr{ \sum_{t=1}^T \indicator{\widehat y_t \neq y_t} } \geq \frac T 2 = \frac 1 2 \lfloor (R/\gamma)^2 \rfloor, \]
+which completes the proof.
 \end{proof}
+
+%& = \frac{R}{\sqrt{T}} \\
+%& \ge \frac{R}{R/\gamma} \\
+%& = \gamma \; .
+%and similarly, for any $i \in \{1,2,\dots,K\} \setminus \{y_t\}$ we have
+%$\ip{w_i}{x_t} = 0$.

### 2019-01-16 ICML-submission/notions-of-linear-separability.tex
before editing sect. 5
thm 12 for randomized

@@
 result is that \textsc{Multiclass Perceptron} is essentially optimal in the
-sense that any deterministic algorithm must make $\left\lfloor (R/\gamma)^2
+sense that any deterministic algorithm must make $\frac 1 2 \left\lfloor (R/\gamma)^2
 \right \rfloor$ mistakes in the worst case.
-\chicheng{And any randomized algorithm must make $\left\lfloor (R/\gamma)^2
-\right \rfloor / 2$ mistakes?}
 For completeness, we state the
@@
 
-\chicheng{Shall we mention the multiclass margin notion that appeared in e.g.}
+\chicheng{Shall we mention that this multiclass margin notion has also appeared in e.g.~\cite{Crammer-Singer-2003}?}
 

### 2019-01-16 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Add reference to binary perceptron

@@
 
-%The algorithm is stated as
-% and
-%the mistake upper bound is stated as.
-
-The idea behind Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
- is to use $K$ copies of the \textsc{Binary
-Perceptron} algorithm,
-\chicheng{Shall we define the binary Perceptron algorithm?}
-where each copy corresponds to a class. At each timestep $t$, upon seeing
-example $x_t$,
-copy $i$ makes a binary prediction on whether $x_t$ belongs to
-class $i$ or not. If at least one copy makes a positive prediction, the
-algorithm chooses its prediction as one of the classes corresponding to a
-positive prediction. If all copies make negative predictions, the algorithms
-makes a prediction uniformly at random.
+The idea behind
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
+to use $K$ copies of the \textsc{Binary Perceptron} algorithm; see e.g.
+\citet[Section 3.3.1]{Shalev-Shwartz-2012}. Each copy corresponds to one of the
+classes. At each timestep $t$, upon seeing example $x_t$, copy $i$ makes a
+binary prediction on whether $x_t$ belongs to class $i$ or not. If at least one
+copy makes a positive prediction, the algorithm chooses its prediction as one of
+the classes corresponding to a positive prediction. If all copies make negative
+predictions, the algorithms makes a prediction uniformly at random.
 

### 2019-01-16 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Move proofs for strongly separable data to appendix

@@
 In this section, we present an algorithm for \textsc{Online Multiclass
-Classification with Bandit Feedback}, namely Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}.
-Under the assumption that the examples are strongly linearly separable
-with a margin (Definition~\ref{definition:strong-linear-separability}),
-we prove \autoref{theorem:strongly-separable-examples-mistake-upper-bound},
-which gives an upper bound on its number of mistakes.
+Classification with Bandit Feedback}, namely
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}.
+Under the assumption that the examples are strongly linearly separable with a
+margin, we give an upper bound on its number of mistakes. This is stated as
+\autoref{theorem:strongly-separable-examples-mistake-upper-bound} below. The
+proof of the theorem can be found in
+Appendix~\ref{section:proofs-for-stringly-separable-examples} in the
+supplementary material.
 
@@
 \end{enumerate}
-then the
-expected number of mistakes
+then the expected number of mistakes
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
@@
 
-%$\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
-%$A
-%= \sum_{t ~:~ S_t \neq \emptyset} z_t$
-%B = \sum_{t ~:~ S_t = \emptyset} z_t
-%\sum_{t ~:~ S_t = \emptyset}
-\begin{proof}
-Let $M = \sum_{t=1}^T z_t$ be the number of
-mistakes Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} makes.
-Let $A = \sum_{t=1}^T \one[S_t \neq \emptyset] z_t$ be the number of mistakes in the rounds
-when $S_t \neq \emptyset$, i.e. the number of rounds line~\ref{line:neg-update} is
-executed.
-In addition, let $B = \sum_{t=1}^T \one[S_t = \emptyset] z_t$ be the
-number of mistakes in the rounds when $S_t = \emptyset$.
-It can be easily seen that $M = A + B$.
-
-Let $C = \sum_{t=1}^T \one[S_t = \emptyset](1 - z_t)$ be the number of rounds
-line~\ref{line:pos-update} gets executed. Let
-$U = \sum_{t=1}^T (\one[S_t \neq \emptyset] z_t + \one[S_t = \emptyset](1 - z_t))$
-be the number of rounds line~\ref{line:pos-update} or~\ref{line:neg-update}
-gets executed. In other words, $U$ is the number of times the $K$-tuple of
-vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets updated. It can be
-easily seen that $U = A + C$.
-
-The key observation is that $\Exp[B] = (K-1) \Exp[C]$.
-To see this, note that if $S_t = \emptyset$, there is $1/K$ probability that the algorithm
-guesses the correct label ($z_t = 0$) and with probability $(K-1)/K$ algorithm's guess is
-incorrect ($z_t = 1$). Therefore,
-\[ \Exp[ z_t |S_t = \emptyset] = \frac{K-1}{K}, \]
-\[ \Exp[B] = \frac{K-1}{K} \Exp \sbr{ \sum_{t=1}^T \one[S_t = \emptyset] }, \]
-\[ \Exp[C] = \frac{1}{K} \Exp \sbr{ \sum_{t=1}^T \one[S_t = \emptyset] }. \]
-
-Putting all the information together, we get that
-\begin{align}
-\Exp[M]
-& = \Exp[A] + \Exp[B] \nonumber \\
-& = \Exp[A] + (K-1) \Exp[C] \nonumber \\
-& \le (K-1) \Exp[A + C] \nonumber\\
-& = (K-1) \Exp[U]  \; .
-\label{eqn:mistake-update}
-\end{align}
-
-To finish the proof, we need to upper bound the number of updates $U$. We claim
-that $U \le \lfloor 4(R/\gamma)^2 \rfloor$ with probability 1.
-The proof of this upper bound is
-similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
-algorithm. Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors that satisfy
-\eqref{equation:strong-linear-separability-1},
-\eqref{equation:strong-linear-separability-2} and
-\eqref{equation:strong-linear-separability-3}.
-The $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$
-changes only if there is an update in round $t$.
-We investigate how $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ and
-$\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$ change. If there is an update in round $t$,
-by lines~\ref{line:pos-update} and~\ref{line:neg-update}, we always have
-$ w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t $,
-and for all $i \neq \widehat y_t$, $w_{i}^{(t+1)} = w_{i}^{(t)}$.
-Therefore,
-\begingroup
-\allowdisplaybreaks
-\begin{align*}
-& \sum_{i=1}^K \norm{w_i^{(t+1)}}^2 \\
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t+1)}}^2 \\
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t}^2 \\
-& = \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 + \underbrace{(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t}}_{\le 0} \\
-& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 \\
-& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + R^2 \; .
-\end{align*}
-\endgroup
-The inequality that $(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t} \leq 0$ is from a case analysis: if line~\ref{line:pos-update} is executed, then $z_t = 0$ and $\ip{w_i^{(t)}}{x_t} \ge 0$; otherwise line~\ref{line:neg-update} is executed, in which case $z_t = 1$ and $\ip{w_i^{(t)}}{x_t} \le 0$.
-
-Hence, after $U$ updates,
-\begin{equation}
-\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
-\label{eqn:norm-ub}
-\end{equation}
-Similarly, if there is an update in round $t$, we have
-\begingroup
-\allowdisplaybreaks
-\begin{align*}
-& \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \\
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
-& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) \\
-& \qquad + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
-& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
-& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \frac \gamma 2,
-\end{align*}
-\endgroup
-where the last inequality follows from a case analysis on $z_t$ and
-Definition~\ref{definition:strong-linear-separability}: if $z_t = 0$, then
-$\widehat y_t = y_t$, by Equation~\eqref{equation:strong-linear-separability-2},
-we have that $\ip{w_{\widehat y_t}^*}{x_t} \geq \frac \gamma 2$; if $z_t = 1$,
-then $\widehat y_t \neq y_t$, by
-Equation~\eqref{equation:strong-linear-separability-3}, we have that
-$\ip{w_{\widehat y_t}^*}{x_t} \le -\frac \gamma 2$.
-
-Thus, after $U$ updates,
-\begin{equation}
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \frac {\gamma U} 2 \; .
-\label{eqn:norm-lb}
-\end{equation}
-Applying Cauchy-Schwartz's inequality twice, and using assumption
-\eqref{equation:strong-linear-separability-1}, we get that
-\begin{align*}
-\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
-& \le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}} \\
-& \le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \\
-& \le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
-\end{align*}
-Combining the above inequality with Equations~\eqref{eqn:norm-ub} and~\eqref{eqn:norm-lb}, we get
-$$
-\left(\frac{\gamma U}{2} \right)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
-$$
-We conclude that $U \le 4(R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor 4(R/\gamma)^2 \rfloor$.
-
-Applying Equation~\eqref{eqn:mistake-update}, we get
-$$
-\Exp[M] \leq (K-1) \Exp[U] \leq (K-1) \lfloor 4(R/\gamma)^2 \rfloor \; . \qedhere
-$$
-\end{proof}
-
 The upper bound $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$ on the expected number of
@@
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
-optimal upto constant factor, as long as the number of classes $K$ is
-at most $O((R/\gamma)^2)$. This is proved in
-\autoref{theorem:strongly-separable-examples-mistake-lower-bound} below.
+optimal upto a constant factor, as long as the number of classes $K$ is at most
+$O((R/\gamma)^2)$. This lower bound is stated as
+\autoref{theorem:strongly-separable-examples-mistake-lower-bound} below. The
+proof of the theorem can be foudn in
+Appendix~\ref{section:proofs-for-stringly-separable-examples} in the
+supplementary material.
 
@@
 
-\paragraph{Remark.} Irrespective of any conditions on $K$, $R$, and $\gamma$, a trivial lower bound
-on the expected number of mistakes of any randomized algorithm is
-$\frac{K-1}{2}$. To see this, note that the adversary can choose an example $(R e_1, y)$,
-where $y$ is a label chosen uniformly from $\cbr{1,2\ldots,K}$, and show this example $K-1$ times.
-The sequence of examples trivially satisfies the strong linear separability condition, and
-the $\frac{K-1}{2}$ expected mistake lower bound follows from Claim 2 of~\citet{Daniely-Helbertal-2013}.
-However, it is unclear if the trivial lower bound is the best possible if $K$ is large,
-i.e., $\omega((R/\gamma)^2)$. We leave this as an open problem.
-
-\begin{proof}
-We use probabilistic method. Let $M = \left\lfloor \frac{1}{4} (R/\gamma)^2
-\right\rfloor$. Let $V = \R^{M+1}$ equipped with the standard inner product.
-Let $e_1, e_2, \dots, e_{M+1}$ be the standard orthonormal basis of $V$. We
-define vectors $v_1, v_2, \dots, v_M \in V$ where $v_j = \frac{R}{\sqrt{2}}(e_j
-+ e_{M+1})$ for $j=1,2,\dots,M$. Let $\ell_1, \ell_2, \dots, \ell_M$ be chosen
-i.i.d. uniformly at random from $\{1,2,\dots,K\}$ and independently of any
-randomness used the by algorithm $\calA$. Let $T = M (K - 1)$. We define examples $(x_1,
-y_1), (x_2, y_2), \dots, (x_T, y_T)$ as follows. For any $j=1,2,\dots,M$ and any
-$h=1,2,\dots,K-1$,
-$$
-(x_{(j-1)(K-1) + h}, y_{(j-1)(K-1) + h}) = (v_j, \ell_j)
-$$
-
-With probability one, the norm of each example is exactly $R$.
-We show that with probability
-one, the examples are strongly separable with margin $\gamma$. To see
-that, consider $w_1^*, w_2^*, \dots, w_K^* \in V$ defined by
-$$
-w_i^* = \sqrt{2} \frac{\gamma}{R} \left( \sum_{j ~:~ \ell_j = i} e_j \right) - \frac{\sqrt{2}}2 \frac{\gamma}{R} e_{M+1}
-$$
-for $i=1,2,\dots,K$.
-
-for $i \in \{1,2,\dots,K\}$ and $j \in
-\{1,2,\dots,M\}$, we consider the inner product of $w_i^*$ and $v_j$.
-If $i = \ell_j$, $\ip{w_i^*}{v_j} = \gamma - \frac \gamma 2 = \frac \gamma 2$;
-otherwise $i \neq \ell_j$, in which case
-$\ip{w_i^*}{v_j} = 0 - \frac \gamma 2 = - \frac \gamma 2$.
-This means that $w_1^*, w_2^*, \dots, w_K^*$ satisfy
-conditions
-\eqref{equation:strong-linear-separability-2} and
-\eqref{equation:strong-linear-separability-3}. Condition \eqref{equation:strong-linear-separability-1}
-is satisfied since
-\begin{multline*}
-\sum_{i=1}^K \norm{w_i^*}^2
-= 2 \frac{\gamma^2}{R^2} \sum_{j=1}^M \norm{e_j}^2 +  \frac{\gamma^2}{2 R^2} K \norm{e_{M+1}}^2 \\
-= 2 \frac{\gamma^2}{R^2} M + \frac{\gamma^2}{2 R^2} K
-\le \frac{1}{2} + \frac{1}{2}
-= 1 \; .
-\end{multline*}
-
-It remains to lower bound the expected number of mistakes of $\calA$. For
-any $j \in \{1,2,\dots,M\}$, consider the expected number of mistakes the
-algorithm makes in rounds $(K-1)(j-1) + 1, (K-1)(j-1) + 2, \dots, (K-1)j$.
-
-Define a filtration $\cbr{\calB_j}_{j=0}^M$,
-where $\calB_j = \sigma((x_1, y_1, \hat{y}_1), \ldots, (x_{(K-1)j}, y_{(K-1)j}, \hat{y}_{(K-1)j}))$
-for every $j$ in $\{1,2,\dots,M\}$.
-By Claim 2 of~\citet{Daniely-Helbertal-2013}, as $\ell_j$
-is chosen uniformly from $\cbr{1,\dots,K}$ and independent of $\calB_{j-1}$ and $\calA$'s
-randomness,
-$$
-\Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t ~\Bigg|~ \calB_{j-1} } \geq \frac{K-1}2 \; .
-$$
-This implies that
-$$
-\Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t } \ge \frac{K-1}2 \; .
-$$
-Summing over all $j$ in $\{1,2,\dots,M\}$,
-$$
-\Exp \sbr{ \sum_{t=1}^{(K-1)M} z_t} \geq \frac{K-1}2 \cdot M = \frac{K-1}2 \left\lfloor \frac 1 4 (R/\gamma)^2 \right\rfloor \; .
-$$
-
-%In these rounds,
-%the algorithm is guessing the label $\ell_j$. Since $\ell_j$ is chosen uniformly
-%at random from the set $\{1,2,\dots,K\}$ and feedback is only binary, the
-%expected number of mistakes the algorithm makes in these rounds is at least
-%$\frac{K-1}{2}$. Altogether, the algorithm makes at least $\frac{K-1}{2} M$
-%mistakes in expectation.
-
-%\chicheng{I think this part need to be formalized, by directly using
-%~\cite{Daniely-Helbertal-2013}, Claim 2.}
-%Can we assume without loss of generality
-%that a deterministic prediction algorithm will have a smaller expected cost?
-%If so, define $F(k)$ be the number of mistake that will be made by the algorithm,
-%if the adversary commits to a label uniformly at random from $\cbr{1,2,\ldots,k}$,
-%and the guessing of the label lasts for $k$ rounds.
-%we can construct a recurrence of $F$: $F(k) = F(k-1) + \frac{k-1}{k}$, and $F(1) = 0$.
-%Therefore, $F(K) = \Omega(K)$.
-
-Finally, since strong separability and norm condition hold with probability one,
-there exists a particular (i.e. deterministic) sequence of examples for which
-the algorithm makes at least $\frac{K-1}2 \left\lfloor \frac 1 4 (R/\gamma)^2
-\right\rfloor$ mistakes in expectation over its internal randomization.
-\end{proof}
+\paragraph{Remark.} Irrespective of any conditions on $K$, $R$, and $\gamma$, a
+trivial lower bound on the expected number of mistakes of any randomized
+algorithm is $\frac{K-1}{2}$. To see this, note that the adversary can choose an
+example $(R e_1, y)$, where $y$ is a label chosen uniformly from
+$\cbr{1,2\ldots,K}$, and show this example $K-1$ times. The sequence of examples
+trivially satisfies the strong linear separability condition, and the
+$\frac{K-1}{2}$ expected mistake lower bound follows from Claim 2
+of~\citet{Daniely-Helbertal-2013}. However, it is unclear if the trivial lower
+bound is the best possible if $K$ is large, i.e., $\omega((R/\gamma)^2)$. We
+leave this as an open problem.
 
@@
 
-The following theorem is a direct consequence of Theorem~\ref{theorem:strongly-separable-examples-mistake-upper-bound}.
+The following theorem is a direct consequence of
+Theorem~\ref{theorem:strongly-separable-examples-mistake-upper-bound}.
 

### 2019-01-16 ICML-submission/appendix-proofs-for-strongly-separable-examples.tex
Move proofs for strongly separable data to appendix

\section{Proofs of Theorems~\ref{theorem:strongly-separable-examples-mistake-upper-bound} and \ref{theorem:strongly-separable-examples-mistake-lower-bound}}
\label{section:proofs-for-stringly-separable-examples}

%$\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
%$A
%= \sum_{t ~:~ S_t \neq \emptyset} z_t$
%B = \sum_{t ~:~ S_t = \emptyset} z_t
%\sum_{t ~:~ S_t = \emptyset}
\begin{proof}[Proof of \autoref{theorem:strongly-separable-examples-mistake-upper-bound}]
Let $M = \sum_{t=1}^T z_t$ be the number of
mistakes Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} makes.
Let $A = \sum_{t=1}^T \one[S_t \neq \emptyset] z_t$ be the number of mistakes in the rounds
when $S_t \neq \emptyset$, i.e. the number of rounds line~\ref{line:neg-update} is
executed.
In addition, let $B = \sum_{t=1}^T \one[S_t = \emptyset] z_t$ be the
number of mistakes in the rounds when $S_t = \emptyset$.
It can be easily seen that $M = A + B$.

Let $C = \sum_{t=1}^T \one[S_t = \emptyset](1 - z_t)$ be the number of rounds
line~\ref{line:pos-update} gets executed. Let
$U = \sum_{t=1}^T (\one[S_t \neq \emptyset] z_t + \one[S_t = \emptyset](1 - z_t))$
be the number of rounds line~\ref{line:pos-update} or~\ref{line:neg-update}
gets executed. In other words, $U$ is the number of times the $K$-tuple of
vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets updated. It can be
easily seen that $U = A + C$.

The key observation is that $\Exp[B] = (K-1) \Exp[C]$.
To see this, note that if $S_t = \emptyset$, there is $1/K$ probability that the algorithm
guesses the correct label ($z_t = 0$) and with probability $(K-1)/K$ algorithm's guess is
incorrect ($z_t = 1$). Therefore,
\[ \Exp[ z_t |S_t = \emptyset] = \frac{K-1}{K}, \]
\[ \Exp[B] = \frac{K-1}{K} \Exp \sbr{ \sum_{t=1}^T \one[S_t = \emptyset] }, \]
\[ \Exp[C] = \frac{1}{K} \Exp \sbr{ \sum_{t=1}^T \one[S_t = \emptyset] }. \]

Putting all the information together, we get that
\begin{align}
\Exp[M]
& = \Exp[A] + \Exp[B] \nonumber \\
& = \Exp[A] + (K-1) \Exp[C] \nonumber \\
& \le (K-1) \Exp[A + C] \nonumber\\
& = (K-1) \Exp[U]  \; .
\label{eqn:mistake-update}
\end{align}

To finish the proof, we need to upper bound the number of updates $U$. We claim
that $U \le \lfloor 4(R/\gamma)^2 \rfloor$ with probability 1.
The proof of this upper bound is
similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
algorithm. Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors that satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2} and
\eqref{equation:strong-linear-separability-3}.
The $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$
changes only if there is an update in round $t$.
We investigate how $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ and
$\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$ change. If there is an update in round $t$,
by lines~\ref{line:pos-update} and~\ref{line:neg-update}, we always have
$ w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t $,
and for all $i \neq \widehat y_t$, $w_{i}^{(t+1)} = w_{i}^{(t)}$.
Therefore,
\begingroup
\allowdisplaybreaks
\begin{align*}
& \sum_{i=1}^K \norm{w_i^{(t+1)}}^2 \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t+1)}}^2 \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t}^2 \\
& = \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 + \underbrace{(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t}}_{\le 0} \\
& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 \\
& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + R^2 \; .
\end{align*}
\endgroup
The inequality that $(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t} \leq 0$ is from a case analysis: if line~\ref{line:pos-update} is executed, then $z_t = 0$ and $\ip{w_i^{(t)}}{x_t} \ge 0$; otherwise line~\ref{line:neg-update} is executed, in which case $z_t = 1$ and $\ip{w_i^{(t)}}{x_t} \le 0$.

Hence, after $U$ updates,
\begin{equation}
\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
\label{eqn:norm-ub}
\end{equation}
Similarly, if there is an update in round $t$, we have
\begingroup
\allowdisplaybreaks
\begin{align*}
& \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) \\
& \qquad + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \frac \gamma 2,
\end{align*}
\endgroup
where the last inequality follows from a case analysis on $z_t$ and
Definition~\ref{definition:strong-linear-separability}: if $z_t = 0$, then
$\widehat y_t = y_t$, by Equation~\eqref{equation:strong-linear-separability-2},
we have that $\ip{w_{\widehat y_t}^*}{x_t} \geq \frac \gamma 2$; if $z_t = 1$,
then $\widehat y_t \neq y_t$, by
Equation~\eqref{equation:strong-linear-separability-3}, we have that
$\ip{w_{\widehat y_t}^*}{x_t} \le -\frac \gamma 2$.

Thus, after $U$ updates,
\begin{equation}
\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \frac {\gamma U} 2 \; .
\label{eqn:norm-lb}
\end{equation}
Applying Cauchy-Schwartz's inequality twice, and using assumption
\eqref{equation:strong-linear-separability-1}, we get that
\begin{align*}
\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
& \le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}} \\
& \le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \\
& \le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
\end{align*}
Combining the above inequality with Equations~\eqref{eqn:norm-ub} and~\eqref{eqn:norm-lb}, we get
$$
\left(\frac{\gamma U}{2} \right)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
$$
We conclude that $U \le 4(R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor 4(R/\gamma)^2 \rfloor$.

Applying Equation~\eqref{eqn:mistake-update}, we get
$$
\Exp[M] \leq (K-1) \Exp[U] \leq (K-1) \lfloor 4(R/\gamma)^2 \rfloor \; . \qedhere
$$
\end{proof}

\begin{proof}[Proof of \autoref{theorem:strongly-separable-examples-mistake-lower-bound}]
We use probabilistic method. Let $M = \left\lfloor \frac{1}{4} (R/\gamma)^2
\right\rfloor$. Let $V = \R^{M+1}$ equipped with the standard inner product.
Let $e_1, e_2, \dots, e_{M+1}$ be the standard orthonormal basis of $V$. We
define vectors $v_1, v_2, \dots, v_M \in V$ where $v_j = \frac{R}{\sqrt{2}}(e_j
+ e_{M+1})$ for $j=1,2,\dots,M$. Let $\ell_1, \ell_2, \dots, \ell_M$ be chosen
i.i.d. uniformly at random from $\{1,2,\dots,K\}$ and independently of any
randomness used the by algorithm $\calA$. Let $T = M (K - 1)$. We define examples $(x_1,
y_1), (x_2, y_2), \dots, (x_T, y_T)$ as follows. For any $j=1,2,\dots,M$ and any
$h=1,2,\dots,K-1$,
$$
(x_{(j-1)(K-1) + h}, y_{(j-1)(K-1) + h}) = (v_j, \ell_j)
$$

With probability one, the norm of each example is exactly $R$.
We show that with probability
one, the examples are strongly separable with margin $\gamma$. To see
that, consider $w_1^*, w_2^*, \dots, w_K^* \in V$ defined by
$$
w_i^* = \sqrt{2} \frac{\gamma}{R} \left( \sum_{j ~:~ \ell_j = i} e_j \right) - \frac{\sqrt{2}}2 \frac{\gamma}{R} e_{M+1}
$$
for $i=1,2,\dots,K$.

for $i \in \{1,2,\dots,K\}$ and $j \in
\{1,2,\dots,M\}$, we consider the inner product of $w_i^*$ and $v_j$.
If $i = \ell_j$, $\ip{w_i^*}{v_j} = \gamma - \frac \gamma 2 = \frac \gamma 2$;
otherwise $i \neq \ell_j$, in which case
$\ip{w_i^*}{v_j} = 0 - \frac \gamma 2 = - \frac \gamma 2$.
This means that $w_1^*, w_2^*, \dots, w_K^*$ satisfy
conditions
\eqref{equation:strong-linear-separability-2} and
\eqref{equation:strong-linear-separability-3}. Condition \eqref{equation:strong-linear-separability-1}
is satisfied since
\begin{multline*}
\sum_{i=1}^K \norm{w_i^*}^2
= 2 \frac{\gamma^2}{R^2} \sum_{j=1}^M \norm{e_j}^2 +  \frac{\gamma^2}{2 R^2} K \norm{e_{M+1}}^2 \\
= 2 \frac{\gamma^2}{R^2} M + \frac{\gamma^2}{2 R^2} K
\le \frac{1}{2} + \frac{1}{2}
= 1 \; .
\end{multline*}

It remains to lower bound the expected number of mistakes of $\calA$. For
any $j \in \{1,2,\dots,M\}$, consider the expected number of mistakes the
algorithm makes in rounds $(K-1)(j-1) + 1, (K-1)(j-1) + 2, \dots, (K-1)j$.

Define a filtration $\cbr{\calB_j}_{j=0}^M$,
where $\calB_j = \sigma((x_1, y_1, \hat{y}_1), \ldots, (x_{(K-1)j}, y_{(K-1)j}, \hat{y}_{(K-1)j}))$
for every $j$ in $\{1,2,\dots,M\}$.
By Claim 2 of~\citet{Daniely-Helbertal-2013}, as $\ell_j$
is chosen uniformly from $\cbr{1,\dots,K}$ and independent of $\calB_{j-1}$ and $\calA$'s
randomness,
$$
\Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t ~\Bigg|~ \calB_{j-1} } \geq \frac{K-1}2 \; .
$$
This implies that
$$
\Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t } \ge \frac{K-1}2 \; .
$$
Summing over all $j$ in $\{1,2,\dots,M\}$,
$$
\Exp \sbr{ \sum_{t=1}^{(K-1)M} z_t} \geq \frac{K-1}2 \cdot M = \frac{K-1}2 \left\lfloor \frac 1 4 (R/\gamma)^2 \right\rfloor \; .
$$

%In these rounds,
%the algorithm is guessing the label $\ell_j$. Since $\ell_j$ is chosen uniformly
%at random from the set $\{1,2,\dots,K\}$ and feedback is only binary, the
%expected number of mistakes the algorithm makes in these rounds is at least
%$\frac{K-1}{2}$. Altogether, the algorithm makes at least $\frac{K-1}{2} M$
%mistakes in expectation.

%\chicheng{I think this part need to be formalized, by directly using
%~\cite{Daniely-Helbertal-2013}, Claim 2.}
%Can we assume without loss of generality
%that a deterministic prediction algorithm will have a smaller expected cost?
%If so, define $F(k)$ be the number of mistake that will be made by the algorithm,
%if the adversary commits to a label uniformly at random from $\cbr{1,2,\ldots,k}$,
%and the guessing of the label lasts for $k$ rounds.
%we can construct a recurrence of $F$: $F(k) = F(k-1) + \frac{k-1}{k}$, and $F(1) = 0$.
%Therefore, $F(K) = \Omega(K)$.

Finally, since strong separability and norm condition hold with probability one,
there exists a particular (i.e. deterministic) sequence of examples for which
the algorithm makes at least $\frac{K-1}2 \left\lfloor \frac 1 4 (R/\gamma)^2
\right\rfloor$ mistakes in expectation over its internal randomization.
\end{proof}

### 2019-01-16 ICML-submission/introduction.tex
Fix introduction

@@
 are identical. However, they differ for multiclass classification with $K \ge 3$
-classes. For multiclass classification with $K$ classes, the standard notion of
-linear separability means that the examples from each class lie in an
-intersection of $K-1$ halfspaces and the examples outside of the class lie in
-the complement of the intersection of the halfspaces. Strong linear separability
-means that examples from each class are separated from the remaining examples by
-a \emph{single} hyperplane.
+classes. For multiclass classification with $K$ classes, weak linear
+separability means that the examples from each class lie in an intersection of
+$K-1$ halfspaces and the examples outside of the class lie in the complement of
+the intersection of the halfspaces. Strong linear separability means that
+examples from each class are separated from the remaining examples by a
+\emph{single} hyperplane.
 
@@
 Perceptron} is very satisfying, since it achieves an information-theoretically
-optimal mistake upper bound, while having low time and memory complexities.
-\footnote{These results are standard in the literature. For completeness, we
-present Theorems~\ref{theorem:mutliclass-perceptron-mistake-upper-bound}
-and~\ref{theorem:online-multiclass-classification-mistake-lower-bound}, along
-with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs}.}
+optimal mistake upper bound, while having low time and memory
+complexities.~\footnote{These results are standard in the literature. For
+completeness, we present these results along with their proofs in
+Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
+material.}
 
@@
 it is not known how to design an efficient algorithm with a finite mistake bound
-before our work. \footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
+before our work.~\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
 claimed that their Conservative OVA algorithm with PA-I update has a finite
@@
 that has an expected number of mistakes at most $(K-1) \lfloor 4(R/\gamma)^2
-\rfloor$. The algorithm can be viewed as running $K$ copies of the
-\textsc{Binary Perceptron} algorithm, one copy for each class. Intuitively
-speaking, the $O(K)$ multiplicative factor is the price we pay for the bandit
-feedback, or more precisely, the lack of full-information feedback. We also
-prove that any (possibly randomized) algorithm makes $\Omega(K (R/\gamma)^2))$
+\rfloor$. The memory complexity and per-round time complexity are both $O(dK)$.
+The algorithm can be viewed as running $K$ copies of the \textsc{Binary
+Perceptron} algorithm, one copy for each class. Intuitively speaking, the $O(K)$
+multiplicative factor in the mistake bound is the price we pay for the bandit
+feedback, or more precisely, the lack of full-information feedback. We prove
+that any (possibly randomized) algorithm must make $\Omega(K (R/\gamma)^2))$
 mistakes in the worst case.
 
-For the case when examples are weakly linearly separable, we construct a feature
-mapping $\phi$ that makes them \emph{strongly} linearly separable. We then use
-the kernelized version of the algorithm, namely
-Algorithm~\ref{algorithm:kernelized}, for the strongly separable case; for more
-details on kernel methods see e.g.~\citet{Scholkopf-Smola-2002} and
-\citet{Shawe-Taylor-Cristianini-2004}. The kernel $k(x,x')$ corresponding to the
-feature mapping $\phi$ has a simple explicit formula and can be computed in
-$O(d)$ time.
+For the case when examples are weakly linearly separable, we construct a
+non-linear feature mapping $\phi$ and associated positive definite kernel
+$k(x,x')$ that makes the examples \emph{strongly} linearly separable. We then
+use the kernelized version of the algorithm for the strongly separable case,
+Algorithm~\ref{algorithm:kernelized}. (For details on kernel methods see
+e.g.~\citet{Scholkopf-Smola-2002} or \citet{Shawe-Taylor-Cristianini-2004}.)
+The kernel $k(x,x')$ corresponding to the feature mapping $\phi$ has a simple
+explicit formula and can be computed in $O(d)$ time.
 
 The number of mistakes of the kernelized algorithm depends on the margin in the
-corresponding feature space. We analyze how the margin parameter of weak
-separability in the original space $\R^d$ gets transformed into a margin
+corresponding feature space. We analyze how the mapping $\phi$ transforms the
+margin parameter of weak separability in the original space $\R^d$ into a margin
 parameter of strong separability in the new feature space. This problem is

### 2019-01-16 ICML-submission/related-work.tex
thm 12 for randomized
Fix related work section

@@
 The problem of online bandit multiclass learning was initially formulated in the
-pioneering work of~\citet{Auer-Long-1999}, under the name of ``weak reinforcement
-model''. They showed that if all examples shown agrees with some
-classifier in a prespecified hypothesis class $\calH$, then the optimal mistake
-bound in the bandit setting can be upper bounded by the optimal mistake bound in
-the full information setting, times a factor of $(2.01 + o(1))K \ln K$.
-\citet{Long-2017} later improved the factor to $(1 + o(1)) K \ln K$ and showed its
- near-optimality.
-\citet{Daniely-Helbertal-2013} extended the results to the setting where the
-performance of the algorithm is measured by its regret, i.e. the difference
-between the number of mistakes made by the algorithm and the number of mistakes
-made by the best classifier in $\calH$ in hindsight. However, all algorithms
-developed in this context are computationally inefficient.
+pioneering work of~\citet{Auer-Long-1999}, under the name of ``weak
+reinforcement model''. They showed that if all examples agree with some
+classifier from a prespecified hypothesis class $\calH$, then the optimal
+mistake bound in the bandit setting can be upper bounded by the optimal mistake
+bound in the full information setting, times a factor of $(2.01 + o(1))K \ln K$.
+\citet{Long-2017} later improved the factor to $(1 + o(1)) K \ln K$ and showed
+its near-optimality. \citet{Daniely-Helbertal-2013} extended the results to the
+setting where the performance of the algorithm is measured by its regret, i.e.
+the difference between the number of mistakes made by the algorithm and the
+number of mistakes made by the best classifier in $\calH$ in hindsight. However,
+all algorithms developed in this context are computationally inefficient.
 
@@
 with a mistake bound of $O(K^2 d \ln(\frac{d}{\gamma}))$, the other with a
-mistake bound of $\widetilde{O}(\frac{K^2}{\gamma^2} \ln T)$.
-The latter result was later improved by \citet{Daniely-Helbertal-2013},
-which gives a computationally inefficient algorithm with a mistake
-upper bound of $\widetilde{O}(\frac{K}{\gamma^2})$.
-In addition, the
-authors propose the \textsc{Banditron} algorithm, a computationally efficient
-algorithm that has a $O(T^{2/3})$ regret against the multiclass hinge loss in
-the general setting, and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weak
-linearly separable setting. The polynomial dependence of \textsc{Banditron}'s
-mistake bound on the time horizon is undesirable for problems with a long time
-horizon. One key open question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}
-is whether one can design computationally efficient algorithms that achieve
-mistake bounds that match or improve over those of inefficient algorithms. In
-this paper, we take a step towards answering this question, showing that
-efficient algorithms with mistake bounds quasipolynomial in $\frac 1 \gamma$
-or quasipolynomial in $K$ can be obtained.
+mistake bound of $\widetilde{O}(\frac{K^2}{\gamma^2} \ln T)$. The latter result
+was later improved by \citet{Daniely-Helbertal-2013}, which gives a
+computationally inefficient algorithm with a mistake upper bound of
+$\widetilde{O}(\frac{K}{\gamma^2})$. In addition, the authors propose the
+\textsc{Banditron} algorithm, a computationally efficient algorithm that has a
+$O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
+and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weak linearly separable
+setting. The polynomial dependence of \textsc{Banditron}'s mistake bound on the
+time horizon is undesirable for problems with a long time horizon. One key open
+question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
+design computationally efficient algorithms that achieve mistake bounds that
+match or improve over those of inefficient algorithms. In this paper, we take a
+step towards answering this question, showing that efficient algorithms with
+mistake bounds quasipolynomial in $\frac 1 \gamma$ or quasipolynomial in $K$ can
+be obtained.
 
@@
 %positive answer. $O(k^2 d \ln(\frac{d}{\gamma^2}))$
-\chicheng{I significantly shortened the discussions of all those $\sqrt{T}$
-regret algorithms here, as I think they are not very relevant.}
 
@@
 where the data is not necessarily separable by some linear
-classifier~\cite{Abernethy-Rakhlin-2009,
-Wang-Jin-Valizadegan-2010,
-Crammer-Gentile-2013,
-Hazan-Kale-2011, Beygelzimer-Orabona-Zhang-2017,
-Foster-Kale-Luo-Mohri-Sridharan-2018}.
-In addition, \citet{Chen-Lin-Lu-2014, Zhang-Jung-Tewari-2018} study online bandit
-multiclass boosting under bandit feedback, where one can view boosting as
-linear classification by treating each base hypothesis as a separate
-feature.
-However, most of these works achieve a regret bound of order $\widetilde{O}(\sqrt{T})$
-to $O(T^{3/4})$. In the weakly separable setting, these algorithms
-only guarantees a mistake upper bound of $\widetilde{O}(\sqrt{T})$, which is
-undesirable for problems with a long time horizon.
-One exception is the \textsc{Newtron} algorithm, where with appropriate
+classifier~\cite{Abernethy-Rakhlin-2009, Wang-Jin-Valizadegan-2010,
+Crammer-Gentile-2013, Hazan-Kale-2011, Beygelzimer-Orabona-Zhang-2017,
+Foster-Kale-Luo-Mohri-Sridharan-2018}. In addition, \citet{Chen-Lin-Lu-2014,
+Zhang-Jung-Tewari-2018} study online bandit multiclass boosting under bandit
+feedback, where one can view boosting as linear classification by treating each
+base hypothesis as a separate feature. However, most of these works achieve a
+regret bound of order $\widetilde{O}(\sqrt{T})$ to $O(T^{3/4})$. In the weakly
+separable setting, these algorithms only guarantees a mistake upper bound of
+$\widetilde{O}(\sqrt{T})$, which is undesirable for problems with a long time
+horizon. One exception is the \textsc{Newtron} algorithm, where with appropriate
 settings of parameter $\alpha$, it is able to achieve a $O(\ln T)$ regret.
-However, as argued
-in ~\citep[][Appendix D]{Beygelzimer-Orabona-Zhang-2017}, if the setting of $\alpha$
-makes the regret bound $O(\sqrt{T})$, the logistic loss of the best linear
-predictor would be $\Omega(T^{3/4})$. Therefore, \textsc{Newtron} is still only
-able to guarantee a mistake upper bound of $O(\sqrt{T})$ in the weakly separable setting.
+However, as argued in ~\citep[][Appendix D]{Beygelzimer-Orabona-Zhang-2017}, if
+the setting of $\alpha$ makes the regret bound $O(\sqrt{T})$, the logistic loss
+of the best linear predictor would be $\Omega(T^{3/4})$. Therefore,
+\textsc{Newtron} is still only able to guarantee a mistake upper bound of
+$O(\sqrt{T})$ in the weakly separable setting.
 
-%\citet{Abernethy-Rakhlin-2009} poses the open problem of
-%whether one can design an efficient algorithm to get a $O(\sqrt{T})$ regret
-%against some reasonable loss functions. \citet{Crammer-Gentile-2013} show that
-%such an algorithm can be obtained, provided that the distribution of the label
-%$y_t$ conditioned on feature vector $x_t$ satisfies certain parametric noise
-%assumption. \citet{Hazan-Kale-2011} developed the \textsc{Newtron} algorithm,
-%which has a regret between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass
-%logistic loss, where the exact order of the regret depends on the diameter of
-%the benchmark class. In particular, if the diameter is $O(\ln T)$, its regret
-%bound would become $O(T^{2/3})$. The \textsc{SOBA} algorithm by
+%\citet{Abernethy-Rakhlin-2009} poses the open problem of whether one can design
+%an efficient algorithm to get a $O(\sqrt{T})$ regret against some reasonable
+%loss functions. \citet{Crammer-Gentile-2013} show that such an algorithm can be
+%obtained, provided that the distribution of the label $y_t$ conditioned on
+%feature vector $x_t$ satisfies certain parametric noise assumption.
+%\citet{Hazan-Kale-2011} developed the \textsc{Newtron} algorithm, which has a
+%regret between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass logistic
+%loss, where the exact order of the regret depends on the diameter of the
+%benchmark class. In particular, if the diameter is $O(\ln T)$, its regret bound
+%would become $O(T^{2/3})$. The \textsc{SOBA} algorithm by
 %\citet{Beygelzimer-Orabona-Zhang-2017} achieves a regret of
@@
 
-%\citet{Chen-Lin-Lu-2014}'s online weak learning condition implies that
-%the set of examples is strongly separable by a convex combination of base
-%hypotheses with a margin. Under this condition, it gives an algorithm with a
-%$O(T^{3/4})$ mistake bound. \citet{Zhang-Jung-Tewari-2018} considers an online
-%weak learning condition, which implies that all examples is separable by a
-%convex combination of base hypotheses with a margin; see~\citet[Theorem
-%3]{Mukherjee-Schapire-2013}. Under this condition, it gives a boosting algorithm
-%with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge parameter. In
-%addition, it gives an adaptive algorithm with a $O(T^{3/4})$ mistake bound.
+%\citet{Chen-Lin-Lu-2014}'s online weak learning condition implies that the set
+%of examples is strongly separable by a convex combination of base hypotheses
+%with a margin. Under this condition, it gives an algorithm with a $O(T^{3/4})$
+%mistake bound. \citet{Zhang-Jung-Tewari-2018} considers an online weak learning
+%condition, which implies that all examples is separable by a convex combination
+%of base hypotheses with a margin; see~\citet[Theorem
+%3]{Mukherjee-Schapire-2013}. Under this condition, it gives a boosting
+%algorithm with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge
+%parameter. In addition, it gives an adaptive algorithm with a $O(T^{3/4})$
+%mistake bound.
 
-%Online bandit multiclass learning is a special case of the contextual
-%bandits problem~\citep{Auer-2003, Langford-Zhang-2008}, where the cost is the
-%classification error. A series of works in the contextual bandits
-%literature focuses on oracle-efficiency, that is, they assume access to an
-%oracle that given a set of cost-sensitve learning examples, generates .
+%Online bandit multiclass learning is a special case of the contextual bandits
+%problem~\citep{Auer-2003, Langford-Zhang-2008}, where the cost is the
+%classification error. A series of works in the contextual bandits literature
+%focuses on oracle-efficiency, that is, they assume access to an oracle that
+%given a set of cost-sensitve learning examples, generates .
 
@@
 with an associated cost vector $c_t$ hidden. The learner then takes an action
-$\widehat{y}_t$, and observes the incurred cost $c_t(\widehat{y}_t)$.
-The goal of the learner is to minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{\pi \in \Pi}
-\sum_{t=1}^T c_t(\pi(x_t))$. The online bandit multiclass learning problem is a
-special case of the contextual bandits problem, where the cost $c_t(i)$ is the
-classification error $\indicator{i \neq y_t}$, and the policy class $\Pi$ is the set of
-linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$. A
-series of works in the contextual bandits learning literature focus on
+$\widehat{y}_t$, and observes the incurred cost $c_t(\widehat{y}_t)$. The goal
+of the learner is to minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) -
+\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$. The online bandit multiclass
+learning problem is a special case of the contextual bandits problem, where the
+cost $c_t(i)$ is the classification error $\indicator{i \neq y_t}$, and the
+policy class $\Pi$ is the set of linear classifiers $\cbr{x \mapsto \argmax_y
+(Wx)_y: W \in \R^{k \times d}}$. A series of works in the contextual bandits
+learning literature focus on
 oracle-efficiency~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
@@
 Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. Specifically, they assume access to
-a policy optimization oracle that can return the policy in $\Pi$ that minimizes its
-empirical cost on any set of cost-sensitive examples, and the algorithm only calls the oracle a
-polynomial number of times. However, these algorithms are not truly
-computationally efficient in our setting, as it is NP-hard in general to find a
-linear classifier that minimizes the empirical cost over a set of
+a policy optimization oracle that can return the policy in $\Pi$ that minimizes
+its empirical cost on any set of cost-sensitive examples, and the algorithm only
+calls the oracle a polynomial number of times. However, these algorithms are not
+truly computationally efficient in our setting, as it is NP-hard in general to
+find a linear classifier that minimizes the empirical cost over a set of
 examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.
 
-%that receives a set of cost-sensitive learning
-%examples and policy class $\Pi$,
+%that receives a set of cost-sensitive learning examples and policy class $\Pi$,
 %as algorithms generate cost-sensitive examples that may not be linearly
@@
 contextual bandits with surrogate losses, focusing on regrets of the form
-$\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{f \in \calF} \sum_{t=1}^T \frac{1}{K} \sum_{i=1}^K c_t(i) \phi( f_i(x_t)
-)$, where $\calF$ contains score functions $f$ such that $\sum_{i=1}^K
-f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac s \gamma, 0)$ or $\min(1,
-\max(1 - \frac s \gamma, 0))$. On one hand, it gives information-theoretic
-mistake upper bounds under various settings of $\calF$, including parametric and
-nonparametric classes. On the other hand, it gives an efficient algorithm that
-has a $O(\sqrt{T})$ regret against the benchmark of $\calF = \cbr{x \mapsto W x:
-W \in \R^{k \times d}, \one^T W = 0}$. A direct application of this result to
-online bandit multiclass linear classification yields an algorithm with a
-$O(\sqrt{T})$ mistake bound in the strongly linearly separable setting.
+$\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{f \in \calF} \sum_{t=1}^T \frac{1}{K}
+\sum_{i=1}^K c_t(i) \phi( f_i(x_t) )$, where $\calF$ contains score functions
+$f$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac
+s \gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
+information-theoretic mistake upper bounds under various settings of $\calF$,
+including parametric and nonparametric classes. On the other hand, it gives an
+efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of
+$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$. A direct
+application of this result to \textsc{Online Bandit Multiclass Linear
+Classification} yields an algorithm with a $O(\sqrt{T})$ mistake bound in the
+strongly linearly separable setting.
 

### 2019-01-16 ICML-submission/notions-of-linear-separability.tex
Fix section 3

@@
 integer, and $\gamma$ be a positive real number. Let $L = ((x_1, y_1), (x_2,
-y_2), \dots, (x_T, y_T))$ be a set of labeled examples in $V \times \{1,2,\dots,K\}$.
-\chicheng{This $L$ notion may be a bit confusing - feel free to edit}
+y_2), \dots, (x_T, y_T))$ be a sequence of labeled examples in $V \times
+\{1,2,\dots,K\}$.
 
-$L$ is said to be \emph{weakly linearly separable with a
-margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
-that
+$L$ is said to be \emph{weakly linearly separable with a margin $\gamma$} if
+there exist vectors $w_1, w_2, \dots, w_K \in V$ such that
 \begin{align}
@@
 integer, and $\gamma$ be a positive real number. Let $L = ((x_1, y_1), (x_2,
-y_2), \dots, (x_T, y_T))$ be labeled examples in $V \times \{1,2,\dots,K\}$.
+y_2), \dots, (x_T, y_T))$ be a sequence of labeled examples in $V \times
+\{1,2,\dots,K\}$.
 
@@
 result is that \textsc{Multiclass Perceptron} is essentially optimal in the
-sense that any deterministic algorithm must make $\frac 1 2 \left\lfloor (R/\gamma)^2
-\right \rfloor$ mistakes in the worst case.
-For completeness, we state the
-\textsc{Multiclass Perceptron} algorithm and give proofs of both of these
-results in Appendix~\ref{section:multiclass-perceptron-proofs}.
+sense that any (possibly randomized) algorithm must make $\frac{1}{2}
+\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
+completeness, we state the \textsc{Multiclass Perceptron} algorithm and give
+proofs of both of these results in
+Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
+material.
 
@@
 The notion of strong linear separability has appeared in the literature; see
-e.g.~\citet{Chen-Chen-Zhang-Chen-Zhang-2009}.
-Intuitively, strong linear
+e.g.~\citet{Chen-Chen-Zhang-Chen-Zhang-2009}. Intuitively, strong linear
 separability means that, for each class $i$, the set of examples belonging to
 class $i$ and the set of examples belonging to the remaining $K-1$ classes are
-separated by a linear classifier $w_i$ by a margin $\frac \gamma 2$.
+separated by a linear classifier $w_i$ with margin $\frac{\gamma}{2}$.
 
-It is easy to see that if a set of labeled examples are strongly linearly
+It is easy to see that if a sequence of labeled examples is strongly linearly
 separable with margin $\gamma$, then it is also weakly linearly separable with
-the same margin. Indeed, if $w_1, w_2, \dots, w_K \in V$
-satisfy \eqref{equation:strong-linear-separability-1},
+the same margin. Indeed, if $w_1, w_2, \dots, w_K \in V$ satisfy
+\eqref{equation:strong-linear-separability-1},
 \eqref{equation:strong-linear-separability-2},
@@
 
-In the special case of $K=2$, if a set of labeled examples are weakly linearly
-separable with a margin $\gamma$, then it is also strongly linearly separable with
-the same margin. Indeed, if $w_1, w_2$ satisfy
+In the special case of $K=2$, if a sequence of labeled examples is weakly
+linearly separable with a margin $\gamma$, then it is also strongly linearly
+separable with the same margin. Indeed, if $w_1, w_2$ satisfy
 \eqref{equation:weak-linear-separability-1} and
@@
 \frac{1}{2}\norm{w_1}^2 + \frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
-Equations~\eqref{equation:strong-linear-separability-2} and~\eqref{equation:strong-linear-separability-3} follow from the fact that $w_1' - w_2' = w_1 - w_2$.
+Equations~\eqref{equation:strong-linear-separability-2}
+and~\eqref{equation:strong-linear-separability-3} follow from the fact that
+$w_1' - w_2' = w_1 - w_2$.
 
@@
 $\gamma$, they are \emph{not} strongly linearly separable with any positive
-margin $\gamma$. For instance, there do not exist linear separators that
-separates the examples belonging to the gray class from the examples belonging
-to the remaining two classes.
+margin $\gamma$. For instance, there does \emph{not} exist a linear separator
+that separates the examples belonging to the gray class from the examples
+belonging to the remaining two classes.
 }

### 2019-01-16 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Fix section 4

@@
 
-In this section, we present an algorithm for \textsc{Online Multiclass
-Classification with Bandit Feedback}, namely
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}.
-Under the assumption that the examples are strongly linearly separable with a
-margin, we give an upper bound on its number of mistakes. This is stated as
+In this section, we consider the case when the examples are strongly linearly
+separable. We present an algorithm for this setting
+(Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
+and we give an upper bound on its number of mistakes, stated as
 \autoref{theorem:strongly-separable-examples-mistake-upper-bound} below. The
@@
 \autoref{theorem:strongly-separable-examples-mistake-lower-bound} below. The
-proof of the theorem can be foudn in
+proof of the theorem can be found in
 Appendix~\ref{section:proofs-for-stringly-separable-examples} in the
@@
 example $(R e_1, y)$, where $y$ is a label chosen uniformly from
-$\cbr{1,2\ldots,K}$, and show this example $K-1$ times. The sequence of examples
+$\cbr{1,2,\dots,K}$, and show this example $K$ times. The sequence of examples
 trivially satisfies the strong linear separability condition, and the
@@
 be extended to nonlinear classification using
-kernels~\cite{Scholkopf-Smola-2002, Shawe-Taylor-Cristianini-2004}. For each
-class, as opposed to explicitly maintaining the predictor's weights for each
-class, we maintain the set of examples whose scaled feature transformations are
-added to the weights in Perceptron updates. We give a formal description of the
-kernelized algorithm in Algorithm~\ref{algorithm:kernelized}.
-
-The following theorem is a direct consequence of
-Theorem~\ref{theorem:strongly-separable-examples-mistake-upper-bound}.
+kernels~\cite{Scholkopf-Smola-2002, Shawe-Taylor-Cristianini-2004}. The formal
+description of the kernelized algorithm is given in
+Algorithm~\ref{algorithm:kernelized}. As opposed to explicitly maintaining the
+weight vector for each class, the algorithm maintains the set of example-scalar
+pairs corresponding to the updates of the non-kernelized algorithm. As a direct
+consequence of
+Theorem~\ref{theorem:strongly-separable-examples-mistake-upper-bound} we get a
+mistake bound for the kernelized algorithm.
 
@@
 \label{theorem:kernelized-upper-bound}
-Let $k(\cdot, \cdot)$ be a kernel function with feature map $\phi$, $K$ be a positive
-integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
-$L = ((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples in
-$V \times \{1,2,\dots,K\}$ such that:
+Let $k(\cdot, \cdot)$ be a positive definite kernel function and let
+$\phi(\cdot)$ be the associated feature map. Let $K$ be a positive integer,
+$\gamma$ be a positive real number, $R$ be a non-negative real number. If $L =
+((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples
+such that:
 \begin{enumerate}
@@
 \end{enumerate}
-then the
-expected number of mistakes
-Algorithm~\ref{algorithm:kernelized}
-makes is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
+then the expected number of mistakes Algorithm~\ref{algorithm:kernelized} makes
+is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
 \end{theorem}

### 2019-01-16 ICML-submission/from-weak-separability-to-strong-separability.tex
Fix beginning of section 5

@@
 
-In this section, we case when the sequence of examples shown by the adversary is
-weakly linearly separable
-(Definition~\ref{definition:weak-linear-separability}). Throughout this section,
-we assume without loss of generality that all examples lie in the unit ball
-$\B(0,1) \subseteq \R^d$.\footnote{Consider the following preprocessing step:
-upon seeing every example $x_t$, we define $\hat{x}_t = \frac{x_t}{\norm{x_t}}$
-as its normalization. It can be easily checked that if $(x_1,y_1), \dots,
-(x_T,y_T)$ is weakly linearly separable by margin $\gamma$ and $\norm{x_t} \le
-\R$ for all $t$, then the set of normalized examples $(\hat{x}_1,y_1), \dots,
-(\hat{x}_T,y_T)$ is weakly linearly separable by margin $\gamma/R$.} Note that
+In this section, we consider case when the examples are weakly linearly
+separable. Throughout this section, we assume without loss of generality that
+all examples lie in the unit ball $\B(0,1) \subseteq \R^d$.\footnote{Instead of
+working with feature vector $x_t$ we can work with normalized feature vectors
+$\widehat{x}_t = \frac{x_t}{\norm{x_t}}$. It can be easily checked that if
+$(x_1,y_1), (x_2,y_2), \dots, (x_T,y_T)$ are weakly linearly separable with
+margin $\gamma$ and $\norm{x_t} \le R$ for all $t$, then the normalized examples
+$(\widehat{x}_1,y_1), \widehat{x}_2,y_2), \dots, (\widehat{x}_T,y_T)$ are weakly
+linearly separable by margin $\gamma/R$.} Note that
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
@@
 
-We consider a kernel function $k(\cdot, \cdot)$ whose corresponding feature map
-$\phi(\cdot)$ transforms any sequence of \emph{weakly} linearly separable
-examples to \emph{strongly} linearly separable sequence of examples.
-Specifically, $\phi$ has the property that if a set of labeled examples in
-$B(0,1)$ is weakly linearly separable with a margin $\gamma$, then after
-applying $\phi$ the examples become strongly linearly separable with a margin
-$\gamma'$ and their norms are bounded by $2$. The parameter $\gamma'$ is a
-function of the old margin $\gamma$ and the number of classes $K$, and is
+We construct a positive definite kernel function $k(\cdot, \cdot)$ whose
+corresponding feature map $\phi(\cdot)$ transforms any sequence of \emph{weakly}
+linearly separable examples to \emph{strongly} linearly separable sequence of
+examples. Specifically, $\phi$ has the property that if a set of labeled
+examples in $\B(0,1)$ is weakly linearly separable with a margin $\gamma$, then
+after applying $\phi$ the examples become strongly linearly separable with a
+margin $\gamma'$ and their norms are bounded by $2$. The parameter $\gamma'$ is
+a function of the old margin $\gamma$ and the number of classes $K$, and is
 specified in \autoref{theorem:margin-transformation} below.
@@
 The last equality together with the formula for $k$ implies that $k(x,x) <
-+\infty$ for any $x$ in $\B(0,1)$.
++\infty$ for any $x$ in $\B(0,1)$ and thus in particular implies that $\phi(x)$
+indeed lies in $\ell_2$.
 
@@
 separable with margin $\gamma > 0$. Let $\phi$ be as defined in
-Equation~\eqref{equation:phi}, and
+equation~\eqref{equation:phi} and let
 \begingroup
@@
 \endgroup
-Then, the set of labeled examples transformed by $\phi$,
+Then, the sequence of labeled examples transformed by $\phi$,
 namely $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots,
@@
 Algorithm~\ref{algorithm:kernelized} with kernel function $k(x,x') =
-\ip{\phi(x)}{\phi(x')}_{\ell_2}$. This is done by simply invoking
-\autoref{theorem:kernelized-upper-bound} with the modified margin $\gamma'$ from
-\autoref{theorem:margin-transformation}. The mistake bound is stated as
-\autoref{corollary:weakly-separable-examples-mistake-upper-bound} below.
+\ip{\phi(x)}{\phi(x')}_{\ell_2}$.
 
@@
 \label{corollary:weakly-separable-examples-mistake-upper-bound}
-Let $K$ be a positive integer and let $\gamma$ be a positive real number. If $L
-= ((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples
-in $V \times \{1,2,\dots,K\}$ such that
-\begin{enumerate}
-\item $L$ is weakly linearly separable with margin $\gamma$,
-\item for all $t$ in $\cbr{1,2,\dots,T}$, $\norm{x_t} \le 1$,
-\end{enumerate}
-then the expected number of mistakes Algorithm~\ref{algorithm:kernelized} makes
+Let $K$ be a positive integer and let $\gamma$ be a positive real number. If
+$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \B(0,1) \times \{1,2,\dots,K\}$
+is a sequence of weakly separable labeled examples with margin $\gamma > 0$,
+then the expected number of mistakes made by Algorithm~\ref{algorithm:kernelized}
+with kernel $k(x,x') = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}_{\R^d}}$
 is at most $2^{\widetilde{O}(\min(K \log^2 \frac{1}{\gamma},
@@
 \end{corollary}
+
+This corollary follows direcly from
+Theorems~\ref{theorem:kernelized-upper-bound}
+and~\ref{theorem:margin-transformation}.
 

### 2019-01-16 arxiv-version/np-hardness-of-the-weak-labeling-problem.tex
add np-hardness proof

@@
 
-Formally, the input to the decision problem are positive integers $d, T, K$ and
-a sequence $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \{0,1\}^d \times
-\{1,2,\dots,K, \overline{1}, \overline{2}, \dots, \overline{K}\}$ of strongly
-and weakly labeled examples. The numbers $1,2,\dots,K$ correspond to strong
-labels and the symbols $\overline{1}, \overline{2}, \dots, \overline{K}$
-correspond to weak labels. We adopt the convention that $\overline{\overline{i}}
-= i$ for any positive integer $i$. The goal is to determine whether or not there
-exist vectors $w_1, w_2, \dots, w_K \in \R^d$ that satisfy the following
-conditions for all $t=1,2,\dots,T$,
+Formally, the weak labeling problem can be described as below: 
+\begin{figure}[H]
+\begin{framed}
+\begin{center}
+    \textbf{Weak Labeling}
+\end{center}
+\textbf{Given: } A set of feature-label pairs: $\{(x_t, y_t)\}_{t=1}^T \subseteq \{0,1\}^d \times \{1,2,\ldots, K, \overline{1}, \overline{2}, \ldots, \overline{K}\}$. \\
+\textbf{Question: } Do there exist $ w_1, \ldots, w_K \in \R^d$ such that for all $t=1, \ldots, T$,  
 \begin{align*}
-y_t \in \{1,2,\dots,K\} \qquad & \Longrightarrow \qquad & \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \qquad \ip{w_{y_t}}{x_t} & > \ip{w_i}{x_t} \; , \\
-y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \qquad & \Longrightarrow & \qquad \exists i \in \{1,2,\dots,K\} \qquad \ip{w_i}{x_t} & > \ip{w_{\overline{y_t}}}{x_t} \; .
+y_t \in \{1,2,\dots,K\} \qquad & \Longrightarrow \qquad & \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \qquad & \ip{w_{y_t}}{x_t}  > \ip{w_i}{x_t} \; , \\
+y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \qquad & \Longrightarrow & \qquad \exists i \in \{1,2,\dots,K\} \qquad & \ip{w_i}{x_t} > \ip{w_{\overline{y_t}}}{x_t} \; .
+\end{align*}
+\end{framed}
+\end{figure}
+
+%Formally, the input to the decision problem are positive integers $d, T, K$ and
+%a sequence $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \{0,1\}^d \times
+%\{1,2,\dots,K, \overline{1}, \overline{2}, \dots, \overline{K}\}$ of strongly
+%and weakly labeled examples. The numbers $1,2,\dots,K$ correspond to strong
+%labels and the symbols $\overline{1}, \overline{2}, \dots, \overline{K}$
+%correspond to weak labels. We adopt the convention that $\overline{\overline{i}}
+%= i$ for any positive integer $i$. The goal is to determine whether or not there
+%exist vectors $w_1, w_2, \dots, w_K \in \R^d$ that satisfy the following
+%conditions for all $t=1,2,\dots,T$,
+%\begin{align*}
+%y_t \in \{1,2,\dots,K\} \qquad & \Longrightarrow \qquad & \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \qquad \ip{w_{y_t}}{x_t} & > \ip{w_i}{x_t} \; , \\
+%y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \qquad & \Longrightarrow & \qquad \exists i \in \{1,2,\dots,K\} \qquad \ip{w_i}{x_t} & > \ip{w_{\overline{y_t}}}{x_t} \; .
+%\end{align*}
+
+The hardness proof is based on a reduction from the set splitting problem, which is proven to be NP-complete by Lovasz \chenyu{Reference needed}, to our weak labeling problem.
+The reduction is adapted from Avrim Blum \chenyu{Reference needed}.
+\begin{figure}[h]
+\begin{framed}
+\begin{center}
+    \textbf{Set Splitting}
+\end{center}
+\textbf{Given: } A finite set $S$ and a collection $C$ of subsets $c_i$ of $S$. \\
+\textbf{Question: } Do there exist disjoint sets $S_1$ and $S_2$ such that $S_1 \cup S_2 = S$ and $\forall i, c_i\not\subseteq S_1$ or $c_i\not\subseteq S_2$? 
+\end{framed}
+\end{figure}
+
+Below we show the reduction. Suppose we are given a set splitting problem with inputs: 
+\begin{align*}
+    &S = \{1, 2, \ldots, N\}, \\
+    &C = \{c_1, \ldots, c_M\}, \\ 
+    &\forall i, c_i \subseteq S. 
 \end{align*}
 
-TODO
+Then we create the weak labeling instance as follows.
+Let $d=N+1$ and $K=3$.
+Define $\zero$ as the zero vector $(0,\ldots, 0)\in \R^N$ and $\e_i$ as the $i$-th standard vector $(0,\ldots, 1, \ldots, 0)\in \R^N$).
+Then we include all the following feature-label pairs:
+\begin{itemize}
+    \item Type 1: $(x,y)=((\zero,1), 3)$,
+    \item Type 2: $(x,y)=((\e_i,1), \overline{3})$, $\forall i\in [N]$,
+    \item Type 3: $(x,y)=\left(\left(\sum_{i\in c_j} \e_i, 1\right), 3\right)$, $\forall j\in[M]$.  
+\end{itemize}
+
+For example, if we have $S=\{1,2,3\}$, $C=\{c_1, c_2\}$, $c_1 = \{1,2\}$, $c_2=\{2,3\}$, then we create the weak labeling sample set as: 
+\begin{align*}
+    \{((0,0,0,1),3), ((1,0,0,1),\overline{3}), ((0,1,0,1),\overline{3}), ((0,0,1,1),\overline{3}), ((1,1,0,1),3), ((0,1,1,1),3)\}.
+\end{align*}
+The following lemma shows that answering this weak labeling problem is equivalent to answering the original set splitting problem. 
+\begin{lemma}
+Suppose we are given a set splitting problem, and we construct a weak labeling problem as described above.
+Then the set splitting problem has a solution $\Longleftrightarrow$ the constructed weak labeling problem has a solution.
+\end{lemma}
+\begin{proof}
+ $(\Longrightarrow)$ Let $S_1, S_2$ be the solution of the set splitting problem. Define
+ \begin{align*}
+     w_1 = \left(a_1, a_2, \cdots, a_N, -\frac{1}{2}\right), 
+ \end{align*}
+ where $\forall i\in[N]$, $a_i=1$ if $i\in S_1$ and $a_i=-N$ if $i\notin S_1$. 
+ Similarly, define
+ \begin{align*}
+     w_2 = \left(b_1, b_2, \cdots, b_N, -\frac{1}{2}\right), 
+ \end{align*}
+ where $\forall i\in[N]$, $b_i=1$ if $i\in S_2$ and $b_i=-N$ if $i\notin S_2$. 
+ Finally, define
+ \begin{align*}
+     w_3 = (0,0,\cdots, 0), 
+ \end{align*}
+ the zero vector. To see this is a solution for the weak labeling problem, we verify separately for Type 1-3 samples defined above. For Type 1 sample, we have
+ \begin{align*}
+     \ip{w_3}{x} = 0 > -\frac{1}{2} = \ip{w_1}{x}=\ip{w_2}{x}. 
+ \end{align*}
+ For a Type 2 sample that corresponds to index $i$, we have either $i\in S_1$ or $i\in S_2$ because $S_1\cup S_2 = [N]$ is guaranteed. Thus, either $a_i=1$ or $b_i=1$. If $a_i=1$ is the case, then
+ \begin{align*}
+     \ip{w_1}{x}=a_i-\frac{1}{2}=\frac{1}{2} > 0 = \ip{w_3}{x}; 
+ \end{align*}
+ similarly if $b_i=1$, we have $\ip{w_2}{x}>\ip{w_3}{x}$. \\
+ For a Type 3 sample that corresponds to index $j$, Since $c_j \not\subset S_1$, there exists some $i'\in c_j$ and $i'\notin S_1$. Thus we have $x_{i'}=1$, $a_{i'}=-N$, and therefore
+ \begin{align*}
+     \ip{w_1}{x}= a_{i'}x_{i'} + \sum_{i\in [N]\backslash\{i'\}} a_ix_i - \frac{1}{2} \leq -N + (N-1)-\frac{1}{2} < 0 = \ip{w_3}{x}. 
+ \end{align*}
+ Because $c_j \not\subset S_2$ also holds, we also have $\ip{w_2}{x}<\ip{w_3}{x}$. This direction is therefore proved. \\
+ \ \\
+ $(\Longleftarrow)$ Given the solution $w_1, w_2, w_3$ of the weak labeling problem, we define 
+ \begin{align*}
+     S_1 = \left\{i\in [N] \Big| \ip{w_1-w_3}{(\e_i, 1)} > 0 \right\}, \\
+     S_2 = \left\{i\in [N] \Big| \ip{w_2-w_3}{(\e_i, 1)} > 0 \right\}.
+ \end{align*}
+ It is not hard to see $S_1\cup S_2 = [N]$.
+Note that $(\e_i, 1)$ is the feature vector for Type 2 samples.
+Because Type 2 samples all have label $\overline{3}$, for any $i\in [N]$, one of the following must hold: $\ip{w_1-w_3}{(\e_i, 1)}>0$ or $\ip{w_2-w_3}{(\e_i, 1)}>0$.
+Thus $i\in S_1$ or $i\in S_2$.
+
+ Now we show $\forall j$, $c_j \not\subset S_1$ and $c_j \not\subset S_2$ by contraction.
+Without loss of generality, suppose there exists some $j$ such that $c_j \subset S_1$.
+By our definition of $S_1$, we have $\ip{w_1-w_3}{(\e_i, 1)} > 0$ for all $i\in c_j$.
+Therefore,
+ \begin{align*}
+     \sum_{i\in c_j}\ip{w_1-w_3}{\left(\e_i, 1\right)} = \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, |c_j|\right)} > 0. 
+ \end{align*}
+ Because Type 1 sample has label $3$, we also have
+ \begin{align*}
+     \ip{w_1-w_3}{\left(\zero, 1\right)} < 0. 
+ \end{align*}
+ Combining the above two inequalities, we get
+ \begin{align*}
+     \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, 1\right)} = \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, |c_j|\right)} - (|c_j|-1)\ip{w_1-w_3}{\left(\zero, 1\right)}>0.  
+ \end{align*}
+ Note that $\left(\sum_{i\in c_j}\e_i, 1\right)$ is a feature vector for Type 3 samples.
+Thus the above inequality contradicts that Type 3 samples have label 3.
+Therefore, $c_j \not\subset S_1$.
+Similarly we can prove $c_j \not\subset S_2$.
+\end{proof}

### 2019-01-16 arxiv-version/np-hardness-of-the-weak-labeling-problem.tex
some minor modification to arxiv version (np-hard section)

@@
 
-The hardness proof is based on a reduction from the set splitting problem, which is proven to be NP-complete by Lovasz \chenyu{Reference needed}, to our weak labeling problem.
-The reduction is adapted from Avrim Blum \chenyu{Reference needed}.
+The hardness proof is based on a reduction from the set splitting problem, which is proven to be NP-complete by Lovasz \cite{garey1979computers}, to our weak labeling problem.
+The reduction is adapted from \cite{blum1989training}.
 \begin{figure}[h]

### 2019-01-16 arxiv-version/np-hardness-of-the-weak-labeling-problem.tex
fixing small error in np-hard proof

@@
  \begin{align*}
-     S_1 = \left\{i\in [N] \Big| \ip{w_1-w_3}{(\e_i, 1)} > 0 \right\}, \\
-     S_2 = \left\{i\in [N] \Big| \ip{w_2-w_3}{(\e_i, 1)} > 0 \right\}.
+     S_1 &= \left\{i\in [N] \Big| \ip{w_1-w_3}{(\e_i, 1)} > 0 \right\}, \\
+     S_2 &= \left\{i\in [N] \Big| \ip{w_2-w_3}{(\e_i, 1)} > 0 \text{\ and\ } i\notin S_1 \right\}.
  \end{align*}
- It is not hard to see $S_1\cup S_2 = [N]$.
-Note that $(\e_i, 1)$ is the feature vector for Type 2 samples.
+ It is not hard to see $S_1 \cap S_2 = \emptyset$ and $S_1\cup S_2 = [N]$.
+The former is because $S_2$ only includes elements that are not in $S_1$.
+For the latter, note that $(\e_i, 1)$ is the feature vector for Type 2 samples.
 Because Type 2 samples all have label $\overline{3}$, for any $i\in [N]$, one of the following must hold: $\ip{w_1-w_3}{(\e_i, 1)}>0$ or $\ip{w_2-w_3}{(\e_i, 1)}>0$.
-Thus $i\in S_1$ or $i\in S_2$.
+This implies $i\in S_1$ or $i\in S_2$.
 
  Now we show $\forall j$, $c_j \not\subset S_1$ and $c_j \not\subset S_2$ by contraction.
-Without loss of generality, suppose there exists some $j$ such that $c_j \subset S_1$.
+Assume there exists some $j$ such that $c_j \subset S_1$.
 By our definition of $S_1$, we have $\ip{w_1-w_3}{(\e_i, 1)} > 0$ for all $i\in c_j$.
@@
 Thus the above inequality contradicts that Type 3 samples have label 3.
-Therefore, $c_j \not\subset S_1$.
-Similarly we can prove $c_j \not\subset S_2$.
+Therefore, $c_j \subset S_1$.
+If we assume there exists some $c_j \not\subset S_2$, same arguments apply and also lead to contradiction.
 \end{proof}

### 2019-01-17 ICML-submission/introduction.tex
another pass over related work

@@
 \begin{protocol}[h]
-\caption{\textsc{Online Multiclass Classification with Bandit Feedback}
+\caption{\textsc{Online Multiclass Classification with Bandit Feedback \chicheng{Shall we emphasize linear here?}}
 \label{algorithm:game-protocol}}
@@
 Definitions~\ref{definition:weak-linear-separability}~and~\ref{definition:strong-linear-separability}.
-The standard notion of multiclass linear separability corresponds to the weak
+The standard notion of multiclass linear separability~\citep[See e.g.][]{Crammer-Singer-2003}
+corresponds to the weak
 linear separability. For binary classification, the weak and strong separability
@@
 then the \textsc{Multiclass Perceptron} algorithm makes at most $\lfloor
-2(R/\gamma)^2 \rfloor$ mistakes. The guarantees provided by \textsc{Multiclass
+2(R/\gamma)^2 \rfloor$ mistakes.
+\chicheng{I just noted that Theorem 3 of~\cite{Crammer-Singer-2003} actually
+has exactly the same upper bound - but it might still make sense to include the
+proof here.}
+The guarantees provided by \textsc{Multiclass
 Perceptron} is very satisfying, since it achieves an information-theoretically
@@
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
-that has an expected number of mistakes at most $(K-1) \lfloor 4(R/\gamma)^2
-\rfloor$. The memory complexity and per-round time complexity are both $O(dK)$.
+that has an expected number of mistakes at most $O(K (R/\gamma)^2))$.
+The memory complexity and per-round time complexity are both $O(dK)$.
 The algorithm can be viewed as running $K$ copies of the \textsc{Binary
@@
 mistakes in the worst case.
+%$(K-1) \lfloor 4(R/\gamma)^2\rfloor$
 
-For the case when examples are weakly linearly separable, we construct a
+For the case when the examples are weakly linearly separable, we construct a
 non-linear feature mapping $\phi$ and associated positive definite kernel
 $k(x,x')$ that makes the examples \emph{strongly} linearly separable. We then
-use the kernelized version of the algorithm for the strongly separable case,
+use the kernelized version of
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
+for the strongly separable case, namely
 Algorithm~\ref{algorithm:kernelized}. (For details on kernel methods see
@@
 The kernel $k(x,x')$ corresponding to the feature mapping $\phi$ has a simple
-explicit formula and can be computed in $O(d)$ time.
+explicit formula and can be computed in $O(d)$ time,
+making Algorithm~\ref{algorithm:kernelized} computationally efficient.
 
@@
 
-The resulting kernelized algorithm runs in time that is polynomial in the
+The resulting kernelized algorithm runs in time polynomial in the
 original dimension of the feature vectors $d$, the number of classes $K$, and
-the number of rounds $T$. We prove that if the examples lie in unit ball of
-$\R^d$ and are weakly separable with margin $\gamma$, the algorithm makes at
+the number of rounds $T$. We prove that if the examples lie in the unit ball of
+$\R^d$ and are weakly linearly separable with margin $\gamma$,
+Algorithm~\ref{algorithm:kernelized} makes at
 most $2^{\widetilde{O}(\min(K \log^2 \frac{1}{\gamma}, \sqrt{\frac{1}{\gamma}}

### 2019-01-17 ICML-submission/related-work.tex
another pass over related work

@@
 the difference between the number of mistakes made by the algorithm and the
-number of mistakes made by the best classifier in $\calH$ in hindsight. However,
+number of mistakes made by the best classifier in $\calH$ in hindsight.
+We remark that
 all algorithms developed in this context are computationally inefficient.
@@
 $O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
-and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weak linearly separable
-setting. The polynomial dependence of \textsc{Banditron}'s mistake bound on the
-time horizon is undesirable for problems with a long time horizon. One key open
+and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weakly linearly separable
+setting.
+In contrast to mild dependencies on the time horizon for mistake bounds of
+computationally inefficient algorithms,
+the polynomial dependence of \textsc{Banditron}'s mistake bound on the
+time horizon is undesirable for problems with a long time horizon, in the
+weakly linearly separable setting. One key open
 question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
@@
 Many works consider bandit multiclass classification in the general setting,
-where the data is not necessarily separable by some linear
+where the examples are not necessarily separable by some linear
 classifier~\cite{Abernethy-Rakhlin-2009, Wang-Jin-Valizadegan-2010,
@@
 base hypothesis as a separate feature. However, most of these works achieve a
-regret bound of order $\widetilde{O}(\sqrt{T})$ to $O(T^{3/4})$. In the weakly
-separable setting, these algorithms only guarantees a mistake upper bound of
+regret of order $\widetilde{O}(\sqrt{T})$ to $O(T^{3/4})$.
+In the weakly linearly
+separable setting, these algorithms at best guarantees a mistake upper bound of
 $\widetilde{O}(\sqrt{T})$, which is undesirable for problems with a long time
 horizon. One exception is the \textsc{Newtron} algorithm, where with appropriate
-settings of parameter $\alpha$, it is able to achieve a $O(\ln T)$ regret.
+settings of parameter $\alpha$, it is able to achieve a $O(\ln T)$ regret against
+the $\alpha$-logistic loss.
 However, as argued in ~\citep[][Appendix D]{Beygelzimer-Orabona-Zhang-2017}, if
-the setting of $\alpha$ makes the regret bound $O(\sqrt{T})$, the logistic loss
+the setting of $\alpha$ makes the regret bound $O(\sqrt{T})$, the $\alpha$-logistic loss
 of the best linear predictor would be $\Omega(T^{3/4})$. Therefore,
-\textsc{Newtron} is still only able to guarantee a mistake upper bound of
-$O(\sqrt{T})$ in the weakly separable setting.
+\textsc{Newtron} at best guarantees a mistake upper bound of
+$O(\sqrt{T})$ in the weakly linearly separable setting.
 
@@
 
-There is a large body of literature on the contextual bandit learning
+There is a large body of literature on the contextual bandits
 problem~\citep{Auer-2003, Langford-Zhang-2008}. In this problem, the learner is
@@
 \min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$. The online bandit multiclass
-learning problem is a special case of the contextual bandits problem, where the
+learning problem can be seen a special case of the contextual bandits problem, where the
 cost $c_t(i)$ is the classification error $\indicator{i \neq y_t}$, and the
@@
 s \gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
-information-theoretic mistake upper bounds under various settings of $\calF$,
-including parametric and nonparametric classes. On the other hand, it gives an
+information-theoretic regret upper bounds under various settings of $\calF$.
+On the other hand, it gives an
 efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of
@@
 strongly linearly separable setting.
+
+%including parametric and nonparametric classes
 

### 2019-01-17 ICML-submission/appendix-multiclass-perceptron.tex
a version within page limit

@@
 \label{theorem:mutliclass-perceptron-mistake-upper-bound}
+\chicheng{Cite~\cite{Crammer-Singer-2003} here?}
 Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive

### 2019-01-17 ICML-submission/from-weak-separability-to-strong-separability.tex
Fix Makefile and citation
a version within page limit

@@
 margin $\gamma$ and $\norm{x_t} \le R$ for all $t$, then the normalized examples
-$(\widehat{x}_1,y_1), \widehat{x}_2,y_2), \dots, (\widehat{x}_T,y_T)$ are weakly
+$(\widehat{x}_1,y_1), (\widehat{x}_2,y_2), \dots, (\widehat{x}_T,y_T)$ are weakly
 linearly separable by margin $\gamma/R$.} Note that
@@
 & \ \cdot \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}, \\
-\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4\sqrt{K}(2K-5/2) 2^{K-1}} \\
-& \ \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} \; .
+\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4\sqrt{K}(4K-5) 2^{K-1}} \\
+& \ \cdot \left(2^{s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} \; .
 \end{align*}
@@
 (\phi(x_T), y_T)$, is strongly linearly separable with margin $\gamma' =
-\max\{\gamma_1, \gamma_2\}$. In addition, $\norm{\phi(x_1)}_{\ell_2},
-\norm{\phi(x_2)}_{\ell_2}, \dots, \norm{\phi(x_T)}_{\ell_2} \le 2$.
+\max\{\gamma_1, \gamma_2\}$. In addition, for all $t$ in $\cbr{1,\ldots,T}$,
+$k(x_t,x_t) \leq 2$.
 \end{theorem}
+%$\norm{\phi(x_1)}_{\ell_2},
+%\norm{\phi(x_2)}_{\ell_2}, \dots, \norm{\phi(x_T)}_{\ell_2} \le 2$
 
@@
 Algorithm~\ref{algorithm:kernelized} with kernel function $k(x,x') =
-\ip{\phi(x)}{\phi(x')}_{\ell_2}$.
+\ip{\phi(x)}{\phi(x')}_{\ell_2}$, under the weak linear separability assumption.
 
@@
 
-This corollary follows direcly from
+This corollary follows directly from
 Theorems~\ref{theorem:kernelized-upper-bound}
@@
 
-\paragraph{Overview.} The idea behind construction and analysis of the mapping
+\paragraph{Overview.} The idea behind the construction and analysis of the mapping
 $\phi$ is polynomial approximation. Specifically, we give $k$ polynomials $p_1$,
@@
 class $i$ lie in
-\[ R_i^+ = \bigcap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \geq \gamma}, \] and all examples from the remaining classes lie in
-\[ R_i^- = \bigcup_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \leq  -\gamma}. \]
+\[ R_i^+ = \bigcap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \norm{x} \le 1, \ip{w_i^* - w_j^*}{x} \geq \gamma}, \] and all examples from the remaining classes lie in
+\[ R_i^- = \bigcup_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \norm{x} \le 1, \ip{w_i^* - w_j^*}{x} \leq  -\gamma}. \]
 Therefore, to satisfy Equations~\eqref{equation:poly-pos-i}
 and~\eqref{equation:poly-neg-i}, it suffices to construct $p_i$ such that:
-\begin{align*}
-x \in R_i^+ & \Rightarrow p_i(x) \ge \frac {\gamma'} 2 \\
+\begin{align}
+x \in R_i^+ & \Rightarrow p_i(x) \ge \frac {\gamma'} 2
+\label{eqn:r-plus}
+\\
 x \in R_i^- & \Rightarrow p_i(x) \le - \frac {\gamma'} 2
-\end{align*}
+\label{eqn:r-minus}
+\end{align}
 
-According to the well known Stone-Weierstrass theorem (see
-e.g.~\citet[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
+According to the well known Stone-Weierstrass theorem~\citep[see
+e.g.][Section~10.10]{Davidson-Donsig-2010}, on a compact set,
 multivariate polynomials uniformly approximate any continuous function.
 Intuitively speaking, we use a multivariate polynomial to approximate, on the
-unit ball of $\R^d$, the indicator function corresponding to the intersection of
-$m=K-1$ halfspaces. Within margin $\gamma$ along the decision boundary, we allow
-the polynomial to attain arbitrary value. The polynomial separates examples in
-one class from examples in the other classes. To be able to quantify $\gamma'$
-we need to quantify certain parameters of the approximating polynomial. We
-construct two different polynomials with different parameters. The parameters
+unit ball of $\R^d$, some scaling of the indicator function corresponding to the intersection of
+$m=K-1$ halfspaces $\bigcap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i^* - w_j^*}{x} \geq 0}$. Within margin $\gamma$ along the decision boundary, we allow
+the polynomial to attain arbitrary value. To be able to quantify $\gamma'$
+we need to quantify certain parameters of the approximating polynomial.
+Following the constructions in~\citet{Klivans-Servedio-2008}
+(which in turn use the constructions in~\citet{Beigel-Reingold-Spielman-1995}), we
+construct two different polynomials with different parameters that satisfy
+Equation~\eqref{eqn:r-plus} and~\eqref{eqn:r-minus}.
+The parameters
 are quantified in
@@
 
-Before we state the theorems, recall that a polynomial of $d$ variables is a
+%The polynomial separates examples in
+%one class from examples in the other classes.
+%
+%the indicator function corresponding to the intersection of
+%$m=K-1$ halfspaces
+%a function that takes value $\frac {\gamma'} 2$ on $R_i^+$
+%and $-\frac {\gamma'} 2$ on $R_i^-$
+
+\paragraph{Details of the proof.} Before we state the theorems, recall that a polynomial of $d$ variables is a
 function $p:\R^d \to \R$ of the form
@@
 for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is non-zero.
-Following the terminology of~\cite{Klivans-Servedio-2008},
+Following the terminology of~\citet{Klivans-Servedio-2008},
 the \emph{norm of a polynomial} $p$ is defined as
@@
 \begin{enumerate}
-\item $p(x) \ge 1/2$ \\ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
-\item $p(x) \le -1/2$ \\ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-\item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$
-\item $\displaystyle \norm{p} \le \left( 188 \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil \right)^{\frac{1}{2} \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil}$
+\item $p(x) \ge 1/2$ \\ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
+\item $p(x) \le -1/2$ \\ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$,
+\item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$,
+\item $\displaystyle \norm{p} \le \left( 188 \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil \right)^{\frac{1}{2} \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil}$.
 \end{enumerate}
@@
 \begin{enumerate}
-\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$ \\
-for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
+\item $\displaystyle p(x) \ge 1/2$ \\
+for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
 
-\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$ \\
-for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
+\item $\displaystyle p(x) \le - 1/2$ \\
+for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$,
 
-\item $\deg(p) \le (2s+1) rm$
-\item $\norm{p} \le (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm}$
+\item $\deg(p) \le (2s+1) rm$,
+\item $\norm{p} \le (4m-1) 2^m \cdot \left(2^s rm (4s+2)^2 \right)^{(s+1/2)rm}$.
 \end{enumerate}
@@
 
-The following lemma expresses any multivariate polynomial in $\R^d$
-as a linear function in $\ell_2$ and gives an upper bound its the norm.
+The following lemma establishes a correspondence
+between any multivariate polynomial in $\R^d$
+and an element in $\ell_2$, and gives an upper bound on its norm.
+Its proof follows from simple algebra, which we defer to
+Appendix~\ref{section:proof-norm-bound}.
 
@@
 
-\begin{proof}
-Note that the polynomial $p$ can be written as
-$p(x) = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c'_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}$.
-We define $c \in \ell_2$ using the multi-index notation as
-$$
-c_{\alpha_1, \alpha_2, \dots, \alpha_d}
-= \frac{c'_{\alpha_1, \alpha_2, \dots, \alpha_d} 2^{(\alpha_1 + \alpha_2 + \dots + \alpha_d)/2}}{\sqrt{\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}}
-$$
-for all tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ such that $\alpha_1 + \alpha_2 + \dots + \alpha_d \le \deg(p)$.
-Otherwise, we define $c_{\alpha_1, \alpha_2, \dots, \alpha_d} = 0$. Clearly,
-$\ip{c}{\phi(x)}_{\ell_2} = p(x)$.
+Using the lemma and the polynomial approximation theorems, we can prove the
+mapping $\phi$ maps any set of weakly linearly separable examples
+to a strongly linearly separable set of examples. Due to space constraints,
+we only sketch the
+proof of Theorem~\ref{theorem:margin-transformation} here, and defer the full
+proof to Appendix~\ref{section:full-proof-of-theorem-margin-transformation}.
 
-Since
-\begin{align*}
-|c_{\alpha_1, \alpha_2, \dots, \alpha_d}|
-& \le 2^{(\alpha_1 + \alpha_2 + \dots + \alpha_d)/2} |c'_{\alpha_1, \alpha_2, \dots, \alpha_d}| \\
-& \le 2^{\deg(p)/2} |c'_{\alpha_1, \alpha_2, \dots, \alpha_d}| \; ,
-\end{align*}
-we have
-\begin{align*}
-\norm{c}_{\ell_2}
-& \le 2^{\deg(p)/2} \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} (c'_{\alpha_1, \alpha_2, \dots, \alpha_d})^2} \\
-& = 2^{\deg(p)/2} \norm{p} \; . \qquad \qedhere
-\end{align*}
-\end{proof}
-
-Using the lemma and the polynomial approximation theorems, we can prove the
-mapping $\phi$ maps any a weakly separable data to a strongly separable data
-set.
-
-\begin{proof}[Proof of Theorem~\ref{theorem:margin-transformation}]
-First osberve that for any $t=1,2,\dots,T$,
-$$
-\norm{\phi(x_t)}_{\ell_2} = k(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
-$$
-
-Since the examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ are weakly
-linearly separable with margin $\gamma$ there are vectors $w_1, w_2, \dots, w_K$
-satisfying \eqref{equation:weak-linear-separability-1} anf
+\begin{proof}[Proof sketch of Theorem~\ref{theorem:margin-transformation}]
+Since the examples $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ are weakly
+linearly separable with margin $\gamma$,, there are vectors $w_1, w_2, \dots, w_K$
+satisfying \eqref{equation:weak-linear-separability-1} and
 \eqref{equation:weak-linear-separability-2}.
@@
 $j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors have norm at most
-$1$.
-Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
-imply that there exists multivariate polynomials $p_i:\R^d \to \R$ and $q_i:\R^d
-\to \R$ such that
+$1$. We consider two cases regarding the relationship between $\gamma_1$ and
+$\gamma_2$.
+
+\paragraph{Case 1: $\gamma_1 \geq \gamma_2$.} In this setting, Theorem~\ref{theorem:polynomial-approximation-1}
+implies that there exist a multivariate polynomial $p_i:\R^d \to \R$
+
 \begin{align*}
-\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{\frac{2}{\gamma}} \right\rceil \; , \\
-\deg(q_i) & = (2s+1) r(K-1) \; .
+\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{\frac{2}{\gamma}} \right\rceil \; ,
 \end{align*}
-Futhermore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
-$q_i(x_t) \ge \frac{1}{4} \cdot 2^{s(s+1)r(K-1)}$ and if $y_t \neq i$ then
-$p_i(x_t) \le -1/2$, $q_i(x) \le - \frac{1}{4} \cdot 2^{s(s+1)r(K-1)}$ and
+such that all examples $x$ in $R_i^+$ (resp. $R_i^-$) satisfy $p_i(x) \geq 1/2$
+(resp. $p_i(x) \leq -1/2$).
+Therefore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
+ and if $y_t \neq i$ then $p_i(x_t) \le -1/2$, and
 \begin{align*}
@@
 \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; , \\
-\norm{q_i} & \le (2K-5/2) 2^{K-1} \\
-& \qquad \cdot \left(2^{2s} r(K-1) (4s+2)^2 \right)^{(s+1/2)r(K-1)} \; .
 \end{align*}
-By \autoref{lemma:norm-bound} there exists $c_i, c_i' \in \ell_2$ such that
-$\ip{c_i}{\phi(x)} = p_i(x)$ and $\ip{c_i'}{\phi(x)} = q_i(x)$ and
+By \autoref{lemma:norm-bound}, there exists $c_i \in \ell_2$ such that
+$\ip{c_i}{\phi(x)} = p_i(x)$, and
 \begin{align*}
@@
 & \le \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
-\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \\
-\norm{c'_i}_{\ell_2} & \le (2K-5/2) 2^{K-1} \\
-& \qquad \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{(s+1/2)r(K-1)} \; .
+\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; .
 \end{align*}
-Define vectors $u_i, u_i' \in \ell_2$ as
+Define vectors $u_i \in \ell_2$ as
 \begin{align*}
@@
 \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}} \; . \\
-u_i' & = \frac{c_i'  \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)}}{\sqrt{K} (2K-5/2) 2^{K-1}} \; .
 \end{align*}
 
-Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$ and
-$\norm{u_1'}^2 + \norm{u_2'}^2 + \dots + \norm{u_K'}^2 \le 1$.
-Futhermore, for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma_1$ and
-$\ip{u'_{y_t}}{x_t} \ge \gamma_2$
+Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$.
+Futhermore, for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma_1$
 and for all $j \in \{1,2,\dots,K\} \setminus \{y_t\}$,
-$\ip{u_j}{x_t} \le - \gamma_1$ and $\ip{u'_j}{x_t} \le - \gamma_2$. In other words,
+$\ip{u_j}{x_t} \le - \gamma_1$. In other words,
 $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
-strongly linearly separable with margin $\gamma_1$ and also strongly linearly
-separable with margin $\gamma_2$. Therefore, the examples are strongly
+strongly linearly separable with margin $\gamma_1 = \max\{\gamma_1, \gamma_2\}$.
+
+\paragraph{Case 2: $\gamma_1 \leq \gamma_2$.} Following the
+same idea as Case 1 and using Theorem~\ref{theorem:polynomial-approximation-1},
+we can show that
+$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
+strongly linearly separable with margin $\gamma_2 = \max\{\gamma_1, \gamma_2\}$.
+%The proof for the case of $\gamma_1 < \gamma_2$
+%is symmetric.
+
+In summary, the examples are strongly
 linearly separable with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
+Finally, observe that for any $t=1,2,\dots,T$,
+\[
+k(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
+\qedhere
+\]
 \end{proof}

### 2019-01-17 ICML-submission/from-weak-separability-to-strong-separability.tex
Small fixes

--- 2019-01-16 ICML-submission/from-weak-separability-to-strong-separability.tex
@@
 \dots, \alpha_d)$ of non-negative integers and $c_{\alpha_1, \alpha_2, \dots,
-\alpha_d}$'s are real coefficients. The \emph{degree} of a polynomial $p$, denoted
-by $\deg(p)$, is the largest value of $\alpha_1 + \alpha_2 + \dots + \alpha_d$
-for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is non-zero.
-Following the terminology of~\cite{Klivans-Servedio-2008},
-the \emph{norm of a polynomial} $p$ is defined as
+\alpha_d}$'s are real coefficients. The \emph{degree} of a polynomial $p$,
+denoted by $\deg(p)$, is the largest value of $\alpha_1 + \alpha_2 + \dots +
+\alpha_d$ for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is
+non-zero. Following the terminology of~\citet{Klivans-Servedio-2008}, the
+\emph{norm of a polynomial} $p$ is defined as
 $$

### 2019-01-17 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex

@@
 (Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
-and we give an upper bound on its number of mistakes, stated as
+and give an upper bound on its number of mistakes, stated as
 \autoref{theorem:strongly-separable-examples-mistake-upper-bound} below. The
@@
 the classes corresponding to a positive prediction. If all copies make negative
-predictions, the algorithms makes a prediction uniformly at random.
+predictions, the algorithms makes a prediction uniformly at random from
+$\cbr{1,\ldots,K}$.
 
@@
 number. For any (possibly randomized) algorithm $\calA$ for the \textsc{Online
-Multiclass Classification with Bandit Feedback} with $K \le
-(R/\gamma)^2$ classes there exists an inner product space $(V,
+Multiclass Classification with Bandit Feedback} problem with $K \le
+(R/\gamma)^2$ classes, there exists an inner product space $(V,
 \ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
@@
 \begin{enumerate}
-  \item $((\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T))$ is strongly linearly separable with margin $\gamma$,
+  \item $((\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T))$,
+  the set of examples in $L$ after feature transformation $\phi$,
+  is strongly linearly separable with margin $\gamma$,
   \item for all $t$ in $\cbr{1,\ldots,T}$, $k(x_t,x_t) \le R^2$,

### 2019-01-17 ICML-submission/appendix-proofs-of-polynomial-approximation-theorems.tex

@@
 \label{section:proof-of-polynomial-approximation}
+
+In this section, we follow the construction of~\citet{Klivans-Servedio-2008}
+(which in turn uses the constructions of~\citet{Beigel-Reingold-Spielman-1995})
+to establish two polynomials of low norm, such that it takes large positive values
+in
+\[ \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\} \]
+and takes large negative values in
+\[ \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le -\gamma \right\} . \]
+We improve the norm bound analysis of~\citet{Klivans-Servedio-2008} in two aspects:
+\begin{enumerate}
+  \item Our upper bounds on the norm of the polynomials do not have any dependency on the
+  dimensionality $d$.
+  \item We remove the requirement that the fractional part of input $x$ must be above some threshold in
+  Theorem~\ref{theorem:polynomial-approximation-2}.
+\end{enumerate}
+A lot of the proof details are similar to those of~\citet{Klivans-Servedio-2008}; nevertheless,
+we provide a self-contained full proof here.
 
@@
 
+We prove the following lemma in this section.
+\autoref{theorem:polynomial-approximation-2} immediately
+follows from this lemma by considering $p' = p \cdot 2^{-s(s+1)rm+1})$
+and algebra.
+
+\begin{lemma}
+\label{lemma:polynomial-approximation-2}
+Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
+\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$.
+Define
+$$
+r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(1/\gamma) \right \rceil \; .
+$$
+Then, there exists a multivariate polynomial $p:\R^d \to \R$ such that
+\begin{enumerate}
+\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$ \\
+for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
+
+\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$ \\
+for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$,
+
+\item $\deg(p) \le (2s+1) rm$,
+\item $\norm{p} \le (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm}$.
+\end{enumerate}
+\end{lemma}
+
 We define several univariate polynomials
@@
 $$
-It easy to verify that
+It is easy to verify that
 $$

### 2019-01-17 ICML-submission/from-weak-separability-to-strong-separability.tex

--- 2019-01-17 ICML-submission/from-weak-separability-to-strong-separability.tex
@@
 \dots, \alpha_d)$ of non-negative integers and $c_{\alpha_1, \alpha_2, \dots,
-\alpha_d}$'s are real coefficients. The \emph{degree} of a polynomial $p$, denoted
-by $\deg(p)$, is the largest value of $\alpha_1 + \alpha_2 + \dots + \alpha_d$
-for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is non-zero.
-Following the terminology of~\citet{Klivans-Servedio-2008},
-the \emph{norm of a polynomial} $p$ is defined as
+\alpha_d}$'s are real coefficients. The \emph{degree} of a polynomial $p$,
+denoted by $\deg(p)$, is the largest value of $\alpha_1 + \alpha_2 + \dots +
+\alpha_d$ for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is
+non-zero. Following the terminology of~\citet{Klivans-Servedio-2008}, the
+\emph{norm of a polynomial} $p$ is defined as
 $$

### 2019-01-17 ICML-submission/introduction.tex

@@
 mistake bound under the strong linear separability condition, their proof of
-Theorem 2 is incorrect. Their Lemma 4 cannot be directly applied to the bandit
+Theorem 2 is incorrect: their Lemma 4 cannot be directly applied to the bandit
 setting, as the algorithm only makes updates on a subset of the $w_i$'s.} We

### 2019-01-17 ICML-submission/notions-of-linear-separability.tex

@@
 
-The notion of weak linear separability with a margin is standard. It is used in
+The notion of weak linear separability with a margin is standard;
+using the notion of multiclass margin~\citep[see e.g.][]{Crammer-Singer-2003},
+weak linear separability with margin $\gamma$ is equivalent to that
+there is a linear classifier that has multiclass margin $\gamma$ on
+all the examples. It is used in
 the full-information setting to upper bound the number of mistakes of the
@@
 
-\chicheng{Shall we mention that this multiclass margin notion has also appeared in e.g.~\cite{Crammer-Singer-2003}?}
+%\chicheng{Shall we mention that this multiclass margin notion has also appeared in e.g.?}
 

### 2019-01-17 ICML-submission/introduction.tex
Fix introdcution

@@
 \begin{protocol}[h]
-\caption{\textsc{Online Multiclass Classification with Bandit Feedback \chicheng{Shall we emphasize linear here?}}
+\caption{\textsc{Online Multiclass Linear Classification with Bandit Feedback}
 \label{algorithm:game-protocol}}
@@
 Definitions~\ref{definition:weak-linear-separability}~and~\ref{definition:strong-linear-separability}.
-The standard notion of multiclass linear separability~\citep[See e.g.][]{Crammer-Singer-2003}
-corresponds to the weak
-linear separability. For binary classification, the weak and strong separability
-are identical. However, they differ for multiclass classification with $K \ge 3$
+The standard notion of multiclass linear
+separability~\citep{Crammer-Singer-2003} corresponds to the weak linear
+separability. For binary classification, the weak and strong separability are
+identical. However, they differ for multiclass classification with $K \ge 3$
 classes. For multiclass classification with $K$ classes, weak linear
@@
 
-In the full-information feedback setting, it is well known that if all examples
-have norm at most $R$ and are weakly linearly separable with a margin $\gamma$,
-then the \textsc{Multiclass Perceptron} algorithm makes at most $\lfloor
-2(R/\gamma)^2 \rfloor$ mistakes.
-\chicheng{I just noted that Theorem 3 of~\cite{Crammer-Singer-2003} actually
-has exactly the same upper bound - but it might still make sense to include the
-proof here.}
-The guarantees provided by \textsc{Multiclass
-Perceptron} is very satisfying, since it achieves an information-theoretically
-optimal mistake upper bound, while having low time and memory
-complexities.~\footnote{These results are standard in the literature. For
-completeness, we present these results along with their proofs in
-Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
-material.}
+In the full-information feedback setting, it is well known
+\citep{Crammer-Singer-2003} that if all examples have norm at most $R$ and are
+weakly linearly separable with a margin $\gamma$, then the \textsc{Multiclass
+Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
+The guarantees provided by \textsc{Multiclass Perceptron} is very satisfying,
+since it achieves an information-theoretically optimal mistake upper bound,
+while having low time and memory complexities.~\footnote{These are
+folklore results. For completeness, we present these results along
+with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs} in the
+supplementary material.}
 
@@
 mistakes in the worst case.
-%$(K-1) \lfloor 4(R/\gamma)^2\rfloor$
 
@@
 use the kernelized version of
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-for the strongly separable case, namely
-Algorithm~\ref{algorithm:kernelized}. (For details on kernel methods see
-e.g.~\citet{Scholkopf-Smola-2002} or \citet{Shawe-Taylor-Cristianini-2004}.)
-The kernel $k(x,x')$ corresponding to the feature mapping $\phi$ has a simple
-explicit formula and can be computed in $O(d)$ time,
-making Algorithm~\ref{algorithm:kernelized} computationally efficient.
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} for
+the strongly separable case, namely Algorithm~\ref{algorithm:kernelized}. (For
+details on kernel methods see e.g.~\citet{Scholkopf-Smola-2002} or
+\citet{Shawe-Taylor-Cristianini-2004}.) The kernel $k(x,x')$ corresponding to
+the feature mapping $\phi$ has a simple explicit formula and can be computed in
+$O(d)$ time, making Algorithm~\ref{algorithm:kernelized} computationally
+efficient.
 

### 2019-01-17 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Small fixes

@@
 {
-\REQUIRE{Number of classes $K$.}
-\REQUIRE{Number of rounds $T$.}
+\REQUIRE{Number of classes $K$, number of rounds $T$.}
 \REQUIRE{Inner product space $(V,\ip{\cdot}{\cdot})$.}
@@
 Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
-integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
-$L = ((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples in
-$V \times \{1,2,\dots,K\}$ such that:
-\begin{enumerate}
-  \item $L$ is strongly linearly separable with margin $\gamma$,
-  \item for all $t$ in $\cbr{1,\ldots,T}$, $\norm{x_t} \le R$,
-\end{enumerate}
-then the expected number of mistakes
+integer, $\gamma$ be a positive real number, $R$ be a non-negative real number.
+If the examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in V \times
+\{1,2,\dots,K\}$ are strongly linearly separable with margin $\gamma$ and for
+all $t \in \cbr{1,\ldots,T}$ satisfy $\norm{x_t} \le R$ then the expected number
+of mistakes
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
@@
 \label{theorem:kernelized-upper-bound}
-Let $k(\cdot, \cdot)$ be a positive definite kernel function and let
-$\phi(\cdot)$ be the associated feature map. Let $K$ be a positive integer,
-$\gamma$ be a positive real number, $R$ be a non-negative real number. If $L =
-((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples
-such that:
+Let $X$ be a non-empty set, let $(V, \ip{\cdot}{\cdot})$ be an inner product
+space. Let $\phi:X \to V$ be a feature map and let $k:X \times X \to \R$,
+$k(x,x') = \ip{\phi(x)}{\phi(x')}$ the associated positive positive definite
+kernel. Let $K$ be a positive integer, $\gamma$ be a positive real number, $R$
+be a non-negative real number. If $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in
+X \times \{1,2,\dots,K\}$ are labeled examples such that:
 \begin{enumerate}
-  \item $((\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T))$,
-  the set of examples in $L$ after feature transformation $\phi$,
-  is strongly linearly separable with margin $\gamma$,
+\item the mapped examples $(\phi(x_1), y_1)$, $(\phi(x_2), y_2)$, $\dots$, $(\phi(x_T), y_T)$
+are strongly linearly separable with margin $\gamma$,
 \item for all $t$ in $\cbr{1,\ldots,T}$, $k(x_t,x_t) \le R^2$,
@@
 {
-\REQUIRE{Number of classes $K$.}
-\REQUIRE{Number of rounds $T$.}
+\REQUIRE{Number of classes $K$, number of rounds $T$.}
 \REQUIRE{Kernel function  $k(\cdot, \cdot)$.}

### 2019-01-17 ICML-submission/appendix-multiclass-perceptron.tex
Small fixes

--- 2019-01-16 ICML-submission/appendix-multiclass-perceptron.tex
@@
 
-\begin{theorem}[Mistake upper bound]
+\begin{theorem}[Mistake upper bound~\cite{Crammer-Singer-2003}]
 \label{theorem:mutliclass-perceptron-mistake-upper-bound}
@@
 only when a mistakes happens. If mistake happens in round $t$, we have
+\begingroup
+\allowdisplaybreaks
 \begin{align*}
@@
 \end{align*}
+\endgroup
 Thus, after $M$ mistakes,
@@
 $R$ be a non-negative real number. For any (possibly randomized) algorithm
-$\calA$ for the
-\textsc{Online Multiclass Classification} problem there exists an
-inner product space $(V, \ip{\cdot}{\cdot})$, a non-negative integer $T$ and a
-sequence of labeled examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$
-examples in $V \times \{1,2,\dots,K\}$ that are weakly linearly separable with margin
-$\gamma$, the norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
-and the algorithm makes at least $\frac 1 2 \lfloor (R/\gamma)^2 \rfloor$ mistakes.
+$\calA$ for the \textsc{Online Multiclass Classification} problem there exists
+an inner product space $(V, \ip{\cdot}{\cdot})$, a non-negative integer $T$ and
+a sequence of labeled examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$
+examples in $V \times \{1,2,\dots,K\}$ that are weakly linearly separable with
+margin $\gamma$, the norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T}
+\le R$ and the algorithm makes at least $\frac 1 2 \lfloor (R/\gamma)^2 \rfloor$
+mistakes.
 \end{theorem}

### 2019-01-17 ICML-submission/from-weak-separability-to-strong-separability.tex
Small fixes

@@
 $(\widehat{x}_1,y_1), (\widehat{x}_2,y_2), \dots, (\widehat{x}_T,y_T)$ are weakly
-linearly separable by margin $\gamma/R$.} Note that
+linearly separable with margin $\gamma/R$.} Note that
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}

### 2019-01-17 ICML-submission/notions-of-linear-separability.tex
Small fixes

--- 2019-01-16 ICML-submission/notions-of-linear-separability.tex
@@
 Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
-integer, and $\gamma$ be a positive real number. Let $L = ((x_1, y_1), (x_2,
-y_2), \dots, (x_T, y_T))$ be a sequence of labeled examples in $V \times
-\{1,2,\dots,K\}$.
-
-$L$ is said to be \emph{weakly linearly separable with a margin $\gamma$} if
-there exist vectors $w_1, w_2, \dots, w_K \in V$ such that
+integer, and $\gamma$ be a positive real number. Labeled examples $(x_1, y_1),
+(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are said to be
+\emph{weakly linearly separable with a margin $\gamma$} if there exist vectors
+$w_1, w_2, \dots, w_K \in V$ such that
 \begin{align}
@@
 Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
-integer, and $\gamma$ be a positive real number. Let $L = ((x_1, y_1), (x_2,
-y_2), \dots, (x_T, y_T))$ be a sequence of labeled examples in $V \times
-\{1,2,\dots,K\}$.
-
-$L$ is said to be \emph{strongly linearly separable with a
-margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
-that
+integer, and $\gamma$ be a positive real number. Labeled examples $(x_1, y_1),
+(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are said to be
+\emph{strongly linearly separable with a margin $\gamma$} if there exist vectors
+$w_1, w_2, \dots, w_K \in V$ such that
 \begin{align}
@@
 
-The notion of weak linear separability with a margin is standard. It is used in
-the full-information setting to upper bound the number of mistakes of the
-\textsc{Multiclass Perceptron} algorithm. It is a folklore result that if a set
-of labeled examples is separable with a margin $\gamma$ and the norm of the
-examples is bounded by $R$, then \textsc{Multiclass Perceptron} algorithm makes
-at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$ mistakes. Another folklore
-result is that \textsc{Multiclass Perceptron} is essentially optimal in the
-sense that any (possibly randomized) algorithm must make $\frac{1}{2}
-\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
-completeness, we state the \textsc{Multiclass Perceptron} algorithm and give
-proofs of both of these results in
+The notion of weak linear separability is a standard assumption used in the
+full-information setting to upper bound the number of mistakes of the
+\textsc{Multiclass Perceptron} algorithm. Namely, \citet{Crammer-Singer-2003}
+prove that if the examples are weakly linearly separable with a margin $\gamma$
+and the norm of the examples is bounded by $R$, then \textsc{Multiclass
+Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
+mistakes. It is a folklore result that \textsc{Multiclass Perceptron} is
+essentially optimal in the sense that any (possibly randomized) algorithm must
+make $\frac{1}{2} \left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the
+worst case. For completeness, we state the \textsc{Multiclass Perceptron}
+algorithm and give proofs of both of these results in
 Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
 material.
-
-\chicheng{Shall we mention that this multiclass margin notion has also appeared in e.g.~\cite{Crammer-Singer-2003}?}
 
@@
 
-It is easy to see that if a sequence of labeled examples is strongly linearly
+It is easy to see that if a set of labeled examples is strongly linearly
 separable with margin $\gamma$, then it is also weakly linearly separable with
@@
 
-In the special case of $K=2$, if a sequence of labeled examples is weakly
+In the special case of $K=2$, if a set of labeled examples is weakly
 linearly separable with a margin $\gamma$, then it is also strongly linearly
@@
 $120^\circ$ wedge. In other words, each class lies in an intersection of two
-halfspaces.
-\chicheng{Do we have an explicit formula for $W$ in this example? It might help
-to provide it.}
-
-While the examples are weakly linearly separable with a positive margin
+halfspaces. While the examples are weakly linearly separable with a positive margin
 $\gamma$, they are \emph{not} strongly linearly separable with any positive

### 2019-01-17 arxiv-version/np-hardness-of-the-weak-labeling-problem.tex
minor edits in arxiv version
Unify bibfiles

@@
 
-The hardness proof is based on a reduction from the set splitting problem, which is proven to be NP-complete by Lovasz \cite{garey1979computers}, to our weak labeling problem.
-The reduction is adapted from \cite{blum1989training}.
+The hardness proof is based on a reduction from the set splitting problem, which is proven to be NP-complete by Lovasz \cite{Garey-Johnson-1979}, to our weak labeling problem.
+The reduction is adapted from \cite{Blum-Rivest-1993}.
 \begin{figure}[h]
@@
 Thus the above inequality contradicts that Type 3 samples have label 3.
-Therefore, $c_j \subset S_1$.
-If we assume there exists some $c_j \not\subset S_2$, same arguments apply and also lead to contradiction.
+Therefore, $c_j \not\subset S_1$.
+If we assume there exists some $c_j \subset S_2$, same arguments apply and also lead to contradiction.
 \end{proof}

### 2019-01-17 ICML-submission/main-all.tex
Switch to one .tex file
Move proofs for strongly separable data to appendix
a version within page limit
Add NP-hardness of weak labeling problem

--- 2019-01-09 ICML-submission/main-supplementary.tex
@@
 \input{notions-of-linear-separability}
+\input{algorithm-for-strongly-linearly-separable-data}
+\input{from-weak-separability-to-strong-separability}
 
@@
 
+\input{appendix-multiclass-perceptron}
+\input{appendix-proofs-for-strongly-separable-examples}
+\input{appendix-margin-transformation}
+\input{appendix-poly-norm-to-rkhs-norm}
+\input{appendix-proofs-of-polynomial-approximation-theorems}
+\input{np-hardness-of-the-weak-labeling-problem}
+
 \end{document}

### 2019-01-17 ICML-submission/np-hardness-of-the-weak-labeling-problem.tex
Add NP-hardness of weak labeling problem

--- 2019-01-17 arxiv-version/np-hardness-of-the-weak-labeling-problem.tex
@@
 
-Formally, the weak labeling problem can be described as below:
+We use for $1,2,\dots,K$ for strong labels and $\overline{1}, \overline{2},
+\dots, \overline{K}$ for weak labels. We adopt the convention that
+$\overline{\overline{i}} = i$ for any positive integer $i$. Formally, the weak
+labeling problem can be described as below:
 \begin{figure}[H]
@@
 \end{center}
-\textbf{Given: } A set of feature-label pairs: $\{(x_t, y_t)\}_{t=1}^T \subseteq \{0,1\}^d \times \{1,2,\ldots, K, \overline{1}, \overline{2}, \ldots, \overline{K}\}$. \\
-\textbf{Question: } Do there exist $ w_1, \ldots, w_K \in \R^d$ such that for all $t=1, \ldots, T$,
+\textbf{Given:} Feature-label pairs $(x_1, y_1)$, $(x_2, y_2)$, \dots, $(x_T, y_T)$ in $\{0,1\}^d \times \{1,2,\dots, K, \overline{1}, \overline{2}, \dots, \overline{K}\}$. \\
+\textbf{Question:} Do there exist $ w_1, w_2, \dots, w_K \in \R^d$ such that for all $t=1,2,\dots,T$,
 \begin{align*}
-y_t \in \{1,2,\dots,K\} \qquad & \Longrightarrow \qquad & \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \qquad & \ip{w_{y_t}}{x_t}  > \ip{w_i}{x_t} \; , \\
-y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \qquad & \Longrightarrow & \qquad \exists i \in \{1,2,\dots,K\} \qquad & \ip{w_i}{x_t} > \ip{w_{\overline{y_t}}}{x_t} \; .
+& y_t \in \{1,2,\dots,K\} \Longrightarrow  \\
+& \quad \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \quad \ip{w_{y_t}}{x_t}  > \ip{w_i}{x_t} \; , \\
+& \text{and} \\
+& y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \Longrightarrow \\
+& \quad \exists i \in \{1,2,\dots,K\} \quad \ip{w_i}{x_t} > \ip{w_{\overline{y_t}}}{x_t} \; ?
 \end{align*}
@@
 
-%Formally, the input to the decision problem are positive integers $d, T, K$ and
-%a sequence $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \{0,1\}^d \times
-%\{1,2,\dots,K, \overline{1}, \overline{2}, \dots, \overline{K}\}$ of strongly
-%and weakly labeled examples. The numbers $1,2,\dots,K$ correspond to strong
-%labels and the symbols $\overline{1}, \overline{2}, \dots, \overline{K}$
-%correspond to weak labels. We adopt the convention that $\overline{\overline{i}}
-%= i$ for any positive integer $i$. The goal is to determine whether or not there
-%exist vectors $w_1, w_2, \dots, w_K \in \R^d$ that satisfy the following
-%conditions for all $t=1,2,\dots,T$,
-%\begin{align*}
-%y_t \in \{1,2,\dots,K\} \qquad & \Longrightarrow \qquad & \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \qquad \ip{w_{y_t}}{x_t} & > \ip{w_i}{x_t} \; , \\
-%y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \qquad & \Longrightarrow & \qquad \exists i \in \{1,2,\dots,K\} \qquad \ip{w_i}{x_t} & > \ip{w_{\overline{y_t}}}{x_t} \; .
-%\end{align*}
-
-The hardness proof is based on a reduction from the set splitting problem, which is proven to be NP-complete by Lovasz \cite{Garey-Johnson-1979}, to our weak labeling problem.
-The reduction is adapted from \cite{Blum-Rivest-1993}.
-\begin{figure}[h]
+The hardness proof is based on a reduction from the set splitting problem, which
+is proven to be NP-complete by Lovasz \cite{Garey-Johnson-1979}, to our weak
+labeling problem. The reduction is adapted from \cite{Blum-Rivest-1993}.
+\begin{figure}[H]
 \begin{framed}
@@
 \end{center}
-\textbf{Given: } A finite set $S$ and a collection $C$ of subsets $c_i$ of $S$. \\
-\textbf{Question: } Do there exist disjoint sets $S_1$ and $S_2$ such that $S_1 \cup S_2 = S$ and $\forall i, c_i\not\subseteq S_1$ or $c_i\not\subseteq S_2$?
+\textbf{Given:} A finite set $S$ and a collection $C$ of subsets $c_i$ of $S$. \\
+\textbf{Question:} Do there exist disjoint sets $S_1$ and $S_2$ such that $S_1 \cup S_2 = S$ and $\forall i, c_i\not\subseteq S_1$ or $c_i\not\subseteq S_2$?
 \end{framed}
@@
 
-Below we show the reduction. Suppose we are given a set splitting problem with inputs:
+Below we show the reduction. Suppose we are given an instance of the set
+splitting problem
 \begin{align*}
-    &S = \{1, 2, \ldots, N\}, \\
-    &C = \{c_1, \ldots, c_M\}, \\
-    &\forall i, c_i \subseteq S.
+S & = \{1, 2, \dots, N\} \; , \\
+C & = \{c_1, c_2, \dots, c_M\} \; .
 \end{align*}
 
-Then we create the weak labeling instance as follows.
-Let $d=N+1$ and $K=3$.
-Define $\zero$ as the zero vector $(0,\ldots, 0)\in \R^N$ and $\e_i$ as the $i$-th standard vector $(0,\ldots, 1, \ldots, 0)\in \R^N$).
-Then we include all the following feature-label pairs:
+We create the weak labeling instance as follows. Let $d=N+1$ and $K=3$.
+Define $\zero$ as the zero vector $(0,\dots,0)\in \R^N$ and $\e_i$ as the
+$i$-th standard vector $(0,\dots, 1, \dots, 0)\in \R^N$). Then we include all
+the following feature-label pairs:
 \begin{itemize}
 \item Type 1: $(x,y)=((\zero,1), 3)$,
-    \item Type 2: $(x,y)=((\e_i,1), \overline{3})$, $\forall i\in [N]$,
-    \item Type 3: $(x,y)=\left(\left(\sum_{i\in c_j} \e_i, 1\right), 3\right)$, $\forall j\in[M]$.
+\item Type 2: $(x,y)=((\e_i,1), \overline{3})$ for all $i \in \{1,2,\dots,N\}$,
+\item Type 3: $(x,y)=\left(\left(\sum_{i\in c_j} \e_i, 1\right), 3\right)$ for all $j \in \{1,2,\dots,M\}$.
 \end{itemize}
 
-For example, if we have $S=\{1,2,3\}$, $C=\{c_1, c_2\}$, $c_1 = \{1,2\}$, $c_2=\{2,3\}$, then we create the weak labeling sample set as:
-\begin{align*}
-    \{((0,0,0,1),3), ((1,0,0,1),\overline{3}), ((0,1,0,1),\overline{3}), ((0,0,1,1),\overline{3}), ((1,1,0,1),3), ((0,1,1,1),3)\}.
-\end{align*}
-The following lemma shows that answering this weak labeling problem is equivalent to answering the original set splitting problem.
+For example, if we have $S=\{1,2,3\}$, $C=\{c_1, c_2\}$, $c_1 = \{1,2\}$,
+$c_2=\{2,3\}$, then we create the weak labeling sample set as:
+\begin{multline*}
+\{
+((0,0,0,1),3), ((1,0,0,1),\overline{3}), ((0,1,0,1),\overline{3}), \\
+((0,0,1,1),\overline{3}), ((1,1,0,1),3), ((0,1,1,1),3)
+\} \; .
+\end{multline*}
+The following lemma shows that answering this weak labeling problem is
+equivalent to answering the original set splitting problem.
+
 \begin{lemma}
-Suppose we are given a set splitting problem, and we construct a weak labeling problem as described above.
-Then the set splitting problem has a solution $\Longleftrightarrow$ the constructed weak labeling problem has a solution.
+Any instance of the set splitting problem is a YES instance if and only if the
+corresponding instance of the weak labeling problem (as described above) is a
+YES instance.
 \end{lemma}
+
 \begin{proof}
 $(\Longrightarrow)$ Let $S_1, S_2$ be the solution of the set splitting problem. Define
+$$
+w_1 = \left(a_1, a_2, \cdots, a_N, -\frac{1}{2}\right),
+$$
+where for all $i \in \{1,2,\dots,N\}$, $a_i=1$ if $i\in S_1$ and $a_i=-N$ if
+$i\notin S_1$. Similarly, define
+$$
+w_2 = \left(b_1, b_2, \cdots, b_N, -\frac{1}{2}\right),
+$$
+where for all $i \in \{1,2,\dots,N\}$, $b_i=1$ if $i \in S_2$ and $b_i=-N$ if
+$i\notin S_2$. Finally, define
+$$
+w_3 = (0,0,\cdots, 0),
+$$
+the zero vector. To see this is a solution for the weak labeling problem, we
+verify separately for Type 1-3 samples defined above. For Type 1 sample, we have
+$$
+\ip{w_3}{x} = 0 > -\frac{1}{2} = \ip{w_1}{x}=\ip{w_2}{x}.
+$$
+For a Type 2 sample that corresponds to index $i$, we have either $i\in S_1$ or
+$i\in S_2$ because $S_1\cup S_2 = \{1,2,\dots,N\}$ is guaranteed. Thus, either
+$a_i=1$ or $b_i=1$. If $a_i=1$ is the case, then
+$$
+\ip{w_1}{x} = a_i - \frac{1}{2} = \frac{1}{2} > 0 = \ip{w_3}{x};
+$$
+similarly if $b_i=1$, we have $\ip{w_2}{x}>\ip{w_3}{x}$. \\ For a Type 3 sample
+that corresponds to index $j$, Since $c_j \not\subset S_1$, there exists some
+$i'\in c_j$ and $i'\notin S_1$. Thus we have $x_{i'}=1$, $a_{i'}=-N$, and
+therefore
 \begin{align*}
-     w_1 = \left(a_1, a_2, \cdots, a_N, -\frac{1}{2}\right),
+\ip{w_1}{x}
+& = a_{i'}x_{i'} + \sum_{i\in \{1,2,\dots,N\} \setminus \{i'\}} a_ix_i - \frac{1}{2} \\
+& \le -N + (N-1)-\frac{1}{2} \\
+& < 0 = \ip{w_3}{x} \; .
 \end{align*}
- where $\forall i\in[N]$, $a_i=1$ if $i\in S_1$ and $a_i=-N$ if $i\notin S_1$.
- Similarly, define
- \begin{align*}
-     w_2 = \left(b_1, b_2, \cdots, b_N, -\frac{1}{2}\right),
- \end{align*}
- where $\forall i\in[N]$, $b_i=1$ if $i\in S_2$ and $b_i=-N$ if $i\notin S_2$.
- Finally, define
- \begin{align*}
-     w_3 = (0,0,\cdots, 0),
- \end{align*}
- the zero vector. To see this is a solution for the weak labeling problem, we verify separately for Type 1-3 samples defined above. For Type 1 sample, we have
- \begin{align*}
-     \ip{w_3}{x} = 0 > -\frac{1}{2} = \ip{w_1}{x}=\ip{w_2}{x}.
- \end{align*}
- For a Type 2 sample that corresponds to index $i$, we have either $i\in S_1$ or $i\in S_2$ because $S_1\cup S_2 = [N]$ is guaranteed. Thus, either $a_i=1$ or $b_i=1$. If $a_i=1$ is the case, then
- \begin{align*}
-     \ip{w_1}{x}=a_i-\frac{1}{2}=\frac{1}{2} > 0 = \ip{w_3}{x};
- \end{align*}
- similarly if $b_i=1$, we have $\ip{w_2}{x}>\ip{w_3}{x}$. \\
- For a Type 3 sample that corresponds to index $j$, Since $c_j \not\subset S_1$, there exists some $i'\in c_j$ and $i'\notin S_1$. Thus we have $x_{i'}=1$, $a_{i'}=-N$, and therefore
- \begin{align*}
-     \ip{w_1}{x}= a_{i'}x_{i'} + \sum_{i\in [N]\backslash\{i'\}} a_ix_i - \frac{1}{2} \leq -N + (N-1)-\frac{1}{2} < 0 = \ip{w_3}{x}.
- \end{align*}
- Because $c_j \not\subset S_2$ also holds, we also have $\ip{w_2}{x}<\ip{w_3}{x}$. This direction is therefore proved. \\
+Because $c_j \not\subset S_2$ also holds, we also have
+$\ip{w_2}{x}<\ip{w_3}{x}$. This direction is therefore proved. \\
 \ \\
@@
 \begin{align*}
-     S_1 &= \left\{i\in [N] \Big| \ip{w_1-w_3}{(\e_i, 1)} > 0 \right\}, \\
-     S_2 &= \left\{i\in [N] \Big| \ip{w_2-w_3}{(\e_i, 1)} > 0 \text{\ and\ } i\notin S_1 \right\}.
+S_1 &= \left\{i \in \{1,2,\dots,n\} ~:~ \ip{w_1-w_3}{(\e_i, 1)} > 0 \right\}, \\
+S_2 &= \left\{i \in \{1,2,\dots,n\} ~:~ \ip{w_2-w_3}{(\e_i, 1)} > 0 \text{\ and\ } i\notin S_1 \right\}.
 \end{align*}
- It is not hard to see $S_1 \cap S_2 = \emptyset$ and $S_1\cup S_2 = [N]$.
-The former is because $S_2$ only includes elements that are not in $S_1$.
-For the latter, note that $(\e_i, 1)$ is the feature vector for Type 2 samples.
-Because Type 2 samples all have label $\overline{3}$, for any $i\in [N]$, one of the following must hold: $\ip{w_1-w_3}{(\e_i, 1)}>0$ or $\ip{w_2-w_3}{(\e_i, 1)}>0$.
-This implies $i\in S_1$ or $i\in S_2$.
+It is not hard to see $S_1 \cap S_2 = \emptyset$ and $S_1\cup S_2 =
+\{1,2,\dots,N\}$. The former is because $S_2$ only includes elements that are
+not in $S_1$. For the latter, note that $(\e_i, 1)$ is the feature vector for
+Type 2 samples. Because Type 2 samples all have label $\overline{3}$, for any $i
+\in \{1,2,\dots,N\}$, one of the following must hold: $\ip{w_1-w_3}{(\e_i,
+1)}>0$ or $\ip{w_2-w_3}{(\e_i, 1)}>0$. This implies $i\in S_1$ or $i\in S_2$.
 
- Now we show $\forall j$, $c_j \not\subset S_1$ and $c_j \not\subset S_2$ by contraction.
-Assume there exists some $j$ such that $c_j \subset S_1$.
-By our definition of $S_1$, we have $\ip{w_1-w_3}{(\e_i, 1)} > 0$ for all $i\in c_j$.
+Now we show $\forall j$, $c_j \not\subset S_1$ and $c_j \not\subset S_2$ by
+contraction. Assume there exists some $j$ such that $c_j \subset S_1$. By our
+definition of $S_1$, we have $\ip{w_1-w_3}{(\e_i, 1)} > 0$ for all $i\in c_j$.
 Therefore,
 \begin{align*}
-     \sum_{i\in c_j}\ip{w_1-w_3}{\left(\e_i, 1\right)} = \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, |c_j|\right)} > 0.
+\sum_{i\in c_j} \ip{w_1-w_3}{\left(\e_i, 1\right)}
+& = \ip{w_1-w_3}{\left(\sum_{i\in c_j} \e_i, |c_j|\right)}  \\
+& > 0.
 \end{align*}
 Because Type 1 sample has label $3$, we also have
- \begin{align*}
+$$
 \ip{w_1-w_3}{\left(\zero, 1\right)} < 0.
- \end{align*}
+$$
 Combining the above two inequalities, we get
 \begin{align*}
-     \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, 1\right)} = \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, |c_j|\right)} - (|c_j|-1)\ip{w_1-w_3}{\left(\zero, 1\right)}>0.
+& \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, 1\right)} \\
+& = \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, |c_j|\right)}  \\
+& \qquad - (|c_j|-1)\ip{w_1-w_3}{\left(\zero, 1\right)} \\
+& > 0 \; .
 \end{align*}
- Note that $\left(\sum_{i\in c_j}\e_i, 1\right)$ is a feature vector for Type 3 samples.
-Thus the above inequality contradicts that Type 3 samples have label 3.
-Therefore, $c_j \not\subset S_1$.
-If we assume there exists some $c_j \subset S_2$, same arguments apply and also lead to contradiction.
+Note that $\left(\sum_{i\in c_j}\e_i, 1\right)$ is a feature vector for Type 3
+samples. Thus the above inequality contradicts that Type 3 samples have label 3.
+Therefore, $c_j \not\subset S_1$. If we assume there exists some $c_j \subset
+S_2$, same arguments apply and also lead to contradiction.
 \end{proof}

### 2019-01-17 ICML-submission/from-weak-separability-to-strong-separability.tex
Some fixes in section 5.1

@@
 \end{theorem}
-%$\norm{\phi(x_1)}_{\ell_2},
-%\norm{\phi(x_2)}_{\ell_2}, \dots, \norm{\phi(x_T)}_{\ell_2} \le 2$
 
@@
 
-\paragraph{Overview.} The idea behind the construction and analysis of the mapping
-$\phi$ is polynomial approximation. Specifically, we give $k$ polynomials $p_1$,
-$\ldots$, $p_k$, such that:
+\paragraph{Overview.} The idea behind the construction and analysis of the
+mapping $\phi$ is polynomial approximation. Specifically, we construct $K$
+multivariate polynomials $p_1, p_2, \dots,p_K$ such that:
 \begin{align}
 \label{equation:poly-pos}
-& \forall t \in \cbr{1,2,\dots,T}, p_{y_t}(x_t) \ge \frac{\gamma'}2 \; ,
+& \forall t \in \cbr{1,2,\dots,T}, p_{y_t}(x_t) \ge \frac{\gamma'}{2} \; ,
 \\
@@
 \forall t \in \cbr{1,2,\dots,T} \ \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t} \\
-p_i(x_t) \leq -\frac{\gamma'}2 \; .
+p_i(x_t) \le - \frac{\gamma'}{2} \; .
 \end{gathered}
 \end{align}
-As each polynomial $p_i$ can be written as $\ip{c_i}{\phi(x)}$ for some $c_i \in
-\ell_2$, it immediately shows that the set of examples $(\phi(x_1),y_1), \ldots,
-(\phi(x_T),y_T)$ is strongly linear separable.
+We then show (\autoref{lemma:norm-bound}) that each polynomial $p_i$ can be
+expressed as $\ip{c_i}{\phi(x)}_{\ell_2}$ for some $c_i \in \ell_2$. This
+immediately implies that that the examples $(\phi(x_1),y_1), \ldots,
+(\phi(x_T),y_T)$ are strongly linearly separable with margin $\gamma'$.
 
-To construct $p_1, p_2, \dots, p_k$ that satisfy
-Equations~\eqref{equation:poly-pos} and~\eqref{equation:poly-neg}, we consider
-constructing each $p_i$ separately. Specifically, $p_i$ needs to satisfy that:
+The conditions \eqref{equation:poly-pos} and~\eqref{equation:poly-neg} are
+equivalent to that
 \begin{align}
 \label{equation:poly-pos-i}
-\forall t \in \cbr{1,2,\dots,T}, y_t = i \Rightarrow p_i(y_t) \ge \frac{\gamma'}2 \; , \\
+\forall t \in \cbr{1,2,\dots,T}, y_t = i \quad \Rightarrow \quad p_i(y_t) \ge \frac{\gamma'}{2} \; , \\
 \label{equation:poly-neg-i}
-\forall t \in \cbr{1,2,\dots,T}, y_t \neq i \Rightarrow p_i(y_t) \le -\frac{\gamma'}2 \; .
+\forall t \in \cbr{1,2,\dots,T}, y_t \neq i \quad \Rightarrow \quad p_i(y_t) \le -\frac{\gamma'}{2} \; .
 \end{align}
+hold for all $i \in \{1,2,\dots,K\}$. We can thus fix $i$ and focus on
+construction of one particular polynomial $p_i$.
 
-Under the weak linear separability assumption, we note that all examples from
-class $i$ lie in
-\[ R_i^+ = \bigcap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \norm{x} \le 1, \ip{w_i^* - w_j^*}{x} \geq \gamma}, \] and all examples from the remaining classes lie in
-\[ R_i^- = \bigcup_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \norm{x} \le 1, \ip{w_i^* - w_j^*}{x} \leq  -\gamma}. \]
-Therefore, to satisfy Equations~\eqref{equation:poly-pos-i}
+Since examples $(x_1,y_1), (x_2, y_2), \dots, (x_T,y_T)$ are weakly linearly separable,
+all examples from class $i$ lie in
+$$
+R_i^+ = \!\!\!\!\! \!\!\!\!\! \bigcap_{j \in \cbr{1,2,\dots,K} \setminus \cbr{i}} \cbr{x \in \B(0,1) ~:~ \ip{w_i^* - w_j^*}{x} \ge \gamma},
+$$
+and all examples from the remaining classes lie in
+$$
+R_i^- = \!\!\!\!\! \!\!\!\!\! \bigcup_{j \in \cbr{1,2,\dots,K} \setminus \cbr{i}} \cbr{x \in \B(0,1) ~:~ \ip{w_i^* - w_j^*}{x} \le -\gamma}.
+$$
+Therefore, to satisfy conditions~\eqref{equation:poly-pos-i}
 and~\eqref{equation:poly-neg-i}, it suffices to construct $p_i$ such that:
 \begin{align}
-x \in R_i^+ & \Rightarrow p_i(x) \ge \frac {\gamma'} 2
 \label{eqn:r-plus}
-\\
+x \in R_i^+ & \Rightarrow p_i(x) \ge \frac {\gamma'} 2 \\
+\label{eqn:r-minus}
 x \in R_i^- & \Rightarrow p_i(x) \le - \frac {\gamma'} 2
-\label{eqn:r-minus}
 \end{align}

### 2019-01-18 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Fixes

@@
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
-optimal upto a constant factor, as long as the number of classes $K$ is at most
+optimal up to a constant factor, as long as the number of classes $K$ is at most
 $O((R/\gamma)^2)$. This lower bound is stated as

### 2019-01-18 ICML-submission/from-weak-separability-to-strong-separability.tex
Fixes

@@
 mapping $\phi$ is polynomial approximation. Specifically, we construct $K$
-multivariate polynomials $p_1, p_2, \dots,p_K$ such that:
+multivariate polynomials $p_1, p_2, \dots,p_K$ such that
 \begin{align}
@@
 Therefore, to satisfy conditions~\eqref{equation:poly-pos-i}
-and~\eqref{equation:poly-neg-i}, it suffices to construct $p_i$ such that:
+and~\eqref{equation:poly-neg-i}, it suffices to construct $p_i$ such that
 \begin{align}
 \label{eqn:r-plus}
-x \in R_i^+ & \Rightarrow p_i(x) \ge \frac {\gamma'} 2 \\
+x \in R_i^+ \qquad & \Longrightarrow \qquad p_i(x) \ge \frac {\gamma'} 2 \; , \\
 \label{eqn:r-minus}
-x \in R_i^- & \Rightarrow p_i(x) \le - \frac {\gamma'} 2
+x \in R_i^- \qquad & \Longrightarrow \qquad p_i(x) \le - \frac {\gamma'} 2 \; .
 \end{align}

### 2019-01-18 ICML-submission/introduction.tex
Fixes

@@
 making its prediction, the learner receives feedback. In contrast with the
-standard full information setting (where the feedback given is the correct label
+standard full-information setting (where the feedback given is the correct label
 $y_t$), here the feedback is only a binary indicator of whether the prediction
@@
 setting, as the algorithm only makes updates on a subset of the $w_i$'s.} We
-design a simple and efficient algorithm, namely
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
-that has an expected number of mistakes at most $O(K (R/\gamma)^2))$.
-The memory complexity and per-round time complexity are both $O(dK)$.
-The algorithm can be viewed as running $K$ copies of the \textsc{Binary
-Perceptron} algorithm, one copy for each class. Intuitively speaking, the $O(K)$
-multiplicative factor in the mistake bound is the price we pay for the bandit
-feedback, or more precisely, the lack of full-information feedback. We prove
-that any (possibly randomized) algorithm must make $\Omega(K (R/\gamma)^2))$
-mistakes in the worst case.
+design a simple and efficient algorithm
+(Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
+that makes at most $O(K (R/\gamma)^2))$ mistakes in expectation. Its memory
+complexity and per-round time complexity are both $O(dK)$. The algorithm can be
+viewed as running $K$ copies of the \textsc{Binary Perceptron} algorithm, one
+copy for each class. We prove that any (possibly randomized) algorithm must make
+$\Omega(K (R/\gamma)^2))$ mistakes in the worst case. The extra $O(K)$
+multiplicative factor the mistake bound, as compared to the full-information
+setting, is the price we pay for the bandit feedback, or more precisely, the
+lack of full-information feedback.
 
@@
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} for
-the strongly separable case, namely Algorithm~\ref{algorithm:kernelized}. (For
-details on kernel methods see e.g.~\citet{Scholkopf-Smola-2002} or
-\citet{Shawe-Taylor-Cristianini-2004}.) The kernel $k(x,x')$ corresponding to
-the feature mapping $\phi$ has a simple explicit formula and can be computed in
-$O(d)$ time, making Algorithm~\ref{algorithm:kernelized} computationally
-efficient.
+the strongly separable case (Algorithm~\ref{algorithm:kernelized}). The kernel
+$k(x,x')$ corresponding to the feature mapping $\phi$ has a simple explicit
+formula and can be computed in $O(d)$ time, making
+Algorithm~\ref{algorithm:kernelized} computationally efficient. For details on
+kernel methods see e.g.~\citet{Scholkopf-Smola-2002} or
+\citet{Shawe-Taylor-Cristianini-2004}.
 

### 2019-01-18 ICML-submission/notions-of-linear-separability.tex
Fixes

@@
 worst case. For completeness, we state the \textsc{Multiclass Perceptron}
-algorithm and give proofs of both of these results in
-Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
+algorithm, the upper and lower bound on the number of mistakes, and their proofs
+in Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
 material.

### 2019-01-18 ICML-submission/from-weak-separability-to-strong-separability.tex
Fixes

@@
 According to the well known Stone-Weierstrass theorem~\citep[see
-e.g.][Section~10.10]{Davidson-Donsig-2010}, on a compact set,
-multivariate polynomials uniformly approximate any continuous function.
-Intuitively speaking, we use a multivariate polynomial to approximate, on the
-unit ball of $\R^d$, some scaling of the indicator function corresponding to the intersection of
-$m=K-1$ halfspaces $\bigcap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i^* - w_j^*}{x} \geq 0}$. Within margin $\gamma$ along the decision boundary, we allow
-the polynomial to attain arbitrary value. To be able to quantify $\gamma'$
-we need to quantify certain parameters of the approximating polynomial.
-Following the constructions in~\citet{Klivans-Servedio-2008}
-(which in turn use the constructions in~\citet{Beigel-Reingold-Spielman-1995}), we
-construct two different polynomials with different parameters that satisfy
-Equation~\eqref{eqn:r-plus} and~\eqref{eqn:r-minus}.
-The parameters
-are quantified in
-Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
-stated below.
+e.g.][Section~10.10]{Davidson-Donsig-2010}, on a compact set, multivariate
+polynomials uniformly approximate any continuous function. Roughly speaking, the
+conditions \eqref{eqn:r-plus} and \eqref{eqn:r-minus} mean that $p_i$
+approximates on $\B(0,1)$ a scalar multiple of the indicator function of the
+intersection of $K-1$ halfspaces $\bigcap_{j \in \cbr{1,2,\dots,K} \setminus
+\cbr{i}} \cbr{x: \ip{w_i^* - w_j^*}{x} \geq 0}$ while within margin $\gamma$ along
+the decision boundary, the polynomial is allowed to attain arbitrary values.
+It is thus clear such a polynomial exists.
 
-%The polynomial separates examples in
-%one class from examples in the other classes.
-%
-%the indicator function corresponding to the intersection of
-%$m=K-1$ halfspaces
-%a function that takes value $\frac {\gamma'} 2$ on $R_i^+$
-%and $-\frac {\gamma'} 2$ on $R_i^-$
+We give two explicit constructions for such polynomial in
+Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}.
+Our constructions are based on \citet{Klivans-Servedio-2008} which in turn uses
+the constructions from~\citet{Beigel-Reingold-Spielman-1995}. More importantly,
+the theorems quantify certain parameters of the polynomial, which will allow us
+to give an upper bound on the transformed margin $\gamma'$.
 
-\paragraph{Details of the proof.} Before we state the theorems, recall that a polynomial of $d$ variables is a
+Before we state the theorems, recall that a polynomial of $d$ variables is a
 function $p:\R^d \to \R$ of the form
@@
 \begin{enumerate}
-\item $p(x) \ge 1/2$ \\ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
-\item $p(x) \le -1/2$ \\ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$,
+\item $p(x) \ge 1/2$ \\ for all $\displaystyle x \in R^+ = \bigcap_{i=1}^m \left\{ x \in \B(0,1) ~:~  \ip{v_i}{x} \ge \gamma \right\}$,
+\item $p(x) \le -1/2$ \\ for all $\displaystyle x \in R^- = \bigcup_{i=1}^m \left\{ x \in \B(0,1) ~:~  \ip{v_i}{x} \le - \gamma \right\}$,
 \item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$,
@@
 \item $\displaystyle p(x) \ge 1/2$ \\
-for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
+for all $\displaystyle x \in R^+ = \bigcap_{i=1}^m \left\{ x \in \B(0,1) ~:~ \ip{v_i}{x} \ge \gamma \right\}$,
 
 \item $\displaystyle p(x) \le - 1/2$ \\
-for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$,
+for all $\displaystyle x \in R^- = \bigcup_{i=1}^m \left\{ x \in \B(0,1) ~:~ \ip{v_i}{x} \le - \gamma \right\}$,
 
@@
 The proofs of the theorems can be found in
-Section~\ref{section:proof-of-polynomial-approximation}. The geometric
-interpretation of the two regions described in parts 1 and 2 of the theorems is
-explained in Figure~\ref{figure:pizza-slice}. Similar but weaker results were
-proved by~\citet{Klivans-Servedio-2008}. In particular, our bounds in parts 1,
-2, 3, 4 of
+Appendix~\ref{section:proof-of-polynomial-approximation} in the supplementary
+material. The geometric interpretation of the two regions described in parts 1
+and 2 of the theorems is explained in Figure~\ref{figure:pizza-slice}. Similar
+but weaker results were proved by~\citet{Klivans-Servedio-2008}. In particular,
+our bounds in parts 1, 2, 3, 4 of
 Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
@@
 \end{center}
-\caption[]{The figure shows the two regions used in parts 1 and 2 of
+\caption[]{The figure shows the two regions $R^+$ and $R^-$ used in parts 1 and
+2 of
 Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
 for the case $m=d=2$ and a particular choice of vectors $v_1, v_2$ and margin
-parameter $\gamma$. These regions are
-$R^+ = \displaystyle \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
-$R^- = \displaystyle \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
-The separating hyperplanes $\ip{v_1}{x} = 0$ and $\ip{v_2}{x} = 0$ are shown as dashed lines.}
+parameter $\gamma$. The separating hyperplanes $\ip{v_1}{x} = 0$ and
+$\ip{v_2}{x} = 0$ are shown as dashed lines.}
 \label{figure:pizza-slice}
@@
 
-The following lemma establishes a correspondence
-between any multivariate polynomial in $\R^d$
-and an element in $\ell_2$, and gives an upper bound on its norm.
-Its proof follows from simple algebra, which we defer to
+The following lemma establishes a correspondence between any multivariate
+polynomial in $\R^d$ and an element in $\ell_2$, and gives an upper bound on its
+norm. Its proof follows from simple algebra, which we defer to
 Appendix~\ref{section:proof-norm-bound}.
@@
 
-Using the lemma and the polynomial approximation theorems, we can prove the
-mapping $\phi$ maps any set of weakly linearly separable examples
-to a strongly linearly separable set of examples. Due to space constraints,
-we only sketch the
+Using the lemma and the polynomial approximation theorems, we can prove that the
+mapping $\phi$ maps any set of weakly linearly separable examples to a strongly
+linearly separable set of examples. Due to space constraints, we only sketch the
 proof of Theorem~\ref{theorem:margin-transformation} here, and defer the full
@@
 Since the examples $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ are weakly
-linearly separable with margin $\gamma$,, there are vectors $w_1, w_2, \dots, w_K$
+linearly separable with margin $\gamma$, there are vectors $w_1, w_2, \dots, w_K$
 satisfying \eqref{equation:weak-linear-separability-1} and
@@
 
-\paragraph{Case 1: $\gamma_1 \geq \gamma_2$.} In this setting, Theorem~\ref{theorem:polynomial-approximation-1}
-implies that there exist a multivariate polynomial $p_i:\R^d \to \R$
+\paragraph{Case 1: $\gamma_1 \geq \gamma_2$.} In this setting,
+Theorem~\ref{theorem:polynomial-approximation-1} implies that there exist a
+multivariate polynomial $p_i:\R^d \to \R$
 
@@
 \norm{p_i} & \le \left(188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
-\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; , \\
+\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; . \\
 \end{align*}
 By \autoref{lemma:norm-bound}, there exists $c_i \in \ell_2$ such that
-$\ip{c_i}{\phi(x)} = p_i(x)$, and
+$\ip{c_i}{\phi(x)}_{\ell_2} = p_i(x)$, and
 \begin{align*}

### 2019-01-18 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
nn alg

@@
 trivially satisfies the strong linear separability condition, and the
-$\frac{K-1}{2}$ expected mistake lower bound follows from Claim 2
-of~\citet{Daniely-Helbertal-2013}. However, it is unclear if the trivial lower
+$\frac{K-1}{2}$ expected mistake lower bound follows from ~\citep[][Claim 2]{Daniely-Helbertal-2013}. However, it is unclear if the trivial lower
 bound is the best possible if $K$ is large, i.e., $\omega((R/\gamma)^2)$. We

### 2019-01-18 ICML-submission/appendix-nearest-neighbor-algorithm.tex
nn alg

\section{Nearest neighbor algorithm}
\begin{algorithm}
\caption{A nearest-neighbor algorithm for \textsc{Online Multiclass Linear Classification with
Bandit Feedback}}
\begin{algorithmic}[1]
\STATE $S \gets \emptyset$.
\FOR{$t=1,2,\ldots,T$:}
\IF{$\min_{(x,y) \in S} \| x_t - x \|_2 \leq \gamma$}
	\STATE $\hat{y}_t \gets \tilde{y}$, where $(\tilde{x}, \tilde{y}) = \argmin_{(x,y) \in S} \| x_t - x \|_2$.
\ELSE
	\STATE Predict $\hat{y}_t$ uniformly at random from $\cbr{1,\ldots,K}$, receive feedback $z_t = \one[\hat{y}_t \neq y_t]$.
  \label{line:nn-explore}
	\IF{$z_t = 0$}
    \STATE $S \gets S \cup \cbr{(x_t, \hat{y}_t)}$.
  \ENDIF
\ENDIF
\ENDFOR
\end{algorithmic}
\label{alg:nn}
\end{algorithm}

We present Algorithm~\ref{alg:nn} in this section. The algorithm is based on the following insight.

\begin{lemma}
Suppose $(x_1,y_1), \ldots, (x_T, y_T)$ is a set of $\gamma$-weakly linearly separable examples.
For $i$, $j$ in $\cbr{1,\ldots,T}$, if $x_i$ and $x_j$ have $\ell_2$ distance at most $\gamma$, then $y_i = y_j$.
\label{lem:nn}
\end{lemma}
\begin{proof}
Suppose for the sake on contradiction that $y_i \neq y_j$. By Definition~\ref{definition:weak-linear-separability}, there exists a set of $k$ vectors $(w_1, \ldots, w_k)$, such that Equations~\eqref{equation:weak-linear-separability-1}
and~\eqref{equation:weak-linear-separability-1} are satisfied.

Specifically,
\[ \ip{w_{y_i} - w_{y_j}}{x_i} \geq \gamma \]
\[ \ip{w_{y_j} - w_{y_i}}{x_j} \geq \gamma \]

This implies that
\[ \ip{w_{y_i} - w_{y_j}}{x_i - x_j} \geq 2\gamma \]

On the other hand,
\[ \ip{w_{y_i} - w_{y_j}}{x_i - x_j} \leq \| w_{y_i} - w_{y_j} \| \| x_i - x_j \| \leq \sqrt{2} \gamma \]
where the first inequality is from Cauchy-Schwarz,
the second inequality is from that
$\|w_{y_i} - w_{y_j}\| \leq \sqrt{2(\|w_{y_i}\|^2 + \|w_{y_j}\|^2)} \leq \sqrt{2}$ and our assumption
on $x_i$ and $x_j$. Therefore, we reach a contradiction.
\end{proof}

\begin{theorem}
Suppose $(x_1,y_1), \ldots, (x_T, y_T)$ is a set of $\gamma$-weakly linearly separable examples. In addition, for all $t$ in $\cbr{1,\ldots,T}$, $\| x_t \| \leq R$. Then, the expected number of mistakes made by Algorithm~\ref{alg:nn} is such that
\[\Exp[M] \leq (K-1) (\frac R \gamma)^d. \]
\label{thm:margin_at_upper}
\end{theorem}
\begin{proof}
Let $b_t$ be the indicator that line~\ref{line:nn-explore} is executed at timestep $t$,
i.e. we fall into the ``else'' case.
Note that if $b_t = 0$, then by Lemma~\ref{lem:nn}, the prediction $\hat{y}_t$ must equal $y_t$, i.e. $z_t = 0$.
Therefore, $M = \sum_{t=1}^T z_t = \sum_{t=1}^T b_t z_t$. Let $U = \sum_{t=1}^T b_t (1-z_t)$; it can be seen that $U$ is the number of times when $S$ gets updated. As $S$ is a $\gamma$-packing over
$\cbr{x: \|x\|_2 \leq R}$, the size of $S$ is at most $(\frac R \gamma)^d$, which is also an upper bound on $U$.

Note that when $b_t = 1$, $\hat{y}_t$ is chosen uniformly at random, we have
\[ \Exp[ z_t | b_t = 1] = \frac{K-1}{K} \]
Therefore,
\[ \Exp[M] = \Exp[\sum_{t=1}^T b_t z_t] = \frac{K-1}{K} \Exp[\sum_{t=1}^T b_t]. \]
On the other hand,
\[ \Exp[U] = \Exp[\sum_{t=1}^T b_t (1-z_t)] = \frac 1 K \Exp[\sum_{t=1}^T b_t]. \]
Therefore,
\[ \Exp[M] = (K-1) \Exp[U] \leq (K-1) (\frac R \gamma)^d. \]
\end{proof}

### 2019-01-18 ICML-submission/introduction.tex
elaboration on Chen et al

@@
 mistake bound under the strong linear separability condition, their proof of
-Theorem 2 is incorrect: their Lemma 4 cannot be directly applied to the bandit
+Theorem 2 is incorrect: first, their Theorem 2
+implies a mistake upper bound of $\frac{R}{\gamma}$ with
+sufficiently large $C$, which contradicts our lower
+bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
+second, their Lemma 4 cannot be directly applied to the bandit
 setting, as the algorithm only makes updates on a subset of the $w_i$'s.} We

### 2019-01-19 ICML-submission/title-and-abstract.tex
Update title-and-abstract.tex
Changed the title

@@
 % Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Online Multiclass Linear Classification with Bandit Feedback}
+\icmltitlerunning{Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case}
 
 \twocolumn[
-\icmltitle{Online Multiclass Linear Classification with Bandit Feedback}
+\icmltitle{Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case}
 

### 2019-01-20 ICML-submission/title-and-abstract.tex
Update title-and-abstract.tex
Changed \frac to slash

@@
 algorithm that achieves a near-optimal mistake bound of
-$O\left(\frac{K}{\gamma^2} \right)$.
+$O\left( K/\gamma^2 \right)$.
 
@@
 an efficient algorithm with a mistake bound of $2^{\widetilde{O}(\min(K \log^2
-\frac{1}{\gamma}, \sqrt{\frac{1}{\gamma}} \log K))}$ \footnote{We use the notation
+(1/\gamma), \sqrt{1/\gamma} \log K))}$ \footnote{We use the notation
 $\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}. Our algorithm

### 2019-01-20 ICML-submission/introduction.tex
Update introduction.tex
Moved the discussion on the Multiclass Perceptron here from Section

@@
 Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
-The guarantees provided by \textsc{Multiclass Perceptron} is very satisfying,
-since it achieves an information-theoretically optimal mistake upper bound,
-while having low time and memory complexities.~\footnote{These are
+%%%%%
+It is also known that any (possibly randomized) algorithm must
+make $\frac{1}{2} \left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the
+worst case.
+These results guarantee that the \textsc{Multiclass Perceptron} achieves an
+information-theoretically optimal mistake upper bound, meanwhile it has
+low time and memory complexities.%
+%The guarantees provided by \textsc{Multiclass Perceptron} is very satisfying,
+%since it achieves an information-theoretically optimal mistake upper bound,
+%while having low time and memory complexities.
+%%%%%
+~\footnote{These are
 folklore results. For completeness, we present these results along

### 2019-01-20 ICML-submission/notions-of-linear-separability.tex
Update notions-of-linear-separability.tex
Moved the discussion on the Multiclass Perceptron lower bound to Section 1 from here.

--- 2019-01-17 ICML-submission/notions-of-linear-separability.tex
@@
 full-information setting to upper bound the number of mistakes of the
-\textsc{Multiclass Perceptron} algorithm. Namely, \citet{Crammer-Singer-2003}
-prove that if the examples are weakly linearly separable with a margin $\gamma$
-and the norm of the examples is bounded by $R$, then \textsc{Multiclass
-Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
-mistakes. It is a folklore result that \textsc{Multiclass Perceptron} is
-essentially optimal in the sense that any (possibly randomized) algorithm must
-make $\frac{1}{2} \left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the
-worst case. For completeness, we state the \textsc{Multiclass Perceptron}
-algorithm and give proofs of both of these results in
-Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
-material.
+\textsc{Multiclass Perceptron} algorithm.
+%%%%%
+(Recall our discussion on the topic in Section~\ref{section:introduction}.)
+%Namely, \citet{Crammer-Singer-2003}
+%prove that if the examples are weakly linearly separable with a margin $\gamma$
+%and the norm of the examples is bounded by $R$, then \textsc{Multiclass
+%Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
+%mistakes. It is a folklore result that \textsc{Multiclass Perceptron} is
+%essentially optimal in the sense that any (possibly randomized) algorithm must
+%make $\frac{1}{2} \left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the
+%worst case. For completeness, we state the \textsc{Multiclass Perceptron}
+%algorithm, the upper and lower bound on the number of mistakes, and their proofs
+%in Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
+%material.
+%%%%%
 

### 2019-01-20 ICML-submission/introduction.tex
Update introduction.tex
Shortened a footnote to save one line

@@
 %%%%%
-~\footnote{These are
-folklore results. For completeness, we present these results along
+~\footnote{
+%%%%%
+%These are folklore results. 
+For completeness, we present these 
+folklore
+%%%%%
+results along
 with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs} in the

### 2019-01-20 ICML-submission/related-work.tex
Update related-work.tex
Slightly edited the last two paragraphs to make them shorter

@@
 of the learner is to minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) -
-\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$. The online bandit multiclass
-learning problem can be seen a special case of the contextual bandits problem, where the
+\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
+%%%%%
+The bandit multiclass
+learning problem can be seen as a special case,
+% of the contextual bandits problem, 
+where the
 cost $c_t(i)$ is the classification error $\indicator{i \neq y_t}$, and the
@@
 (Wx)_y: W \in \R^{k \times d}}$. A series of works in the contextual bandits
-learning literature focus on
-oracle-efficiency~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
+learning literature 
+%focus on oracle-efficiency~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
+%Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
+%Syrgkanis-Krishnamurthy-Schapire-2016,
+%Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. Specifically, they 
+assume access to
+a policy optimization oracle that returns a policy in $\Pi$ that minimizes
+its empirical cost on any set of cost-sensitive examples, and 
+%the
+construct algorithms that call 
+%algorithm only calls 
+the oracle a polynomial number of times%
+~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
 Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
 Syrgkanis-Krishnamurthy-Schapire-2016,
-Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. Specifically, they assume access to
-a policy optimization oracle that can return the policy in $\Pi$ that minimizes
-its empirical cost on any set of cost-sensitive examples, and the algorithm only
-calls the oracle a polynomial number of times. However, these algorithms are not
+Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
+%%%%%
+However, these algorithms are not
 truly computationally efficient in our setting, as it is NP-hard in general to
@@
 s \gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
-information-theoretic regret upper bounds under various settings of $\calF$.
-On the other hand, it gives an
-efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of
+information-theoretic regret upper bounds
+%%%%%
+%under
+ for
+%%%%%
+various settings of $\calF$. On the other hand, it gives an efficient algorithm 
+%%%%%
+with an 
+%%%%%
+$O(\sqrt{T})$ regret against the benchmark of
 $\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$. A direct
 application of this result to \textsc{Online Bandit Multiclass Linear
-Classification} yields an algorithm with a $O(\sqrt{T})$ mistake bound in the
-strongly linearly separable setting.
+Classification} 
+%%%%%
+%yields 
+gives
+%%%%%
+an algorithm with $O(\sqrt{T})$ mistake bound in the
+strongly linearly separable %%%%%
+case.
+%%%%%
 

### 2019-01-20 ICML-submission/introduction.tex
Update introduction.tex
Changed frac to slash

@@
 Algorithm~\ref{algorithm:kernelized} makes at
-most $2^{\widetilde{O}(\min(K \log^2 \frac{1}{\gamma}, \sqrt{\frac{1}{\gamma}}
+most $2^{\widetilde{O}(\min(K \log^2 (1/\gamma), \sqrt{1/\gamma}
 \log K))}$ mistakes.

### 2019-01-20 ICML-submission/related-work.tex
Update related-work.tex
Changed frac to slash

@@
 inefficient algorithms that work in the weakly linearly separable setting, one
-with a mistake bound of $O(K^2 d \ln(\frac{d}{\gamma}))$, the other with a
-mistake bound of $\widetilde{O}(\frac{K^2}{\gamma^2} \ln T)$. The latter result
+with a mistake bound of 
+$O(K^2 d \ln(d/\gamma))$,
+the other with a
+mistake bound of $\widetilde{O}((K^2/\gamma^2) \ln T)$. The latter result
 was later improved by \citet{Daniely-Helbertal-2013}, which gives a
 computationally inefficient algorithm with a mistake upper bound of
-$\widetilde{O}(\frac{K}{\gamma^2})$. In addition, the authors propose the
+$\widetilde{O}(K/\gamma^2)$. 
+In addition, the authors propose the
 \textsc{Banditron} algorithm, a computationally efficient algorithm that has a

### 2019-01-20 ICML-submission/introduction.tex
Update introduction.tex
Replaced the cases in the definition of z_t in Protocol 1 by the indicator function. Additionally, introduced the notation of \one

@@
 \STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.}
-\STATE{Observe feedback $z_t \in \{0,1\}$, \\ \qquad where $z_t = \begin{cases}
-0 & \text{if $\widehat y_t = y_t$,} \\
-1 & \text{if $\widehat y_t \neq y_t$.}
-\end{cases}$
+\STATE{Observe feedback
+$z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
+%$z_t \in \{0,1\}$, \\ \qquad where $z_t = \begin{cases}
+%0 & \text{if $\widehat y_t = y_t$,} \\
+%1 & \text{if $\widehat y_t \neq y_t$.}
+%\end{cases}$
 }
@@
 The performance of the learner is measured by its cumulative number of
-mistakes $\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$.
+mistakes $\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$,
+where $\one$ denotes the indicator function..
 

### 2019-01-20 ICML-submission/notions-of-linear-separability.tex
Update notions-of-linear-separability.tex
Merged the definition of the weak and the strong separability together

@@
 
-\begin{definition}[Weak linear separability]
+\begin{definition}
+[Linear separability]
 \label{definition:weak-linear-separability}
 Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
-integer, and $\gamma$ be a positive real number. Labeled examples $(x_1, y_1),
-(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are said to be
+integer, and $\gamma$ be a positive real number. 
+We say that labeled examples $(x_1, y_1),
+(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are 
+%said to be
+\begin{enumerate}
+\item
 \emph{weakly linearly separable with a margin $\gamma$} if there exist vectors
@@
 \forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
-\ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; .
+\ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; ,
 \end{gathered}
 \end{align}
-\end{definition}
-
-\begin{definition}[Strong linear separability]
-\label{definition:strong-linear-separability}
-Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
-integer, and $\gamma$ be a positive real number. Labeled examples $(x_1, y_1),
-(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are said to be
+\item
 \emph{strongly linearly separable with a margin $\gamma$} if there exist vectors
@@
 & \begin{gathered}
-\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
+\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
 \ip{x_t}{w_i} \le - \frac \gamma 2 \; .
@@
 \end{align}
+\end{enumerate}
 \end{definition}

### 2019-01-20 ICML-submission/notions-of-linear-separability.tex
Update notions-of-linear-separability.tex

@@
 separable with margin $\gamma$, then it is also weakly linearly separable with
-the same margin. Indeed, if $w_1, w_2, \dots, w_K \in V$ satisfy
+the same margin (or larger). Indeed, if $w_1, w_2, \dots, w_K \in V$ satisfy
 \eqref{equation:strong-linear-separability-1},

### 2019-01-21 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Update algorithm-for-strongly-linearly-separable-data.tex
Corrected a typo
Update algorithm-for-strongly-linearly-separable-data.tex
Reformulated the mistake lower bound theorem, added some small fix to the remark, fixed some typos in the kernel algorithm theorem, changed frac to slash throughout, and shortened the "observe feedback" lines in the two algorithms

--- 2019-01-18 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
@@
 the classes corresponding to a positive prediction. If all copies make negative
-predictions, the algorithms makes a prediction uniformly at random from
+predictions, the algorithm makes a prediction uniformly at random from
 $\cbr{1,\ldots,K}$.
@@
 \STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
-\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
+\STATE{Observe feedback $z_t = \indicator{\widehat y_t \neq y_t}$}
 \IF{$z_t = 1$}
@@
 \STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
-\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
+\STATE{Observe feedback $z_t  = \indicator{\widehat y_t \neq y_t}$}
 \IF{$z_t = 1$}
@@
 If the examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in V \times
-\{1,2,\dots,K\}$ are strongly linearly separable with margin $\gamma$ and for
-all $t \in \cbr{1,\ldots,T}$ satisfy $\norm{x_t} \le R$ then the expected number
+\{1,2,\dots,K\}$ are strongly linearly separable with margin $\gamma$ and 
+%%%%%
+$\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
+%for all $t \in \cbr{1,\ldots,T}$ satisfy $\norm{x_t} \le R$ 
+%%%%%
+then the expected number
 of mistakes
@@
 Let $\gamma$ be a positive real number, and $R$ be a non-negative real
-number. For any (possibly randomized) algorithm $\calA$ for the \textsc{Online
+number. 
+%%%%%
+Any (possibly randomized) algorithm makes at least 
+$((K-1)/2)\left\lfloor (R/\gamma)^2/4 \right\rfloor$ mistakes in expectation 
+on some \textsc{Online
 Multiclass Classification with Bandit Feedback} problem with $K \le
-(R/\gamma)^2$ classes, there exists an inner product space $(V,
-\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ in $V \times
-\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
-norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
-number of mistakes $\calA$ makes is at least $\frac{K-1}{2} \left\lfloor
-\frac{1}{4} (R/\gamma)^2 \right\rfloor$.
+(R/\gamma)^2$ classes and labeled
+examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in V \times
+\{1,2,\dots,K\}$ for some inner product space $(V,
+\ip{\cdot}{\cdot})$ that are strongly linearly separable with margin $\gamma$ and satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ .
+%
+%For any (possibly randomized) algorithm $\calA$ for the \textsc{Online
+%Multiclass Classification with Bandit Feedback} problem with $K \le
+%(R/\gamma)^2$ classes, there exists an inner product space $(V,
+%\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
+%examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ in $V \times
+%\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
+%norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
+%number of mistakes $\calA$ makes is at least $\frac{K-1}{2} \left\lfloor
+%\frac{1}{4} (R/\gamma)^2 \right\rfloor$.
+%%%%%
 \end{theorem}
 
-\paragraph{Remark.} Irrespective of any conditions on $K$, $R$, and $\gamma$, a
-trivial lower bound on the expected number of mistakes of any randomized
-algorithm is $\frac{K-1}{2}$. To see this, note that the adversary can choose an
-example $(R e_1, y)$, where $y$ is a label chosen uniformly from
+\paragraph{Remark.} 
+%%%%%
+If $\gamma \le R$ then, irrespective 
+%%%%%
+of any other conditions on $K$, $R$, and $\gamma$, 
+a trivial lower bound on the expected number of mistakes of any randomized
+algorithm is $(K-1)/2$. To see this, note that the adversary can choose an
+example $(R e_1, y)$, where $e_1$ is some arbitrary unit vector in $V$ and $y$ is a label chosen uniformly from
 $\cbr{1,2,\dots,K}$, and show this example $K$ times. The sequence of examples
 trivially satisfies the strong linear separability condition, and the
-$\frac{K-1}{2}$ expected mistake lower bound follows from Claim 2
-of~\citet{Daniely-Helbertal-2013}. However, it is unclear if the trivial lower
+$(K-1)/2$ expected mistake lower bound follows from ~\citep[][Claim 2]{Daniely-Helbertal-2013}. However, it is unclear if the trivial lower
 bound is the best possible if $K$ is large, i.e., $\omega((R/\gamma)^2)$. We
@@
 space. Let $\phi:X \to V$ be a feature map and let $k:X \times X \to \R$,
-$k(x,x') = \ip{\phi(x)}{\phi(x')}$ the associated positive positive definite
+$k(x,x') = \ip{\phi(x)}{\phi(x')}$ be the associated positive definite
 kernel. Let $K$ be a positive integer, $\gamma$ be a positive real number, $R$
@@
 \STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
-\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
+\STATE{Observe feedback $z_t =  \indicator{\widehat y_t \neq y_t}$}
 \IF{$z_t = 1$}

### 2019-01-21 ICML-submission/introduction.tex
Update introduction.tex
Fixed a bad reference (coming from merging the two separability definitions)

@@
 stated in
-Definitions~\ref{definition:weak-linear-separability}~and~\ref{definition:strong-linear-separability}.
+Definition~\ref{definition:weak-linear-separability}.
 The standard notion of multiclass linear

### 2019-01-21 ICML-submission/appendix-proofs-for-strongly-separable-examples.tex
Fixes
Update appendix-proofs-for-strongly-separable-examples.tex
Fixed the bad reference (coming from merging the definitions of the two separability notions)

@@
 \[ \Exp[ z_t |S_t = \emptyset] = \frac{K-1}{K}, \]
-\[ \Exp[B] = \frac{K-1}{K} \Exp \sbr{ \sum_{t=1}^T \one[S_t = \emptyset] }, \]
-\[ \Exp[C] = \frac{1}{K} \Exp \sbr{ \sum_{t=1}^T \one[S_t = \emptyset] }. \]
+\[ \Exp[B] = \frac{K-1}{K} \Exp \sbr{ \sum_{t=1}^T \indicator{S_t = \emptyset} }, \]
+\[ \Exp[C] = \frac{1}{K} \Exp \sbr{ \sum_{t=1}^T \indicator{S_t = \emptyset} }. \]
 
@@
 where the last inequality follows from a case analysis on $z_t$ and
-Definition~\ref{definition:strong-linear-separability}: if $z_t = 0$, then
+Definition~\ref{definition:weak-linear-separability}: if $z_t = 0$, then
 $\widehat y_t = y_t$, by Equation~\eqref{equation:strong-linear-separability-2},

### 2019-01-21 ICML-submission/appendix-proofs-of-polynomial-approximation-theorems.tex
nn alg
add one paragraph to intro + change algorithm style

@@
 \autoref{theorem:polynomial-approximation-2} immediately
-follows from this lemma by considering $p' = p \cdot 2^{-s(s+1)rm+1})$
+follows from this lemma by considering $p' = p \cdot 2^{-s(s+1)rm+1}$
 and algebra.
@@
 where we used that $1/\gamma \le 2^s$ and $\norm{v} \le 1$.
-Since $q_v(x) = f_{i,v}(\frac{\ip{v}{x}}{\gamma}) \prod_{i=1}^s \left(f_{i,v}(\frac{\ip{v}{x}})\right)^2$,
+Since $q_v(x) = f_{i,v}(\frac{\ip{v}{x}}{\gamma}) \prod_{i=1}^s \left(f_{i,v}(\frac{\ip{v}{x}}{\gamma})\right)^2$,
 using part 1 of \autoref{lemma:properties-of-norm-of-polynomials} we upper bound the norm of $q_v$

### 2019-01-21 ICML-submission/introduction.tex
add one paragraph to intro + change algorithm style

@@
 \label{algorithm:game-protocol}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$, number of rounds $T$.}
-\FOR{$t=1,2,\dots,T$}
-\STATE Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.
-\STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.}
-\STATE{Observe feedback
+\textbf{Require:} Number of classes $K$, number of rounds $T$.\\
+\For{$t=1,2,\dots,T$}{
+     Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.\\
+     Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.
+     Observe feedback
           $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
@@
 }
-\ENDFOR
-}
-\end{algorithmic}
+
 \end{protocol}
@@
 
-For the case when the examples are weakly linearly separable, we construct a
+For the case when the examples are weakly linearly separable, it was open for a long 
+time whether there exist \textit{efficient} algorithms with finite mistake 
+bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}. 
+Furthermore, in~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, they ask the following question:
+is there \textit{any} algorithm with a finite mistake bound that has no explicit dependence 
+on the dimensionality of the feature vectors? We answer both questions affirmatively by
+providing an efficient algorithm with finite dimensionless mistake bound 
+(Algorithm~\ref{algorithm:kernelized}) (Note: the second question was previously 
+answered by~\cite{Daniely-Helbertal-2013} with an inefficient algorithm).
+
+The strategy used in Algorithm~\ref{algorithm:kernelized} is to construct a
 non-linear feature mapping $\phi$ and associated positive definite kernel
-$k(x,x')$ that makes the examples \emph{strongly} linearly separable. We then
-use the kernelized version of
+$k(x,x')$ that makes the examples \emph{strongly} linearly separable in a higher-dimensional space. 
+We then use the kernelized version of
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} for

### 2019-01-22 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
add one paragraph to intro + change algorithm style
Definition and reference added for positive definite kernels

@@
 
+%\begin{algorithm}[h]
+%\caption{\textsc{Bandit Algorithm for Strongly Linearly Separable Examples}
+%\label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
+%\begin{algorithmic}[1]
+%{
+%\REQUIRE{Number of classes $K$, number of rounds $T$.}
+%\REQUIRE{Inner product space $(V,\ip{\cdot}{\cdot})$.}
+%\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$} \\
+%\FOR{$t=1,2,\dots,T$}
+%\STATE{Observe feature vector $x_t \in V$}
+%\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$}
+%\IF{$S_t = \emptyset$}
+%\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
+%\STATE{Observe feedback $z_t = \indicator{\widehat y_t \neq y_t}$}
+%\IF{$z_t = 1$}
+%\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
+%\ELSE
+%\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ \\ \qquad  for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
+%\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$}
+%\label{line:pos-update}
+%\ENDIF
+%\ELSE
+%\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
+%\STATE{Observe feedback $z_t  = \indicator{\widehat y_t \neq y_t}$}
+%\IF{$z_t = 1$}
+%\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
+%\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
+%\label{line:neg-update}
+%\ELSE
+%\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
+%\ENDIF
+%\ENDIF
+%\ENDFOR
+%}
+%\end{algorithmic}
+%\end{algorithm}
+
 \begin{algorithm}[h]
+\SetAlgoLined
+\LinesNumbered
 \caption{\textsc{Bandit Algorithm for Strongly Linearly Separable Examples}
 \label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$, number of rounds $T$.}
-\REQUIRE{Inner product space $(V,\ip{\cdot}{\cdot})$.}
-\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t \in V$}
-\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$}
-\IF{$S_t = \emptyset$}
-\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
-\STATE{Observe feedback $z_t = \indicator{\widehat y_t \neq y_t}$}
-\IF{$z_t = 1$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ \\ \qquad  for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$}
-\label{line:pos-update}
-\ENDIF
-\ELSE
-\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
-\STATE{Observe feedback $z_t  = \indicator{\widehat y_t \neq y_t}$}
-\IF{$z_t = 1$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
-\label{line:neg-update}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ENDIF
-\ENDIF
-\ENDFOR
+\textbf{Require:} Number of classes $K$, number of rounds $T$. \\
+\textbf{Require:} Inner product space $(V,\ip{\cdot}{\cdot})$.  \\
+\nl Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$\\ 
+\nl \For{$t=1,2,\dots,T$}{
+\nl    Observe feature vector $x_t \in V$ \\
+\nl    Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$\\
+\nl    \If{$S_t = \emptyset$}{
+\nl         Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$ \\
+\nl         Observe feedback $z_t = \indicator{\widehat y_t \neq y_t}$\\
+\nl          \If{$z_t = 1$}{
+\nl               Set $w_i^{(t+1)} = w_i^{(t)}$, $\forall i \in \{1,2,\dots,K\}$
               }
-\end{algorithmic}
+\nl          \Else{
+\nl               Set $w_i^{(t+1)} = w_i^{(t)}$, $\forall i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$ \\
+\nl Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$  \label{line:pos-update}      
+              }
+        }
+\nl     \Else{
+\nl           Predict $\widehat y_t \in S_t$ chosen arbitrarily \\
+\nl           Observe feedback $z_t  = \indicator{\widehat y_t \neq y_t}$ \\
+\nl            \If{$z_t = 1$}{
+\nl                Set $w_i^{(t+1)} = w_i^{(t)}$, $\forall i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$ \\
+\nl  Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$   \label{line:neg-update}            
+               }
+\nl           \Else{
+\nl                 Set $w_i^{(t+1)} = w_i^{(t)}$, $\forall i \in \{1,2,\dots,K\}$
+           }
+      }
+}
+
 \end{algorithm}
@@
 be extended to nonlinear classification using
-kernels~\cite{Scholkopf-Smola-2002, Shawe-Taylor-Cristianini-2004}. The formal
-description of the kernelized algorithm is given in
-Algorithm~\ref{algorithm:kernelized}. As opposed to explicitly maintaining the
+\emph{positive definite kernels} (or \emph{kernels}, for short), which are 
+functions of the form $k: X^2 \to V$ for some set $X$ and inner product space 
+$(V, \ip{\cdot}{\cdot})$ such that the matrix $\left(k(x_i,x_j)\right)_{i,j=1}^m$ 
+is positive semidefinite for any positive integer $m$ and $x_1, \dots, x_m \in X$
+~\citep[][Definition 2.5]{Scholkopf-Smola-2002}. 
+%kernels~\cite{Scholkopf-Smola-2002, Shawe-Taylor-Cristianini-2004}. The formal
+%description of the kernelized algorithm is given in
+%Algorithm~\ref{algorithm:kernelized}. 
+As opposed to explicitly maintaining the
 weight vector for each class, the algorithm maintains the set of example-scalar
@@
 \label{algorithm:kernelized}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$, number of rounds $T$.}
-\REQUIRE{Kernel function  $k(\cdot, \cdot)$.}
-\STATE{Initialize $J_1^{(1)} = J_2^{(1)} = \dots = J_K^{(1)} = \emptyset$}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$.}
-\STATE{Compute \\ $S_t = \left\{ i ~:~ 1 \le i \le K, \ \sum_{(x,y) \in J_i^{(t)}} y k(x, x_t) \ge 0 \right\}$}
-\IF{$S_t = \emptyset$}
-\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
-\STATE{Observe feedback $z_t = \indicator{\widehat y_t \neq y_t}$}
-\IF{$z_t = 1$}
-\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ELSE
-\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad  for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
-\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, +1)}$}
-\ENDIF
-\ELSE
-\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
-\STATE{Observe feedback $z_t =  \indicator{\widehat y_t \neq y_t}$}
-\IF{$z_t = 1$}
-\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
-\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, -1)}$}
-\ELSE
-\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ENDIF
-\ENDIF
-\ENDFOR
+\textbf{Require:} Number of classes $K$, number of rounds $T$.\\
+\textbf{Require:} Kernel function  $k(\cdot, \cdot)$. \\
+Initialize $J_1^{(1)} = J_2^{(1)} = \dots = J_K^{(1)} = \emptyset$ \\
+\For{$t=1,2,\dots,T$} {
+     Observe feature vector $x_t$.\\
+     Compute \\ $S_t = \left\{ i ~:~ 1 \le i \le K, \ \sum_{(x,y) \in J_i^{(t)}} y k(x, x_t) \ge 0 \right\}$ \\
+     \If{$S_t = \emptyset$}{
+           Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$ \\
+           Observe feedback $z_t = \indicator{\widehat y_t \neq y_t}$ \\
+           \If{$z_t = 1$}{
+                Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$
            }
-\end{algorithmic}
+           \Else{
+                Set $J_i^{(t+1)} = J_i^{(t)}$, $\forall i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$ \\
+                Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, +1)}$
+           }
+      }
+      \Else{
+           Predict $\widehat y_t \in S_t$ chosen arbitrarily \\
+           Observe feedback $z_t =  \indicator{\widehat y_t \neq y_t}$ \\
+           \If{$z_t = 1$}{
+                Set $J_i^{(t+1)} = J_i^{(t)}$, $\forall i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$\\
+                Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, -1)}$ 
+           }
+           \Else {
+                Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$
+           }
+      }
+}
+
 \end{algorithm}

### 2019-01-22 ICML-submission/from-weak-separability-to-strong-separability.tex
Changed p_i(y_t) to p_i(x_t) in (9) and (10)
Changed 0 to \zero; reformulated display in Thm 5
(Margin transformation theorem)

@@
 separable. Throughout this section, we assume without loss of generality that
-all examples lie in the unit ball $\B(0,1) \subseteq \R^d$.\footnote{Instead of
+all examples lie in the unit ball $\B(\zero,1) \subseteq \R^d$.\footnote{Instead of
 working with feature vector $x_t$ we can work with normalized feature vectors
@@
 examples. Specifically, $\phi$ has the property that if a set of labeled
-examples in $\B(0,1)$ is weakly linearly separable with a margin $\gamma$, then
+examples in $\B(\zero,1)$ is weakly linearly separable with a margin $\gamma$, then
 after applying $\phi$ the examples become strongly linearly separable with a
@@
 
-The kernel function $k:\B(0,1) \times \B(0,1) \to \R$ is defined as
+The kernel function $k:\B(\zero,1) \times \B(\zero,1) \to \R$ is defined as
 $$
@@
 coordinates of $\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of
-non-negative integers, the feature map that corresponds to $k$ is $\phi: \B(0,1)
+non-negative integers, the feature map that corresponds to $k$ is $\phi: \B(\zero,1)
 \to \ell_2$,
@@
 The last equality together with the formula for $k$ implies that $k(x,x) <
-+\infty$ for any $x$ in $\B(0,1)$ and thus in particular implies that $\phi(x)$
++\infty$ for any $x$ in $\B(\zero,1)$ and thus in particular implies that $\phi(x)$
 indeed lies in $\ell_2$.
@@
 \label{theorem:margin-transformation}
-Let $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ in $\B(0,1) \times
+Let $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ in $\B(\zero,1) \times
 \{1,2,\dots,K\}$ be a sequence of labeled examples that is weakly linearly
@@
 equation~\eqref{equation:phi} and let
+%\begingroup
+%\allowdisplaybreaks
+%\begin{align*}
+%r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1, \quad \quad s = \left \lceil \log_2(2/\gamma) \right \rceil, \\
+%\gamma_1 & = \frac{1}{2\sqrt{K}}  \\
+%& \ \cdot \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}, \\
+%\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4\sqrt{K}(4K-5) 2^{K-1}} \\
+%& \ \cdot \left(2^{s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} \; .
+%\end{align*}
+%\endgroup
 \begingroup
@@
 \begin{align*}
-r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1, \quad \quad s = \left \lceil \log_2(2/\gamma) \right \rceil, \\
-\gamma_1 & = \frac{1}{2\sqrt{K}}  \\
-& \ \cdot \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}, \\
-\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4\sqrt{K}(4K-5) 2^{K-1}} \\
-& \ \cdot \left(2^{s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} \; .
+%r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1, \quad \quad s = \left \lceil \log_2(2/\gamma) \right \rceil, \\
+\gamma_1 = & \frac{ 
+  \left[
+    376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil 
+  \right]^{
+    \frac{-\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil}{2}
+  }
+}{2\sqrt{K}}, 
+\\
+\gamma_2 = & \frac{
+   \left(2^{s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} 
+}{4\sqrt{K}(4K-5) 2^{K-1}}
+\\
+&  \cdot 2^{s(s+1)r(K-1)}
+\; ,
 \end{align*}
 \endgroup
+where $r = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1$ and $s = \left \lceil \log_2(2/\gamma) \right \rceil$.
 Then, the sequence of labeled examples transformed by $\phi$,
@@
 Let $K$ be a positive integer and let $\gamma$ be a positive real number. If
-$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \B(0,1) \times \{1,2,\dots,K\}$
+$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \B(\zero,1) \times \{1,2,\dots,K\}$
 is a sequence of weakly separable labeled examples with margin $\gamma > 0$,
@@
 \label{equation:poly-pos-i}
-\forall t \in \cbr{1,2,\dots,T}, y_t = i \quad \Rightarrow \quad p_i(y_t) \ge \frac{\gamma'}{2} \; , \\
+\forall t \in \cbr{1,2,\dots,T}, y_t = i \quad \Rightarrow \quad p_i(x_t) \ge \frac{\gamma'}{2} \; , \\
 \label{equation:poly-neg-i}
-\forall t \in \cbr{1,2,\dots,T}, y_t \neq i \quad \Rightarrow \quad p_i(y_t) \le -\frac{\gamma'}{2} \; .
+\forall t \in \cbr{1,2,\dots,T}, y_t \neq i \quad \Rightarrow \quad p_i(x_t) \le -\frac{\gamma'}{2} \; .
 \end{align}
@@
 $$
-R_i^+ = \!\!\!\!\! \!\!\!\!\! \bigcap_{j \in \cbr{1,2,\dots,K} \setminus \cbr{i}} \cbr{x \in \B(0,1) ~:~ \ip{w_i^* - w_j^*}{x} \ge \gamma},
+R_i^+ = \!\!\!\!\! \!\!\!\!\! \bigcap_{j \in \cbr{1,2,\dots,K} \setminus \cbr{i}} \cbr{x \in \B(\zero,1) ~:~ \ip{w_i^* - w_j^*}{x} \ge \gamma},
 $$
@@
 $$
-R_i^- = \!\!\!\!\! \!\!\!\!\! \bigcup_{j \in \cbr{1,2,\dots,K} \setminus \cbr{i}} \cbr{x \in \B(0,1) ~:~ \ip{w_i^* - w_j^*}{x} \le -\gamma}.
+R_i^- = \!\!\!\!\! \!\!\!\!\! \bigcup_{j \in \cbr{1,2,\dots,K} \setminus \cbr{i}} \cbr{x \in \B(\zero,1) ~:~ \ip{w_i^* - w_j^*}{x} \le -\gamma}.
 $$
@@
 conditions \eqref{eqn:r-plus} and \eqref{eqn:r-minus} mean that $p_i$
-approximates on $\B(0,1)$ a scalar multiple of the indicator function of the
+approximates on $\B(\zero,1)$ a scalar multiple of the indicator function of the
 intersection of $K-1$ halfspaces $\bigcap_{j \in \cbr{1,2,\dots,K} \setminus
@@
 \begin{enumerate}
-\item $p(x) \ge 1/2$ \\ for all $\displaystyle x \in R^+ = \bigcap_{i=1}^m \left\{ x \in \B(0,1) ~:~  \ip{v_i}{x} \ge \gamma \right\}$,
-\item $p(x) \le -1/2$ \\ for all $\displaystyle x \in R^- = \bigcup_{i=1}^m \left\{ x \in \B(0,1) ~:~  \ip{v_i}{x} \le - \gamma \right\}$,
+\item $p(x) \ge 1/2$ \\ for all $\displaystyle x \in R^+ = \bigcap_{i=1}^m \left\{ x \in \B(\zero,1) ~:~  \ip{v_i}{x} \ge \gamma \right\}$,
+\item $p(x) \le -1/2$ \\ for all $\displaystyle x \in R^- = \bigcup_{i=1}^m \left\{ x \in \B(\zero,1) ~:~  \ip{v_i}{x} \le - \gamma \right\}$,
 \item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$,
@@
 \item $\displaystyle p(x) \ge 1/2$ \\
-for all $\displaystyle x \in R^+ = \bigcap_{i=1}^m \left\{ x \in \B(0,1) ~:~ \ip{v_i}{x} \ge \gamma \right\}$,
+for all $\displaystyle x \in R^+ = \bigcap_{i=1}^m \left\{ x \in \B(\zero,1) ~:~ \ip{v_i}{x} \ge \gamma \right\}$,
 
 \item $\displaystyle p(x) \le - 1/2$ \\
-for all $\displaystyle x \in R^- = \bigcup_{i=1}^m \left\{ x \in \B(0,1) ~:~ \ip{v_i}{x} \le - \gamma \right\}$,
+for all $\displaystyle x \in R^- = \bigcup_{i=1}^m \left\{ x \in \B(\zero,1) ~:~ \ip{v_i}{x} \le - \gamma \right\}$,
 

### 2019-01-22 ICML-submission/introduction.tex
Fixed a small issue in Protocol 1

@@
      Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.\\
-     Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.
+     Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
      Observe feedback

### 2019-01-22 ICML-submission/introduction.tex
Removed an extra dot

@@
 mistakes $\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$,
-where $\one$ denotes the indicator function..
+where $\one$ denotes the indicator function.
 

### 2019-01-22 ICML-submission/appendix-experiment.tex
add experiments

\section{Supplementary Materials for Section~\ref{sec:experiments}}
\label{sec:supp-to-experiment}
The three-class data we used in Section~\ref{sec:experiments} is originally generated in a $d=2$ plate as shown in the following figure: 
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}  
        \captionsetup{justification=centering}
        \begin{center}
        \hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_points}
        \caption{Strongly separable case}
        \label{fig:strong-points}
        \end{center}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth} 
        \captionsetup{justification=centering}
        \centering
        \hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_points}
         \caption{Weakly separable case}
    \end{subfigure}
    \vspace*{-0.2cm}
    \caption{Data distribution for Section~\ref{sec:experiments}}
    % \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$. }
\end{figure}

However, in 2D, the samples in Figure~\ref{fig:strong-points} do not satisfy the strong linear separability defined in Definition~\ref{definition:weak-linear-separability}, which requires that any class can be separated from all the others by a hyperplane that \textit{passes through the origin}. We therefore raise the dimensionality to 3D by adding a constant feature to all samples. This is equivalent to allowing the separating hyperplanes to have a bias, so that they do not need to pass through the origin. Thus Figure~\ref{fig:strong-points} becomes strongly linearly separable. To better understand how each algorithm works, we plot below the final decision boundary that is learned by each algorithm.

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}  
        \captionsetup{justification=centering}
        \begin{center}
        \hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_banditron_points}
        \caption{Strongly separable case}
        \label{fig:strong-points}
        \end{center}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth} 
        \captionsetup{justification=centering}
        \centering
        \hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_banditron_points}
         \caption{Weakly separable case}
    \end{subfigure}
    \vspace*{-0.2cm}
    \caption{\textsc{Banditron}'s decision boundary}
    % \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$. }
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}  
        \captionsetup{justification=centering}
        \begin{center}
        \hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_linear_ova_points}
        \caption{Strongly separable case}
        \label{fig:strong-points}
        \end{center}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth} 
        \captionsetup{justification=centering}
        \centering
        \hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_linear_ova_points}
         \caption{Weakly separable case}
    \end{subfigure}
    \vspace*{-0.2cm}
    \caption{Our Algorithm with linear kernel (Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})'s decision boundary}
    % \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$. }
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}  
        \captionsetup{justification=centering}
        \begin{center}
        \hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_rational_ova_points}
        \caption{Strongly separable case}
        \label{fig:strong-points}
        \end{center}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth} 
        \captionsetup{justification=centering}
        \centering
        \hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_rational_ova_points}
         \caption{Weakly separable case}
    \end{subfigure}
    \vspace*{-0.2cm}
    \caption{Our Algorithm with rational kernel (Algorithm~\ref{algorithm:kernelized})'s decision boundary}
    % \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$. }
\end{figure}

### 2019-01-22 ICML-submission/empirical-comparison.tex
add experiments

 \section{Experiments}
\label{sec:experiments}
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.23\textwidth} 
        \captionsetup{justification=centering}
        \begin{center}
        \hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0.1cm, 0, 0}, clip]{figures/strong3}
        \caption{Strongly separable case}
        \end{center}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth} 
        \captionsetup{justification=centering}
        \centering
        \hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0.1cm, 0, 0}, clip]{figures/weak3}
        \caption{Weakly separable case}
    \end{subfigure}
    \vspace*{-0.2cm}
    \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$. }
    %\includegraphics[width=0.25\textwidth]{figures/weak3}
    \label{fig:both}
\end{figure}

We compare our algorithm with \textsc{Banditron} empirically to show that our kernelized bandit algorithm can have significant advantage over \textsc{Banditron} is the separable case.

We generate strongly and weakly separable samples with $K=3$ in a similar sense those in Figure~\ref{figure:weakly-linearly-separable-examples-with-margin}. They are originally generated in a $d=2$ plate, and then lifted to $d=3$ by adding a constant feature. We provide the figures of their exact look in Appendix~\ref{sec:supp-to-experiment}. Different from Figure~\ref{figure:weakly-linearly-separable-examples-with-margin}, the three classes are non-uniform and imbanlanced: class 1 occupies a smaller sector between $-15^\circ$ and $15^\circ$, while class 2 and class 3 occupy $[15^\circ, 180^\circ]$ and $[-180^\circ, -15^\circ]$ respectively. On the other hand, $80\%$ of data comes from class 1, while $10\%$ comes from class 2 and 3 each.

In real world, data can often be non-uniform and imbalanced. We demonstrate that \textsc{Banditron} is weak especially under these situations, while our algorithm still performs well.

We choose sample size as $5\times 10^6$ and margin as $\gamma=0.05$ (in both strongly weakly separable cases). All results are averaged over $20$ runs.

We plot the number of mistakes against time in Figure~\ref{fig:both}. We can see there is indeed a dilemma for \textsc{Banditron}: when picking a relatively large exploration rate, it suffers from the cost of continuous exploration; when picking a relatively small exploration rate, it cannot adapt its model quickly enough (this problem exacerbates when a majority class occupies a small region, like class 1). Striking a balance between the two extremes leads to the $\sqrt{T}$ mistake bound. On the contrary, our algorithm makes significant progress on every mistake it makes, leading to a finite mistake bound.

### 2019-01-22 ICML-submission/from-weak-separability-to-strong-separability.tex
Reformulated the displays in Case 1
Changed item 4 in poly approx thm for halfspaces I
add experiments

@@
 \item $p(x) \le -1/2$ \\ for all $\displaystyle x \in R^- = \bigcup_{i=1}^m \left\{ x \in \B(\zero,1) ~:~  \ip{v_i}{x} \le - \gamma \right\}$,
-\item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$,
-\item $\displaystyle \norm{p} \le \left( 188 \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil \right)^{\frac{1}{2} \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil}$.
+\item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{{1}/{\gamma}} \right\rceil$,
+\item $\displaystyle \norm{p} \le \left[ 188 \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{{1}/{\gamma}} \right\rceil \right]^{
+  \frac{
+    \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{{1}/{\gamma}} \right\rceil
+  }{2}
+}$.
 \end{enumerate}
@@
 \begin{center}
-\input{figures/pizza-slice}
+ \scalebox{.65}{\input{figures/pizza-slice}}
 \end{center}
@@
 \begin{proof}[Proof sketch of Theorem~\ref{theorem:margin-transformation}]
-Since the examples $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ are weakly
+Since the examples $(x_1, y_1)$,  $\dots$, $(x_T, y_T)$ are weakly
 linearly separable with margin $\gamma$, there are vectors $w_1, w_2, \dots, w_K$
@@
 \begin{align*}
-\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{\frac{2}{\gamma}} \right\rceil \; ,
+\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{{2}/{\gamma}} \right\rceil \; ,
 \end{align*}
@@
 \begin{align*}
-\norm{p_i} & \le \left(188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
-\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; . \\
+&\norm{p_i} 
+\\
+& \le 
+\left[
+  188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil 
+\right]^{
+  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil }{2}
+} \; . \\
 \end{align*}
@@
 \begin{align*}
-\norm{c_i}_{\ell_2}
-& \le \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
-\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; .
+&\norm{c_i}_{\ell_2}
+\\
+& \le 
+\left[
+  376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil 
+\right]^{
+  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil}{2}
+} \; .
 \end{align*}
@@
 \begin{align*}
-u_i & = \frac{c_i}{\sqrt{K} \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
-\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}} \; . \\
+u_i & = 
+\frac{c_i/\sqrt{K}}{ 
+  \left[
+    376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil 
+  \right]^{
+    \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}{2}
+  }
+} \; . \\
 \end{align*}

### 2019-01-22 ICML-submission/introduction.tex
add experiments

@@
 bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}. 
-Furthermore, in~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, they ask the following question:
+Furthermore, in~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, they ask the question:
 is there \textit{any} algorithm with a finite mistake bound that has no explicit dependence 

### 2019-01-22 ICML-submission/appendix-experiment.tex
small fix

@@
 Thus Figure~\ref{fig:strong-points} becomes strongly linearly separable.
-To better understand how each algorithm works, we plot below the final decision boundary that is learned by each algorithm.
+To better understand how each algorithm works, we plot in Figure~\ref{fig:banditron-points},~\ref{fig:linearova-points},~\ref{fig:rationalova-points} the final decision boundary that is learned by each algorithm.
 
@@
         \caption{Strongly separable case}
-        \label{fig:strong-points}
         \end{center}
@@
     \caption{\textsc{Banditron}'s decision boundary}
+     \label{fig:banditron-points}
     % \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$. }
@@
     \caption{Our Algorithm with linear kernel (Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})'s decision boundary}
+    \label{fig:linearova-points} 
    % \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$. }
@@
     \caption{Our Algorithm with rational kernel (Algorithm~\ref{algorithm:kernelized})'s decision boundary}
+    \label{fig:rationalova-points}
     % \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$. }

### 2019-01-22 ICML-submission/empirical-comparison.tex
small fix

@@
 
-We generate strongly and weakly separable samples with $K=3$ in a similar sense those in Figure~\ref{figure:weakly-linearly-separable-examples-with-margin}.
+We generate strongly and weakly separable samples with $K=3$ in a similar sense to those in Figure~\ref{figure:weakly-linearly-separable-examples-with-margin}.
 They are originally generated in a $d=2$ plate, and then lifted to $d=3$ by adding a constant feature.

### 2019-01-22 ICML-submission/introduction.tex
tweaked to fit into 8 pages

@@
 Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
-viewed as a repeated game between the learner and the adversary. At each
-timestep $t$, the adversary chooses a labeled example $(x_t, y_t)$ where the
-feature vector $x_t \in \R^d$ is revealed to the learner and the correct label
-$y_t$ is kept secret by the adversary. Upon receiving the feature vector $x_t$,
-the learner is asked to make a prediction $\widehat{y}_t$. Immediately after
-making its prediction, the learner receives feedback. In contrast with the
-standard full-information setting (where the feedback given is the correct label
-$y_t$), here the feedback is only a binary indicator of whether the prediction
+viewed as a repeated game between a learner and an adversary. At each
+timestep $t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals $x_t\in \R^d$ to the learner.  
+Upon receiving $x_t$, the learner makes a prediction $\widehat{y}_t$ and receives feedback. 
+In contrast to the
+standard full-information setting, where the feedback given is the correct label
+$y_t$, here the feedback is only a binary indicator of whether the prediction
 was correct or not. The protocol of the problem is formally stated below.
@@
 separability~\citep{Crammer-Singer-2003} corresponds to the weak linear
-separability. For binary classification, the weak and strong separability are
-identical. However, they differ for multiclass classification with $K \ge 3$
-classes. For multiclass classification with $K$ classes, weak linear
-separability means that the examples from each class lie in an intersection of
-$K-1$ halfspaces and the examples outside of the class lie in the complement of
+separability. %For binary classification, the weak and strong separability are
+%identical. However, they differ for multiclass classification with $K \ge 3$
+%classes. 
+For multiclass classification with $K$ classes, weak linear
+separability requires that all examples from the same class lie in an intersection of $K-1$ halfspaces and all other examples lie in the complement of
 the intersection of the halfspaces. Strong linear separability means that
@@
 worst case.
-These results guarantee that the \textsc{Multiclass Perceptron} achieves an
-information-theoretically optimal mistake upper bound, meanwhile it has
-low time and memory complexities.%
-%The guarantees provided by \textsc{Multiclass Perceptron} is very satisfying,
-%since it achieves an information-theoretically optimal mistake upper bound,
-%while having low time and memory complexities.
-%%%%%
+The \textsc{Multiclass Perceptron} achieves an
+information-theoretically optimal mistake bound, while being
+computationally and memory efficient.
 ~\footnote{

### 2019-01-22 ICML-submission/notions-of-linear-separability.tex
Update notions-of-linear-separability.tex
Changed some frac to slash
add experiments

@@
 the mistake bound for the \textsc{Multiclass Perceptron} algorithm. The second
-notion is stronger, i.e. more restrictive. However, it is more suitable for the
-bandit setting, since it allows for a simple and efficient algorithm; see
-Section~\ref{section:algorithm-for-strongly-linearly-separable-data}.
+notion is stronger, i.e. more restrictive. %However, it is more suitable for the
+%bandit setting, since it allows for a simple and efficient algorithm; see
+%Section~\ref{section:algorithm-for-strongly-linearly-separable-data}.
 
@@
 \label{equation:strong-linear-separability-2}
-& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \frac \gamma 2 \; , \\
+& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \gamma/2 \; , \\
 \label{equation:strong-linear-separability-3}
@@
 \forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
-\ip{x_t}{w_i} \le - \frac \gamma 2 \; .
+\ip{x_t}{w_i} \le - \gamma/2 \; .
 \end{gathered}
@@
 
-The notion of weak linear separability is a standard assumption used in the
-full-information setting to upper bound the number of mistakes of the
-\textsc{Multiclass Perceptron} algorithm.
+%The notion of weak linear separability is a standard assumption used in the
+%full-information setting to upper bound the number of mistakes of the
+%\textsc{Multiclass Perceptron} algorithm.
 %%%%%
-(Recall our discussion on the topic in Section~\ref{section:introduction}.)
+%(Recall our discussion on the topic in Section~\ref{section:introduction}.)
 %Namely, \citet{Crammer-Singer-2003}
@@
 \begin{center}
-\input{figures/weakly-linearly-separable-examples-with-margin}
+ \scalebox{.8}{\input{figures/weakly-linearly-separable-examples-with-margin}}
 \end{center}

### 2019-01-22 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
add experiments
Fixes

@@
 integer, $\gamma$ be a positive real number, $R$ be a non-negative real number.
-If the examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in V \times
-\{1,2,\dots,K\}$ are strongly linearly separable with margin $\gamma$ and 
-%%%%%
-$\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
-%for all $t \in \cbr{1,\ldots,T}$ satisfy $\norm{x_t} \le R$ 
-%%%%%
-then the expected number
-of mistakes
+If the examples $(x_1, y_1), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are
+strongly linearly separable with margin $\gamma$ and $\norm{x_1}, \norm{x_2},
+\dots, \norm{x_T} \le R$ then the expected number of mistakes
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
@@
 \label{theorem:strongly-separable-examples-mistake-lower-bound}
-Let $\gamma$ be a positive real number, and $R$ be a non-negative real
-number. 
-%%%%%
-Any (possibly randomized) algorithm makes at least 
-$((K-1)/2)\left\lfloor (R/\gamma)^2/4 \right\rfloor$ mistakes in expectation 
-on some \textsc{Online
-Multiclass Classification with Bandit Feedback} problem with $K \le
-(R/\gamma)^2$ classes and labeled
-examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in V \times
-\{1,2,\dots,K\}$ for some inner product space $(V,
-\ip{\cdot}{\cdot})$ that are strongly linearly separable with margin $\gamma$ and satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ .
-%
-%For any (possibly randomized) algorithm $\calA$ for the \textsc{Online
-%Multiclass Classification with Bandit Feedback} problem with $K \le
-%(R/\gamma)^2$ classes, there exists an inner product space $(V,
-%\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
-%examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ in $V \times
-%\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
-%norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
-%number of mistakes $\calA$ makes is at least $\frac{K-1}{2} \left\lfloor
-%\frac{1}{4} (R/\gamma)^2 \right\rfloor$.
-%%%%%
+Let $\gamma$ be a positive real number, $R$ be a non-negative real number and
+let $K \le (R/\gamma)^2$ be a positive integer. Any (possibly randomized)
+algorithm makes at least $((K-1)/2)\left\lfloor (R/\gamma)^2/4 \right\rfloor$
+mistakes in expectation on some \textsc{Online Multiclass Classification with
+Bandit Feedback} problem with $K$ classes and labeled examples $(x_1, y_1),
+(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ for some inner
+product space $(V, \ip{\cdot}{\cdot})$ that are strongly linearly separable with
+margin $\gamma$ and satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$.
 \end{theorem}
@@
 \paragraph{Remark.}
-%%%%%
-If $\gamma \le R$ then, irrespective 
-%%%%%
-of any other conditions on $K$, $R$, and $\gamma$, 
-a trivial lower bound on the expected number of mistakes of any randomized
-algorithm is $(K-1)/2$. To see this, note that the adversary can choose an
-example $(R e_1, y)$, where $e_1$ is some arbitrary unit vector in $V$ and $y$ is a label chosen uniformly from
-$\cbr{1,2,\dots,K}$, and show this example $K$ times. The sequence of examples
-trivially satisfies the strong linear separability condition, and the
-$(K-1)/2$ expected mistake lower bound follows from ~\citep[][Claim 2]{Daniely-Helbertal-2013}. However, it is unclear if the trivial lower
-bound is the best possible if $K$ is large, i.e., $\omega((R/\gamma)^2)$. We
-leave this as an open problem.
+If $\gamma \le R$ then, irrespective of any other conditions on $K$, $R$, and
+$\gamma$, a trivial lower bound on the expected number of mistakes of any
+randomized algorithm is $(K-1)/2$. To see this, note that the adversary can
+choose an example $(R e_1, y)$, where $e_1$ is some arbitrary unit vector in $V$
+and $y$ is a label chosen uniformly from $\cbr{1,2,\dots,K}$, and show this
+example $K$ times. The sequence of examples trivially satisfies the strong
+linear separability condition, and the $(K-1)/2$ expected mistake lower bound
+follows from ~\citep[][Claim 2]{Daniely-Helbertal-2013}. However, it is unclear
+if the trivial lower bound is the best possible if $K$ is large, i.e.,
+$\omega((R/\gamma)^2)$. We leave this as an open problem.
 
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} can
-be extended to nonlinear classification using
-\emph{positive definite kernels} (or \emph{kernels}, for short), which are 
-functions of the form $k: X^2 \to V$ for some set $X$ and inner product space 
-$(V, \ip{\cdot}{\cdot})$ such that the matrix $\left(k(x_i,x_j)\right)_{i,j=1}^m$ 
-is positive semidefinite for any positive integer $m$ and $x_1, \dots, x_m \in X$
-~\citep[][Definition 2.5]{Scholkopf-Smola-2002}. 
-%kernels~\cite{Scholkopf-Smola-2002, Shawe-Taylor-Cristianini-2004}. The formal
-%description of the kernelized algorithm is given in
-%Algorithm~\ref{algorithm:kernelized}. 
-As opposed to explicitly maintaining the
-weight vector for each class, the algorithm maintains the set of example-scalar
-pairs corresponding to the updates of the non-kernelized algorithm. As a direct
-consequence of
+be extended to nonlinear classification using \emph{positive definite kernels}
+(or \emph{kernels}, for short), which are functions of the form $k: X \times X
+\to V$ for some set $X$ and inner product space $(V, \ip{\cdot}{\cdot})$ such
+that the matrix $\left(k(x_i,x_j)\right)_{i,j=1}^m$ is a symmetric positive
+semidefinite for any positive integer $m$ and $x_1, x_2, \dots, x_m \in X$
+\citep[Definition 2.5]{Scholkopf-Smola-2002}. As opposed to explicitly
+maintaining the weight vector for each class, the algorithm maintains the set of
+example-scalar pairs corresponding to the updates of the non-kernelized
+algorithm. As a direct consequence of
 Theorem~\ref{theorem:strongly-separable-examples-mistake-upper-bound} we get a
@@
 \begin{enumerate}
-\item the mapped examples $(\phi(x_1), y_1)$, $(\phi(x_2), y_2)$, $\dots$, $(\phi(x_T), y_T)$
+\item the mapped examples $(\phi(x_1), y_1)$, $\dots$, $(\phi(x_T), y_T)$
 are strongly linearly separable with margin $\gamma$,

### 2019-01-22 ICML-submission/appendix-experiment.tex
Fixes

@@
 \label{sec:supp-to-experiment}
-The three-class data we used in Section~\ref{sec:experiments} is originally generated in a $d=2$ plate as shown in the following figure: 
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.23\textwidth}  
-        \captionsetup{justification=centering}
-        \begin{center}
-        \hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_points}
-        \caption{Strongly separable case}
-        \label{fig:strong-points}
-        \end{center}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.23\textwidth} 
-        \captionsetup{justification=centering}
-        \centering
-        \hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_points}
-         \caption{Weakly separable case}
-    \end{subfigure}
-    \vspace*{-0.2cm}
-    \caption{Data distribution for Section~\ref{sec:experiments}}
-    % \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$. }
-\end{figure}
 

### 2019-01-22 ICML-submission/appendix-multiclass-perceptron.tex
Fixes

@@
 & = \frac{\gamma}{R} \sum_{\substack{s : 1 \le s \le T \\ y_s = i}} \ip{e_s}{R e_t} \\
-& = \gamma \cdot \sum_{\substack{s : 1 \le s \le T \\ y_s = i}} \one[s = t] \\
-& = \gamma \cdot \one[y_t = i]
+& = \gamma \cdot \sum_{\substack{s : 1 \le s \le T \\ y_s = i}} \indicator{s = t} \\
+& = \gamma \cdot \indicator{y_t = i}
 \; .
@@
 We now give a lower bound on the number of mistakes $\calA$ makes.
-Define a filtration $\cbr{\calB_t}_{t=0}^T$,
-where $\calB_t = \sigma((x_1, y_1, \hat{y}_1), \ldots, (x_t, y_t, \hat{y}_t))$.
-As $y_t$ is chosen uniformly from $\cbr{1,\ldots,K}$ and independent of
-$\calB_{t-1}$ and $\hat{y}_t$,
-\[ \Exp[ \indicator{\widehat y_t \neq y_t} | \calB_{t-1} ] \geq 1 - \frac 1 K \geq \frac 1 2. \]
-This implies that
-\[ \Exp[ \indicator{\widehat y_t \neq y_t} ] \geq \frac 1 2. \]
+As $y_t$ is chosen uniformly from $\{1,2,\dots,K\}$ and independent of
+$\calA$'s randomization
+$$
+\Exp[ \indicator{\widehat y_t \neq y_t} ] \ge 1 - \frac{1}{K} \ge \frac{1}{2} \; .
+$$
 Summing over all $t$ in $\cbr{1,\ldots,T}$, we conclude that
-\[ \Exp \sbr{ \sum_{t=1}^T \indicator{\widehat y_t \neq y_t} } \geq \frac T 2 = \frac 1 2 \lfloor (R/\gamma)^2 \rfloor, \]
+$$
+\Exp \sbr{ \sum_{t=1}^T \indicator{\widehat y_t \neq y_t} } \geq \frac T 2 = \frac 1 2 \lfloor (R/\gamma)^2 \rfloor,
+$$
 which completes the proof.

### 2019-01-22 ICML-submission/appendix-proofs-for-strongly-separable-examples.tex
Fixes

@@
 
-%$\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$
-%$A
-%= \sum_{t ~:~ S_t \neq \emptyset} z_t$
-%B = \sum_{t ~:~ S_t = \emptyset} z_t
-%\sum_{t ~:~ S_t = \emptyset}
 \begin{proof}[Proof of \autoref{theorem:strongly-separable-examples-mistake-upper-bound}]
-Let $M = \sum_{t=1}^T z_t$ be the number of
-mistakes Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} makes.
-Let $A = \sum_{t=1}^T \one[S_t \neq \emptyset] z_t$ be the number of mistakes in the rounds
-when $S_t \neq \emptyset$, i.e. the number of rounds line~\ref{line:neg-update} is
-executed.
-In addition, let $B = \sum_{t=1}^T \one[S_t = \emptyset] z_t$ be the
-number of mistakes in the rounds when $S_t = \emptyset$.
-It can be easily seen that $M = A + B$.
+Let $M = \sum_{t=1}^T z_t$ be the number of mistakes
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
+makes. Let $A = \sum_{t=1}^T \one[S_t \neq \emptyset] z_t$ be the number of
+mistakes in the rounds when $S_t \neq \emptyset$, i.e. the number of rounds
+line~\ref{line:neg-update} is executed. In addition, let $B = \sum_{t=1}^T
+\one[S_t = \emptyset] z_t$ be the number of mistakes in the rounds when $S_t =
+\emptyset$. It can be easily seen that $M = A + B$.
 
 Let $C = \sum_{t=1}^T \one[S_t = \emptyset](1 - z_t)$ be the number of rounds
-line~\ref{line:pos-update} gets executed. Let
-$U = \sum_{t=1}^T (\one[S_t \neq \emptyset] z_t + \one[S_t = \emptyset](1 - z_t))$
-be the number of rounds line~\ref{line:pos-update} or~\ref{line:neg-update}
-gets executed. In other words, $U$ is the number of times the $K$-tuple of
-vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets updated. It can be
-easily seen that $U = A + C$.
+line~\ref{line:pos-update} gets executed. Let $U = \sum_{t=1}^T (\one[S_t \neq
+\emptyset] z_t + \one[S_t = \emptyset](1 - z_t))$ be the number of rounds
+line~\ref{line:pos-update} or~\ref{line:neg-update} gets executed. In other
+words, $U$ is the number of times the $K$-tuple of vectors $(w_1^{(t)},
+w_2^{(t)}, \dots, w_K^{(t)})$ gets updated. It can be easily seen that $U = A +
+C$.
 
@@
 
-With probability one, the norm of each example is exactly $R$.
-We show that with probability
-one, the examples are strongly separable with margin $\gamma$. To see
-that, consider $w_1^*, w_2^*, \dots, w_K^* \in V$ defined by
+The norm of each example is exactly $R$. The examples are strongly separable
+with margin $\gamma$. To see that, consider $w_1^*, w_2^*, \dots, w_K^* \in V$
+defined by
 $$
@@
 
-for $i \in \{1,2,\dots,K\}$ and $j \in
-\{1,2,\dots,M\}$, we consider the inner product of $w_i^*$ and $v_j$.
+For $i \in \{1,2,\dots,K\}$ and $j \in
+\{1,2,\dots,M\}$, consider the inner product of $w_i^*$ and $v_j$.
 If $i = \ell_j$, $\ip{w_i^*}{v_j} = \gamma - \frac \gamma 2 = \frac \gamma 2$;
@@
 
-Define a filtration $\cbr{\calB_j}_{j=0}^M$,
-where $\calB_j = \sigma((x_1, y_1, \hat{y}_1), \ldots, (x_{(K-1)j}, y_{(K-1)j}, \hat{y}_{(K-1)j}))$
-for every $j$ in $\{1,2,\dots,M\}$.
-By Claim 2 of~\citet{Daniely-Helbertal-2013}, as $\ell_j$
-is chosen uniformly from $\cbr{1,\dots,K}$ and independent of $\calB_{j-1}$ and $\calA$'s
-randomness,
+Define a filtration of $\sigma$-algebras $\cbr{\calB_j}_{j=0}^M$, where $\calB_j
+= \sigma((x_1, y_1, \hat{y}_1), \ldots, (x_{(K-1)j}, y_{(K-1)j},
+\hat{y}_{(K-1)j}))$ for every $j$ in $\{1,2,\dots,M\}$. By Claim 2
+of~\citet{Daniely-Helbertal-2013}, as $\ell_j$ is chosen uniformly from
+$\cbr{1,\dots,K}$ and independent of $\calB_{j-1}$ and $\calA$'s randomness,
 $$
-\Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t ~\Bigg|~ \calB_{j-1} } \geq \frac{K-1}2 \; .
+\Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t ~\Bigg|~ \calB_{j-1} } \ge \frac{K-1}{2} \; .
 $$
@@
 $$
-\Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t } \ge \frac{K-1}2 \; .
+\Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t } \ge \frac{K-1}{2} \; .
 $$
@@
 
-%In these rounds,
-%the algorithm is guessing the label $\ell_j$. Since $\ell_j$ is chosen uniformly
-%at random from the set $\{1,2,\dots,K\}$ and feedback is only binary, the
-%expected number of mistakes the algorithm makes in these rounds is at least
-%$\frac{K-1}{2}$. Altogether, the algorithm makes at least $\frac{K-1}{2} M$
-%mistakes in expectation.
-
-%\chicheng{I think this part need to be formalized, by directly using
-%~\cite{Daniely-Helbertal-2013}, Claim 2.}
-%Can we assume without loss of generality
-%that a deterministic prediction algorithm will have a smaller expected cost?
-%If so, define $F(k)$ be the number of mistake that will be made by the algorithm,
-%if the adversary commits to a label uniformly at random from $\cbr{1,2,\ldots,k}$,
-%and the guessing of the label lasts for $k$ rounds.
-%we can construct a recurrence of $F$: $F(k) = F(k-1) + \frac{k-1}{k}$, and $F(1) = 0$.
-%Therefore, $F(K) = \Omega(K)$.
-
 Finally, since strong separability and norm condition hold with probability one,

### 2019-01-22 ICML-submission/empirical-comparison.tex
Fixes

--- 2019-01-22 ICML-submission/empirical-comparison.tex
@@
 \label{sec:experiments}
+
+We compare our algorithm with \textsc{Banditron} empirically to show that our
+kernelized bandit algorithm can have significant advantage over
+\textsc{Banditron} in the separable case.
+
+We generated strongly and weakly separable samples with $K=3$ classes shown
+in~\autoref{figure:strongly-and-weakly-separable-datasets}. The data sets are
+shown as two-dimensional, however, we used a third dimension (so-called
+\emph{constant} feature) i.e. a feature that for every example is set to $1$. We
+added the constant feature so that \autoref{figure:strongly-separable-dataset}
+is actually strongly lineraly separable. For both data sets, the sample size is
+$T=5\times 10^6$ and the margin is $\gamma=0.05$.
+
+\begin{figure}[h]
+\centering
+\begin{subfigure}[b]{0.23\textwidth}
+\captionsetup{justification=centering}
+\begin{center}
+\hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_points}
+\caption{Strongly separable case}
+\label{figure:strongly-separable-dataset}
+\end{center}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.23\textwidth}
+\captionsetup{justification=centering}
+\centering
+\hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_points}
+\caption{Weakly separable case}
+\label{figure:weakly-separable-dataset}
+\end{subfigure}
+\vspace*{-0.2cm}
+\caption{Strongly and weakly generated data sets with $K=3$ classes. All examples lie in
+the unit ball. Class 1 is depicted red. Classes 2 and 3 are depcited gree and
+blue, respectively. $80\%$ of example belong to class 1, $10\%$ of the data
+belong to class 2 and $10\%$ belong to class 3. Class 1 occupies the angle
+interval $[-15^\circ, 15^\circ]$, while classes 2 and 3 occupy angle intervals
+$[15^\circ, 180^\circ]$ and $[-180^\circ, -15^\circ]$ respectively. We removed
+points that lie within margin $\gamma=0.05$ of the linear separators.}
+\label{figure:strongly-and-weakly-separable-datasets}
+\end{figure}
+
+All results are averaged over $20$ runs.
+We plot the number of mistakes against time in Figure~\ref{fig:both}. We can see
+there is indeed a dilemma for \textsc{Banditron}: when picking a relatively
+large exploration rate, it suffers from the cost of continuous exploration; when
+picking a relatively small exploration rate, it cannot adapt its model quickly
+enough (this problem exacerbates when a majority class occupies a small region,
+like class 1). Striking a balance between the two extremes leads to the
+$\sqrt{T}$ mistake bound. On the contrary, our algorithm makes significant
+progress on every mistake it makes, leading to a finite mistake bound.
+
 \begin{figure}
@@
     \vspace*{-0.2cm}
-    \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$. }
-    %\includegraphics[width=0.25\textwidth]{figures/weak3}
+    \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$.}
     \label{fig:both}
 \end{figure}
-
-We compare our algorithm with \textsc{Banditron} empirically to show that our kernelized bandit algorithm can have significant advantage over \textsc{Banditron} is the separable case.
-
-We generate strongly and weakly separable samples with $K=3$ in a similar sense those in Figure~\ref{figure:weakly-linearly-separable-examples-with-margin}.
-They are originally generated in a $d=2$ plate, and then lifted to $d=3$ by adding a constant feature.
-We provide the figures of their exact look in Appendix~\ref{sec:supp-to-experiment}.
-Different from Figure~\ref{figure:weakly-linearly-separable-examples-with-margin}, the three classes are non-uniform and imbanlanced: class 1 occupies a smaller sector between $-15^\circ$ and $15^\circ$, while class 2 and class 3 occupy $[15^\circ, 180^\circ]$ and $[-180^\circ, -15^\circ]$ respectively.
-On the other hand, $80\%$ of data comes from class 1, while $10\%$ comes from class 2 and 3 each.
-
-In real world, data can often be non-uniform and imbalanced. We demonstrate that \textsc{Banditron} is weak especially under these situations, while our algorithm still performs well.
-
-We choose sample size as $5\times 10^6$ and margin as $\gamma=0.05$ (in both strongly weakly separable cases). All results are averaged over $20$ runs.
-
-We plot the number of mistakes against time in Figure~\ref{fig:both}.
-We can see there is indeed a dilemma for \textsc{Banditron}: when picking a relatively large exploration rate, it suffers from the cost of continuous exploration; when picking a relatively small exploration rate, it cannot adapt its model quickly enough (this problem exacerbates when a majority class occupies a small region, like class 1).
-Striking a balance between the two extremes leads to the $\sqrt{T}$ mistake bound.
-On the contrary, our algorithm makes significant progress on every mistake it makes, leading to a finite mistake bound.

### 2019-01-22 ICML-submission/from-weak-separability-to-strong-separability.tex
Fixes

@@
 
-\begin{proof}[Proof sketch of Theorem~\ref{theorem:margin-transformation}]
-Since the examples $(x_1, y_1)$,  $\dots$, $(x_T, y_T)$ are weakly
-linearly separable with margin $\gamma$, there are vectors $w_1, w_2, \dots, w_K$
-satisfying \eqref{equation:weak-linear-separability-1} and
-\eqref{equation:weak-linear-separability-2}.
+%\begin{proof}[Proof sketch of Theorem~\ref{theorem:margin-transformation}]
+%Since the examples $(x_1, y_1)$,  $\dots$, $(x_T, y_T)$ are weakly
+%linearly separable with margin $\gamma$, there are vectors $w_1, w_2, \dots, w_K$
+%satisfying \eqref{equation:weak-linear-separability-1} and
+%\eqref{equation:weak-linear-separability-2}.
 
-Fix any $i \in \{1,2,\dots,K\}$. Consider the $K-1$ vectors $(w_i - w_j)/2$ for
-$j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors have norm at most
-$1$. We consider two cases regarding the relationship between $\gamma_1$ and
-$\gamma_2$.
+%Fix any $i \in \{1,2,\dots,K\}$. Consider the $K-1$ vectors $(w_i - w_j)/2$ for
+%$j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors have norm at most
+%$1$. We consider two cases regarding the relationship between $\gamma_1$ and
+%$\gamma_2$.
 
-\paragraph{Case 1: $\gamma_1 \geq \gamma_2$.} In this setting,
-Theorem~\ref{theorem:polynomial-approximation-1} implies that there exist a
-multivariate polynomial $p_i:\R^d \to \R$
+%\paragraph{Case 1: $\gamma_1 \geq \gamma_2$.} In this setting,
+%Theorem~\ref{theorem:polynomial-approximation-1} implies that there exist a
+%multivariate polynomial $p_i:\R^d \to \R$
 
-\begin{align*}
-\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{{2}/{\gamma}} \right\rceil \; ,
-\end{align*}
-such that all examples $x$ in $R_i^+$ (resp. $R_i^-$) satisfy $p_i(x) \geq 1/2$
-(resp. $p_i(x) \leq -1/2$).
-Therefore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
- and if $y_t \neq i$ then $p_i(x_t) \le -1/2$, and
-\begin{align*}
-&\norm{p_i} 
-\\
-& \le 
-\left[
-  188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil 
-\right]^{
-  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil }{2}
-} \; . \\
-\end{align*}
-By \autoref{lemma:norm-bound}, there exists $c_i \in \ell_2$ such that
-$\ip{c_i}{\phi(x)}_{\ell_2} = p_i(x)$, and
-\begin{align*}
-&\norm{c_i}_{\ell_2}
-\\
-& \le 
-\left[
-  376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil 
-\right]^{
-  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil}{2}
-} \; .
-\end{align*}
-Define vectors $u_i \in \ell_2$ as
-\begin{align*}
-u_i & = 
-\frac{c_i/\sqrt{K}}{ 
-  \left[
-    376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil 
-  \right]^{
-    \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}{2}
-  }
-} \; . \\
-\end{align*}
+%\begin{align*}
+%\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{{2}/{\gamma}} \right\rceil \; ,
+%\end{align*}
+%such that all examples $x$ in $R_i^+$ (resp. $R_i^-$) satisfy $p_i(x) \geq 1/2$
+%(resp. $p_i(x) \leq -1/2$).
+%Therefore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
+% and if $y_t \neq i$ then $p_i(x_t) \le -1/2$, and
+%\begin{align*}
+%&\norm{p_i}
+%\\
+%& \le
+%\left[
+%  188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
+%\right]^{
+%  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil }{2}
+%} \; . \\
+%\end{align*}
+%By \autoref{lemma:norm-bound}, there exists $c_i \in \ell_2$ such that
+%$\ip{c_i}{\phi(x)}_{\ell_2} = p_i(x)$, and
+%\begin{align*}
+%&\norm{c_i}_{\ell_2}
+%\\
+%& \le
+%\left[
+%  376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
+%\right]^{
+%  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil}{2}
+%} \; .
+%\end{align*}
+%Define vectors $u_i \in \ell_2$ as
+%\begin{align*}
+%u_i & =
+%\frac{c_i/\sqrt{K}}{
+%  \left[
+%    376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
+%  \right]^{
+%    \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}{2}
+%  }
+%} \; . \\
+%\end{align*}
 
-Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$.
-Futhermore, for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma_1$
-and for all $j \in \{1,2,\dots,K\} \setminus \{y_t\}$,
-$\ip{u_j}{x_t} \le - \gamma_1$. In other words,
-$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
-strongly linearly separable with margin $\gamma_1 = \max\{\gamma_1, \gamma_2\}$.
+%Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$.
+%Futhermore, for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma_1$
+%and for all $j \in \{1,2,\dots,K\} \setminus \{y_t\}$,
+%$\ip{u_j}{x_t} \le - \gamma_1$. In other words,
+%$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
+%strongly linearly separable with margin $\gamma_1 = \max\{\gamma_1, \gamma_2\}$.
 
-\paragraph{Case 2: $\gamma_1 \leq \gamma_2$.} Following the
-same idea as Case 1 and using Theorem~\ref{theorem:polynomial-approximation-1},
-we can show that
-$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
-strongly linearly separable with margin $\gamma_2 = \max\{\gamma_1, \gamma_2\}$.
-%The proof for the case of $\gamma_1 < \gamma_2$
-%is symmetric.
+%\paragraph{Case 2: $\gamma_1 \leq \gamma_2$.} Following the
+%same idea as Case 1 and using Theorem~\ref{theorem:polynomial-approximation-1},
+%we can show that
+%$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
+%strongly linearly separable with margin $\gamma_2 = \max\{\gamma_1, \gamma_2\}$.
 
-In summary, the examples are strongly
-linearly separable with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
-Finally, observe that for any $t=1,2,\dots,T$,
-\[
-k(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
-\qedhere
-\]
-\end{proof}
+%In summary, the examples are strongly
+%linearly separable with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
+%Finally, observe that for any $t=1,2,\dots,T$,
+%\[
+%k(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
+%\qedhere
+%\]
+%\end{proof}

### 2019-01-22 ICML-submission/empirical-comparison.tex
Fix experiments section

@@
 \section{Experiments}
-\label{sec:experiments}
+\label{section:experiments}
 
-We compare our algorithm with \textsc{Banditron} empirically to show that our
-kernelized bandit algorithm can have significant advantage over
-\textsc{Banditron} in the separable case.
-
-We generated strongly and weakly separable samples with $K=3$ classes shown
-in~\autoref{figure:strongly-and-weakly-separable-datasets}. The data sets are
-shown as two-dimensional, however, we used a third dimension (so-called
-\emph{constant} feature) i.e. a feature that for every example is set to $1$. We
-added the constant feature so that \autoref{figure:strongly-separable-dataset}
-is actually strongly lineraly separable. For both data sets, the sample size is
-$T=5\times 10^6$ and the margin is $\gamma=0.05$.
+We implemented
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
+Algorithm~\ref{algorithm:kernelized} with
+kernel~\eqref{equation:rational-kernel}, and the \textsc{Banditron} algorithm.
+We generated strongly and weakly separable data sets with $K=3$ classes. The
+data sets are shown in~\autoref{figure:strongly-and-weakly-separable-datasets}.
+Although, the data sets are shown as two-dimensional, we used a third dimension,
+the so-called \emph{constant feature}, i.e. a feature that for every example is
+set to $1$. We added the constant feature so that
+\autoref{figure:strongly-separable-dataset} is actually strongly lineraly
+separable. For both data sets, the sample size is $T=5\times 10^6$ and the
+margin is $\gamma=0.05$.
 
@@
 \vspace*{-0.2cm}
-\caption{Strongly and weakly generated data sets with $K=3$ classes. All examples lie in
-the unit ball. Class 1 is depicted red. Classes 2 and 3 are depcited gree and
-blue, respectively. $80\%$ of example belong to class 1, $10\%$ of the data
-belong to class 2 and $10\%$ belong to class 3. Class 1 occupies the angle
-interval $[-15^\circ, 15^\circ]$, while classes 2 and 3 occupy angle intervals
-$[15^\circ, 180^\circ]$ and $[-180^\circ, -15^\circ]$ respectively. We removed
-points that lie within margin $\gamma=0.05$ of the linear separators.}
+\caption{Strongly and weakly generated data sets with $K=3$ classes. All
+examples lie in the unit ball of $\R^2$. Class 1 is depicted red. Classes 2 and
+3 are depcited gree and blue, respectively. $80\%$ of the examples belong to class 1,
+$10\%$ belong to class 2 and $10\%$ belong to class 3. Class 1
+occupies the angle interval $[-15^\circ, 15^\circ]$, while classes 2 and 3
+occupy angle intervals $[15^\circ, 180^\circ]$ and $[-180^\circ, -15^\circ]$
+respectively. We removed points that lie within margin $\gamma=0.05$ of the
+linear separator.}
 \label{figure:strongly-and-weakly-separable-datasets}
@@
 
-All results are averaged over $20$ runs.
-We plot the number of mistakes against time in Figure~\ref{fig:both}. We can see
-there is indeed a dilemma for \textsc{Banditron}: when picking a relatively
-large exploration rate, it suffers from the cost of continuous exploration; when
-picking a relatively small exploration rate, it cannot adapt its model quickly
-enough (this problem exacerbates when a majority class occupies a small region,
-like class 1). Striking a balance between the two extremes leads to the
-$\sqrt{T}$ mistake bound. On the contrary, our algorithm makes significant
-progress on every mistake it makes, leading to a finite mistake bound.
+We evaluated all three the algorithms on the two data sets. Since all three
+algorithms are randomized, we run each algorithm $20$ times. \textsc{Banditron}
+has exploration rate parameter $\epsilon$ for which we tried values $\epsilon
+\in \{0.02, 0.01, 0.005, 0.002, 0.001, 0.0005 \}$. The average cumulative number
+of mistakes up to round $t$ as a function $t$ are shown in
+Figures~\ref{figure:number-of-mistakes-strongly-separable-dataset}
+and~\ref{figure:number-of-mistakes-weakly-separable-dataset}.
+
+We can see there is a dilemma for \textsc{Banditron}. When the
+exploration rate $\epsilon$ is large, it suffers from the cost of exploration.
+When the exploration rate is small, it cannot adapt its model quickly enough.
+This problem is exacerbated when a majority class occupies a small region, like
+class 1. Striking a balance between the two extremes leads to the
+$\Theta(\sqrt{T})$ number of mistakes. In contrast, our algorithm makes
+significant progress on every mistake it makes, leading to a finite mistake
+bound.
+
+Appendix~\ref{section:supp-to-experiment} shows decision boundaries
+that each of the algorithms learns.
 
@@
 \centering
-    \begin{subfigure}[b]{0.23\textwidth}
-        \captionsetup{justification=centering}
-        \begin{center}
-        \hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0.1cm, 0, 0}, clip]{figures/strong3}
-        \caption{Strongly separable case}
-        \end{center}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.23\textwidth}
-        \captionsetup{justification=centering}
+\includegraphics[width=0.45\textwidth]{figures/strong3}
+\caption{Strongly separable case. Cumulative number of mistakes of various algorithms.}
+\label{figure:number-of-mistakes-strongly-separable-dataset}
+\end{figure}
+
+\begin{figure}
 \centering
-        \hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0.1cm, 0, 0}, clip]{figures/weak3}
-        \caption{Weakly separable case}
-    \end{subfigure}
-    \vspace*{-0.2cm}
-    \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$.}
-    \label{fig:both}
+\includegraphics[width=0.45\textwidth]{figures/weak3}
+\caption{Weakly separable case. Cumulative number of mistakes of various algorithms.}
+\label{figure:number-of-mistakes-weakly-separable-dataset}
 \end{figure}

### 2019-01-22 ICML-submission/from-weak-separability-to-strong-separability.tex
Fix experiments section

@@
 The kernel function $k:\B(\zero,1) \times \B(\zero,1) \to \R$ is defined as
-$$
+\begin{equation}
+\label{equation:rational-kernel}
 k(x,x') = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}_{\R^d}} \; .
-$$
+\end{equation}
 Note that kernel function $k(x,x')$ can be evaluated in $O(d)$ time.
@@
 mapping $\phi$ maps any set of weakly linearly separable examples to a strongly
-linearly separable set of examples. Due to space constraints, we only sketch the
-proof of Theorem~\ref{theorem:margin-transformation} here, and defer the full
-proof to Appendix~\ref{section:full-proof-of-theorem-margin-transformation}.
+linearly separable set of examples. Due to space constraints, we defer the full
+proof to Appendix~\ref{section:proof-of-theorem-margin-transformation}.
 

### 2019-01-22 ICML-submission/appendix-nearest-neighbor-algorithm.tex
Fixes

@@
 \section{Nearest neighbor algorithm}
+\label{section:nearest-neighbor-algorithm}
+
 \begin{algorithm}
@@
 \IF{$\min_{(x,y) \in S} \| x_t - x \|_2 \leq \gamma$}
-	\STATE $\hat{y}_t \gets \tilde{y}$, where $(\tilde{x}, \tilde{y}) = \argmin_{(x,y) \in S} \| x_t - x \|_2$.
+	\STATE $\hat{y}_t \gets \tilde{y}$, where $(\tilde{x}, \tilde{y}) = \argmin_{(x,y) \in S} \norm{x_t - x}_2$.
 \ELSE
-	\STATE Predict $\hat{y}_t$ uniformly at random from $\cbr{1,\ldots,K}$, receive feedback $z_t = \one[\hat{y}_t \neq y_t]$.
+	\STATE Predict $\hat{y}_t$ uniformly at random from $\cbr{1,2,\dots,K}$, receive feedback $z_t = \indicator{\hat{y}_t \neq y_t}$.
   \label{line:nn-explore}
@@
 
-We present Algorithm~\ref{alg:nn} in this section. The algorithm is based on the following insight.
+We present Algorithm~\ref{alg:nn} in this section. The algorithm is based on the
+following insight.
 
 \begin{lemma}
-Suppose $(x_1,y_1), \ldots, (x_T, y_T)$ is a set of $\gamma$-weakly linearly separable examples.
-For $i$, $j$ in $\cbr{1,\ldots,T}$, if $x_i$ and $x_j$ have $\ell_2$ distance at most $\gamma$, then $y_i = y_j$.
-\label{lem:nn}
+Suppose $(x_1,y_1), \ldots, (x_T, y_T)$ is a set of $\gamma$-weakly linearly
+separable examples. For $i$, $j$ in $\cbr{1,\ldots,T}$, if $x_i$ and $x_j$ have
+$\ell_2$ distance at most $\gamma$, then $y_i = y_j$. \label{lem:nn}
 \end{lemma}
+
 \begin{proof}
-Suppose for the sake on contradiction that $y_i \neq y_j$.
-By Definition~\ref{definition:weak-linear-separability}, there exists a set of $k$ vectors $(w_1, \ldots, w_k)$, such that Equations~\eqref{equation:weak-linear-separability-1}
+Suppose for the sake on contradiction that $y_i \neq y_j$. By
+Definition~\ref{definition:weak-linear-separability}, there exists a set of $k$
+vectors $(w_1, \ldots, w_k)$, such that
+Equations~\eqref{equation:weak-linear-separability-1}
 and~\eqref{equation:weak-linear-separability-1} are satisfied.
@@
 \begin{theorem}
-Suppose $(x_1,y_1), \ldots, (x_T, y_T)$ is a set of $\gamma$-weakly linearly separable examples.
-In addition, for all $t$ in $\cbr{1,\ldots,T}$, $\| x_t \| \leq R$.
-Then, the expected number of mistakes made by Algorithm~\ref{alg:nn} is such that
-\[\Exp[M] \leq (K-1) (\frac R \gamma)^d. \]
 \label{thm:margin_at_upper}
+Suppose $(x_1,y_1), \ldots, (x_T, y_T)$ is a set of $\gamma$-weakly linearly
+separable examples. In addition, for all $t$ in $\cbr{1,2,\dots,T}$, $\| x_t \|
+\leq R$. Then, the expected number of mistakes made by Algorithm~\ref{alg:nn} is
+such that \[\Exp[M] \le (K-1) (\frac R \gamma)^d. \]
 \end{theorem}
+
 \begin{proof}
-Let $b_t$ be the indicator that line~\ref{line:nn-explore} is executed at timestep $t$,
-i.e. we fall into the ``else'' case.
-Note that if $b_t = 0$, then by Lemma~\ref{lem:nn}, the prediction $\hat{y}_t$ must equal $y_t$, i.e. $z_t = 0$.
-Therefore, $M = \sum_{t=1}^T z_t = \sum_{t=1}^T b_t z_t$. Let $U = \sum_{t=1}^T b_t (1-z_t)$; it can be seen that $U$ is the number of times when $S$ gets updated. As $S$ is a $\gamma$-packing over
-$\cbr{x: \|x\|_2 \leq R}$, the size of $S$ is at most $(\frac R \gamma)^d$, which is also an upper bound on $U$.
+Let $b_t$ be the indicator that line~\ref{line:nn-explore} is executed at
+timestep $t$, i.e. we fall into the ``else'' case. Note that if $b_t = 0$, then
+by Lemma~\ref{lem:nn}, the prediction $\hat{y}_t$ must equal $y_t$, i.e. $z_t =
+0$. Therefore, $M = \sum_{t=1}^T z_t = \sum_{t=1}^T b_t z_t$. Let $U =
+\sum_{t=1}^T b_t (1-z_t)$; it can be seen that $U$ is the number of times when
+$S$ gets updated. As $S$ is a $\gamma$-packing over $\cbr{x: \|x\|_2 \leq R}$,
+the size of $S$ is at most $(\frac R \gamma)^d$, which is also an upper bound on
+$U$.
 

### 2019-01-22 ICML-submission/appendix-proofs-for-strongly-separable-examples.tex
Fixes

@@
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
-makes. Let $A = \sum_{t=1}^T \one[S_t \neq \emptyset] z_t$ be the number of
+makes. Let $A = \sum_{t=1}^T \indicator{S_t \neq \emptyset} z_t$ be the number of
 mistakes in the rounds when $S_t \neq \emptyset$, i.e. the number of rounds
 line~\ref{line:neg-update} is executed. In addition, let $B = \sum_{t=1}^T
-\one[S_t = \emptyset] z_t$ be the number of mistakes in the rounds when $S_t =
+\indicator{S_t = \emptyset} z_t$ be the number of mistakes in the rounds when $S_t =
 \emptyset$. It can be easily seen that $M = A + B$.
 
-Let $C = \sum_{t=1}^T \one[S_t = \emptyset](1 - z_t)$ be the number of rounds
-line~\ref{line:pos-update} gets executed. Let $U = \sum_{t=1}^T (\one[S_t \neq
-\emptyset] z_t + \one[S_t = \emptyset](1 - z_t))$ be the number of rounds
+Let $C = \sum_{t=1}^T \indicator{S_t = \emptyset}(1 - z_t)$ be the number of rounds
+line~\ref{line:pos-update} gets executed. Let $U = \sum_{t=1}^T (\indicator{S_t \neq
+\emptyset} z_t + \indicator{S_t = \emptyset}(1 - z_t))$ be the number of rounds
 line~\ref{line:pos-update} or~\ref{line:neg-update} gets executed. In other

### 2019-01-22 ICML-submission/appendix-nearest-neighbor-algorithm.tex
Clean-ups

@@
 
-\begin{algorithm}
-\caption{A nearest-neighbor algorithm for \textsc{Online Multiclass Linear Classification with
-Bandit Feedback}}
+\begin{algorithm}[H]
+\caption{\textsc{Nearest-Neighbor Algorithm}}
 \begin{algorithmic}[1]
+\REQUIRE{Number of classes $K$, number of rounds $T$.}
+\REQUIRE{Inner product space $(V,\ip{\cdot}{\cdot})$.}
 \STATE $S \gets \emptyset$.
 \FOR{$t=1,2,\ldots,T$:}
-\IF{$\min_{(x,y) \in S} \| x_t - x \|_2 \leq \gamma$}
-	\STATE $\hat{y}_t \gets \tilde{y}$, where $(\tilde{x}, \tilde{y}) = \argmin_{(x,y) \in S} \norm{x_t - x}_2$.
+\IF{$\min_{(x,y) \in S} \norm{x_t - x} \le \gamma$}
+  \STATE{Find nearest neighbor \\ $(\widetilde{x}, \widetilde{y}) = \argmin_{(x,y) \in S} \norm{x_t - x}$}
+	\STATE{Predict $\widehat{y}_t = \widetilde{y}$}
 \ELSE
-	\STATE Predict $\hat{y}_t$ uniformly at random from $\cbr{1,2,\dots,K}$, receive feedback $z_t = \indicator{\hat{y}_t \neq y_t}$.
-  \label{line:nn-explore}
+	\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
+	\STATE{Receive feedback $z_t = \indicator{\widehat{y}_t \neq y_t}$}
+  \label{line:nearest-neighbor-explore}
 	\IF{$z_t = 0$}
-    \STATE $S \gets S \cup \cbr{(x_t, \hat{y}_t)}$.
+    \STATE $S \gets S \cup \cbr{(x_t, \widehat{y}_t)}$.
   \ENDIF
@@
 \end{algorithmic}
-\label{alg:nn}
+\label{algorithm:nearest-neighbor}
 \end{algorithm}
 
-We present Algorithm~\ref{alg:nn} in this section. The algorithm is based on the
-following insight.
+In this section we analyze \textsc{Nearest-Neighbor Algorithm} shown as
+Algorithm~\ref{algorithm:nearest-neighbor}. The algorithm is based on the idea
+that two examples that are close to each other must have the same label. Lemma
+below formalizes this intuition.
 
 \begin{lemma}
-Suppose $(x_1,y_1), \ldots, (x_T, y_T)$ is a set of $\gamma$-weakly linearly
-separable examples. For $i$, $j$ in $\cbr{1,\ldots,T}$, if $x_i$ and $x_j$ have
-$\ell_2$ distance at most $\gamma$, then $y_i = y_j$. \label{lem:nn}
+\label{lemma:nearest-neighbor}
+Let $(V,\ip{\cdot}{\cdot})$ be a vector space, $K$ be a positive integer and let
+$\gamma$ be a positive real number. Suppose $(x_1,y_1), (x_2,y_2), \dots, (x_T,
+y_T) \in V \times \{1,2,\dots,K\}$ are labeled examples that are weakly linearly
+separable with margin $\gamma$. For $i$, $j$ in $\cbr{1,2,\dots,T}$, if
+$\norm{x_i - x_j}_2 \le \gamma$ then $y_i = y_j$.
 \end{lemma}
@@
 Suppose for the sake on contradiction that $y_i \neq y_j$. By
-Definition~\ref{definition:weak-linear-separability}, there exists a set of $k$
+Definition~\ref{definition:linear-separability}, there exists a set of $k$
 vectors $(w_1, \ldots, w_k)$, such that
-Equations~\eqref{equation:weak-linear-separability-1}
-and~\eqref{equation:weak-linear-separability-1} are satisfied.
+conditions~\eqref{equation:weak-linear-separability-1}
+and~\eqref{equation:weak-linear-separability-2} are satisfied.
 
 Specifically,
-\[ \ip{w_{y_i} - w_{y_j}}{x_i} \geq \gamma \]
-\[ \ip{w_{y_j} - w_{y_i}}{x_j} \geq \gamma \]
-
+\begin{align*}
+\ip{w_{y_i} - w_{y_j}}{x_i} & \ge \gamma \; , \\
+\ip{w_{y_j} - w_{y_i}}{x_j} & \ge \gamma \; .
+\end{align*}
 This implies that
-\[ \ip{w_{y_i} - w_{y_j}}{x_i - x_j} \geq 2\gamma \]
+$$
+\ip{w_{y_i} - w_{y_j}}{x_i - x_j} \ge 2\gamma \; .
+$$
 
 On the other hand,
-\[ \ip{w_{y_i} - w_{y_j}}{x_i - x_j} \leq \| w_{y_i} - w_{y_j} \| \| x_i - x_j \| \leq \sqrt{2} \gamma \]
-where the first inequality is from Cauchy-Schwarz,
-the second inequality is from that
-$\|w_{y_i} - w_{y_j}\| \leq \sqrt{2(\|w_{y_i}\|^2 + \|w_{y_j}\|^2)} \leq \sqrt{2}$ and our assumption
-on $x_i$ and $x_j$. Therefore, we reach a contradiction.
+$$
+\ip{w_{y_i} - w_{y_j}}{x_i - x_j} \le \norm{w_{y_i} - w_{y_j}} \cdot \norm{x_i - x_j} < \sqrt{2} \gamma
+$$
+where the first inequality is from Cauchy-Schwartz inequality, the second
+inequality is from that $\norm{w_{y_i} - w_{y_j}} \le \sqrt{2(\norm{w_{y_i}}^2 +
+\norm{w_{y_j}}^2)} \leq \sqrt{2}$ and our assumption on $x_i$ and $x_j$.
+Therefore, we reach a contradiction.
 \end{proof}
@@
 \begin{theorem}
-\label{thm:margin_at_upper}
-Suppose $(x_1,y_1), \ldots, (x_T, y_T)$ is a set of $\gamma$-weakly linearly
-separable examples. In addition, for all $t$ in $\cbr{1,2,\dots,T}$, $\| x_t \|
-\leq R$. Then, the expected number of mistakes made by Algorithm~\ref{alg:nn} is
-such that \[\Exp[M] \le (K-1) (\frac R \gamma)^d. \]
+\label{theorem:margin_at_upper}
+Let $K$ and $d$ be positive integers and let $\gamma$ be a positive real number.
+Suppose $(x_1,y_1), \ldots, (x_T, y_T) \in \R^d \times \{1,2,\dots,K\}$ are
+labeled examples that are weakly linearly separable with margin $\gamma$ and
+satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$. Then, the expected
+number of mistakes made by Algorithm~\ref{algorithm:nearest-neighbor} is at most
+$$
+(K-1) \left( \frac{R}{\gamma} \right)^d \; .
+$$
 \end{theorem}
@@
 \begin{proof}
-Let $b_t$ be the indicator that line~\ref{line:nn-explore} is executed at
-timestep $t$, i.e. we fall into the ``else'' case. Note that if $b_t = 0$, then
-by Lemma~\ref{lem:nn}, the prediction $\hat{y}_t$ must equal $y_t$, i.e. $z_t =
-0$. Therefore, $M = \sum_{t=1}^T z_t = \sum_{t=1}^T b_t z_t$. Let $U =
-\sum_{t=1}^T b_t (1-z_t)$; it can be seen that $U$ is the number of times when
-$S$ gets updated. As $S$ is a $\gamma$-packing over $\cbr{x: \|x\|_2 \leq R}$,
-the size of $S$ is at most $(\frac R \gamma)^d$, which is also an upper bound on
-$U$.
+Let $M$ be the number of mistakes made by the algorithm. Let $b_t$ be the
+indicator that line~\ref{line:nearest-neighbor-explore} is executed at timestep
+$t$, i.e. we fall into the ``else'' case. Note that if $b_t = 0$, then by
+Lemma~\ref{lemma:nearest-neighbor}, the prediction $\widehat{y}_t$ must equal
+$y_t$, i.e. $z_t = 0$. Therefore, $M = \sum_{t=1}^T z_t = \sum_{t=1}^T b_t z_t$.
+Let $U = \sum_{t=1}^T b_t (1-z_t)$. Clearly, $|S| = U$. Since $S$ is a
+$\gamma$-packing over $\cbr{x \in \R^d ~:~ \norm{x} \le R}$, the size of $S$ is
+at most $(\frac R \gamma)^d$, which is also an upper bound on $U$.
 
-Note that when $b_t = 1$, $\hat{y}_t$ is chosen uniformly at random, we have
-\[ \Exp[ z_t | b_t = 1] = \frac{K-1}{K} \]
+Note that when $b_t = 1$, $\widehat{y}_t$ is chosen uniformly at random, we have
+$$
+\Exp[ z_t | b_t = 1] = \frac{K-1}{K} \; .
+$$
 Therefore,
-\[ \Exp[M] = \Exp[\sum_{t=1}^T b_t z_t] = \frac{K-1}{K} \Exp[\sum_{t=1}^T b_t]. \]
+$$
+\Exp[M] = \Exp \left[ \sum_{t=1}^T b_t z_t \right] = \frac{K-1}{K} \Exp \left[ \sum_{t=1}^T b_t \right] \; .
+$$
 On the other hand,
-\[ \Exp[U] = \Exp[\sum_{t=1}^T b_t (1-z_t)] = \frac 1 K \Exp[\sum_{t=1}^T b_t]. \]
+$$
+\Exp[U] = \Exp \left[ \sum_{t=1}^T b_t (1-z_t) \right] = \frac 1 K \Exp \left[\sum_{t=1}^T b_t \right] \; .
+$$
 Therefore,
-\[ \Exp[M] = (K-1) \Exp[U] \leq (K-1) (\frac R \gamma)^d. \]
+$$
+\Exp[M] = (K-1) \Exp[U] \leq (K-1) \left(\frac{R}{\gamma} \right)^d \; .
+$$
 \end{proof}

### 2019-01-22 ICML-submission/appendix-proofs-for-strongly-separable-examples.tex
Clean-ups

@@
 where the last inequality follows from a case analysis on $z_t$ and
-Definition~\ref{definition:weak-linear-separability}: if $z_t = 0$, then
+Definition~\ref{definition:linear-separability}: if $z_t = 0$, then
 $\widehat y_t = y_t$, by Equation~\eqref{equation:strong-linear-separability-2},

### 2019-01-22 ICML-submission/introduction.tex
Clean-ups

@@
 Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
-viewed as a repeated game between a learner and an adversary. At each
-timestep $t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals $x_t\in \R^d$ to the learner.  
-Upon receiving $x_t$, the learner makes a prediction $\widehat{y}_t$ and receives feedback. 
-In contrast to the
-standard full-information setting, where the feedback given is the correct label
-$y_t$, here the feedback is only a binary indicator of whether the prediction
-was correct or not. The protocol of the problem is formally stated below.
+viewed as a repeated game between a learner and an adversary. At each timestep
+$t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals $x_t\in
+\R^d$ to the learner. Upon receiving $x_t$, the learner makes a prediction
+$\widehat{y}_t$ and receives feedback. In contrast with the standard
+full-information setting, where the feedback given is the correct label $y_t$,
+here the feedback is only a binary indicator of whether the prediction was
+correct or not. The protocol of the problem is formally stated below.
 
@@
 Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
-     Observe feedback
-          $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
-%$z_t \in \{0,1\}$, \\ \qquad where $z_t = \begin{cases}
-%0 & \text{if $\widehat y_t = y_t$,} \\
-%1 & \text{if $\widehat y_t \neq y_t$.}
-%\end{cases}$
+Observe feedback $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
 }
-
 \end{protocol}
@@
 two notions of linear separability, \emph{weak} and \emph{strong}, formally
-stated in
-Definition~\ref{definition:weak-linear-separability}.
-The standard notion of multiclass linear
-separability~\citep{Crammer-Singer-2003} corresponds to the weak linear
-separability. %For binary classification, the weak and strong separability are
-%identical. However, they differ for multiclass classification with $K \ge 3$
-%classes. 
-For multiclass classification with $K$ classes, weak linear
-separability requires that all examples from the same class lie in an intersection of $K-1$ halfspaces and all other examples lie in the complement of
+stated in \autoref{definition:linear-separability}. The standard notion of
+multiclass linear separability~\citep{Crammer-Singer-2003} corresponds to the
+weak linear separability. For multiclass classification with $K$ classes, weak
+linear separability requires that all examples from the same class lie in an
+intersection of $K-1$ halfspaces and all other examples lie in the complement of
 the intersection of the halfspaces. Strong linear separability means that
@@
 weakly linearly separable with a margin $\gamma$, then the \textsc{Multiclass
-Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
-%%%%%
-It is also known that any (possibly randomized) algorithm must
-make $\frac{1}{2} \left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the
-worst case.
-The \textsc{Multiclass Perceptron} achieves an
-information-theoretically optimal mistake bound, while being
-computationally and memory efficient.
-~\footnote{
-%%%%%
-%These are folklore results. 
-For completeness, we present these 
-folklore
-%%%%%
-results along
-with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs} in the
-supplementary material.}
+Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes. It
+is also known that any (possibly randomized) algorithm must make $\frac{1}{2}
+\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. The
+\textsc{Multiclass Perceptron} achieves an information-theoretically optimal
+mistake bound, while being computationally and memory efficient.~\footnote{For
+completeness, we present these folklore results along with their proofs in
+Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
+material.}
 
@@
 mistake bound under the strong linear separability condition, their proof of
-Theorem 2 is incorrect: first, their Theorem 2
-implies a mistake upper bound of $\frac{R}{\gamma}$ with
-sufficiently large $C$, which contradicts our lower
+Theorem 2 is incorrect: first, their Theorem 2 implies a mistake upper bound of
+$\frac{R}{\gamma}$ with sufficiently large $C$, which contradicts our lower
 bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
-second, their Lemma 4 cannot be directly applied to the bandit
-setting, as the algorithm only makes updates on a subset of the $w_i$'s.} We
-design a simple and efficient algorithm
+second, their Lemma 4 cannot be directly applied to the bandit setting, as the
+algorithm only makes updates on a subset of the $w_i$'s.} We design a simple and
+efficient algorithm
 (Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
@@
 $\Omega(K (R/\gamma)^2))$ mistakes in the worst case. The extra $O(K)$
-multiplicative factor the mistake bound, as compared to the full-information
+multiplicative factor in the mistake bound, as compared to the full-information
 setting, is the price we pay for the bandit feedback, or more precisely, the
@@
 
-For the case when the examples are weakly linearly separable, it was open for a long 
-time whether there exist \textit{efficient} algorithms with finite mistake 
+For the case when the examples are weakly linearly separable, it was open for a
+long time whether there exist \textit{efficient} algorithms with finite mistake
 bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}.
 Furthermore, in~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, they ask the question:
-is there \textit{any} algorithm with a finite mistake bound that has no explicit dependence 
-on the dimensionality of the feature vectors? We answer both questions affirmatively by
-providing an efficient algorithm with finite dimensionless mistake bound 
-(Algorithm~\ref{algorithm:kernelized}) (Note: the second question was previously 
-answered by~\cite{Daniely-Helbertal-2013} with an inefficient algorithm).
+Is there \textit{any} algorithm with a finite mistake bound that has no explicit
+dependence on the dimensionality of the feature vectors? We answer both
+questions affirmatively by providing an efficient algorithm with finite
+dimensionless mistake bound (Algorithm~\ref{algorithm:kernelized}).\footnote{An
+in inefficient algorithm was given by~\cite{Daniely-Helbertal-2013}.}
 
@@
 non-linear feature mapping $\phi$ and associated positive definite kernel
-$k(x,x')$ that makes the examples \emph{strongly} linearly separable in a higher-dimensional space. 
-We then use the kernelized version of
+$k(x,x')$ that makes the examples \emph{strongly} linearly separable in a
+higher-dimensional space. We then use the kernelized version of
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} for
@@
 \log K))}$ mistakes.
+
+In Appendix~\ref{section:nearest-neighbor-algorithm}, we propose a very
+different algorithm that is based on the obvious idea that two points that are
+close enough must have the same label. Here, close enough means that they cannot
+be separated from each other by a linear separator with a margin.

### 2019-01-22 ICML-submission/notions-of-linear-separability.tex
Clean-ups

@@
 [Linear separability]
-\label{definition:weak-linear-separability}
+\label{definition:linear-separability}
 Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive

### 2019-01-22 ICML-submission/introduction.tex
Fixes

@@
 
-In Appendix~\ref{section:nearest-neighbor-algorithm}, we propose a very
-different algorithm that is based on the obvious idea that two points that are
-close enough must have the same label. Here, close enough means that they cannot
-be separated from each other by a linear separator with a margin.
+In Appendix~\ref{section:nearest-neighbor-algorithm}, we propose and analyze a
+very different algorithm for weakly separable data. The algorithm is based on
+the obvious idea that two points that are close enough must have the same label.
+
+Finally, we study two questions related to the computational and
+information-theoretic hardness of the problem. Any algorithm for the bandit
+setting collects information in the form of so called \emph{strongly labeled}
+and \emph{weakly labeled} examples. Strongly labeled examples are those for
+which we know the class label. Weakly labeled example is an example for which we
+know that class label can be anything except for a particular one class.
+In Appendix~\ref{section:np-hardness-of-weak-labeling-problem}, we show that the offline
+problem of finding a linear multiclass separator consistent with a set of
+strongly and weakly labeled examples is NP-hard. In
+Appendix~\ref{section:mistake-lower-bound-for-ignorant-algorithms}, we show that
+any algorithm that uses only strongly-labeled examples and ignores weakly
+labeled examples makes at least $\Omega\left( \left(1/(160 \gamma)\right)^{(d-2)/4} \right)$
+mistakes.

### 2019-01-22 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Fixes

--- 2019-01-10 arxiv-version/mistake-lower-bound-for-ignorant-algorithms.tex
@@
 \section{Mistake lower bound for ignorant algorithms}
+\label{section:mistake-lower-bound-for-ignorant-algorithms}
+
 In this section, we prove a mistake lower bound for a family of algorithms called \textit{ignorant algorithms}.

### 2019-01-22 ICML-submission/appendix-proofs-of-polynomial-approximation-theorems.tex
Fixes

@@
 & = \norm{ \sum_{j=0}^s c_j (f_i)^j }^2 \\
-& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 \qquad \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
+& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 \quad \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
 & = (s + 1) \sum_{j=0}^s (c_j)^2 \norm{(f_i)^j}^2 \\
-& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} \qquad \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
+& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} \quad \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
 & \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j 2^{2j} \\
@@
 & = (s + 1) s^s 2^{2s} \norm{T_s}^2 \\
-& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} \qquad \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
+& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} \quad \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
 & = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
-& \le \left(8(1+\sqrt{2})^2 s \right)^s \quad \text{(since $s+1 \le 2^s$ for any integer $s \ge 0$)} \\
+& \le \left(8(1+\sqrt{2})^2 s \right)^s
 & \le \left(47 s \right)^s \; .
@@
 \endgroup
+where we used that $s+1 \le 2^s$ for any non-negative integer $s$.
 Finally,

### 2019-01-22 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Fixes

@@
 
-In this section, we prove a mistake lower bound for a family of algorithms called \textit{ignorant algorithms}.
-For simplicity, we assume $(x_t, y_t)\in\mathbb{R}^{d}\times [K]$ in this section.
-As the name suggests, ignorant algorithms ignore the examples on which they make mistakes.
-This assumption seems strong, but as we will explain below, it is actually natural,
-and several recently proposed bandit classification algorithms that achieve the $\sqrt{T}$-regret bound belong to this family, e.g., SOBA~\citep{Beygelzimer-Orabona-Zhang-2017}, OBAMA~\citep{Foster-Kale-Luo-Mohri-Sridharan-2018}.
-We will see that under the $\gamma$-weak linearly separability assumption,
-if a bandit classification algorithm wants to achieve a mistake bound better than $\Theta\left(\min\{\sqrt{T}, (1/\gamma)^{\Theta(d)}\}\right)$, where $d$ is the feature dimension, it must perform some meaningful update when it makes a mistake.
+In this section, we prove a mistake lower bound for a family of algorithms
+called \textit{ignorant algorithms}. Ignorant algorithms ignore the examples on
+which they make mistakes. As an example, \textsc{Nearest-Neighbor Algorithm}
+(Algorithm~\ref{algorithm:nearest-neighbor}) presented in
+Appendix~\ref{section:nearest-neighbor-algorithm} is an ingnorant algorithm.
+This assumption seems strong, but as we will explain below, it is actually
+natural, and several recently proposed bandit classification algorithms that
+achieve the $\sqrt{T}$-regret bound belong to this family, e.g.,
+SOBA~\citep{Beygelzimer-Orabona-Zhang-2017},
+OBAMA~\citep{Foster-Kale-Luo-Mohri-Sridharan-2018}. We will see that under the
+$\gamma$-weak linearly separability assumption, if a bandit classification
+algorithm wants to achieve a mistake bound better than
+$\Theta\left(\min\{\sqrt{T}, (1/\gamma)^{\Theta(d)}\}\right)$, where $d$ is the
+feature dimension, it must perform some meaningful update when it makes a
+mistake.
 
@@
 \begin{definition} \label{definition:ignorant-algorithm}
-    A bandit classification algorithm $\mathcal{A}$ is ignorant if for all $t\in[T]$,
-    $\widehat y_t\in \{1,2\}$ is drawn from some distribution that is jointly determined by
+A bandit classification algorithm $\mathcal{A}$ is ignorant if for all
+$t\in[T]$, $\widehat y_t\in \{1,2\}$ is drawn from some distribution that is
+jointly determined by
 \begin{enumerate}
@@
 \item $H_t\triangleq \left( (x_{\tau_1}, y_{\tau_1}), (x_{\tau_2}, y_{\tau_2}), \ldots, (x_{\tau_{n_t}}, y_{\tau_{n_t}}) \right)$,
-        where $1 \leq \tau_1<\ldots <\tau_{n_t} < t$, and $\{\tau_1, \ldots, \tau_{n_t}\}$
+where $1 \leq \tau_1 < \dots < \tau_{n_t} < t$, and $\{\tau_1, \ldots, \tau_{n_t}\}$
 are the rounds in which the algorithm predicts correctly (that is,
-        $\{\tau_1, \ldots, \tau_{n_t}\} = \{1\leq \tau<t: \widehat y_\tau=y_\tau\}$).
+$\{\tau_1, \ldots, \tau_{n_t}\} = \{1 \le \tau < t ~:~ \widehat y_\tau=y_\tau\}$).
 \end{enumerate}
-    We use $p_t(\cdot|x_t)\in \{p\in \mathbb{R}_+^2: p^\top\mathbf{1}=1\}$ to denote the distribution $\widehat y_t$ is drawn from.
-Note that we let the current feature vector $x_t$ be an argument to $p_t$ to incorporate its dependency on $x_t$.
-Therefore, for an ignorant algorithm, the function $p_t(\cdot|\cdot)$ is only determined by $H_t$.
+We use $p_t(\cdot|x_t)\in \{p\in \mathbb{R}_+^2: p^\top\mathbf{1}=1\}$ to denote
+the distribution $\widehat y_t$ is drawn from. Note that we let the current
+feature vector $x_t$ be an argument to $p_t$ to incorporate its dependency on
+$x_t$. Therefore, for an ignorant algorithm, the function $p_t(\cdot|\cdot)$ is
+only determined by $H_t$.
 \end{definition}
 
-An ignorant algorithm does not learn from mistakes in the following sense. Suppose that an ignorant algorithm predicts incorrectly at time $t$ ($\widehat y_t \neq y_t$).
-Then at time $t+1$, if it is given the same feature vector $x_{t+1}=x_t$, it will predict the label with the same distribution $p_{t+1}(\cdot|x_{t+1})=p_{t+1}(\cdot|x_t)=p_t(\cdot|x_t)$.
-Below we describe the difficulty of learning from mistakes using a class of natural approaches under the weak separability assumption.
-Consider an approach similar to OBAMA: in each round $t$,
-we create a \textit{convex} loss function $\widehat \ell_t: \mathbb{R}^{K\times d}\rightarrow \mathbb{R}$ that gives a loss value $\widehat \ell_t(W)$ to
-all linear models $W\in\mathbb{R}^{K\times d}$ ($W=[w_1 \ldots w_K]^\top$ for $w_1, \ldots, w_K$ defined in Definition~\ref{definition:linear-separability}).
-The requirement for $\widehat{\ell}_t$ to be convex is due to computational efficiency.
-To let $\widehat{\ell}_t$ reflect the loss, if $\widehat y_t \neq y_t$, we want to assign larger loss values $\widehat{\ell_t}(W)$ to the inconsistent models $\mathcal{W}=\{W: \ip{w_{\widehat y_t}}{x_t} \geq \ip{w_i}{x_t}, \forall i\in[K]\}$,
-while for other $W$'s, we want $\widehat{\ell_t}(W)$ to be smaller.
-The following fact can be verified when $K\geq 3$, which suggests there is no way to define the loss $\widehat \ell_t$ that satisfies the above properties constraints:
-there exists $W_1, W_2, W_3$, where $W_2$ is in the line segment between $W_1$ and $W_3$, such that $W_2\in \mathcal{W}$, while $W_1, W_3 \notin \mathcal{W}$.
-On one hand, by convexity, we should have $\widehat{\ell}_t(W_2)\leq \max\{\widehat{\ell}_t(W_1), \widehat{\ell}_t(W_3)\}$;
-on the other hand, to penalize $\mathcal{W}$, we should have $\widehat{\ell}_t(W_2) > \widehat{\ell}_t(W_1)$ and $\widehat{\ell}_t(W_2) > \widehat{\ell}_t(W_3)$.
-Clearly, these two requirements contradict each other.
+An ignorant algorithm does not learn from mistakes in the following sense.
+Suppose that an ignorant algorithm predicts incorrectly at time $t$ ($\widehat
+y_t \neq y_t$). Then at time $t+1$, if it is given the same feature vector
+$x_{t+1}=x_t$, it will predict the label with the same distribution
+$p_{t+1}(\cdot|x_{t+1})=p_{t+1}(\cdot|x_t)=p_t(\cdot|x_t)$. Below we describe
+the difficulty of learning from mistakes using a class of natural approaches
+under the weak separability assumption. Consider an approach similar to OBAMA:
+in each round $t$, we create a \textit{convex} loss function $\widehat \ell_t:
+\mathbb{R}^{K\times d}\rightarrow \mathbb{R}$ that gives a loss value $\widehat
+\ell_t(W)$ to all linear models $W\in\mathbb{R}^{K\times d}$ ($W=[w_1 \ldots
+w_K]^\top$ for $w_1, \ldots, w_K$ defined in
+Definition~\ref{definition:linear-separability}). The requirement for
+$\widehat{\ell}_t$ to be convex is due to computational efficiency. To let
+$\widehat{\ell}_t$ reflect the loss, if $\widehat y_t \neq y_t$, we want to
+assign larger loss values $\widehat{\ell_t}(W)$ to the inconsistent models
+$\mathcal{W}=\{W: \ip{w_{\widehat y_t}}{x_t} \geq \ip{w_i}{x_t}, \forall
+i\in[K]\}$, while for other $W$'s, we want $\widehat{\ell_t}(W)$ to be smaller.
+The following fact can be verified when $K\geq 3$, which suggests there is no
+way to define the loss $\widehat \ell_t$ that satisfies the above properties
+constraints: there exists $W_1, W_2, W_3$, where $W_2$ is in the line segment
+between $W_1$ and $W_3$, such that $W_2\in \mathcal{W}$, while $W_1, W_3 \notin
+\mathcal{W}$. On one hand, by convexity, we should have
+$\widehat{\ell}_t(W_2)\leq \max\{\widehat{\ell}_t(W_1),
+\widehat{\ell}_t(W_3)\}$; on the other hand, to penalize $\mathcal{W}$, we
+should have $\widehat{\ell}_t(W_2) > \widehat{\ell}_t(W_1)$ and
+$\widehat{\ell}_t(W_2) > \widehat{\ell}_t(W_3)$. Clearly, these two requirements
+contradict each other.
 
 The following theorem states the mistake lower bound for ignorant algorithms.
+
 \begin{theorem}[Mistake Lower Bound for Ignorant Algorithms]
 \label{theorem:ignorant_lower_bound}
-    Suppose $\mathcal{A}$ is an ignorant bandit classification algorithm.
-    There exists an adversary that can sequentially choose $(x_1, y_1), (x_2, y_2), \ldots, (x_T, y_T) \in \mathbb{R}^d\times \{1,2\}$,
-    such that $\forall t\in[T], \|x_t\|\leq 1$, $\{(x_t, y_t)\}_{t=1}^T$ is $\gamma$-strongly linearly separable,
-    and the expected number of mistakes made by $\mathcal{A}$ is lower bounded as
+Suppose $\mathcal{A}$ is an ignorant bandit classification algorithm. There
+exists an adversary that can sequentially choose $(x_1, y_1), (x_2, y_2),
+\ldots, (x_T, y_T) \in \mathbb{R}^d\times \{1,2\}$, such that $\forall t\in[T],
+\|x_t\|\leq 1$, $\{(x_t, y_t)\}_{t=1}^T$ is $\gamma$-strongly linearly
+separable, and the expected number of mistakes made by $\mathcal{A}$ is lower
+bounded as
 \begin{align*}
-        \Exp\left[ \sum_{t=1}^T \indicator{\widehat y_t \neq y_t} \right] \geq \frac{1}{10}\min\left\{\sqrt{T},
-        \left(\frac{1}{160\gamma}\right)^{\frac{d-2}{4}} \right\}.
+\Exp\left[ \sum_{t=1}^T \indicator{\widehat y_t \neq y_t} \right]
+\geq \frac{1}{10}\min\left\{\sqrt{T}, \left(\frac{1}{160\gamma}\right)^{\frac{d-2}{4}} \right\} \; .
 \end{align*}
 \end{theorem}
+
 Before proving the theorem, we need the following lemma.
@@
 \begin{proof}
-By Lemma 6 of~\cite{Long-1995}, there exists a set of $N = (\frac{1}{2\sqrt{40\gamma}})^{d-2}$ $(d-1)$-dimensional vectors $z_1, \ldots, z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that
-$\theta(z_i, z_j) \geq \sqrt{40 \gamma}$. As $\cos\theta \leq 1-\theta^2/5$ for every $\theta \in [0,\pi]$,
-this implies that
+By Lemma 6 of~\cite{Long-1995}, there exists a set of $N =
+(\frac{1}{2\sqrt{40\gamma}})^{d-2}$ $(d-1)$-dimensional vectors $z_1, \ldots,
+z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that $\theta(z_i, z_j) \geq
+\sqrt{40 \gamma}$. As $\cos\theta \leq 1-\theta^2/5$ for every $\theta \in
+[0,\pi]$, this implies that
 \[ z_i \cdot z_j \begin{cases} = 1 ,& i = j, \\ \leq 1- 8\gamma ,& i \neq j. \end{cases} \]
 
-Define $v_i = (\frac12 z_i, \frac12)$, and $u_i = (\frac 12 z_i, -\frac 12(1-4\gamma))$ for all $i$ in $[N]$.
-It can be easily checked that for all $i$, $\|v_i\| \leq 1$ and $\|u_i\| \leq 1$.
-In addition,
-\[ u_i \cdot v_j = \frac 1 4 z_i \cdot z_j - \frac {1-4\gamma} 4 \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases}\]
+Define $v_i = (\frac12 z_i, \frac12)$, and $u_i = (\frac 12 z_i, -\frac
+12(1-4\gamma))$ for all $i$ in $[N]$. It can be easily checked that for all $i$,
+$\|v_i\| \leq 1$ and $\|u_i\| \leq 1$. In addition,
+$$
+u_i \cdot v_j
+= \frac 1 4 z_i \cdot z_j - \frac {1-4\gamma} 4 \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases}
+$$
 \end{proof}
@@
 \begin{align}
-    \mathbf{E}\left[\sum_{t=1}^{T} \indicator{\widehat y_t\neq y_t}\right]
-    &\geq \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
-    & \geq \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}A_t\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}B_t\right] \nonumber \\
+& \mathbf{E}\left[\sum_{t=1}^{T} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
+& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
+& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}A_t\right] \nonumber \\
+& \qquad + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}B_t\right] \nonumber \\
 & = \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \mathbf{E}_t\left[\indicator{\widehat y_t\neq y_t}A_t\right]\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right] \nonumber \\
-    & \geq \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} q_0 A_t\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right],
+& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} q_0 A_t\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right],
 \label{eqn:mistake_lower_bound_temp}
 \end{align}
-where in the first inequality we use $A_t+B_t\leq 1$;
-in the equality, we use  $B_{t+1}=B_t\indicator{\widehat y_t\neq y_t}$ by $B_t$'s definition;
-in the last inequality we use the fact that when $t\leq N$ and $A_t=1$, it must be $y_t=1$.
-Now, denote $T_1 = \argmin_{\tau} \{ p_\tau(1|x_\tau) \geq 1-q_0 \}$ (if such $\tau$ does not exist or is larger than $\min\{T,N\}$, we simply let $T_1=\min\{T,N\}+1$).
-Then $A_t=1$ for all $t\leq T_1-1$.
+where in the first inequality we use $A_t+B_t\leq 1$; in the equality, we use
+$B_{t+1}=B_t\indicator{\widehat y_t\neq y_t}$ by $B_t$'s definition; in the last
+inequality we use the fact that when $t\leq N$ and $A_t=1$, it must be $y_t=1$.
+Now, denote $T_1 = \argmin_{\tau} \{ p_\tau(1|x_\tau) \ge 1-q_0 \}$ (if such
+$\tau$ does not exist or is larger than $\min\{T,N\}$, we simply let
+$T_1=\min\{T,N\}+1$). Then $A_t=1$ for all $t\leq T_1-1$.
 
-Note that $B_{T_1}=1$, and for $t\geq T_1$ we have $\Exp[B_{t+1}=0|B_t=1]=\Pr[\widehat y_t=y_t|B_t=1]=\Pr[\widehat y_t=2|B_t=1]\leq q_0$ because the algorithm is ignorant.
-Thus the second term in \eqref{eqn:mistake_lower_bound_temp} can be calculated as
+Note that $B_{T_1}=1$, and for $t \ge T_1$ we have
+$\Exp[B_{t+1}=0|B_t=1]=\Pr[\widehat y_t=y_t~|~B_t=1] = \Pr[\widehat y_t=2|B_t=1] \le
+q_0$ because the algorithm is ignorant. Thus the second term in
+\eqref{eqn:mistake_lower_bound_temp} can be calculated as
 
 \begin{align*}
-    \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}}B_{t+1}\right]\geq \mathbf{E}\left[\sum_{t=T_1}^{\min\{ T,N \}} (1-q_0)^{t-T_1+1} \right]
-    = \frac{1-q_0}{q_0}\mathbf{E}\left[1-(1-q_0)^{\min\{T,N\}-T_1+1}\right].
+& \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}}B_{t+1}\right] \\
+& \ge \mathbf{E}\left[\sum_{t=T_1}^{\min\{ T,N \}} (1-q_0)^{t-T_1+1} \right] \\
+& = \frac{1-q_0}{q_0}\mathbf{E}\left[1-(1-q_0)^{\min\{T,N\}-T_1+1}\right] \; .
 \end{align*}
 Combining \eqref{eqn:mistake_lower_bound_temp} and the above inequalities, we get
-\begin{align}
-    \mathbf{E}\left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right]\geq \mathbf{E}\left[q_0(T_1-1)+\frac{1-q_0}{q_0}\left(1-(1-q_0)^{\min\{T,N\}-T_1+1}\right)\right].
+\begin{multline}
 \label{eqn:mistake_lower_bound_temp2}
-\end{align}
-In the case $T_1\geq \frac{1}{2}\min\{T,N\}+1$, the right-hand side of \eqref{eqn:mistake_lower_bound_temp2} is lower bounded by $\frac{1}{2}q_0\min\{T,N\}=\frac{1}{2}\min\{\sqrt{T}, \sqrt{N}\}$; in the case $T_1< \frac{1}{2}\min\{T,N\}+1$, it is lower bounded by
+\mathbf{E} \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \ge
+\\ \mathbf{E}\left[q_0(T_1-1)+\frac{1-q_0}{q_0}\left(1-(1-q_0)^{\min\{T,N\}-T_1+1}\right)\right].
+\end{multline}
+In the case $T_1\geq \frac{1}{2}\min\{T,N\}+1$, the right-hand side of
+\eqref{eqn:mistake_lower_bound_temp2} is lower bounded by
+$\frac{1}{2}q_0\min\{T,N\}=\frac{1}{2}\min\{\sqrt{T}, \sqrt{N}\}$; in the case
+$T_1< \frac{1}{2}\min\{T,N\}+1$, it is lower bounded by
 \begin{align*}
-    \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2}\min\{T,N\}}\right)= \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2q_0^2}}\right)\geq \frac{1-\frac{1}{\sqrt{2}}}{q_0}\left(1-\frac{1}{\sqrt{e}}\right)\geq \frac{1}{10}\min\{\sqrt{T}, \sqrt{N}\}.
+& \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2}\min\{T,N\}}\right) \\
+& = \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2q_0^2}}\right) \\
+& \ge \frac{1-\frac{1}{\sqrt{2}}}{q_0}\left(1-\frac{1}{\sqrt{e}}\right) \\
+& \ge \frac{1}{10}\min\{\sqrt{T}, \sqrt{N}\} \; .
 \end{align*}
@@
 \begin{proof}[Proof for Theorem~\ref{theorem:ignorant_lower_bound} (Part II: linear separability)]
-Observe that in Algorithm~\ref{algorithm:adversary-strategy}, in the beginning the adversary always set the label to $1$;
-once it sets $y_t=2$ at some $t$, it lets $(x_s, y_s)=(x_t, y_t)=(v_t, 2)$ for all $s\geq t$.
-Consider $w_2=u_t$ and $w_1=-u_t$, for $u_t$ as defined in Lemma~\ref{lem:embed_d_gamma}.
-Then by Lemma~\ref{lem:embed_d_gamma}, we have $\ip{w_2}{x_s} = \ip{u_t}{v_t} \geq \gamma, \forall s \geq t$
-and $\ip{w_2}{x_s} = \ip{u_t}{v_s} \leq - \gamma, \forall s< t$;
-also $\ip{w_1}{x_s} \leq -\gamma, \forall s \geq t$
-and $\ip{w_1}{x_s} \geq  \gamma, \forall s<t$.
-Thus, the example set is always $\gamma$-strongly separable.
+Observe that in Algorithm~\ref{algorithm:adversary-strategy}, in the beginning
+the adversary always set the label to $1$; once it sets $y_t=2$ at some $t$, it
+lets $(x_s, y_s)=(x_t, y_t)=(v_t, 2)$ for all $s\geq t$. Consider $w_2=u_t$ and
+$w_1=-u_t$, for $u_t$ as defined in Lemma~\ref{lem:embed_d_gamma}. Then by
+Lemma~\ref{lem:embed_d_gamma}, we have $\ip{w_2}{x_s} = \ip{u_t}{v_t} \geq
+\gamma, \forall s \geq t$ and $\ip{w_2}{x_s} = \ip{u_t}{v_s} \leq - \gamma,
+\forall s< t$; also $\ip{w_1}{x_s} \leq -\gamma, \forall s \geq t$ and
+$\ip{w_1}{x_s} \geq  \gamma, \forall s<t$. Thus, the example set is always
+$\gamma$-strongly separable.
 \end{proof}

### 2019-01-22 ICML-submission/introduction.tex
Fixes

@@
 \label{algorithm:game-protocol}}
-\textbf{Require:} Number of classes $K$, number of rounds $T$.\\
+\textbf{Require:} Number of classes $K$, number of rounds $T$. \\
+\textbf{Require:} Inner product space $(V,\ip{\cdot}{\cdot})$. \\
 \For{$t=1,2,\dots,T$}{
-Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.\\
+Adversary chooses example $(x_t, y_t) \in V \times \{1,2,\dots,K\}$ where $x_t$ is revealed to the learner.\\
 Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\

### 2019-01-22 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Fixes

@@
 called \textit{ignorant algorithms}. Ignorant algorithms ignore the examples on
-which they make mistakes. As an example, \textsc{Nearest-Neighbor Algorithm}
-(Algorithm~\ref{algorithm:nearest-neighbor}) presented in
-Appendix~\ref{section:nearest-neighbor-algorithm} is an ingnorant algorithm.
-This assumption seems strong, but as we will explain below, it is actually
-natural, and several recently proposed bandit classification algorithms that
-achieve the $\sqrt{T}$-regret bound belong to this family, e.g.,
-SOBA~\citep{Beygelzimer-Orabona-Zhang-2017},
-OBAMA~\citep{Foster-Kale-Luo-Mohri-Sridharan-2018}. We will see that under the
-$\gamma$-weak linearly separability assumption, if a bandit classification
-algorithm wants to achieve a mistake bound better than
-$\Theta\left(\min\{\sqrt{T}, (1/\gamma)^{\Theta(d)}\}\right)$, where $d$ is the
-feature dimension, it must perform some meaningful update when it makes a
-mistake.
+which they make mistakes. This assumption seems strong, but as we will explain
+below, it is actually natural, and several recently proposed bandit
+classification algorithms that achieve the $\sqrt{T}$-regret bound belong to
+this family, e.g., SOBA~\citep{Beygelzimer-Orabona-Zhang-2017},
+OBAMA~\citep{Foster-Kale-Luo-Mohri-Sridharan-2018}. Also,
+\textsc{Nearest-Neighbor Algorithm} (Algorithm~\ref{algorithm:nearest-neighbor})
+presented in Appendix~\ref{section:nearest-neighbor-algorithm} is an ingnorant
+algorithm.
+
+Under the assumption that the examples lie in in the unit ball of $\R^d$ and are
+weakly linearly separable with margin $\gamma$, we show that any ignorant
+algorithm must make $\Theta\left(\min\{\sqrt{T},
+(1/\gamma)^{\Theta(d)}\}\right)$ mistakes in the worst case. In other words, an
+algorithm that achieves a better mistake bound cannot ignore examples on which
+it makes a mistake and it must make a meaningful update on such examples.
 
@@
 \item $x_t$
-\item $H_t\triangleq \left( (x_{\tau_1}, y_{\tau_1}), (x_{\tau_2}, y_{\tau_2}), \ldots, (x_{\tau_{n_t}}, y_{\tau_{n_t}}) \right)$,
-where $1 \leq \tau_1 < \dots < \tau_{n_t} < t$, and $\{\tau_1, \ldots, \tau_{n_t}\}$
+\item $H_t \triangleq \left( (x_{\tau_1}, y_{\tau_1}), (x_{\tau_2}, y_{\tau_2}), \ldots, (x_{\tau_{n_t}}, y_{\tau_{n_t}}) \right)$,
+where $1 \le \tau_1 < \dots < \tau_{n_t} < t$, and $\{\tau_1, \ldots, \tau_{n_t}\}$
 are the rounds in which the algorithm predicts correctly (that is,
@@
 \end{enumerate}
-We use $p_t(\cdot|x_t)\in \{p\in \mathbb{R}_+^2: p^\top\mathbf{1}=1\}$ to denote
+We use $p_t(\cdot|x_t)\in \{p\in \R_+^2 ~:~ p^\top\mathbf{1}=1\}$ to denote
 the distribution $\widehat y_t$ is drawn from. Note that we let the current
@@
 in each round $t$, we create a \textit{convex} loss function $\widehat \ell_t:
-\mathbb{R}^{K\times d}\rightarrow \mathbb{R}$ that gives a loss value $\widehat
-\ell_t(W)$ to all linear models $W\in\mathbb{R}^{K\times d}$ ($W=[w_1 \ldots
+\R^{K\times d} \to \R$ that gives a loss value $\widehat
+\ell_t(W)$ to all linear models $W \in \R^{K\times d}$ ($W=[w_1 \ldots
 w_K]^\top$ for $w_1, \ldots, w_K$ defined in
@@
 assign larger loss values $\widehat{\ell_t}(W)$ to the inconsistent models
-$\mathcal{W}=\{W: \ip{w_{\widehat y_t}}{x_t} \geq \ip{w_i}{x_t}, \forall
+$\mathcal{W}=\{W: \ip{w_{\widehat y_t}}{x_t} \ge \ip{w_i}{x_t}, \forall
 i\in[K]\}$, while for other $W$'s, we want $\widehat{\ell_t}(W)$ to be smaller.
-The following fact can be verified when $K\geq 3$, which suggests there is no
+The following fact can be verified when $K\ge 3$, which suggests there is no
 way to define the loss $\widehat \ell_t$ that satisfies the above properties
@@
 \mathcal{W}$. On one hand, by convexity, we should have
-$\widehat{\ell}_t(W_2)\leq \max\{\widehat{\ell}_t(W_1),
+$\widehat{\ell}_t(W_2)\le \max\{\widehat{\ell}_t(W_1),
 \widehat{\ell}_t(W_3)\}$; on the other hand, to penalize $\mathcal{W}$, we
@@
 exists an adversary that can sequentially choose $(x_1, y_1), (x_2, y_2),
-\ldots, (x_T, y_T) \in \mathbb{R}^d\times \{1,2\}$, such that $\forall t\in[T],
-\|x_t\|\leq 1$, $\{(x_t, y_t)\}_{t=1}^T$ is $\gamma$-strongly linearly
+\ldots, (x_T, y_T) \in \R^d\times \{1,2\}$, such that $\forall t\in[T],
+\|x_t\|\le 1$, $\{(x_t, y_t)\}_{t=1}^T$ is $\gamma$-strongly linearly
 separable, and the expected number of mistakes made by $\mathcal{A}$ is lower
@@
 \Exp\left[ \sum_{t=1}^T \indicator{\widehat y_t \neq y_t} \right]
-\geq \frac{1}{10}\min\left\{\sqrt{T}, \left(\frac{1}{160\gamma}\right)^{\frac{d-2}{4}} \right\} \; .
+\ge \frac{1}{10}\min\left\{\sqrt{T}, \left(\frac{1}{160\gamma}\right)^{\frac{d-2}{4}} \right\} \; .
 \end{align*}
@@
 Before proving the theorem, we need the following lemma.
+
 \begin{lemma}
-\label{lem:embed_d_gamma}
-Let $\gamma \in (0,\frac 1 {160})$.
-There exists vectors $v_1, \ldots, v_N, u_1, \ldots, u_N\in \mathbb{R}^d$, where $N = (\Omega(\frac{1}{\gamma}))^{(d-2)/2}$, such that:
-$\| v_i \|_2 \leq 1$, $\| u_i \|_2 \leq 1$ for all $i$ in $[N]$, and for all $i, j$ in $[N]$,
-\[ u_i \cdot v_j \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases} \]
+\label{lemma:embed_d_gamma}
+Let $\gamma \in (0,\frac 1 {160})$, let $d$ be a positive integer and let $N = (\Omega(\frac{1}{\gamma}))^{(d-2)/2}$.
+There exist vectors $v_1, v_2, \dots, v_N, u_1, u_2, \dots, u_N \in \R^d$ such that for all $i, j \in \{1,2,\dots,N\}$
+\begin{align*}
+\norm{v_i} & \le 1 \, \\
+\norm{u_i} & \le 1 \, \\
+\ip{u_i}{v_j} & \ge \gamma & & \text{if $i=j$,} \\
+\ip{u_i}{v_j} & \le -\gamma & & \text{if $i \neq j$.}
+\end{align*}
 \end{lemma}
+
 \begin{proof}
@@
 (\frac{1}{2\sqrt{40\gamma}})^{d-2}$ $(d-1)$-dimensional vectors $z_1, \ldots,
-z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that $\theta(z_i, z_j) \geq
-\sqrt{40 \gamma}$. As $\cos\theta \leq 1-\theta^2/5$ for every $\theta \in
+z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that $\theta(z_i, z_j) \ge
+\sqrt{40 \gamma}$. As $\cos\theta \le 1-\theta^2/5$ for every $\theta \in
 [0,\pi]$, this implies that
-\[ z_i \cdot z_j \begin{cases} = 1 ,& i = j, \\ \leq 1- 8\gamma ,& i \neq j. \end{cases} \]
+$$
+\ip{z_i}{z_j} \begin{cases} = 1 ,& i = j, \\ \le 1- 8\gamma ,& i \neq j. \end{cases}
+$$
 
-Define $v_i = (\frac12 z_i, \frac12)$, and $u_i = (\frac 12 z_i, -\frac
-12(1-4\gamma))$ for all $i$ in $[N]$. It can be easily checked that for all $i$,
-$\|v_i\| \leq 1$ and $\|u_i\| \leq 1$. In addition,
+Define $v_i = (\frac12 z_i, \frac12)$, and $u_i = (\frac{1}{2} z_i, -\frac{1}{2}(1-4\gamma))$ for all $i \in \{1,2,\dots,N\}$.
+It can be easily checked that for all $i$,
+$\norm{v_i} \le 1$ and $\norm{u_i} \le 1$. In addition,
 $$
-u_i \cdot v_j
-= \frac 1 4 z_i \cdot z_j - \frac {1-4\gamma} 4 \begin{cases} \geq \gamma ,& i = j, \\ \leq -\gamma ,& i \neq j. \end{cases}
+\ip{u_i}{v_j}
+= \frac{1}{4} \ip{z_i}{z_j} - \frac {1-4\gamma} 4 \begin{cases} \ge \gamma ,& i = j, \\ \le -\gamma ,& i \neq j. \end{cases}
 $$
@@
 {
-\STATE{\textbf{Define} $q_0=\max\left\{\frac{1}{\sqrt{T}}, \frac{1}{\sqrt{N}}\right\}$, where $N$ is defined in Lemma~\ref{lem:embed_d_gamma}.
-Also, let $v_1, \ldots, v_N$ be those defined in Lemma~\ref{lem:embed_d_gamma}.}
+\STATE{\textbf{Define} $q_0=\max\left\{\frac{1}{\sqrt{T}}, \frac{1}{\sqrt{N}}\right\}$, where $N$ is defined in Lemma~\ref{lemma:embed_d_gamma}.
+Also, let $v_1, \ldots, v_N$ be those defined in Lemma~\ref{lemma:embed_d_gamma}.}
 \STATE{\textbf{Initialize} $\textsc{phase}= 1$. }
@@
     \IF{$\textsc{phase}=1$}
-       \IF{$p_t(1|v_t)\geq 1-q_0$}
+       \IF{$p_t(1|v_t)\ge 1-q_0$}
           \STATE{$(x_t, y_t)\leftarrow (v_t, 1)$}
@@
 \begin{align*}
-A_t &= \indicator{\forall \tau\leq t, p_\tau(1|x_\tau)<1-q_0} \\
-B_t &= \indicator{\exists \tau\leq t, p_\tau(1|x_\tau)\geq 1-q_0
+A_t &= \indicator{\forall \tau\le t, p_\tau(1|x_\tau)<1-q_0} \\
+B_t &= \indicator{\exists \tau\le t, p_\tau(1|x_\tau)\ge 1-q_0
  \text{\ and\ } \forall s\in[\tau,t), \widehat y_s \neq y_s}.
@@
 & \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} q_0 A_t\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right],
-\label{eqn:mistake_lower_bound_temp}
+\label{equation:mistake_lower_bound_temp}
 \end{align}
-where in the first inequality we use $A_t+B_t\leq 1$; in the equality, we use
+where in the first inequality we use $A_t+B_t\le 1$; in the equality, we use
 $B_{t+1}=B_t\indicator{\widehat y_t\neq y_t}$ by $B_t$'s definition; in the last
-inequality we use the fact that when $t\leq N$ and $A_t=1$, it must be $y_t=1$.
+inequality we use the fact that when $t\le N$ and $A_t=1$, it must be $y_t=1$.
 Now, denote $T_1 = \argmin_{\tau} \{ p_\tau(1|x_\tau) \ge 1-q_0 \}$ (if such
 $\tau$ does not exist or is larger than $\min\{T,N\}$, we simply let
-$T_1=\min\{T,N\}+1$). Then $A_t=1$ for all $t\leq T_1-1$.
+$T_1=\min\{T,N\}+1$). Then $A_t=1$ for all $t\le T_1-1$.
 
@@
 q_0$ because the algorithm is ignorant. Thus the second term in
-\eqref{eqn:mistake_lower_bound_temp} can be calculated as
+\eqref{equation:mistake_lower_bound_temp} can be calculated as
 
@@
 \end{align*}
-Combining \eqref{eqn:mistake_lower_bound_temp} and the above inequalities, we get
+Combining \eqref{equation:mistake_lower_bound_temp} and the above inequalities, we get
 \begin{multline}
-\label{eqn:mistake_lower_bound_temp2}
+\label{equation:mistake_lower_bound_temp2}
 \mathbf{E} \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \ge
@@
 \end{multline}
-In the case $T_1\geq \frac{1}{2}\min\{T,N\}+1$, the right-hand side of
-\eqref{eqn:mistake_lower_bound_temp2} is lower bounded by
+In the case $T_1\ge \frac{1}{2}\min\{T,N\}+1$, the right-hand side of
+\eqref{equation:mistake_lower_bound_temp2} is lower bounded by
 $\frac{1}{2}q_0\min\{T,N\}=\frac{1}{2}\min\{\sqrt{T}, \sqrt{N}\}$; in the case
@@
 the adversary always set the label to $1$; once it sets $y_t=2$ at some $t$, it
-lets $(x_s, y_s)=(x_t, y_t)=(v_t, 2)$ for all $s\geq t$. Consider $w_2=u_t$ and
-$w_1=-u_t$, for $u_t$ as defined in Lemma~\ref{lem:embed_d_gamma}. Then by
-Lemma~\ref{lem:embed_d_gamma}, we have $\ip{w_2}{x_s} = \ip{u_t}{v_t} \geq
-\gamma, \forall s \geq t$ and $\ip{w_2}{x_s} = \ip{u_t}{v_s} \leq - \gamma,
-\forall s< t$; also $\ip{w_1}{x_s} \leq -\gamma, \forall s \geq t$ and
-$\ip{w_1}{x_s} \geq  \gamma, \forall s<t$. Thus, the example set is always
+lets $(x_s, y_s)=(x_t, y_t)=(v_t, 2)$ for all $s\ge t$. Consider $w_2=u_t$ and
+$w_1=-u_t$, for $u_t$ as defined in Lemma~\ref{lemma:embed_d_gamma}. Then by
+Lemma~\ref{lemma:embed_d_gamma}, we have $\ip{w_2}{x_s} = \ip{u_t}{v_t} \ge
+\gamma, \forall s \ge t$ and $\ip{w_2}{x_s} = \ip{u_t}{v_s} \le - \gamma,
+\forall s< t$; also $\ip{w_1}{x_s} \le -\gamma, \forall s \ge t$ and
+$\ip{w_1}{x_s} \ge  \gamma, \forall s<t$. Thus, the example set is always
 $\gamma$-strongly separable.

### 2019-01-22 ICML-submission/introduction.tex
Fix typos in introduction

@@
 (Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
-that makes at most $O(K (R/\gamma)^2))$ mistakes in expectation. Its memory
+that makes at most $O(K (R/\gamma)^2)$ mistakes in expectation. Its memory
 complexity and per-round time complexity are both $O(dK)$. The algorithm can be
@@
 copy for each class. We prove that any (possibly randomized) algorithm must make
-$\Omega(K (R/\gamma)^2))$ mistakes in the worst case. The extra $O(K)$
+$\Omega(K (R/\gamma)^2)$ mistakes in the worst case. The extra $O(K)$
 multiplicative factor in the mistake bound, as compared to the full-information
@@
 bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}.
-Furthermore, in~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, they ask the question:
+Furthermore, \citet{Kakade-Shalev-Shwartz-Tewari-2008} ask the question:
 Is there \textit{any} algorithm with a finite mistake bound that has no explicit
@@
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} for
-the strongly separable case (Algorithm~\ref{algorithm:kernelized}). The kernel
-$k(x,x')$ corresponding to the feature mapping $\phi$ has a simple explicit
-formula and can be computed in $O(d)$ time, making
-Algorithm~\ref{algorithm:kernelized} computationally efficient. For details on
-kernel methods see e.g.~\citet{Scholkopf-Smola-2002} or
+the strongly separable case. The kernel $k(x,x')$ corresponding to the feature
+mapping $\phi$ has a simple explicit formula and can be computed in $O(d)$ time,
+making Algorithm~\ref{algorithm:kernelized} computationally efficient. For
+details on kernel methods see e.g.~\citet{Scholkopf-Smola-2002} or
 \citet{Shawe-Taylor-Cristianini-2004}.

### 2019-01-22 ICML-submission/from-weak-separability-to-strong-separability.tex
Fixes in section 5

@@
 Using this theorem we derive a mistake bound for
-Algorithm~\ref{algorithm:kernelized} with kernel function $k(x,x') =
-\ip{\phi(x)}{\phi(x')}_{\ell_2}$, under the weak linear separability assumption.
+Algorithm~\ref{algorithm:kernelized} with kernel \eqref{equation:rational-kernel}
+under the weak linear separability assumption.
 
@@
 then the expected number of mistakes made by Algorithm~\ref{algorithm:kernelized}
-with kernel $k(x,x') = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}_{\R^d}}$
+with kernel $k(x,x')$ defined by \eqref{equation:rational-kernel}
 is at most $2^{\widetilde{O}(\min(K \log^2 \frac{1}{\gamma},
@@
 \label{equation:poly-pos}
-& \forall t \in \cbr{1,2,\dots,T}, p_{y_t}(x_t) \ge \frac{\gamma'}{2} \; ,
+& \forall t \in \cbr{1,2,\dots,T}, \qquad p_{y_t}(x_t) \ge \frac{\gamma'}{2} \; ,
 \\

### 2019-01-23 ICML-submission/appendix-nearest-neighbor-algorithm.tex
Fixes
Clean-ups

@@
 \begin{algorithm}[H]
-\caption{\textsc{Nearest-Neighbor Algorithm}}
-\begin{algorithmic}[1]
-\REQUIRE{Number of classes $K$, number of rounds $T$.}
-\REQUIRE{Inner product space $(V,\ip{\cdot}{\cdot})$.}
-\STATE $S \gets \emptyset$.
-\FOR{$t=1,2,\ldots,T$:}
-\IF{$\min_{(x,y) \in S} \norm{x_t - x} \le \gamma$}
-  \STATE{Find nearest neighbor \\ $(\widetilde{x}, \widetilde{y}) = \argmin_{(x,y) \in S} \norm{x_t - x}$}
-	\STATE{Predict $\widehat{y}_t = \widetilde{y}$}
-\ELSE
-	\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
-	\STATE{Receive feedback $z_t = \indicator{\widehat{y}_t \neq y_t}$}
-  \label{line:nearest-neighbor-explore}
-	\IF{$z_t = 0$}
-    \STATE $S \gets S \cup \cbr{(x_t, \widehat{y}_t)}$.
-  \ENDIF
-\ENDIF
-\ENDFOR
-\end{algorithmic}
+\SetAlgoLined
+\LinesNumbered
+\caption{\textsc{Nearest-Neighbor Algorithm}
 \label{algorithm:nearest-neighbor}
+}
+\textbf{Require:} Number of classes $K$, number of rounds $T$. \\
+\textbf{Require:} Inner product space $(V,\ip{\cdot}{\cdot})$. \\
+\nl Initialize $S \gets \emptyset$ \\
+\nl \For{$t=1,2,\ldots,T$:}{
+\nl  \If{$\min_{(x,y) \in S} \norm{x_t - x} \le \gamma$}{
+\nl    Find nearest neighbor \\
+       \qquad \qquad $(\widetilde{x}, \widetilde{y}) = \argmin_{(x,y) \in S} \norm{x_t - x}$ \\
+\nl	  Predict $\widehat{y}_t = \widetilde{y}$
+  }
+  \Else{
+\nl	  Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$
+      \label{line:nearest-neighbor-explore} \\
+\nl	  Receive feedback $z_t = \indicator{\widehat{y}_t \neq y_t}$ \\
+\nl	  \If{$z_t = 0$}{
+\nl      $S \gets S \cup \cbr{(x_t, \widehat{y}_t)}$
+    }
+  }
+}
 \end{algorithm}
@@
 In this section we analyze \textsc{Nearest-Neighbor Algorithm} shown as
-Algorithm~\ref{algorithm:nearest-neighbor}. The algorithm is based on the idea
-that two examples that are close to each other must have the same label. Lemma
-below formalizes this intuition.
+Algorithm~\ref{algorithm:nearest-neighbor}. The algorithm is based on obvious
+the idea that under weak linear assumption two examples that are close to each
+other must have the same label. Lemma below formalizes this intuition.
 
-\begin{lemma}
-\label{lemma:nearest-neighbor}
+\begin{lemma}[Separation lemma]
+\label{lemma:separation-lemma}
 Let $(V,\ip{\cdot}{\cdot})$ be a vector space, $K$ be a positive integer and let
@@
 
-\begin{theorem}
-\label{theorem:margin_at_upper}
-Let $K$ and $d$ be positive integers and let $\gamma$ be a positive real number.
-Suppose $(x_1,y_1), \ldots, (x_T, y_T) \in \R^d \times \{1,2,\dots,K\}$ are
-labeled examples that are weakly linearly separable with margin $\gamma$ and
-satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$. Then, the expected
-number of mistakes made by Algorithm~\ref{algorithm:nearest-neighbor} is at most
+We also need to define several notions. A subset $S \subseteq \R^d$ is called a
+$\gamma$-packing if for any $x,x' \in S$ such that $x \neq x'$ we have $\norm{x -
+x'} > \gamma$. The following lemma is standard. Also recall that $B(x,R) = \{ x'
+\in \R^d ~:~ \norm{x' - x} \le R \}$ denotes the closed ball of radius $R$
+centered a point $x$.
+
+\begin{lemma}[Size of $\gamma$-packing]
+\label{lemma:size-of-packing}
+Let $\gamma$ and $R$ be positive real numbers.
+If $S \subseteq B(\zero,R) \subseteq \R^d$ is a $\gamma$-packing then
 $$
-(K-1) \left( \frac{R}{\gamma} \right)^d \; .
+|S| \le \left( \frac{2R}{\gamma} + 1 \right)^d \; .
+$$
+\end{lemma}
+
+\begin{proof}
+If $S$ is a $\gamma$-packing then $\{ B(x,\gamma/2) ~:~ x \in S \}$
+is a collection of disjoint balls of radius $\gamma$ that fit into $B(\zero,R + \gamma/2)$.
+Thus,
+$$
+|S| \cdot \Vol(B(\zero, \gamma/2)) \le \Vol(B(\zero,R + \gamma/2))
+$$
+Hence,
+\begin{align*}
+|S|
+& \le \frac{\Vol(B(\zero,R + \gamma/2))}{\Vol(B(\zero, \gamma/2))} \\
+& = \left( \frac{R + \gamma/2}{\gamma/2} \right)^d \\
+& = \left( \frac{2R}{\gamma} + 1 \right)^d \; .
+\end{align*}
+\end{proof}
+
+\begin{theorem}[Mistake upper bound for \textsc{Nearest-Neighbor Algorithm}]
+\label{theorem:mistake-bound-for-nearest-neighbor-algorithm}
+Let $K$ and $d$ be positive integers and let $\gamma,R$ be a positive real
+numbers. Suppose $(x_1,y_1), \ldots, (x_T, y_T) \in
+\R^d \times \{1,2,\dots,K\}$ are labeled examples that are weakly linearly
+separable with margin $\gamma$ and satisfy $\norm{x_1}, \norm{x_2}, \dots,
+\norm{x_T} \le R$. Then, the expected number of mistakes made by
+Algorithm~\ref{algorithm:nearest-neighbor} is at most
+$$
+(K-1) \left( \frac{2R}{\gamma} + 1\right)^d \; .
 $$
@@
 $t$, i.e. we fall into the ``else'' case. Note that if $b_t = 0$, then by
-Lemma~\ref{lemma:nearest-neighbor}, the prediction $\widehat{y}_t$ must equal
+Lemma~\ref{lemma:separation-lemma}, the prediction $\widehat{y}_t$ must equal
 $y_t$, i.e. $z_t = 0$. Therefore, $M = \sum_{t=1}^T z_t = \sum_{t=1}^T b_t z_t$.
-Let $U = \sum_{t=1}^T b_t (1-z_t)$. Clearly, $|S| = U$. Since $S$ is a
-$\gamma$-packing over $\cbr{x \in \R^d ~:~ \norm{x} \le R}$, the size of $S$ is
-at most $(\frac R \gamma)^d$, which is also an upper bound on $U$.
+Let $U = \sum_{t=1}^T b_t (1-z_t)$. Clearly, $|S| = U$. Since $S \subseteq B(\zero, R)$
+is a $\gamma$-packing, $U = |S| \le (\frac{2R}{\gamma} + 1)^d$.
 
@@
 $$
-\Exp[ z_t | b_t = 1] = \frac{K-1}{K} \; .
+\Exp[ z_t ~|~ b_t = 1] = \frac{K-1}{K} \; .
 $$
@@
 $$
-\Exp[M] = (K-1) \Exp[U] \leq (K-1) \left(\frac{R}{\gamma} \right)^d \; .
+\Exp[M] = (K-1) \Exp[U] \leq (K-1) \left(\frac{2R}{\gamma} + 1 \right)^d \; .
 $$

### 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Clean-ups

@@
 The ignorant algorithm is formally defined as follows.
-\begin{definition} \label{definition:ignorant-algorithm}
-A bandit classification algorithm $\mathcal{A}$ is ignorant if for all
-$t\in[T]$, $\widehat y_t\in \{1,2\}$ is drawn from some distribution that is
-jointly determined by
+\begin{definition}
+\label{definition:ignorant-algorithm}
+A bandit classification algorithm $\calA$ is ignorant if for all $t \in
+\{1,2,\dots,T\}$, $\widehat y_t\in \{1,2\}$ is drawn from some distribution that
+is jointly determined by
 \begin{enumerate}
@@
 \label{theorem:ignorant_lower_bound}
-Suppose $\mathcal{A}$ is an ignorant bandit classification algorithm. There
-exists an adversary that can sequentially choose $(x_1, y_1), (x_2, y_2),
-\ldots, (x_T, y_T) \in \R^d\times \{1,2\}$, such that $\forall t\in[T],
-\|x_t\|\le 1$, $\{(x_t, y_t)\}_{t=1}^T$ is $\gamma$-strongly linearly
-separable, and the expected number of mistakes made by $\mathcal{A}$ is lower
-bounded as
-\begin{align*}
-\Exp\left[ \sum_{t=1}^T \indicator{\widehat y_t \neq y_t} \right]
-\ge \frac{1}{10}\min\left\{\sqrt{T}, \left(\frac{1}{160\gamma}\right)^{\frac{d-2}{4}} \right\} \; .
-\end{align*}
+Suppose $\calA$ is an ignorant bandit classification algorithm. There
+exists an adversary that can sequentially choose $(x_1, y_1), (x_2, y_2), \dots,
+(x_T, y_T) \in \R^d\times \{1,2\}$ so that the examples $\gamma$-strongly
+linearly separable, $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$, and the
+expected number of mistakes made by $\calA$ is at least
+$$
+\frac{1}{10}\min\left\{\sqrt{T}, \left(\frac{1}{160\gamma}\right)^{\frac{d-2}{4}} \right\} \; .
+$$
 \end{theorem}
@@
 Let $\gamma \in (0,\frac 1 {160})$, let $d$ be a positive integer and let $N = (\Omega(\frac{1}{\gamma}))^{(d-2)/2}$.
-There exist vectors $v_1, v_2, \dots, v_N, u_1, u_2, \dots, u_N \in \R^d$ such that for all $i, j \in \{1,2,\dots,N\}$
+There exist vectors $u_1, u_2, \dots, u_N, v_1, v_2, \dots, v_N \in \R^d$ such that for all $i, j \in \{1,2,\dots,N\}$,
 \begin{align*}
-\norm{v_i} & \le 1 \, \\
-\norm{u_i} & \le 1 \, \\
+\norm{u_i} & \le 1 \; , \\
+\norm{v_j} & \le 1 \; , \\
 \ip{u_i}{v_j} & \ge \gamma & & \text{if $i=j$,} \\
@@
 [0,\pi]$, this implies that
-$$
-\ip{z_i}{z_j} \begin{cases} = 1 ,& i = j, \\ \le 1- 8\gamma ,& i \neq j. \end{cases}
-$$
+\begin{align*}
+\ip{z_i}{z_j} &= 1 && \text{if $i = j$,} \\
+\ip{z_i}{z_j} &\le 1 - 8\gamma && \text{if $i \neq j$.}
+\end{align*}
 
@@
 It can be easily checked that for all $i$,
-$\norm{v_i} \le 1$ and $\norm{u_i} \le 1$. In addition,
+$\norm{v_i} \le 1$ and $\norm{u_i} \le 1$. Additionally,
 $$
-\ip{u_i}{v_j}
-= \frac{1}{4} \ip{z_i}{z_j} - \frac {1-4\gamma} 4 \begin{cases} \ge \gamma ,& i = j, \\ \le -\gamma ,& i \neq j. \end{cases}
+\ip{u_i}{v_j} = \frac{1}{4} \ip{z_i}{z_j} - \frac {1-4\gamma} 4 \; .
 $$
+Thus,
+\begin{align*}
+\ip{u_i}{v_j} &\ge \gamma && \text{if $i=j$,} \\
+\ip{u_i}{v_j} &\le -\gamma && \text{if $i \neq j$.}
+\end{align*}
 \end{proof}
 
-\begin{proof}[Proof for Theorem~\ref{theorem:ignorant_lower_bound} (PartI: Mistake lower bound)]
+\begin{proof}[Proof for Theorem~\ref{theorem:ignorant_lower_bound} (Part I: Mistake lower bound)]
 We consider the strategy for the adversary described in Algorithm~\ref{algorithm:adversary-strategy}.

### 2019-01-23 ICML-submission/np-hardness-of-the-weak-labeling-problem.tex
Fixes
Clean-ups

@@
 \section{NP-hardness of the weak labeling problem}
+\label{section:np-hardness-of-weak-labeling-problem}
 
@@
 
-We use for $1,2,\dots,K$ for strong labels and $\overline{1}, \overline{2},
-\dots, \overline{K}$ for weak labels. We adopt the convention that
-$\overline{\overline{i}} = i$ for any positive integer $i$. Formally, the weak
+We use symbols $1,2,\dots,K$ for strong labels and symbols $\overline{1},
+\overline{2}, \dots, \overline{K}$ for weak labels. We adopt the convention that
+$\overline{\overline{i}} = i$ for any symbol $i$. Formally, the weak
 labeling problem can be described as below:
@@
 & \le -N + (N-1)-\frac{1}{2} \\
-& < 0 = \ip{w_3}{x} \; .
+& < 0  \\
+& = \ip{w_3}{x} \; .
 \end{align*}
@@
 S_1 &= \left\{i \in \{1,2,\dots,n\} ~:~ \ip{w_1-w_3}{(\e_i, 1)} > 0 \right\}, \\
-S_2 &= \left\{i \in \{1,2,\dots,n\} ~:~ \ip{w_2-w_3}{(\e_i, 1)} > 0 \text{\ and\ } i\notin S_1 \right\}.
+S_2 &= \left\{i \in \{1,2,\dots,n\} ~:~ \ip{w_2-w_3}{(\e_i, 1)} > 0 \right. \\
+& \qquad \qquad \qquad \left. \text{\ and\ } i \notin S_1 \right\}.
 \end{align*}

### 2019-01-23 ICML-submission/appendix-nearest-neighbor-algorithm.tex
Fixes

@@
 
-\begin{lemma}[Separation lemma]
-\label{lemma:separation-lemma}
+\begin{lemma}[Non-separation lemma]
+\label{lemma:non-separation-lemma}
 Let $(V,\ip{\cdot}{\cdot})$ be a vector space, $K$ be a positive integer and let
@@
 Suppose for the sake on contradiction that $y_i \neq y_j$. By
-Definition~\ref{definition:linear-separability}, there exists a set of $k$
-vectors $(w_1, \ldots, w_k)$, such that
+Definition~\ref{definition:linear-separability}, there exists
+vectors $w_1, \ldots, w_K$ such that
 conditions~\eqref{equation:weak-linear-separability-1}
@@
 $$
-\ip{w_{y_i} - w_{y_j}}{x_i - x_j} \le \norm{w_{y_i} - w_{y_j}} \cdot \norm{x_i - x_j} < \sqrt{2} \gamma
+\ip{w_{y_i} - w_{y_j}}{x_i - x_j} \le \norm{w_{y_i} - w_{y_j}} \cdot \norm{x_i - x_j} \le \sqrt{2} \gamma
 $$
@@
 $\gamma$-packing if for any $x,x' \in S$ such that $x \neq x'$ we have $\norm{x -
-x'} > \gamma$. The following lemma is standard. Also recall that $B(x,R) = \{ x'
+x'} > \gamma$. The following lemma is standard. Also recall that $\B(x,R) = \{ x'
 \in \R^d ~:~ \norm{x' - x} \le R \}$ denotes the closed ball of radius $R$
@@
 Let $\gamma$ and $R$ be positive real numbers.
-If $S \subseteq B(\zero,R) \subseteq \R^d$ is a $\gamma$-packing then
+If $S \subseteq \B(\zero,R) \subseteq \R^d$ is a $\gamma$-packing then
 $$
@@
 \begin{proof}
-If $S$ is a $\gamma$-packing then $\{ B(x,\gamma/2) ~:~ x \in S \}$
-is a collection of disjoint balls of radius $\gamma$ that fit into $B(\zero,R + \gamma/2)$.
+If $S$ is a $\gamma$-packing then $\{ \B(x,\gamma/2) ~:~ x \in S \}$
+is a collection of disjoint balls of radius $\gamma$ that fit into $\B(\zero,R + \gamma/2)$.
 Thus,
 $$
-|S| \cdot \Vol(B(\zero, \gamma/2)) \le \Vol(B(\zero,R + \gamma/2))
+|S| \cdot \Vol(\B(\zero, \gamma/2)) \le \Vol(\B(\zero,R + \gamma/2))
 $$
@@
 |S|
-& \le \frac{\Vol(B(\zero,R + \gamma/2))}{\Vol(B(\zero, \gamma/2))} \\
+& \le \frac{\Vol(\B(\zero,R + \gamma/2))}{\Vol(\B(\zero, \gamma/2))} \\
 & = \left( \frac{R + \gamma/2}{\gamma/2} \right)^d \\
@@
 $t$, i.e. we fall into the ``else'' case. Note that if $b_t = 0$, then by
-Lemma~\ref{lemma:separation-lemma}, the prediction $\widehat{y}_t$ must equal
+Lemma~\ref{lemma:non-separation-lemma}, the prediction $\widehat{y}_t$ must equal
 $y_t$, i.e. $z_t = 0$. Therefore, $M = \sum_{t=1}^T z_t = \sum_{t=1}^T b_t z_t$.
-Let $U = \sum_{t=1}^T b_t (1-z_t)$. Clearly, $|S| = U$. Since $S \subseteq B(\zero, R)$
+Let $U = \sum_{t=1}^T b_t (1-z_t)$. Clearly, $|S| = U$. Since $S \subseteq \B(\zero, R)$
 is a $\gamma$-packing, $U = |S| \le (\frac{2R}{\gamma} + 1)^d$.

### 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Fixes

@@
 \R^{K\times d} \to \R$ that gives a loss value $\widehat
-\ell_t(W)$ to all linear models $W \in \R^{K\times d}$ ($W=[w_1 \ldots
-w_K]^\top$ for $w_1, \ldots, w_K$ defined in
+\ell_t(W)$ to all linear models $W \in \R^{K\times d}$ ($W=[w_1 \dots
+w_K]^\top$ for $w_1, w_2, \dots, w_K$ defined in
 Definition~\ref{definition:linear-separability}). The requirement for

### 2019-01-23 ICML-submission/introduction.tex
Fixes

@@
 which we know the class label. Weakly labeled example is an example for which we
-know that class label can be anything except for a particular one class.
-In Appendix~\ref{section:np-hardness-of-weak-labeling-problem}, we show that the offline
-problem of finding a linear multiclass separator consistent with a set of
-strongly and weakly labeled examples is NP-hard. In
-Appendix~\ref{section:mistake-lower-bound-for-ignorant-algorithms}, we show that
-any algorithm that uses only strongly-labeled examples and ignores weakly
-labeled examples makes at least $\Omega\left( \left(1/(160 \gamma)\right)^{(d-2)/4} \right)$
-mistakes.
+know that class label can be anything except for a particular one class. In
+Appendix~\ref{section:np-hardness-of-weak-labeling-problem}, we show that the
+offline problem of finding a linear multiclass separator consistent with a set
+of strongly and weakly labeled examples is NP-hard. In
+Appendix~\ref{section:mistake-lower-bound-for-ignorant-algorithms}, we prove a
+lower bound on the number of mistakes of any algorithm that uses only
+strongly-labeled examples and ignores weakly labeled examples.

### 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Fixes

--- 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
@@
 \label{definition:ignorant-algorithm}
-A bandit classification algorithm $\calA$ is ignorant if for all $t \in
-\{1,2,\dots,T\}$, $\widehat y_t\in \{1,2\}$ is drawn from some distribution that
-is jointly determined by
+An algorithm $\calA$ for \textsc{Online Multiclass Linear Classification with
+Bandit Feedback} is called \emph{ignorant} if for all $t \in \{1,2,\dots,T\}$,
+$\widehat y_t$ is drawn from some distribution that is jointly determined by
 \begin{enumerate}
@@
 are the rounds in which the algorithm predicts correctly (that is,
-$\{\tau_1, \ldots, \tau_{n_t}\} = \{1 \le \tau < t ~:~ \widehat y_\tau=y_\tau\}$).
+$\{\tau_1, \dots, \tau_{n_t}\} = \{1 \le \tau < t ~:~ \widehat y_\tau=y_\tau\}$).
 \end{enumerate}
-We use $p_t(\cdot|x_t)\in \{p\in \R_+^2 ~:~ p^\top\mathbf{1}=1\}$ to denote
+We use $p_t(\cdot|x_t)\in \{p\in \R_+^K ~:~ p^\top\mathbf{1}=1\}$ to denote
 the distribution $\widehat y_t$ is drawn from. Note that we let the current
@@
 An ignorant algorithm does not learn from mistakes in the following sense.
-Suppose that an ignorant algorithm predicts incorrectly at time $t$ ($\widehat
-y_t \neq y_t$). Then at time $t+1$, if it is given the same feature vector
-$x_{t+1}=x_t$, it will predict the label with the same distribution
-$p_{t+1}(\cdot|x_{t+1})=p_{t+1}(\cdot|x_t)=p_t(\cdot|x_t)$. Below we describe
-the difficulty of learning from mistakes using a class of natural approaches
-under the weak separability assumption. Consider an approach similar to OBAMA:
-in each round $t$, we create a \textit{convex} loss function $\widehat \ell_t:
-\R^{K\times d} \to \R$ that gives a loss value $\widehat
-\ell_t(W)$ to all linear models $W \in \R^{K\times d}$ ($W=[w_1 \ldots
-w_K]^\top$ for $w_1, \ldots, w_K$ defined in
-Definition~\ref{definition:linear-separability}). The requirement for
-$\widehat{\ell}_t$ to be convex is due to computational efficiency. To let
-$\widehat{\ell}_t$ reflect the loss, if $\widehat y_t \neq y_t$, we want to
-assign larger loss values $\widehat{\ell_t}(W)$ to the inconsistent models
-$\mathcal{W}=\{W: \ip{w_{\widehat y_t}}{x_t} \ge \ip{w_i}{x_t}, \forall
-i\in[K]\}$, while for other $W$'s, we want $\widehat{\ell_t}(W)$ to be smaller.
-The following fact can be verified when $K\ge 3$, which suggests there is no
-way to define the loss $\widehat \ell_t$ that satisfies the above properties
-constraints: there exists $W_1, W_2, W_3$, where $W_2$ is in the line segment
-between $W_1$ and $W_3$, such that $W_2\in \mathcal{W}$, while $W_1, W_3 \notin
-\mathcal{W}$. On one hand, by convexity, we should have
-$\widehat{\ell}_t(W_2)\le \max\{\widehat{\ell}_t(W_1),
-\widehat{\ell}_t(W_3)\}$; on the other hand, to penalize $\mathcal{W}$, we
-should have $\widehat{\ell}_t(W_2) > \widehat{\ell}_t(W_1)$ and
-$\widehat{\ell}_t(W_2) > \widehat{\ell}_t(W_3)$. Clearly, these two requirements
-contradict each other.
+Suppose that an ignorant algorithm predicts incorrectly at time $t$. Then at
+time $t+1$, if it is given the same feature vector $x_{t+1}=x_t$, it will
+predict the label with the same distribution
+$p_{t+1}(\cdot|x_{t+1})=p_{t+1}(\cdot|x_t)=p_t(\cdot|x_t)$.
+
+% Below we describe
+%the difficulty of learning from mistakes using a class of natural approaches
+%under the weak separability assumption. Consider an approach similar to OBAMA:
+%in each round $t$, we create a \textit{convex} loss function $\widehat \ell_t:
+%\R^{K\times d} \to \R$ that gives a loss value $\widehat
+%\ell_t(W)$ to all linear models $W \in \R^{K\times d}$ ($W=[w_1 \dots
+%w_K]^\top$ for $w_1, w_2, \dots, w_K$ defined in
+%Definition~\ref{definition:linear-separability}). The requirement for
+%$\widehat{\ell}_t$ to be convex is due to computational efficiency. To let
+%$\widehat{\ell}_t$ reflect the loss, if $\widehat y_t \neq y_t$, we want to
+%assign larger loss values $\widehat{\ell_t}(W)$ to the inconsistent models
+%$\mathcal{W}=\{W: \ip{w_{\widehat y_t}}{x_t} \ge \ip{w_i}{x_t}, \forall
+%i\in[K]\}$, while for other $W$'s, we want $\widehat{\ell_t}(W)$ to be smaller.
+%The following fact can be verified when $K\ge 3$, which suggests there is no
+%way to define the loss $\widehat \ell_t$ that satisfies the above properties
+%constraints: there exists $W_1, W_2, W_3$, where $W_2$ is in the line segment
+%between $W_1$ and $W_3$, such that $W_2\in \mathcal{W}$, while $W_1, W_3 \notin
+%\mathcal{W}$. On one hand, by convexity, we should have
+%$\widehat{\ell}_t(W_2)\le \max\{\widehat{\ell}_t(W_1),
+%\widehat{\ell}_t(W_3)\}$; on the other hand, to penalize $\mathcal{W}$, we
+%should have $\widehat{\ell}_t(W_2) > \widehat{\ell}_t(W_1)$ and
+%$\widehat{\ell}_t(W_2) > \widehat{\ell}_t(W_3)$. Clearly, these two requirements
+%contradict each other.
 
@@
 \begin{theorem}[Mistake Lower Bound for Ignorant Algorithms]
-\label{theorem:ignorant_lower_bound}
-Suppose $\calA$ is an ignorant bandit classification algorithm. There
-exists an adversary that can sequentially choose $(x_1, y_1), (x_2, y_2), \dots,
-(x_T, y_T) \in \R^d\times \{1,2\}$ so that the examples $\gamma$-strongly
-linearly separable, $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$, and the
-expected number of mistakes made by $\calA$ is at least
+\label{theorem:ignorant-lower-bound}
+Suppose $\calA$ is an ignorant algorithm for \textsc{Online Multiclass Linear
+Classification with Bandit Feedback}. There exists an adversary that can
+sequentially choose labeled examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)
+\in \R^d\times \{1,2\}$ so that the examples are $\gamma$-strongly linearly
+separable, $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$, and the expected
+number of mistakes made by $\calA$ is at least
 $$
@@
 \label{lemma:embed_d_gamma}
-Let $\gamma \in (0,\frac 1 {160})$, let $d$ be a positive integer and let $N = (\Omega(\frac{1}{\gamma}))^{(d-2)/2}$.
+Let $\gamma \in (0,\frac{1}{160})$, let $d$ be a positive integer and let $N = (\frac{1}{2\sqrt{40\gamma}})^{d-2}$.
 There exist vectors $u_1, u_2, \dots, u_N, v_1, v_2, \dots, v_N \in \R^d$ such that for all $i, j \in \{1,2,\dots,N\}$,
@@
 \begin{proof}
-By Lemma 6 of~\cite{Long-1995}, there exists a set of $N =
-(\frac{1}{2\sqrt{40\gamma}})^{d-2}$ $(d-1)$-dimensional vectors $z_1, \ldots,
-z_N$ on the unit sphere $\mathbb{S}^{d-2}$, such that $\theta(z_i, z_j) \ge
-\sqrt{40 \gamma}$. As $\cos\theta \le 1-\theta^2/5$ for every $\theta \in
-[0,\pi]$, this implies that
+By Lemma 6 of~\citet{Long-1995}, there exists a set of $N$ dimensional vectors
+$z_1, z_2, \dots, z_N \in \R^{d-1}$ such that $\norm{z_1} = \norm{z_2} = \dots =
+\norm{z_N} = 1$ and the angle between the vectors is $\measuredangle(z_i, z_j) \ge
+\sqrt{40 \gamma}$. Since $\cos\theta \le 1-\theta^2/5$ for any $\theta \in
+[-\pi,\pi]$, this implies that
 \begin{align*}
@@
 
-\begin{proof}[Proof for Theorem~\ref{theorem:ignorant_lower_bound} (Part I: Mistake lower bound)]
+\begin{proof}[Proof for Theorem~\ref{theorem:ignorant-lower-bound} (Part I: Mistake lower bound)]
 We consider the strategy for the adversary described in Algorithm~\ref{algorithm:adversary-strategy}.
@@
 
-\begin{proof}[Proof for Theorem~\ref{theorem:ignorant_lower_bound} (Part II: linear separability)]
+\begin{proof}[Proof for Theorem~\ref{theorem:ignorant-lower-bound} (Part II: linear separability)]
 Observe that in Algorithm~\ref{algorithm:adversary-strategy}, in the beginning

### 2019-01-23 ICML-submission/empirical-comparison.tex
Fixes

@@
 data sets are shown in~\autoref{figure:strongly-and-weakly-separable-datasets}.
-Although, the data sets are shown as two-dimensional, we used a third dimension,
-the so-called \emph{constant feature}, i.e. a feature that for every example is
-set to $1$. We added the constant feature so that
+Although, the data sets are shown as two-dimensional, we used a third dimension
+that for every example is equal to $1$. In other words, we added the so-called
+\emph{constant feature}. The constant feature is necessary so that
 \autoref{figure:strongly-separable-dataset} is actually strongly lineraly
@@
 
-We evaluated all three the algorithms on the two data sets. Since all three
+We evaluated all three algorithms on the two data sets. Since all three
 algorithms are randomized, we run each algorithm $20$ times. \textsc{Banditron}

### 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Spell check

@@
 \textsc{Nearest-Neighbor Algorithm} (Algorithm~\ref{algorithm:nearest-neighbor})
-presented in Appendix~\ref{section:nearest-neighbor-algorithm} is an ingnorant
+presented in Appendix~\ref{section:nearest-neighbor-algorithm} is an ignorant
 algorithm.

### 2019-01-23 ICML-submission/from-weak-separability-to-strong-separability.tex
minor

--- 2019-01-22 ICML-submission/from-weak-separability-to-strong-separability.tex
@@
 
-In this section, we consider case when the examples are weakly linearly
+In this section, we consider the case when the examples are weakly linearly
 separable. Throughout this section, we assume without loss of generality that
@@
 after applying $\phi$ the examples become strongly linearly separable with a
-margin $\gamma'$ and their norms are bounded by $2$. The parameter $\gamma'$ is
+margin $\gamma'$ and their squared norms are bounded by $2$. The parameter $\gamma'$ is
 a function of the old margin $\gamma$ and the number of classes $K$, and is
@@
 
-%\begin{proof}[Proof sketch of Theorem~\ref{theorem:margin-transformation}]
-%Since the examples $(x_1, y_1)$,  $\dots$, $(x_T, y_T)$ are weakly
-%linearly separable with margin $\gamma$, there are vectors $w_1, w_2, \dots, w_K$
-%satisfying \eqref{equation:weak-linear-separability-1} and
-%\eqref{equation:weak-linear-separability-2}.
+\begin{proof}[Proof sketch of Theorem~\ref{theorem:margin-transformation}]
+Since the examples $(x_1, y_1)$,  $\dots$, $(x_T, y_T)$ are weakly
+linearly separable with margin $\gamma$, there are vectors $w_1, w_2, \dots, w_K$
+satisfying \eqref{equation:weak-linear-separability-1} and
+\eqref{equation:weak-linear-separability-2}.
 
-%Fix any $i \in \{1,2,\dots,K\}$. Consider the $K-1$ vectors $(w_i - w_j)/2$ for
-%$j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors have norm at most
-%$1$. We consider two cases regarding the relationship between $\gamma_1$ and
-%$\gamma_2$.
+Fix any $i \in \{1,2,\dots,K\}$. Consider the $K-1$ vectors $(w_i - w_j)/2$ for
+$j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors have norm at most
+$1$. We consider two cases regarding the relationship between $\gamma_1$ and
+$\gamma_2$.
 
-%\paragraph{Case 1: $\gamma_1 \geq \gamma_2$.} In this setting,
-%Theorem~\ref{theorem:polynomial-approximation-1} implies that there exist a
-%multivariate polynomial $p_i:\R^d \to \R$
+\paragraph{Case 1: $\gamma_1 \geq \gamma_2$.} In this setting,
+Theorem~\ref{theorem:polynomial-approximation-1} implies that there exist a
+multivariate polynomial $p_i:\R^d \to \R$
 
-%\begin{align*}
-%\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{{2}/{\gamma}} \right\rceil \; ,
-%\end{align*}
-%such that all examples $x$ in $R_i^+$ (resp. $R_i^-$) satisfy $p_i(x) \geq 1/2$
-%(resp. $p_i(x) \leq -1/2$).
-%Therefore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
-% and if $y_t \neq i$ then $p_i(x_t) \le -1/2$, and
-%\begin{align*}
-%&\norm{p_i}
-%\\
-%& \le
-%\left[
-%  188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
-%\right]^{
-%  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil }{2}
-%} \; . \\
-%\end{align*}
-%By \autoref{lemma:norm-bound}, there exists $c_i \in \ell_2$ such that
-%$\ip{c_i}{\phi(x)}_{\ell_2} = p_i(x)$, and
-%\begin{align*}
-%&\norm{c_i}_{\ell_2}
-%\\
-%& \le
-%\left[
-%  376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
-%\right]^{
-%  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil}{2}
-%} \; .
-%\end{align*}
-%Define vectors $u_i \in \ell_2$ as
-%\begin{align*}
-%u_i & =
-%\frac{c_i/\sqrt{K}}{
-%  \left[
-%    376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
-%  \right]^{
-%    \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}{2}
-%  }
-%} \; . \\
-%\end{align*}
+\begin{align*}
+\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{{2}/{\gamma}} \right\rceil \; ,
+\end{align*}
+such that all examples $x$ in $R_i^+$ (resp. $R_i^-$) satisfy $p_i(x) \geq 1/2$
+(resp. $p_i(x) \leq -1/2$).
+Therefore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
+ and if $y_t \neq i$ then $p_i(x_t) \le -1/2$, and
+\begin{align*}
+&\norm{p_i}
+\\
+& \le
+\left[
+  188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
+\right]^{
+  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil }{2}
+} \; . \\
+\end{align*}
+By \autoref{lemma:norm-bound}, there exists $c_i \in \ell_2$ such that
+$\ip{c_i}{\phi(x)}_{\ell_2} = p_i(x)$, and
+\begin{align*}
+&\norm{c_i}_{\ell_2}
+\\
+& \le
+\left[
+  376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
+\right]^{
+  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil}{2}
+} \; .
+\end{align*}
+Define vectors $u_i \in \ell_2$ as
+\begin{align*}
+u_i & =
+\frac{c_i/\sqrt{K}}{
+  \left[
+    376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
+  \right]^{
+    \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}{2}
+  }
+} \; . \\
+\end{align*}
 
-%Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$.
-%Futhermore, for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma_1$
-%and for all $j \in \{1,2,\dots,K\} \setminus \{y_t\}$,
-%$\ip{u_j}{x_t} \le - \gamma_1$. In other words,
-%$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
-%strongly linearly separable with margin $\gamma_1 = \max\{\gamma_1, \gamma_2\}$.
+Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$.
+Futhermore, for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma_1$
+and for all $j \in \{1,2,\dots,K\} \setminus \{y_t\}$,
+$\ip{u_j}{x_t} \le - \gamma_1$. In other words,
+$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
+strongly linearly separable with margin $\gamma_1 = \max\{\gamma_1, \gamma_2\}$.
 
-%\paragraph{Case 2: $\gamma_1 \leq \gamma_2$.} Following the
-%same idea as Case 1 and using Theorem~\ref{theorem:polynomial-approximation-1},
-%we can show that
-%$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
-%strongly linearly separable with margin $\gamma_2 = \max\{\gamma_1, \gamma_2\}$.
+\paragraph{Case 2: $\gamma_1 \leq \gamma_2$.} Following the
+same idea as Case 1 and using Theorem~\ref{theorem:polynomial-approximation-1},
+we can show that
+$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
+strongly linearly separable with margin $\gamma_2 = \max\{\gamma_1, \gamma_2\}$.
+%The proof for the case of $\gamma_1 < \gamma_2$
+%is symmetric.
 
-%In summary, the examples are strongly
-%linearly separable with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
-%Finally, observe that for any $t=1,2,\dots,T$,
-%\[
-%k(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
-%\qedhere
-%\]
-%\end{proof}
+In summary, the examples are strongly
+linearly separable with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
+Finally, observe that for any $t=1,2,\dots,T$,
+\[
+k(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
+\qedhere
+\]
+\end{proof}

### 2019-01-23 ICML-submission/introduction.tex
Spell check introduction
minor

--- 2019-01-22 ICML-submission/introduction.tex
@@
 Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
-viewed as a repeated game between a learner and an adversary. At each timestep
-$t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals $x_t\in
-\R^d$ to the learner. Upon receiving $x_t$, the learner makes a prediction
-$\widehat{y}_t$ and receives feedback. In contrast with the standard
-full-information setting, where the feedback given is the correct label $y_t$,
-here the feedback is only a binary indicator of whether the prediction was
-correct or not. The protocol of the problem is formally stated below.
+viewed as a repeated game between a learner and an adversary. At each
+timestep $t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals $x_t\in \R^d$ to the learner.
+Upon receiving $x_t$, the learner makes a prediction $\widehat{y}_t$ and receives feedback.
+In contrast to the
+standard full-information setting, where the feedback given is the correct label
+$y_t$, here the feedback is only a binary indicator of whether the prediction
+was correct or not. The protocol of the problem is formally stated below.
 
@@
 \label{algorithm:game-protocol}}
-\textbf{Require:} Number of classes $K$, number of rounds $T$. \\
-\textbf{Require:} Inner product space $(V,\ip{\cdot}{\cdot})$. \\
+\textbf{Require:} Number of classes $K$, number of rounds $T$.\\
 \For{$t=1,2,\dots,T$}{
-Adversary chooses example $(x_t, y_t) \in V \times \{1,2,\dots,K\}$ where $x_t$ is revealed to the learner.\\
+     Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.\\
      Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
-Observe feedback $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
+     Observe feedback
+          $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
+%$z_t \in \{0,1\}$, \\ \qquad where $z_t = \begin{cases}
+%0 & \text{if $\widehat y_t = y_t$,} \\
+%1 & \text{if $\widehat y_t \neq y_t$.}
+%\end{cases}$
 }
+
 \end{protocol}
@@
 two notions of linear separability, \emph{weak} and \emph{strong}, formally
-stated in \autoref{definition:linear-separability}. The standard notion of
-multiclass linear separability~\citep{Crammer-Singer-2003} corresponds to the
-weak linear separability. For multiclass classification with $K$ classes, weak
-linear separability requires that all examples from the same class lie in an
-intersection of $K-1$ halfspaces and all other examples lie in the complement of
+stated in
+Definition~\ref{definition:weak-linear-separability}.
+The standard notion of multiclass linear
+separability~\citep{Crammer-Singer-2003} corresponds to the weak linear
+separability. %For binary classification, the weak and strong separability are
+%identical. However, they differ for multiclass classification with $K \ge 3$
+%classes.
+For multiclass classification with $K$ classes, weak linear
+separability requires that all examples from the same class lie in an intersection of $K-1$ halfspaces and all other examples lie in the complement of
 the intersection of the halfspaces. Strong linear separability means that
@@
 weakly linearly separable with a margin $\gamma$, then the \textsc{Multiclass
-Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes. It
-is also known that any (possibly randomized) algorithm must make $\frac{1}{2}
-\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. The
-\textsc{Multiclass Perceptron} achieves an information-theoretically optimal
-mistake bound, while being computationally and memory efficient.~\footnote{For
-completeness, we present these folklore results along with their proofs in
-Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
-material.}
+Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
+%%%%%
+It is also known that any (possibly randomized) algorithm must
+make $\frac{1}{2} \left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the
+worst case.
+The \textsc{Multiclass Perceptron} achieves an
+information-theoretically optimal mistake bound, while being
+computationally and memory efficient.
+~\footnote{
+%%%%%
+%These are folklore results.
+For completeness, we present these
+folklore
+%%%%%
+results along
+with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs} in the
+supplementary material.}
 
@@
 claimed that their Conservative OVA algorithm with PA-I update has a finite
-mistake bound under the strong linear separability condition, their proof of
-Theorem 2 is incorrect: first, their Theorem 2 implies a mistake upper bound of
-$\frac{R}{\gamma}$ with sufficiently large $C$, which contradicts our lower
+mistake bound under the strong linear separability condition, their
+Theorem 2 is incorrect: first, their Theorem 2
+implies a mistake upper bound of $\frac{R}{\gamma}$ with
+sufficiently large $C$, which contradicts our lower
 bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
-second, their Lemma 4 cannot be directly applied to the bandit setting, as the
-algorithm only makes updates on a subset of the $w_i$'s.} We design a simple and
-efficient algorithm
+second, their Lemma 4 cannot be directly applied to the bandit
+setting, as the algorithm only makes updates on a subset of the $w_i$'s.} We
+design a simple and efficient algorithm
 (Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
@@
 $\Omega(K (R/\gamma)^2))$ mistakes in the worst case. The extra $O(K)$
-multiplicative factor in the mistake bound, as compared to the full-information
+multiplicative factor the mistake bound, as compared to the full-information
 setting, is the price we pay for the bandit feedback, or more precisely, the
@@
 
-For the case when the examples are weakly linearly separable, it was open for a
-long time whether there exist \textit{efficient} algorithms with finite mistake
+For the case when the examples are weakly linearly separable, it was open for a long
+time whether there exist \textit{efficient} algorithms with finite mistake
 bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}.
 Furthermore, in~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, they ask the question:
-Is there \textit{any} algorithm with a finite mistake bound that has no explicit
-dependence on the dimensionality of the feature vectors? We answer both
-questions affirmatively by providing an efficient algorithm with finite
-dimensionless mistake bound (Algorithm~\ref{algorithm:kernelized}).\footnote{An
-in inefficient algorithm was given by~\cite{Daniely-Helbertal-2013}.}
+is there \textit{any} algorithm with a finite mistake bound that has no explicit dependence
+on the dimensionality of the feature vectors? We answer both questions affirmatively by
+providing an efficient algorithm with finite dimensionless mistake bound
+(Algorithm~\ref{algorithm:kernelized}).~\footnote{The second question was previously
+answered by~\cite{Daniely-Helbertal-2013} with an inefficient algorithm.}
 
@@
 non-linear feature mapping $\phi$ and associated positive definite kernel
-$k(x,x')$ that makes the examples \emph{strongly} linearly separable in a
-higher-dimensional space. We then use the kernelized version of
+$k(x,x')$ that makes the examples \emph{strongly} linearly separable in a higher-dimensional space.
+We then use the kernelized version of
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} for
@@
 \log K))}$ mistakes.
-
-In Appendix~\ref{section:nearest-neighbor-algorithm}, we propose and analyze a
-very different algorithm for weakly separable data. The algorithm is based on
-the obvious idea that two points that are close enough must have the same label.
-
-Finally, we study two questions related to the computational and
-information-theoretic hardness of the problem. Any algorithm for the bandit
-setting collects information in the form of so called \emph{strongly labeled}
-and \emph{weakly labeled} examples. Strongly labeled examples are those for
-which we know the class label. Weakly labeled example is an example for which we
-know that class label can be anything except for a particular one class.
-In Appendix~\ref{section:np-hardness-of-weak-labeling-problem}, we show that the offline
-problem of finding a linear multiclass separator consistent with a set of
-strongly and weakly labeled examples is NP-hard. In
-Appendix~\ref{section:mistake-lower-bound-for-ignorant-algorithms}, we show that
-any algorithm that uses only strongly-labeled examples and ignores weakly
-labeled examples makes at least $\Omega\left( \left(1/(160 \gamma)\right)^{(d-2)/4} \right)$
-mistakes.

### 2019-01-23 ICML-submission/related-work.tex
minor

@@
 step towards answering this question, showing that efficient algorithms with
-mistake bounds quasipolynomial in $\frac 1 \gamma$ or quasipolynomial in $K$ can
-be obtained.
+mistake bounds quasipolynomial in $1/\gamma$ (for constant $K$)
+or quasipolynomial in $K$ (for constant $\gamma$) can be obtained.
 

### 2019-01-23 ICML-submission/appendix-experiment.tex

@@
-\section{Supplementary Materials for Section~\ref{sec:experiments}}
-\label{sec:supp-to-experiment}
+\section{Supplementary Materials for Section~\ref{section:experiments}}
+\label{section:supp-to-experiment}
 
-However, in 2D, the samples in Figure~\ref{fig:strong-points} do not satisfy the strong linear separability defined in Definition~\ref{definition:weak-linear-separability}, which requires that any class can be separated from all the others by a hyperplane that \textit{passes through the origin}.
-We therefore raise the dimensionality to 3D by adding a constant feature to all samples.
-This is equivalent to allowing the separating hyperplanes to have a bias, so that they do not need to pass through the origin.
-Thus Figure~\ref{fig:strong-points} becomes strongly linearly separable.
-To better understand how each algorithm works, we plot in Figure~\ref{fig:banditron-points},~\ref{fig:linearova-points},~\ref{fig:rationalova-points} the final decision boundary that is learned by each algorithm.
+To better understand how each algorithm works, we plot in
+Figure~\ref{fig:banditron-points},~\ref{fig:linearova-points},~\ref{fig:rationalova-points}
+the final decision boundary that is learned by each algorithm.
 
@@
      \label{fig:banditron-points}
-    % \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$. }
 \end{figure}
@@
     \label{fig:linearova-points}
-   % \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$. }
 \end{figure}
@@
     \label{fig:rationalova-points}
-    % \caption{Comparison between our algorithm and Banditron with different exploration parameter $\epsilon$ under $\gamma=0.05$ and $K=3$. }
 \end{figure}

### 2019-01-23 ICML-submission/introduction.tex

--- 2019-01-23 ICML-submission/introduction.tex
@@
 Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
-viewed as a repeated game between a learner and an adversary. At each timestep
+viewed as a repeated game between a learner and an adversary. At each time step
 $t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals $x_t\in
@@
 claimed that their Conservative OVA algorithm with PA-I update has a finite
-mistake bound under the strong linear separability condition, their proof of
+mistake bound under the strong linear separability condition, their
 Theorem 2 is incorrect: first, their Theorem 2 implies a mistake upper bound of

### 2019-01-23 ICML-submission/introduction.tex
minor

@@
 mistake bound under the strong linear separability condition, their
-Theorem 2 is incorrect: first, their Theorem 2 implies a mistake upper bound of
-$\frac{R}{\gamma}$ with sufficiently large $C$, which contradicts our lower
+Theorem 2 is incorrect: first, their Lemma 1 (with $C = +\infty$) along with Theorem 1
+implies a mistake upper bound of
+$(\frac{R}{\gamma})^2$, which contradicts our lower
 bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
-second, their Lemma 4 cannot be directly applied to the bandit setting, as the
+second, their Lemma 1 cannot be directly applied to the bandit setting, as the
 algorithm only makes updates on a subset of the $w_i$'s.} We design a simple and

### 2019-01-23 ICML-submission/empirical-comparison.tex
Spell check
polished the experiment section

--- 2019-01-22 ICML-submission/empirical-comparison.tex
@@
 
-We implemented
-Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
-Algorithm~\ref{algorithm:kernelized} with
-kernel~\eqref{equation:rational-kernel}, and the \textsc{Banditron} algorithm.
-We generated strongly and weakly separable data sets with $K=3$ classes. The
-data sets are shown in~\autoref{figure:strongly-and-weakly-separable-datasets}.
-Although, the data sets are shown as two-dimensional, we used a third dimension,
-the so-called \emph{constant feature}, i.e. a feature that for every example is
-set to $1$. We added the constant feature so that
-\autoref{figure:strongly-separable-dataset} is actually strongly lineraly
-separable. For both data sets, the sample size is $T=5\times 10^6$ and the
-margin is $\gamma=0.05$.
+In this section, we provide an empirical evaluation on our algorithms, verifying their
+effectiveness on linearly separable datasets.
+We generate strongly and weakly linearly separable datasets with $K=3$ classes in
+$\R^3$, where the third dimension of every example is always equal to $1$
+(i.e. a \emph{constant feature}).
+See Figures~\ref{figure:strongly-separable-dataset} and~\ref{figure:weakly-separable-dataset}
+ for visualizations
+of the two datasets, along with detailed descriptions of the two data distributions.
+
+%~\autoref{figure:strongly-and-weakly-separable-datasets}
+%For both datasets, the sample size is $T=5\times 10^6$ and the
+%margin is $\gamma=0.05$.
+%Projections of the examples from the two datasets onto their first two coordinates
+% are shown in
+%We added a third dimension
+%to every example that is equal to $1$. In other words, we added the so-called
+%\emph{constant feature}. The constant feature is necessary so that
+%\autoref{figure:strongly-separable-dataset} is actually strongly linearly
+%separable.
 
@@
 \vspace*{-0.2cm}
-\caption{Strongly and weakly generated data sets with $K=3$ classes. All
-examples lie in the unit ball of $\R^2$. Class 1 is depicted red. Classes 2 and
-3 are depcited gree and blue, respectively. $80\%$ of the examples belong to class 1,
+\caption{Strongly and weakly separable datasets with $K=3$ classes. Here
+ we show projections of the examples onto their first two coordinates, which
+ lie in the unit ball of $\R^2$. Class 1 is depicted red. Classes 2 and
+3 are depicted green and blue, respectively. $80\%$ of the examples belong to class 1,
 $10\%$ belong to class 2 and $10\%$ belong to class 3. Class 1
@@
 occupy angle intervals $[15^\circ, 180^\circ]$ and $[-180^\circ, -15^\circ]$
-respectively. We removed points that lie within margin $\gamma=0.05$ of the
-linear separator.}
+respectively. The examples are strongly and weakly linearly separable with a margin of $\gamma=0.05$, respectively.}
 \label{figure:strongly-and-weakly-separable-datasets}
@@
 
-We evaluated all three the algorithms on the two data sets. Since all three
-algorithms are randomized, we run each algorithm $20$ times. \textsc{Banditron}
-has exploration rate parameter $\epsilon$ for which we tried values $\epsilon
-\in \{0.02, 0.01, 0.005, 0.002, 0.001, 0.0005 \}$. The average cumulative number
-of mistakes up to round $t$ as a function $t$ are shown in
+%We removed points that lie within margin $\gamma=0.05$ of the
+%linear separator.
+
+We implement
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
+Algorithm~\ref{algorithm:kernelized} with
+rational kernel~\eqref{equation:rational-kernel}, and the \textsc{Banditron} algorithm.
+We evaluate these algorithms on the above two datasets, with a time horizon of
+$T=5\times 10^6$.
+\textsc{Banditron}
+has exploration rate parameter $\epsilon$, for which we tried values $\epsilon
+\in \{0.02, 0.01, 0.005, 0.002, 0.001, 0.0005 \}$.
+Since all three
+algorithms are randomized, we run each algorithm $20$ times.
+The average cumulative number
+of mistakes up to round $t$ as a function of $t$ are shown in
 Figures~\ref{figure:number-of-mistakes-strongly-separable-dataset}
@@
 
-We can see there is a dilemma for \textsc{Banditron}. When the
-exploration rate $\epsilon$ is large, it suffers from the cost of exploration.
-When the exploration rate is small, it cannot adapt its model quickly enough.
-This problem is exacerbated when a majority class occupies a small region, like
-class 1. Striking a balance between the two extremes leads to the
-$\Theta(\sqrt{T})$ number of mistakes. In contrast, our algorithm makes
-significant progress on every mistake it makes, leading to a finite mistake
-bound.
+We can see that there is a tradeoff in the setting of the exploration rate $\epsilon$
+for \textsc{Banditron}. For a large $\epsilon$, \textsc{Banditron} suffers from the cost of exploration, whereas for small $\epsilon$, its model cannot be updated quickly enough.
+As expected, Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} has a small number of mistakes in the strongly linearly separable setting, while having a large number
+of mistakes in the weakly linearly separable setting, due to the limited representation power of linear classifiers.
+In contrast,
+Algorithm~\ref{algorithm:kernelized} with rational kernel has a small number of mistakes in both settings, exhibiting strong adaptivity guarantees.
+Appendix~\ref{section:supp-to-experiment} shows the decision boundaries
+that each of the algorithms learns.
 
-Appendix~\ref{section:supp-to-experiment} shows decision boundaries
-that each of the algorithms learns.
+%This problem is exacerbated when a class of large proportion occupies a small region
+%(e.g. class 1).
+%In contrast, our algorithms make
+%significant progress on every mistake it makes, leading to a finite mistake
+%bound.
+%Striking a balance between the two extremes leads to the
+%$\Theta(\sqrt{T})$ number of mistakes.
 
@@
 \includegraphics[width=0.45\textwidth]{figures/strong3}
-\caption{Strongly separable case. Cumulative number of mistakes of various algorithms.}
+\caption{The cumulative number of mistakes versus the number of rounds,
+in the strongly separable case (\autoref{figure:strongly-separable-dataset}) for various algorithms.}
 \label{figure:number-of-mistakes-strongly-separable-dataset}
@@
 \includegraphics[width=0.45\textwidth]{figures/weak3}
-\caption{Weakly separable case. Cumulative number of mistakes of various algorithms.}
+\caption{The cumulative number of mistakes versus the number of rounds,
+in the weakly separable case (\autoref{figure:weakly-separable-dataset}) for various algorithms.}
 \label{figure:number-of-mistakes-weakly-separable-dataset}

### 2019-01-23 ICML-submission/from-weak-separability-to-strong-separability.tex
polished the experiment section

@@
 
-We construct a positive definite kernel function $k(\cdot, \cdot)$ whose
+We use a positive definite kernel function $k(\cdot, \cdot)$, namely
+\emph{rational kernel}~\citep{Shalev-Shwartz-Shamir-Sridharan-2011}, whose
 corresponding feature map $\phi(\cdot)$ transforms any sequence of \emph{weakly}
@@
 
-The kernel function $k:\B(\zero,1) \times \B(\zero,1) \to \R$ is defined as
+The rational kernel $k:\B(\zero,1) \times \B(\zero,1) \to \R$ is defined as
 \begin{equation}

### 2019-01-23 ICML-submission/introduction.tex
polished the experiment section

@@
 the obvious idea that two points that are close enough must have the same label.
+\chicheng{I wonder if the mistake bound of this algorithm is too large to be included
+as ``our contributions'' - perhaps we should only mention it as a folklore/baseline?}
 
@@
 Appendix~\ref{section:np-hardness-of-weak-labeling-problem}, we show that the
-offline problem of finding a linear multiclass separator consistent with a set
+offline problem of finding a multiclass linear classifier consistent with a set
 of strongly and weakly labeled examples is NP-hard. In

### 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
.

@@
 below, it is actually natural, and several recently proposed bandit
-classification algorithms that achieve the $\sqrt{T}$-regret bound belong to
+classification algorithms that achieve $\sqrt{T}$ regret bounds belong to
 this family, e.g., SOBA~\citep{Beygelzimer-Orabona-Zhang-2017},
@@
 \begin{enumerate}
-\item $x_t$
+\item $x_t$,
 \item $H_t \triangleq \left( (x_{\tau_1}, y_{\tau_1}), (x_{\tau_2}, y_{\tau_2}), \ldots, (x_{\tau_{n_t}}, y_{\tau_{n_t}}) \right)$,
@@
 
-\begin{theorem}[Mistake Lower Bound for Ignorant Algorithms]
+\begin{theorem}[Mistake lower bound for ignorant algorithms]
 \label{theorem:ignorant-lower-bound}
@@
 \in \R^d\times \{1,2\}$ so that the examples are $\gamma$-strongly linearly
-separable, $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$, and the expected
+separable, $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$, and the expected
 number of mistakes made by $\calA$ is at least

### 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
clarification

@@
 \end{align}
-where in the first inequality we use $A_t+B_t\le 1$; in the equality, we use
+where in the first inequality we use the fact that $A_t$ and $B_t$ cannot be $1$ simultaneously; in the equality, we use
 $B_{t+1}=B_t\indicator{\widehat y_t\neq y_t}$ by $B_t$'s definition; in the last
-inequality we use the fact that when $t\le N$ and $A_t=1$, it must be $y_t=1$.
+inequality we use the fact that when $t\le N$ and $A_t=1$, it must be $y_t=1$ and $\Pr[\widehat y_t=y_t]=p_t(1|x_t)<1-q_0$.
 Now, denote $T_1 = \argmin_{\tau} \{ p_\tau(1|x_\tau) \ge 1-q_0 \}$ (if such
@@
 
-Note that $B_{T_1}=1$, and for $t \ge T_1$ we have
-$\Exp[B_{t+1}=0|B_t=1]=\Pr[\widehat y_t=y_t~|~B_t=1] = \Pr[\widehat y_t=2|B_t=1] \le
-q_0$ because the algorithm is ignorant. Thus the second term in
+Note that $B_{T_1}=1$, and for $t \geq T_1$ the adversary will switch to ``$\textsc{phase}=2$'' and has $y_t=2$. Therefore, 
+$\Exp[B_{t+1}=0|B_{t}=1]=\Pr[\widehat y_t=y_t~|~B_t=1] = \Pr[\widehat y_t=2|B_t=1].$ 
+Note that when $B_t=1$, by definition there exists a $\tau\le t$ with $p_\tau(1|x_\tau)\ge 1-q_0$, 
+and the algorithm all makes mistakes at $\tau, \tau+1, \ldots, t$. Since the algorithm is ignorant, and when $\textsc{phase}=2$, 
+the features all remain the same, we have $p_t(1|x_t)=p_{t-1}(1|x_{t-1})=\cdots=p_\tau(1|x_\tau)\ge 1-q_0$. 
+Thus we can further upper bound $\Exp[B_{t+1}=0|B_{t}=1]$ by $\Pr[\widehat y_t=2|B_t=1]\leq q_0$. Thus the second term in
 \eqref{equation:mistake_lower_bound_temp} can be calculated as

### 2019-01-23 ICML-submission/empirical-comparison.tex
shortening to 8 pages

@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/strong3}
+\includegraphics[width=0.42\textwidth]{figures/strong3}
 \caption{The cumulative number of mistakes versus the number of rounds,
-in the strongly separable case (\autoref{figure:strongly-separable-dataset}) for various algorithms.}
+in the strongly separable distribution of \autoref{figure:strongly-separable-dataset} for various algorithms.}
 \label{figure:number-of-mistakes-strongly-separable-dataset}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/weak3}
+\includegraphics[width=0.42\textwidth]{figures/weak3}
 \caption{The cumulative number of mistakes versus the number of rounds,
-in the weakly separable case (\autoref{figure:weakly-separable-dataset}) for various algorithms.}
+in the weakly separable distribution of \autoref{figure:weakly-separable-dataset} for various algorithms.}
 \label{figure:number-of-mistakes-weakly-separable-dataset}

### 2019-01-23 ICML-submission/from-weak-separability-to-strong-separability.tex
shortening to 8 pages

@@
 \end{equation}
-Note that kernel function $k(x,x')$ can be evaluated in $O(d)$ time.
+Note that $k(x,x')$ can be evaluated in $O(d)$ time.
 
@@
 the constructions from~\citet{Beigel-Reingold-Spielman-1995}. More importantly,
-the theorems quantify certain parameters of the polynomial, which will allow us
-to give an upper bound on the transformed margin $\gamma'$.
+the theorems quantify certain parameters of the polynomial, which allows us
+to upper bound the transformed margin $\gamma'$.
 
@@
 
-The proofs of the theorems can be found in
-Appendix~\ref{section:proof-of-polynomial-approximation} in the supplementary
-material. The geometric interpretation of the two regions described in parts 1
+The proofs of the theorems are in
+Appendix~\ref{section:proof-of-polynomial-approximation}.
+The geometric interpretation of the two regions described in parts 1
 and 2 of the theorems is explained in Figure~\ref{figure:pizza-slice}. Similar
-but weaker results were proved by~\citet{Klivans-Servedio-2008}. In particular,
+but weaker results were proved by~\citet{Klivans-Servedio-2008}. Specifically,
 our bounds in parts 1, 2, 3, 4 of

### 2019-01-23 ICML-submission/notions-of-linear-separability.tex
shortening to 8 pages

@@
 with a positive margin $\gamma$ but is not strongly linearly separable with
-any positive margin $\gamma$. An example of such set of labeled examples is
-shown in~\autoref{figure:weakly-linearly-separable-examples-with-margin}.
+any positive margin.~\autoref{figure:weakly-linearly-separable-examples-with-margin}
+shows one such set of labeled examples.
 

### 2019-01-23 ICML-submission/appendix-experiment.tex
minor

@@
 
-To better understand how each algorithm works, we plot in
-Figure~\ref{fig:banditron-points},~\ref{fig:linearova-points},~\ref{fig:rationalova-points}
-the final decision boundary that is learned by each algorithm.
+We plot in
+Figures~\ref{fig:banditron-points},~\ref{fig:linearova-points},~\ref{fig:rationalova-points}
+the final decision boundaries learned by each algorithm in the two datasets (Figures~\ref{figure:number-of-mistakes-strongly-separable-dataset}
+and~\ref{figure:number-of-mistakes-weakly-separable-dataset}), i.e. its decision boundaries
+output at round $T+1$.
 
@@
     \vspace*{-0.2cm}
-    \caption{\textsc{Banditron}'s decision boundary}
+    \caption{\textsc{Banditron}'s final decision boundaries}
      \label{fig:banditron-points}
@@
     \vspace*{-0.2cm}
-    \caption{Our Algorithm with linear kernel (Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})'s decision boundary}
+    \caption{Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}'s final decision boundaries}
     \label{fig:linearova-points}
 \end{figure}
+%Our Algorithm with linear kernel (
+%To better understand how each algorithm works,
+%Our Algorithm with rational kernel (
 
@@
     \vspace*{-0.2cm}
-    \caption{Our Algorithm with rational kernel (Algorithm~\ref{algorithm:kernelized})'s decision boundary}
+    \caption{Algorithm~\ref{algorithm:kernelized} (with rational kernel)'s final decision boundaries}
     \label{fig:rationalova-points}

### 2019-01-23 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Fixes
Beautify section 4
Spell check

@@
 \citet[Section 3.3.1]{Shalev-Shwartz-2012}. Each copy corresponds to one of the
-classes. At each timestep $t$, upon seeing example $x_t$, copy $i$ makes a
+classes. At each time step $t$, upon seeing example $x_t$, copy $i$ makes a
 binary prediction on whether $x_t$ belongs to class $i$ or not. If at least one
@@
 }
-
 \end{algorithm}
@@
 algorithm makes at least $((K-1)/2)\left\lfloor (R/\gamma)^2/4 \right\rfloor$
-mistakes in expectation on some \textsc{Online Multiclass Classification with
-Bandit Feedback} problem with $K$ classes and labeled examples $(x_1, y_1),
+mistakes in expectation on some sequence of labeled examples $(x_1, y_1),
 (x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ for some inner
-product space $(V, \ip{\cdot}{\cdot})$ that are strongly linearly separable with
-margin $\gamma$ and satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$.
+product space $(V, \ip{\cdot}{\cdot})$ such that the examples are strongly
+linearly separable with margin $\gamma$ and satisfy $\norm{x_1}, \norm{x_2},
+\dots, \norm{x_T} \le R$.
 \end{theorem}
@@
 (or \emph{kernels}, for short), which are functions of the form $k: X \times X
-\to V$ for some set $X$ and inner product space $(V, \ip{\cdot}{\cdot})$ such
-that the matrix $\left(k(x_i,x_j)\right)_{i,j=1}^m$ is a symmetric positive
-semidefinite for any positive integer $m$ and $x_1, x_2, \dots, x_m \in X$
-\citep[Definition 2.5]{Scholkopf-Smola-2002}. As opposed to explicitly
-maintaining the weight vector for each class, the algorithm maintains the set of
-example-scalar pairs corresponding to the updates of the non-kernelized
-algorithm. As a direct consequence of
+\to \R$ for some set $X$ such that the matrix
+$\left(k(x_i,x_j)\right)_{i,j=1}^m$ is a symmetric positive semidefinite for any
+positive integer $m$ and $x_1, x_2, \dots, x_m \in X$ \citep[Definition
+2.5]{Scholkopf-Smola-2002}.\footnote{Every kernel has an associated feature map
+$\phi:X \to V$ for some inner product space $(V,\ip{\cdot}{\cdot})$ such that
+$k(x,x') = \ip{\phi(x)}{\phi(x')}$.} As opposed to explicitly maintaining the
+weight vector for each class, the algorithm maintains the set of example-scalar
+pairs corresponding to the updates of the non-kernelized algorithm. As a direct
+consequence of
 Theorem~\ref{theorem:strongly-separable-examples-mistake-upper-bound} we get a
@@
 are strongly linearly separable with margin $\gamma$,
-\item for all $t$ in $\cbr{1,\ldots,T}$, $k(x_t,x_t) \le R^2$,
+\item $k(x_1, x_1), k(x_2, x_2), \dots, k(x_T,x_T) \le R^2$,
 \end{enumerate}

### 2019-01-23 ICML-submission/introduction.tex
removed chicheng's comment
Fixes

@@
 viewed as a repeated game between a learner and an adversary. At each time step
-$t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals $x_t\in
-\R^d$ to the learner. Upon receiving $x_t$, the learner makes a prediction
-$\widehat{y}_t$ and receives feedback. In contrast with the standard
+$t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals the
+feature vector $x_t$ to the learner. Upon receiving $x_t$, the learner makes a
+prediction $\widehat{y}_t$ and receives feedback. In contrast with the standard
 full-information setting, where the feedback given is the correct label $y_t$,
@@
 In Appendix~\ref{section:nearest-neighbor-algorithm}, we propose and analyze a
-very different algorithm for weakly separable data. The algorithm is based on
-the obvious idea that two points that are close enough must have the same label.
-\chicheng{I wonder if the mistake bound of this algorithm is too large to be included
-as ``our contributions'' - perhaps we should only mention it as a folklore/baseline?}
+very different algorithm for weakly linearly separable data. The algorithm is
+based on the obvious idea that two points that are close enough must have the
+same label.
+%\chicheng{I wonder if the mistake bound of this algorithm is too large to be included
+%as ``our contributions'' - perhaps we should only mention it as a folklore/baseline?}
 
@@
 which we know the class label. Weakly labeled example is an example for which we
-know that class label can be anything except for a particular one class. In
+know that class label can be anything except for one particular class. In
 Appendix~\ref{section:np-hardness-of-weak-labeling-problem}, we show that the

### 2019-01-23 ICML-submission/related-work.tex
polished the experiment section
Fixes

@@
 The problem of online bandit multiclass learning was initially formulated in the
-pioneering work of~\citet{Auer-Long-1999}, under the name of ``weak
-reinforcement model''. They showed that if all examples agree with some
-classifier from a prespecified hypothesis class $\calH$, then the optimal
-mistake bound in the bandit setting can be upper bounded by the optimal mistake
-bound in the full information setting, times a factor of $(2.01 + o(1))K \ln K$.
-\citet{Long-2017} later improved the factor to $(1 + o(1)) K \ln K$ and showed
-its near-optimality. \citet{Daniely-Helbertal-2013} extended the results to the
+pioneering work of~\citet{Auer-Long-1999} under the name of ``weak reinforcement
+model''. They showed that if all examples agree with some classifier from a
+prespecified hypothesis class $\calH$, then the optimal mistake bound in the
+bandit setting can be upper bounded by the optimal mistake bound in the full
+information setting, times a factor of $(2.01 + o(1))K \ln K$. \citet{Long-2017}
+later improved the factor to $(1 + o(1)) K \ln K$ and showed its
+near-optimality. \citet{Daniely-Helbertal-2013} extended the results to the
 setting where the performance of the algorithm is measured by its regret, i.e.
 the difference between the number of mistakes made by the algorithm and the
-number of mistakes made by the best classifier in $\calH$ in hindsight.
-We remark that
-all algorithms developed in this context are computationally inefficient.
+number of mistakes made by the best classifier in $\calH$ in hindsight. We
+remark that all algorithms developed in this context are computationally
+inefficient.
 
@@
 inefficient algorithms that work in the weakly linearly separable setting, one
-with a mistake bound of
-$O(K^2 d \ln(d/\gamma))$,
-the other with a
-mistake bound of $\widetilde{O}((K^2/\gamma^2) \ln T)$. The latter result
-was later improved by \citet{Daniely-Helbertal-2013}, which gives a
-computationally inefficient algorithm with a mistake upper bound of
-$\widetilde{O}(K/\gamma^2)$.
-In addition, the authors propose the
+with a mistake bound of $O(K^2 d \ln(d/\gamma))$, the other with a mistake bound
+of $\widetilde{O}((K^2/\gamma^2) \ln T)$. The latter result was later improved
+by \citet{Daniely-Helbertal-2013}, which gives a computationally inefficient
+algorithm with a mistake upper bound of $\widetilde{O}(K/\gamma^2)$. In
+addition,~\citet{Kakade-Shalev-Shwartz-Tewari-2008} propose the
 \textsc{Banditron} algorithm, a computationally efficient algorithm that has a
@@
 and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weakly linearly separable
-setting.
-In contrast to mild dependencies on the time horizon for mistake bounds of
-computationally inefficient algorithms,
-the polynomial dependence of \textsc{Banditron}'s mistake bound on the
-time horizon is undesirable for problems with a long time horizon, in the
-weakly linearly separable setting. One key open
-question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
-design computationally efficient algorithms that achieve mistake bounds that
-match or improve over those of inefficient algorithms. In this paper, we take a
-step towards answering this question, showing that efficient algorithms with
-mistake bounds quasipolynomial in $1/\gamma$ (for constant $K$)
-or quasipolynomial in $K$ (for constant $\gamma$) can be obtained.
+setting. In contrast to mild dependencies on the time horizon for mistake bounds
+of computationally inefficient algorithms, the polynomial dependence of
+\textsc{Banditron}'s mistake bound on the time horizon is undesirable for
+problems with a long time horizon, in the weakly linearly separable setting. One
+key open question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether
+one can design computationally efficient algorithms that achieve mistake bounds
+that match or improve over those of inefficient algorithms. In this paper, we
+take a step towards answering this question, showing that efficient algorithms
+with mistake bounds quasipolynomial in $1/\gamma$ (for constant $K$) or
+quasipolynomial in $K$ (for constant $\gamma$) can be obtained.
 
@@
 base hypothesis as a separate feature. However, most of these works achieve a
-regret of order $\widetilde{O}(\sqrt{T})$ to $O(T^{3/4})$.
-In the weakly linearly
-separable setting, these algorithms at best guarantees a mistake upper bound of
-$\widetilde{O}(\sqrt{T})$, which is undesirable for problems with a long time
-horizon. One exception is the \textsc{Newtron} algorithm, where with appropriate
-settings of parameter $\alpha$, it is able to achieve a $O(\ln T)$ regret against
-the $\alpha$-logistic loss.
-However, as argued in ~\citep[][Appendix D]{Beygelzimer-Orabona-Zhang-2017}, if
-the setting of $\alpha$ makes the regret bound $O(\sqrt{T})$, the $\alpha$-logistic loss
-of the best linear predictor would be $\Omega(T^{3/4})$. Therefore,
-\textsc{Newtron} at best guarantees a mistake upper bound of
-$O(\sqrt{T})$ in the weakly linearly separable setting.
+regret of order $\widetilde{O}(\sqrt{T})$ to $O(T^{3/4})$. In the weakly
+linearly separable setting, these algorithms at best guarantees a mistake upper
+bound of $\widetilde{O}(\sqrt{T})$, which is undesirable for problems with a
+long time horizon. One exception is the \textsc{Newtron} algorithm, where with
+appropriate settings of parameter $\alpha$, it is able to achieve a $O(\ln T)$
+regret against the $\alpha$-logistic loss. However, as argued in
+~\citep[][Appendix D]{Beygelzimer-Orabona-Zhang-2017}, if the setting of
+$\alpha$ makes the regret bound $O(\sqrt{T})$, the $\alpha$-logistic loss of the
+best linear predictor would be $\Omega(T^{3/4})$. Therefore, \textsc{Newtron} at
+best guarantees a mistake upper bound of $O(\sqrt{T})$ in the weakly linearly
+separable setting.
 
@@
 
-%Online bandit multiclass learning is a special case of the contextual bandits
-%problem~\citep{Auer-2003, Langford-Zhang-2008}, where the cost is the
-%classification error. A series of works in the contextual bandits literature
-%focuses on oracle-efficiency, that is, they assume access to an oracle that
-%given a set of cost-sensitve learning examples, generates .
-
 There is a large body of literature on the contextual bandits
@@
 of the learner is to minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) -
-\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
-%%%%%
-The bandit multiclass
-learning problem can be seen as a special case,
-% of the contextual bandits problem,
-where the
-cost $c_t(i)$ is the classification error $\indicator{i \neq y_t}$, and the
-policy class $\Pi$ is the set of linear classifiers $\cbr{x \mapsto \argmax_y
-(Wx)_y: W \in \R^{k \times d}}$. A series of works in the contextual bandits
-learning literature
-%focus on oracle-efficiency~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
-%Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
-%Syrgkanis-Krishnamurthy-Schapire-2016,
-%Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. Specifically, they
-assume access to
-a policy optimization oracle that returns a policy in $\Pi$ that minimizes
-its empirical cost on any set of cost-sensitive examples, and
-%the
-construct algorithms that call
-%algorithm only calls
-the oracle a polynomial number of times%
+\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$. The bandit multiclass learning
+problem can be seen as a special case, where the cost $c_t(i)$ is the
+classification error $\indicator{i \neq y_t}$, and the policy class $\Pi$ is the
+set of linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times
+d}}$. A series of works in the contextual bandits learning literature assume
+access to a policy optimization oracle that returns a policy in $\Pi$ that
+minimizes its empirical cost on any set of cost-sensitive examples, and
+construct algorithms that call the oracle a polynomial number of times%
 ~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
@@
 Syrgkanis-Krishnamurthy-Schapire-2016,
-Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
-%%%%%
-However, these algorithms are not
+Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. However, these algorithms are not
 truly computationally efficient in our setting, as it is NP-hard in general to
@@
 examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.
-
-%that receives a set of cost-sensitive learning examples and policy class $\Pi$,
-%as algorithms generate cost-sensitive examples that may not be linearly
-%separable Algorithms that satisfy oracle efficiency has been proposed in the
-%literature, for example.
 
@@
 s \gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
-information-theoretic regret upper bounds
-%%%%%
-%under
- for
-%%%%%
-various settings of $\calF$. On the other hand, it gives an efficient algorithm
-%%%%%
-with an
-%%%%%
-$O(\sqrt{T})$ regret against the benchmark of
-$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$. A direct
-application of this result to \textsc{Online Bandit Multiclass Linear
-Classification}
-%%%%%
-%yields
-gives
-%%%%%
-an algorithm with $O(\sqrt{T})$ mistake bound in the
-strongly linearly separable %%%%%
-case.
-%%%%%
+information-theoretic regret upper bounds for various settings of $\calF$. On
+the other hand, it gives an efficient algorithm with an $O(\sqrt{T})$ regret
+against the benchmark of $\calF = \cbr{x \mapsto W x: W \in \R^{k \times d},
+\one^T W = 0}$. A direct application of this result to \textsc{Online Bandit
+Multiclass Linear Classification} gives an algorithm with $O(\sqrt{T})$ mistake
+bound in the strongly linearly separable case.
 

### 2019-01-23 ICML-submission/empirical-comparison.tex
Fixed experiments section

@@
 
-In this section, we provide an empirical evaluation on our algorithms, verifying their
-effectiveness on linearly separable datasets.
-We generate strongly and weakly linearly separable datasets with $K=3$ classes in
-$\R^3$, where the third dimension of every example is always equal to $1$
-(i.e. a \emph{constant feature}).
-See Figures~\ref{figure:strongly-separable-dataset} and~\ref{figure:weakly-separable-dataset}
- for visualizations
-of the two datasets, along with detailed descriptions of the two data distributions.
-
-%~\autoref{figure:strongly-and-weakly-separable-datasets}
-%For both datasets, the sample size is $T=5\times 10^6$ and the
-%margin is $\gamma=0.05$.
-%Projections of the examples from the two datasets onto their first two coordinates
-% are shown in
-%We added a third dimension
-%to every example that is equal to $1$. In other words, we added the so-called
-%\emph{constant feature}. The constant feature is necessary so that
-%\autoref{figure:strongly-separable-dataset} is actually strongly linearly
-%separable.
+In this section, we provide an empirical evaluation on our algorithms, verifying
+their effectiveness on linearly separable datasets. We generated strongly and
+weakly linearly separable datasets with $K=3$ classes in $\R^3$ i.i.d. from two
+data distributions. Figures~\ref{figure:strongly-separable-dataset}
+and~\ref{figure:weakly-separable-dataset} show visualizations of the two
+datasets, along with detailed descriptions of the distributions.
 
@@
 \vspace*{-0.2cm}
-\caption{Strongly and weakly separable datasets with $K=3$ classes. Here
- we show projections of the examples onto their first two coordinates, which
- lie in the unit ball of $\R^2$. Class 1 is depicted red. Classes 2 and
-3 are depicted green and blue, respectively. $80\%$ of the examples belong to class 1,
-$10\%$ belong to class 2 and $10\%$ belong to class 3. Class 1
-occupies the angle interval $[-15^\circ, 15^\circ]$, while classes 2 and 3
-occupy angle intervals $[15^\circ, 180^\circ]$ and $[-180^\circ, -15^\circ]$
-respectively. The examples are strongly and weakly linearly separable with a margin of $\gamma=0.05$, respectively.}
+\caption{Strongly and weakly linearly separable datasets in $\R^3$ with $K=3$
+classes and $T=5\times 10^6$ examples. Here we show projections of the examples
+onto their first two coordinates, which lie in the ball of radius $1/\sqrt{2}$
+centered at the origin. The third coordinate is $1/\sqrt{2}$ for all examples.
+Class 1 is depicted red. Classes 2 and 3 are depicted green and blue,
+respectively. $80\%$ of the examples belong to class 1, $10\%$ belong to class 2
+and $10\%$ belong to class 3. Class 1 lies in the angle interval $[-15^\circ,
+15^\circ]$, while classes 2 and 3 lie in the angle intervals $[15^\circ,
+180^\circ]$ and $[-180^\circ, -15^\circ]$ respectively. The examples are
+strongly and weakly linearly separable with a margin of $\gamma=0.05$,
+respectively. (Examples lying within margin $\gamma$ of the linear separators
+were rejected during sampling.)}
 \label{figure:strongly-and-weakly-separable-datasets}
@@
 
-%We removed points that lie within margin $\gamma=0.05$ of the
-%linear separator.
-
-We implement
+We implemented
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
-Algorithm~\ref{algorithm:kernelized} with
-rational kernel~\eqref{equation:rational-kernel}, and the \textsc{Banditron} algorithm.
-We evaluate these algorithms on the above two datasets, with a time horizon of
-$T=5\times 10^6$.
-\textsc{Banditron}
-has exploration rate parameter $\epsilon$, for which we tried values $\epsilon
-\in \{0.02, 0.01, 0.005, 0.002, 0.001, 0.0005 \}$.
-Since all three
-algorithms are randomized, we run each algorithm $20$ times.
-The average cumulative number
-of mistakes up to round $t$ as a function of $t$ are shown in
+Algorithm~\ref{algorithm:kernelized} with rational
+kernel~\eqref{equation:rational-kernel}, and the \textsc{Banditron} algorithm.
+We evaluated these algorithms on the two datasets. \textsc{Banditron} has an
+exploration rate parameter, for which we tried values $0.02, 0.01, 0.005, 0.002,
+0.001, 0.0005$. Since all three algorithms are randomized, we run each algorithm
+$20$ times. The average cumulative number of mistakes up to round $t$ as a
+function of $t$ are shown in
 Figures~\ref{figure:number-of-mistakes-strongly-separable-dataset}
@@
 
-We can see that there is a tradeoff in the setting of the exploration rate $\epsilon$
-for \textsc{Banditron}. For a large $\epsilon$, \textsc{Banditron} suffers from the cost of exploration, whereas for small $\epsilon$, its model cannot be updated quickly enough.
-As expected, Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} has a small number of mistakes in the strongly linearly separable setting, while having a large number
-of mistakes in the weakly linearly separable setting, due to the limited representation power of linear classifiers.
-In contrast,
-Algorithm~\ref{algorithm:kernelized} with rational kernel has a small number of mistakes in both settings, exhibiting strong adaptivity guarantees.
-Appendix~\ref{section:supp-to-experiment} shows the decision boundaries
-that each of the algorithms learns.
-
-%This problem is exacerbated when a class of large proportion occupies a small region
-%(e.g. class 1).
-%In contrast, our algorithms make
-%significant progress on every mistake it makes, leading to a finite mistake
-%bound.
-%Striking a balance between the two extremes leads to the
-%$\Theta(\sqrt{T})$ number of mistakes.
+We can see that there is a tradeoff in the setting of the exploration rate for
+\textsc{Banditron}. With large exploration parameter, \textsc{Banditron} suffers
+from over-exploration, whereas with small exploration parameter, its model
+cannot be updated quickly enough. As expected,
+Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} has
+a small number of mistakes in the strongly linearly separable setting, while
+having a large number of mistakes in the weakly linearly separable setting, due
+to the limited representation power of linear classifiers. In contrast,
+Algorithm~\ref{algorithm:kernelized} with rational kernel has a small number of
+mistakes in both settings, exhibiting strong adaptivity guarantees.
+Appendix~\ref{section:supp-to-experiment} shows the decision boundaries that
+each of the algorithms learns.
 
@@
 \includegraphics[width=0.42\textwidth]{figures/strong3}
-\caption{The cumulative number of mistakes versus the number of rounds,
-in the strongly separable distribution of \autoref{figure:strongly-separable-dataset} for various algorithms.}
+\caption{Average cumulative number of mistakes of various algorithms versus the
+number of rounds for the strongly linearly separable dataset of
+\autoref{figure:strongly-separable-dataset}.}
 \label{figure:number-of-mistakes-strongly-separable-dataset}
@@
 \includegraphics[width=0.42\textwidth]{figures/weak3}
-\caption{The cumulative number of mistakes versus the number of rounds,
-in the weakly separable distribution of \autoref{figure:weakly-separable-dataset} for various algorithms.}
+\caption{Average cumulative number of mistakes of various algorithms versus the
+number of rounds for the weakly linearly separable dataset of
+\autoref{figure:weakly-separable-dataset}.}
 \label{figure:number-of-mistakes-weakly-separable-dataset}

### 2019-01-23 ICML-submission/appendix-proofs-for-strongly-separable-examples.tex
lower bound changes in the strongly separable case

@@
 \begin{proof}[Proof of \autoref{theorem:strongly-separable-examples-mistake-lower-bound}]
-We use probabilistic method. Let $M = \left\lfloor \frac{1}{4} (R/\gamma)^2
+%We use probabilistic method. 
+Let $M = \left\lfloor \frac{1}{4} (R/\gamma)^2
 \right\rfloor$. Let $V = \R^{M+1}$ equipped with the standard inner product.
@@
 
-Finally, since strong separability and norm condition hold with probability one,
-there exists a particular (i.e. deterministic) sequence of examples for which
+Thus there exists a particular sequence of examples for which
 the algorithm makes at least $\frac{K-1}2 \left\lfloor \frac 1 4 (R/\gamma)^2

### 2019-01-23 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
small tweak

@@
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
-to use $K$ copies of the \textsc{Binary Perceptron} algorithm; see e.g.
-\citet[Section 3.3.1]{Shalev-Shwartz-2012}. Each copy corresponds to one of the
-classes. At each time step $t$, upon seeing example $x_t$, copy $i$ makes a
-binary prediction on whether $x_t$ belongs to class $i$ or not. If at least one
-copy makes a positive prediction, the algorithm chooses its prediction as one of
-the classes corresponding to a positive prediction. If all copies make negative
-predictions, the algorithm makes a prediction uniformly at random from
+to use $K$ copies of the \textsc{Binary Perceptron} algorithm, one copy per class; see e.g.
+\citet[Section 3.3.1]{Shalev-Shwartz-2012}.
+Upon seeing each example $x_t$, copy $i$ predicts 
+whether or not $x_t$ belongs to class $i$.
+Multiclass predictions are done by evaluating all $K$ binary predictors and outputting any class with a positive prediction.
+If all binary predictions are negative, the algorithm chooses a prediction a prediction uniformly at random from
 $\cbr{1,\ldots,K}$.
@@
 supplementary material.
+\citet{Daniely-Helbertal-2013} provide a lower bound under the assumption of weak linear separability, which does not immediately imply a lower bound under the stronger notion.
 
@@
 linear separability condition, and the $(K-1)/2$ expected mistake lower bound
-follows from ~\citep[][Claim 2]{Daniely-Helbertal-2013}. However, it is unclear
-if the trivial lower bound is the best possible if $K$ is large, i.e.,
-$\omega((R/\gamma)^2)$. We leave this as an open problem.
+follows from ~\citep[][Claim 2]{Daniely-Helbertal-2013}. %However, it is unclear
+%if the trivial lower bound is the best possible if $K$ is large, i.e.,
+%$\omega((R/\gamma)^2)$. We leave this as an open problem.
 

### 2019-01-23 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex

@@
 supplementary material.
-\citet{Daniely-Helbertal-2013} provide a lower bound under the assumption of weak linear separability, which does not immediately imply a lower bound under the stronger notion.
 
@@
 \paragraph{Remark.}
+\citet{Daniely-Helbertal-2013} provide a lower bound under the assumption of weak linear separability, which does not immediately imply a lower bound under the stronger notion.
 If $\gamma \le R$ then, irrespective of any other conditions on $K$, $R$, and

### 2019-01-23 ICML-submission/related-work.tex

@@
 
-Many works consider bandit multiclass classification in the general setting,
-where the examples are not necessarily separable by some linear
-classifier~\cite{Abernethy-Rakhlin-2009, Wang-Jin-Valizadegan-2010,
+The general problem of linear bandit multiclass learning has received considerable attention~\cite{Abernethy-Rakhlin-2009, Wang-Jin-Valizadegan-2010,
 Crammer-Gentile-2013, Hazan-Kale-2011, Beygelzimer-Orabona-Zhang-2017,
-Foster-Kale-Luo-Mohri-Sridharan-2018}. In addition, \citet{Chen-Lin-Lu-2014,
+Foster-Kale-Luo-Mohri-Sridharan-2018}. \citet{Chen-Lin-Lu-2014,
 Zhang-Jung-Tewari-2018} study online bandit multiclass boosting under bandit
 feedback, where one can view boosting as linear classification by treating each
-base hypothesis as a separate feature. However, most of these works achieve a
-regret of order $\widetilde{O}(\sqrt{T})$ to $O(T^{3/4})$. In the weakly
-linearly separable setting, these algorithms at best guarantees a mistake upper
-bound of $\widetilde{O}(\sqrt{T})$, which is undesirable for problems with a
-long time horizon. One exception is the \textsc{Newtron} algorithm, where with
-appropriate settings of parameter $\alpha$, it is able to achieve a $O(\ln T)$
-regret against the $\alpha$-logistic loss. However, as argued in
-~\citep[][Appendix D]{Beygelzimer-Orabona-Zhang-2017}, if the setting of
-$\alpha$ makes the regret bound $O(\sqrt{T})$, the $\alpha$-logistic loss of the
-best linear predictor would be $\Omega(T^{3/4})$. Therefore, \textsc{Newtron} at
-best guarantees a mistake upper bound of $O(\sqrt{T})$ in the weakly linearly
-separable setting.
+base hypothesis as a separate feature.  
+%However, most of these works achieve a
+%regret of order $\widetilde{O}(\sqrt{T})$ to $O(T^{3/4})$.  
+In the weakly linearly separable setting, however, 
+all these algorithms guarantee a mistake 
+bound of ${O}(\sqrt{T})$ at best.
+%One exception is the \textsc{Newtron} algorithm, which---with
+%an appropriate setting of parameter $\alpha$---can achieve a $O(\ln T)$
+%regret against the $\alpha$-logistic loss. However, as argued in
+%~\citep[][Appendix D]{Beygelzimer-Orabona-Zhang-2017}, if the setting of
+%$\alpha$ makes the regret bound $O(\sqrt{T})$, the $\alpha$-logistic loss of the
+%best linear predictor would be $\Omega(T^{3/4})$. Therefore, \textsc{Newtron} at
+%best guarantees a mistake upper bound of $O(\sqrt{T})$ in the weakly linearly
+%separable setting.
 
@@
 
-There is a large body of literature on the contextual bandits
-problem~\citep{Auer-2003, Langford-Zhang-2008}. In this problem, the learner is
+There is a large body of literature on contextual bandit
+learning~\citep{Auer-2003, Langford-Zhang-2008}. In this problem, the learner is
 given a policy class $\Pi$, and at each timestep $t$, an example $x_t$ is shown,
@@
 set of linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times
-d}}$. A series of works in the contextual bandits learning literature assume
+d}}$. A series of papers in the contextual bandits learning literature assume
 access to a policy optimization oracle that returns a policy in $\Pi$ that

### 2019-01-23 src/octave/compute_kernel.m
delete old codes

@@ -1,183 +1,0 @@
-function K = compute_kernel(in1,in2,in3,in4)
-% COMPUTE_KERNEL Calculates the kernel values
-%
-%   K = COMPUTE_KERNEL(X,IND1,IND2,KERNEL_PARAMS) calculates the kernel
-%   matrix for the data X, using the indexes in IND1 and IND2. The type of
-%   kernel and the parameters are passed through the structure
-%   KERNEL_PARAMS.
-%   K is a matrix with a number of rows equal to the number of indexes of
-%   IND1 and number of rows equal to the number of indexes in IND2.
-%
-%   K = COMPUTE_KERNEL(X1,X2,KERNEL_PARAMS) calculates the kernel matrix
-%   between the data X1 and the data X2. The type of kernel
-%   and the parameters are passed through the structure KERNEL_PARAMS.
-%   K is a matrix with a number of rows equal to the number of columns of
-%   X1 and number of rows equal to the number of columns of X2.
-%
-%   KERNEL_PARAMS is a struct with the field type with one of the following
-%   strings:
-%
-%       'linear'              Linear kernel or dot product
-%       'poly'                Polynomial kernel
-%       'rbf'                 Gaussian Radial Basis Function kernel
-%       'sigmoid'             Sigmoidal kernel
-%       'triangular'          Triangular kernel
-%       'intersection'        Intersection kernel
-%       'intersection_sparse' Intersection kernel for sparse matrices
-%       'expchi2'             Exponential Chi^2 kernel
-%       'expchi2_sparse'      Exponential Chi^2 kernel for sparse matrices
-%       'vovk_inf_poly'       Vovk infinite polynomial
-%
-%   The other fields of KERNEL_PARAMS depend on the specific kernel.
-%
-%   Note that K is always returned as a dense matrix.
-%
-%   Warning: For expchi2_sparse each feature vector must have sum of the
-%   elements equal to 1.
-%
-%   Example:
-%       % Load the data
-%       load synth_2d
-%       % Define a Gaussian kernel, with scale = 2
-%       hp.type='rbf'
-%       hp.gamma=2
-%       % Builds the kernel matrix
[…]

### 2019-01-23 src/octave/draw_results.m

@@ -1,115 +1,0 @@
-%close all;
-%clear all;
-
-% rseed_list = [1686, 543264, 7454213, 4545, 9621];
-rseed_list = [1686];
-folder = 'results_mg0.1000_n0.0000';
-
-dataset = 'strong';  
-ga_list = logspace(-0, -4, 16);
-nu_list = logspace(0, -4, 16);
-legend_list = {};
-
-% linear ova
-tmp = [];
-for r=1:length(rseed_list)
-   rseed = rseed_list(r);
-   filename = sprintf('%s/linova_%s_sd%d.mat', folder, dataset, rseed);
-   A = load(filename); 
-   tmp = [tmp, A.aer(end)]; 
-end
-loglog(ga_list, ones(size(ga_list))*mean(tmp));   hold on;
-legend_list = [legend_list, 'linear ova'];
-
-
-% rational ova
-err = [];
-for nu_idx = 1:length(nu_list)
-   tmp = []; 
-   for r=1:length(rseed_list)
-      rseed = rseed_list(r);
-      filename = sprintf('%s/ova_%s_sd%d_nu%0.4f.mat', folder, dataset, rseed, nu_list(nu_idx));
-      A = load(filename); 
-      tmp = [tmp, A.aer(end)];
-   end
-   err = [err, mean(tmp)];
-end
-loglog(nu_list, err); 
-legend_list = [legend_list, 'rational ova'];
-
-% original rational ova
-err = [];
-for nu_idx = 1:length(nu_list)
-   tmp = []; 
-   for r=1:length(rseed_list)
-   
-      rseed = rseed_list(r);
-      filename = sprintf('%s/ovao_%s_sd%d_nu%0.4f.mat', folder, dataset, rseed, nu_list(nu_idx));
-      A = load(filename); 
-      tmp = [tmp, A.aer(end)];
-   end
-   err = [err, mean(tmp)];
-end
-loglog(nu_list, err); 
-legend_list = [legend_list, 'rational ova (original)'];
-
-% banditron
-err = [];
-for ga_idx=1:length(ga_list)
-   tmp = []; 
-   for r=1:length(rseed_list)
-      rseed = rseed_list(r);
-      filename = sprintf('%s/ban_%s_sd%d_ga%0.4f.mat', folder, dataset, rseed, ga_list(ga_idx));
-      A = load(filename); 
-      tmp = [tmp, A.aer(end)];
-   end
-   err = [err, mean(tmp)];
[…]

### 2019-01-23 src/octave/generate_syn.m

@@ -1,31 +1,0 @@
-% generate synthetic data
-
-clear all
-v=zeros(120,9);
-for i=1:9
-    v(:,i)=(rand(120,1)<1/4);
-end
-
-
-s=10^4;
-p=zeros(400,s);
-t=zeros(1,s);
-for i=1:s
-    idx=randperm(9);
-    tmp=zeros(400,1);
-    tmp(1:120,1)=v(:,idx(1));
-    t(i)=idx(1);
-    idx_on=find(tmp==1);
-    shuffle_idx=randperm(numel(idx_on));
-    tmp(idx_on(shuffle_idx(1:5)))=0;
-    shuffle_idx=randperm(280);
-    tmp(120+shuffle_idx(1:20))=1;
-    p(:,i)=tmp;
-end
-p=sparse(p);
-
-idx=randperm(numel(t));
-n=s/100*5;
-t_noise=t;
-
-t_noise(idx(1:n))=randi(9,n,1);

### 2019-01-23 src/octave/generate_weak_separable.m

@@ -1,21 +1,0 @@
-function [W, X, Y] = generate_weak_separable(n_sample, dim, n_cla, margin)
-X = zeros(dim,n_sample);
-Y = zeros(n_sample,1);
-W = 2*rand(dim,n_cla)-1;   %dim=2, #class=5
-for i=1:n_sample
-    while(1)
-       x_i = 2*rand(dim,1)-1; 
-       x_i = x_i/sum(x_i.^2);
-       [score, clas] = sort(W'*x_i, 'descend');
-       cla_i = clas(1); 
-       if score(1)-score(2)>margin
-           break
-       end
-       % [tmp, cla_i] = max(W'*x_i);
-    end
-    X(:,i) = x_i/norm(x_i); 
-    Y(i) = cla_i;
-end
-
-
-end

### 2019-01-23 src/octave/generate_weak_separable2.m

@@ -1,30 +1,0 @@
-function [W, X, Y] = generate_weak_separable2(n_sample, dim, n_cla, margin)
-assert(dim >= n_cla); 
-randdim = randsample(dim, n_cla); 
-X = zeros(dim,n_sample);
-Y = zeros(n_sample,1);
-W = zeros(dim, n_cla); 
-for i=1:n_cla
-   W(randdim(i),i) = 1;
-end
-for i=1:n_sample
-    x_i = 2*rand(dim,1)-1;
-    x_i = x_i/norm(x_i);
-    [score, clas] = sort(W'*x_i, 'descend');
-    cla_i = clas(1); 
-    if score(1)-score(2) < margin
-       x_i(randdim(cla_i)) = x_i(randdim(cla_i)) + margin;
-    end
-    x_i = x_i/norm(x_i);
-    
-    [score, clas] = sort(W'*x_i, 'descend');
-    cla_i = clas(1); 
-    if score(1)-score(2) < margin
-       x_i(randdim(cla_i)) = x_i(randdim(cla_i)) + margin;
-    end
-    x_i = x_i/norm(x_i);
-    
-    X(:,i) = x_i; 
-    Y(i) = cla_i;
-end
-end

### 2019-01-23 src/octave/newtron_diag_train.m

@@ -1,86 +1,0 @@
-function model = newtron_diag_train(X,Y,model)
-%UNTITLED Summary of this function goes here
-%   Detailed explanation goes here
-
-n = length(Y);   % number of training samples
-
-if isfield(model,'gamma')==0
-    model.gamma = .01;
-end
-
-if isfield(model,'alpha')==0
-    model.alpha = 10;
-end
-
-if isfield(model,'D')==0
-    model.D = 1;
-end
-
-if isfield(model,'beta')==0
-    model.beta = 0.01;
-end
-
-if isfield(model,'iter')==0
-    model.iter = 0;
-    model.w = zeros(model.n_cla,size(X,1));
-    model.errTot = 0;
-    model.numSV = zeros(numel(Y),1);
-    model.aer = zeros(numel(Y),1);
-    model.pred = zeros(model.n_cla,numel(Y));
-    
-    model.diagA=ones(size(X,1)*model.n_cla,1)/model.D;
-    model.b = zeros(model.n_cla*size(X,1),1);
-end
-
-for i=1:n
-    model.iter = model.iter+1;
-        
-    val_f = exp(model.alpha*model.w*X(:,i));
-    val_f=val_f/sum(val_f);
-    
-    Yi = Y(i);
-    
-    Prob = (1-model.gamma)*val_f+model.gamma/model.n_cla;
-    explore=(rand()<model.gamma);
-    if explore==1
-        y_tilde=randi(model.n_cla);
-    else
-        random_vect = (rand<cumsum(val_f));
-        [dummy,y_tilde] = max(random_vect);
-    end
-    model.errTot = model.errTot+(y_tilde~=Yi);
-    model.aer(model.iter) = model.errTot/model.iter;
-    model.pred(:,model.iter) = val_f;
-    
-    if y_tilde==Yi
-        f1=(1-val_f(y_tilde))/(Prob(y_tilde)*model.n_cla);
-        f1Xi=X(:,i)'*f1;
-        tmp = repmat(f1Xi,[model.n_cla,1]); 
-        tmp(y_tilde,:) = -f1Xi;
-        kbeta=Prob(y_tilde)*model.beta;
-    else
-        f1=val_f(y_tilde)/(Prob(y_tilde)*model.n_cla);
-        f1Xi=f1*X(:,i)';
-        tmp = repmat(-f1Xi,[model.n_cla,1]); 
-        tmp(y_tilde,:) = f1Xi;
[…]

### 2019-01-23 src/octave/ova_k_perceptron_train.m

@@ -1,93 +1,0 @@
-function model = ova_k_perceptron_train(X,Y,model)
-n = length(Y);   % number of training samples
-if isfield(model,'n_cla')==0
-    model.n_cla=max(Y);
-end
-
-%%%%%% the following implementation are similar to k_perceptron_train.m %%%%%%
-if isfield(model,'iter')==0
-    model.iter=0;
-    model.errTot=0;
-    model.aer=zeros(numel(Y),1);
-    model.pred=zeros(model.n_cla,numel(Y));
-    model.beta_list= cell(model.n_cla, 1);
-    %model.numSV_list=cell(model.n_cla, 1);
-    model.SV_list=cell(model.n_cla, 1); 
-    model.dim = size(X,1);
-end
-
-for j=1:model.n_cla
-    model.beta_list{j} = [];
-    model.SV_list{j} = zeros(model.dim,0);
-end
-%model.S_list
-for i=1:n
-    model.iter = model.iter+1;
-    val_f = zeros(1, model.n_cla); 
-    for j=1:model.n_cla
-        if numel(model.SV_list{j})>0
-           subK_f = feval(model.ker, model.SV_list{j}, X(:,i), model.kerparam); 
-           val_f(j) = model.beta_list{j} * subK_f; 
-        else
-           val_f(j) = 0;
-        end
-    end
-    
-    % if any of val_f is positive, pick the largest one (what if randomly pick one?)
-    % else uniformly randomly pick one
-    [maxval_f, maxidx] = max(val_f);
-    if maxval_f >= 0
-        Yhat = maxidx; 
-    else 
-        Yhat = unidrnd(model.n_cla);
-    end
-    
-    model.errTot = model.errTot + (Yhat~=Y(i));
-    model.aer(model.iter)=model.errTot/model.iter;
-    model.pred(:,model.iter)=val_f;
-    
-    if Yhat==Y(i)   % guess correctly
-        for j=1:model.n_cla
-            if(j~= Yhat && val_f(j)>=0)    % can possibly use val_f(j)>-margin
-                if size(model.SV_list{j},2) >= model.maxSV
-                    mn_idx = ceil(model.maxSV*rand); 
-                elseif numel(model.SV_list{j})==0
-                    mn_idx = 1; 
-                else
-                    mn_idx = size(model.SV_list{j},2)+1;
-                end
-                model.beta_list{j}(mn_idx) = -1; 
[…]

### 2019-01-23 src/octave/run_experiments.m

@@ -1,55 +1,0 @@
-clear all;
-close all;
-
-%load syn_data_matlab
-load results_banditron_clean
-
-%[t, p] = libsvmread('/home/bremen/Projects/datasets/covtype.scale');
-%t=t';
-%p=p';
-
-model_bak=model_init();
-model_bak.n_cla=numel(unique(t));
-
-%[p,t_noise]=shuffledata(p,t_noise);
-%p(end+1,:)=1;
-
-%model_perc=perceptron_multi_train(p,t,model_bak);
-
-%noise=2.^(-16:-1);
-err=zeros(numel(noise),10);
-err_newtron=zeros(numel(noise),10);
-for j=1:10
-    for i=1:numel(noise)
-      %model_bak.gamma=noise(i);
-      %model_banditron=banditron_multi_train(p,t,model_bak);
-      %err(i,j)=model_banditron.aer(end);
-      
-      model_bak.gamma=noise(i);
-      model_newtron=newtron_diag_train(p,t,model_bak);
-      err_newtron(i,j)=model_newtron.aer(end);      
-    end
-end
-
-err_soba_diag=zeros(numel(noise),10);
-for j=1:10
-    for i=1:numel(noise)
-      model_bak.gamma=noise(i);
-      model_soba_diag=soba_diag_multi_train(p,t,model_bak);
-      err_soba_diag(i,j)=model_soba_diag.aer(end);      
-    end
-end
-
-
-%for i=1:numel(noise)
-%  model_bak.gamma=noise(i);
-%model_soba=soba_multi_train(p,t,model_bak);
-%  err_soba(i)=model_soba.aer(end);
-%end
-
-%save results_baselines_noise
-
-%plot(noise, err);
-%hold on;
-%plot(noise, model_perc.aer(end),'k');
-%plot(noise, model_soba.aer(end),'r');

### 2019-01-23 src/octave/soba_multi_train.m

@@ -1,138 +1,0 @@
-function model = soba_multi_train(X,Y,model)
-% SOBA_MULTI_TRAIN Banditron algorithm
-%
-%    MODEL = SOBA_MULTI_TRAIN(X,Y,MODEL) trains a multiclass
-%    classifier using SOBA.
-%
-%    Additional parameters:
-%    - model.n_cla is the number of classes.
-%    - model.gamma is the parameter that controls the trade-off between
-%      exploration and exploitation.
-%      Default value is 0.01.
-%
-%   References:
-%     - Kakade, S. M., Shalev-Shwartz, S., & Tewari, A. (2008).
-%       Efficient bandit algorithms for online multiclass prediction.
-%       Proceedings of the 25th International Conference on Machine
-%       Learning (pp. 440–447).
-%
-%    This file is part of the DOGMA library for MATLAB.
-%    Copyright (C) 2009-2012, Francesco Orabona
-%    If you use this software in a paper you have to cite
-%     - Francesco Orabona. (2009)
-%       DOGMA: a MATLAB toolbox for Online Learning
-%       Software available at http://dogma.sourceforge.net
-%
-%    This program is free software: you can redistribute it and/or modify
-%    it under the terms of the GNU General Public License as published by
-%    the Free Software Foundation, either version 3 of the License, or
-%    (at your option) any later version.
-%
-%    This program is distributed in the hope that it will be useful,
-%    but WITHOUT ANY WARRANTY; without even the implied warranty of
-%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-%    GNU General Public License for more details.
-%
-%    You should have received a copy of the GNU General Public License
-%    along with this program.  If not, see <http://www.gnu.org/licenses/>.
-%
-%    Contact the author: francesco [at] orabona.com
-
-n = length(Y);   % number of training samples
-rand('state',0);
-
-if isfield(model,'gamma')==0
-    model.gamma = .01;
-end
-
-if isfield(model,'a')==0
[…]

### 2019-01-23 src/octave/svm2mat.m

@@ -1,29 +1,0 @@
-function y=svm2mat(s)
-% Usage: y=svm2mat ('filename')
-clc
-fid = fopen(s);
-i=1;
-while ~feof(fid) % not end of the file 
-       s = fgetl(fid); % get a line 
-       s1=[];  j=1;
-       while (j<=length(s))
-             while( s(j)~=' ')    
-                   s1=[s1 s(j)];
-                   j=j+1;   
-             end  
-             j=j+1;   
-             s1=[s1 ' '];              
-             while ( (j<length(s)) && (s(j)~=':') )   
-                    j=j+1;   
-             end             
-             j=j+1;   
-       end
-        s2=str2num(s1) ;
-        if (i==1)
-            yy=zeros(1,length(s2));
-        end
-        yy=[yy ; s2];
-        i=i+1;      
-end
-yy(1,:)=[];
-y=yy;

### 2019-01-23 ICML-submission/src/k_banditron_multi_train.m
delete one redundant src file

@@ -1,120 +1,0 @@
-function model = k_banditron_multi_train(X,Y,model)
-% BANDITRON_MULTI_TRAIN Banditron algorithm
-%
-%    MODEL = BANDITRON_MULTI_TRAIN(X,Y,MODEL) trains a multiclass
-%    classifier according to the Banditron algorithm.
-%
-%    Additional parameters:
-%    - model.n_cla is the number of classes.
-%    - model.gamma is the parameter that controls the trade-off between
-%      exploration and exploitation.
-%      Default value is 0.01.
-%
-%   References:
-%     - Kakade, S. M., Shalev-Shwartz, S., & Tewari, A. (2008).
-%       Efficient bandit algorithms for online multiclass prediction.
-%       Proceedings of the 25th International Conference on Machine
-%       Learning (pp. 440??47).
-%
-%    This file is part of the DOGMA library for MATLAB.
-%    Copyright (C) 2009-2012, Francesco Orabona
-%    If you use this software in a paper you have to cite
-%     - Francesco Orabona. (2009)
-%       DOGMA: a MATLAB toolbox for Online Learning
-%       Software available at http://dogma.sourceforge.net
-%
-%    This program is free software: you can redistribute it and/or modify
-%    it under the terms of the GNU General Public License as published by
-%    the Free Software Foundation, either version 3 of the License, or
-%    (at your option) any later version.
-%
-%    This program is distributed in the hope that it will be useful,
-%    but WITHOUT ANY WARRANTY; without even the implied warranty of
-%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-%    GNU General Public License for more details.
-%
-%    You should have received a copy of the GNU General Public License
-%    along with this program.  If not, see <http://www.gnu.org/licenses/>.
-%
-%    Contact the author: francesco [at] orabona.com
-
-n = length(Y);   % number of training samples
-
-if isfield(model,'iter')==0
-    model.iter = 0;
-    %model.w = zeros(size(X,1),model.n_cla);
-    model.beta_list= cell(model.n_cla, 1); 
-    model.SV_list=cell(model.n_cla, 1); 
[…]

### 2019-01-23 ICML-submission/related-work.tex
modified related work

@@
 In the weakly linearly separable setting, however, 
-all these algorithms guarantee a mistake 
+these algorithms can guarantee a mistake 
 bound of ${O}(\sqrt{T})$ at best.
@@
 
-There is a large body of literature on contextual bandit
-learning~\citep{Auer-2003, Langford-Zhang-2008}. In this problem, the learner is
-given a policy class $\Pi$, and at each timestep $t$, an example $x_t$ is shown,
-with an associated cost vector $c_t$ hidden. The learner then takes an action
-$\widehat{y}_t$, and observes the incurred cost $c_t(\widehat{y}_t)$. The goal
-of the learner is to minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) -
-\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$. The bandit multiclass learning
-problem can be seen as a special case, where the cost $c_t(i)$ is the
-classification error $\indicator{i \neq y_t}$, and the policy class $\Pi$ is the
-set of linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times
-d}}$. A series of papers in the contextual bandits learning literature assume
-access to a policy optimization oracle that returns a policy in $\Pi$ that
-minimizes its empirical cost on any set of cost-sensitive examples, and
-construct algorithms that call the oracle a polynomial number of times%
-~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
+The problem considered here is a special case of the
+contextual bandit problem~\citep{Auer-2003, Langford-Zhang-2008}. 
+In this general problem, there is a hidden cost vector $c_t$ associated with every prediction in $\{1,\ldots,K\}$ in round $t$.
+Upon receiving $x_t$ and predicting $\widehat{y}_t \in \{1,\ldots,K\}$, the learner gets to observe the incurred cost $c_t(\widehat{y}_t)$.
+The goal of the learning is to minimize its regret with respect to the best predictor in some predefined policy class $\Pi$, given by $\sum_{t=1}^T c_t(\widehat{y}_t) -
+\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
+Bandit multiclass learning is a special case
+where the cost $c_t(i)$ is the classification error $\indicator{i \neq y_t}$ and 
+the policy class is the set of linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$.
+There has been significant progress on the general contextual bandit problem, 
+assuming access to an optimization oracle that returns a policy in $\Pi$ with the smallest total cost on any given set of cost-sensitive examples~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
 Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
 Syrgkanis-Krishnamurthy-Schapire-2016,
-Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. However, these algorithms are not
-truly computationally efficient in our setting, as it is NP-hard in general to
-find a linear classifier that minimizes the empirical cost over a set of
-examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.
+Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
+While solving a more general problem that does not make assumptions on the structure of the cost vector $c_t$ or the policy class, these results assume that $x_t$s or $(x_t,c_t)$s are generated i.i.d., in addition to assuming oracle access to search through $\Pi$, neither of which we assume here.
+
+%However, these algorithms are not
+%truly computationally efficient in our setting, as it is NP-hard in general to
+%find a linear classifier that minimizes the empirical cost over a set of
+%examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.
 

### 2019-01-23 ICML-submission/related-work.tex
tweaked related work

@@
 In the weakly linearly separable setting, however, 
-these algorithms can guarantee a mistake 
+these algorithms can only guarantee a mistake 
 bound of ${O}(\sqrt{T})$ at best.
@@
 contextual bandit problem~\citep{Auer-2003, Langford-Zhang-2008}. 
-In this general problem, there is a hidden cost vector $c_t$ associated with every prediction in $\{1,\ldots,K\}$ in round $t$.
+In this general problem, there is a hidden cost vector $c_t$ associated with every prediction in round $t$.
 Upon receiving $x_t$ and predicting $\widehat{y}_t \in \{1,\ldots,K\}$, the learner gets to observe the incurred cost $c_t(\widehat{y}_t)$.
-The goal of the learning is to minimize its regret with respect to the best predictor in some predefined policy class $\Pi$, given by $\sum_{t=1}^T c_t(\widehat{y}_t) -
+The goal of the learner is to minimize its regret with respect to the best predictor in some predefined policy class $\Pi$, given by $\sum_{t=1}^T c_t(\widehat{y}_t) -
 \min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
@@
 the policy class is the set of linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$.
-There has been significant progress on the general contextual bandit problem, 
+There has been significant progress on the general contextual bandit problem
 assuming access to an optimization oracle that returns a policy in $\Pi$ with the smallest total cost on any given set of cost-sensitive examples~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
@@
 Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
-While solving a more general problem that does not make assumptions on the structure of the cost vector $c_t$ or the policy class, these results assume that $x_t$s or $(x_t,c_t)$s are generated i.i.d., in addition to assuming oracle access to search through $\Pi$, neither of which we assume here.
+While solving a more general problem without making assumptions on the structure of the cost vector $c_t$ or the policy class, these results assume that $x_t$ vectors or $(x_t,c_t)$ pairs are generated i.i.d.
+and that such an oracle abstracting efficient search through $\Pi$ is available---neither of which we assume here.
 

### 2019-01-23 ICML-submission/src/other-algorithms/k_banditron_multi_train.m
.

@@ -1,0 +1,124 @@
+function model = k_banditron_multi_train(X,Y,model)
+% BANDITRON_MULTI_TRAIN Banditron algorithm
+%
+%    MODEL = BANDITRON_MULTI_TRAIN(X,Y,MODEL) trains a multiclass
+%    classifier according to the Banditron algorithm.
+%
+%    Additional parameters:
+%    - model.n_cla is the number of classes.
+%    - model.gamma is the parameter that controls the trade-off between
+%      exploration and exploitation.
+%      Default value is 0.01.
+%
+%   References:
+%     - Kakade, S. M., Shalev-Shwartz, S., & Tewari, A. (2008).
+%       Efficient bandit algorithms for online multiclass prediction.
+%       Proceedings of the 25th International Conference on Machine
+%       Learning (pp. 440??47).
+%
+%    This file is part of the DOGMA library for MATLAB.
+%    Copyright (C) 2009-2012, Francesco Orabona
+%    If you use this software in a paper you have to cite
+%     - Francesco Orabona. (2009)
+%       DOGMA: a MATLAB toolbox for Online Learning
+%       Software available at http://dogma.sourceforge.net
+%
+%    This program is free software: you can redistribute it and/or modify
+%    it under the terms of the GNU General Public License as published by
+%    the Free Software Foundation, either version 3 of the License, or
+%    (at your option) any later version.
+%
+%    This program is distributed in the hope that it will be useful,
+%    but WITHOUT ANY WARRANTY; without even the implied warranty of
+%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%    GNU General Public License for more details.
+%
+%    You should have received a copy of the GNU General Public License
+%    along with this program.  If not, see <http://www.gnu.org/licenses/>.
+%
+%    Contact the author: francesco [at] orabona.com
+
+n = length(Y);   % number of training samples
+
+if isfield(model,'iter')==0
+    model.iter = 0;
+    %model.w = zeros(size(X,1),model.n_cla);
+    model.beta_list= cell(model.n_cla, 1); 
[…]

### 2019-01-23 ICML-submission/src/run_experiments.m

@@ -1,7 +1,7 @@
 clear all; 
 close all;
 rng(99990);
-N = 5000; 
+N = 50000; 
 K = 3;    % now only support K=3 
 gamma = 0.05;
 W = [1,0; cos(pi*30/180), sin(pi*30/180); cos(-pi*30/180), sin(-pi*30/180)];
@@ -25,7 +25,8 @@ for i=1:N
        else
            angle = (330*rand()+15)*pi/180;
        end
-       len = 1;  % change to random functions when 
+       len = 1;  % this is for strongly separable
+                 % change to random functions when 
                  % generating weakly separable 
        X(i,:) = [len*cos(angle), len*sin(angle)];
        [values, idxs] = sort(W*X(i,:)', 'descend');
@@ -39,7 +40,7 @@ for i=1:N
     end
 end
 
-X_ext = normr(X_ext);
+X_ext = X_ext/sqrt(2);
 
 %%%%% scatter weak samples %%%%%
 plot_idx = 1:100:N;
@@ -63,7 +64,6 @@ model_linova = ova_perceptron_train(X_ext', Y, model_linova);
 errTot = model_linova.errTot;
 figure(300); plot(plot_idx, errTot(plot_idx), '.-'); hold on;
 legend_list = [legend_list, 'Our Algorithm (linear)'];
-figure; hold on;
 
 % 2. Banditron
 for g = [0.1, 0.05, 0.005, 0.0005]

### 2019-01-23 ICML-submission/src/k_banditron_multi_train.m
add codes for more algorithms

@@ -45,7 +45,7 @@ if isfield(model,'iter')==0
     %model.w = zeros(size(X,1),model.n_cla);
     model.beta_list= cell(model.n_cla, 1); 
     model.SV_list=cell(model.n_cla, 1); 
-    model.errTot = 0;
+    model.errTot = zeros(numel(Y),1);
     model.numSV = zeros(numel(Y),1);
     model.aer = zeros(numel(Y),1);
     model.pred = zeros(model.n_cla,numel(Y));
@@ -85,8 +85,12 @@ for i=1:n
     random_vect = (rand<cumsum(Prob));
     [dummy,y_tilde] = max(random_vect);
     
-    model.errTot = model.errTot+(y_tilde~=Yi);
-    model.aer(model.iter) = model.errTot/model.iter;
+    if model.iter>1
+        model.errTot(model.iter) = model.errTot(model.iter-1)+(y_tilde~=Yi);
+    else
+        model.errTot(model.iter) + (y_tilde~=Yi);
+    end
+    model.aer(model.iter) = model.errTot(model.iter)/model.iter;
     model.pred(:,model.iter) = val_f;
 
     if size(model.SV_list{y_hat},2) >= model.maxSV

### 2019-01-23 ICML-submission/src/newtron_diag_train.m

@@ -23,7 +23,7 @@ end
 if isfield(model,'iter')==0
     model.iter = 0;
     model.w = zeros(model.n_cla,size(X,1));
-    model.errTot = 0;
+    model.errTot=zeros(numel(Y,1));
     model.numSV = zeros(numel(Y),1);
     model.aer = zeros(numel(Y),1);
     model.pred = zeros(model.n_cla,numel(Y));
@@ -48,8 +48,12 @@ for i=1:n
         random_vect = (rand<cumsum(val_f));
         [dummy,y_tilde] = max(random_vect);
     end
-    model.errTot = model.errTot+(y_tilde~=Yi);
-    model.aer(model.iter) = model.errTot/model.iter;
+    if model.iter>1
+        model.errTot(model.iter) = model.errTot(model.iter-1)+(y_tilde~=Yi);
+    else
+        model.errTot(model.iter) + (y_tilde~=Yi);
+    end
+    model.aer(model.iter) = model.errTot(model.iter)/model.iter;
     model.pred(:,model.iter) = val_f;
     
     if y_tilde==Yi

### 2019-01-23 ICML-submission/src/perceptron_multi_train.m

@@ -41,7 +41,7 @@ if isfield(model,'iter')==0
     model.iter=0;
     model.w=zeros(model.n_cla,size(X,1));
     model.w2=zeros(model.n_cla,size(X,1));
-    model.errTot=0;
+    model.errTot=zeros(numel(Y,1));
     model.numSV=zeros(numel(Y),1);
     model.aer=zeros(numel(Y),1);
     model.pred=zeros(model.n_cla,numel(Y));
@@ -57,8 +57,12 @@ for i=1:n
     tmp=val_f; tmp(Yi)=-inf;
     [mx_val,idx_mx_val]=max(tmp);
 
-    model.errTot=model.errTot+(val_f(Yi)<=mx_val);
-    model.aer(model.iter)=model.errTot/model.iter;
+    if model.iter>1
+        model.errTot(model.iter) = model.errTot(model.iter-1)+(val_f(Yi)<=mx_val);
+    else
+        model.errTot(model.iter) + (val_f(Yi)<=mx_val);
+    end
+    model.aer(model.iter) = model.errTot(model.iter)/model.iter;
     model.pred(:,model.iter)=val_f;
     
     if val_f(Yi)<=mx_val

### 2019-01-23 ICML-submission/src/run_experiments.m

@@ -26,7 +26,7 @@ for i=1:N
            angle = (330*rand()+15)*pi/180;
        end
        len = 1;  % this is for strongly separable
-                 % change to random functions when 
+                 % change to rand() when 
                  % generating weakly separable 
        X(i,:) = [len*cos(angle), len*sin(angle)];
        [values, idxs] = sort(W*X(i,:)', 'descend');
@@ -42,7 +42,7 @@ end
 
 X_ext = X_ext/sqrt(2);
 
-%%%%% scatter weak samples %%%%%
+%%%%% scatter samples %%%%%
 plot_idx = 1:100:N;
 Nplot = length(plot_idx);
 color_param = zeros(Nplot,3);
@@ -52,13 +52,14 @@ color_param(:,3) = (Y(plot_idx)==3);
 scatter(X(plot_idx,1), X(plot_idx,2), 30, color_param); 
 
 
-%%%%%%%%% runs %%%%%%%%%
+%%%%%%%%% runs for different algorithms %%%%%%%%%
 % (for code simplicity, we only show one run here)
 see = randi(100000);
 rng(see);
 legend_list = {};
 
 % 1. our algorithm with linear kernel
+fprintf('--Our Algorithm (linear)--\n')
 model_linova = model_init();
 model_linova = ova_perceptron_train(X_ext', Y, model_linova);
 errTot = model_linova.errTot;
@@ -66,6 +67,7 @@ figure(300); plot(plot_idx, errTot(plot_idx), '.-'); hold on;
 legend_list = [legend_list, 'Our Algorithm (linear)'];
 
 % 2. Banditron
+fprintf('--Banditron--\n')
 for g = [0.1, 0.05, 0.005, 0.0005]
    model_ban = model_init();
    model_ban.gamma = g;
@@ -77,6 +79,7 @@ for g = [0.1, 0.05, 0.005, 0.0005]
 end
  
 % 3. our algorithm with rational kernel
+fprintf('--Our Algorithm (rational)--\n')
 hp.nu = 0.5; 
 hp.type = 'rational';
 model_ova = model_init(@compute_kernel,hp);
@@ -86,5 +89,52 @@ model_ova = ova_k_perceptron_train(X_ext',Y, model_ova);
 errTot = model_ova.errTot;
 figure(300); plot(plot_idx, errTot(plot_idx), '--');
 legend_list = [legend_list, 'Our Algorithm (rational kernel)'];
+
[…]

### 2019-01-23 ICML-submission/src/soba_diag_multi_train.m

@@ -14,7 +14,7 @@ function model = soba_diag_multi_train(X,Y,model)
 %     - Kakade, S. M., Shalev-Shwartz, S., & Tewari, A. (2008).
 %       Efficient bandit algorithms for online multiclass prediction.
 %       Proceedings of the 25th International Conference on Machine
-%       Learning (pp. 440–447).
+%       Learning (pp. 440??47).
 %
 %    This file is part of the DOGMA library for MATLAB.
 %    Copyright (C) 2009-2012, Francesco Orabona
@@ -54,7 +54,7 @@ end
 if isfield(model,'iter')==0
     model.iter = 0;
     model.w = zeros(model.n_cla,size(X,1));
-    model.errTot = 0;
+    model.errTot=zeros(numel(Y,1));
     model.numSV = zeros(numel(Y),1);
     model.aer = zeros(numel(Y),1);
     model.pred = zeros(model.n_cla,numel(Y));
@@ -86,8 +86,12 @@ for i=1:n
     random_vect = (rand<cumsum(Prob));
     [dummy,y_tilde] = max(random_vect);
     
-    model.errTot = model.errTot+(y_tilde~=Yi);
-    model.aer(model.iter) = model.errTot/model.iter;
+    if model.iter>1
+        model.errTot(model.iter) = model.errTot(model.iter-1)+(y_tilde~=Yi);
+    else
+        model.errTot(model.iter) + (y_tilde~=Yi);
+    end
+    model.aer(model.iter) = model.errTot(model.iter)/model.iter;
     model.pred(:,model.iter) = val_f;
 
     if y_tilde==Yi

### 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Clean-up Appendix I

@@
 weakly linearly separable with margin $\gamma$, we show that any ignorant
-algorithm must make $\Theta\left(\min\{\sqrt{T},
-(1/\gamma)^{\Theta(d)}\}\right)$ mistakes in the worst case. In other words, an
-algorithm that achieves a better mistake bound cannot ignore examples on which
-it makes a mistake and it must make a meaningful update on such examples.
+algorithm must make at least $\Omega \left( \left(\frac{1}{160 \gamma}\right)^{(d-2)/4} \right)$
+mistakes in the worst case. In other words, an algorithm that achieves a better
+mistake bound cannot ignore examples on which it makes a mistake and it must
+make a meaningful update on such examples.
 
-The ignorant algorithm is formally defined as follows.
-\begin{definition}
-\label{definition:ignorant-algorithm}
+To formally define ignorant algorithms, we define the conditional distribution
+from which an algorithm draws its predictions. Formally, given an algorithm
+$\calA$ and an adversarial strategy, we define
+\begin{multline*}
+p_t(y|x) = \\
+\Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] \; .
+\end{multline*}
+In other words, in any round $t$, conditioned on the past $t-1$ rounds, the
+algorithm $\calA$ chooses $y_t$ from probability distribution $p_t(\cdot|x_t)$.
+Formally, $p_t$ is a function $p:\{1,2,\dots,K\} \times \R^d \to [0,1]$
+such that $\sum_{y=1}^K p_t(y|x) = 1$ for any $x \in \R^d$.
+
+\begin{definition}[Ignorant algorithm]
 An algorithm $\calA$ for \textsc{Online Multiclass Linear Classification with
-Bandit Feedback} is called \emph{ignorant} if for all $t \in \{1,2,\dots,T\}$,
-$\widehat y_t$ is drawn from some distribution that is jointly determined by
-\begin{enumerate}
-\item $x_t$,
-\item $H_t \triangleq \left( (x_{\tau_1}, y_{\tau_1}), (x_{\tau_2}, y_{\tau_2}), \ldots, (x_{\tau_{n_t}}, y_{\tau_{n_t}}) \right)$,
-where $1 \le \tau_1 < \dots < \tau_{n_t} < t$, and $\{\tau_1, \ldots, \tau_{n_t}\}$
-are the rounds in which the algorithm predicts correctly (that is,
-$\{\tau_1, \dots, \tau_{n_t}\} = \{1 \le \tau < t ~:~ \widehat y_\tau=y_\tau\}$).
-\end{enumerate}
-We use $p_t(\cdot|x_t)\in \{p\in \R_+^K ~:~ p^\top\mathbf{1}=1\}$ to denote
-the distribution $\widehat y_t$ is drawn from. Note that we let the current
-feature vector $x_t$ be an argument to $p_t$ to incorporate its dependency on
-$x_t$. Therefore, for an ignorant algorithm, the function $p_t(\cdot|\cdot)$ is
-only determined by $H_t$.
+Bandit Feedback} is called \emph{ignorant} if for every $t=1,2,\dots,T$,
+$p_t$ is determined solely by the sequence
+$(x_{a_1}, y_{a_1}), (x_{a_2}, y_{a_2}), \dots, (x_{a_n}, y_{a_n})$
+in the rounds $1 \le a_1 < a_2 < \dots < a_n < t$ in which
+the algorithm makes a correct prediction.
 \end{definition}
 
-An ignorant algorithm does not learn from mistakes in the following sense.
-Suppose that an ignorant algorithm predicts incorrectly at time $t$. Then at
-time $t+1$, if it is given the same feature vector $x_{t+1}=x_t$, it will
-predict the label with the same distribution
-$p_{t+1}(\cdot|x_{t+1})=p_{t+1}(\cdot|x_t)=p_t(\cdot|x_t)$.
+An equivalent definition of an ignorant algorithm is that the memory state of
+the algorithm does not change after it makes a mistake. Equivalently,
+the memory state of an ignorant algorithm is completely determined
+by the sequence of labeled examples on which it made correct prediction.
 
-% Below we describe
-%the difficulty of learning from mistakes using a class of natural approaches
-%under the weak separability assumption. Consider an approach similar to OBAMA:
-%in each round $t$, we create a \textit{convex} loss function $\widehat \ell_t:
-%\R^{K\times d} \to \R$ that gives a loss value $\widehat
-%\ell_t(W)$ to all linear models $W \in \R^{K\times d}$ ($W=[w_1 \dots
-%w_K]^\top$ for $w_1, w_2, \dots, w_K$ defined in
-%Definition~\ref{definition:linear-separability}). The requirement for
-%$\widehat{\ell}_t$ to be convex is due to computational efficiency. To let
-%$\widehat{\ell}_t$ reflect the loss, if $\widehat y_t \neq y_t$, we want to
-%assign larger loss values $\widehat{\ell_t}(W)$ to the inconsistent models
-%$\mathcal{W}=\{W: \ip{w_{\widehat y_t}}{x_t} \ge \ip{w_i}{x_t}, \forall
-%i\in[K]\}$, while for other $W$'s, we want $\widehat{\ell_t}(W)$ to be smaller.
-%The following fact can be verified when $K\ge 3$, which suggests there is no
-%way to define the loss $\widehat \ell_t$ that satisfies the above properties
-%constraints: there exists $W_1, W_2, W_3$, where $W_2$ is in the line segment
-%between $W_1$ and $W_3$, such that $W_2\in \mathcal{W}$, while $W_1, W_3 \notin
-%\mathcal{W}$. On one hand, by convexity, we should have
-%$\widehat{\ell}_t(W_2)\le \max\{\widehat{\ell}_t(W_1),
-%\widehat{\ell}_t(W_3)\}$; on the other hand, to penalize $\mathcal{W}$, we
-%should have $\widehat{\ell}_t(W_2) > \widehat{\ell}_t(W_1)$ and
-%$\widehat{\ell}_t(W_2) > \widehat{\ell}_t(W_3)$. Clearly, these two requirements
-%contradict each other.
+To explain the definition, consider an ignorant algorithm $\calA$. Suppose that
+on a sequence of examples $(x_1, y_1), (x_2, y_2), \dots, (x_{t-1}, y_{t-1})$
+generated by some adversary the algorthm $\calA$ makes correct predictions in
+rounds $a_1, a_2, \dots, a_n$ where $1 \le a_1 < a_2 < \dots < a_n < t$ and
+errors on rounds $\{1,2,\dots,t-1\} \setminus \{a_1, a_2, \dots, a_n\}$. Suppose
+that on another sequence of examples $(x_1', y_1'), (x_2', y_2'), \dots,
+(x_{s-1}', y_{s-1}')$ generated by another adversary the algorithm $\calA$ makes
+correct predictions in rounds $b_1, b_2, \dots, b_n$ where $1 \le b_1 < b_2 <
+\dots < b_n < s$ and errors on rounds $\{1,2,\dots,s-1\} \setminus \{b_1, b_2,
+\dots, b_n\}$. Futhermore, suppose
+\begin{align*}
+(x_{a_1}, y_{a_1}) &= (x'_{b_1}, y'_{b_1}) \; , \\
+(x_{a_2}, y_{a_2}) &= (x'_{b_2}, y'_{b_2}) \; , \\
+\vdots \\
+(x_{a_n}, y_{a_n}) &= (x'_{b_2}, y'_{b_n}) \; .
+\end{align*}
+Then, the definition
+\begin{multline*}
+\Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] = \\
+\Pr[y_t' = y ~|~ (x_1', y_1'), (x_2', y_2') \dots, (x_{t-1}', y_{t-1}'), x_t' = x] \; .
+\end{multline*}
+Note that the sequences $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_{t-1},
+y_{t-1})$ and $(x_1', y_1')$, $(x_2', y_2')$, $\dots$, $(x_{s-1}', y_{s-1}')$
+might have different lengths and and $\calA$ might error in different sets of
+rounds. As a special case, if an ignorant algorithm makes a mistake in round $t$
+then $p_{t+1}=p_t$.
 
-The following theorem states the mistake lower bound for ignorant algorithms.
+Our main result is the following lower bound on the expected number of mistakes
+for ignorant algorithms.
 
@@
 \label{theorem:ignorant-lower-bound}
-Suppose $\calA$ is an ignorant algorithm for \textsc{Online Multiclass Linear
-Classification with Bandit Feedback}. There exists an adversary that can
-sequentially choose labeled examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)
-\in \R^d\times \{1,2\}$ so that the examples are $\gamma$-strongly linearly
-separable, $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$, and the expected
+Let $\gamma \in (0,1)$ and let $d$ be a positive integer. Suppose $\calA$ is an
+ignorant algorithm for \textsc{Online Multiclass Linear Classification with
+Bandit Feedback}. There exists $T$ and an adversary that sequentially chooses
+labeled examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \R^d\times
+\{1,2\}$ such that the examples are strongly linearly separable with magin
+$\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$, and the expected
 number of mistakes made by $\calA$ is at least
 $$
-\frac{1}{10}\min\left\{\sqrt{T}, \left(\frac{1}{160\gamma}\right)^{\frac{d-2}{4}} \right\} \; .
+\frac{1}{10} \left(\frac{1}{160\gamma}\right)^{\frac{d-2}{4}} \; .
 $$
@@
 
-\begin{proof}[Proof for Theorem~\ref{theorem:ignorant-lower-bound} (Part I: Mistake lower bound)]
-We consider the strategy for the adversary described in Algorithm~\ref{algorithm:adversary-strategy}.
-\begin{algorithm}[h]
+\begin{proof}
+We consider the strategy for the adversary described in
+Algorithm~\ref{algorithm:adversary-strategy}.
+
+\begin{algorithm}
 \caption{\textsc{Adversary's strategy}}
 \label{algorithm:adversary-strategy}
-\begin{algorithmic}[1]
-{
-\STATE{\textbf{Define} $q_0=\max\left\{\frac{1}{\sqrt{T}}, \frac{1}{\sqrt{N}}\right\}$, where $N$ is defined in Lemma~\ref{lemma:embed_d_gamma}.
-Also, let $v_1, \ldots, v_N$ be those defined in Lemma~\ref{lemma:embed_d_gamma}.}
-\STATE{\textbf{Initialize} $\textsc{phase}= 1$. }
-\FOR{$t=1,\dots,\min\{T,N\}$}
-    \IF{$\textsc{phase}=1$}
-       \IF{$p_t(1|v_t)\ge 1-q_0$}
-          \STATE{$(x_t, y_t)\leftarrow (v_t, 1)$}
-       \ELSE
-          \STATE{$(x_t, y_t)\leftarrow (v_t, 2)$}
-          \STATE $\textsc{phase}\leftarrow 2$
-       \ENDIF
-    \ELSIF{$\textsc{phase}=2$}
-       \STATE $(x_t, y_t)\leftarrow (x_{t-1}, y_{t-1})$.
-    \ENDIF
-\ENDFOR
-\FOR{$t=\min\{T,N\}+1, \ldots, T$}
-    \STATE $(x_t, y_t)\leftarrow (x_{t-1}, y_{t-1})$.
-\ENDFOR
+\textbf{Define} $T=N$ and $v_1, v_2, \dots, v_N$ as in Lemma~\ref{lemma:embed_d_gamma}.\\
+\textbf{Define} $q_0=\frac{1}{\sqrt{T}}$. \\
+\textbf{Initialize} $\textsc{phase}= 1$. \\
+\For{$t=1,2,\dots,T$}{
+    \If{$\textsc{phase}=1$}{
+       \If{$p_t(1|v_t)\ge 1-q_0$}{
+          $(x_t, y_t)\leftarrow (v_t, 1)$
+        }
+       \Else{
+          $(x_t, y_t)\leftarrow (v_t, 2)$ \\
+          $\textsc{phase}\leftarrow 2$
+       }
+    }
+    \Else{
+         $(x_t, y_t)\leftarrow (x_{t-1}, y_{t-1})$
+    }
+}
+\end{algorithm}
 
-}
-\end{algorithmic}
-\end{algorithm}
-For this strategy, we prove the mistake lower bound of any ignorant algorithm.
 Define the indicators
@@
 & \mathbf{E}\left[\sum_{t=1}^{T} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
-& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
-& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}A_t\right] \nonumber \\
-& \qquad + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \indicator{\widehat y_t\neq y_t}B_t\right] \nonumber \\
-& = \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} \mathbf{E}_t\left[\indicator{\widehat y_t\neq y_t}A_t\right]\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right] \nonumber \\
-& \ge \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} q_0 A_t\right] + \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}} B_{t+1}\right],
+& \ge \mathbf{E}\left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}A_t\right] \nonumber \\
+& \qquad + \mathbf{E}\left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}B_t\right] \nonumber \\
+& = \mathbf{E}\left[\sum_{t=1}^T \mathbf{E}_t\left[\indicator{\widehat y_t\neq y_t}A_t\right]\right] + \mathbf{E}\left[\sum_{t=1}^T B_{t+1}\right] \nonumber \\
+& \ge \mathbf{E}\left[\sum_{t=1}^T q_0 A_t\right] + \mathbf{E}\left[\sum_{t=1}^T B_{t+1}\right],
 \label{equation:mistake_lower_bound_temp}
 \end{align}
-where in the first inequality we use the fact that $A_t$ and $B_t$ cannot be $1$ simultaneously; in the equality, we use
-$B_{t+1}=B_t\indicator{\widehat y_t\neq y_t}$ by $B_t$'s definition; in the last
-inequality we use the fact that when $t\le N$ and $A_t=1$, it must be $y_t=1$ and $\Pr[\widehat y_t=y_t]=p_t(1|x_t)<1-q_0$.
-Now, denote $T_1 = \argmin_{\tau} \{ p_\tau(1|x_\tau) \ge 1-q_0 \}$ (if such
-$\tau$ does not exist or is larger than $\min\{T,N\}$, we simply let
-$T_1=\min\{T,N\}+1$). Then $A_t=1$ for all $t\le T_1-1$.
+where in the first inequality we use the fact that $A_t$ and $B_t$ cannot be $1$
+simultaneously; in the equality, we use $B_{t+1}=B_t\indicator{\widehat y_t\neq
+y_t}$ by $B_t$'s definition; in the last inequality we use the fact that when
+$t\le N$ and $A_t=1$, it must be $y_t=1$ and $\Pr[\widehat
+y_t=y_t]=p_t(1|x_t)<1-q_0$. Now, denote $T_1 = \argmin_{\tau} \{
+p_\tau(1|x_\tau) \ge 1-q_0 \}$ (if such $\tau$ does not exist or is larger than
+$T$, we simply let $T_1=T+1$). Then $A_t=1$ for all $t\le
+T_1-1$.
 
-Note that $B_{T_1}=1$, and for $t \geq T_1$ the adversary will switch to ``$\textsc{phase}=2$'' and has $y_t=2$. Therefore, 
-$\Exp[B_{t+1}=0|B_{t}=1]=\Pr[\widehat y_t=y_t~|~B_t=1] = \Pr[\widehat y_t=2|B_t=1].$ 
-Note that when $B_t=1$, by definition there exists a $\tau\le t$ with $p_\tau(1|x_\tau)\ge 1-q_0$, 
-and the algorithm all makes mistakes at $\tau, \tau+1, \ldots, t$. Since the algorithm is ignorant, and when $\textsc{phase}=2$, 
-the features all remain the same, we have $p_t(1|x_t)=p_{t-1}(1|x_{t-1})=\cdots=p_\tau(1|x_\tau)\ge 1-q_0$. 
-Thus we can further upper bound $\Exp[B_{t+1}=0|B_{t}=1]$ by $\Pr[\widehat y_t=2|B_t=1]\leq q_0$. Thus the second term in
-\eqref{equation:mistake_lower_bound_temp} can be calculated as
+Note that $B_{T_1}=1$, and for $t \geq T_1$ the adversary will switch to
+``$\textsc{phase}=2$'' and has $y_t=2$. Therefore,
+$\Exp[B_{t+1}=0|B_{t}=1]=\Pr[\widehat y_t=y_t~|~B_t=1] = \Pr[\widehat
+y_t=2|B_t=1].$ Note that when $B_t=1$, by definition there exists a $\tau\le t$
+with $p_\tau(1|x_\tau)\ge 1-q_0$, and the algorithm all makes mistakes at $\tau,
+\tau+1, \ldots, t$. Since the algorithm is ignorant, and when
+$\textsc{phase}=2$, the features all remain the same, we have
+$p_t(1|x_t)=p_{t-1}(1|x_{t-1})=\cdots=p_\tau(1|x_\tau)\ge 1-q_0$. Thus we can
+further upper bound $\Exp[B_{t+1}=0|B_{t}=1]$ by $\Pr[\widehat y_t=2|B_t=1]\leq
+q_0$. Thus the second term in \eqref{equation:mistake_lower_bound_temp} can be
+calculated as
 
 \begin{align*}
-& \mathbf{E}\left[\sum_{t=1}^{\min\{T,N\}}B_{t+1}\right] \\
-& \ge \mathbf{E}\left[\sum_{t=T_1}^{\min\{ T,N \}} (1-q_0)^{t-T_1+1} \right] \\
-& = \frac{1-q_0}{q_0}\mathbf{E}\left[1-(1-q_0)^{\min\{T,N\}-T_1+1}\right] \; .
+\mathbf{E}\left[\sum_{t=1}^T B_{t+1}\right]
+& \ge \mathbf{E}\left[\sum_{t=T_1}^T (1-q_0)^{t-T_1+1} \right] \\
+& = \frac{1-q_0}{q_0}\mathbf{E}\left[1-(1-q_0)^{T - T_1 + 1}\right] \; .
 \end{align*}
@@
 \mathbf{E} \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \ge
-\\ \mathbf{E}\left[q_0(T_1-1)+\frac{1-q_0}{q_0}\left(1-(1-q_0)^{\min\{T,N\}-T_1+1}\right)\right].
+\\ \mathbf{E}\left[q_0(T_1-1)+\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-T_1+1}\right)\right].
 \end{multline}
-In the case $T_1\ge \frac{1}{2}\min\{T,N\}+1$, the right-hand side of
+In the case $T_1\ge \frac{1}{2}T + 1$, the right-hand side of
 \eqref{equation:mistake_lower_bound_temp2} is lower bounded by
-$\frac{1}{2}q_0\min\{T,N\}=\frac{1}{2}\min\{\sqrt{T}, \sqrt{N}\}$; in the case
-$T_1< \frac{1}{2}\min\{T,N\}+1$, it is lower bounded by
+$\frac{1}{2}q_0 T = \frac{1}{2} \sqrt{T}$. In the case
+$T_1< \frac{1}{2}T+1$, it is lower bounded by
 \begin{align*}
-& \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2}\min\{T,N\}}\right) \\
+& \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2}T}\right) \\
 & = \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2q_0^2}}\right) \\
 & \ge \frac{1-\frac{1}{\sqrt{2}}}{q_0}\left(1-\frac{1}{\sqrt{e}}\right) \\
-& \ge \frac{1}{10}\min\{\sqrt{T}, \sqrt{N}\} \; .
+& \ge \frac{1}{10} \sqrt{T} \; .
 \end{align*}
-Combining both cases concludes the proof.
+
+Observe that in phase 1, the labels are equal to $1$ and in phase 2 the labels
+are equal to $2$. Let $t$ be the round in which the switch happens. (If it never
+happens, define $t=T+1$.) Note that $(x_t, y_t)=(x_{t+1}, y_{t+1})= \dots =
+(x_T, y_T) = (v_t, 2)$. Consider the vectors $u_1, u_2, \dots, u_N$ as defined
+in Lemma~\ref{lemma:embed_d_gamma} We claim that $w_1=-u_t/2$ and $w_2=u_t/2$
+satisfy the conditions of strong linear separabaility.
+
+Clearly $\norm{w_1}^2 + \norm{w_2}^2 \le (\norm{w_1} + \norm{w_2})^2 \le
+(\frac{1}{2} + \frac{1}{2})^2 \le 1$. By Lemma~\ref{lemma:embed_d_gamma}, we
+have $\ip{w_2/2}{x_s} = \ip{u_t/2}{v_t} \ge \gamma/2, \forall s \ge t$ and
+$\ip{w_2/2}{x_s} = \ip{u_t/2}{v_s} \le - \gamma/2$ for all $s<t$. Similarly,
+$\ip{w_1/2}{x_s} \le -\gamma/2$ for all $s \ge t$ and $\ip{w_1/2}{x_s} \ge
+\gamma/2$ for all $s < t$. Thus, the examples are strongly separable with margin
+$\gamma$.
 \end{proof}
-
-\begin{proof}[Proof for Theorem~\ref{theorem:ignorant-lower-bound} (Part II: linear separability)]
-Observe that in Algorithm~\ref{algorithm:adversary-strategy}, in the beginning
-the adversary always set the label to $1$; once it sets $y_t=2$ at some $t$, it
-lets $(x_s, y_s)=(x_t, y_t)=(v_t, 2)$ for all $s\ge t$. Consider $w_2=u_t$ and
-$w_1=-u_t$, for $u_t$ as defined in Lemma~\ref{lemma:embed_d_gamma}. Then by
-Lemma~\ref{lemma:embed_d_gamma}, we have $\ip{w_2}{x_s} = \ip{u_t}{v_t} \ge
-\gamma, \forall s \ge t$ and $\ip{w_2}{x_s} = \ip{u_t}{v_s} \le - \gamma,
-\forall s< t$; also $\ip{w_1}{x_s} \le -\gamma, \forall s \ge t$ and
-$\ip{w_1}{x_s} \ge  \gamma, \forall s<t$. Thus, the example set is always
-$\gamma$-strongly separable.
-\end{proof}

### 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Small fixes

@@
 \begin{proof}
-By Lemma 6 of~\citet{Long-1995}, there exists a set of $N$ dimensional vectors
-$z_1, z_2, \dots, z_N \in \R^{d-1}$ such that $\norm{z_1} = \norm{z_2} = \dots =
-\norm{z_N} = 1$ and the angle between the vectors is $\measuredangle(z_i, z_j) \ge
-\sqrt{40 \gamma}$. Since $\cos\theta \le 1-\theta^2/5$ for any $\theta \in
-[-\pi,\pi]$, this implies that
+By Lemma 6 of~\citet{Long-1995}, there exists vectors $z_1, z_2, \dots, z_N \in
+\R^{d-1}$ such that $\norm{z_1} = \norm{z_2} = \dots = \norm{z_N} = 1$ and the
+angle between the vectors is $\measuredangle(z_i, z_j) \ge \sqrt{40 \gamma}$ for
+$i \neq j$, $i,j \in \{1,2,\dots,N\}$. Since $\cos\theta \le 1-\theta^2/5$ for
+any $\theta \in [-\pi,\pi]$, this implies that
 \begin{align*}
@@
 
-Define $v_i = (\frac12 z_i, \frac12)$, and $u_i = (\frac{1}{2} z_i, -\frac{1}{2}(1-4\gamma))$ for all $i \in \{1,2,\dots,N\}$.
-It can be easily checked that for all $i$,
-$\norm{v_i} \le 1$ and $\norm{u_i} \le 1$. Additionally,
+Define $v_i = (\frac{1}{2} z_i, \frac{1}{2})$, and $u_i = (\frac{1}{2} z_i,
+-\frac{1}{2}(1-4\gamma))$ for all $i \in \{1,2,\dots,N\}$. It can be easily
+checked that for all $i$, $\norm{v_i} \le 1$ and $\norm{u_i} \le 1$.
+Additionally,
 $$
@@
 
-Note that $B_{T_1}=1$, and for $t \geq T_1$ the adversary will switch to
+Note that $B_{T_1}=1$, and for $t \ge T_1$ the adversary will switch to
 ``$\textsc{phase}=2$'' and has $y_t=2$. Therefore,

### 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Clean-up Appendix I

@@
     \If{$\textsc{phase}=1$}{
-       \If{$p_t(1|v_t)\ge 1-q_0$}{
+       \If{$p_t(1|v_t) < 1-q_0$}{
           $(x_t, y_t)\leftarrow (v_t, 1)$
@@
 
-Define the indicators
+Let $\tau$ be the time step $t$ in which the adversary sets $\textsc{phase}\leftarrow 2$.
+If the adversary never sets $\textsc{phase}\leftarrow 2$, we define $\tau = T + 1$.
+Then,
+\begin{align}
+& \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
+& \ge \Exp\left[\sum_{t=1}^{\tau - 1} \indicator{\widehat y_t\neq y_t}\right]
++ \Exp\left[\sum_{t=\tau}^T \indicator{\widehat y_t\neq y_t}\right] \; .
+\end{align}
+We upper bound each of last two terms separately.
+
+In rounds $1,2,\dots,\tau-1$, the algorithm predicts the incorrect class $2$
+with probability at least $q_0$. Thus,
+$$
+\Exp\left[\sum_{t=1}^{\tau - 1} \indicator{\widehat y_t\neq y_t}\right] = q_0 \Exp[\tau] \; .
+$$
+In rounds $\tau, \tau+1, \dots, T$, all the examples are the same and are equal
+to $(v_\tau, 2)$. Let $s$ be the first time step $t$ such that $t \ge \tau$
+and the algorithm makes a correct prediction. If the algorithm makes mistakes
+in all rounds $\tau, \tau+1, \dots, T$, we define $s = T+1$.
+By definition the algorithm makes mistakes in rounds $\tau, \tau+1, \dots, s-1$
+Then,
+$$
+\Exp\left[\sum_{t=\tau}^T \indicator{\widehat y_t\neq y_t}\right] \ge \Exp[s-\tau].
+$$
+Since the algorithm is ignorant, conditioned on $\tau$, the random variable $s-\tau$
+has a truncated geometric distribution with parameter $p_\tau(2|v_\tau) \le q_0$.
+Therefore,
+$$
+\Exp[s-\tau ~|~ \tau]
+\ge
+\Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \; .
+$$
+
+Combining the two, we have that
 \begin{align*}
-A_t &= \indicator{\forall \tau\le t, p_\tau(1|x_\tau)<1-q_0} \\
-B_t &= \indicator{\exists \tau\le t, p_\tau(1|x_\tau)\ge 1-q_0
- \text{\ and\ } \forall s\in[\tau,t), \widehat y_s \neq y_s}.
+& \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
+& \ge q_0 \Exp[\tau] + \Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-T_1+1}\right)\right] \\
+& =  \Exp \left[ \Exp \left[ q_0 \tau + \frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \right] \; .
 \end{align*}
-Then we have
-\begin{align}
-& \mathbf{E}\left[\sum_{t=1}^{T} \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
-& \ge \mathbf{E}\left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}A_t\right] \nonumber \\
-& \qquad + \mathbf{E}\left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}B_t\right] \nonumber \\
-& = \mathbf{E}\left[\sum_{t=1}^T \mathbf{E}_t\left[\indicator{\widehat y_t\neq y_t}A_t\right]\right] + \mathbf{E}\left[\sum_{t=1}^T B_{t+1}\right] \nonumber \\
-& \ge \mathbf{E}\left[\sum_{t=1}^T q_0 A_t\right] + \mathbf{E}\left[\sum_{t=1}^T B_{t+1}\right],
-\label{equation:mistake_lower_bound_temp}
-\end{align}
-where in the first inequality we use the fact that $A_t$ and $B_t$ cannot be $1$
-simultaneously; in the equality, we use $B_{t+1}=B_t\indicator{\widehat y_t\neq
-y_t}$ by $B_t$'s definition; in the last inequality we use the fact that when
-$t\le N$ and $A_t=1$, it must be $y_t=1$ and $\Pr[\widehat
-y_t=y_t]=p_t(1|x_t)<1-q_0$. Now, denote $T_1 = \argmin_{\tau} \{
-p_\tau(1|x_\tau) \ge 1-q_0 \}$ (if such $\tau$ does not exist or is larger than
-$T$, we simply let $T_1=T+1$). Then $A_t=1$ for all $t\le
-T_1-1$.
-
-Note that $B_{T_1}=1$, and for $t \ge T_1$ the adversary will switch to
-``$\textsc{phase}=2$'' and has $y_t=2$. Therefore,
-$\Exp[B_{t+1}=0|B_{t}=1]=\Pr[\widehat y_t=y_t~|~B_t=1] = \Pr[\widehat
-y_t=2|B_t=1].$ Note that when $B_t=1$, by definition there exists a $\tau\le t$
-with $p_\tau(1|x_\tau)\ge 1-q_0$, and the algorithm all makes mistakes at $\tau,
-\tau+1, \ldots, t$. Since the algorithm is ignorant, and when
-$\textsc{phase}=2$, the features all remain the same, we have
-$p_t(1|x_t)=p_{t-1}(1|x_{t-1})=\cdots=p_\tau(1|x_\tau)\ge 1-q_0$. Thus we can
-further upper bound $\Exp[B_{t+1}=0|B_{t}=1]$ by $\Pr[\widehat y_t=2|B_t=1]\leq
-q_0$. Thus the second term in \eqref{equation:mistake_lower_bound_temp} can be
-calculated as
-
-\begin{align*}
-\mathbf{E}\left[\sum_{t=1}^T B_{t+1}\right]
-& \ge \mathbf{E}\left[\sum_{t=T_1}^T (1-q_0)^{t-T_1+1} \right] \\
-& = \frac{1-q_0}{q_0}\mathbf{E}\left[1-(1-q_0)^{T - T_1 + 1}\right] \; .
-\end{align*}
-Combining \eqref{equation:mistake_lower_bound_temp} and the above inequalities, we get
-\begin{multline}
-\label{equation:mistake_lower_bound_temp2}
-\mathbf{E} \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \ge
-\\ \mathbf{E}\left[q_0(T_1-1)+\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-T_1+1}\right)\right].
-\end{multline}
-In the case $T_1\ge \frac{1}{2}T + 1$, the right-hand side of
-\eqref{equation:mistake_lower_bound_temp2} is lower bounded by
-$\frac{1}{2}q_0 T = \frac{1}{2} \sqrt{T}$. In the case
-$T_1< \frac{1}{2}T+1$, it is lower bounded by
+We lower bound the last expression by considering two cases for $\tau$.
+If $\tau \ge \frac{1}{2}T + 1$, then the last expression is lower bounded by
+$\frac{1}{2}q_0 T = \frac{1}{2} \sqrt{T}$. If
+$\tau < \frac{1}{2}T+1$, it is lower bounded by
 \begin{align*}
@@
 Observe that in phase 1, the labels are equal to $1$ and in phase 2 the labels
-are equal to $2$. Let $t$ be the round in which the switch happens. (If it never
-happens, define $t=T+1$.) Note that $(x_t, y_t)=(x_{t+1}, y_{t+1})= \dots =
+are equal to $2$. Note that $(x_\tau, y_\tau)=(x_{\tau+1}, y_{\tau+1})= \dots =
 (x_T, y_T) = (v_t, 2)$. Consider the vectors $u_1, u_2, \dots, u_N$ as defined
-in Lemma~\ref{lemma:embed_d_gamma} We claim that $w_1=-u_t/2$ and $w_2=u_t/2$
+in Lemma~\ref{lemma:embed_d_gamma} We claim that $w_1=-u_\tau/2$ and $w_2=u_\tau/2$
 satisfy the conditions of strong linear separabaility.
@@
 (\frac{1}{2} + \frac{1}{2})^2 \le 1$. By Lemma~\ref{lemma:embed_d_gamma}, we
-have $\ip{w_2/2}{x_s} = \ip{u_t/2}{v_t} \ge \gamma/2, \forall s \ge t$ and
-$\ip{w_2/2}{x_s} = \ip{u_t/2}{v_s} \le - \gamma/2$ for all $s<t$. Similarly,
-$\ip{w_1/2}{x_s} \le -\gamma/2$ for all $s \ge t$ and $\ip{w_1/2}{x_s} \ge
-\gamma/2$ for all $s < t$. Thus, the examples are strongly separable with margin
+have $\ip{w_2/2}{x_t} = \ip{u_\tau/2}{v_\tau} \ge \gamma/2, \forall t \ge \tau$ and
+$\ip{w_2/2}{x_t} = \ip{u_\tau/2}{v_t} \le - \gamma/2$ for all $t < \tau$. Similarly,
+$\ip{w_1/2}{x_t} \le -\gamma/2$ for all $t \ge \tau$ and $\ip{w_1/2}{x_t} \ge
+\gamma/2$ for all $t < \tau$. Thus, the examples are strongly separable with margin
 $\gamma$.

### 2019-01-23 ICML-submission/introduction.tex
small typo

@@
 dimensionless mistake bound (Algorithm~\ref{algorithm:kernelized}).\footnote{An
-in inefficient algorithm was given by~\cite{Daniely-Helbertal-2013}.}
+inefficient algorithm was given by~\cite{Daniely-Helbertal-2013}.}
 

### 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Small fixes

@@
 below, it is actually natural, and several recently proposed bandit
-classification algorithms that achieve $\sqrt{T}$ regret bounds belong to
-this family, e.g., SOBA~\citep{Beygelzimer-Orabona-Zhang-2017},
+classification algorithms that achieve $\sqrt{T}$ regret bounds belong to this
+family, e.g., SOBA~\citep{Beygelzimer-Orabona-Zhang-2017},
 OBAMA~\citep{Foster-Kale-Luo-Mohri-Sridharan-2018}. Also,
@@
 weakly linearly separable with margin $\gamma$, we show that any ignorant
-algorithm must make at least $\Omega \left( \left(\frac{1}{160 \gamma}\right)^{(d-2)/4} \right)$
-mistakes in the worst case. In other words, an algorithm that achieves a better
-mistake bound cannot ignore examples on which it makes a mistake and it must
-make a meaningful update on such examples.
+algorithm must make at least $\Omega \left( \left(\frac{1}{160
+\gamma}\right)^{(d-2)/4} \right)$ mistakes in the worst case. In other words, an
+algorithm that achieves a better mistake bound cannot ignore examples on which
+it makes a mistake and it must make a meaningful update on such examples.
 
@@
 $(x_{a_1}, y_{a_1}), (x_{a_2}, y_{a_2}), \dots, (x_{a_n}, y_{a_n})$
-in the rounds $1 \le a_1 < a_2 < \dots < a_n < t$ in which
+of labeled examples
+from the rounds $1 \le a_1 < a_2 < \dots < a_n < t$ in which
 the algorithm makes a correct prediction.
@@
 are equal to $2$. Note that $(x_\tau, y_\tau)=(x_{\tau+1}, y_{\tau+1})= \dots =
-(x_T, y_T) = (v_t, 2)$. Consider the vectors $u_1, u_2, \dots, u_N$ as defined
-in Lemma~\ref{lemma:embed_d_gamma} We claim that $w_1=-u_\tau/2$ and $w_2=u_\tau/2$
-satisfy the conditions of strong linear separabaility.
+(x_T, y_T) = (v_\tau, 2)$. Consider the vectors $u_1, u_2, \dots, u_N$ as
+defined in Lemma~\ref{lemma:embed_d_gamma} We claim that $w_1=-u_\tau/2$ and
+$w_2=u_\tau/2$ satisfy the conditions of strong linear separabaility.
 

### 2019-01-23 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Fixes

--- 2019-01-23 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
@@
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
-to use $K$ copies of the \textsc{Binary Perceptron} algorithm, one copy per class; see e.g.
-\citet[Section 3.3.1]{Shalev-Shwartz-2012}.
-Upon seeing each example $x_t$, copy $i$ predicts 
-whether or not $x_t$ belongs to class $i$.
-Multiclass predictions are done by evaluating all $K$ binary predictors and outputting any class with a positive prediction.
-If all binary predictions are negative, the algorithm chooses a prediction a prediction uniformly at random from
-$\cbr{1,\ldots,K}$.
+to use $K$ copies of the \textsc{Binary Perceptron} algorithm, one copy per
+class; see e.g. \citet[Section 3.3.1]{Shalev-Shwartz-2012}. Upon seeing each
+example $x_t$, copy $i$ predicts whether or not $x_t$ belongs to class $i$.
+Multiclass predictions are done by evaluating all $K$ binary predictors and
+outputting any class with a positive prediction.  If all binary predictions are
+negative, the algorithm chooses a prediction a prediction uniformly at random
+from $\cbr{1,\ldots,K}$.
 
@@
 Appendix~\ref{section:proofs-for-stringly-separable-examples} in the
-supplementary material.
-\citet{Daniely-Helbertal-2013} provide a lower bound under the assumption of weak linear separability, which does not immediately imply a lower bound under the stronger notion.
+supplementary material. \citet{Daniely-Helbertal-2013} provide a lower bound
+under the assumption of weak linear separability, which does not immediately
+imply a lower bound under the stronger notion.
 
@@
 positive integer $m$ and $x_1, x_2, \dots, x_m \in X$ \citep[Definition
-2.5]{Scholkopf-Smola-2002}.\footnote{Every kernel has an associated feature map
-$\phi:X \to V$ for some inner product space $(V,\ip{\cdot}{\cdot})$ such that
+2.5]{Scholkopf-Smola-2002}.\footnote{For every kernel there exists an associated feature map
+$\phi:X \to V$ into some inner product space $(V,\ip{\cdot}{\cdot})$ such that
 $k(x,x') = \ip{\phi(x)}{\phi(x')}$.} As opposed to explicitly maintaining the

### 2019-01-23 ICML-submission/empirical-comparison.tex
Add reference to Francesco's source code

@@
 Algorithm~\ref{algorithm:kernelized} with rational
-kernel~\eqref{equation:rational-kernel}, and the \textsc{Banditron} algorithm.
+kernel~\eqref{equation:rational-kernel} and used implementation of
+\textsc{Banditron} algorithm by \citet{Orabona09}.\footnote{All the source code
+is included in the supplementary material.}
 We evaluated these algorithms on the two datasets. \textsc{Banditron} has an

### 2019-02-05 ICML-submission/appendix-proofs-of-polynomial-approximation-theorems.tex
a pass over the paper

@@
 
-We prove third property by induction on $n$. Indeed, by definition
+We prove the third property by induction on $n$. Indeed, by definition
 $$
@@
 
-Fourth property has the similar proof as third property. It suffices
+The fourth property has the similar proof as the third property. It suffices
 to replace $\cos$ and $\sin$ with $\cosh$ and $\sinh$ respectively.
 
-Fifth property follows from the third property. Indeed, for any $z \in [-1,1]$
+The fifth property follows from the third property. Indeed, for any $z \in [-1,1]$
 there exists $\theta \in \R$ such that $\cos \theta = z$. Thus, $|T_n(z)| =
@@
 & = (1 + \sqrt{2})^{n+1} \; .
+\qedhere
 \end{align*}
-
 \end{proof}
 
+We are now ready to prove~\autoref{theorem:polynomial-approximation-1}.
 Let $r = \left\lceil \log_2(2m) \right\rceil$ and $s = \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$.
@@
 
-The third property follows from observation that degree of $p$
+The third property follows from the observation that the degree of $p$
 is the same as the degree of any one of the terms
@@
 & = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
-& \le \left(8(1+\sqrt{2})^2 s \right)^s
+& \le \left(8(1+\sqrt{2})^2 s \right)^s \\
 & \le \left(47 s \right)^s \; .
@@
 \{1,2,\dots,n\}$ be such that $2^{j-1} \le z \le 2^j$. This implies that
-$(z+2^{j})^2 \ge 4 (z - 2^j)^2$. We can write $\frac{P_n(z)}{-P_n(-z)}$ as a
+$(z+2^{j})^2 \ge (2^j)^2 \ge 4 (z - 2^j)^2$. We can write $\frac{P_n(z)}{-P_n(-z)}$ as a
 product of $n+1$ non-negative fractions
@@
 \item If $z \in [1,2^n]$ then $S_{n,r}(z) \in [1,1+\frac{1}{2m}]$.
-\item If $z \in [-2^n, -1]$ then $S_{n,r} \in [-1-\frac{1}{2m}, -1]$.
+\item If $z \in [-2^n, -1]$ then $S_{n,r}(z) \in [-1-\frac{1}{2m}, -1]$.
 \item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
@@
 part 2 of~\autoref{lemma:properties-of-p-n}, $c \in [0,\frac{1}{4^r}]$. Since
-$r \ge \frac{1}{2} \log_2(4m+1)$ that means that $c \in [0,\frac{1}{4m+1}]$. Thus,
+$r \ge \frac{1}{2} \log_2(4m+1)$, this means that $c \in [0,\frac{1}{4m+1}]$. Thus,
 $S_{n,r}(z) = \frac{1+c}{1-c} \in [1,1 + \frac{1}{2m}]$.
@@
 
-\item Observe that $S_{n,r}(z)$ can be written as
+\item Recall that $S_{n,r}(z)$ can be written as
 $$
-S_{n,r}(z) = \frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} = \frac{1 + c}{1 - c}
+S_{n,r}(z) = \frac{1 + c}{1 - c}
 $$
@@
 $S_{n,r}(z)$ is odd, for $z \in [-1,0]$, $S_{n,r}(z) \in [-1,0]$.
+
+%\frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} =
 
@@
 & \le -1 + (m-1) \left( 1 + \frac{1}{2m} \right) - \left(m - \frac{1}{2} \right) \\
-& \le 1/2 \; .
+& \le -1/2 \; .
+\qedhere
 \end{align*}
@@
 
-To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-2} first
+To prove parts 1 and 2 of \autoref{lemma:polynomial-approximation-2} first
 note that part 4 of \autoref{lemma:properties-of-s-n-r} implies that for any $x$
@@
 depends on which of the two sets $x$ lies in. Since signs of $Q(x)$ and $p(x)$
-are the same, it remains to show that $|p(x)| \ge m^{s^2m/2}$. Indeed,
+are the same, it remains to show that $|p(x)| \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$.
+Indeed,
 \begin{align*}
@@
 \end{align*}
-where we used that $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4} \ge 1/2$.
+where we used that $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-\frac 1 4} \ge 1/2$.
 
-To prove part 3 of \autoref{theorem:polynomial-approximation-2} note that
+%m^{s^2m/2}
+
+To prove part 3 of \autoref{lemma:polynomial-approximation-2} note that
 $\deg(P_s) = 2s+1$. Thus, $\deg(A_{s,r})$ and $\deg(B_{s,r})$ are at most
@@
 
-It remains to prove part 4 of \autoref{theorem:polynomial-approximation-2}.
+It remains to prove part 4 of \autoref{lemma:polynomial-approximation-2}.
 For any $i \in \{0,1,2,\dots,s\}$ and any $v \in \R^d$ such that $\norm{v} \le 1$
@@
 $$
-\norm{f_{i,v}}^2 = \norm{v}^2/\gamma^2 + 2^{2i} \le 2 \cdot 2^s \; .
+\norm{f_{i,v}}^2 = \norm{v}^2/\gamma^2 + 2^{2i} \le 2 \cdot 2^{2s} \; .
 $$
@@
 & \le (2s+1)^{2s+1} \norm{f_{0,v}}^2 \prod_{i=1}^s \norm{f_{i,v}}^4 \\
-& \le  (2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \; .
+& \le  (2s+1)^{2s+1} (2 \cdot 2^{2s})^{2s + 1} \; .
 \end{align*}
@@
 & \le 2\norm{(q_v)^r}^2 + 2\norm{(q_{-v})^r}^2 \\
-& \le 2 r^{r(2s+1)} \norm{q_v}^{2r} + 2 r^{r(2s+1)} \norm{q_{-v}}^{2r} \\
-& \le 4 r^{r(2s+1)} \left((2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \right)^{2r} \\
-& = 4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \; .
+& \le 2 r^{r(2s+1)} (\norm{q_v}^{2})^r + 2 r^{r(2s+1)} (\norm{q_{-v}}^{2})^r \\
+& \le 4 r^{r(2s+1)} \left((2s+1)^{2s+1} (2 \cdot 2^s)^{2s + 1} \right)^{r} \\
+& = 4 \left(2^{2s} r (4s+2) \right)^{(2s+1)r} \; .
 \end{align*}
@@
 & \qquad + \left(m - \frac{1}{2} \right) m^{(s+1/2)rm} \prod_{j=1}^m \norm{b_{v_j}} \\
-& \le (2m-1/2) m^{(s+1/2)rm} \left(4 \left(2^{2s} r (4s+2)^2 \right)^{(2s+1)r} \right)^{m/2} \\
-& = (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm} \; .
+& \le (2m-1/2) m^{(s+1/2)rm} \left(4 \left(2^{2s} r (4s+2) \right)^{(2s+1)r} \right)^{m/2} \\
+& = (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2) \right)^{(s+1/2)rm} \; .
 \end{align*}

### 2019-02-05 ICML-submission/introduction.tex
a pass over the paper

@@
 Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
-Observe feedback $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
+Observe feedback $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$.
 }
@@
 \textsc{Multiclass Perceptron} achieves an information-theoretically optimal
-mistake bound, while being computationally and memory efficient.~\footnote{For
+mistake bound, while being time and memory efficient.~\footnote{For
 completeness, we present these folklore results along with their proofs in
@@
 mistake bound under the strong linear separability condition, their
-Theorem 2 is incorrect: first, their Lemma 1 (with $C = +\infty$) along with Theorem 1
+Theorem~2 is incorrect: first, their Lemma~1 (with $C = +\infty$) along with their Theorem~1
 implies a mistake upper bound of
-$(\frac{R}{\gamma})^2$, which contradicts our lower
-bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
-second, their Lemma 1 cannot be directly applied to the bandit setting, as the
-algorithm only makes updates on a subset of the $w_i$'s.} We design a simple and
+$(\frac{R}{\gamma})^2$, which contradicts the lower
+bound in our Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
+second, their Lemma~1 cannot be directly applied to the bandit feedback setting.}
+We design a simple and
 efficient algorithm
@@
 Algorithm~\ref{algorithm:kernelized} makes at
-most $2^{\widetilde{O}(\min(K \log^2 (1/\gamma), \sqrt{1/\gamma}
-\log K))}$ mistakes.
+most $\min (2^{\widetilde{O}(K \log^2
+(1/\gamma))}, 2^{\widetilde{O}(\sqrt{1/\gamma} \log K)})$ mistakes.
 

### 2019-02-05 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
a pass over the paper

@@
 which they make mistakes. This assumption seems strong, but as we will explain
-below, it is actually natural, and several recently proposed bandit
+below, it is actually natural, and several recently proposed bandit linear
 classification algorithms that achieve $\sqrt{T}$ regret bounds belong to this
@@
 
-\begin{proof}
+\begin{proof}[Proof of \autoref{theorem:ignorant-lower-bound}]
 We consider the strategy for the adversary described in
@@
 $$
-\Exp\left[\sum_{t=1}^{\tau - 1} \indicator{\widehat y_t\neq y_t}\right] = q_0 \Exp[\tau] \; .
+\Exp\left[\sum_{t=1}^{\tau - 1} \indicator{\widehat y_t\neq y_t}\right] = q_0 \Exp[(\tau - 1)] \; .
 $$
@@
 in all rounds $\tau, \tau+1, \dots, T$, we define $s = T+1$.
-By definition the algorithm makes mistakes in rounds $\tau, \tau+1, \dots, s-1$
-Then,
+By definition the algorithm makes mistakes in rounds $\tau, \tau+1, \dots, s-1$.
+Therefore,
 $$
@@
 & \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
-& \ge q_0 \Exp[\tau] + \Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-T_1+1}\right)\right] \\
-& =  \Exp \left[ \Exp \left[ q_0 \tau + \frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \right] \; .
+& \ge q_0 \Exp[\tau - 1] + \Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right)\right] \\
+& =  \Exp \left[ \Exp \left[ q_0 (\tau - 1) + \frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \right] \; .
 \end{align*}
@@
 defined in Lemma~\ref{lemma:embed_d_gamma} We claim that $w_1=-u_\tau/2$ and
-$w_2=u_\tau/2$ satisfy the conditions of strong linear separabaility.
+$w_2=u_\tau/2$ satisfy the conditions of strong linear separability.
 
@@
 $\ip{w_1/2}{x_t} \le -\gamma/2$ for all $t \ge \tau$ and $\ip{w_1/2}{x_t} \ge
-\gamma/2$ for all $t < \tau$. Thus, the examples are strongly separable with margin
-$\gamma$.
+\gamma/2$ for all $t < \tau$. Thus, the examples are strongly linearly
+separable with margin $\gamma$.
 \end{proof}

### 2019-02-05 ICML-submission/np-hardness-of-the-weak-labeling-problem.tex
a pass over the paper

@@
 The hardness proof is based on a reduction from the set splitting problem, which
-is proven to be NP-complete by Lovasz \cite{Garey-Johnson-1979}, to our weak
+is proven to be NP-complete by Lov\'asz \cite{Garey-Johnson-1979}, to our weak
 labeling problem. The reduction is adapted from \cite{Blum-Rivest-1993}.
@@
 \textbf{Given:} A finite set $S$ and a collection $C$ of subsets $c_i$ of $S$. \\
-\textbf{Question:} Do there exist disjoint sets $S_1$ and $S_2$ such that $S_1 \cup S_2 = S$ and $\forall i, c_i\not\subseteq S_1$ or $c_i\not\subseteq S_2$?
+\textbf{Question:} Do there exist disjoint sets $S_1$ and $S_2$ such that $S_1 \cup S_2 = S$ and $\forall i, c_i\not\subseteq S_1$ and $c_i\not\subseteq S_2$?
 \end{framed}
@@
 Now we show $\forall j$, $c_j \not\subset S_1$ and $c_j \not\subset S_2$ by
-contraction. Assume there exists some $j$ such that $c_j \subset S_1$. By our
+contradiction. Assume there exists some $j$ such that $c_j \subset S_1$. By our
 definition of $S_1$, we have $\ip{w_1-w_3}{(\e_i, 1)} > 0$ for all $i\in c_j$.

### 2019-02-05 ICML-submission/related-work.tex
a pass over the paper

@@
 Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
-While solving a more general problem without making assumptions on the structure of the cost vector $c_t$ or the policy class, these results assume that $x_t$ vectors or $(x_t,c_t)$ pairs are generated i.i.d.
+However, such an oracle abstracting efficient search through $\Pi$ is generally not available
+in our setting due to computational hardness results~\citep{Arora-Babai-Stern-Sweedyk-1997}.
+
+%While solving a more general problem without making assumptions on the structure of the cost vector $c_t$ or the policy class, these results assume that $x_t$ vectors or $(x_t,c_t)$ pairs are generated i.i.d.
 and that such an oracle abstracting efficient search through $\Pi$ is available---neither of which we assume here.
 
+%While solving a more general problem without making assumptions on the structure of the cost vector $c_t$ or the policy class,
 %However, these algorithms are not
@@
 \sum_{i=1}^K c_t(i) \phi( f_i(x_t) )$, where $\calF$ contains score functions
-$f$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac
+$f = (f_1, \ldots, f_K)$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac
 s \gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives

### 2019-02-05 ICML-submission/title-and-abstract.tex
Update title-and-abstract.tex
Added a sentence on answering an open question in the Banditron paper
Removed the open problem reference from abstract
minor
a pass over the paper

@@
 \twocolumn[
-\icmltitle{Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case}
+\icmltitle{Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case}
 
@@
 \item Under the more challenging weak linear separability condition, we design
-an efficient algorithm with a mistake bound of $2^{\widetilde{O}(\min(K \log^2
-(1/\gamma), \sqrt{1/\gamma} \log K))}$ \footnote{We use the notation
-$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}. Our algorithm
+an efficient algorithm with a mistake bound of $\min (2^{\widetilde{O}(K \log^2
+(1/\gamma))}, 2^{\widetilde{O}(\sqrt{1/\gamma} \log K)})$ \footnote{We use the notation
+$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}.
+Our algorithm
 is based on kernel Perceptron, which is inspired by the work

### 2019-02-05 arxiv/appendix-multiclass-perceptron.tex
added arxiv folder

--- 2019-01-22 ICML-submission/appendix-multiclass-perceptron.tex
@@
 Two results are folklore. The first result is
-\autoref{theorem:mutliclass-perceptron-mistake-upper-bound} which states that if
+\autoref{theorem:multiclass-perceptron-mistake-upper-bound} which states that if
 examples are linearly separable with margin $\gamma$ and examples have norm
@@
 \label{algorithm:mutliclass-classification}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$}
-\STATE{Predict $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
-\ENDFOR
+\textbf{Require:} Number of classes $K$, number of rounds $T$. \\
+\textbf{Require:} Inner product space $(V,\ip{\cdot}{\cdot})$. \\
+\For{$t=1,2,\dots,T$}{
+Adversary chooses example $(x_t, y_t) \in V \times \{1,2,\dots,K\}$, where $x_t$ is revealed to the learner.\\
+Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
+Observe feedback $y_t$.
 }
-\end{algorithmic}
 \end{protocol}
@@
 \label{algorithm:mutliclass-perceptron}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
-\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t \in V$}
-\STATE{Predict $\widehat y_t = \argmax_{i \in \{1,2,\dots,K\}} \ip{w_t^{(i)}}{x_t}$}
-\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
-\IF{$\widehat y_t \neq y_t$}
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}$}
-\STATE{Update $w_{y_t}^{(t+1)} = w_{y_t}^{(t)} + x_t$}
-\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
-\ELSE
-\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
-\ENDIF
-\ENDFOR
+\textbf{Require:} Number of classes $K$, number of rounds $T$. \\
+\textbf{Require:} Inner product space $(V,\ip{\cdot}{\cdot})$. \\
+Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$ \\
+\For{$t=1,2,\dots,T$}{
+  Observe feature vector $x_t \in V$ \\
+  Predict $\widehat y_t = \argmax_{i \in \{1,2,\dots,K\}} \ip{w_t^{(i)}}{x_t}$ \\
+  Observe $y_t \in \{1,2,\dots,K\}$ \\
+  \If{$\widehat y_t \neq y_t$}{
+    Set $w_i^{(t+1)} = w_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{y_t, \widehat y_t\}$ \\
+    Update $w_{y_t}^{(t+1)} = w_{y_t}^{(t)} + x_t$ \\
+    Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$ \\
   }
-\end{algorithmic}
+  \Else{
+    Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$ \\
+  }
+}
 \end{algorithm}
@@
 \begin{theorem}[Mistake upper bound~\cite{Crammer-Singer-2003}]
-\label{theorem:mutliclass-perceptron-mistake-upper-bound}
+\label{theorem:multiclass-perceptron-mistake-upper-bound}
 Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, let $K$ be a positive
@@
 So each time a mistake happens, $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ increases by at most $2R^2$. Thus,
-$$
+\begin{equation}
 \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le 2R^2 M \; .
-$$
-Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors satisfying the
+\label{equation:perceptron-norm-ub}
+\end{equation}
+Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors satisfying
 \eqref{equation:weak-linear-separability-1} and
@@
 Thus, after $M$ mistakes,
-$$
+\[
+\label{equation:perceptron-ip-lb}
 \sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma M \; .
-$$
+\]
 We upper bound the left hand side by using Cauchy-Schwartz inequality twice and
@@
 \end{align*}
-Combining all inequalities, we get
+Combining the above inequality with Equations~\eqref{equation:perceptron-norm-ub}
+and~\eqref{equation:perceptron-ip-lb}, we get
 $$
@@
 Let labels $y_1, \ldots, y_T$ be chosen i.i.d uniformly at random from
-$\cbr{1,2,\ldots,K}$ and independently of any randomness used by the algirithm
+$\cbr{1,2,\ldots,K}$ and independently of any randomness used by the algorithm
 $\calA$.
@@
 We now give a lower bound on the number of mistakes $\calA$ makes.
-As $y_t$ is chosen uniformly from $\{1,2,\dots,K\}$ and independent of
-$\calA$'s randomization
+As $y_t$ is chosen uniformly from $\{1,2,\dots,K\}$, independently from
+$\calA$'s randomization and the first $t-1$ examples,
 $$

### 2019-02-05 arxiv/appendix-nearest-neighbor-algorithm.tex
added arxiv folder

--- 2019-01-23 ICML-submission/appendix-nearest-neighbor-algorithm.tex
@@
 \LinesNumbered
+\setcounter{AlgoLine}{0}
 \caption{\textsc{Nearest-Neighbor Algorithm}
@@
   }
-  \Else{
+\nl \Else{
 \nl	  Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$
@@
 In this section we analyze \textsc{Nearest-Neighbor Algorithm} shown as
-Algorithm~\ref{algorithm:nearest-neighbor}. The algorithm is based on obvious
-the idea that under weak linear assumption two examples that are close to each
-other must have the same label. Lemma below formalizes this intuition.
+Algorithm~\ref{algorithm:nearest-neighbor}. The algorithm is based on the obvious
+idea that, under the weak linear separability assumption, two examples that are close to each
+other must have the same label. The lemma below formalizes this intuition.
 
@@
 \in \R^d ~:~ \norm{x' - x} \le R \}$ denotes the closed ball of radius $R$
-centered a point $x$.
+centered a point $x$. For set $S \subseteq \R^d$, denote by $\Vol(S)$ the volume of
+$S$.
 
@@
 Let $M$ be the number of mistakes made by the algorithm. Let $b_t$ be the
-indicator that line~\ref{line:nearest-neighbor-explore} is executed at timestep
+indicator that line~\ref{line:nearest-neighbor-explore} is executed at time step
 $t$, i.e. we fall into the ``else'' case. Note that if $b_t = 0$, then by

### 2019-02-05 arxiv/appendix-proofs-for-strongly-separable-examples.tex
added arxiv folder

--- 2019-01-23 ICML-submission/appendix-proofs-for-strongly-separable-examples.tex
@@
 \endgroup
-The inequality that $(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t} \leq 0$ is from a case analysis: if line~\ref{line:pos-update} is executed, then $z_t = 0$ and $\ip{w_i^{(t)}}{x_t} \ge 0$; otherwise line~\ref{line:neg-update} is executed, in which case $z_t = 1$ and $\ip{w_i^{(t)}}{x_t} \le 0$.
+The inequality that $(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t} \leq 0$ is from a case analysis: if line~\ref{line:pos-update} is executed, then $z_t = 0$ and $\ip{w_{\widehat y_t}^{(t)}}{x_t} < 0$;
+ otherwise line~\ref{line:neg-update} is executed, in which case $z_t = 1$ and $\ip{w_{\widehat y_t}^{(t)}}{x_t} \ge 0$.
 
@@
 
-The norm of each example is exactly $R$. The examples are strongly separable
+The norm of each example is exactly $R$. The examples are strongly linearly separable
 with margin $\gamma$. To see that, consider $w_1^*, w_2^*, \dots, w_K^* \in V$

### 2019-02-05 arxiv/empirical-comparison.tex
added arxiv folder

--- 2019-01-23 ICML-submission/empirical-comparison.tex
@@
 kernel~\eqref{equation:rational-kernel} and used implementation of
-\textsc{Banditron} algorithm by \citet{Orabona09}.\footnote{All the source code
+\textsc{Banditron} algorithm by \citet{Orabona09}.\footnote{The source code
 is included in the supplementary material.}
@@
 Appendix~\ref{section:supp-to-experiment} shows the decision boundaries that
-each of the algorithms learns.
+each of the algorithms learns by the end of the last round.
 

### 2019-02-05 arxiv/from-weak-separability-to-strong-separability.tex
added arxiv folder

--- 2019-01-23 ICML-submission/from-weak-separability-to-strong-separability.tex
@@
 linearly separable examples to \emph{strongly} linearly separable sequence of
-examples. Specifically, $\phi$ has the property that if a set of labeled
+examples.
+Specifically, $\phi$ has the property that if a set of labeled
 examples in $\B(\zero,1)$ is weakly linearly separable with a margin $\gamma$, then
 after applying $\phi$ the examples become strongly linearly separable with a
-margin $\gamma'$ and their squared norms are bounded by $2$. The parameter $\gamma'$ is
+margin $\gamma'$ and their squared norms are bounded by $2$.
+\footnote{Other kernels, such as the polynomial kernel
+$k(x,x') = (1+\ip{x}{x'})^d$, or the multinomial kernel~\citep{Goel-Klivans-2017} $k(x,x') = \sum_{i=0}^d(\ip{x}{x'})^i$,
+will have similar properties for large enough $d$.}
+The parameter $\gamma'$ is
 a function of the old margin $\gamma$ and the number of classes $K$, and is
@@
 \gamma_2 = & \frac{
-   \left(2^{s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)}
+   \left(2^{s+1} r(K-1) (4s+2) \right)^{-(s+1/2)r(K-1)}
 }{4\sqrt{K}(4K-5) 2^{K-1}}
-\\
-&  \cdot 2^{s(s+1)r(K-1)}
 \; ,
@@
 \endgroup
+
+%\\
+%&  \cdot 2^{s(s+1)r(K-1)}
+
 where $r = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1$ and $s = \left \lceil \log_2(2/\gamma) \right \rceil$.
@@
 with kernel $k(x,x')$ defined by \eqref{equation:rational-kernel}
-is at most $2^{\widetilde{O}(\min(K \log^2 \frac{1}{\gamma},
-\sqrt{\frac{1}{\gamma}} \log K))}$.
+is at most $\min (2^{\widetilde{O}(K \log^2
+(1/\gamma))}, 2^{\widetilde{O}(\sqrt{1/\gamma} \log K)})$.
 \end{corollary}
@@
 immediately implies that that the examples $(\phi(x_1),y_1), \ldots,
-(\phi(x_T),y_T)$ are strongly linearly separable with margin $\gamma'$.
+(\phi(x_T),y_T)$ are strongly linearly separable with a positive margin.
 
@@
 \item $\deg(p) \le (2s+1) rm$,
-\item $\norm{p} \le (4m-1) 2^m \cdot \left(2^s rm (4s+2)^2 \right)^{(s+1/2)rm}$.
+\item $\norm{p} \le (4m-1) 2^m \cdot \left(2^s rm (4s+2) \right)^{(s+1/2)rm}$.
 \end{enumerate}
@@
 The proofs of the theorems are in
-Appendix~\ref{section:proof-of-polynomial-approximation}.
-The geometric interpretation of the two regions described in parts 1
-and 2 of the theorems is explained in Figure~\ref{figure:pizza-slice}. Similar
-but weaker results were proved by~\citet{Klivans-Servedio-2008}. Specifically,
-our bounds in parts 1, 2, 3, 4 of
+Appendix~\ref{section:proof-of-polynomial-approximation}. The geometric
+interpretation of the two regions $R^+$ and $R^-$ in the theorems is explained
+in Figure~\ref{figure:pizza-slice}. Similar but weaker results were proved
+by~\citet{Klivans-Servedio-2008}. Specifically, our bounds in parts 1, 2, 3, 4
+of
 Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
@@
 linearly separable set of examples. Due to space constraints, we defer the full
-proof to Appendix~\ref{section:proof-of-theorem-margin-transformation}.
+proof of Theorem~\ref{theorem:margin-transformation} to
+Appendix~\ref{section:proof-of-theorem-margin-transformation}.
 

### 2019-02-05 arxiv/notions-of-linear-separability.tex
added arxiv folder

--- 2019-01-23 ICML-submission/notions-of-linear-separability.tex
@@
 first notion is the standard notion of linear separability used in the proof of
-the mistake bound for the \textsc{Multiclass Perceptron} algorithm. The second
+the mistake bound for the \textsc{Multiclass Perceptron} algorithm\citep[see e.g.][]{Crammer-Singer-2003}. The second
 notion is stronger, i.e. more restrictive. %However, it is more suitable for the

### 2019-02-05 arxiv/title-and-abstract.tex
added arxiv folder

--- 2019-02-05 ICML-submission/title-and-abstract.tex
@@
 % Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case}
+%\icmltitlerunning{Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case}
 
-\twocolumn[
-\icmltitle{Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case}
+%\twocolumn[
+%\icmltitle{Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case}
 
-\begin{icmlauthorlist}
-\icmlauthor{Alina Beygelzimer}{yahoo}
-\icmlauthor{D\'avid P\'al}{yahoo}
-\icmlauthor{Bal\'azs Sz\"or\'enyi}{yahoo}
-\icmlauthor{Devanathan Thiruvenkatachari}{nyu}
-\icmlauthor{Chen-Yu Wei}{usc}
-\icmlauthor{Chicheng Zhang}{microsoft}
+\title{Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case}
 
-\end{icmlauthorlist}
+%\begin{icmlauthorlist}
+\author[1]{Alina Beygelzimer}
+\author[1]{D\'avid P\'al}
+\author[1]{Bal\'azs Sz\"or\'enyi}
+\author[2]{Devanathan Thiruvenkatachari}
+\author[3]{Chen-Yu Wei}
+\author[4]{Chicheng Zhang}
 
-\icmlaffiliation{yahoo}{Yahoo Research, New York, NY, USA}
-\icmlaffiliation{nyu}{New York University, New York, MA, USA}
-\icmlaffiliation{usc}{University of Southern California, Los Angeles, CA, USA}
-\icmlaffiliation{microsoft}{Microsoft Research, New York, NY, USA}
+%\end{icmlauthorlist}
 
-\icmlcorrespondingauthor{D\'avid P\'al}{davidko.pal@gmail.com}
+\affil[1]{Yahoo Research, New York, NY, USA}
+\affil[2]{New York University, New York, MA, USA}
+\affil[3]{University of Southern California, Los Angeles, CA, USA}
+\affil[4]{Microsoft Research, New York, NY, USA}
 
-\icmlkeywords{multi-armed bandits, contextual bandits, online classification, linear separability}
+\maketitle
+%\icmlcorrespondingauthor{D\'avid P\'al}{davidko.pal@gmail.com}
 
-\vskip 0.3in
-]
+%\icmlkeywords{multi-armed bandits, contextual bandits, online classification, linear separability}
 
-\printAffiliationsAndNotice{}
+%\vskip 0.3in
+%]
+
+%\printAffiliationsAndNotice{}
 

### 2019-02-05 arxiv/appendix-experiment.tex
widened the eqns

--- 2019-01-23 ICML-submission/appendix-experiment.tex
@@
 and~\ref{figure:number-of-mistakes-weakly-separable-dataset}), i.e. its decision boundaries
-output at round $T+1$.
+output at the end of round $T = 5 \times 10^6$.
 
@@
         \begin{center}
-        \hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_banditron_points}
+        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_banditron_points}
         \caption{Strongly separable case}
@@
     \end{subfigure}
-    \hfill
     \begin{subfigure}[b]{0.23\textwidth}
@@
         \centering
-        \hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_banditron_points}
+        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_banditron_points}
          \caption{Weakly separable case}
     \end{subfigure}
-    \vspace*{-0.2cm}
+    \captionsetup{justification=centering}
     \caption{\textsc{Banditron}'s final decision boundaries}
@@
         \begin{center}
-        \hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_linear_ova_points}
+        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_linear_ova_points}
         \caption{Strongly separable case}
@@
         \centering
-        \hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_linear_ova_points}
+        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_linear_ova_points}
          \caption{Weakly separable case}
     \end{subfigure}
-    \vspace*{-0.2cm}
+    \captionsetup{justification=centering}
     \caption{Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}'s final decision boundaries}
@@
         \begin{center}
-        \hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_rational_ova_points}
+        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_rational_ova_points}
         \caption{Strongly separable case}
@@
         \centering
-        \hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_rational_ova_points}
+        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_rational_ova_points}
          \caption{Weakly separable case}
     \end{subfigure}
-    \vspace*{-0.2cm}
+    \captionsetup{justification=centering}
     \caption{Algorithm~\ref{algorithm:kernelized} (with rational kernel)'s final decision boundaries}

### 2019-02-05 arxiv/empirical-comparison.tex
widened the eqns

@@
   \centering
-\begin{subfigure}[b]{0.23\textwidth}
+\begin{subfigure}[b]{0.3\textwidth}
 \captionsetup{justification=centering}
 \begin{center}
-\hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_points}
+\includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_points}
 \caption{Strongly separable case}
@@
 \end{subfigure}
-\hfill
-\begin{subfigure}[b]{0.23\textwidth}
+\begin{subfigure}[b]{0.3\textwidth}
 \captionsetup{justification=centering}
 \centering
-\hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_points}
+\includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_points}
 \caption{Weakly separable case}
@@
 \end{subfigure}
-\vspace*{-0.2cm}
 \caption{Strongly and weakly linearly separable datasets in $\R^3$ with $K=3$

### 2019-02-05 arxiv/mistake-lower-bound-for-ignorant-algorithms.tex
widened the eqns

--- 2019-02-05 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
@@
 $\calA$ and an adversarial strategy, we define
-\begin{multline*}
+\[
 p_t(y|x) = \\
 \Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] \; .
-\end{multline*}
+\]
 In other words, in any round $t$, conditioned on the past $t-1$ rounds, the
@@
 $p_t$ is determined solely by the sequence
-$(x_{a_1}, y_{a_1}), (x_{a_2}, y_{a_2}), \dots, (x_{a_n}, y_{a_n})$
+$(x_{a_1}, y_{a_1})$,$(x_{a_2}, y_{a_2})$, $\dots$, $(x_{a_n}, y_{a_n})$
 of labeled examples
@@
 To explain the definition, consider an ignorant algorithm $\calA$. Suppose that
-on a sequence of examples $(x_1, y_1), (x_2, y_2), \dots, (x_{t-1}, y_{t-1})$
+on a sequence of examples $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_{t-1}, y_{t-1})$
 generated by some adversary the algorthm $\calA$ makes correct predictions in
@@
 \end{align*}
-Then, the definition
-\begin{multline*}
-\Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] = \\
+Then, as $\calA$ is ignorant,
+\[
+\Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] =
 \Pr[y_t' = y ~|~ (x_1', y_1'), (x_2', y_2') \dots, (x_{t-1}', y_{t-1}'), x_t' = x] \; .
-\end{multline*}
+\]
 Note that the sequences $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_{t-1},
@@
 Let $\gamma \in (0,\frac{1}{160})$, let $d$ be a positive integer and let $N = (\frac{1}{2\sqrt{40\gamma}})^{d-2}$.
-There exist vectors $u_1, u_2, \dots, u_N, v_1, v_2, \dots, v_N \in \R^d$ such that for all $i, j \in \{1,2,\dots,N\}$,
+There exist vectors $u_1, u_2, \dots, u_N$, $v_1, v_2, \dots, v_N$ in $\R^d$ such that for all $i, j \in \{1,2,\dots,N\}$,
 \begin{align*}
@@
 \norm{v_j} & \le 1 \; , \\
-\ip{u_i}{v_j} & \ge \gamma & & \text{if $i=j$,} \\
-\ip{u_i}{v_j} & \le -\gamma & & \text{if $i \neq j$.}
+\ip{u_i}{v_j} & \ge \gamma, \quad \text{if $i=j$,} \\
+\ip{u_i}{v_j} & \le -\gamma, \quad \text{if $i \neq j$.}
 \end{align*}
@@
 \begin{align*}
-\ip{z_i}{z_j} &= 1 && \text{if $i = j$,} \\
-\ip{z_i}{z_j} &\le 1 - 8\gamma && \text{if $i \neq j$.}
+\ip{z_i}{z_j} &= 1, \quad \text{if $i = j$,} \\
+\ip{z_i}{z_j} &\le 1 - 8\gamma, \quad \text{if $i \neq j$.}
 \end{align*}
@@
 \begin{align*}
-\ip{u_i}{v_j} &\ge \gamma && \text{if $i=j$,} \\
-\ip{u_i}{v_j} &\le -\gamma && \text{if $i \neq j$.}
+\ip{u_i}{v_j} &\ge \gamma, \quad \text{if $i=j$,} \\
+\ip{u_i}{v_j} &\le -\gamma, \quad \text{if $i \neq j$.}
 \end{align*}
@@
 Then,
-\begin{align}
-& \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
-& \ge \Exp\left[\sum_{t=1}^{\tau - 1} \indicator{\widehat y_t\neq y_t}\right]
+\begin{align*}
+ \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right]
+ \ge \Exp\left[\sum_{t=1}^{\tau - 1} \indicator{\widehat y_t\neq y_t}\right]
 + \Exp\left[\sum_{t=\tau}^T \indicator{\widehat y_t\neq y_t}\right] \; .
-\end{align}
+\end{align*}
 We upper bound each of last two terms separately.
@@
 \begin{align*}
-& \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
+ \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] 
 & \ge q_0 \Exp[\tau - 1] + \Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right)\right] \\

### 2019-02-05 draft/notions-of-linear-separability.tex
rename arxiv

--- 2019-01-09 arxiv-version/notions-of-linear-separability.tex
@@
 \end{align}
-\label{def:linear-sep}
 \end{definition}
@@
 \end{align}
-\label{def:strong-linear-sep}
 \end{definition}

### 2019-02-05 ICML-submission/appendix-multiclass-perceptron.tex
Fixes
revert icml submission folder

@@
 \label{algorithm:mutliclass-classification}}
-\begin{algorithmic}[1]
-{
-\REQUIRE{Number of classes $K$. Number of rounds $T$.}
-\FOR{$t=1,2,\dots,T$}
-\STATE{Observe feature vector $x_t$}
-\STATE{Predict $\widehat y_t \in \{1,2,\dots,K\}$}
-\STATE{Observe $y_t \in \{1,2,\dots,K\}$}
-\ENDFOR
+\textbf{Require:} Number of classes $K$, number of rounds $T$. \\
+\textbf{Require:} Inner product space $(V,\ip{\cdot}{\cdot})$. \\
+\For{$t=1,2,\dots,T$}{
+Adversary chooses example $(x_t, y_t) \in V \times \{1,2,\dots,K\}$, where $x_t$ is revealed to the learner.\\
+Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
+Observe feedback $y_t$
 }
-\end{algorithmic}
 \end{protocol}

### 2019-02-05 ICML-submission/introduction.tex
revert icml submission folder

--- 2019-01-23 ICML-submission/introduction.tex
@@
 mistake bound under the strong linear separability condition, their
-Theorem 2 is incorrect: first, their Lemma 1 (with $C = +\infty$) along with Theorem 1
+Theorem~2 is incorrect: first, their Lemma~1 (with $C = +\infty$) along with their Theorem~1
 implies a mistake upper bound of
-$(\frac{R}{\gamma})^2$, which contradicts our lower
-bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
-second, their Lemma 1 cannot be directly applied to the bandit setting, as the
-algorithm only makes updates on a subset of the $w_i$'s.} We design a simple and
+$(\frac{R}{\gamma})^2$, which contradicts the lower
+bound in our Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
+second, their Lemma~1 cannot be directly applied to the bandit setting.} We design a simple and
 efficient algorithm

### 2019-02-05 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
revert icml submission folder

--- 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
@@
 & \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
-& \ge q_0 \Exp[\tau] + \Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-T_1+1}\right)\right] \\
+& \ge q_0 \Exp[\tau] + \Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right)\right] \\
 & =  \Exp \left[ \Exp \left[ q_0 \tau + \frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \right] \; .

### 2019-02-05 arxiv/introduction.tex
very minor change

--- 2019-02-05 ICML-submission/introduction.tex
@@
 long time whether there exist \textit{efficient} algorithms with finite mistake
-bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}.
+bound~\citep{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}.
 Furthermore, \citet{Kakade-Shalev-Shwartz-Tewari-2008} ask the question:
@@
 making Algorithm~\ref{algorithm:kernelized} computationally efficient. For
-details on kernel methods see e.g.~\citet{Scholkopf-Smola-2002} or
-\citet{Shawe-Taylor-Cristianini-2004}.
+details on kernel methods see e.g.~\citep{Scholkopf-Smola-2002} or
+\citep{Shawe-Taylor-Cristianini-2004}.
 

### 2019-02-05 arxiv/related-work.tex
very minor change

--- 2019-02-05 ICML-submission/related-work.tex
@@
 
-The general problem of linear bandit multiclass learning has received considerable attention~\cite{Abernethy-Rakhlin-2009, Wang-Jin-Valizadegan-2010,
+The general problem of linear bandit multiclass learning has received considerable attention~\citep{Abernethy-Rakhlin-2009, Wang-Jin-Valizadegan-2010,
 Crammer-Gentile-2013, Hazan-Kale-2011, Beygelzimer-Orabona-Zhang-2017,
@@
 where the cost $c_t(i)$ is the classification error $\indicator{i \neq y_t}$ and
-the policy class is the set of linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$.
+the policy class is the set of linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{K \times d}}$.
 There has been significant progress on the general contextual bandit problem
@@
 the other hand, it gives an efficient algorithm with an $O(\sqrt{T})$ regret
-against the benchmark of $\calF = \cbr{x \mapsto W x: W \in \R^{k \times d},
+against the benchmark of $\calF = \cbr{x \mapsto W x: W \in \R^{K \times d},
 \one^T W = 0}$. A direct application of this result to \textsc{Online Bandit

### 2019-02-06 arxiv/mistake-lower-bound-for-ignorant-algorithms.tex
elaborating on truncated geom

@@
 $$
-Since the algorithm is ignorant, conditioned on $\tau$, the random variable $s-\tau$
-has a truncated geometric distribution with parameter $p_\tau(2|v_\tau) \le q_0$.
+Since the algorithm is ignorant, conditioned on $\tau$, $s-\tau+1$ has the same distribution as
+$\min(X, T-\tau+2)$, where $X$ is drawn from a geometric distribution with parameter
+$p_\tau(2|v_\tau)$.
+
+By Lemma~\ref{lem:truncated-geom} below,
+\[
+  \Exp\left[s-\tau+1 \mid \tau, p_\tau(2|v_\tau) \right] = F(p_\tau(2|v_\tau), T-\tau+2) \geq F(q_0, T-\tau+2).
+\]
 Therefore,
@@
 \ge
-\Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \; .
+F(q_0, T-\tau+2) - 1
+=
+\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) \; .
 $$
+
+%the random variable $s-\tau+1$
+%has a truncated geometric distribution with parameter $p_\tau(2|v_\tau) \le q_0$.
+%Specifically, conditioned on $\tau$,
 
@@
 (x_T, y_T) = (v_\tau, 2)$. Consider the vectors $u_1, u_2, \dots, u_N$ as
-defined in Lemma~\ref{lemma:embed_d_gamma} We claim that $w_1=-u_\tau/2$ and
+defined in Lemma~\ref{lemma:embed_d_gamma}. We claim that $w_1=-u_\tau/2$ and
 $w_2=u_\tau/2$ satisfy the conditions of strong linear separability.
@@
 \end{proof}
+
+\begin{lemma}
+For $p \in (0,1)$ and $N \geq 1$, denote by $F(p, N) = \frac{1}{p}(1 - (1-p)^N)$.
+\begin{enumerate}
+  \item $F(p, N)$ is monotonically decreasing in $p$.
+  \item If $X \sim \Geom(p)$, then $\Exp[\min(X, N)] = F(p, N)$.
+\end{enumerate}
+\label{lem:truncated-geom}
+\end{lemma}
+\begin{proof}
+We show the two items respectively.
+\begin{enumerate}
+\item By calculus,
+\[ \frac{\partial F(p,n)}{\partial p} = \frac{(1-p)^{N-1} (1 + (N-1)p) - 1}{p^2}. \]
+Now, note that for any $p \in (0,1)$,
+\[ (1 + (N-1)p) \leq \frac{1}{(1 - p)^{N-1}} \]
+We therefore get $\frac{\partial F(p,n)}{\partial p} < 0$ for all $p$, showing the first item.
+
+\item We have the following decomposition on $\Exp[X]$:
+\[ \Exp[X] = \Exp[X \one[X \leq N]] + \Prob(X \geq N+1) \Exp[X|X \geq N+1] \]
+By the memoryless property of geometric distribution, $\Exp[X|X \geq N+1] = N + \Exp[X] = N + \frac 1 p$.
+Therefore,
+\[ \Exp[X] = \Exp[X \one[X \leq N]] + \Prob(X \geq N+1) \cdot N + \Prob(X \geq N+1) \cdot \frac 1 p. \]
+At the same time, observe that $\Exp[X \one[X \leq N]] + \Prob(X \geq N+1) \cdot N = \Exp[\min(X, N)]$.
+Therefore,
+\[ \Exp[\min(X, N)] = \frac 1 p \cdot (1 - \Prob(X \geq N+1)) = \frac{1}{p}(1 - (1-p)^N) = F(p, N). \qedhere \]
+\end{enumerate}
+\end{proof}

### 2019-02-06 arxiv/mistake-lower-bound-for-ignorant-algorithms.tex
.

--- 2019-02-05 arxiv/mistake-lower-bound-for-ignorant-algorithms.tex
@@
 $$
-Since the algorithm is ignorant, conditioned on $\tau$, the random variable $s-\tau$
-has a truncated geometric distribution with parameter $p_\tau(2|v_\tau) \le q_0$.
-Therefore,
-$$
-\Exp[s-\tau ~|~ \tau]
-\ge
-\Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \; .
-$$
+%Since the algorithm is ignorant, conditioned on $\tau$, $s-\tau+1$ has the same distribution as
+%$\min(X, T-\tau+2)$, where $X$ is drawn from a geometric distribution with parameter
+%$p_\tau(2|v_\tau)$.
+Since the algorithm is ignorant, conditiond on $\tau$, $s-\tau$ follows a truncated 
+geometric distribution with parameter $q\triangleq p_\tau(2|v_\tau)$
+(i.e., $s-\tau$ is $0$ with probability $q$, $1$ with probability $(1-q)q$, $2$ with probability $(1-q)^2q, \ldots$). Its expectation can be calculated as follows: 
+\begin{align*}
+\Exp[s-\tau~|~\tau] 
+&= \sum_{i=1}^{T+1-\tau} i\times  \Pr[s-\tau=i]= \sum_{i=1}^{T+1-\tau}\sum_{j=1}^i \Pr[s-\tau=i] = \sum_{j=1}^{T+1-\tau}\sum_{i=j}^{T+1-\tau} \Pr[s-\tau=i] \\
+&= \sum_{j=1}^{T+1-\tau}\Pr[s-\tau\geq j] = \sum_{j=1}^{T+1-\tau}(1-q)^j \geq  \sum_{j=1}^{T+1-\tau}(1-q_0)^j = \frac{1-q_0}{q_0}\left( 1-(1-q_0)^{T-\tau+1} \right). 
+\end{align*}
+%By Lemma~\ref{lem:truncated-geom} below,
+%\[
+%  \Exp\left[s-\tau+1 \mid \tau, p_\tau(2|v_\tau) \right] = F(p_\tau(2|v_\tau), T-\tau+2) \geq F(q_0, T-\tau+2).
+%\]
+%Therefore,
+%$$
+%\Exp[s-\tau ~|~ \tau]
+%\ge
+%F(q_0, T-\tau+2) - 1
+%=
+%\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) \; .
+%$$
+
+%the random variable $s-\tau+1$
+%has a truncated geometric distribution with parameter $p_\tau(2|v_\tau) \le q_0$.
+%Specifically, conditioned on $\tau$,
 
@@
 \end{proof}
+
+%\begin{lemma}
+%For $p \in (0,1)$ and $N \geq 1$, denote by $F(p, N) = \frac{1}{p}(1 - (1-p)^N)$.
+%\begin{enumerate}
+%  \item $F(p, N)$ is monotonically decreasing in $p$.
+%  \item If $X \sim \Geom(p)$, then $\Exp[\min(X, N)] = F(p, N)$.
+%\end{enumerate}
+%\label{lem:truncated-geom}
+%\end{lemma}
+%\begin{proof}
+%We show the two items respectively.
+%\begin{enumerate}
+%\item By calculus,
+%\[ \frac{\partial F(p,n)}{\partial p} = \frac{(1-p)^{N-1} (1 + (N-1)p) - 1}{p^2}. \]
+%Now, note that for any $p \in (0,1)$,
+%\[ (1 + (N-1)p) \leq \frac{1}{(1 - p)^{N-1}} \]
+%We therefore get $\frac{\partial F(p,n)}{\partial p} < 0$ for all $p$, showing the first item.
+
+%\item We have the following decomposition on $\Exp[X]$:
+%\[ \Exp[X] = \Exp[X \one[X \leq N]] + \Prob(X \geq N+1) \Exp[X|X \geq N+1] \]
+%By the memoryless property of geometric distribution, $\Exp[X|X \geq N+1] = N + \Exp[X] = N + \frac 1 p$.
+%Therefore,
+%\[ \Exp[X] = \Exp[X \one[X \leq N]] + \Prob(X \geq N+1) \cdot N + \Prob(X \geq N+1) \cdot \frac 1 p. \]
+%At the same time, observe that $\Exp[X \one[X \leq N]] + \Prob(X \geq N+1) \cdot N = \Exp[\min(X, N)]$.
+%Therefore,
+%\[ \Exp[\min(X, N)] = \frac 1 p \cdot (1 - \Prob(X \geq N+1)) = \frac{1}{p}(1 - (1-p)^N) = F(p, N). \qedhere \]
+%\end{enumerate}
+%\end{proof}

### 2019-02-06 arxiv/np-hardness-of-the-weak-labeling-problem.tex
widened the eqns
.

--- 2019-02-05 ICML-submission/np-hardness-of-the-weak-labeling-problem.tex
@@
 We use symbols $1,2,\dots,K$ for strong labels and symbols $\overline{1},
-\overline{2}, \dots, \overline{K}$ for weak labels. We adopt the convention that
-$\overline{\overline{i}} = i$ for any symbol $i$. Formally, the weak
+\overline{2}, \dots, \overline{K}$ for weak labels. Formally, the weak
 labeling problem can be described as below:
@@
 \begin{align*}
-& y_t \in \{1,2,\dots,K\} \Longrightarrow  \\
-& \quad \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \quad \ip{w_{y_t}}{x_t}  > \ip{w_i}{x_t} \; , \\
+& y_t \in \{1,2,\dots,K\} \Longrightarrow \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \quad \ip{w_{y_t}}{x_t}  > \ip{w_i}{x_t} \; , \\
 & \text{and} \\
-& y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \Longrightarrow \\
-& \quad \exists i \in \{1,2,\dots,K\} \quad \ip{w_i}{x_t} > \ip{w_{\overline{y_t}}}{x_t} \; ?
+& y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \Longrightarrow \exists i \in \{1,2,\dots,K\} \quad \ip{w_i}{x_t} > \ip{w_{\overline{y_t}}}{x_t} \; ?
 \end{align*}
@@
 \begin{align*}
-S & = \{1, 2, \dots, N\} \; , \\
-C & = \{c_1, c_2, \dots, c_M\} \; .
+S = \{1, 2, \dots, N\} \; ,
+C = \{c_1, c_2, \dots, c_M\} \; .
 \end{align*}
@@
 $c_2=\{2,3\}$, then we create the weak labeling sample set as:
-\begin{multline*}
+\[
 \{
-((0,0,0,1),3), ((1,0,0,1),\overline{3}), ((0,1,0,1),\overline{3}), \\
+((0,0,0,1),3), ((1,0,0,1),\overline{3}), ((0,1,0,1),\overline{3}),
 ((0,0,1,1),\overline{3}), ((1,1,0,1),3), ((0,1,1,1),3)
 \} \; .
-\end{multline*}
+\]
 The following lemma shows that answering this weak labeling problem is
@@
 & = a_{i'}x_{i'} + \sum_{i\in \{1,2,\dots,N\} \setminus \{i'\}} a_ix_i - \frac{1}{2} \\
-& \le -N + (N-1)-\frac{1}{2} \\
-& < 0  \\
-& = \ip{w_3}{x} \; .
+& \le -N + (N-1)-\frac{1}{2} < 0 = \ip{w_3}{x} \; .
 \end{align*}
@@
 S_1 &= \left\{i \in \{1,2,\dots,n\} ~:~ \ip{w_1-w_3}{(\e_i, 1)} > 0 \right\}, \\
-S_2 &= \left\{i \in \{1,2,\dots,n\} ~:~ \ip{w_2-w_3}{(\e_i, 1)} > 0 \right. \\
-& \qquad \qquad \qquad \left. \text{\ and\ } i \notin S_1 \right\}.
+S_2 &= \left\{i \in \{1,2,\dots,n\} ~:~ \ip{w_2-w_3}{(\e_i, 1)} > 0 \text{\ and\ } i \notin S_1 \right\}.
 \end{align*}
@@
 \sum_{i\in c_j} \ip{w_1-w_3}{\left(\e_i, 1\right)}
-& = \ip{w_1-w_3}{\left(\sum_{i\in c_j} \e_i, |c_j|\right)}  \\
-& > 0.
+ = \ip{w_1-w_3}{\left(\sum_{i\in c_j} \e_i, |c_j|\right)} > 0.
 \end{align*}
@@
 \begin{align*}
-& \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, 1\right)} \\
-& = \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, |c_j|\right)}  \\
-& \qquad - (|c_j|-1)\ip{w_1-w_3}{\left(\zero, 1\right)} \\
-& > 0 \; .
+& \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, 1\right)}
+ = \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, |c_j|\right)} - (|c_j|-1)\ip{w_1-w_3}{\left(\zero, 1\right)}  > 0 \; .
 \end{align*}

### 2019-02-06 arxiv/appendix-experiment.tex
refer to pdfs as opposed to eps to save space

@@
     \centering
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \captionsetup{justification=centering}
         \begin{center}
-        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_banditron_points}
+        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_banditron_points.pdf}
         \caption{Strongly separable case}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \captionsetup{justification=centering}
         \centering
-        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_banditron_points}
+        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_banditron_points.pdf}
          \caption{Weakly separable case}
@@
     \centering
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \captionsetup{justification=centering}
         \begin{center}
-        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_linear_ova_points}
+        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_linear_ova_points.pdf}
         \caption{Strongly separable case}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \captionsetup{justification=centering}
         \centering
-        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_linear_ova_points}
+        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_linear_ova_points.pdf}
          \caption{Weakly separable case}
@@
     \centering
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \captionsetup{justification=centering}
         \begin{center}
-        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_rational_ova_points}
+        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_rational_ova_points.pdf}
         \caption{Strongly separable case}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \captionsetup{justification=centering}
         \centering
-        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_rational_ova_points}
+        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_rational_ova_points.pdf}
          \caption{Weakly separable case}

### 2019-02-06 arxiv/empirical-comparison.tex
.
refer to pdfs as opposed to eps to save space

@@
 \begin{center}
-\includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_points}
+\includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_points.pdf}
 \caption{Strongly separable case}
@@
 \centering
-\includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_points}
+\includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_points.pdf}
 \caption{Weakly separable case}
@@
 
-\begin{figure}
+\begin{minipage}{.45\textwidth}
+\begin{figure}[H]
 \centering
-\includegraphics[width=0.42\textwidth]{figures/strong3}
+\includegraphics[width=0.98\textwidth]{figures/strong3}
 \caption{Average cumulative number of mistakes of various algorithms versus the
@@
 \end{figure}
-
-\begin{figure}
+\end{minipage}
+\hfill
+\begin{minipage}{.45\textwidth}
+\begin{figure}[H]
 \centering
-\includegraphics[width=0.42\textwidth]{figures/weak3}
+\includegraphics[width=0.98\textwidth]{figures/weak3}
 \caption{Average cumulative number of mistakes of various algorithms versus the
@@
 \end{figure}
+\end{minipage}

### 2019-03-10 ICML-submission/rebuttal.txt
some comments on the theoretical parts in the rebuttal

We thank all reviewers for their insightful comments. We will make a pass,
and incorporate all the detailed comments in the final version of the paper.

We believe that extending the algorithms to handle the general
contextual bandit learning setting (where each example is associated
with a cost vector) requires nontrivial modifications to the algorithm;
a first step towards this question would be to establish
regret guarantees for when the examples shown is still multiclass, but
linearly nonseparable - we leave this for future work.

Regarding Appendix G, we agree that it is not related to the main story
 of the paper. Nevertheless, we think that this is a baseline that has not
 appeared in the literature and we include it for completeness.

We will add some discussions on achievable mistake bounds in the weakly
linearly separable case,
and its interaction with computational efficiency requirements.
It is known that in (Daniely and Herbertal, 2013)
that when 1/gamma^2 < d, any algorithm must make \Omega(K / \gamma^2) mistakes,
and when 1/gamma^2 > K^3 d, any algorithm must make \Omega( d K^2 ) mistakes.
In addition, (Daniely and Herbertal, 2013) gives a computationally inefficient
 algorithm that has a mistake upper bound of \tilde{O}( \min( K/\gamma^2, d K^2) );
 the algorithm involves a key step of computing (margin-based) Littlestone dimensions of subsets of multiclass linear classifiers, which is not known how to do efficiently.

### 2019-03-10 ICML-submission/rebuttal.txt
a pass over rebutal

@@
-We thank all reviewers for their insightful comments. We will make a pass,
-and incorporate all the detailed comments in the final version of the paper.
+We thank all reviewers for their insightful comments. We will make a pass, and incorporate all the detailed comments in the final version of the paper.
 
-We believe that extending the algorithms to handle the general
-contextual bandit learning setting (where each example is associated
-with a cost vector) requires nontrivial modifications to the algorithm;
-a first step towards this question would be to establish
-regret guarantees for when the examples shown is still multiclass, but
-linearly nonseparable - we leave this for future work.
+-----
+Reviewer #2
+We believe that extending the algorithms to handle the general contextual bandit learning setting (where each example is associated with a cost vector) requires nontrivial modifications to the algorithm; a first step towards this question would be to establish regret guarantees for when the examples shown is still multiclass, but linearly nonseparable - we leave this for future work.
 
-Regarding Appendix G, we agree that it is not related to the main story
- of the paper. Nevertheless, we think that this is a baseline that has not
- appeared in the literature and we include it for completeness.
+Regarding Appendix G, we agree that it is not related to the main story of the paper.
+Nevertheless, we think that this is a baseline that has not appeared in the literature and we include it for completeness.
 
-We will add some discussions on achievable mistake bounds in the weakly
-linearly separable case,
-and its interaction with computational efficiency requirements.
-It is known that in (Daniely and Herbertal, 2013)
-that when 1/gamma^2 < d, any algorithm must make \Omega(K / \gamma^2) mistakes,
-and when 1/gamma^2 > K^3 d, any algorithm must make \Omega( d K^2 ) mistakes.
-In addition, (Daniely and Herbertal, 2013) gives a computationally inefficient
- algorithm that has a mistake upper bound of \tilde{O}( \min( K/\gamma^2, d K^2) );
- the algorithm involves a key step of computing (margin-based) Littlestone dimensions of subsets of multiclass linear classifiers, which is not known how to do efficiently.
+In Appendix F, the Banditron's boundary is plot with the version with the largest exploration rate (the 0.02 one in Figure 4 and 5).
+This version explores the most, and gives the most accurate decision boundary.
+We would add more explanation on this in the final version.
+
+-----
+Reviewer #3 and #5
+We will add some discussions on achievable mistake bounds in the weakly linearly separable case, and its interaction with computational efficiency requirements.
+It is known that in (Daniely and Herbertal, 2013) that when 1/gamma^2 < d, any algorithm must make \Omega(K / \gamma^2) mistakes, and when 1/gamma^2 > K^3 d, any algorithm must make \Omega( d K^2 ) mistakes.
+In addition, (Daniely and Herbertal, 2013) gives a computationally inefficient algorithm that has a mistake upper bound of \tilde{O}( \min( K/\gamma^2, d K^2) ); the algorithm involves a key step of computing (margin-based) Littlestone dimensions of subsets of multiclass linear classifiers, which is not known how to do efficiently.
+
+-----
+Reviewer #5
+i.
+We leave the non-separable case as an important future direction.
+Using our current analysis framework, we believe that there will still involve the quasi-polynomial factors on K and \gamma; and the bound will only depend on L, the number of mistakes made by the best linear classifier, instead of T.
+To derive this, one can first re-derive our Theorem 2 for the non-separable case, and then again use the kernel trick.
+
+ii.
+"Efficient" means that run-time is polynomial in K, d, \gamma, T.
+This follows the typical definition in online learning literature, but we will more formally define it in the final version.
+Since J_i^{(t)} only includes the samples on which the i-th binary perceptron makes mistakes, in the separable case, their number will be finite based on perceptron's guarantee.
+Therefore, it can be much better than O(t) in the separable case.
+
+iii.
+Our work indeed only improves Kakade et al.
+and Daniely & Helbert et al.'s algorithms in efficiency, but not in mistake bound.
+Why Daniely and Herbertal's algorithm is inefficient is answered above.
+
+iv.
+Larger-scale experiment on real data is also a future work.
+Currently our experiment section is more for verifying that the algorithm indeed works as expected.
+We will improve our figure based on your suggestion.
+
+v. See above for the answer.

### 2019-03-12 ICML-submission/rebuttal.txt
a pass over rebuttal
answering Reviewer 4

@@
-We thank all reviewers for their insightful comments. We will make a pass, and incorporate all the detailed comments in the final version of the paper.
+We thank all reviewers for their insightful comments. 
+We will make a pass, and incorporate all the detailed 
+comments in the final version of the paper.
 
@@
 Reviewer #2
-We believe that extending the algorithms to handle the general contextual bandit learning setting (where each example is associated with a cost vector) requires nontrivial modifications to the algorithm; a first step towards this question would be to establish regret guarantees for when the examples shown is still multiclass, but linearly nonseparable - we leave this for future work.
+We believe that extending the algorithms to handle 
+the general contextual bandit learning setting (where 
+each example is associated with a cost vector) requires 
+nontrivial modifications to the algorithm; a first step 
+towards this question would be to establish regret 
+guarantees for when the examples shown is still multiclass, 
+but linearly nonseparable - we leave this for future work.
 
-Regarding Appendix G, we agree that it is not related to the main story of the paper.
-Nevertheless, we think that this is a baseline that has not appeared in the literature and we include it for completeness.
+Regarding Appendix G, we agree that it is not related 
+to the main story of the paper. Nevertheless, we think 
+that this is a baseline that has not appeared in the 
+literature and we include it for completeness.
 
-In Appendix F, the Banditron's boundary is plot with the version with the largest exploration rate (the 0.02 one in Figure 4 and 5).
-This version explores the most, and gives the most accurate decision boundary.
-We would add more explanation on this in the final version.
+In Appendix F, the Banditron's boundary is plot with the 
+version with the largest exploration rate (the 0.02 one 
+in Figure 4 and 5). This version explores the most, and 
+gives the most accurate decision boundary. We would add 
+more explanation on this in the final version.
+
+-----
+Reviewer #4
+Thanks for the clarification suggestions. We will incorporate 
+them into our final version.
 
@@
 Reviewer #3 and #5
-We will add some discussions on achievable mistake bounds in the weakly linearly separable case, and its interaction with computational efficiency requirements.
-It is known that in (Daniely and Herbertal, 2013) that when 1/gamma^2 < d, any algorithm must make \Omega(K / \gamma^2) mistakes, and when 1/gamma^2 > K^3 d, any algorithm must make \Omega( d K^2 ) mistakes.
-In addition, (Daniely and Herbertal, 2013) gives a computationally inefficient algorithm that has a mistake upper bound of \tilde{O}( \min( K/\gamma^2, d K^2) ); the algorithm involves a key step of computing (margin-based) Littlestone dimensions of subsets of multiclass linear classifiers, which is not known how to do efficiently.
+We will add some discussions on achievable mistake bounds 
+in the weakly linearly separable case, and its interaction 
+with computational efficiency requirements. It is known 
+that in (Daniely and Herbertal, 2013) that when 1/gamma^2 < d, 
+any algorithm must make \Omega(K / \gamma^2) mistakes, and 
+when 1/gamma^2 > K^3 d, any algorithm must make \Omega( d K^2 ) 
+mistakes. In addition, (Daniely and Herbertal, 2013) gives a 
+computationally inefficient algorithm that has a mistake 
+upper bound of \tilde{O}( \min( K/\gamma^2, d K^2) ); the 
+algorithm involves a key step of computing (margin-based) 
+Littlestone dimensions of subsets of multiclass linear 
+classifiers, which is not known how to do efficiently.
 
@@
 Reviewer #5
-i.
-We leave the non-separable case as an important future direction.
-Using our current analysis framework, we believe that there will still involve the quasi-polynomial factors on K and \gamma; and the bound will only depend on L, the number of mistakes made by the best linear classifier, instead of T.
-To derive this, one can first re-derive our Theorem 2 for the non-separable case, and then again use the kernel trick.
+i. We leave the non-separable case as an important future 
+direction. Using our current analysis framework, we believe 
+that there will still involve the quasi-polynomial factors 
+on K and \gamma; and the bound will only depend on L, the 
+number of mistakes made by the best linear classifier, instead 
+of T. To derive this, one can first re-derive our Theorem 2 
+for the non-separable case, and then again use the kernel trick.
 
-ii.
-"Efficient" means that run-time is polynomial in K, d, \gamma, T.
-This follows the typical definition in online learning literature, but we will more formally define it in the final version.
-Since J_i^{(t)} only includes the samples on which the i-th binary perceptron makes mistakes, in the separable case, their number will be finite based on perceptron's guarantee.
-Therefore, it can be much better than O(t) in the separable case.
+ii. "Efficient" means that run-time is polynomial in K, d, 
+\gamma, T. This follows the typical definition in online 
+learning literature, but we will more formally define it in 
+the final version. Since J_i^{(t)} only includes the samples 
+on which the i-th binary perceptron makes mistakes, in the 
+separable case, their number will be finite based on perceptron's 
+guarantee. Therefore, it can be much better than O(t) in the 
+separable case.
 
-iii.
-Our work indeed only improves Kakade et al.
-and Daniely & Helbert et al.'s algorithms in efficiency, but not in mistake bound.
-Why Daniely and Herbertal's algorithm is inefficient is answered above.
+iii. Our work indeed only improves Kakade et al. and 
+Daniely & Helbert et al.'s algorithms in efficiency, but not 
+in mistake bound. Why Daniely and Herbertal's algorithm is 
+inefficient is answered above.
 
-iv.
-Larger-scale experiment on real data is also a future work.
-Currently our experiment section is more for verifying that the algorithm indeed works as expected.
-We will improve our figure based on your suggestion.
+iv. Indeed, currently our experiment section is more for 
+verifying that the algorithm is working as expected. As a future
+work, we will test our algorithm on larger-scale and real problems.
 

### 2019-03-13 ICML-submission/rebuttal.txt
.
Fixes of the rebuttal

--- 2019-03-10 ICML-submission/rebuttal.txt
@@
-We thank all reviewers for their insightful comments. We will make a pass,
-and incorporate all the detailed comments in the final version of the paper.
+We thank all reviewers for their helpful comments.  We will incorporate all
+comments in the final version of the paper.
 
-We believe that extending the algorithms to handle the general
-contextual bandit learning setting (where each example is associated
-with a cost vector) requires nontrivial modifications to the algorithm;
-a first step towards this question would be to establish
-regret guarantees for when the examples shown is still multiclass, but
-linearly nonseparable - we leave this for future work.
+-----
+Reviewer #2
 
-Regarding Appendix G, we agree that it is not related to the main story
- of the paper. Nevertheless, we think that this is a baseline that has not
- appeared in the literature and we include it for completeness.
+Regarding Appendix G, we agree that it is not related to the main story of the
+paper. However, it is an important example of an "ignorant" algorithm and the
+lower bound that we prove in Appendix I applies to it.
 
-We will add some discussions on achievable mistake bounds in the weakly
-linearly separable case,
-and its interaction with computational efficiency requirements.
-It is known that in (Daniely and Herbertal, 2013)
-that when 1/gamma^2 < d, any algorithm must make \Omega(K / \gamma^2) mistakes,
-and when 1/gamma^2 > K^3 d, any algorithm must make \Omega( d K^2 ) mistakes.
-In addition, (Daniely and Herbertal, 2013) gives a computationally inefficient
- algorithm that has a mistake upper bound of \tilde{O}( \min( K/\gamma^2, d K^2) );
- the algorithm involves a key step of computing (margin-based) Littlestone dimensions of subsets of multiclass linear classifiers, which is not known how to do efficiently.
+In Appendix F, the Banditron's boundary is plotted with the version with
+exploration rate of 0.02. This version explores the most, and gives the most
+accurate decision boundary. We would add more explanation on this in the final
+version.
+
+-----
+Reviewer #4
+
+(1) The problem was motivated in the Banditron paper (Kakade et al. 2008). One
+application area is web content optimization and web advertising.
+
+(2) The phenomenon of finite number of mistakes is explained by Theorem 2 and
+Corollary 6.
+
+-----
+Reviewer #3
+
+The lower bound for strongly separable case (Theorem 3) implies the same lower
+bound for the weakly separable case. This lower bound is actually tight, since
+there exists an (inefficient) algorithm that makes at most O(K / \gamma^2)
+mistakes due to Daniely and Herbertal, 2013 (see their Theorem 2).  We are not
+aware of any mistake lower bound for computationaly efficient algorithms under
+the weakly separable assumption. We will add a discussion in the paper.
+
+-----
+Reviewer #5
+
+i. There has been substanstial amount of work on the non-separable case
+as discussed in Section 2 (lines 128--137). Our paper focuses
+on the remaining open case when the data is linearly separable; there
+was non known computationaly efficient algorithm with finite mistake bound.
+
+ii. "Efficient" means that run-time is polynomial in K, d, 1/\gamma, T. We will
+define this explicitly in the paper.  Since J_i^{(t)} only includes the samples
+on which the i-th binary perceptron makes mistakes, in the separable case,
+their number will be finite based on perceptron's guarantee. The expected size of
+J_i^{(t)} is upper bounded by it min(t, (1/gamma')^2).
+
+iii. Our work indeed only improves Kakade et al. and Daniely & Helbert et al.'s
+algorithms in efficiency, but not in mistake bound.
+
+Daniely and Herbertal's algorithm is inefficient because it involves a key step
+of computing (margin-based) Littlestone dimensions of subsets of multiclass
+linear classifiers, which is not known how to do efficiently.
+
+iv. We will add error bars to the plots. The focus of this submission is
+largely theoretical and the goal of the experiments is to verift that the
+algorithms work as expected.
+
+v. See the answer for Reviewer #3.

### 2019-03-14 ICML-submission/rebuttal.txt
minor

@@
 
-In Appendix F, the Banditron's boundary is plotted with the version with
+In Appendix F, Banditron's decision boundary is plotted with the version with
 exploration rate of 0.02. This version explores the most, and gives the most
-accurate decision boundary. We would add more explanation on this in the final
+accurate decision boundary. We will add more explanation on this in the final
 version.
@@
 mistakes due to Daniely and Herbertal, 2013 (see their Theorem 2).  We are not
-aware of any mistake lower bound for computationaly efficient algorithms under
+aware of any mistake lower bound for computationally efficient algorithms under
 the weakly separable assumption. We will add a discussion in the paper.
@@
 
-i. There has been substanstial amount of work on the non-separable case
+i. There has been substantial amount of work on the non-separable case
 as discussed in Section 2 (lines 128--137). Our paper focuses
 on the remaining open case when the data is linearly separable; there
-was non known computationaly efficient algorithm with finite mistake bound.
+was no known computationally efficient algorithm with finite mistake bound before
+our work.
 
-ii. "Efficient" means that run-time is polynomial in K, d, 1/\gamma, T. We will
+ii. "Efficient" means that the run-time is polynomial in K, d, 1/\gamma, T. We will
 define this explicitly in the paper.  Since J_i^{(t)} only includes the samples
-on which the i-th binary perceptron makes mistakes, in the separable case,
-their number will be finite based on perceptron's guarantee. The expected size of
-J_i^{(t)} is upper bounded by it min(t, (1/gamma')^2).
+on which the i-th binary perceptron makes mistakes, its size is upper bounded by t.
+This implies that the algorithm runs in polynomial time.
 
-iii. Our work indeed only improves Kakade et al. and Daniely & Helbert et al.'s
-algorithms in efficiency, but not in mistake bound.
-
-Daniely and Herbertal's algorithm is inefficient because it involves a key step
+iii. Our work indeed only improves Kakade et al. and Daniely & Helbertal's
+algorithms in computational efficiency, but not in mistake bound.
+ - Kakade et al.'s algorithm is computationally inefficient because it requires
+enumerating over a grid of O(1/\gamma)^kd linear classifiers.
+ - Daniely & Helbertal's algorithm is computationally inefficient because it involves a key step
 of computing (margin-based) Littlestone dimensions of subsets of multiclass
@@
 iv. We will add error bars to the plots. The focus of this submission is
-largely theoretical and the goal of the experiments is to verift that the
+largely theoretical and the goal of the experiments is to verify that the
 algorithms work as expected.

### 2019-03-14 ICML-submission/rebuttal.txt
minor

@@
 
-(1) The problem was motivated in the Banditron paper (Kakade et al. 2008). One
+(1) The problem was motivated in the Banditron paper (Kakade et al., 2008). One
 application area is web content optimization and web advertising.
 
-(2) The phenomenon of finite number of mistakes is explained by Theorem 2 and
-Corollary 6.
+(2) The phenomenon of finite number of mistakes made by our algorithms with
+different settings of kernel functions is explained by Theorem 2 and Corollary 6.
 
@@
 there exists an (inefficient) algorithm that makes at most O(K / \gamma^2)
-mistakes due to Daniely and Herbertal, 2013 (see their Theorem 2).  We are not
+mistakes due to Daniely & Helbertal, 2013 (see their Theorem 2).  We are not
 aware of any mistake lower bound for computationally efficient algorithms under
@@
  - Daniely & Helbertal's algorithm is computationally inefficient because it involves a key step
-of computing (margin-based) Littlestone dimensions of subsets of multiclass
+of computing (margin-based) Littlestone's dimensions of subsets of multiclass
 linear classifiers, which is not known how to do efficiently.

### 2019-05-03 ICML-camera-ready/appendix-experiment.tex
add camera-ready folder

--- 2019-02-05 arxiv/appendix-experiment.tex
@@
     \centering
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \captionsetup{justification=centering}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \captionsetup{justification=centering}
@@
     \centering
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \captionsetup{justification=centering}
         \begin{center}
-        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_linear_ova_points}
+        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_linear_ova_points}
         \caption{Strongly separable case}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \captionsetup{justification=centering}
         \centering
-        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_linear_ova_points}
+        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_linear_ova_points}
          \caption{Weakly separable case}
@@
     \centering
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \captionsetup{justification=centering}
         \begin{center}
-        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_rational_ova_points}
+        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_rational_ova_points}
         \caption{Strongly separable case}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.25\textwidth}
         \captionsetup{justification=centering}
         \centering
-        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_rational_ova_points}
+        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_rational_ova_points}
          \caption{Weakly separable case}

### 2019-05-03 ICML-camera-ready/appendix-proofs-of-polynomial-approximation-theorems.tex
add camera-ready folder

--- 2019-02-05 ICML-submission/appendix-proofs-of-polynomial-approximation-theorems.tex
@@
 \autoref{lemma:simple-inequality} implies that for any multi-index $A$,
-\begin{multline*}
-\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
+\[
+\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
 \le M_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
-\end{multline*}
+\]
 where $M_A$ is the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 +
@@
 
-To prove the part 3, we use generalized triangle inequality and
+To prove part 3, we use generalized triangle inequality and
 \autoref{lemma:simple-inequality}. We have
-\begin{multline*}
-\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \\ \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
-\end{multline*}
+\[
+\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
+\]
 \end{proof}
@@
 T_0(z) & = 1  \; , \\
-T_1(z) & = z \; , \\
-T_{n+1}(z) & = 2zT_n(z) - T_{n-1}(z) & \text{for $n \ge 1$.}
+T_1(z) & = z  \; ,\\
+T_{n+1}(z) & = 2zT_n(z) - T_{n-1}(z), \quad \text{for $n \ge 1$.}
 \end{align*}
@@
 \begin{align*}
-p(x) & = m + \frac{1}{2} - \left( T_s(1 - \ip{v_i}{x}) \right)^r \\
-& \qquad - \sum_{\substack{j ~:~  1 \le j \le m \\ j \neq i}} \left( T_s(1 - \ip{v_j}{x}) \right)^r \\
-& \le m + \frac{1}{2} - 2m + (m - 1) \\
-& \le - \frac{1}{2} \; .
+p(x) & = m + \frac{1}{2} - \left( T_s(1 - \ip{v_i}{x}) \right)^r - \sum_{\substack{j ~:~  1 \le j \le m \\ j \neq i}} \left( T_s(1 - \ip{v_j}{x}) \right)^r \\
+& \le m + \frac{1}{2} - 2m + (m - 1) \le - \frac{1}{2} \; .
 \end{align*}
@@
 \begin{enumerate}
-\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$ \\
-for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
+\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
 
-\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$ \\
-for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$,
+\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$,
 
@@
 \begin{align*}
-P_n(z) & = (z - 1) \prod_{i=1}^n (z - 2^i)^2 && \text{for $n \ge 0$,} \\
-A_{n,k}(z) & = (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$,} \\
-B_{n,k}(z) & = - (P_n(z))^k - (P_n(-z))^k && \text{for $n,k \ge 0$.}
+P_n(z) & = (z - 1) \prod_{i=1}^n (z - 2^i)^2, \quad \text{for $n \ge 0$,} \\
+A_{n,k}(z) & = (P_n(z))^k - (P_n(-z))^k,  \quad \text{for $n,k \ge 0$,} \\
+B_{n,k}(z) & = - (P_n(z))^k - (P_n(-z))^k,  \quad \text{for $n,k \ge 0$.}
 \end{align*}
 We define the polynomial $p:\R^d \to \R$ as
-\begin{multline*}
-p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right] \\
+\[
+p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
 - \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-\end{multline*}
+\]
 
@@
 \begin{align*}
-S_{n,k}(z) & = \frac{A_{n,k}(z)}{B_{n,k}(z)} && \text{for $n,k \ge 0$,}
+S_{n,k}(z) & = \frac{A_{n,k}(z)}{B_{n,k}(z)}, \quad \text{for $n,k \ge 0$,}
 \end{align*}
@@
 \begin{enumerate}
-\item $Q(x) \ge \frac{1}{2}$ \\ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
-\item $Q(x) \le -\frac{1}{2}$ \\ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
+\item $Q(x) \ge \frac{1}{2}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
+\item $Q(x) \le -\frac{1}{2}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
 \end{enumerate}
@@
 & = \left( \sum_{i=1}^m S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
-& = S_{s,r}\left( \frac{\ip{v_j}{x}}{\gamma} \right) + \left( \sum_{\substack{i ~:~ 1 \le i \le m \\ i \neq j}} S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right)  \\
-& \qquad - \left(m - \frac{1}{2} \right) \\
+& = S_{s,r}\left( \frac{\ip{v_j}{x}}{\gamma} \right) + \left( \sum_{\substack{i ~:~ 1 \le i \le m \\ i \neq j}} S_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \right) - \left(m - \frac{1}{2} \right) \\
 & \le -1 + (m-1) \left( 1 + \frac{1}{2m} \right) - \left(m - \frac{1}{2} \right) \\
@@
 Note that
-\begin{multline*}
-p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right]  \\
-- \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
-\end{multline*}
+\[
+p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
+\]
 We bound the norms of these polynomials. We have
@@
 \begin{align*}
-& \norm{p} \\
+\norm{p} 
 & \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\

### 2019-05-03 ICML-camera-ready/mistake-lower-bound-for-ignorant-algorithms.tex
add camera-ready folder

--- 2019-02-06 arxiv/mistake-lower-bound-for-ignorant-algorithms.tex
@@
 with probability at least $q_0$. Thus,
-$$
+\begin{equation}
 \Exp\left[\sum_{t=1}^{\tau - 1} \indicator{\widehat y_t\neq y_t}\right] = q_0 \Exp[(\tau - 1)] \; .
-$$
+\label{eqn:err-phase1}
+\end{equation}
 In rounds $\tau, \tau+1, \dots, T$, all the examples are the same and are equal
@@
 Therefore,
-$$
+\begin{equation}
 \Exp\left[\sum_{t=\tau}^T \indicator{\widehat y_t\neq y_t}\right] \ge \Exp[s-\tau].
-$$
+\label{eqn:err-phase2}
+\end{equation}
 %Since the algorithm is ignorant, conditioned on $\tau$, $s-\tau+1$ has the same distribution as
@@
 %$p_\tau(2|v_\tau)$.
-Since the algorithm is ignorant, conditiond on $\tau$, $s-\tau$ follows a truncated 
-geometric distribution with parameter $q\triangleq p_\tau(2|v_\tau)$
-(i.e., $s-\tau$ is $0$ with probability $q$, $1$ with probability $(1-q)q$, $2$ with probability $(1-q)^2q, \ldots$). Its expectation can be calculated as follows: 
+Since the algorithm is ignorant, conditioned on $\tau$ and $q \triangleq p_\tau(2|v_\tau)$, $s-\tau$ follows a truncated geometric distribution with parameter $q$
+(i.e., $s-\tau$ is $0$ with probability $q$, $1$ with probability $(1-q)q$, $2$ with probability $(1-q)^2q, \ldots$). Its conditional expectation can be calculated as follows:
 \begin{align*}
-\Exp[s-\tau~|~\tau] 
-&= \sum_{i=1}^{T+1-\tau} i\times  \Pr[s-\tau=i]= \sum_{i=1}^{T+1-\tau}\sum_{j=1}^i \Pr[s-\tau=i] = \sum_{j=1}^{T+1-\tau}\sum_{i=j}^{T+1-\tau} \Pr[s-\tau=i] \\
-&= \sum_{j=1}^{T+1-\tau}\Pr[s-\tau\geq j] = \sum_{j=1}^{T+1-\tau}(1-q)^j \geq  \sum_{j=1}^{T+1-\tau}(1-q_0)^j = \frac{1-q_0}{q_0}\left( 1-(1-q_0)^{T-\tau+1} \right). 
+\Exp[s-\tau~|~\tau, q]
+&= \sum_{i=1}^{T+1-\tau} i \times \Pr[s-\tau = i |~\tau, q ] \\
+&= \sum_{j=1}^{T+1-\tau}\Pr[s-\tau\geq j | ~\tau, q] = \sum_{j=1}^{T+1-\tau}(1-q)^j \geq  \sum_{j=1}^{T+1-\tau}(1-q_0)^j = \frac{1-q_0}{q_0}\left( 1-(1-q_0)^{T-\tau+1} \right).
 \end{align*}
+
+Therefore, by the tower property of conditional expectation,
+\[ \Exp[s-\tau~|~\tau] = \Exp\left[ \Exp\left[s-\tau~\middle|~\tau, q\right]~ \middle| ~\tau\right] \geq \frac{1-q_0}{q_0}\left( 1-(1-q_0)^{T-\tau+1}\right). \]
+
+%= \sum_{i=1}^{T+1-\tau}\sum_{j=1}^i \Pr[s-\tau=i] = \sum_{j=1}^{T+1-\tau}\sum_{i=j}^{T+1-\tau} \Pr[s-\tau=i] \\
 %By Lemma~\ref{lem:truncated-geom} below,
@@
 
-Combining the two, we have that
+Combining this fact with Equations~\eqref{eqn:err-phase1} and~\eqref{eqn:err-phase2}, we have that
 \begin{align*}
@@
 & \ge q_0 \Exp[\tau - 1] + \Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right)\right] \\
-& =  \Exp \left[ \Exp \left[ q_0 (\tau - 1) + \frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \right] \; .
+& =  \Exp \left[  q_0 (\tau - 1) + \frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right)  \right] \; .
 \end{align*}
+
+%\Exp \left[~\middle|~ \tau \right]
+
 We lower bound the last expression by considering two cases for $\tau$.

### 2019-05-03 ICML-camera-ready/notions-of-linear-separability.tex
add camera-ready folder

--- 2019-01-23 ICML-submission/notions-of-linear-separability.tex
@@
 first notion is the standard notion of linear separability used in the proof of
-the mistake bound for the \textsc{Multiclass Perceptron} algorithm. The second
+the mistake bound for the \textsc{Multiclass Perceptron} algorithm \citep[see e.g.][]{Crammer-Singer-2003}. The second
 notion is stronger, i.e. more restrictive. %However, it is more suitable for the
@@
 & \begin{gathered}
-\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
+\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad
 \ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; ,
@@
 \label{equation:strong-linear-separability-2}
-& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \gamma/2 \; , \\
+& \forall t \in \{1,2,\dots,T\} \qquad \ip{x_t}{w_{y_t}} \ge \gamma/2 \; , \\
 \label{equation:strong-linear-separability-3}
 & \begin{gathered}
-\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
+\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\}, \qquad
 \ip{x_t}{w_i} \le - \gamma/2 \; .
@@
 The notion of strong linear separability has appeared in the literature; see
-e.g.~\citet{Chen-Chen-Zhang-Chen-Zhang-2009}. Intuitively, strong linear
+e.g.~\citep{Chen-Chen-Zhang-Chen-Zhang-2009}. Intuitively, strong linear
 separability means that, for each class $i$, the set of examples belonging to

### 2019-05-03 ICML-camera-ready/related-work.tex
add camera-ready folder

--- 2019-02-05 arxiv/related-work.tex
@@
 take a step towards answering this question, showing that efficient algorithms
-with mistake bounds quasipolynomial in $1/\gamma$ (for constant $K$) or
+with mistake bounds quasipolynomial in $1/\gamma$ (for constant $K$) and
 quasipolynomial in $K$ (for constant $\gamma$) can be obtained.

### 2019-05-03 ICML-camera-ready/from-weak-separability-to-strong-separability.tex
fix some formatting issues

--- 2019-02-05 arxiv/from-weak-separability-to-strong-separability.tex
@@
 product $\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. If we index the
-coordinates of $\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of
+coordinates of $\ell_2$ by $d$-tuples $(\alpha_1, \dots, \alpha_d)$ of
 non-negative integers, the feature map that corresponds to $k$ is $\phi: \B(\zero,1)
@@
 \begin{align}
-& \left(\phi(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \nonumber \\
-& \qquad \cdot \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
+& \left(\phi(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \dots, \alpha_d)} \nonumber \\ 
+&= x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \cdot \sqrt{2^{-(\alpha_1 + \dots + \alpha_d)} \binom{\alpha_1 + \dots + \alpha_d}{\alpha_1,  \dots, \alpha_d}}
 \label{equation:phi}
 \end{align}
-where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots,
-\alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2!
-\dots \alpha_d!}$ is the multinomial coefficient. It can be easily checked that
+where $\binom{\alpha_1 + \dots + \alpha_d}{\alpha_1, \dots,
+\alpha_d} = \frac{(\alpha_1 + \dots + \alpha_d)!}{\alpha_1! \dots \alpha_d!}$ is the multinomial coefficient. It can be easily checked that
 $$
@@
   }
-}{2\sqrt{K}},
-\\
+}{2\sqrt{K}}, \\
 \gamma_2 = & \frac{
@@
 & \begin{gathered}
-\forall t \in \cbr{1,2,\dots,T} \ \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t} \\
+\forall t \in \cbr{1,2,\dots,T} \ \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t}, \\
 p_i(x_t) \le - \frac{\gamma'}{2} \; .
@@
 p(x)
-& = p(x_1, x_2, \dots, x_d) \\
-& = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
+&= p(x_1, x_2, \dots, x_d) \\
+&= \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
 \end{align*}
@@
 \begin{enumerate}
-\item $p(x) \ge 1/2$ \\ for all $\displaystyle x \in R^+ = \bigcap_{i=1}^m \left\{ x \in \B(\zero,1) ~:~  \ip{v_i}{x} \ge \gamma \right\}$,
-\item $p(x) \le -1/2$ \\ for all $\displaystyle x \in R^- = \bigcup_{i=1}^m \left\{ x \in \B(\zero,1) ~:~  \ip{v_i}{x} \le - \gamma \right\}$,
+\item $p(x) \ge 1/2$ for all $\displaystyle x \in R^+ = \bigcap_{i=1}^m \left\{ x \in \B(\zero,1) ~:~  \ip{v_i}{x} \ge \gamma \right\}$,
+\item $p(x) \le -1/2$ for all $\displaystyle x \in R^- = \bigcup_{i=1}^m \left\{ x \in \B(\zero,1) ~:~  \ip{v_i}{x} \le - \gamma \right\}$,
 \item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{{1}/{\gamma}} \right\rceil$,
@@
 \begin{enumerate}
-\item $\displaystyle p(x) \ge 1/2$ \\
+\item $\displaystyle p(x) \ge 1/2$
 for all $\displaystyle x \in R^+ = \bigcap_{i=1}^m \left\{ x \in \B(\zero,1) ~:~ \ip{v_i}{x} \ge \gamma \right\}$,
 
-\item $\displaystyle p(x) \le - 1/2$ \\
+\item $\displaystyle p(x) \le - 1/2$
 for all $\displaystyle x \in R^- = \bigcup_{i=1}^m \left\{ x \in \B(\zero,1) ~:~ \ip{v_i}{x} \le - \gamma \right\}$,

### 2019-05-03 ICML-camera-ready/appendix-experiment.tex
entomological changes; reviews; some formatting issues fixed

@@
 
-We plot in
-Figures~\ref{fig:banditron-points},~\ref{fig:linearova-points},~\ref{fig:rationalova-points}
-the final decision boundaries learned by each algorithm in the two datasets (Figures~\ref{figure:number-of-mistakes-strongly-separable-dataset}
-and~\ref{figure:number-of-mistakes-weakly-separable-dataset}), i.e. its decision boundaries
-output at the end of round $T = 5 \times 10^6$.
+Figures~\ref{fig:banditron-points},~\ref{fig:linearova-points}, and~\ref{fig:rationalova-points} show the final decision boundaries learned by each algorithm on the two datasets (Figures~\ref{figure:number-of-mistakes-strongly-separable-dataset} and~\ref{figure:number-of-mistakes-weakly-separable-dataset}),
+after $T = 5 \times 10^6$ rounds. We used the version of Banditron
+with exploration rate of 0.02, which explores the most.
 

### 2019-05-03 ICML-camera-ready/empirical-comparison.tex
add camera-ready folder
entomological changes; reviews; some formatting issues fixed

--- 2019-02-05 arxiv/empirical-comparison.tex
@@
 kernel~\eqref{equation:rational-kernel} and used implementation of
-\textsc{Banditron} algorithm by \citet{Orabona09}.\footnote{The source code
-is included in the supplementary material.}
+\textsc{Banditron} algorithm by \citet{Orabona09}.%\footnote{The source code
+%is included in the supplementary material.}
 We evaluated these algorithms on the two datasets. \textsc{Banditron} has an
@@
 
-\begin{figure}
+\begin{minipage}{.45\textwidth}
+\begin{figure}[H]
 \centering
-\includegraphics[width=0.42\textwidth]{figures/strong3}
-\caption{Average cumulative number of mistakes of various algorithms versus the
-number of rounds for the strongly linearly separable dataset of
+\includegraphics[width=0.98\textwidth]{figures/strong3}
+\caption{The average cumulative number of mistakes versus the
+number of rounds on the strongly linearly separable dataset in
 \autoref{figure:strongly-separable-dataset}.}
@@
 \end{figure}
-
-\begin{figure}
+\end{minipage}
+\hfill
+\begin{minipage}{.45\textwidth}
+\begin{figure}[H]
 \centering
-\includegraphics[width=0.42\textwidth]{figures/weak3}
-\caption{Average cumulative number of mistakes of various algorithms versus the
-number of rounds for the weakly linearly separable dataset of
+\includegraphics[width=0.98\textwidth]{figures/weak3}
+\caption{The average cumulative number of mistakes versus the
+number of rounds on the weakly linearly separable dataset in
 \autoref{figure:weakly-separable-dataset}.}

### 2019-05-03 ICML-camera-ready/from-weak-separability-to-strong-separability.tex
entomological changes; reviews; some formatting issues fixed

@@
 We use a positive definite kernel function $k(\cdot, \cdot)$, namely
-\emph{rational kernel}~\citep{Shalev-Shwartz-Shamir-Sridharan-2011}, whose
+a \emph{rational kernel}~\citep{Shalev-Shwartz-Shamir-Sridharan-2011} whose
 corresponding feature map $\phi(\cdot)$ transforms any sequence of \emph{weakly}
-linearly separable examples to \emph{strongly} linearly separable sequence of
+linearly separable examples to a \emph{strongly} linearly separable sequence of
 examples.
@@
 product $\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. If we index the
-coordinates of $\ell_2$ by $d$-tuples $(\alpha_1, \dots, \alpha_d)$ of
+coordinates of $\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of
 non-negative integers, the feature map that corresponds to $k$ is $\phi: \B(\zero,1)
@@
 \begin{align}
-& \left(\phi(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \dots, \alpha_d)} \nonumber \\ 
-&= x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \cdot \sqrt{2^{-(\alpha_1 + \dots + \alpha_d)} \binom{\alpha_1 + \dots + \alpha_d}{\alpha_1,  \dots, \alpha_d}}
+\begin{split}
+&\left(\phi(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = \\
+& x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \cdot \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
+\end{split}
 \label{equation:phi}
 \end{align}
-where $\binom{\alpha_1 + \dots + \alpha_d}{\alpha_1, \dots,
-\alpha_d} = \frac{(\alpha_1 + \dots + \alpha_d)!}{\alpha_1! \dots \alpha_d!}$ is the multinomial coefficient. It can be easily checked that
+where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots,
+\alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2!
+\dots \alpha_d!}$ is the multinomial coefficient. It can be easily checked that
 $$
@@
 \label{theorem:margin-transformation}
-Let $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ in $\B(\zero,1) \times
+Let $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ $\in \B(\zero,1) \times
 \{1,2,\dots,K\}$ be a sequence of labeled examples that is weakly linearly
@@
   }
-}{2\sqrt{K}}, \\
+}{2\sqrt{K}},\\
 \gamma_2 = & \frac{
@@
 & \begin{gathered}
-\forall t \in \cbr{1,2,\dots,T} \ \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t}, \\
+\forall t \in \cbr{1,2,\dots,T} \ \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t}, \qquad
 p_i(x_t) \le - \frac{\gamma'}{2} \; .
@@
 expressed as $\ip{c_i}{\phi(x)}_{\ell_2}$ for some $c_i \in \ell_2$. This
-immediately implies that that the examples $(\phi(x_1),y_1), \ldots,
+immediately implies that the examples $(\phi(x_1),y_1), \ldots,
 (\phi(x_T),y_T)$ are strongly linearly separable with a positive margin.
@@
 p(x)
-&= p(x_1, x_2, \dots, x_d) \\
-&= \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
+ = p(x_1, x_2, \dots, x_d) = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
 \end{align*}

### 2019-05-03 ICML-camera-ready/introduction.tex
entomological changes; reviews; some formatting issues fixed

--- 2019-02-05 arxiv/introduction.tex
@@
 
-The bandit feedback setting, however, is much more challenging. For the case
-when the examples are strongly linearly separable, to the best of our knowledge,
-it is not known how to design an efficient algorithm with a finite mistake bound
-before our work.~\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
+The bandit feedback setting, however, is much more challenging. For the 
+strongly linearly separable case, we are not aware of any 
+prior efficient algorithm with a finite mistake bound.
+~\footnote{Although~\citet{Chen-Chen-Zhang-Chen-Zhang-2009}
 claimed that their Conservative OVA algorithm with PA-I update has a finite

### 2019-05-03 ICML-camera-ready/mistake-lower-bound-for-ignorant-algorithms.tex
entomological changes; reviews; some formatting issues fixed

@@
 Then, as $\calA$ is ignorant,
-\[
-\Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] =
-\Pr[y_t' = y ~|~ (x_1', y_1'), (x_2', y_2') \dots, (x_{t-1}', y_{t-1}'), x_t' = x] \; .
-\]
+\begin{align*}
+\Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] = \\
+\Pr[y_t' = y ~|~ (x_1', y_1'), (x_2', y_2') \dots, (x_{t-1}', y_{t-1}'), x_t' = x].
+\end{align*}
 Note that the sequences $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_{t-1},
@@
 &= \sum_{i=1}^{T+1-\tau} i \times \Pr[s-\tau = i |~\tau, q ] \\
-&= \sum_{j=1}^{T+1-\tau}\Pr[s-\tau\geq j | ~\tau, q] = \sum_{j=1}^{T+1-\tau}(1-q)^j \geq  \sum_{j=1}^{T+1-\tau}(1-q_0)^j = \frac{1-q_0}{q_0}\left( 1-(1-q_0)^{T-\tau+1} \right).
+&= \sum_{j=1}^{T+1-\tau}\Pr[s-\tau\geq j | ~\tau, q] \\
+& = \sum_{j=1}^{T+1-\tau}(1-q)^j \geq  \sum_{j=1}^{T+1-\tau}(1-q_0)^j \\
+& = \frac{1-q_0}{q_0}\left( 1-(1-q_0)^{T-\tau+1} \right).
 \end{align*}

### 2019-05-03 ICML-camera-ready/notions-of-linear-separability.tex
fix some formatting issues
entomological changes; reviews; some formatting issues fixed

@@
 \label{section:notions-of-linear-separability}
-
+Let $[n]=\{1,2,\ldots,n\}$.
 We define two notions of linear separability for multiclass classification. The
@@
 We say that labeled examples $(x_1, y_1),
-(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are
-%said to be
-\begin{enumerate}
-\item
+(x_2, y_2), \dots, (x_T, y_T) \in V \times [K]$ are
+\\ \vskip .01in
 \emph{weakly linearly separable with a margin $\gamma$} if there exist vectors
@@
 \label{equation:weak-linear-separability-1}
-& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
+\sum_{i=1}^K \norm{w_i}^2 & \le 1, \\
 \label{equation:weak-linear-separability-2}
-& \begin{gathered}
-\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad
-\ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; ,
-\end{gathered}
+\ip{x_t}{w_{y_t}} & \ge \ip{x_t}{w_i} + \gamma \quad
+\forall t \in [T]\ \forall i \in [K] \setminus \{y_t\}, 
 \end{align}
-\item
-\emph{strongly linearly separable with a margin $\gamma$} if there exist vectors
+
+and \emph{strongly linearly separable with a margin $\gamma$} if there exist vectors
 $w_1, w_2, \dots, w_K \in V$ such that
@@
 \label{equation:strong-linear-separability-1}
-& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
+\sum_{i=1}^K \norm{w_i}^2 & \le 1, \\
 \label{equation:strong-linear-separability-2}
-& \forall t \in \{1,2,\dots,T\} \qquad \ip{x_t}{w_{y_t}} \ge \gamma/2 \; , \\
+\ip{x_t}{w_{y_t}} & \ge \gamma/2 \quad  \forall t \in [T], \\
 \label{equation:strong-linear-separability-3}
-& \begin{gathered}
-\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\}, \qquad
-\ip{x_t}{w_i} \le - \gamma/2 \; .
-\end{gathered}
+\ip{x_t}{w_i} & \le - \gamma/2 \quad
+\forall t \in [T]\ \forall i \in [K] \setminus \{y_t\}.
 \end{align}
-\end{enumerate}
 \end{definition}

### 2019-05-03 ICML-camera-ready/from-weak-separability-to-strong-separability.tex

@@
 \end{align}
-where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots,
-\alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2!
-\dots \alpha_d!}$ is the multinomial coefficient. It can be easily checked that
+where $\binom{\alpha_1 + \dots + \alpha_d}{\alpha_1, \dots,
+\alpha_d} = \frac{(\alpha_1 + \dots + \alpha_d)!}{\alpha_1! \dots \alpha_d!}$ is the multinomial coefficient. It can be easily checked that
 $$
@@
 & \begin{gathered}
-\forall t \in \cbr{1,2,\dots,T} \ \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t}, \qquad
+\forall t \in \cbr{1,2,\dots,T} \ \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t}, \\
 p_i(x_t) \le - \frac{\gamma'}{2} \; .
@@
 p(x)
- = p(x_1, x_2, \dots, x_d) = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
+&= p(x_1, x_2, \dots, x_d) \\
+&= \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
 \end{align*}

### 2019-05-08 ICML-camera-ready/appendix-proofs-of-polynomial-approximation-theorems.tex
pushed the scaling into the proof of Theorem 8

@@
-\section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
+\section{Proofs of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
 \label{section:proof-of-polynomial-approximation}
@@
 \item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then,
+$\norm{\sum_{j=1}^n p_j} \le \sum_{j=1}^n \norm{p_j}$.
+Consequently,
 $\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
@@
 
-To prove part 3, we use generalized triangle inequality and
-\autoref{lemma:simple-inequality}. We have
+The first inequality of part 3 follows from triangle inequality in Euclidean spaces, by viewing the polynomials
+$p = \sum_{A} c_A x^A$ as multidimensional vectors $(c_A)$, and $\| p \| = \| (c_A) \|$.
+
+For the second inequality, by~\autoref{lemma:simple-inequality}, we have
 \[
@@
 
-We prove the following lemma in this section.
-\autoref{theorem:polynomial-approximation-2} immediately
-follows from this lemma by considering $p' = p \cdot 2^{-s(s+1)rm+1}$
-and algebra.
+%We prove the following lemma in this section.
+%\autoref{theorem:polynomial-approximation-2} immediately
+%follows from this lemma by considering $p' = p \cdot 2^{-s(s+1)rm+1}$
+%and algebra.
 
-\begin{lemma}
-\label{lemma:polynomial-approximation-2}
-Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
-\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$.
-Define
-$$
-r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(1/\gamma) \right \rceil \; .
-$$
-Then, there exists a multivariate polynomial $p:\R^d \to \R$ such that
-\begin{enumerate}
-\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
+%\begin{lemma}
+%\label{lemma:polynomial-approximation-2}
+%Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
+%\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$.
+%Define
+%$$
+%r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(1/\gamma) \right \rceil \; .
+%$$
+%Then, there exists a multivariate polynomial $p:\R^d \to \R$ such that
+%\begin{enumerate}
+%\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
 
-\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$,
+%\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$,
 
-\item $\deg(p) \le (2s+1) rm$,
-\item $\norm{p} \le (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm}$.
-\end{enumerate}
-\end{lemma}
+%\item $\deg(p) \le (2s+1) rm$,
+%\item $\norm{p} \le (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm}$.
+%\end{enumerate}
+%\end{lemma}
 
@@
 \end{align*}
-We define the polynomial $p:\R^d \to \R$ as
+We define the polynomial $p':\R^d \to \R$ as
 \[
-p(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
+p'(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
 - \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
 \]
+Finally, we define the polynomial $p := 2^{-s(s+1)rm+1} \cdot p'$. We are going to show
+that this polynomial $p$ satisfies the required properties.
 
@@
 $$
-p(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
+p'(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
 $$
@@
 
-To prove parts 1 and 2 of \autoref{lemma:polynomial-approximation-2} first
+To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-2} first
 note that part 4 of \autoref{lemma:properties-of-s-n-r} implies that for any $x$
@@
 |p(x)|
-& = |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
-& \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
-& \ge \frac{1}{2} |Q(x)| \cdot 2^{s(s+1)rm} \\
-& \ge \frac{1}{4} \cdot 2^{s(s+1)rm} \quad \text{(\autoref{lemma:properties-of-q})} \; .
+& = 2^{-s(s+1)rm+1} \cdot |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
+& \ge 2^{-s(s+1)rm+1} \cdot |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
+& \ge |Q(x)| \ge \frac{1}{2} \quad \text{(\autoref{lemma:properties-of-q})} \; .
 \end{align*}
@@
 
-To prove part 3 of \autoref{lemma:polynomial-approximation-2} note that
+To prove part 3 of \autoref{theorem:polynomial-approximation-2} note that
 $\deg(P_s) = 2s+1$. Thus, $\deg(A_{s,r})$ and $\deg(B_{s,r})$ are at most
@@
 
-It remains to prove part 4 of \autoref{lemma:polynomial-approximation-2}.
+It remains to prove part 4 of \autoref{theorem:polynomial-approximation-2}.
 For any $i \in \{0,1,2,\dots,s\}$ and any $v \in \R^d$ such that $\norm{v} \le 1$
@@
 \[
-p(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
+p'(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
 \]
@@
 \end{align*}
-The same upper bound holds for $\norm{b_v}^2$. Finally,
+The same upper bound holds for $\norm{b_v}^2$. Therefore,
 \begin{align*}
-\norm{p} 
+\norm{p'}
 & \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
@@
 \end{align*}
+Finally,
+$\norm{p} = 2^{-s(s+1)rm+1} \norm{p'} \leq (4m-1) 2^m \cdot \left(2^s rm (4s+2) \right)^{(s+1/2)rm}$. The theorem follows.

### 2019-05-08 ICML-camera-ready/from-weak-separability-to-strong-separability.tex
some formatting issue
pushed the scaling into the proof of Theorem 8

--- 2019-05-03 ICML-camera-ready/from-weak-separability-to-strong-separability.tex
@@
 where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots,
-\alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2!
-\dots \alpha_d!}$ is the multinomial coefficient. It can be easily checked that
+\alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$ is the multinomial coefficient. It can be easily checked that
 $$
@@
 Theorems~\ref{theorem:kernelized-upper-bound}
-and~\ref{theorem:margin-transformation}.
+and~\ref{theorem:margin-transformation}. We remark that under the weakly linearly
+separable setting,~\citep{Daniely-Helbertal-2013} gives a mistake lower bound of
+$\Omega(\frac{K}{\gamma^2})$ for {\em any algorithm} (see also~\autoref{theorem:strongly-separable-examples-mistake-lower-bound}).
+We leave the possibility of designing efficient algorithms that
+have mistakes bounds matching this lower bound as an important open question.
 

### 2019-05-08 ICML-camera-ready/introduction.tex
pushed the scaling into the proof of Theorem 8

@@
 \textsc{Multiclass Perceptron} achieves an information-theoretically optimal
-mistake bound, while being time and memory efficient.~\footnote{For
+mistake bound, while being time and memory efficient.\footnote{We call an algorithm
+ computationally efficient, if its running time is polynomial in $K$, $d$, $1/\gamma$
+ and $T$.}
+\footnote{For
 completeness, we present these folklore results along with their proofs in

### 2019-05-08 ICML-camera-ready/main-all.tex
add camera-ready folder
pushed the scaling into the proof of Theorem 8

--- 2019-01-17 ICML-submission/main-all.tex
@@
 \input{from-weak-separability-to-strong-separability}
+\input{empirical-comparison}
 
 \bibliography{biblio}
+%\bibliographystyle{plainnat}
 \bibliographystyle{icml2019}
@@
 % Use appendices only in supplementray material.
+\onecolumn
 \appendix
@@
 
+\section*{Acknowledgments} We thank Francesco Orabona and Wen Sun
+for helpful initial discussions, and thank Adam Klivans and Rocco Servedio for helpful
+discussions on~\citep{Klivans-Servedio-2008} and
+pointing out the reference~\citep{Klivans-Servedio-2004}.
+
 \input{appendix-multiclass-perceptron}
 \input{appendix-proofs-for-strongly-separable-examples}
-\input{appendix-margin-transformation}
 \input{appendix-poly-norm-to-rkhs-norm}
 \input{appendix-proofs-of-polynomial-approximation-theorems}
+\input{appendix-margin-transformation}
+\input{appendix-experiment}
+\input{appendix-nearest-neighbor-algorithm}
 \input{np-hardness-of-the-weak-labeling-problem}
+\input{mistake-lower-bound-for-ignorant-algorithms}
 

### 2019-05-08 ICML-camera-ready/title-and-abstract.tex
add camera-ready folder
entomological changes; reviews; some formatting issues fixed
pushed the scaling into the proof of Theorem 8

--- 2019-02-05 ICML-submission/title-and-abstract.tex
@@
 % Therefore, a short form for the running title is supplied here:
+%\icmltitlerunning{Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case}
+
+%\twocolumn[
+%\icmltitle{Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case}
+
 \icmltitlerunning{Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case}
@@
 \begin{icmlauthorlist}
-\icmlauthor{Alina Beygelzimer}{yahoo}
 \icmlauthor{D\'avid P\'al}{yahoo}
@@
 \icmlauthor{Chicheng Zhang}{microsoft}
+\icmlauthor{Alina Beygelzimer}{yahoo}
 
@@
 \icmlaffiliation{yahoo}{Yahoo Research, New York, NY, USA}
-\icmlaffiliation{nyu}{New York University, New York, MA, USA}
+\icmlaffiliation{nyu}{New York University, New York, NY, USA}
 \icmlaffiliation{usc}{University of Southern California, Los Angeles, CA, USA}
@@
 \printAffiliationsAndNotice{}
+
+%\title{Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case}
+
+%\begin{icmlauthorlist}
+%\author[1]{Alina Beygelzimer \thanks{beygel@verizonmedia.com}}
+%\author[1]{D\'avid P\'al \thanks{dpal@verizonmedia.com}}
+%\author[1]{Bal\'azs Sz\"or\'enyi \thanks{balazs.szorenyi@verizonmedia.com}}
+%\author[2]{Devanathan Thiruvenkatachari\thanks{dt1295@nyu.edu}}
+%\author[3]{Chen-Yu Wei\thanks{chenyu.wei@usc.edu}}
+%\author[4]{Chicheng Zhang\thanks{chicheng.zhang@microsoft.com}}
+
+%beygel@oath.com
+%balazs.szorenyi@oath.com
+%szorenyi.balazs@gmail.com
+%beygel@gmail.com
+%davidko.pal@gmail.com
+%\end{icmlauthorlist}
+
+%\affil[1]{Yahoo Research, New York, NY, USA}
+%\affil[2]{New York University, New York, MA, USA}
+%\affil[3]{University of Southern California, Los Angeles, CA, USA}
+%\affil[4]{Microsoft Research, New York, NY, USA}
+
+%\maketitle
+%\icmlcorrespondingauthor{D\'avid P\'al}{davidko.pal@gmail.com}
+
+%\icmlkeywords{multi-armed bandits, contextual bandits, online classification, linear separability}
+
+%\vskip 0.3in
+%]
+
+%\printAffiliationsAndNotice{}
 
@@
 an efficient algorithm with a mistake bound of $\min (2^{\widetilde{O}(K \log^2
-(1/\gamma))}, 2^{\widetilde{O}(\sqrt{1/\gamma} \log K)})$ \footnote{We use the notation
-$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}.
+(1/\gamma))}, 2^{\widetilde{O}(\sqrt{1/\gamma} \log K)})$.\footnote{We use the notation
+$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}
 Our algorithm

### 2019-05-08 ICML-camera-ready/algorithm-for-strongly-linearly-separable-data.tex
add camera-ready folder
pushed the scaling into the proof of Theorem 8
Fixes

--- 2019-01-23 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
@@
 proof of the theorem can be found in
-Appendix~\ref{section:proofs-for-stringly-separable-examples} in the
-supplementary material.
+Appendix~\ref{section:proofs-for-stringly-separable-examples}.
 
@@
 to use $K$ copies of the \textsc{Binary Perceptron} algorithm, one copy per
-class; see e.g. \citet[Section 3.3.1]{Shalev-Shwartz-2012}. Upon seeing each
+class; see e.g. \citep[Section 3.3.1]{Shalev-Shwartz-2012}. Upon seeing each
 example $x_t$, copy $i$ predicts whether or not $x_t$ belongs to class $i$.
@@
 outputting any class with a positive prediction.  If all binary predictions are
-negative, the algorithm chooses a prediction a prediction uniformly at random
-from $\cbr{1,\ldots,K}$.
+negative, the algorithm chooses a prediction uniformly at random
+from $\cbr{1,2,\dots,K}$.
 
@@
 strongly linearly separable with margin $\gamma$ and $\norm{x_1}, \norm{x_2},
-\dots, \norm{x_T} \le R$ then the expected number of mistakes
+\dots, \norm{x_T} \le R$ then the expected number of mistakes that
 Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
@@
 proof of the theorem can be found in
-Appendix~\ref{section:proofs-for-stringly-separable-examples} in the
-supplementary material. \citet{Daniely-Helbertal-2013} provide a lower bound
+Appendix~\ref{section:proofs-for-stringly-separable-examples}.
+\citet{Daniely-Helbertal-2013} provide a lower bound
 under the assumption of weak linear separability, which does not immediately
@@
 positive integer $m$ and $x_1, x_2, \dots, x_m \in X$ \citep[Definition
-2.5]{Scholkopf-Smola-2002}.\footnote{For every kernel there exists an associated feature map
-$\phi:X \to V$ into some inner product space $(V,\ip{\cdot}{\cdot})$ such that
-$k(x,x') = \ip{\phi(x)}{\phi(x')}$.} As opposed to explicitly maintaining the
-weight vector for each class, the algorithm maintains the set of example-scalar
-pairs corresponding to the updates of the non-kernelized algorithm. As a direct
-consequence of
+2.5]{Scholkopf-Smola-2002}.\footnote{For every kernel there exists an associated
+feature map $\phi:X \to V$ into some inner product space $(V,\ip{\cdot}{\cdot})$
+such that $k(x,x') = \ip{\phi(x)}{\phi(x')}$.} As opposed to explicitly
+maintaining the weight vector for each class, the algorithm maintains the set of
+example-scalar pairs corresponding to the updates of the non-kernelized
+algorithm. As a direct consequence of
 Theorem~\ref{theorem:strongly-separable-examples-mistake-upper-bound} we get a
@@
 \end{enumerate}
-then the expected number of mistakes Algorithm~\ref{algorithm:kernelized} makes
+then the expected number of mistakes that Algorithm~\ref{algorithm:kernelized} makes
 is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.

### 2019-05-08 ICML-camera-ready/appendix-proofs-of-polynomial-approximation-theorems.tex
Fixes

@@
 $$
-Cancelling common terms leads to an equivalent inequality
+We multiply out the terms and get
 $$
-k - j \le n - j \; ,
+nk - kj + k - nj + j^2 - j \le nk - nj + n - kj + j^2 - j \; .
 $$
-which since $n \ge k$ by assumption.
+We cancel common terms and get an equivalent inequality $k \ge n$, which
+holds by the assumption.
 \end{proof}
@@
 Interested reader can learn more about Chebyshev polynomials
-from the book by \cite{Mason-Handscomb-2002}.
+from the book by \citet{Mason-Handscomb-2002}.
 
@@
 $$
-Tho prove this inequality we use the summation formula
+To prove this inequality we use the summation formula
 $$
@@
 
-%We prove the following lemma in this section.
-%\autoref{theorem:polynomial-approximation-2} immediately
-%follows from this lemma by considering $p' = p \cdot 2^{-s(s+1)rm+1}$
-%and algebra.
-
-%\begin{lemma}
-%\label{lemma:polynomial-approximation-2}
-%Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
-%\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$.
-%Define
-%$$
-%r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(1/\gamma) \right \rceil \; .
-%$$
-%Then, there exists a multivariate polynomial $p:\R^d \to \R$ such that
-%\begin{enumerate}
-%\item $\displaystyle p(x) \ge \frac{1}{4} \cdot 2^{s(s+1)rm}$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$,
-
-%\item $\displaystyle p(x) \le - \frac{1}{4} \cdot 2^{s(s+1)rm}$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$,
-
-%\item $\deg(p) \le (2s+1) rm$,
-%\item $\norm{p} \le (2m-1/2) 2^m \cdot \left(2^{2s} rm (4s+2)^2 \right)^{(s+1/2)rm}$.
-%\end{enumerate}
-%\end{lemma}
-
 We define several univariate polynomials
@@
 \end{align*}
-We define the polynomial $p':\R^d \to \R$ as
-\[
-p'(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
+We define the polynomial $q:\R^d \to \R$ as
+$$
+q(x) = \left[ \sum_{i=1}^m A_{s,r}\left( \frac{\ip{v_i}{x}}{\gamma} \right) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \right]
 - \left(m - \frac{1}{2} \right) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
-\]
-Finally, we define the polynomial $p := 2^{-s(s+1)rm+1} \cdot p'$. We are going to show
+$$
+Finally, we define $p(x) = 2^{-s(s+1)rm+1} q(x)$. We are going to show
 that this polynomial $p$ satisfies the required properties.
@@
 $$
-p'(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
+q(x) = Q(x) \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \; .
 $$
@@
 \{1,2,\dots,n\}$ be such that $2^{j-1} \le z \le 2^j$. This implies that
-$(z+2^{j})^2 \ge (2^j)^2 \ge 4 (z - 2^j)^2$. We can write $\frac{P_n(z)}{-P_n(-z)}$ as a
-product of $n+1$ non-negative fractions
+$(z+2^{j})^2 \ge (2^j)^2 \ge 4 (z - 2^j)^2$. We can write
+$\frac{P_n(z)}{-P_n(-z)}$ as a product of $n+1$ non-negative fractions
 $$
@@
 \item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
-\item If $z \in [-2^n,2^n]$ then \\ $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
+\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
 \end{enumerate}
@@
 $S_{n,r}(z)$ is odd, for $z \in [-1,0]$, $S_{n,r}(z) \in [-1,0]$.
-
-%\frac{\displaystyle 1 + \left( - \frac{P_n(z)}{P_n(-z)}\right)^r}{\displaystyle 1 - \left( - \frac{P_n(z)}{P_n(-z)}\right)^r} =
 
@@
 Note that
-\[
-p'(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
-\]
+$$
+q(x) = \left[ \sum_{i=1}^m a_{v_i}(x) \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}(x) \right] - \left(m - \frac{1}{2} \right) \prod_{j=1}^n b_{v_j}(x) \; .
+$$
 We bound the norms of these polynomials. We have
@@
 \begin{align*}
-\norm{p'}
+\norm{q}
 & \le \left[ \sum_{i=1}^m \norm{a_{v_i} \prod_{\substack{j ~:~ 1 \le j \le m \\ j \neq i}} b_{v_j}} \right] + \left(m - \frac{1}{2} \right) \norm{\prod_{j=1}^m b_{v_j}} \\
@@
 Finally,
-$\norm{p} = 2^{-s(s+1)rm+1} \norm{p'} \leq (4m-1) 2^m \cdot \left(2^s rm (4s+2) \right)^{(s+1/2)rm}$. The theorem follows.
+$\norm{p} = 2^{-s(s+1)rm+1} \norm{q} \leq (4m-1) 2^m \cdot \left(2^s rm (4s+2) \right)^{(s+1/2)rm}$. The theorem follows.

### 2019-05-08 ICML-camera-ready/mistake-lower-bound-for-ignorant-algorithms.tex
Fixes

@@
 \[
-p_t(y|x) = \\
+p_t(y|x) =
 \Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] \; .
@@
 on a sequence of examples $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_{t-1}, y_{t-1})$
-generated by some adversary the algorthm $\calA$ makes correct predictions in
+generated by some adversary the algorithm $\calA$ makes correct predictions in
 rounds $a_1, a_2, \dots, a_n$ where $1 \le a_1 < a_2 < \dots < a_n < t$ and
@@
 Then, as $\calA$ is ignorant,
-\begin{align*}
-\Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] = \\
+$$
+\Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] =
 \Pr[y_t' = y ~|~ (x_1', y_1'), (x_2', y_2') \dots, (x_{t-1}', y_{t-1}'), x_t' = x].
-\end{align*}
+$$
 Note that the sequences $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_{t-1},

### 2019-05-08 ICML-camera-ready/np-hardness-of-the-weak-labeling-problem.tex
entomological changes; reviews; some formatting issues fixed
Fixes

--- 2019-02-06 arxiv/np-hardness-of-the-weak-labeling-problem.tex
@@
 
-We use symbols $1,2,\dots,K$ for strong labels and symbols $\overline{1},
-\overline{2}, \dots, \overline{K}$ for weak labels. Formally, the weak
+We use symbols $[K]=\{1,2,\dots,K\}$ for strong labels and $[\overline{K}]
+=\{\overline{1},
+\overline{2}, \dots, \overline{K}\}$ for weak labels. Formally, the weak
 labeling problem can be described as below:
@@
 \begin{align*}
-& y_t \in \{1,2,\dots,K\} \Longrightarrow \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \quad \ip{w_{y_t}}{x_t}  > \ip{w_i}{x_t} \; , \\
+& y_t \in [K] \Longrightarrow \forall i \in [K] \setminus \{y_t\} \quad \ip{w_{y_t}}{x_t}  > \ip{w_i}{x_t} \; , \\
 & \text{and} \\
-& y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \Longrightarrow \exists i \in \{1,2,\dots,K\} \quad \ip{w_i}{x_t} > \ip{w_{\overline{y_t}}}{x_t} \; ?
+& y_t \in [\overline{K}] \Longrightarrow \exists i \in [K] \quad \ip{w_i}{x_t} > \ip{w_{\overline{y_t}}}{x_t} \; ?
 \end{align*}
@@
 Define $\zero$ as the zero vector $(0,\dots,0)\in \R^N$ and $\e_i$ as the
-$i$-th standard vector $(0,\dots, 1, \dots, 0)\in \R^N$). Then we include all
+$i$-th standard vector $(0,\dots, 1, \dots, 0)\in \R^N$. Then we include all
 the following feature-label pairs:

### 2019-05-08 ICML-camera-ready/title-and-abstract.tex
Fixes

--- 2019-02-05 ICML-submission/title-and-abstract.tex
@@
 an efficient algorithm with a mistake bound of $\min (2^{\widetilde{O}(K \log^2
-(1/\gamma))}, 2^{\widetilde{O}(\sqrt{1/\gamma} \log K)})$ \footnote{We use the notation
-$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}.
-Our algorithm
-is based on kernel Perceptron, which is inspired by the work
-of \citet{Klivans-Servedio-2008} on improperly learning intersection of halfspaces.
-%is based on a infinite-dimensional feature mapping that transforms weakly linear
-%separable examples to strongly linear separable examples, which in turn is
-%of \citet{Shalev-Shwartz-Shamir-Sridharan-2011},
+(1/\gamma))}, 2^{\widetilde{O}(\sqrt{1/\gamma} \log K)})$.\footnote{We use the
+notation $\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.} Our
+algorithm is based on kernel Perceptron and is inspired by the work of
+\citet{Klivans-Servedio-2008} on improperly learning intersection of halfspaces.
 \end{enumerate}

### 2019-06-18 ICML-camera-ready/main-all.tex
change some figures
acknowledgement

--- 2019-01-17 ICML-submission/main-all.tex
@@
 \input{from-weak-separability-to-strong-separability}
+\input{empirical-comparison}
+
+\section*{Acknowledgments} We thank Francesco Orabona and Wen Sun
+for helpful initial discussions, and thank Adam Klivans and Rocco \mbox{Servedio} for helpful
+discussions on~\citep{Klivans-Servedio-2008} and
+pointing out the reference~\citep{Klivans-Servedio-2004}. We also thank Dylan Foster, 
+Akshay \mbox{Krishnamurthy}, and Haipeng Luo for providing a candidate solution to our problem. 
+Finally, we thank Shang-En Huang and \mbox{Mengxiao} Zhang for helpful discussions on the hardness results.
 
 \bibliography{biblio}
+%\bibliographystyle{plainnat}
 \bibliographystyle{icml2019}
@@
 \input{appendix-proofs-for-strongly-separable-examples}
-\input{appendix-margin-transformation}
 \input{appendix-poly-norm-to-rkhs-norm}
 \input{appendix-proofs-of-polynomial-approximation-theorems}
+\input{appendix-margin-transformation}
+\input{appendix-experiment}
+\input{appendix-nearest-neighbor-algorithm}
 \input{np-hardness-of-the-weak-labeling-problem}
+\input{mistake-lower-bound-for-ignorant-algorithms}
 
